% FIXME: Add an option to the main build to put these in their original positions
\chapter{Disclaimers and Epigraphs}

Included here are the disclaimers and epigraphs from the first thirty or so chapters. N.B. Chapter 11 in the original (Omake Files I–III) is Appendix B in this PDF.

{% start of spacing changes
\setlength{\parindent}{0pt}
\setlength{\parskip}{1em}

\filbreak
--- 1 ---

Disclaimer: J. K. Rowling owns Harry Potter, and no one owns the methods of rationality.

\begin{em}
Beneath the moonlight glints a tiny fragment of silver, a fraction of a line{\ldots}

(black robes, falling)

{\ldots}blood spills out in litres, and someone screams a word.
\end{em}

\filbreak
--- 2 ---

\texttt{\#include "stddisclaimer.h"}

"\emph{Of course it was my fault. There’s no one else here who could be responsible for anything.}"

\filbreak
--- 3 ---

If J. K. Rowling asks you about this story, you know nothing.

"\emph{But then the question is---who?}"

\filbreak
--- 4 ---

Disclaimer: J. K. Rowling is watching you from where she waits, eternally in the void between worlds.

"\emph{World domination is such an ugly phrase. I prefer to call it world optimisation.}"

\filbreak
--- 5 ---

J. K. Rowling is staring at you. Can you feel her eyes on you? She’s reading your mind using her Rowling Rays.

"\emph{It would’ve required a \emph{supernatural intervention} for him to have \emph{your} morality given \emph{his} environment.}"

\filbreak
--- 6 ---

Blah blah disclaimer blah blah Rowling blah blah ownership.

\emph{You think your day was surreal? Try mine.}

\filbreak
--- 7 ---

Whoa. A spokesman for Rowling’s literary agent said that Rowling is okay with the existence of fanfiction as long as no one charges for it and everyone’s clear that the original copyrights belong to her? That’s really cool of her. So thank you, JKR, and thine is the kingdom!

"\emph{Your dad is almost as awesome as my dad.}"

\filbreak
--- 8 ---

All these worlds are J. K. Rowling’s, except Europa. Attempt no fanfics there.

"\emph{Allow me to warn you that challenging my ingenuity is a dangerous sort of project, and may tend to make your life a lot more surreal.}"

\filbreak
--- 9 ---

All your base are belong to J. K. Rowling.

\emph{You never did know what tiny event might upset the course of your master plan.}

\filbreak
--- 10 ---

All your base are still belong to Rowling.

And now you will sit through the Sorting Hat singing its version of Evanescence’s “My Immortal”, which has never happened before.

just kidding

\filbreak
--- 11 ---

Hail the Dark Lord Rowling.

\filbreak
--- 12 ---

ph’nglui mglw’nafh J. K. Rowling wgah’nagl fhtagn

"\emph{Wonder what’s wrong with \emph{him}.}"

\filbreak
--- 13 ---

Elen sila J. K. Rowling omentielvo.

"\emph{That’s one of the most obvious riddles I’ve ever heard.}"

\filbreak
--- 14 ---

Melenkurion abatha! Duroc minas mill J. K. Rowling!

\emph{There were mysterious questions, but a mysterious answer was a
contradiction in terms.}

\filbreak
--- 15 ---

Love as thou Rowling.

"\emph{I’m sure I’ll find the time somewhere.}"

\filbreak
--- 16 ---

The enemy’s gate is Rowling.

\emph{I’m not a psychopath, I’m just very creative.}

\filbreak
--- 17 ---

You have always been J. K. Rowling.

"\emph{You start to see the pattern, hear the rhythm of the world.}"

\filbreak
--- 18 ---

Any sufficiently advanced J. K. Rowling is indistinguishable from magic.

"\emph{That does sound like the sort of thing I would do, doesn’t it?}"

\filbreak
--- 19 ---

Blood for the blood god! Skulls for J. K. Rowling!

\filbreak
--- 20 ---

That which can be destroyed by the Rowling should be.

\filbreak
--- 21 ---

Rowling is whoever does Rowling’s job.

\filbreak
--- 22 ---

The key to strategy is not to choose \emph{a} path to J. K. Rowling, but to choose so that \emph{all} paths lead to some J. K. Rowling.

\filbreak
--- 23 ---

Everybody wants a rock to wind a piece of string around J. K. Rowling.

\filbreak
--- 24 ---

J. K. Rowling coils and strikes, unseen; Orca circles, hard and lean.

\filbreak
--- 25 ---

To seek out new life, and J. K. Rowling!

\filbreak
--- 26 ---

Yakka foob mog. Grug pubbawup zink wattoom gazork. Chumble spuzz J. K. Rowling.

\filbreak
--- 27 ---

J. K. Rowling is 87\% confident you will burst into flames.

\filbreak
--- 28 ---
 
Whatever can go Rowling will go Rowling.

\filbreak
--- 29 ---

Unfortunately, no one can be told who J. K. Rowling is. You have to see her for yourself.

\filbreak
--- 30 ---

J. K. Rowling if a man tries to bother you, you can think blue, count two, and look for a red
shoe.

\filbreak
--- 33 ---

I just recite to myself, over and over, until I can choose sleep: It all adds up to J. K. Rowling.
} % end of spacing changes

%  LocalWords:  stddisclaimer JKR ph’nglui mglw’nafh wgah’nagl fhtagn Elen
%  LocalWords:  sila omentielvo Melenkurion abatha Duroc minas Yakka foob
%  LocalWords:  mog Grug pubbawup zink wattoom gazork Chumble spuzz
