\chapter{Status Differentials}

\lettrine{W}{renching} disorientation, that was how it felt to walk out of Platform Nine and Three-Quarters into the rest of Earth, the world that Harry had once thought was the only real world. People dressed in casual shirts and pants, instead of the more dignified robes of wizards and witches. Scattered bits of trash here and there around the benches. A forgotten smell, the fumes of burned gasoline, raw and sharp in the air. The ambiance of the King’s Cross train station, less bright and cheerful than Hogwarts or Diagon Alley; the people seemed smaller, more afraid, and likely would have eagerly traded their problems for a dark wizard to fight. Harry wanted to cast \emph{Scourgify} for the dirt, and \emph{Everto} for the garbage, and if he’d known the spell, a Bubble-Head Charm so he wouldn’t have to breathe the air. But he couldn’t use his wand, in this place...

This, Harry realized, must be what it felt like to go from a First World country to a Third World country.

Only it was the Zeroth World which Harry had left, the wizarding world, of Cleansing Charms and house elves; where, between the healer’s arts and your own magic, you could hit one hundred and seventy before old age really started catching up with you.

And nonmagical London, Muggle Earth, to which Harry had temporarily returned. This was where Mum and Dad would live out the rest of their lives, unless technology leapfrogged over wizardry’s quality of life, or something deeper in the world changed.

Without even thinking about it, Harry’s head turned and his eyes darted behind him to see the wooden trunk that was scurrying after him, unnoticed by any Muggles, the clawed tentacles offering quick confirmation that, yes, he hadn’t just imagined it all...

And then there was the other reason for the tight feeling in his chest.

His parents didn’t know.

They didn’t know \emph{anything}.

They didn’t know...

“Harry?” called a thin, blonde woman whose perfectly smooth and unblemished skin made her look a good deal younger than thirty-three; and Harry realized with a start that it \emph{was} magic, he hadn’t known the signs before but he could see them now. And whatever sort of potion lasted that long, it must have been terribly dangerous, because most witches didn’t do that to themselves, they weren’t that desperate...

There was water gathering in Harry’s eyes.

“\emph{Harry?}” yelled an older-looking man with a paunch gathering about his stomach, dressed with ostentatious academic carelessness in a black vest thrown over a dark grey-green shirt, someone who would always be a professor anywhere he went, who would certainly have been one of the most brilliant wizards of his generation, if he’d been born with two copies of that gene, instead of zero...

Harry raised his hand and waved to them. He couldn’t speak. He couldn’t speak at all.

They came over to him, not running, but at a steady, dignified walk; that was how fast Professor Michael Verres-Evans walked, and Mrs.~Petunia Evans-Verres wasn’t about to walk any faster.

The smile on his father’s face wasn’t very wide, but then his father never was given to huge smiles; it was, at least, as wide as Harry had ever seen it, wider than when a new grant came in, or when one of his students got a position, and you couldn’t ask for a wider smile than that.

Mum was blinking hard, and she was trying to smile but not doing a very good job.

“So!” said his father as he came striding up. “Made any revolutionary discoveries yet?”

Of course Dad thought he was joking.

It hadn’t hurt quite so much when his parents didn’t believe in him, back when no one \emph{else} had believed in him either, back when Harry hadn’t \emph{known} how it felt to be taken seriously by people like Headmaster Dumbledore and Professor Quirrell.

And that was when Harry realized that the Boy-Who-Lived only existed in magical Britain, that there wasn’t any such person in Muggle London, just a cute little eleven-year-old boy going home for Christmas.

“Excuse me,” Harry said, his voice trembling, “I’m going to break down and cry now, it doesn’t mean there was anything wrong at school.”

Harry started to move forward, and then stopped, torn between hugging his father and hugging his mother, he didn’t want either one to feel slighted or that Harry loved them more than the other—

“You,” said his father, “are a very silly boy, Mr.~Verres,” and he gently took Harry by the shoulders and pushed him into the arms of his mother, who was kneeling down, tears already streaking her cheek.

“Hello, Mum,” Harry said with his voice wavering, “I’m back.” And he hugged her, amid the noisy mechanical sounds and the smell of burned gasoline; and Harry started crying, because he knew that nothing \emph{could} go back, least of all him.
\sbreak
The sky was completely dark, and stars were coming out, by the time they negotiated the Christmas traffic to the university town that was Oxford, and parked in the driveway of the small, dingy-looking old house that their family used to keep the rain off their books.

As they walked up the brief stretch of pavement leading to the front door, they passed a series of flower-pots holding small, dim electric lights (dim since they had to recharge themselves off solar power during the day), and the lights lit up just as they passed. The hard part had been finding motion sensors that were waterproof and triggered at just the right distance...

In Hogwarts there were real torches like that.

And then the front door opened and Harry stepped into their living-room, blinking hard.

\emph{Every inch of wall space is covered by a bookcase. Each bookcase has six shelves, going almost to the ceiling. Some bookshelves are stacked to the brim with hardcover books: science, math, history, and everything else. Other shelves have two layers of paperback science fiction, with the back layer of books propped up on old tissue boxes or two-by-fours, so that you can see the back layer of books above the books in front. And it still isn’t enough. Books are overflowing onto the tables and the sofas and making little heaps under the windows...}

The Verres household was just as he’d left it, only with more books, which was also just how he’d left it.

And a Christmas tree, naked and undecorated just two days before Christmas Eve, which threw Harry briefly before he realized, with a warm feeling blossoming in his chest, that of course his parents had \emph{waited}.

“We took the bed out of your room to make room for more bookcases,” said his father. “You can sleep in your trunk, right?”

“\emph{You} can sleep in my trunk,” said Harry.

“That reminds me,” said his father. “What \emph{did} they end up doing about your sleep cycle?”

“Magic,” Harry said, making a beeline for the door that opened upon his bedroom, just in case Dad \emph{wasn’t} joking...

“That’s not an explanation!” said Professor Verres-Evans, just as Harry shouted, “\emph{You used up all the open space on my bookcases?}”
\sbreak
Harry had spent the 23\Rd of December shopping for Muggle things that he couldn’t just Transfigure; his father had been busy and had said that Harry would need to walk or take the bus, which had suited Harry just fine. Some of the people at the hardware store had given Harry questioning looks, but he’d said with an innocent voice that his father was shopping nearby and was very busy and had sent him to get some things (holding up a list in carefully adult-looking half-illegible handwriting); and in the end, money was money.

They had all decorated the Christmas tree together, and Harry had put a tiny dancing fairy on top (two Sickles, five Knuts at Gambol \& Japes).

Gringotts had readily exchanged Galleons for paper money, but they didn’t seem to have any simple way to turn larger quantities of gold into tax-free, unsuspicious Muggle money in a numbered Swiss bank account. This had rather spiked Harry’s plan to turn most of the money he’d self-stolen into a sensible mix of 60\% international index funds and 40\% Berkshire Hathaway. For the moment, Harry had diversified his assets a little further by sneaking out late at night, invisible and Time-Turned, and burying one hundred golden Galleons in the backyard. He’d always always \emph{always} wanted to do that anyway.

Some of December 24\Th had been spent with the Professor reading Harry’s books and asking questions. Most of the experiments his father had suggested were impractical, at least for the moment; of those remaining, Harry had done many of them already. (“Yes, Dad, I checked what happened if Hermione was given a changed pronunciation and she didn’t know whether it was changed, that was the very first experiment I did, Dad!”)

The last question Harry’s father had asked, looking up from \emph{Magical Draughts and Potions} with an expression of bewildered disgust, was whether it all made sense if you were a wizard; and Harry had answered no.

Whereupon his father had declared that magic was unscientific.

Harry was still a little shocked at the idea of pointing to a section of \emph{reality} and calling it unscientific. Dad seemed to think that the conflict between his intuitions and the universe meant that the universe had a problem.

(Then again, there were lots of physicists who thought that quantum mechanics was weird, instead of quantum mechanics being normal and them being weird.)

Harry had shown his mother the healer’s kit he’d bought to keep in their house, though most of the potions wouldn’t work on Dad. Mum had stared at the kit in a way that made Harry ask whether Mum’s sister had ever bought anything like that for Grandpa Edwin and Grandma Elaine. And when Mum still hadn’t answered, Harry had said hastily that she must have just never thought of it. And then, finally, he’d fled the room.

Lily Evans probably \emph{hadn’t} thought of it, that was the sad thing. Harry knew that other people had a tendency to not-think about painful subjects, in the same way they had a tendency not to deliberately rest their hands on red-hot stove burners; and Harry was starting to suspect that most Muggleborns rapidly acquired a tendency to not-think about their family, who were all going to die before they reached their first century anyway.

Not that Harry had any intention of letting \emph{that} happen, of course.

And then it was late in the day on December 24\Th and they were driving off for their Christmas Eve dinner.
\sbreak
The house was huge, not by Hogwarts standards, but certainly by the standards of what you could get if your father was a distinguished professor trying to live in Oxford. Two stories of brick gleaming in the setting sun, with windows on top of windows and one tall window that went up much further than glass should go, that was going to be one huge living room...

Harry took a deep breath, and rang the doorbell.

There was a distant call of “Honey, can you get it?”

This was followed by a slow patter of approaching steps.

And then the door opened to reveal a genial man, of fat and rosy cheeks and thinning hair, in a blue button-down shirt straining slightly at the seams.

“Dr.~Granger?” Harry’s father said briskly, before Harry could even speak. “I’m Michael, and this is Petunia and our son Harry. The food’s in the magical trunk,” and Dad made a vague gesture behind him—not quite in the direction of the trunk, as it happened.

“Yes, please, come in,” said Leo Granger. He stepped forward and took the wine bottle from the Professor’s outstretched hands, with a muttered “Thank you,” and then stepped back and waved at the living room. “Have a seat. And,” his head turning down to address Harry, “all the toys are downstairs in the basement, I’m sure Herm will be down shortly, it’s the first door on your right,” and pointed toward a hallway.

Harry just looked at him for a moment, conscious that he was blocking his parents from coming in.

“Toys?” said Harry in a bright, high-pitched voice, with his eyes wide. “I love toys!”

There was an intake of breath from his mother behind him, and Harry strode into the house, managing not to stomp too hard as he walked.

The living room was every bit as large as it had looked from outside, with a huge vaulted ceiling dangling a gigantic chandelier, and a Christmas tree that must have been murder to maneuver through the door. The lower levels of the tree were thoroughly and carefully decorated in neat patterns of red and green and gold, with a newfound sprinkling of blue and bronze; the heights that only a grownup could reach were carelessly, randomly draped with strings of lights and wreaths of tinsel. A hallway extended until it terminated in the cabinetry of a kitchen, and wooden stairs with polished metal railings stretched up toward a second floor.

“Gosh!” Harry said. “This is a big house! I hope I don’t get lost in here!”
\sbreak
Dr.~Roberta Granger was feeling rather nervous as dinner approached. The turkey and the roast, their own contributions to the common project, were steadily cooking away in the oven; the other dishes were to be brought by their guests, the Verres family, who had adopted a boy named Harry. Who was known to the wizarding world as the Boy-Who-Lived. And who was also the only boy that Hermione had ever called “cute”, or noticed at all, really.

The Verreses had said that Hermione was the only child in Harry’s age group whose existence their son had ever acknowledged in any way whatsoever.

And it might’ve been jumping the gun just a little; but both couples had a sneaking suspicion that wedding bells might be in the offing a few years down the road.

So while Christmas Day would be spent, as always, with her husband’s family, they’d decided to spend Christmas Eve meeting their daughter’s possible future in-laws.

The doorbell rang while she was right in the middle of basting the turkey, and she raised her voice and shouted, “\emph{Honey, can you get it?}”

There was a brief groan of a chair and its occupant, and then there was the sound of her husband’s heavy footsteps and the door swinging open.

“Dr.~Granger?” said an older man’s brisk voice. “I’m Michael, and this is Petunia and our son Harry. The food’s in the magical trunk.”

“Yes, please, come in,” said her husband, followed by a muttered “Thank you” that indicated some sort of present had been accepted, and “Have a seat.” Then Leo’s voice altered to a tone of artificial enthusiasm, and said, “And all the toys are downstairs in the basement, I’m sure Herm will be down shortly, it’s the first door on your right.”

There was a brief pause.

Then a young boy’s bright voice said, “Toys? I love toys!”

There was the sound of footsteps entering the house, and then the same bright voice said, “Gosh! This is a big house! I hope I don’t get lost in here!”

Roberta closed up the oven, smiling. She’d been a bit worried about the way Hermione’s letters had described the Boy-Who-Lived—though certainly her daughter hadn’t said anything indicating that Harry Potter was \emph{dangerous;} nothing like the dark hints written in the books Roberta had bought, supposedly for Hermione, during their trip to Diagon Alley. Her daughter hadn’t said much at all, only that Harry talked like he came out of a book, and Hermione was studying harder than she ever had in her life just to stay ahead of him in class. But from the sound of it, Harry Potter was an ordinary eleven-year-old boy.

She got to the front door just as her daughter came clattering frantically down the stairs at a speed that didn’t look safe at all, Hermione had claimed that witches were more resistant to falls but Roberta wasn’t quite sure she believed that—

Roberta took in her first sight of Professor and Mrs.~Verres, who were both looking rather nervous, just as the boy with the legendary scar on his forehead turned to her daughter and said, now in a lower voice, “Well met on this fairest of evenings, Miss Granger.” His hand stretched back, as though offering his parents on a silver platter. “I present to you my father, Professor Michael Verres-Evans, and my mother, Mrs.~Petunia Evans-Verres.”

And as Roberta’s mouth was gaping open, the boy turned back to his parents and said, now in that bright voice again, “Mum, Dad, this is Hermione! She’s really smart!”

“\emph{Harry!}” hissed her daughter. “Stop that!”

The boy swiveled again to regard Hermione. “I’m afraid, Miss Granger,” the boy said gravely, “that you and I have been exiled to the labyrinthine recesses of the basement. Let us leave them to their adult conversations, which would no doubt soar far above our own childish intellects, and resume our ongoing discussion of the implications of Humean projectivism for Transfiguration.”

“Excuse us, please,” said her daughter in a very firm tone, and grabbed the boy by his left sleeve, and dragged him into the hallway—Roberta swiveled helplessly to track them as they went past her, the boy gave her a cheery wave—and then Hermione pulled the boy into the basement access and slammed the door behind her.

“I, ah, I apologize for...” said Mrs.~Verres in a faltering voice.

“I’m sorry,” said the Professor, smiling fondly, “Harry can be a bit touchy about that sort of thing. But I expect he’s right about us not being interested in their conversation.”

\emph{Is he dangerous?} Roberta wanted to ask, but she kept her silence and tried to think of subtler questions. Her husband beside her was chuckling, as if he’d found what they’d just seen funny, rather than frightening.

The most terrible Dark Lord in history had tried to kill that boy, and the burnt husk of his body had been found next to the crib.

Her possible future son-in-law.

Roberta had been increasingly apprehensive about giving her daughter over to witchcraft—especially after she’d read the books, put the dates together, and realized that her magical mother had probably been killed at the height of Grindelwald’s terror, \emph{not} died giving birth to her as her father had always claimed. But Professor McGonagall had made other visits after her first trip, to “see how Miss Granger is doing”; and Roberta couldn’t help but think that if Hermione said her parents were being troublesome about her witching career, something would be done to \emph{fix} them...

Roberta put her best smile on her face, and did what she could to spread some pretended Christmas cheer.
\sbreak
The dining room table was much longer than six people—er, four people and two children—really needed, but all of it was draped with a tablecloth of fine white linen, and the dishes had been needlessly transferred to fancy serving plates, which at least were of stainless steel rather than real silver.

Harry was having a bit of trouble concentrating on the turkey.

The conversation had turned to Hogwarts, naturally; and it’d been obvious to Harry that his parents were hoping that Hermione would trip up and say more about Harry’s school life than Harry had been telling them. And either Hermione had realized this, or she was just automatically steering clear of anything that might prove troublesome.

So \emph{Harry} was fine.

But unfortunately Harry had made the mistake of owling his parents with all sorts of facts about Hermione that she hadn’t told her \emph{own} parents.

Like that she was general of an army in their after-school activities.

Hermione’s mother had looked very alarmed, and Harry had quickly interrupted and done his best to explain that all the spells were stunners, Professor Quirrell was always watching, and the existence of magical healing meant that lots of things were much less dangerous than they sounded, at which point Hermione had kicked him hard under the table. Thankfully Harry’s father, who Harry had to admit was better than him at some things, had announced with firm professorial authority that he hadn’t worried at all, since he couldn’t imagine children being allowed to do it if it was dangerous.

That wasn’t why Harry was having trouble enjoying dinner, though.

...the problem with feeling sorry for yourself was that it never took any time at all to find someone else who had it worse.

Dr.~Leo Granger had asked, at one point, whether that nice teacher who’d seemed to like Hermione, Professor McGonagall, was awarding her lots of points in school.

Hermione had said yes, with an apparently genuine smile.

Harry had managed, with some effort, to stop himself from icily pointing out that Professor McGonagall would never show favoritism to any Hogwarts student, and that Hermione was getting lots of points because she’d earned \emph{every, single, one.}

At another point, Leo Granger had offered the table his opinion that Hermione was very smart and could have gone to medical school and become a dentist, if not for the whole witch business.

Hermione had smiled again, and a quick glance had prevented Harry from suggesting Hermione might also have been an \emph{internationally famous scientist}, and asking whether that thought would’ve occurred to the Grangers if they’d had a \emph{son} instead of a \emph{daughter}, or if it was unacceptable either way for their offspring to do better than them.

But Harry was rapidly reaching his boiling point.

And becoming a \emph{lot} more appreciative of the fact that his own father had \emph{always} done everything he could to support Harry’s development as a prodigy and \emph{always} encouraged him to reach higher and \emph{never} belittled a single one of his accomplishments, even if a child prodigy was still just a child. Was this the sort of household he could have ended up in, if Mum had married Vernon Dursley?

Harry was doing what he could, though.

“And she’s really beating you in \emph{all} your classes except broomstick riding and Transfiguration?” said Professor Michael Verres-Evans.

“Yes,” Harry said with forced calm, as he cut himself another bite of Christmas Eve turkey. “By solid margins, in most of them.” There were other circumstances under which Harry would have been more reluctant to admit that, which was why he hadn’t gotten around to telling his father until now.

“Hermione has always been quite good in school,” said Dr.~Leo Granger in a satisfied tone.

“Harry competes at the national level!” said Professor Michael Verres-Evans.

“Dear!” said Petunia.

Hermione was giggling, and that wasn’t making Harry feel any better about her situation. It didn’t seem to bother Hermione and \emph{that bothered Harry.}

“I’m not embarrassed to lose to her, Dad,” Harry said. Right at this moment he wasn’t. “Did I mention that she memorized all her schoolbooks before the first day of class? And yes, I tested it.”

“Is that, ah, \emph{usual} for her?” Professor Verres-Evans said to the Grangers.

“Oh, yes, Hermione’s always memorizing things,” said Dr.~Roberta Granger with a cheerful smile. “She knows every recipe in all my cookbooks by heart. I miss her every time I make dinner.”

Judging by the look on his father’s face, Dad was feeling at least some of what Harry felt.

“Don’t worry, Dad,” Harry said, “she’s getting all the advanced material she can take, now. Her teachers at Hogwarts know she’s smart, \emph{unlike her parents!}”

His voice had risen on the last three words, and even as all faces turned to stare at him and Hermione kicked him again, Harry knew that he’d blown it, but it was too much, just way too much.

“Of course we know she’s smart,” said Leo Granger, starting to look offended at the child who’d had the temerity to raise his voice at their dinner table.

“You don’t have the tiniest idea,” said Harry, the ice now leaking into his voice. “You think she reads a lot of books and it’s cute, right? You see a perfect report card and you think it’s good that she’s doing well in class. Your daughter is the most talented witch of her generation and the brightest star of Hogwarts, and someday, Dr.~and Dr.~Granger, the fact that you were her parents will be the only reason that history remembers you!”

Hermione, who had calmly got up from her seat and walked around the table, chose that moment to grab Harry’s shirt by the shoulder and pull him out of his chair. Harry let himself be pulled, but as Hermione dragged him away, he said, raising his voice even louder, “It is entirely possible that in a thousand years, the fact that Hermione Granger’s parents were dentists will be the only reason anyone remembers dentistry!”
\sbreak
Roberta stared at where her daughter had just dragged the Boy-Who-Lived out of the room with a patient look upon her young face.

“I’m terribly sorry,” said Professor Verres with an amused smile. “But please don’t worry, Harry always talks like that. Aren’t they just like a married couple already?”

The frightening thing was that they \emph{were.}
\sbreak
Harry had been expecting a rather severe lecture from Hermione.

But after Hermione pulled them into the basement access and closed the door behind them, she’d turned around—

—and was smiling, genuinely so far as Harry could tell.

“Please don’t, Harry,” she said in a soft voice. “Even though it’s very nice of you. Everything’s fine.”

Harry just looked at her. “How can you stand it?” he said. He had to keep his voice quiet, they didn’t want the parents to hear, but it rose in pitch if not in volume. “\emph{How can you stand it?}”

Hermione shrugged, and said, “Because that’s the way parents \emph{should} be?”

“No,” Harry said, his voice low and intense, “it’s not, my father \emph{never} puts me down—well, he \emph{does}, but never like that—”

Hermione held up a single finger, and Harry waited, watching her search for words. It took her a while before she said, “Harry... Professor McGonagall and Professor Flitwick like me because I’m the most talented witch of my generation and the brightest star of Hogwarts. And Mum and Dad don’t know that, and you’ll never be able to tell them, but they love me anyway. Which means that everything is just the way it should be, at Hogwarts and at home. And since they’re \emph{my} parents, Mr.~Potter, \emph{you} don’t get to argue.” She was once again smiling her mysterious smile from dinnertime, and looking at Harry very fondly. “\emph{Is} that clear, Mr.~Potter?”

Harry nodded tightly.

“Good,” said Hermione, and leaned over and kissed him on the cheek.
\sbreak
The conversation had only just gotten started again when a distant high-pitched yelp floated back to them,

“\emph{Hey! No kissing!}”

The two fathers burst out in laughter just as the two mothers rose up from their chairs with identical looks of horror and dashed toward the basement.

When the children had been brought back, Hermione was saying in an icy tone that she was never going to kiss Harry ever again, and Harry was saying in an outraged voice that the Sun would burn down to a cold dead cinder before he let her get close enough to try.

Which meant that everything was just the way it should be, and they all sat back down again to finish their Christmas dinner.

