\chapter{Shut Up and Do The Impossible}

\lettrine{T}{he} gibbous moon
riding higher in the cloudless sky, the stars and wash of the Milky Way visible
in all their majesty within the darkness, all these shone down upon the
graveyard to bear witness from their unimaginable distances.

In the instant when Harry had realised there was no way at all left to save
everyone, his mind's voices had fallen away, become one, a single purpose
taking up every fraction of his mind.

Fifty seconds.

Forty seconds.

Harry's eyes tracked slowly across the air, until his gaze landed on the first
Death Eater, the one closest to him.

Thirty seconds?

Twenty seconds?

"\parsel{Time'ss almosst up---}" hissed Voldemort.

"\parsel{I do know ssecretss you would like to know,}" Harry hissed. He didn't
look directly at the Dark Lord as he spoke. "\parsel{But mosst valuable knowledge
to you, I think, would be my ideass ass to how world might be desstroyed. Yet,
to tell you ssuch thoughtss might lead to desstruction of world. Do not know
prophecy, but if there iss prophecy, that makess it more than ussually probable
that any action I take might have that effect. Or to tell you ssuch might
prevent desstruction of world, ssince you do sseem motivated to avoid it. Not
allowed to make ssuch a decission mysself. Would need to awaken and conssult
girl-child friend. Vow requiress.}"

There was a long pause. The Dark Lord, floating above and behind the curve of
Death Eaters with leveled wands, began to laugh as Salazar Slytherin had
thought a snake would laugh, cold amusement in the form of a hiss. "\parsel{Do
you know how to desstroy world, then?}"

"\parsel{Cannot deliberately try to imagine method. You might have way for
sservant to ssteal my thoughtss. Vow prohibitss. But ssusspect I could devisse
method, if girl-child ssaid to try.}"

Harry's eyes drifted slowly to another Death Eater, and another.

More snakish laughter. "\parsel{Clever. You have my complimentss for thinking of
ssuch tacticss. But no.}"

"\parsel{Know it iss annoying, but with world and your eternity at sstake, would
you not---}"

"\parsel{Greater rissk to world in introducing ssuch complicationss, delaying
your end. I will sstudy Muggle ssciencess mysself, think of all you might
imagine. Now sspeak ssuch ssecretss as you may tell me, or thiss endss.}"

Slowly Harry's vision tracked across the graveyard in careful arcs, ignoring
the Dark Lord except as a floating blackness in his peripheral vision. His
mouth went on speaking with only half his attention. "\parsel{Have thought of
idea you might not have conssidered, teacher. Your attempt to kill me might
fail in certain sspecific way desspite all your precautionss, perhapss lead
into my desstroying world later. Would not ordinarily deem probable, but with
prophecy at hand, may well be sso.}"

Voldemort went still, in the air. "\parsel{How?}"

"\parsel{Am not obligated to tell you.}"

A cold anger began to seethe through the snakish reply. "\parsel{Though I
undersstand well your dessperation and attempted clevernesss, thiss beginss to
annoy me. I will not withhold from killing you, for that iss sstill greater
rissk. To fail to tell me your thought rissks desstroying world. Sspeak!}"

"\parsel{No. Vow doess not obligate me to any possitive action.}"

The Dark Lord stared down at Harry Potter, who glanced up at the angry face
only briefly before his eyes went back to the next Death Eater. Some of them
were shifting their stances slightly, but they stood still, and said no words
as they leveled their wands. The silver skull masks could not be read.

Then the Dark Lord began to chuckle again. "\parsel{Ssurvive your death, you
think you might? No, child, my horcruxess are not linked to you alsso. I would
know if they were. Or iss there other reasson you think you might ssurvive
beyond my ways of enssuring your death?}"

Harry didn't allow himself to be distracted. The repeated failures didn't
matter, they only led into the next action in the chain---but he \emph{still
needed a next action}---

"\parsel{Now sspeak a ssecret,}" the Dark Lord hissed, "\parsel{or I---}"

"\parsel{Life-eaterss will purssue you alwayss, hate you alwayss, sseek you out
wherever you go, if what I have jusst done wass ssuccesssful, I have caused
them to be set upon you! Guardian Charm ssecret will be beyond you for long
time to come, perhapss forever! Besst defensse againsst life-eaterss would die
with me!}"

"\parsel{Thiss iss sstarting to become ssad{\ldots}}" the Dark Lord's voice
trailed off. "\parsel{Ah. I ssee. Life-eaterss resspond to expectationss. You
tell me I will be hunted, I expect to be hunted, they hunt me. Ssuch iss rare,
but not unheard-of. Valuable ssecret, yess. Can ssee many ussess.}" A cruel
smile. "\parsel{I sshall allow you to sselect one persson to be ssaved.}"

"\parsel{Mysself.}"

"\parsel{Would tell you to die with dignity, but knowing mysself, I know it for
futility. You have wassted my kindly gift jusst then by annoying me, and I
retract it. Any other ssecretss?}"

"\parsel{Yess. Really interessting oness, too. Ssome you are unlikely to figure
out on your own, not for very long time if ever. If I ssay I have told you all
that do not rissk world, will you not torment any of my friendss or family? All
of thiss sspeech sstarted becausse you left me no way at all to ssave
everyone.}"

The Dark Lord stood still in the air for a long moment.

And Harry's eyes went on tracking slowly across the graveyard, as his hand
remained tight upon his wand.

In the instant when Harry had realized there was no way left to save everyone---

He couldn't speak any incantation in English. But Transfiguration was wordless.

There was no material in contact with his wand's end except air, which couldn't
be Transfigured. But Voldemort didn't know about partial Transfiguration, which
Harry could use to Transfigure a tiny bit of the material from his wand itself.

"\parsel{You're sstalling,}" the Dark Lord said. "\parsel{Jusst to delay death? Or
with other purposse?}"

Harry said nothing, his other work slowing as his mind sought a continuation of
the conversation that would work even against the Dark Lord's will---

"\parsel{Sspeak and tell me purposse, or thiss endss now and your friendss suffer
for lifetimess!}"

"\parsel{Lower Muggle weapon and do not point wand in my direction,}" Harry
hissed, putting as much cold danger as he could into the snake's voice.
"\parsel{Sspeak no commandss to sservantss. I do posssesss capabilitiess of which
you are ignorant. Can usse one ssuch capacity to causse huge explossion almosst
insstantly, without sspeaking incantation. Sslay your new body, all sservantss,
Sstone sscattered to who knowss where.}"

At his current level of practice Harry could Transfigure one cubic millimeter
as fast as he could apply his will and magic.

One cubic millimeter of antimatter.

It wasn't a world-ending threat.

Voldemort could have been carved from stone. "\parsel{You bluff, ssomehow.}"

"\parsel{Not bluffing. Sspeaking in ssnaketalk, I tell you, I can do it almosst
insstantly, before any sspell can be casst at me, I think. You know very little
of sscience ass yet. Power I would command iss sstronger than processs that
fuelss sstarss.}"

"\parsel{Vow will sstop you,}" hissed Voldemort. "\parsel{You cannot rissk world.
Take no risskss, none, with clever ideass!}"

"\parsel{Would not rissk world. I esstimated ssize of explossion, nowhere near
that large.}"

"\parsel{You do NOT know, fool! Cannot be SURE!}" Voldemort's hiss was climbing
higher.

"\parsel{I am reassonably certain. Vow will not sstop me.}"

There was an increasing fury in Voldemort's expression, and yet his hiss
carried a tinge of fear. "\parsel{I sshall wreak pain beyond imagining on all you
care for---}"

"\parsel{Sshut up. I dissregard all ssuch threatss now, as theory of gamess
ssayss I sshould. Only reasson you make threatss iss that you expect me to
resspond.}" That, too, Harry had truly understood in the last extremity.
"\parsel{Offer me ssomething I want, teacher. For your new body, for your
continued holding of Sstone, for livess of your sservantss.}"

Harry's mouth was running on automatic, his real attention elsewhere.

\emph{Beneath the moonlight glints a tiny fragment of silver, a fraction of a
line{\ldots}}

From a tiny spot on the end of Harry's wand, a cubic millimeter of anchor,
stretched out a thin line of Transfigured spider-silk. It would have broken at
once, if tested; it would have gone unremarked, if any had noticed its glint.
Less than a tenth of a millimeter in cross-section, the tiny shape represented
by the extended line of spider-silk was something Harry could Transfigure
swiftly, ten centimeters of length to a cubic millimeter of total volume; and
Harry could Transfigure a cubic millimeter in a fraction of a second. He was
forcing the Transfiguration outward, extending it through the air as fast as he
could without risking the transformation.

The tracing line of spider-silk looped around a Death Eater's hood at neck
level, returned to the pattern of threads.

Voldemort's face was now impassive. "\parsel{You musst not leave here alive.
Ssenssible people called good would alsso agree, thiss I tell you in ssnake'ss
sspeech. But all your friendss I will treat kindly and protect under my reign,
if you agree to die now ass good persson sshould.}"

The last Death Eater was looped. The pattern of spider-silk was complete. The
web had been drawn with loops around all the Death Eater's necks. The ends of
those loops had been anchored to a central circle; and that central circle in
turn had three threads stretching across its center. The entire pattern still
touching the anchor-line stretching out of Harry's wand.

Over the next seconds, those near-invisible threads of reflected moonlight
turned black.

Filaments narrower, stronger, and sharper than steel wire; braided carbon
nanotubes, each individual tube all a single molecule.

Harry hissed, "\parsel{Want you to alsso promisse to treat nationss kindly under
your rule. Will not accept lesss.}"

Voldemort hovered still in the air, snake-face showing a dawning fury.

The last two threads stretched out from the dark pattern, black theads already
in the form of nanotubes. They moved lightly through the air toward the Dark
Lord himself, toward the sleeve just above Voldemort's left hand that held the
gun, toward the sleeve above the right hand that held the yew wand, threads
placed high at first to give them time to drift slowly downward through the
air. The threads looped around, went over themselves, tied slippable knots.
Began to tighten, coming closer to the sleeve, as Harry Transfigured them
shorter---

Harry felt the tickle of Voldmort's power beginning to touch his own in the
back of his mind; at the same time the Dark Lord's eyes widened, his mouth
opened.

And Harry Transfigured the black threads stretching across the black pattern's
center to a quarter their previous size, shrinking the circle, yanking hard on
everything attached, tightening loops.

\emph{(Black robes, falling.)}

Harry wasn't looking there, he didn't see the falling masks, the blood, in the
back of his mind he felt some explosions of magic like he'd felt when Hermione
died but he ignored them, Harry's eyes only saw the Dark Lord's hands and wand
and gun dropping downward, and then Harry's wand was rising, pointing---

Harry screamed, "\emph{STUPORFY!}"

The red bolt the color of the Stunning Hex winged toward Voldemort, blazing
across the graveyard almost faster than the eye could see.

Without any hesitation despite his wounds the Dark Lord jerked down and right
through the air.

And the red bolt from Professor Flitwick's secret Swerving Stunner turned in
midair and slammed into Voldemort.

The pain that flashed through Harry's scar was searing, it made him cry out and
a red haze appear across his vision, despite everything Harry dropped his wand
in pain and sheer fatigue.

As Harry let go of his wand, the pain began to clear---
