\namedpartchapter{The Stanford Prison Experiment}{TSPE}{IX}{Curiosity}
\lettrine{B}{roomsticks} had been invented during what a Muggle would have called the Dark Ages, supposedly by a legendary witch named Celestria Relevo, allegedly the great-great-granddaughter of Merlin.

Celestria Relevo, or whichever person or group had really invented those enchantments, hadn’t known a darned thing about Newtonian mechanics.

Broomsticks, therefore, worked by Aristotelian physics.

They went where you pointed them.

If you wanted to move straight forward, you pointed them straight forward; you didn’t worry about keeping some of the thrust going downward to cancel out the effect of gravity.

If you turned a broomstick, all of its new velocity was in the new direction of pointing, it didn’t go sideways based on its old momentum.

Broomsticks had maximum speeds, not maximum accelerations. Not because of anything to do with air resistance, but because a broomstick had some maximum Aristotelian impetus its enchantments could exert.

Harry had never explicitly \emph{noticed} that before, despite being dextrous enough to get the best grades in flying class. Broomsticks worked so much like the human mind \emph{instinctively expected them to work} that his brain had managed to \emph{entirely overlook their physical absurdity.} Harry, on his first Thursday of broomstick lessons, had been distracted by more interesting-seeming phenomena, words written on paper and a glowing red ball. So his brain had simply suspended its disbelief, marked the reality of broomsticks as accepted, and proceeded to have its fun, without ever once \emph{thinking of the question} whose answer would have been obvious. For it is a sad fact that we only ever \emph{think} about a tiny fraction of all the phenomena we encounter...

That is the story of how Harry James Potter-Evans-Verres was almost killed by his own lack of curiosity.

Because rockets did \emph{not} work by Aristotelian physics.

Rockets did \emph{not} work like a human mind instinctively thought a flying thing should work.

A rocket-assisted broomstick, therefore, did \emph{not} move like the magical broomsticks upon which Harry was such a very good flyer.

None of this actually went through Harry’s mind at the time.

For one thing, the loudest noise he’d ever heard in his life was preventing him from hearing himself think.

For another thing, accelerating upward at four gravities meant that he had around two and a half seconds, total, to go from the bottom to the top of Azkaban.

And even if they were two and a half of the \emph{longest} seconds in the history of Time, that wasn’t enough room to do much thinking.

There was time only to see the lights of the Aurors’ curses arrowing down at him, slightly angle the broomstick to avoid them, realize that the broomstick was simply continuing on with mostly the same momentum instead of going in the direction he pointed it, and activate the wordless concepts

*\emph{crap*}

and

\emph{*Newton*}

whereupon Harry angled the broomstick much harder and then they started to very quickly approach the wall so he angled it back the other way and there were more lights coming down and the Dementors were sliding smoothly up toward them along with some kind of giant winged creature of white-golden flame so Harry wrenched the broomstick back toward the sky but now he was still sliding toward another wall so he tilted the broom slightly and he stopped approaching but he was too close so he tilted it again and then the distant Aurors on their broomsticks weren’t very distant at all and he was going to crash into that woman so he spun his broomstick straight away from her and then in another instant he realized his rocket was an extremely powerful flamethrower and in a fraction of a second it would be pointing directly at the Auror so he spun the broomstick sideways as he kept going up and he couldn’t remember if it was pointing at any Aurors now but at least it wasn’t pointing at \emph{her}

Harry missed another Auror by about a meter, zipping past him on a sideways-pointed flamethrower moving upward at, Harry would later guess, around 300 kilometers per hour.

If there were any screams of roasted Aurors he didn’t hear them, but this was not evidence one way or another, because all that Harry was hearing at the moment was an extremely loud noise.

A couple of \emph{calmer if not quieter} seconds later, there didn’t seem to be any Aurors around, or any Dementors, or any giant winged flame creatures, and the vast and terrible edifice of Azkaban looked surprisingly tiny from this height.

Harry got the broomstick pointed toward the Sun, faintly visible through the clouds, it wasn’t high in the sky at this time of day and month of winter, and the broomstick accelerated for another two seconds in that direction and picked up an amazing amount of speed very quickly before the solid-fuel rocket burned itself out.

After that, once Harry could hear himself think again, when there was only the howling wind from their ridiculous speed, and Harry’s enchantment-assisted fingers gripping the broomstick were merely resisting the decelerating drag of moving way faster than terminal velocity, \emph{that} was when Harry actually thought all that stuff about Newtonian mechanics and Aristotelian physics and broomsticks and rocketry and the importance of curiosity and how he was never going to do anything this Gryffindor ever again or at least not until after he learned the Dark Lord’s secret of immortality and \emph{why} had he listened to Professor Quirinus “\emph{I asssure you, boy, I would not attempt thisss if I did not anticipate my own ssurvival}” Quirrell instead of Professor Michael “Son, if you try anything to do with rockets on your own, I mean \emph{anything whatsoever} without a trained professonal watching, you will die and that will make Mum sad” Verres-Evans.
\sbreak
“\shout{What?}” shrieked Amelia at the mirror.
\sbreak
The wind had died down to a bearable level as the air resistance slowed them, giving Harry plenty of opportunity to listen to the buzzing, ringing sound that seemed to fill his whole brain.

Professor Quirrell had been supposed to cast a Quieting Charm on the rocket exhaust...\ apparently there were limits to what Quieting Charms could do...\ in retrospect, Harry should have Transfigured a pair of earplugs, not just trusted to the Quieting Charm, though that probably wouldn’t have been enough either...

Well, magical healing probably had something to treat permanent hearing damage.

No, really, magical healing probably had something to treat that. He’d seen students go to Madam Pomfrey with injuries that sounded a lot worse...

\emph{Is there some way of transplanting an imaginary personality to someone else’s head?} asked Hufflepuff. \emph{I don’t want to live in yours anymore.}

Harry shoved it all into the back of his mind, there really wasn’t anything he could do about it right now. Was there anything he \emph{should} be worrying about—

Then Harry glanced behind him, remembering for the first time to check whether Bellatrix or Professor Quirrell had been blown off the broomstick.

But the green snake was still in its harness, and the emaciated woman was still clinging to the broomstick, her face still charged with unhealthy color and her eyes still bright and dangerous. Her shoulders were shaking like she was laughing hysterically, and her lips were moving as though to shout, but no sound was coming out—

Oh, right.

Harry took off the hood of his cloak, tapped his ears to let her know he couldn’t hear.

Whereupon Bellatrix grasped her wand, pointed it at Harry, and suddenly the ringing in his ears diminished, he could hear her.

A moment later he regretted it; the imprecations she was screaming at Azkaban, Dementors, Aurors, Dumbledore, Lucius, Bartemy Couch, something called the Order of the Phoenix, and all who stood in the way of her Dark Lord, et cetera, were not suitable for younger and more sensitive listeners; and her laughter was hurting his newly healed ears.

“Enough, Bella,” Harry finally said, and her voice stopped on the instant.

There was a pause. Harry pulled the Cloak back over his head, just on general principles; and realized in the same instant that they might have telescopes down there or something, in retrospect pulling down his hood for even a moment had been an incredibly dumb move, he hoped the whole mission didn’t end up failing because of that one error...

\emph{We’re not really cut out for this, are we?} observed Slytherin.

\emph{Hey,} Hufflepuff objected in sheer reflex, \emph{we can’t expect to do anything perfectly the first time, we probably just need more practice \shout{forget I said that}.}

Harry looked back again, saw Bellatrix looking around with a puzzled, wondering look on her face. Her head kept turning, turning.

And finally Bellatrix said, her voice now lower, “My Lord, where are we?”

\emph{What do you mean?} was what Harry wanted to say, but the Dark Lord would never admit to not understanding anything, so Harry replied, dryly, “We are on a broomstick.”

\emph{Does she think she’s dead, that this is Heaven?}

Bellatrix’s hands were still chained to the broomstick, so it was only a finger that came up and pointed when she said, “What is \emph{that?}”

Harry followed the direction of her finger and saw...\ nothing in particular, actually...

Then Harry realized. After they’d gone up high enough, there hadn’t been any clouds to obscure it any more.

“That is the Sun, dear Bella.”

It came out remarkably controlled, the Dark Lord sounding perfectly calm and maybe a little impatient with her, even as the tears started down Harry’s cheeks.

In the endless cold, in the pitch blackness, the Sun would surely have been...

A happy memory...

Bellatrix’s head kept turning.

“And the fluffy things?” she said.

“Clouds.”

There was a pause, and then Bellatrix said, “But what \emph{are} they?”

Harry didn’t answer her, there was no way his voice could have been steady, would have been steady, it was all he could do to keep his breathing perfectly regular while he cried.

After a while, Bellatrix breathed, so softly Harry almost didn’t hear, “Pretty...”

Her face slowly relaxed, the color leaving its paleness almost as quickly as it had arrived.

Her skeletal body slumped down against the broomstick.

The borrowed wand dangled lifelessly from the strap attached to her unmoving hand.

\shout{You have got to be kidding—}

Harry’s mind remembered then, the Pepper-Up potion came at a cost; Bellatrix would \emph{ssleep for a conssiderable time,} Professor Quirrell had said.

And in the same instant another part of Harry became utterly convinced, looking back at the chalk-white emaciated woman, seeming deader in the bright sunlight than anything Harry had ever seen alive, that she \emph{was} dead, that she had just uttered her last word, that Professor Quirrell had misjudged the dosage—

—or deliberately sacrificed Bellatrix to guard their own escape—

\emph{Is she breathing?}

Harry couldn’t see if she was breathing.

There was no way, on the broomstick, to reach back and take her pulse.

Harry looked ahead to make sure they weren’t about to run into any flying rocks, kept on steering the broomstick toward the Sun, the invisible boy and the possibly dead woman riding off into the afternoon, while his fingers gripped the wood so hard they turned white.

He couldn’t reach back and perform artificial respiration.

He couldn’t use anything from his healer’s kit.

\emph{Trust Professor Quirrell to have not endangered her?}

Strange, it was strange, that even genuinely believing that Professor Quirrell hadn’t meant to kill the Auror (for it \emph{would} have been stupid), thinking of the Defense Professor’s reassurances no longer felt reassuring.

Then it occurred to Harry that he had yet to check—

Harry looked back, and hissed, “\emph{Teacher?}”

The snake did not stir within its harness, and said no word.

...maybe the snake, not being an actual rider, hadn’t been protected from the acceleration. Or maybe coming that close to the Dementors without a shield, even for a moment in Animagus form, had knocked out the Defense Professor.

That wasn’t good.

It was to have been Professor Quirrell who told Harry when it was safe to use the portkey.

Harry steered the broomstick with whitened fingers, and thought, he thought very hard for a small unmeasured length of time, during which Bellatrix might or might not have been breathing, during which Professor Quirrell himself might have already been not-breathing for a while.

And Harry decided that while it was possible to recover from the error of wasting the portkey in his possession, it was not possible to recover from the error of letting a brain go too long without oxygen.

So Harry took the next portkey in the sequence from his pouch, as he slowed his broomstick to a halt in the bright blue air (Harry didn’t know, when he thought about it, whether a portkey’s ability to adjust for the Earth’s rotation also included the ability to match velocity in general with its new surroundings), touched the portkey to the broomstick, and...

Harry paused, still holding the twig, the mate of the twig he had snapped what seemed like two weeks ago. He was feeling a sudden reluctance; his brain seemed to have learned the rule, by some purely neural process of negative reinforcement, that Snapping Twigs Is A Bad Idea.

But that wasn’t actually logical, so Harry snapped the twig anyway.
\sbreak
There was a thunderous boom from behind the nearby metal door, causing Amelia to drop the mirror she was holding and spin around with her wand in hand, and then that door burst open to reveal Albus Dumbledore, standing there in front of a great smoking hole in the prison wall.

“Amelia,” said the old wizard. There was no trace of any of his customary levity, his eyes were hard as sapphires beneath his half-moon glasses. “I must leave Azkaban and I must do so \emph{now}. Is there any faster way than a broomstick to get beyond the wards?”

“No—”

“Then I require your fastest broomstick, at once!”

The place where Amelia \emph{wanted} to be was with the Auror who had been injured by that Fiendfyre or whatever it had been.

What she \emph{needed} to do was find out what Dumbledore knew.

“You!” the old witch barked at the team around her. “Keep clearing the corridors until you’re at bottom, they may not all have escaped yet!” And then, to the old wizard, “Two broomsticks. You can brief me once we’re in the air.”

There was a match of stares, but not a long one.
\sbreak
A sickeningly hard yank caught at Harry’s abdomen, considerably harder than the yank that had transported him to Azkaban, and this time the distance traversed was great enough that he could hear an instant of silence, watch the unseeable space between spaces, in the crack between one place and another.
\sbreak
The Sun, which had shone on the two only briefly, was swiftly occluded by a raincloud as they shot away from Azkaban, in the direction of the wind and faster than the wind.

“Who’s behind it?” shouted Amelia to the broomstick flying a pace away from her.

“One of two people,” Dumbledore said back, “I know not, at this instant, who. If the first, then we are in trouble. If the second, we are all in far greater trouble.”

Amelia didn’t spare any breath for sighs. “When will you know?”

The old wizard’s voice was grim, quiet and yet somehow rising above the wind. “Three things they need for perfection, if it is that one: The flesh of the Dark Lord’s most faithful servant, the blood of the Dark Lord’s greatest foe, and access to a certain grave. I had thought Harry Potter safe, with their attempt on Azkaban all but failed—though I still set guards upon him—but now I am fearful indeed. They have access to Time, someone with a Time-Turner is sending messages for them; and I suspect the kidnap attempt on Harry Potter has already taken place some hours ago. Which is why \emph{we} have not heard about it, being in Azkaban where Time cannot knot itself. That past came after our own future, you see.”

“And if it is the other?” shouted Amelia. What she had heard already was worrying enough; that sounded like the darkest of Dark rituals, and centering on the dead Dark Lord himself.

The old wizard, his face now even grimmer, said nothing, only shook his head.
\sbreak
When the portkey’s yank had subsided, the Sun was only just peeking over the horizon, looking more like dawn than sunset, as their broom hovered low above a brief expanse of dark-orange rock and sand, arranged into lumpy hills like someone had kneaded the land’s dough a few times and then forgotten to roll it flat. In the near distance, waves rolled past in an endless vista of water, though the ground over which the broomstick hovered was above sea level by meters at the least.

Harry blinked at the dawn colors, and then realized the portkey had been international.

“Oy!” came a brisk, female shout from behind him, and Harry spun the broomstick to look. A middle-aged lady was holding up one hand to her mouth in a deliberate calling gesture, and bustling forward. Her kindly features, narrow eyes, and umber skin marked a race unfamiliar to Harry; she was clad in brilliant purple robes of a style Harry had never seen before; and when her lips opened again she spoke with an accent that Harry couldn’t place, for he was not widely traveled. “Where were you? You’re two hours late! I almost gave up on the lot of you...\ hello?”

There was a brief pause. Harry’s thoughts seemed to be moving oddly, too slow, everything felt distant, like there was a thick pane of glass between himself and the world, and another thick pane of glass between himself and his feelings, so that he could see, but not touch. It had come over him upon seeing the dawn’s light and the kindly witch, and thinking that it all seemed like a proper end to the adventure.

Then the witch was rushing forward and drawing her wand; a muttered word severed the cuffs that bound the emaciated woman to the broomstick, and Bellatrix was being floated down onto the sandy rock with her skeletal arms and pale legs dangling like lifeless things. “Oh, Merlin,” whispered the witch, “Merlin, Merlin, Merlin...”

\emph{She appears concerned,} thought an abstract, distant thing between two panes of glass. \emph{Is that what a real healer would say, or is it what someone told to put on a performance would say?}

As though it wasn’t Harry who spoke, but some other part of himself behind yet another pane of glass, a whisper came from his lips. “The green snake on her back is an Animagus.” Not high the whisper, not cold, only quiet. “He is unconscious.”

The witch’s head twitched up, to look at where that voice had seemed to speak out of empty air, and then looked back down at Bellatrix. “You’re not Mister Jaffe.”

“That would be the Animagus,” whispered Harry’s lips. \emph{Oh,} thought the Harry behind glass, listening to the sound of his own lips, \emph{that makes sense; Professor Quirrell must have used a different name.}

“Since when is \emph{he} a—bah, forget it.” The witch laid her wand on the snake’s nose for a moment, then shook her head sharply. “Nothing wrong with him that a day’s rest won’t cure. \emph{Her...}”

“Can you wake him up now?” whispered Harry’s lips. \emph{Is that a good idea?} thought Harry, but his lips definitely seemed to think so.

Again the sharp headshake. “If an Innervate didn’t work on him—” began the witch.

“I did not attempt one,” whispered Harry’s lips.

“What? Why—oh, never mind. \emph{Innervate.}”

There was a pause, and then a snake slowly crawled out of its harness. Slowly the green head came up, looked around.

A blur later, Professor Quirrell was standing, and a moment later had sagged to his knees.

“Lie down,” said the witch without looking up from Bellatrix. “That you in there, Jeremy?”

“Yes,” said the Defense Professor rather hoarsely, as he carefully laid himself down on a relatively flat patch of sandy orange rock. He was not so pale as Bellatrix, but his face was bloodless in the dim dawn light. “Salutations, Miss Camblebunker.”

“I told you,” said the witch, sharpness in her voice and a slight smile on her face, “call me Crystal, this isn’t Britain and we’ll have none of your formality here. \emph{And} it’s Doctor now, not Miss.”

“My apologies, Doctor Camblebunker.” This was followed by a dry chuckle.

The witch’s smile grew a little wider, her voice that much sharper. “Who’s your friend?”

“You don’t need to know.” The Defense Professor’s eyes were closed, where he lay on the ground.

“How wrong did it go?”

Very dryly indeed: “You can read about it tomorrow in any newspaper with an international section.”

The witch’s wand was tapping here, there, poking and prodding all over Bellatrix’s body. “I missed you, Jeremy.”

“Truly?” said the Defense Professor, sounding slightly surprised.

“Not even a tiny little bit. If I didn’t owe you—”

The Defense Professor started to laugh, and then it turned into more of a coughing fit.

\emph{What do you think?} said Slytherin to the Inner Critic, while Harry listened from behind the glass walls. \emph{Performance, or reality?}

\emph{Can’t tell,} said Harry’s Inner Critic. \emph{I’m not in top critical form right now.}

\emph{Can anyone think of a good probe to gather more information?} said Ravenclaw.

Again that whisper from the empty air above the broomstick: “What is the chance of undoing all that was done to her?”

“Oh, let’s see. Legilimency and unknown Dark rituals, ten years for that to set in place, followed by ten years of Dementor exposure? Undo\emph{ that?} You’re out of your skull, Mister Whoever-You-Are. The question is whether there’s anything \emph{left,} and I’d call that maybe one chance in three—” The witch suddenly cut herself off. Her voice, when it spoke again, was quieter. “If you were her friend, before...\ then no, you’re never getting her back. Best understand that now.”

\emph{I’m voting that this is a performance,} said the Inner Critic. \emph{She wouldn’t just blurt all that out in response to one question unless she was looking for an opportunity.}

\emph{Noted, but I’m putting a low weight of confidence on that,} said Ravenclaw. \emph{It’s very hard not to let your suspicions control your perceptions when you’re trying to weigh evidence that subtle.}

“What potion did you give her?” the witch said after opening Bellatrix’s mouth and peering inside, her wand flashing multiple colors of illumination.

The man lying on the ground calmly said, “Pepper-Up—”

“\emph{Were you out of your mind?}”

Again the coughing laugh.

“She’ll sleep for a week if she’s lucky,” the witch said, and clucked her tongue. “I’ll owl you when she opens her eyes, I suppose, so you can come back and talk her into that Unbreakable Vow. Have you got anything to stop her from killing me on the spot, if she manages to even move for another month?”

The Defense Professor, eyes still closed, took a sheet of paper from his robes; a moment later, words began to appear on it, accompanied by tiny wisps of smoke. When the smoke had stopped rising, the paper floated over toward the woman.

The woman looked over the paper with raised eyebrows, gave a sardonic snort. “This had better work, Jeremy, or my last will and testament says that my whole estate goes into putting a bounty on your head. Speaking of which—”

The Defense Professor reached again into his robes and tossed the witch a bag that made a clinking sound. The witch caught it, weighed it, made a pleased sound.

Then she stood up, and the pale skeletal woman floated off the ground beside her. “I’m heading back,” said the witch. “I can’t start my work here.”

“Wait,” said the Defense Professor, and with a gesture retrieved his wand from Bellatrix’s hand and harness. Then his hand pointed the wand at Bellatrix, and moved in a small circular gesture, accompanied by a quiet, “\emph{Obliviate}.”

“\emph{That’s it},” snapped the witch, “I’m taking her out of here before anyone does her any more damage—” One arm came around to hug the bony form of Bellatrix Black to her side, and they both disappeared with the loud \shout{pop}! of Apparition.

And there was silence in that lumpy place, but for the gentle rush of the passing waves, and a little breath of wind.

\emph{I think the performance is finished,} said the Inner Critic. \emph{I give it two and a half out of five stars. She’s probably not a very experienced actor.}

\emph{I wonder if a real healer would seem more fake than an actor told to play one?} mused Ravenclaw.\emph{\\}

Like watching a television show, that was how it felt, like watching a television show whose characters you didn’t particularly empathize with, that was all that could be seen and felt from behind the glass walls.

Somehow, Harry managed to move his lips himself, send his own voice out into the still dawn air, and then was surprised to hear his own question. “How many different people are you, anyway?”

The pale man lying on the ground didn’t laugh, but from the broomstick Harry’s eyes saw the sides of Professor Quirrell’s lips curling up, the edge of that familiar sardonic smile. “I cannot say that I bothered keeping count. How many are you?”

It shouldn’t have shaken the inner Harry so much, hearing that response, and yet he felt—he felt—unstable, like his own center had been subtracted—

Oh.

“Excuse me,” said Harry’s voice. It now sounded as distant and detached as the fading Harry felt. “I’m going to faint in a few seconds, I think.”

“Use the fourth portkey I gave you, the one I said was our fallback refuge,” said the man lying on the ground, calmly but swiftly. “It will be safer there. And continue wearing your cloak.”

Harry’s free hand retrieved another twig from his pouch and snapped it.

There was another portkey yank, internationally long, and then he was somewhere black.

“\emph{Lumos},” said Harry’s lips, some part of him looking out for the safety of the whole.

He was inside what looked like a Muggle warehouse, a deserted one.

Harry’s legs climbed off the broomstick, lay on the floor. His eyes closed, and some tidy fraction of self willed his light to fail, before the darkness took him.
\sbreak
“Where will you go?” yelled Amelia. They were almost at the edge of the wards.

“Backward in time to protect Harry Potter,” said the old wizard, and before Amelia could even open her lips to ask if he wanted help, she felt the boundary of the wards as they crossed them.

There was a pop of Apparition, and the wizard and the phoenix vanished, leaving behind the borrowed broomstick.

