\chapter{Reciprocation}

\lettrine{P}{etunia} Evans-Verres’s lips were trembling and her eyes were tearing up as Harry hugged her midsection on Platform Nine of King’s Cross Station. “Are you sure you don’t want me to come with you, Harry?”

Harry glanced over to his father Michael Verres-Evans, who was looking stereotypically stern-but-proud, and then back to his mother, who really did look rather…discomposed. “Mum, I know you don’t like the wizarding world very much. You don’t have to come with. I mean it.”

Petunia winced. “Harry, you shouldn’t worry about me, I’m your mother and if you need someone with you—”

“Mum, I’m going to be on my own at Hogwarts for \emph{months} and \emph{months.} If I can’t manage a train platform alone, better to find out sooner rather than later so we can abort.” He lowered his voice to a whisper. “Besides, Mum, they all love me over there. If I have any problems, all I need to do is take off my sweatband,” Harry tapped the exercise band covering his scar, “and I’ll have \emph{way} more help than I can handle.”

“Oh, Harry,” Petunia whispered. She knelt down and hugged him hard, face to face, their cheeks resting against each other. Harry could feel her ragged breathing, and then he heard a muffled sob escape. “Oh, Harry, I do love you, always remember that.”

\emph{It’s like she’s afraid she’ll never see me again,} the thought popped into Harry’s head. He knew the thought was true but he didn’t know why Mum was so afraid.

So he made a guess. “Mum, you know that I’m not going to turn into your sister just because I’m learning magic, right? I’ll do any magic you ask for—if I can, I mean—or if you want me \emph{not} to use any magic around the house, I’ll do that too, I promise I’ll never let magic come between us—”

A tight hug cut off his words. “You have a good heart,” his mother whispered into his ear. “A very good heart, my son.”

Harry choked up himself a little, then.

His mother released him, and stood up. She took a handkerchief out of her handbag, and with a trembling hand dabbed at the running make-up around her eyes.

There were no questions about his father accompanying him to the magical side of King’s Cross Station. Dad had trouble just looking at Harry’s trunk directly. Magic ran in families, and Michael Verres-Evans couldn’t even walk.

So instead his father just cleared his throat. “Good luck at school, Harry,” he said. “Do you think I bought you enough books?”

Harry had explained to his father about how he thought this might be his big chance to do something really revolutionary and important, and Professor Verres-Evans had nodded and dumped his extremely busy schedule for two solid days in order to go on the Greatest Second-hand Bookshop Raid Ever, which had covered four cities and produced \emph{thirty} boxes of science books now sitting in the cavern level of Harry’s trunk. Most of the books had gone for a pound or two, but some of them definitely \emph{hadn’t,} like the very latest \emph{Handbook of Chemistry and Physics} or the complete 1972 set of the \emph{Encyclopædia Britannica.} His father had tried to block Harry off from seeing the till displays but Harry figured his father must have spent \emph{at least} a thousand pounds. Harry had said to his father that he would pay him back as soon as he figured out how to convert wizarding gold into Muggle money, and his father had told him to go boil his head.

And then his father had asked him: \emph{Do you think I bought you enough books?} It was quite clear what answer Dad wanted to hear.

Harry’s throat was hoarse, for some reason. “You can never have enough books,” he recited the Verres family motto, and his father knelt down and gave him a quick, firm embrace. “But you \emph{certainly} tried,” Harry said, and felt himself choking up again. “It was a really, really, \emph{really} good try.”

His Dad straightened. “So…” he said. “Do \emph{you} see a Platform Nine-and-Three-Quarters?”

King’s Cross Station was huge and busy, with walls and floors paved with ordinary dirt-stained tiles. It was full of ordinary people hurrying about their ordinary business, having ordinary conversations which generated lots and lots of ordinary noise. King’s Cross Station had a Platform Nine (which they were standing on) and a Platform Ten (right next to it) but there was nothing between Platform Nine and Platform Ten except a thin, unpromising barrier wall. A great skylight overhead let in plenty of light to illuminate the total lack whatsoever of any Platform Nine-and-Three-Quarters.

Harry stared around until his eyes watered, thinking, \emph{come on, mage-sight, come on, mage-sight}, but absolutely nothing appeared to him. He thought about taking out his wand and waving it, but Professor McGonagall had warned him against using his wand. Plus if there was another shower of multicoloured sparks that might lead to being arrested for setting off fireworks inside a train station. And that was assuming his wand didn’t decide to do something else, like blowing up all of King’s Cross. Harry had only lightly skimmed his schoolbooks (though that skim was quite bizarre enough) in a very quick effort to determine what sort of science books to buy over the next 48 hours.

Well, he had—Harry glanced at his watch—one whole hour to figure it out, since he was supposed to be on the train at eleven. Maybe this was the equivalent of an IQ test and the stupid kids couldn’t become wizards. (And the amount of extra time you gave yourself would determine your Conscientiousness, which was the second most important factor in scholarly success.)

“I’ll figure it out,” Harry said to his waiting parents. “It’s probably some sort of test thingy.”

His father frowned. “Hm…maybe look for a trail of mixed footprints on the ground, leading somewhere that doesn’t seem to make sense—”

“\emph{Dad!}” Harry said. “Stop that! I haven’t even \emph{tried} to figure it out on my own!” It was a very good suggestion, too, which was worse.

“Sorry,” his father apologised.

“Ah…” Harry’s mother said. “I don’t think they would do that to a student, do you? Are you sure Professor McGonagall didn’t tell you anything?”

“Maybe she was distracted,” Harry said without thinking.

“\emph{Harry!}” hissed his father and mother in unison. “\emph{What did you do?}”

“I, um—” Harry swallowed. “Look, we don’t have time for this now—”

“\emph{Harry!}”

“I mean it! We don’t have time for this now! Because it’s a really long story and I’ve got to figure out how to get to school!”

His mother had a hand over her face. “How bad was it?”

“I, ah,” \emph{I can’t talk about that for reasons of National Security,} “about half as bad as the Incident with the Science Project?”

“\emph{Harry!}”

“I, er, oh look there are some people with an owl I’ll go ask them how to get in!” and Harry ran away from his parents towards the family of fiery redheads, his trunk automatically slithering behind him.

The plump woman looked to him as he arrived. “Hello, dear. First time at Hogwarts? Ron’s new, too—” and then she peered closely at him. “\emph{Harry Potter?}”

Four boys and a red-headed girl and an owl all swung around and then froze in place.

“Oh, \emph{come on!}” Harry protested. He’d been planning to go as Harry Verres at least until he got to Hogwarts. “I bought a sweatband and everything! How come you know who I am?”

“Yes,” Harry’s father said, coming up behind him with long easy strides, “how \emph{do} you know who he is?” His voice indicated a certain dread.

“Your picture was in the newspapers,” said one of two identical-looking twins.

“\shout{Harry!}”

“\emph{Dad!} It’s not like that! It’s ’cause I defeated the Dark Lord You-Know-Who when I was one year old!”

“\shout{What?}”

“Mum can explain.”

“\shout{What?}”

“Ah…Michael dear, there are certain things I thought it would be best not to bother you with until now—”

“Excuse me,” Harry said to the red-headed family who were all staring at him, “but it would be quite extremely helpful if you could tell me how to get to Platform Nine-and-Three-Quarters \emph{right now}.”

“Ah…” said the woman. She raised a hand and pointed at the wall between platforms. “Just walk straight at the barrier between platforms nine and ten. Don’t stop and don’t be scared you’ll crash into it, that’s very important. Best do it at a bit of a run if you’re nervous.”

“And whatever you do, don’t think of an elephant.”

“\emph{George!} Ignore him, Harry dear, there’s no reason not to think of an elephant.”

“I’m Fred, Mum, not George—”

“Thanks!” Harry said and took off at a run towards the barrier—

Wait a minute, it wouldn’t work \emph{unless he believed in it?}

It was at times like this that Harry hated his mind for actually working fast enough to realise that this was a case where “resonant doubt” applied, that is, if he’d started out thinking that he would go through the barrier he’d have been fine, only now he was worried about whether he sufficiently \emph{believed} he’d go through the barrier, which meant that he actually \emph{was} worried about crashing into it—

“\emph{Harry! Get back here, you have some explaining to do!}” That was his Dad.

Harry shut his eyes and ignored everything he knew about justified credibility and just tried to believe \emph{really hard} that he’d go through the barrier and—

—the sounds around him changed.

Harry opened his eyes and stumbled to a halt, feeling vaguely dirtied by having made a deliberate effort to believe something.

He was standing in a bright, open-air platform next to a single huge train, fourteen long carriages headed up by a massive scarlet-metal steam engine with a tall chimney that promised death to air quality. The platform was already lightly crowded (even though Harry was a full hour early); dozens of children and their parents swarmed around benches, tables, and various hawkers and stalls.

It went entirely without saying that there was no such place in King’s Cross Station and no room to hide it.

\emph{Okay, so either (a)~I just teleported somewhere else entirely (b)~they can fold space like nobody’s business or (c)~they are simply ignoring all the rules.}

There was a slithering sound behind him, and Harry turned around to observe that his trunk had indeed followed him on its small clawed tentacles. Apparently, for magical purposes, his luggage had also managed to believe with sufficient strength to pass through the barrier. That was actually a little disturbing when Harry started thinking about it.

A moment later, the youngest-looking red-haired boy came through the iron archway (iron archway?) at a run, pulling his trunk behind him on a lead and nearly crashing into Harry. Harry, feeling stupid for having stayed around, quickly began moving away from the landing area, and the red-haired boy followed him, yanking hard on his trunk’s lead in order to keep up. A moment later, a white owl fluttered through the archway and came to rest on the boy’s shoulder.

“Cor,” said the red-haired boy, “are you \emph{really} Harry Potter?”

\emph{Not this again.} “I have no logical way of knowing that for certain. My parents raised me to \emph{believe} that my name was Harry James Potter-Evans-Verres, and many people here have told me that I \emph{look} like my parents, I mean my other parents, but,” Harry frowned, realising, “for all \emph{I} know, there could easily be spells to polymorph a child into a specified appearance—”

“Er, what, mate?”

\emph{Not headed for Ravenclaw, I take it.} “Yes, I’m Harry Potter.”

“I’m Ron Weasley,” said the tall skinny freckled long-nosed kid, and stuck out a hand, which Harry politely shook as they walked. The owl gave Harry an oddly measured and courteous hoot (actually more of an eehhhhh sound, which surprised Harry).

At this point Harry realised the potential for imminent catastrophe. “Just a second,” he said to Ron, and opened one of the drawers of his trunk, the one that if he recalled correctly was for Winter Clothes—it was—and then he found the lightest scarf he owned, underneath his winter coat. Harry took off his sweatband, and just as quickly unfolded the scarf and tied it around his face. It was a little hot, especially in the summer, but Harry could live with that.

Then he shut that drawer and pulled out another drawer and drew forth black wizarding robes, which he shrugged over his head, now that he was out of Muggle territory.

“There,” Harry said. The sound came out slightly muffled through the scarf over his face. He turned to Ron. “How do I look? Stupid, I know, but am I identifiable as Harry Potter?”

“Er,” Ron said. He closed his mouth, which had been open. “Not really, Harry.”

“Very good,” Harry said. “However, so as not to obviate the point of the whole exercise, you will henceforth address me as,” Verres might not work any more, “Mr~Spoo.”

“Okay, Harry,” Ron said uncertainly.

\emph{The Force is not particularly strong in this one.} “Call…me…Mister…Spoo.”

“Okay, Mister Spoo—” Ron stopped. “I can’t do that, it makes me feel stupid.”

\emph{That’s not just a feeling.} “Okay. \emph{You} pick a name.”

“Mr~Cannon,” Ron said at once. “For the Chudley Cannons.”

“Ah…” Harry knew he was going to terribly regret asking this. “Who or what are the Chudley Cannons?”

“\emph{Who’re the Chudley Cannons?} Only the most brilliant team in the whole history of Quidditch! Sure, they finished at the bottom of the league last year, but—”

“What’s Quidditch?”

Asking this was also a mistake.

“So let me get this straight,” Harry said as it seemed that Ron’s explanation (with associated hand gestures) was winding down. “Catching the Snitch is worth \emph{one hundred and fifty points?}”

“Yeah—”

“How many ten-point goals does one side usually score \emph{not} counting the Snitch?”

“Um, maybe fifteen or twenty in professional games—”

“That’s just wrong. That violates every possible rule of game design. Look, the rest of this game sounds like it might make sense, sort of, for a sport I mean, but you’re basically saying that catching the Snitch overwhelms almost any ordinary point spread. The two Seekers are up there flying around looking for the Snitch and usually not interacting with anyone else, spotting the Snitch first is going to be mostly luck—”

“It’s not luck!” protested Ron. “You’ve got to keep your eyes moving in the right pattern—”

“That’s not \emph{interactive,} there’s no back-and-forth with the other player and how much fun is it to watch someone incredibly good at moving their eyes? And then whichever Seeker gets lucky swoops in and grabs the Snitch and makes everyone else’s work moot. It’s like someone took a real game and grafted on this pointless extra position so that you could be the Most Important Player without needing to really get involved or learn the rest of it. Who was the first Seeker, the King’s idiot son who wanted to play Quidditch but couldn’t understand the rules?” Actually, now that Harry thought about it, that seemed like a surprisingly good hypothesis. Put him on a broomstick and tell him to catch the shiny thing…

Ron’s face pulled into a scowl. “If you don’t like Quidditch, you don’t have to make fun of it!”

“If you can’t criticise, you can’t optimise. I’m suggesting how to \emph{improve the game.} And it’s very simple. Get rid of the Snitch.”

“They won’t change the game just ’cause \emph{you} say so!”

“I \emph{am} the Boy-Who-Lived, you know. People will listen to me. And maybe if I can persuade them to change the game at Hogwarts, the innovation will spread.”

A look of absolute horror was spreading over Ron’s face. “But, but if you get rid of the Snitch, how will anyone know when the game ends?”

“\emph{Buy…a…clock.} It would be a lot fairer than having the game sometimes end after ten minutes and sometimes not end for hours, and the schedule would be a lot more predictable for the spectators, too.” Harry sighed. “Oh, stop giving me that look of absolute horror, I probably won’t \emph{actually} take the time to destroy this pathetic excuse for a national sport and remake it stronger and smarter in my own image. I’ve got way, way, \emph{way} more important stuff to worry about.” Harry looked thoughtful. “Then again, it wouldn’t \emph{take} much time to write up the Ninety-Five Theses of the Snitchless Reformation and nail it to a church door—”

“Potter,” drawled a young boy’s voice, “\emph{what} is that on your face and \emph{what} is standing next to you?”

Ron’s look of horror was replaced by utter hatred. “\emph{You!}”

Harry turned his head; and indeed it was Draco Malfoy, who might have been forced to wear standard school robes, but was making up for that with a trunk looking at least as magical and far more elegant than Harry’s own, decorated in silver and emeralds and bearing what Harry guessed to be the Malfoy family crest, a beautiful fanged serpent over crossed ivory wands.

“Draco!” Harry said. “Er, or Malfoy if you prefer, though that kind of sounds like Lucius to me. I’m glad to see you’re doing so well after, um, our last meeting. This is Ron Weasley. And I’m trying to go incognito, so call me, eh,” Harry looked down at his robes, “Mister Black.”

“\emph{Harry!}” hissed Ron. “You can’t use \emph{that} name!”

Harry blinked. “Why not?” It \emph{sounded} nicely dark, like an international man of mystery—

“I’d say it’s a \emph{fine} name,” said Draco, “but it belongs to the Noble and Most Ancient House of Black. I’ll call you Mr~Silver.”

“\emph{You} get away from…from Mr~Gold,” Ron said coldly, and took a forward step. “He doesn’t need to talk to the likes of you!”

Harry raised a placating hand. “I’ll go by Mr~Bronze, thanks for the naming schema. And, Ron, um,” Harry struggled to find a way to say this, “I’m glad you’re so…enthusiastic about protecting me, but I don’t particularly mind talking to Draco—”

This was apparently the last straw for Ron, who spun on Harry with eyes now aflame with outrage. “\emph{What?} Do you \emph{know} who this is?”

“Yes, Ron,” Harry said, “you may remember that I called him Draco without him needing to introduce himself.”

Draco sniggered. Then his eyes lit on the white owl on Ron’s shoulder. “Oh, what’s \emph{this?}” Draco said in a drawl rich with malice. “Where’s the famous Weasley family rat?”

“Buried in the backyard,” Ron said coldly.

“Aw, how sad. Pot…ah, Mr~Bronze, I should mention that the Weasley family is widely agreed to have \emph{the best pet story ever}. Want to tell it, Weasley?”

Ron’s face contorted. “You wouldn’t think it was funny if it happened to \emph{your} family!”

“Oh,” Draco purred, “but it wouldn’t ever \emph{happen} to the Malfoys.”

Ron’s hands clenched into fists—

“That’s enough,” Harry said, putting as much quiet authority into the voice as he could manage. It was clear that whatever this was about, it was a painful memory for the red-haired kid. “If Ron doesn’t want to talk about it, he doesn’t have to talk about it, and I’d ask that you not talk about it either.”

Draco turned a surprised look on Harry, and Ron nodded. “That’s right, Harry! I mean Mr~Bronze! You see what kind of person he is? Now tell him to go away!”

Harry counted to ten inside his head, which for him was a very quick \emph{12345678910}—an odd habit left over from the age of five when his mother had first instructed him to do it, and Harry had reasoned that his way was faster and ought to be just as effective. “I’m not telling him to go away,” Harry said calmly. “He’s welcome to talk to me if he wants.”

“Well, I don’t intend to hang around with anyone who hangs around with Draco Malfoy,” Ron announced coldly.

Harry shrugged. “That’s up to you. \emph{I} don’t intend to let anyone say who I can and can’t hang around with.” Silently chanting, \emph{please go away, please go away…}

Ron’s face went blank with surprise, like he’d actually expected that line to work. Then Ron spun about, yanked his luggage’s lead and stormed off down the platform.

“If you didn’t like him,” Draco said curiously, “why didn’t you just walk away?”

“Um…his mother helped me figure out how to get to this platform from King’s Cross Station, so it was kind of hard to tell him to get lost. And it’s not that I \emph{hate} this Ron guy,” Harry said, “I just, just…” Harry searched for words.

“Don’t see any reason for him to exist?” offered Draco.

“Pretty much.”

“Anyway, Potter…if you really were raised by Muggles—” Draco paused here, as if waiting for a denial, but Harry didn’t say anything “—then you mightn’t know what it’s like to be famous. People want to take up \emph{all} of our time. You \emph{have} to learn to say no.”

Harry nodded, putting a thoughtful look on his face. “That sounds like good advice.”

“If you try to be nice, you just end up spending the most time with the pushiest ones. Decide who you \emph{want} to spend time with and make everyone else leave. You’re just getting here, Potter, so everyone’s going to judge you by who they see you with, and you don’t want to be seen with the likes of Ron Weasley.”

Harry nodded again. “If you don’t mind my asking, how did you recognise me?”

“\emph{Mister Bronze},” Draco drawled, “I \emph{have} met you, remember. I saw someone going around with a scarf wrapped around his head, looking absolutely ridiculous. So I took a \emph{guess.}”

Harry bowed his head, accepting the compliment. “I’m \emph{terribly} sorry about that,” Harry said. “Our first meeting, I mean. I didn’t mean to embarrass you in front of Lucius.”

Draco waved it off while giving Harry an odd look. “I just wish Father could have come in while \emph{you} were flattering \emph{me}—” Draco laughed. “But thank \emph{you} for what you said to Father. If not for that, I might’ve had a harder time explaining.”

Harry swept a deeper bow. “And thank \emph{you} for reciprocating with what you said to Professor McGonagall.”

“You’re welcome. Though one of the assistants must’ve sworn her closest friend to absolute secrecy, because Father says there’re \emph{weird rumours} going around, like you and I got in a fight or something.”

“Ouch,” Harry said, wincing. “I’m \emph{really} sorry—”

“No, we’re used to it, Merlin knows there’s lots of rumours about the Malfoy family already.”

Harry nodded. “I’m glad to hear you’re not in trouble.”

Draco smirked. “Father has, um, a \emph{refined} sense of humour, but he \emph{does} understand making friends. He understands it \emph{very} well. He made me repeat that before I went to bed every night for the last month, ‘I will make friends at Hogwarts.’ When I explained everything to him and he saw that’s what I was doing, he bought me an ice-cream.”

Harry’s jaw dropped. “\emph{You managed to spin that into an ice-cream?}”

Draco nodded, looking every bit as smug as the feat deserved. “Well, father \emph{knew} what I was doing, of course, but he’s the one who taught me \emph{how} to do it, and if I grin the right way \emph{while} I’m doing it, that makes it a father-son thing and then he \emph{has} to buy me an ice-cream or I’ll give him this sort of sad look, like I think I must have disappointed him.”

Harry eyed Draco calculatingly, sensing the presence of another master. “You’ve had \emph{lessons} on how to manipulate people?”

“Of course,” Draco said proudly. “I’m a \emph{Malfoy.} Father bought me tutors.”

“Wow,” Harry said. Reading Robert Cialdini’s \emph{Influence: Science and Practice} probably didn’t stack up very high compared to that (though it was still one heck of a book). “Your dad is almost as awesome as my dad.”

Draco’s eyebrows rose loftily. “Oh? And what does \emph{your} father do?”

“He buys me books.”

Draco considered this. “That doesn’t sound very impressive.”

“You had to be there. Anyway, I’m glad to hear all that. The way Lucius was looking at you, I thought he was going to c-crucify you.”

“My father really loves me,” Draco said firmly. “He wouldn’t ever do that.”

“Um…” Harry said. He remembered the black-robed, white-haired figure of elegance that had stormed through Madam Malkin’s, wielding that beautiful, deadly silver-handled cane. It wasn’t easy to visualise him as a doting father. “Don’t take this the wrong way, but how do you \emph{know} that?”

“Huh?” It was clear that this was a question Draco did not commonly ask himself.

“I ask the fundamental question of rationality: why do you believe what you believe? What do you think you know and how do you think you know it? What makes you think Lucius wouldn’t sacrifice you the same way he’d sacrifice anything else for power?”

Draco shot Harry another odd look. “Just what do \emph{you} know about Father?”

“Um…seat on the Wizengamot, seat on Hogwarts’ Board of Governors, incredibly wealthy, has the ear of Minister Fudge, has the confidence of Minister Fudge, probably has some highly embarrassing photos of Minister Fudge, most prominent blood purist now that the Dark Lord’s gone, former Death Eater who was found to have the Dark Mark but got off by claiming to be under the Imperius Curse, which was ridiculously implausible and pretty much everyone knew it…evil with a capital ‘E’ and a born killer…I think that’s it.”

Draco’s eyes had narrowed to slits. “McGonagall told you that, did she.”

“No, she wouldn’t say \emph{anything} to me about Lucius afterwards, except to stay away from him. So during the Incident at the Potions Shop, while Professor McGonagall was busy yelling at the shopkeeper and trying to get everything under control, I grabbed one of the customers and asked \emph{them} about Lucius.”

Draco’s eyes were wide again. “Did you \emph{really?}”

Harry gave Draco a puzzled look. “If I lied the first time, I’m not going to tell you the truth just because you ask twice.”

There was a certain pause as Draco absorbed this.

“You’re so completely going to be in Slytherin.”

“I’m so completely going to be in Ravenclaw, thank you very much. I only want power so I can get books.”

Draco giggled. “Yeah, right. Anyway…to answer what you asked…” Draco took a deep breath, and his face turned serious. “Father once missed a Wizengamot vote for me. I was on a broom and I fell off and broke a lot of ribs. It really hurt. I’d never hurt that much before and I thought I was going to die. So Father missed this really important vote, because he was there by my bed at St. Mungo’s, holding my hands and promising me that I was going to be okay.”

Harry glanced away uncomfortably, then, with an effort, forced himself to look back at Draco. “Why are you telling me \emph{that?} It seems sort of…private…”

Draco gave Harry a serious look. “One of my tutors once said that people form close friendships by knowing private things about each other, and the reason most people don’t make close friends is because they’re too embarrassed to share anything really important about themselves.” Draco turned his palms out invitingly. “Your turn?”

Knowing that Draco’s hopeful face had probably been drilled into him by months of practice did not make it any less effective, Harry observed. Actually it \emph{did} make it \emph{less} effective, but unfortunately not \emph{ineffective.} The same could be said of Draco’s clever use of reciprocation pressure with an unsolicited gift, a technique which Harry had read about in his social psychology books (one experiment had shown that an unconditional gift of \$5 was twice as effective as a conditional offer of \$50 in getting people to fill out surveys). Draco had made an unsolicited gift of a confidence, and now invited Harry to offer a confidence in return…and the thing was, Harry \emph{did} feel pressured. Refusal, Harry was certain, would be met with a look of sad disappointment, and maybe a small amount of contempt indicating that Harry had lost points.

“Draco,” Harry said, “just so you know, I recognise exactly what you’re doing right now. My own books called it \emph{reciprocation} and they talk about how giving someone a straight gift of two Sickles was found to be twice as effective as offering them twenty Sickles in getting them to do what you want…” Harry trailed off.

Draco was looking sad and disappointed. “It’s not meant as a trick, Harry. It’s a real way of becoming friends.”

Harry held up a hand. “I didn’t say I wasn’t going to respond. I just need time to pick something that’s private but just as non-damaging. Let’s say…I wanted you to know that I can’t be rushed into things.” A pause to reflect could go a long way in defusing the power of a lot of compliance techniques, once you learned to recognise them for what they were.

“All right,” Draco said. “I’ll wait while you come up with something. Oh, and please take off the scarf while you say it.”

\emph{Simple but effective.}

And Harry couldn’t help but notice how clumsy, awkward, graceless his attempt at resisting manipulation / saving face / showing off had appeared compared to Draco. \emph{I need those tutors.}

“All right,” Harry said after a time. “Here’s mine.” He glanced around and then rolled the scarf back up over his face, exposing everything but the scar. “Um…it sounds like you can really rely on your father. I mean…if you talk to him seriously, he’ll always listen to you and take you seriously.”

Draco nodded.

“Sometimes,” Harry said, and swallowed. This was surprisingly hard, but then it was meant to be. “Sometimes I wish my own Dad was like yours.” Harry’s eyes flinched away from Draco’s face, more or less automatically, and then Harry forced himself to look back at Draco.

Then it hit Harry \emph{what on Earth he’d just said}, and Harry hastily added, “Not that I wish my Dad was a flawless instrument of death like Lucius, I only mean taking me seriously—”

“I understand,” Draco said with a smile. “There…now doesn’t it feel like we’re a little closer to being friends?”

Harry nodded. “Yeah. It does, actually. Um…no offence, but I’m going to put on my disguise again, I \emph{really} don’t want to deal with—”

“I understand.”

Harry rolled the scarf back down over his face.

“My father takes all his friends seriously,” Draco said. “That’s why he has lots of friends. You should meet him.”

“I’ll think about it,” Harry said in a neutral voice. He shook his head in wonder. “So you really are his one weak point. Huh.”

Now Draco was giving Harry a \emph{really} odd look. “You want to go get something to drink and find somewhere to sit down?”

Harry realised he had been standing in one place for too long, and stretched himself, trying to crick his back. “Sure.”

The platform was starting to fill up now, but there was still a quieter area on the far side away from the red steam engine. Along the way they passed a stall containing a bald, bearded man offering newspapers and comic books and stacked neon-green cans.

The stall-holder was, in fact, leaning back and drinking out of one of the neon-green cans at the exact point when he spotted the refined and elegant Draco Malfoy approaching along with a mysterious boy looking incredibly stupid with a scarf tied over his face, causing the stall-holder to experience a sudden coughing fit in mid-drink and dribble a large amount of neon-green liquid onto his beard.

“’Scuse me,” Harry said, “but what \emph{is} that stuff, exactly?”

“Comed-Tea,” said the stall-holder “If you drink it, something surprising is bound to happen which makes you spill it on yourself or someone else. But it’s charmed to vanish just a few seconds later—” Indeed the stain on his beard was already disappearing.

“How droll,” said Draco. “How very, very droll. Come, Mr~Bronze, let’s go find another—”

“Hold on,” Harry said.

“\emph{Oh come on!} That’s just, just \emph{juvenile!}”

“No, I’m sorry Draco, I \emph{have} to investigate this. What happens if I drink Comed-Tea while doing my best to keep the conversation completely serious?”

The stall-holder smiled mysteriously. “Who knows? A friend walks by in a frog costume? Something unexpected is bound to happen—”

“No. I’m sorry. I just don’t believe it. That violates my much-abused suspension of disbelief on so many levels I don’t even have the language to describe it. There is, there is just \emph{no way} a bloody \emph{drink} can manipulate reality to produce \emph{comedy setups}, or I’m going to give up and retire to the Bahamas—”

Draco groaned. “Are we \emph{really} going to do this?”

“You don’t have to drink it but I \emph{have} to investigate. \emph{Have} to. How much?”

“Five Knuts the can,” the stall-holder said.

“\emph{Five Knuts?} You can sell reality-manipulating fizzy drinks for \emph{five Knuts the can?}” Harry reached into his pouch, said “four Sickles, four Knuts”, and slapped them down on the counter. “Two dozen cans please.”

“I’ll also take one,” Draco sighed, and started to reach for his pockets.

Harry shook his head rapidly. “No, I’ve got this, doesn’t count as a favour either, I want to see if it works for you too.” He took a can from the stack now placed on the counter and tossed it to Draco, then started feeding his pouch. The pouch’s Widening Lip ate the cans accompanied by small burping noises, which wasn’t exactly helping to restore Harry’s faith that he would some day discover a reasonable explanation for all this.

Twenty-two burps later, Harry had the last purchased can in his hand, Draco was looking at him expectantly, and the two of them pulled the ring at the same time.

Harry rolled up his scarf to expose his mouth, and they tilted their heads back and drank the Comed-Tea.

It somehow \emph{tasted} bright green—extra-fizzy and limer than lime.

Aside from that, nothing else happened.

Harry looked at the stall-holder, who was watching them benevolently.

\emph{All right, if this guy just took advantage of a natural accident to sell me twenty-four cans of nothing, I’m going to applaud his creative entrepreneurial spirit and then kill him.}

“It doesn’t always happen immediately,” the stall-holder said. “But it’s guaranteed to happen once per can, or your money back.”

Harry took another long drink.

Once again, nothing happened.

\emph{Maybe I should just chug the whole thing as fast as possible…and hope my stomach doesn’t explode from all the carbon dioxide, or that I don’t burp while drinking it…}

No, he could afford to be a \emph{little} patient. But honestly, Harry didn’t see how this was going to work. You couldn’t go up to someone and say “Now I’m going to surprise you” or “And now I’m going to tell you the punchline of the joke, and it’ll be really funny.” It ruined the shock value. In Harry’s state of mental preparedness, Lucius Malfoy could have walked past in a ballerina outfit and it wouldn’t have made him do a proper spit-take. Just what sort of wacky shenanigan was the universe supposed to cough up \emph{now?}

“Anyway, let’s sit down,” Harry said. He prepared to swig another drink and started towards the distant seating area, which put him at the right angle to glance back and see the portion of the stall’s newspaper stand that was devoted to a newspaper called \emph{The Quibbler}, which was showing the following headline:

\headline{Boy-Who-Lived Gets\\ Draco Malfoy Pregnant}

“\emph{Gah!}” screamed Draco as bright green liquid sprayed all over him from Harry’s direction. Draco turned to Harry with fire in his eyes and grabbed his own can. “You son of a mudblood! Let’s see how \emph{you} like being spat upon!” Draco took a deliberate swig from the can just as his own eyes caught sight of the headline.

In sheer reflex action, Harry tried to block his face as the spray of liquid flew in his direction. Unfortunately he blocked using the hand containing the Comed-Tea, sending the rest of the green liquid to splash out over his shoulder.

Harry stared at the can in his hand even as he went on choking and spluttering and the green colour started to vanish from Draco’s robes.

Then he looked up and stared at the newspaper headline.

\headline{Boy-Who-Lived Gets\\ Draco Malfoy Pregnant}

Harry’s lips opened and said, “buh-bluh-buh-buh…”

Too many competing objections, that was the problem. Every time Harry tried to say “But we’re only eleven!” the objection “But men can’t get pregnant!” demanded first priority and was then run over by “But there’s nothing between us, really!”

Then Harry looked down at the can in his hand again.

He was feeling a deep-seated desire to run away screaming at the top of his lungs until he dropped from lack of oxygen, and the only thing stopping him was that he had once read that outright panic was the sign of a \emph{truly} important scientific problem.

Harry snarled, threw the can violently into a nearby rubbish bin, and stalked back over to the stall. “One copy of \emph{The Quibbler,} please.” Harry paid over four more Knuts, retrieved another can of Comed-Tea from his pouch, and then stalked over to the picnic area with the blond-haired boy, who was staring at his own can with an expression of frank admiration.

“I take it back,” Draco said, “that was pretty good.”

“Hey, Draco, you know what I bet is even better for becoming friends than exchanging secrets? Committing murder.”

“I have a tutor who says that,” Draco allowed. He reached inside his robes and scratched himself with an easy, natural motion. “Who’ve you got in mind?”

Harry slammed \emph{The Quibbler} down hard on the picnic table. “The guy who came up with this headline.”

Draco groaned. “Not a guy. A girl. A \emph{ten-year-old} girl, can you believe it? She went nuts after her mother died and her father, who owns this newspaper, is \emph{convinced} that she’s a seer, so when he doesn’t know he asks Luna Lovegood and believes \emph{anything} she says.”

Not really thinking about it, Harry pulled the ring on his next can of Comed-Tea and prepared to drink. “Are you kidding me? That’s even worse than Muggle journalism, which I would have thought was physically impossible.”

Draco snarled. “She has some sort of perverse obsession about the Malfoys, too, and her father is politically opposed to us so he prints every word. As soon as I’m old enough I’m going to rape her.”

Green liquid spurted out of Harry’s nostrils, soaking into the scarf still covering that area. Comed-Tea and lungs did not mix, and Harry spent the next few seconds frantically coughing.

Draco looked at him sharply. “Something wrong?”

It was at this point that Harry came to the sudden realisation that (a)~the sounds coming from the rest of the train platform had turned into more of a blurred white noise at around the same time Draco had reached inside his robes, and (b)~when he had discussed committing murder as a bonding method, there had been exactly one person in the conversation who’d thought they were joking.

\emph{Right. Because he} seemed \emph{like such a normal kid. And he} is \emph{a normal kid, he is just what you’d} expect \emph{a baseline male child to be like if Darth Vader were his doting father.}

“Yes, well,” Harry coughed, oh god how was he going to get out of this conversational wedge, “I was just surprised at how you were willing to discuss it so openly, you didn’t seem worried about getting caught or anything.”

Draco snorted. “Are you joking? \emph{Luna Lovegood’s} word against mine?”

Holy crap on a holy stick. “There’s no such thing as magical truth detection, I take it?” \emph{Or DNA testing…yet.}

Draco looked around. His eyes narrowed. “That’s right, you don’t know anything. Look, I’ll explain things to you, I mean the way it really works, just like you were already in Slytherin and asked me the same question. But you’ve got to swear not to say anything about it.”

“I swear,” Harry said.

“The courts use Veritaserum, but it’s a joke really, you just get yourself Obliviated before you testify and then claim the other person was Memory-Charmed with a fake memory. Of course if you’re just some normal person, the courts presume in favour of Obliviation, not False Memory Charms. But the court has discretion, and if \emph{I’m} involved then it impinges on the honour of a Noble House, so it goes to the Wizengamot, where Father has the votes. After I’m found not guilty the Lovegood family has to pay reparations for tarnishing my honour. And they know from the start that’s how it’ll go, so they’ll just keep their mouths shut.”

A cold chill was coming over Harry, a chill that came with instructions to keep his voice and face normal. \emph{Note to self: Overthrow government of magical Britain at earliest convenience.}

Harry coughed again to clear his throat. “Draco, please please \emph{please} don’t take this the wrong way, my word is my bond, but like you said I could be in Slytherin and I really want to ask for informational purposes, so what would happen \emph{theoretically speaking} if I \emph{did} testify that I’d heard you plan it?”

“Then if I was anyone other than a Malfoy, I’d be in trouble,” Draco answered smugly. “Since I \emph{am} a Malfoy…Father has the votes. And afterwards he’d crush you…well, I guess not easily, since you \emph{are} the Boy-Who-Lived, but Father is pretty good at that sort of thing.” Draco frowned. “’Sides, \emph{you} talked about murdering her, why weren’t you worried about \emph{me} testifying after she turns up dead?”

\emph{How, oh how did my day go this wrong?} Harry’s mouth was already moving faster than he could think. “That’s when I thought she was \emph{older!} I don’t know how it works \emph{here}, but in Muggle Britain the courts would get a lot more upset about someone killing a child—”

“That makes sense,” Draco said, still looking a bit suspicious. “But anyway, it’s always smarter if it doesn’t go to the Aurors at all. If we’re careful only to do things that Healing Charms can fix, we can just Obliviate her afterwards and then do it all again next week.” Then the blonde-haired boy giggled, a youthful high-pitched sound. “Though just imagine her saying she’d been done by Draco Malfoy \emph{and} the Boy-Who-Lived, not even \emph{Dumbledore} would believe her.”

\emph{I am going to tear apart your pathetic little magical remnant of the Dark Ages into pieces smaller than its constituent atoms.} “Actually, can we hold off on that? After I found out that headline came from a girl a year younger than me, I had a different thought for my revenge.”

“Huh? Do tell,” Draco said, and started to take another swig of his Comed-Tea.

Harry didn’t know if the enchantment worked more than once per can, but he \emph{did} know he could avoid the blame, so he was careful to time it exactly right:

“I was thinking \emph{some day I’m going to marry that woman.}”

Draco made a horrid ker-splutching sound and leaked green fluid out the corners of his mouth like a broken car radiator. “\emph{Are you nuts?}”

“Quite the opposite, I’m so sane it burns like ice.”

“You’ve got weirder taste than a Lestrange,” Draco said, sounding half-admiring about it. “And I suppose you want her all to yourself, huh?”

“Yep. I can owe you a favour for it—”

Draco waved it off. “Nah, this one’s free.”

Harry stared down at the can in his hand, the coldness settling into his blood. Charming, happy, generous with his favours to his friends, Draco wasn’t a psychopath. That was the sad and awful part, knowing human psychology well enough to \emph{know} that Draco \emph{wasn’t} a monster. There had been ten thousand societies over the history of the world where this conversation could have happened. No, the world would have been a very different place indeed, if it took an \emph{evil mutant} to say what Draco had said. It was very simple, very human, it was the default if nothing else intervened. To Draco, his enemies weren’t people.

And in the slowed time of this slowed country, here and now as in the darkness-before-dawn prior to the Age of Reason, the son of a sufficiently powerful noble would simply take for granted that he was above the law, at least when it came to some peasant girl. There were places in Muggle-land where it was still the same way, countries where that sort of nobility still existed and still thought like that, or even grimmer lands where it wasn’t just the nobility. It was like that in every place and time that didn’t descend directly from the Enlightenment. A line of descent, it seemed, which didn’t quite include magical Britain, for all that there had been cross-cultural contamination of things like ring-pull drinks cans.

\emph{And if Draco doesn’t change his mind about wanting revenge, and I don’t throw away my own chance at happiness in life to marry some poor crazy girl, then all I’ve just bought is time, and not too much of it…}

For one girl. Not for others.

\emph{I wonder how difficult it would be to just make a list of all the top blood purists and kill them.}

They’d tried exactly that during the French Revolution, more or less—make a list of all the enemies of Progress and remove everything above the neck—and it hadn’t worked out well from what Harry recalled. Maybe he needed to dust off some of those history books his father had bought him, and see if what had gone wrong with the French Revolution was something easy to fix.

Harry gazed up at the sky, and at the pale shape of the Moon, visible this morning through the cloudless air.

\emph{So the world is broken and flawed and insane, and cruel and bloody and dark. This is news? You always knew that, anyway…}

“You’re looking all serious,” Draco said. “Let me guess, your Muggle parents told you that this sort of thing was bad.”

Harry nodded, not quite trusting his voice.

“Well, like Father says, there may be four houses, but in the end everyone belongs to either Slytherin or Hufflepuff. And frankly, you’re not on the Hufflepuff end. If you decide to side with the Malfoys under the table…our power and your reputation…you could get away with things even \emph{I} can’t do. Want to \emph{try} it for a while? See what it’s like?”

\emph{Aren’t we a clever little serpent. Eleven years old and already coaxing your prey from hiding…}

Harry thought, considered, chose his weapon. “Draco, you want to explain the whole blood purity thing to me? I’m sort of new.”

A wide smile crossed Draco’s face. “You really should meet Father and ask \emph{him}, you know, he’s our leader.”

“Give me the thirty-second version.”

“Okay,” Draco said. He drew in a deep breath, and his voice grew slightly lower, and took on a cadence. “Our powers have grown weaker, generation by generation, as the mudblood taint increases. Where Salazar and Godric and Rowena and Helga once raised Hogwarts by their power, creating the Locket and the Sword and the Diadem and the Cup, no wizard of these faded days has risen to rival them. We are fading, all fading into Muggles as we interbreed with their spawn and allow our Squibs to live. If the taint is not checked, soon our wands will break and all our arts cease, the line of Merlin will end and the blood of Atlantis fail. Our children will be left scratching at the dirt to survive like the mere Muggles, and darkness will cover all the world for ever.” Draco took another swig from his drinks can, looking satisfied; that seemed to be the whole argument as far as he was concerned.

“Persuasive,” Harry said, meaning it descriptively rather than normatively. It was a standard pattern: The Fall from Grace, the need to guard what purity remained against contamination, the past sloping upwards and the future sloping only down. And that pattern also had its \emph{counter}…”I have to correct you on one point of fact, though. Your information about the Muggles is a bit out of date. We aren’t exactly scratching at the dirt any more.”

Draco’s head snapped around. “\emph{What?} What do you mean, \emph{we?}”

“We. The scientists. The line of Francis Bacon and the blood of the Enlightenment. Muggles didn’t just sit around crying about not having wands, we have our \emph{own} powers now, with or without magic. If all your powers fail then we will all have lost something very precious, because your magic is the only hint we have as to how the universe must \emph{really} work—but you won’t be left scratching at the ground. Your houses will still be cool in summer and warm in winter, there will still be doctors and medicine. Science can keep you alive if magic fails. It’d be a tragedy, but not literally the end of all the light in the world. Just saying.”

Draco had backed up several feet and his face was full of mixed fear and disbelief. “\emph{What in the name of Merlin are you talking about, Potter?}”

“Hey, I listened to \emph{your} story, won’t you listen to mine?” \emph{Clumsy,} Harry chided himself, but Draco actually did stop backing off and seem to listen.

“Anyway,” Harry said, “I’m saying that you don’t seem to have been paying much attention to what goes on in the Muggle world.” Probably because the whole wizarding world seemed to regard the rest of Earth as a slum, deserving around as much news coverage as the \emph{Financial Times} awarded to the routine agonies of Burundi. “All right. Quick check. Have wizards ever been to the Moon? You know, that thing?” Harry pointed up to that huge and distant globe.

“\emph{What?}” Draco said. It was pretty clear the thought had never occurred to the boy. “\emph{Go} to the—it’s just a—” His finger pointed at the little pale thingy in the sky. “You can’t Apparate to somewhere you’ve never \emph{been} and how would anyone get to the Moon in the \emph{first} place?”

“Hold on,” Harry said to Draco, “I’d like to show you a book I brought with me, I think I remember what box it’s in.” And Harry stood up and knelt down and yanked out the stairs to the cavern level of his trunk, then tore down the stairs and heaved a box off another box, coming perilously close to treating his books with disrespect, and snatched off the box cover and quickly but carefully pried out a stack of books—

(Harry had inherited the nigh-magical Verres ability to remember where all his books were, even after seeing them just once, which was rather mysterious considering the lack of any genetic connection.)

And Harry raced back up the stairs and shoved the staircase back into the trunk with his heel, and, panting, turned the pages of the book until he found the picture he wanted to show to Draco.

The one with the white, dry, cratered land, and the suited people, and the blue-white globe hanging over it all.

That picture.

\emph{The} picture, if only one picture in all the world were to survive.

“\emph{That},” Harry said, his voice trembling because he couldn’t quite keep the pride out, “is what the Earth looks like from the Moon.”

Draco slowly leaned over. There was a strange expression on his young face. “If that’s a \emph{real} picture, why isn’t it moving?”

\emph{Moving?} Oh. “Muggles can do moving pictures but they need a bigger box to show it, they can’t fit them onto single book pages yet.”

Draco’s finger moved to one of the suits. “What are those?” His voice starting to waver.

“Those are human beings. They are wearing suits that cover their whole bodies to give them air, because there is no air on the Moon.”

“That’s impossible,” Draco whispered. There was terror in his eyes, and utter confusion. “No Muggle could ever do that. \emph{How…}”

Harry took back the book, flipped the pages until he found what he saw. “This is a rocket going up. The fire pushes it higher and higher, until it gets to the Moon.” Flipped pages again. “This is a rocket on the ground. That tiny speck next to it is a person.” Draco gasped. “Going to the Moon cost the equivalent of…probably around a thousand million Galleons.” Draco choked. “And it took the efforts of…probably more people than live in all of magical Britain.” \emph{And when they arrived, they left a plaque that said, ‘We came in peace, for all mankind.’ Though you’re not yet ready to hear those words, Draco Malfoy…}

“You’re telling the truth,” Draco said slowly. “You wouldn’t fake a whole book just for this—and I can hear it in your voice. But…but…”

“How, without wands or magic? It’s a long story, Draco. Science doesn’t work by waving wands and chanting spells, it works by knowing how the universe works on such a deep level that you know exactly what to do in order to make the universe do what you want. If magic is like casting \emph{Imperio} on someone to make them do what you want, then science is like knowing them so well that you can convince them it was their own idea all along. It’s a lot more difficult than waving a wand, but it works when wands fail, just like if the \emph{Imperius} failed you could still try persuading a person. And Science builds from generation to generation. You have to really \emph{know} what you’re doing to do science—and when you really understand something, you can explain it to someone else. The greatest scientists of one century ago, the brightest names that are still spoken with reverence, their powers are as \emph{nothing} to the greatest scientists of today. There is no equivalent in science of your lost arts that raised Hogwarts. In science our powers wax by the year. And we are beginning to understand and unravel the secrets of life and inheritance. We’ll be able to look at the very blood of which you spoke, and see what makes you a wizard, and in one or two more generations, we’ll be able to persuade that blood to make all your children powerful wizards too. So you see, your problem isn’t nearly as bad as it looks, because in a few more decades, science will be able to solve it for you.”

“But…” Draco said. His voice was trembling. “If \emph{Muggles} have that kind of power…then…what are \emph{we?}”

“No, Draco, that’s not it, don’t you see? Science taps the power of human understanding to look at the world and figure out how it works. It can’t fail without humanity itself failing. Your magic could turn off, and you would hate that, but you would still be \emph{you}. You would still be alive to regret it. But because science rests upon my human intelligence, it is the power that cannot be removed from me without removing \emph{me.} Even if the laws of the universe change on me, so that all my knowledge is void, I’ll just figure out the new laws, as has been done before. It’s not a \emph{Muggle} thing, it’s a \emph{human} thing, it just refines and trains the power you use every time you look at something you don’t understand and ask ‘Why?’ You’re of Slytherin, Draco, don’t you see the implication?”

Draco looked up from the book to Harry. His face showed dawning understanding. “Wizards can learn to use this power.”

Very carefully, now…the bait is set, now the hook…”If you can learn to think of yourself as a \emph{human} instead of a \emph{wizard} then you can train and refine your powers as a human.”

And if \emph{that} instruction wasn’t in \emph{every} science curriculum, Draco didn’t need to know it, did he?

Draco’s eyes were now thoughtful. “You’ve…already done this?”

“To some extent,” Harry allowed. “My training isn’t complete. Not at eleven. But—my father \emph{also} bought me tutors, you see.” Sure, they’d been starving grad students, and it had only been because Harry slept on a 26-hour cycle, but leave all that aside for now…

Slowly, Draco nodded. “You think you can master \emph{both} arts, add the powers together, and…” Draco stared at Harry. “Make yourself Lord of the two worlds?”

Harry gave an evil laugh, it just seemed to come naturally at that point. “You have to realise, Draco, that the whole world you know, all of magical Britain, is just one square on a much larger game board. The game board that includes places like the Moon, and the stars in the night sky, which are lights just like the Sun only unimaginably far away, and things like galaxies that are vastly huger than the Earth and Sun, things so large that only scientists can see them and you don’t even know they exist. But I really \emph{am} Ravenclaw, you know, not Slytherin. I don’t want to rule the universe. I just think it could be more sensibly organised.”

There was awe on Draco’s face. “Why are you telling \emph{me} this?”

“Oh…there aren’t many people who know how to do \emph{true} science—understanding something for the very first time, even if it confuses the hell out of you. Help would be helpful.”

Draco stared at Harry with his mouth open.

“But make no mistake, Draco, true science really \emph{isn’t} like magic, you can’t just do it and walk away unchanged like learning how to say the words of a new spell. The power comes with a cost, a cost so high that most people refuse to pay it.”

Draco nodded at this as though, finally, he’d heard something he could understand. “And that cost?”

“Learning to admit you’re wrong.”

“Um,” Draco said after the dramatic pause had stretched on for a while. “You going to explain that?”

“Trying to figure out how something works on that deep level, the first ninety-nine explanations you come up with are wrong. The hundredth is right. So you have to learn how to admit you’re wrong, over and over and over again. It doesn’t sound like much, but it’s so hard that most people can’t do science. Always questioning yourself, always taking another look at things you’ve always taken for granted,” like having a Snitch in Quidditch, “and every time you change your mind, you change yourself. But I’m getting way ahead of myself here. Way ahead of myself. I just want you to know…I’m offering to share some of my knowledge. If you want. There’s just one condition.”

“Uh huh,” Draco said. “You know, Father says that when someone says that to you, it is never a good sign, ever.”

Harry nodded. “Now, don’t mistake me and think that I’m trying to drive a wedge between you and your father. It’s not about that. It’s just about me wanting to deal with someone my own age, rather than having this be between me and Lucius. I think your father would be okay with that too, he knows you have to grow up sometime. But your moves in our game have to be your own. That’s my condition—that I’m dealing with you, Draco, not your father.”

“I’ve got to go,” Draco said. He stood up. “I’ve got to go off and think about this.”

“Take your time,” Harry said.

The sounds of the train platform changed from blurs into murmurs as Draco wandered off.

Harry slowly exhaled the air he’d been holding in without quite realising it, and then looked at the watch on his wrist, a simple mechanical model that his father had bought him in hope it would work in magic’s presence. The second-hand was still ticking, and if the minute hand was right, then it wasn’t quite eleven just yet. He probably ought to get on the train soon and start looking for whatsherface, but it seemed worth taking a few minutes first to do some breathing exercises and see if his blood warmed up again.

But when Harry looked up from his watch, he saw two figures approaching, looking utterly ridiculous with their faces cloaked by winter scarves.

“Hello, Mr~Bronze,” said one of the masked figures. “Can we interest you in joining the Order of Chaos?”

\latersection{Aftermath:}

Not too long after that, when all that day’s fuss had finally subsided, Draco was bent over a desk with quill in hand. He had a private room in the Slytherin dungeons, with its own desk and its own fire—sadly not even \emph{he} rated a connection to the Floo system, but at least Slytherin didn’t buy into that utter nonsense about making \emph{everyone} sleep in dorms. There weren’t many private rooms, you had to be the \emph{very} best within the House of the better sort, but that could be taken for granted with the House of Malfoy.

\emph{Dear Father,} Draco wrote.

And then he stopped.

Ink slowly dripped from his quill, staining the parchment near the words.

Draco wasn’t stupid. He was young, but his tutors had trained him well. Draco knew that Potter probably felt a lot more sympathy towards Dumbledore’s faction than Potter was letting on…though Draco did think Potter could be tempted. But it was crystal clear that Potter was trying to tempt Draco just as Draco was trying to tempt him.

And it was also clear that Potter was brilliant, and a whole lot more than just slightly mad, and playing a vast game that Potter himself mostly didn’t understand, improvised at top speed with the subtlety of a bull in a china shop. But Potter had managed to choose a tactic that Draco couldn’t just walk away from. He had offered Draco a part of his own power, gambling that Draco couldn’t use it without becoming more like him. His father had called this an advanced technique, and had warned Draco that it often didn’t work.

Draco knew he hadn’t understood everything that had happened…but Potter had offered \emph{him} the chance to play and right now it was \emph{his.} And if he blurted the whole thing out, it would become Father’s.

In the end it was as simple as that. The lesser techniques require the unawareness of the target, or at least their uncertainty. Flattery has to be plausibly disguised as admiration. (“You should have been in Slytherin” is an old classic, highly effective on a certain type of person who isn’t expecting it, and if it works you can repeat it.) But when you find someone’s ultimate lever it doesn’t matter if they know you know. Potter, in his mad rush, had guessed a key to Draco’s soul. And if Draco knew that Potter knew it—even if it had been an obvious sort of guess—that didn’t change anything.

So now, for the first time in his life, he had real secrets to keep. He was playing his own game. There was an obscure pain to it, but he knew that Father would be proud, and that made it all right.

Leaving the ink drippings in place—there was a message there, and one that his father would understand, for they had played the game of subtleties more than once—Draco wrote out the one question that really had gnawed at him about the whole affair, the part that it seemed he \emph{ought} to understand, but he didn’t, not at all.

\begin{writtenNote}
\letterAddress{Dear Father:}

Suppose I told you that I met a student at Hogwarts, not already part of our circle of acquaintances, who called you a ‘flawless instrument of death’ and said that I was your ‘one weak point’. What would you say about him?

\end{writtenNote}

It didn’t take long after that for the family owl to bring the reply.


\begin{writtenNote}
\letterAddress{My beloved son:}

I would say that you had been so fortunate as to meet someone who enjoys the intimate confidence of our friend and valuable ally, Severus Snape.

\end{writtenNote}

Draco stared at the letter for a while, and finally threw it into the fire.

%  LocalWords:  etunia Cor eehhhhh Spoo Snitchless Aw Scuse limer Gah
%  LocalWords:  buh bluh ker splutching whatsherface
