\partchapter{Failure}{I}

\lettrinepara{T}{he} Dark Lord was laughing.

\hplettrineextrapara
From the empty air came the voice of the Defence Professor laughing wildly, so high and terrible his laughter; it was Voldemort’s laughter now, the Dark Lord’s laughter beyond all hiding or restraint.

Harry’s mind was disarrayed. His eyes kept staring at where Albus Dumbledore had been. There was a horror in him that was too huge for understanding or reflection. His mind kept trying to fall back through time and undo reality, but that wasn’t a sort of magic that existed, and reality stayed the same.

He had lost, he had lost Dumbledore, there were no take-backs, and that meant he had lost the war.

And the Dark Lord went on laughing.

“Ah, ah hah, ah hah hah ha! Professor Dumbledore, ah, Professor Dumbledore, such a fitting end to our game!” Another burst of wild laughter. “The wrong sacrifice even at the finish, for the piece you gave up everything to save was already in my possession! The wrong trap even from the beginning, for I could have abandoned this body at any time! Ah, hahahahaha, aha! You never did learn cunning, you poor old fool.”

“You—” A voice was coming from Harry’s throat. “You—”

“Ahahahaha! Why, yes, little child, you were always along on this adventure as my hostage, it was your whole purpose in being here. Ha, hahahaha! You are decades too young to play this game against the real Tom Riddle, child.” The Dark Lord drew back the hood of the Cloak, his head becoming visible, and began to remove the rest of the Cloak. “And now, boy, \parsel{you have helped me, yes indeed, and so it is time to resurrect your girl-child friend. To keep promise.}” The Dark Lord’s smile was cold, cold indeed. “I suppose you have doubts? Mark well, I could kill you this instant, for there is no longer a Headmaster of Hogwarts to be informed of it. Doubt me all you wish, but remember that.” The hand was once more holding the gun. “Now come along, foolish child.”

And they left.

They went back out through the door into the Potions room, the Dark Lord banishing the returned purple fire with a stroke of his wand. They went through the chamber where the boggart had been, and the chamber of ruined chess statues, and through the burned door of the chamber of keys. The Dark Lord floated up through the trapdoor, and Harry struggled up afterwards through the spiral staircase of leaves, the tendrils of the Devil’s Snare twitching and then moving back as though afraid. The Boy-Who-Lived was trying hard not to burst into tears, and his dark-side patterns weren’t helping, maybe because Voldemort had never known or dealt with guilt.

They passed the huge three-headed Inferi, and at a whispered word from the Dark Lord it collapsed over the trapdoor and became a corpse again.

They passed Severus Snape standing guard, who told them both that he was guarding the door, and that they must leave or he would deduct House points.

The Dark Lord spoke the words “\emph{Hyakuju montauk}” without pausing in his stride, accompanied by a jab of his wand; and Severus staggered before he lifelessly drew himself up beside the door once more.

“What—” Harry said, as he followed. “What did you—”

“Just fulfilling my obligation to my faithful servant. It shall not kill him, as I promised you.” The Dark Lord laughed again.

“The hostages—” Harry said. It was hard to keep his voice steady. “The students, you said you’d stop whatever is going to kill them—”

“\parsel{Yes. Stop worrying. Will do on our way out.}”

“Out?”

“We are leaving, child.” The Dark Lord was still smiling.

The bad feeling this raised was lost in a sea of other bad feelings.

The Dark Lord was now consulting what he’d called the Hogwarts Map, the handwritten lines upon it seeming to move as they walked. Some part of Harry’s mind that had been considering what to do if they ran into Aurors on patrol (whom the Dark Lord could kill, or Obliviate, in an instant) gave up that hope as well.

They went down the Grand Staircase to the second floor, encountering no one.

The Dark Lord made a turn Harry did not know, and went down another stair-flight. As they descended past one floor and another, the windows stopped and the torches began, they were within the Slytherin dungeons now.

Ahead, the form of a person in Hogwarts robes appeared.

The Dark Lord kept walking toward that person.

Harry followed.

A sixth or seventh-year Slytherin was waiting by a section of wall that was set with an artistic carving of Salazar Slytherin wielding his wand, against what looked like a giant covered in icicles. The witch made no comment at seeing Professor Quirrell walking upright, or seeing Harry in his company, or seeing the gun in the Defence Professor’s hand. If her eyes were blank, Harry couldn’t tell the difference.

The Dark Lord reached into his robes, took out a Knut, and flipped it to her. “Klaudia Alicja Tabor, I command you thus. Take this Knut to the spell circle I showed you beneath the Quidditch stands and put it in the centre. Then Obliviate yourself of the last six hours.”

“Yes, lord,” the witch said, bowing to him, and went on her way.

“I thought—” Harry said. “I thought you needed the Stone to—”

The Dark Lord was still smiling, he had never stopped smiling. “I did not say that part in Parseltongue, child. All I said in Parseltongue was that I had set events in motion to kill students, events that I would stop if I obtained the Stone. The rest was in human speech. I would also have stopped the Blood Fort sacrifice if I had not obtained the Stone, so long as I was not discovered and restrained. The students of Hogwarts are a valuable resource, whom I have already spent much time training.” Then the Dark Lord hissed to the wall, “\parsel{Open.}”

Harry’s eyes saw the tiny snake that had been set in the upper-left of the carving, even as the wall slowly swung backward, revealing the opening of a huge pipe. Moss grew on its sides and a musty dusty smell welled up from it; the interior was also covered with cobwebs in multiple sheets.

“Spiders…” murmured the Dark Lord. He sighed, and for that brief moment he sounded once more like Professor Quirrell.

The Dark Lord walked into the huge pipe, the cobwebs burning away before him. Harry, not seeing any other better options, followed.

The pipe branched in a Y-shape, then branched again. The Dark Lord went left, then right.

The pipe came to a solid metal wall. “\parsel{Open,}” the Dark Lord hissed, and a crack appeared in the metal; it seemed to fold into itself.

Beyond was the middle of a long, stone tunnel.

“We shall be walking a while,” said the Dark Lord. “Did you have more questions to ask, little child?”

“I—I can’t think of any—right now—”

Another cold laugh replied to this, and they walked into the tunnel, turning right.

Harry didn’t know, then or ever, how long he walked; the light of burning spiderwebs was too dim to read his mechanical watch, and Harry had not thought to look at the time before entering. It felt like they walked for miles, miles beneath the ground.

Slowly, Harry’s mind tried to recover itself a final time. Very possibly final, if he was right about the Dark Lord killing him after this…though the Dark Lord had said that he would resurrect Hermione, which seemed pointless if that was true…was that simply the Dark Lord following through on a promise he would not otherwise have been able to make in Parseltongue…why had he not just shot Harry on the spot…

\emph{Seriously,} some last functioning part of his brain said to all the other parts, \emph{this would be a good time to think of something, something that the Dark Lord has not already thought of, something we can do without our pouch or our wand or our Time-Turner, something that Professor Quirrell has not imagined we can do…think, think, pretty pretty please think of something? Don’t shut down now, even if you’re scared, even if we’ve never really really faced death before in the sense of being about to die in the next hour, \emph{this is not the time to shut down—}}

Harry’s mind stayed blank.

\emph{Suppose,} said that last remaining part, \emph{suppose we try to condition on the fact that we win this, or at least get out of this alive. If someone \emph{told you as a fact} that you had survived, or even won, somehow made everything turn out okay, what would you think had happened—}

\emph{Not legitimate procedure,} whispered Ravenclaw, \emph{the universe doesn’t work like that, we’re just going to die.}

\emph{Someone realises we’re missing,} thought Hufflepuff, \emph{and Mad-Eye Moody shows up with a squad of Aurors and rescues us. I think the time has come to admit we’re not more competent than the standard authorities.}

\emph{The saving factor does have to be something we \emph{do} somehow,} said the last voice. \emph{Otherwise there’s no point in our thinking about it.}

\emph{Problem two,} said Gryffindor. \emph{Harry Potter isn’t missing, he’s right there at the Quidditch match where everyone can see him. Professor Quirrell thought of that too, it’s part of why he sent that fake note. Problem three. I don’t think Mad-Eye Moody and an Auror squad can beat the Dark Lord, and certainly not before he kills us. I’m not sure the entire DMLE can beat the Dark Lord if he’s fighting seriously and Dumbledore is gone. Problem four. The Quidditch match was not disrupted, that’s probably the only reason why Professor Quirrell was willing to try something as complicated as bringing us along on this trip in the first place.}

\emph{Thinking along different lines,} ventured Slytherin, \emph{maybe Professor Quirrell calls in someone else to Memory-Charm us}. \emph{Legilimency, Imperius, Confundus, who knows what else, we’re not a perfect Occlumens. Then the Dark Lord would have a smart—well, sort-of smart lieutenant that he could use. That could be another reason why Professor Quirrell was so willing to tell us secrets, if he knew that the memory would disappear. It’s also a reason to leave the Hogwarts wards, so the Dark Lord can call Bellatrix to Apparate in and do the work…}

\emph{This entire reasoning process is illegitimate and I refuse to participate,} said Ravenclaw.

\emph{What lovely last words,} said the last voice. \emph{Now shut up and think.}

Rough stone tunnel went by underfoot, Harry’s shoes sometimes dipping into moisture or nearly slipping on a curved surface. The neurons in his brain, which kept on firing, imagined voices talking to each other, yelling at each other, even as the Listener stayed numb with horror and shame.

Gryffindor and Hufflepuff were conducting a debate about suicide by charging the Dark Lord’s gun, or by swallowing the little jewel on Harry’s steel ring. It seemed unclear whether the fate of the world was better or worse if the Dark Lord had Harry as a mind-slave; if the Dark Lord was going to win anyway, it might be better if he won faster.

And the last voice kept talking through it all; even in the depths of failure that last voice remained. \emph{What else did the Dark Lord always say in human speech and never in Parseltongue? Do we remember? Anything like that, anything at all?}

It was all too distant in time, too distant in time even though it had all happened this very day. The Dark Lord had told him in Parseltongue just now that it was time to revive Hermione, and then he’d said other things all in English, Harry could hardly remember for all that they’d just been spoken. Before then…before then there’d been the Circle of Concealment, when Professor Quirrell had hissed that the barrier would explode if touched. And the Defence Professor had said in English for Harry not to take off his Cloak or try crossing the Circle, said in English that the resonance might strike Professor Quirrell afterwards but Harry would be dead. Said in English that if Harry touched the magic and Professor Quirrell didn’t remember how to halt the resonance, it would kill them both…

\emph{Suppose it doesn’t kill us both,} said the last voice. \emph{On Halloween in Godric’s Hollow, the Dark Lord’s body was burned and we only ended up with a scar on our forehead. Suppose the resonance between us is deadlier to the Dark Lord than to us. What if this entire time we’ve been able to kill the Dark Lord at any time, just by dashing forward and touching our hands to any part of his exposed skin? And then it makes our scar bleed again, but that’s all. The sense of ‘stop, don’t do that’ is inherited from the Dark Lord’s worst memory of his mistake in Godric’s Hollow, it may not actually apply to the Boy-Who-Lived.}

A small note of hope rose.

Rose, and was quashed.

\emph{The Dark Lord can just throw away his wand,} droned Ravenclaw. \emph{Professor Quirrell can turn into his Animagus form. Even if he dies the Dark Lord will possess someone else and return, and then torture our parents, to punish us.}

\emph{We might be able to get to our parents in time,} said the last voice. \emph{We might be able to hide them. We might be able to get the Philosopher’s Stone away from the Dark Lord if we killed his current body now, and that Stone could provide the nucleus of a counter-army.}

The Dark Lord was moving on through the stony corridor. His hand still held the gun. He was at least four metres away from Harry.

\emph{If we dart forward, he will sense us approaching through the resonance,} said Hufflepuff. \emph{He will fly forward rapidly, he can do that, he has the broomstick-enchantments that let him fly. He will fly forward, turn around, and fire the gun. He knows about the resonance, he’s thought of this already. This is not something the Dark Lord has failed to consider. He will be ready for it, and waiting.}

\emph{Continuing the same line of argument,} said the last voice. \emph{Suppose we can freely cast magic on Professor Quirrell but he can’t cast it on us.}

\emph{Why would that be true?} demanded Ravenclaw. \emph{In fact, we have evidence that it’s false. In Azkaban, when Professor Quirrell’s Avada Kedavra hit our Patronus Charm, it felt like our head was splitting apart—}

\emph{Suppose that was all \emph{his} magic going out of control. Suppose if we’d just cast, say, a Luminos targeting him, nothing bad would have happened.}

\emph{But why?} said Ravenclaw. \emph{Why suppose that?}

\emph{Because,} thought Harry, \emph{it explains why Professor Quirrell didn’t \emph{warn me} not to cast any magic on him in Azkaban. Because Professor Quirrell never said in Parseltongue, that I can remember, that I’d hurt myself if I tried to cast magic on him. He could have given me that warning, but he didn’t, even though he gave me a lot of other warnings. Absence of evidence is weak evidence of absence.}

There was a pause while Harry’s parts considered this.

\emph{We don’t actually have our wand,} said Ravenclaw.

\emph{We might get it back at some point,} thought the last voice.

\emph{But even then,} Harry thought, and the grey hopelessness returned, \emph{the resonance is something the Dark Lord knows about. He’s already thought of everything I can do with that, he already has a response prepared. That was my mistake from the beginning. I didn’t respect the Dark Lord’s intelligence, I didn’t think that maybe he knew everything I knew and could see everything I saw and had already taken it into account.}

\emph{Then,} said the last voice, \emph{conditional on our winning, we must have hit him with something he doesn’t know about.}

\emph{Dementors,} offered Gryffindor.

\emph{The Dark Lord \emph{knows} we can destroy, deflect, and possibly control Dementors,} said Ravenclaw. \emph{He doesn’t know how, but he knows we have the capability, and where the heck would we get a Dementor anyway?}

Maybe, ventured Hufflepuff, \emph{the Dark Lord’s whole horcrux system would short out via the resonance if we grabbed him and held him, sacrificing our own life to destroy him forever.}

\emph{Balderdash,} said Ravenclaw. \emph{But I guess it doesn’t hurt to engage in some pleasant fantasy before we die, no matter how stupid.}

\emph{If Lord Voldemort had a strong enough fear of death,} Hufflepuff argued, \emph{if he wanted strongly enough to just not need to think about death again, then the horcrux system \emph{could} have design flaws like that. It never occurred to Voldemort to test his horcruxes on someone else, that could indicate he wasn’t able to think about the subject clearly—}

\emph{So his fear of death is his fatal weakness?} said Ravenclaw. \emph{Yeah, no. I’m thinking someone with over a hundred horcruxes might have a few fail-safe mechanisms in there.}

And Harry’s brain went on thinking.

A genuine asymmetry in the magical resonance between them…seemed improbable, there was no reason for the magical effect to work like that. But the magical backlash could hit the stronger wizard harder, the more powerful magic resonating more dangerously. That could explain the observed event in Godric’s Hollow (Voldemort explodes, baby survives), and also explain the observed event in Azkaban (Voldemort severely impaired by backlash of his strong magic, first-year Boy-Who-Lived hit by lighter backlash of his weak magic). Or if it was only the caster’s magic that resonated, that could also explain both those two observations. That might even explain why Professor Quirrell had been in no rush to warn Harry against casting any magic on him. Though there was another obvious reason why Professor Quirrell would avoid raising the subject of the resonance; it was a gigantic hint about the mystery of Godric’s Hollow, if Harry had ever made the connection.

The part that was numb with grief and guilt took this opportunity to observe, speaking of obliviousness, that after events at Hogwarts had turned serious, they really really \emph{really REALLY} should have reconsidered the decision made on First Thursday, at the behest of Professor McGonagall, \emph{not to tell Dumbledore about the sense of doom that Harry got around Professor Quirrell.} It was true that Harry hadn’t been sure who to trust, there was a long stretch where it had seemed plausible that Dumbledore was the bad guy and Professor Quirrell the heroic opposition, but…

Dumbledore would have realised.

Dumbledore would have realised instantly.

The wise old wizard with the true phœnix on his shoulder would have known, and Harry hadn’t trusted him, Harry hadn’t told him all the relevant facts, and the reason for this had been sheer neglect to reconsider a cached decision made four days into the start of the school year. It had been marked ‘something not to tell Dumbledore’ and even after Azkaban, even after Hermione died, even after everything, Harry had simply forgot to promote the question to deliberation and reconsider the trade-off.

Another wave of grief and shame washed over Harry, and for a time he walked on in the silence of the last voice, other voices being happy enough to fill the gap.

After what was at least several miles, and many grey thoughts, the stone tunnel ended.

The Dark Lord climbed up stone steps, and Harry followed after.

The two of them came into a dark, dank stone building. Dirty old stone doors swung open without being touched.

Before them lay marble slabs, rising up from bare ground, upon them names and dates. The tombstones were scattered in nothing like neat rows, and the rest of the graveyard ran wild.

The moon above was over three-quarters full, already seeming bright with night not fully fallen.

Harry had stopped walking upon seeing the graveyard. There was a blaring alarm in his brain saying to be \emph{anywhere other than here,} but there weren’t any options for accomplishing that. So that alarm cried unanswered, even as behind Harry the stone doors of the mausoleum swung shut again and sealed themselves.

The Dark Lord came into the centre of the scattered graveyard. He stopped walking, and waved his wand above his head in a small circle.

There was a rumbling sound, and smoothly from the ground rose an altar, at least two metres wide and of black stone carved with grey sigils. And then surrounding the altar groaned up six dark-marble obelisks, regularly spaced, gleaming darkly beneath the fading twilight sky.

The unanswerable alarm in Harry’s brain grew louder.

“This,” said the Dark Lord in Professor Quirrell’s cadences, “is a workspace I made for myself, convenient to either Hogwarts or Hogsmeade.” The Dark Lord flourished a hand at the altar. “That is where Miss~Granger shall revive, and also where I shall be reborn into my true body. I shall remake myself first, of course. \parsel{Magics to revive girl-child easier with true body.}” A strange snakish laughter accompanied these words. “\parsel{Rest assured that though some aspects of girl-child’s resurrection shall be what others consider Dark, girl-child will not be harmed or made ugly by it. Shall still look like herself, mind shall be her own, nor shall I or mine harm her after.}”

Harry’s tongue was dry and his mind was having trouble functioning. “Please, Professor, would you say in Parseltongue what is your real purpose in resurrecting Miss~Granger?”

“\parsel{To restore to you girl-child friend’s counsel and restraint. To make sure she is part of the world for you to care about. That, boy, is truly the greater part of the reason I am doing this deed.}” Again snakish laughter accompanied these words, conveying sardonic awareness of some vast irony.

A small spark of hope kindled inside Harry, alongside the much greater note of confusion, and the fear that a perfect Occlumens could indeed lie in Parseltongue. Harry didn’t understand why the Dark Lord was doing this, if the next step was just to kill the Boy-Who-Lived or enslave him…

Maybe he’d just never understood Professor Quirrell at all, maybe somehow Harry’s model of Tom Riddle was just \emph{that wrong}…maybe the Boy-Who-Lived would be Obliviated of the last day and dropped off somewhere with a confused Hermione Granger, while Lord Voldemort went on to conquer the world…?

Hope flared up in Harry, but it was a confused hope that didn’t make any sense. It didn’t square with the Dark Lord who had mocked Dumbledore and laughed at his defeat. Harry couldn’t come up with any consistent account of Professor Quirrell’s motives that allowed for something like that.

\emph{I do not know what is meant to happen next.}

The Dark Lord had moved forward to the altar. He knelt there, and seemed to reach deep into the stone of the altar itself, drawing forth a vial of liquid that looked black in the fading twilight.

When the Dark Lord spoke again his voice was clipped and precise. “Blood, blood, blood so wisely hidden,” said the Dark Lord.

And the obelisks surrounding the altar began to speak, voices like a chanting chorus coming from the motionless stones, cadences older than Latin.

\emph{Apokatastethi, apokatastethi, apokatastethi to soma mou emoi.}

\emph{Apokatastethi, apokatastethi, apokatastethi to soma mou emoi.}

The obelisks’ chant echoed after the end of each line, as if they were speaking out of synchrony with each other. The blood was poured from the vial, and it seemed to catch and hang over the altar, slowly expanding through the air, taking on a shape.

\emph{Apokatastethi, apokatastethi, apokatastethi to soma mou emoi (emoi).}

\emph{Apokatastethi, apokatastethi, apokatastethi to soma mou emoi (emoi).}

A tall form rested upon the altar, and even in the dimming twilight it looked too pale.

The Defence Professor reached his hand into his robe, and drew forth a small irregular chunk of red glass.

He placed that upon the tall pale body.

The Stone stayed there for a time, minutes at least. The irregular chunk of red glass did not glow, or flash, or give any other indication of power.

Then the Stone moved, just a little, turning slightly upon the body.

The Defence Professor took back the Stone into his robes, and prodded the tall form that lay motionless upon the altar, touching the eyes with his fingers, poking the chest with his wand.

He threw back his head, then, and laughed.

“Incredible,” said the Dark Lord, in the voice of the Defence Professor that Harry had known. “Fixed, it is fixed in form! A mere construct sustained by magic, become the true substance at the Stone’s touch! And yet I sensed nothing! Nothing! I feared I had been deceived, that I had obtained a false Stone, but the substance proves true to my every test!” The Defence Professor tucked the red glass back into his robes. “That is eldritch even by my standards, I admit.”

Then the Defence Professor walked around the altar, five times he walked around it, chanting something too low for Harry to hear.

The Dark Lord placed his wand in the hand of the figure lying on the altar.

He placed his hands, both of them, over the body’s forehead.

The Dark Lord spoke. “\emph{Fal. Tor. Pan.}”

Without any warning there was a flash like lightning that lit up the entire graveyard, and Harry staggered back a step, his hands involuntarily going to his forehead. It felt as if he had been shot there, or a wasp stung him, upon his scar.

The Defence Professor collapsed.

And the too-tall figure sat up upon the altar.

It swung around smoothly, and stood tall upon the ground, at least a head higher than a normal man. The form’s limbs were lean and pale, little-muscled but giving an impression of terrible strength.

Harry took another staggering step back, his hands still clasped to his scar. Though the distance between them was wide, Harry felt a sense of terrifying apprehension in the air, as though the sense of doom had always been been \emph{out of focus} and had now clarified, concentrated into a physical pain in the scar on Harry’s forehead.

Was that what Voldemort was \emph{supposed} to look like? The nose looked like, it looked like it had \emph{malfunctioned} during the resurrection process—

The too-tall figure threw back his head and laughed, raising his hands and wand to look at them. The left hand opened wide and it was like a pale half-spider with four over-long legs, fingers caressing the wand held in the other hand. Leaves stirred up from the graveyard, approaching to dance around the too-tall figure, surrounding him and clothing him, reforming into a high-necked shirt and flowing robes; and Lord Voldemort was laughing. Exactly the mirthless laughter that Harry remembered coming from his own throat inside the Dementor’s nightmare, precise in tone and timbre.

Red eyes gleamed beneath the fading twilight, their pupils slitted like a cat’s.

The form that Voldemort had abandoned raised itself, quivering, from the ground; and in a voice that Harry could barely hear, Quirinus Quirrell gasped, “Free—oh, free—”

“\emph{Stupefy,}” said the high cold voice of Voldemort, and Quirinus Quirrell was blasted down into the ground; then, with a wave of Voldemort’s other hand, Quirinus Quirrell was picked up and flung away from the altar.

Voldemort walked away from the altar, then turned and looked at Harry; and the pain in Harry’s scar flared at it.

“Frightened, child?” Voldemort hissed, like there was an undercurrent of Parseltongue even to the Dark Lord’s human speech. “Good. Place the girl on the altar, and break your Transfiguration. \parsel{Is time for me to revive her.}”

\emph{Is this really going to happen? Are we really going to do this?}

Harry swallowed, mastering his fear through that note of impossible hope amid the confusion, and walked over to the altar. Then Harry took off his left shoe, and his left sock, and took off the toe-ring that was Hermione Granger, the Transfigured shape identical to the toe-ring that had been given Harry as an emergency portkey. There was a twinge of regret in Harry for not having the real portkey now, but only a twinge; an inner-circle Death Eater would routinely put up boundaries against portkeys, if Severus had been right. Behind Harry, Voldemort laughed again in what sounded like surprised appreciation.

“I need my wand to \emph{Finite} her,” Harry said aloud.

“You do \emph{not}.” High the voice and cruel. “You learned to sustain a Transfiguration by touch alone, without further use of the wand. You can likewise break your own Transfiguration wandlessly, by commanding your sustaining magic to drain away. Do so now.”

Harry swallowed, and touched the toe-ring. He had to try three times, and clear his mind, before he could push his magic out of the toe-ring, as before he had learned to make a tiny stream of magic flow in.

The breaking of the spell went much more slowly that way than a \emph{Finite Incantatem}, almost like the sped-up reverse of watching something being Transfigured. The toe-ring distorted, flowing together, expanding. Colours changed, textures changed.

Two-thirds of a dead girl lay strewn across the altar, on her side with one arm falling off the altar’s edge, the position in which the reversion had chanced to place her. No blood flowed now from the chewed stumps of her thighs. The dead girl wore Hermione Granger’s face, but twisted and pale. It was as Harry had seen before in the hospital’s back room, the image burned into his brain during thirty long minutes of Transfiguration, the image he had reproduced during four even longer hours to Transfigure the decoy. The dead girl was naked, for her clothes were not part of her, and had not been Transfigured.

The sight brought back flashbacks, of the hours spent in the infirmary room, of the nightmares afterwards, all of which Harry suppressed.

“Go back,” said Voldemort’s high voice. “This is my work, now.”

Harry swallowed, and retreated from the altar, to the mouth of the long corridor where he’d stood before. “Her body is, should be, around five Celsius, I cooled her so, so there wouldn’t be brain damage—” Harry’s own voice was wavering in pitch. \emph{Is he really going to do this? Really?} There had to be a catch and Harry just couldn’t see it. Voldemort had said that neither he nor any of his would harm Hermione, that her body and mind would be her own—\emph{why?}

Voldemort walked forth to the altar once more, orienting the body before him with a wave of his hand to lie straight across the altar. The Dark Lord spoke with high monotone precision, “Flesh, flesh, flesh so wisely hidden.”

The obelisks began chanting once more.

\emph{Apokatastethi, apokatastethi, apokatastethi to soma hou emoi (emoi).}

\emph{Apokatastethi, apokatastethi, apokatastethi to soma hou emoi (emoi).}

New flesh flowed out of the stumps of the girl’s thighs, creeping forward like an ooze and solidifying.

The obelisks ceased chanting. A complete form lay naked upon the altar.

It didn’t look like Hermione. A Hermione Granger should be standing up and talking, she should have her Hogwarts uniform.

Voldemort raised a hand, then hissed, as though in annoyance. With a violent gesture, the robes around Quirinus Quirrell’s sleeping from were torn in half, his purple-and-green tie shredded, and his suit-jacket drawn from him to where Voldemort stood. Some part of Harry flinched, as if seeing the Dark Lord Voldemort attacking Professor Quirrell.

Voldemort plunged his hand deliberately into the suit jacket, which jerked as though something were being broken; then Voldemort shook out the suit jacket onto the ground beside him, emptying out the contents. Harry’s pouch fell from it, and his Time-Turner, and a broomstick, and Voldemort’s gun, and the Cloak, and a number of amulets and rings and stranger devices that Harry did not recognize.

And finally a chunk of red glass, which was laid upon Hermione Granger’s form, and allowed to stay there for a time.

Minutes passed. The Dark Lord donned an amulet from the heap of things beside the altar; also from the heap, Voldemort took four short wooden rods with straps upon them, and reached beneath his robes to attach them, it looked like they went on his upper arms and upper thighs. The Dark Lord rose into the air, moved left, right, up and down, seeming to wobble slightly at first; then his flight stabilized.

The chunk of red glass turned, slightly.

The Dark Lord Voldemort floated to the ground, and prodded Hermione Granger’s body with his wand.

“\parsel{There is an obstacle,}” hissed Voldemort.

In Harry’s mind the expectation of betrayal or other failure had already been so strong that the confirmation came only as a dull shock, not a sharp one. “\parsel{What obstacle?}”

“\parsel{Girl’s body is restored. Substance is repaired. But not magic, or life…this is body of dead Muggle.}” Voldemort turned from the altar, began to pace. “The full ritual would solve this. But that would require time…time and the blood of Granger’s enemy, and I do not think Draco Malfoy still qualifies, nor can I take my own blood unwillingly…foolish.” Voldemort’s voice was a lower hiss. “Foolish, I should have foreseen this, and prepared. Her brain might awaken with an electrical shock, I know that much of Muggle medicine…but would her magic return to her? That I do not know, and I suspect if she awakens as a Muggle she will be a Muggle forever. Still, I can think of nothing better.” The Dark Lord raised his wand—

“Wait!” Harry blurted, feeling hope return. \emph{She needs a spark of life and magic, just a spark to get her started…}

Voldemort turned and looked at him. The snakelike face showed some slight degree of surprise.

“\parsel{Think I have something that might work,}” Harry hissed. “\parsel{Needs wand. Have no intentions to use it against you.}” Harry said nothing about expecting his intentions wouldn’t change; he’d simply blurted out the idea fast enough that he hadn’t formed any specific intentions yet.

“This,” Voldemort hissed, “I desire to see.” The Dark Lord reached into the heap of things by the altar, and picked up the wrapped form of Harry’s wand. It was thrown, gliding through the air and then dropping at Harry’s feet; and then the Dark Lord floated back, the heap of things moving smoothly backwards with him.

Harry unwrapped his wand, and moved forward.

\emph{We have our wand back, that’s step one,} said the last voice, the voice of hope.

No part of Harry had any idea what step two might be, but it was still step one accomplished.

And Harry stood before the reformed body of Hermione Granger, who was still naked and dead, on a twilight-lit stone altar.

“Lord Voldemort,” Harry said, “I beg you, please give her some clothes. It might help me do this.”

“Granted,” hissed Voldemort. The pain in Harry’s scar flared as the naked girl’s body lifted into the air, then flared again as dead leaves danced around her and she was clothed in the seeming of a Hogwarts uniform, though the trim was red instead of blue. Hermione Granger’s hands folded over her chest, her legs straightened, and her body drifted back down.

Harry looked at her.

Focused on her, now that she looked human again.

\emph{She looks like she is sleeping, not dead.} It took a conscious effort to look for breathing, fail to see it, and make the deduction. So far as naked perception was concerned…Hermione might as well be alive, right now.

That Hermione Granger would not approve of this situation, taken as a whole, seemed beyond question. But it didn’t mean that she would rather stay dead than be alive, other things being equal, though they might not be.

\emph{Because you wish to live, because my best guess is that you would wish to live…}

Harry reached out his shaking left hand, and touched Hermione’s forehead. It was warm now, not the chill of five degrees Celsius; either Voldemort had increased her body temperature to normal, or the magic of the ritual had done it automatically. Which meant that Hermione’s brain was currently warm and without oxygen, come to think.

That did it, the sense of urgency rising in him.

Harry’s feet assumed the stance, his wand swung up to point at Hermione Granger’s dead body. The \emph{only} thing wrong with Hermione’s body was that it was dead; everything else about that body was right, only one thing needed changing.

\emph{You don’t belong here, death.}

“\shout{Expecto,}” Harry shouted, feeling \emph{the magic and the life} rise up into the Patronus Charm that was fuelled by both, “\shout{Patronum!}”

The girl in the Hogwarts uniform was surrounded by a blazing aura of silver fire, as the Patronus was born inside her.

Harry staggered, as he felt a \emph{dip,} a bite. Intuition or Tom Riddle’s memory told Harry that the life and magic that had just flowed into Hermione would never return to him, either one. It hadn’t been all his life or all his magic, not by a long shot, there hadn’t been \emph{time} to expend that much, but whatever he’d just expended was gone forever.

And Hermione Granger was breathing, just like she was sleeping, rhythmic inhalations and exhalations. The twilight sky had dimmed further, and Harry could not see if colour was returning to her, but it should have been, it certainly should have been. She looked to be sleeping peacefully, and it wasn’t because being dead looked like sleeping, it was because she was asleep and her body was fine and nothing was hurting her while she slept.

Some part of Harry, that had somehow managed not to speak up earlier, quietly pointed out that they were still in a graveyard, the recently victorious Lord Voldemort was still in control of the situation, and that his guess about Hermione wanting to be alive was just a guess.

Harry was still smiling, as he slowly lowered his wand. The celebratory fireworks going off inside his mind were restrained, Harry wasn’t screaming and running around in little circles like Professor Flitwick, but that—

That—

\emph{\emph{That,}} Harry said aloud inside his mind, \emph{\emph{That} is what I call Step Two.}

“Interesting,” said the cold high voice. “Your Patronus draws upon your life as well as your magic…I guessed that much, for it was too powerful for a first-year to fuel with magic alone. And yet there must be more to the puzzle, since not just any life-fuelled spell would have done…was your happy thought the image of her returning to life? Was that all it took?” Lord Voldemort was again toying with his wand, a dark interest in those red-slitted eyes. “I suspect I will feel quite stupid when I finally comprehend that spell, some day in my eternity. Now step away from the girl. \parsel{There is more work I intend to do, to give her best chance of continued life.}”

Harry stepped back, reluctantly, the sense of tension starting to return to him. He almost tripped over one haphazard grave marker, as the Dark Lord continued to walk forward.

Standing before the altar, the Dark Lord laid one finger upon Hermione Granger’s forehead.

Then the Dark Lord tapped his finger upon Hermione Granger’s forehead, and said, in a voice so low Harry almost did not hear, “\emph{Requiescus.}”

Voldemort waved his hand at an obelisk, which began to rotate, turning itself to lay flat upon the ground, pointing outward. “Fascinating indeed,” Voldemort hissed. “She is alive, and magical, and not another Tom Riddle as I feared you might have made her.”

The tension was rising again in Harry. He’d put his wand away into the back belt of his trousers, he \emph{did not want} to remind Voldemort that he still had the wand on him. “What are you doing to her now?”

Another obelisk turned, lay flat upon the ground. “\parsel{There is old, lost ritual to sacrifice magical creature, transfer magical nature to subject. Limitations are great. Transfer is temporary, only few hours. Subject sometimes dies when transfer wears off. But Stone will make permanent.}”

Four obelisks lay flat upon the ground, evenly spaced; the other two obelisks had been floated away.

Voldemort began to reach into his own mouth, checked himself, hissed with annoyance again. He gestured at the sleeping mouth of Quirinus Quirrell, and from Quirrell’s mouth floated up two teeth, almost invisible in the falling night. One of these went to the pile of items, the other floated to before the altar.

Moments later, Harry cried out and took a step back.

Huge and misshapen, lumpy skin, legs thick as tree-trunks, a small head that looked like a coconut perched upon a boulder.

A mountain troll stood within the circle of obelisks, motionless as though asleep while standing.

“\emph{What are you doing?}”

Voldemort’s mouth was stretched in a wide smile; it looked \emph{horrible} on him, like his face had too many teeth. “\parsel{Shall sacrifice my fallback weapon, and girl-child shall gain troll’s power of regeneration. Transfiguration sickness is nothing before that, if perchance it was not fixed by previous ritual. And no knife shall slay girl-child, nor cutting curse, nor sickness take her.}”

“Why—why are you doing this?” Harry’s voice shook.

“\parsel{Have not the tiniest intention of letting girl-child die again, after going to such lengths to resurrect her.}”

Harry swallowed. “I’m very confused.” Was Voldemort \emph{practising being nice?} This hypothesis did not seem like a sufficient explanation.

“Stay well back,” Voldemort said coldly. “This ritual is Darker than the last.” The Dark Lord began a new chant, softer syllables that seemed to seethe through the air like living things; and Harry, feeling a new surge of apprehension, stepped backwards.

Then Harry cried aloud, as pain flared again within his scar. The mountain troll crumbled in on itself, becoming ashes hanging in the air, then dust, and then the dust seemed to blow away without going anywhere; it was gone.

Hermione Granger slept on peacefully, whatever spell of repose Voldemort had cast on her being sufficient to the task.

“Um,” Harry said in a small voice. “Did it work?”

“\emph{Diffindo.}”

Harry stepped forward with a choked yell, and then halted, both as the stupidity of his motion caught up with him, and as the sudden cut that the Severing Charm had opened on Hermione’s leg closed almost as quickly as it had been made. In seconds there was only a light stain of blood on the surrounding flesh.

The Stone was laid again on Hermione, and after a time it turned. Voldemort laughed once more, as he passed his hand over her. “Marvellous.”

Then another tiny tooth was floating within the circle of obelisks; and an instant later, a unicorn stood where the troll had stood before, eyes dull and head lowered.

“What?” Harry said. “Why a \emph{unicorn?}”

“\parsel{Power of unicorn’s blood to preserve life makes excellent combination with troll’s healing. Only Fiendfyre and Killing Curse shall girl-child fear, from this day.}” A flicker of snakish laughter. “\parsel{Besides, had spare unicorn left over, might as well use.}”

“Unicorn’s blood has side effects-”

“\parsel{That is only when power of unicorn’s blood is stolen by another. This spell will make power of unicorn belong inside girl-child, as if she was always born that way.}”

The grim chant and its seething words began again.

Harry watched, not understanding in the slightest.

\emph{Forget understanding, what am I seeing?}

\emph{I’m seeing the Dark Lord Voldemort going to enormous lengths to resurrect Hermione Granger and keep her alive. It’s like he thinks that his own life depends on Hermione Granger being alive, somehow.}

The confused parts of Harry looked around for a procedure to follow. ‘Make a prediction based on your best current hypothesis’ was the first thought that came to mind, but it didn’t seem to lead anywhere. The plot of the story wasn’t going how it ought to, after the villain had won.

Again the blaze of pain in his scar, like a blow to Harry’s forehead. The unicorn swayed, and then disintegrated as the troll had done.

The Dark Lord laid the Stone upon Hermione’s form once more, clasping her hands around it.

Voldemort watched the unremarkable process for a time, then turned while the Stone still laid on her, making a high humming sound in his throat. “Ah, yes,” hissed Voldemort. “That would be most appropriate. Do you still have the diary I gave you, boy? The diary of the famous scientist?”

Harry’s brain took a moment to place what Voldemort was talking about. It had been in Mary’s Room, in Mary’s Place, in October, that precious gift from a friend. The thought should have triggered a wave of awful sadness, for the Professor Quirrell that had been lost or never real; but there had been enough of that emotion already, and his brain had set it aside for now.

“Yes,” Harry said aloud. “I think it’s in my pouch, can I check?” Harry \emph{knew} it was in the pouch. He’d loaded it up with everything that he might possibly conceivably need, that he owned or had bought; everything that could have been a quest item.

From the heap of items by the altar, Harry’s mokeskin pouch was drawn out, tossed to Harry’s feet.

“Roger Bacon’s diary,” Harry said as he reached in a hand, and the diary appeared. Professor Quirrell had said that the diary would emerge unscathed from a fire, so Harry threw it toward Voldemort’s altar. Harry did not wince; there were more important things to worry about than polite treatment of books, even that one.

Voldemort picked up the diary, examining it, appearing quite absorbed.

Harry, as quietly and unobtrusively as he could, attached the pouch to his belt loop in back, where it wouldn’t be visible, near where Harry had put his wand.

\emph{Step three, the pouch.}

“Yes,” Voldemort hissed as he flipped pages of the diary, “this will do quite well.” The Stone moved slightly, and the Dark Lord’s other hand stored the Stone again within his robes.

“What was your hidden purpose behind the diary?” Harry said when the pouch was attached to his belt, and he’d put both of his empty hands where Voldemort could see them again. “I tried translating a little at the beginning, but it was going slowly—” Actually, it had been excruciatingly slow and Harry had found other priorities.

“\parsel{Diary was exactly what it seemed, a gift meant to seduce you to my side.}” Voldemort made intricate gestures in the air with his wand, not even looking at what his hand was doing, as he held the diary in his other hand. For a moment Harry thought he could see a trail of darkness in the air, but the moonlight was too faint for certainty. “And now, my dear boy,” Voldemort’s high voice was laced with grim amusement, as his wand briefly tapped Hermione Granger’s forehead with a casual gesture, “I make this diary into a far more precious gift, a sign of how much wisdom I have learned from you. For I would never want you to be deprived of Hermione Granger’s counsel and restraint, not ever while the stars yet live. \emph{Avada Kedavra.}”

The green bolt of the Killing Curse blazed out faster than Harry could possibly have cast the Patronus Charm, faster than he could possibly have moved, it was already over even as Harry cried out and went for his wand.

Quirinus Quirrell’s unconscious body did not even jerk, in death. The green light struck into it without other sign.

Darkness glowed in the air, anti-light in the trails that Voldemort had made before, and the Diary of Roger Bacon darkened as though corruption were creeping over it, even as a shiver appeared in the air around Hermione Granger’s form.

The pain in Harry’s scar flared overwhelmingly, like a brand driven into his forehead, it sent Harry dodging unthinkingly to one side as Tom Riddle’s reflexes took over.

And Voldemort was also screaming, shrieking as he dropped the diary to the ground, holding his own head and screaming.

\emph{Chance—}

The last voice of hope said that, as Harry tried frantically to think, to understand. There wasn’t any \emph{point} in trying to kill Voldemort now, it might only \emph{annoy} him, weapons couldn’t kill him while any of his hundreds of horcruxes remained—

But it still seemed worth it to temporarily discarnate Voldemort, take the Stone and Hermione and run.

Harry’s right hand had already taken his wand. His left hand went around to his back, reached awkwardly into his pouch, began to make a silent sign, three English letters.

“No!” cried Voldemort. He’d dropped his hands from his head, was staring at Hermione’s body as though bewildered. “No, no!”

The item came up from Harry’s pouch into his hand, and Harry began to step forward as smoothly as he could, diminishing the range between them to what his brief trials had shown was doable.

“My great creation—” gasped Voldemort. His voice was high, sounding panicked. “Two different spirits cannot exist in the same world—it is gone, it is severed! A horcrux, I must make a horcrux at once—” Voldemort’s gaze fell on Hermione Granger’s still-sleeping form, and he began to raise his wand in the air, executing the same gestures as before.

Harry raised his gun and pulled the trigger three times.

%  LocalWords:  hah hahahahaha Ahahahaha hahahaha Hyakuju montauk Klaudia
%  LocalWords:  Alicja Apokatastethi apokatastethi mou emoi Fal hou
%  LocalWords:  Requiescus
