\chapter{Self-Actualization, \replacement{Final}{Finale}: Responsibility}

\lettrine{I}{t} was a looping, meandering alley in the midst of Hogwarts, wandering like a stray lock of hair; sometimes crossing itself, it seemed, but you couldn’t ever get to the end if you gave into the temptation of apparent shortcuts.

At the end of the tangle, six students leaned against rough stones, robes black against the grey walls and trimmed in green, eyes darting from one to each other. Torches burned in the windowless sconce, casting light to ward off the darkness and heat to ward off the chill of the Slytherin dungeons.

“I am \emph{certain,}” Reese Belka snapped, “absolutely \emph{certain,} that was no true ritual. Little firstie witches can’t do that kind of magic, and even if they could, who’s ever heard of a Dark ritual which \emph{sacrifices} a sealed horror for—\emph{that?}”

“Were you—” said Lucian Bole. “I mean—after that girl snapped her fingers—”

Belka’s glare should have melted him. “No,” she spat, “I was \emph{not.}”

“That is, she wasn’t naked,” drawled Marcus Flint, his broad shoulders leaning back in apparent relaxation against the lumpy stone surface. “Covered in chocolate frosting, yes, but not naked.”

“This day Potter has offered great insult to our Houses,” said the grim voice of Jaime Astorga.

“Yes, well, I’m sorry to be blunt,” Randolph Lee said evenly. The seventh-year duelist rubbed at his chin, where a faint fuzz of beard had been allowed to grow. “But when someone sticks you to the ceiling, it’s a message, Astorga. It’s a message which says: I’m an incredibly powerful Dark Wizard who could’ve done anything to you I damn well pleased, and I don’t care if your House is offended, either.”

Robert Jugson III gave a soft, low laugh at this, a chuckle that sent chills down several spines. “It makes you wonder if you picked the wrong side, doesn’t it? I’ve heard tales about \emph{messages} like that, sent at the old Dark Lord’s bidding...”

“I’m not ready to kneel to Potter just yet,” said Astorga, staring hard into Jugson’s eyes.

“Neither am I,” said Belka.

Jugson was holding his wand, and he turned it idly back and forth in his fingers, pointing it up and then downward. “Are you a Gryffindor or a Slytherin?” said Jugson. “Everyone’s got a price. Everyone smart.”

This statement produced a moment of silence.

“Shouldn’t Malfoy be here?” Bole said tentatively.

Flint gave a dismissive flick of his fingers. “Whatever Malfoy’s plotting, he wants to put on an air of innocence. He can’t be seen missing at the same time as us.”

“But everyone \emph{knows} that already,” said Bole. “Even in the other Houses.”

“Yes, very clumsy,” said Belka. She snorted. “Malfoy or no, he’s just a little firstie and we don’t need him here.”

“I will owl my father,” Jugson said softly, “and \emph{he} will speak to Lord Malfoy himself—” Abruptly, Jugson stopped speaking.

“I don’t know about \emph{you}, dearies,” Belka said with fake sweetness, “but \emph{I} don’t plan on running scared from a false ritual, and \emph{I’m} not done with Potter and his pet mudblood.”

Nobody answered. All their gazes were looking past her.

Slowly, Belka turned around to see what the others were staring at.

“You will do \emph{nothing,}” hissed their Head of House. Severus Snape’s face was enraged, when he spoke small spots of spittle flew from his mouth, further dotting his already-dirtied robes. “You fools have done \emph{enough!} You have embarrassed my House—\emph{lost} to first-years—now you speak of embroiling noble Lords of the Wizengamot in your \emph{pathetic} childish squabbles? \emph{I} shall deal with this matter. \emph{You} will not embarrass this House again, you will not \emph{risk} embarrassing this House again! You are \emph{done} with fighting witches, and if I hear otherwise—”
\sbreak
If you thought they’d be sitting next to each other at dinnertime, after that, you’d be quite mistaken.

“What does she \emph{want} from me?” came the plaintive cry of a boy who, for all his extensive reading in the scientific literature, was still a bit naive about certain things. “Did she \emph{want} to get beaten up?”

The upper-year Ravenclaw boys who’d sat down next to him at the dinner-table exchanged swift glances with each other until, by some unspoken protocol, the most experienced of their number spoke.

“Look,” said Arty Grey, the seventh-year who was leading in their competition by three witches and a Defense Professor, “the thing you’ve got to understand is, just because she’s \emph{angry} doesn’t mean you lost points. Miss Granger is angry because she got all frightened and you’re \emph{there to be blamed,} you understand? But at the same time, even though she won’t admit it, she’ll be touched that her boyfriend went to such ridiculous and frankly insane lengths to protect her.”

“This is not about \emph{points,}” ground out Harry Potter, the words visibly escaping from between his clenched teeth. Dinner sat ignored on the table in front of him. “This is about \emph{justice.} And \emph{I. Am. Not. Her. Boyfriend!}”

This was met by a certain amount of sniggering from all present.

“Yeah, well,” said a sixth-year Ravenclaw boy, “I think after she kisses you to bring you out of Dementation and you stick forty-four bullies to the ceiling for her, we’ve gone way past ‘she’s not my girlfriend, really’ and into the question of what your kids will be like. Wow, that’s a scary thought...” The Ravenclaw trailed off and then said, in a smaller voice, “Please don’t look at me like that.”

“Look,” said Arty Grey, “I’m sorry to be blunt about this, but you can have justice or you can have girls, you can’t have both at the same time.” He clapped a companionable hand on Harry Potter’s shoulder. “You’ve got potential, kid, more potential than any wizard I’ve ever seen, but you’ve got to learn how to \emph{use} it, you know? Be a bit sweeter to them, learn some spells to clean up that mess you call hair. Above all, you need to hide your evilness better—not \emph{too} well, but better. Nice well-groomed boys get girls, and Dark Wizards also get girls, but nice well-groomed boys suspected of being \emph{secretly} Dark get more girls than you can imagine—”

“Not interested,” Harry said flatly, as he picked up the boy’s hand from his shoulder and unceremoniously dropped it.

“But you will be,” said Arty Grey, his voice low and foreboding. “Ah, you will be!”

Elsewhere along the same table—

“\emph{Romantic?}” shrieked Hermione Granger, so loudly that some of the girls next to her winced. “\emph{What part of that was romantic?} He didn’t \emph{ask!} He never \emph{asks!} He just sends ghosts after people and glues them to ceilings and does whatever he wants with \emph{my} life!”

“But don’t you see?” said a fourth-year witch. “It means that even though he’s evil, he \emph{loves} you!”

“You’re not helping,” said Penelope Clearwater a little further down the table, but she was ignored. Several older witches had started toward Hermione, after she’d sat down at the extreme opposite end of the table from Harry Potter, but then a swifter cloud of younger girls had surrounded Hermione in an impenetrable barrier.

“Boys,” said Hermione Granger, “should not be allowed to love girls without asking them first! This is true in a number of ways and especially when it comes to gluing people to the ceiling!”

This was also ignored. “It’s just like a play!” sighed a third-year girl.

“A play?” said Hermione. “I’d like to see the play where anything like \emph{this} happens!”

“Oh,” said the third-year girl, “I was thinking of that really \emph{romantic} one where there’s this very nice, sweet boy who makes a Floo call, only he mispronounces his destination and stumbles out into this room full of Dark Wizards who are performing a forbidden ritual that should’ve stayed forever lost to time, and they’re sacrificing seven victims in order to unseal this ancient horror which is supposed to grant someone a wish if it’s freed, so of course the boy’s presence interrupts the ritual, and as the horror is eating all the Dark Wizards and everyone is dying the boy’s last thought is that he wishes he could’ve had a girlfriend, and the next thing you know the boy is lying in the lap of this beautiful woman whose eyes are burning with a dreadful light, only she doesn’t understand anything about being human so the boy always has to stop her eating people. This is just like that play, only you’re the boy and Harry Potter is the girl!”

“That...” Hermione said, feeling quite surprised. “That actually \emph{does} sound something like—”

“It \emph{does?}” blurted a second-year girl sitting across the table, who was now leaning forward, looking horrified and yet even more fascinated.

“No!” said Hermione. “I mean—\emph{he’s not my boyfriend!}”

Two seconds later, Hermione’s ears caught up with what her lips had just said.

The fourth-year witch put her hand on Hermione’s shoulder and gave her a comforting squeeze. “Miss Granger,” she said in a soothing voice, “I think if you’re really honest with yourself, you’ll admit that the real reason you’re angry with your dark master is that he channeled his unspeakable powers through Tracey Davis instead of you.”

Hermione’s mouth opened but her throat locked up before the words came out, which was probably a good thing, because if she’d actually yelled that loudly it would’ve broken something.

“How’s that possible, actually?” said the third-year girl. “I mean for Harry Potter to work through another girl even though he’s bound himself to you? Do the three of you have one of those, you know, arrangements?”

“\emph{Gaaaaack,}” said Hermione Granger, her throat still locked, her brain halted, and her vocal cords spontaneously making a noise like she was coughing up a yak.
\sbreak
\emph{(Later.)}

“I don’t understand why you’re being so \emph{unreasonable},” said another second-year witch, who’d replaced the third-year-girl after Hermione had threatened to ask Tracey to eat her soul. “I mean, really, if someone like Harry Potter rescued \emph{me}, I’d be—sending him thank-you cards, and hugging him, and,” the girl’s face was a bit red, “well, kissing him, I’d hope.”

“Yeah!” said the other second-year witch. “I’ve never understood why girls in plays get \emph{angry} when the main character goes out of his way to be nice to them. \emph{I} wouldn’t act like that if the hero liked \emph{me.}”

Hermione Granger had dropped her head to the dinner table, her hands slowly pulling at her hair.

“You just don’t understand male psychology,” the fourth-year witch said in an authoritative voice. “Granger’s got to make it \emph{look} like she can mysteriously resist his seductive charm.”
\sbreak
\emph{(Even later.)}

And so before long Hermione Granger had turned to the only person left she could talk to, the only person guaranteed to understand her point of view—

“They’re all mad,” said Hermione Granger as she strode vigorously toward Ravenclaw tower, having left dinner a bit early. “Everyone except you and me, Harry, I mean \emph{everyone} except us in this whole school of Hogwarts, they’re all entirely \emph{mad.} And Ravenclaw girls are the \emph{worst,} I don’t know \emph{what} Ravenclaw girls go reading when they get older, but I’m certain they ought not to be reading it. One witch asked me if the two of us had soul-bonded, which I’m going to look up in the library tonight, but I’m pretty sure has never actually happened—”

“I don’t even know a \emph{name} for this kind of fallacious reasoning,” said Harry Potter. The boy was walking normally, which meant he often had to skip forward a few steps to match her own indignation-fueled speed. “I seriously think if it was up to \emph{them}, they’d be dragging us off this minute to get our names changed to Potter-Evans-Verres-Granger... Ugh, saying that out loud makes me realize how awful it sounds.”

“You mean \emph{your} name would be Potter-Evans-Verres-Granger and \emph{mine} would be Granger-Potter-Evans-Verres,” said Hermione. “It’s too horrible to imagine.”

“No,” said the boy, “House Potter is a Noble House, so I think that name stays in front—”

“\emph{What?}” she said indignantly. “Who says \emph{we} have to—”

There was a sudden awful silence, broken only by the thuds of their shoes.

“\emph{Anyhow,}” Hermione said hastily, “some of the crazy things they said at dinner got me thinking, so I just want to say, Harry, that I really am grateful to you for saving me and everybody from getting beat up, and even though some parts of this afternoon upset me, I’m sure we can just talk about it calmly.”

“Ah...” Harry said with a faint and tentative smile, his eyes showing a mixture of befuddlement and apprehension, “that’s...\ good, I guess?”

To be specific, there’d been the fourth-year witch explaining that, since Harry was the evil wizard who’d fallen in love with Hermione, and Hermione was the pure and innocent girl who would either redeem him or get seduced by the Dark Arts herself, it followed that Hermione \emph{had} to be perpetually indignant at anything Harry did, even if it was him heroically saving her from certain doom, just so that their romance wouldn’t resolve itself before the end of Act IV. And \emph{then} Penelope Clearwater, who Hermione had really thought was smarter than that, had remarked in a loud voice that for identical reasons it was \emph{impossible} for Hermione to just go over and talk sensibly with Harry about why she was feeling hurt, and anyway Dark Wizards were attracted to passionate defiance in a woman, not logic. This was the point at which Hermione had shoved herself up from the benches, stomped furiously over to where Harry was sitting, and asked him in a reasonable voice if the two of them could go for a walk and sort things out.

“So in other words,” Hermione said in her calmest voice ever, “you’re not really in trouble with me, I’m still talking to you, we’re still friends, and we’re still studying together. We’re \emph{not} having a fight. Right?”

Somehow this only seemed to increase Harry Potter’s apprehension. “Right,” said the Boy-Who-Lived.

“Great!” said Hermione. “So, \emph{have} you worked out why I was upset, Mr.~Potter?”

There was a pause. “You wanted me to keep out of your affairs?” Harry said cautiously. “I mean—I know you wanted to do things on your own. And I \emph{was} staying out of your way, until I’d heard you’d gotten ambushed by three junior Death Eaters and, honestly, I wasn’t expecting that. \emph{Professor Quirrell} wasn’t expecting that. I started to worry you’d gotten in over your head and then, no offense Hermione, forty-four bullies in a massed ambush is way beyond what \emph{anyone} could handle without help. That’s why I thought you really needed help just that once—”

“No, that part’s fine,” said Hermione. “We \emph{were} in over our heads, honestly. Please guess again, Mr.~Potter.”

“Um,” said Harry. “What Tracey did...\ startled you?”

“Startled me, Mr.~Potter?” There might have been a touch of acidity in her voice. “No, Mr.~Potter, I was \emph{scared.} I was \emph{frightened.} I wouldn’t want to admit to being afraid of just \emph{dragons} or something, people might think I was \emph{cowardly}, but when you can hear distant voices crying ‘Tekeli-li! Tekeli-li!’ and there’s pools of blood seeping out from under all the doors, then it’s okay to be scared.”

“I \emph{am} sorry,” Harry said with what sounded like genuine regret. “I thought you’d realize it was me.”

“And the \emph{reason} we all got scared like that, Mr.~Potter, was that \emph{you didn’t ask first!}” Despite her intentions, Hermione found her voice was rising again. “You should’ve \emph{asked} me before you did something like that, Harry! You should’ve said very specifically, ‘Hermione, can I make blood come out from under the doors?’ It’s important to be specific when you’re asking about that sort of thing!”

The boy rubbed the back of his neck as he walked. “I...\ honestly, I just thought you’d \emph{have} to say no.”

“Yes, Mr.~Potter, \emph{I could’ve said no}. That’s \emph{the whole point of asking first}, Mr.~Potter!”

“No, I mean you’d have \emph{had} to say no, whether or not it was what you \emph{really} wanted. And then all of you would’ve gotten beaten up and it would’ve been \emph{my} fault for asking first.”

Hermione’s eyebrows went up in a bit of surprise, and she kept walking for a few steps while she tried to understand this. “What?” she said.

“Well...” the boy said a bit slowly. “I mean...\ you’re the Sunshine General, aren’t you? You \emph{couldn’t} say yes to me scaring people, not even bullies, not even to save your friends from getting beaten up. You would’ve \emph{had} to say no, and then you would’ve gotten hurt. This way, you can tell people honestly that you had no idea and that it wasn’t your fault. That’s why I didn’t warn you.”

Hermione stopped walking, turned to face Harry full on instead of just turning her head. Her voice was carefully even as she said, “Harry, you’ve \emph{got} to stop coming up with clever reasons for doing stupid things.”

Harry’s eyebrows flew up. After a moment he said, “Look... I know what you mean, of course, but there’s still the question of whether it’s actually \emph{is} a good idea, not just a clever one—”

“I understand why you did what you did today,” Hermione said. “But I want you to promise that from now on, you’ll ask me first, always, even if you can come up with a reason why you shouldn’t.”

There was a pause that stretched, and Hermione could feel her heart sinking.

“Hermione—” Harry started to say.

“\emph{Why?}” The frustration burst out into her voice. “\emph{Why is it so awful? All you have to do is ask!”}

Harry’s eyes were very serious. “Who in \SPHEW do you try hardest to defend, Hermione? Who are you most afraid for, when you fight?”

“Hannah Abbott,” Hermione said without having to think about it, and then felt a little bad, because Hannah \emph{was} trying hard and she \emph{had} improved a lot—

“Would you feel okay about trusting someone else, like Tracey, with \emph{final} responsibility for protecting Hannah? If you knew Hannah was about to walk into an ambush, and you came up with a plan for protecting her, would you feel good about letting Tracey say whether or not you were allowed to do it?”

“Well...\ no?” said Hermione, puzzled.

The green eyes of the Boy-Who-Lived were steady on hers. “Would you trust \emph{Hannah} to have the final say in whether she needed protecting?”

“I—” said Hermione, and then paused. It was strange, she knew the right answer and she also knew the right answer wasn’t actually true. Hannah was trying so hard to prove she wasn’t afraid, even though she \emph{was,} and it was easy to see how the Hufflepuff girl might try \emph{too} hard—

Then Hermione realized the implication. “You think I’m like \emph{Hannah?}”

“Not...\ exactly...” Harry ran his hands through his mess of hair. “Listen, Hermione, what would \emph{you} have suggested doing, if I’d warned you about an ambush by forty-four bullies?”

“I would’ve done the \emph{responsible} thing and told \emph{Professor McGonagall} and let \emph{her} take care of it,” Hermione said promptly. “And \emph{then} there wouldn’t have been darkness and people screaming and horrible blue light—”

But Harry just shook his head. “That’s \emph{not} the responsible thing to do, Hermione. It’s what someone playing the \emph{role} of a responsible girl would do. \emph{Yes}, I thought of going to Professor McGonagall. But she would’ve only stopped the disaster \emph{once.} Probably before any disturbance happened in the first place, like by telling the bullies she knew. If the bullies got punished just for plotting, it would be by losing House points, or at worst a day’s detention, not anything that would really scare them. And then the bullies would have \emph{tried again}. Fewer of them, with better operational security so I didn’t hear about it. They would probably ambush \emph{one} of you, alone. Professor McGonagall doesn’t have the \emph{authority} to do something scary enough to protect you—and \emph{she} wouldn’t have overstepped her authority, because she’s not really responsible.”

“\emph{Professor McGonagall} isn’t responsible?” Hermione said in\-cre\-dulously. She jammed her hands on her hips, now openly glaring at him. “Are you \emph{nuts?”}

The boy didn’t blink. “You could call it heroic responsibility, maybe,” Harry Potter said. “Not like the usual sort. It means that whatever happens, no matter what, it’s \emph{always} your fault. Even if you tell Professor McGonagall, she’s not responsible for what happens, \emph{you} are. Following the school rules isn’t an excuse, someone else being in charge isn’t an excuse, even trying your best isn’t an excuse. There just aren’t any excuses, you’ve got to \emph{get the job done no matter what}.” Harry’s face tightened. “That’s why I say you’re not thinking responsibly, Hermione. Thinking that your job is done when you tell Professor McGonagall—that isn’t heroine thinking. Like Hannah being beat up is \emph{okay} then, because it isn’t \emph{your fault} anymore. Being a heroine means your job isn’t finished until you’ve done\emph{ whatever it takes} to protect the other girls, \emph{permanently.}” In Harry’s voice was a touch of the steel he had acquired since the day Fawkes had been on his shoulder. “You can’t think as if just following the rules means you’ve done your duty.”

“I think,” Hermione said evenly, “that you and I might disagree about some things, Mr.~Potter. Like whether you or Professor McGonagall is more \emph{responsible}, and whether being \emph{responsible} usually involves people running around and screaming, and how much it’s a good idea to follow school rules. And just because we disagree, Mr.~Potter, doesn’t mean that \emph{you} get the final say.”

“Well,” said Harry, “you asked what was \emph{so} awful about having to ask you first, and it was a surprisingly good question, so I examined my mind and that’s what I found. I think my real fear is that if Hannah is in trouble and I come up with a way to save her that seems weird or dark or something, you might not weigh the consequences to Hannah. You might not accept the heroine’s responsibility of coming up with \emph{some} way to save her, somehow, no matter what. Instead you’d just carry out the \emph{role} of Hermione Granger, the sensible Ravenclaw girl; and the \emph{role} of Hermione Granger automatically says no, whether or not she has a better plan in mind. And then forty-four bullies will take turns beating up Hannah Abbott, and it’ll all be my fault because I \emph{knew,} even if I didn’t want reality to be that way, I knew that was how it would go. I’m pretty sure that was my secret, wordless, unutterable fear.”

The frustration was building up inside her again. “It’s \emph{my} life!” Hermione burst out. She could imagine what it would be like with Harry messing with her all the time, constantly inventing justifications not to ask her first and not to listen to her objections. She shouldn’t have to \emph{win an argument} just to—“There’ll \emph{always} be some reason, you can \emph{always} say I’m not thinking right! I want my\emph{ own life!} Otherwise I’ll walk away, I really will, I mean it Harry.”

Harry sighed. “This is exactly where I didn’t want things to end up, and here we are. You’re afraid of just the same thing I am, aren’t you? Afraid that if \emph{you} let go of the steering wheel, we’ll crash.” The corners of his lips twisted, but it didn’t look like a real smile. “That’s something I can understand.”

“I don’t think you understand \emph{at all!}” Hermione said sharply. “You said we’d be \emph{partners,} Harry!”

That stopped him, she could see it stop him.

“How about this?” Harry said at last. “I’ll promise to ask you first before I do anything that could be interpreted as meddling in your affairs. Only \emph{you’ve} got to promise \emph{me} to be reasonable, Hermione. I mean \emph{really}, genuinely, stop and think for twenty seconds first, treat it as a real choice. The sort of reasonableness where you realize I’m offering a way to protect the other girls, and that if you automatically say \emph{no} without considering it properly, there’s this \emph{actual consequence} where Hannah Abbott ends up in the hospital.”

Hermione stared at Harry, as his recitation wound down.

“Well?” said Harry.

“I shouldn’t have to make promises,” she said, “just to be \emph{consulted} about \emph{my own life.}” She turned from Harry and began walking toward the Ravenclaw tower, not looking at him. “But I’ll think about it, anyway.”

She heard Harry sigh, and after that they walked in silence for a while, passing through an archway of some reddish metal like copper, into a corridor that was just like the one they’d left except that it was tiled in pentagons instead of squares.

“Hermione...” said Harry. “I’ve been watching you and thinking, since the day you said you were going to be a hero. You’ve \emph{got} the courage. You’ll fight for what’s right, even in the face of enemies that would scare other people away. You’ve certainly got the raw intelligence for it, and you’re probably a better person inside than I am. But even so...\ well, to be honest, Hermione... I can’t quite see you filling Dumbledore’s shoes, leading magical Britain’s fight against You-Know-Who. Not yet, anyway.”

Hermione had turned her head to stare at Harry, who just went on walking, as though lost in thought. Fill \emph{those} shoes? She’d never tried to imagine herself that way. She’d never \emph{imagined} imagining herself that way.

“And maybe I’m wrong,” Harry said as they walked. “Maybe I’ve just read too many stories where the heroes never do the sensible thing and follow the rules and tell their Professor McGonagalls, so my brain doesn’t think you’re a proper storybook hero. Maybe it’s you who’s the sane one, Hermione, and me who’s just being silly. But every time you talk about following rules or relying on teachers, I get that same feeling, like it’s bound up with this one last thing that’s stopping you, one last thing that puts your PC self to sleep and turns you into an NPC again...” Harry let out a sigh. “Maybe that’s why Dumbledore said I should have wicked stepparents.”

“He said \emph{what?}”

Harry nodded. “I still don’t know whether the Headmaster was joking or...\ the thing is, he was \emph{right} in a way. I \emph{had} loving parents, but I never felt like I could trust their decisions, they weren’t \emph{sane} enough. I always knew that if I didn’t think things through myself, I might get hurt. Professor McGonagall will do whatever it takes to get the job done \emph{if} I’m there to nag her about it, she doesn’t break rules on her own without heroic supervision. Professor Quirrell really \emph{is} someone who gets things done no matter what, and he’s the only other person I know who notices stuff like the Snitch ruining Quidditch. But\emph{ him} I can’t trust to be \emph{good}. Even if it’s sad, I think that’s part of the environment that creates what Dumbledore calls a hero—people who don’t have anyone else to shove final responsibility onto, and that’s why they form the mental habit of tracking everything themselves.”

Hermione didn’t say anything to that, but she was thinking back to something Godric Gryffindor had written near the end of his very short autobiography. Briefly and without any explanation, because the scroll had been meant to be copied by hand, centuries before the Muggle printing press had inspired wizards to invent the Reading-Writing Quill.

\emph{No rescuer hath the rescuer,} Godric Gryffindor had written. \emph{No Lord hath the champion, no mother and no father, only nothingness above.}

If \emph{that} was the price of being a hero, Hermione wasn’t sure she wanted to pay it. Or maybe—though it wasn’t the sort of thing she would have thought, before she started hanging around Harry—maybe Godric Gryffindor had gotten it \emph{wrong}.

“Do you trust \emph{Dumbledore?”} Hermione said. “I mean, he’s right here in our school and he’s the most legendary hero in the whole world—”

“He \emph{was} the most legendary hero,” said Harry. “Now he sets chickens on fire. Honestly, does Dumbledore seem reliable to \emph{you?}”

Hermione didn’t answer.

Side by side, the two of them began to climb huge wide spiral stairs, the steps alternating between bronze metal and blue stone; the final approach to where the Ravenclaw portrait waited to guard their dorm with silly riddles.

“Oh, and I just thought of something I should tell you,” Harry said when they were about halfway up. “Since it affects your life and all. Think of it as a sort of down payment—”

“What is it?” said Hermione.

“I predict \SPHEW is about to retire.”

“\emph{Retire?}” Hermione said, almost stumbling on one of the stairs.

“Yeah,” Harry said. “I mean, I could be wrong, but I suspect the teachers are about to clamp down hard on fighting in the corridors.” Harry was grinning as he spoke, a glint in his eyes behind the glasses hinting at secret knowledge. “Cast new wards to detect offensive hexes, or start verifying reports of bullying using Veritaserum—I can think of several ways they might shut it down. But if I’m right, it’s something to celebrate, Hermione, you and all of you. You kicked up enough public ruckus that you got them to actually \emph{do} something about the bullying. \emph{All} the bullying.”

Slowly, then, a smile began to creep up her lips, and as she reached the top of the stairs and began walking toward the Ravenclaw portrait for her riddle, Hermione felt rather lighter on her feet, a wonderful lifting feeling spreading through her like she’d been pumped full of helium.

Somehow, despite all the effort the eight of them had put in, she hadn’t expected \emph{that} much, she hadn’t expected it to actually \emph{work}.

They’d made a \emph{difference...}
\sbreak
It was the end of breakfast-time on the next morning.

The students from every year sat very still in their benches, all heads turned in the same direction, toward the Head Table, before which one lone first-year girl stood rigid and motionless, her head tilted back to stare up at the Head of House Slytherin.

Professor Snape’s face was twisted with fury and triumph, vindictive as any painting of a Dark Wizard; and behind him the other Professors sat at the Head Table, watching with faces as though carved from stone.

“—permanently disbanded,” spat the Potions Master. “Your self-proclaimed Society is \emph{outlawed} within Hogwarts, by my decision as a Professor! If your Society or any member of it is discovered fighting in the hallways again, Granger, you will be \emph{personally} held responsible and expelled, by me, from the Hogwarts School of Witchcraft and Wizardry!”

That first-year girl stood there, before the Head Table where she’d been called before only to receive commendations and smiles; stood there with her spine held tall and upright in its curve like a centaur’s bow, giving nothing to the enemy.

That first-year witch stood there with all tears and anger bottled, her face still, nothing changing of her outward appearance, while something slowly broke inside her, she could feel it breaking.

It broke further when Professor Snape gave her two weeks detention for the crime of violence in school, sneering with the contemptuous face he’d shown them all on the first day of Potions, and with a little twist in the corner of his smile that said the Potions Master knew exactly how unfair he was being.

Whatever-it-was inside her cracked all the way through, from top to bottom, when Professor Snape took one hundred points from Ravenclaw.

It ended, then, and Snape told her she was dismissed.

She turned around and saw that at the Ravenclaw table, Harry Potter was sitting still in his place, she couldn’t see his expression from here, she saw his fists on the table but she couldn’t see if they were clenched white like her own. She had whispered to him, when Professor Snape had called her, that he wasn’t to do anything without asking first.

Hermione wheeled back again to look at the Head Table, just as Snape was turning away from her to resume his place.

“I said you’re dismissed, girl,” said the sneering voice, but there was a pleased smile on Snape’s face, like he was waiting for her to do something—

Hermione strode forward another five steps toward the Head Table and said in a breaking voice, “Headmaster?”

Utter silence filled the Great Hall.

Headmaster Dumbledore said nothing, didn’t move. It was as though he, too, was just carved from stone.

Hermione turned her gaze to look at Professor Flitwick, whose head, barely visible above the table, seemed to be staring down into his lap. Beside him, Professor Sprout’s face was very tight, she seemed to be forcing herself to watch, and her lips were trembling, but she said nothing.

Professor McGonagall’s chair was empty, the Deputy Headmistress hadn’t shown up to breakfast that morning.

“Why aren’t any of you saying anything?” said Hermione Granger. Her voice was trembling with the last of her hope, the last desperate reach for help from that place inside her. “You \emph{know} what he’s doing is wrong!”

“Two more weeks’ detention, for insolence,” Snape said silkily.

It shattered.

She looked at the Head Table for a few seconds longer, at Professor Flitwick and Professor Sprout and the empty place where Professor McGonagall should’ve been. Then Hermione Granger turned and began walking toward the Ravenclaw table.

There was a babble of voices starting up, as the students came unfrozen from where they’d sat.

And then, as she was almost to the Ravenclaw table—

The dry voice of Professor Quirrell cut through everything, and that voice said, “One hundred points to Miss Granger for doing what is right.”

Hermione almost fell over her own feet; and then she continued forward, even as Snape shouted something furious, even as Professor Quirrell leaned back in his chair and began to laugh, even as Dumbledore’s voice was saying something she didn’t catch and then she was sitting down at the Ravenclaw table again next to Harry Potter.

Harry Potter was frozen beside her, he looked like someone who didn’t dare move.

“It’s all right,” her voice said to him, automatically without there being any choice or thought involved, although really it wasn’t right at all. “But can you see if you can get me out of Snape’s detentions, like you did yourself that time?”

Harry Potter nodded, a single jerky motion of his head. “I—” said Harry. “I—I’m sorry, this—this is all my fault—”

“Don’t be \emph{ridiculous}, Harry.” It was odd how her voice was coming out all normal, and without her thinking about what to say. Hermione looked down at her breakfast plate, but eating seemed to be clearly out of the question, there was a roiling and churning in her stomach which suggested that she was already on the verge of throwing up, which was odd because she could have sworn her whole body felt numb, like she wasn’t feeling anything, at the same time.

“And,” her voice said, “if you want to break school rules or something, you can ask me about it, I promise I won’t just say no.”
\sbreak
\begin{centering}

\emph{Non est salvatori salvator,\\neque defensori dominus,\\nec pater nec mater,\\nihil supernum.}

—Godric Gryffindor,\\1202 \abbrev{C.E.}

\end{centering}


