\partchapter{The Truth}{II}

\lettrinepara{T}{\emph{om}} \emph{Riddle.}

\hplettrineextrapara
The words seemed to echo inside Harry’s head, sparking resonances that as quickly died away, broken patterns trying to complete themselves and failing.

\emph{Tom Riddle is a}

\emph{Tom Riddle was the}

\emph{Riddle}

There were other priorities occupying Harry’s attention.

Professor Quirrell was pointing a gun at him.

And for some reason Lord Voldemort hadn’t fired it yet.

Harry’s voice came out in more of a croak. “What is it that you want from me?”

“Your death,” said Professor Quirrell, “is clearly not what I am about to say, since I have had plenty of time to kill you if I wished. The fateful battle between Lord Voldemort and the Boy-Who-Lived is a figment of Dumbledore’s imagination. I know where to find your family’s house in Oxford, and I am familiar with the concept of sniper rifles. You would have died before you ever touched a wand. I hope this is clear to you, Tom?”

“Crystal,” Harry whispered. His body was still shaking, running programs more suited to fleeing a tiger than casting delicate spells or \emph{thinking.} But Harry could think of one thing the person pointing a gun at him obviously wanted him to do, a question that person was waiting for him to ask, and Harry did so. “Why are you calling me Tom?”

Professor Quirrell regarded him steadily. “Why \emph{am} I calling you Tom? Answer. Your intellect is not everything I hoped for, but it should suffice for this.”

Harry’s mouth seemed to know the answer before his brain could manage to focus on the question. “Tom Riddle is your name. Our name. That’s who Lord Voldemort is, or was, or—something.”

Professor Quirrell nodded. “Better. You have already vanquished the Dark Lord, the one and only time that you will ever do so. I have already destroyed all but a remnant of Harry Potter, eliminating the difference between our spirits and enabling us to reside in the same world. Now that it is clear to you that the battle between us is a lie, you might act sensibly to advance your own interests. Or you might not.” The gun jabbed slightly forward, causing prickles of sweat to appear on Harry’s forehead. “Drop your wand. \emph{Now}.”

Harry dropped it.

“Step away from the wand,” said Professor Quirrell.

Harry obeyed.

“Reach toward your neck,” said Professor Quirrell, “and remove your Time-Turner, touching it by the chain only. Place the Time-Turner on the ground, then step away from it as well.”

This also Harry did. Even in his state of shock, his mind still looked for a way to spin the Time-Turner in the process, a sudden move that would win; but Harry knew that Professor Quirrell would already be imagining himself in Harry’s position, looking for the same possible opportunities.

“Remove your pouch and place it also on the ground, then step away.”

Harry did this.

“Very good,” said the Defence Professor. “Now. It is time for me to obtain the Philosopher’s Stone. I mean to bring along these four first-years here, suitably Obliviated of their most recent memories so that they still recall their original purpose. Snape I shall control and set to guard this door. After this day’s work is done, I intend to kill Snape for the betrayals he has offered my other identity. The three heir-children I shall take with me afterwards, to shape their future loyalties. And know this, I have taken hostages. I have already set in motion a spell that will kill hundreds of Hogwarts students, including many you called friends. I can stop that spell using the Stone, if I obtain it successfully. If I am interrupted before then, or if I choose not to stop the spell, hundreds of students will die.” Professor Quirrell’s voice was still mild. “Do you yet perceive any interests you have at stake, boy? I would smile to hear you say ‘no’, but that is too much to hope.”

“I’d like,” Harry managed to say, through the horror, and the heartbreak, and the knives slicing away at an emotional connection that hurt like living flesh as it was cut, “for you not to do those things, Professor.” \emph{Why, Professor Quirrell, why, why did it have to turn out like this, I don’t, I don’t, I don’t want this to be happening…}

“Very well,” Professor Quirrell said. “I grant you permission to offer me something I want.” The gun gestured invitingly. “That is a rare privilege, child. Lord Voldemort does not usually negotiate for what he wants.”

Some part of Harry’s mind scrabbled frantically, looking for something, anything that might be of more value to Lord Voldemort or Professor Quirrell than child hostages or Severus’s death.

Another part of him, the part that had never stopped thinking, already knew his answer.

“You already have an idea for what you want from me,” Harry said, through the sickness and the bleeding wounds in his soul. “What is it?”

“Your help in obtaining the Philosopher’s Stone.”

Harry swallowed. He couldn’t stop his eyes from going to the gun, then back up at Professor Quirrell’s face.

He was aware that the hero in a storybook was supposed to say ‘No’, but now that he was actually in a situation like this, saying ‘No’ didn’t seem to make sense.

“I am disappointed that you need to think about this,” said Professor Quirrell. “It is straightforward that you should obey me for now, since I hold every advantage over you. I have taught you better than this; in this situation you should certainly pretend to lose. You can expect to gain nothing by resisting, except pain. You should have calculated that it was better to answer sooner, and not earn my distrust.” Professor Quirrell’s eyes studied him curiously. “Perhaps Dumbledore has filled your ears with nonsense about noble defiance? I find such morals amusing, since they are so easy to manipulate. I assure you that I can make defiance seem morally worse, and you would be well advised to submit before I demonstrate how.” The gun stayed pointed at Harry; but with a wave of Professor Quirrell’s other hand, Tracey Davis rose up into the air, spun lazily, her limbs spread-eagled—

—then, even as new adrenaline hammered at Harry’s heart, Tracey floated back down again.

“Choose,” said Professor Quirrell. “This begins to try my patience.”

\emph{I should have spoken just then, before he might’ve ripped off Tracey’s legs, no, I shouldn’t have, the Headmaster said I mustn’t show Lord Voldemort that I’ll do things if he threatens my friends because that will just make him threaten more of them—only what he said before isn’t a \emph{threat} it’s just the sort of thing Lord Voldemort \emph{does}—}

Harry took a deep breath, several of them. Whatever part of him kept on running on full automatic was screaming at the remainder of his mind that it \emph{could not afford to stay in shock.} Shocks were of finite duration, neurons kept firing regardless, the only reason Harry’s mind would shut down while his brain kept running was if Harry’s self-model \emph{believed} his mind would shut down—

“I don’t mean to try your patience,” Harry said. His voice was cracking. That was good. Sounding like he was still in shock meant that Lord Voldemort might give him more time. “But if Lord Voldemort had a reputation for keeping his bargains, I don’t know about it.”

“An obvious concern,” Professor Quirrell said. “There is a simple answer, and I would have enforced it upon you in any case. \parsel{Snakes can’t lie}. And since I have a tremendous distaste for stupidity, I suggest you do not say anything like ‘What do you mean?’ You are smarter than that, and I do not have time for such conversations as ordinary people inflict on one another.”

Harry swallowed. Snakes can’t lie. “\parsel{Two plus two equals four.}” Harry had tried to say that two plus two equalled three, and the word \emph{four} had slipped out instead.

“Good. When Salazar Slytherin invoked the Parselmouth curse upon himself and all his children, his true plan was to ensure his descendants could trust one another’s words, whatever plots they wove against outsiders.” Professor Quirrell had adopted his lecturing pose from Battle Magic, like someone putting on a well-worn mask, but the gun remained pointed in his hand. “Occlumency cannot fool the Parselmouth curse as it can fool Veritaserum, and you may put that to the trial also. Now listen well. \parsel{Come with me, promise your best aid in getting Stone, and I shall leave these children behind unharmed. Hostages are real, hundreds of students die tonight unless I stop events already set in motion. Will spare hostages if I obtain Stone successfully.} And mark also this, mark it well: \parsel{I cannot be truly slain by any power known to me, and losing Stone will not stop me from returning, nor spare you or yours my wrath.} Any impetuous act you are contemplating cannot win the game for you, boy. I do credit your ability to annoy me, and suggest you avoid doing so.”

“You said,” Harry’s voice was strange in his own ears, “that the Philosopher’s Stone had different powers from what legend said. You said that to me in Parseltongue. Tell me what the Stone really does, before I agree to help you get it.” If it was something along the lines of gaining total power over the universe, then \emph{nothing} was worth an incrementally greater chance of Lord Voldemort getting the Stone.

“Ah,” said Professor Quirrell, and smiled. “You are thinking. That is better, and as a reward I shall offer you a further incentive for cooperation. Eternal life and youth, the creation of gold and silver. Suppose these are true benefits of holding the Stone. Tell me, boy. What is the Stone’s power?”

It might have been the adrenaline still in him, being actually useful for his brain for once. It might have been the power of being told that an answer existed, and that the evidence wasn’t a lie. “It can make Transfigurations permanent.”

Then Harry stopped, as he heard what his own mouth had just said.

“Correct,” said Professor Quirrell. “Thus, whoever holds the Philosopher’s Stone is able to perform human Transfiguration.”

Harry’s torn mind was knocked about yet again, as he realized what further incentive would be offered him.

“You stole Miss~Granger’s remains and Transfigured them into some innocuous-appearing target,” said Professor Quirrell. “A Transfigured target that you must keep somewhere about your own person, in order to sustain the Transfiguration. Ah, I see your eyes going to that ring upon your hand, but of course Miss~Granger would not be the little jewel set into the ring, would it? That would be too obvious. No, I expect you Transfigured Granger’s remains into the ring itself, letting the aura of the Transfigured jewel mask the magic in the Transfigured ring.”

“Yes,” Harry said, forcing out the word. It was a lie, for once, and Harry’s glance had been deliberate. Harry had expected someone to challenge him on the steel ring, he’d tried to provoke that challenge so he could prove to be innocent yet again, though nobody had taken him up on it—maybe Dumbledore had just sensed that the steel by itself wasn’t magical.

“Fine and good,” said Professor Quirrell. “Now come with me, help me to obtain the Stone, and I will resurrect Hermione Granger on your behalf. Her death has had unfortunate effects on you, and I would not mind undoing them. That, as I understand you, is your greatest desire. I have done you many kindnesses, and I would not mind doing you this one more.” A blank-eyed Professor Sprout had now risen from the ground and was pointing her own wand at Harry. “\parsel{Help me obtain Stone of Transfiguration, and I shall try my hardest to resurrect your girl-child friend to true and lasting life. That said, boy, I am swiftly running out of patience with you, and you shall not like what comes next.}” This last line was hissed out in a voice that conveyed the impression of a snake rearing its head to strike.

\later

Even then.

Even then, with all the world upturned, with shock after shock, even then Harry’s brain did not stop being a brain, or completing the patterns its circuits had been wired to complete.

Harry knew that this was too good an offer to make to someone at whom you were pointing a gun.

Unless you \emph{desperately} needed their help to get the Philosopher’s Stone out of the magic mirror.

And there wasn’t any time left to plan, only the thought that, if Professor Quirrell really was going this far to get his help—what Harry \emph{wanted} was to demand Professor Quirrell promise not to kill anyone in the future in exchange for his help now, but Harry had a strong sense that Professor Quirrell would reply ‘Don’t be ridiculous’ and there wasn’t time for ordinary conversation. Harry had to guess the highest safe request in advance—

Professor Quirrell’s eyes narrowed, his lips parted—

“If I help you,” Harry’s mouth said, “I want your promise that you aren’t planning to turn on me when this is over. I want you to not kill Professor Snape or anyone else in Hogwarts for at least a week. And I want answers, the truth about everything that’s been going on this whole time, everything you know about my nature.”

The pale blue eyes regarded him dispassionately.

\emph{I really think we could have thought of something better to ask for than that,} said Harry’s Slytherin side. \emph{But I suppose we were legitimately out of time, and whatever we need to do next, answers will help.}

Harry wasn’t listening to that voice right now. Cold chills were still going down his spine from hearing the words that had just come out of his lips, addressed to the man with the gun.

“That is your condition for helping me to obtain the Stone?” said Professor Quirrell.

Harry nodded, unable to form words.

“\parsel{Agreed,}” hissed Professor Quirrell. “\parsel{Help me, and you shall have answers to your questions, so long as they are about past events, and not my plans for the future. I do not intend to raise my hand or magic against you in future, so long as you do not raise your hand or magic against me. Shall kill none within school grounds for a week, unless I must. Now promise that you will not attempt to warn against me or escape. Promise to put forth your own best efforts toward helping me to obtain the Stone. And your girl-child friend shall be revived by me, to true life and health; nor shall me or mine ever seek to harm her.}” A twisted smile. “\parsel{Promise, boy, and the bargain will be struck.}”

“I promise,” whispered Harry.

\emph{\scream{What?}} screamed other parts of his mind.

\emph{Um, he’s still pointing a gun at us,} pointed out Slytherin. \emph{We don’t actually have a choice, we’re just getting as much mileage out of this as possible.}

\emph{You bastard,} said Hufflepuff. \emph{Do you think this is what Hermione would have wanted? This is Lord Voldemort we’re talking about, do we even know how many people he’s killed, and will kill?}

\emph{I deny that we are compromising with Lord Voldemort for Hermione’s sake,} said Slytherin. \emph{Since there is, in fact, a gun and we can’t otherwise stop him. Also, Mum and Dad would want us to just go along and stay safe.}

Professor Quirrell regarded him steadily. “Repeat the full promise in Parseltongue, boy.”

“\parsel{I shall help you obtain the Stone…I cannot promise I will use my best efforts, my heart will not be in it, I fear. I intend to try. Shall not do anything I think will annoy you to no good end. Shall call no help if I expect them to be killed by you or for hostages to die. I’m sorry, teacher, but it is best I can do.}” Harry’s mind was settling, composing itself, as the decision was made. He would stay with Professor Quirrell, go with him to get the Stone, save the student hostages, and…and…and Harry didn’t know, except that he’d go on thinking.

“You actually are sorry about that?” Professor Quirrell looked amused. “I suppose it shall have to do. Then keep two other things in mind: \parsel{I have plan to stop even schoolmaster, if he appears before us.} And also this: I will occasionally ask you to say in Parseltongue whether you have betrayed me. \parsel{The bargain is struck.}”

\later

After that, Professor Sprout picked up Harry’s wand, and wrapped it in shimmering cloth; then she placed it on the floor, and again pointed her wand at Harry. Only then did Professor Quirrell lower his gun, which seemed to disappear into his hand, and pick up Harry’s wrapped wand, tucking it into his robes.

The True Cloak of Invisibility was removed from the sleeping form of Lesath Lestrange, and Professor Quirrell took the Cloak, as well as Harry’s pouch and Time-Turner.

Then Professor Quirrell cast a mass Obliviation followed by the mass version of the False Memory Charm, the one that just had the subject fill in the blanks using their own suggestibility, on all the students present. Afterwards Professor Sprout floated away the sleeping children, now wearing an expression that seemed annoyed and preoccupied, as if they’d been in some Herbology accident.

Professor Quirrell then turned back to where the Potions Master lay sprawled, bent over and placed his wand on Professor Snape’s forehead. “\emph{Alienis nervus mobile lignum.}”

The Defence Professor stepped back, and began to move his left fingers in the air as though manipulating a puppet on strings.

Professor Snape pushed himself up from the ground by smooth motions, and stood once more before the corridor door.

“\emph{Alohomora,}” Professor Quirrell said, pointing his wand at the forbidden door. The Defence Professor looked rather amused. “Would you do the honours, boy?”

Harry swallowed. He was once again having second thoughts, and third thoughts.

It was strange how you could do something even while knowing it was the wrong thing, not the selfish thing but the \emph{wrong thing to do} on some deeper level.

But the man behind him was holding the gun; it had once more appeared in his hand at Harry’s hesitation.

Harry laid his hand on the door-knocker, and took several deep breaths, again composing his mind as best he could. Go through with it, don’t get shot, don’t let the hostages die, be there to optimize events, be there to watch for opportunities and stay capable of taking them. It wasn’t a good choice, but all the other ones seemed worse.

Harry pushed open the forbidden door, and stepped through.

%  LocalWords:  om Alienis nervus
