\partchapter{Taboo Tradeoffs}{I}

\lettrine{T}{he} words dropped into Harry’s consciousness and shattered his thoughts into a hundred shards of incredulity, the shock of adrenaline running into so much confusion that—

“She—” Harry said. “She—she wouldn’t—WHAT?”

The Aurors weren’t paying any attention to him. Komodo spoke again, still in that colorless voice. “Mr.~Malfoy has regained consciousness in St.~Mungo’s and named you, Hermione Granger, as his assaulter. He has repeated these accusations under two drops of Veritaserum. The \replacement{Blood-Cooling}{Blood-Chilling} Charm you cast upon Mr.~Malfoy would have killed him if he had not been found and treated, and it must be presumed known to you that this was a fatal curse. I therefore arrest you upon the serious charge of attempted murder and you will be taken into Ministry custody to be interrogated under three drops of Veritaserum—”

“\emph{Are you mad?}” the words burst out of Harry’s mouth, as he shoved himself up from the Ravenclaw table, an instant before Auror Butnaru’s hand clamped down hard upon his shoulder. Harry ignored it. “That’s \emph{Hermione Granger} you’re trying to arrest, the nicest girl in Ravenclaw, she helps Hufflepuffs with their homework, she’d \emph{die} before she tried to kill \emph{anyone—}”

Hermione Granger’s face had crumpled. “I did it,” she whispered in a tiny voice. “It was me.”

Another huge rock fell on Harry’s thoughts and crushed their fragile order, bursting fragments of comprehension into dust.

Dumbledore’s face seemed to have aged decades over the course of seconds. “Why, Miss Granger?” Dumbledore said, his own voice barely above a whisper. “Why would you do such a thing?”

“I’m,” Hermione said, “I’m, I’m—sorry—I don’t know why I—” She seemed to collapse in on herself, her voice was formed of nothing but sobs, and the only words that could be made out were, “I thought—killed him—sorry—”

And Harry should have said something, should have done something, should have jumped up out of his seat and stunned all three Aurors and then gone on to some incredibly clever next move, but the twice-shattered fragments of his thought processes could yield no output. Butnaru’s hand pushed Harry gently but firmly back into his seat and Harry found himself \emph{stuck} there like he’d been glued, he tried to grab his wand for a \emph{Finite} and it wouldn’t come out of his pocket, the three Aurors and Dumbledore escorted Hermione out of the Great Hall amid a rising storm of outcries and the doors began to swing shut behind them—nothing made sense, it was surreal beyond all reckoning, like he’d been transported into an alternate universe, and then Harry’s mind flashed back to another day of confusion and in a moment of desperate inspiration he finally realized what the Weasley twins had done to Rita Skeeter, and his voice rose in a scream, \scream{“Hermione you didn’t do it you’ve been False-Memory-Charmed!”}

But the doors had already shut.
\sbreak
Minerva couldn’t possibly have stood still, she paced back and forth through the Headmaster’s office, the back of her mind half-expecting Severus or Harry to tell her to shut up and sit down, but neither the Potions Master or the Boy-Who-Lived seemed much concerned with her, both of their gazes focused on Albus Dumbledore where he had emerged from the Floo. There were sounds in the background that nobody heard. Severus seemed as passionless as ever, sitting in a small cushioned chair beside the Headmaster’s desk. The old wizard stood terrible and upright by the still-burning fireplace, robed in black like a starless night, radiating power and dismay. All her own thoughts were of utter confusion and horror. Harry Potter sat on a wooden stool with his fingers gripping the seat, and his eyes were fury and freezing ice.

At 6:33\AM, Quirinus Quirrell had Flooed St.~Mungo’s from his office for immediate pickup of Draco Malfoy. Professor Quirrell had found Mr.~Malfoy in the trophy room of Hogwarts, on the verge of death from the continuing effects of the Blood-Chilling Charm slowly lowering his body temperature. Professor Quirrell had immediately dispelled the Charm, cast stabilizing spells on Mr.~Malfoy, and levitated him to his office to Floo him to St.~Mungo’s for further treatment. After this, Professor Quirrell had informed the Headmaster, stating the facts briefly before vanishing through the Floo; the Aurors, notified by St.~Mungo’s, had demanded his presence for questioning.

The clear intent of the Blood-Chilling Charm had been to kill Draco Malfoy so slowly that the wards of Hogwarts, set to detect sudden injury, would not trigger. Under interrogation, Professor Quirrell had told the Aurors that he had cast several tracking Charms upon Mr.~Malfoy’s person in January, shortly after Mr.~Malfoy’s return to Hogwarts from Yuletime break. Professor Quirrell had cast tracking Charms because he had learned of a person with a motive to harm Mr.~Malfoy. Professor Quirrell had refused to identify this person. The tracking Charms which Professor Quirrell had cast were triggered by Mr.~Malfoy’s health falling below an absolute level, rather than by sudden changes, and had therefore alerted Professor Quirrell before Mr.~Malfoy had died.

Two drops of Veritaserum, sufficient to prevent Mr.~Malfoy from withholding any meliorating or moderating information in his statements, had shown that Mr.~Malfoy had—legally under the laws of Noble Houses, illegally under the regulations of Hogwarts—challenged Hermione Granger to a duel. Mr.~Malfoy had won the duel but had then, as he left, been attacked from behind by Miss Granger with a Stunning Hex. After this Mr.~Malfoy knew nothing.

Three drops of Veritaserum, requiring her to volunteer all relevant information, had caused Hermione Granger to confess that she had stunned Draco Malfoy from behind, and then, in a fit of anger, cast the Blood-Chilling Charm on him, with the deliberate intention of killing him slowly enough to evade identification from the Hogwarts wards, whose workings she had read about in \emph{Hogwarts: A History}. She had been horrified at herself upon awakening the next morning, but had not told anyone of what she’d done, believing Draco Malfoy to be already dead—as he certainly would have been after seven hours, had his body’s own magic not been resisting the effects of the Blood-Chilling Charm.

“Her trial,” said Albus Dumbledore, “is set for tomorrow at noon.”

“\emph{What?}” the word burst out of Harry Potter. The Boy-Who-Lived didn’t rise from his chair, but Minerva saw his fingers whiten where they gripped the wooden seat beneath him. “That’s insane! You can’t do a police investigation in one day—”

The Potions Master raised his voice. “This is not \emph{Muggle} Britain, Mr.~Potter!” Severus’s face was as expressionless as ever, but the bite in his voice was sharp. “The Aurors have an accusation under Veritaserum and a confession under Veritaserum. So far as they are concerned, the investigation is \emph{done}.”

“Not quite,” said Dumbledore, just as Harry seemed ready to explode. “I have insisted to Amelia that this matter be given the utmost scrutiny. Unfortunately, as the ill-fated duel was at midnight—”

“\emph{Supposed} duel,” Harry said sharply.

“As the \emph{supposed} duel was at midnight—yes, you’re quite right, Harry—it is beyond the range of any Time-Turner—”

“Also \emph{supposedly},” the Boy-Who-Lived said coldly. “And rather \emph{suspiciously}, since the alleged murder suspect doesn’t know about Time-Turners. I hope that an invisible Auror was immediately sent back in time as far as possible to observe—”

Dumbledore inclined his head. “I went \emph{myself,} Harry, the moment I heard. But by the time I reached the trophy room, Mr.~Malfoy was already unconscious and Miss Granger had gone—”

“No,” said Harry Potter. “You reached the trophy room and saw Draco unconscious. That is all you observed, Headmaster. You did not \emph{observe} Hermione there, or watch her leave. Let us distinguish observation from inference.” The boy’s head turned to look at her. “Imperius, Obliviation, False Memory Charm, Legilimency. Professor McGonagall, am I leaving out any mind-affecting spell that could have made Hermione do this or make her believe she’d done it?”

“The Confundus Charm,” she said. And the Dark Arts had never been her study, but she knew—“And certain Dark rituals. But none of those could be performed in Hogwarts without alarm.”

The boy nodded, his eyes still directly addressing her. “Which of those spells can be detected? Which would the Aurors try to detect?”

“The Confundus Charm would wear off in a few hours,” she said, after a moment to gather her thoughts. “Miss Granger would remember the Imperius. Obliviation cannot be detected by any known means, but only a Professor could have cast that spell upon a student without alarm from the Hogwarts wards. Legilimency—can only be detected by another Legilimens, I think—”

“I requested that Miss Granger be examined by the court Legilimens,” said Dumbledore. “The examination showed—”

“Do we trust him?” said Harry.

“Her,” said Dumbledore. “Sophie McJorgenson, whom I remember as an honest student of Ravenclaw, and she is bound by the Unbreakable Vow to tell the truth of what she sees—”

“Could someone else be Polyjuiced as her?” Harry Potter interrupted again. “What did you \emph{observe,} Headmaster?”

Albus said heavily, “A person who looked like Madam McJorgenson told us that a single Legilimens had lightly touched Miss Granger’s mind some months ago. That is from January, Harry, when I communicated with Miss Granger about the matter of a certain Dementor. That was expected; but what I did not expect was the rest of what Sophie found.” The old wizard turned to gaze into the Floo fire, letting the orange flames reflect on his face. “As you say, Harry, a False Memory Charm is one possibility; they are, when cast perfectly, indistinguishable from true memory—”

“That doesn’t surprise me,” Harry interrupted. “Studies show that human memories are more or less rewritten every time we remember them—”

“Harry,” Minerva said softly, and the boy’s mouth clamped shut.

The old wizard continued. “—but a False Memory Charm of such quality requires as much time to create as a true memory. Creating a detailed memory of ten minutes would be ten minutes’ work. And according to the court Legilimens,” Albus’s face now seemed more tired and lined than before, “Miss Granger has been obsessing over Mr.~Malfoy since the day that Severus...\ yelled at her. She has been thinking of how Mr.~Malfoy might be in league with Professor Snape, how he might be planning to harm her and harm Harry—imagining it for hours every day—it would be impossible to create false memories for so much time.”

“The appearance of insanity...” Severus murmured softly, as though he were speaking to himself. “\emph{Could} it be natural? No, it is too disastrous to be pure accident; too convenient for \emph{someone,} I have no doubt. A Muggle drug, perhaps? But that would not be enough—Miss Granger’s madness would have to be \emph{guided}—”

“Ah!” Harry said suddenly. “I get it now. The \emph{first} False Memory Charm was cast on Hermione after Professor Snape yelled at her, and showed, say, Draco and Professor Snape plotting to kill her. Then last night that False Memory was \emph{removed} by Obliviation, leaving behind the memories of her obsessing about Draco for no apparent reason, at the same time she and Draco were given false memories of the duel.”

Minerva blinked in startlement. It would have been a thousand years before she thought of that possibility.

The Potions Master was frowning thoughtfully, eyes intent. “The \emph{reaction} to a False Memory Charm is hard to predict in advance, Mr.~Potter, without Legilimency. The subjects do not always act as expected, when they first remember the false memories. It would have been a risky ploy. But I suppose that is one way Professor Quirrell could have done it.”

“\emph{Professor Quirrell?}” said Harry. “What motive does \emph{he} have to—”

The Potions Master said dryly, “The Defense Professor is always a suspect, Mr.~Potter. You will notice a trend, given time.”

Albus raised up a hand, a silencing gesture, and their heads all turned to look at him. “But in this case there is another suspect,” Albus said quietly. “Voldemort.”

That deadliest of unspeakable words seemed to echo around the room, canceling all the heat from the orange flames of the fireplace.

“I do not know,” the old wizard said slowly, “I know all too little, of the methods of Voldemort’s immortality. He searched out those books before I did, I think. All I could find were ancient tales, scattered across too many volumes for him to remove. But to find truth among many stories is also a wizard’s mastery, and this I have endeavored to do. There is a human sacrifice, a murder, of that I am certain; committed in coldest blood, the victim dying in horror. And old, old tales of wizards possessed, doing mad deeds, claiming the names of Dark Lords thought defeated; and there is usually a device, of that Dark Lord, which they wield...” Albus looked at Harry, the ancient eyes searching the younger. “I think, Harry—though you will call it only inference—that the act of murder splits the soul. That by ritual of blackest horror, the torn fragment of soul is chained to this world. To a material thing of this world. Which must be, or which then becomes, a device of power.”

\emph{Horcrux.} The terrible name echoed in Minerva’s mind, though it seemed that—for what reason she did not know—Albus would not speak that word in front of Harry.

“And therefore,” the old wizard finished quietly, “the remainder of the soul is bound to its chained part, lingering here when its body is destroyed. A sad and painful existence, I think it would be; less than spirit, less than the meanest ghost...” The old wizard’s eyes were locked on Harry, who gazed back with his eyes narrowed. “It would take time for that mutilated soul to regain a mockery of life. That is why we have had our ten-year reprieve, I believe; why Voldemort did not return at once. But in time...\ that revenant would become capable of rising again.” The old wizard spoke with grim precision. “It is clear, from the stories, that the Dark Lords who return by possessing another’s form, wield lesser magics than they once knew. I do not think Voldemort would be satisfied with that. He would take some other avenue to life. But Voldemort was more Slytherin than Salazar, grasping at every opportunity. He would \emph{use} his pitiful state, \emph{use} his power of possession, if he had reason. If he could benefit by another’s...\ inexplicable fury.” Albus’s voice had fallen to almost a whisper. “That is what I suspect happened to Miss Granger.”

Minerva’s throat was very dry. “He’s \emph{here,}” she gasped. “\emph{Here,} in \emph{Hogwarts}—”

Then she stopped, because the \emph{reason} Voldemort had come to Hogwarts—

The old wizard glanced at her only briefly, and said, still in that whisper, “I am sorry, Minerva, you were right.”

Harry’s voice was edged. “Right about what?”

“Voldemort’s strongest avenue to life,” Dumbledore said heavily. “The most desirable road for him, by which he would rise greater and more terrible than ever before. It is guarded here, within this castle—”

“Excuse me,” Harry said politely. “Are you stupid?”

“Harry,” she said, but there was no force in her voice.

“I mean, maybe you haven’t noticed this, Headmaster Dumbledore, but this castle is full of \emph{\shout{children—}}”

“\emph{I had no choice!}” bellowed Dumbledore. The blue eyes were blazing now, beneath the half-moon spectacles. “I do not \emph{own} it, that thing which Voldemort desires. It belongs to another, and is held here by \emph{his} consent! I \emph{asked} if it could be kept in the Department of Mysteries. But \emph{he} would not permit that—he said it must be within the wards of Hogwarts, in the place of the Founders’ protection—” Dumbledore passed his hand across his forehead. “No,” the old wizard said in a quieter voice. “I cannot pass this blame to him. He is right. There is too much power in that thing, too much that men desire. I agreed that the trap should be laid behind the wards of Hogwarts, in the place of my own power.” The old wizard bowed his head. “I knew Voldemort would worm his way here somehow, and planned to trap him. I did not think—I did not dream—that he would tarry in an enemy fortress one minute longer than he must.”

“But,” said Severus in some puzzlement, “what would the Dark Lord possibly gain by killing Lucius’s only heir?”

“Point of order,” Harry Potter said, a hard edge in his voice. “The motives of whoever’s behind this are not the primary issue. Our top priority at this point is that an innocent Hogwarts student is in \emph{trouble!}”

The green eyes locked with the blue, as Albus Dumbledore gazed back at the Boy-Who-Lived—

“Quite right, Mr.~Potter,” Minerva said, she hadn’t even thought about it, the words just seemed to pop out of her lips. “Albus, who is watching over Miss Granger now?”

“Professor Flitwick has gone to her,” the Headmaster said.

“She needs a \emph{lawyer,}” Harry said. “Anyone who just blurts out ‘I did it’ to the police—”

“Unfortunately,” Minerva said, her tone taking on some of Professor McGonagall’s sternness without thinking, “I doubt a lawyer will be any use to Miss Granger at this point, Mr.~Potter. She is to face the judgment of the Wizengamot, and they would be exceedingly unlikely to free her on a technicality.”

Harry was looking at her with an utterly incredulous expression, as though suggesting that Hermione Granger didn’t need a lawyer was akin to suggesting that she be set on fire.

“She is correct, Mr.~Potter,” Severus said quietly. “Few court processes in this country involve lawyers.”

Harry lifted his glasses and rubbed his eyes, briefly. “Fine. How do we get Hermione off the hook, exactly? I suppose it’s too much to hope that with all the lawyers gone, the judges understand the concept of ‘common sense’ and ‘prior probability’ well enough to realize that twelve-year-old girls basically never commit cold-blooded murders?”

“It is the Wizengamot that she faces,” said Severus. “The oldest Noble Houses, and certain other wizards of influence.” Severus’s face twisted in something approaching his customary sarcasm. “As for them showing common sense—you might as well expect them to make you a bacon sandwich, Potter.”

Harry nodded, his mouth set. “Exactly what sort of penalty is Hermione facing? Snapped wand and expulsion—”

“No,” Severus said. “Nothing that light. Are you willfully misunderstanding, Potter? She is facing the \emph{Wizengamot}. There is no set penalty. There is only the vote.”

Harry Potter murmured, “\emph{The rule of law, in complex times, has proved itself deficient; we much prefer the rule of men, it’s vastly more efficient...} There’s no constraining legal rules at all, then?”

Light glinted off the old wizard’s half-moon glasses; he spoke carefully, and not without anger. “Legally, Harry, we are dealing with a blood debt from Hermione Granger to the House of Malfoy. The Lord of Malfoy proposes a repayment of that debt, and then the Wizengamot votes on his proposal. That is all.”

“But...” Harry said slowly. “Lucius was Sorted into Slytherin, he’s \emph{got} to realize that Hermione was just a pawn. Not the one he should actually be angry at. Right?”

“No, Harry Potter,” Albus Dumbledore said heavily. “That is how you \emph{wish} Lucius Malfoy would think. Lucius Malfoy himself...\ will not share your desire that he think that way.”

Harry gazed at the Headmaster, his eyes growing colder, at the same time that Minerva herself had to clamp down harder on her own emotions, stop her pacing and try to breathe. She’d been trying not to think about it, trying to turn her thoughts away from it, but she knew. She’d known since the instant she’d heard. She could see it in Albus’s eyes—

“Is she facing capital punishment?” Harry said quietly, and chills went all the way down Minerva’s spine at the undertones of that voice.

“No!” Albus said. “No, not the Kiss, not Azkaban, not for a first-year in Hogwarts. Our country is not so lost, not yet.”

“But Lucius Malfoy,” Severus said tonelessly, “certainly will not be satisfied with only snapping her wand.”

“All right,” Harry said commandingly. “As I see it, we’ve got two essential lines of attack. Line one, find the real culprit. Line two, other leverage over Lucius. Professor Quirrell saved Draco’s life, does that create a blood debt from House Malfoy to him that he could redeem to cancel Hermione’s?”

Minerva blinked in startlement again.

“No,” Dumbledore said. The old wizard shook his head. “It was a clever thought—but no, Harry, I’m afraid not. Even in the unlikely event that our Defense Professor reveals himself to be of a Noble House, there is an exception when the Wizengamot suspects that the life-debt may have been created deliberately, for that very purpose. And the Defense Professor is hardly above suspicion. Thus Lucius would argue.”

Harry nodded once, face set. “So a commoner can have a blood debt to a Noble House, but not vice versa. Somehow I’m not surprised. But House Potter \emph{does} count as a Noble House, from what I’ve heard. Headmaster, I know I said I wouldn’t—but under the circumstances—that time Draco cast that torture hex on me, is that debt enough—”

“No,” the old wizard said (even as she blurted “\emph{What?}” and Severus lifted an eyebrow). “It would not have been enough, and now it is no debt at all. You are an Occlumens and cannot testify under Veritaserum. Draco Malfoy could be Obliviated of his own memory before he could testify—” Albus hesitated. “Harry...\ whatever you have done with Draco, you must assume that Lucius Malfoy will soon know of it.”

Harry’s head sank into his hands. “He’ll give Draco Veritaserum.”

“Yes,” Albus said quietly.

The Boy-Who-Lived didn’t say anything, as he sat with his head in his hands.

The Potions Master looked genuinely shocked. “Draco really \emph{was} trying to help Miss Granger,” Severus said. “You—Potter, you \emph{actually—}”

“Turned him?” Harry said from between his hands. “I was about three-quarters done. Taught him the Patronus Charm and everything. I don’t know what will happen now, though.”

“Voldemort has struck a grave blow against us, this day,” Albus said. The sound of old wizard’s voice was like the look of the boy with his head in his hands. “He has taken two of our pieces, with one... No. I should have seen it earlier. He has taken two of \emph{Harry’s} pieces with one move. Voldemort has begun his game again, not against myself, but against \emph{Harry}. Voldemort knows the prophecy, he knows who his last foe shall be. He is not waiting to face Hermione Granger and Draco Malfoy at Harry’s side when they are grown. He is striking at them \emph{now}.”

“Maybe it’s You-Know-Who and maybe it isn’t,” Harry said, his voice sounding a little unsteady. “Let’s not narrow down the hypothesis space prematurely.” Harry took a breath and lowered his hands. “The other thing we can try is to nail the real culprit before the trial—or at least find solid evidence that \emph{someone} else did it.”

“Mr.~Potter,” said Minerva, “Professor Quirrell told the Aurors that he knew of someone with a motive to harm Mr.~Malfoy. Do \emph{you} know who he was talking about?”

“Yes,” Harry said, after a hesitation. “But I think I shall conduct that part of my investigation with the Defense Professor—just as I would not have Professor Quirrell in the room while we were discussing how to investigate \emph{him.}”

“He suspects me?” Severus said, then gave a short laugh. “Why, of course he does.”

“My own plan,” said Harry, “is to go look at the trophy room where the supposed duel took place and see if I can discover anything anomalous. If you can tell the investigating Aurors to let me through—”

“What investigating Aurors?” Severus said tonelessly.

Harry Potter took a deep breath, slowly let it out, and then spoke again. “In mystery books it usually takes longer than one day to solve a crime, but twenty-six hours is—no, \emph{thirty} hours is eighteen hundred minutes. And I can think of at least one other important place to look for clues—though it’ll have to be someone who can get into the Ravenclaw girls’ dorm. Back when Hermione was fighting bullies, she was finding notes under her pillow each morning, telling her where to go—”

“\emph{Albus...}” ground out Minerva.

“I did not send them,” said the old wizard. His white eyebrows had lifted in surprise. “I knew nothing of this. You think she was being played, Harry?”

“It’s a possibility,” Harry said. “More so, because there’s a part of this puzzle that you don’t know about yet.” Harry’s voice lowered, grew more intense. “Headmaster, you already know that I got my father’s invisibility cloak from someone who left a note under my pillow signed ‘Santa Claus’. I think we have to assume that’s the same person who left notes for Hermione—”

“Harry,” the old wizard said, and hesitated momentarily. “Returning your father’s cloak to you, does not seem to me like the act of a villain—”

“\emph{Listen},” Harry Potter said urgently. “The part you \emph{don’t} know is that after Bellatrix Black escaped from Azkaban, I found another note under my pillow, also signed ‘Santa Claus’, saying that they’d heard you were shutting me up inside Hogwarts, and that they were giving me an escape route to the Salem Witches’ Institute in America. That note came with a deck of cards, in which the King of Hearts was supposedly a portkey—”

“\emph{Mr.~Potter!}” cried Professor McGonagall, she hadn’t even thought before she spoke. “That could well be a \emph{kidnapping attempt!} You should have told—”

“\emph{Yes}, Professor, I did the sensible thing,” the boy said levelly. “As \emph{adapted to the circumstances}, I did the sensible thing. I told Professor Quirrell. And according to Professor Quirrell, that portkey goes to somewhere in London—it’s definitely not strong enough to be an international portkey. Now it’s \emph{possible} that the person who sent the note is honest, and that the point in London is just a way station.” The boy reached into his robes and took out a deck of cards, along with a folded paper note. “I will trust you \emph{not} to go in guns blazing—I mean wands blazing—just in case the sender is an ally of mine, if not yours. But if this is a trap, I say we spring it \emph{now}. And whoever it is, take them \emph{alive} so we can exhibit them before the Wizengamot, I cannot overemphasize that part.”

Severus rose from his chair, his eyes now intent, and moved toward Harry. “I’ll need a hair of yours for Polyjuice, Mr.~Potter—”

“Let us not be hasty!” said Albus. “We have not yet examined the notes sent to Miss Granger; there may be no resemblance after all. Severus, would you enter her dorm room and see if you can find those?”

Harry’s eyebrows had raised, even as he stood to offer the Potions Master better access to his mess of hair. “You think two \emph{different} people are running around Hogwarts leaving notes beneath pillows?”

Severus gave a brief sardonic laugh, as his hand moved forward and plucked a hair, which soon was being carefully wrapped in silk. “Quite possibly. If I have learned anything in my tenure as Head of Slytherin, I have learned what ridiculous messes arise when there is more than one plotter and more than one plan. But Headmaster—I think Mr.~Potter is correct that I should follow this portkey and see where it leads.”

Albus hesitated, and then nodded reluctantly. “I will speak to you before you go, then.”
\sbreak
Even as Harry Potter left the room for his own investigations, Severus had spun on his heel and was striding swiftly toward the jar of Floo powder, his cloak rising behind him with his speed. “I’ll get some raw Polyjuice, add the hair, and go. Headmaster, will you stand by to—”

“Albus,” Minerva said, surprised at how steady her own voice was, “did you leave those notes under Mr.~Potter’s pillow?”

Severus’s hand halted an instant before casting Floo powder into the fire.

Dumbledore nodded to her, though the accompanying smile seemed a bit hollow. “You know me far too well, my dear.”

“And I suppose the portkey goes to a friendly home where Mr.~Potter would be kept safe and sound until you arrived to pick him up and return him to Hogwarts?” Her voice tight—it was sensible, she could not deny it was sensible, but somehow it seemed a little cruel.

“It would have depended on the circumstances,” the old wizard said quietly. “If Harry had gone so far—I might have let him make good his escape, for a time. Better to know where he was going, and ensure it was somewhere safe, with friends—”

“And to think,” said Professor McGonagall, “that I had thought to reprimand Mr.~Potter for not telling us about this important matter! Upbraid him for not having the sense to trust us!” Her voice had risen in volume. “I shall skip that lecture, I suppose!”

Severus was gazing at the Headmaster with narrowed eyes. “And the notes to Miss Granger—”

“The Defense Professor, very likely,” the old wizard said. “Still—that is only a guess.”

“I shall go look for them,” Severus said. “And then, I suppose, start looking for You-Know-Who.” A frown crossed the Potions Master’s face. “A task at which I haven’t the faintest idea of where to start. Do you know of any magics to find a soul, Headmaster?”
\sbreak
The Divination classroom was lit by the dim red light of a hundred small fires where burned a hundred kinds of incense, so that if you were to ask in one word what the room looked like, the answer would be ‘smoke’. (Assuming you bothered to look at anything, when your nose was threatening to overload and die.) If your gaze could pierce those dank mists, you would see a tiny, cluttered room in which forty stuffed armchairs, most of them unused, were crammed around a small open space in the center of the room, where a circular trapdoor waited on your escape.

“The grim!” Professor Trelawney said in a quavering voice, as she peered into George Weasley’s teacup. “The grim! It is a sign of death! One whom you know, George—someone you know is to die! And soon—yes, it shall be quite soon, I think—unless of course it is later—”

It would have been a good deal scarier, thought Fred and George, if she hadn’t said the same thing to every single other student in their Divination class. They were hardly even thinking about it at this point; all their thoughts were on today’s disaster—

The trapdoor in the floor flew open with a bang that caused Professor Trelawney to shriek and spill George’s tea all over his robes, and then an instant later Dumbledore was whooshing up out of the floor with a bird of fire upon his shoulder.

“Fred!” the old wizard said commandingly. His robes were the black of a moonless night, his eyes hard like blue diamonds. “George! With me, now!”

There was an collective gasp and by the time Fred and George were climbing down the ladder after the Headmaster, the entire class was already speculating what role they’d played in the attempted murder of Draco Malfoy.

The trapdoor had hardly slammed shut above them before all nearby sounds muted and the old wizard spun on them and held out a hand and commanded, “Give me the map!”

“M-map?” said Fred or George in total shock. They’d never even suspected that Dumbledore suspected. “Why, w-we don’t know what you’re—”

“Hermione Granger is in trouble,” said the old wizard.

“The Map is in our dorm,” George or Fred said immediately. “Just give us a few minutes to get it and we’ll—”

The wizard’s arms swept them up as if they were hugging-pillows, there was a piercing cry and a flash of fire and then the three of them were in the third-year Gryffindor’s boys’ dorm.

A few moments later, Fred and George were handing over the Map to the Headmaster, wincing only slightly at the sacrilege of giving their precious piece of the Hogwarts security system to the person who actually owned it, and the old wizard was frowning at the apparent blankness.

“You’ve got to say,” they explained, “\emph{I solemnly swear that I am up to no good—}”

“I decline to lie,” said the old wizard. He held the Map high and bellowed, “Hear me, Hogwarts! \emph{Deligitor prodi!}” An instant later the Headmaster was wearing the Sorting Hat, which looked \emph{scarily right} upon his head, as though Dumbledore had always been waiting for a patchwork pointed hat to complete his existence.

(Fred and George immediately memorized this phrase, just in case it would work for somebody besides the Headmaster, and began trying to think of pranks that would involve the Sorting Hat.)

The old wizard wasted not a moment before sweeping the Sorting Hat off his head and turning it upside-down—it was hard to tell with the Hat upside-down, but it looked a bit cross at the treatment—and then plunged in his hand and drew out a crystal rod. With this instrument he began tracing rune-like patterns on the Map, muttering strange incantations that sounded not quite like Latin and echoed in their ears in an unusually creepy fashion. In the midst of tracing one rune he looked up at both of them, fixing them with a sharp glare. “I will return this to you later, sons of Weasley. Go back to class.”

“Yes, Headmaster,” they said, and hesitated. “Ah—about Hermione Granger, is she really going to be bound to serve Draco Malfoy forever as his—”

“\emph{Go,}” said the old wizard.

They went.

When he was alone in the room, the old wizard looked down at the map, which had now written upon itself a fine line drawing of the Gryffindor dorms in which they stood, the small handwritten \emph{Albus P.W.B. Dumbledore} the only name left therein.

The old wizard smoothed the map, bent over it, and whispered, “Find Tom Riddle.”
\sbreak
The interrogation room at the Department of Magical Law Enforcement was usually lit by a small orange light, so that the Auror interrogating you would be leaning toward your uncomfortable metal chair with most of their face in shadow, preventing you from reading their expression, even as they read yours.

As soon as Mr.~Quirrell had entered the room, the small orange light had dimmed and begun flickering like a candle about to be blown out by the wind. The room was now lit by a sourceless ice-colored glow which illuminated all of \replacement{the }{}Mr.~Quirrell’s pale skin like alabaster, except, somehow, his eyes, which stayed in darkness.

The Auror on duty outside had surreptitiously tried to dispel this effect four times without the slightest success, despite the fact that Mr.~Quirrell had politely surrendered his wand upon being detained for interrogation, and had shown no sign of speaking any incantations nor exerting any other power.

“Quirinus... Quirrell,” drawled the man now sitting across from where the Defense Professor had waited courteously. The interrogator had tawny hair that swept back like a lion’s mane, with yellowish eyes set into the sternly lined face of a man late in his tenth decade. The man was, at this moment, leafing through a large folder of parchments that he had taken from a black and very solid-looking briefcase after he had limped into the room and sat down, seeming not to look at the face of the man he was interrogating. He had not introduced himself.

After some further leafing through parchments, carried out in silence, the Auror spoke again. “Born the 26\Th of September, 1955, to Quondia Quirrell, of an acknowledged tryst with Lirinus Lumblung...” intoned the Auror. “Sorted into Ravenclaw... O.W.L.S. quite good... N.E.W.T.S. in Charms, Transfiguration...\ an Outstanding in Muggle Studies, impressive... Ancient Runes, and ah yes, Defense. An Outstanding in that as well. Went on to become quite the tourist, visiting all sorts of places. Portkey visas for Transylvania, the Forbidden Empire, the City of Endless Night...\ my my, \emph{Texas}.” The man looked up from the portfolio, eyes narrowed. “What were you doing \emph{there}, Mr.~Quirrell?”

“Sightseeing, mostly in the Muggle areas,” the Defense Professor said easily. “As you say, I am quite the tourist.”

The man listened to this with a frown, then looked back down, then up again. “I also see that you visited Fuyuki City in 1983.”

The Defense Professor lifted an eyebrow in mild puzzlement. “What of it?”

“What did you do in Fuyuki City?” The question snapped out razor-sharp.

The Defense Professor frowned slightly. “Nothing of any account. I visited some better-known sights, some less-known sights, and aside from that, kept to myself.”

“Really?” the Auror said softly. “I find that reply rather interesting.”

“How so?” said the Defense Professor.

“Because there was no visa listed for Fuyuki City.” The man slammed the folder shut. “You’re not Quirinus Quirrell. Who the \emph{hell} are you?”
\sbreak
The Potions Master walked quietly into the Ravenclaw girls’ dorm, the first-year dorm room, a festive place where bronze and blue competed to be the color of stuffed animals, scarves and dresses, small bits of inexpensive jewelry, and posters of famous people. Hermione Granger’s bed was easy to identify; it was the one that had been attacked by a book monster.

Nobody else seemed to be around, at that time of day, and a number of spells verified this.

The Potions Master searched under Hermione Granger’s pillow, and beneath her bed, and then began going through her trunk, sorting through mentionable and unmentionable items without change of expression, and finally succeeded in drawing forth a set of papers describing places and times where bullies would be found, all of the papers signed only with an elaborate ‘S’.

A brief burst of fire later, the papers were gone, and the Potions Master left to report the failure of his mission.
\sbreak
The Defense Professor was sitting calmly with his hands still folded in his lap. “If you consult Headmaster Dumbledore,” said the Defense Professor, “you will find that he is well aware of this matter, and that I agreed to teach his Defense class on the explicit condition that no inquiry be made into my—”

In a lightning motion, the interrogator whipped out his wand and spat “\emph{Polyfluis Reverso!}” at the same time that the Defense Professor sneezed, which somehow caused the mirror-silvered ray to disrupt in a shower of white sparks.

“Pardon me,” the Defense Professor said politely.

The smile that the Auror gave had absolutely no mirth in it. “So where’s the real Quirinus Quirrell, eh? Under an Imperius in the bottom of a trunk somewhere, while you take a hair now and then for your illegal Polyjuice?”

“You are making highly questionable assumptions,” the Defense Professor said with an edged voice. “What makes you think I did not steal his body outright using incredibly Dark magic?”

This was followed by a certain pause.

“I suggest,” the Auror said, “that you take this seriously, Mr.~Whoever-You-Are.”

“I’m sorry,” said the Defense Professor, leaning back in his chair, “but I see little reason to humble myself on this particular occasion. What are you going to do, kill me?”

“I don’t appreciate your humor,” the Auror said softly.

“How unfortunate for you, Rufus Scrimgeour,” said the Defense Professor. “You have my deepest sympathy.” He tilted his head, seeming to study the interrogator; and even within the shadow of the ice-light, the eyes glinted.
\sbreak
Padma stared down at her plate.

“Hermione wouldn’t just \emph{do} that!” yelled Mandy Brocklehurst, who was practically in tears, in fact she \emph{was} in tears, her voice would have been loud enough to silence the Great Hall if it hadn’t been for all the other students also screaming at each other. “I—I bet Malfoy tried to—to \emph{do} things to her—”

“Our General would \emph{never} do that!” Kevin Entwhistle yelled even louder than Mandy.

“Of course he would!” shouted Anthony Goldstein. “Malfoy’s the son of a \emph{Death Eater!}”

Padma stared down at her plate.

Draco was the General of her army.

Hermione was the founder of S.P.H.E.W.

Draco had trusted her to be his second-in-command.

Hermione was her fellow Ravenclaw.

Both of them were her friends, maybe the two best friends she had besides family.

Padma stared down at her plate. She was glad the Sorting Hat hadn’t offered her Hufflepuff. If she’d been Sorted into Hufflepuff it would probably have been much more painful, trying to decide where her divided loyalties lay...

She blinked and realized that her vision had gotten blurry again, and raised a trembling hand to wipe once more at her eyes.

Morag MacDougal snorted so loudly it was audible even amid the pandemonium of lunch, and said in a loud voice, “I bet Granger \emph{cheated} in her battle yesterday, I bet that’s why Malfoy challenged her \emph{-}”

“All of you \emph{\shout{Shut up!}}” roared Harry Potter, as he hit the table with his fists so hard that plates rattled all the way along it.

At any other time it would have gotten Professors reprimanding him, this time it just got a few nearby students to look.

“I’d wanted to eat lunch,” Harry Potter said, “and then get back to investigating, so I wasn’t going to talk. But you’re all being \emph{silly}, and when the truth comes out you’re going to regret what you said about innocent people. Draco didn’t do anything, Hermione didn’t do anything, they were both False-Memory-Charmed!” Harry Potter’s voice had been rising on the last words. “\emph{How is that not \shout{Bloody Obvious}?}”

“You think we’ll believe \emph{that?}” Kevin Entwhistle yelled right back at him. “That’s what everyone says! ‘I didn’t do it, it was all just a False Memory Charm!’ You think we’re \emph{stupid?}”

And Morag nodded right along with him, with a condescending look.

The look that came over Harry Potter’s face then made Padma flinch.

“I see,” Harry Potter said, it wasn’t a shout so Padma had to strain to hear it. “Professor Quirrell isn’t here to explain to me how stupid people are, but I bet this time I can get it on my own. People do something dumb and get caught and are given Veritaserum. Not romantic master criminals, because \emph{they} wouldn’t get caught, \emph{they} would have learned Occlumency. Sad, pathetic, incompetent criminals get caught, and confess under Veritaserum, and they’re desperate to stay out of Azkaban so they say they were False-Memory-Charmed. Right? So your brain, by sheer Pavlovian association, links the idea of False Memory Charms to pathetic criminals with unbelievable excuses. You don’t have to consider the specific details, your brain just \emph{pattern-matches} the hypothesis into a bucket of things you don’t believe, and you’re done. Just like my father thought that magical hypotheses could never be believed, because he’d heard so many stupid people talking about magic. Believing a hypothesis that involves False Memory Charms is \emph{low-status}.”

“What are you \emph{blithering} about?” said Morag, looking down her nose at the Boy-Who-Lived.

“You think we’d believe anything \emph{you} say?” yelled a slightly older-looking Ravenclaw witch who Padma didn’t recognize. “When \emph{you} turned Granger Dark?”

“And I’m not going to complain,” Harry Potter said in an eerily calm voice, “about wizards not having any logic and believing the craziest things. Because I said that to Professor Quirrell once, and he just gave me this \emph{look} and said that if I wasn’t blinded by my upbringing I could think of a hundred more ridiculous things that lots of Muggles believe. What you’re all doing is very human and very normal and doesn’t make you \emph{unusually} bad people, so I’m not going to complain.” The Boy-Who-Lived rose up from his bench. “I’ll see you all later.”

And Harry Potter walked away from them, walked away from all of them.

“You’re not thinking he’s \emph{right,} are you?” said Su Li from beside her, in a tone which made it clear what \emph{she} thought.

“I—” said Padma. Her words seemed to be caught in her throat, her thoughts seemed to be caught in her head. “I—I mean—I—”
\sbreak
If you think hard enough you can do the impossible.

(It had always been an article of faith with Harry. There’d been a time when he’d acknowledged the laws of physics as ultimate limitations, and now he suspected there were no true limits at all.)

If you think \emph{fast} enough you can sometimes do the impossible \emph{quickly}...

...sometimes.

Only sometimes.

Not always.

Not \emph{reliably}.

The Boy-Who-Lived stared around the trophy room, surrounded by awards and cups and plates and shields and statues and medals kept behind thousands, perhaps tens of thousands, of crystal glass displays. For as many centuries as Hogwarts had existed, this room had been accumulating details. A week, a month, maybe even a year, wouldn’t have sufficed to take the ‘examine’ option on every item in the room. Harry had asked Professor Flitwick if there was any way to detect damage to the wards around the crystal cases, verify the residue that a real duel should have left behind. Harry had raced through the Hogwarts library looking for spells to tell the difference between old fingerprints and new fingerprints, or to detect lingering exhalations in a room. And all these attempts at playing detective had failed.

There were no clues, none that he was smart enough to find.

Professor Snape had said that the portkey led to an empty house in London, with no sign of anyone or anything else.

Professor Snape hadn’t found any notes in Hermione’s dorm.

Headmaster Dumbledore had said that Voldemort’s spirit was probably hiding out in the Chamber of Secrets where the Hogwarts security system couldn’t find him. Harry had snuck into the Slytherin dungeons under the Cloak of Invisibility and spent the rest of the afternoon looking through all the obvious places, but he hadn’t found anything snaky that answered back when spoken to. The entrance to the Chamber of Secrets, it seemed, hadn’t been meant to be found in a day.

Harry had talked to all of Hermione’s friends that would still talk to him, and none of them had remembered Hermione saying anything specific about why she’d believed that Draco was plotting against her.

Professor Quirrell hadn’t come back from the Ministry as of dinnertime. The older students seemed to think that this year’s Defense Professor would probably end up being blamed for the incident, and fired for teaching Hogwarts students to be too violent. They’d talked about the Defense Professor as though he were already gone.

Harry had used up all six hours from his Time-Turner, and there were still no clues, and he had to go to sleep now if he wanted to be functional at Hermione’s trial the next day.

The Boy-Who-Destroyed-a-Dementor was standing in the middle of the Hogwarts trophy room, his wand dropped at his feet.

He was crying.

Sometimes you call your brain and it doesn’t answer.

The trial of Hermione Granger started on schedule the next day.
