\partchapter{Self-Actualization}{I}

\begin{em}\lettrine{H}{essitation} iss alwayss eassy, rarely usseful.\par\end{em}

\quad\quad So the Defense Professor had told him; and while you could quibble about the details of the proverb, Harry understood the weaknesses of Ravenclaws well enough to know that you had to try \emph{answering} your own quibbles. Did some plans call for waiting? Yes, many plans called for \emph{delayed action}; but that was not the same as \emph{hesitating} to \emph{choose}. Not delaying because you knew the right moment to do what was necessary, but delaying because you couldn’t make up your mind—there was no cunning plan which called for that.

Did you sometimes need more information to choose? Yes, but that could also turn into an excuse for delaying; and it would be \emph{tempting} to delay, when you were faced with a choice between two painful alternatives, and \emph{not choosing} would avoid the mental pain for a time. So you would pick a piece of information you couldn’t easily obtain, and claim that you couldn’t possibly decide without it; that would be your excuse. Although if you knew \emph{what} information you needed, knew \emph{when} and \emph{how} you would obtain that information, and knew what you would \emph{do} depending on each possible observation, then that was less suspicious as an excuse for hesitating.

If you \emph{weren’t} just hesitating, you ought to be able to choose \emph{in advance} what you would do, once you had the extra information you claimed you needed.

If the Dark Lord were \emph{really} out there, would it be smart to go along with Professor Quirrell’s plan to have someone impersonate the Dark Lord?

No. Definitely no. Absolutely not.

And if Harry knew for a \emph{fact} that the Dark Lord \emph{wasn’t} really out there...\ in \emph{that} case...

The Defense Professor’s office was a small room, at least today; it had changed since the last time Harry had seen it, the stone of the room becoming darker, more polished. Behind the Defense Professor’s desk stood the single empty bookcase that always decorated the room, a tall bookcase stretching almost from the floor to the ceiling, with seven empty wooden shelves. Harry had only once seen Professor Quirrell take a book from those empty shelves, and never seen him put a book back.

The green snake swayed above the seat of the chair behind the Defense Professor’s desk, the lidless eyes staring unblinking at Harry from close to his own eye level.

They were warded now by twenty-two spells, all that could be cast within Hogwarts without attracting the Headmaster’s attention.

“\emph{No,}” hissed Harry.

The green snake cocked its head, tilting it slightly; no emotion was conveyed by the gesture, not that Harry’s Parselmouth talent conveyed to him. “\emph{Reasson not?}” said the green snake.

“\emph{Too rissky,}” Harry said simply. That was true whether or not the Dark Lord was out there. Forcing himself to decide in advance had made him realize that he’d just been using the unanswered question as an excuse to hesitate; the sane decision was the same, either way.

For a moment the dark pitted eyes seemed to gleam blackly, for a moment the scaled mouth gaped to expose the fangs. “\emph{Think you have learned wrong lessson, boy, from previouss failure. My planss are not in habit of failing, and lasst one would have gone flawlesssly, but for your own foolisshnesss. Correct lessson iss to follow ssteps laid down for you by older and wisser Sslytherin, tame your wild impulssess.”}

“\emph{Lessson I learned is not to try plotss that would make girl-child friend think I am evil or boy-child friend think I am sstupid,}” Harry snapped back. He’d been planning a more temporizing response than that, but somehow the words had just slipped out.

The \emph{sssss}-ing sound that came from the snake was not heard by Harry as words, only as pure fury. A moment later, “\emph{You told them—}”

“\emph{Of coursse not! But know what they would ssay.}”

There was a long pause as the snake-head swayed, staring at Harry; again no detectable emotion came through, and Harry wondered what Professor Quirrell could be thinking that would take Professor Quirrell that long to think.

“\emph{You sserioussly care what thosse two think?}” came the snake’s final hiss. “\emph{True younglingss thosse two are, not like you. Could not weigh adult matterss.}”

“\emph{Might have done better than me,}” Harry hissed. “\emph{Boy-child friend would have assked after ssecret motivess before asssenting to resscue woman—}”

“\emph{Glad you undersstand that now,}” the snake hissed coldly. “\emph{Alwayss assk after other’ss advantage. Next learn to alwayss assk after your own. If my plan iss not to your tasste, what iss yours?}”

“\emph{If necesssary—sstay at sschool ssix yearss and sstudy. Hogwartss sseemss fine place to dwell. Bookss, friendss, sstrange but tassty food.}” Harry wanted to chuckle, but there wasn’t any gesture in Parseltongue for the kind of laughter he wanted to express.

The pits of the snake’s eyes seemed almost black. “\emph{Eassy to ssay that now. Ssuch as you and I, we do not tolerate imprissonment. You will losse patience long before sseventh year, perhapss before end of thiss one. I sshall plan accordingly.}”

And before Harry could hiss another word of Parseltongue, the human-shape of Professor Quirrell was sitting in his chair once more. “So, Mr.~Potter,” said the Defense Professor, his voice as calm as if they had been discussing nothing important, as if the whole conversation had not occurred at all, “I hear that you have begun to practice dueling. Not the worthless sort with \emph{rules}, I hope?”
\sbreak
Hannah Abbott looked as unnerved as Hermione had ever seen her (except on the day of the phoenix, the day Bellatrix Black had escaped, which shouldn’t ought to count for anyone). The Hufflepuff girl had come over to the Ravenclaw table during dinner, and tapped Hermione on her shoulder, and very nearly dragged her away—

“Neville and Harry Potter are learning dueling from Mr.~Diggory!” Hannah blurted as soon as they were a few steps away from the table.

“Who?” said Hermione.

“\emph{Cedric Diggory!}” said Hannah. “He’s the Captain of our Quidditch Team, and general of an army, and he’s taking \emph{all} the electives and getting better grades than anyone, and I hear he learns dueling from professional tutors during the summers, and he once beat \emph{two} seventh-year students, and even some teachers call him the Super Hufflepuff, and Professor Sprout says we should all emu, uh, emudate him or something like that, and—”

After Hannah finally stopped for air (the list had gone on for a while), Hermione managed to insert a word in edgewise.

“Sunshine Soldier Abbott!” said Hermione. “Calm \emph{down}. We’re not going to be fighting General Diggory, right? Sure, Neville’s studying to beat us, but we can study too—”

“Don’t you \emph{see?}” Hannah shrieked, raising her voice a lot louder then it should’ve been, if they were trying to keep the conversation private from all the Ravenclaws looking at them. “Neville isn’t studying to beat \emph{us!} He’s practicing so he can fight \emph{Bellatrix Black!} They’re going to go through us like a Bludger through a stack of pancakes!”

The Sunshine General gave her soldier a look. “Listen,” said Hermione, “I don’t think a few weeks of practice is going to make anyone an invincible fighter. Plus we already \emph{know} how to handle invincible fighters. We’ll concentrate fire on them and they’ll go down just like Draco.”

The Hufflepuff girl was looking at her with mixed admiration and skepticism. “Aren’t you even, you know, \emph{worried?}”

“Oh, \emph{honestly!}” said Hermione. Sometimes it was hard being the only sensible person in your whole school year. “Haven’t you ever heard the saying, the only thing we have to fear is fear itself?”

“\emph{What?}” said Hannah. “That’s crazy, what about Lethifolds lurking in the darkness, and being put under the Imperius Curse, and horrible Transfiguration accidents and—”

“I \emph{mean,}” said Hermione, exasperation leaking out into her now-raised voice, she’d been hearing this sort of thing \emph{all week} now, “how about if we wait until \emph{after} the Chaos Legion \emph{actually} crushes us to get so scared of them and \emph{did you just mutter ‘Gryffindors’ under your voice?}”

A few moments later, Hermione was walking back to her place at the table with a sweet smile plastered onto her young face, it wasn’t the terrible cold glare of Harry’s dark side but it was the scariest face \emph{she} knew how to make.

Harry Potter was going \emph{down.}
\sbreak
“This is loony,” gasped Neville, with what tiny amount of breath he could spare from being completely out of breath.

“This is \emph{brilliant!}” said Cedric Diggory. The eyes of the Super Hufflepuff gleamed with manic enthusiasm, shining like the sweat on his forehead as he stamped his feet through the dance of one of his dueling postures. His usually-light steps had changed to heavier stomps, which might have had something to do with the Transfigured metal weights they’d all attached to their arms and legs and strapped over their chests. “Where do you \emph{get} these ideas, Mr.~Potter?”

“A strange old shop...\ in Oxford...\ and I’m never...\ shopping there...\ again.” \emph{Thud.}


