\partchapter{Failure}{II}

\lettrine{E}{ven} as Harry had
raised the gun, he'd \emph{known} he was making a mistake, his forebrain saw it
and tried to stop his hand, but somehow the sick certainty didn't propagate
fast enough to prevent his finger from pulling the trigger---

The echo of the shots died away within the graveyard.

A fraction of a second before Harry had pulled the trigger, Voldemort had
jabbed his wand downward, and a wide wall of dirt had shot up between them from
the graveyard earth, intercepting all three bullets.

An instant after that, pain flared in Harry's scar, a crawling feeling came
close to his skin; and then Harry's pouch, clothes, gun, everything except his
wand disappeared, leaving him naked but for the wand still in his right hand,
and the glasses he'd Charmed to stick to his nose. The steel ring upon his left
pinky finger was yanked off hard enough to scrape skin, taking the Transfigured
jewel with it.

"That," said the voice of Voldemort from behind the dirt wall, "was
\emph{absolutely} predictable. Do you really think I would shout it aloud for
you to hear, if my immortality were disrupted? Really, stupid child? Lower your
wand, do not raise it up again at any time, or you die upon the spot."

Harry swallowed, and pointed his wand downward. "You would have been
disappointed in me," Harry said, his own voice now unusually high, "if I'd
missed an opportunity like that, I mean." There was no time to think, and
Harry's mouth was operating on autopilot for trying to placate evil overlords
that might have paternal feelings for you and whom you'd just failed to
assassinate.

Voldemort stepped around from behind the dirt wall, smiling that horrible smile
that seemed to contain too many teeth. "I promised not to raise my hand or wand
against you, child, if you did not raise your hand or wand against me."

"I used bullets," Harry said, his voice still high. "That's not a fist or a
spell."

"My curse thinks differently. That is the puzzle piece that you missed. Did you
think I would leave the peace between us to mere fortune? Before I created you,
I invoked a curse upon myself and all other Tom Riddles who would descend from
me. A curse to enforce that none of us would threaten the others' immortality,
so long as the other made no attempt upon our own. Typical of that ridiculous
fiasco, the curse seems to have ended up binding me, but taking no hold upon
the infant with his self so lost." A low, lethal chuckle. "\parsel{But you tried
to end my true life jusst then, sstupid child. Now cursse iss lifted, and I may
kill you any time I wissh.}"

"I see," Harry said. He did see; \emph{that} was why Voldemort had told him
about his horcrux system in the first place, just to set up the moment when
Harry knowingly tried to violate his immortality. Harry's mind was frantically
churning through options, none of which seemed helpful. His pouch, his clothes,
Harry saw by the moonlight that they all now lay in another heap by the altar,
out of reach. "And now you kill me?" Harry still had his wand, presumably the
Dark Lord couldn't cast his own magic on that, or his glasses, because of the
disharmony. \emph{Cast my own spell first? No, Voldemort just jabs his wand
downward to make another shield, then shoots me---what else is there? WHAT
ELSE?}

"Still a fool. If no further matters remained between us, I would already have
killed you." The dirt wall crumbled at another gesture of the wand, and
Voldemort moved smoothly back toward the heap of items by the altar. The Dark
Lord stretched out a hand, and the diary of Roger Bacon flew to him.
"\parsel{Thiss iss, indeed, horcrux of girl-child, my ssuperior verssion.}" In
his other hand appeared a parchment. "\parsel{Thiss iss ritual for ressurrecting
her, if it musst be done again. Insstructionss are honesst, no trapss. Remember
that girl-child'ss sspirit cannot float free like ghosst, Ressurrection Sstone
iss my horcrux, not herss. Do not losse her horcrux, or her sspirit may be
trapped within it.}" Voldemort reached down, picked up Harry's pouch, fed both
the diary and the parchment into it. "\parsel{Remember that, in casse something
goess wrong with next movess.}"

"I don't understand what is happening," Harry said. There was nothing else
left. "Please explain to me."

The Dark Lord was now regarding Harry with a grim look. "\parsel{When girl-child
died, wass in company of sschool'ss Sseer, heard prophecy sspoken that you
would become force of vasst desstruction. You would become threat beyond
imagination, beyond apocalypsse. That iss why I went to ssuch lengthss to undo
my killing of girl-child, keep it undone.}"

"Are," what "are you sure," what.

"\parsel{Dare not ssay sspecificss to you. Prophecy I heard of mysself led me to
fulfill it. Have not forgotten that dissasster.}" Voldemort backed further away
from Harry, red slitted eyes fixed upon the Boy-Who-Lived, gun unwavering in
the left hand. "\parsel{All thiss, all I have done, iss to ssmassh that desstiny
at every point of intervention. If ssome fate makess me fail in what comess
next, idiot-child of foretold desstruction, then you musst kill yoursself to
ssave girl-child. Elsse all you claim to value diess by your own hand.}"

"I," Harry's voice went up an octave, "I," another octave, "I \emph{really
really wouldn't do that, seriously!}"

"\parsel{Ssilence, fool. Remain ssilent unlesss given leave by me to sspeak. Keep
your wand pointed down and do not raisse it unlesss told. Elsse you die upon
the sspot, and mark that I ssaid that in Parsseltongue.}" Voldemort reached
into the altar again.

For a second Harry's mind couldn't process what he was seeing, and then he saw
that Voldemort was holding a human arm, severed near the shoulder; it seemed
too thin, that arm.

The Dark Lord pressed his wand to the flesh above the severed arm's elbow, and
the fingers twitched, twitched like they were alive; by dim moonlight Harry saw
a darker mark appear on that flesh, just above the elbow.

Seconds later the first hooded figure appeared inside the graveyard with the
popping sound of an Apparition. A moment after that came another pop, and then
another.

The hooded figures wore silver skull masks, and moonlight fled from the robes
beneath them.

"Master!" cried one of the black robes, the third to arrive. The voice was of
peculiar timbre, from behind the silver skull mask. "Master---it has been so
long---we had lost hope---"

"Silence!" shouted the high voice of the Dark Lord Voldemort. Every trace of
Professor Quirrell was now gone from the too-tall figure. "Train your wand upon
the Boy-Who-Lived, and watch him! Do not be distracted, not by anything! Stun
him at once if he moves, if he begins to speak!"

More pops. Between graves, behind a tree, in all the shadowy spaces, more black
robes were Apparating, all hooded and masked. Some of them voiced exclamations
of joy, many of those sounding rather forced; others moved forwards as though
to greet their Master. Voldemort gave them all the same instruction, except
that some were commanded to Cruciate Harry Potter if he moved, others to
restrain the Boy-Who-Lived if he moved, others told to fire hexes and curses,
others told to cancel his magic.

Thirty-seven pops, Harry counted before the black robes and skull masks seemed
to stop arriving.

All of them were now holding their wands pointed at Harry, aligned in a
semicircle before him, where they wouldn't get into each other's lines of fire.

Harry continued pointing his wand downward, insofar as he had been told that,
if he tried to raise it, he would die. He remained silent, insofar as he had
been told that if he tried to speak, he would die. He tried not to shiver in
the falling night temperatures, for he was naked, and it was getting colder.

\emph{You know,} said the last voice within Harry, the voice of hope, \emph{I
think this is getting pretty bad even by my standards.}
