\namedpartchapter{Self-Actualization}{SA}{VII}{Plausible Deniability}

\lettrine{T}{he} winter Sun had well set by the time dinner ended, and so it was amid the peaceful light of stars twinkling down from the enchanted ceiling of the Great Hall that Hermione left for the Ravenclaw Tower alongside her study partner Harry Potter, who lately seemed to have a \emph{ridiculous} amount of time for studying. She hadn’t the faintest idea of when Harry was doing his actual homework, except that it was getting done, maybe by house elves while he slept.

Nearly every single pair of eyes in the whole Hall lay on them as they passed through the mighty doors of the dining-room, which were more like siege gates of a castle than anything students ought to go through on the way back from supper.

They went out without speaking, and walked until the distant babble of student conversation had faded into silence; and then the two of them went on a little further through the stone corridors before Hermione finally spoke.

“Why’d you do that, Harry?”

“Do what?” said the Boy-Who-Lived in an abstracted tone, as if his mind were quite elsewhere, thinking about vastly more important things.

“I mean, why didn’t you just \emph{tell} them no?”

“Well,” Harry said, as their shoes pattered across the tiles, “I can’t just go around saying ‘no’ every time someone asks me about something I haven’t done. I mean, suppose someone asks me, ‘Harry, did you pull the prank with the invisible paint?’ and I say ‘No’ and then they say ‘Harry, do you know who messed with the Gryffindor Seeker’s broomstick?’ and I say ‘I refuse to answer that question.’ It’s sort of a giveaway.”

“And \emph{that’s} why,” Hermione said carefully, “you told everyone...” She concentrated, rembering the exact words. “That if hypothetically there \emph{was} a conspiracy, you could not confirm or deny that the true master of the conspiracy was Salazar Slytherin’s ghost, and in fact you wouldn’t even be able to admit the conspiracy existed so people ought to stop asking you questions about it.”

“Yep,” said Harry Potter, smiling slightly. “That’ll teach them to take hypothetical scenarios too seriously.”

“And you told \emph{me} not to answer anything—”

“They might not \emph{believe} you, if you deny it,” said Harry. “So it’s better to say nothing, unless you want them to think you’re a liar.”

“But—” Hermione said helplessly. “But—but now people think I’m \emph{doing} things for \emph{Salazar Slytherin!}” The way the Gryffindors had been looking at her—the way the \emph{Slytherins} had been looking at her—

“It goes along with being a hero,” Harry said. “Have you seen what the \emph{Quibbler} says about \emph{me?}”

For a brief second Hermione imagined her parents reading a newspaper article about her, and instead of the story being about her winning a nationwide spelling bee or any of the other ways she’d imagined getting into the papers, the headline said “HERMIONE GRANGER GETS DRACO MALFOY PREGNANT”.

It was enough to make you think twice about the whole heroine business.

Harry’s voice turned a bit more formal. “Speaking of which, Miss Granger, how goes your latest quest?”

“Well,” said Hermione, “unless the ghost of Salazar Slytherin really \emph{does} show up and tell us where to find bullies, I don’t think we’re going to have much luck.” Not that she was sorry about that.

She glanced over at Harry, and saw the boy giving her a peculiarly intense look.

“You know, Hermione,” the boy said quietly, as though to make sure that nobody else in the world heard, “I think you’re right. I think some people get a lot more help than others in becoming heroes. And \emph{I} don’t think that’s fair, either.”

And Harry grabbed at her witch’s robes where they lay over her arm, and hustled her into a side-hall of the corridor they were walking through, her mouth gaping open in surprise even as Harry’s wand came into his hand, they rounded a curve of the side-hall and it was so narrow that it was almost pushing her and Harry into each other, even as Harry pointed to the way they’d come and softly said “\emph{Quietus}”, then a moment later, in the other direction, “\emph{Quietus}” again.

The boy looked searchingly around them, not just to every side, but even upward toward the ceiling and down toward the floor.

And then Harry stuck a hand in his pouch and said, “Invisibility cloak.”

“\emph{Gleep?}” said Hermione.

Harry was already drawing out folds of shimmering black fabric from the mokeskin device. “Don’t worry,” the boy said with a small grin, “they’re so rare that nobody bothered to make a school rule against them...”

And then Harry held out the dark velvet mesh to her, and said, his voice strangely formal, “I do not give you, but loan you, my cloak, unto Hermione Jean Granger. Protect her well.”

She stared at the shimmering velvet of the cloak, cloth that swallowed all the light that fell on it except what glinted from small strange reflections, fabric so perfectly black it should’ve shown dust or lint or \emph{something} but it didn’t, the longer you looked the more you felt like what you were seeing wasn’t really there at all, but then you blinked again and it was just a black cloak.

“Take it, Hermione.”

Hardly even thinking, Hermione stretched out her hand to grasp the fabric; and then just as her brain woke up and she started to pull her hand back, Harry let go of the cloak and it started to fall and she grabbed at it without thinking. And the instant her fingers touched and held the cloak she felt an intangible jolt run through her like picking up her wand for the first time; and it was like she heard a song being sung, ever so faintly, in the back of her mind.

“That’s one of my quest items, Hermione,” Harry said softly. “It belonged to my father, and it’s not something I can replace, if it’s lost. Don’t loan it to anyone else, don’t show it to anyone, don’t tell anyone it exists...\ but if you want to borrow it for a while, just come to me and ask.”

Hermione finally tore her eyes loose from the depthless black folds and stared back up at Harry.

“I can’t—”

“You certainly can,” Harry said. “Because there’s nothing even the tiniest bit fair about my finding this gift-wrapped in a box next to my bed one morning, and you...\ not.” Harry paused thoughtfully. “Unless you \emph{did} get your own invisibility cloak, in which case never mind.”

Then the implications of \emph{invisibility cloak} finally dawned on her, and she pointed a shocked finger at Harry, though they were close enough together that she couldn’t quite straighten her arm properly, and her voice rose with considerable indignation as she said, “So \emph{that’s} how you disappeared from the Potions closet! And the time when—” and then she trailed off, because even \emph{with} an invisibility cloak she still couldn’t see how Harry had...

Harry buffed his fingernails on his robes with artful nonchalance, and said, “Well, you knew there had to be \emph{some} trick to it, right? And now the heroine will mysteriously know where and when to find bullies—just like she listened to the bullies planning it, even though nobody her age could \emph{possibly} have turned herself invisible to spy on them.”

There was a pause and a silence.

“Harry—” she said. “I’m—I’m not sure anymore that fighting bullies is such a good idea.”

Harry’s eyes stayed steady on hers. “Because the other girls might get hurt?”

She nodded, just nodded.

“That’s \emph{their} choice, Hermione, just like it’s yours. \emph{I} decided not to do the obvious stupid thing that everyone does in books, try to keep you safe and protected and helpless, and have you get really angry at me, and push me away while you go off on your own and get into even more trouble, and then heroically pull through it successfully, after which I’d finally have my epiphany and realize that blah blah blah etcetera. I know how that part of my life story goes, so I’m just skipping over it. If I can predict what I’m going to think later, I might as well go ahead and think it now. Anyway, my point is, you shouldn’t smother \emph{your} friends to keep them safe, either. Just tell them up front it’s predictably going to go horribly wrong, and if they still want to be heroines after that, fine.”

It was at times like this that Hermione wondered if she was \emph{ever} going to get used to the way Harry thought. “Harry, I really,” her voice stuck for a second, “really, \emph{really} don’t want them getting hurt! Especially because of something I started!”

“Hermione,” Harry said seriously, “I’m pretty sure you did the right thing. I don’t see what could realistically happen to them that would be \emph{worse} for them, in the long run, than\emph{ not trying}.”

“What if they get \emph{badly} hurt?” Hermione said. Her voice felt blocked in her throat; she remembered Captain Ernie saying how Harry had just stared straight into the eyes of a bully as the bully bent his finger back, before Professor Sprout had arrived to save him; and there was another thought that came after that, about Hannah and her delicate hands with the fingernails that she carefully painted in Hufflepuff yellow every morning, but that wasn’t allowed to be imagined. “And then—they’ll never do anything courageous, ever again—”

“I don’t think it works like that,” Harry said steadily. “Even if it all goes mind-bogglingly wrong, I don’t think it works like that inside a human mind. The important thing is believing about yourself that you’re someone who can break your boundaries. Trying and getting hurt can’t possibly be worse for you than being... \emph{stuck}.”

“What if you’re \emph{wrong,} Harry?”

Harry paused for a moment, and then shrugged a little sadly, and said, “What if I’m right?”

Hermione looked back at the black mesh running over her hand. From the inside the cloak felt strangely soft and yet firm against her palm, as if it was trying to give her hand a reassuring hug.

Then she lifted her arm back up, holding the cloak back to Harry.

Harry didn’t move to take it.

“I—” said Hermione. “I mean, thank you, thank you a lot, but I’m still thinking about it, so you can take it back for now. And... Harry, I don’t think it’s right to \emph{spy} on people—”

“Not even on known bullies, to rescue their victims?” Harry said. “\emph{I’ve} never been bullied, but I’ve been through a realistic simulation, and it didn’t feel very pleasant. Have you ever been bullied, Hermione?”

“No,” she said in a quiet voice, and went on holding out Harry’s invisibility cloak to him.

Finally Harry took back his cloak—she felt a small twitch of loss as the inaudible song vanished from the back of her mind—and started to stuff the black material back into his pouch.

As the pouch ate the last of the fabric, Harry turned from her, to break the Quieting Barrier—

“And, um,” Hermione said. “That’s not \emph{the} Cloak of Invisibility, is it? The one we read about in the library on page eighteen of Paula Vieira’s translation of Gottschalk’s \emph{An Illustrated Scroll of Lost Devices}?”

Harry turned his head back, grinning slightly, and said in exactly the same tone of voice he’d used earlier with the other students at dinner, “I cannot confirm or deny that I possess magical artifacts of incredible power.”
\sbreak
When Hermione climbed into bed that night she was still trying to decide. Her life had been simpler at dinnertime, back when there hadn’t \emph{been} any practical way for them to find bullies; and now she had to choose again; not for herself, this time, but for her friends. In her mind’s eye she kept seeing Dumbledore’s lined face and the pain it hadn’t quite hidden, and in her mind’s ears she kept hearing Harry’s voice saying ‘That’s their choice, Hermione, just like it’s yours.’

And her hand kept remembering the sensation of the cloak against her fingers, replaying it over and over in her mind. There was a power to the feeling that compelled her thoughts to return to it, and to the song she’d heard/hadn’t heard in a part of her mind and magic which now lay silent once more.

Harry had spoken to the cloak like it was a \emph{person}, telling it to take good care of her. Harry had said the cloak had belonged to his father, that he couldn’t replace it if it was lost...

But... Harry wouldn’t \emph{really} do that, would he?

Just \emph{hand} her one of the three Deathly Hallows created centuries before Hogwarts?

She could say that she felt flattered, but this went \emph{way} beyond feeling flattered, into making her wonder just what she was to Harry, exactly.

Maybe Harry was the sort of person who went around loaning ancient lost magical artifacts to \emph{anyone} he considered a friend, but—

But when she thought about \emph{which} part of his life Harry had said he’d skipped over, the part where he tried to keep her safe and protected...

Hermione stared up at the ceiling of the Ravenclaw dorm. Somewhere beyond her bed, Mandy and Su were talking. She’d turned up her Quieting Charm to where she couldn’t hear the exact words, but could still hear their faint murmur; there was something comforting about sleeping in a dorm with the other girls. Harry kept his own Quieter turned up all the way, she knew.

She was starting to wonder if maybe Harry actually \emph{did}, well...

You know...

\emph{Like} her.

It took Hermione Granger a long time to fall asleep that night.

And when she woke up the next morning there was a small slip of parchment peeking out from under her pillow which said \emph{At half-past ten you will find a bully in the fourth passageway to the left of the hall leaving the Potions classroom—S.}
\sbreak
When Hermione entered the Great Hall that morning, her stomach was filled with flying butterflies the size of Hippogriffs; even as she approached the Ravenclaw breakfast table she still hadn’t decided what to \emph{do.}

There was an empty place next to Padma, she saw. That would be where to sit down, if she was going to tell Padma and then ask Padma to tell Daphne and Tracey.

Hermione walked toward the empty place next to Padma.

There were words waiting in her throat, \emph{Padma, I got a}\emph{ mysterious}\emph{ message—}

And she could feel a huge brick wall inside her, stopping the words from coming out. She’d be putting Hannah and Susan and Daphne \emph{in danger}. Taking them and leading them by the hand straight into trouble. That was Wrong.

Or she could just go try to handle the bully herself, without telling her friends anything, and that, quite obviously, was also Wrong.

Hermione knew she was being faced with a Moral Dilemma, just like all those wizards and witches she’d read about in stories. Only in stories people always got a \emph{right} choice and a wrong choice, not two wrong ones, which seemed a bit unfair. But she had the sense, somehow—maybe it came from the way Harry always talked about how the history books would see them—that she was faced with a Heroic Decision, and that her whole life might end up going one way or another, depending on what she chose right now, \emph{this morning}.

Hermione sat down at the table without looking to either side, just gazing at the plate and silverware like they might have answers hidden inside, thinking as hard as she ever had, and a few seconds later she heard Padma’s voice whispering almost in her ear, “Daphne says she knows where a bully’s going to be at ten-thirty today.”
\sbreak
Doomed.

They were all doomed, in Susan Bones’s opinion.

Auntie sometimes told stories which started out like this, people doing something they \emph{knew} was stupid, and the stories usually ended with someone being \emph{doomed} all over the floor and all over the walls and getting on Auntie’s shoes.

“Hey, Padma,” muttered Parvati, her voice just barely audible over the soft impacts of eight girls tiptoeing through the corridor leading to the Potions classroom, “d’you know why Hermione’s been sighing all morning—”

“No talking!” hissed Lavender, the harsh whisper sounding much louder than Parvati’s mutter. “You never know when Evil might be listening!”

\emph{“Shhh!}” said three other girls even more loudly.

Utterly, totally, quite extremely doomed.

As they approached the fourth passageway to the left of the Potions classroom, where Daphne’s mysterious informant had said the bullying would take place, the eight of them moved slower, the sound of their feet got softer, and finally General Granger made the gesture that meant \emph{Halt, I’ll look ahead}.

Lavender raised a hand, then, and when Hermione turned to look at her, Lavender, looking puzzled, pointed straight down the corridor, gestured to herself, and then tried to sign something else that Susan didn’t understand—

General Granger shook her head, and once again, this time with slower, more exaggerated movements, made the sign for \emph{Halt, I’ll look ahead}.

Lavender, looking even more puzzled, pointed back the way they’d come, and made a bouncing gesture with her other hand.

Now everyone else was looking even more confused than Lavender, and Susan thought with some acerbity that evidently one hour of practice done two days ago wasn’t enough to remember a new set of code signals.

Hermione pointed at Lavender, then at the floor beneath Lavender’s feet, the expression on her face making it very clear that the intended meaning was \emph{You. Stay. Here.}

Lavender nodded.

\emph{Doom doom doom,} went the words of the Chaos Legion’s marching song through Susan’s mind, \emph{doom doom doom doom doom doom}...

Hermione reached into her robes, and drew out a little rod with a mirror on the end of it and an eyepiece. Very very softly indeed, the Ravenclaw girl crept up to the wall, right next to where the passageway opened off the corridor, and peeked just the tip of the eyepiece around the corner.

Then a little more.

Then a little more.

Then General Granger cautiously stuck her head around the side.

General Granger turned back to them, nodded, and made the hand gesture for \emph{follow me}.

Susan felt a little better as she crept forward. The part of the Plan which called for them to arrive thirty minutes before the bully had, apparently, actually worked. Maybe they were only \emph{slightly} doomed...?
\sbreak
At ten-twenty-nine, almost on the dot, the bully showed up. If anyone had been present to hear—though the corridor was apparently empty—they would have heard his shoes clicking solidly through the main corridor, entering the passageway, walking toward where the passageway turned its first corner, turning that corner, and then stopping in some surprise upon seeing that the passageway now terminated in a solid brick wall where no wall had been before.

Then the bully shrugged and turned away, as he leaned back to watch the main passage from just around the corner.

It \emph{was} the castle Hogwarts, after all.

Behind the hastily Transfigured thin panels they’d assembled into the outward appearance of a brick wall, the girls waited; not speaking, not moving, hardly even breathing, but watching through the eyeholes they’d left themselves.

As Susan’s gaze took in the bully, she could feel the tightening of her chest all the way into her toes. The boy looked to be in his seventh-year if not \emph{older}, and his robes were trimmed in green instead of the red they’d been hoping for, and he had \emph{muscles}, and after staring for a bit longer, Susan realized his stance had the balance that meant that he \emph{dueled}.

Then they all heard the sound of more feet approaching from the corridor. The fourth-year Gryffindors and Slytherins had just been let out of Potions class.

The footsteps pattered past, and diminished and faded, and the bully didn’t do anything. For a moment Susan felt an instant of relief—

Then another, smaller group of footsteps approached.

The bully still didn’t do anything, as the footsteps went past.

That happened a few more times.

And then, as there approached the faintly audible sound of one last set of footsteps, the seven girls heard the bully’s voice saying, clear and cold and quiet, “\emph{Protego}”.

Someone \emph{did} gasp then, though fortunately very very quietly. If they couldn’t get in even a single shot—

The bullies were learning \emph{already}, Susan realized, she hadn’t expected \SPHEW to be able to do this very often before the bullies caught on—but—Hermione had already defeated three bullies—and the school had been buzzing with speculation about Salazar Slytherin’s ghost, yesterday—

\emph{He’s expecting us!}

Susan would have whispered to give up, to abort the plan, only there was no way to convey a message to—

“\emph{Silencio},” said the bully in a soft, deliberate voice with his wand pointed toward the corridor, the blue haze of his Shielding Charm shimmering around him. “\emph{Accio} victim.”

When the fourth-year boy came into their field of vision he was dangling upside down as if an invisible hand were holding him high by one leg, his red-trimmed robes beginning to slide down his thighs to reveal the pants beneath. His mouth was opening and closing helpessly, no sound coming out.

“I suppose you’re wondering what’s going on,” the seventh-year Slytherin said in a quiet, cold voice. “Don’t worry. It’s so simple even a Gryffindor could understand.”

With that, the Slytherin’s left hand formed a fist and drove hard into the Gryffindor’s belly. The fourth-year boy’s body jerked around frantically, but still no words left his mouth.

“You’re my victim,” said the older Slytherin. “I’m a bully. I’m going to beat you up. And we’ll see if anyone stops me.”

It was at that moment that Susan realized it was a trap.

And in almost the same moment, there rang out the mighty and high-pitched voice of a young girl, crying, “\emph{Stop, evildoer! Finite Incantatem!}”

\emph{Lavender}, thought Susan, agonized. The Gryffindor girl had volunteered to be a distraction, while the rest of them executed a flank attack from where the bully wouldn’t expect it, that had been the plan, only now—

“In the name of Hogwarts,” cried Lavender’s voice, though they couldn’t see her, “and in the name of heroines everywhere, I command you to let go of that EEK!”

“\emph{Expelliarmus},” said the bully. “\emph{Stupefy}. \emph{Accio} stupid heroine.”

When Lavender floated into their vision, dangling by one foot and unconscious, Susan blinked; the girl was dressed in a bright crimson-and-gold skirt and blouse, instead of her usual Hogwarts robes.

The bully was also giving the girl’s upside-down body an odd look, and then he pointed his wand at her and said “\emph{Finite Incantatem},” but the clothes stayed the same.

Then the bully shrugged, and, still facing in the direction of Lavender instead of the dangling fourth-year boy, drew back his fist—

“\emph{Lagann!}” yelled five voices, and five green spirals blasted from five wands aimed through five holes in the false wall, and an instant later Hermione’s voice shouted “\emph{Stupefy!}”

Five green spirals shattered ineffectually on blue haze, and Hermione’s red bolt bounced off the haze and struck the fourth-year boy, who jerked and then was still.

And the seventh-year bully turned around, smiling grimly, as the first-year girls screamed and charged.
\sbreak
Susan’s eyes flew open and instantly she was rolling away from where she’d lain on the floor, her lungs still on fire and her whole body still aching from when she’d been hit, the battle had only moved forward a few seconds from what she could see, Hannah’s body falling with her arm still stretched out toward Susan, “\emph{Glisseo!}” shouted Hermione but the older boy just slashed his wand down leaving a trail of green glow behind and Hermione’s Charm visibly disrupted into a shower of blue-white sparks, then in almost the same motion the bully said “\emph{Stupefy!}” and Hermione was blown backward and Susan summoned up all the magic she had left and shouted “\emph{Innervate!}” at Hermione’s body even as the bully turned toward her, the bully’s wand pointed in her direction again and then Padma yelled “\emph{Prismatis!}” just before the bully shouted “\emph{Impedimenta!}”, the rainbow sphere forming \emph{around the bully} and the seventh-year Slytherin staggered as his own hex was reflected back at him, but an instant later the bully’s wand swept back to tap himself and then Padma’s Prismatic Sphere shattered like a blown soap bubble as the bully’s wand cut through it and “\emph{Innervate!}” yelled Parvati at Hannah’s body and Tracey and Lavender screamed at the same time, “\emph{Wingardium Leviosa!}”—
\sbreak
Hannah Abbott held out her wand with a hand that trembled with exhaustion, she didn’t have enough magic left for even one \emph{Innervate}, now.

The rest of the passageway was silent, scattered bodies lying across the ground, Padma and Tracey and Lavender, Hermione and Parvati in a heap against one wall, Susan standing in petrified rigor as her eyes tracked it all helplessly, even the Gryffindor boy lying sprawled and motionless (Hermione had woken him and he’d fought, but it hadn’t been enough).

It had been a very short battle.

The bully was still smiling, the only signs of his exertion a wavering ripple in the blue glow surrounding him, and a few beads of sweat on his forehead.

The bully raised his arm, wiped the sweat off his forehead, and stalked toward her like a man-shaped living Lethifold.

Hannah turned and fled, spun and ran with screams kept bound in her choking throat, sprinted past the fallen paneling of the fake brick wall, ran down the passageway with all the speed she could muster, weaving as much as she could—

Just before Hannah got to the turn in the passageway, the bully’s voice from behind her said “\emph{Cluthe!}” and she got awful cramps all through her legs, she fell down and slid and hit her head against the wall, only she didn’t even notice the pain of the smack as she started to scream with the twisting muscles—

The bully was still stalking toward her, Hannah saw as she turned her head; stalking toward her like a man-shaped living Lethifold, still wearing that dreadful smile.

And she rolled, despite the pain as her leg muscles knotted up around themselves, she rolled around the corner of the passageway, and screamed, “Go \emph{away!}”

“I think not,” said the bully, his voice deep and scary like that of a grown man, sounding very close at hand now.

The bully walked around the corner and Daphne Greengrass stabbed her Most Ancient Blade directly into his groin.

There was a flash that lit up the whole corridor—
\sbreak
It was with a subdued mien that seven girls left Madam Pomfrey’s office, leaving one of their own behind in a hospital bed.

Hannah would be all right in about thirty-five minutes, the healer had said; torn muscles were easy to mend.

Daphne had done all the talking, and according to her, Hannah had suffered a mishap with a Road-Running Charm which had caused the leg cramps. Madam Pomfrey had given them a sharp look but hadn’t argued, even though that Charm was around six years above their level.

Madam Pomfrey had also given Daphne a potion to help with her state of total magical exhaustion, and warned her not to cast any spells for the next three hours. That, supposedly, was from Daphne using up too much magic trying to \emph{Finite} Hannah, rather than the Most Ancient Blade drawing out all of her power to break the \emph{Protego}.

The rest of them had decided not to say anything about the bruises under their robes until they could get some older girls to cast \emph{Episkey}. There were limits to what Daphne could talk around.

The whole thing, Susan thought, had been too close, much too close. If the bully had so much as looked around the corner—if he’d taken a moment to recast his Shielding Charm—

“We should stop,” said Susan, as soon as the seven of them had gotten out of hearing range of the healer’s office. “We should stop doing this.”

For some reason, then, even though they were supposed to vote on this sort of thing, everyone turned to look at General Granger.

The Sunshine General didn’t seem to see them looking at her, she just strode on, gazing off straight ahead.

After a little while, Hermione Granger said, in a voice that sounded thoughtful and a little sad, “Hannah said \emph{she} didn’t want us to stop. I’m not sure it’s right for us to...\ be less brave \emph{for} her, than she is.”

All the other girls, except Susan, nodded at that.

“I think that’s got to be as bad as it gets,” said Parvati. “And we can handle it. We’ve proved that now.”

Susan couldn’t think of anything to say to that. She didn’t think that shrieking at the top of her lungs about blatant stupidity and DOOM would be persuasive. And she couldn’t just \emph{leave} the other girls, either. Wasn’t it enough to be cursed with hard work, why did Hufflepuffs have to be \emph{loyal} on top of everything else?

“By the way, Lavender,” said Padma. “What in the name of Merlin’s underpants were you \emph{wearing} back there?”

“My hero outfit,” said the Gryffindor girl.

Daphne sounded weary, as she spoke without turning her own head from where she was plodding through the hall. “It’s the costume of the Soldier of Gryffindor from the play \emph{Chronicles of the Lunarian Soldiers}.”

“Did you Transfigure it?” said Parvati, looking puzzled. “But the bully cast \emph{Finite} on you—”

“Nope!” Lavender said. “It’s \emph{real!} See, I just Transfigured my hero outfit into a regular shirt and skirt \emph{beforehand}, so all I had to do was cast \emph{Finite} on myself after I saw the bully. Do you want your own, Parvati? I got mine made yesterday by Katarina and Joshua in sixth-year, for twelve Sickles—”

“I think,” General Granger said in a careful voice, “that would make us all look a little silly.”

“Well,” said Lavender, “we should vote on whether to—”

“I think,” General Granger said, “that no matter what \emph{anyone} votes, I’m not going to be caught \emph{dead} wearing one of those costumes—”

Susan ignored the argument. She was trying to think up some sort of clever strategy for being less doomed.
\sbreak
The whole Great Hall went silent, even if only for a moment, as the seven of them walked into lunch.

Then the applause started.

It was scattered, not the massive applause of everyone applauding at once. A lot of it came from the Gryffindor table, less from Hufflepuff and Ravenclaw, and none from Slytherin.

Daphne felt her face tightening. She’d \emph{hoped} —well, maybe after they found a Gryffindor bully to stop and a Slytherin to rescue, her fellow Slytherins would realize—

She looked at the Hufflepuff table.

Neville Longbottom was applauding with his hands held high above his head, although he wasn’t smiling. Maybe he’d heard about Hannah, or maybe he was wondering why Hannah wasn’t there.

Then, not quite able to help herself, she glanced toward the Head Table.

Professor Sprout’s face was lined with concern. She and Professor McGonagall were leaning their heads toward Headmaster Dumbledore, who had a solemn look, and all their lips were moving quickly. Professor Flitwick looked more resigned than anything else, and Quirrell, face slack, was taking trembling stabs at his soup using a spoon gripped in a fist.

Professor Snape was looking directly at—

\emph{Her?}

Or—at Hermione Granger, standing next to her?

A small, thin smile crossed the Potions Master’s face, and he raised his hands, brought them together once in a motion that was too slow to be a real clap; and then the Potions Master turned back to his plate, ignoring the conversations around him.

Daphne felt a little chill go down her spine, and she hastily turned to walk toward the Slytherin table. Susan and Lavender and Parvati peeled off from their group, heading toward the Hufflepuff and Gryffindor tables on the other side of the Great Hall.

It happened as they were passing the part of the Slytherin table where the Slytherin Quidditch team sat.

That was when Hermione stumbled suddenly, stumbled \emph{hard} like she was being yanked off her feet, and went sprawling into the gap between where Marcus Flint and Lucian Bole sat, and there was a sad little splutching sound as Hermione’s face ended up in Flint’s plate of steak and mashed potatoes.

Everything seemed to happen too quickly then, or maybe it was just Daphne herself who was thinking too slow, as Flint let out a bellow of indignation and his hand yanked Hermione back and threw her into the Ravenclaw table, and she bounced off a student’s back and collapsed onto the ground—

The quiet spread out in ripples.

Hermione pushed herself up on her hands, though she didn’t get all the way to her feet, Daphne could see that her whole body was shaking, and that her face was still covered with mashed potatoes with scattered pieces of steak embedded like carbuncles.

For a long moment, nobody spoke, nobody moved. Like nobody in the whole Great Hall could imagine, any more than Daphne could, what happened next.

Then Flint’s powerful voice, the voice of the Slytherin Captain that bellowed commands on the Quidditch pitch, said in a dangerous rumble, “You ruined my food, girl.”

Another moment of frozen silence. Hermione’s head—Daphne could see it trembling—turned to look at the Slytherin Quidditch Captain.

“Apologize to me,” said Flint.

Harry Potter started to push himself up from the Ravenclaw table, and then stopped abruptly, halfway to his feet, as if he’d just thought of something—

Then five other people stood up from the Ravenclaw table.

All of the Slytherin Quidditch team stood up, their wands coming into their hands, and then students stood up at the Gryffindor table and at the Hufflepuff table and without thinking Daphne turned to look at the Head Table and she saw that the Headmaster was still sitting down, watching, just watching, Dumbledore was \emph{just watching} and he had one hand out as though to restrain Professor McGonagall—in just one second someone would shout a spell and then it would be too late, \emph{why wasn’t the Headmaster doing anything}—

And a voice said, “My apologies.”

Daphne turned back to look, her mouth gaping open in absolute shock.

“\emph{Scourgify},” said that smooth voice, and the mashed potatoes vanished from Hermione’s face, revealing the Ravenclaw’s surprised expression as Draco Malfoy approached her, sheathed his wand again, and then knelt to one knee beside her and offered her a hand.

“Sorry about that, Miss Granger,” said Draco Malfoy’s polite voice. “I guess someone thought they were being funny.”

Hermione took Draco’s hand, and Daphne suddenly realized what was about to happen—

But Draco Malfoy \emph{didn’t} raise Hermione halfway up and then drop her.

He just pulled her to her feet.

“Thanks,” said Hermione.

“You’re welcome,” Draco Malfoy said in a loud voice, not looking to either side to see where all four Houses of Hogwarts were staring at him in total shock. “Just remember, being cunning and ambitious doesn’t mean you have to be like that.”

And then Draco Malfoy went back to his seat at the Slytherin bench and sat down like he hadn’t—he hadn’t just—\emph{he’d just}—

Hermione went to the nearest empty place at the Ravenclaw bench and sat down.

A number of other people, rather slowly, sat down.

“Daphne?” said Tracey. “Are you all right?”
\sbreak
Draco’s heart was hammering in his chest so hard he worried it might explode right out of his chest in a shower of blood, like that curse Amycus Carrow had used once on a puppy.

Draco’s face stayed completely controlled, because he knew (it’d been drilled into him over and over) that if he showed the slightest sign of the fear he was feeling, his Housemates would rip him apart like a swarm of Acromantulas.

There’d been no time to check with Harry Potter, no time to plot, no time to think, just the instant of realizing that the time to start rescuing Slytherin’s reputation was \emph{right then}.

From all sides of the long Slytherin table, angry faces stared at Draco.

But they were outnumbered by the faces that just looked puzzled.

“All right, I give up,” said a sixth-year boy that Draco didn’t recognize, sitting across from him and two places to his right. “Why did you do that, Malfoy?”

Although his mouth was very dry, Draco didn’t swallow. That would have been a sign of fear. Instead he took a bite of carrots, which had the most moisture of anything on his plate, and chewed and swallowed, thinking as rapidly as he could.

“You know,” Draco said, making his voice as cutting as he could—as his heart thumped even harder in his chest, as everyone around him stopped talking to listen—“there’s \emph{probably} some way to make Slytherin look even \emph{worse} than attacking eight first-year girls from all four Houses who are working together to stop bullies, but I can’t think of \emph{how}. This way we get the benefit of what Greengrass is doing.”

The puzzled faces stayed puzzled.

“What?” said the sixth-year boy, and “Wait, \emph{what} benefit?” said a fifth-year girl sitting to his right.

“It makes Slytherin House look better,” said Draco.

The Slytherins around him were giving him quizzical gazes like he’d just tried to explain algebra.

“Look better to \emph{who?}” said the sixth-year boy.

“But you just helped a \emph{mudblood},” said the fifth-year girl. “How’s \emph{that s}upposed to look good?”

Draco’s throat closed up. His brain was experiencing a hideous malfunction during which it couldn’t think of anything to say except the truth—

Then, “It’s probably some kind of tremendously clever scheme Malfoy’s got going,” said a fifth-year boy. “You know, like in \emph{The Tragedy of Light}, where everything that looks like a setback is part of the plot. And it ends with Granger’s head on a stick and nobody suspecting that it was him.”

“\emph{That} makes sense,” someone said from further down the table, and there was a lot of nodding.
\sbreak
“Do \emph{you} know what the boss’s up to?” Vincent muttered in an undertone.

Gregory Goyle didn’t reply. In his mind he could hear very clearly his master’s voice, saying,\emph{ I can’t believe I believed every word of that}, the day the rumor had started about Salazar Slytherin showing Potter and Granger where to find bullies.

“Mr.~Goyle?” whispered Vincent.

Gregory Goyle’s lips shaped the words, \emph{Oh no,} but no sound came out.
\sbreak
Hermione had left lunch early that day, for some reason she hadn’t felt hungry. Those few seconds of horrible humiliation had kept burning through her mind, over and over, the feeling of her face squishing into the mashed potatoes and then being thrown through the air and then the Slytherin’s boy’s voice saying ‘Apologize to me’...\ it might have been the first time in her whole life that she’d felt like \emph{hating} someone. The boy who’d thrown her (Marcus Flint, they’d said his name was) and whoever had cast the tripping Jinx on her in the first place...\ she’d felt it, for one horrible instant she’d wanted to go tell Harry that if he started getting \emph{creative} on her behalf, she wouldn’t object.

She hadn’t been a minute out of the Great Hall before she’d heard the sound of running feet behind, and turned to see Daphne racing toward her.

And listened to what her Sunshine Soldier had to say...

“Don’t you \emph{understand?}” Daphne’s voice was barely below a shriek. “Just because someone’s nice to you doesn’t mean they’re your friend! He’s \emph{Draco Malfoy!} His father’s a Death Eater, all the parents of all his friends are Death Eaters—Nott, Goyle, Crabbe, \emph{everyone around him}, do you get it? They \emph{all} despise Muggleborns, they want everyone like you to \emph{die}, they think you’re good for nothing but being a \emph{sacrifice} in horrible Dark rituals! Draco is \emph{the next Lord Malfoy}, he’s been raised from birth to hate you and he’s been raised from birth to \emph{lie!}” Daphne’s gray-green eyes stared fiercely at her, demanding assent and understanding.

“He—” Hermione said falteringly. She remembered the rooftop, the awful jolt as she started to fall, Draco Malfoy’s hand grabbing hers and holding it so hard that she’d had bruises afterward. She’d had to tell him twice before he finally let her fall. “Maybe Draco Malfoy isn’t like them—”

Daphne’s whisper was almost a scream. “If he \emph{doesn’t} end up doing you ten times as hard as he just helped you, his \emph{life} is \emph{over}, do you understand? I mean Lucius Malfoy would \emph{literally} disinherit him! D’you know what the chance is that he’s \emph{not} up to something?”

“Tiny?” said Hermione in a small voice.

“\emph{Zero!}” hissed Daphne. “I mean \emph{none!} I mean \emph{less} than zero! I mean the chance is so small that you couldn’t find it with three Magnifying Charms and a Point-Me spell and—and—and an ancient map and a centaur prophet! Everyone in Slytherin knows he’s plotting to do something to you and doesn’t want to be suspected, I heard someone say he was seen pointing his wand at you just before you tripped—don’t you \emph{see?} \emph{This is all part of Malfoy’s plan!}”
\sbreak
Draco sat eating his steak with roasted cauliflower florets and Ashwinder sauce (it wasn’t made from real Ashwinder eggs, it just tasted like fire), trying not to laugh and trying not to cry.

He’d \emph{heard} about plausible deniability, but hadn’t realized how much it mattered until he found that Malfoys didn’t have any.

“You want to know my plot?” said Draco. “\emph{Here’s} my plot. I’m not going to do \emph{anything} and then the \emph{next} time people think I’m plotting something, they won’t be sure.”

“Huh...” said the fifth-year boy. “I don’t think I believe you, that doesn’t sound cunning enough to be really it—”

“That’s what he \emph{wants} you to think,” said the fifth-year girl.
\sbreak
“Albus,” Minerva said dangerously, “did you \emph{plan} all this?”
\sbreak
“Well, if I \emph{did} snap my fingers under the table, I wouldn’t just \emph{tell} you that—”
\sbreak
The Defense Professor’s quavering hand dropped his spoon into the soup again.
\sbreak
“What do you mean, \emph{set you up?}” said Millicent. The two of them were sitting cross-legged on Daphne’s bed, having come there straight from the Great Hall after lunch. “With my Seer’s eyes that stare through Time Itself, I saw you \emph{winning}.”

Daphne stared at Millicent, her own merely mortal eyes rather narrowed at the moment. “That boy was \emph{expecting} us.”

“Well, yeah!” said Millicent. “Everyone knows you’re hunting bullies!”

“Hannah got hit by a really painful hex,” Daphne said. “She had to visit a healer, Millicent! If we’re friends you should’ve \emph{warned} me!”

“Look, Daphne, I \emph{told} you—” The Slytherin girl paused, as if trying to remember something, and then said, “I mean, I told you, what I See \emph{has} to come to pass. If I try to change it, if \emph{anyone} tries to change it, really terrible, awful, no good, extremely bad things will happen. And then it’ll come to pass \emph{anyway}. If I See you getting beaten up, I \emph{can’t} tell you that, because then you’d try to \emph{not go}, and \emph{then} —” Millicent stopped.

“And then?” Daphne said skeptically. “I mean, what happens if we just don’t go?”

“I don’t \emph{know!}” said Millicent. “But it probably makes being eaten by Lethifolds look like a tea party!”

“Look, even I know that’s not how prophecies work,” Daphne said, then paused. “At least prophecies don’t work like that in plays...” Admittedly, there were all sorts of tragedies where trying to avoid a prophecy \emph{made} it happen, or where, on the other hand, trying to \emph{go along} with a prophecy was the only reason why it happened. But you \emph{could} make prophecies happen your own way if you were clever enough; or someone who loved you enough could take your place; or with enough effort it was possible to break a prophecy outright... Then again, in plays the Seers never remembered what they Saw, either...

Millicent must have seen Daphne’s hesitation, because the other girl started looking a little more confident. “Well,” Millicent said sharply, “this isn’t a play! Look, I’ll tell you if I See it being a hard battle or an easy one. But that’s \emph{all} I can do, you understand? And if I say ‘hard’ you \emph{can’t} not show up! Or—or—” Millicent’s eyes rolled back in her head, and she intoned hollowly, “\emph{Those who try to cheat their destinies will come to sad and gloomy ends—”}
\sbreak
Professor Sprout shook her head, her face looking tight.

“But—” said Susan. “But you helped \emph{Harry Potter} that one time—”

“And it was made \emph{quite clear} to me,” Professor Sprout said in a voice that sounded like someone was using a Shrinking Charm to squeeze her throat, “that it was Professor Snape’s job, and not mine, to keep order in Slytherin House—Miss Bones, \emph{please}, you don’t have to \emph{do} this if—”

“Yes, I \emph{do} have to,” Susan said unhappily. “I’m a Hufflepuff, we have to be loyal.”
\sbreak
“A mysterious parchment under your pillow?” said Harry Potter, looking up from where he was sitting, in the Quieted nook where they were studying. Then the boy’s green eyes narrowed. “It wasn’t from Santa Claus, was it?”

Pause.

“Okay,” said Hermione. “I’m \emph{not} going to ask, and you’re \emph{not} going to tell me, and we’re \emph{both} going to pretend you never said that and I don’t know anything about it—”
\sbreak
Susan approached the table as soon as the older girl was alone, glancing around the Hufflepuff common room to make sure nobody was watching (the way Auntie had taught her to do it, so that it wouldn’t be obvious that she was looking).

“Hey, Susie,” said the seventh-year Hufflepuff. “Do you already need more—”

“Can I please talk to you privately for a bit?” Susan said.
\sbreak
Jaime Astorga, seventh-year of Slytherin, and until recently considered a promising upstart on the youth dueling circuit, stood ramrod straight in Professor Snape’s office, with his teeth clenched tight and sweat trickling down his spine.

“I distinctly recall,” said the Head of his House in a sardonic drawl, “that I warned you, and a number of others this very morning, that there were certain first-year girls who might prove annoying, if a fighter were \emph{incautious} and allowed himself to be \emph{taken by surprise}.”

Professor Snape stalked in a slow circle around him.

“I—” said Jaime, as more sweat beaded on his forehead. He knew how ridiculous it sounded, how much of a pathetic excuse. “Sir, they shouldn’t have been able to—” One first-year-girl shouldn’t have been able to break his \emph{Protego}, no matter what sort of ancient Charm she used—Greengrass must have had \emph{help}—

But it was very clear that his Head of House wouldn’t believe that.

“Oh, I quite agree,” murmured Snape in a low tone, instinct with menace. “They shouldn’t have. I begin to wonder if Mr.~Malfoy, whatever his plotting, has a point, Astorga. It cannot be good for the repute of Slytherin’s House if our fighters, rather than demonstrating their strength, lose to little girls!” Snape’s voice had risen. “It is well that you had the good taste to be defeated by a little girl who is a fellow Slytherin of a Noble House, Astorga, or I would deduct points from you myself!”

Jaime Astorga’s fists clenched at his side, but he couldn’t think of a thing to say.

It was some time before Jaime Astorga was allowed to leave the presence of his Head of House.

And afterward, only the walls, the floor, and the ceiling saw Severus Snape’s smile.
\sbreak
That evening Draco was visited by his father’s owl, Tanaxu, who wasn’t green but only because there weren’t such things as green owls. The best Father had been able to find was an owl of the purest silver feathers, with great luminous green eyes, and a beak as sharp and cruel as any snake’s fang. The parchment wrapped around Tanaxu’s leg was short and to the point:

\emph{What are you doing, my son?}

The parchment that Draco sent back was equally short, and it said,

\emph{I am trying to stop harm done to Slytherin’s reputation, father.}

In as much time as it took for an owl to fly from Hogwarts to Malfoy Manor and back again, the family owl bore another message to Draco, and this one said only:

\emph{What are you really doing?}

Draco stared at the parchment he’d unwrapped from the owl’s leg. His hands trembled, as he held up the parchment to the light of his fireplace. Five words, carved in black ink, shouldn’t have been scarier than death.

There wasn’t very much time to think. Father knew exactly how long it took for a message to go from Malfoy Manor to Hogwarts and back again; he would know if Draco delayed to compose a careful lie.

But Draco still waited until his hand stopped trembling, before he wrote his reply, the only answer he’d thought of that Father might accept.

\emph{I am preparing for the next war.}

Draco wrapped that parchment around the owl’s leg and tied it, and then sent Tanaxu winging out from his room, through the halls of Hogwarts, into the night.

He waited, but no reply came.


