\chapter{Machiavellian Intelligence Hypothesis}

\subsection{Act 3:}

\lettrine{D}{raco} waited in a small windowed alcove he’d found near the Great Hall, stomach churning.

There would be a price, and it would not be small. Draco had known that as soon as he’d woken up and realized that he didn’t dare enter the Great Hall for breakfast because he might see Harry Potter there and Draco didn’t know what would happen after that.

Footsteps approached.

“Here ya go,” said Vincent’s voice. “Now da boss ain’t in a good mood today, so ya’d better watch your step.”

Draco was going to skin that idiot alive and send back the flayed body with a request for a more intelligent servant, like a dead gerbil.

One set of footsteps went off, and the other set of footsteps came closer.

The churning in Draco’s stomach got worse.

Harry Potter came into sight. His face was carefully neutral, but his blue-trimmed robes looked oddly askew, as if they hadn’t been put on quite right—

“\emph{Your hand,}” Draco said without thinking about it at all.

Harry raised his left arm, as though to look at it himself.

The hand dangled limply from it, like something dead.

“Madam Pomfrey said it’s not permanent,” Harry said quietly. “She said it should mostly recover by the time classes start tomorrow.”

For a single instant the news came as a relief.

And then Draco realized.

“You went to Madam Pomfrey,” whispered Draco.

“Of course I did,” said Harry Potter, as though stating the obvious. “My hand wasn’t working.”

It was slowly dawning on Draco what an \emph{absolute} fool he’d been, far worse than the older Slytherins he’d chewed out.

He’d just taken for granted that no one would go to the authorities when a Malfoy did something to them. That no one would want Lucius Malfoy’s eye on them, ever.

But Harry Potter wasn’t a frightened little Hufflepuff trying to stay out of the game. He was already playing it, and Father’s eye was already on him.

“What else did Madam Pomfrey say?” said Draco, his heart in his throat.

“Professor Flitwick said that the spell cast on my hand had been a Dark torture hex and extremely serious business, and that refusing to say who did it was absolutely unacceptable.”

There was a long pause.

“And then?” Draco said in a shaking voice.

Harry Potter smiled slightly. “I apologized deeply, which made Professor Flitwick look \emph{very} stern, and then I told Professor Flitwick that the whole thing was, indeed, extremely serious, secret, \emph{delicate} business, and that I’d already informed the Headmaster about the project.”

Draco gasped. “No! Flitwick isn’t going to just accept that! He’ll check with Dumbledore!”

“Indeed,” said Harry Potter. “I was promptly hauled off to the Headmaster’s office.”

Draco was trembling now. If Dumbledore brought Harry Potter before the Wizengamot, willingly or otherwise, and had the Boy-Who-Lived testify under Veritaserum that Draco had tortured him...\ too many people loved Harry Potter, Father could \emph{lose} that vote...

Father might be able to convince Dumbledore not to do that, but it would \emph{cost.} Cost terribly. The game had rules now, you couldn’t just threaten someone at random any more. But Draco had walked into Dumbledore’s hands of his own free will. And Draco was a very valuable hostage.

Though since Draco couldn’t be a Death Eater now, he wasn’t as valuable as Father thought.

The thought tore at his heart like a Cutting Charm.

“Then what?” whispered Draco.

“Dumbledore deduced immediately that it was you. He knew we’d been associating.”

The worst possible scenario. If Dumbledore hadn’t guessed who did it, he might not have risked using Legilimency just to find out...\ but if Dumbledore \emph{knew...}

“And?” Draco forced out the word.

“We had a little chat.”

“And?”

Harry Potter grinned. “And I explained that it would be in his best interest not to do anything.”

Draco’s mind ran into a brick wall and splattered. He just stared at Harry Potter with his mouth hanging slack like a fool.

It took that long for Draco to remember.

Harry knew Dumbledore’s mysterious secret, the one Snape used as his hold.

Draco could just see it now. Dumbledore looking all stern, concealing his eagerness as he explained to Harry what a terribly serious matter this was.

And Harry politely telling Dumbledore to keep his mouth shut if he knew what was good for him.

Father had warned Draco against people like this, people who could ruin you and still be so likable that it was hard to hate them properly.

“After which,” Harry said, “the Headmaster told Professor Flitwick that this was, indeed, a secret and delicate matter of which he had already been informed, and that he did not think pressing it at this time would help me or anyone. Professor Flitwick started to say something about the Headmaster’s usual plotting going much too far, and I had to interrupt at that point and explain that it had been my \emph{own} idea and not anything the Headmaster forced me into, so Professor Flitwick spun around and started lecturing \emph{me}, and the Headmaster interrupted \emph{him} and said that as the Boy-Who-Lived I was doomed to have weird and dangerous adventures so I was safer if I got into them on purpose instead of waiting for them to happen by accident, and that was when Professor Flitwick threw up his little hands and started shrieking in a high-pitched voice at \emph{both} of us about how he didn’t care what we were cooking up together, but this wasn’t ever to happen again for as long as I was in Ravenclaw House or he would have me thrown out and I could go to Gryffindor which was where all this \emph{Dumbledoring} belonged—”

Harry was making it \emph{very} hard for Draco to hate him.

“Anyway,” Harry said, “I didn’t want to be thrown out of Ravenclaw, so I promised Professor Flitwick that nothing like this would happen again, and if it did, I would just tell him who did it.”

Harry’s eyes should have been cold. They weren’t. The voice should have made it a deadly threat. It wasn’t.

And Draco saw the question that should have been obvious, and it killed the mood in an instant.

“Why...\ didn’t you?”

Harry walked over to the window, into the small beam of sunlight shining into the alcove, and turned his head outward, toward the green grounds of Hogwarts. The brightness shone on him, on his robes, on his face.

“Why didn’t I?” Harry said. His voice caught. “I guess because I just couldn’t get angry at you. I knew I’d hurt you first. I won’t even call it fair, because what I did to you was worse than what you did to me.”

It was like running into another brick wall. Harry could have been speaking archaic Greek for all Draco understood him then.

Draco’s mind scrabbled for patterns and came up flat blank. The statement was a concession that hadn’t been in Harry’s best interests. It wasn’t even what Harry should say to make Draco a more loyal servant, now that Harry held power over him. For that Harry should be emphasizing how kindly he’d been, not how much he’d hurt Draco.

“Even so,” Harry said, and now his voice was lower, almost a whisper, “please don’t do that again, Draco. It hurt, and I’m not sure I could forgive you a second time. I’m not sure I’d be able to want to.”

Draco just didn’t get it.

Was Harry trying to be \emph{friends} with him?

There was no way Harry Potter could be dumb enough to believe that was still possible after what he’d done.

You could be someone’s friend and ally, like Draco had tried to do with Harry, or you could destroy their life and leave them no other options. Not both.

But then Draco didn’t understand what else Harry \emph{could} be trying.

And a strange thought came to Draco then, something Harry had kept talking about yesterday.

And the thought was: \emph{Test it.}

\emph{You’re awakened as a scientist now,} Harry had said, \emph{and even if you never learn to use your power, you’ll always, be looking, for ways, to test, your beliefs...} Those ominous words, spoken in gasps of agony, had kept running through Draco’s mind.

If Harry \emph{was} pretending to be the repentant friend who had accidentally hurt someone...

“You \emph{planned} what you did to me!” Draco said, managing to put a note of accusation in his voice. “You didn’t do it because you got angry, you did it because you \emph{wanted} to!”

\emph{Fool,} Harry Potter would say, \emph{of course I planned it, and now you’re mine—}

Harry turned back toward Draco. “What happened yesterday \emph{wasn’t} the plan,” Harry said, his voice seeming stuck in his throat. “The \emph{plan} was that I would teach you why you were always better off knowing the truth, and then we would try together to discover the truth about blood, and whatever the answer was we would accept it. Yesterday I...\ rushed things.”

“Always better off knowing the truth,” Draco said coldly. “Like you did me a \emph{favor.}”

Harry nodded, blowing Draco’s mind completely, and said, “What if Lucius comes up with the same idea I did, that the problem is stronger wizards having fewer children? He might start a program to pay the strongest purebloods to have more children. In fact, if blood purism \emph{were} right, that’s just what Lucius \emph{should} be doing—addressing the problem on \emph{his} side, where he can make things happen right away. Right now, Draco, you’re the only friend Lucius has who would try to stop him from wasting the effort, because you’re the only one who knows the \emph{real} truth and can predict the real results.”

The thought came to Draco that Harry Potter had been raised in a place so strange that he was now effectively a magical creature rather than a wizard. Draco simply couldn’t guess what Harry would say or do next.

“\emph{Why?}” Draco said. Putting pain and betrayal into his voice wasn’t hard at all. “Why did you \emph{do} this to me? What \emph{was} your plan?”

“Well,” Harry said, “you’re Lucius’s heir, and believe it or not, Dumbledore thinks I belong to him. So we could grow up and fight their battles with each other. Or we could do something else.”

Slowly, Draco’s mind wrapped around this. “You want to provoke a fight to the finish between them, then seize power after they’re both exhausted.” Draco felt cold dread in his chest. He would \emph{have} to try and stop that no matter the cost to himself—

But Harry shook his head. “Stars above, \emph{no!}”

“No...?”

“You wouldn’t go along with that and neither would I,” said Harry. “This is \emph{our} world, we don’t want to break it. But imagine, say, Lucius thought the Conspiracy was your tool and you were on his side, Dumbledore thought the Conspiracy was my tool and I was on his side, Lucius thought that you’d turned me and Dumbledore believed the Conspiracy was mine, Dumbledore thought that I’d turned you and Lucius believed the Conspiracy was yours, and so they both helped us out but only in ways that the other one wouldn’t notice.”

Draco did not have to fake being speechless.

Father had once taken him to see a play called \emph{The Tragedy of Light}, about this \emph{incredibly} clever Slytherin named Light who’d set out to purify the world of evil using an ancient ring that could kill anyone whose name and face he knew, and who’d been opposed by another incredibly clever Slytherin, a villain named Lawliet, who’d worn a disguise to conceal his true face; and Draco had shouted and cheered at all the right parts, especially in the middle; and then the play had ended sadly and Draco had been hugely disappointed and Father had gently pointed out that the word ‘Tragedy’ was right there in the title.

Afterward, Father had asked Draco if he understood why they had gone to see this play.

Draco had said it was to teach him to be as cunning as Light and Lawliet when he grew up.

Father had said that Draco couldn’t possibly be more wrong, and pointed out that while Lawliet had cleverly concealed his face there had been no good reason for him to tell Light his \emph{name}. Father had then gone on to demolish almost every part of the play, while Draco listened with his eyes growing wider and wider. And Father had finished by saying that plays like this were \emph{always} unrealistic, because if the playwright had known what someone \emph{actually} as smart as Light would \emph{actually} do, the playwright would have tried to take over the world himself instead of just writing plays about it.

That was when Father had told Draco about the Rule of Three, which was that any plot which required more than three different things to happen would never work in real life.

Father had \emph{further} explained that since only a fool would attempt a plot that was \emph{as complicated as possible}, the real limit was two.

Draco couldn’t even find words to describe the sheer gargantuan unworkability of Harry’s master plan.

But it was \emph{just} the sort of mistake you would make if you didn’t have any mentors and thought you were clever and had learned about plotting by watching plays.

“So,” said Harry, “what do you think of the plan?”

“It’s clever...” Draco said slowly. Shouting \emph{brilliant!} and gasping in awe would have looked too suspicious. “Harry, can I ask a question?”

“Sure,” said Harry.

“Why did you buy Granger an expensive pouch?”

“To show no hard feelings,” said Harry at once. “Though I expect she’ll also feel awkward if she refuses any small requests I make over the next couple of months.”

And that was when Draco realized that Harry actually \emph{was} trying to be his friend.

Harry’s move against Granger \emph{had} been smart, maybe even brilliant. Make your enemy not suspect you, \emph{and} put them into your debt in a friendly way so that you could maneuver them into position \emph{just by asking them}. Draco couldn’t have gotten away with that, his target would have been too suspicious, but the Boy-Who-Lived \emph{could.} So the first step of Harry’s plot was to give his enemy an expensive present, Draco wouldn’t have thought of that, but it could \emph{work...}

If you were Harry’s enemy, his plots might be hard to see through at first, they might even be stupid, but his reasoning would make \emph{sense} once you understood it, you would comprehend that he was trying to hurt you.

The way Harry was acting toward Draco right now did \emph{not} make sense.

Because if you were Harry’s \emph{friend,} then he tried to be friends with you in the alien, incomprehensible way he’d been raised by Muggles to do, even if it meant destroying your entire life.

The silence stretched.

“I know that I’ve abused our friendship terribly,” Harry said finally. “But please realize, Draco, that in the end, I just wanted the two of us to find the truth together. Is that something you can forgive?”

A fork with two paths, but with only one path easy to go back on later if Draco changed his mind...

“I guess I understand what you were trying to do,” Draco lied, “so yes.”

Harry’s eyes lit up. “I’m glad to hear that, Draco,” he said softly.

The two students stood in that alcove, Harry still dipped in the lone sunbeam, Draco in shadow.

And Draco realized with a note of horror and despair, that although it was a terrifying fate indeed to be Harry’s friend, Harry now had so many different avenues for threatening Draco that being his enemy would be even \emph{worse}.

Probably.

Maybe.

Well, he could always switch to being enemies later...

He was doomed.

“So,” Draco said. “Now what?”

“We study again next Saturday?”

“It better not go like the last one—”

“Don’t worry, it won’t,” said Harry. “A few more Saturdays like \emph{that} and you’d be ahead of \emph{me.}”

Harry laughed. Draco didn’t.

“Oh, and before you go,” Harry said, and grinned sheepishly. “I know this is a bad time, but I wanted to ask you for advice about something, actually.”

“Okay,” Draco said, still a bit distracted by that last statement.

Harry’s eyes grew intent. “Buying that pouch for Granger used up most of the gold I managed to steal from my Gringotts vault—”

What.

“—and McGonagall has the vault key, or Dumbledore does now, maybe. And I was just about to launch a plot that might take some money, so I was wondering if you know how I can get access—”

“I’ll loan you the money,” said Draco’s mouth in sheer existential reflex.

Harry looked taken aback, but in a pleased way. “Draco, you don’t have to—”

“How much?”

Harry named the amount and Draco couldn’t quite keep the shock from showing on his face. That was almost all the spending money Father had given Draco to last out the whole year, Draco would be left with just a few Galleons—

Then Draco mentally kicked himself. All he had to do was write Father and explain that the money was gone because he had managed to \emph{loan it to Harry Potter,} and Father would send him a special congratulatory note written in golden ink, a giant Chocolate Frog that would take two weeks to eat, and ten times as many Galleons just in case Harry Potter needed another loan.

“It’s way too much, isn’t it,” said Harry. “I’m sorry, I shouldn’t have asked—”

“Excuse me, I \emph{am} a Malfoy, you know,” said Draco. “I was just surprised you \emph{wanted} that much.”

“Don’t worry,” Harry Potter said cheerfully. “It’s nothing that threatens your family’s interests, just me being evil.”

Draco nodded. “No problem, then. You want to go get it right now?”

“Sure,” said Harry.

As they left the alcove and started heading toward the dungeons, Draco couldn’t help but ask, “So \emph{can} you tell me which plot this is for?”

“Rita Skeeter.”

Draco thought some very bad words to himself, but it was far too late to say no.
\sbreak
By the time they’d reached the dungeons, Draco had started pulling together his thoughts again.

He \emph{was} having trouble hating Harry Potter. Harry \emph{had} been trying to be friendly, he was just insane.

And that wasn’t going to stop Draco’s revenge or even slow it down.

“So,” Draco said, after looking around to make certain no one was nearby. Their voices would both be Blurred, of course, but it never hurt to be extra sure. “I’ve been thinking. When we bring new recruits into the Conspiracy, they’re going to have to \emph{think} we’re equals. Otherwise it would only take \emph{one} of them to blow the plot to Father. You already worked that out, right?”

“Naturally,” said Harry.

“\emph{Will} we be equals?” said Draco.

“I’m afraid not,” Harry said. It was clear that he was trying to sound gentle, and also clear that he was trying to suppress a good deal of condescension and not quite succeeding. “I’m sorry, Draco, but you don’t even know what the word \emph{Bayesian} in \emph{Bayesian Conspiracy} means right now. You’re going to have to study for months before we take anyone else in, just so you can put up a \emph{good front}.”

“Because I don’t know enough science,” Draco said, carefully keeping his voice neutral.

Harry shook his head at that. “The problem isn’t that you’re ignorant of specific science things like deoxyribose nucleic acid. \emph{That} wouldn’t stop you from being my equal. The problem is that you aren’t trained in the methods of rationality, the \emph{deeper} secret knowledge behind how all those discoveries got made in the first place. I’ll \emph{try} to teach you those, but they’re a lot harder to learn. Think of what we did yesterday, Draco. Yes, you did some of the work. But I was the only one in control. You answered some of the questions. I asked all of them. You helped push. I did the steering by myself. And without the methods of rationality, Draco, you can’t possibly steer the Conspiracy where it needs to go.”

“I see,” said Draco, his voice sounding disappointed.

Harry’s voice tried to gentle itself even more. “I’ll try to respect your expertise, Draco, about things like people stuff. But you need to respect my expertise too, and there’s just no \emph{way} you could be my equal when it comes to steering the Conspiracy. You’ve only been a scientist for \emph{one day}, you know \emph{one} secret about deoxyribose nucleic acid, and you aren’t trained in \emph{any} of the methods of rationality.”

“I understand,” said Draco.

And he did.

\emph{People stuff,} Harry had said. Seizing control of the Conspiracy probably wouldn’t even be difficult. And afterward, he would kill Harry Potter just to be sure—

The memory rose up in Draco of how sick inside it had felt last night, knowing Harry was screaming.

Draco thought some more bad words.

Fine. He \emph{wouldn’t} kill Harry. Harry had been raised by Muggles, it wasn’t his fault he was insane.

Instead, Harry would live on, just so that Draco could tell him that it had all been for Harry’s own good, really, he ought to be grateful—

And with a sudden twitch of surprised pleasure, Draco realized that it actually \emph{was} for Harry’s own good. If Harry tried to carry out his plan of playing Dumbledore and Father for fools, he would \emph{die.}

That made it \emph{perfect.}

Draco would take all of Harry’s dreams away from him, just as Harry had done to him.

Draco would tell Harry that it had been for his own good, and it would be absolutely true.

Draco would wield the Conspiracy and the power of science to purify the wizarding world, and Father would be as proud of him as if he’d been a Death Eater.

Harry Potter’s evil plots would be foiled, and the forces of right would prevail.

The perfect revenge.

Unless...

\emph{Just pretend to be pretending to be a scientist,} Harry had told him.

Draco didn’t have words to describe exactly what was wrong with Harry’s mind—

(since Draco had never heard the term \emph{depth of recursion})

—but he could guess what sort of plots it implied.

...unless all that was exactly what Harry \emph{wanted} Draco to do as part of some even \emph{larger} plot which Draco would play \emph{right into} by trying to foil this one, Harry might even \emph{know} that his plan was unworkable, it might have no purpose \emph{except} luring Draco to thwart it—

No. That way lay \emph{madness.} There \emph{had} to be a limit. The Dark Lord himself hadn’t been \emph{that} twisty. That sort of thing didn’t happen in real life, only in Father’s silly bedtime stories about foolish gargoyles who always ended up furthering the hero’s plans every time they tried to stop him.
\sbreak
And beside Draco, Harry walked along with a smile on his face, thinking about the evolutionary origins of human intelligence.

In the beginning, before people had quite understood how evolution worked, they’d gone around thinking crazy ideas like \emph{human intelligence evolved so that we could invent better tools.}

The reason why this was crazy was that only one person in the tribe had to invent a tool, and then everyone else would use it, and it would spread to other tribes, and still be used by their descendants a hundred years later. That was great from the perspective of scientific progress, but in evolutionary terms, it meant that the person who invented something didn’t have much of a fitness \emph{advantage}, didn’t have all that many \emph{more} children than everyone else. Only \emph{relative} fitness advantages could increase the relative frequency of a gene in the population, and drive some lonely mutation to the point where it was universal and everyone had it. And brilliant inventions just weren’t common enough to provide the sort of consistent selection pressure it took to promote a mutation. It was a natural guess, if you looked at humans with their guns and tanks and nuclear weapons and compared them to chimpanzees, that the intelligence was there to make the technology. A natural guess, but wrong.

Before people had quite understood how evolution worked, they’d gone around thinking crazy ideas like \emph{the climate changed, and tribes had to migrate, and people had to become smarter in order to solve all the novel problems.}

But human beings had four times the brain size of a chimpanzee. 20\% of a human’s metabolic energy went into feeding the brain. Humans were \emph{ridiculously} smarter than any other species. That sort of thing didn’t happen because the environment stepped up the difficulty of its problems a little. Then the organisms would just get a little smarter to solve them. Ending up with that gigantic outsized brain must have taken some sort of \emph{runaway} evolutionary process, something that would push and push without limits.

And today’s scientists had a pretty good guess at what that runaway evolutionary process had been.

Harry had once read a famous book called \emph{Chimpanzee Politics.} The book had described how an adult chimpanzee named Luit had confronted the aging alpha, Yeroen, with the help of a young, recently matured chimpanzee named Nikkie. Nikkie had not intervened directly in the fights between Luit and Yeroen, but had prevented Yeroen’s other supporters in the tribe from coming to his aid, distracting them whenever a confrontation developed between Luit and Yeroen. And in time Luit had won, and become the new alpha, with Nikkie as the second most powerful...

...though it hadn’t taken very long after that for Nikkie to form an alliance with the defeated Yeroen, overthrow Luit, and become the \emph{new} new alpha.

It really made you appreciate what millions of years of hominids trying to outwit \emph{each other}—an evolutionary arms race without limit—had led to in the way of increased mental capacity.

’Cause, y’know, a human would have totally seen that one coming.
\sbreak
And beside Harry, Draco walked along, suppressing his smile as he thought about his revenge.

Someday, maybe in years but someday, Harry Potter would learn just what it meant to underestimate a Malfoy.

Draco had awakened as a scientist in a single day. Harry had said that wasn’t supposed to happen for months.

But of course if you were a Malfoy, you would be a more powerful scientist than anyone who wasn’t.

So Draco would learn all of Harry Potter’s methods of rationality, and then when the time was ripe—


