\partchapter{Humanism}{IV}
\lettrine{T}{he} last tip of the Sun was sinking below the horizon, the red light fading from the treetops, only the blue sky illuminating the six people standing upon the winter-dried and snow-spotted grass, near a vacant cage.

Harry felt...\ well, \emph{normal} again. Sane-ish. The spell hadn’t undone the day and its damage, hadn’t made the injuries as if they had never been, but his hurts had been...\ bandaged, meliorated? It was hard to describe.

Dumbledore was also looking healthier, though not fully restored. The old wizard’s head turned for a moment, locked eyes with Professor Quirrell, then looked back to Harry. “Harry,” Dumbledore said, “are you about to collapse in exhaustion and possibly die?”

“No, strangely enough,” Harry said. “That took something out of me, but a lot less than I thought it would.” \emph{Or maybe it gave something back, as well as taking...} “Honestly, I expected my body to be hitting the ground with a thud about now.”

There was a distinct body-hitting-the-ground-with-a-thuddish sort of sound.

“Thank you for taking care of that, Quirinus,” said Dumbledore to Professor Quirrell, who was now standing above and behind the unconscious forms of the three Aurors. “I confess I am still feeling a bit peaky. Though I shall handle the Memory Charms myself.”

Professor Quirrell inclined his head, and then looked at Harry. “I will omit a good deal of useless incredulity,” said Professor Quirrell, “remarks to the effect that Merlin himself failed to do that, et cetera. Let us go straight to asking the important question. What the sweet slithering snakes was \emph{that?}”

“The Patronus Charm,” Harry said. “Version 2.0.”

“I rejoice to see that you are your usual self again,” said Dumbledore. “But you are not going \emph{anywhere}, young Ravenclaw, until you tell me what exactly was that warm and happy thought.”

“Hm...” said Harry. He tapped a contemplative finger on his cheek. “I wonder if I should?”

Professor Quirrell muffled a sudden grin.

“Please?” said the Headmaster.

Harry felt an impulse and decided to go with it. It was dangerous, but there might not ever be a better opportunity until the end of time.

“Three sodas,” Harry said to his pouch, then looked up at the Defense Professor and the Headmaster of Hogwarts. “Gentlemen,” Harry said, “I bought these sodas on my first visit to Platform Nine and Three-Quarters, on the day I entered into Hogwarts. I have been saving them for special occasions; there is a minor enchantment on them to ensure they are drunk at the right time. This is the last of my supply, but I do not think there will ever come a finer occasion. Shall we?”

Dumbledore took a soda can from Harry, and Harry tossed another to Professor Quirrell. The two older men each muttered identical charms over the can and frowned briefly at the result. Harry, for his part, simply popped the top and drank.

The Defense Professor and the Headmaster of Hogwarts politely followed suit.

Harry said, “I thought of my absolute rejection of death as the natural order.”

It might not be the right kind of warm feeling you needed to cast a Patronus Charm, but it was going into Harry’s Top 10 nonetheless.

The looks he got from the Defense Professor and the Headmaster briefly made Harry nervous, as the spilled Comed-Tea faded out of existence; but then the two of them each glanced at the other and both apparently decided that they couldn’t get away with doing anything really awful to Harry in the other’s presence, just as Harry had been counting on.

“Mr.~Potter,” said Professor Quirrell, “even \emph{I} know that is not how things are supposed to work.”

“Indeed,” said Dumbledore. “Explain.”

Harry opened his mouth, and then, as realization hit him, rapidly snapped his mouth shut again. Godric hadn’t told anyone, nor had Rowena if she’d known; there might have been any number of wizards who’d figured it out and kept their mouths shut. You couldn’t forget if you \emph{knew} that was what you were trying to do; once you realized \emph{how} it worked, the animal form of the Patronus Charm would never work for you again—and most wizards didn’t have the right upbringing to turn on Dementors and destroy them—

“Erm, sorry about this,” said Harry. “But I’ve just this instant realized that explaining would be an \emph{incredibly} bad idea until you work some things out on your own.”

“Is that the truth, Harry?” Dumbledore said slowly. “Or are you just pretending to be wise—”

“\emph{Headmaster!}” said Professor Quirrell, sounding genuinely shocked. “Mr.~Potter has told you that this spell is not spoken of with those who cannot cast it! You do not press a wizard on such matters!”

“If I told you—” Harry began.

“No,” Professor Quirrell said, sounding rather severe. “You don’t tell us \emph{why,} Mr.~Potter, you simply tell us that we are not to know. If you wish to devise a hint, you do so carefully, at leisure, not in the midst of conversation.”

Harry nodded.

“But,” said the Headmaster. “But, but what am I to tell the Ministry? You can’t just \emph{lose} a Dementor!”

“Tell them I ate it,” said Professor Quirrell, causing Harry to choke on the soda he had unthinkingly raised to his lips. “I don’t mind. Shall we head on back, Mr.~Potter?”

The two of them began to walk the dirt path back to Hogwarts, leaving behind Albus Dumbledore staring forlornly at the empty cage and the three sleeping Aurors awaiting their Memory Charms.
\replacement{\sbreak}{}

\subsection{Aftermath, Harry Potter and Professor Quirrell:}

They walked for a while before Professor Quirrell spoke, and all background noise dropped into silence when he did.

“You are exceptionally good at killing things, my student,” said Professor Quirrell.

“Thank you,” Harry said sincerely.

“I am not prying,” said Professor Quirrell, “but on the off-chance that it was \emph{only} the Headmaster who you did not trust with the secret...?”

Harry considered this. Professor Quirrell already couldn’t cast the animal Patronus Charm.

But you couldn’t untell a secret, and Harry was a fast enough learner to realize that he ought to at least \emph{think} for a while before unleashing this one upon the world.

Harry shook his head.

Professor Quirrell nodded acceptance.

“Out of curiosity, Professor Quirrell,” said Harry, “if your bringing the Dementor to Hogwarts had been part of an evil plot, what would have been its goal?”

“Assassinate Dumbledore while he was weakened,” Professor Quirrell said without even hesitating. “Hm. The Headmaster told you he was suspicious of me?”

Harry said nothing for a second while he tried to think of a reply, and then gave up when he realized he’d already answered.

“Interesting...” Professor Quirrell said. “Mr.~Potter, it is not out of the question that there \emph{was} a plot at work today. Your wand ending up that close to the Dementor’s cage \emph{could} have been an accident. Or one of the Aurors could have been Imperiused, Confunded, or Legilimized to exert an influence. Flitwick and myself should not be excluded as suspects, in your calculation. One notes that Professor Snape canceled all his classes today, and I suspect he is powerful enough to Disillusion himself; the Aurors cast detection charms early on, but they did not repeat them immediately before your turn. But most easily of all, Mr.~Potter, the deed could have been plotted by Dumbledore himself; and if he \emph{did}, why, he might also take steps in advance to cast your suspicion elsewhere.”

They walked on for a few steps.

“But why \emph{would} he?” Harry said.

The Defense Professor stayed quiet a moment, and then said, “Mr.~Potter, what steps have you taken to investigate the Headmaster’s character?”

“Not many,” said Harry. “Not enough.”

“Then I will observe,” said Professor Quirrell, “that you do not find out all there is to know about a man by asking only his friends.”

Now it was Harry’s turn to walk a few steps in silence on the slightly beaten dirt path that led back to Hogwarts. He’d really been supposed to know better than that already. Confirmation bias was the technical term; it meant, among other things, that when you chose your information sources, there was a notable tendency to choose information sources that agreed with your current opinions.

“Thank you,” Harry said. “Actually... I didn’t say it earlier, did I? Thank you for \emph{everything}. If another Dementor ever threatens you, or for that matter, slightly annoys you, just let me know and I’ll introduce it to Mister Glowy Person. I don’t like it when Dementors slightly annoy my friends.”

That got him an indecipherable glance from Professor Quirrell. “You destroyed the Dementor because it threatened me?”

“Erm,” Harry said, “I’d sort of decided on it before then, but yes, that would have been sufficient reason by itself.”

“I see,” said Professor Quirrell. “And what would you have done about the threat to me if your spell \emph{hadn’t} worked for destroying the Dementor?”

“Plan B,” said Harry. “Encase the Dementor in dense metal with a high melting point, probably tungsten, drop it into an active volcano, and hope it ends up inside Earth’s mantle. Ah, the whole planet is filled with molten lava under its surface—”

“Yes,” said Professor Quirrell. “I know.” The Defense Professor was wearing a very odd smile. “I really should have thought of that myself, all things considered. Tell me, Mr.~Potter, if you wanted to lose something where no one would ever find it again, where would you put it?”

Harry considered this question. “I suppose I shouldn’t ask \emph{what} you’ve found that needs losing—”

“Quite,” said Professor Quirrell, as Harry had expected; and then, “Perhaps you will be told when you are older,” which Harry hadn’t.

“Well,” said Harry, “besides trying to get it into the molten core of the planet, you could bury it in solid rock a kilometer underground in a randomly selected location—maybe teleport it in, if there’s some way to do that blindly, or drill a hole and repair the hole afterward; the important thing would be not to leave any traces leading there, so it’s just an anonymous cubic meter somewhere in the Earth’s crust. You could drop it into the Mariana Trench, that’s the deepest depth of ocean on the planet—or just pick some random other ocean trench, to make it less obvious. If you could make it bouyant and invisible, then you could throw it into the stratosphere. Or ideally you would launch it into space, with a cloak against detection, and a randomly fluctuating acceleration factor that would take it out of the Solar System. And afterward, of course, you’d Obliviate yourself, so even you didn’t know exactly where it was.”

The Defense Professor was laughing, and it sounded even odder than his smile.

“Professor Quirrell?” Harry said.

“All excellent suggestions,” said Professor Quirrell. “But tell me, Mr.~Potter, why those exact five?”

“Huh?” said Harry. “They just seemed like the obvious sorts of ideas.”

“Oh?” said Professor Quirrell. “But there is an interesting pattern to them, you see. One might say it sounds like something of a riddle. I must admit, Mr.~Potter, that although it has had its ups and downs, on the whole, this has been a surprisingly good day.”

And they continued walking down the path that led to the gates of Hogwarts, quite some distance apart; as Harry, without even thinking about it, automatically stayed far enough away from the Defense Professor not to trigger that sense of doom, which for some reason seemed unusually strong right now.
\replacement{\sbreak}{}

\subsection{Aftermath, Daphne Greengrass:}

Hermione had refused to answer any questions, and as soon as they’d passed the split leading to the Slytherin dungeons, Daphne and Tracey had peeled off at once, walking as quickly as they could. Rumor traveled fast in Hogwarts, so they’d have to go to the dungeons right away if they wanted to be the first to tell everyone the story.

“Now remember,” said Daphne, “don’t just blurt out about the kiss as soon as we walk in, okay? It works better if we tell the whole story in order.”

Tracey nodded excitedly.

And as soon as they burst into the Slytherin common room, Tracey Davis took a deep breath and shouted, “\emph{Everyone! Harry Potter couldn’t cast the Patronus Charm and the Dementor almost ate him and Professor Quirrell saved him but then Potter was all evil until Granger brought him back with a kiss! It’s true love for sure!}”

It was ordered storytelling of a sort, Daphne supposed.

The news failed to produce the expected reaction. Most of the girls glanced over and then stayed in their couches, or the boys simply kept reading in their chairs.

“Yes,” said Pansy sourly, from where she was sitting with Gregory’s feet in her lap, leaning back and reading what seemed to be a coloring book, “Millicent already told us.”

\emph{How—}

“Why didn’t \emph{you} kiss him first, Tracey?” said Flora and Hestia Carrow from their own chairs. “Now Potter’s going to marry a mudblood girl! \emph{You} could’ve been his true love and gotten into a rich Noble House and everything if you’d just kissed him first!”

Tracey’s face was a picture in stunned realization.

“\emph{What?}” shrieked Daphne. “Love does not work like that!”

“Of course it does,” stated Millicent from where she was practicing some sort of Charm while looking out a window at the swirling waters of the Hogwarts Lake. “First kiss gets the prince.”

“\emph{It wasn’t their first kiss!}” shouted Daphne. “Hermione was \emph{already} his true love! That’s why \emph{she} could bring him back!” Then Daphne realized what she’d just said and winced internally, but as the saying went, you had to fit the tongue to the ear.

“Whoa, whoa, whoa, what?” said Gregory, swinging his feet off Pansy’s lap. “What’s this? Miss Bulstrode didn’t tell that part.”

Everyone else was also looking at Daphne, now.

“Oh, yeah,” said Daphne, “Harry shoved her away and shouted, ‘I told you, no kissing!’ Then Harry screamed like he was dying and Fawkes started singing to him—I’m not sure which one of those happened first, actually—”

“That doesn’t sound like true love to \emph{me,}” said the Carrow twins. “That sounds like the \emph{wrong person} kissed him.”

“It was supposed to be \emph{me},” whispered Tracey. Her face was still stunned. “\emph{I} was supposed to be his true love. Harry Potter was \emph{my} general. I should’ve, I should’ve fought Granger for him—”

Daphne spun on Tracey, incensed. “\emph{You?} Take Harry away from Hermione?”

“Yeah!” said Tracey. “Me!”

“You’re nuts,” Daphne stated with conviction. “Even if you \emph{had} kissed him first, you know what that would make you? The sad little lovestruck girl who dies in the hero’s arms at the end of Act Two.”

“\emph{You take that back!}” shouted Tracey.

Meanwhile, Gregory had crossed the room to where Vincent was doing his homework. “Mr.~Crabbe,” Gregory said in a low voice, “I think Mr.~Malfoy needs to know about this.”
\replacement{\sbreak}{}

\subsection{Aftermath, Hermione Granger:}

Hermione stared at the wax-sealed paper, on the surface of which was inscribed simply the number \emph{42.}

\emph{I figured out why we couldn’t cast the Patronus Charm, Hermione, it doesn’t have anything to do with us not being happy enough. But I can’t tell you. I couldn’t even tell the Headmaster. It needs to be even more secret than partial Transfiguration, for now, anyway. But if you ever need to fight Dementors, the secret is written here, cryptically, so that if someone doesn’t know it’s about Dementors and the Patronus Charm, they won’t know what it means...}

She’d told Harry about seeing him dying, her parents dying, all her friends dying, everyone dying. She hadn’t told him about her terror of dying alone, somehow that was still too painful.

Harry had told her about remembering his parents dying, and that he’d thought it was funny.

\emph{There’s no light in the place the Dementor takes you, Hermione. No warmth. No caring. It’s somewhere that you can’t even understand happiness. There’s pain, and fear, and those can still drive you. You can hate, and take pleasure in destroying what you hate. You can laugh, when you see other people hurting. But you can’t ever be happy, you can’t even remember what it is that isn’t there anymore... I don’t think there’s any way I can ever explain just what you saved me from. I’m usually ashamed to put people to trouble, I usually can’t stand it when people make sacrifices for me, but this one time I’ll say that no matter what it ends up costing you to have kissed me, don’t ever doubt for a second that it was the right thing to do.}

Hermione hadn’t realized just how \emph{little} the Dementor had touched her, how small and shallow had been the darkness into which it had taken her.

She’d seen everyone dying, and that had still been able to hurt.

Hermione put the paper back into her pouch, like a good girl ought to.

She’d really wanted to read it, though.

She was frightened of Dementors.
\replacement{\sbreak}{}

\subsection{Aftermath, Minerva McGonagall:}

She felt frozen; she shouldn’t have been so shocked, she shouldn’t have found Harry so hard to face, but after what he’d been through... She had searched the young boy in front of her for any signs of Dementation, and failed to find them. But something about the calm with which he had asked such a foreboding question seemed deeply worrying. “Mr.~Potter, I can’t possibly speak of such matters without the Headmaster’s permission!”

The boy in her office took this in without changing expression. “I would prefer not to disturb the Headmaster over this matter,” Harry said calmly. “I \emph{insist} on not disturbing him, in fact, and you did promise that our conversation would be kept private. So let me put it this way. I know that there was, in fact, a prophecy. I know that you are the one who originally heard it from Professor Trelawney. I know that the prophecy identified the child of James and Lily as someone dangerous to the Dark Lord. And I know who I am, indeed everyone now knows who I am, so you are revealing nothing new or dangerous, if you tell me only this: What was the \emph{exact wording} which identified \emph{me,} the child of James and Lily?”

Trelawney’s hollow voice echoed in her mind—

\headline{Born to those who have thrice defied him,\\Born as the seventh month dies...}

“Harry,” said Professor McGonagall, “I can’t possibly tell you that without permission!” It chilled her to the bone that Harry knew so much already, she couldn’t imagine how Harry had learned—

The boy looked at her with strange, sorrowful eyes. “Can you not sneeze without the Headmaster’s permission, Professor McGonagall? For I do promise to you that I have good reason to ask, and good reason to keep the question private.”

“Please don’t, Harry,” she whispered.

“All right,” Harry said. “One simple question. Please. Was the Potter family mentioned by \emph{name?} Does the prophecy literally say ‘Potter’?”

She stared at Harry for a while. She couldn’t have said why or where she got the sense that this was a critical point, that she could not lightly refuse the request, nor lightly accede to it—

“No,” she finally said. “Please, Harry, don’t ask any more.”

The boy smiled, a little sadly it seemed, and said, “Thank you, Minerva. You are a good woman and true.”

And while her mouth was still open in utter shock, Harry Potter got up and left the office; and only then did she realize that Harry had taken her refusal as an answer, and the true answer at that—

Harry closed the door behind himself.

The logic had presented itself with a strange diamondlike clarity. Harry couldn’t have said if it had come to him during Fawkes’s singing, or maybe even before.

Lord Voldemort had killed James Potter. He had preferred to spare Lily Potter’s life. He had continued his attack, therefore, with the sole purpose of killing their infant child.

Dark Lords were not usually scared of infant children.

So there was a prophecy about Harry Potter being dangerous to Lord Voldemort, and Lord Voldemort had known that prophecy.

\emph{“I give you this rare chance to flee. But I will not trouble myself to subdue you, and your death here will not save your child. Step aside, foolish woman, if you have any sense in you at all!”}

Had it been a whim, to give her that chance? But then Lord Voldemort would not have tried to persuade her. Had the prophecy warned Lord Voldemort against killing Lily Potter? Then Lord Voldemort \emph{would} have troubled himself to subdue her. Lord Voldemort had been \emph{mildly} inclined not to kill Lily Potter. The preference had been stronger than a whim, but not as strong as a warning.

So suppose that someone whom Lord Voldemort considered a lesser ally or servant, useful but not indispensable, had begged the Dark Lord to spare Lily’s life. Lily’s, but not James’s.

This person had known that Lord Voldemort would attack the house of the Potters. Had known both the prophecy, and the fact that the Dark Lord knew it. Otherwise he would not have begged Lily’s life.

According to Professor McGonagall, besides herself, the other two who knew of the prophecy were Albus Dumbledore and Severus Snape.

Severus Snape, who had loved Lily before she was Lily Potter, and hated James.

Severus, then, had learned of the prophecy, and told it to the Dark Lord. Which he had done because the prophecy had not described the Potters by name. It had been a riddle, and Severus had solved that riddle only too late.

But if Severus had been the \emph{first} to hear the prophecy, and disposed to tell it to the Dark Lord, then why would he also have told Dumbledore or Professor McGonagall?

Therefore Dumblefore or Professor McGonagall had heard it first.

The Headmaster of Hogwarts had no obvious reason to tell the Transfiguration Professor about an extremely sensitive and crucial prophecy. But the Transfiguration Professor had every reason to tell the Headmaster.

It seemed likely, then, that Professor McGonagall had been the first to hear it.

The prior probabilities said that it had been Professor Trelawney, Hogwarts’s resident seer. Seers were rare, so if you counted up most of the seconds Professor McGonagall had spent in the presence of a seer over the course of her lifetime, most of those seer-seconds would be Trelawney-seconds.

Professor McGonagall had told Dumbledore, and would have told no one else about the prophecy without permission.

Therefore, it was Albus Dumbledore who had arranged for Severus Snape to somehow learn of the prophecy. And Dumbledore himself had solved the riddle successfully, or he would not have selected \emph{Severus}, who had once loved Lily, as the intermediary.

Dumbledore had deliberately arranged for Lord Voldemort to hear about the prophecy, in hopes of luring him to his death. Perhaps Dumbledore had arranged for Severus to learn only \emph{some} of the prophecy, or there were other prophecies of which Severus had remained innocent...\ somehow Dumbledore had known that an \emph{immediate} attack on the Potters would still lead to Lord Voldemort’s \emph{immediate} defeat, although Lord Voldemort himself had not believed this. Or maybe that had just been a lucky stroke of Dumbledore’s insanity, his taste for bizarre plots...

Severus had ended up serving Dumbledore afterward; perhaps the Death Eaters would not look kindly on Severus if Dumbledore revealed his role in their defeat.

Dumbledore had tried to arrange for Harry’s mother to be spared. But that part of his plot had failed. And he had knowingly condemned James Potter to his death.

Dumbledore was responsible for the deaths of Harry’s parents. \emph{If} the whole chain of logic was correct. Harry could not, in justice, say that successfully ending the Wizarding War did not count as extenuating circumstances. But somehow this still... \emph{bothered him a great deal.}

And it was time and past time to ask Draco Malfoy what the \emph{other} side of that war had to say about the character of Albus Percival Wulfric Brian Dumbledore.

