\chapter{Asking the Wrong~Questions}

\epigraph{“That’s one of the most obvious riddles I’ve ever heard.”}{}

\lettrine{A}{s} soon as Harry opened his eyes in the Ravenclaw first-year boys’ dormitory, on the morning of his first full day at Hogwarts, he knew something was wrong.

It was quiet.

\emph{Too} quiet.

Oh, right... There was a Quietus Charm on his bed’s headboard, controlled by a small slider bar, which was the only reason it was ever possible for anyone to go to sleep in Ravenclaw.

Harry sat up and looked around, expecting to see others rising for the day—

The dorm, empty.

The beds, rumpled and unmade.

The sun, coming in at a rather high angle.

His Quieter turned all the way up to maximum.

And his mechanical alarm clock was still running, but the alarm was turned off.

He’d been allowed to sleep until 9:52\AM, apparently. Despite his best efforts to synchronize his 26-hour sleep cycle to his arrival at Hogwarts, he hadn’t gotten to sleep last night until around 1\AM. He’d been planning to wake up at 7:00\AM with the other students, he could stand being a little sleep-deprived his first day so long as he got some sort of magical fix before tomorrow. But now he’d missed breakfast. And his very first class at Hogwarts, in Herbology, had started one hour and twenty-two minutes ago.

The anger was slowly, slowly wakening in him. Oh, what a nice little prank. Turn off his alarm. Turn up the Quieter. And let Mr.~Bigshot Harry Potter miss his first class, and be blamed for being a heavy sleeper.

When Harry found out who’d done this...

No, this could only have been done with the cooperation of all twelve other boys in the Ravenclaw dorm. All of them would have seen his sleeping form. All of them had let him sleep through breakfast.

The anger drained away, replaced by confusion and a horribly wounded feeling. They’d \emph{liked} him. He’d thought. Last night, he’d thought they liked him. \emph{Why...}

As Harry stepped out of the bed, he saw a piece of paper attached to his headboard, facing outward.

The paper said,

\begin{writtenNote}
\letterAddress{My fellow Ravenclaws,}

It’s been an extra long day. Please let me sleep in and don’t worry about my missing breakfast. I haven’t forgotten about my first class.

\letterClosing[Yours,]{Harry Potter.}
\end{writtenNote}

And Harry stood there, frozen, ice water beginning to trickle through his veins.

The paper was in his own handwriting, in his own mechanical pencil.

And he didn’t remember writing it.

And... Harry squinted at the piece of paper. And unless he was imagining it, the words “I haven’t forgotten” were written in a different style, as if he was trying to tell himself something...?

Had he \emph{known} he was going to be Obliviated? Had he stayed up late, committed some sort of crime or covert activity, and then...\ but he didn’t \emph{know} the Obliviate spell...\ had someone else...\ what...

A thought occurred to Harry. If he \emph{had} known he was going to be Obliviated...

Still in his pajamas, Harry ran around his bed to his trunk, pressed his thumb against the lock, pulled out his pouch, stuck in his hand and said “Note to myself.”

And another piece of paper popped into his hand.

Harry took it out, staring at it. It too was in his own handwriting.

The note said:

\begin{writtenNote}
\letterAddress{Dear Me,}

Please play the game. You can only play the game once in a lifetime. This is an irreplaceable opportunity.

Recognition code 927, I am a potato.

\letterClosing[Yours,]{You.}
\end{writtenNote}

Harry nodded slowly. “Recognition code 927, I am a potato” was indeed the message he had worked out in advance—some years earlier, while watching \abbrev{tv}—that only he would know. If he had to identify a duplicate of himself as being really \emph{him,} or something. Just in case. Be~Prepared.

Harry couldn’t \emph{trust} the message, there might be other spells involved. But it ruled out any simple prank. He had definitely written this and he definitely didn’t remember writing it.

Staring at the paper, Harry became aware of ink showing through from the other side.

He flipped it over.

The reverse side read:

\begin{writtenNote}\centering
\textsc{Instructions for The Game:}

you do not know the rules of the game\\you do not know the stakes of the game\\you do not know the objective of the game\\you do not know who controls the game\\you do not know how to end the game

You start with 100 points.\\Begin.
\end{writtenNote}

Harry stared at the “instructions”. This side wasn’t handwritten; the writing was perfectly regular, hence artificial. It looked as if it had been inscribed by a Quotes Quill, such as the one he’d bought to take dictation.

He had \emph{absolutely no clue} what was going on.

Well...\ step one was to get dressed and eat. Maybe reverse the order of that. His stomach felt rather empty.

He’d missed breakfast, of course, but he was Prepared for that eventuality, having visualized it in advance. Harry put his hand into his pouch and said “Snack bars”, expecting to get the box of meal bars he’d bought before departing for Hogwarts.

What popped up did not feel like a box of meal bars.

When Harry brought his hand into his field of vision he saw two tiny candy bars—not nearly enough for a meal—attached to a note, and the note was inscribed in the same writing as the game instructions.

The note said:
\begin{align*}
\hbox{\scshape Attempt failed: }&\hbox{\scshape −1 point}\\
\hbox{\scshape Current points: }&\hbox{99}\\
\hbox{\scshape Physical state: }&\hbox{\scshape Still hungry}\\
\hbox{\scshape Mental state: }&\hbox{\scshape Confused}
\end{align*}

“Gleehhhhh” Harry’s mouth said without any sort of conscious intervention or decision on his part.

He stood there for around a minute.

One minute later, it \emph{still} didn’t make any sense and he \emph{still} had absolutely no idea what was going on and his brain hadn’t even \emph{begun} to grasp at any \emph{hypotheses} like his mental hands were encased in rubber balls and couldn’t pick anything up.

His stomach, which had its own priorities, suggested a possible experimental probe.

“Ah...” Harry said to the empty room. “I don’t suppose I could spend a point and get my box of meal bars back?”

There was only silence.

Harry put his hand into the pouch and said “Box of meal bars.”

A box that felt like the right shape popped up into his hand...\ but it was too light, and it was open, and it was empty, and the note attached to it said:
\begin{align*}\hbox{\scshape Points spent: }&\hbox{1}\\
\hbox{\scshape Current points: }&\hbox{98}\\
\hbox{\scshape You have gained: }&\hbox{\scshape A box of Meal Bars}
\end{align*}

“I’d like to spend one point and get the \emph{actual meal bars} back,” said Harry.

Again, silence.

Harry put his hand into the pouch and said “meal bars”.

Nothing came up.

Harry shrugged despairingly and went over to the cabinet he’d been given near his bed, to get his wizard’s robes for the day.

On the floor of the cabinet, under his robes, were the meal bars, and a note:
\begin{align*}
\hbox{\scshape Points spent: }&\hbox{1}\\
\hbox{\scshape Current points: }&\hbox{97}\\
\hbox{\scshape You have gained: }&\hbox{\scshape 6 meal bars}\\
\hbox{\scshape You are still wearing: }&\hbox{\scshape Pajamas}\\
\intertext{\scshape \centering Do not eat while you are wearing your pajamas\\
You will get a Pajama Penalty}
\end{align*}

\emph{And now I know that whoever controls the game is insane.}

“My guess is that the game is controlled by Dumbledore,” Harry said out loud. Maybe \emph{this} time he could set a new land speed record for being quick on the uptake.

Silence.

But Harry was starting to pick up the pattern; the note would be in the next place he looked. So Harry looked under his bed.
\begin{align*}\intertext{\scshape \centering
Ha! Ha ha ha ha ha!\\Ha ha ha ha ha ha!\\Ha! Ha! Ha! Ha! Ha! Ha!\\Dumbledore does not control the game\\Bad guess\\Very bad guess\\−20 points\\And you are still wearing pajamas\\it is your fourth move\\and you are still wearing pajamas}
\hbox{\scshape Pajama penalty: }&\hbox{\scshape −2 points}\\
\hbox{\scshape Current points: }&\hbox{75}
\end{align*}

Welp, Harry was screwed. It was only his first day at school and once you ruled out Dumbledore, he didn’t know the name of anyone else here who was this crazy.

His body more or less on autopilot, Harry gathered up a set of robes and underwear, pulled out the cavern level of his trunk (he was a very private sort of person and someone might walk into the dorm), got dressed, and then went back upstairs to put away his pajamas.

Harry paused before pulling out the cabinet drawer that held his pajamas. If the pattern here held true...

“How can I earn more points?” Harry said out loud.

Then he pulled out the drawer.
\begin{align*}\intertext{\scshape \centering
Opportunities to do good are everywhere\\but darkness is where the light needs to be}
\hbox{\scshape Cost of question: }&\hbox{\scshape 1 point}\\
\hbox{\scshape Current points: }&\hbox{74}\\
\intertext{\scshape \centering Nice underwear\\Did your mother pick them out?}
\end{align*}

Harry crushed the note in his hand, face flaming scarlet. Draco’s curse came back to him. \emph{Son of a mudblood—}

At this point he knew better than to say it out loud. He would probably get a Profanity Penalty.

Harry girded himself with his mokeskin pouch and wand. He peeled off the wrapper of one his meal bars and threw it into the room’s rubbish bin, where it landed atop a mostly-uneaten Chocolate Frog, a crumpled envelope and some green and red wrapping paper. He put the other meal bars into his mokeskin pouch.

He looked around in a final, desperate, and ultimately futile search for clues.

And then Harry left the dorm, eating as he went, in search of the Slytherin dungeons. At least that was what he \emph{thought} the line was about.

Trying to navigate the halls of Hogwarts was like...\ probably \emph{not} quite as bad as wandering around inside an Escher painting, that was the sort of thing you said for rhetorical effect rather than for its being true.

A short time later, Harry was thinking that in fact an Escher painting would have both pluses and minuses compared to Hogwarts. Minuses: No consistent gravitational orientation. Pluses: At least the stairs wouldn’t move around \shout{while you were still on them.}

Harry had originally climbed four flights of stairs to get to his dorm. After clambering down no fewer than twelve flights of stairs without getting anywhere near the dungeons, Harry had concluded that (1) an Escher painting would be a \emph{cakewalk} by comparison, (2) he was somehow \emph{higher} in the castle than when he’d started, and (3) he was so \emph{thoroughly} lost that he wouldn’t have been surprised to look out of the next window and see two moons in the sky.

Backup plan A had been to stop and ask for directions, but there seemed to be an extreme lack of people wandering around, as if the beggars were all attending class the way they were supposed to or something.

Backup plan B...

“I’m lost,” Harry said out loud. “Can, um, the spirit of the Hogwarts castle help me or something?”

“I don’t think this castle has a spirit,” observed a wizened old lady in one of the paintings on the walls. “Life, perhaps, but not spirit.”

There was a brief pause.

“Are you—” Harry said, and then shut his mouth. On second thought, no he was \shout{not} going to ask the painting whether it was fully conscious in the sense of being aware of its own awareness.

“I’m Harry Potter,” said his mouth, more or less on automatic. Also more or less on automatic, Harry stuck out a hand toward the painting.

The woman in the painting looked down at Harry’s hand and raised her eyebrows.

Slowly, the hand dropped back to Harry’s side.

“Sorry,” Harry said, “I’m sort of new here.”

“So I perceive, young raven. Where are you trying to go?”

Harry hesitated. “I’m not really sure,” he said.

“Then perhaps you are already there.”

“Well, wherever I \emph{am} trying to go, I don’t think \emph{this} is it...” Harry shut his mouth, aware of just how much he was sounding like an idiot. “Let me start over. I’m playing this game only I don’t know what the rules are—” That didn’t really work either, did it. “Okay, third try. I’m looking for opportunities to do good so I can score points, and all I have is this cryptic hint about how darkness is where the light needs to be, so I was trying to go down but I seem to keep going up instead...”

The old lady in the painting was looking at him rather skeptically.

Harry sighed. “My life tends to get a bit peculiar.”

“Would it be fair to say that you don’t know where you’re trying to go or even why you’re trying to get there?”

“\emph{Entirely} fair.”

The old lady nodded. “I’m not sure that being lost in the castle is your most important problem, young man.”

“True, but unlike the more important problems, it’s a problem I can understand how to solve and \emph{wow} is this conversation turning into a metaphor for human existence, I didn’t even realize that was happening until just now.”

The lady eyed Harry appraisingly. “You \emph{are} a fine young raven, aren’t you? For a moment I was starting to wonder. Well then, as a general rule, if you keep on turning left, you’re bound to keep going down.”

That sounded strangely familiar but Harry couldn’t recall where he’d heard it before. “Um...\ you seem like a very intelligent person. Or a picture of a very intelligent person...\ anyway, have you heard of a mysterious game where you can only play once, and they won’t tell you the rules?”

“Life,” said the lady at once. “That’s one of the most obvious riddles I’ve ever heard.”

Harry blinked. “No,” he said slowly. “I mean I got an actual note and everything saying that I had to play the game but I wouldn’t be told the rules, and someone is leaving me little slips of paper telling me how many points I’ve lost for violating the rules, like a minus two point penalty for wearing pajamas. Do you know anyone here at Hogwarts who’s crazy enough and powerful enough to do something like that? Besides Dumbledore, I mean?”

The picture of a lady sighed. “I’m only a picture, young man. I remember Hogwarts as it was—not Hogwarts as it is. All I can tell you is that if this were a riddle, the answer would be that the game is life, and that while we do not make all the rules ourselves, the one who awards or takes points is always you. If it is not riddle but reality—then I do not know.”

Harry bowed very low to the picture. “Thank you, milady.”

The lady curtseyed to him. “I wish I could say that I’ll remember you with fondness,” she said, “but I probably won’t remember you at all. Farewell, Harry Potter.”

He bowed again in reply, and started to climb down the nearest flight of stairs.

Four left turns later he found himself staring down a corridor that ended, abruptly, in a tumbled mound of large rocks—as if there had been a cave-in, only the surrounding walls and ceiling were intact and made of quite regular castle stones.

“All right,” Harry said to the empty air, “I give up. I’m asking for another hint. How do I get to where I need to go?”

“A hint! A hint, you say?”

The excited voice came from a painting on the wall not far away, this one a portrait of a middle-aged man in the loudest pink robes that Harry had ever seen or even imagined. In the portrait he was wearing a droopy old pointed hat with a fish on it (not a drawing of a fish, mind, but a fish).

“Yes!” Harry said. “A hint! A hint, I say! Only not just \emph{any} hint, I’m looking for a \emph{specific} hint, it’s for a game I’m playing—”

“Yes, yes! A hint for the game! You’re Harry Potter, aren’t you? I’m Cornelion Flubberwalt! I was told by Erin the Consort who was told by Lord Weaselnose who was told by, I forget really. But it was a message for \emph{me} to give to you! For \emph{me!} No one’s cared about me in, I don’t know how long, maybe ever, I’ve been stuck down here in this bloody useless old corridor—a hint! I have your hint! It will only cost you three points! Do you want it?”

“Yes! I want it!” Harry was aware that he probably ought to keep his sarcasm under control but he just couldn’t seem to help himself.

“The darkness can be found between the green study rooms and McGonagall’s Transfiguration class! That’s the hint! And get a move on, you’re slower than a sack of snails! Minus ten points for being slow! Now you have 61 points! That was the rest of the message!”

“Thank you,” Harry said. He was really getting behind on the game here. “Um... I don’t suppose you know where the message \emph{originally} came from, do you?”

“It was spoken by a hollow voice that belled forth from a gap within the air itself, a gap that opened upon a fiery abyss! That’s what they told me!”

Harry was no longer sure, at this point, whether this was the sort of thing he ought to be skeptical about, or the sort of thing he should just take in stride. “And how can I find the line between the green study rooms and Transfiguration class?”

“Just spin back around and go left, right, down, down, right, left, right, up, and left again, you’ll be at the green study room and if you go in and walk straight out the opposite side you’ll be on a big curvy corridor that goes to an intersection and on the right side of that intersection will be a long straight hallway that goes to the Transfiguration classroom!” The figure of the middle-aged man paused. “At least that’s how it was when \emph{I} was in Hogwarts. This \emph{is} a Monday on an odd-numbered year, isn’t it?”

“Pencil and mechanical paper,” Harry said to his pouch. “Er, cancel that, paper and mechanical pencil.” He looked up. “Could you repeat that?”

After getting lost another two times, Harry felt that he was beginning to understand the basic rule for navigating the ever-changing maze that was Hogwarts, namely, \emph{ask a painting for directions}. If this reflected some sort of incredibly deep life lesson he couldn’t figure out what it was.

The green study room was a surprisingly pleasant space with sunlight streaming in from windows of green-stained glass that showed dragons in calm, pastoral scenes. It had chairs that looked extremely comfortable, and tables that seemed very well-suited to studying in the company of one to three friends.

Harry couldn’t \emph{actually} walk straight through and out the door on the other side. There were \emph{bookshelves} set into the wall, and he had to go over and read some of the titles, so as to not lose his claim to the Verres family name. But he did it quickly, mindful of the complaint about being slow, and then went out the other side.

He was walking down the “big curvy corridor” when he heard a young boy’s voice cry out.

At times like this, Harry had an excuse to sprint all-out with no regards for saving energy or doing proper warmup exercises or worrying about crashing into things, a sudden frantic flight that nearly came to an equally sudden halt as he almost ran over a group of six first-year Hufflepuffs...

...who were huddled together, looking rather scared and like they desperately wanted to do something but couldn’t figure out what, which probably had something to do with the group of five older Slytherins who seemed to be surrounding another young boy.

Harry was suddenly rather angry.

“\emph{Excuse me!}” shouted Harry at the top of his lungs.

It might not have been necessary. People were already looking at him. But it certainly served to stop all the action cold.

Harry walked past the cluster of Hufflepuffs toward the Slytherins.

They looked down at him with expressions that ranged from anger to amusement to delight.

Part of Harry’s brain was screaming in panic that these were much older and bigger boys who could stomp him flat.

Another part said dryly that anyone caught seriously stomping the Boy-Who-Lived was in for a whole \emph{world} of trouble, especially if they were a pack of older Slytherins and there were seven Hufflepuffs who saw it, and that the chance of them doing him any permanent damage in the presence of witnesses was nearly zero. The only real weapon the older boys had against him was his own fear, if he allowed that.

Then Harry saw that the boy they had trapped was Neville Longbottom.

Of course.

That settled it. Harry had decided to apologize humbly to Neville and that meant Neville was \emph{his}, how \emph{dare} they?

Harry reached out and grabbed Neville by the wrist and \emph{yanked} him out from between the Slytherins, the boy stumbling in shock as Harry pulled him out and in nearly the same motion pushed his own way through the same gap.

And Harry stood in the center of the Slytherins where Neville had stood, looking up at the much older, larger, and stronger boys.

“Hello,” Harry said. “I’m the Boy-Who-Lived.”

There was a rather awkward pause. No one seemed to know where the conversation was supposed to go from there.

Harry’s eyes dropped downward and saw some books and papers scattered around the floor. Oh, the old game where you let the boy try to pick up his books and then knock them out of his hand again. Harry couldn’t remember ever being the object of that game himself, but he had a good imagination and his imagination was making him furious. Well, once the larger situation was resolved it would be easy enough for Neville to come back and pick up his materials, provided that the Slytherins stayed too focused on him to think of doing anything to the books.

Unfortunately his straying eyes had been noted. “Ooh,” said the largest of the boys, “did ‘oo want the widdle books—”

“Shut up,” Harry said coldly. \emph{Keep them off balance. Don’t do what they expect. Don’t fall into a pattern that calls for them to bully you.} “Is this part of some incredibly clever plan that will gain you future advantage, or is it as pointless a disgrace to the name of Salazar Slytherin as it—”

The largest boy shoved Harry Potter hard, and he went sprawling out of the circle of Slytherins onto the hard stone floor of Hogwarts.

And the Slytherins laughed.

Harry rose up in what seemed to him like terribly slow motion. He didn’t know yet how to use his wand, but there was no reason to let that stop him, under the circumstances.

“I’d like to pay \emph{as many points as it takes} to get rid of this person,” Harry said, pointing with his finger to the largest Slytherin.

Then Harry lifted his other hand, said “Abracadabra,” and snapped his fingers.

At the word \emph{Abracadabra} two of the Hufflepuffs screamed, including Neville, three other Slytherins leaped desperately out of the way of Harry’s finger, and the largest Slytherin staggered back with an expression of shock, a sudden splash of red decorating his face and neck and chest.

Harry had \emph{not} been expecting \emph{that}.

Slowly, the largest Slytherin reached up to his head, and peeled off the pan of cherry pie that had just draped itself over him. The largest Slytherin held the pan in his hand for a moment, staring at it, then dropped it to the floor.

It probably wasn’t the best time in the world for one of the Hufflepuffs to start laughing, but that was exactly what one of the Hufflepuffs was doing.

Then Harry caught sight of the note on the bottom of the pan.

“Hold on,” Harry said, and darted forward to pick up the note. “This note’s for me, I think—”

“\emph{You,”} growled the largest Slytherin, “\emph{you, are, going, to—}”

“\emph{Look} at this!” shouted Harry, brandishing the note at the older Slytherin. “I mean, just \emph{look} at this! Can you believe I’m being charged 30 points for shipping and handling on one lousy pie? 30 points! I’m turning a loss on the deal even after rescuing an innocent boy in distress! And storage fees? Conveyance charges? Drayage costs? How do you get \emph{drayage costs} on a \emph{pie?}”

There was another one of those awkward pauses. Harry thought deadly thoughts at whichever Hufflepuff couldn’t seem to stop giggling, that idiot was going to get him hurt.

Harry stepped back and shot the Slytherins his best lethal glare. “Now go away or I will just keep making your existence more and more surreal until you do. Let me warn you...\ messing with \emph{my} life tends to make \emph{your} life... \emph{a little hairy.} Get it?”

In a single terrible motion, the largest Slytherin whipped his wand out to point at Harry and in the same instant was hit on the other side of his head by another pie, this one bright blueberry.

The note on this pie was rather large and clearly readable. “You might want to read the note on that pie,” Harry observed. “I think it’s for you this time.”

The Slytherin slowly reached up, took the pie pan, turned it over with a wet glop that dropped more blueberry on the floor, and read a note that said:
\begin{center}
\scshape \MakeUppercase{Warning}\\\MakeUppercase{No} magic may be used on the contestant\\while the Game is in progress\\Further interference in the Game\\\MakeUppercase{will} be reported to the Game Authorities
\end{center}

The expression of sheer bafflement on the Slytherin’s face was a look of art. Harry thought that he might be starting to like this Game Controller.

“Look,” Harry said, “you want to call it a day? I think things are spiraling out of control here. How about you go back to Slytherin and I go back to Ravenclaw and we all just cool down a bit, okay?”

“I’ve got a better idea,” hissed the largest Slytherin. “How about if you accidentally break all your fingers?”

“How in Merlin’s name do you stage a believable accident after making the threat in front of a dozen witnesses, you \emph{idiot}—”

The largest Slytherin slowly, deliberately reached out toward Harry’s hands, and Harry froze in place, the part of his brain that was noticing the other boy’s age and strength finally managing to make itself heard, screaming, \shout{What the heck am I doing?}

“Wait!” said one of the other Slytherins, his voice suddenly panicky. “Stop, you shouldn’t actually do that!”

The largest Slytherin ignored him, taking Harry’s right hand firmly in his left hand, and taking Harry’s index finger in his right hand.

Harry stared the Slytherin straight in the eyes. Part of Harry was screaming, this wasn’t supposed to happen, this wasn’t \emph{allowed} to happen, grownups would never let something like this \emph{actually} happen—

Slowly, the Slytherin started to bend his index finger backward.

\emph{He hasn’t actually broken my finger and it is beneath me to so much as flinch until he does. Until then, this is just another attempt to cause fear.}

“Stop!” said the Slytherin who had objected before. “Stop, this is a very bad idea!”

“I rather agree,” said an icy voice. An older woman’s voice.

The largest Slytherin let go of Harry’s hand and leaped backward as if burned.

“Professor Sprout!” cried one of the Hufflepuffs, sounding as glad as anyone Harry had ever heard in his life.

Into Harry’s field of vision, as he turned, stalked a dumpy little woman with messily curled grey hair and clothes covered with dirt. She pointed an accusing finger at the Slytherins. “Explain yourselves,” she said. “What are you doing with my Hufflepuffs and...” she looked at him. “My fine student, Harry Potter.”

\emph{Uh oh. That’s right, it was \textsc{her} class I missed this morning.}

“He threatened to kill us!” blurted one of the other Slytherins, the same one who’d called for a halt.

“What?” Harry said blankly. “I did \emph{not!} If I was going to kill you I wouldn’t make public threats first!”

A third Slytherin laughed helplessly and then stopped abruptly as the other boys shot him deadly glares.

Professor Sprout had adopted a rather skeptical expression. “What death threat would this be, exactly?”

“The Killing Curse! He pretended to use the Killing Curse on us!”

Professor Sprout turned to look at Harry. “Yes, quite a terrible threat from an eleven-year-old boy. Though still not something you should \emph{ever} dream of pretending, Harry Potter.”

“I don’t even know the \emph{words} to the Killing Curse,” Harry said promptly. “And I didn’t have my wand out at any time.”

Now Professor Sprout was giving Harry a skeptical look. “I suppose this boy hit \emph{himself} with two pies, then.”

“He \emph{didn’t} use his wand!” blurted one of the young Hufflepuffs. “I don’t know how he did it either, he just snapped his fingers and there was pie!”

“Really,” said Professor Sprout after a pause. She drew her own wand. “I won’t require it, since you do seem to be the victim here, but would you mind if I checked your wand to verify that?”

Harry took out his wand. “What do I—”

“\emph{Priori Incantatem,}” said Sprout. She frowned. “That’s odd, your wand doesn’t seem to have been used at all.”

Harry shrugged. “It hasn’t, actually, I only got my wand and schoolbooks a few days ago.”

Sprout nodded. “Then we have a clear case of accidental magic from a boy who felt threatened. And the rules plainly state that you are not to be held responsible. As for \emph{you...}” she turned toward the Slytherins. Her eyes dropped deliberately to Neville’s books lying on the floor.

\sloppypar There was a long silence during which she looked at the five Sly\-therins.

“Three points from Slytherin, \emph{each},” she said finally. “And six from \emph{him,}” pointing to the boy covered in pie. “Don’t you \emph{ever} meddle with my Hufflepuffs again, or my student Harry Potter either. Now \emph{go.}”

She didn’t have to repeat herself; the Slytherins turned and walked away very quickly.

Neville went and started picking up his books. He seemed to be crying, but only a little. It might have been from delayed shock, or it might have been because the other boys were helping him.

“Thank you \emph{very} much, Harry Potter,” Professor Sprout said to him. “Seven points to Ravenclaw, one for each Hufflepuff you helped protect. And I won’t say anything more.”

Harry blinked. He’d been expecting something more along the lines of a lecture about keeping himself out of trouble, and a rather severe scolding for missing his very first class.

Maybe he \emph{should} have gone to Hufflepuff. Sprout was cool.

“\emph{Scourgify,}” Sprout said to the mess of pie on the floor, which promptly vanished.

And she left, walking along the hall that led to the green study room.

“How did you \emph{do} that?” hissed one of the Hufflepuff boys as soon as she was gone.

Harry smiled smugly. “I can make anything I want happen just by snapping my fingers.”

The boy’s eyes widened. “\emph{Really?}”

“No,” said Harry. “But when you’re telling everyone this story be sure to share it with Hermione Granger in first-year Ravenclaw, she has an anecdote you might find amusing.” He had absolutely no clue what was happening, but he wasn’t about to pass up the opportunity to add to his growing legend. “Oh, and what was all that about the Killing Curse?”

The boy gave him a strange look. “You really don’t know?”

“If I did, I wouldn’t be asking.”

“The words to the Killing Curse are,” the boy swallowed, and his voice dropped to a whisper, and he held his hands away from his sides as if to make it very clear that he wasn’t holding a wand, “\emph{Avada Kedavra.}”

\emph{Well of course they are.}

Harry put this on his growing list of things to never ever tell his Dad, Professor Michael Verres-Evans. It was bad enough talking about how you were the only person to survive the fearsome Killing Curse, without having to admit that the Killing Curse was “Abracadabra.”

“I see,” Harry said after a pause. “Well, that’s the last time I ever say \emph{that} before snapping my fingers.” Though it \emph{had} produced an effect that might be tactically useful.

“\emph{Why} did you—”

“Raised by Muggles, Muggles think it’s a joke and that it’s funny. Seriously, that’s what happened. Sorry, but can you remind me of your name?”

“I’m Ernie Macmillan,” said the Hufflepuff. He held out his hand, and Harry shook it. “Honored to meet you.”

Harry executed a slight bow. “Pleased to meet you, skip the honored thing.”

Then the other boys crowded round him and there was a sudden flood of introductions.

When they were done, Harry swallowed. This was going to be very difficult. “Um...\ if everyone would excuse me... I have something to say to Neville—”

All eyes turned to Neville, who took a step back, his face looking apprehensive.

“I suppose,” Neville said in a tiny voice, “you’re going to say I should’ve been braver—”

“Oh, no, nothing like that!” Harry said hastily. “Nothing to do with \emph{that}. It’s just, um, something the Sorting Hat told me—”

Suddenly the other boys looked \emph{very} interested, except for Neville, who was looking even \emph{more} apprehensive.

There seemed to be something blocking Harry’s throat. He knew he should just blurt it out, and it was like he’d swallowed a large brick that was just stuck in the way.

It was like Harry had to manually take control of his lips and produce each syllable individually, but he managed to make it happen. “I’m, sor, ry.” He exhaled and took a deep breath. “For what I did, um, the other day. You...\ don’t have to be gracious about it or anything, I’ll understand if you just hate me. This isn’t about me trying to look cool by apologizing or your having to accept it. What I did was wrong.”

There was a pause.

Neville clutched his books tighter to his chest. “Why did you do it?” he said in a thin, wavering voice. He blinked, as if trying to hold back tears. “Why does \emph{everyone} do that to me, even the Boy-Who-Lived?”

Harry suddenly felt smaller than he ever had in his life. “I’m sorry,” Harry said again, his voice now hoarsened. “It’s just...\ you looked so scared, it was like a sign over your head saying ‘victim’, and I wanted to show you that things \emph{don’t} always turn out badly, that sometimes the monsters give you chocolate... I thought if I showed you that, you might realize there wasn’t so much to be afraid of—”

“But there \emph{is,}” whispered Neville. “You saw it today, there \emph{is!}”

“They wouldn’t have done anything really bad in front of witnesses. Their main weapon is fear. That’s why they target \emph{you,} because they can see you’re afraid. I wanted to make you less afraid...\ show you that the fear was worse than the thing itself...\ or that was what I told myself, but the Sorting Hat told me that I was lying to myself and that I really did it because it was fun. So that’s why I’m apologizing—”

“You hurt me,” said Neville. “Just now. When you grabbed me and pulled me away from them.” Neville held out his arm and pointed to where Harry had grabbed him. “I might have a bruise here later from how hard you pulled. You hurt me worse than anything the Slytherins did by bumping into me, actually.”

“\emph{Neville!}” hissed Ernie. “He was trying to \emph{save} you!”

“I’m sorry,” whispered Harry. “When I saw that I just got...\ really angry...”

Neville looked at him steadily. “So you yanked me out really hard and put yourself in where I was and went, ‘Hello, I’m the Boy-Who-Lived’.”

Harry nodded.

“I think you’re going to be really cool someday,” Neville said. “But right now, you’re not.”

Harry swallowed the sudden knot in his throat and walked away. He continued down the corridor to the intersection, then turned left into a hallway and kept on walking, blindly.

What was he \emph{supposed} to do here? Never get angry? He wasn’t sure he could have done anything without being angry and who knows what would have happened to Neville and his books then. Besides, Harry had read enough fantasy books to know how \emph{this} one went. He would try to suppress the anger and he would fail and it would keep coming out again. And after this whole long journey of self-discovery he would learn at the end that his anger was a part of himself and that only by accepting it could he learn to use it wisely. \emph{Star Wars} was the only universe in which the answer actually \emph{was} that you were supposed to cut yourself off completely from negative emotions, and something about Yoda had always made Harry hate the little green moron.

So the obvious time-saving plan was to skip the journey of self-discovery and go straight to the part where he realized that only by accepting his anger as a part of himself could he stay in control of it.

The problem was that he didn’t \emph{feel} out of control when he was angry. The cold rage made him feel like he was \emph{in} control. It was only when he looked back that \emph{events as a whole} seemed to have...\ blown up out of control, somehow.

He wondered how much the Game Controller cared about that sort of thing, and whether he’d won or lost points for it. Harry himself felt like he’d lost quite a few points, and he was sure the old lady in the picture would have told him that his was the only opinion that mattered.

And Harry was also wondering whether the Game Controller had sent Professor Sprout. It was the logical thought: the note had threatened to notify the Game Authorities, and then there Professor Sprout was. Maybe Professor Sprout \emph{was} the Game Controller—the \emph{Head of House Hufflepuff} would be the \emph{last} person anyone would suspect, which ought to put her near the top of Harry’s list. He’d read one or two mystery novels, too.

“So how am I doing in the game?” Harry said out loud.

A sheet of paper flew over his head, as if someone had thrown it from behind him—Harry turned around, but there was no one there—and when Harry turned forward again, the note was settling to the floor.

The note said:
\begin{align*}
\hbox{\scshape Points for style: }&\hbox{10}\\
\hbox{\scshape Points for good thinking: }&\hbox{−3,000,000}\\
\hbox{\scshape Ravenclaw House points bonus: }&\hbox{70}\\
\hbox{\scshape Current points: }&\hbox{−2,999,871}\\
\hbox{\scshape Turns remaining: }&\hbox{2}
\end{align*}

“\emph{Minus three million points?”} Harry said indignantly to the empty hallway. “That seems excessive! I want to file an appeal with the Game Authorities! And how am I supposed to make up three million points in the next two turns?”

Another note flew over his head.
\begin{align*}
\hbox{\scshape Appeal: }&\hbox{\scshape Failed}\\
\hbox{\scshape Asking the wrong questions: }&\hbox{−1,000,000,000,000 points}\\
\hbox{\scshape Current points: }&\hbox{−1,000,002,999,871}\\
\hbox{\scshape Turns remaining: }&\hbox{1}
\end{align*}

Harry gave up. With one turn remaining all he could do was take his best shot, even if it wasn’t very good. “My guess is that the game represents life.”

A final sheet of paper flew over his head, reading:
\begin{center}\scshape
Attempt failed\\
Failed Failed Failed\\
Aiiiiiiiiiieeeeeeeeeeeeee\\
Current points: minus Infinity\\
\MakeUppercase{You have lost the game}

Final instruction:\\
\emph{go to Professor McGonagall’s office}
\end{center}

The last line was in his own handwriting.

Harry stared at the last line for a while, then shrugged. Fine. Professor McGonagall’s office it would be. If \emph{she} was the Game Controller...

Okay, honestly, Harry had absolutely no idea how he would feel if Professor McGonagall was the Game Controller. His mind was just drawing a complete blank. It was, literally, unimaginable.

A couple of portraits later—it wasn’t a long trip, Professor McGonagall’s office wasn’t far from her Transfiguration classroom, at least not on Mondays on odd-numbered years—Harry stood outside the door to her office.

He knocked.

“Come in,” said Professor McGonagall’s muffled voice.

He entered.

“Mr.~Potter?” said Professor McGonagall. “I wasn’t expecting you here. What’s this about?”


