\partchapter{Taboo Tradeoffs}{III}

\lettrine{I}{n} rising half-circles of dark stone, a great sea of upraised hands.

\quad The Lords and Ladies of the Wizengamot, in plum-colored robes marked with a silver ‘W’, stared down in stern rebuke at a young girl trembling in chains. If they had, in any particular ethical system, damned themselves, they clearly thought quite highly of themselves for having done so.

Harry’s breath was trembling in his chest. His dark side had come up with a plan—and then rotated itself back out again because speaking too icily would not be to Hermione’s advantage; a fact which the only-half-cold Harry had somehow not realized...

“The vote carries, in favor,” intoned the secretary, when all the tallying was done, and the upraised hands fell back down. “The Wizengamot recognizes the blood debt owed by Hermione Granger to House Malfoy for the attempted murder of its scion and ending of its line.”

Lucius Malfoy was smiling in grim satisfaction. “And now,” said the white-maned wizard, “I say that her debt shall be paid—”

Harry clenched his fists beneath the bench and shouted, “By the debt owed from House Malfoy to House Potter!”

“Silence!” snapped the woman in too much pink makeup sitting next to Minister Fudge. “You’ve disrupted these proceedings quite enough already! Aurors, escort him out!”

“Wait,” said Augusta Longbottom from the top tier of seats. “What debt is this?”

Lucius’s hands whitened on his cane. “House Malfoy owes no debt to you!”

It wasn’t the world’s most solid hope, it was based on one newspaper article from a woman who’d been False-Memory-Charmed, but Rita Skeeter had seemed to find it plausible, that Mr.\ Weasley had allegedly owed James Potter a debt because...

“I’m surprised you’ve forgotten,” Harry said evenly. “Surely it was a cruel and painful period of your life, laboring under the Imperius curse of He-Who-Must-Not-Be-Named, until you were freed of it by the efforts of House Potter. By my mother, Lily Potter, who died for it, and by my father, James Potter, who died for it, and by me, of course.”

There was a brief silence within the Most Ancient Hall.

“Why, what an excellent point, Mr.\ Potter,” said the old witch who’d been identified as Madam Bones. “I, too, am quite surprised that Lord Malfoy would forget such a significant event. It must have been such a happy day for him.”

“Yes,” said Augusta Longbottom. “He must have been so grateful.”

Madam Bones nodded. “House Malfoy could not possibly deny that debt—unless, perhaps, Lord Malfoy is to tell us that he has misremembered something? I should take quite a professional interest in that. We are always trying to improve our picture of those dark days.”

Lucius Malfoy’s hands gripped the silver snake-handle of his cane like he was about to strike with it, unleash whatever power it kept—

Then the Lord Malfoy seemed to relax, and a chill smile came over his face. “Of course,” he said easily. “I do confess I had not understood, but the child is quite correct. But I do not quite think the two debts cancel—House Potter was only trying to save itself, after all—”

“Not so,” Dumbledore said from above.

“—and therefore,” intoned Lucius Malfoy, “I demand monetary compensation as well, for the redemption of the blood debt owed my son. That, too, is the law.”

Harry felt a strange inward flinch. That had also been in the newspaper article, Mr.\ Weasley had demanded an additional ten thousand Galleons—

“How much?” said the Boy-Who-Lived.

Lucius was still wearing the cold smile. “One hundred thousand Galleons. If you have not that much in your vault, I suppose I must accept a promissory note for the remainder.”

A roar of protest went up from Dumbledore’s side of the room, even some of the plum-colored robes in the middle looked shocked.

“Shall we put it to vote of the Wizengamot?” said Lucius Malfoy. “I think few of us would like to see the little murderess go free. By a show of hands, that additional compensation of one hundred thousand Galleons would be required to cancel the debt!”

The clerk began tallying, but that vote was also clear.

Harry stood there, breathing deeply.

\emph{You’d better not even have to think about this,} Harry’s inner Gryffindor said threateningly.

\emph{It’s a major purchase,} observed Ravenclaw. \emph{We ought to spend a lot of time thinking about it.}

It shouldn’t have been hard. It \emph{shouldn’t} have. Two million pounds was only money, and money was only worth what it could buy...

It was strange how much psychological attachment you could have to ‘only money’, or how painful it could be to imagine losing a bank vault full of gold that you hadn’t even imagined existed just one year earlier.

\emph{Kimball Kinnison wouldn’t hesitate,} said Gryffindor. \emph{Seriously. Like, snap decision. What sort of hero are you? I already hate you just for having to think about it for longer than 50 milliseconds.}

\emph{This is real life,} said Ravenclaw. \emph{Losing all your money is a lot more painful for real people in real life than in heroic books.}

\emph{What?} demanded Gryffindor. \emph{Whose side are you on?}

\emph{I wasn’t advocating for a particular answer,} said Ravenclaw, \emph{I was just saying it because it was true.}

\emph{Could a hundred thousand Galleons be used to save more than one life if spent some other way?} said Slytherin. \emph{We have research to do, battles to fight, the difference between being 40,000 Galleons rich and being 60,000 Galleons in debt is not trivial—}

\emph{So we’ll just use one of our ways to make money fast and earn it all back,} said Hufflepuff.

\emph{It’s not certain those will work,} said Slytherin, \emph{and a lot of them require starting cash—}

\emph{Personally,} said Gryffindor, \emph{I vote that we save Hermione and then gang up and kill our inner Slytherin.}

The clerk’s voice said that the tally had been recorded and the vote had passed...

Harry’s lips opened.

“I accept your offer,” said Harry’s lips, without any hesitation, without any decision having been made; just as if the internal debate had been pretense and illusion, the true controller of the voice having been no part of it.

It was clear that Lucius Malfoy had not been expecting that reply.

The Lord Malfoy’s mask of calm shattered, his eyes widened, he stared at Harry in sheer blank astonishment. His mouth had opened slightly, though he wasn’t speaking, and if he was making any peculiar noises it couldn’t be heard over the roar of simultaneous gasps from the Wizengamot—

A tap of stone silenced the crowd.

“No,” said the voice of Dumbledore.

Harry’s head jerked around to stare at the ancient wizard.

Dumbledore’s lined face was pale, the silver beard was visibly trembling, he looked like he was in the final throes of a terminal illness. “I’m—sorry, Harry—but this choice is not yours—for I am still the guardian of your vault.”

“\emph{What?}” said Harry, too shocked to compose his reply.

“I cannot let you go into debt to Lucius Malfoy, Harry! I cannot! You do not know—you do not realize—”

\emph{\shout{Die.}}

Harry didn’t even know which part of himself had spoken, it might have been a unanimous vote, the pure rage and fury pouring through him. For an instant he thought that the sheer force of the anger might take magical wing and fly out to strike the Headmaster, send him tumbling back dead from the podium—

But when that mental voice had spoken, the old wizard was still standing there, gazing at Harry, long dark wand in his right hand, short black rod in his left.

And Harry’s eyes also went to the red-golden bird with its claws resting on the shoulder of Dumbledore’s black robes, silent when no phoenix should have been silent. “Fawkes,” Harry said, his voice sounding strange in his own ears, “can you scream at him for me?”

The fiery bird on the old wizard’s shoulder didn’t scream. Maybe the Wizengamot had demanded that a spell of silence be put on the creature, otherwise it probably would have been screaming the whole time. But Fawkes hit his master, one golden wing buffeting the old wizard’s head.

“I cannot, Harry!” the old wizard said, the agony clear in his voice. “I am doing as I must do!”

And Harry knew, then, as he looked at the red-golden bird, what he had to do as well. It should have been obvious from the beginning, that solution.

“Then I too will do what I must,” Harry said up to Dumbledore, as though the two of them stood alone in the room. “You do realize that, don’t you?”

The old wizard shook his trembling head. “You will change your mind when you are older—”

“I’m not talking about that,” Harry said, his voice still strange in his own ears. “I mean that I will not allow Hermione Granger to be eaten by Dementors under any circumstances. Period. Regardless of what any law says, and no matter what I have to do to stop it. Do I still need to spell it out?”

A strange male voice spoke from somewhere far away, “Be sure that the girl is taken directly to Azkaban, and put under extra guard.”

Harry waited, staring at the old wizard, and then spoke again. “I will go to Azkaban,” Harry said to the old wizard, as though they stood alone in the world, “before Hermione can be taken there, and start snapping my fingers. It may cost me my life, but by the time she gets there, there won’t be an Azkaban anymore.”

Some members of the Wizengamot gasped in surprise.

Then a greater number started laughing.

“How would you even get there, little boy?” someone said, from among those who were laughing.

“I have my ways of going places,” said the boy’s distant voice. Harry kept his eyes on Dumbledore, on the old wizard staring at him in shock. Harry didn’t look directly at Fawkes, didn’t give his plan away; but in his mind he prepared to summon the phoenix to transport him, prepared to fill his mind with light and fury, to call for the fire-bird with all his might, he might have to do it upon the instant if Dumbledore pointed his wand—

“Would you truly?” the old wizard said to Harry, also as if the two of them stood alone in the room.

The room went silent again as everyone stared in shock at the Chief Warlock of the Wizengamot, who seemed to be taking the mad threat completely seriously.

The old wizard’s eyes were locked only on Harry. “Would you risk everything—everything—only for her?”

“Yes,” Harry said back in reply.

\emph{That’s the wrong answer, you know,} said Slytherin. \emph{Seriously.}

\emph{But it’s the true answer.}

“You will not see reason?” said the old wizard.

“Apparently not,” Harry said back.

The gazes stayed locked.

“This is terrible folly,” said the old wizard.

“I am aware of this,” answered the hero. “Now get out of my way.”

Strange light glinted in the ancient blue eyes. “As you will, Harry Potter, but know that this is not over.”

The rest of the world faded back into existence.

“I withdraw my objection,” said the old wizard, “Harry Potter may do as he wishes,” and the Wizengamot exploded in a roar of shock, only to be silenced by a final tap of the stone rod.

Harry turned his head back to look at Lord Malfoy, who looked like he’d seen a cat turn into a person and start eating other cats. To call the look confused did not begin to describe it.

“You would truly...” Lucius Malfoy said slowly. “You would truly pay a hundred thousand Galleons, to save one mudblood girl.”

“I think there’s about forty thousand in my Gringotts vault,” Harry said. It was strange how that was \emph{still} causing more internal pain than the thought of taking an over-fifty-percent risk to his life to destroy Azkaban. “As for the other sixty thousand—what are the rules, exactly?”

“It comes due when you graduate Hogwarts,” the old wizard said from high above. “But Lord Malfoy has certain rights over you before then, I fear.”

Lucius Malfoy stood motionless, frowning down at Harry. “Who is she to you, then? \emph{What} is she to you, that you would pay so much to keep her from harm?”

“My friend,” the boy said quietly.

Lucius Malfoy’s eyes narrowed. “By the report I received, you cannot cast the Patronus Charm, and Dumbledore knows this. The power of a single Dementor nearly killed you. You would not dare venture near Azkaban in your own person—”

“That was in January,” said Harry. “This is April.”

Lucius Malfoy’s eyes remained cool and calculating. “You pretend you can destroy Azkaban, and Dumbledore pretends to believe it.”

Harry did not reply.

The white-haired man turned slightly, toward the center of the half-circle, as though to address the greater Wizengamot. “I withdraw my offer!” shouted the Lord of Malfoy. “I will not accept the debt to House Potter in payment, not even for a hundred thousand Galleons! The girl’s blood debt to House Malfoy stands!”

Again the roar of many voices. “Dishonorable!” someone cried. “You acknowledge the debt to House Potter, and yet you would—” and then that voice cut off.

“I acknowledge the debt, but the law does not strictly oblige me to accept it in cancellation,” said Lord Malfoy with a grim smile. “The girl is no part of House Potter; the debt I owe House Potter is no debt to her. As for the \emph{dishonor}—” Lucius Malfoy paused. “As for the grave shame I feel at my ingratitude toward the Potters, who have done so much for me—” Lucius Malfoy bowed his head. “May my ancestors forgive me.”

“Well, boy?” called the scarred man sitting at Lord Malfoy’s right hand. “Go and destroy Azkaban, then!”

“I’d like to see that,” said another voice. “Will you be selling tickets?”

It went without saying that Harry didn’t pick this particular moment to give up.

\emph{The girl is no part of House Potter—}

He had, in fact, seen the obvious way out of the dilemma almost instantly.

It might have taken him longer if he hadn’t recently overheard a number of conversations between older Ravenclaw girls, and read a certain number of Quibbler stories.

He was, nonetheless, having trouble accepting it.

\emph{This is ridiculous,} said a part of Harry which had just dubbed itself the Internal Consistency Checker. \emph{Our actions here are completely incoherent. First you feel less emotional reluctance to risk your bloody \shout{Life} and probably \shout{Die} for Hermione, than to part with a stupid heap of gold. And now you’re balking just at getting married?}

\emph{\shout{System Error.}}

\emph{You know what?} said Internal Consistency Checker. \emph{You’re stupid.}

\emph{I didn’t say no,} thought Harry. \emph{I was just saying \shout{System Error}.}

\emph{I vote for destroying Azkaban,} said Gryffindor. \emph{It needs to be done anyway.}

\emph{Really, really stupid,} said Internal Consistency Checker. \emph{Oh, screw this, I’m assuming control of our body.}

The boy took a deep breath, and opened his mouth—

By this point Harry Potter had entirely forgotten the existence of Professor McGonagall, who had been sitting there this whole time undergoing a number of interesting changes of facial expression which Harry had not been looking at because he was distracted. It would have been overly harsh to say that Harry had forgotten her because he did not consider her a PC. It could be more kindly said that Professor McGonagall was not visibly a solution to any of his current problems, and therefore she was not part of the universe.

So Harry, who at this point had a fair amount of adrenaline in his bloodstream, startled and jumped quite visibly when Professor McGonagall, her eyes now blazing with impossible hope and the tears on her cheek half-dried, leapt to her feet and cried, “\emph{With me, Mr.\ Potter!}” and, without waiting for a reply, tore down the stairs that led to the bottom platform where waited a chair of dark metal.

It took a moment, but Harry ran after; though it took him longer to reach the bottom, after Professor McGonagall vaulted half the stairs with a strange catlike motion and landed with the astonished-looking Auror trio already pointing their wands at her.

“Miss Granger!” cried Professor McGonagall. “Can you speak yet?”

Much as with Professor McGonagall, there was a certain sense in which it could be said that Harry had forgotten about the existence of Hermione Granger, because Harry had been tilting his neck back to look upward rather than downward, and because he hadn’t considered her a solution to any of his current problems. Though it was hardly certain, in fact it wasn’t at all probable, that Harry remembering to look at Hermione or think about what she must be feeling, would have helped anything in the slightest.

Harry reached the bottom of the stairs and saw Hermione Granger full on—

Without thinking, without being able to help himself, Harry shut his eyes, but he’d seen.

Her school robes around her neck, soaked all the way through with tears.

The way she’d been looking away from \emph{him}.

And the eye of memory and sympathy, which could not be shut, which could not look away, knew that Hermione had recounted the worst shame of her life in front of the nobility of magical Britain and Professor McGonagall and Dumbledore and Harry; and then been sentenced to Azkaban where she would be exposed to Dementors until she went mad and died; and then she’d heard that Harry was going to give away all his money and go into debt to save her, and maybe even sacrifice his life

and with the Dementor standing only a few paces behind her

she hadn’t said anything...

“Y-yes,” whispered the voice of Hermione Granger. “I c-can talk.”

Harry opened his eyes again and saw her face, now looking at him. It didn’t say anything like what he thought Hermione was feeling, faces couldn’t say anything that complicated, all facial muscles could do was contort themselves into knots.

“H-H-Harry, I-I’m so, I’m so—”

“Shut up,” Harry suggested.

“s-s-sorry—”

“If you’d never met me on the train you wouldn’t be in any trouble right now. So shut up,” said Harry Potter.

“Both of you stop being silly,” Professor McGonagall said in her firm Scottish accent (it was strange how much that helped). “Mr.\ Potter, hold out your wand so that Miss Granger’s fingers can touch it. Miss Granger, repeat after me. Upon my life and magic—”

Harry did as he was bid, thrusting his wand forward to touch Hermione’s fingers; and then Hermione’s faltering voice said, “Upon my life and magic—”

“I swear service to the House of Potter—” said Professor McGonagall.

And Hermione, without waiting for any further instructions, said, the words spilling out of her in a rush, “I swear service to the House of Potter, to obey its Master or Mistress, and stand at their right hand, and fight at their command, and follow where they go, until the day I die.”

All those words had been blurted out in a desperate gasp before Harry could have thought or said anything, if he’d been mad enough to interrupt.

“Mr.\ Potter, repeat these words,” said Professor McGonagall. “I, Harry, heir and last scion of the Potters, accept your service, until the end of the world and its magic.”

Harry took a breath and said, “I, Harry, heir and last scion of the Potters, accept your service, until the end of the world and its magic.”

“That’s it,” said Professor McGonagall. “Well done.”

Harry looked up, and saw that the entire Wizengamot, whose existence he’d forgotten, was staring at them.

And then Minerva McGonagall, who \emph{was} Head of House Gryffindor even if she didn’t always act like it, looked up high above at where Lucius Malfoy stood; and she said to him before the entire Wizengamot, “I regret every point I ever gave you in Transfiguration, you vile little worm.”

Whatever Lucius was about to say in reply was silenced by a tap of the short rod in Dumbledore’s hand. “Ahem!” said the old wizard from his podium of dark stone. “This session has carried on quite considerably, and if it is not dismissed soon, some of us may miss their entire luncheon. The law of this matter is clear. You have already voted on the terms of the bargain, and Lord Malfoy cannot legally decline it. As we have far exceeded our allotted time, I now, in accordance with the last decision of the survivors of the eighty-eighth Wizengamot, adjourn this session.”

The old wizard tapped the rod of dark stone three times.

“You fools!” shouted Lucius Malfoy. The white hair was shaking as though in a wind, the face beneath was pale with fury. “Do you think you’ll get away with what you’ve done today? Do you think that girl can try to murder my son and escape unscathed?”

The toad-like pink-makeup woman, whose name Harry could no longer remember, was standing up from her seat. “Why, of course not,” she said with a sickening smile. “After all, the girl \emph{is} still a murderess, and I think the Ministry shall be watching her affairs quite closely—it hardly seems wise that she should be allowed to wander the streets, after all—”

Harry was fed up at this point.

Without waiting to listen, Harry turned on his heel and strode forward in long steps toward—

The horror only he could truly see, the absence of color and space, the wound in the world, above which floated a tattered cloak; most imperfectly guarded by a running moonlit squirrel and fluttering silver sparrow.

His dark side had also noticed, when it was looking through the entire room for anything that could possibly be used as a weapon, that the enemy had been foolish enough to bring a Dementor into Harry’s presence. That was a powerful weapon indeed, and one that Harry might wield better than its supposed masters. There had been a time in Azkaban when Harry had told twelve Dementors to turn and go, and they had gone.

\emph{The Dementors are Death, and the Patronus Charm works by thinking about happy thoughts instead of Death.}

If Harry’s theory was correct, that one sentence would be all it took to pop the Aurors’ Patronus Charms like a soap bubble, and ensure that nobody within reach of his voice could cast another one.

\emph{I am going to cancel the Patronus Charms and prevent any more Patronuses from being cast. And then my Dementor, flying faster than any broomstick, is going to Kiss everyone here who voted to send a twelve-year-old girl to Azkaban.}

Say that, to set up the if-then expectation, and wait for people to understand and laugh. Then speak the fatal truth; and when the Aurors’ Patronuses winked out to prove the point, either people’s \emph{anticipations} of the mindless void, or Harry’s threat of its destruction, would make the Dementor obey. Those who had sought to compromise with the darkness would be consumed by it.

It was the other solution his dark side had devised.

Ignoring the gasps rising from behind him, Harry crossed the radius of the Patronuses, strode to a single pace from Death. Its unhindered fear burst around him like a whirlpool, like stepping next to the sucking drain of some huge bathtub emptying out its water; but with the false Patronuses no longer obscuring the level on which they interacted, Harry could reach the Dementor even as it could reach him. Harry looked straight into the pulling vacuum and—

\emph{the Earth among the stars}

all his triumph at saving Hermione

\emph{someday the reality of which you are a shadow will cease to exist}

Harry took all the silver emotion that fueled his Patronus Charm and \emph{shoved} it at the Dementor; and expected Death’s shadow to flee from him—

—and as Harry did that, he flung his hands up and shouted \scream{“Boo!”}

The void retreated sharply away from Harry until it came up against the dark stone behind.

In the hall there was a deathly silence.

Harry turned his back on the empty void, and looked up at where the toad-woman stood. She was pale beneath the pink makeup, her mouth opening and closing like a fish.

“I make you this one offer,” said the Boy-Who-Lived. “I never learn that you’ve been interfering with me or any of mine. And you never find out why the unkillable soul-eating monster is scared of me. Now sit down and shut up.”

The toad-woman fell back down to her bench without a word.

Harry looked further up.

“A riddle, Lord Malfoy!” the Boy-Who-Lived shouted across the Most Ancient Hall. “I know you weren’t in Ravenclaw, but try to answer this one anyway! What destroys Dark Lords, frightens Dementors, and owes you sixty thousand Galleons?”

For an instant Lord Malfoy stood there with eyes slightly widened; then his face fell back into calm scorn, and his voice spoke coolly in reply. “Are you openly threatening me, Mr.\ Potter?”

“I’m not threatening you,” said the Boy-Who-Lived. “I’m \emph{scaring} you. There’s a difference.”

“Enough, Mr.\ Potter,” said Professor McGonagall. “We shall be late for afternoon Transfiguration as it is. And do come back here, you’re still terrifying that poor Dementor.” She turned to the Aurors. “Mr.\ Kleiner, if you would!”

Harry strode back to them, as the Auror addressed moved forward and pressed a short rod of dark metal to the dark metal chair, muttering an inaudible word of dismissal.

The chains slithered back as smoothly as they had come forth; and Hermione pushed herself out of the chair as fast as she could, and half-ran and half-staggered forward a few steps.

Harry held out his arms—

—and Hermione half-jumped half-fell into Professor McGonagall’s arms, beginning to sob hysterically.

\emph{Hmpfh,} said a voice inside Harry. \emph{I kind of thought we’d earned that one ourselves.}

\emph{Oh, shut up.}

Professor McGonagall was holding Hermione so firmly that you might have thought it was a mother holding her daughter, or maybe granddaughter. After a few moments Hermione’s sobs slowed, and then stopped. Professor McGonagall suddenly shifted her stance and grabbed onto her more tightly; the girl’s hands were dangling limply, now, and her eyes were closed—

“She’ll be fine, Mr.\ Potter,” Professor McGonagall said softly in Harry’s direction, without looking at him. “She just needs a few hours in one of Madam Pomfrey’s beds.”

“All right, then,” Harry said. “Let’s get her to Madam Pomfrey’s.”

“Yes,” said Dumbledore, as he descended to the bottom of the dark stone stairs. “Let us all go home, indeed.” His blue eyes were locked on Harry, as hard as sapphires.
\sbreak
The Lords and Ladies of the Wizengamot are departing their wooden benches, leaving as they came, looking rather nervous.

The vast majority are thinking ‘The Dementor was frightened of the Boy-Who-Lived!’

Some of the shrewder ones are already wondering how this will affect the delicate power balance of the Wizengamot—if a new piece has appeared upon the gameboard.

Almost none are thinking anything along the lines of ‘I wonder how he did that.’

This is the truth of the Wizengamot: Many are nobles, many are wealthy magnates of business, a few came by their status in other ways. Some of them are stupid. Most are shrewd in the realms of business and politics, but their shrewdness is circumscribed. Almost none have walked the path of a powerful wizard. They have not read through ancient books, scrutinized old scrolls, searching for truths too powerful to walk openly and disguised in conundrums, hunting for true magic among a hundred fantastic fairy tales. When they are not looking at a contract of debt, they abandon what shrewdness they possess and relax with some comfortable nonsense. They believe in the Deathly Hallows, but they also believe that Merlin fought the dread Totoro and imprisoned the Ree. They know (because that too is part of the standard legend) that a powerful wizard must learn to distinguish the truth among a hundred plausible lies. But it has not occurred to them that they might do the same.

(Why not? Why, indeed, would wizards with enough status and wealth to turn their hands to almost any endeavor, choose to spend their lives fighting over lucrative monopolies on ink importation? The Headmaster of Hogwarts would hardly see the question; of course most people should not be powerful wizards, just as most people should not be heroes. The Defense Professor could explain at great and cynical length why their ambitions are so trivial; to him, too, there is no puzzle. Only Harry Potter, for all the books he has read, is unable to understand; to the Boy-Who-Lived the life choices of the Lords and Ladies seem incomprehensible—not what a good person would do, nor yet an evil person either. Now which of the three is most wise?)

For whatever reason, then, most of the Wizengamot has never walked the path that leads to powerful wizardry; they do not seek out what is hidden. For them, there is no \emph{why.} There is no explanation. There is no causality. The Boy-Who-Lived, who was already halfway into the magisterium of legend, has now been promoted all the way there; and it is a brute fact, simple and unexplained, that the Boy-Who-Lived frightens Dementors. Ten years earlier they were told that a one-year-old boy defeated the most terrible Dark Lord of their generation, perhaps the most evil Dark Lord ever to live; and they just accepted that too.

You are not meant to question that sort of thing (they know in some unspoken way). If the most terrible Dark Lord in history, confronts an innocent baby—why, how could he \emph{not} be vanquished? The rhythm of the play demands it. You are supposed to applaud, not stand up from your seat in the audience and say ‘Why?’ It is just the story’s conceit, that in the end the Dark Lord is brought down by a little child; and if you are going to question that, you might as well not attend the play in the first place.

It does not occur to them to second-guess the application of such reasoning to the events they have seen with their own eyes in the Most Ancient Hall. Indeed, they are not consciously aware that they are using story-reasoning on real life. As for scrutinizing the Boy-Who-Lived with the same careful logic they would use on \replacement{an}{a} political alliance or a business arrangement—what brain would associate to \emph{that,} when a part of the legendary magisterium is at hand?

But there are a very few, seated on those wooden benches, who do \emph{not} think like this.

There are a certain few of the Wizengamot who have read through half-disintegrated scrolls and listened to tales of things that happened to someone’s brother’s cousin, not for entertainment, but as part of a quest for power and truth. They have already marked the Night of Godric’s Hollow, as reported by Albus Dumbledore, as an anomalous and potentially important event. They have wondered why it happened, if it did happen; or if not, why Dumbledore is lying.

And when an eleven-year-old boy rises up and says “Lucius Malfoy” in that cold adult voice, and goes on to speak words one simply would not expect to hear from a first-year in Hogwarts, they do not allow the fact to slip into the lawless blurs of legends and the premises of plays.

They mark it as a clue.

They add it to the list.

This list is beginning to look somewhat alarming.

It doesn’t particularly help when the boy yells “BOO!” at a Dementor and the decaying corpse presses itself flat against the opposite wall and its horrible ear-hurting voice rasps, “\emph{Make him go away.}”
