\partchapter{Self-Actualization}{II}

\lettrine{I}{n} the high reaches of Hogwarts where rooms and corridors changed on a daily basis, where the territory itself was uncertain and not just the map, where the stability of the castle began to fray into dreams and chaos without changing its architectural style or apparent solidity—in the high reaches of Hogwarts, a battle would soon be fought.

The presence of so many students would stabilize the corridors for a time, by dint of constant observation. The rooms and corridors of Hogwarts sometimes \emph{moved} even while people looked directly at them, but they wouldn’t \emph{change}. Even after eight centuries, Hogwarts was still a little shy about changing in front of people.

But despite that transient permanence (the Defense Professor had said) the upper reaches of Hogwarts still had a military realism: you had to learn the ground anew each time, and check every closet for secret corridors all over again.

Sunday it was, Sunday the first of March. Professor Quirrell had recovered enough to supervise battles once more, and they were all catching up on the backlog.

The Dragon General, Draco Malfoy, watched two compasses he held in either hand. One compass was the color of the Sun, the other had a multicolored, iridescent sheen to indicate Chaos. The other two generals, Draco knew, had been given their own compasses; only Hermione Granger’s hand, and Harry Potter’s hand, would hold a compass that was orange-red and flickered in its reflections like fire, pointing always to the direction of the largest active contingent of Dragon Army.

Without those compasses they might have searched for days and never found each other, which was a territorial hazard of fighting in the upper levels of Hogwarts.

Draco had a bad feeling about what would happen when Dragon Army found the Chaos Legion. Harry Potter had changed since Bellatrix Black had escaped; the Heir of Slytherin had begun to seem truly Lordly now (and how had Professor Quirrell known that would happen?) Draco would have felt a lot better with Hermione Granger standing alongside him with her twenty-three Sunshine Soldiers in tow, but no, the Sunshine General was being stupidly proud and refusing to accept aid against General Potter. She wanted to take down Potter herself, she’d told him.

The Noble and Most Ancient House of Malfoy had maintained their influence over Britain for centuries by understanding that you couldn’t always be \emph{the} most powerful. Sometimes another Lord was just stronger, and you had to settle for \emph{merely} being his foremost lieutenant. You could build up \emph{quite} a position of wealth and power over a dozen generations of being second in command. You just had to be careful, each time, not to let your House be dragged down with the fall of the Lord you served. That was the Malfoy tradition which centuries of experience had honed...

And so Father had thoroughly explained to Draco that if he ran into someone who was obviously stronger than him, Draco was \emph{not} to resent this and \emph{not} to deny it and \emph{not} to throw a tantrum that could sabotage his potential position, but Draco \emph{was} to make sure that his place in the next generation’s power structure wasn’t any lower than second.

Granger, apparently, had never gotten this lecture from her own parents, and was still in denial about the obvious fact that Harry Potter was becoming stronger than her.

So Draco had secretly met with Captain Goldstein and Captain Bones and Captain Macmillan and they’d agreed to all do their best to make sure that Dragon and Sunshine didn’t engage each other before they engaged the larger threat of Chaos.

It wasn’t \emph{really} violating the agreement against traitors, you weren’t soliciting traitors if you honestly meant to \emph{help} the other army.

A high ringing tone belled through the corridors to signal the start of the battle, and a moment later Draco shouted “\emph{Go!}” and the Dragons started running. It would tire his soldiers, it would cost them something even after they stopped and caught their breath, but they \emph{had} to put Chaos directly between themselves and the Sunshine Regiment.
\sbreak
Harry and Neville walked at a leisurely pace through the corridors, Harry watching the yellow-golden compass that pointed toward the location of the Sunshine Regiment, and Neville keeping a lookout just in case they ran into someone else.

Their footsteps sounded a bit thumpy, if you listened closely.

“So,” the Chaotic Lieutenant said after a while. “That’s why you had us practice dueling with all that weight strapped on?”

Harry nodded, keeping his eyes on the compass that led to Sunshine; if the apparent direction started to change quickly then they were getting close.

“I didn’t want to say anything in front of the others, but a couple of weeks isn’t a lot of time to put on extra muscle,” said Neville. “And the balance is different, and I think this weighs \emph{more} actually, and doesn’t this count as Transfiguring a Muggle artifact?”

“Nope,” Harry said. “I checked that in advance. You can see it in Hogwarts statues, so some wizards \emph{used} to wear it, even if they were just being fashionable for the Dark Ages.” And since nobody would ever try this if they \emph{weren’t} fighting first-year students using weak spells like the Sleep Hex, it didn’t count as giving away good ideas, either.

They came to a Y-intersection, an annoying one; neither corridor bent in quite the right way to take them on a direct intercept course toward where Sunshine would go as they followed the Chaos Legion following Dragon Army. So Harry chose what seemed like the better of the two options, and Neville followed.

“We’d better try a quick Silencing Charm on this stuff when we get close,” Neville said. “It’s kind of noisy, they might figure it out.”

Harry nodded, and then said “Good idea” in case Neville hadn’t been looking at him.

They trudged on through the stone-floored corridor of the upper reach of Hogwarts, lit by windows of plain glass or stained glass, now and then passing statues of witches and dragons and even the occasional wizard-knight in plate armor or chainmail.
\sbreak
The Sunshine Soldiers were striding through a long, wide corridor with their wands out and pointed. They couldn’t use the Prismatic Shield while they were maneuvering, but Parvati Patil and Jenny Rustad were currently maintaining \emph{Contegos} around the officer group, who would be the first targets of any ambush.

Their tactic for the next battle, she and her officers had decided, would be to mix directly in with the enemy soldiers as fast as possible—after having practiced among \emph{themselves} how to support one another, avoid hitting each other, and get into positions where enemy soldiers would hesitate to fire. They’d only gotten in four hours practice, but she thought her troops would already be better at that kind of mixed-in fighting than soldiers who hadn’t practiced at all. It seemed like the sort of tactic Chaos would use, but they hadn’t actually used it yet.

It was a good strategy, she believed. And yet still, no matter how much she’d lectured her soldiers, they’d persisted in whispering fearful rumors about what Harry and Neville were learning to do. Finally she’d gone off and talked with Captain Goldstein, who understood things like Troop Morale, and Anthony had suggested—

“That’s weird,” Captain Macmillan spoke up suddenly, frowning at the fiery and iridescent compasses he held in either hand. (Ernie was, as Harry would have termed it, “good at spatial visualization”, and so had been designated to hold both compasses and try to figure out what their enemies were doing.) “I think... Dragon’s not moving fast anymore... I think they got on the other side of Chaos from us first...\ and it looks like Chaos is moving to attack them instead of trying to maneuver out from in between?”

Hermione frowned, trying to understand, and she saw similar frowns on the faces of Anthony and Ron. If Chaos and Dragon attacked each other straight out, and spent all their forces fighting each other, that was practically conceding the battle to Sunshine...

“Potter thinks we’re allied so he’s attacking Malfoy now, before Dragon can link up with us,” said Blaise Zabini from the common ranks of soldiers. “Or Potter just thinks he can beat both armies in a row, if he attacks them separately.” The Slytherin boy gave a condescending sigh. “Are you going to promote me back to officer now? You lot are hopeless without me, you know.”

They all ignored the talking noises coming from Zabini’s mouth.

“We still moving in the right direction?” said Anthony.

“Yeah,” said Ernie.

“We getting close to them?” said Ron.

“Not yet—”

That was when the huge black-wooden doors at the end of the corridor flew open and crashed into the wall, revealing two figures almost completely enveloped in grey cloaks, grey cloth stretched over the faces beneath the grey hoods, one of those figures already raising a wand and pointing it directly at her.

And then the face of the game changed drastically, as Harry’s voice, high and strained with the effort, screamed the word:

“\emph{Stupefy!}”

The dueling-grade stunner blasted toward her, she was so shocked that she didn’t start to move until almost too late, as the red jet of light \emph{smashed} right through the \emph{Contego} shield to their front and she just barely dodged, there was a tingle on her arm as the red light went past her, and she saw out of the corner of her eye Susan getting hit and blown off her feet into Ron—

“\emph{Somnium!}” bellowed Anthony’s voice, followed a moment later by a dozen voices crying “\emph{Somnium!}”

Hermione frantically pushed herself to her feet, and as she rose, she saw the two figures in the grey cloaks just standing there.

You couldn’t \emph{see} Sleep Hexes, the spell was too weak—

But there was no way they all could’ve \emph{missed}.

“\emph{Stupefy!}” shrieked the voice of Neville Longbottom, and another red jet shot at her, she fell in an undignified heap as she desperately twisted out of the way, and when she scrambled up, panting, she saw that this time the stunbolt had gotten Ron where he’d been rising from the ground.

“Hello there, Sunshine,” said Harry’s voice from beneath his hood.

“We’re the Grey Knights of Chaos,” said Neville’s voice.

“We’ll be your opponents for this battle,” said Harry’s voice, “while Chaos’s \emph{other} army slaughters the Dragons.”

“And by the way,” said Neville’s voice, “we’re invincible.”
\sbreak
The two boys in their grey cloaks and robes, grey cloth over their faces, stood facing Sunshine’s entire army, seemingly unfazed by a dozen Sleep Hexes.

Daphne heard a soft sigh from beside her, and when her head turned she saw that Hannah’s lips were parted, and the Hufflepuff girl’s eyes were huge, and she was staring at—

It would have been hard to describe the jumble of thoughts that flashed through Daphne’s mind as she realized that Hannah was staring at Neville rather than Harry, which in turn seemed to trigger some part of her into noticing that in point of fact Neville \emph{had} been getting pretty interesting lately as boys went, in fact right now the Last Scion of Longbottom was seeming downright \emph{cool,} and something woke up inside her and her own lips parted and everything the Lady her Mother had ever instructed her about demure demeanors and flattery and scented shampoo blew straight out of her mind so hard it should have fluffed her hair about her ears, because she’d watched Hermione and Harry and she knew how she wanted \emph{her} own courtship to go—

Her Lady Mother had also recently instructed her on a few spells it might be embarrassing not to know if you belonged to the Noble and Most Ancient House of Greengrass.

Daphne’s wand swung to point to her left, and she shouted “\emph{Tonare!}”

The wand went over her head, and she spoke the incantation “\emph{Ravum Calvaria!}”

And finally she grasped her wand in both hands and shrieked, “\emph{Lucis Gladius!}”

The huge magical drain almost sent her to her knees, but she bore it, and when the blazing shape had fully formed and stabilized the drain was a little less.

Still, she had a feeling she’d better not try to fight with this for long.

That everyone was staring at her went \emph{quite} without saying, and she \emph{should} have leaped forward to confront Neville with her hair billowing around her, but it was all she could do to walk forward steadily to level her Most Ancient Blade at Neville Longbottom. That everyone moved aside and made way for her also went without saying.

“\emph{I hight Daphne, of the Noble and Most Ancient House of Greengrass!}” she cried. “\emph{Greengrass of Sunshine!}” The dueling forms had gone completely out of her mind, she’d seen enough plays to remember death challenges and blood challenges but she couldn’t remember at all what was appropriate for this, so she just pointed the incandescent sword toward the object of her crush and yelled, “\emph{Let’s see what you got, Nevvy!}”

Once again Harry’s voice shrieked “\emph{Stupefy!}”, and later on, when she was remembering this, she could never quite believe she’d managed to do it, but she slashed out with her blade of light like it was a Beater’s bat, and \emph{hit the stunbolt back at Harry} who just barely managed to twist out of the way.

“\emph{Tonare!}” shouted Neville, of the Noble and Most Ancient House of Longbottom. “\emph{Ravum Calvaria, Lucis Gladius!}”
\sbreak
For a few seconds, no one did anything but stare at Neville and Daphne as they started whacking at each other. They were both moving slowly, and Hermione guessed that the spell was taking a lot of strength out of them. It wasn’t very impressive by comparison, if you were a Muggleborn and you’d watched certain movies.

But you still had to give them extra credit for using lightsabers at all.

“Point of order,” said Harry’s voice. “I know the Defense Professor is watching, but I still have to ask, does anyone know whether they’ll slice each other in half if they actually hit—”

“No,” Hermione said absently. This had been in one of her history books, though she’d had no idea the magical dueling sword looked like \emph{that}. “They cast it so it’ll only stun if it touches.”

“You \emph{know} that spell?”

“Oh, no, it’s the Charm of the Most Ancient Blade, it’s only legal for Noble and Most Ancient Houses to use—”

Hermione stopped talking and looked at Harry, or Harry’s grey hood rather.

“Well,” said Harry’s voice, “I guess I could take down the rest of the Sunshine Regiment by myself, then.” She couldn’t see his face, but his voice sounded like he was smiling.

“You dodged when Daphne hit your own spell back at you,” Hermione said. “So whatever you did, you’re \emph{not} invincible. A \emph{Stupefy} can still get you.”

“Interesting theory,” said Harry’s voice from beneath the hood. “Got anyone in your army who can test it?”

“I read about the Stunning Hex once,” said Hermione. “A few months ago. I wonder if I can remember the instructions right?” Her wand came up to point at Harry.

There was a slight pause, as nearby a boy and a girl breathing in audible gasps slowly whacked at each other with lightsabers.

“Of course,” Harry said, leveling his own wand on her, “\emph{I} can just use Somnium on you. That’ll take a lot less effort.”

New \emph{Contego} shields sprung into existence in front of her, cast by Jenny and Parvati, even as Harry spoke.

The tip of Hermione’s own wand began making small motions in the air, a diamond within a circle, a diamond within a circle, rehearsing the gesture to match exactly what she remembered seeing in the book. It would be a difficult feat even for her, but she \emph{had} to cast the spell right on the first try, she couldn’t afford any failed castings that would sap her energy.

“You know,” said Hermione Granger, “I understand that it’s not really your fault, but I’m getting tired of hearing people talk about the Boy-Who-Lived like you’re—like you’re some kind of \emph{god} or something.”

“Same here, I must say,” said Harry Potter. “It’s sad how people keep underestimating me.”

Her wand kept rehearsing the diamond within the circle, over and over. Harry would be recharging his own strength, she knew, even as she practiced as much as she could before her attack. “I’m starting to think you need taking down a peg, General Chaos.”

“You could be right,” Harry said equably. His feet began to shuffle through what she recognized as a duelist’s dance. “Unfortunately there’s nothing left that can defeat me now except another Harry Potter.”

“Let me be specific, Mr.~Potter. \emph{I’m} taking you down a peg.”

“You and what other army?”

“You think you’re pretty cool, don’t you,” said Hermione.

“Why, yes,” said Harry. “Yes, I do. Some might call that arrogant, but am I supposed to be the last person in Hogwarts to notice how awesome I am?”

Hermione raised her left hand into the air, and made a fist.

It was a signal. Eight designated soldiers in her army would be pointing their wands at her, and quietly casting \emph{Wingardium Leviosa}.

They’d practiced \emph{this,} too, once Hermione had given up on lecturing her soldiers, and at Anthony’s suggestion, tried giving them a Sunshine General who \emph{looked} like she could defeat invincible enemies.

“You pretend you’re Superman,” said Hermione. She raised her left fist higher in the air, and the eight soldiers supporting her Hovered her off the ground. “\emph{Well here’s Super Hermione!}” Her hand pushed forward, and as she shot rapidly through the air toward Harry, regretting only that she couldn’t see the look on his face, her wand made a diamond within a circle and she summoned up all the magic she could, it felt like she imagined touching a live wire would feel as the too-powerful spell poured through her when her voice screamed “\emph{Stupefy!}”

The red bolt burst from her wand, perfectly formed.

Harry dodged it.

And then, because they hadn’t practiced doing this part inside of hallways, she crashed into a wall.
\sbreak
“\emph{Somnium!}” shrieked Draco, and then after only a few seconds to recharge, “\shout{Somnium, curse you!}”

He \emph{knew} he was hitting Theodore, the other boy wasn’t even trying to dodge, but the scion of Nott only grinned as evilly as his father and leveled his wand—

Draco managed to leap aside just as Theodore said “\emph{Somnium!}” but Draco was getting winded, he couldn’t keep this up, Theodore wasn’t bothering to dodge at all while Draco had to keep moving, this was \emph{crazy.}

He had enough strength now to fire again, but—

\emph{Stupidity is doing the same thing and expecting a different result,} Harry had said, this was \emph{Harry’s} work somehow, it couldn’t be a Muggle artifact anymore but Draco couldn’t figure out what it \emph{could} be, and he should be thinking of hypotheses and ways to test them but he was too busy frantically dodging as Theodore laughed and shot another Sleep Hex at him, Draco felt a little numbness in his side that time as he twisted, that had been a very very near miss and finally Draco couldn’t take it anymore, he didn’t bother working out what theory he was testing or why as he just—

“\emph{Luminos!}” shouted Draco, and Theodore was haloed in red light, “\emph{Dulak!}” and it went out again (so Theodore \emph{was} still being affected by magic), “\emph{Expelliarmus!}” and Theodore’s wand went flying (that had been a good spell to cast anyway now that Draco realized it) but Theodore was rushing toward Draco with his arms outstretched to grapple so Draco yelled “\emph{Flipendo!}” and the other boy’s feet were abruptly yanked up—

—and Theodore’s back hit the ground with a surprisingly loud and \emph{metallic}-sounding crash.

Draco’s vision was swimming now from casting four spells in such fast succession, and Theodore was already scrambling to his feet, so there wasn’t even time to think in words, but Draco still managed to say “\emph{Somnium!}” and \emph{this} time he aimed for Theodore’s face instead of the chest.

Theodore dodged (he \emph{dodged!}) and the boy shouted “\emph{Code seven on Malfoy!}”

“\emph{Prismatis!}” cried Padma’s voice and there was suddenly a shimmering rainbow wall in front of Draco, just as four Chaotic voices cried “\emph{Somnium!}”

And there was a pause, as everyone looked at the huge Prismatic Sphere protecting the remnants of Dragon Army.

Casting that fifth spell had sent Draco to his hands and knees, but he looked up and managed to say, as clearly as he could, “If the Sleep Hex—doesn’t work—aim for the face—I think the Lieutenants are wearing metal shirts.”

“You’ve already lost too many soldiers,” Finnigan said loudly from across the barrier, “we’ll beat you anyway,” and then the Gryffindor boy laughed evilly. He did the evil laughter almost as well as Harry Potter by now, and the other Chaotic Legionnaires started laughing with him soon afterward.

Draco could see from the corner of his eye where Gregory and Vincent lay unconscious. Padma was still sustaining the Prismatic Sphere, the largest one he’d ever seen her cast; but she was breathing hard, still visibly sweaty from when they’d all jogged to get into position, the Ravenclaw girl was a strong witch but not an \emph{athletic} one.

He really hoped General Granger got here soon and hit Chaos from behind. General Potter and Neville of Chaos were missing, and Draco could guess where they’d gone, but two soldiers couldn’t delay the whole Sunshine Regiment for too long all by themselves, could they?
\sbreak
She knew it wasn’t fair, that the other girl had given all she could, but Hermione still wished that Daphne had lasted longer.

“\emph{Lagann!}” said Neville’s voice from behind her as she flew, and there was the sound of a Prismatic Wall shattering, Hannah’s voice desperately cried “\emph{Somnium!}” and then a few moments later Neville’s voice calmly said “Somnium” and there was the thud of another of her soldiers falling over.

And the force keeping her in the air diminished again, Hermione could feel the grab of the Hover Charms straining at her, but now it just wasn’t enough.

Her flight stopped and she began falling in slow motion toward the ground, and she should’ve signaled her soldiers to just \emph{drop} her, but she was too angry and confused and not thinking fast enough and still trying to muster the strength for one last Stunning Hex, and so there was nowhere to go when Harry pointed his wand at her and said “\emph{Somnium}” and that was the last word that Hermione Granger heard of her battle.


