\namedpartchapter{The Stanford Prison Experiment}{TSPE}{VII}{Constrained Cognition}
\lettrine{H}{arry} had \emph{hoped} that he’d just achieved fusion with his mysterious dark side and would be enabled to draw on all of its benefits with none of its drawbacks, call up the crystal clarity and indomitable will on demand, without needing to go cold or angry.

Once again, he’d overestimated how much progress he’d made. \emph{Something} had happened, but Harry still had a mysterious dark side, it was still separate from him, and his ordinary self was still domitable. And despite the repair work he’d done on his dark side’s fear of death, he didn’t dare go dark while unshielded in Azkaban, that was tempting fate way too much.

Which was unfortunate, because a bit of nondomitability would have \emph{sure come in handy about now.}

What made it harder was that he couldn’t slump against a wall, couldn’t break into tears, couldn’t even heave a sigh. His dear Bella was watching him and that wasn’t the sort of thing her Dark Lord would do.

“My Lord—” Bellatrix said. Her low voice was strained. “The Dementors—they are coming—I can feel them, my Lord—”

“Thank you, Bella,” said a dry voice, “I already know that.”

Harry couldn’t sense the holes in the world the same way as when he’d been wearing the Deathly Hallow, but he could feel the empty pull increasing in intensity. At first he’d mistaken it for the result of descending a stairwell, until he and Bellatrix had finished descending and the pull had gone on increasing. Then decreased, as the Dementors moved away along the spiral, then increased as they went up another flight of stairs... There were Dementors within Azkaban itself now, and they were coming for him. Of course they were. Harry might be resistant now, but he was not \emph{hidden.}

\emph{New requirement,} Harry told his brain. \emph{Find a way of defeating Dementors that doesn’t invoke my Patronus Charm. Alternatively, find yet another way of hiding someone from Dementors, besides the Cloak of Invisibility—}

\emph{I quit,} said his brain. \emph{Find yourself another piece of computing substrate to solve your ridiculously overconstrained problems.}

\emph{I mean it,} thought Harry.

\emph{So do I,} said his brain. \emph{Put up your Patronus Charm and wait for the Aurors to find you. Be sensible. It’s over.}

\emph{Give up...}

The sucking emptiness seemed to pull harder, as he thought it; and Harry realized what was happening, concentrated more intensely on the stars, turned his mind away from the despair—

\emph{You know,} observed the logical side of him, \emph{if you’re not allowed to think} any \emph{negative thoughts because that will open your mind to the Dementors,} that’s\emph{ a cognitive bias too, how would you know if it actually} was\emph{ time to give up?}

A desperate sobbing scream rose up from below, words mixed in like “no” and “away”. The prisoners knew, the prisoners could feel it.

The Dementors were coming.

“My Lord, you—you should not risk yourself for me—take back your Cloak—”

“Be silent, fool,” hissed an angry voice. “When I decide to sacrifice you I will tell you so.”

\emph{She’s got a valid point,} said Slytherin. \emph{You} shouldn’t\emph{ risk yourself for her, there’s no way her life is as valuable as yours.}

For an instant Harry considered sacrificing Bellatrix to save himself—

And in that moment, some of the dim orange gas-light seemed to flee the corridor, a touch of cold crept over Harry’s fingertips. And he knew, then, that to think of leaving Bellatrix to the shadows of Death, would make him vulnerable once more. Even in the moment of making the decision, he might become unable to cast the Patronus Charm, for he would have given up the thought that had saved him before.

It occurred to Harry that he could still take the Cloak from Bellatrix afterward, even if he couldn’t cast the Patronus Charm; and then he had to wrench his thoughts away from that option, focus firmly on his decision \emph{not} to do it, or he might have just fallen over where he stood. For the whirlpool of emptiness swirling around him was now deadly strong; there were screams coming from \emph{above}, and the screams below had stopped.

\emph{This is ridiculous,} said his logical side. \emph{Rational agents shouldn’t have to put up with this sort of censored reasoning process, all the theorems assume that how you think doesn’t affect reality apart from your actual actions, which is why you’re free to choose an optimal algorithm without worrying about how your thoughts interact with Dementors—}

...

\emph{That is a really dumb idea,} said Gryffindor. \emph{Even I think it’s a dumb idea and I’m your Gryffindor side. You’re not seriously going to just stand there and—}
\sbreak
“We have a fix!” shouted Ora, holding up her magic mirror as though in triumph. “The Dementor outside the inner wall pointed to level seven, C spiral, that’s where they are!”

Her Aurors were looking at her expectantly.

“No,” Amelia said in a level voice. “That’s where \emph{one} of them is. The Dementors still can’t find Bellatrix Black. We are not running down there and letting her through in the confusion, and we are not dividing our forces to be ambushed. So long as we move with caution, we can’t lose. Tell Scrimgeour and Shacklebolt to keep going down level by level, same as before—”

The old wizard was already striding forward. Amelia didn’t even bother cursing him, this time, as once again their carefully constructed shields parted like water and rippled gently in his wake.
\sbreak
Harry waited at the beginning of the corridor, just next to the stairs leading upward. Bellatrix and the snake were behind him, concealed by the Deathly Hallow that Harry had mastered; he knew, though he could not see, that the emaciated sorceress was sitting upon the stairs, slumped back, since Harry had withdrawn his Hover Charm to free up his mind and magic.

Harry’s eyes were fixed on the far end of the corridor, next to the stairs that led downward. Not in his mind now, but in true reality, the light in the corridor had dimmed, the temperature had fallen. The fear thundered over him and around him like a sea whipped by hurricane winds, and the sucking emptiness had become a howling draw toward some approaching black hole.

Up the stairs at the far end, floating smoothly through the dying air, came the voids, the absences, the wounds in the world.

And Harry expected them to stop.

With all the will and focus he could muster, Harry \emph{expected them to stop.}

Anticipated their stopping.

Believed they would stop.

...that was the idea, anyway...

Harry shut down the dangerous stray thought, and \emph{expected the Dementors to halt.} They had no intelligence of their own, they were just wounds in the world, their form and structure was borrowed from others’ expectations. People had been able to negotiate with them, offer them victims in exchange for cooperation, only because they \emph{believed Dementors would bargain.} So if Harry believed hard enough that the voids would turn and go, they would turn and go.

But the wounds in the world kept coming, the swirling fear seemed like a solid thing now, the emptiness tearing at matter as well as mind, substance as well as spirit, you could see the metal beginning to tarnish as the holes in the world passed.

A small sound came from behind him, from Bellatrix, but she said no word, for she had been instructed to remain silent.

\emph{Don’t think of them as creatures, think of them as psychosensitive objects, they can be controlled if I can control myself—}

The problem was that he \emph{couldn’t} control himself so easily, couldn’t make himself believe blue was green by an act of will. Couldn’t suppress all those thoughts about how irrational it was to \emph{make} yourself believe something. How \emph{impossible} it was to trick yourself into believing something if you \emph{knew} that was what you were doing. All the training Harry had given himself against self-deception was refusing to switch off \emph{no matter how harmful it was in this unique special case—}

The shadows of Death crossed the halfway point of the corridor, and Harry held up his hand, fingers spread, and said in a voice of firm and confident command, “Stop.”

The shadows of Death stopped.

Behind Harry, Bellatrix gave a strangled gasp, like it was being torn out of her.

Harry gestured to her, the signal he had set up in advance which meant, \emph{repeat what you heard the Dementors say.}

“They say,” Bellatrix said, her voice was shaking, “they said, ‘Bellatrix Black was promised us. Tell us where she hides, and you will be spared.’”

“Bellatrix?” Harry said, making his voice sound amused. “She escaped a while ago.”

A moment later, Harry realized that he should have said that Bellatrix was among the Aurors in the top level, that would have caused more confusion—

No, it was wrong to think of the Dementors as trickable, they were merely \emph{things,} they were controlled only by \emph{expectations—}

“They say,” Bellatrix said in a cracked voice, “they say they know you’re lying.”

The voids began to move forward again.

\emph{Her anticipations are more solidly believed than mine; she is controlling them, unwittingly—}

“Don’t resist,” Harry said, pointing his wand behind him.

“I, I love you, farewell, my Lord—”

“\emph{Somnium.}”

It had helped, strangely enough, hearing those particular awful words, understanding Bellatrix’s mistake; it reminded Harry why he was fighting.

“Stop,” Harry said again. Bellatrix was asleep; now only his own will, his own expectations rather, should control those spheres of annihilation—

But they kept on gliding forward, and Harry couldn’t stop himself from worrying that the previous experience had damaged his confidence, which meant that he \emph{wouldn’t} be able to stop them, and as he noticed himself thinking that, he doubted even more—he needed more time to prepare, really ought to practice controlling just one Dementor in a cage first—

There was only a quarter of corridor now between Harry and the shadows of death, the empty winds were so strong that Harry could feel the erosion beginning in the cracks of himself.

And the thought came to Harry that maybe he was wrong, maybe Dementors \emph{did} have their own desires and planning capability. Or maybe they were controlled by how \emph{everyone} thought they worked, not just whoever was closest to them. And in either case—

Harry drew up his wand into the starting position for the Patronus Charm, and spoke.

“One of your number went to Hogwarts and did not return. It no longer exists; that Death is dead.”

The Dementors halted, a dozen wounds in the world stood motionless, while the emptiness screamed around them like a deadly wind to nowhere.

“Turn and go and do not speak of this to anyone, little shadows, or I will destroy you as well.”

Harry’s fingers slid into the starting position for the Patronus Charm, and readied himself to cast it; in his mind, the Earth shone among the stars, the day side bright and blue with reflected sunlight, the night side glimmering with the light of human cities. Harry wasn’t bluffing, wasn’t trying to do anything tricky with his thoughts. The shadows of Death would move forward and be annihilated, or they would depart, he was equally ready for either...

And the voids retreated back as smoothly as they came, the winds of nothingness lessening with each meter they traversed, as they slid back down the stairs, and departed.

Whether they truly had their own pseudo-intelligence, or whether Harry had finally succeeded in \emph{expecting} them to go...\ that, Harry didn’t know.

But they were gone.

Harry took a moment to sit down beside the unconscious Bellatrix on the stairs, and slumped down as she was slumped, closing his eyes for a moment, only a moment, he sure as hell wasn’t planning to sleep in Azkaban, but he needed to take that moment. The Aurors would still be going down the stairs slowly, Harry hoped, so it wouldn’t hurt to take just five minutes to rest. Harry was careful to keep his thoughts positive, cheerful, \emph{my, I’ll just have some nice regenerative rest here, and then I’ll feel better,} rather than, say, \emph{my, I’ll just collapse in emotional and physical exhaustion,} because the Dementors hadn’t yet retreated very far.

\emph{And by the way,} Harry said to his brain, \emph{you’re fired.}
\sbreak
“I found him!” cried the old wizard’s voice.

\emph{Who?} thought Amelia, as she turned to see Dumbledore’s return, carrying in his arms—

—the one sight, the one person, she would never have expected to behold—

—a man in torn red robes, looking scorched like he’d fought a small war, blood dried on many cuts. His eyes were open, and he was chewing on a bar of chocolate, held in his one living hand.

Bahry One-Hand was \emph{alive.}

A glad cry went up, her Aurors lowering their wands, some of them already starting to rush forward.

“\emph{Stay on guard!}” bellowed Amelia. “Check them both for Polyjuice—scan Bahry for small Animagi or traps—”
\sbreak
“\emph{Innervate. Wingardium Leviosa.}”

There was a pause. Harry sensed, though he could not quite see, that the invisible woman was pushing herself to her feet, and turning her head to look around. “I’m...\ alive...?”

Harry was sorely tempted to say no, just to see what she made of that. Instead he hissed, “Don’t ask stupid questions.”

“What happened?” whispered Bellatrix.

And the Dark Lord gave a wild, high-pitched laugh, and said, “I scared the Dementors away, my dear Bella.”

There was a pause. Harry wished he could see Bellatrix’s face; had he said the wrong thing?

After a time, in a quavering voice, “Could it be, my Lord, that in your new form, you have begun to care for me—”

“No,” Harry said coldly, and turned from her (though he kept his wand on her), and began walking. “And take care that you do not offend me again, or I will abandon you here, use or no use. Now follow, or be left behind; I have work to do.”

Harry strode forward, not listening to the gasping sounds that came from behind him; he knew Bellatrix was following.

...because the last thing that woman needed, the very last thing she needed to start thinking before the psychiatric healer began trying to deprogram her, was to believe that her Dark Lord could ever love her back.
\sbreak
The old wizard smoothed his silver beard contemplatively, looking at where Auror Bahry was being carried out of the room by two strong Aurors.

“Do you understand this, Amelia?”

“No,” she said simply. She suspected some trap they hadn’t yet been able to fathom, which was why Auror Bahry was going to be kept outside the main party and guarded.

“Perhaps,” the old wizard said at length, “whichever of their number can cast the Patronus Charm, is more than a simple hostage. Someone who was tricked into this, mayhap? For whatever reason, they left your Auror alive; let us not be the first to wield deadly curses, when we find them—”

“I see,” said the old witch in sudden realization, “\emph{that} was their plan. It costs them nothing to Oblivate him and leave him alive, and makes \emph{us} hesitate—” Amelia nodded decisively, and said to her people, “We carry on as before.”

The old wizard sighed. “Any news from the Dementors?”

“If I tell you,” Amelia snapped, “will you run off again?”

“It costs you nothing, Amelia,” the old wizard said quietly, “and may save one of your own people the fight.”

\emph{Costs me nothing except my chance at vengeance—}

But that was nothing compared to the other, the annoying old wizard was often right in the end, it was part of what made him so annoying.

“The Dementors have ceased to answer questions about the other person they said they saw,” Amelia told him, “and they will not say why, nor where.”

Dumbledore turned to the blazing silver phoenix on his shoulder, whose light illuminated the whole corridor, and received a silent headshake in reply. “I cannot detect them either,” said Dumbledore. Then he shrugged. “I suppose I shall just walk the whole spiral from top to bottom and see if anything turns up, shall I?”

Amelia would have ordered him not to do it, if she thought that would have made the tiniest difference.

“Albus,” said Amelia as the old wizard turned to depart, “even you can be ambushed.”

“Nonsense, my dear,” the old wizard said cheerfully as he strode off yet again, waving as though in admonition his fifteen-inch wand of unidentifiable dark-grey wood, “I’m invincible.”

There was a pause.

(“He didn’t just really say that—” whispered the newest Auror present, a still-prim young lady by the name of Noelle Curry, to the senior member of her trio, Auror Brooks. “Did he?”)

(“He can get away with it,” Isabel whispered back to her, “he’s \emph{Dumbledore,} not even Fate takes him seriously anymore.”)

“And that,” Amelia said heavily, for the benefit of the younger Aurors, “is why we never call him in on anything unless we absolutely must.”
\sbreak
Harry lay very still on the hard bench that served as the bed of this cell, a blanket pulled over him, staying as absolutely motionless as he could while he waited for the fear to return. There was a Patronus approaching, and a powerful one. Bellatrix was hidden by a Deathly Hallow, no easy Charm would penetrate that; but Harry did not know what other arts the Aurors might employ to detect his own self, and dared not reveal his ignorance by asking her. So Harry lay on a hard bed, in a cell with a locked door, and the mighty metal door locked behind him, in absolute darkness, with a thin blanket pulled over him, hoping that whoever it was wouldn’t look in, or wouldn’t look too closely if they did—

That wasn’t a point Harry could affect, really, that part of his fate lay entirely in the hands of the Hidden Variables. Most of his mind was concentrating on the ongoing Transfiguration he was performing.

Listening in the silence, Harry heard the quick footsteps approach; they paused outside his door, and then—

—continued onward.

Soon the fear returned.

Harry didn’t allow himself to notice his own relief, any more than he allowed himself to notice the fear. He was holding in his mind the form of a Muggle device rather larger than a car battery, and slowly applying that Form to the substance of an ice cube (which Harry had frozen using \emph{Frigideiro} on water from a bottle in his pouch). You weren’t supposed to Transfigure things to be burned, but between the original substance being water, and the Bubble-Head Charm to protect their air supply, Harry hoped that this wouldn’t make him or anyone else sick.

Now it was just a question of whether there would be enough time before the Aurors did a detailed check on this cell block, for Harry to finish this Transfiguration, and the partial Transfiguration he would do after that—
\sbreak
When the old wizard strode back empty-handed, even Amelia began to feel a twinge of worry. She and the other two Auror teams had worked a third of the way down the three spirals, in synchrony so as not to allow any gap in their coverage that could be jumped by cutting through a ceiling, and they’d yet to find any sign.

“Might I ask you to report?” Amelia said, keeping the edge out of her voice.

“First a simple walk from top to bottom,” said the old wizard. He was frowning, wrinkling his face even more than usual. “I examined Bellatrix’s cell, and found a death doll left in her place. This escape was meant to go unremarked, I think. There is something hidden in the corner beneath a scrap of cloth; I left that undisturbed for your Aurors to examine. On the return trip, I opened each door and looked within the cells. I saw nothing Disillusioned, only the prisoners—”

They were interrupted by a scream from the red-golden phoenix, and all her Aurors flinched from it. Condemnation was in it, and an urgent demand that almost started Amelia running from the corridor on the spot.

“—in rather distressing condition,” Dumbledore said quietly. For a moment the blue eyes were very cold beneath the half-moon glasses. “Will any of you speak to me of the consequences of their actions?”

“\emph{I} did not—” Amelia began.

“I know,” said the old wizard. “My apologies, Amelia.” He sighed. “Some of the more recent prisoners had scraps of their magic left, when I looked upon them, but I sensed no uneaten power; the strongest had only as much magic left as a first-year child. I heard Fawkes scream in distress many times, but never challenge. It seems you shall have to continue your search; they can hide well enough to escape my mere glance.”
\sbreak
When Harry finished his first Transfiguration, he sat up, pulled back the blanket that had covered him, cast a quick \emph{Lumos,} glanced at his watch, and was shocked to see that nearly an hour and thirty minutes had passed. How much of that time had gone by since someone had opened the door and then closed it again—Harry hadn’t been looking in that direction, of course—that, Harry couldn’t guess.

“My Lord...?” whispered Bellatrix’s voice, soft and very tentative.

“You may speak now,” Harry said. He’d told her to remain silent while he worked.

“That was Dumbledore who looked upon us.”

Pause.

“Interesting,” Harry said neutrally. He was glad he had not noticed this at the time. That sounded like a \emph{rather close shave}.

Harry said a word to his pouch, and began drawing forth the magical device that he would mate to the product of his hour’s labor. Then, when that was drawn forth, another word brought forth a tube of industrial-strength glue; before using it, Harry cast the Bubble-Head Charm on himself and Bellatrix, and had Bellatrix cast the same Charm on the snake, so that the glue fumes in the enclosed cell would not harm them.

When the glue had begun to set, binding technology to magic, Harry laid it down upon the bed, and sat down on the floor, resting his magic and will for a moment before essaying the next Transfiguration.

“My Lord...” Bellatrix said hesitantly.

“Yes?” said the dry voice.

“What is that device you made?”

Harry thought rapidly. It seemed like a good chance to check his plans with her, under the guise of leading questions.

“Consider, my dear Bella,” said Harry smoothly. “How difficult is it for a powerful wizard to cut the walls of Azkaban?”

There was a pause, and then Bellatrix’s voice came, slow and puzzled, “Not difficult at all, my Lord...?”

“Indeed,” said the dry, high voice of Bella’s master. “Suppose one were to do this, and fly through the hole on a broomstick, and soar up and away. Rescuing a prisoner from Azkaban would seem easy then, would it not?”

“But my Lord...” said Bella. “The Aurors would—they have their own broomsticks, my Lord, fast ones—”

Harry listened, it was as he had thought. The Dark Lord replied, again in tones of smoothly Socratic inquiry, and Bellatrix asked a further question, which Harry had not expected, but Harry’s own counterquestion showed that it should not matter in the end. And in response to Bellatrix’s last question, the Dark Lord only smiled, and said that it was time for him to resume his work.

And then Harry got up from the floor of the cell, went to the far end of the cells, and touched his wand to the hard surface of the wall—the wall of Azkaban, the solid metal that separated them from direct exposure to the Dementors’ pit.

And Harry began a partial Transfiguration.

This spell would go faster, Harry hoped. He’d spent hours and hours practicing the unique magic, which had made it routine, not much more difficult for him than ordinary Transfiguration. The shape he was changing had not all that much total volume, the Transfigured shape might be tall and wide and long, but it was very thin. Half a millimeter, Harry had thought, would be enough, considering the perfect smoothness...

On the long bench that served as a prison bed, where Harry had set down the Transfigured technological device and the mated magic item for the glue to dry, tiny letters in golden script gleamed on the Muggle artifact. Harry hadn’t really \emph{planned} for them to be there, but they’d kept running through the back of his mind, and so seemed to have become part of the Transfigured form.

Ther were many different things Harry could have said before using this particular triumph of technological ingenuity. Any number of things that would be, in one sense or another, appropriate. Or at least things that Harry \emph{could} have said, \emph{would} have said, if Bellatrix had not been there.

But there was only one thing to say, that Harry would only get the chance to say just this once, and probably never get a better chance to say ever again. (Or \emph{think,} anyway, if he couldn’t say it.) He hadn’t seen the actual movie, but he’d seen a preview, and for some reason the phrase had stuck in his mind.

The tiny golden letters upon the Muggle device said,

\emph{All right, you primitive screwheads! Listen up!}

