\chapter{End-of-year Exam}

\lettrine{T}{he} gibbous moon riding higher in the cloudless sky, the stars and wash of the Milky Way visible in all their majesty within the darkness: all these illuminated thirty-seven skull masks gleaming above black robes, and the darker-clad Lord Voldemort, whose eyes shone red.

“Welcome, my Death Eaters,” spoke Lord Voldemort’s voice, smooth and high and terrible. “No, do not look at me, you fools! Eyes upon the Potter child! Ten years, it has been, ten years since we last met. Yet you answer my call as though it were yesterday…” The Dark Lord Voldemort came near to one hooded figure, tapped fingers upon the mask. “In a hastily Transfigured \emph{mockery} of a Death Eater’s true armour, with a childish Charm to distort your voice. Explain, Mr~Honour.”

“Our old masks and robes…” said the robe whose mask the Dark Lord had tapped. Even through the distorting timbre of the mask, the fear in it was audible. “We…we were not fighting in them, Master, with you gone…so I did not maintain their enchantments…and then you summoned me to appear here, masked, and I…I always held faith in you, Master, but I did not know you would return this very day…I am truly sorry to have displeased you…”

“Enough.” The Dark Lord moved on to stand behind another figure, that seemed to tremble, though it kept its mask facing the Boy-Who-Lived, and its wand held level. “I might think more kindly of such neglect, if you had pursued my agenda by other means…Mr~Counsel. Yet I return to find—what? A country conquered in my name?” The high voice climbed higher. “No! I find you playing ordinary politics in the Wizengamot! I find your brothers still abandoned in Azkaban! It is a disappointment to me…I confess myself disappointed…You thought I was gone, the Dark Mark dead, and you forsook my purpose. Is that right, Mr~Counsel?”

“No, Master!” cried that masked figure. “We knew you would return—but, but we could not fight Dumbledore without you—”

“\emph{Crucio.}”

A horrible scream tore out of the mask, piercing the night, it continued for long, long seconds.

“Get up,” the Dark Lord said to the figure that had collapsed upon the ground. “Keep your wand on Harry Potter. \emph{Do not lie to me again.}”

“Yes, Master,” sobbed the figure, as it pushed itself to its feet.

Voldemort resumed pacing behind the black-robed figures. “I suppose you are also wondering what Harry Potter is doing here…Why he is a guest at my rebirthing party.”

“I know, Master!” said one of the robes. “You mean to prove your power by killing him, in front of us all, to leave no doubt as to which of you is stronger! To show how your Killing Curse can slay even this so-called Boy-Who-Lived!”

There was a pause. None of the cloaked figures dared to speak.

Slowly, the Dark Lord Voldemort, in his high-collared shirt and dark robes, turned to face the Death Eater who had spoken.

“That,” whispered Voldemort in a voice chill as death, “is a little too much folly for me to credit, Mr~Sallow. You heard that theory of how I died, and tried to provoke me into repeating a mistake?” Lord Voldemort was floating, rising high off the ground. “I suppose you came to prefer your laziness to my mastery, \emph{Macnair?}”

The Death Eater who’d spoken was suddenly surrounded by a blue haze. He spun, slashed his wand at the Dark Lord, and cried “\emph{Avada Kedavra!}”

Voldemort simply tilted to one side in mid-air, dodging the green bolt.

“\emph{Avada Kedavra!}” cried the Death Eater. His hand that didn’t hold a wand was making other gestures, further colours and layers building up in his shielding haze with each gesture completed. “Help me, my brothers! If we all—”

The Death Eater fell in seven flaming pieces to the ground, chunks of flesh with the cauterized edges still glowing.

“Eyes and wands on Harry Potter, all of you,” Voldemort repeated, his voice low and dangerous. “And Macnair acted in sheer stupidity just then, for I command your Marks, as I \emph{always} shall. \emph{I am immortal.}”

“Master,” said another robe. “The girl upon the altar—is she to serve us for a Dark Revel? She seems unworthy of such a joyous occasion. I could find better, Master, if you give me leave for just a short time—”

“No, Mr~Friendly,” said Voldemort, sounding rather amused. “The little witch you see upon the altar is none other than Hermione Granger—”

“What?” cried one of the black robes, and then, “I’m sorry, Master, I’m sorry, I beg your—”

“\emph{Crucio.}” This screaming only lasted a few seconds, and Voldemort had performed it as though it were perfunctory. Afterwards Voldemort’s voice returned to low amusement. “I have resurrected this mudblood through the Darkest of magics, for my own purposes. You shall not offer her the slightest trouble, any of you. You are better off dead than if I learn my little experiment came to harm at your hands. This order is absolute, regardless of other circumstances—even if she escapes, let us say.” A cold high laugh, as if at some joke that nobody else understood.

“Master,” one of the robes said in a faltering voice distorted by his skull mask. “Master, please—I would never defy you, I am obedient as you see—but Master, I beg you, let me return, the better to serve you later—I came here in haste, forsaking—Master, with so many of us being gone, others will wonder, they will mark the absences, who has disappeared. Soon there shall be no alibi I can offer.”

A cold high laugh. “Ah, Mr~White, the most delinquent of my servants. I have not yet decided if you will survive your punishment. I have less need of you than I once did, Mr~White. In two days’ time the Death Eaters shall walk openly. My powers have increased, and I have just this day disposed of Dumbledore.” More gasps of shock arose from the Death Eaters, Voldemort paid them no heed. “Tomorrow I shall slay Bones, Crouch, Moody, and Scrimgeour, if they have not fled. The rest of you shall go into the Ministry and the Wizengamot, and cast Imperius Curses as I direct you. We are \emph{finished} waiting. By tomorrow’s nightfall I shall have declared myself Lord Ruler of Britain!”

Intakes of breath rose from the gathered masks, but one figure was laughing.

“You find me amusing, Mr~Grim?”

“Apologies, Master,” said the robed figure who had laughed, his wand perfectly level upon where Harry stood. “I was glad to hear you had dispatched Dumbledore. I fled from Britain in cowardly fear of him, having lost faith in your return.”

Voldemort’s chuckle resounded within the graveyard. “Your candour earns you my mercy, Mr~Grim. I was surprised to see you here tonight; you are more competent than I suspected. But before we turn our attention to happier matters, there is a certain affair to which we must attend. Tell me, Mr~Grim, if the Boy-Who-Lived swore an oath to you, might you trust him?”

“Master…I don’t understand…” said Mr~Grim. One or two of the other Death Eaters turned their masks toward Voldemort before quickly fixing the skull gaze on Harry.

“Answer me,” Voldemort hissed. “This is not a trick, Mr~Grim, and you \emph{will} answer truthfully or bear the consequences. You knew the boy’s forebears, did you not? Knew them for straightforward folk? If the boy freely chose to swear to you an oath, even knowing you for a Death Eater, might you trust in his words? Answer me!” Voldemort’s voice rose to a shriek.

“I…yes, Master, I suppose I might…”

“Good,” Voldemort said coldly. “The potential for trust must exist, to be sacrificed. And for the bonder of the Unbreakable Vow…which of you shall sacrifice their magic? It shall be quite the long Vow…much longer than usual…much magic shall be required for that…” Voldemort smiled his awful smile. “Mr~White shall do.”

“No, please! \emph{Master, I beg you!} I served you better than any—as best I could—”

“\emph{Crucio,}” said Voldemort, and Mr~White screamed through his mask’s distortion for what seemed like a full minute. “Be grateful if I leave you your life! Now approach the boy, Mr~Grim, Mr~White. From behind him, idiot! You must not block the others’ wands! And the rest of you, you must fire if Harry Potter tries to run, even if it means striking at your fellow Death Eaters.”

Mr~White took time to approach, the black robes seeming to shake, even as Mr~Grim moved smoothly into position.

“What is to be the Vow, Master?” came the voice of Mr~Grim.

“Ah, yes,” Voldemort said. The Dark Lord went on pacing behind the semicircle of Death Eaters. “Today—though I hardly expect even you to believe me—today we are doing Merlin’s work, my Death Eaters. Yes! Before us stands a great danger, who in his blundering folly has been prophesied to wreak destruction such as even I can scarcely imagine. The Boy-Who-Lived! The boy who frightens \emph{Dementors!} The cattle who believe they own this world should have been more worried when they saw that. Useless, all of them!”

“Forgive me—” said one black robe in a halting voice. “Master—surely, if that is so—Master, why don’t we just kill him right away?”

Voldemort laughed, a strange bitter laugh. When he spoke on his high voice was precise. “Here is the oath’s intent, Mr~Grim, Mr~White, Harry Potter. Listen well and comprehend the Vow that must be sworn, for its intent is also binding, and you three must share an understanding of its meaning. You will swear, Harry Potter, not to destroy the world, to take no risks when it comes to not destroying the world. This Vow may \emph{not} force you into any positive action, on account of that, this Vow does not force your hand to any stupidity. Do you understand that, Mr~Grim, Mr~White? We are dealing with a prophecy of destruction. A \emph{prophecy!} They can fulfil themselves in twisted ways. We must be cautious that this Vow itself does not bring that prophecy about. We dare not let this Vow force Harry Potter to stand idly after some disaster is already set in motion by his hand, because he must take some lesser risk if he tries to stop it. Nor must the Vow force him to choose a risk of truly vast destruction, over a certainty of lesser destruction. But all Harry Potter’s \emph{foolishness,}” Voldemort’s voice climbed, “all his \emph{recklessness,} all his \emph{grandiose schemes} and \emph{good intentions}—he shall not risk them leading to disaster! He shall not gamble with the Earth’s fate! No researches that might lead to catastrophe! No unbinding of seals, no opening of gates!” Voldemort’s voice lowered again. “Unless this very Vow itself is somehow leading into the destruction of the world, in which case, Harry Potter, you must ignore it in that particular regard. You will \emph{not} trust yourself alone in making such a determination, you must confide honestly and fully in your trusted friend, and see if that one agrees. Such is this Vow’s meaning and intent. It forces only such acts as Harry Potter might choose himself, having learned that he is a prophesied instrument of destruction. For the capacity for choice must also exist, to be sacrificed. Do you understand, Mr~White?”

“I—I think so—oh, Master, \emph{please,} do not let the Vow be so long—”

“Silence, fool, you do a more useful thing this day than you have ever done. Mr~Grim?”

“I think, Master, that it must be repeated to me.”

Voldemort smiled that too-wide smile, and said it all again using different words.

“And now,” Voldemort said coldly, “Harry Potter, you will keep your wand low, and permit Mr~Grim to touch his wand to yours; and you will speak such words as I direct you. If Harry Potter speaks any other word, then cut him down, the rest of you.”

“Yes, Master,” came the thirty-four-fold chorus.

Harry was chilled, and shivering, and not only because he was naked in the night. He didn’t understand why Voldemort was \emph{not} just killing him. There seemed to be only a single line leading into the future, and it was Voldemort’s chosen line, and Harry did not know what came after this.

“Mr~White,” said Voldemort. “Touch your wand to Harry Potter’s hand, and repeat these words. Magic that flows in me, bind this Vow.”

Mr~White spoke those words. Even through the distortion effect of his mask, it sounded as though his heart were breaking.

Behind Voldemort the obelisks chanted, a language that Harry did not know; three times they repeated their words, then fell silent.

“Mr~Grim,” said Voldemort. “Think of the reasons why you might trust this boy, if he had given this oath freely. Think of that potential for trust, and \emph{sacrifice} it as you say…”

“By my trust that I hold for you,” said Mr~Grim, “be you held.”

And then it was Harry Potter’s turn to repeat Lord Voldemort’s words, and Harry did so.

“I vow…” Harry said. His voice shook, but he spoke. “That I shall not…by any act of mine…destroy the world…I shall take no chances…in not destroying the world…if my hand is forced…I may take the course…of lesser destruction over greater destruction…unless it seems to me that this Vow itself…leads to the world’s end…and the friend…in whom I have confided honestly…agrees that this is so. By my own free will…” Harry could feel it, as the rite was invoked, the shining cords of power wrapping around his wand and Mr~Grim’s wand, wrapping around his hand where Mr~White’s wand touched it, wrapping around his \emph{self} on some disturbingly abstract level. Harry could feel himself \emph{invoking} his power of free choice, and he knew that his next words would \emph{sacrifice} it, that this was absolutely the last chance to turn back.

“…so shall it be,” said the coldly precise voice of Lord Voldemort.

“…so shall it be,” Harry repeated, and he knew in that moment that the content of the Vow was no longer something he could decide whether or not to do, it was simply the way in which his body and mind would move. It was not a vow he could break even by sacrificing his life in the process. Like water flowing downhill or a calculator summing numbers, it was just a thing-Harry-Potter-would-do.

“Did the Vow take, Mr~White?”

Mr~White sounded like he was weeping. “Yes, Master…I have lost so much, please, I have been punished enough.”

“Return to your places…” said Voldemort. “Good. All eyes on the Potter child, prepare to fire the instant he tries to flee, or raise his wand, or speak any word…” The Dark Lord floated high in the air, the black-clad figure overlooking the graveyard. Again he held a gun in his left hand, and his wand in his right. “Better. \emph{Now} we shall kill the Boy-Who-Lived.”

Mr~White staggered. Mr~Grim was laughing again, and so were others.

“I did not do that to be funny,” Voldemort said coldly. “We are dealing with a \emph{prophecy}, fools. We are snipping the threads of destiny one by one; carefully, carefully, not knowing when we may first encounter resistance. This is the order in which the next acts shall be done. First Harry Potter shall be stunned, then his limbs severed and the wounds cauterized. Mr~Friendly and Mr~Honour will examine him for any trace of unusual magics. One of you shall shoot the boy many times with my Muggle weapon, and then as many of you as can shall strike him with the Killing Curse. Only then will Mr~Grim crush his skull and brains with the mundane substance of a tombstone. I shall verify his corpse, then his corpse shall be burned with Fiendfyre, then we will exorcise the surrounding area in case he has left a ghost. I myself will guard this place until six hours have passed, for I do not fully trust the wards I have set against Time’s looping; and four of you shall search the surroundings for signs of anything noteworthy. Even after that we must remain vigilant for any sign of Harry Potter’s renewed presence, in case Dumbledore has left some unimagined trick in play. If you can think of any trick that I have missed in being sure that Harry Potter’s threat is ended, speak now and I shall reward you handsomely…speak now, in Merlin’s name!”

There was stunned silence amid the cemetery; no one made to speak.

“Useless, the lot of you,” Voldemort said with bitter scorn. “Now I shall ask Harry Potter one final question, and he is to answer that question for my ears alone, in Parseltongue. Strike the boy down at once if he answers with anything but hisses, if he tries to speak one word of human speech.” Then Voldemort hissed, “\parsel{Power I know not, it was said that you would have. The Muggle Arts I have now learned of from you, and I am already studying them. Your power over life-eaters must be comprehended for oneself, or so you say. If there is any other power you possess, that I may come to have, tell me of it now. Else, I intend to torment certain of those you care for. Some lives I have already promised you, but others I did not. Your mudblood servants in your little army. Your precious parents. All shall suffer for what will seem to them like eternities; and then I shall send them, broken, into the life-eater prison to remember it, until they waste and die. For each unknown power you tell me how to master, or other secret you tell me that I desire to know, you may name one more of those to instead be protected and honoured under my reign. This also I promise and intend to keep.}” Voldemort’s smiling expression now came through as if it were a snake’s gaping fangs, and the meaning that expression bore among snakes, a promise that whoever beheld the teeth was to be consumed by them. “\parsel{Waste not time in thoughts of escape, if you care for those ones. You have sixty seconds to begin telling me something I wish to know, and then your death begins.}”

%  LocalWords:  Grim’s
