\chapter{Self Centeredness}
\lettrine{P}{adma} Patil had finished her dinner a little late, getting on toward seven-thirty, and was now striding quickly out of the Great Hall on her way to the Ravenclaw dorm and the study rooms. Gossiping was fun and destroying Granger’s reputation was more fun, but it could distract from schoolwork. She’d put off a six-inch essay on \emph{lomillialor} wood due in next morning’s Herbology class, and she needed to finish it tonight.

It was while she was passing through a long, twisting, narrow stone corridor that the whisper came, sounding like it was coming from right behind her.

“\emph{Padma Patil...}”

She spun around quick as lightning, her wand already snatched up from a pocket of her robes and leaping into her hands, if Harry Potter thought he could sneak up on and scare \emph{her} that easily—

There was no one there.

Instantly Padma spun around and looked in the other direction, if it had been a Ventriloquism Charm—

There was no one there, either.

The whispering sigh came again, soft and dangerous with a slight hissing undertone.

“\emph{Padma Patil, Slytherin girl...}”

“Harry Potter, Slytherin boy,” she said out loud.

She’d fought Potter and his Chaos Legion a dozen times over, and she \emph{knew} that this was Harry Potter doing this somehow...

...even though the Ventriloquism Charm was only line-of-sight, and in the winding corridor, she could easily see all the way to the nearest twist both forward and backward, and there was no one there...

...it didn’t matter. She knew her enemy.

There was a whispery chuckle, now coming from beside her, and she spun around and pointed her wand at the whisper and shouted “\emph{Luminos!}”

The red bolt of light shot out and struck the wall, which lit with a crimson glow that soon faded.

She hadn’t really expected it to work. Harry Potter couldn’t \emph{possibly} be invisible, not really invisible, that was magic most \emph{grownups} couldn’t do, and she’d never believed nine-tenths of the stories about him.

The whispery voice laughed again, now on her other side.

“Harry Potter stands on the precipice,” whispered the voice, now sounding very close to her ear, “he is wavering, but you, you are already falling, Slytherin girl...”

“The hat never called out Slytherin for \emph{my} name, Potter!” She backed up against the wall, so she wouldn’t have to watch behind herself, and raised her wand in an attack stance.

Again the soft laugh. “Harry Potter has been in the Ravenclaw common room for the last half-hour, helping Kevin Entwhistle and Michael Corner rehearse Potions recipes. But it matters not. I am here to deliver a warning to you, Padma Patil, and if you choose to ignore it, that is your own affair.”

“Fine,” she said coldly. “Go ahead and warn me, Potter, I’m not afraid of you.”

“Slytherin was a great House, once,” said the whisper; it sounded sadder, now. “Slytherin was once a House you would have been proud to choose, Padma Patil. But something turned wrong, something turned sour; do you know what went awry in Slytherin House, Padma Patil?”

“No, and I don’t care!”

“But you should care,” said the whisper, now sounding like it was coming from just behind her head where it stood almost pressed against the wall. “For you are still that girl whom the Sorting Hat offered that choice. Do you think that just choosing Ravenclaw means that you are not Pansy Parkinson, and will not ever become Pansy Parkinson, no matter how you conduct yourself otherwise?”

Despite everything, now, small chills of fear were spreading out from her spine and running over her skin. She’d heard \emph{those} stories about Harry Potter too, that he was a secret Legilimens. But she still stood straight, and she put all the bite she could into her voice when she said, “The Slytherins went Dark to get power, just like \emph{you} did, Potter. And \emph{I} won’t, not ever.”

“But you’ll spread vicious rumors about an innocent girl,” whispered the voice, “even though it will not help you attain any of your own ambitions, and without considering that she has powerful allies who might take offense. That is is not the proud Slytherin of the old days, Padma Patil, that is not the pride of Salazar, that is Slytherin gone rotten, Padma Parkinson not Padma Malfoy...”

She was getting more creeped out than she ever had been in her life, and the possibility was starting to occur to her that this might \emph{really} be a ghost. She hadn’t ever heard that ghosts could hide themselves like this, but maybe they just didn’t usually do it—not to mention that most ghosts weren’t this \emph{eerie,} they were just dead people after all—“Who \emph{are} you? The Bloody Baron?”

“When Harry Potter was bullied and beaten,” the voice whispered, “he commanded all his allies to refrain from vengeance; do you remember that, Padma Patil? For Harry Potter is wavering, but not yet lost; he is struggling, he knows himself to be in peril. But Hermione Granger made no such request of her own allies. Harry Potter is angered with you now, Padma Patil, more angered than he would ever be on his own behalf...\ and \emph{he} has allies of his own.”

A shudder went through her, she knew that it was visible and she hated herself for it.

“Oh, don’t be afraid,” breathed the voice. “I will not hurt you. For you see, Padma Patil, Hermione Granger truly is innocent. \emph{She} does not stand on the precipice, \emph{she} is not falling. She did not ask her allies to refrain from hurting you, because the thought did not even occur to her as a possibility. And Harry Potter knows very well that if he hurt you or caused you to be hurt, for Hermione Granger’s sake, then she would never speak to him again until the Sun burned low and the last star failed in the night sky.” The voice was very sad now. “She truly is a kindly girl, a person such as I could only wish to be...”

“Granger can’t cast the Patronus Charm!” said Padma. “If she was really as nice as she pretends to be—”

“Can \emph{you} cast the Patronus Charm, Padma Patil? You dared not even attempt it, you feared what the result would be.”

“That’s not \emph{true!} I didn’t have time, that was all!”

The whisper continued. “But Hermione Granger did try, openly before her friends, and when her magic failed she was surprised and dismayed. For there are secrets to the Patronus Charm that few ever knew, and maybe none now know but I.” A soft, whispery chuckle. “Let it stand that it is no stain of her spirit that halts her light from coming forth. Hermione Granger cannot cast the Patronus Charm for the very same reason that Godric Gryffindor, who raised these halls, never could.”

The corridor \emph{was} becoming colder, she was certain of it, as though someone were using the Chilling Charm.

“And Harry Potter is not Hermione Granger’s only ally.” Now there was an undertone of dry amusement in that whisper, it reminded her suddenly and frighteningly of Professor Quirrell. “Filius Flitwick and Minerva McGonagall are quite fond of her, I do believe. Did it occur to you that if those two learned what you were doing to Hermione Granger, they might become less fond of you? They might not intervene openly, perhaps; but they might be a little slower to award you House Points, a little slower to steer opportunities your way—”

“Potter \emph{snarked} on me?”

A ghostly chuckle, a dry heh-heh-heh. “Do you think those two are stupid, deaf and blind?” In a sadder whisper, “Do you think Hermione Granger is not precious to them, that they will not see her hurting? As they might have been fond of you once, their bright young Padma Patil, but you are throwing it away...”

Padma’s throat was dry. She hadn’t thought of that, not at all.

“I wonder how many people will end up caring for you, Padma Patil, on this path that you now tread. Is it worth that much, just to distance yourself further from your sister? To be the shadow to Parvati’s light? Your deepest fear has always been to fall into harmony with her, \emph{back} into harmony with her I should say; but is it worth hurting an innocent girl, just to make yourself that much more different? Must you be the \emph{evil} twin, Padma Patil, can you not find a different good to pursue?”

Her heart was hammering in her chest. She’d, she’d never talked about that with \emph{anyone—}

“I have always wondered at how students bully each other,” sighed the voice. “How children make life difficult for themselves, how they turn their schools into prisons even with their own hands. Why do human beings make their own lives so unpleasant? I can give you a part of the answer, Padma Patil. It is because people do not stop and think before causing pain, if they do not imagine that they themselves could also be hurt, that they might also suffer from their own misdeeds. But suffer you will, oh, yes, Padma Patil, suffer you will, if you stay on this road. You will suffer the same pain of loneliness, the same pain of others’ fear and distrust, that you now inflict on Hermione Granger. Only for you it will be deserved.”

Her wand was shaking in her hand.

“You did not choose sides when you went to Ravenclaw, girl. You choose your side by the way you live your life, what you do to other people and what you do to yourself. Will you illuminate others’ lives, or darken them? That is the choice between Light and Dark, not any word the Sorting Hat cries out. And the hard part, Padma Patil, is not saying ‘Light’, the hard part is deciding which is which, and admitting it to yourself when you begin down the wrong road.”

There was silence. It went on for a time, and Padma realized that she had been dismissed.

Padma almost dropped her wand, when she tried to put it back into her pocket. She almost fell, when she took a step forward away from the wall, and turned to go—

“I have not always chosen rightly beween Light and Dark,” the whisper said, now loud and harsh directly into her ear. “Do not take my wisdom as a final word, girl, do not fear to question it, for though I tried I have sometimes failed, oh, yes, I have failed. But you are hurting a true innocent, and you will achieve none of your ambitions by doing so, it is not for any cunning plan. You are inflicting pain purely for the sake of the pleasure it brings you. I have not always chosen rightly between Light and Dark, but that I know for darkness, for certain. You are hurting an innocent girl, and escaping retribution only because she is too kindly to tolerate her allies moving against you. I cannot hurt you for that, so know only that I cannot respect it. You are unworthy of Slytherin; go and do your Herbology homework, Ravenclaw girl!”

The final whisper came out in a louder hiss that sounded almost like a snake, and Padma fled, she fled down the corridors like Lethifolds were chasing her, she ran heedless of the rules about running in the corridors, even when she passed other students who looked at her in surprise, she did not stop, she ran all the way to the Ravenclaw dorms with her pulse pounding in her neck, the door asked her “Why does the Sun shine in the day instead of the nighttime?” and it took her three tries before she could make her answer coherent, and then the door came open and she saw—

—a few girls and boys, some young and some old, all staring at her, and in one corner at the pentagonal table, Harry Potter and Michael Corner and Kevin Entwhistle, looking up from their textbooks.

“Sweet Merlin!” exclaimed Penelope Clearwater, rising from a couch. “What happened to you, Padma?”

“I,” she stuttered, “I, I heard—a ghost—”

“It wasn’t the Bloody Baron, was it?” said Clearwater. She drew her wand and a moment later she was holding a cup, and then an \emph{Aguamenti} later the cup was filled with water. “Here, drink this, sit down—”

Padma was already striding toward the pentagonal table. She looked at Harry Potter, who was looking at her with his own gaze, calm and grave and a little sad.

“\emph{You} did this!” Padma said. “How—you—how dare you!”

There was a sudden hush in the Ravenclaw dorm.

Harry just looked at her.

And said, “Is there anything I can help you with?”

“Don’t deny it,” Padma said, her voice shaking, “\emph{you} set that ghost on me, it \emph{said}—”

“I mean it,” Harry said. “Can I help you with anything? Get you some food, or go fetch a soda for you, or help you with your homework, or anything like that?”

Everyone was staring at the two of them.

“Why?” Padma said. She couldn’t think of anything else to say, she didn’t understand.

“Because some of us are standing on the precipice,” Harry said. “And the difference is what you do for other people. Will you let me help you with something, Padma, please?”

She stared at him, and knew, in that moment, that he’d gotten his own warning, same as her.

“I...” she said. “I’ve got to write six inches on \emph{lomillialor}—”

“Let me run up to my dorm room and get my Herbology stuff,” Harry said. He rose from the pentagonal table, looked at Entwhistle and Corner. “Sorry, guys, I’ll see you later.”

They didn’t say anything, just stared, along with everyone else in the dorm room, as Harry Potter walked over to the stairs.

And just as he started up, he said, “And no one’s to pester her with questions unless \emph{she} wants to talk about it, I hope everyone’s \emph{got that?}”

“Got it,” said most of the first years and some of the older students, a few of them sounding quite scared.
\sbreak
And she talked about a lot of things with Harry Potter besides \emph{lomillialor} wood—even her fear of falling back into harmony with Parvati, which she’d never talked about with \emph{anyone} before, but then Harry’s ghostly ally already knew. And Harry had reached into his pouch and pulled out some \emph{odd} books, loaning them to her on condition of complete secrecy, saying that if she could comprehend those books it would change the pattern of her thinking enough that she’d never fall into harmony with Parvati again...

At nine o’ clock, when Harry said he had to go, the essay was only half done.

And when Harry paused, and looked at her on the way out, and said that \emph{he} thought she was worthy of Slytherin, it made her feel good for a whole minute before she realized what had just been said to her and who had said it.
\sbreak
When Padma got down to breakfast, that morning, she saw Mandy see her and whisper something to the girl sitting beside her at the Ravenclaw table.

She saw that girl get up from the bench and walk toward her.

Last night Padma had been glad that girl roomed in the other dorm; but now that she thought about it, this was worse, now she had to do it in front of \emph{everyone}.

But even though Padma was sweating, she knew what she had to do.

The girl came closer—

“I’m sorry.”

“What?” said Padma. That was \emph{her} line.

“I’m sorry,” repeated Hermione Granger. Her voice was loud so that everyone could hear. “I... I didn’t ask Harry to do that, and I was angry with him when I found out, and I made him promise not to do it again to \emph{anyone}, and I’m not talking to him for a week... I’m really, \emph{really} sorry, Miss Patil.”

Hermione Granger’s back was stiff, her face was stiff, you could see the sweat on her face.

“Um,” said Padma. Her own thoughts were pretty much scrambled, now...

Padma’s gaze flicked to the Ravenclaw table, where one boy was watching them with tight eyes and his hands clenched in his lap.
\sbreak
\emph{Earlier:}

“I told you to be \emph{nicer!}” shrieked Hermione.

Harry was starting to sweat. He’d never actually heard Hermione scream at him before, and it was quite loud in the empty classroom.

“I—but—but I \emph{was} nice!” Harry protested. “I practically \emph{redeemed} her, Padma was going down the wrong path and I turned her off it! I probably changed her whole life to be happier! Besides, you should’ve heard the \emph{original} version of what Professor Quirrell suggested I do—” at which point Harry realized what he was saying and closed his mouth a second too late.

Hermione clutched at her chestnut curls, a gesture Harry hadn’t seen from her before. “What’d \emph{he} say to do? \emph{Kill} her?”

The Defense Professor had suggested that Harry identify all the key influential students inside and outside his year and try to gain control of the entire Hogwarts rumor mill, remarking that this was a generally useful and amusing challenge for any true Slytherin attending Hogwarts.

“Nothing like \emph{that,}” Harry said quickly, “he just said in a general way that I should get influence over the people spreading rumors, and \emph{I} decided that the \emph{nice} version of that would be to just inform Padma directly about the meaning of what she was doing, and the possible consequences of her actions, instead of trying to threaten her or anything like that—”

“\emph{You call that not threatening someone?}” Hermione’s hands were pulling at her hair now.

“Um...” Harry said. “I guess she might’ve felt a \emph{little} threatened, but Hermione, people will do whatever they think they can get away with, they don’t care about how much it hurts other people if it doesn’t hurt themselves, if Padma thinks there’s \emph{no} consequences to spreading lies about you then of \emph{course} she’ll just go on doing it—”

“And you think there’s going to be no consequences to what \emph{you} did?”

Harry got a sudden sick feeling to his stomach.

Hermione had the angriest look on her that he’d ever seen. “What do you think the other students think of you now, Harry? Of \emph{me?} If Harry doesn’t like the way you talk about Hermione, you’ll get ghosts set on you, is that what you want them to think?”

Harry opened his mouth and no words came out, he just...\ hadn’t thought about it that way, actually...

Hermione reached down to grab her books from the table where she’d slammed them. “I’m not talking to you for a week, and I’ll \emph{tell} everyone I’m not talking to you for a week, and I’ll tell them \emph{why}, and \emph{maybe} that’ll undo some of what you just did. And after that week, I’ll—I’ll decide then what to do, I guess—”

“\emph{Hermione!}” Harry’s own voice rose to a shriek of desperation. “\emph{I was trying to help!}”

The girl turned back and looked at him as she opened the classroom door.

“Harry,” she said, and her voice trembled a little beneath the anger, “Professor Quirrell is sucking you into the darkness, he really is, I mean it, Harry.”

“This...\ wasn’t him, this wasn’t what he said to do, this was just \emph{me}—”

Hermione’s voice was almost a whisper now. “Someday you’re going to go out to lunch with him, and it will be your dark side that comes back, or maybe even you won’t come back at all.”

“I promise you,” Harry said, “that I \emph{will} come back from lunch.”

He wasn’t even thinking as he said it.

And Hermione just turned around and strode out and slammed the door behind her.

\emph{Way to invoke the laws of dramatic irony, moron,} observed Harry’s Internal Critic. \emph{Now you’re going to die this Saturday, your last words will be ‘I’m sorry, Hermione’, and she’ll always regret that the last thing she did was slam the door—}

\emph{Oh, shut up.}
\sbreak
When Padma sat down with Hermione for breakfast, and said in a voice loud enough for others to hear that the ghost had just told her things that were important for her to hear, and Harry Potter had been right to do it, there were some people who were less frightened afterward, and some who were frightened more.

And afterward people \emph{did} say fewer nasty things about Hermione, at least in the first year, at least in public where Harry Potter might hear about it.

When Professor Flitwick asked Harry if he was responsible for what had happened to Padma, and Harry said yes, Professor Flitwick told him that he was to serve two days’ detention. Even if it had only been a ghost and Padma hadn’t been hurt, still, that wasn’t acceptable behavior for a Ravenclaw student. Harry nodded and said that he understood why the Professor had to do that, and wouldn’t protest; but considering that it \emph{did} seem to have turned Padma around, did Professor Flitwick really think, off the record, that he’d done the wrong thing? And Professor Flitwick paused, seeming to actually think about it, and then said to Harry, in a solemnly squeaky voice, that he needed to learn how to relate to other students the normal way.

And Harry couldn’t help but think that this was advice that Professor Quirrell would never give him.

Harry couldn’t help but think that if he’d done it Professor Quirrell’s way, the normal \emph{Slytherin} way, a mixture of positive and negative incentives to bring Padma and the other rumor-mongers under his explicit control, then Padma wouldn’t have talked about it, and Hermione would have never found out...

...in which case Padma wouldn’t have been redeemed, she would have stayed on the wrong path, and she herself would have suffered from that eventually. It wasn’t as if Harry had \emph{lied} to Padma in any way, when he was Time-Turned and invisible and using the Ventriloquism Charm.

Harry still wasn’t sure whether he’d done the right thing, or \emph{a} right thing, and Hermione hadn’t relented on not talking to him—though she was talking a lot with Padma. It hurt more than Harry had expected, going back to studying by himself; like his brain had already started to forget its long-honed skill of being alone.

The days until Saturday’s lunch with Professor Quirrell seemed to go by very, very slowly.

