\chapter[Interlude: Crossing~the~Boundary]{Interlude:\protect\linebreak{}Crossing the Boundary}

\lettrine{I}{t} was almost midnight.

\quad\quad Staying up late was simple enough for Harry. He just hadn’t used the Time-Turner. Harry followed a tradition of timing his sleep cycle to make sure he was awake for when Christmas Eve turned into Christmas Day; because while he’d never been young enough to \emph{believe} in Santa Claus, he’d once been young enough to doubt.

It would have been nice if there \emph{had} been a mysterious figure who entered your house in the night and brought you presents...

A chill went down Harry’s spine then.

An intimation of something dreadful approaching.

A creeping terror.

A sense of doom.

Harry sat bolt upright in bed.

He looked at the window.

“\emph{Professor Quirrell?}” Harry shrieked very quietly.

Professor Quirrell made a slight lifting gesture, and Harry’s window seemed to fold into its frame. At once a cold gust of winter blew into the room through the gap, along with a scant few flakes of snow from a sky spotted with grey night-clouds, amid the black and stars.

“Fear not, Mr.~Potter,” said the Defense Professor in a normal voice. “I have Charmed your parents asleep; they shall not wake until I have departed.”

“No one’s supposed to know where I am!” said Harry, still keeping the shriek quiet. “Even owls are supposed to deliver my mail to Hogwarts, not here!” Harry had agreed to that willingly; it would be silly if a Death Eater could win the whole war at any time just by owling him a magically triggered hand grenade.

\looseness+1 Professor Quirrell was grinning, from where he stood in the backyard beyond the window. “Oh, I shouldn’t worry, Mr.~Potter. You \emph{are} well protected against locating Charms, and no blood purist is likely to think of consulting a phone book.” His grin grew wider. “And it did take considerable effort to cross the wards that the Headmaster put around this house—though of course anyone who knew your address could simply wait outside and attack you the next time you left.”

Harry stared at Professor Quirrell for a while. “What are you \emph{doing} here?” Harry said finally.

The smile left Professor Quirrell’s face. “I’ve come to apologize, Mr.~Potter,” the Defense Professor said quietly. “I should not have spoken to you so harshly as I—”

“Don’t,” Harry said. He looked down at the blanket that he was clutching around his pajamas. “Just don’t.”

“Have I offended you that much?” said Professor Quirrell’s quiet voice.

“No,” Harry said. “But you \emph{will} if you apologize.”

\looseness+1“I see,” said Professor Quirrell, and in an instant his voice grew stern. “Then if I am to treat you as an equal, Mr.~Potter, I should say that you have gravely violated the etiquette that holds between friendly Slytherins. If you are not currently playing the game against someone, you \emph{must} not meddle in their plans like that, not without asking them \emph{before}. For you do not know what their true design may be, nor what stakes they may lose. It would mark you as their enemy, Mr.~Potter.”

“I’m sorry,” Harry said, in just the same quiet tone that Professor Quirrell had used.

“Apology accepted,” said Professor Quirrell.

“But,” Harry said, still quietly, “you and I really must speak further on politics, at some point.”

Professor Quirrell sighed. “I know you dislike condescension, \replacement{Mr.~Potter}{Mister Potter}—”

That was a bit of an understatement.

“But it would be even more condescending,” said Professor Quirrell, “if I were not to state it clearly. You are missing some life experience, Mr.~Potter.”

“And does everyone who has sufficient life experience agree with you, then?” said Harry calmly.

“What good is life experience to someone who plays Quidditch?” said Professor Quirrell, and shrugged. “I think you will change your mind in time, after every trust you place has failed you, and you have become cynical.”

The Defense Professor said it as though it were the most ordinary statement in the world, framed against the black and the stars and the cloud-spotted sky, as one or two tiny snowflakes blew past him in the biting winter air.

“That reminds me,” said Harry. “Merry Christmas.”

“I suppose,” said Professor Quirrell. “After all, if it is \emph{not} an apology, then it must be a Christmas gift. The very first one I have ever given, in fact.”

Harry hadn’t even started yet on learning Latin so he could read the experimental diary of Roger Bacon; and he hardly dared open his mouth to ask.

“Put on your winter coat,” said Professor Quirrell, “or take a warming potion if you have one; and meet me outside, under the stars. I shall see if I can maintain it a little longer this time.”

It took Harry a moment to process the words, and then he was dashing for the coat closet.

Professor Quirrell kept the spell of starlight going for more than an hour, though the Defense Professor’s face grew strained, and he had to sit down after a while. Harry protested only once, and was shushed.

They crossed the boundary from Christmas Eve to Christmas Day within that timeless void where Earthly rotations meant nothing, the one true everlasting Silent Night.

And just as promised, Harry’s parents slept soundly all through it, until Harry was safely back in his room, and the Defense Professor had gone.

