\namedpartchapter{The Stanford Prison Experiment}{TSPE}{XIII}{Aftermaths}

\subsection{Aftermath, Hermione Granger:}

\lettrine{S}{he} was just starting to close up her books and put away her homework in preparation for sleep, Padma and Mandy stacking up their own books across the table from her, when Harry Potter walked into the Ravenclaw common room; and it was only then that she realized, she hadn’t seen him at all since breakfast.

That realization was rapidly stomped-on by a much more startling one.

There was a golden-red winged creature on Harry’s shoulder, a bright bird of fire.

And Harry looked sad and worn and really \emph{tired} like the phoenix was the only thing keeping him on his feet, but there was still a warmth about him, if you crossed your eyes you might have thought you were looking at the Headmaster somehow, that was the impression that went through Hermione’s mind even though it didn’t make any sense.

Harry Potter trudged across the Ravenclaw common room, past sofas full of staring girls, past cardgame-circles of staring boys, heading for her.

In theory she wasn’t talking to Harry Potter yet, his week wasn’t up until tomorrow, but whatever was going on was clearly a \emph{whole} lot more important than that—

“Fawkes,” Harry said, just as she was opening her mouth, “that girl over there is Hermione Granger, she’s not talking to me right now because I’m an idiot, but if you want to be on a good person’s shoulder she’s better than me.”

So much exhaustion and hurt in Harry Potter’s voice—

But before she could figure out what to do about it, the phoenix had glided off Harry’s shoulder like a fire creeping up a matchstick on fast-forward, flashing toward her; there was a phoenix flying in front of her and staring at her with eyes of light and flame.

“\emph{Caw?}” asked the phoenix.

Hermione stared at it, feeling like she was facing a question on a test she’d forgotten to study for, the one most important question and she’d gone her whole life without studying for it, she couldn’t find anything to say.

“I’m—” she said. “I’m only twelve, I haven’t \emph{done} anything yet—”

The phoenix just glided gently around, rotating around one wingtip like the being of light and air that it was, and soared back to Harry Potter’s shoulder, where it settled down quite firmly.

“You silly boy,” said Padma across from her, looking like she was deciding whether to laugh or grimace, “phoenixes aren’t for smart girls who do their homework, they’re for idiots who charge straight at five older Slytherin bullies. There’s a reason why the Gryffindor colors are red and gold, you know.”

There was a lot of friendly laughter in the Ravenclaw common room.

Hermione wasn’t one of the laughing ones.

Neither was Harry.

Harry had put a hand over his face. “Tell Hermione I’m sorry,” he said to Padma, his voice almost fallen to a whisper. “Tell her I forgot that phoenixes are animals, they don’t understand time and planning, they don’t understand people who are \emph{going} to do good things later—I’m not sure they understand really the notion of there being something that a person \emph{is}, all they see is what people do. Fawkes doesn’t know what twelve means. Tell Hermione I’m sorry—I shouldn’t have—it just all goes wrong, doesn’t it?”

Harry turned to go, the phoenix still on his shoulder, began slowly trudging toward the staircase that led up to his dorm.

And Hermione couldn’t leave it at that, she just \emph{couldn’t} leave it at that. She didn’t know if it was her competition with Harry or something else. She just couldn’t leave it with the phoenix turning away from her.

She \emph{had} to—

Her mind keyed a frantic question to the entirety of her excellent memory, found just one thing—

“I was going to run in front of the Dementor to try and save Harry!” she shouted a little desperately at the red-golden bird. “I mean, I actually did start running and everything! That was stupid and courageous, right?”

With a warbling cry the phoenix launched itself from Harry’s shoulder again, back toward her like a spreading blaze, it circled her three times like she was the center of an inferno, and for just a moment its wing brushed against her cheek, before the phoenix soared back to Harry.

There was a hush in the Ravenclaw common room.

“Told you so,” Harry said aloud, and then he started climbing the stairs up to his bedroom; he seemed to climb very quickly, like he was very light on his feet for some reason, so that in just a moment he and Fawkes were gone.

Hermione held up a trembling hand to her cheek where Fawkes had brushed her with his wing, a spot of warmth lingering there like that one small patch of skin had been very gently set on fire.

She’d answered the question of the phoenix, she supposed, but it felt to her like she’d just barely squeaked by on the test, like she’d gotten a 62 and she could’ve gotten 104 if she’d tried harder.

If she’d tried at \emph{all}.

She hadn’t really \emph{been} trying, when she thought about it.

Just doing her homework—

\emph{Who have you saved?}
\replacement{\sbreak}{}

\subsection{Aftermath, Fawkes:}

\noindent{}Nightmares, the boy had expected, screams and begging and howling hurricanes of emptiness, the discharge of the horrors being laid down into memory, and in that fashion, perhaps, becoming part of the past.

And the boy knew that the nightmares would come.

The next night, they would come.

The boy dreamed, and in his dreams the world was on fire, Hogwarts was on fire, his home was on fire, the streets of Oxford were on fire, all ablaze with golden flames that shone but did not consume, and all the people walking through the blazing streets were shining with white light brighter than the fire, like they were flames themselves, or stars.

The other first-year boys came to bed, and saw it for themselves, the wonder whose rumor they had already heard, that in his bed Harry Potter lay silent and motionless, a gentle smile on his face, while perched on his pillow a red-golden bird watched over him, with bright wings swept above him like a blanket pulled over his head.

The reckoning had been put off one more night.
\replacement{\sbreak}{}

\subsection{Aftermath, Draco Malfoy:}

\noindent{}Draco straightened his robes, making sure the green trim was straight. He waved his wand over his own head and said a Charm that Father had taught him while other children were still playing in mud, a Charm which ensured that not a single speck of lint or dust would dirty his wizard’s robes.

Draco picked up the mysterious envelope that Father had owled him, and tucked it into his robes. He had already used \emph{Incendio} and \emph{Everto} on the mysterious note.

And then he headed off to breakfast, to seat himself on exactly the same tick of the clock where the food appeared, if he could manage it, so that it would seem like all others had been waiting on his appearance to eat. Because when you were the scion of Malfoy you were first in everything, including breakfast, that was why.

Vincent and Gregory were waiting for him outside the door of his private room, up even before he was—though not, of course, dressed quite as sharply.

The Slytherin common room was deserted, anyone who got up this early was heading straight to breakfast anyway.

The dungeon halls were silent but for their own footsteps, empty and echoing.

The Great Hall was a hubbub of alarm despite the relative few arrivals, some younger children crying, students running back and forth between tables or standing in knots shouting at each other, a red-robed prefect was standing in front of two green-trimmed students and yelling at them and Snape was striding toward the mess—

The noise dimmed a little as people caught sight of Draco, as some of the faces turned to stare at him, and fell quiet.

The food appeared on the tables. No one looked at it.

And Snape spun on his heel, abandoning his target, and headed straight toward Draco.

A knot of fear clutched at Draco’s heart, had something happened to Father—no, surely Father would have told him—whatever was happening, why hadn’t Father told him—

There were bags of fatigue beneath Snape’s eyes, Draco saw as their Head of House came close, the Potions Master had never been a sharp dresser (that was an understatement) but his robes were even dirtier and more disarrayed this morning, spotted with extra grease.

“You haven’t heard?” hissed their Head of House as he came close. “For pity’s sake, Malfoy, don’t you have a newspaper delivered?”

“What is it, Profe—”

“Bellatrix Black was taken from Azkaban!”

“\emph{What?}” said Draco in shock, as Gregory behind him said something he really shouldn’t have and Vincent just gasped.

Snape was gazing at him with narrowed eyes, then nodded abruptly. “Lucius told you nothing, then. I see.” Snape gave a snort, turned away—

“Professor!” said Draco. The implications were just starting to dawn on him, his mind spinning frantically. “Professor, what should I do—Father didn’t instruct me—”

“Then I \emph{suggest},” Snape said sneeringly, as he strode away, “that you \emph{tell} them that, Malfoy, as your father intended!”

Draco glanced back at Vincent and Gregory, though he didn’t know why he was bothering, of course they looked even more confused than he did.

And Draco walked forward to the Slytherin table, and sat down at the far end, which was still empty of sitters.

Draco put a sausage omelet on his plate, began eating it with automatic motions.

Bellatrix Black had been taken from Azkaban.

Bellatrix Black had been taken from Azkaban...?

Draco didn’t know what to make of that, it was as totally unexpected as the Sun going out—well, the Sun would expectedly go out in six billion years but this was as unexpected as the Sun going out \emph{tomorrow}. Father wouldn’t have done it, Dumbledore wouldn’t have done it, \emph{no one} should have been \emph{able} to do it—what did it \emph{mean}—what \emph{use} would Bellatrix be to anyone after ten years in Azkaban—even if she got strong again, what use was a powerful sorceress who was completely evil and insane and fanatically devoted to a Dark Lord who wasn’t around anymore?

“Hey,” said Vincent from where he was sitting next to Draco, “I don’t understand, boss, why’d we do that?”

“\emph{We} didn’t do it, you dolt!” snapped Draco. “Oh, for Merlin’s sake, if even \emph{you} think we—didn’t your father ever tell you any stories about Bellatrix Black? She tortured Father once, she tortured \emph{your} father, she’s tortured \emph{everyone,} the Dark Lord once told her to Crucio \emph{herself} and she \emph{did it!} She didn’t do crazy things to inspire fear and obedience in the populace, she did crazy things because she’s crazy! She’s a \emph{bitch} is what she is!”

“Oh, really?” said an incensed voice from behind Draco.

Draco didn’t look up. Gregory and Vincent would be watching his back.

“I would’ve thought you’d be happy—”

“—to hear that a Death Eater had been freed, Malfoy!”

Amycus Carrow had always been one of the \emph{other} problem people; Father had once told Draco to make sure he was never alone in the same room with Amycus...

Draco turned around and gave Flora and Hestia Carrow his Number Three Sneer, the one that said that he was in a Noble and Most Ancient House and they weren’t and yes, that mattered. Draco said in their general direction, certainly not deigning to address \emph{them} in particular, “There’s Death Eaters and then there’s Death Eaters,” and then turned back to his food.

There were two furious huffs in unison, and then two pairs of shoes stormed off toward the other end of the Slytherin table.

It was a few minutes later that Millicent Bulstrode ran up to them, visibly out of breath, and said, “Mr.~Malfoy, did you hear?”

“About Bellatrix Black?” said Draco. “Yeah—”

“No, about Potter!”

“What?”

“Potter was going around with a \emph{phoenix} on his shoulder last night, looking like he’d been dragged through ten leagues of mud, they say that the phoenix took him to Azkaban to try to stop Bellatrix and he fought a duel with her and they blew up half the fortress!”

“\emph{What?}” said Draco. “Oh, there is just no \emph{way} that—”

Draco stopped.

He’d said that a number of times about Harry Potter and had started to notice a trend.

Millicent ran off to tell someone else.

“You don’t \emph{really} think—” said Gregory.

“I honestly don’t know anymore,” said Draco.

A few minutes later, after Theodore Nott had sat down across from him and William Rosier had gone to sit with the Carrow twins, Vincent nudged him and said, “There.”

Harry Potter had entered the Great Hall.

Draco watched him closely.

There was no alarm on Harry’s face as he saw, no surprise or shock, he just looked...

It was the same distant, self-absorbed look Harry wore when he was trying to figure out the answer to a question Draco couldn’t understand yet.

Draco hastily shoved himself up from the bench of the Slytherin table, saying “Stay behind,” and walked with all decorous speed toward Harry.

Harry seemed to notice his approach just as the other boy was turning toward the Ravenclaw table, and Draco—

—gave Harry one quick look—

—and then walked right past him, straight out of the Great Hall.

It was a minute later that Harry peered around the corner of the small stony nook where Draco had waited, it might not fool everyone but it would create plausible deniability.

“\emph{Quietus},” said Harry. “Draco, what—”

Draco took the envelope out of his robes. “I have a message for you from Father.”

“\emph{Huh?}” said Harry, and took the envelope from Draco, and tore it open in a rather un-neat manner, and drew forth a sheet of parchment and unfolded it and—

Harry gave a sharp intake of breath.

Then Harry looked at Draco.

Then Harry looked back down at the parchment.

There was a pause.

Harry said, “Did Lucius tell you to report on my reaction to this?”

Draco paused for a moment, weighing, and then opened his mouth—

“I see he did,” said Harry, and Draco cursed himself, he should’ve known better, only it \emph{had} been hard to decide. “What are you going to tell him?”

“That you were surprised,” said Draco.

“Surprised,” Harry said flatly. “Yeah. Good. Tell him that.”

“What \emph{is} it?” said Draco. And then, as he saw Harry looking conflicted, “If you’re dealing with Father behind my back—”

And Harry, without a word, gave Draco the paper.

It said:

\emph{I know it was you.}

“\shout{What the—}”

“I was going to ask \emph{you} that,” said Harry. “Have you got \emph{any} idea what’s up with your Dad?”

Draco stared at Harry.

Then Draco said, “\emph{Did} you do it?”

“What?” said Harry. “What \emph{possible} reason would I—\emph{how} would I—”

“Did you do it, Harry?”

“No!” Harry said. “Of course not!”

Draco had listened carefully, but he hadn’t detected any hesitation or tremor.

So Draco nodded, and said, “I’ve got no idea what Father’s thinking but it \emph{can’t}, I mean it \emph{can’t possibly} be good. And, um...\ people are also saying...”

“What,” said Harry warily, “are they saying, Draco?”

“Did a phoenix \emph{really} take you to Azkaban to try to stop Bellatrix Black from escaping—”
\replacement{\sbreak}{}

\subsection{Aftermath, Neville Longbottom:}

\noindent{}Harry had only just sat down at the Ravenclaw table for the first time, hoping to grab a quick bite of food. He knew he needed to go off and think about things, but there was a tiny remaining bit of phoenix’s peace (even after the encounter with Draco) that he still wanted to cling to, some beautiful dream of which he remembered nothing but the beauty; and the part of him that \emph{wasn’t} feeling peaceful was waiting for all the anvils to finish dropping on him, so that when he went off to think and be by himself for a while, he could batch-process all the disasters at once.

Harry’s hand grasped a fork, lifted a bite of mashed potatoes toward his mouth—

And there was a shriek.

Every now and then someone would shout when they heard the news, but Harry’s ears \emph{recognized} this one—

Harry was up from the bench in an instant, heading toward the Hufflepuff table, a horrible sick feeling dawning in the pit of his stomach. It was one of those things he hadn’t considered when he’d decided to commit the crime, because Professor Quirrell had planned for no one to know; and now, afterward, Harry just—hadn’t \emph{thought} of it—

\emph{This,} Hufflepuff said with bitter intensity, \emph{is also your fault.}

But by the time Harry got there, Neville was sitting down and eating fried sausage patties with Snippyfig Sauce.

The Hufflepuff boy’s hands were trembling, but he cut the food, and ate it, without dropping it.

“Hello, General,” Neville said, his voice wavering only slightly. “Did you fight a duel with Bellatrix Black last night?”

“No,” Harry said. His own voice was also wavery, for some reason.

“Didn’t think so,” said Neville. There was a scraping sound as his knife cut the sausage again. “I’m going to hunt her down and kill her, can I count on you to help?”

There were startled gasps from the mass of Hufflepuffs who had gathered around Neville.

“If she comes after you,” Harry said hoarsely, \emph{if it was all a terrible mistake, if it was all a lie,} “I’ll defend you even with my life,” \emph{won’t let you get hurt for what I did, no matter what,} “but I won’t help you go after her, Neville, friends don’t help friends commit suicide.”

Neville’s fork paused on the way to his mouth.

Then Neville put the bite of food in his mouth, chewed again.

And Neville swallowed it.

And Neville said, “I didn’t mean \emph{right now}, I mean after I graduate Hogwarts.”

“Neville,” Harry said, keeping his voice under very careful control, “I think, even after you graduate, that might still be a \emph{just plain} \emph{stupid idea.} There’s got to be much more experienced Aurors tracking her—” \emph{oh, wait, that’s not good}—

“Listen to him!” said Ernie Macmillan, and then an older-looking Hufflepuff girl standing close to Neville said, “Nevvy, please, think about it, he’s right!”

Neville stood up.

Neville said, “Please don’t follow me.”

Neville walked away from all of them; Harry and Ernie reaching out involuntarily toward him, and some of the other Hufflepuffs as well.

And Neville sat down at the Gryffindor table, and distantly (though they had to strain to hear) they heard Neville say, “I’m going to hunt her down and kill her after I graduate, anyone want to help?” and at least five voices said “Yes” and then Ron Weasley said loudly, “Get in line, you lot, I got an owl from Mum this morning, she says to tell everyone she’s called dibs” and someone said “\emph{Molly Weasley} against \emph{Bellatrix Black?} Who does she even think she’s kidding—” and Ron reached over to a plate and hefted a muffin—

Someone tapped Harry on the shoulder, and he turned around and saw an unfamiliar green-trimmed older girl, who handed him a parchment envelope and then quickly strode away.

Harry stared at the envelope for a moment, then started walking toward the nearest wall. That wasn’t very private, but it should be private enough, and Harry didn’t want to give the impression of having much to hide.

That had been a Slytherin System delivery, what you used if you wanted to communicate with someone without anyone else knowing that the two of you had talked. The sender gave an envelope to someone who had a reputation for being a reliable messenger, along with ten Knuts; that first person would take five Knuts and pass the envelope to another messenger along with the other five Knuts, and the second messenger would open up that envelope and find another envelope with a name written on it and deliver that envelope to that person. That way neither of the two people passing the message knew both the sender \emph{and} the recipient, so no one else knew that those two parties had been in contact...

When Harry reached the wall, he put the envelope inside his robes, opened it beneath the folds of cloth, and carefully snuck a peek at the parchment he drew forth.

It said,

\begin{writtenNote}
Classroom to the left of Transfiguration, 8 in the morning.

\letterClosing{—LL.}
\end{writtenNote}

Harry stared at it, trying to remember if he knew anyone with the initials LL.

His mind searched...

Searched...

Retrieved—

“The \emph{Quibbler} girl?” Harry whispered incredulously, and then shut his mouth. She was only ten years old, she shouldn’t be in Hogwarts at all!
\replacement{\sbreak}{}

\subsection{Aftermath, Lesath Lestrange:}

\noindent{}Harry was standing in the unused classroom next to Transfiguration at 8\AM, waiting, he’d at least managed to get some food into himself before facing the next disaster, Luna Lovegood...

The door to the classroom opened, and Harry saw, and gave himself a really \emph{hard} mental kick.

One more thing he hadn’t thought of, one more thing he \emph{really should have.}

The older boy’s green-trimmed formal robes were askew, there were red spots on them looking very much like small dots of fresh blood, and one corner of his mouth had the look of a place that had been cut and healed, by \emph{Episkey} or some other minor medical Charm that didn’t quite erase all the damage.

Lesath Lestrange’s face was streaked with tears, fresh tears and half-dried tears, and there was water in his eyes, a promise of still more on the way. “\emph{Quietus,}” said the older boy, and then “\emph{Homenum Revelio}” and some other things, while Harry thought frantically and without much luck.

And then Lesath lowered his wand and sheathed it in his robes, and slowly this time, formally, the older boy dropped to his knees on the dusty classroom floor.

Bowed his head all the way down, until his forehead also touched the dust, and Harry would have spoken but he was voiceless.

Lesath Lestrange said, in a breaking voice, “My life is yours, my Lord, and my death as well.”

“I,” Harry said, there was a huge lump in his throat and he was having trouble speaking, “I—” \emph{didn’t have anything to do with it,} he should have been saying, should be saying \emph{right now,} but then again the innocent Harry would have had trouble speaking too—

“Thank you,” whispered Lesath, “thank you, my Lord, oh, thank you,” the sound of a choked-off sob came from the kneeling boy, all Harry could see of him was the hair on the back of his head, nothing of his face. “I’m a fool, my Lord, an ungrateful bastard, unworthy to serve you, I cannot abase myself enough, for I—I shouted at you after you helped me, because I thought you were refusing me, and I didn’t even realize until this morning that I’d been such a fool as to ask you in front of Longbottom—”

“I didn’t have anything to do with it,” Harry said.

(It was still very hard to tell an outright lie like that.)

Slowly Lesath raised his head from the floor, looked up at Harry.

“I understand, my Lord,” said the older boy, his voice wavering a little, “you do not trust my cunning, and indeed I have shown myself a fool... I only wanted to say to you, that I am not ungrateful, that I know it must have been hard enough to save only one person, that they’re alerted now, that you can’t—get Father—but I am not ungrateful, I will never be ungrateful to you again. If ever you have a use for this unworthy servant, call me wherever I am, and I will answer, my Lord—”

“I was not involved in any way.”

(But it got easier each time.)

Lesath gazed up at Harry, said uncertainly, “Am I dismissed from your presence, my Lord...?”

“I am not your Lord.”

Lesath said, “Yes, my Lord, I understand,” and pushed himself back up from the floor, stood straight and bowed deeply, then backed away from Harry until he turned to open the classroom door.

As Lesath’s hand touched the doorknob, he paused.

Harry couldn’t see Lesath’s face, as the older boy’s voice said, “Did you send her to someone who would take care of her? Did she ask about me at all?”

And Harry said, his voice perfectly level, “Please stop that. I was not involved in any way.”

“Yes, my Lord, I’m sorry, my Lord,” said Lesath’s voice; and the Slytherin boy opened the door and went out and shut the door behind him. His feet sped up as he ran away, but not fast enough that Harry couldn’t hear him start sobbing.

\emph{Would I cry?} wondered Harry. \emph{If I knew nothing, if I was innocent, would I cry right now?}

Harry didn’t know, so he just kept looking at the door.

And some unbelievably tactless part of him thought, \emph{Yay, we completed a quest and got a minion—}

\emph{Shut up. If you ever want to vote on anything ever again...\ shut up.}
\replacement{\sbreak}{}

\subsection{Aftermath, Amelia Bones:}

\noindent{}“Then his life isn’t in danger, I take it,” said Amelia.

The healer, a stern-eyed old man who wore his robes white (he was a Muggleborn and honoring some strange tradition of Muggles, of which Amelia had never asked, although privately she thought it made him look too much like a ghost), shook his head and said, “Definitely not.”

Amelia looked at the human form resting unconscious on the healer’s bed, the burned and blasted flesh, the thin sheet that covered him for modesty’s sake having been peeled back at her command.

He might make a full recovery.

He might not.

The healer had said it was too early to say.

Then Amelia looked at the other witch in the room, the detective.

“And you say,” Amelia said, “that the burning matter was Transfigured from \emph{water}, presumably in the form of ice.”

The detective nodded her head, and said, sounding puzzled, “It could have been much worse, if not for—”

“How \emph{very nice} of them,” she spat, and then pressed a weary hand to her forehead. No...\ no, it \emph{had} been intended as a kindness. By the final stage of the escape there would be no point in trying to fool anyone. Whoever had done this, then, \emph{had} been trying to mitigate the damage—and they’d been thinking in terms of Aurors breathing the smoke, not of anyone being attacked with the fire. If it had been them still in control, no doubt, they would have steered the rocker more mercifully.

But Bellatrix Black had ridden the rocker out of Azkaban alone, all the watching Aurors had agreed on that, they’d had their Anti-Disillusionment Charms active and there had been only one woman on that rocker, though the rocker had sported two sets of stirrups.

Some good and innocent person, capable of casting the Patronus Charm, had been tricked into rescuing Bellatrix Black.

Some innocent had fought Bahry One-Hand, carefully subduing an experienced Auror without significantly injuring him.

Some innocent had Transfigured the fuel for the Muggle artifact on which the two of them had been to ride out of Azkaban, making it from frozen water for the benefit of her Aurors.

And then their usefulness to Bellatrix Black had ended.

You would have expected anyone capable of subduing Bahry One-Hand to have foreseen that part. But then you wouldn’t have expected anyone who could cast the Patronus Charm to try rescuing Bellatrix Black in the first place.

Amelia passed her hand down over her eyes, closing them for a moment in silent mourning. \emph{I wonder who it was, and how You-Know-Who manipulated them...\ what story they could} possibly \emph{have been told...}

She didn’t even realize until a moment later that the thought meant she was starting to believe. Perhaps because, no matter how difficult it was to believe Dumbledore, it was becoming more difficult \emph{not} to recognize the hand of that cold, dark intelligence.
\replacement{\sbreak}{}

\subsection{Aftermath, Albus Dumbledore:}

\noindent{}It might have been only fifty-seven seconds before breakfast ended and he might have needed four twists of his Time-Turner, but in the end, Albus Dumbledore did make it.

“Headmaster?” squeaked the polite voice of Professor Filius Flitwick, as the old wizard passed him by on his way to his seat. “Mr.~Potter left a message for you.”

The old wizard stopped. He looked inquiringly at the Charms Professor.

“Mr.~Potter said that after he woke up, he realized how unfair had been the things he said to you after Fawkes screamed. Mr.~Potter said that he wasn’t saying anything about anything else, just apologizing for that one part.”

The old wizard kept looking at his Charms Professor, and still did not speak.

“Headmaster?” squeaked Filius.

“Tell him I said thank you,” said Albus Dumbledore, “but that it is wiser to listen to phoenixes than to wise old wizards,” and sat down at his place three seconds before all the food vanished.
\replacement{\sbreak}{}

\subsection{Aftermath, Professor Quirrell:}

\noindent{}“No,” Madam Pomfrey snapped at the child, “you may \emph{not} see him! You may not \emph{pester} him! You may not ask him \emph{one little question!} He is to rest \emph{in bed} and do \emph{nothing} for at least \emph{three days!}”
\replacement{\sbreak}{}

\subsection{Aftermath, Minerva McGonagall:}

\noindent{}She was heading toward the infirmary, and Harry Potter was leaving it, when they passed each other.

The look he gave her wasn’t angry.

It wasn’t sad.

It didn’t say much at all.

It was like...\ like he was looking at her just long enough to make it clear that he \emph{wasn’t} deliberately avoiding looking at her.

And then he looked away before she could figure out what look to give him in return; as though he wanted to spare her that, as well.

He didn’t say anything as he walked past her.

Neither did she.

What could there possibly be to say?
\replacement{\sbreak}{}

\subsection{Aftermath, Fred and George Weasley:}

\noindent{}They actually yelped out loud, when they turned the corner and saw Dumbledore.

It wasn’t that the Headmaster had popped up out of nowhere and was staring at them with a stern expression. Dumbledore was always doing \emph{that}.

But the wizard was dressed in formal black robes and looking \emph{very} ancient and \emph{very} powerful and he was giving the two of them a \shout{sharp look}.

“Fred and George Weasley!” spake Dumbledore in a Voice of Power.

“Yes, Headmaster!” they said, snapping upright and giving him a crisp military salute they’d seen in some old pictures.

“Hear me well! You are the friends of Harry Potter, is this so?”

“Yes, Headmaster!”

“Harry Potter is in danger. He \emph{must not} go beyond the wards of Hogwarts. Listen to me, sons of Weasley, I beg you listen: you know that I am as Gryffindor as yourselves, that I too know there are higher rules than rules. But this, Fred and George, this one thing is of the most terrible importance, there must be no exception this time, small or great! If you help Harry to leave Hogwarts he may \emph{die!} Does he send you on a mission, you may go, does he ask you to bring him items, you may help, but if he asks you to smuggle his own person out of Hogwarts, you \emph{must refuse!} Do you understand?”

“Yes, Headmaster!” They said it without even thinking, really, and then exchanged uncertain looks with each other—

The bright blue eyes of the Headmaster were intent upon them. “No. Not without thinking. If Harry asks you to bring him out, you must refuse, if he asks you to tell him the way, you must refuse. I will not ask you to report him to me, for that I know you would never do. But beg him on my behalf to go to \emph{me,} if it is of such importance, and \emph{I} will guard him as he walks. Fred, George, I am sorry to strain your friendship so, but it is his \emph{life.}”

The two of them looked at each other for a long while, not communicating, only thinking the same things at the same time.

They looked back at Dumbledore.

They said, with a chill running through them as they spoke the name, “Bellatrix Black.”

“You may safely assume,” said the Headmaster, “that it is at least that bad.”

“Okay—”

“—got it.”
\replacement{\sbreak}{}

\subsection{Aftermath, Alastor Moody and Severus Snape:}

\noindent{}When Alastor Moody had lost his eye, he had commandeered the services of a most erudite Ravenclaw, Samuel H. Lyall, whom Moody mistrusted slightly less than average because Moody had refrained from reporting him as an unregistered werewolf; and he had paid Lyall to compile a list of every known magical eye, and every known hint to their location.

When Moody had gotten the list back, he hadn’t bothered reading most of it; because at the top of the list was the Eye of Vance, dating back to an era before Hogwarts, and currently in the possession of a powerful Dark Wizard ruling over some tiny forgotten hellhole that wasn’t in Britain or anywhere else he’d have to worry about silly rules.

That was how Alastor Moody had lost his left foot and acquired the Eye of Vance, and how the oppressed souls of Urulat had been liberated for a period of around two weeks before another Dark Wizard moved in on the power vacuum.

He’d considered going after the Left Foot of Vance next, but had decided against it after he realized that would be \emph{just what they were expecting.}

Now Mad-Eye Moody was turning slowly, always turning, surveying the graveyard of Little Hangleton. It should have been a lot gloomier, that place, there should have been some mark of all the death which had been planned there in Voldie’s meetings, but in the broad daylight it seemed like nothing but a grassy place marked by ordinary tombstones, demarcated by the chained twists of fragile, easily climbable metal that Muggles used instead of wards. (Moody could not comprehend what the Muggles were thinking on that score, if they were \emph{pretending} to have wards, or what, and he had decided not to ask whether Muggle criminals respected the pretense.)

Moody didn’t actually \emph{need} to turn to survey the graveyard, of course.

The Eye of Vance saw the full globe of the world in every direction around him, no matter where it was pointing.

But there was no particular reason to let a former Death Eater like Severus Snape know that.

Sometimes people called Moody ‘paranoid’.

Moody always told them to survive a hundred years of hunting Dark Wizards and then get back to him about that.

Mad-Eye Moody had once worked out how long it had taken him, in retrospect, to achieve what he now considered a decent level of caution—weighed up how much experience it had taken him to get \emph{good} instead of \emph{lucky}—and had begun to suspect that most people died before they got there. Moody had once expressed this thought to Lyall, who had done some ciphering and figuring, and told him that a typical Dark Wizard hunter would die, on average, eight and a half times along the way to becoming ‘paranoid’. This explained a great deal, assuming Lyall wasn’t lying.

Yesterday, Albus Dumbledore had told Mad-Eye Moody that the Dark Lord had used unspeakable dark arts to survive the death of his body, and was now awake and abroad, seeking to regain his power and begin the Wizarding War anew.

Someone else might have reacted with incredulity.

“I can’t believe you lot never told me about this resurrection thing,” Mad-Eye Moody said with considerable acerbity. “D’you realize how long it’ll take me to do the grave of every ancestor of every Dark Wizard I’ve ever killed who could’ve been smart enough to make a horcrux? You’re not just \emph{now} doing this one, are you?”

“I redose this one every year,” Severus Snape said calmly, uncapping the third flask of what the man had \emph{claimed} would be seventeen bottles, and beginning to wave his wand over it. “The other ancestral graves we’ve been able to locate were poisoned with only the long-lasting substances, since some of us have less free time than yourself.”

Moody watched the fluid spiraling out of the vial and vanishing, to appear within the bones where marrow had once been. “But you think it’s worth the effort of the trap, instead of just Vanishing the bones.”

“He \emph{does} have other avenues to life, should he perceive this one blocked,” Snape said dryly, uncapping a fourth bottle. “And before you ask, it must be the original grave, the place of first burial, the bone removed during the ritual and not before. Thus he cannot have retrieved it earlier; and also there is no point in substituting the skeleton of a weaker ancestor. He would notice it had lost all potency.”

“Who else knows about this trap?” Moody demanded.

“You. Me. The Headmaster. No one else.”

Moody snorted. “Pfah. Did Albus tell Amelia, Bartemius, and that McGonagall woman about the resurrection ritual?”

“Yes—”

“If Voldie finds out that Albus knows about the resurrection ritual and that Albus told \emph{them}, Voldie’ll figure that Albus told \emph{me,} and Voldie \emph{knows} I’d think of this.” Moody shook his head in disgust. “What’re these other ways Voldie could come back to life?”

Snape’s hand paused on the fifth bottle (it was all Disillusioned, of course, the whole operation was Disillusioned, but that meant less than nothing to Moody, it just marked you in his Eye’s sight as trying-to-hide), and the former Death Eater said, “You don’t need to know.”

“You’re learning, son,” said Moody with mild approval. “What’s in the bottles?”

Snape opened the fifth bottle, gestured with his wand to begin the substance flowing toward the grave, and said, “This one? A Muggle narcotic called \abbrev{LSD}. A conversation yesterday put me in mind of Muggle things, and \abbrev{LSD} seemed the most interesting option, so I hurried to obtain some. If it is incorporated into the resurrection potion, I suspect its effects will be permanent.”

“What does it do?” said Moody.

“It is said that the effects are impossible to describe to anyone who has not used it,” drawled Snape, “and I have not used it.”

Moody nodded approval as Snape opened the sixth flask. “What about that one?”

“Love potion.”

\emph{“Love potion?}” said Moody.

“Not of the standard sort. It is meant to trigger a two-way bond with an unbearably sweet Veela woman named Verdandi who the Headmaster hopes might be able to redeem even him, if they truly loved each other.”

“\emph{Gah!}” said Moody. “That bloody sentimental fool—”

“Agreed,” Severus Snape said calmly, his attention focused on his work.

“Tell me you’ve at least got some Malaclaw venom in there.”

“Second flask.”

“Iocane powder.”

“Either the fourteenth or fifteenth bottle.”

“Bahl’s Stupefaction,” Moody said, naming an extremely addictive narcotic with interesting side effects on people with Slytherin tendencies; Moody had once seen an addicted Dark Wizard go to ridiculous lengths to get a victim to lay hands on a certain exact portkey, instead of just having someone toss the target a trapped Knut on their next visit to town; and after going to all that work, the addict had gone to the \emph{further} effort to lay a \emph{second Portus,} on the \emph{same portkey,} which had, on a second touch, transported the victim back to safety. To this day, even taking the drug into account, Moody could not imagine what could have possibly been going through the man’s mind at the time he had cast the second Portus.

“Tenth vial,” said Snape.

“Basilisk venom,” offered Moody.

“\emph{What?}” spat Snape. “Snake venom is a positive component of the resurrection potion, you fool! Not to mention that it would dissolve the bone and all the other substances! And where would \emph{we} even get—”

“Calm down, son, I was just checking to see if you could be trusted.”

Mad-Eye Moody continued his (secretly unnecessary) slow turning, surveying the graveyard, and the Potions Master continued pouring.

“Hold on,” Moody said suddenly. “How do you know \emph{this} is really where—”

“Because it says ‘Tom Riddle’ on the easily moved headstone,” Snape said dryly. “And I have just won ten Sickles from the Headmaster, who bet you would think of that before the fifth bottle. So much for constant vigilance.”

There was a pause.

“How long did it take Albus to reali—”

“Three years after we learned of the ritual,” said Snape, in a tone not quite like his usual sardonic drawl. “In retrospect, we should have consulted you earlier.”

Snape uncapped the ninth bottle.

“We poisoned all the other graves as well, with long-lasting substances,” remarked the former Death Eater. “It \emph{is} possible that we are in the correct graveyard. He may not have planned this far ahead back when he was slaughtering his family, and he cannot move the grave itself—”

“The true location doesn’t look like a graveyard any more,” Moody said flatly. “He moved all the \emph{other} graves here and Memory-Charmed the Muggles. Not even Bellatrix Black would be told anything about that until just before the ritual started. \emph{No one} knows the true location now except him.”

They continued their futile work.
\replacement{\sbreak}{}

\subsection{Aftermath, Blaise Zabini:}

\noindent{}The Slytherin common room could be accurately and precisely described as a remilitarized zone; the moment you stepped through the portrait hole you would see that the left half of the room was Definitely Not Talking to the right half and vice versa. It was very clear, it did not need to be explained to anyone, that you did \emph{not} have the option of \emph{not taking sides}.

At a table in the exact middle of the room, Blaise Zabini sat by himself, reading a book and smirking. He had a reputation now, and meant to keep it.
\replacement{\sbreak}{}

\subsection{Aftermath, Daphne Greengrass and Tracey Davis:}

\noindent{}“You doing anything interesting today?” said Tracey.

“Nah,” said Daphne, “just some reading.”
\replacement{\sbreak}{}

\subsection{Aftermath, Harry Potter:}

\noindent{}If you went high enough in Hogwarts, you didn’t see many other people around, just corridors and windows and staircases and the occasional portrait, and now and then some interesting sight, such as a bronze statue of a furry creature like a small child, holding a peculiar flat spear...

If you went high enough in Hogwarts, you didn’t see many other people around, which suited Harry.

There were much worse places to be trapped, Harry supposed. In fact you probably couldn’t think of anywhere \emph{better} to be trapped than an ancient castle with a fractal ever-changing structure that meant you couldn’t ever run out of places to explore, full of interesting people and interesting books and incredibly important knowledge unknown to Muggle science.

If Harry hadn’t been told that he \emph{couldn’t} leave, he probably would’ve \emph{jumped} at the chance to spend more time in Hogwarts, he would’ve plotted and connived to get it. Hogwarts was literally \emph{optimal,} not in all the realms of possibility maybe, but certainly on the real planet Earth, it was the Maximum Fun Location.

How could the castle and its grounds seem so much smaller, so much more confining, how could the rest of the world become so much more interesting and important, the instant Harry had been told that he wasn’t allowed to leave? He’d spent \emph{months} here and hadn’t felt claustrophobic \emph{then.}

\emph{You} know \emph{the research on this,} observed some part of himself, \emph{it’s just standard scarcity effects, like that time where as soon as a county outlawed phosphate detergents, people who’d never cared before drove to the next county in order to buy huge loads of phosphate detergent, and surveys showed that they rated phosphate detergents as gentler and more effective and even easier-pouring...\ and if you give two-year-olds a choice between a toy in the open and one protected by a barrier they can go around, they’ll ignore the toy in the open and go for the one behind the barrier...\ salespeople know that they can sell things just by telling the customer it might not be available...\ it was all in Cialdini’s book} Influence, \emph{everything you’re feeling right now, the grass is always greener on the side that’s not allowed.}

If Harry hadn’t been told that he couldn’t leave, he probably would’ve \emph{jumped} at the chance to stay at Hogwarts over the summer...

...but not the rest of his life.

That was sort of the problem, really.

Who knew whether there \emph{was} still a Dark Lord Voldemort for him to defeat?

Who knew whether He-Who-Must-Not-Be-Named still existed outside of the imagination of a possibly-not-just-pretending-to-be-crazy old wizard?

Lord Voldemort’s body had been found burned to a crisp, there couldn’t really be such things as souls. How could Lord Voldemort still be alive? How did Dumbledore \emph{know} that he was alive?

And if there wasn’t a Dark Lord, Harry couldn’t defeat him, and he would be trapped in Hogwarts forever.

...maybe he would be legally allowed to escape after he graduated his seventh year, six years and four months and three weeks from now. It wasn’t \emph{that} long as lengths of time went, it only \emph{seemed} like long enough for protons to decay.

Only it wasn’t \emph{just} that.

It wasn’t \emph{just} Harry’s freedom that was at stake.

The Headmaster of Hogwarts, the Chief Warlock of the Wizengamot, the Supreme Mugwump of the International Confederation of Wizards, was quietly sounding the alarm.

A \emph{false} alarm.

A false alarm which \emph{Harry} had triggered.

\emph{You know,} said the part of him that refined his skills, \emph{didn’t you sort of ponder, once, how every different profession has a different way to be excellent, how an excellent teacher isn’t like an excellent plumber; but they all have in common certain methods of not being stupid; and that one of the most important such techniques is to face up to your little mistakes before they turn into \shout{big} mistakes?}

...although this already seemed to qualify as a \shout{big} mistake, actually...

\emph{The point being,} said his inner monitor, \emph{it’s getting worse literally by the minute. The way spies turn people is, they get them to commit a little sin, and then they use the little sin to blackmail them into a bigger sin, and then they use \shout{that} sin to make them do even bigger things and then the blackmailer owns their soul.}

\emph{Didn’t you once think about how the person being blackmailed, if they could foresee the whole path, would just decide to take the punch on the first step, take the hit of exposing that first sin? Didn’t you decide that you would do that, if anyone ever tried to blackmail you into doing something major in order to conceal something little? Do you see the similarity here, Harry James Potter-Evans-Verres?}

Only it wasn’t little, it already wasn’t little, there would be a lot of very powerful people extremely angry at Harry, not just for the false alarm but for \emph{freeing Bellatrix from Azkaban,} if the Dark Lord \emph{did} exist and did come after him later, that war might already be lost—

\emph{You don’t think they’ll be impressed by your honesty and rationality and foresight in stopping this before it snowballs even further?}

Harry did \emph{not}, in fact, think this; and after a moment’s reflection, whichever part of himself he was talking to, had to agree that this was absurdly optimistic.

His wandering feet took him near an open window, and Harry went over, and leaned his arms on the ledge, and stared down at the grounds of Hogwarts from high above.

Brown that was barren trees, yellow that was dead grass, ice-colored ice that was frozen creeks and frozen streams...\ whichever school official had dubbed it ‘The Forbidden Forest’ really hadn’t understood marketing, the name just made you want to go there even more. The sun was sinking in the sky, for Harry had been thinking for some hours now, thinking mostly the same thoughts over and over, but with key differences each time, like his thoughts were not going in circles, but climbing a spiral, or descending it.

He still couldn’t believe that he’d gone through the \emph{entire} thing with Azkaban—he’d switched off his Patronus before it took all his life, he’d stunned an Auror, he’d figured out how to hide Bella from the Dementors, he’d faced down twelve Dementors and scared them away, he’d invented the rocket-assisted broomstick, and ridden it—he’d gone through the \emph{entire} thing without ever \emph{once} rallying himself by thinking, \emph{I have to do this...\ because... I promised Hermione I’d come back from lunch!} It felt like some sort of irrevocably missed opportunity, like, having done it wrong \emph{that} time, he would never be able to get it \emph{right} no matter what sort of challenge he faced the next time, or what sort of promise he’d made to who. Because then he would just be doing it awkwardly and deliberately to make up for having missed it the \emph{first} time around, instead of being able to make the same sort of heroic declarations he’d be able to make if he’d managed to remember his promise to Hermione. Like that one wrong turn was irrevocable, you only got one chance, had to do it right on the first try...

He should’ve remembered that promise to Hermione \emph{before} going to Azkaban.

Why had he decided to do that, again?

\emph{My working hypothesis is that you’re stupid,} said Hufflepuff.

\emph{That is not a useful fault analysis,} thought Harry.

\emph{If you want a little more detail,} said Hufflepuff, \emph{the Defense Professor of Hogwarts was all like ‘Let’s get Bellatrix Black out of Azkaban!’ and you were like ‘Okay!’}

\emph{Hold on, \shout{that’s} not fair—}

\emph{Hey,} said Hufflepuff, \emph{notice how, once you’re all the way up here, and the individual trees sort of blur together, you can actually see the shape of the forest?}

Why \emph{had} he done it...?

Not because of any cost-benefit calculation, that was for sure. He’d been too embarrassed to pull out a sheet of paper and start calculating expected utilities, he’d worried that Professor Quirrell would stop respecting him if he said no or even hesitated too much to help a maiden in distress.

He’d thought, somewhere deep inside him, that if your mysterious teacher offered you the first mission, the first chance, the call to adventure, and you said \emph{no}, then your mysterious teacher walked away from you in disgust, and you never got another chance to be a hero...

...yeah, that had been it. In retrospect, that had been it. He’d gone and started thinking his life had a plot and here was a plot twist, as opposed to, oh, say, here was a proposal to \emph{break Bellatrix Black out of Azkaban.} That had been the true and original reason for the decision in the split second where it had been made, his brain perceptually recognizing the narrative where he said ‘no’ as dissonant. And when you thought about it, that wasn’t a rational way to make decisions. Professor Quirrell’s ulterior motive to obtain the last remains of Slytherin’s lost lore, before Bellatrix died and it was irrevocably forgotten, seemed impressively sane by comparison; a benefit commensurate with what had appeared at the time as a small risk.

It didn’t seem fair, it didn’t seem \emph{fair}, that \emph{this} was what happened if he lost his grip on his rationality for just a tiny fraction of a second, the tiny fraction of a second required for his brain to decide to be more comfortable with ‘yes’ arguments than ‘no’ arguments during the discussion that had followed.

From high above, far enough above that the individual trees blurred together, Harry stared out at the forest.

Harry \emph{didn’t} want to confess and ruin his reputation forever and get everyone angry at him and maybe end up killed by the Dark Lord later. He’d rather be trapped in Hogwarts for six years than face that. That was how he felt. And so it was in fact helpful, a relief, to be able to cling to a single decisive factor, which was that if Harry confessed, Professor Quirrell would go to Azkaban and die there.

(A catch, a break, a stutter in Harry’s breathing.)

If you phrased it \emph{that} way...\ why, you could even pretend to be a hero, instead of a coward.

Harry lifted his eyes from the Forbidden Forest, looked up at the clear blue forbidden sky.

Stared out the glass panes at the big bright burning thing, the fluffy things, the mysterious endless blue in which they were embedded, that strange new unknown place.

It...\ actually did help, it helped quite a lot, to think that his own troubles were nothing compared to being in Azkaban. That there were people in the world who were \emph{really} in trouble and Harry Potter was not one of them.

What was he going to do about Azkaban?

What was he going to do about magical Britain?

...which side was he on, now?

In the bright light of day, everything that Albus Dumbledore had said certainly \emph{sounded} a lot wiser than Professor Quirrell. Better and brighter, more moral, more \emph{convenient,} wouldn’t it be nice if it were true. And the thing to remember was that Dumbledore believed things \emph{because} they sounded nice, but Professor Quirrell was the one who was \emph{sane}.

(Again the catch in his breathing, it happened each time he thought of Professor Quirrell.)

But just because something sounded nice, didn’t make it \emph{wrong,} either.

And if the Defense Professor \emph{did} have a flaw in his sanity, it was that his outlook on life was \emph{too negative.}

\emph{Really?} inquired the part of Harry that had read eighteen million experimental results about people being too optimistic and overconfident. \emph{Professor Quirrell is too pessimistic? So pessimistic that his expectations routinely} undershoot \emph{reality? Stuff him and put him in a museum, he’s unique. Which one of you two planned the perfect crime, and} then \emph{put in all the error margin and fallbacks that ended up saving your butt,} just in case \emph{the perfect crime went wrong? Hint hint, his name wasn’t Harry Potter.}

But “pessimistic” wasn’t the correct word to describe Professor Quirrell’s problem—if a problem it truly was, and not the superior wisdom of experience. But to Harry it looked like Professor Quirrell was constantly interpreting everything in the worst possible light. If you handed Professor Quirrell a glass that was 90\% full, he’d tell you that the 10\% empty part proved that no one \emph{really} cared about water.

That was a very good analogy, now that Harry thought about it. Not all of magical Britain was like Azkaban, that glass was well over half full...

Harry stared up at the bright blue sky.

...although, \emph{following} the analogy, if Azkaban existed, then maybe it \emph{did} prove that the 90\% good part was there for other reasons, people trying to \emph{make a show of kindness} as Professor Quirrell had put it. For if they were truly kind they would not have made Azkaban, they would storm the fortress to tear it down...\ wouldn’t they?

Harry stared up at the bright blue sky. If you wanted to be a rationalist you had to read an awful lot of papers on flaws in human nature, and some of those flaws were innocent logical failures, and some of them looked a lot darker.

Harry stared up at the bright blue sky, and thought of the Milgram experiment.

Stanley Milgram had done it to investigate the causes of World~War~II, to try to understand why the citizens of Germany had obeyed Hitler.

So he had designed an experiment to investigate \emph{obedience,} to see if Germans were, for some reason, more liable to obey harmful orders from authority figures.

First he’d run a pilot version of his experiment on American subjects, as a control.

And afterward he hadn’t bothered trying it in Germany.

Experimental apparatus: A series of 30 switches set in a horizontal line, with labels starting at ‘15 volts’ and going up to ‘450 volts’, with labels for each group of four switches. The first group of four labeled ‘Slight Shock’, the sixth group labeled ‘Extreme Intensity Shock’, the seventh group labeled ‘Danger: Severe Shock’, and the two last switches left over labeled just ‘XXX’.

And an actor, a confederate of the experimenter, who had appeared to the true subjects to be someone just like them: someone who had answered the same ad for participants in an experiment on learning, and who had lost a (rigged) lottery and been strapped into a chair, along with the electrodes. The true experimental subjects had been given a slight shock from the electrodes, just so that they could see that it worked.

The true subject had been told that the experiment was on the effects of punishment on learning and memory, and that part of the test was to see if it made a difference what sort of person administered the punishment; and that the person strapped to the chair would try to memorize sets of word pairs, and that each time the ‘learner’ got one wrong, the ‘teacher’ was to administer a successively stronger shock.

At the 300-volt level, the actor would stop trying to call out answers and begin kicking at the wall, after which the experimenter would instruct the subjects to treat non-answers as wrong answers and continue.

At the 315-volt level the pounding on the wall would be repeated.

After that nothing would be heard.

If the subject objected or refused to press a switch, the experimenter, maintaining an impassive demeanor and dressed in a gray lab coat, would say ‘Please continue’, then ‘The experiment requires that you continue’, then ‘It is absolutely essential that you continue’, then ‘You have no other choice, you \emph{must} go on’. If the fourth prod still didn’t work, the experiment halted there.

Before running the experiment, Milgram had described the experimental setup, and then asked fourteen psychology seniors what percentage of subjects \emph{they} thought would go all the way up to the 450-volt level, what percentage of subjects would press the last of the two switches marked XXX, after the victim had stopped responding.

The most pessimistic answer had been 3\%.

The actual number had been 26 out of 40.

The subjects had sweated, groaned, stuttered, laughed nervously, bitten their lips, dug their fingernails into their flesh. But at the experimenter’s prompting, they had, most of them, gone on administering what they believed to be painful, dangerous, possibly lethal electrical shocks. All the way to the end.

Harry could hear Professor Quirrell laughing, in his mind; the Defense Professor’s voice saying something along the lines of: \emph{Why, Mr.~Potter, even I had not been so cynical; I knew men would betray their most cherished principles for money and power, but I did not realize that a stern look also sufficed.}

It was dangerous, to try and guess at evolutionary psychology if you weren’t a professional evolutionary psychologist; but when Harry had read about the Milgram experiment, the thought had occurred to him that situations like this had probably arisen many times in the ancestral environment, and that most potential ancestors who’d tried to disobey Authority were dead. Or that they had, at least, done less well for themselves than the obedient. People \emph{thought} themselves good and moral, but when push came to shove, some evolved switch flipped in their brain, and it was suddenly a lot harder to heroically defy Authority than they thought. Even if you could do it, it wouldn’t be easy, it wouldn’t be some effortless display of heroism. You would tremble, your voice would break, you would be afraid; would you be able to defy Authority even then?

Harry blinked, then; because his brain had just made the connection between Milgram’s experiment and what Hermione had done on her first day of Defense class, she’d refused to shoot a fellow student, even when Authority had told her that she must, she had trembled and been afraid but she had still refused. Harry had seen that happen right in front of his own eyes and he still hadn’t made the connection until now...

Harry stared down at the reddening horizon, the Sun was sinking lower, the sky fading, darkening, even if most of it was still blue, soon it would turn to night. The gold and red colors of Sun and sunset reminded him of Fawkes; and Harry wondered, for a moment, if it must be a sad thing to be a phoenix, and call and cry and scream without being heeded.

But Fawkes would never give up, as many times as he died he would always be reborn, for Fawkes was a being of light and fire, and despairing over Azkaban belonged to the darkness just as much as did Azkaban itself.

If you were given a glass half-empty and half-full, then that was the way reality was, that was the truth and it was so; but you still had a choice of how to \emph{feel} about it, whether you would despair over the empty half or rejoice in the water that was there.

Milgram had tried certain other variations on his test.

In the eighteenth experiment, the experimental subject had only needed to call out the test words to the victim strapped into the chair, and record the answers, while someone \emph{else} pressed the switches. It was the same apparent suffering, the same frantic pounding followed by silence; but it wasn’t \emph{you} pressing the switch. \emph{You} just watched it happen, and read the questions to the person being tortured.

37 of 40 subjects had continued their participation in that experiment to the end, the 450-volt end marked ‘XXX’.

And if you were Professor Quirrell, you might have decided to feel cynical about that.

But 3 out of 40 subjects had \emph{refused} to participate all the way to the end.

The Hermiones.

They did exist, in the world, the people who wouldn’t fire a Simple Strike Hex at a fellow student even if the Defense Professor ordered them to do it. The ones who had sheltered Gypsies and Jews and homosexuals in their attics during the Holocaust, and sometimes lost their lives for it.

And were those people from some other species than humanity? Did they have some extra gear in their heads, some additional chunk of neural circuitry, which lesser mortals did not possess? But that was not likely, given the logic of sexual reproduction which said that the genes for complex machinery would be scrambled beyond repair, if they were not universal.

Whatever parts Hermione was made from, everyone had those same parts inside them somewhere...

...well, that was a nice thought but it wasn’t \emph{strictly} true, there was such a thing as literal brain damage, people could \emph{lose} genes and the complex machine could stop working, there were sociopaths and psychopaths, people who lacked the gear to care. Maybe Lord Voldemort had been born like that, or maybe he had known good and yet still chosen evil; at this point it didn’t matter in the slightest. But a \emph{supermajority} of the population ought to be capable of learning to do what Hermione and Holocaust resisters did.

The people who had been run through the Milgram experiment, who had trembled and sweated and nervously laughed as they went all the way to pressing the switches marked ‘XXX’, many of them had written to thank Milgram, afterward, for what they had learned about themselves. That, too, was part of the story, the legend of that legendary experiment.

The Sun had almost sunk below the horizon now, a last golden tip peeking above the faraway tops of trees.

Harry looked at it, that tip of Sun, his glasses were supposed to be proof against \abbrev{UV} so he ought to be able to look directly at it without damaging his eyes.

Harry stared directly at it, that tiny fraction of the Light that was not obscured and blocked and hidden, even if it was only 3 parts out of 40, the other 37 parts were there somewhere. The 7.5\% of the glass that was full, which proved that people really did care about water, even if that force of caring within themselves was too often defeated. If people truly didn’t care, the glass would have been truly empty. If everyone had been like You-Know-Who inside, secretly cleverly selfish, there would have been no resisters to the Holocaust at all.

Harry looked at the sunset, on the second day of the rest of his life, and knew that he had switched sides.

Because he couldn’t believe in it any more, he couldn’t really, not after going to Azkaban. He couldn’t do what 37 out of 40 people would vote for him to do. Everyone might have inside them what it took to be Hermione, and someday they might learn; but \emph{someday} wasn’t \emph{now}, not here, not today, not in the real world. If you were on the side of 3 out of 40 people then you weren’t a political majority, and Professor Quirrell had been right, Harry would not bow his head in submission when that happened.

There was a sort of awful appropriateness to it. You shouldn’t go to Azkaban and come back having not changed your mind about anything important.

\emph{So is Professor Quirrell right, then?} asked Slytherin. \emph{Leaving out whether he’s good or evil, is he} right? \emph{Are you, to them, whether they know it or not, their next Lord? We’ll just leave out the Dark part, that’s him being cynical again. But is it your intention now to rule? I’ve got to say, that makes even} me \emph{nervous.}

\emph{Do you think you can be trusted with power?} said Gryffindor. \emph{Isn’t there some sort of rule that people who want power shouldn’t have it? Maybe we should make Hermione the ruler instead.}

\emph{Do you think you’re fit to run a society and not have it collapse into total chaos inside of three weeks flat?} said Hufflepuff. \emph{Imagine how loudly Mum would scream if she’d heard you’d been elected Prime Minister, now ask yourself, are you sure she’s wrong about that?}

\emph{Actually,} said Ravenclaw, \emph{I have to point out that all this political stuff sounds overwhelmingly boring. How about if we leave all the electioneering to Draco and stick to science? It’s what we’re actually good at, and that’s been known to improve the human condition too, y’know.}

\emph{Slow down,} thought Harry at his components, \emph{we don’t have to decide everything right now. We’re allowed to ponder the problem as fully as possible before coming to a solution.}

The last part of the Sun sank below the horizon.

It was strange, this feeling of not quite knowing who you were, which side you were on, of having \emph{not already made up your mind} about something as major as that, there was an unfamiliar sensation of freedom in it...

And that reminded him of what Professor Quirrell had said to his last question, which reminded him of Professor Quirrell, which made it hard once more to breathe, started that burning sensation in Harry’s throat, sent his thoughts around that loop of the climbing spiral once again.

Why was he so sad, now, whenever he thought of Professor Quirrell? Harry was used to knowing himself, and he didn’t know why he felt so sad...

It felt like he’d lost Professor Quirrell forever, lost him in Azkaban, that was how it felt. As surely as if the Defense Professor had been eaten by Dementors, consumed in the empty voids.

\emph{Lost him! Why did I lose him? Because he said Avada Kedavra and there was in fact a perfectly good reason even though I didn’t see it for a couple of hours? Why can’t things go back to the way they were?}

But then it hadn’t \emph{been} the Avada Kedavra. That might have played a part in irreversibly collapsing a structure of rationalizations and flinches and carefully not thinking about certain things. But it hadn’t been the Avada Kedavra, that hadn’t been the disturbing thing that Harry had seen.

\emph{What did I see...?}

Harry looked at the fading sky.

He’d seen Professor Quirrell turn into a hardened criminal while facing the Auror, and the apparent change of personalities had been effortless, and complete.

Another woman had known the Defense Professor as ‘Jeremy Jaffe’.

\emph{How many different people are you, anyway?}

\emph{I cannot say that I bothered keeping count.}

You couldn’t help but wonder...

...whether ‘Professor Quirrell’ was just one more name on the list, just one more person that had been \emph{turned into}, made up in the service of some unguessable goal.

Harry would always be wondering now, every time he talked to Professor Quirrell, if it was a mask, and what motive was behind that mask. With every dry smile, Harry would be trying to see what was pulling the levers on the lips.

\emph{Is that how other people will start thinking of me, if I get too Slytherin? If I pull off too many plots, will I never be able to smile at anyone again, without them wondering what I really mean by it?}

Maybe there was some way to restore a trust in surface appearances and make a normal human relationship possible again, but Harry couldn’t think of what it might be.

That was how Harry had lost Professor Quirrell, not the person, but the...\ connection...

Why did that hurt so much?

Why did it feel so lonely, now?

Surely there were other people, maybe better people, to trust and befriend? Professor McGonagall, Professor Flitwick, Hermione, Draco, not to mention Mum and Dad, it wasn’t like Harry was \emph{alone...}

Only...

A choking sensation grew in Harry’s throat as he understood.

Only Professor McGonagall, Professor Flitwick, Hermione, Draco, they all of them sometimes knew things that Harry didn’t, but...

They did not excel above Harry \emph{within} his own sphere of power; such genius as they possessed was not like his genius, and his genius was not like theirs; he might look upon them as peers, but not look \emph{up} to them as his \emph{superiors.}

None of them had been, none of them could ever be...

Harry’s mentor...

That was who Professor Quirrell had been.

That was who Harry had lost.

And the manner in which he had lost his first mentor might or might not allow Harry to ever get him back. Maybe someday he would know all Professor Quirrell’s hidden purposes and the doubts between them would go away; but even if that seemed possible, it didn’t seem very probable.

There was a gust of wind, outside Hogwarts, it bent the empty trees, rippled the lake whose heart was still unfrozen, made a whispering sound as it slid past the window that looked upon the half-twilit world, and Harry’s thoughts wandered outward for a time.

Then returned inward again, to the next step of the spiral.

\emph{Why am I different from the other children my age?}

If Professor Quirrell’s answer to that had been an evasion, then it was a very well-calculated one. Deep enough and complex enough, sufficiently full of suggestions of hidden meaning, to serve as a trap for a Ravenclaw who couldn’t be diverted by less. Or maybe Professor Quirrell had meant his answer honestly. Who knew what motive might have pulled that lever on those lips?

\emph{I will say this much, Mr.~Potter: You are already an Occlumens, and I think you will become a perfect Occlumens before long. Identity does not mean, to such as us, what it means to other people. Anyone we can imagine, we can be; and the true difference about you, Mr.~Potter, is that you have an unusually good imagination. A playwright must contain his characters, he must be larger than them in order to enact them within his mind. To an actor or spy or politician, the limit of his own diameter is the limit of who he can pretend to be, the limit of which face he may wear as a mask. But for such as you and I, anyone we can imagine, we can} be, \emph{in reality and not pretense.} \emph{While you imagined yourself a child, Mr.~Potter, you} were \emph{a child. Yet there are other existences you could support, larger existences, if you wished. Why are you so free, and so great in your circumference, when other children your age are small and constrained? Why can you imagine and} become \emph{selves more adult than a mere child of a playwright should be able to compose? That I do not know, and I must not say what I guess. But what you have, Mr.~Potter, is freedom.}

If that was a snow job it was one heck of a distracting one.

And the still more worrisome thought was that Professor Quirrell hadn’t \emph{realized} how disturbed Harry would be, how \emph{wrong} that speech would sound to him, how much damage it would do to his trust in Professor Quirrell.

There ought to always be one real person who you \emph{truly} were, at the center of everything...

Harry stared out at the falling night, the gathering darkness.

...right?
\sbreak
It was almost bedtime when Hermione heard the scattered intakes of breath and looked up from her copy of \emph{Beauxbatons: A History} to see the missing boy, the boy who had been misplaced at lunch that Sunday, whose dinner nonappearance had been accompanied by rumors—and she hadn’t believed them because they were \emph{completely ridiculous}, but she’d felt a little queasiness inside—that he’d withdrawn from Hogwarts in order to hunt down Bellatrix Black.

“\emph{Harry!}” she shrieked, she didn’t even realize that she was talking directly to him for the first time in a week, or notice how some other students started at the sound of her yelling all the way across the Ravenclaw common room.

Harry’s eyes had already lifted to her, he was already walking toward her, so she stopped halfway out of her chair—

A few moments later, Harry was seated across from her, and he was putting away his wand after casting a Quieting barrier around them.

(And an awful lot of Ravenclaws were trying not to look like they were watching.)

“Hey,” Harry said. His voice wavered. “I missed you. You’re...\ going to talk to me again, now?”

Hermione nodded, she just nodded, she couldn’t think of what to say. She’d missed Harry too, but she was realizing, with a guilty sort of feeling, that it might’ve been a lot worse for him. She had other friends, Harry...\ it didn’t feel \emph{fair}, sometimes, that Harry talked to only her like that, so that she \emph{had} to talk to him; but Harry had a look about him like unfair things had been happening to \emph{him}, too.

“What’s been going \emph{on?}” she said. “There’s all sorts of rumors. There were people saying you’d run off to fight Bellatrix Black, there were people saying you’d run off to \emph{join} Bellatrix Black—” and \emph{those} rumors had said that Hermione had just made up the thing about the phoenix, and she’d yelled that the whole Ravenclaw common room had seen it, so then the next rumor had claimed she’d made up \emph{that} part too, which was stupidity of such an inconceivable level that it left her \emph{completely flabbergasted.}

“I can’t talk about it,” Harry said in a bare whisper. “Can’t talk about a lot of it. I wish I could tell you everything,” his voice wavered, “but I can’t... I guess, if it helps or anything, I’m not going to lunch with Professor Quirrell any more...”

Harry put his hands over his face, then, covering his eyes.

Hermione felt the queasy feeling all through her stomach.

“Are you crying?” said Hermione.

“Yeah,” said Harry, his voice sounding a little breathy. “I don’t want anyone else to see.”

There was a little silence. Hermione wanted to help but she didn’t know what to do about a boy crying, and she didn’t know what was happening; she felt like huge things were happening around her—no, around Harry—and if she knew what they were she would probably be scared, or alarmed, or something, but she didn’t know anything.

“Did Professor Quirrell do something wrong?” she said at last.

“That’s not why I can’t go to lunch with him any more,” Harry said, still in that bare whisper with his hands pressed over his eyes. “That was the Headmaster’s decision. But yeah, Professor Quirrell said some things to me that made me trust him less, I guess...” Harry’s voice sounded very shaky. “I’m feeling kind of alone right now.”

Hermione put her hand on her cheek, for a moment, where Fawkes had touched her yesterday. She’d kept thinking about that touch, over and over, maybe because she \emph{wanted} it to be important, to mean something to her...

“Is there any way I can help?” she said.

“I want to do something normal,” Harry said from behind his hands. “Something very normal for first-year Hogwarts students. Something eleven-year-olds and twelve-year-olds like us are \emph{supposed} to do. Like play a game of Exploding Snap or something... I don’t suppose you have the cards or know the rules or anything like that?”

“Um... I \emph{don’t} know the rules, actually...” said Hermione. “I know they \emph{explode}.”

“I don’t suppose Gobstones?” said Harry.

“Don’t know the rules and they \emph{spit} at you. Those are \emph{boy} games, Harry!”

There was a pause. Harry ground his hands against his face to wipe it, and then took his hands away; and then he was looking at her, looking a little helpless. “Well,” Harry said, “what \emph{do} wizards and witches our age do, when they play, you know, the kind of pointless silly games we’re \emph{supposed} to play at this age?”

“Hopscotch?” said Hermione. “Jump-rope? Unicorn attack? \emph{I} don’t know, \emph{I} read books!”

Harry started laughing, and Hermione started giggling along with him even though she didn’t know quite why, but it \emph{was} funny.

“I guess that helped a little,” said Harry. “Actually I think it helped more than playing Gobstones for an hour could’ve possibly helped, so thanks for being you. And no matter what, I’m \emph{not} having anyone Obliviate everything I know about calculus. I’d sooner die.”

“\emph{What?}” said Hermione. “Why—why would you \emph{ever} want to do \emph{that?}”

Harry stood up from the table, and there was a rush of restored background noise as his rise broke the Quieting Charm. “I’m a tad sleepy so I’m going off to bed,” Harry said, now his voice was ordinary and wry, “I’ve got some lost time to make up for, but I’ll see you at breakfast, and then at Herbology, if that’s all right. Not to mention it wouldn’t be fair to dump all my depression on you. G’night, Hermione.”

“Good night, Harry,” she said, feeling very confused and alarmed. “Pleasant dreams.”

Harry stumbled a little as she said that, and then he continued on toward the stairs that led to the first-year-boys’ dorms.
\sbreak
Harry turned the Quieting Charm all the way up, on the head of his bedboard, so that he wouldn’t wake anyone else up if he screamed.

Set his alarm to wake him up for breakfast (if he wasn’t up already by that hour, if indeed he slept at all).

Got into bed, laid down—

—felt the lump beneath his pillow.

Harry stared up at the canopy above his bed.

Hissed under his breath, “Oh, you’ve got to be kidding me...”

It took a few seconds before Harry could muster the heart to sit up in bed, pull the blanket over himself and his pillow to obscure the deed from the other boys, cast a low-intensity \emph{Lumos} and see what was under his pillow.

There was a parchment, and a deck of playing cards.

The parchment read,

\begin{writtenNote}
A little bird told me that Dumbledore has shut the door of your cage.

On this occasion, I’ve got to admit Dumbles might have a point. Bellatrix Black is loosed upon the world once more, and that’s not good news for any good person. Honestly, if it was me in Dumbledore’s shoes, I’d probably be doing the same thing right now, no offense.

But just in case there’s more to it than that... The Salem Witches’ Institute in America accepts boys as well, despite the name. They’re good people and I’m certain they would protect you even from Dumbledore, if you needed it. Britain thinks you need Dumbledore’s permission to emigrate to magical America, but magical America disagrees. So in the final extremity, get outside the wards of Hogwarts and tear in half the King of Hearts from this deck of cards.

That you should resort to it only in the final extremity goes without saying.

\letterClosing[Be well, Harry Potter.]{—Santa Claus}
\end{writtenNote}

Harry stared down at the pack of cards.

It \emph{couldn’t} take him anywhere else, not right now, portkeys didn’t work here.

But he still felt unnerved about the prospect of picking it up, even to hide it inside his trunk...

Well, he’d \emph{already} picked up the parchment, which could just as easily have been enchanted with a trap, if a trap was involved.

But still.

“Wingardium Leviosa,” Harry whispered, and Hovered the packet of cards to lie next to where his alarm clock rested in a pocket of the headboard. He’d deal with it tomorrow.

And then Harry lay back in bed, and closed his eyes, to dream without any phoenix to protect him, and pay his reckoning.
\sbreak
He came awake with a gasp of horror, not a scream, he’d yet to scream this night, but his blanket was all tangled around him from where his sleeping form had jerked as he dreamed of running, trying to get away from the gaps in space that were pursuing him through a corridor of metal lit by dim gaslight, an endlessly long corridor of metal lit by dim gaslight, and he hadn’t \emph{known}, in the dream, that touching those voids meant he would die horribly and leave his still-breathing body empty behind him, all he’d known was that he had to run and run and run from the wounds in the world sliding after him—

Harry started to cry again, it wasn’t for the horror of the chase, it was that he’d run away while someone behind him was screaming for help, screaming for him to come back and save her, help her, she was being eaten, she was going to die, and in the dream Harry had run away instead of helping her.

\emph{“\shout{Don’t go!}” The voice came in a scream from behind the metal door. “No, no, no, don’t go, don’t take it away, don’t don’t don’t—”}

Why had Fawkes ever rested on his shoulder? He’d walked away. Fawkes should hate him.

Fawkes should hate Dumbledore. \emph{He’d} walked away.

Fawkes should hate everyone—

The boy wasn’t awake, wasn’t dreaming, his thoughts were jumbled and confused in the shadowlands that bordered sleep and waking, unprotected by the safety rails that his aware mind imposed on itself, the careful rules and censors. In that shadowland his brain had woken up enough to think, but something else was too sleepy to act; his thoughts ran free and wild, unconstrained by his self-concept, his waking self’s ideals of what he shouldn’t think. That was the freedom of his brain’s dreams, as his self-concept slept. Free to repeat, over and over, Harry’s new worst nightmare:

\emph{“No, I didn’t mean it, please don’t die!”}

\emph{“No, I didn’t mean it, please don’t die!”}

\emph{“No, I didn’t mean it, please don’t die!”}

A rage grew in him alongside the self-loathing, a terrible hot wrath / icy cold hatred, for the world which had done that to her / for himself, and in his half-awake state Harry fantasized escapes, fantasized ways out of the moral dilemma, he imagined himself hovering above the vast triangular horror of Azkaban, and whispering an incantation unlike any syllables that had ever been heard before on Earth, whispers that echoed all the way across the sky and were heard on the other side of the world, and there was a blast of silver Patronus fire like a nuclear explosion that tore apart all the Dementors in an instant and ripped apart the metal walls of Azkaban, shattered the long corridors and all the dim orange lights, and then a moment later his brain remembered that there were people in there, and rewrote the half-dream fantasy to show all the prisoners laughing as they flew away in flocks from the burning wreck of Azkaban, the silver light restoring the flesh to their limbs as they flew, and Harry started crying harder into his pillow, because he couldn’t do it, because he wasn’t God—

He’d sworn upon his life and magic and his art as a rationalist, he’d sworn by all he held sacred and all his happy memories, he’d given his oath so now he had to do something, \emph{had to do something, had to \shout{do something}—}

Maybe it was pointless.

Maybe trying to follow rules was pointless.

Maybe you just burned down Azkaban however.

And in fact he’d sworn he’d do it, so now that was what he had to do.

He’d just do whatever it took to get rid of Azkaban, that was all. If that meant ruling Britain, fine, if that meant finding a spell to whisper that would echo all across the sky, whatever, the important thing was to destroy Azkaban.

That was the side he was on, that was who he was, so there, it was done.

His waking mind would have demanded a lot more details before accepting that as an answer, but in his half-dreaming state it felt like enough of a resolution to let his tired mind fall truly asleep again, and dream the next nightmare.
\replacement{\sbreak}{}

\subsection{Final Aftermath:}

\noindent{}She came awake with a gasp of horror, a disruption of her breathing that left her feeling deprived of air and yet her lungs didn’t move, she woke up with an unvoiced scream on her lips and no words, no words came forth, for she could not understand what she had seen, \emph{she could not understand what she had seen}, it was too large for her to encompass and still taking shape, she could not put words to that formless shape and so she could not discharge it, could not discharge it and become innocent and unknowing once more.

“What time is it?” she whispered.

Her golden jeweled alarm clock, the beautiful and magical and expensive alarm clock that the Headmaster had given her as a gift upon her employment at Hogwarts, whispered back, “Around two in the morning. Go back to sleep.”

Her sheets were soaked in sweat, her nightclothes soaked in sweat, she took her wand from beside the pillow and cleaned herself up before she tried to go back to sleep, she tried to go back to sleep and eventually succeeded.

Sybill Trelawney went back to sleep.

