\namedpartchapter{Self-Actualization}{SA}{VIII}{The Sacred and the Mundane}

\begin{em}\lettrine{T}{he} red jet of fire took Hannah full in the face, flipping her end-over-heels and smacking her head straight into the stone wall, where her pale face seemed to linger for an instant, framed by flying strands of brown-golden hair, before she collapsed to the ground in a heap of robes, as the third and final volley of blazing green spirals brought down their foe’s Shield Charm.\par\end{em}

The March days marched by, filled with lectures and study and homework, breakfast and lunch and dinner.

\emph{The Gryffindor boy stared at the eight of them, tension in every line of his body’s frame, his face working soundlessly; and then his hands released their clenched grasp on the Slytherin boy’s lapels, and he walked away without anyone saying a word. (Well, Lavender almost said a word—her mouth was just opening in indignation, maybe because she hadn’t gotten a chance to declaim her speech—but luckily Hermione spotted it and made the gesture that meant \shout{shut up.}}

Then there was sleeping, of course. You wouldn’t want to forget about sleeping just because it seemed so normal.

\emph{“Innervate!” said the young voice of Susan Bones, and Hermione’s eyes flew open and her lips drew in air with a gasp, her lungs feeling heavy like there was a huge weight resting on her chest. Beside her, Hannah was already sitting up, holding her head in her hands and grimacing. Daphne had warned them that this would be a ‘hard’ fight, creating a certain trepidation in Hermione, and indeed in all of them. Except maybe Susan, who’d just shown up at the appointed meeting-time, and walked alongside them without speaking, and fought the seventh-year bully until she was the last girl standing. Maybe the Gryffindor had been reluctant to fight the last daughter of Bones, or maybe Susan had just gotten very lucky; at any rate, when Hermione had tried to sit up again, she’d realized that her chest had felt heavy because there was, in fact, a rather large body sprawled on top of her.}

And you wouldn’t want to forget about magic either, even if the actual moment of casting a spell only formed a very small part of your day. It was the whole point of Hogwarts, after all.

\emph{“Okay, how about if we all ride around on skateboards?” said Lavender. “We could get places faster than walking. And we’d look really awesome on skateboards, Muggle artifacts may not be as fast as broomsticks but they look cooler—we should vote on it—”}

As for the remaining fractions of time, you would fill that according to your nature: gossip about upper-year romances, or books and study sessions.

\emph{Hermione reached out a trembling hand to grasp her copy of} Hogwarts: A History \emph{from where it had fallen, the ever-comforting book only a pace distant from where she herself had ended up on the floor, after the red-robed upper-year girl had “bumped” her into a wall. And then the older Gryffindor witch had walked away without a look back, only a whispered “Salazar’s—” and a word that hurt her more than anything the Slytherins said about mudbloods, ‘mudblood’ was just a strange wizarding word but Hermione knew the word the Gryffindor had said. She couldn’t get used to it, she just couldn’t get used to being hated. It still hurt just as much every time it happened, and somehow it hurt even more coming from the Gryffindors who were} supposed \emph{to be the good ones.}

Harry had divided up eight of his soldiers among the other armies, as ordered; he’d voluntarily given up \emph{two} Chaotic Lieutenants, sending Dean Thomas to Dragon Army and then trading Seamus Finnigan to her for Blaise Zabini, who Harry had said was being “underutilized” in Sunshine. Lavender had elected to join most of \SPHEW in Sunshine; Tracey had decided to stay with Chaos.

\emph{“So you can work your charms on General Potter?” said Lavender, as Hermione ignored both of them as hard as she could. “I’ve got to say, Traces, I think our Sunshine General has him pretty well sewn up by now—you’d have better luck convincing Hermione that the three of you should have one of those, you know, arrangements—”}

Nobody had figured out yet what Draco Malfoy was plotting.

\emph{“Certain?” said Harry Potter, sounding rather reluctant. “You know a rationalist isn’t ever certain of anything, Hermione, not even that two and two make four. I can’t actually read Malfoy’s mind, and if I could, I couldn’t be certain he wasn’t a perfect Occlumens. All I can say is that based on what I’ve seen of Malfoy, it’s a lot more plausible than Daphne Greengrass thinks, that he actually is trying to show the Slytherins a better way. We should...\ we really should try to go along with that, Hermione.”}

(Well, Harry seemed to think Draco Malfoy was a good guy. But then the trouble was that Harry also tended to trust people like Professor Quirrell.)
\sbreak

“Professor Quirrell,” Harry said, “I’m worried about the hatred Slytherin House seems to be developing for Hermione Granger.”

They were sitting in the Defense Professor’s office, Harry sitting far back from the teacher’s desk (and the sense of pending disaster was still noticeable, even then), the empty bookcase still framing Professor Quirrell’s balding head. The cup balanced on Harry’s thigh was filled with Professor Quirrell’s obscure, probably-expensive Chinese tea, and it said something about the way Harry had been thinking lately that he’d needed to make a conscious decision to drink it.

“And this concerns me for what reason?” said Professor Quirrell, sipping his tea.

“Yes, well,” said Harry, “I’m just going to ignore that—oh, stop that, Professor Quirrell, \emph{you’ve} been plotting to restore Slytherin House’s reputation since at least the first Friday of this year.”

There might have been a tiny crack of a smile, at the edges of those thin pale lips; and then again, there might not have been. “I think Slytherin’s House will do well enough in the end, Mr.~Potter, regardless of the fate of one girl. But I do agree that the present outlook is not favorable for your little friend. The bullies of two Houses, many of them with powerful and well-connected families, see Miss Granger as a threat to their reputation and a shame to their pride. As powerful a motive as that is to hurt her, it pales compared to the raw envy of the Gryffindors, who see an outsider gaining the laurels of heroism which they have dreamed of since childhood.” Now the smile on Professor Quirrell’s lips was definite, though slight. “And then there are those of Slytherin House who hear that Salazar Slytherin’s ghost has abandoned them to favor a mudblood. I wonder if you can even conceive, Mr.~Potter, of how such as they would react? Those who do not believe it would cheerfully kill Miss Granger for the insult. And as for those Slytherins who wonder deep down, in some quiet place within themselves, if it might perhaps be \emph{true...} their inner panic is something scarcely to be contemplated.” Professor Quirrell sipped his tea equably. “When you are more experienced, Mr.~Potter, you will see such consequences in advance of your plotting. As it stands, you are being ill-served by your willful ignorance of all human nature you deem unpleasant.”

Harry sipped his own tea.

“Ah...” said Harry. “Professor Quirrell...\ help?”

“I already offered Miss Granger my help,” said Professor Quirrell, “as soon as I foresaw what would develop. My student told me, in polite terms, to stay out of her business. Nor would she tell you anything different, I expect. As I have little to truly gain or lose in this matter, I hardly intend to press the point.” The Defense Professor shrugged, his teacup held steady in the exactly-right polite grip, so that the surface of the liquid did not even ripple as Professor Quirrell leaned back within his chair. “Do not worry too much, Mr.~Potter. Emotions run high around Miss Granger, but she is in less danger than you might imagine. When you are older, you will learn that the first and foremost thing which any ordinary person does is nothing.”
\sbreak
The envelope which the Slytherin System had delivered to Daphne at lunch was unsigned, as always; the parchment within named a time and a place and said, simply, \emph{“Hard.”}

That wasn’t what had concerned Daphne. What had concerned Daphne was that Millicent didn’t seem to be looking in her or Tracey’s direction at lunch that day. She’d just stared straight ahead at her plate and eaten. Millicent had looked up just once that Daphne saw, in the direction of the Hufflepuff table, and then looked quickly back down again; though Daphne was too far away to see the expression on Millicent’s face, since Millicent had sat down far away from her and Tracey.

Daphne had thought about that during lunch, with a sick feeling in her stomach unlike anything she’d felt before, and which had caused her to stop eating halfway through her first plate.

\emph{What I See has to come to pass...\ it probably makes being eaten by Lethifolds look like a tea party...}

It wasn’t any conscious decision that Daphne made, nothing like Slytherins were supposed to do, no weighing of the benefits to herself.

Instead—

Daphne told Hannah and Susan and everyone, that her informant had warned her that the next bully was going to target Hufflepuffs in particular, and that the bully planned to risk the teachers’ wrath in order to \emph{really} hurt either Hannah or Susan, like \emph{seriously}, and the two of them needed to stay out of this one.

Hannah had agreed to stay out of it.

Susan had—
\sbreak
“\emph{What are you doing here?}” yelled General Granger, though it was sort of a yell and a whisper at the same time.

Susan’s round face didn’t change, like the Hufflepuff girl had suddenly developed the sort of experienced blankness that Daphne’s own Mother used. “Am I here, really?” Susan said calmly.

“\emph{You said you wouldn’t come!}”

“Did I say that?” said Susan. She flipped her wand casually in one hand, leaning against the stone wall of the corridor where they were waiting, her reddish-brown hair somehow arranging itself in perfect order against the yellow trim of her witch’s robes. “I wonder why. Maybe I didn’t want Hannah to get any strange ideas. Hufflepuff loyalty, you know.”

“If you don’t leave,” said the Sunshine General, “I’ll call a mission abort, and we’ll \emph{all} go back to our study halls, Miss Bones!”

“\emph{Hey!}” said Lavender. “We didn’t vote on—”

“That’s fine by me,” said Susan, who was keeping a steady gaze on the other end of the corridor where it merged into the tiled hallway where they’d been told to expect the bully. “I’ll just stay here myself, then.”

“Why—” said Daphne. Her heart was in her throat. \emph{If I try to change it, if} anyone \emph{tries to change it, really terrible, awful, no good, extremely bad things will happen. And then it’ll come to pass anyway...} “Why are you doing this?”

“It’s not like me,” said Susan. “I know. But—” Susan shrugged. “People don’t always behave like themselves, you know.”

They pleaded.

They begged.

Susan didn’t even say anything anymore, she just kept watching, waiting.

Daphne was nearly crying, she kept wondering if she’d \emph{caused} this, if trying to change Fate was making this happen \emph{worse}—

“Daphne,” said Hermione, her voice sounding much higher than usual, “go get a teacher. Run.”

Daphne spun on her heels and started to pelt down the other direction of the stony corridor, and then she realized, and she turned back to where all the other girls except Susan were watching her go, and Daphne, feeling like she was about to throw up, said, “I can’t...”

“\emph{What?}” said Hermione.

“I think it gets worse every time you try to fight it,” said Daphne. That was how it worked in plays, sometimes.

Hermione stared at her, and then Hermione said, “Padma.”

The other Ravenclaw girl just tore right out of there without arguing. Daphne watched her go, knowing that Padma wasn’t as good a runner as her, and now wondering if maybe that would turn out to be the \emph{only reason} why help would come too late...

“Bullies are here,” Susan said laconically. “Huh, they’ve got a hostage.”

They all whirled, and looked, and saw—

\emph{Three} older bullies, Daphne’s eyes recognized Reese Belka who was a top lieutenant in one of the seventh-year armies, and Randolph Lee who was number two in the Hogwarts dueling club, and worst of all, Robert Jugson III, in his sixth year, whose father was almost certainly a Death Eater.

All three were surrounded by Shielding Charms, blue hazes that glowed beneath the surface in ribbons of other color and showed occasional faceting above, multi-layered shields like the three of them thought they were fighting serious duelists and had expended energy accordingly.

And behind them, bound and supported by glowing ropes, was Hannah Abbott. Her eyes were wide and panicked and her mouth was moving, though they couldn’t hear anything through the \emph{Quietus} they’d put up earlier.

Then Jugson made an offhand gesture with his wand, and the glowing ropes flung Hannah at them, there was a small pop as Hannah’s body blew through the Quieting barrier, Susan’s wand was instantly pointing at Hannah and Susan’s voice muttered “\emph{Wingardium Leviosa}”—

“\emph{Run!}” screamed Hannah, as she was gently lowered to the ground.

But the corridor behind them and in front of them was now blocked with a glowing gray field, a barrier spell that Daphne didn’t recognize.

“Do I need to explain what this is about?” Lee said with false joviality. The seventh-year duelist was sporting a smile that didn’t reach his eyes. “Well, just in case, you little inconveniences, and that includes you Miss Greengrass, you’ve been quite enough trouble and you’ve told quite enough lies. We brought your little friend just to make sure everyone knew we got all of you—though I suppose the other Ravenclaw girl is hiding around a corner or clinging to the ceiling somewhere? Well, no matter. This is your—”

“Enough talk,” said Robert Jugson III, “time for pain,” and raised his wand. “\emph{Cluthe!}”

Simultaneously Susan pointed her wand and said “\emph{Prismatis!}” and a small rainbow sphere formed in midair almost instantly, the miniature barrier so condensed and bright that it stayed intact even as Jugson’s hex hit it and bounced off toward Belka, whose wand flashed to swat away the dark bolt; and then a moment later the many-colored blaze was gone.

Daphne’s eyes went wide for a moment; she’d never thought of using a Prismatic Sphere like \emph{that}—

“Jugsy, honey?” said Belka. Her lips widened in a vicious smile. “I thought we discussed this. First we beat them, \emph{then} we play.”

“P-please,” said Hermione Granger in a faltering voice, “let them go—I, I, I promise I’ll—”

“Oh, really,” said Lee in an annoyed tone. “Are you about to offer to turn yourself over if we let the others go? We’ve got \emph{all} of you, now.”

Jugson smiled, then. “It could be funny,” said the sixth-year junior Death Eater, softly and with menace. “How about if you lick my shoes, mudblood, and \emph{one} of your friends can go? Pick whichever one you like best, leave the others to get hurt.”

“Nope,” said the young voice of Susan Bones, “not going to happen,” and with a blindingly fast motion the Hufflepuff girl leapt leftward just as a red stunbolt erupted from Belka’s wand, Daphne could hardly \emph{see} the movement as Susan seemed to hit the corridor wall and then bounce off it like she was a rubber ball and her legs smashed into Jugson’s \emph{face}, it didn’t go through the shield but the sixth-year went sprawling backward with the impact and Susan followed him downward and her foot stamped down on the boy’s wand arm, again being repelled by the shield, “\emph{Elmekia!}” shouted Lee and Parvati shouted “\emph{Prismatis!}” and the rainbow wall formed but the fiery blue blast passed right through it like it wasn’t even there, the bolt missed Susan by inches, there was a whirlwind of motion that Daphne couldn’t follow during which Belka had her feet knocked out from under her, but the older witch just rolled back to a stand and then—

Daphne saw it coming, and her lips started to mouth “\emph{Pris—}” but it was already too late.

Three blasts of brilliance slammed into Susan at once, she had her wand raised as though she could counter them and there was a white flash as the hexes struck the magical wood, but then Susan’s legs convulsed and sent her flying into a corridor wall. Her head hit with a strange cracking sound, and then Susan fell down and lay motionless with her head at an odd-seeming angle, her wand still clutched in one outstretched hand.

There was a moment of frozen silence.

Parvati scrambled over to where Susan lay, pressed a thumb over the pulse point on Susan’s wrist, and then—then slowly, tremblingly, Parvati rose to her feet, her eyes huge—

“\emph{Vitalis revelio},” said Lee just as Parvati opened her mouth, and Susan’s body was surrounded a warm red glow. Now the seventh-year boy really was grinning. “Probably just a broken collarbone, I’d say. Nice try, though.”

“Merlin, they \emph{are} tricky,” said Jugson.

“You had me going for a second there, dearies.” The seventh-year girl wasn’t smiling at all.

“\emph{Tonare!}” screamed Daphne, raising her wand above her head and focusing harder than she ever had in her life. “\emph{Rava calvaria! Lucis—}”

She didn’t even see the hex that got her.
\sbreak
Hermione felt the jolt of Innervation bringing her awake, and out of some intuitive strategism she \emph{didn’t} roll to her feet right away; it had been a completely hopeless battle and she didn’t know what she could do but some instinct told her that leaping to her feet wasn’t it.

Just a crack, Hermione opened her eyes, and the thin rays of light that entered them showed Parvati backing away from all three bullies, the last girl standing that Hermione could see.

And her eyes also showed Tracey fallen not far away from her, and Hermione’s wand was still in her hand; and so, desperately hoping the Slytherin girl would show more sense than she usually did, Hermione made the wand movements as subtly as she could, and hardly moving her lips, whispered, “Innervate.”

Hermione felt the spell working, but Tracey didn’t move. Hermione hoped it was because Tracey was being cunning, and waiting to...

What \emph{could} they do?

Hermione didn’t know, and the panic that had waited through the moments of fighting was starting to eat her up inside now that she was still, now that she was trying to think, now that she could see that it was all absolutely hopeless.

That was when Hermione heard a thud, and though it was out of her field of vision now, she knew that Parvati had fallen.

A moment of silence came, and passed.

“Now what?” said the voice of the scary-soft boy.

“Now we wake up the mudblood,” said the precise voice of the scary-formal boy, “and find out who’s \emph{really} behind them, not Salazar Slytherin’s ghost.”

“No, dears,” said the voice of the scary-sweet girl, “\emph{first} we bind them all \emph{very} securely—”

And then there was a sound like lightning and thunder and Hermione’s eyes widened in shock before she could stop herself, and in her widened field of vision she saw the scary-soft boy convulsing as yellow arcs of energy crawled over him like giant blazing worms. His wand flew out of his hand as he collapsed to the ground, twitching, and then a moment later he lay still.

“Is everyone else asleep now?” said a voice. “Good.”

Susan Bones rose from the floor near where the scary-soft boy had stood, neck still oddly bent. Then she rolled her head around her shoulders, a casual loose motion, and her head was straight again.

The round-faced first-year girl stood facing the remaining two bullies with one hand cocked on her hip.

Grinning.

And surrounded by faceted blue haze.

“Polyjuice!” spat the bully-girl.

“\emph{Polyfluis Reverso!}” roared the remaining boy bully.

Something like the form of a mirrored scarf spat out of his wand—

Passed without resistance through the haze surrounding Susan—

For an instant, she glowed in a strange mirror-color, like a reflection of herself—

And then the glow faded.

The young girl still stood there, hand on her hip.

“Wrong,” said Susan.

“And \emph{this} is the truth,” said Susan. “In case nobody ever told you—”

In her small hand a wand rose up, blurred by the blue haze surrounding it.

“You don’t mess with the ‘Puffs,” said Susan, and with a grey flash so bright it hurt Hermione’s half-closed eyes, the real battle started.

It went on for a while.

Some of the ceiling got melted.

The girl-bully tried to cry a truce, that they would leave and take Jugson with them, and Susan roared out the syllables of a curse Hermione recognized as Abi-Dalzim’s Horrid Wilting which was illegal in seven countries.

Eventually the girl-bully lay unconscious and unawakenable on the ground, and the last boy-bully had fled leaving his companions’ bodies behind, and Susan was leaned over against one wall, covered in sweat and her scorched robes soaked through with wet spots, gasping for breath, and clutching at her right shoulder using her left hand.

After a while Susan straightened up, and turned to look back at where her fellow witches were sleeping on the floor.

Well, they \emph{should’ve} been sleeping on the floor.

Lavender was already sitting up with eyes as wide as watermelons.

“That...” said Lavender.

“Was...” said Tracey.

“\emph{What?}” said Hermione.

“I mean,\emph{ what?}” said Parvati.

“\emph{Cool!}” said Lavender.

“Oh, hell,” said Susan Bones. Her face had already looked a little pale beneath the sweat, and now it was getting paler, looking almost frighteningly white. “Ah...\ could I convince you that you hallucinated all that?”

There was a rapid exchange of glances. Hermione looked at Parvati, Parvati looked at Lavender, Lavender briefly locked gazes with Tracey.

The four of them looked back at Susan and shook their heads.

“Oh, hell,” said Susan again. “Look I’ll be back in a few minutes but I’ve really got to go now \emph{please} don’t say anything bye!”

And Susan ran out into the hallway, moving surprisingly fast, before anyone could say another word.

“No, seriously, \emph{what?}” said Parvati.

“\emph{Innervate},” said Hermione, pointing her wand at Daphne, whose body she hadn’t been able to see before; and Lavender pointed her wand at Hannah’s body and said the same.

Hannah’s eyes opened and she tried frantically to roll to her feet, but collapsed to the ground halfway through.

“It’s okay, Hannah!” said Lavender. “We won.”

“We \emph{what?}” said Hannah from her little heap on the floor.

Daphne hadn’t stirred, but Hermione could see her chest rising and falling, and the breathing rhythm looked normal enough. “I think she’s okay,” said Hermione, “but—” She took a moment to swallow, her mouth was still dry. This had all gotten way, way, \emph{way} out of hand. “I think we ought to take Daphne to Madam Pomfrey’s...”

“Sure, sure, just \emph{give me a second here} and I’ll \emph{probably be fine},” said Parvati.

“Ex\emph{cuse} me,” Hannah said in a tone that was polite, but firm. “How did we win? And why does the ceiling look all melty?”

There was a pause.

“Susan did it,” said Tracey.

“Yeah,” said Parvati, voice only slightly shaky as she stood up and started to brush off her red-trimmed robes, “it turns out that Susan Bones is the Heir of Hufflepuff and she’s opened up the long-lost entrance to Helga Hufflepuff’s Chamber of Hard Work and Practice.”

“\emph{Huh?}” said Hannah, who was feeling over herself as if to make sure all her body parts were still there. “I thought that was just something Professor Sprout says to teach us an Important Moral Lesson—\emph{Susan} is?”

Slowly, Hermione was beginning to feel a bit more together. It hadn’t really been more than thirty seconds of extreme terror, at least not the parts she’d been conscious for. “Actually,” Hermione said carefully, as her mind started to work again, “I’m pretty sure that \emph{is} just something Professor Sprout says, it wasn’t in \emph{Hogwarts: A History} or anywhere else I’ve read—”

“\emph{She’s a double witch!}” shouted Tracey, her voice so high it cracked. “She\emph{ is!} She’s one of \emph{them!} She’s been this whole time!”

“\emph{What?}” yelled Parvati, twisting around to look at Tracey. “That is the \emph{looniest} thing—”

“Of \emph{course!}” said Lavender, now all the way on her feet and starting to bounce up and down with excitement. “I should’ve\emph{ realized!}”

“Susan’s a \emph{what?}” said Hermione.

“A \emph{double} witch!” said Tracey.

“You see,” said Lavender, speaking very rapidly, “There’ve always been stories, about these children who are born as super magicians who can cast spells no one else can, and there’s a whole secret school hidden inside Hogwarts with classes that only they can see and go to—”

“Those are just \emph{stories!}” yelled Parvati. “That’s not how real life works! I mean, sure, I read those books too—”

“Just a minute, please,” said Hermione. Maybe her mind \emph{was} feeling a little slow after all. “You mean even though you \emph{already} get to go to a magical school and everything, you still want to go to a \emph{double} magical school?”

Lavender looked at her, puzzled. “What?” said Lavender. “Who \emph{wouldn’t} want to have super extra magical powers? It would be like this whole amazing \emph{destiny} and everything! It’d mean you were \emph{special!}”

Hannah nodded to that, looking up from where she’d crawled to Daphne’s side and was checking the girl for broken bones. “I wish \emph{I} was a double witch,” Hannah said, and then, sounding a little sadder, “though I don’t believe there is any such thing, really...\ what did you see Susan do, exactly? I mean, are you sure you weren’t just seeing things after getting stunned?”

Hermione truly, truly couldn’t find any words at this point.

“Oh, no,” said Tracey. The Slytherin girl spun around to look at the entrance to the corridor, her robes fluttering around her. “Oh no! We’ve got to get out of here! We’ve got to get away before Susan comes back with someone who can Super-Memory-Charm us!”

“Susan wouldn’t \emph{do} that!” said Parvati. “I mean, if there even \emph{was} —”

“\shout{What’s going on here?}” roared a high-pitched squeaky voice, as Professor Flitwick stormed into the partially melted corridor like a small, dangerously compressed package of pure academic fury, an ashen-faced Padma gasping along behind him.
\sbreak
“What\emph{ happened?}” Susan blurted to the girl who looked exactly like her, except for the scorched robes damp with sweat.

“Ooh, great question!” said the other Susan Bones as she rapidly skinned off what was left of her borrowed clothes. A moment later the girl began to Metamorphose back into her more accustomed form of Nymphadora Tonks. “Sorry but I couldn’t think of anything myself so you’ve got about three minutes to decide on an answer to that—”
\sbreak
As Daphne Greengrass observed afterward with some acidity, the flaw in Hermione’s cunning plan to make sure that House points were taken evenly from all four Houses if they got caught, was that it didn’t work on \emph{detentions}.

They’d all agreed to keep their mouths shut about Susan’s mysterious powers—even Tracey, after Susan threatened to have her Super-Memory-Charmed if she didn’t promise. Unfortunately, they discovered at dinnertime that someone had forgotten to tell the \emph{bullies} about their agreement, and also that Susan Bones had sacrificed her soul to dreadful forbidden powers which now inhabited the hulk of her body and that was why they’d all gotten detention.

“Hermione?” Harry Potter said to her from beside her at the dinner table, his voice very tentative. “Please don’t take offense, and I’ll understand if you say it’s none of my business, but I think all this is starting to spin out of control.”

Hermione went on mashing the slice of chocolate cake on her plate into a seamless mush of cake and icing. “Yes,” Hermione said, her voice might have been a little acerbic, “that was what I said to Professor Flitwick while I was apologizing to him, that I knew things had gotten out of hand, and he yelled: \emph{Really, Miss Granger? Do you think?} in a squeak so loud that my ears caught on fire. I mean my ears \emph{actually caught on fire}. Professor Flitwick had to put them out again.”

Harry had put his hand to his forehead. “Excuse me,” Harry said. His face was perfectly straight. “Sometimes I still have a little trouble getting used to that sort of thing. Hey, Hermione, remember when we were young and naive and we still thought the world was a relatively understandable place?”

Hermione put her fork down and looked at him for a moment. “Do you sometimes wish you were a Muggle, Harry?”

“\emph{Huh?}” said Harry. “Well, of course not! I mean, even if I was a Muggle, I’d probably have tried someday to take over the worrrrlllll—” as Hermione gave him a \emph{look} and the boy hastily swallowed the word and said, “I mean \emph{optimize} of course, you \emph{know} that’s what I really mean, Hermione! My point is, it’s not like my \emph{goals} would change one way or another. But with magic it’s going to be a lot easier to get things done than if I had to do stuff using only the Muggle capability set. If you think about it logically, that’s \emph{why} I’m going to Hogwarts instead of just ignoring all this and studying for a career in nanotechnology.”

Hermione, having finished hand-crafting her Chocolate Cake Sauce, began to dip her carrots in it and eat them.

“Why do you ask?” said Harry. “Do \emph{you} wish you were back in the Muggle world?”

“Not exactly,” Hermione said, as she crunched into both the carrot and the chocolate. “I was just, well, feeling strange about having \emph{wanted} to be a witch... Did you want to be a wizard when you were little?”

“Of course,” Harry said promptly. “I also wanted psychic powers and super-strength and adamantium-reinforced bones and my own flying castle and sometimes I felt sad that I might have to settle for just being a famous scientist and an astronaut.”

Hermione nodded. “You know,” she said softly, “I think the witches and wizards who \emph{grow up} here don’t really appreciate magic properly...”

“Well, of course they don’t,” Harry said, “that’s what gives us our advantage. Isn’t that obvious? I mean seriously, that was bloody obvious to me within five minutes of walking into Diagon Alley.” There was a puzzled look on the boy’s face, like he couldn’t understand why she was paying attention to something so ordinary.


