\chapter{Caring}

\subsection{June 3rd, 1992.}

\lettrine{P}{rofessor} Quirrell was very sick.

\quad\quad
He'd seemed better for a while, after drinking his unicorn's blood in May, but
the air of intense power which had surrounded him afterward hadn't lasted even
a day. By the Ides of May, Professor Quirrell's hands had been trembling again,
though subtly. The Defense Professor's medical regimen had been interrupted too
early, it seemed.

Six days ago Professor Quirrell had collapsed at dinnertime.

Madam Pomfrey had tried to forbid Professor Quirrell from teaching classes, and
Professor Quirrell had shouted at her in front of everyone. The Defense
Professor had shouted that he was dying regardless, and would use his remaining
time as he chose.

So Madam Pomfrey, blinking hard, had forbidden the Defense Professor from doing
anything \emph{except} teaching his classes. She'd asked for a volunteer to
help her take Professor Quirrell to a room in the Hogwarts infirmary. More than
a hundred students had risen to their feet, only half wearing green.

The Defense Professor no longer sat at the Head Table during mealtimes. He
didn't cast spells during lessons. The oldest students who had the most
Quirrell points helped him to teach, the seventh-years who had already sat
their Defense N.E.W.T.s in May. They took turns floating him from his room in
the infirmary to his classes, and brought him food at mealtimes. Professor
Quirrell proctored his Battle Magic classes from a chair, sitting.

Watching Hermione die had hurt more than this, but that had ended much more
quickly.

\emph{This is the true Enemy.}

Harry had already thought that, after Hermione had died. Being forced to watch
Professor Quirrell die, day by day, week by week, had not done much to change
his mind.

\emph{This is the true Enemy I have to face,} Harry thought in Wednesday's
Defense class, watching Professor Quirrell leaning far to one side of his chair
before that day's seventh-year assistant caught him. \emph{Everything else is
just shadows and distraction.}

Harry had been turning over Trelawney's prophecy in his mind, wondering if
maybe the true Dark Lord had nothing to do with Lord Voldemort at all.
\emph{Born to those who have thrice defied him} seemed to strongly invoke the
Peverell brothers and the three Deathly Hallows---though Harry didn't exactly
see how Death could have marked him as an equal, which seemed to imply some
sort of deliberate action on Death's part.

\emph{This alone is the true Enemy,} Harry thought. \emph{After this will come
Professor McGonagall, Mum and Dad, even Neville in his time, unless the wound
in the world can be healed before then.}

There was nothing Harry could do. Madam Pomfrey was already doing for Professor
Quirrell what magic could do, and magic seemed strictly superior to Muggle
techniques when it came to healing.

There was nothing Harry could do.

Nothing he could do.

Nothing.

Nothing at all.
\sbreak
Harry raised his hand, and knocked upon the door, in case the person there
could no longer detect him.

"What is it?" came a strained voice from the infirmary room.

"It's me."

There was a long pause. "Come in," said that voice.

Harry slipped inside and closed the door behind him, and cast the Quieting
Charm. He stood as far away from Professor Quirrell as he could, just in case
his own magic was making the Professor feel uncomfortable.

Though the sense of doom was fading, fading with each passing day.

Professor Quirrell was lying back in his infirmary bed, only his head propped
up by a pillow. A coverlet of cottony material, red with black stitching,
covered him to his chest. A book hovered before his eyes, outlined in a pale
glow which also surrounded a black cube lying by the bed. Not the Defense
Professor's own magic, then, but a device of some kind.

The book was \emph{Thinking Physics} by Epstein, the same book Harry had lent
to Draco a few months back. Harry had stopped fretting about its possible
misuse several weeks earlier.

"This---" Professor Quirrell said, and coughed, it didn't sound quite right.
"This is a fascinating book{\ldots} if I'd ever realized{\ldots}" A laugh,
mixed with another cough. "Why did I assume the Muggle arts{\ldots} must not be
mine? That they would be{\ldots} of no use to me? Why did I never bother
trying{\ldots} to test it experimentally{\ldots} as you would say? In
case{\ldots} my assumption{\ldots} was wrong? It seems sheerly foolish of
me{\ldots} in retrospect{\ldots}"

Harry was having more trouble speaking than Professor Quirrell was. Wordlessly,
Harry reached into his pocket, and laid a kerchief on the floor; which he
unfolded to reveal a small white pebble, smooth and round.

"What's that?" said the Defense Professor.

"It's a, it's a, Transfigured, unicorn."

Harry had checked the books, had learned that since he was too young to have
sexual thoughts he would be able to approach a unicorn without fear. The same
books had said nothing about unicorns being smart. Harry had already noticed
that every intelligent magical species was at least partially humanoid, from
merfolk to centaurs to giants, from elves to goblins to veela. All had
essentially humanlike emotions, many were known to interbreed with humans.
Harry had already reasoned out that magic didn't create new intelligence but
just changed the shape of genetically human beings. Unicorns were equinoid,
were not even partially humanoid, didn't talk, used no tools, they were almost
certainly just magical horses. If it was right to eat a cow to feed yourself
for a day, then it \emph{had} to be right to drink a unicorn's blood in order
to stave off death for weeks. You couldn't have it both ways.

So Harry had gone into the Forbidden Forest wearing his Cloak. He had searched
the Grove of Unicorns until he saw her, a proud creature with a pure white coat
and violet hair, with three blue blotches on her flank. Harry had gone over,
and the sapphire eyes had stared at him inquisitively. Harry had tapped out the
sequence 1--2--3 on the ground several times with his shoes. The unicorn had
shown no sign of responding in kind. Harry had reached over, taken her hoof in
his hand, and tapped the same sequence with the unicorn's hoof. The unicorn had
only looked at him curiously.

And something about feeding the unicorn the sleeping-potion-laced sugar cubes
had still felt like murder.

\emph{That magic gives their existence a weight of meaning which no mere animal
could possess{\ldots} to slay something innocent to save oneself, that is a
very grave sin.} Those two phrases, from Professor McGonagall, from the
centaur, had both run through Harry's mind, over and over as the white unicorn
had yawned, laid down on the ground, and closed its eyes for what would be the
last time. The Transfiguration had lasted an hour, and Harry's eyes had watered
repeatedly as he worked. The unicorn's death might not have come then, but it
would come soon enough, and it was foreign to Harry's nature to try to refuse
responsibility of any kind. Harry would just have to hope that, if you didn't
kill the unicorn to save yourself, if you did it to help a friend, it would be
acceptable in the end.

Professor Quirrell's eyebrows had climbed toward his hairline. His voice was
less soft, had something of his normal sharpness, as he said, "I forbid you
from doing that again."

"I wondered if you'd say that," Harry said. He swallowed again. "But this
unicorn is already, already doomed, so you might as well take it,
Professor{\ldots}"

"Why have you done this?"

If the Defense Professor really didn't understand that, he was slower on the
uptake than anyone Harry had ever met. "I kept thinking there was nothing I
could do," Harry said. "I got tired of thinking it."

Professor Quirrell closed his eyes. His head leaned back into the pillow. "You
were lucky," the Defense Professor said in a soft voice, "that a unicorn in
Transfigured form{\ldots} did not set off the Hogwarts wards, as a strange
creature{\ldots} I shall have to{\ldots} take this outside the grounds, to make
use of it{\ldots} but that can be managed. I shall tell them that I wish to
look upon the lake{\ldots} I will ask you to sustain the Transfiguration before
you go, and it should last long enough, after that{\ldots} and with my last
strength, dispel whatever death-alarms were placed to watch over the
herd{\ldots} which, the unicorn being not yet dead, but only Transfigured, will
not yet have triggered{\ldots} you were very lucky, Mr.~Potter."

Harry nodded. He started to speak, then stopped again. Words seemed to stick in
his throat once more.

\emph{You already calculated the expected utilities, if it works, if it goes
wrong. You assigned probabilities, you multiplied, and then you threw out the
answer and went with your new gut feeling, which was the same. So say it.}

"Do you know," Harry said unsteadily, "of any way at all, by which your life
might be saved?"

The Defense Professor's eyes opened. "Why{\ldots} do you ask me that, boy?"

"There's{\ldots} a spell I heard of, a ritual---"

"Be silent," said the Defense Professor.

An instant later a snake lay in the bed.

Even the snake's eyes were dull.

It did not rise.

"\parsel{Sspeak on,}" hissed that snake, its flickering tongue its only motion.

"There is{\ldots} \parsel{there iss a ritual, I heard of from the sschoolmasster,
by which he thinkss the Dark Lord might have lived on. It iss called}---"and
Harry stopped, as he realized that he did know how to say the word in
Parseltongue. "Horcrux. \parsel{It requiress a death, I have heard. But if you
are dying in any casse, you might try to adapt the ritual, even at great rissk
for the new sspell, sso that it can be done with a different ssacrifice. It
would change the whole world, if you ssucceed}---\parsel{though I don't know anything
about the sspell}---\parsel{the sschoolmasster thought it tore off a piece of ssoul,
though I don't ssee how that could be true}---"

The snake was hissing laughter, strange sharp laughter, almost hysterical.
"\parsel{You tell me of that sspell? Me? You musst learn more caution in the
future, boy. But it matterss not. I learned of the horcrux sspell ssince long
ago. It iss meaninglesss.}"

"Meaningless?" Harry said aloud in surprise.

"\parsel{Would be pointlesss sspell from beginning, if ssoulss exissted. Tear
piece of ssoul? That iss lie. Missdirection to hide true ssecret. Only one who
doess not believe in common liess will reasson further, ssee beneath
obsscuration, realisse how to casst sspell. Required murder iss not
ssacrificial ritual at all. Ssudden death ssometimes makess ghosst, if magic
burssts and imprintss on nearby thing. Horcrux sspell channelss death-bursst
through casster, createss your own ghosst insstead of victim'ss, imprintss
ghosst in sspecial device. Ssecond victim pickss up horcrux device, device
imprintss your memoriess into them. But only memoriess from time horcrux device
wass made. You ssee flaw?}"

The burning sensation was back in Harry's throat. "\parsel{No continuity of}---"
there wasn't a snake word for consciousness "---\parsel{sself, you would go on
thinking after making the horcrux, then sself with new memoriess diess and iss
not resstored}---"

"\parsel{Yess, you do ssee. Alsso Merlin'ss Interdict preventss powerful sspells
from passing through ssuch a device, ssince it iss not truly alive. Dark
Wizardss who think to return thuss are weaker, eassily disspatched. None have
perssissted long by ssuch meanss. Perssonalitiess change, mix with victim'ss.
Death iss not truly gainssaid. Real sself is losst, as you ssay. Not to my
pressent tasste. Admit I conssidered it, long ago.}"

A man was lying in the infirmary bed once more. The Defense Professor breathed,
then made a wretched coughing sound.

"Can you give me a full recipe for the spell?" Harry said, after a moment's
deliberation. "There might be some way to improve on the flaws, with enough
research. Some way to do it ethically and have it work." Like doing the
transfer into a clone body with a blank brain, instead of an innocent victim,
which might also improve the fidelity of the personality transfer{\ldots}
though that still left the other problems.

Professor Quirrell made a short sound, under his breath, that might have been
laughter. "You know, boy," Professor Quirrell whispered, "I had thought{\ldots}
to teach you everything{\ldots} the seeds of all the secrets I knew{\ldots}
from one living mind to another{\ldots} so that later, when you found the right
books, you would be able to understand{\ldots} I would have passed on my
knowledge to you, my heir{\ldots} we would have begun as soon as you asked
me{\ldots} but you never asked."

Even the grief surrounding by Harry like thick water gave way to that, to the
sheer magnitude of the missed opportunity. "I was supposed to---? I didn't know
I was supposed to---!"

Another coughing chuckle. "Ah yes{\ldots} the unknowing Muggleborn{\ldots} in
heritage if not in blood{\ldots} that is you. But I thought{\ldots} better of
it{\ldots} that you should not walk my path{\ldots} it was not a good path, in
the end."

"It's not too late, Professor!" Harry said. A part of Harry yelled that he was
being selfish, and then another part shouted that down; there would be other
people to help.

"Yes, it is too late{\ldots} and you shall not{\ldots} persuade me
otherwise{\ldots} I have{\ldots} thought better of it{\ldots} as I said{\ldots}
I am too full{\ldots} of secrets better left unknown{\ldots} \emph{look at me.}"

Harry looked, almost despite himself.

He saw a still-unwrinkled face, looking old and pained, beneath a head rapidly
losing its hair, even the sides looking wispy now; Harry saw a face he'd always
thought was sharp, now revealed as \emph{thin,} muscle and fat fading away from
the face, as from the arms beneath it, like the skeletal form of Bellatrix
Black he'd seen in Azkaban---

Harry's head wrenched aside, unthinkingly.

"You see," whispered the Professor. "I dislike to sound cliched{\ldots}
Mr.~Potter{\ldots} but the truth is{\ldots} the Arts called Dark{\ldots} really
are not good for a person{\ldots} in the end."

Professor Quirrell breathed in, breathed out. There was quiet for a time in the
infirmary, the two of them watched only by the elaborately ornamented stone of
the walls.

"Is there anything left{\ldots} unsaid between us?" said Professor Quirrell. "I
am not dying today{\ldots} mind you{\ldots} not right now{\ldots} but I do not
know how long{\ldots} I shall be able to converse."

"There's," Harry said, swallowed again. "There's a lot of things, way too many
things, but{\ldots} it might be the wrong thing to ask, but I don't want---this
one question unanswered---snake?"

A snake lay on the bed.

"\parsel{I learned how the Killing Cursse workss. Requiress true hate to casst,
not much hate, but musst want target dead, they ssay. In prisson with
life-eaterss, you casst Killing Cursse at guard}---\parsel{ssaid you did not want him
dead}---\parsel{wass that lie? Here, now, at thiss disstance}---\parsel{you may sspeak
truth}---\parsel{even if you fear it reflectss poorly on you}---\parsel{it sshould not matter
now, teacher. I wissh to know. Musst know. Will not abandon you, either way.}"

A man lay on the bed.

"Listen carefully," Professor Quirrell whispered. "I will tell you a
conundrum{\ldots} a riddle of a dangerous spell{\ldots} when you know the
answer to that puzzle{\ldots} you will also know{\ldots} the answer to your
question{\ldots} are you listening?"

Harry nodded.

"There is a limitation{\ldots} to the Killing Curse. To cast it once{\ldots} in
a fight{\ldots} you must hate enough{\ldots} to want the other dead. To cast
Avada{\ldots} Kedavra twice{\ldots} you must hate enough{\ldots} to kill
twice{\ldots} to cut their throat with your own hands{\ldots} to watch them
die{\ldots} then do it again. Very few{\ldots} can hate enough{\ldots} to kill
someone{\ldots} five times{\ldots} they would{\ldots} get bored." The Defense
Professor breathed several times, before continuing. "But if you look at
history{\ldots} you will find some Dark Wizards{\ldots} who could cast the
Killing Curse{\ldots} over and over. A nineteenth-century witch{\ldots} who
called herself Dark Evangel{\ldots} the Aurors called her A. K. McDowell. She
could cast the Killing Curse{\ldots} a dozen times{\ldots} in one fight. Ask
yourself{\ldots} as I asked myself{\ldots} what is the secret{\ldots} that she
knew? What is deadlier than hate{\ldots} and flows without limit?"

\emph{A second level to the Avada Kedavra spell, just like with the Patronus
Charm{\ldots}}

"I don't really care," Harry answered.

The Defense Professor chuckled wetly. "Good. You are{\ldots} learning. So you
see{\ldots}" A pause of transformation. "\parsel{I did not wissh guard dead,
after all. Casst Killing Cursse, but not with hate.}" And then a man.

Harry swallowed hard. It was both better, and worse, than what Harry had
suspected; and characteristic enough of Professor Quirrell. A cracked soul, for
certain; but Professor Quirrell had never claimed to be whole.

"Any else{\ldots} to say?" said the man in the bed.

"Are you absolutely sure," Harry said, "that there is nothing you've ever heard
of that might save you, Professor? In all your lore? Finding and uniting all
three Deathly Hallows, an ancient artifact that Merlin sealed behind a riddle
nobody's ever figured out? You've seen some of what I can do. That I'm good at
solving riddles. You know I can figure things out, sometimes, that other
wizards can't. I---" Harry's voice broke. "I have a strong preference for your
life, over your death, Professor Quirrell."

There was a long pause.

"One thing," whispered Professor Quirrell. "One thing{\ldots} that might do
it{\ldots} or it might not{\ldots} but to obtain it{\ldots} is beyond your
power, or mine{\ldots}"

\emph{Oh, it was just the setup for a subquest,} said Harry's Inner Critic.

All the other parts screamed for that part to shut up. Life didn't work like
that. Ancient artifacts could be found, but not in a month, not when you
couldn't leave Hogwarts and were still in your first year.

Professor Quirrell took in a deep breath. Exhaled. "I'm sorry{\ldots} that came
out{\ldots} too dramatic. Do not{\ldots} get your hopes up{\ldots} Mr.~Potter.
You asked{\ldots} for anything{\ldots} no matter how unlikely. There is{\ldots}
a certain object{\ldots} called{\ldots}"

A snake lay on the bed.

"\parsel{The Philossopher'ss Sstone,}" hissed the snake.

If there'd been a mass-manufacturable means of safe immortality this entire
time and nobody had bothered, Harry was going to snap and kill everyone.

"\parsel{I read of it in a book,}"Harry hissed. "\parsel{Concluded it wass obviouss
myth. No reason why ssame device would provide immortality and endlesss gold.
Not unlesss ssomeone wass jusst inventing happy sstoriess. Not to mention,
every ssane persson sshould have been ressearching wayss to make more Sstoness,
or kidnapping maker to produce. Thought of you sspecifically, teacher.}"

A hissing of cold laughter. "\parsel{Reassoning iss wisse, but not wisse enough.
Like with horcrux sspell, abssurdity hidess true ssecret. True Sstone iss not
what that legend ssayss. True power iss not what sstoriess claim. Sstone's
ssuppossed maker wass not one who made it. One who holdss it now, wass not born
to name now ussed. Yet Sstone iss powerful healing device in truth. Have you
heard it sspoken of?}"

"\parsel{Jusst in the book.}"

"\parsel{One who holdss Sstone iss repossitory of much lore. Taught
sschoolmasster many ssecretss. Sschoolmasster hass ssaid nothing of Sstone'ss
holder, nothing of Sstone? No hintss?}"

"\parsel{Not that I can eassily recall,}" Harry replied honestly.

"\parsel{Ah,}"hissed the snake. "\parsel{Ah, well.}"

"\parsel{Could assk sschoolmasster}---"

"\parsel{No! Do not assk him, boy. He would not take quesstion well.}"

"\parsel{But if the Sstone only healss}---"

"\parsel{Sschoolmasster doess not believe that, would not believe that. Too many
have ssought Sstone, or ssought holder's lore. Do not assk. Musst not assk. Do
not try to obtain Sstone yoursself. I forbid.}"

A man lay on the bed once more. "I am at{\ldots} my limit{\ldots}" said
Professor Quirrell. "I must regain{\ldots} my strength{\ldots} before I
go{\ldots} to the forest{\ldots} with your gift. Leave now{\ldots} but sustain
the Transfiguration{\ldots} before you go."

Harry reached out, touched the white pebble lying within the kerchief, renewing
the Transfiguration on it. "It should last for one hour and fifty-three minutes
after this," Harry said.

"Your studies{\ldots} do well."

It was far longer than Harry's Transfigurations had lasted at the start of the
school year. Second-year spells came to him easily now, without strain; which
wasn't surprising, since he would be twelve in less than two months. Harry
could even have cast a Memory Charm, if it had been good for someone to forget
every memory involving their left arm. He was climbing the power ladder,
slowly, from very far down.

The thought came with a potential for sadness, a thought of one door opening as
another closed; which Harry also rejected.
\sbreak
The door to the infirmary closed behind Harry, as the Boy-Who-Lived walked
swiftly and with purpose, shrugging on his Invisibility Cloak as he moved.
Soon, presumably, Professor Quirrell would call for assistance; and an older
student trio would guide the Defense Professor into some quiet place, maybe the
forest, with an excuse of viewing the lake or some such. Someplace the Defense
Professor could eat a unicorn undetected, after Harry's Transfiguration wore
off.

And then Professor Quirrell would be healthier, for a time. His power would
return to him as strong as he'd ever been, for a much shorter time.

It wouldn't last.

Harry's fists clenched as he strode, the tension radiating up his arm muscles.
If the Defense Professor's treatment regimen hadn't been interrupted, by Harry
and the Aurors that \emph{he} had brought to Hogwarts{\ldots}

It was stupid to blame himself, Harry knew it was stupid and somehow his brain
was doing it anyway. Like his brain was searching, carefully finding and
selecting some way for this to be his fault, no matter how far it had to
stretch.

As if having things be his fault were the only way that his brain knew how to
grieve.

A trio of seventh-year Slytherins passed Harry's invisible form in the hallway,
heading for the healer's offices where the Professor waited, looking deeply
serious and concerned. Was that how other people grieved?

Or did they, on some level, not really \emph{care,} as Professor Quirrell
thought?

\emph{There is a second level to the Killing Curse.}

Harry's brain had solved the riddle instantly, in the moment of first hearing
it; as though the knowledge had always been inside him, waiting to make itself
known.

Harry had read once, somewhere, that the opposite of happiness wasn't sadness,
but boredom; and the author had gone on to say that to find happiness in life
you asked yourself not what would make you happy, but what would excite you.
And by the same reasoning, hatred wasn't the true opposite of love. Even hatred
was a kind of respect that you could give to someone's existence. If you cared
about someone enough to prefer their dying to their living, it meant you were
thinking about them.

It had come up much earlier, before the Trial, in conversation with Hermione;
when she'd said something about magical Britain being Prejudiced, with
considerable and recent justification. And Harry had thought---but not
said---that at least she'd been let into Hogwarts to be spat upon.

Not like certain people living in certain countries, who were, it was
\emph{said}, as human as anyone else; who were \emph{said} to be sapient
beings, worth more than any mere unicorn. But who nonetheless wouldn't be
allowed to live in Muggle Britain. On that score, at least, no Muggle had the
right to look a wizard in the eye. Magical Britain might discriminate against
Muggleborns, but at least it allowed them inside so they could be spat upon in
person.

\emph{What is deadlier than hate, and flows without limit?}

"Indifference," Harry whispered aloud, the secret of a spell he would never be
able to cast; and kept striding toward the library to read anything he could
find, anything at all, about the Philosopher's Stone.
