\partchapter{Coordination Problems}{I}

\lettrine[nindent=0pt]{T}{he} terrifying part was how fast the whole thing had spiraled out of control.

“Albus,” Minerva said, not even trying to keep the worry out of her voice as the two of them entered the Great Hall, “something has to be done.”

The atmosphere at Hogwarts before Yuletide was usually bright and cheerful. The Great Hall had already been decorated in green and red, after a Slytherin and a Gryffindor whose Yule wedding had become a symbol of friendship transcending Houses and allegiances, a tradition almost as ancient as Hogwarts itself and which had even spread to Muggle countries.

Now the students eating dinner were glancing nervously over their shoulders, or sending vicious glares at other tables, or at some tables arguing heatedly. You could have described the atmosphere as \emph{tense,} perhaps, but the phrase coming to Minerva’s mind was \emph{fifth degree of caution.}

Take a school, into four Houses divided...

Now into each year, add three armies at war.

And the partisanship of Dragon and Sunshine and Chaos had spread beyond the first-years; they had become the armies for those who had no armies. Students were wearing armbands with insignia of fire or smile or upraised hand, and hexing each other in the corridors. All three first-year generals had told them to stop—even Draco Malfoy had heard her out and then nodded grimly—but their supposed followers hadn’t listened.

Dumbledore gazed out at the tables with a distant look. “\emph{In every city,}” the old wizard quoted softly, “\emph{the population has been divided for a long time past into the Blue and the Green factions... And they fight against their opponents knowing not for what end they imperil themselves... So there grows up in them against their fellow men a hostility which has no cause, and at no time does it cease or disappear, for it gives place neither to the ties of marriage nor of relationship nor of friendship, and the case is the same even though those who differ with respect to these colours be brothers or any other kin. I, for my part, am unable to call this anything except a disease of the soul...}”

“I’m sorry,” said Minerva, “I don’t—”

“Procopius,” said Dumbledore. “They took their chariot-racing very seriously, in the Roman Empire. Yes, Minerva, I agree that something must be done.”

“Soon,” Minerva said, her voice lowering even further. “Albus, I think it must be done before Saturday.”

On Sunday, most students would leave Hogwarts to stay the holiday with their families; Saturday, then, was the final battle of the three first-year armies that would determine the awarding of Professor Quirrell’s thrice-cursed Christmas wish.

Dumbledore glanced over at her, studying her gravely. “You fear that the explosion will come then, and someone will be hurt.”

Minerva nodded.

“And that Professor Quirrell will be blamed.”

Minerva nodded again, her face tight. She had long since become wise in the ways that Defense Professors were fired. “Albus,” Minerva said, “we cannot lose Professor Quirrell now, we \emph{cannot!} If he but stays through January our fifth-years will pass their \abbrev{owl}s, if he stays through March our seventh-years will pass their \abbrev{newt}s, he is remedying years of neglect in months, a whole generation will grow up able to defend themselves in spite of the Dark Lord’s curse—you must stop the battle, Albus! Ban the armies now!”

“I am not sure the Defense Professor would take that kindly,” said Dumbledore, glancing over toward the Head Table where Quirrell was drooling into his soup. “He did seem most attached to his armies, though when I agreed I thought there would be four in each year.” The old wizard sighed. “A clever man, probably with the best of intentions; but perhaps not clever enough, I fear. And to ban the armies might also trigger the explosion.”

“But then Albus, what will you \emph{do?}”

The old wizard favored her with a benign smile. “Why, I shall plot, of course. It’s the new fashion in Hogwarts.”

And they had come too close to the Head Table for Minerva to say anything more.
\sbreak
The terrifying part was how fast the whole thing had spiraled out of control.

The first battle in December had been...\ messy, or so Draco had heard.

The second battle had been \emph{deranged}.

And the next one would be \emph{worse}, unless the three of them together succeeded in their last desperate attempt to stop it.

“Professor Quirrell, this is insanity,” Draco said flatly. “This isn’t Slytherin any more, it’s just...” Draco was at a loss for words. He waved his hands helplessly. “You can’t possibly do any real plots with all this stuff going on. Last battle, one of my soldiers faked his own suicide. We have \emph{Hufflepuffs} trying to plot, and they think they can, but they \emph{can’t.} Things just happen at random now, it doesn’t have anything to do with who’s cleverest, or which army fights best, it’s...” He couldn’t even describe it.

“I agree with Mr.~Malfoy,” said Granger in the tones of someone who hadn’t ever expected to hear herself saying those words. “Allowing traitors isn’t working, Professor Quirrell.”

Draco had tried forbidding anyone in his army to plot except him, and that had just driven the plots underground, no one wanted to be left out when the soldiers in \emph{other} armies got to plot. After miserably losing their last battle, he’d finally given in and revoked his decree; but by then his soldiers had already started setting their own personal plans in motion, without any sort of central coordination.

After being told all the plans, or what his soldiers claimed were their plans, Draco had tried to sketch a plot to win the final battle. It had required considerably more than three different things to go right, and Draco had used \emph{Incendio} on the paper and \emph{Everto} to vanish the ashes, because if Father had seen it he would have been disowned.

Professor Quirrell’s eyelids were half-closed, his chin resting on his hands as he leaned forward onto his desk. “And you, Mr.~Potter?” said the Defense Professor. “Are you likewise in agreement?”

“All we’d need to do is shoot Franz Ferdinand and we could start World War One,” said Harry. “It’s gone to complete chaos. I’m all for it.”

“\emph{Harry!}” said Draco in utter shock.

He didn’t even realize until a second later that he’d said it at exactly the same time, and in exactly the same tone of indignation, as Granger.

Granger shot him a startled glance, and Draco carefully kept his face neutral. Oops.

“That’s right!” said Harry. “I’m betraying you! Both of you! Again! Ha ha!”

Professor Quirrell was smiling thinly, though his eyes were still half-closed. “And why is that, Mr.~Potter?”

“Because I think I can cope with the chaos better than Miss Granger or Mr.~Malfoy,” said the traitor. “Our war is a zero-sum game, and it doesn’t matter whether it’s easy or hard in an absolute sense, only who does better or worse.”

Harry Potter was learning far too fast.

Professor Quirrell’s eyes moved beneath their lids to regard Draco, and then Granger. “In truth, Mr.~Malfoy, Miss Granger, I simply could not live with myself if I shut down the grand debacle before its climax. One of your soldiers has even become a quadruple agent.”

“\emph{Quadruple?}” said Granger. “But there’s only three sides in the war!”

“Yes,” said Professor Quirrell, “you’d think that, wouldn’t you. I am not sure that there has ever in history been a quadruple agent, or any army with such a high fraction of real and pretended traitors. We are exploring new realms, Miss Granger, and we cannot turn back now.”

Draco left the Defense Professor’s office with his teeth gritting hard against each other, and Granger looking even more annoyed beside him.

“I can’t believe you did that, Harry!” said Granger.

“Sorry,” Harry said, not sounding sorry at all, his lips curved up in a merry smile of evil. “Remember, Hermione, it \emph{is} just a game, and why should generals like us be the only ones who get to plot? And besides, what are the two of you going to do about it? Team up against me?”

Draco traded glances with Granger, knowing that his own face was as tight as hers. Harry had been relying, more and more openly and gloatingly, on Draco’s refusal to make common cause with a mudblood girl; and Draco was beginning to get \emph{sick} of having that used against him. If this kept up much longer he \emph{was} going to ally with Granger just to crush Harry Potter, and see how much the son of a mudblood liked \emph{that.}
\sbreak
The terrifying part was how fast the whole thing had spiraled out of control.

Hermione stared at the parchment Zabini had given her, feeling utterly and completely helpless.

There were names, and lines connecting the names to other names, and some of the lines were in different colors and...

“Tell me,” said General Granger, “is there anyone in my army who \emph{isn’t} a spy?”

The two of them weren’t in the office but in another, deserted classroom, and they were alone; because, Colonel Zabini had said, it was now nearly certain that at least one of the captains was a traitor. Probably Captain Goldstein, but Zabini didn’t know for sure.

Her question had put an ironic smile on the young Slytherin’s face. Blaise Zabini always seemed a little disdainful of her, but he didn’t seem to actively dislike her; nothing like the derision he held for Draco Malfoy, or the resentment he had developed for Harry Potter. She had worried at first about Zabini betraying her, but the boy seemed desperate to show that the other two generals were no better than him; and Hermione thought that while Zabini would probably be happy to sell her out to anyone \emph{else}, he’d never let Malfoy or Harry win.

“Most of your soldiers \emph{are} still loyal to you, I’m pretty sure,” said Zabini. “It’s just that no one wants to be left out of the fun.” The scornful look on the Slytherin’s face made it clear what he thought of people who didn’t take plotting seriously. “So they think they can be double agents and secretly work for our side while pretending to betray us.”

“And that would also go for anyone in the \emph{other} armies who says they want to be \emph{our} spy,” Hermione said carefully.

The young Slytherin shrugged. “I think I did a good job of telling which ones really want to sell out Malfoy, I’m not sure \emph{anyone} really wants to sell out Potter to you. But Nott is a sure bet for betraying Potter to Malfoy and since I had Entwhistle approach him supposedly on behalf of Malfoy and Entwhistle really reports to us, that’s almost as good—”

Hermione closed her eyes for a moment. “We’re going to lose, aren’t we?”

“Look,” Zabini said patiently, “You’re in the lead right now on Quirrell points. We just have to not lose this last battle \emph{completely} and you’ll have enough Quirrell points to win the Christmas wish.”

Professor Quirrell had announced that the final battle would operate on a formal scoring system, which he’d been asked to do to avoid recriminations afterward. Each time you shot someone, the general of your army got two Quirrell points. A gong would ring through the battle area (they didn’t know yet where they would be fighting, though Hermione was hoping for the forest again, where Sunshine did well) and its pitch would tell which army had won the points. And if anyone was faking being hit, the gong would ring out anyway, and then a double gong would ring later, after no fixed time, to hail the retraction. And if you called the name of an army, cried “For Sunshine!” or “For Chaos!” or “For Dragon!”, it switched your allegiance to that army...

Even Hermione had been able to see the flaw in \emph{that} set of rules. But Professor Quirrell had gone on to announce that if you’d been originally assigned to Sunshine, nobody could shoot you in the name of Sunshine—or rather, they could, but then Sunshine lost a single Quirrell point, symbolized by a triple gong. That prevented you from shooting your own soldiers for points, and discouraged suiciding before the enemy got you, but you could still shoot spies if you had to.

Right now, Hermione had two hundred and forty-four Quirrell points, and Malfoy had two hundred and nineteen, and Harry had two hundred and twenty-one; and there were twenty-four soldiers in each army.

“So we fight carefully,” Hermione said, “and just try not to lose too badly.”

“No,” said Zabini. The young Slytherin’s face was now serious. “The problem is, Malfoy and Potter both know that their only way to win is to combine and crush us, then fight it out on their own. So here’s what I think we should do—”

Hermione left the classroom in something of a daze. Zabini’s plan hadn’t been the obvious one, it had been strange and complicated and layered and the sort of thing she would’ve expected Harry to come up with, not Zabini. It felt wrong just for her to be able to \emph{understand} a plan like that. Young girls shouldn’t be able to understand plans like that. The Hat would’ve Sorted her into Slytherin, if it’d seen that she could understand plans like that...
\sbreak
The awesome thing was how fast he’d been able to escalate the chaos once he started doing it deliberately.

Harry sat in his office; he’d been given the authority to order furniture from the house elves, so he’d ordered a throne, and curtains in a black and crimson pattern. Scarlet light like blood, mixed with shadow, poured over the floor.

Something in Harry felt like he’d finally come home.

Before him stood the four Lieutenants of Chaos, his most trusted minions, one of whom was a traitor.

This. This was what life should be like.

“We are gathered,” said Harry.

“Let Chaos reign,” chorused his four Lieutenants.

“My hovercraft is full of eels,” said Harry.

“I will not buy this record, it is scratched,” chorused his four Lieutenants.

“All mimsy were the borogroves.”

“And the mome raths outgrabe!”

That concluded the formalities.

“How goes the confusion?” Harry said in a dry whisper like Emperor Palpatine.

“It goes well, General Chaos,” said Neville in the tone he always used for military matters, a tone so deep that the boy often had to stop and cough. The Chaotic Lieutenant was neatly dressed in his black school robes, trimmed in the yellow of Hufflepuff House, and his hair was parted and combed in the usual look for an earnest young boy. Harry had liked the incongruity better than any of the cloaks they’d tried. “Our Legionnaires have begun five new plots since yesterday evening.”

Harry smiled evilly. “Do any of them have a chance of working?”

“I don’t think so,” said Neville of Chaos. “Here’s the report.”

“Excellent,” said Harry, and laughed chillingly as he took the parchment from Neville’s hand, trying his best to make it sound like he was choking on dust. That brought the total to sixty.

Let Draco \emph{try} to handle that. Let him \emph{try}.

And as for Blaise Zabini...

Harry laughed again, and this time it didn’t even take an effort to sound evil. He really needed to borrow someone’s pet Kneazle for his staff meetings, so he’d have a cat to stroke while he did this.

“Can the Legion stop making plots now?” said Finnigan of Chaos. “I mean, don’t we have enough already—”

“No,” Harry said flatly. “We can \emph{never} have enough plots.”

Professor Quirrell had put it perfectly. They were pushing the boundaries further, perhaps, then they had ever been pushed; and Harry wouldn’t have been able to live with himself if he’d turned back now.

There came a knock at the door.

“That will be the Dragon General,” Harry said, smiling with evil prescience. “He arrives precisely as I expected. Do show him in, and yourselves out.”

And the four Lieutenants of Chaos shuffled out, casting dark looks at Draco as the enemy general entered into Harry’s secret lair.

If he wasn’t allowed to do this when he was older, Harry was just going to stay eleven forever.
\sbreak
The sun was dripping through the red curtains, sending rays of blood dancing across the floor from behind Harry Potter’s grownup-sized cushioned chair, which he had covered in gold and silver glitter and insisted on referring to as his throne.

(Draco was beginning to feel a lot more confident that he’d done the right thing in deciding to overthrow Harry Potter before he could take over the world. Draco couldn’t even \emph{imagine} what it would be like to live under his rule.)

“Good evening, Dragon General,” said Harry Potter in a chill whisper. “You have arrived just as I expected.”

This was not surprising, considering that Draco and Harry had agreed on the meeting time in advance.

And it also wasn’t evening, but by now Draco knew better than to say anything.

“General Potter,” Draco said with as much dignity as he could manage, “you know that our two armies have to work together for \emph{either} of us to win Professor Quirrell’s wish, right?”

“Yesss,” hissed Harry, like the boy thought he was a Parselmouth. “We must cooperate to destroy Sunshine, and only then fight it out between us. But if one of us betrays the other earlier on, that one could gain an advantage in the later fight. And the Sunshine General, who knows all this, will try to trick each of us into thinking the other has betrayed them. And you and I, who know that, will be tempted to betray the other and pretend that it is Granger’s trickery. And Granger knows \emph{that}, as well.”

Draco nodded. That much was obvious. “And...\ both of us \emph{only} want to win, and there’s no one else who’ll punish either of us if we defect...”

“Precisely,” said Harry Potter, his face now turning serious. “We are faced with a \emph{true} Prisoner’s Dilemma.”

The Prisoner’s Dilemma, according to Harry’s teachings, ran thus: Two prisoners had been locked in separate cells. There was evidence against each prisoner, but only minor evidence, enough for a prison sentence of two years piece. Each prisoner could opt to \emph{defect,} betray the other, testify against them in court; and this would take one year off their own prison sentence, but add two years to the other’s. Or a prisoner could \emph{cooperate,} staying silent. So if both prisoners defected, each testifying against the other, they would serve three years apiece; if both cooperated, or stayed silent, they would serve two years each; but if one defected and the other cooperated, the defector would serve a single year, and the cooperator would serve four.

And both prisoners had to make their decision without knowing the other one’s choice, and neither would be given a chance to change their decision afterward.

Draco had observed that if the two prisoners had been Death Eaters during the Wizarding War, the Dark Lord would have killed any traitors.

Harry had nodded and said that was \emph{one} way to resolve the Prisoner’s Dilemma—and in fact both Death Eaters would \emph{want} there to be a Dark Lord for exactly that reason.

(Draco had asked Harry to stop and let him to think about this for a while before they continued. It had explained a \emph{lot} about why Father and his friends had agreed to serve under a Dark Lord who often wasn’t nice to them...)

In fact, Harry had said, this was pretty much the reason why people had governments—\emph{you} might be better off if you stole from someone else, just like each prisoner would be individually better off if they defected in the Prisoner’s Dilemma. But if \emph{everyone} thought like that, the country would fall into chaos and everyone would be worse off, like what would happen if both prisoners defected. So people let themselves be ruled by governments, just like the Death Eaters had let themselves be ruled by the Dark Lord.

(Draco had asked Harry to stop again. Draco had always taken for granted that ambitious wizards put themselves in power because they wanted to rule, and people let themselves be ruled because they were scared little Hufflepuffs. And this, on reflection, still seemed true; but Harry’s perspective was fascinating even if it was wrong.)

But, Harry had continued afterward, the fear of a third party punishing you was not the \emph{only} possible reason to cooperate in the Prisoner’s Dilemma.

Suppose, Harry had said, you were playing the game against a magically produced identical copy of yourself.

Draco had said that if there were two Dracos, of course neither Draco would want anything bad to happen to the other one, not to mention that no Malfoy would let himself become known as a traitor.

Harry had nodded again, and said that this was yet \emph{another} solution to the Prisoner’s Dilemma—people might cooperate because they cared about each other, or because they had senses of honor, or because they wanted to preserve their reputation. Indeed, Harry had said, it was rather difficult to construct a \emph{true} Prisoner’s Dilemma—in real life, people usually cared about the other person, or their honor or their reputation or a Dark Lord’s punishment or \emph{something} besides the prison sentences. But suppose the copy had been of someone \emph{completely} selfish—

(Pansy Parkinson had been the example they’d used)

—so each Pansy only cared what happened to \emph{her} and not to the other Pansy.

\emph{Given} that this was all Pansy cared about...\ and that there was no Dark Lord...\ and Pansy wasn’t worried about her reputation...\ and Pansy either had no sense of honor or didn’t consider herself obligated to the other prisoner... \emph{then} would the rational thing be for Pansy to cooperate, or defect?

Some people, Harry said, claimed that the rational thing to do was for Pansy to defect against her copy, but Harry, plus someone named Douglas Hofstadter, thought these people were wrong. Because, Harry had said, if Pansy defected—not at random, but for what seemed to her like \emph{rational reasons}—then the other Pansy would think exactly the same way. Two identical copies wouldn’t decide different things. So Pansy had to choose between a world in which both Pansies cooperated, or a world in which both Pansies defected, and she was better off if both copies cooperated. And if Harry had thought ‘rational’ people \emph{did} defect in the Prisoner’s Dilemma, then he wouldn’t have done anything to spread that kind of ‘rationality’, because a country or a conspiracy full of ‘rational’ people would dissolve into chaos. You would tell your \emph{enemies} about ‘rationality’.

Which had all \emph{sounded} reasonable at the time, but \emph{now} the thought was occurring to Draco that...

“\emph{You} said,” Draco said, “that the rational solution to the Prisoner’s Dilemma is to cooperate. But of course \emph{you} would want me to believe that, wouldn’t you?” And if Draco was fooled into cooperating, Harry would just say, \emph{Ha ha, betrayed you again!} and laugh at him about it afterward.

“I wouldn’t fake your lessons,” Harry said seriously. “But I have to remind you, Draco, that I didn’t say you should just automatically cooperate. Not on a \emph{true} Prisoner’s Dilemma like this one. What I said was that when you choose, you shouldn’t think like you’re choosing for just yourself, \emph{or} like you’re choosing for everyone. You should think like you’re choosing for all the people who are \emph{similar enough} to you that they’ll probably do the same thing you do for the same reasons. And also choosing the predictions made by anyone who knows you well enough to predict you accurately, so that you never have to regret being rational because of the correct predictions that other people make about you—remind me to explain about Newcomb’s Problem at some point. So the question you and I have to ask, Draco, is this: are we similar enough that we’ll probably do the \emph{same thing} whatever it is, making our decisions in mostly the same way? Or do we know each other well enough to predict each other, so that \emph{I} can predict whether you’ll cooperate or defect, and \emph{you} can predict that I’ve decided to do the same thing I predict you’ll do, because \emph{I} know that you can predict me deciding that?”

...and Draco could not help but think that since he had to strain just to understand \emph{half} of that, the answer was obviously ‘No’.

“Yes,” said Draco.

There was a pause.

“I see,” said Harry, sounding disappointed. “Oh, well. I guess we’ll have to think of some other way, then.”

Draco hadn’t thought that was going to work.

Draco and Harry talked about it back and forth. They had both agreed much earlier that what they did on the battlefield would \emph{not} count as broken promises in real life—though Draco was a little angry about what Harry had done in Professor Quirrell’s office, and said so.

But if the two of them couldn’t rely on honor or friendship, that \emph{did} leave the question of how to get their armies to work together on beating Sunshine, despite everything Granger might try to break them up. Professor Quirrell’s rules didn’t make it tempting to let Sunshine kill the other army’s soldiers—that just increased the bar you had to pass yourself—but it did tempt each side to steal kills instead of acting like a single army would, or to shoot some of the other side’s soldiers during the confusion of battle...
\sbreak
Hermione was walking back to Ravenclaw not really looking where she was going, her mind preoccupied with war and treachery and other age-inappropriate concepts, and she turned a corner and bumped straight into a grownup.

“Sorry,” she said automatically, and then, entirely without thinking, “\emph{Eeeeek!}”

“Don’t worry, Miss Granger,” said the cheerful smile, set beneath the twinkling eyes, and above the silver beard, of the \scream{Headmaster of Hogwarts}. “You are quite forgiven.”

Her gaze was helplessly locked on the kindly face of the most powerful wizard in the world, who was also the Chief Warlock, who was also the Supreme Mugwump, who had gone insane years ago from the stress of fighting the Dark Lord, and numerous other facts that were popping up into her mind one after the other while her throat went on making little embarrassing squeaks.

“In fact, Miss Granger,” said Albus Percival Wulfric Brian Dumbledore, “it is quite lucky that we bumped into each other. Why, I was just now wondering curiously what the three of you were thinking of asking for your wishes...”
\sbreak
Saturday dawned bright and clear and with the students speaking in hushed voices, as though the first to shout might set off the explosion.
\sbreak
Draco had hoped that they would be fighting in the upper levels of Hogwarts again. Professor Quirrell had said that real fights were more likely to take place in cities than forests, and fighting inside schoolrooms and corridors was supposed to simulate that, with ribbons to mark the allowed areas. Dragon Army had done well in those fights.

Instead, just as Draco had feared, Professor Quirrell had come up with something \emph{special} for this battle.

The battleground was the Hogwarts Lake.

And not in boats, either.

They were fighting \emph{underwater}.

The Giant Squid had been temporarily paralyzed; spells had been set in place to keep away the grindylows; Professor Quirrell had gone and talked to the merfolk; and all the soldiers had been issued \emph{potions of underwater action} that allowed them to breathe, see clearly, talk to each other, and swim not quite as fast as a fast walk by kicking their legs.

A huge silver sphere hung in the center of the battleground, shining like a small underwater moon. It would help to provide a sense of direction—at first. The moon would slowly go into eclipse as the battle went on, and when it had gone entirely dark, the battle would end if it hadn’t already.

War in water. You couldn’t defend a perimeter, attackers could come at you from any direction, and even with the potion you couldn’t see very far in the darkness of the lake.

And if you swam too far away from the action, you would start to glow after a while, and be easy to hunt down—ordinarily if an army scattered and ran instead of fighting, Professor Quirrell would just declare them defeated; but today they were working on a points system. Of course you still had some time \emph{before} you started to glow, if you wanted to play assassin.

Dragon Army had been set low in the water at the start of the game; above and far away, the distant underwater moon shone. The murky water was mostly lit by \emph{Lumos} Charms, though his soldiers would extinguish the lights as soon as they began maneuvers. There was no point in letting the enemy see you before you saw them.

Draco kicked his legs a few times, propelling him to a higher position from which he could gaze down at where his soldiers hovered in the water.

The conversations died down almost at once under Draco’s icy glare, his soldiers looking up at him with gratifying expressions of fear and worry.

“Listen to me very carefully,” said General Malfoy. His voice came out a little lower, a little burbly with bubbles, \emph{libsten to me vebwy caerbfully}, but the sound traveled clearly. “There’s only one way we can win this. We’ve got to march on Sunshine together with Chaos, and beat Sunshine. \emph{Then} we fight it out with Potter and win. That’s \emph{got} to happen, understand? No matter what else goes on, that part \emph{has} to happen that way—”

And Draco explained the plan he and Harry had come up with.

Astonished looks were exchanged among the soldiers.

“—and if any of \emph{your} plots get in the way of that,” finished Draco, “after we are out of the water, I will set you on \emph{fire}.”

There was a nervous chorus of yessirs.

“And everyone with secret orders, make sure you carry them out \emph{to the letter,}” said Draco.

Around half his soldiers \emph{openly nodded,} and Draco marked them for death after he rose to power.

Of course all the private orders were fake, like one Dragon being told to offer a false traitor’s commission to another Dragon, and the second Dragon being told in hushed confidence to report anything said by the first Dragon. Draco had told each Dragon that the whole war could depend on that one thing, and that he hoped they understood it was more important than the plans they’d previously made. With luck that would keep all the idiots happy, and maybe flush out a few spies to boot, if the reports didn’t match the instructions.

Draco’s real plan for winning against Chaos...\ well, it was simpler than the one he’d burned, but Father still wouldn’t have liked it. Despite trying, though, Draco hadn’t been able to think of anything better. It was a plot that couldn’t \emph{possibly} have worked against anyone except Harry Potter. In fact it had \emph{been} Harry’s plan originally, according to the traitor, though Draco had guessed that without being told. Draco and the traitor had just modified it a little...
\sbreak
Harry took a deep breath, feeling the water gurgle harmlessly in his lungs.

They’d fought in the forest, and he hadn’t gotten a chance to say it.

They’d fought in the corridors of Hogwarts, and he hadn’t gotten a chance to say it.

They’d fought in the air, broomsticks issued to every soldier, and it still hadn’t made sense to say it.

Harry had thought he wouldn’t ever get to say those words, not while he was still young enough for them to be real...

The Chaos Legionnaires were looking at Harry in puzzlement, as their general swam with his feet pointing up toward the distant light of the surface, and his head pointed down toward the murky depths.

“\emph{Why are you upside down?}” the young commander shouted at his army, and began to explain how to fight after you abandoned the privileged orientation of gravity.
\sbreak
A hollow, booming bell echoed through the water, and on the instant, Zabini and Anthony and five other soldiers struck out downward, into the murky depths of the lake. Parvati Patil, the only Gryffindor in the group, turned her head back for a moment and gave them all a cheery wave as she dived; and after a moment, Scott and Matt did the same. The rest just sank and vanished.

General Granger swallowed a lump in her throat as she watched them go. She was risking everything on this, dividing her army instead of just trying to take as many enemy soldiers with them as possible.

The thing to realize, Zabini had told her, was that no army would move until they had a plan that let them expect victory. Sunshine couldn’t just plan to win themselves, they had to make both other armies \emph{think} they would win until it was too late.

Ernie and Ron still looked like they were in shock. Susan was gazing after the disappearing soldiers with a calculating look. Her army, what was left of it, just looked bewildered, traceries of light dappling on their uniforms as they all drifted just below the sunlit surface of the lake.

“\emph{Now} what?” said Ron.

“Now we wait,” said Hermione, loudly enough for all the soldiers to hear. It felt odd to talk with her mouth full of water, she kept feeling like she was committing some sort of horrible impoliteness at the dinner table and was about to drool all over herself. “All of us left here are going to get zapped, but that was going to happen anyway with Dragon and Chaos ganging up on us. We’ve just got to take as many of them with us as we can.”

“I’ve got a plan,” said one of her Sunshine Soldiers... Hannah, her voice had been a little hard to recognize at first. “It’s like all complicated, but I know how we can get Dragon and Chaos to start fighting each other—”

“Me too!” said Fay. “I’ve got a plan too! See, Neville Longbottom is secretly on our side—”

“\emph{You} were talking to Neville?” said Ernie. “That’s not right, \emph{I} was the one who—”

Daphne Greengrass and a couple of other Slytherins who hadn’t gone with Zabini were giggling helplessly as the cries of “No, wait, \emph{I} was the one who got Longbottom” erupted from one soldier after another.

Hermione just looked at them all wearily.

“Okay,” said Hermione when it had all died down, “does everyone get it? All your plots were faked by the Chaos Legion, or maybe some by Dragon. Anyone who \emph{really} wanted to betray Harry or Malfoy went straight to me or Zabini, not you. Just go ahead and compare notes on all your secret plots and you’ll see it for yourselves.” She might not be as good at plotting as Zabini, but she could always understand what all her officers told her, that was why Professor Quirrell had made her the general. “So don’t bother trying to do any plots when the other armies get here. Just fight, okay? Please?”

“But,” said Ernie with shock on his face, “Neville is in \emph{Hufflepuff!} You’re saying he \emph{lied} to us?”

Daphne was laughing so hard and so helplessly that the exhalations had turned her upside down in the water.

“I’m not sure \emph{what} Longbottom is,” said Ron darkly, “but I don’t think he’s a Hufflepuff any more. Not now that \emph{Harry Potter’s} got to him.”

“Do you know,” said Susan, “I \emph{asked} him that, and Neville told me he had become a Chaos Hufflepuff?”

“\emph{Anyway},” said Hermione in a loud voice. “Zabini took with everyone who we thought was a spy, so in \emph{our} army we can stop watching each other quite so hard now, I hope.”

“\emph{Anthony} was a spy?” yelled Ron.

“\emph{Parvati} was a spy?” gasped Hannah.

“Parvati was \emph{totally} a spy,” said Daphne. “She shopped at the spy shoe store and wore spy lipstick, and someday she’s going to marry a nice spy husband and have a lot of little spies.”

And then a gong sound echoed through the water, indicating that Sunshine had just scored two points.

This was shortly followed by the triple gong of Dragon losing a single point.

Traitors weren’t allowed to kill generals, not after the disaster of the first battle in December when all three generals had been shot in the first minute. But with any luck...

“Aw,” said Hermione. “It sounds like Mr.~Crabbe is taking a little nap.”
\sbreak
Like two shoals of fish, the armies swam along.

Neville Longbottom kicked his feet in slow, measured motions. Diving, always diving in whatever direction you happened to be moving. You wanted to show the enemy the smallest profile, present them with your head or your feet. So you were always diving, downward and head-first, and the enemy was always \emph{down.}

Like every Chaos Legionnaire in the army, Neville’s head was constantly rotating as he swam, looking up, down, around, to every side. Not just watching for Sunshine Soldiers, but watching for any sign that a Chaos Legionnaire had drawn their wand and was about to betray them. Usually traitors waited until the confusion of battle to make their move, but that early gong had put them all on guard.

...the truth was, Neville was feeling sad about that. In November he’d been a soldier in a united army, all of them pulling together and helping each other, and now they were all watching each other constantly for the first signs of betrayal. It might have been more fun for General Chaos, but it wasn’t nearly as much fun for Neville.

The direction formerly known as ‘up’ was getting steadily brighter, as they came closer to the surface and Sunshine.

“Wands out,” said General Chaos.

Neville’s squad drew their wands, pointing them straight ahead toward the enemy, as their heads scanned around more rapidly. If there were Sunny traitors, the time was approaching for them to strike.

The other shoal of fish, Dragon Army, was doing the same thing.

“\emph{Now!}” shouted the distant voice of the Dragon General.

“\emph{Now!}” shouted General Chaos.

“\emph{For Sunshine!”} shouted all the soldiers in both armies, and charged downward.
\sbreak
“\emph{What?}” said Minerva involuntarily as she watched the screens from next to the lake, a cry echoed in many other places; all of Hogwarts was watching this battle as they had watched the first.

Professor Quirrell was laughing dryly. “I warned you, Headmaster. It is impossible to have rules without Mr.~Potter exploiting them.”
\sbreak
For long precious seconds, as the forty-seven soldiers charged her own seventeen, Hermione’s mind went blank.

Why...

Then it all snapped into place.

Every time a soldier originally from Sunshine got shot by someone crying the name of Sunshine, she would lose a Quirrell point. When two Sunshine Soldiers were shot by either army, \emph{both} enemy armies would be two points closer to overtaking her, it was the same gain only \emph{shared}. And if anyone shot another soldier \emph{not} in the name of Sunshine, that gong \emph{wouldn’t} get lost in the confusion...

Hermione was suddenly very glad that Zabini hadn’t gone with the obvious plan of starting trouble between the other two armies while they attacked Sunshine.

It was still disheartening, though, that sense of your chances closing down, of hope being taken away.

Most of Hermione’s soldiers were still looking confused, but some had expressions of dawning horror as they got it.

“It’s all right,” Susan Bones said firmly. Heads turned to look at the Sunshine Captain. “Our job is the same, to take as many of them with us as we can. And remember, Zabini took away all the spies! We don’t have to stay on the lookout like \emph{they} do!” The girl was smiling defiantly, provoking answering smiles from many of the other soldiers, even from Hermione herself. “It can be like it was in November. We just have to keep our heads high, fight our best, and trust each other—”

Daphne shot her.
\sbreak
“\emph{Blood for the blood god!}” shrieked Neville of Chaos, though since he was underwater it came out more like ‘Blubbled for the blubbled glub!’

Captain Weasley spun and raised his wand toward Neville and fired. But Neville was swimming \emph{downward} toward him, wand pointed straight ahead, and that meant the Simple Shield could shelter Neville’s entire profile; if anyone shot him now, it wasn’t going to be Sunny Ron.

A grimly determined look came over Captain Weasley’s face, and he arrowed straight up toward Neville, mouthing the word \emph{Contego,} though the shield wasn’t visible in the water.

The two enemy champions shot toward each other like arrows released from bows, each aimed to split the other down the middle. They had dueled many times before, but this time would pay for all.

(Far away by the lakeside, a hundred breaths were held.)

“\emph{Rainbows and unicorns!}” roared the Sunshine Captain.

“\emph{The Black Goat with a thousand young!}”

“\emph{Do your homework!}”

Closer and yet closer, the two champions charged, neither willing to swerve, the first person to turn would present a vulnerable broadside and get shot, though if neither lost their nerve they would crash right into each other...

Falling straight down as the enemy rose straight up to meet him, hammer descending to meet anvil in a path neither was willing to leave...

“\emph{Special attack, Chaotic Twist!}”

Neville saw the look of horror on Captain Weasley’s face as the Hover Charm caught him. They’d tested it before the battle had started; and just as Harry had suspected, \emph{Wingardium Leviosa} became a whole new sort of weapon once everyone was swimming underwater.

“\emph{Curse you, Longbottom!}” shrieked Ron Weasley, “\emph{Can’t you ever fight without your dumb special attacks—}”

and by that time the Sunshine Captain had been spun around sideways and Neville shot him in the leg.

“I don’t fight fair,” said Neville to the sleeping form, “I fight like Harry Potter.”
\sbreak
\emph{Granger: 237 / Malfoy: 217 / Potter: 220}

It still hurt every time he had to shoot Hermione. Harry could hardly stand to look at the expression of peace that had come over her sleeping face, arms now drifting aimlessly as the curves of sunlight moved over her camouflage uniform and the cloud of her chestnut hair.

And if Harry had tried to duck out of being the one to shoot her...\ not only would Draco have known what it meant, \emph{Hermione} would have been offended.

\emph{She’s not dead,} Harry said to his brain as his kicking feet pushed him away, \emph{she’s just resting. \scream{Idiot}.}

\emph{Are you sure?} said his brain. \emph{What if she’s an ex-Hermione? Could we go back and check?}

Harry glanced back briefly.

\emph{See, she’s fine, there are bubbles coming out of her mouth.}

\emph{Could’ve been her last breath escaping.}

\emph{Oh be quiet. Why are you being so paranoid-protective, anyway?}

\emph{Er, first real friend we’ve ever had in our whole life? Hey, remember what happened to our pet rock?}

\emph{Would you \scream{shut up} about that worthless lump of rubble, it wasn’t even alive let alone sentient, that is like the most pathetic childhood trauma ever—}

The two armies swiftly separated, becoming two shoals of fish once more.

General Granger had gone down seventeen points, and taken three Chaotics and two Dragons with her; and one Chaotic and two Dragons had been shot as traitors. So she’d lost net seven points, Harry had lost one, Draco had lost two; that put Sunshine twenty points up on Dragon, and seventeen points up on Chaos. Chaos could still win easily if they exterminated all twenty remaining Dragons. The wild card, of course, being those seven remaining Sunshine Soldiers...

...if you could call them that.

The two shoals swam uneasily next to each other, the soldiers in each army awaiting an order to call out their true allegiances, and attack...

“Everyone who got them,” Harry said loudly, “remember Special Orders One through Three. And don’t forget it’s Merlin Says on Three. Do not acknowledge.”

The trustworthy two-thirds of the army did not nod, and the other third just looked puzzled.

\emph{Special Order One: Don’t bother trying to call out any codewords in this battle, don’t expend effort on any plot not specially approved by the commander; just swim, shield, and fire.}

Hermione and Draco had both been fighting their soldiers, trying to get them to stop plotting on their own all through December. Harry had egged his soldiers on and supported their plotting through the last two battles...\ while also telling them that at some \emph{future} point he might ask them to put a plot or two on hold, to which they’d all readily agreed. So now, in this critical battle, they were happy to obey.

Neither Hermione or Draco could have given that order successfully, Harry was certain. It was the difference between your soldiers seeing you as an ally in their plotting, and seeing you as a spoilsport old fuddy-duddy who didn’t want them to have any fun. Imposition of order equaled escalation of chaos, and it also worked in reverse...

“There they are!” shouted someone, and pointed.

From the depths of the lake arose the forgotten ones, the ones who’d forsaken the last battle, the seven missing Sunshine Soldiers, glowing with the bright aura of cowards, now fading as they returned to battle.

The two shoals of fish wavered, pointing wands uneasily.

“Hold your fire!” shouted Harry, and a similar cry came from General Malfoy.

There was a moment of held breath.

Then the seven Sunshine Soldiers swam up to join Dragon Army.

There was a triumphant cheer from Dragon Army.

There were cries of dismay from a third of the Chaos Legion.

Some of the other two-thirds smiled, though they shouldn’t have.

Harry wasn’t smiling.

\emph{Oh, this is so completely not going to work...}

But Harry hadn’t been able to think of anything better.

“Special Orders Two and Three still apply!” shouted Harry. “Fight!”

“\emph{For the Chaos Legion!}” roared twenty Chaotic Legionnaires.

“\emph{For Dragon Army!}” roared twenty Dragon Warriors and seven Sunshine Soldiers.

And the Chaotics dived straight downward, as all the traitors got ready to strike.
\sbreak
\emph{Granger: 237 / Malfoy: 220 / Potter: 226}

Draco’s head darted around frantically, trying to weigh up what was happening; somehow, despite his greater forces, he’d \emph{lost the initiative.} Four small Chaotic forces were being pursued by four larger Dragon forces, but because Draco’s forces were the ones trying to force an engagement, it meant that they had to \emph{follow} where Chaos \emph{ran,} and somehow that was producing concentrations of Chaotic force that would fire into the exposed sides of Dragon—

It was happening \emph{again!}

“\emph{Prismatis!}” shouted Draco, raising his wand, and that shield you could see even through the water, a sparkling multicolored flat wall wide enough to shield Draco and the five other Dragons with him from the Chaotic force that had just started firing on them as they swam past, and \emph{that} let the other five Dragons turn \emph{their} attentions back to the Chaotic force they’d been chasing—

There was a tense moment as sleep spell after sleep spell crashed into Draco’s Prismatic Wall, and Draco was hoping to Merlin that none of those four Chaotics had learned the Breaking Drill Hex—

Then there was the bell of a Dragon victory, and the Chaotic force spun head-for-foot and began swimming away; and Draco, his hands now shaking slightly, dropped the Prismatic Wall and lowered his wand.

Fighting in water was more exhausting even than fighting on broomsticks.

“\emph{Do not pursue!}” Draco cried to his soldiers as they started to follow, then, “\emph{Sonorus! \scream{Reform on me}!}”

The Dragon forces started converging on Draco, and the Chaotic forces spun around and began \emph{pursuing} the Dragons on the instant—Draco swore out loud as he heard the bell of a Chaotic victory, someone hadn’t gotten their Simple Shield oriented right—and then the Dragon forces were in supporting range of each other and the Chaotics were moving back into the murky distance.

Somehow, despite their numerical superiority, the Dragons had scored three times against the Chaotics and the Chaotics had scored four times back, and he’d heard one Dragon spy get executed. Either Harry Potter had thought of a lot of very good ideas very fast, or for some unimaginable reason he’d already spent a lot of time working out how to fight underwater. This wasn’t working, and Draco needed to rethink things.

It looked like everyone was having trouble aiming while swimming, too, the battle might last long enough that time would be called...\ the distant underwater moon was only half full now, that wasn’t good...\ he had to rethink things \emph{fast...}

“What is it?” said Padma Patil, as she and her force swam over toward Draco.

Padma was his second-in-command; she was clever and powerful, and better yet, she hated Granger and saw Harry as a rival, which made her \emph{trustworthy.} Working with Padma was making him realize the truth of the old adage that Ravenclaw was sister to Slytherin; Draco had been surprised when his father had told him it was an acceptable House for his future wife, but now he saw the sense of it.

“Wait until we’re all here,” Draco said. The truth was, he needed to catch his breath. That was the trouble with being the general \emph{and} the most powerful wizard, you had to keep using magic.

Zabini came in next, commanding a force of two Sunnies and four Dragons, one of whom was Gregory keeping an eye on Zabini. Draco didn’t trust Zabini. And neither Draco nor Zabini trusted the Sunnies enough to make them a majority of any unit; they were \emph{supposed} to be loyal either to Draco directly, or to Granger who’d been fooled by the promise that the Dragons would be betrayed in the end after both forces had been depleted, just as Harry’s more trusted Chaotics should’ve been fooled into not shooting at the Sunnies by the promise of their firing fake Sleep Hexes and switching to support Chaos later; but it was possible some of the Sunnies \emph{were} loyal to Chaos and \emph{weren’t} firing real Sleep Hexes and that was why Dragon wasn’t winning the way their numerical advantage should’ve let them win...

The next unit that approached was depleted, three soldiers holding wands on two other soldiers, who were swimming with empty hands.

Draco gritted his teeth. More traitor problems. He needed to talk to Professor Quirrell about having some way to \emph{punish} traitors at least, conditions like these were \emph{unrealistic}, in real life you tortured your traitors to death.

“General Malfoy!” shouted the commander of the problem unit as it swam up, a Ravenclaw boy named Terry. “We don’t know what to do—Cesi shot Bogdan, but Cesi says Kellah told him that Bogdan shot Specter—”

“I \emph{didn’t!}” said Kellah.

“Yes you \emph{did!}” shrieked Cesi. “General Malfoy, \emph{she’s} the spy, I should’ve rea—”

“\emph{Somnium,}” said Draco.

There was the triple bell of a one-point loss from Dragon, and then Kellah’s limp body began to float away in the water.

Draco \emph{had} heard the word ‘recursion’ by this point, and he knew a Harry Potter plot when he saw one.

(Unfortunately Draco had \emph{not} heard of autoimmune disorders, and the thought did \emph{not} readily occur to him that a clever virus would begin its attack by creating symptoms of an autoimminue disorder so as to get the body to distrust its own immune system...)

“\emph{General order!}” said Draco, raising his voice. “Nobody gets to shoot spies except myself, Gregory, Padma, and Terry. If anyone sees anything suspicious they come to one of \emph{us.}”

And then—

There was the bell of Sunshine scoring two points.

“\emph{What?}” said Draco and Zabini around the same time; their heads swiveled around. No one seemed to have gotten hit, and all the Sunshine soldiers were present and accounted for. (Except Parvati, who had been shot by some still-unknown traitor in Padma’s squad; and of course Padma had shot Parvati again in case she was faking, so it wasn’t her...)

“A Sunny traitor in Chaos?” said Zabini, sounding puzzled. “But all the ones I knew about were supposed to strike during Chaos’s attack on Sunshine—”

“No!” said Padma in a tone of sudden realization. “That was \emph{Chaos} executing a spy!”

“\emph{What?}” said Zabini. “But why—”

And Draco got it. \emph{Damn it!} “Because Potter thinks he’s safe for how much he beats Sunshine, but not for how much he beats \emph{us!} So he doesn’t want to lose a single point when he executes a traitor! \emph{General order!} If you have to execute a traitor, call Sunshine first! Do that only until the Sunshine bell has rung four more times! And don’t forget to switch back to Dragon afterward—”
\sbreak
\emph{Granger: 253 / Malfoy: 252 / Potter: 252}

Longbottom’s body drifted chaotically through the water, arms and legs disarrayed. After Draco had finally got a hit in they’d all shot him \emph{again} just to be sure.

Nearby was Harry Potter, now protected by a Prismatic Sphere, looking at them all grimly as the last sliver of crescent moon slowly diminished, somewhere far away. If Longbottom had managed to shoot one more soldier (Draco knew Harry was thinking), if the two Chaotics had managed to hold out just a little longer, they might have \emph{won}...

After Draco had reformed his forces and struck out again, the ensuing battle and execution of spies in Sunshine’s name had left Sunshine exactly one point ahead of Dragon and Chaos both. Once Harry had started doing it, Draco had been left with no choice but to follow suit.

But now they had General Chaos outnumbered three to one, the survivors of Dragon Army and the last remaining Sunny traitor: Draco, and Padma, and Zabini.

And Draco, who was no fool, had ordered Padma to take Zabini’s wand after Longbottom had shot Gregory and fallen in turn to Draco. The boy had given him an insulted look, told Draco that he owed him for this, and handed it over.

That left Draco and Padma to take down General Chaos.

“I don’t suppose you’d like to surrender?” said Draco, smiling as evilly as any smile he’d ever directed at Harry Potter.

“Sleep before surrender!” shouted General Chaos.

“Just so you know,” said Draco, “Zabini doesn’t actually \emph{have} an older sister for you to rescue from Gryffindor bullies. But Zabini \emph{does} have a mother who doesn’t approve of Muggleborns like Granger, and I wrote her a few notes, and offered Zabini a few favors—nothing involving my father, just things \emph{I} can do in school. And by the way, Zabini’s mother doesn’t approve of the Boy-Who-Lived, either. Just in case you still thought Zabini was really on your side.”

Harry’s face grew even grimmer.

Draco raised his wand, and began breathing rhythmically, building up strength for a Breaking Drill Hex. Granger’s Prismatic Sphere was almost as strong as Draco’s now, and Harry’s wasn’t much weaker, where did those two find \emph{time?}

“\emph{Lagann!}” spoke Draco, putting everything he had into it, and the green spiral blazed out and Harry’s shield shattered, and at almost the same moment—

“\emph{Somnium!}” said Padma.
\sbreak
\emph{Granger: 253 / Malfoy: 252 / Potter: 254}

Harry let out a long breath of relief, and not just because he didn’t have to hold the Prismatic Sphere any more. His hand was shaking as he lowered his wand.

“You know,” said Harry, “I was pretty worried there for a moment.”

\emph{Special Order Two: If a Sunny traitor doesn’t seem to be really shooting at you, fake being hit occasionally. Prefer targeting Dragons to Sunnies but go ahead and shoot Sunnies if you can’t shoot Dragons.}

\emph{Special Order Three: Merlin says do not shoot at Blaise Zabini or either Patil twin.}

With a wide grin, Parvati Patil stripped the Transfigured patch off her uniform’s insignia, and let it float away in the water.

“Gryffindors for Chaos,” she said, and handed Zabini his wand back.

“Thank you \emph{very} much,” Harry said, and bowed sweepingly to the Gryffindor girl. “And thank \emph{you} as well,” bowing to Zabini. “You know, when you came to me with that plan, I wondered if you were brilliant or crazy, and I’ve decided that you’re both. And by the way,” Harry said, now turning as though to address Draco’s body, “Zabini \emph{does} have a cousin—”

“\emph{Somnium,}” said Zabini’s voice.
\sbreak
\emph{Granger: 255 / Malfoy: 252 / Potter: 254}

And Harry Potter’s body floated away, his expression of shock and horror quickly relaxing into sleep.

“On second thought,” Parvati said cheerfully, “make that Gryffindors for Sunshine.”

She started to laugh, more exhiliarated than she’d ever been in her life, she’d \emph{finally} gotten to assassinate and replace her twin sister and she’d wanted to do that since \emph{forever,} and this had been \emph{perfect,} it had all been \emph{perfect}—

—and then her wand spun around in a lightning motion just as Zabini’s wand turned to point at her.

“Wait!” said Zabini. “Do not shoot, do not resist. That’s an order.”

“\emph{What?}” said Parvati.

“Sorry,” said Zabini, looking not-quite-sincerely apologetic, “but I can’t be totally \emph{sure} you’re for Sunshine. So I order you to let me shoot you.”

“\emph{Hold on!}” said Parvati. “We’re only ahead of Chaos by one point! If you shoot me now—”

“I’ll shoot you in the name of Dragon, \emph{obviously},” said Zabini, now sounding a little superior. “Just because we tricked \emph{them} into doing it, doesn’t mean it won’t work for us.”

Parvati stared at him, her eyes narrowing. “General Malfoy said your mother doesn’t like Hermione.”

“I suppose,” said Zabini, still with that superior smirk. “But some of us are more willing than Draco Malfoy to annoy a parent.”

“And Harry Potter said you have a cousin—”

“Nope,” said Zabini.

Parvati stared at him, trying to think, but she wasn’t really good at plotting; Zabini’d said the plan was to secretly keep the scores of Chaos and Dragon as even as possible so they’d use Sunshine’s name to execute their traitors instead of losing even a single point, and that had \emph{worked}...\ but...\ she had the feeling she was missing something, she wasn’t a Slytherin...

“Why don’t \emph{I} shoot \emph{you} in the name of Dragon?” said Parvati.

“Because I outrank you,” said Zabini.

Parvati had a bad feeling about this.

She stared at him for a long moment.

And then—

“\emph{Somni—}” she started to say, and then realized she hadn’t said \emph{for Dragon,} and frantically cut herself off—
\sbreak
\emph{Granger: 255 / Malfoy: 254 / Potter: 254}

“Hey, everyone,” said Blaise Zabini’s face on the screens, looking quite amused, “guess it’s all down to me.”

All by the lakeside, people were holding their breath.

Sunshine was ahead of Dragon and Chaos by exactly one point.

Blaise Zabini could shoot himself in the name of either Dragon or Chaos, or just leave things the way they were.

A series of chimes indicated that the last minute of time was running out.

And the Slytherin was smiling a strange, twisted smile, and casually toying with his wand, the dark wood barely visible in the dark water.

“You know,” said Blaise Zabini’s voice, in the tones of someone who’d been rehearsing the words for a while, “it’s just a game, really. And games are supposed to be \emph{fun.} So how about if I just do whatever I feel like?”
