\partchapter{Self-Actualization}{VI}

\lettrine{“W}{ell,”} Daphne whispered, keeping her voice as low as she could, “at least now I don’t feel like the only sane person in Hogwarts any more.”

“Because now you’ve got the rest of us as friends?” whispered Lavender Brown, who was tiptoeing along at her left side.

“I don’t think that’s what she means,” General Granger murmured from Lavender’s own left.

They crept slowly and carefully through the corridors of Hogwarts, all eight of them keeping both ears peeled for the slightest sound of Trouble, just like it was a battle and they were looking for enemy soldiers to ambush; only in this case they were looking for bullies to Vanquish and victims to Rescue in the span between the end of breakfast-time and when Lavender and Parvati had to get to their Herbology class.

Lavender had argued that if one first-year girl could take down three older bullies, then eight first-year girls ought to be able to outfight twenty-four older bullies because of Multiplication.

Judging by her frantic spluttering and waving of hands, General Granger hadn’t found this convincing.

Padma had stayed silent for a bit during the ensuing argument, and then observed thoughtfully that even in Hogwarts, beating up first-year girls probably wouldn’t be good for your reputation as a bully.

Parvati had straightened up at this, exclaiming that this meant they were the \emph{only ones} who could do something about Hogwarts’s bully problem, which made it \emph{really truly} heroinic. Plus the \emph{whole reason} their parents had moved to Britain was so that the two of them could attend the world’s only magical school with a 0\% fatality rate, and what was the point if they didn’t take advantage and try a few things?

To which General Granger had responded that Parvati didn’t understand the point of a perfect safety record \emph{at all}—

Lavender had said that if they were \emph{really} all friends together and not Hermione’s followers like Professor Quirrell thought, then they should vote on things like this.

Daphne had known that hers would be the deciding vote after Hermione and Susan and Hannah voted no. And so Daphne had considered it carefully after her first flush of enthusiasm wore off. She \emph{was} a Slytherin, after all, and that meant it was \emph{her} responsibility to keep a watchful eye on their own interests while they were all running around trying to help people—her job to figure out how risky it really was, and whether it would be worth it for \emph{them}, just like Mother would have done in her place. Always looking out for yourself and your friends like that, was what real Slytherining was all about...

Hannah Abbott, the nervous little Hufflepuff girl, had in a small trembling voice said “Yes.”

And now Daphne and Susan and Hermione \emph{had} to stay with the other five, they couldn’t \emph{possibly} let the others go off on their own. Because no Gryffindor would ever live down hurting the last surviving child of the Bones family, and no Slytherin would dare assault a daughter of the Noble and Most Ancient House of Greengrass. (Daphne \emph{hoped} so, anyway.) And General Granger who’d started the whole thing...\ you didn’t even have to ask.

The corridors of Hogwarts passed them by one after another, their tense hands never straying far from their wands, as stone and wood and Everburning Torches came into vision and then moved past. At one point they heard footsteps and drew in their breath, hands almost dropping to their wands, but it was just a lone older Ravenclaw who looked at them curiously before sniffing and dropping his head back to his book as he walked on.

The heroines crept past solemn oaken panels carved with gilded frescos, and came to a dead end leading into a boys’ bathroom, and turned around, and wandered \emph{back} through the solemn oaken panels carved with gilded frescos, and then turned through dusty old brick corridors grouted with worn cement, which sort of led them in a circle actually, so they consulted a portrait and then went down a \emph{different} dusty old brick corridor instead, that took them to a brief rise of marble stairs that should’ve put them on the third-and-a-halfth floor if it’d been anywhere but Hogwarts, and then it was back to tiled stone pavement again, and skylights that let shafts of sunlight pour down even though they were nowhere near the roof, and after they’d followed that passageway around a few corners it took them to another boys’ bathroom, clearly marked with a plaque showing the silhouette of a robed figure whizzing into a toilet.

The eight of them stood before the closed door and stared with a certain amount of weariness.

“I’m bored,” said Lavender.

Padma made a show of taking a pocketwatch out of her robes and looking at it. “Sixteen minutes and thirty seconds,” she said. “A new record for the longest attention span in Gryffindor.”

“\emph{I} don’t think this is going to work either,” said Susan. “And I’m a \emph{Hufflepuff}.”

“Y’know,” Lavender said thoughtfully, “I wonder if maybe what \emph{really} makes someone a hero, is that when they try something like this, something interesting\emph{ actually happens}.”

“I bet you’re right,” said Tracey. “I bet if we had \emph{Harry Potter} with us, we’d run into three bullies and a hidden room full of treasure in the first five minutes. I bet that all General Chaos has to do is go to the bathroom and he, like, finds Slytherin’s Chamber of Secrets or something—”

Daphne couldn’t quite let that one go past. “You think Lord Slytherin would’ve put the entrance to the Chamber of Secrets in a \emph{bathroom—}”

“What I’m \emph{saying,}” said Susan, as Tracey was opening her mouth to reply, “is that we’ve got no way of actually \emph{finding} any bullies. I mean, all \emph{they’ve} got to do is find a Hufflepuff somewhere, but we’ve got to run across them at exactly the right \emph{time}, d’you see? Which is a \emph{very good problem} because if we \emph{did} find them we’d all get squished like bugs. Can’t we just do the forbidden third-floor corridor like we’re \emph{supposed} to?”

Lavender snorted scornfully. “You don’t become a \emph{real} heroine just by doing the forbidden things the Headmaster \emph{tells} you not to do!”

(Daphne’s mind tried to wrap around this statement as she silently thanked the Sorting Hat for not putting her anywhere near Gryffindor.)

“Come to think...” Parvati said slowly, “I mean, what’re the odds that Harry Potter would run across those five bullies on his \emph{first morning} of school? He must’ve had \emph{some} way of finding them.”

Daphne happened to be standing where looking at Parvati let her see Hermione, so she noticed the Ravenclaw girl’s expression change—and then she realized that the Sunshine General had \emph{also} found some bullies just recently—

“Oh!” said Padma in a tone of sudden realization. “Of course! He got told by the ghost of Salazar Slytherin!”

“\emph{What?}” said Daphne at the same time as several other people.

“That’s who the ghost was that scared me, I’m pretty sure,” Padma explained. “I mean I only figured it out afterward, but...\ yeah. Salazar Slytherin’s ghost doesn’t like it when Slytherins bully people, he thinks it shames his name, and the ghost is still keyed into the Hogwarts wards so he knows everything that happens, I bet.”

Daphne’s mouth was hanging open; and she saw that Hannah had put a hand to her forehead and was leaning against the stone walls, while Tracey’s eyes were blazing like little brown stars.

\emph{Salazar Slytherin’s ghost?}

Had leagued himself with \emph{Harry Potter?}

And had sent \emph{Hermione Granger} to stop Derrick’s crew?

She would have paid a hundred Galleons to be there when Draco Malfoy got told about this.

Although considering how fast rumors spread through Hogwarts, now that Padma had spilled the beans, Millicent had probably told him thirty minutes ago...

In fact...\ now that Daphne \emph{thought} about it...

“So,” said Parvati. “We’ve got to ask the Boy-Who-Lived where to find Salazar Slytherin’s ghost? Wow, I guess if I’m saying stuff like that out loud, I might actually be turning into a heroine—”

“Yes!” said Lavender. “We’ve got to ask the Boy-Who-Lived where to find Salazar Slytherin’s ghost!”

“We’ve got to ask...\ the Boy-Who-Lived...\ where to find Salazar Slytherin’s ghost...” repeated Hannah in a nervous voice, like she was forcing herself to say it.

“And if \emph{that} doesn’t work,” shouted Tracey, “we’ll stun Harry Potter, tie him up and bring him \emph{with} us!”
\sbreak
It said something, Hermione Granger thought, and it was something rather sad—as the eight of them strolled back through the maze of twisty little passages that was Hogwarts, their time before the next class having run out without finding any bullies—that she genuinely didn’t know whether Harry Potter had been led around by the ghost of Salazar Slytherin or a phoenix or \emph{what.} And whatever Harry had done, she hoped it \emph{didn’t} work for them. And most of all she hoped that the others didn’t vote for Tracey’s idea of stunning Harry Potter and carting his unconscious body around with them to attract Adventures. That couldn’t possibly work in real life, or, if it did, she was giving up.

Hermione looked from witch to witch, Tracey chatting with Lavender, and the others making occasional remarks; and her gaze caught on a girl who was subdued and quiet, the one person whose thoughts right now she couldn’t guess at all.

“Hannah?” she said to the girl walking alongside her. Hermione tried to make her voice as gentle as she could. “You don’t have to answer, but is it okay if I ask why you voted yes on fighting bullies?”

Hermione had thought she’d made her voice soft, but everyone stopped walking, and Lavender and Tracey halted their conversation and looked at them.

Hannah’s cheeks were already reddening, and just as Hannah opened her mouth—

“It’s ’cause she’s got more courage than \emph{you} think, obviously,” said Lavender.

Hannah paused with her mouth open.

She closed her mouth.

She swallowed, hard and visibly, while her cheeks reddened even further.

Then Hannah took a deep breath, and said, in a small voice, “There’s a boy I like.”

The Hufflepuff girl flinched as she said it, and her head darted around nervously to look at everyone looking at her, while the pause and silence stretched.

“Um, okay?” Susan said eventually.

“I’ve got \emph{five} boys I like,” said Lavender.

“Padma and I knew we’d both like the same boys,” said Parvati, “so we made a list and flipped a Knut to see who got to pick first.”

“I know who \emph{I’m} destined to marry,” said Tracey. “I don’t care what the world says, he’s meant to be mine!”

This made all the other girls look expectantly at Hermione, whose brain had gone ahead and flushed Tracey’s last statement entirely so it could focus on just on the first thing Hannah had said.

“Um,” said Hermione. She carefully continued keeping her voice gentle. “Hannah, the reason why you joined the Society for Promotion of Heroic Equality for Witches was that there’s a boy who might like you more if you become a hero?”

The Hufflepuff girl nodded again, her cheeks reddening even further while she stared down at her own reflection in her black-polished shoes.

“She likes Neville Longbottom, actually,” Daphne said. The Slytherin gave a woeful sigh. “And unfortunately for her, he’s going to marry someone else. It’s very tragic.”

This produced a high-pitched \emph{eeping} sound from Hannah as she went on staring at her feet.

“Wait what?” said Lavender. “Neville’s going to marry someone else? How do you know about this? \emph{Who?}”

Daphne just shook her head sadly with a downcast expression.

“\emph{Excuse me},” said Hermione, and then when the others looked at her again, “Ah...” while she tried to organize her thoughts. “I mean, um... Hannah...\ trying to become a hero so that a boy will like you isn’t very \emph{feminist}.”

“It’s pronounced \emph{feminine} actually,” said Padma.

“And why’re you calling Hannah unfeminine?” said Susan. “There’s nothing unfeminine about wanting to impress a boy.”

“Besides,” said Parvati, sounding puzzled, “isn’t the whole point that we’re trying to be heroes even though that isn’t feminine?”

The ensuing discussion would not be remembered by Hermione Granger as one of her most successful forays into the realms of political education. She tried to explain, and then after the resulting argument tried to explain again, while the other seven girls looked at her more and more skeptically. Afterward Daphne declared in the imperious tones of the future Lady Greengrass that if this feminism business meant girls weren’t allowed to pursue boys in whichever way they pleased, then feminism could stay in the Muggle lands where it belonged. Lavender suggested that maybe witchism could say that witches got to do anything they wanted, which sounded like more fun than feminism. And finally Padma closed off further discussion by observing wearily that she didn’t see much point to going on arguing, since \SPHEW wasn’t \emph{about} anything to do with feminism in the first place, it was just about more girls becoming heroes.

Hermione had given up at that point.
\sbreak
As their Charms session that day ended and the first-year Ravenclaws began shuffling out of the class, Hermione was already wincing to herself. They’d made it to class just barely before the opening gong, they’d had to run right over to their desks and sit down, so there hadn’t been time for the awful thing to happen \emph{yet;} but that just meant that Hermione got to look forward to the coming disaster for the \emph{whole class.}

Sure enough, after Professor Flitwick squeaked his dismissal and everyone rose from their chairs, Harry began walking toward her; and for her own part Hermione shoved her book into her mokeskin pouch and very quickly walked over to the door and threw it open and headed into the corridors, and of course Harry followed her with a surprised look because they had a library session scheduled—

“Hermione?” Harry said as he closed the door behind him. “What’s wrong?”

The door flew open behind Harry not a moment after he closed it, almost hitting Harry as he stepped out of the way, and Padma Patil stepped out of the classroom with a dreadful look of determination upon her face.

“Excuse me, Mr.~Potter,” came the awful words, the young girl’s high voice resounding through the corridor like the gloomy bells of doom, “can I ask you for help with something?”

Harry’s eyebrows drew up, and he said, “You can \emph{ask,} of course.”

“Can you tell us how to talk to Salazar Slytherin’s ghost? We want him to tell us where to find bullies, like he tells you.”

There was a little bit of silence in the corridor outside the classroom.

The door opened again, and Su peered out with an inquiring look—

“Well, we’ve got to get to the library,” Harry said quite casually, his face looking relaxed, “would you mind following us?” and began to walk off in the direction that led to the library on odd-numbered days of the month, and Su made like she was going to follow but Harry’s face turned toward her for a moment.

It wasn’t until Harry had rounded a corner that he drew his wand, said in a low precise voice “\emph{Quietus}” and then turned to Padma and said, “An interesting guess, Miss Patil.”

Padma looked rather smug, then; and said, “I \emph{should’ve} figured it out earlier, really. There was that \emph{hiss} in the ghost’s voice, I should’ve thought Parselmouth right away, even before he started talking about Godric Gryffindor.”

Harry’s face didn’t change. “May I ask, Miss Patil, whether you’ve shared this thought with—”

“She said it in front of everyone in \SPHEW,” Hermione said.

Harry’s eyes had that look they had when he was very rapidly calculating something, and then he said, “Hermione, what’s the chance that—”

“She said it in front of Lavender \emph{and} Tracey.”

“Um,” said Padma. “Should I not’ve done that?”
\sbreak
“Wait here,” growled Mr.~Goyle, and went around the corner; and there was the sound of him knocking on Draco Malfoy’s private room.

There was a bit of a queasy feeling in Tracey’s stomach, and she reminded herself again that since Padma had spilled the beans \emph{someone} was bound to tell Draco Malfoy, and it might as well be \emph{her}, and it wasn’t as if she \emph{owed} Harry Potter anything, and a Slytherin had to do what was necessary to achieve her Ambitions.

She’d been collecting Ambitions ever since Professor Quirrell told her off, and so far she’d decided that she wanted to own her own Nimbus 2000 broomstick, become super famous, marry Harry Potter, eat Chocolate Frogs for breakfast every day, and defeat at least \emph{three} Dark Lords just to show Professor Quirrell who was ordinary.

“Mr.~Malfoy will see you,” said the low, menacing voice of Mr.~Goyle as he returned. “And you’d better hope he doesn’t think you’re wasting his time.” The boy loomed at her briefly, and then stepped aside.

Tracey added having her own servants to her list of Ambitions, and entered.

The Malfoy private bedroom looked just like Daphne’s. She’d been privately hoping for diamond chandeliers or golden frescos on the walls—she’d never have said it in front of Daphne, but the House of Malfoy \emph{was} a step up from Greengrass. But it was just a small bedroom like Daphne’s, and the only difference was that Malfoy’s stuff was decorated in silver snakes instead of emerald plants.

As she stepped through the doorway, Draco Malfoy—who was perfectly groomed even inside his own bedroom—rose up from his desk chair to greet her with a small friendly bow, wearing a charming smile just like she was someone who \emph{mattered,} which made Tracey so flustered that she forgot everything she’d rehearsed inside her head and just blurted out, “I’ve got something to tell you!”

“Yes, Gregory said so,” Draco Malfoy said smoothly. “Please, Miss Davis, sit down.” He gestured to \emph{his own desk chair}, even as he sat down on his bed.

She felt somewhat lightheaded as she carefully sat herself down in Malfoy’s own chair, her fingers unthinkingly fiddling with how her dress robes fell across her knees, trying to make them look as elegant and uncreased as Draco Malfoy’s—

“So, Miss Davis,” said Draco Malfoy. “What did you want to tell me?”

Tracey hesitated, and then when Malfoy’s face started to look a bit impatient, just stammered it all out, everything Padma had said about Salazar Slytherin’s ghost sending Harry Potter to stop bullies and also what Daphne had told her about Hermione Granger being in on it—

Draco Malfoy’s expression didn’t change at all as she spoke, not even in the slightest, and it dawned on Tracey with a sickening lurch in her stomach.

“You don’t \emph{believe} me!” she said.

There was a slight pause.

“Well,” said Draco Malfoy, with a smile that wasn’t quite as charming as his last one, “I \emph{do} believe that’s what Padma said and what Daphne said, so thank you anyway, Miss Davis.” The boy rose from where he’d been sitting on his bed, and Tracey, not even thinking, rose from the chair.

As he was escorting her to the door, just as he was about to turn the knob, it occurred to Tracey that—“You didn’t ask what I wanted for the information,” she said.

Draco Malfoy gave her some kind of look, she didn’t quite know what it was supposed to mean, and he didn’t say anything.

“Well, anyway,” Tracey said, making an on-the-spot change to her previous Plans, “I \emph{don’t} want anything for the information, I was just being friendly.”

A brief look of surprise crossed Draco Malfoy’s face for just an instant before his expression flattened again and he said, “It’s not that easy to become friends with a Malfoy, Miss Davis.”

Tracey smiled, and meant it. “Well, I’ll just go on being friendly, then,” she said, and left the room with a skip in her step, feeling like a real Slytherin for maybe the first time in her life, and having just decided that Draco Malfoy would be one of her husbands too.
\sbreak
After the girl was gone, Gregory came in, shut the door again and said, “Are you alright, Mr.~Malfoy?”

Draco said nothing to his servant and friend. His eyes gazed off into nowhere, like he was trying to stare through the wall of his bedroom, through the Hogwarts lake that surrounded the Slytherin dungeons, through Earth’s crust and atmosphere and the interstellar dust of the Milky Way, into the utterly empty and lightless void between galaxies which no wizard and no scientist had ever seen.

“Mr.~Malfoy?” Gregory said, starting to sound a little worried.

“I can’t believe I believed every word of that,” said Draco.
\sbreak
Daphne finished her final inch of Transfiguration and looked up across the Slytherin common room, at where Millicent Bulstrode was still working on her own homework. It was time to come to a Decision.

If \SPHEW did go around trying to stun bullies, the bullies wouldn’t like it, that was certain. And they’d try to do something unpleasant about it, which was also certain. On the other hand, if the bullies got really nasty then Hermione could ask Harry Potter for help, or they could pool their combined Quirrell points and ask the Defense Professor for a favor... No, the thing that Daphne was \emph{really} worried about was if this business got them in bad with Professor Snape. You didn’t want to \emph{ever} end up on the wrong side of Professor Snape.

But since the day she’d challenged Neville to a Most Ancient Duel, she’d noticed people looking at her differently. Even the Slytherins who’d made fun of her were looking at her differently. It was dawning on Daphne that being the daughter of the Noble and Most Ancient House of Greengrass brought in a \emph{lot} more respect if you were a beautiful \emph{heroine} born to a Most Ancient House, and not just a pretty noble girl. It was the difference between having your role played by the lead actress and having your role played by a two-Galleon extra with a screechy laugh.

Fighting bullies might not be the \emph{best} way to become a heroine. But Father had once told her that the trouble with passing up opportunities was that it was habit-forming. If you told yourself you were waiting for a better opportunity next time, why, next time you’d probably tell yourself the same thing. Father had said that most people spent their whole \emph{lives} waiting for an opportunity that was good enough, and then they died. Father had said that while seizing opportunities \emph{would} mean that all sorts of things went wrong, it wasn’t nearly as bad as being a hopeless lump. Father had said that \emph{after} she got into the habit of seizing opportunities, \emph{then} it was time to start being picky about them.

On the other hand, Mother had warned her not to take all of Father’s advice, and said that Daphne wasn’t allowed to ask about Father’s sixth year in Hogwarts until she was at least thirty years old.

Still (her Mother had confessed with a sigh) in the end Father \emph{had} gotten Mother to marry him and successfully plotted his way into a Most Ancient House, so there \emph{was} that.

Millicent Bulstrode finished her homework and began putting her things away.

Daphne stood up from her desk, and walked over.

Millicent swung out her legs from the table and stood up, slinging her bookbag over one shoulder, then looked over at where Daphne was approaching, the girl’s expression puzzled.

“Hey, Millicent,” Daphne said as she drew near, making her voice low and excited, “guess what I figured out today?”

“The thing about Salazar Slytherin’s ghost helping Granger?” said Millicent. “I already heard about that—”

“No,” Daphne said in a hushed whisper, “this is even \emph{better.}”

“Really?” Millicent said, in an equally low, equally excited voice. “What is it?”

Daphne looked around conspiratorially. “Come to my room and I’ll tell you.”

They went off toward the stairs that led downward, the private rooms were even lower in the lake than the seventh-year dorms...

Soon enough Daphne was sitting in her comfy desk-chair and Millicent had bounced over to the edge of her bed.

“\emph{Quietus,}” said Daphne, when they were both seated; and then instead of putting her wand away inside her robes, Daphne just let her hand fall naturally down to her side, still holding the wand, just in case.

“All \emph{right!}” said Millicent. “What \emph{is} it?”

“You know what I figured out?” said Daphne. “I figured out that you get the gossip \emph{so} fast, you know about things \emph{before they actually happen}.”

Daphne had half-expected Millicent to turn white and fall over, and she didn’t really, but the girl did flinch pretty hard before she started stammering denials.

“Don’t worry,” said Daphne with her sweetest smile, “I won’t tell anyone else you’re a seer. I mean, we’re friends, right?”
\sbreak
Rianne Felthorne, seventh-year of Slytherin, was working diligently on yet another two-foot essay (she was taking everything except Divination and Muggle Studies and her N.E.W.T. year seemed to consist \emph{entirely} of homework) when her Head of House strode up to the table she was working at and barked “You will come with me, Miss Felthorne!” and walked away even as she frantically began putting away her parchment and book and quill.

When she caught up with Professor Snape, he was waiting just outside the room and gazing at her with half-lidded eyes that seemed far too intense; and before she could ask what this was about he spun without a word and stalked off through the hallways, so that she had to scramble to keep up.

Their walk took them down a flight of stairs, and then another, below what she’d thought was the lowest level of the Slytherin dungeons. And the corridors began to look older in their appearance, the architecture reverting back in time by centuries into roughened stone held together by crude-looking mortar. She began to wonder if Professor Snape was taking her to the \emph{real} dungeons that she’d heard rumors of, the true dungeons of Hogwarts that had been sealed off to all but faculty; and if maybe Professor Snape did terrible things down there to innocent helpless young girls but that was probably just wishful thinking on her part.

They went down another flight of stairs, and came out into a room that was no room at all, but an empty rock cavern with a single door, pierced by many dark openings and lit by a single torch of ancient style that fired as they entered.

Professor Snape took out his wand, then, and began to cast Charm after Charm, she lost track of how many; and when the Potions Master was done he turned back toward her, locked his intense eyes on hers, and said in a level voice unlike his usual drawl, “You will say nothing to anyone of this matter, Miss Felthorne, nothing now or ever. If that is acceptable to you, nod. If not, we will turn and go.”

She nodded, frightened and with a strange hope dawning in her heart (well, not exactly her heart).

“The task I have for you is very simple, Miss Felthorne,” said Professor Snape’s toneless voice, “and your extremely generous pay of fifty Galleons is merely to compensate you for being Memory-Charmed afterward.”

She drew an involuntary breath. Her family might be rich but they had other daughters and kept her on a tight leash and it was certainly a lot of money for \emph{her}.

Then her ears caught up with the words \emph{Memory-Charmed} and for a moment she felt outraged, there was no point if she couldn’t keep the memories, what sort of girl did Professor Snape think she \emph{was?}

“You surely know,” said Severus Snape, “of Miss Hermione Granger, the Sunshine General?”

“\emph{What?}” said Rianne Felthorne in sudden horror and disgust. “She’s in her \emph{first year!} \emph{Ew!}”

