\partchapter{Humanism}{I}

\lettrine{T}{he} gentle sun of January shone on the cold fields outside Hogwarts.

\quad\quad For some of the students it was a study hour, and others had been let out of class. The first-years who’d signed up for it were practicing a certain spell, a spell that was most advantageously learned outdoors, beneath the bright sun and a clear blue sky, rather than within the confines of any classroom. Cookies and lemonade were also considered helpful.

The early gestures of the spell were complex and precise; you twitched your wand once, twice, thrice, and four times with small tilts at exactly the right relative angles, you shifted your forefinger and thumb exactly the right distances...

The Ministry thought this meant it was futile to try and teach anyone the spell before their fifth year. There had been a few known cases of younger children learning it, and this had been dismissed as “genius”.

It might not have been a very polite way of putting it, but Harry was beginning to see why Professor Quirrell had claimed that the Ministry Committee of Curriculum would have been of greater benefit to wizardkind if they had been used as landfill.

So the gestures were complicated and delicate. That didn’t stop you from learning it when you were eleven. It meant you had to be extra careful and practice each part for a lot longer than usual, that was all.

Most Charms that could only be learned by older students were like that because they required more strength of magic than any young student could muster. But the Patronus Charm \emph{wasn’t} like that, it wasn’t difficult because it needed too much magic, it was difficult because it took \emph{more} than mere magic.

It took the warm, happy feelings that you kept close in your heart, the loving memories, a different kind of strength that you didn’t need for ordinary spells.

Harry twitched his wand once, twice, thrice and four times, shifted his fingers exactly the right distances...

\emph{“Good luck at school, Harry. Do you think I bought you enough books?”}

\emph{“You can never have enough books...\ but you certainly tried, it was a really, really, really good try...”}

It had brought tears to his eyes, the first time Harry had remembered and tried to put it into the spell.

Harry brought the wand up and around and brandished it, a gesture that didn’t have to be precise, only bold and defiant.

“\emph{Expecto Patronum!}” cried Harry.

Nothing happened.

Not a single flicker of light.

When Harry looked up, Remus Lupin was still studying the wand, a rather troubled look on his faintly scarred face.

Finally Remus shook his head. “I’m sorry, Harry,” the man said quietly. “Your wandwork was exactly right.”

And there wasn’t a flicker of light anywhere else, either, because all the other first-years who were supposed to be practicing their Patronus Charms had been glancing out of the corners of their eyes at Harry instead.

The tears were threatening to come back into Harry’s eyes, and they weren’t happy tears. Of all the things, of all the things, Harry had never expected this.

There was something horribly humiliating about being informed that you weren’t happy enough.

What did Anthony Goldstein have inside him that Harry didn’t, that made Anthony’s wand shine with that bright light?

Did Anthony love his own father more?

“What thought were you using to cast it?” said Remus.

“My father,” Harry said, his voice trembling. “I asked him to buy me some books before I came to Hogwarts, and he did, and they were expensive, and then he asked me if they were enough—”

Harry didn’t try to explain about the Verres family motto.

“Take a rest before you try a different thought, Harry,” said Remus. He gestured toward where some other students were sitting on the ground, looking disappointed or embarrassed or regretful. “You won’t be able to cast a Patronus Charm while you’re feeling ashamed of not being grateful enough.” There was a gentle compassion in Mr.~Lupin’s voice, and for a moment, Harry felt like hitting something.

Instead Harry turned around, and stalked to where the other failures were sitting. The other students whose wandwork had also been proclaimed perfect, and who were now supposed to be searching for happier thoughts; by the looks of them they weren’t making much progress. There were many robes there trimmed in dark blue, and a handful of red, and one lone Hufflepuff girl who was still crying. The Slytherins hadn’t even bothered showing up, except for Daphne Greengrass and Tracey Davis, who were still trying to get the gestures.

Harry plopped down on the cold dead grass of winter, next to the student whose failure had surprised him the most.

“So you couldn’t do it either,” Hermione said. She’d fled the field at first, but she’d come back after that, and you had to look closely at her reddened eyes to see that she’d been crying.

“I,” Harry said, “I, I’d probably feel a lot worse about that if you hadn’t failed, you’re the nicest, person I know, that I’ve ever met, Hermione, and if \emph{you} also can’t do it, it means I might still be, be good...”

“I should have gone to Gryffindor,” Hermione whispered. She blinked hard a few times, but she didn’t wipe her eyes.
\sbreak
The boy and the girl walked forward together, definitely not holding hands, but each drawing a kind of strength from the other’s presence, something that let them ignore the whispers of their year-mates, as they walked through the hallway approaching the great doors of Hogwarts.

Harry hadn’t been able to cast the Patronus Charm no matter what happy thought he tried. People hadn’t seemed surprised by that, which made it even worse. Hermione hadn’t been able to do it either. People had been \emph{very} surprised by that, and Harry had seen her starting to get the same sidelong looks as him. The other Ravenclaws who’d failed weren’t getting those looks. But Hermione was the Sunshine General, and her fans were treating it like she’d failed them, somehow, like she’d betrayed a promise she’d never made.

The two of them had gone to the library to research the Patronus Charm, which was Hermione’s way of dealing with distress, as it was sometimes also Harry’s. Study, learn, try to understand \emph{why...}

The books had confirmed what the Headmaster had told Harry; often, wizards who couldn’t cast the Patronus Charm in practice would be able to do so in the presence of a real Dementor, going from flat failure all the way to a full corporeal Patronus. It defied all logic, the Dementor’s aura of fear ought to make it \emph{harder} to wield a happy thought; but that was the way it was.

So the two of them were both going to give it one last try, there was no way either of them wouldn’t give it one last try.

It was the day the Dementor came to Hogwarts.

Earlier, Harry had unTransfigured his father’s rock from where it usually rested on his pinky ring in the form of a tiny diamond, and placed the huge gray stone back into his pouch. Just in case Harry’s magic failed entirely, when he confronted the darkest of all creatures.

Harry had already started to feel pessimistic, and he wasn’t even in front of a Dementor yet.

“I bet you can do it and I can’t,” Harry said in a whisper. “I bet that’s what happens.”

“It felt wrong to me,” Hermione said, her voice even quieter than his. “I tried it this morning and I realized. When I was doing the brandish at the end, even before I said the words, it felt wrong.”

Harry didn’t say anything. He’d felt the same thing, right from the start, though it had taken another five attempts using five other happy thoughts before he’d been able to acknowledge it to himself. Every time he tried to brandish his wand, it had felt hollow; the spell he was trying to learn didn’t fit him.

“It doesn’t mean we’re going to be Dark Wizards,” said Harry. “Lots of people who can’t cast the Patronus Charm aren’t Dark Wizards. Godric Gryffindor wasn’t a Dark Wizard...”

Godric had defeated Dark Lords, fought to protect commoners from Noble Houses and Muggles from wizards. He’d had many fine friends and true, and lost no more than half of them in one good cause or another. He’d listened to the screams of the wounded, in the armies he’d raised to defend the innocent; young wizards of courage had rallied to his calls, and he’d buried them afterward. Until finally, when his wizardry had only just begun to fail him in his old age, he’d brought together the three other most powerful wizards of his era to raise Hogwarts from the bare ground; the one great accomplishment to Godric’s name that wasn’t about war, any kind of war, no matter how just. It was Salazar, and not Godric, who’d taught the first Hogwarts class in Battle Magic. Godric had taught the first Hogwarts class in Herbology, the magics of green growing life.

To his last day he’d never been able to cast the Patronus Charm.

Godric Gryffindor had been a good man, not a happy one.

Harry didn’t believe in angst, he couldn’t stand reading about whiny heroes, he knew a billion other people in the world would have given anything to trade places with him, and...

And on his deathbed, Godric had told Helga (for Salazar had abandoned him, and Rowena passed before) that he didn’t regret any of it, and he was \emph{not} warning his students not to follow in his footsteps, no one was \emph{ever} to say he’d told anyone not to follow in his footsteps. If it had been the right thing for \emph{him} to do, then he wouldn’t tell anyone else to choose wrongly, not even the youngest student in Hogwarts. And yet for those who \emph{did} follow in his footsteps, he hoped they would remember that Gryffindor had told his House that it was all right for them to be happier than him. That red and gold would be bright warm colors, from now on.

And Helga had promised him, weeping, that when she was Headmistress she would make sure of it.

Whereupon Godric had died, and left no ghost behind him; and Harry had shoved the book back to Hermione and walked away a little, so she wouldn’t see him crying.

You wouldn’t think that a book with an innocent title like “The Patronus Charm: Wizards Who Could and Couldn’t” would be the saddest book Harry had ever read.

Harry...

Harry didn’t want that.

To be in that book.

Harry didn’t want that.

The rest of the school just seemed to think that \emph{No Patronus} meant \emph{Bad Person,} plain and simple. Somehow the fact that Godric Gryffindor also hadn’t been able to cast the Patronus Charm seemed not to get repeated. Maybe people didn’t talk about it to respect his last wish, Fred and George probably didn’t know and Harry certainly wasn’t about to tell them. Or maybe the other failures didn’t mention it because it was less shameful, the smaller loss of pride and status, to be thought Dark rather than unhappy.

Harry saw that Hermione, beside him, was blinking hard; and he wondered if she was thinking of Rowena Ravenclaw, who’d also loved books.

“Okay,” Harry whispered. “Happier thoughts. If you do go to a full corporeal Patronus, what do you think your animal will be?”

“An otter,” Hermione said at once.

“An \emph{otter?}” Harry whispered incredulously.

“Yes, an otter,” said Hermione. “What about yours?”

“Peregrine falcon,” Harry said without hesitation. “It can dive faster than three hundred kilometers per hour, it’s the fastest living creature there is.” The peregrine falcon had been Harry’s favorite animal since forever. Harry was determined to become an Animagus someday, just to get that as his form, and fly by the strength of his own wings, and see the land below with sharper eyes... “But why an \emph{otter?}”

Hermione smiled, but didn’t say anything.

And the vast doors of Hogwarts swung open.

They walked for a time, the children, over a pathway that led toward the unforbidden forest, and continued through the forest itself. The Sun was lowering to near the horizon, the shadows long, the sunlight filtered through the bare branches of the winter trees; for it was January, and the first-years the last to learn, that day.

Then the path swerved and took a new direction, and they all saw it in the distance, the clearing in the forest, and the sere winter grounds, yellowing dried grass whitened by a few small remnants of snow.

The human figures still small at that range. The two spots of dim white light from the Aurors’ Patronuses, and the brighter spot of silver light from the Headmaster’s, next to something...

Harry squinted.

Something...

It must have been purely Harry’s imagination, because there shouldn’t have been any way for a Dementor to reach past three corporeal Patronuses, but he thought he could feel a touch of emptiness brushing at his mind, brushing straight at the soft inner center of himself without any respect for Occlumency barriers.
\sbreak
Seamus Finnigan was ashen and trembling as he rejoined the students milling about on the withered and snow-spotted grass. Seamus’s Patronus Charm had been successful, but there was still that interval between when the Headmaster dispelled his own Patronus and when you were supposed to cast your own, when you faced the Dementor’s fear unshielded.

Up to twenty seconds of exposure at five paces was certainly safe, even for an eleven-year-old wizard with weak resistance and a still-maturing brain. There was a lot of variance in how hard the Dementor’s power hit people, which was another thing not quite understood; but twenty seconds was definitely safe.

Forty seconds of Dementor exposure at five paces might \emph{possibly} have been enough to cause permanent damage, though only to the most sensitive subjects.

It was harsh training even by the standards of Hogwarts, where the way you learned to fly on a hippogriff was by being tossed on one and told to get going. Harry was no fan of overprotectiveness, and if you looked at the difference in maturity between a fourth-year in Hogwarts and a fourteen-year-old Muggle, it was clear that Muggles were smothering their children...\ but even Harry had started to wonder if this was pushing it. Not every hurt could be healed afterward.

But if you couldn’t cast the spell under those conditions, it meant you couldn’t rely on using the Patronus Charm to defend yourself; overconfidence was even more dangerous to wizards than to Muggles. Dementors could drain your magic and your physical vitality, not just your happy thoughts, which meant you might \emph{not} be able to Apparate away if you waited too long, or if you didn’t recognize the approaching fear until the Dementor was within range for its attack. (During his reading, Harry had discovered with considerable horror that some books claimed the Dementor’s Kiss would \emph{eat your soul} and that this was the reason for the permanent mindless coma into which it put the victims. And that wizards who \emph{believed this} had deliberately used the Dementor’s Kiss to \emph{execute criminals.} It was a certainty that some called criminals were innocent, and even if they weren’t, \emph{destroying their souls?} If Harry had believed in souls, he would have...\ drawn a blank, he just couldn’t think of an appropriate response to that.)

The Headmaster was taking security seriously, and so were the three Aurors standing guard. Their leader was an Asianish-looking man, solemn without being grim, Auror Komodo, whose wand never left his hand. His Patronus, an orangutan of solid moonlight, paced back and forth between the Dementor and the first-years awaiting their turn; beside the orangutan moved the bright white panther of Auror Butnaru, a man with a piercing gaze, long black hair in a ponytail, and a long braided goatee. Those two Aurors, and their two Patronuses, were all watching the Dementor. On the opposite side of the students was the resting Auror Goryanof, tall and thin and pale and unshaven, sitting back on a chair he’d conjured without word or wand, and maintaining an absentminded pokerface as he scanned the entire scene. Professor Quirrell had shown up not long after the first-years began their attempts, and his eyes never strayed far from Harry. The tiny Professor Flitwick, who had been a champion duellist, was fiddling absently with his wand; and \emph{his} eyes, peering out from within the huge puffy beard that served as his face, stayed focused on Professor Quirrell.

And it must have been Harry’s imagination, but Professor Quirrell seemed to wince slightly each time the Headmaster’s Patronus winked out to test the next student. Maybe Professor Quirrell was imagining the same placebo effect as Harry, that backwash of emptiness caressing at his mind.

“Anthony Goldstein,” called the voice of the Headmaster.

Harry quietly walked toward Seamus, even as Anthony began to approach the shining silver phoenix, and...\ whatever it was beneath the tattered cloak.

“What did you see?” Harry asked Seamus in a low voice.

A lot of students hadn’t answered Harry, when he’d tried to gather the data; but Seamus was Finnigan of Chaos, one of Harry’s lieutenants. Maybe that wasn’t fair, but...

“Dead,” said Seamus in a whisper, “grayish and slimy...\ dead and left in water for a while... “

Harry nodded. “That’s what a lot of people see,” Harry said. He projected confidence, even though it was fake, because Seamus needed it. “Go eat some chocolate, you’ll feel better.”

Seamus nodded and stumbled off toward the table of healing sweets.

“\emph{Expecto Patronum!}” cried a young boy’s voice.

Then there were gasps of shock, even from the Aurors.

Harry spun around to look—

There was a brilliant silver bird standing between Anthony Goldstein and the cage. The bird reared its head and let out a cry, and the cry was also silver, as bright and hard and beautiful as metal.

And something in the back of Harry’s mind said, \emph{if that’s a peregrine falcon, I’m going to strangle him in his sleep.}

\emph{Shut up,} Harry said to the thought, \emph{do you want us to be a Dark Wizard?}

\emph{What’s the point? You’re going to end up as one eventually.}

That...\ wasn’t something Harry would usually have thought...

\emph{It’s a placebo effect,} Harry told himself again. \emph{The Dementor can’t actually get to me through three corporeal Patronuses, I’m just imagining what I think it’s like. When I actually face the Dementor, it’ll feel completely different, and then I’ll know I was just being silly before.}

A slight chill went down Harry’s spine then, because he had a feeling that yes, it \emph{would} be completely different, and not in a positive direction.

The blazing silver phoenix sprang back into existence from the Headmaster’s wand, the lesser bird vanished; and Anthony Goldstein began to walk back.

The Headmaster was coming with Anthony instead of calling out the next name, the Patronus waiting behind to guard the Dementor.

Harry glanced over to where Hermione was standing, just behind the glowing panther. Hermione’s turn would have come next, but had apparently just been delayed.

She looked stressed.

Earlier, she’d politely asked Harry to please stop trying to destress her.

Dumbledore was smiling slightly as he escorted Anthony back toward the others; smiling only slightly, because the Headmaster looked very, very tired.

“Unbelievable,” said Dumbledore in a voice that sounded much weaker than his accustomed boom. “A corporeal Patronus, in his first year. And an astounding number of successes among the other young students. Quirinus, I must acknowledge that you have proved your point.”

Professor Quirrell inclined his head. “A simple enough guess, I should think. A Dementor attacks through fear, and children are less afraid.”

“\emph{Less} afraid?” said Auror Goryanof from where he was sitting.

“So I said as well,” said Dumbledore. “And Professor Quirrell pointed out that adults had more courage, not less to fear; which thought, I confess, had never occurred to me before.”

“That was not my \emph{precise} phrasing,” Professor Quirrell said dryly, “but it will do. And the rest of our agreement, Headmaster?”

Dumbledore looked wry, for a moment. “As you say. I admit I was not expecting to lose that bet, Quirinus, but you have proven your wisdom.”

All the students were looking at them, puzzled; except Hermione, who was staring in the direction of the cage and the tall decaying robes; and Harry, who was watching everyone, since he was imagining himself feeling paranoid.

Professor Quirrell said, in tones that did not invite further comments, “I am allowed to teach the Killing Curse to students who wish to learn it. Which will render them considerably safer from Dark Wizards and other pests, and it is foolish to think they will otherwise know no deadly magics.” Professor Quirrell paused, his eyes narrowing. “Headmaster, I respectfully observe that you are not looking well. I suggest leaving the remainder of the day’s task to Professor Flitwick.”

Dumbledore shook his head. “We are almost done for the day, Quirinus. I will last.”

Hermione had approached Anthony. “Captain Goldstein,” she said, and her voice trembled only a little, “can you give me any advice?”

“Don’t be afraid,” Anthony said firmly. “Don’t think about anything it tries to make you think about. You’re not just holding up the wand in front of you as a shield against the fear, you’re \emph{brandishing} your wand to drive the fear away, that’s how you make a happy thought into something solid...” Anthony shrugged helplessly. “I mean, I \emph{heard} all that before, but...”

Other students were starting to congregate around Anthony, with their own questions.

“Miss Granger?” the Headmaster said. His voice might have been gentle, or just weakened.

Hermione straightened her shoulders, and followed him.

“What did you see under the cloak?” Harry said to Anthony.

Anthony looked at Harry, surprised, and then answered, “A very tall man who was dead, I mean, sort of dead-shaped and dead-colored...\ it hurt to see him and I knew that was the Dementor trying to get at me.”

Harry looked back out at where Hermione was confronting the cage and the cloak.

Hermione raised her wand into position for the first gestures.

The Headmaster’s phoenix winked out of existence.

And Hermione gave a tiny, pathetic shriek, flinched—

—took a step back, Harry could see her wand moving, and then she brandished it and said “Expecto Patronum!”

Nothing happened.

Hermione turned and ran.

“\emph{Expecto Patronum!}” said the Headmaster’s deeper voice, and the silver phoenix blazed back to life.

The young girl stumbled, and kept running, strange sounds beginning to come from her throat.

“\emph{Hermione!}” Susan yelled it, and Hannah, and Daphne, and Ernie, and they all started to run toward her; even as Harry, who was always thinking one step ahead, spun on his own heel and ran for the table with the chocolate.

Even after Harry had shoved the chocolate into Hermione’s mouth and she’d chewed and swallowed, she was still breathing in great gasps and crying, her eyes still seemed unfocused.

\emph{She can’t have been permanently Demented,} Harry thought desperately at the confusion inside him, the horrible fear and deathly fury beginning to twist around each other, \emph{she can’t have been, she wasn’t exposed for even ten seconds let alone forty—}

But she could be \emph{temporarily} Demented, as Harry realized in that moment, there wasn’t any rule that you couldn’t be \emph{temporarily} injured by a Dementor in just ten seconds if you were sensitive enough.

Then Hermione’s eyes seemed to focus, and dart around, and settle on him.

“Harry,” she gasped, and the other students went silent. “Harry, don’t. \emph{Don’t!}”

Harry was suddenly afraid to ask what he shouldn’t do, was \emph{he} in her worst memories, or some sleep’s nightmare that she was now reliving in waking life?

“\emph{Don’t go near it!”} said Hermione. Her hand reached out, grabbed him by the lapel of his robes. “You mustn’t go near it, Harry! \emph{It spoke to me, Harry, it knows you, it knows you’re here!}”

“What—” Harry said, and then cursed himself for asking.

“\emph{The Dementor!}” said Hermione. Her voice rose to a shriek. “\emph{Professor Quirrell wants it to eat you!}”

In the sudden hush, Professor Quirrell came forward a few steps; but he didn’t approach any closer (Harry was there, after all). “Miss Granger,” he said, and his voice was grave, “I think you should have some more chocolate.”

“\emph{Professor Flitwick, don’t let Harry try, send him back!}”

The Headmaster had arrived by then, and he and Professor Flitwick were exchanging worried looks.

“I did not hear the Dementor speak,” the Headmaster said. “Still...”

“Just ask,” said Professor Quirrell, sounding a little weary.

“Did the Dementor say \emph{how} it would get to Harry?” said the Headmaster.

“All his tastiest parts first,” said Hermione, “it would—it would eat—”

Hermione blinked. Some sanity seemed to come back into her eyes.

Then she started crying.

“You were too brave, Hermione Granger,” the Headmaster said. His voice was gentle, and clearly audible. “Too much braver than I comprehended. You should have turned and run, not endured and tried to complete your Charm. When you are older and stronger, Miss Granger, I know that you will try again, and I know that you will succeed.”

“I’m sorry,” Hermione said in gasps, “I’m sorry, I’m sorry, I’m sorry... I’m sorry, Harry, I can’t tell you what I saw, I didn’t look at it, I didn’t dare look at it, I knew it was too horrible to ever be seen...”

It should have been Harry, but he’d hesitated, because his hands were all chocolatey; and then Ernie and Susan were there, helping Hermione from where she’d fallen on the grass, leading her toward the snacks table.

Five bars of chocolate later, Hermione seemed to be all right again, and she went over and apologized to Professor Quirrell; but she was always watching Harry, every time that he glanced in her direction. He’d stepped toward her only once, and stopped when she’d stepped away. Her eyes had silently apologized, and silently pleaded for him to leave her be.
\sbreak
Neville Longbottom had seen something dead and half-dissolved, oozing and running with a face like a squashed sponge.

It was the worst thing anyone had yet described seeing. Neville had been able to produce a small flicker of light from his wand before, but he had, intelligently and with great presence of mind, turned and run away instead of trying to cast his own Patronus Charm.

(The Headmaster had said nothing to the other students, told no one else to be less brave; but Professor Quirrell had calmly observed that if you made the mistake \emph{after} being warned, that was when ignorance became stupidity.)

“Professor Quirrell?” Harry said in a low voice, having come as close to the Defense Professor as he dared. “What do \emph{you} see when you—”

“Don’t ask.” The voice was very flat.

Harry nodded respectfully. “What was your \emph{original} phrasing to the Headmaster, if I can ask?”

Dryly. “Our worst memories can only grow worse as we grow older.”

“Ah,” Harry said. “Logical.”

Something strange flickered in Professor Quirrell’s eyes, then, as he looked at Harry. “Let us hope,” Professor Quirrell said, “that you succeed upon this try, Mr.~Potter. For if you do, the Headmaster may teach you his trick of using a Patronus to send messages that cannot be forged or intercepted, and the military importance of that is impossible to overstate. It would be a tremendous advantage to the Chaos Legion, and someday, I suspect, this entire country. But if you do \emph{not} succeed, Mr.~Potter...\ well, \emph{I} shall understand.”
\sbreak
Padma Patil had said, in a wavering voice, “Ouch”; she hadn’t screamed or run, and Dumbledore had recast his Patronus right away.

Parvati Patil had produced a corporeal Patronus in the form of a tiger, larger than Dumbledore’s phoenix, though not nearly as bright. There had been a great burst of applause from all the watchers, though not the same shock as when Anthony had done it.

And then it was Harry’s turn.

The Headmaster called the name of Harry Potter, and Harry was afraid.

Harry knew, he knew that he was going to fail, and he knew that it was going to hurt.

But he still had to try; because sometimes, in the presence of a Dementor, a wizard went from not a flicker of light to a full corporeal Patronus, and no one understood why.

And because if Harry \emph{couldn’t} defend himself from Dementors, he had to be able to recognize their approach, recognize the feeling of them in his mind, and run before it was too late.

\emph{What is my worst memory...?}

Harry had expected the Headmaster to give him a worried look, or a hopeful look, or deeply wise advice; but instead Albus Dumbledore only watched him with quiet calm.

\emph{He thinks I’m going to fail, but he won’t sabotage me by telling me so,} thought Harry, \emph{if he had true words of encouragement to speak, he would speak them...}

The cage came closer. It was already tarnished, but not rusted away to nothing, not yet.

The cloak came closer. It was unraveling and shot through with unpatched holes; it had been new that morning, Auror Goryanof had said.

“Headmaster?” Harry said. “What do you see?”

The Headmaster’s voice was also calm. “The Dementors are creatures of fear, and as your fear of the Dementor diminishes, so does the fearsomeness of its form. I see a tall, thin, naked man. He is not decaying. He is only slightly painful to look upon. That is all. What do you see, Harry?”

...Harry couldn’t see under the cloak.

Or that wasn’t right, it was that his mind was \emph{refusing} to see what was under the cloak...

No, his mind was trying to see the \emph{wrong} thing under the cloak, Harry could feel it, his eyes trying to force a mistake. But Harry had done his best to train himself to notice that tiny feeling of confusion, to automatically flinch away from making stuff up; and every time his mind tried to start inventing a lie about what was under the cloak, that reflex was fast enough to shut it down.

Harry looked under the cloak and saw...

An open question. Harry wouldn’t let his mind see something false, and so he didn’t see anything, like the part of his visual cortex getting that signal was just ceasing to exist. There was a blind spot under the cloak. Harry couldn’t know what was under there.

Just that it was far worse than any decaying mummy.

The unseeable horror beneath the cloak was very close, now, but the blazing bird of moonlight, the white phoenix, yet lay between them.

Harry wanted to run away like some of the other students had. Half the ones who’d had no luck with their Patronus Charms just hadn’t shown up today in the first place. Of those remaining, half had fled before the Headmaster had even dispelled his own Patronus, and no one had said a word. There’d been a little laughter when Terry had turned and walked back before his own try; and Susan and Hannah, who’d gone before, had yelled at everyone to shut up.

But Harry was the Boy-Who-Lived, and he would lose much respect if he was seen to give up without even trying...

Pride and roles seemed to diminish and fall away, in the presence of whatever lay beneath the cloak.

\emph{Why am I still here?}

It wasn’t the shame of others thinking him cowardly, that kept Harry’s feet in place.

It wasn’t the hope of repairing his reputation that brought up his wand.

It wasn’t the desire to master the Patronus Charm as magic, that moved his fingers into the initial position.

It was something else, something that \emph{had} to oppose whatever lay beneath the cloak, this was the true darkness and Harry had to find out whether it lay within him, the power to drive it back.

Harry had planned to try one final time to think of his book-shopping spree with his father, but instead, at the last minute, facing the Dementor, a different memory occurred to him, something he hadn’t tried before; a thought that wasn’t warm and happy in the ordinary way, but felt righter, somehow.

And Harry remembered the stars, remembered them burning terribly bright and unwavering in the Silent Night; he let that image fill him, fill all of him like an Occlumency barrier across his entire mind, became once again the bodiless awareness of the void.

The bright silver shining phoenix vanished.

And the Dementor smashed into his mind like the fist of God.

\headline{Fear / Cold / Darkness}

There was an instant when the two forces clashed head-on, when the peaceful starlit memory held its own against the fear, even as Harry’s fingers began the wand motions, practiced until they had become automatic. They weren’t warm and happy, those blazing points of light in perfect blackness; but it was an image the Dementor could not easily pierce. For the silent burning stars were vast and unafraid, and to shine in the cold and darkness was their natural state.

But there was a flaw, a crack, a fault-line in the immovable object trying to resist that irresistible force. Harry felt a twinge of anger at the Dementor for trying to feed on him, and it was like slipping on wet ice. Harry’s mind began to slide sideways, into bitterness, black fury, deathly hatred—

Harry’s wand came up in the final brandish.

It felt wrong.

“Expecto Patronum,” his voice spoke, the words hollow and pointless.

And Harry fell into his dark side, fell down into his dark side, further and faster and deeper than ever before, down down down as the slide accelerated, as the Dementor latched onto the exposed and vulnerable parts and fed on them, eating away the light. A fading reflex scrabbled for warmth, but even as an image of Hermione came to him, or an image of Mum and Dad, the Dementor twisted it, showed him Hermione lying dead on the ground, the corpses of his mother and father, and then even that was sucked away.

Into the vacuum rose the memory, the worst memory, something forgotten so long ago that the neural patterns shouldn’t have still existed.

\emph{“Lily, take Harry and go! It’s him!” shouted a man’s voice. “Go! Run! I’ll hold him off!”}

\emph{And Harry couldn’t help but think, in the empty depths of his dark side, how ridiculously overconfident James Potter had been. Hold off Lord Voldemort? With what?}

\emph{Then the other voice spoke, high-pitched like the hiss of a teakettle, and it was like dry ice laid on Harry’s every nerve, like a brand of metal cooled to liquid helium temperatures and laid on every part of him. And the voice said:}

\emph{“Avadakedavra.”}

(The wand flew from the boy’s nerveless fingers as his body began to convulse and fall, the Headmaster’s eyes widening in alarm as he began his own Patronus Charm.)

\emph{“Not Harry, not Harry, please not Harry!” screamed the woman’s voice.}

\emph{Whatever was left of Harry listened with all the light drained out of him, in the dead void of his heart, and wondered if she thought that Lord Voldemort would stop because she asked politely.}

\emph{“Step aside, woman!” said the shrill voice of burning cold. “For you I am not come, only the boy.”}

\emph{“Not Harry! Please...\ have mercy...\ have mercy...”}

\emph{Lily Potter, Harry thought, seemed not to understand what type of people became Dark Lords in the first place; and if this was the best strategy she could conceive to save her child’s life, that was her final failure as a mother.}

\emph{“I give you this rare chance to flee,” said the shrill voice. “But I will not trouble myself to subdue you, and your death here will not save your child. Step aside, foolish woman, if you have any sense in you at all!”}

\emph{“Not Harry, please no, take me, kill me instead!”}

\emph{The empty thing that was Harry wondered if Lily Potter seriously imagined that Lord Voldemort would say yes, kill her, and then depart leaving her son unharmed.}

\emph{“Very well,” said the voice of death, now sounding coldly amused, “I accept the bargain. Yourself to die, and the child to live. Now drop your wand so that I can murder you.”}

\emph{There was a hideous silence.}

\emph{Lord Voldemort began to laugh, horrible contemptuous laughter.}

\emph{And then, at last, Lily Potter’s voice shrieked in desperate hate, “Avada ke—”}

\emph{The lethal voice finished first, the curse rapid and precise.}

\emph{“Avadakedavra.”}

\emph{A blinding flare of green marked the end of Lily Potter.}

\emph{And the boy in the crib saw it, the eyes, those two crimson eyes, seeming to glow bright red, to blaze like miniature suns, filling Harry’s whole vision as they locked to his own—}
\sbreak
The other children saw Harry Potter fall, they heard Harry Potter scream, a thin high-pitched scream that seemed to pierce their ears like knives.

There was a brilliant silver flash as the Headmaster bellowed “\emph{Expecto Patronum!}” and the blazing phoenix returned to being.

But Harry Potter’s horrible scream went on and on and on, even as the Headmaster scooped up the boy in his arms and bore him away from the Dementor, even as Neville Longbottom and Professor Flitwick both went for the chocolate at the same time and—

Hermione knew it, she knew it as she saw it, she knew that her nightmare had been real, it was coming true, somehow it was coming true.

“Get him chocolate!” demanded the voice of Professor Quirrell, pointlessly, because Professor Flitwick’s tiny form was already cannonballing toward where the Headmaster was racing toward the students.

Hermione was moving forward herself, though she didn’t know what else she meant to do—

“\emph{Cast Patronuses!}” shouted the Headmaster, as he brought Harry behind the Aurors. “\emph{Everyone who can! Get them between Harry and the Dementor! It’s still feeding on him!}”

There was a moment of frozen horror.

“\emph{Expecto Patronum!}” shouted Professor Flitwick and Auror Goryanof, and then Anthony Goldstein, but he failed the first time, and then Parvati Patil, who succeeded, and then Anthony tried again and his silver bird spread its wings and screamed at the Dementor, and Dean Thomas roared the words like they had been written in letters of fire and his wand gave birth to a towering white bear; there were eight blazing Patronuses all in a line between Harry and the Dementor, and Harry went on screaming and screaming as the Headmaster laid him on the dried grass.

Hermione couldn’t cast a Patronus Charm, so she ran toward where Harry lay. In her mind, something tried to guess how long it had been already. Was it twenty seconds? More?

There was a dreadful agony and bewilderment on the face of Albus Dumbledore. His long black wand was in his hand, but he spoke no spells, only looked down at Harry’s convulsing body in horror—

Hermione didn’t know what to do, she didn’t know what to do, she didn’t understand what was happening, and the most powerful wizard in the world seemed equally at a loss.

“\emph{Use your phoenix!}” bellowed Professor Quirrell. “\emph{Take him far away from that Dementor!}”

Without a single word the Headmaster scooped up Harry in his arms and vanished in a crack of fire along with the suddenly appearing Fawkes; and the Headmaster’s Patronus winked out, where it had guarded the Dementor.

Horror and confusion and sudden babble.

“Mr.~Potter should recover,” Professor Quirrell said, raising his voice, but his tone now calm once again, “I think it was just over twenty seconds.”

Then the blazing white phoenix appeared again, like it was flying before them from elsewhere, to Hermione Granger came the creature of moonlight, and it cried to her in Albus Dumbledore’s voice:

“\emph{It still feeds on him, even here! How? If you know, Hermione Granger, you must tell me! Tell me!}”

The senior Auror turned to stare at her, and so did many students. Professor Flitwick didn’t turn, he was now leveling his wand on Professor Quirrell, who was holding out clearly empty hands.

Seconds ticked past, uncounted.

She couldn’t remember it, she couldn’t remember the nightmare clearly, she couldn’t remember why she had thought it was possible, why she had been afraid—

Hermione realized then what she ought to do, and it was the hardest decision of her life.

What if whatever had happened to Harry, happened to her too?

All her limbs cold as death, her vision gone dark, fear overwhelming everything; she’d seen Harry dying, Mum and Dad dying, all her friends dying, everyone dying, so that in the end, when she died, she would be alone. That was her secret nightmare she’d never talked about with anyone, that had given the Dementor its power over her, the loneliest thing was to die alone.

She didn’t want to go to that place again, she, she didn’t, she didn’t want to stay there forever—

\emph{You have courage enough for Gryffindor,} said the calm voice of the Sorting Hat in her memory, \emph{but you will do what is right in any House I give you. You will learn, you will stand by your friends, in any House you choose. So don’t be afraid, Hermione Granger, just decide where you belong...}

There was no time for deciding, Harry was dying.

“I can’t remember now,” said Hermione, her voice cracking, “but just hold on, I’ll go in front of the Dementor again...”

She started to run toward the Dementor.

“Miss Granger!” squeaked Professor Flitwick, but he made no move to stop her, only kept holding his wand on Professor Quirrell.

“\emph{Everyone!}” shouted Auror Komodo in a voice of military command. “\emph{Get your Patronuses out of her way!}”

“\shout{Flitwick!}” roared Professor Quirrell. “\shout{Summon Potter’s wand!}”

Even as Hermione understood, Professor Flitwick was already crying “\emph{Accio!}”, and she saw the stick of wood zooming up from where it had lain almost touching the Dementor’s cage.
\sbreak
The eyes opened, dead and vacant.

“\emph{Harry!}” gasped a voice in the colorless world. “\emph{Harry! Speak to me!}”

The face of Albus Dumbledore leaned over into the field of vision, which had been occupied by a distant marble ceiling.

“You’re annoying,” said the empty voice. “You should die.”

