\partchapter{The Stanford Prison Experiment}{XII}

\lettrine{M}{inerva} gazed up at the clock, the golden hands and silver numerals, the jerking motion. Muggles had invented that, and until they had, wizards had not bothered keeping time. Bells, timed by a sanded hourglass, had served Hogwarts for its classes when it was built. It was one of the things that blood purists wished not to be true, and therefore Minerva knew it.

She had received an Outstanding on her Muggle Studies \abbrev{N.E.W.T.}, which now seemed to her a mark of shame, considering how little she knew. Her younger self had realized, even then, that the class was a sham, taught by a pureblood, supposedly because Muggleborns could not appreciate what wizardborns needed to be told, and actually because the Board of Governors did not approve of Muggles at all. But when she was seventeen the Outstanding grade had been the main thing that mattered to her, she was saddened to remember...

\emph{If Harry Potter and Voldemort fight their war with Muggle weapons there will be nothing left of the world but fire!}

She couldn’t imagine it, and the reason she couldn’t imagine it was that she couldn’t imagine Harry fighting You-Know-Who.

She had encountered the Dark Lord four times and survived each one, three times with Albus to shield her and once with Moody at her side. She remembered the damaged, snakelike face, the faint green scales scattered over the skin, the glowing red eyes, the voice that laughed in a high-pitched hiss and promised nothing but cruelty and torment: the monster pure and complete.

And Harry Potter was easy to picture in her mind, the bright expression on the face of a young boy who wavered between taking the ludicrous seriously and taking the serious ludicrously.

And to think of the two of them facing off at wandpoint was too painful to be imagined.

They had no right, no right at all to set this on an eleven-year-old boy. She knew what the Headmaster had decided for him this day, for she had been told to make the arrangements; and if it had been her at the same age she would have raged and screamed and cried and been inconsolable for weeks, and...

\emph{He is no ordinary first-year,} Albus had said. \emph{He is marked as the Dark Lord’s equal, and he has power the Dark Lord knows not.}

The terrible hollow voice booming from Sybill Trelawney’s throat, the true and original prophecy, echoed once more through her mind. She had a feeling it didn’t mean what the Headmaster thought it did, but there was no way to put the difference into words.

And even so it still seemed true, that if there were any eleven-year-old within the Earth entire who could bear this burden, that boy approached her office now. And if she said anything at all like ‘poor Harry’ to his face...\ well, he wouldn’t like it.

\emph{So now I’ve got to find some way to kill an immortal Dark Wizard,} Harry had said on the day he had first learned.\emph{ I really wish you had told me that before I started shopping...}

She’d been Head of House Gryffindor for long enough, she’d watched enough friends die, to know that there were some people you couldn’t save from becoming heroes.

There came a knock at the door, and Professor McGonagall said, “Enter.”

When Harry entered, his face had the same cold, alert look she’d seen in Mary’s Place; and she wondered for an instant if he’d been wearing that same mask, that same self, this whole day.

The young boy seated himself on the chair before her desk, and said, “So is it time for me to be told what’s going on?” Neutral the words, not the sharpness that should have gone with the expression.

Professor McGonagall’s eyes rose in surprise before she could stop them, and she said, “The Headmaster told you nothing, Mr.~Potter?”

The boy shook his head. “Only that he’d received a warning that I might be in danger, but I was safe now.”

Minerva was having trouble meeting his gaze. How could they \emph{do} this to him, how could they lay this upon an eleven-year-old boy, this war, this destiny, this prophecy...\ and they didn’t even \emph{trust} him...

She forced herself to look at Harry directly, and saw that his green eyes were calm as they rested on her.

“Professor McGonagall?” the boy said quietly.

“Mr.~Potter,” said Professor McGonagall, “I’m afraid it is not my place to explain, but if after this the Headmaster \emph{still} does not tell you anything, you may come back to me and I will go yell at him for you.”

The boy’s eyes widened, something of the real Harry showing through the crack before the cool mask was set back in place.

“In any case,” Professor McGonagall said briskly. “I’m sorry for the inconvenience, Mr.~Potter, but I need to ask you to use your Time-Turner to go back six hours to three o’clock, and give the following message to Professor Flitwick: Silver on the tree. Ask the Professor to note down the time at which you gave him that message. Afterward the Headmaster wishes to meet with you at your convenience.”

There was a pause.

Then the boy said, “I am suspected of misusing my Time-Turner, then?”

“Not by \emph{me!}” Professor McGonagall said hastily. “I \emph{am} sorry for the inconvenience, Mr.~Potter.”

There was another pause, and then the young boy shrugged. “It’ll play hob with my sleep schedule but I suppose it can’t be helped. Please let the house elves know that if I ask for an early breakfast at, say, three A.M. tomorrow morning, I’m to receive it.”

“Of course, Mr.~Potter,” she said. “Thank you for understanding.”

The boy rose up from his chair and gave her a formal nod, then slipped out the door with his hand already going under his shirt to where his Time-Turner waited; and she almost called out \emph{Harry!} only she wouldn’t have known what to say after.

Instead she waited, her eyes on the clock.

How long did she need to wait for Harry Potter to go back in time?

She didn’t need to wait at all, actually; if he had done it, then it had already happened...

Minerva knew, then, that she was delaying because she was nervous, and the realization saddened her. Mischief, yes, unspeakable unthinkable mischief with all the prudence and foresight of a falling rock—she didn’t know how the boy had tricked the Hat into not Sorting him to Gryffindor where he obviously belonged—but nothing dark or harmful, not ever. Beneath that mischief his goodness ran as deep and as true as the Weasley twins’, though not even the Cruciatus Curse could have gotten her to say that out loud.

“\emph{Expecto Patronum},” she said, and then, “Go to Professor Flitwick, and bear back his reply after you ask him this: ‘Did Mr.~Potter give you a message from me, what was that message, and when did you receive it?’”
\sbreak
One hour earlier, having used the last remaining spin of his Time-Turner after putting on the Cloak of Invisibility, Harry tucked the hourglass back into his shirt.

And he set out toward the Slytherin dungeons, striding as quickly as his invisible legs could manage, though not running. Thankfully the Deputy Headmistress’s office was already on a lower floor of Hogwarts...

A few staircases later, taken two steps but not three steps at once, Harry stopped at a corridor around whose final bend lay the entrance to the Slytherin dorms.

Harry took a piece of parchment (not paper) out of his \replacement{parch}{pouch}, took a Quotes Quill (not pen) out of his pouch, and told the quill, “Write these letters exactly as I say them: Z-P-G-B-S-Y, space, F-V-Y-I-R-E-B-A-G-U-R-G-E-R-R.”

There were two kinds of codes in cryptography, codes that stopped your little brother from reading your message and codes that stopped major governments from reading your message, and this was the first kind of code, but it was better than nothing. In theory, no one should read it anyway; but even if they did, they wouldn’t remember anything interesting unless they did cryptography first.

Harry then put that parchment in a parchment envelope, and with his wand melted a little green wax to seal it.

In principle, of course, Harry could’ve done all that hours earlier, but somehow waiting until \emph{after} he heard the message from Professor McGonagall’s own lips seemed less like Messing With Time.

Harry then put that envelope inside another envelope, which already contained another sheet of paper with other instructions, and five silver Sickles.

He closed that envelope (which already had a name written on the outside), sealed it with more green wax, and pressed a final Sickle into that seal.

Then Harry put \emph{that} envelope into the very last envelope on which was written in large letters the name “Merry Tavington”.

And Harry peeked around the bend to where the scowling portrait that served as the door to the Slytherin dorms waited; and as he did not wish the portrait to recall not-seeing anyone invisible, Harry used the Hover Charm to float the envelope to the scowling man, and tap it against him.

The scowling man looked down at the envelope, peering at it through a monocle, and sighed, and turned around to face toward the inside of the Slytherin dorms, and called, “Message for Merry Tavington!”

The envelope was then allowed to fall to the floor.

A few moments later the portrait door opened, and Merry snatched up the envelope from the floor.

She would open it up and find a Sickle and an envelope addressed to a fourth-year student named Margaret Bulstrode.

(Slytherins did this sort of thing all the time, and a Sickle definitely constituted a rush order.)

Margaret would open \emph{her} envelope, and find five Sickles along with an envelope to be dropped off in an unused classroom...

...\emph{after} she used her Time-Turner to go back five hours...

...whereupon she would find another five Sickles waiting for her, if she got there quickly.

And an invisible Harry Potter would be waiting in that classroom from three \abbrev{PM} to three-thirty, just in case someone tried the obvious test.

Well, it had been obvious to Professor Quirrell, anyway.

It had also been obvious to Professor Quirrell that (a) Margaret Bulstrode had a Time-Turner and (b) she wasn’t very strict about how she used it, e.g. sharing really good pieces of gossip “before” anyone else had heard.

Some of the tension leaked off Harry as he strode away from the portrait door, still invisible. Somehow his mind had still managed to worry about the plan, even\emph{ knowing} that it had already succeeded. Now there remained only the confrontation with Dumbledore, and then he was done for the day...\ he’d go to the Headmaster’s gargoyles at 9\abbrev{PM}, since doing it at 8\abbrev{PM} would seem more suspicious. This way he could claim that he’d just misunderstood what Professor McGonagall had meant by “afterward”...

The obscure pain clutched at Harry’s heart again as he thought of Professor McGonagall.

So Harry retreated a little further into his dark side, which had worn the calm expression and kept the fatigue off his face, and kept walking.

There would come a reckoning, but sometimes you had to borrow everything you could today, and let the payments come due tomorrow.
\sbreak
Even Harry’s dark side was feeling the exhaustion by the time the spiraling staircase had delivered him to the great oaken door that was the final gate to Dumbledore’s office; but since Harry was now \emph{legally} four hours past his natural bedtime, it was safe to let some of the fatigue show, the physical if not the emotional.

The oaken door swung open—

Harry’s eyes had already been focused in the direction of the great desk, the throne behind it; so it took a moment to register that the throne was empty, the desk barren but for a single leatherbound volume; and then Harry shifted his gaze to see the wizard standing among his fiddly things, the mysterious unknown devices in their scores. Fawkes and the Sorting Hat occupied their respective perches, a bright cheerful blaze crackled in a nook that Harry had not before realized was a fireplace, and there were the two umbrellas and three red slippers for left feet. All things in their place and in their customary appearance except the old wizard himself, standing tall and dressed in robes of the most formal black. It came as a shock to the eyes, those robes on that person, it was as if Harry had seen his father wearing a business suit.

Very ancient was the appearance of Albus Dumbledore, and sorrowful.

“Hello, Harry,” said the old wizard.

From within an alternate self maintained like an Occlumency construct, an innocent-Harry who had absolutely no idea what was happening inclined his head coldly, and said, “Headmaster. I expect you’ve heard back from Deputy Headmistress McGonagall by now, so if it’s fine by you, I would \emph{really} like to know what is going on.”

“Yes,” said the old wizard, “it is time, Harry Potter.” The back straightened, only slightly for the wizard had already been standing straight; but somehow even that small change made the wizard seem a foot taller, and stronger if not younger, formidable though not dangerous, his potency gathered about him like a cowl. In a clear voice, then, he spoke: “This day your war against Voldemort has begun.”

“What?” said the outer Harry who knew nothing, while something watching from inside thought much the same only with a lot more profanity attached.

“Bellatrix Black has been taken from Azkaban, she has escaped from a prison inescapable,” the old wizard said. “It is a feat that bears Voldemort’s signature if ever I have seen it; and she, his most faithful servant, is one of three requisites he must obtain to rise again in a new body. After ten years the enemy you once defeated has returned, as was foretold.”

Neither part of Harry could think of anything to say to that, at least not for the few seconds before the old wizard continued.

“It need change little for you, for now,” said the old wizard. “I have begun reconstituting the Order of the Phoenix that will serve you, I have alerted the few souls who can and should understand: Amelia Bones, Alastor Moody, Bartemius Crouch, certain others. Of the prophecy—yes, there is a prophecy—I have not told them, but they know that Voldemort is returned, and they know that you are to play some vital role. They and I shall fight your war in its lesser beginnings, while you grow stronger, and perhaps wiser, here at Hogwarts.” The old wizard’s hand came up, as though beseeching. “So to you, for now, there is but one change, and I implore you to understand its necessity. Do you recognize the book on my desk, Harry?”

The inner part of Harry was screaming and banging its head against imaginary walls, while the outer Harry turned and stared at what proved to be—

There was a rather long pause.

Then Harry said, “It is a copy of \emph{The Lord of the Rings} by J. R. R. Tolkien.”

“You recognized a quote from that book,” said Dumbledore, an intent look in his eyes, “so I assume you remember it well. If I am mistaken, let me be corrected.”

Harry just stared at him.

“It is important to understand,” said Dumbledore, “that this book is not a realistic depiction of a wizarding war. John Tolkien never fought Voldemort. Your war will not be like the books you have read. Real life is not like stories. Do you understand, Harry?”

Harry, rather slowly, nodded yes; and then shook his head no.

“In particular,” said Dumbledore, “there is a certain very foolish thing that Gandalf does in the first book. He makes many mistakes, does Tolkien’s wizard; but this one error is the most unforgivable. That mistake is this: When Gandalf first suspected, even for a moment, that Frodo held the One Ring, he should have moved Frodo to Rivendell \emph{at once.} He might have been embarrassed, that old wizard, if his suspicions had proven false. He might have found it awkward to so command Frodo, and Frodo would have been greatly inconvenienced, needing to set aside many other plans and pastimes. But a little embarrassment, and awkwardness, and inconvenience, is as nothing compared to the loss of your whole war, when the nine Nazgul swoop down on the Shire while you are reading old scrolls in Minas Tirith, and take the Ring at once. And it is not Frodo alone who would have been hurt; all Middle-Earth would have fallen into slavery. If it had \emph{not} been only a story, Harry, they would have lost their war. Do you understand what I am saying?”

“Er...” said Harry, “not exactly...” There was something about Dumbledore when he was like this, which made it hard to stay properly cold; his dark side had trouble with weird.

“Then I will spell it out,” said the old wizard. His voice was stern, his eyes were sad. “Frodo should have been moved to Rivendell at once by Gandalf himself—and Frodo should never have left Rivendell without guard. There should have been no night of terror in Bree, no Barrow-downs, no Weathertop where Frodo was wounded, they could have lost their entire war any of those times, for Gandalf’s folly! Do you understand now what I am saying to you, son of Michael and Petunia?”

And the Harry who knew nothing did understand.

And the Harry who knew nothing saw that it was the smart, the wise, the intelligent and sane, the \emph{right} thing to do.

And the Harry who knew nothing said just what an innocent Harry \emph{would} have said, while the silent watcher screamed in confusion and agony.

“You’re saying,” Harry said, his voice shaking as the emotions inside burned through the outer calm, “that I’m not going home to my parents for Easter.”

“You \emph{will} see them again,” the old wizard said swiftly. “I will beg them to come here to be with you, I will extend them every courtesy during their visits. But you are not going home for Easter, Harry. You are not going home for the summer. You are no longer taking lunches in Diagon Alley, even with Professor Quirrell to watch you. Your blood is the second requisite Voldemort needs to rise as strong as before. So you are never again leaving the bounds of Hogwarts’s wards without a vital reason, and a guard strong enough to fend off any attack for long enough to get you to safety. “

Water was beginning at the corners of Harry’s eyes. “Is that a request?” said his quavering voice. “Or an order?”

“I’m sorry, Harry,” the old wizard said softly. “Your parents will see the necessity, I hope; but if not... I am afraid they have no recourse; the law, however wrongly, does not recognize them as your guardians. I am sorry, Harry, and I will understand if you despise me for it, but it must be done.”

Harry whirled, looked at the door, he couldn’t look at Dumbledore any more, couldn’t trust his own face.

\emph{This is the cost to yourself,} said Hufflepuff within his mind, \emph{even as you imposed costs on others. Will that change your whole view of the matter, the way Professor Quirrell thinks it will?}

Automatically, the mask of the innocent Harry said exactly what it would have said: “Are my parents in danger? Do \emph{they} need to be moved here?”

“No,” said the old wizard’s voice. “I do not think so. The Death Eaters learned, toward the end of the war, not to attack the Order’s families. And if Voldemort is now acting without his former companions, he still knows that it is I who make the decisions for now, and he knows that I would give him nothing for any threat to your family. I have taught him that I do not give in to blackmail, and so he will not try.”

Harry turned back then, and saw a coldness on the old wizard’s face to match the shift in his voice, Dumbledore’s blue eyes grown hard as steel behind the glasses, it didn’t match the person but it matched the formal black robes.

“Is that everything, then?” said Harry’s trembling voice. Later he would think about this, later he would think of some cunning countermeasure, later he would ask Professor Quirrell if there was any way to convince the Headmaster he was mistaken. Right now, maintaining the mask was taking all of Harry’s attention.

“Voldemort used a Muggle artifact to escape Azkaban,” the old wizard said. “He is watching you and learning from you, Harry Potter. Soon a man named Arthur Weasley at the Ministry will issue an edict that all use of Muggle artifacts must cease in the Defense Professor’s battles. In the future, when you have a good idea, keep it closer about yourself.”

It didn’t seem important by comparison. Harry just nodded, and said again, “Is that everything?”

There was a pause.

“Please,” said the old wizard in a whisper. “I have no right to ask your forgiveness, Harry James Potter-Evans-Verres, but please, at least say that you understand why.” There was water in the old wizard’s eyes.

“I understand,” said the voice of the outer Harry who did understand, “I mean... I was sort of thinking about it anyway...\ wondering whether I could get you and my parents to let me stay over at Hogwarts during the summer like the orphans, so I could read the library here, it’s just more interesting at Hogwarts anyway...”

A choking sound came from Albus Dumbledore’s throat.

Harry turned again toward the door. It wasn’t escape unscathed, but it was escape.

He took a step forward.

His hand reached to the door-handle.

A piercing cry split the air—

As though in slow motion, as Harry spun, he saw the phoenix already launched through the air and winging toward him.

From the true Harry, the one who knew his own guilt, came a flash of panic, he hadn’t thought of that, hadn’t anticipated it, he’d prepared to face Dumbledore but he’d forgotten about \emph{Fawkes—}

Flap, flap, and flap, three times the phoenix’s wings flapped like the flaring up and dying down of a fire, duration seemed to pass too slowly as Fawkes soared over the mysterious devices toward where Harry stood.

And the red-golden bird was hovering in front of him with gentle wing-sweeps, bobbing in the air like a candle-flame.

“What is it, Fawkes?” said the false Harry in puzzlement, looking the phoenix in the eyes, as he would if he were innocent. The real Harry, feeling the same awful sickness inside as when Professor McGonagall had expressed her trust in him, thought, \emph{Did I turn evil today, Fawkes? I didn’t think I was evil... Do you hate me now? If I’ve become something a phoenix hates, maybe I should just give it up now, give up everything now and confess—}

Fawkes screamed, the most terrible cry Harry had ever heard, a scream that set all the devices vibrating and made all the sleeping figures start within their portraits.

It pierced through all of Harry’s defenses like a white-hot sword through butter, collapsed all his layers like a punctured balloon popping, reshuffled his priorities in an instant as he remembered the one most important thing; the tears began pouring freely from Harry’s eyes, down his cheeks, his voice choked as the words came out of his throat like coughing up lava—

“Fawkes says,” Harry’s voice said, “he wants me, to do, something, about, the prisoners, in Azkaban—”

“Fawkes, \emph{no!}” said the old wizard. Dumbledore strode forward, reaching out to the phoenix with a pleading hand. The old wizard’s voice was almost as desperate as the phoenix’s scream had been. “You cannot ask that of him, Fawkes, he’s only a boy still!”

“You went to Azkaban,” Harry whispered, “you took Fawkes with you, he saw—\emph{you} saw—you were \emph{there}, you saw—\shout{Why didn’t you do anything? Why didn’t you let them out?}”

When the instruments stopped vibrating, Harry realized that Fawkes had screamed at the same time as his own scream, that the phoenix was now flying next to Harry and facing Dumbledore at his side, the red-golden head level with his own.

“Can you,” whispered the old wizard, “can you truly hear the voice of the phoenix so clearly?”

Harry was sobbing almost too hard to speak, for all the metal doors he’d passed, the voices he’d heard, the worst memories, the desperate begging as he walked away, all of it had burst into his mind like fire at the phoenix’s scream, all the inner bulwarks smashed. Harry didn’t know whether he could truly hear the voice of the phoenix so clearly, whether he would have understood Fawkes without already knowing. All Harry knew was that he had a plausible excuse to say the things Professor Quirrell had told him he must \emph{never} raise in conversation from this day forth; because this was just what an innocent Harry would have said, would have done, if he \emph{had} heard so clearly. “They’re hurting—we have to help them—”

“I \emph{can’t!}” cried Albus Dumbledore. “Harry, Fawkes, I \emph{can’t}, there’s nothing I can do!”

Another piercing scream.

“\shout{Why not? Just go in and take them out!”}

The old wizard wrenched his gaze from the phoenix, his eyes meeting Harry’s instead. “Harry, tell Fawkes for me! Tell him it’s not that simple! Phoenixes aren’t mere animals but they \emph{are} animals, Harry, they can’t understand—”

“I don’t understand either,” Harry said, his voice trembling. “I don’t understand why you’re \emph{feeding people to Dementors! Azkaban isn’t a prison, it’s a torture chamber and you’re torturing those people to \shout{death}!}”

“Percival,” said the old wizard hoarsely, “Percival Dumbledore, my own father, Harry, my own father died in Azkaban! I know, I know it is a horror! \emph{But what would you have of me?} To break Azkaban by force? Would you have me declare open rebellion against the Ministry?”

\shout{Caw}!

There was a pause, and Harry’s trembling voice said, “Fawkes doesn’t know anything about governments, he just wants you—to take the prisoners out—of their cells—and he’ll help you fight, if anyone stands in your way—and—and so will I, Headmaster! I’ll go with you and destroy any Dementor that comes near! We’ll worry about the political fallout afterward, I bet that you and I together could get away with it—”

“Harry,” whispered the old wizard, “phoenixes do not understand how winning a battle can lose a war.” Tears were streaming down the old wizard’s cheeks, dripping into his silver beard. “The battle is all they know. They are good, but not wise. That is why they choose wizards to be their masters.”

“Can you bring out the Dementors to where I can get at them?” Harry’s voice was begging, now. “Bring them out in groups of fifteen—I think I could destroy that many at a time without hurting myself—”

The old wizard shook his head. “It was hard enough to pass off the loss of one—they might give me one more, but never two—they are considered national possessions, Harry, weapons in case of war—”

Fury blazed in Harry then, blazed up like fire, it might have come from where a phoenix now rested on his own shoulder, and it might have come from his own dark side, and the two angers mixed within him, the cold and the hot, and it was a strange voice that said from his throat, “Tell me something. What does a government have to do, what do the voters have to do with their democracy, what do the \emph{people} of a \emph{country} have to do, before I ought to decide that I’m not on their side any more?”

The old wizard’s eyes widened where he stared at the boy with a phoenix upon his shoulder. “Harry...\ are those your words, or the Defense Professor’s—”

“Because there has to be \emph{some} point, doesn’t there? And if it’s not Azkaban, where is it, then?”

“Harry, listen, please, hear me! Wizards could not live together if they each declared rebellion against the whole, every time they differed! Always there will be \emph{something} —”

“\emph{Azkaban is not just something! It’s evil!}”

“Yes, even evil! Even some evils, Harry, for wizards are not perfectly good! And yet it is better that we live in peace, than in chaos; and for you and I to break Azkaban by force would be the beginning of \emph{chaos}, can you not see it?” The old wizard’s voice was pleading. “And it is possible to oppose the will of your fellows openly or in secret, without \emph{hating} them, without declaring them evil and enemy! I do not think the people of this country deserve that of you, Harry! And even if some of them did—what of the children, what of the students in Hogwarts, what of the many good people mixed in with the bad?”

Harry looked on his shoulder at where Fawkes had perched, saw the phoenix’s eyes gazing back at him, they did not glow and yet they blazed, red flames in a sea of golden fire.

\emph{What do you think, Fawkes?}

“Caw?” said the phoenix.

Fawkes didn’t understand the conversation.

The young boy looked at the old wizard, and said in a thick voice, “Or maybe the phoenixes are wiser than us, smarter than us, maybe they follow us around hoping that someday we’ll \emph{listen} to them, someday we’ll \emph{get} it, someday we’ll just \emph{take}, the prisoners, \emph{out,} of their \emph{cells—}”

Harry spun and pulled open the oaken door and stepped onto the staircase and slammed the door behind him.

The stairwell began rotating, Harry began descending, and he put his face in his hands, and began to weep.

It wasn’t until he was halfway to the bottom that he noticed the difference, noticed the warmth still spreading through him, and realized that—

“Fawkes?” Harry whispered.

—the phoenix was still on his shoulder, perched there as he had seen him a few times upon Dumbledore’s.

Harry looked again into the eyes, red flames in golden fire.

“You’re not my phoenix now...\ are you?”

Caw!

“Oh,” Harry said, his voice trembling a little, “I’m glad to hear that, Fawkes, because I don’t think—the Headmaster—I don’t think he deserves—”

Harry stopped, took a breath.

“I don’t think he deserves that, Fawkes, he was just trying to be wise...”

Caw!

“But you’re angry at him and trying to make a point. I understand.”

The phoenix nestled his head against Harry’s shoulder, and the stone gargoyle walked smoothly aside to let Harry pass back into the corridors of Hogwarts.

