\chapter{Contagious Lies}

\lettrine{H}{ermione} Granger had read somewhere once, that one of the keys to staying thin was to pay attention to the food you ate, to notice yourself eating it, so that you were satisfied with the meal. This morning she’d made herself toast, and put butter on the toast, and cinnamon on the butter, and it really should’ve been enough to get her to \emph{notice,} this time, the goodness that was in front of her...

Without noticing the cinnamon or the butter, without noticing the food or that she was eating, Hermione swallowed another bite of toast, and said, “Can you try explaining that again? I’m still completely flabbergasted.”

“It’s pretty straightforward, if you think like a Light-Side Slytherin,” said the boy that everyone else in school, excepting only the two of them, now believed to be her true love. Harry Potter’s spoon absentmindedly stirred his breakfast cereal; he hadn’t taken many bites of it this morning, not that Hermione had seen. “Every good thing in the world brings its own opposition into existence. Phoenixes are no exception.”

Hermione took another unnoticed bite out of her buttered and cinnamoned toast, and said, “How can anyone \emph{not understand} that Fawkes thinks you’re a good enough person to ride around on your shoulder? He wouldn’t do that with a Dark Wizard! He just wouldn’t!”

And she hadn’t yelled at anyone about Fawkes’s touch on her \emph{own} cheek, because she knew it wouldn’t be right—that if a phoenix touched you, you weren’t supposed to brag about it, that wasn’t what a phoenix was \emph{for}.

But she’d really \emph{hoped} that it would squash the rumors about Harry Potter going evil and Hermione Granger following him down.

And it hadn’t.

And she truly couldn’t understand why not.

Harry ate another bite of his cereal, his eyes going distant now, no longer meeting her own. “Think of it this way: You skip school one day, and you lie and tell your teacher you were sick. The teacher tells you to bring a doctor’s note, so you forge one. The teacher says she’s going to call the doctor to check, so you have to give her a fake number for the doctor, and get a friend to pretend to be the doctor when she calls—”

“You did \emph{what?}”

Harry looked up from his cereal then, and now he was smiling. “I’m not saying I really \emph{did} that, Hermione...” Then his eyes abruptly dropped back down to his cereal. “No. Just an example. Lies propagate, that’s what I’m saying. You’ve got to tell more lies to cover them up, lie about every fact that’s connected to the first lie. And if you \emph{kept on} lying, and you \emph{kept on} trying to cover it up, sooner or later you’d even have to start lying about the general laws of thought. Like, someone is selling you some kind of alternative medicine that doesn’t work, and any double-blind experimental study will confirm that it doesn’t work. So if someone wants to \emph{go on} defending the lie, they’ve got to get you to disbelieve in the experimental method. Like, the experimental method is just for merely \emph{scientific} kinds of medicine, not amazing alternative medicine like theirs. Or a good and virtuous person should believe as strongly as they can, no matter what the evidence says. Or truth doesn’t exist and there’s no such thing as objective reality. A lot of common wisdom like that isn’t just \emph{mistaken,} it’s anti-epistemology, it’s \emph{systematically} wrong. Every rule of rationality that tells you how to find the truth, there’s someone out there who needs you to believe the opposite. If you once tell a lie, the truth is ever after your enemy; and there’s a lot of people out there telling lies—” Harry’s voice stopped.

“What does that have to do with Fawkes?” she said.

Harry withdrew his spoon from his cereal, and pointed in the direction of the Head Table. “The Headmaster has a phoenix, right? And he’s Chief Warlock of the Wizengamot? So he’s got political opponents, like Lucius. Now, d’you think that opposition is going to just roll over and surrender, because Dumbledore has a phoenix and they don’t? Do you think they’ll admit that Fawkes is even \emph{evidence} that Dumbledore’s a good person? Of course not. They’ve got to invent \emph{something} to say that makes Fawkes... \emph{not important.} Like, phoenixes only follow people who charge straight at anyone they think is evil, so having a phoenix just means you’re an idiot or a dangerous fanatic. Or, phoenixes just follow people who are pure Gryffindor, so Gryffindor they don’t have the virtues of other Houses. Or it just shows how much courage a magical animal thinks you have, nothing else, and it wouldn’t be fair to judge politicians based on that. They have to say \emph{something} to deny the phoenix. I bet Lucius didn’t even have to make up anything new. I bet it had all been said before, centuries ago, since the first time someone had a phoenix riding on his shoulder, and someone else wanted people not to take that into account as evidence. I bet by the time Fawkes came along it was already common wisdom, it would have just seemed \emph{strange} to take into account who a phoenix liked or disliked. It would be like a Muggle newspaper testing political candidates to rate their level of scientific literacy. Every force for Good that exists in this universe, there’s someone else who benefits from people discounting it, or fencing it into a narrow box where it can’t get to them.”

“But—” Hermione said. “Okay, I see why Lucius Malfoy doesn’t want anyone to think that Fawkes matters, but why does anyone who \emph{isn’t} a bad guy \emph{believe} it?”

Harry Potter gave a little shrug. His spoon dropped back into his cereal, and went on stirring without a pause. “Why does any kind of cynicism appeal to people? Because it seems like a mark of maturity, of sophistication, like you’ve seen everything and know better. Or because putting something down feels like pushing yourself up. Or they don’t have a phoenix themselves, so their political instinct tells them there’s no advantage to be gained from saying nice things about phoenixes. Or because being cynical feels like knowing a secret truth that common people don’t know...” Harry Potter looked in the direction of the Head Table, and his voice dropped until it was almost a whisper. “I think maybe that’s what \emph{he’s} getting wrong—that he’s cynical about everything else, but not about cynicism itself.”

Without thinking, Hermione looked in the direction of the Head Table herself, but the Defense Professor’s seat was still empty, as it had been on Monday and Tuesday; the Deputy Headmistress had pronounced, earlier, that Professor Quirrell’s classes for today would be canceled.

Afterward, when Harry had eaten a few bites of treacle tart and then left the table, Hermione looked at Anthony and Padma, who had been coincidentally eating nearby but certainly not eavesdropping or anything.

Anthony and Padma looked back at her.

Padma said hesitantly, “Is it just me, or has Harry Potter started talking like a more \emph{complicated} sort of book in the last few days? I mean, I haven’t been listening to him very long—”

“It’s not just you,” said Anthony.

Hermione didn’t say anything, but she was becoming increasingly worried. Whatever had happened to Harry Potter on the day of the phoenix, it had changed him; there was something new in him now. Not cold, but \emph{hard.} Sometimes she caught him staring out a window at nothing visible, a look of grim determination on his face. In Herbology class on Monday, a Venus Fire Trap had gone out of control; and Harry had tackled Terry out of the way of a fireball even as Professor Sprout had shouted a Flame-Freezing Charm; and when Harry had risen from the floor he’d just gone back to his place like nothing interesting had happened. And when for once she’d gotten a better test score than Harry in their Transfiguration exam, later that same Monday, Harry had smiled at her as though to congratulate her, instead of gritting his teeth; and...\ that had bothered her \emph{a lot}.

She was getting the sense that Harry...

...was pulling away from her...

“He seems a lot \emph{older} all of a sudden,” said Anthony. “Not like a real grownup, I can’t imagine \emph{Harry} as a grownup, but it’s like he suddenly turned into a \emph{fourth-year version} of...\ of \emph{whatever} he is.”

“Well,” Padma said. She daintily dabbed a chocolate-flavored scone with some scone-flavored frosting. “I think Dragon and Sunshine had better ally during the next battle or Mr.~Harry Potter is going to \emph{smash} us. We were allied last time, and even then Chaos almost won—”

“Yeah,” said Anthony. “You’re right, Miss Patil. Tell the Dragon General that we want to meet with you—”

“No!” said Hermione. “We shouldn’t \emph{have} to gang up on General Potter just to stand a chance. That doesn’t make sense, especially now that nobody can use Muggle things anymore. It’s still twenty-four soldiers in every army.”

Neither Padma or Anthony said anything to that.
\sbreak
Knock-knock, knock-knock.

“Come in, Mr.~Potter,” she said.

The door creaked open, and Harry Potter slipped through the opening into her office; he pushed the door shut behind him with one hand, and wordlessly seated himself in the cushioned chair that now stood in front of her desk. She’d Transfigured that chair so often that it sometimes changed form to reflect her mood, without any wand movement or incantation or even conscious intent. Right now, that chair had become deeply cushioned, so that as Harry sat down he sank into it, as though the chair were hugging him.

Harry didn’t seem to notice. There was an air of quiet determination about the boy; his eyes had locked steadily with hers, and not let up for a moment. “You called me?” said the boy.

“I did,” said Professor McGonagall. “I have two pieces of good news for you, Mr.~Potter. First—have you met Mr.~Rubeus Hagrid, at all? The groundskeeper? He was an old friend of your parents.”

Harry hesitated. Then, “Mr.~Hagrid spoke to me a bit after I got here,” Harry said. “I think it was on Tuesday of my first week of school. He didn’t say he knew my parents, though. At the time I thought he just wanted to introduce himself to the Boy-Who-Lived...\ did he have some kind of hidden agenda? He didn’t \emph{seem} like the type...”

“Ah...” she said. It took her a moment to pull her thoughts together. “It’s a long story, Mr.~Potter, but Mr.~Hagrid was falsely accused of murdering a student, five decades ago. Mr.~Hagrid’s wand was snapped, and he was expelled. Later, when Professor Dumbledore became Headmaster, he gave Mr.~Hagrid a place here as Keeper of Grounds and Keys.”

Harry’s eyes watched her intently. “You said that five decades ago was the last time a student died in Hogwarts, and you were certain that five decades ago was the last time someone heard the Sorting Hat’s secret message.”

She felt a slight chill—even the Headmaster or Severus might not have made that connection that quickly—and said, “Yes, Mr.~Potter. Someone opened the Chamber of Secrets, but this was not believed, and Mr.~Hagrid was blamed for the resulting death. However, the Headmaster has located the additional enchantment on the Sorting Hat, and he has shown it to a special panel of the Wizengamot. As a result, Mr.~Hagrid’s sentence has been revoked—just this morning, in fact—and he will be allowed to acquire a new wand.” She hesitated. “We...\ have not yet told Mr.~Hagrid of this, Mr.~Potter. We were waiting until the deed was done, so as not to give him false hope after so long. Mr.~Potter...\ we were wondering if we could tell Mr.~Hagrid that it was you who helped him...?”

She saw the weighing look in his eyes—

“I remember Mr.~Hagrid holding you when you were a baby,” she said. “I think he would be very happy to know.”

She could see it, though, on Harry’s face, the moment when he decided that Rubeus wouldn’t be any use to him.

Harry shook his head. “Bad enough that someone might deduce there was a Parselmouth in this year’s crop of students,” Harry said. “I think it’d be more prudent to just keep it all as secret as possible.”

She remembered James and Lily, who’d never hesitated to return the friendship the huge, bluff man had offered them, for all that James was the scion of a Noble House or Lily a budding Charms Mistress, and Rubeus a mere half-giant whose wand had been snapped...

“Because you don’t expect him to prove useful, Mr.~Potter?”

There was silence. She hadn’t intended to say that out loud.

Sadness crossed Harry’s face. “Probably,” Harry said quietly. “But I don’t think he and I would get along, do you?”

Something seemed to be stuck in her throat.

“Speaking of making use of people,” Harry said. “It seems I’m going to be thrown into a war with a Dark Lord sometime soon. So while I’m in your office, I’d like to ask that my sleep cycle be extended to thirty hours per day. Neville Longbottom wants to start practicing dueling, there’s an older Hufflepuff who offered to teach him, and they invited me to join. Plus there’s other things I want to learn too—and if you or the Headmaster think I should study anything in particular, in order to become a powerful wizard when I grow up, let me know. Please direct Madam Pomfrey to administer the appropriate potion, or whatever it is that she needs to do—”

“\emph{Mr.~Potter!}”

Harry’s eyes gazed directly into her own. “Yes, Minerva? I know it wasn’t your idea, but I’d like to survive the use the Headmaster’s making of me. Please don’t be an obstacle to that.”

It almost broke her. “Harry,” she whispered in a bare voice, “children shouldn’t have to \emph{think} like that!”

“You’re right, they shouldn’t,” Harry said. “A \emph{lot} of children have to grow up too early, though, not just me; and most children like that would probably trade places with me in five seconds. I’m not going to pity myself, Professor McGonagall, not when there are people out there in real trouble and I’m not one of them.”

She swallowed, hard, and said, “Mr.~Potter, at thirty hours per day, you’ll—get \emph{older,} you’ll age faster—” \emph{Like Albus.}

“And in my fifth year I’ll be around the same physiological age as Hermione,” said Harry. “Doesn’t seem \emph{that} terrible.” There was a wry smile now on Harry’s face. “Honestly, I’d probably want this even if there \emph{weren’t} a Dark Lord. Wizards live for a while, and either wizards or Muggles will probably push that out even further over the next century. There’s no reason \emph{not} to pack as many hours into a day as I can. I’ve got things I plan to do, and ’twere well they were done quickly.”

There was a long pause.

“All right,” Minerva said. It came out as almost a whisper. She raised her voice. “All right, Mr.~Potter, I shall ask the Headmaster, and if he agrees, it shall be done.”

Harry’s eyes narrowed for a moment. “I see. Then please remind the Headmaster that Godric Gryffindor, in his last words, said that if it had been the right thing for him to do, then he wouldn’t tell anyone else to choose wrongly, not even the youngest student in Hogwarts.”

And she knew with a hollow feeling that any chance of Albus stopping this, stopping any of this, had just Vanished into nothingness. That was what Albus had told her when she’d objected that Cameron Edward was too young, and then when she’d objected that Peter Pevensie was too young, and finally she’d given up objecting. “Who told you that, Mr.~Potter?” \emph{Not Albus—surely Albus would never} say\emph{ that to any student—}

“I’ve been doing a lot of reading lately,” Harry said. His body started to rise from the enveloping chair, then halted. “Dare I ask about the second piece of good news?”

“Oh,” she said. “Ah—Professor Quirrell has woken up and says that you may—”
\sbreak
The Hogwarts infirmary was a brilliantly open space, skylit on all four sides despite seeming to be located squarely in the middle of the castle. White beds in long rows stretched out, only three of them occupied at the moment. One older boy and one older girl on opposite sides, both lying motionless with their eyes closed, probably unconscious and spell-bound while some healing Charm or Potion reconfigured their bodies in uncomfortable ways; and the third occupant had the curtain drawn around their bed, which was presumably a good thing. Madam Pomfrey had pushed him along with a hard shove and told him not to gawk, and Harry had needed to remind himself sharply that some people still didn’t know who the Boy-Who-Lived was—either that, or Madam Pomfrey’s identity was bound up with her absolute dominance of her own hospital, etcetera, whatever.

Behind the rows of beds were five doors, leading into the private rooms where they stored the patients who would be staying for days instead of hours, but whose condition didn’t warrant a transfer to St.~Mungo’s.

Windowless, skyless, unlit but for a single smokeless torch on one of the solid stone walls; that was the room behind the middle door. Harry had wondered whether professors could ask Hogwarts to change itself; or if the infirmary always had a room like that available, for people who didn’t enjoy the light.

In the center of the room, between two equal bedstands that looked to have been carved from the same grey marble as the walls, rested a white hospital bed, looking vaguely orangish in the unsmoking torchlight; and within that bed, a white sheet pulled up about his thighs and wearing a hospital gown, sat Professor Quirrell with his back slightly propped up against the headboard of the bed.

There was something frightening about seeing Professor Quirrell in one of Madam Pomfrey’s beds, even if the Defense Professor appeared uninjured. Even knowing that Professor Quirrell had deliberately arranged his own apparent defeat at Severus’s hands, to give himself an excuse to recover his strength from Azkaban. Harry had never \emph{actually} watched anyone dying in a hospital bed, but he’d seen too many movies. It was an intimation of mortality, and the Defense Professor was \emph{not} supposed to be mortal.

Madam Pomfrey had told Harry that he was absolutely forbidden to pester her patient.

Harry had said, “I understand”, which technically did not say anything about obedience.

The stern old healer had then turned, and started to say to Professor Quirrell that he was absolutely not to overexert himself or...\ upset himself...

Madam Pomfrey had trailed off, hurriedly turned around, and fled the room.

“Not bad,” Harry observed, after the door had shut behind the escaping medical matron. “I’ve got to learn how to do that, sometime.”

Professor Quirrell smiled a smile with absolutely no humor content, and said, his voice sounding a good deal dryer than its usual dryness, “Thank you for your artistic critique, Mr.~Potter.”

Harry stared into the pale blue eyes, and thought that Professor Quirrell looked...

...older.

It was subtle, it might have just been Harry’s imagination, it might have been the poor lighting. But the hair above Quirinus Quirrell’s forehead might have receded a bit, what remained might have thinned and greyed, an advancing of the baldness that had already been visible on the back of his head. The face might have grown a little sunken.

The pale blue eyes had stayed sharp and intense.

“I am glad,” Harry said quietly, “to see you in what appears to be good health.”

“Appearances can be deceiving, of course,” said Professor Quirrell. He gave a flick of his fingers, and when his hand finished the gesture he was holding his wand. “Would you believe that woman thinks she has confiscated this from me?”

Six incantations the Defense Professor spoke then; six of the thirty that he had used to safeguard their important conversations in Mary’s Room.

Harry raised his eyebrows, silently quizzical.

“That is all I can manage for now,” said the Defense Professor. “I expect it shall prove sufficient. Still, there is a proverb: If you do not wish a thing heard, do not say it. Consider it to apply in full measure. I am told that you were trying to see me?”

“Yes,” Harry said. He paused, gathered his thoughts. “Did the Headmaster, or anyone, tell you that we can’t go to lunch any more?”

“Something along those lines,” said the Defense Professor. And without changing expression, “Of course I was terribly sorry to hear it.”

“It’s more extreme than that, actually,” said Harry. “I’m confined to Hogwarts and its grounds indefinitely. I can’t leave without a guard and a good reason. I’m not going home for summer, and maybe not ever again. I was hoping...\ to speak with you, about that.”

There was a pause.

The Defense Professor exhaled a breath like a brief sigh, and said, “We shall just have to rely on the known fact that the Deputy Headmistress will personally murder anyone who tries to report me. Mr.~Potter, I intend to keep this conversation on track so that we may conclude it quickly, is that understood?”

Harry nodded, and—

In the light of the single torch, shaded toward the reddish end of the optical spectrum, the snake’s green scales were not very reflective, and the blue-and-white banding hardly more so. Dark seemed the snake, in that light. The eyes, which had seemed like gray pits before, now reflected the torchlight, and seemed brighter than the rest of the snake.

“\emph{Sso,}” hissed the venomous creature. “\emph{What did you wissh to ssay?}”

And Harry hissed, “\emph{Sschoolmasster thinkss that woman’ss former Lord iss the one who sstole her from prisson}.”

Harry \emph{had} thought about it this time, and carefully, before he had decided that he would reveal to Professor Quirrell \emph{only} that the Headmaster believed that; and \emph{not} say anything about the prophecy which had set Voldemort on Harry’s parents, nor that the Headmaster was reconstituting the Order of the Phoenix...\ it was a risk, a significant risk, but Harry needed an ally in this.

“\emph{He believess that one iss alive?}” the snake finally said. The divided, two-pronged tongue flickered rapidly from side to side, sardonic snakish laughter. “\emph{Ssomehow I am not ssurprissed.}”

“\emph{Yess,}” Harry hissed dryly, “\emph{very amussing, I am ssure. Except now am sstuck in Hogwartss for next ssix years, for ssafety! I have decided that I will, indeed, sseek power; and confinement iss not helpful for that. Musst convince sschoolmasster that Dark Lord iss not yet awakened, that esscape was work of ssome other power—}”

Again the rapid flickering of the snake’s tongue; the snakish laughter was stronger, dryer, this time. “\emph{Amateur foolisshnesss.}”

“\emph{Pardon?}” hissed Harry.

“\emph{You ssee misstake, think of undoing, ssetting time back to sstart. Yet not even with hourglasss can time be undone. Musst move forward insstead. You think of convincing otherss they are misstaken. Far eassier to convince them they are right. Sso conssider, boy: what new happensstance would make schoolmasster decide you were ssafe once more, ssimultaneoussly advance your other agendass?”}

Harry stared at the snake, puzzled. His mind tried to comprehend and unravel the riddle—

“\emph{Iss it not obviouss?}” hissed the snake. Again the tongue flickered sardonic laughter. “\emph{To free yoursself, to gain power in Britain, you musst again be sseen to defeat the Dark Lord.}”
\sbreak
In reddish-orange flickering torchlight, a green snake swayed above a white hospital bed, as the boy stared into the embers of its eyes.

“\emph{Sso,}” Harry said finally. “\emph{Let uss be clear on what iss propossed. You ssuggesst that we sset up imposstor to imperssonate Dark Lord.”}

“\emph{Ssomething like that.} \emph{Woman we resscued will cooperate, sshould be mosst convincing when sshe iss sseen at hiss sside.}” More sardonic tongue-flickering. “\emph{You are kidnapped from Hogwartss to public location, many witnesssess, wardss keep out protectorss. Dark Lord announcess that he hass at long lasst regained physical form, after wandering as sspirit for yearss; ssayss that he hass gained sstill greater power, not even you can sstop him now. Offerss to let you duel. You casst guardian Charm, Dark Lord laughss at you, ssayss he iss not life-eater. Casstss Killing Cursse at you, you block, watcherss ssee Dark Lord explode—”}

“\emph{Casst Killing Cursse?}” Harry hissed in incredulity. “\emph{At me? Again? Ssecond time? Nobody will believe Dark Lord could posssibly be that sstupid—}”

“\emph{You and I are only two people in country who would notice that,}” hissed the snake. “\emph{Trusst me on thiss, boy.}”

“\emph{What if there iss third, ssomeday?}”

The snake swayed thoughtfully. “\emph{Could write different sscript for play, if you wissh. Whatever sscenario, sshould leave open posssibility Dark Lord might return yet again—nation musst think they are sstill dependent on you to protect them.}”

Harry stared into the red-flickering pits of the snake’s eyes.

“\emph{Well?}” hissed the swaying form.

The obvious thought was that going along with the Defense Professor’s plots and deceptions a \emph{second} time, spinning an even \emph{more} complicated lie to cover up the first mistake, and creating \emph{another} fatal vulnerability if anyone ever discovered the truth, would be \emph{exactly} the same sort of stupidity as the putative Dark Lord using the Killing Curse again. It didn’t even take his Hufflepuff side to point that out, Harry thought it in his very own mental voice.

But there was also a certain question as to whether the appropriate moral to learn from the last experience was to always say \emph{no} immediately to the Defense Professor, or...

“\emph{Will think about it,}” hissed Harry. “\emph{Will not ansswer right away, thiss time, will enumerate risskss and benefitss firsst—}”

“\emph{Undersstood,}” hissed the snake. “\emph{But remember thiss, boy, other eventss proceed without you. Hessitation iss alwayss eassy, rarely usseful.”}
\sbreak
The boy emerged from the private room into the main infirmary, running nervous fingers through his messy black hair as he walked past the white beds, occupied and unoccupied.

Shortly afterward, the boy emerged from the Hogwarts infirmary entirely, passing Madam Pomfrey on the way out with a distracted nod.

The boy walked out into a hallway, then into a larger corridor, and then stopped and leaned against the wall.

The thing was...

...he really \emph{didn’t} want to be stuck in Hogwarts for the next six years; and when you thought about it...

...the Incident with Rescuing Bellatrix From Azkaban wasn’t \emph{just} imposing costs on Harry. Other people would be worrying, living in fear of the Dark Lord’s return, expending unknown resources to take unknown precautions. Harry could demand that they write the script in such fashion as to make it seem \emph{not} plausible that the Dark Lord would return a third time. And then people would relax, it would all be over.

Unless of course there actually \emph{was} a Dark Lord out there to be feared. There \emph{had} been a prophecy.

The boy leaning against the wall vented a soft sigh, and started walking again.

Harry had almost forgotten, but he \emph{had} gotten around to showing Professor Quirrell the deck of cards he’d been given on Sunday night by ‘Santa Claus’, within which the King of Hearts was allegedly a portkey that would take him to the Salem Witches’ Institute in America. Although of course Harry hadn’t told Professor Quirrell \emph{who’d} sent him the card, nor what it was \emph{supposed} to do, before he’d asked Professor Quirrell if it was possible to tell where the portkey would send him.

The Defense Professor had transformed back to human form, and examined the King of Hearts, tapping it a few times with his wand.

And according to Professor Quirrell...

...the portkey would send the user somewhere in London, but he couldn’t pinpoint it any nearer than that.

Harry had shown Professor Quirrell the note that had accompanied the deck of cards, saying nothing of the earlier notes.

Professor Quirrell had taken it in at a glance, given a dry chuckle, and observed that if you read the note \emph{carefully}, it did not \emph{explicitly} say that the portkey would take him to the Salem Witches’ Institute.

You needed to learn to pay attention to that kind of subtlety, Professor Quirrell said, if you wanted to be a powerful wizard when you grew up; or, indeed, if you wanted to grow up at all.

The boy sighed again as he trudged off to class.

He was starting to wonder if all the other wizarding schools were also like this, or if it was only Hogwarts that had a problem.


