\partchapter{Roles}{I}

\lettrine{A}{} simple \emph{Innervate} from the Headmaster had awakened Fred Weasley, followed by a preliminary healing Charm for a broken arm and cracked ribs. Harry’s voice had distantly told the Headmaster about the Transfigured acid inside the troll’s head (Dumbledore had looked down over the side of the terrace and made a gesture before returning) and then about the Weasley twins’ minds having been tampered with, carrying on a separate conversation that Harry remembered but could not process.

Harry still stood over Hermione’s body, he hadn’t moved from that spot, thinking as fast as he could through the sense of dissociation and fragmented time, was there anything he should be doing \emph{now,} any opportunities that were passing irrevocably. Some way to reduce the amount of magical omnipotence that would be required later. A temporal beacon effect to mark this instant for later time travel, if he someday found a way to travel back further than six hours. There were theories of time travel under General Relativity (which had seemed much less plausible before Harry had run across Time-Turners) and those theories said you couldn’t go back to before the time machine was built—a relativistic time machine maintained a continuous pathway through time, it didn’t teleport anything. But Harry didn’t see anything helpful he could do using spells in his lexicon, Dumbledore wasn’t being very cooperative, and in any case this was several minutes after the critical location within Time

“Harry,” the Headmaster whispered, laying his hand on Harry’s shoulder. He had vanished from where he was standing over the Weasley twins and come into existence beside Harry; George Weasley had discontinously teleported from where he was sitting to be kneeling next to his brother’s side, and Fred was now lying straight with his eyes open and wincing as he breathed. “Harry, you must go from this place.”

“Hold on,” said Harry’s voice. “I’m trying to think if there’s anything else I can do.”

The old wizard’s voice sounded helpless. “Harry—I know you do not believe in souls—but whether Hermione is watching you now, or no, I do not think she would wish for you to be like this.”

...no, it was obvious.

Harry leveled his wand at Hermione’s body—

“Harry! What are you—”

—and poured \emph{everything} down his arm into his hand—

\emph{“Frigideiro!”}

“—doing?”

“Hypothermia,” Harry said distantly, as he staggered. It’d been one of the spells he and Hermione had experimented on, a lifetime ago, so he was able to control it precisely, though it had taken a lot of power to affect that much mass. Hermione’s body should now be at almost exactly five degrees Celsius. “People have been revived from cold water after more than thirty minutes without breathing. The cold protects you from brain damage, you see, it slows everything down. There’s a saying Muggle doctors have, you’re not dead until you’re warm and dead—I think they even cool down the patient during some surgeries, if they have to stop someone’s heart for a while.”

Fred and George started sobbing.

Dumbledore’s face was already streaked with tears. “I’m sorry,” he whispered. “Harry, I’m so sorry, but you have to stop this.” The Headmaster took Harry by the shoulders and pulled on him.

Harry allowed himself to be turned away from Hermione’s body, walked forward as the Headmaster pushed him away from the blood. The Cooling Charm would buy him time. Hours at least, maybe days if he could manage to keep casting the spell on Hermione or if they stored her body somewhere cold.

Now there was time to think.
\sbreak

Minerva had seen Albus’s face and she’d known something was wrong; there had been time for her to wonder what had happened, and even who had died; her mind flashing to Alastor, to Augusta, to Arthur and Molly, all the most likely targets at the start of Voldemort’s second rise. She had thought that she had steeled herself, she had thought herself ready for the worst.

Then Albus spoke, and all the steel left her.

\emph{Not Hermione—no—}

Albus gave her a brief space to weep; and then told her that Harry Potter, who had watched Miss Granger die, had seated himself outside the infirmary storeroom where Miss Granger’s remains were being kept, refusing to move from the spot, and telling anyone who spoke to him to go away so he could think.

The only thing that had elicited any reaction from the boy was when Fawkes had tried to sing to him; Harry Potter had shrieked at the phoenix not to do that, his feelings were real, he didn’t want magic trying to \emph{heal} them like they were a disease. After that Fawkes had refused to sing again.

Albus thought that she might have the best chance of reaching Harry Potter now.

So she had to pull herself together, and clean up her face; there would be time later for private grief, when her surviving children no longer needed her.

Minerva McGonagall pulled together the dislocated pieces of herself, wiped her eyes a final time, and laid her hand on the doorknob of the infirmary section whose back storeroom was now being used, for the second time this century and for the fifth time since the castle of Hogwarts had been raised, as the resting place of a promising young student.

She opened the door.

Harry Potter’s eyes gazed at her. The boy was sitting on the floor in front of the door to the back storeroom, and holding his wand in his lap. If those eyes were grieving, if they were empty, if they were even broken, it couldn’t be seen from looking at the boy’s face. There were no dried tears on those cheeks.

“Why are you here, Professor McGonagall?” Harry Potter said. “I told the Headmaster I’d like to be left alone for a while.”

She couldn’t think of anything to say. \emph{To help you—you’re not all right –} but she didn’t know what to say, there was nothing she could imagine saying that would make things better. She hadn’t planned ahead before she’d walked into the room, having not been at her best.

“What are you thinking about?” Minerva said. It was the only sentence that came into her mind. Albus had told her that Harry had been saying, over and over, that he was thinking; and she had to get Harry talking, somehow.

Harry stared half at her and half past her, a tension coming into his face, as she held her breath.

It took a while before Harry spoke.

“I’m trying to think if there’s anything I should be doing right now,” said Harry Potter. “It’s hard, though. My mind keeps on imagining ways the past could have gone differently if I’d thought faster, and I can’t rule out that there might be a key insight in there somewhere.”

“Mr.~Potter—” she said falteringly. “Harry, I don’t think it’s healthy for you to be—thinking like that—”

“I disagree. It’s not thinking that gets people killed.” The words were spoken in a level monotone, as though reciting lines from a book.

“Harry,” she said, hardly even thinking as she said it, “there’s nothing you could have done—”

Something flickered in Harry’s expression. His eyes seemed to focus on her for the first time.

“Nothing I could have \emph{done?”} Harry’s voice rose on the last word. \emph{“Nothing I could have DONE? I’ve lost track of how many different ways I could’ve saved her! If I’d asked to have us all given communications mirrors! If I’d insisted on Hermione being taken out of Hogwarts and put in a school that isn’t insane! If I’d snuck out immediately instead of trying to argue with normal people! If I’d remembered the Patronus earlier! If I’d thought through possible emergencies and trained myself to think about Patronuses earlier! Even at the very last minute it might not have been too late! I killed the troll and turned to her and she was still ALIVE and I just knelt next to her listening to her last words like an IDIOT instead of casting the Patronus again and calling Dumbledore to send Fawkes!} Or if I’d just approached the whole problem from a different angle—if I’d looked for a student with a Time-Turner to send a message back in time \emph{before} I found out about anything happening to her, instead of ending up with an outcome that can’t be altered—I \emph{asked} the Headmaster to go back and save Hermione and then fake everything, fake the dead body, edit everyone’s memories, but Dumbledore said that he tried something like that once and it didn’t work and he lost another friend instead. Or if I’d—if I’d only gone with—if, that night—”

Harry pressed his hands over his face, and when he removed them again, his face was calm and composed once more.

“Anyway,” said Harry Potter, now in a monotone again, “I don’t want to repeat that mistake, so I’m going to spend until dinnertime thinking if there’s anything I should be doing. If I haven’t thought of anything by then I’ll go to dinner and eat. Now please go away.”

She was aware now that tears were sliding down her cheeks, again. “Harry—Harry, you have to believe that this isn’t your fault!”

“Of course it’s my fault. There’s no one else here who could be responsible for anything.”

“No! You-Know-Who killed Hermione!” She was hardly aware of what she was saying, that she hadn’t screened the room against who might be listening. “Not you! No matter what else you could’ve done, it’s not you who killed her, it was Voldemort! If you can’t believe that you’ll go mad, Harry!”

“That’s not how responsibility works, Professor.” Harry’s voice was patient, like he was explaining things to a child who was certain not to understand. He wasn’t looking at her anymore, just staring off at the wall to her right side. “When you do a fault analysis, there’s no point in assigning fault to a part of the system you can’t change afterward, it’s like stepping off a cliff and blaming gravity. Gravity isn’t going to change next time. There’s no point in trying to allocate responsibility to people who aren’t going to alter their actions. Once you look at it from that perspective, you realize that allocating blame never helps anything unless you blame yourself, because you’re the only one whose actions you can change by putting blame there. That’s why Dumbledore has his room full of broken wands. He understands that part, at least.”

Some distant part of her mind made a note to wait until much later and then speak sharply to the Headmaster about what he was showing to impressionable young children. She might even scream at him this time. She’d been thinking about screaming at him anyway, because of Miss Granger—

“You’re \emph{not} responsible,” she said, though her voice trembled. “It’s the Professors—it’s us who are responsible for student safety, not you.”

Harry’s eyes flicked back to her. “\emph{You’re} responsible?” There was a tightness in the voice. “You want me to hold you responsible, Professor McGonagall?”

She raised her chin and nodded. It would be better, by far, than Harry blaming himself.

The boy pushed himself up from where he was sitting on the floor, and took a step forward. “All right, then,” Harry said in a monotone. “I tried to do the sensible thing, when I saw Hermione was missing and that none of the Professors knew. I asked for a seventh-year student to go with me on a broomstick and protect me while we looked for Hermione. I asked for help. I begged for help. And nobody helped me. Because you gave everyone an absolute order to stay in one place or they’d be expelled, no excuses. No matter what else Dumbledore gets wrong, he at least thinks of his students as people, not animals that have to be herded into a pen and kept from wandering out. You knew you weren’t any good at military thinking, your first idea was to have us walking through the hallways, you knew some students there were better than you at strategy and tactics, and you still nailed us down in one room without any discretionary judgment. So when something you didn’t foresee happened and it would’ve made perfect sense to send out a seventh-year student on a fast broom to look for Hermione Granger, the students knew you wouldn’t understand or forgive. They weren’t afraid of the troll, they were afraid of you. The discipline, the conformity, the \emph{cowardice} that you instilled in them delayed me just long enough for Hermione to die. Not that I should’ve tried asking for help from normal people, of course, and I will change and be less stupid next time. But if I were dumb enough to allocate responsibility to someone who isn’t me, that’s what I’d say.”

Tears were streaming down her cheeks.

“That’s what I’d tell you if I thought you could be responsible for anything. But normal people don’t choose on the basis of consequences, they just play roles. There’s a picture in your head of a stern disciplinarian and you do whatever that picture would do, whether or not it makes any sense. A stern disciplinarian would order the students back to their rooms, even if there was a troll roaming the hallways. A stern disciplinarian would order students not to leave the Hall on pain of expulsion. And the little picture of Professor McGonagall that you have in your head can’t learn from experience or change herself, so there isn’t any point to this conversation. People like you aren’t responsible for anything, people like me are, and when we fail there’s no one else to blame.”

The boy strode forward to stand directly before her. His hand darted beneath his robes, brought forth the golden sphere that was the Ministry-issued protective shell of his Time Turner. He spoke in a dead, level voice without any emphasis. “This could’ve saved Hermione, if I’d been able to use it. But you thought it was your role to shut me down and get in my way. Nobody has died in Hogwarts in fifty years, you said that when you locked it, do you remember? I should’ve asked again after Bellatrix Black got loose from Azkaban, or after Hermione got framed for attempted murder. But I forgot because I was stupid. Please unlock it now before any of my other friends die.”

Unable to speak, she brought forth her wand and did so, releasing the time-keyed enchantment she’d laced into the shell’s lock.

Harry Potter flipped open the golden shell, looked at the tiny glass hourglass within its circles, nodded, and then snapped the case shut. “Thank you. Now go away.” The boy’s voice cracked again. “I have to think.”
\sbreak

She closed the door behind her, an awful and still mostly-muffled sound escaping her throat—

Albus shimmered into existence beside her, taking on a brief garish hue as the Disillusionment wore off.

She did not jump, quite. “I’ve told you, stop doing that,” Minerva said. Her voice sounded dull in her own ears. “That was private.”

Albus flickered his fingers at the door behind her. “I was afraid Mr.~Potter might do you some harm.” The Headmaster paused, then said quietly, “I am very surprised that you stood there and took that.”

“All I had to do was say ‘Mr.~Potter’, and he would have stopped.” Her voice had dropped almost to a whisper. “Just that, and he would have stopped. And then he would have had no one to say those awful things to, no one at all.”

“I thought Mr.~Potter’s remarks were entirely unfair and undeserved,” Albus said.

“If it had been you, Albus, you would not have threatened to expel anyone leaving the room. Can you honestly tell me otherwise?”

Albus’s brows rose. “Your role in this disaster was tiny, your decisions quite sensible at the time, and it is only Harry Potter’s perfect hindsight that lets him imagine otherwise. Surely you are wiser than to blame yourself for this, Minerva.”

She knew perfectly well that Albus would be placing a picture of Hermione in that awful room of his, that it would occupy a place of honor. Albus would hold \emph{himself} responsible, she was certain, even though he hadn’t even been in Hogwarts at the time. But not her.

\emph{So you also don’t think it’s worth the trouble of holding me responsible...}

She slumped against the nearest wall, trying not to let the tears emerge again; she’d never seen Albus weep save thrice. “You have always believed in your students, as I never have. They would not have been afraid of you. They would have known you would understand.”

“Minerva—”

“I am not fit to succeed you as Headmistress. We both know it.”

“You are wrong,” Albus said quietly. “When the time comes, you will be the forty-fifth Headmistress of Hogwarts and you will do an excellent job of it.”

She shook her head. “What now, Albus? If he will not listen to me, then who?”
\sbreak

It was perhaps half an hour later. The boy still guarded the door to where his best friend’s body lay, sitting his vigil. He was staring downward, at his wand as it lay in his hands. Sometimes his face screwed up in thought, at other times it relaxed.

Although the door did not open, and there was no sound, the boy looked up. He composed his face. His voice, when he spoke, was dull. “I don’t want company.”

The door opened.

The Defense Professor of Hogwarts entered into the room and shut the door behind him, taking up careful position in a corner between two walls, as far away from the boy as the room permitted. A sharp sense of catastrophe had risen in the air between the two of them, and hung there unchanging.

“Why are you here?” said the boy.

The man tilted his head slightly. Pale eyes examined the boy as though he were a specimen of life from a distant planet, and correspondingly dangerous.

“I’ve come to apologize, Mr.~Potter,” the man said quietly.

“Apologize for what?” the boy said. “Why, what could \emph{you} have done to prevent Hermione’s death?”

“I should have thought to check for the presence of yourself, Mr.~Longbottom, and Miss Granger, all of whom were obvious next targets,” the Defense Professor said without hesitation. “Mr.~Hagrid was not mentally equipped to command the student contingent. I should have ignored the Deputy Headmistress’s request for silence, and told her to leave behind Professor Flitwick, who would have been better able to defend the students from any threat, and who could have maintained communication via Patronus.”

“Correct.” The boy’s voice was razor-sharp. “I’d forgotten there was someone else in Hogwarts who could be responsible for things. So why didn’t you think of it, Professor? Because I don’t believe that \emph{you} were stupid.”

There was a pause, and the boy’s fingers whitened on his wand.

“You did not think of it either, Mr.~Potter, at the time.” There was a weariness in the Defense Professor’s voice. “I am smarter than you. I think faster than you. I am more experienced than you. But the gap between the two of us is not the same as the gap between us and them. If you can miss something, then so can I.” The man’s lips twisted. “You see, I deduced at once that the troll was but a distraction from some other matter, and of no great importance in itself. So long as nobody sent the students wandering pointlessly through the halls, or uncaringly dispatched the young Slytherins to those very dungeons where the troll had been spotted.”

The boy did not seem to relax. “I suppose that is plausible.”

“In any case,” said the man, “if there is anyone who can be said to be responsible for Miss Granger’s death, it is myself, not you. It is I, not you, who should have—”

“I perceive that you have spoken to Professor McGonagall and that she has given you a script to follow.” The boy did not bother keeping the bitterness from his voice. “If you have something to say to me, Professor, say it without the masks.”

There was a pause.

“As you wish,” the Defense Professor said emotionlessly. The pale eyes stayed keen and sharp. “I do regret that the girl is dead. She was a good student in my Defense class, and could have been an ally to you later. I would wish to console you for your loss, but I cannot see how to go about doing so. Naturally, if I find the ones responsible I shall kill them. You are welcome to join in should circumstances permit.”

“How touching,” the boy said, his voice cool. “You are not claiming to have liked Hermione, then?”

“Her charms were lost on me, I suspect. I no longer form such bonds easily.”

The boy nodded. “Thank you for being honest. Is that all, Professor?”

There was a pause.

“The castle is scarred, now,” said the man standing in the corner.

“What?”

“When a certain ancient device in my possession informed me that Miss Granger was on the verge of death, I cast that spell of cursed fire of which I once spoke. I burned through some walls and floors so that my broomstick could take a more direct path.” The man still spoke tonelessly. “Hogwarts will not heal such wounds easily, if at all. I suppose it will be necessary to patch over the holes with lesser conjurations. I regret that now, since I was in any case too late.”

“Ah,” said the boy. He closed his eyes briefly. “You did want to save her. You wanted it so strongly that you made some sort of actual effort. I suppose your mind, if not theirs, would be capable of that.”

A brief, dry smile from the man.

“Thank you for that, Professor. But I would like to be left alone now until dinnertime. You of all people will understand. Is that all?”

“Not quite,” the man said. A tinge of sardonic dryness now returned to his voice. “You see, based on recent experiences, I am concerned that you may now intend to do something extremely foolish.”

“Such as what?” said the boy.

“I am not quite sure. Perhaps you have decided that a universe without Miss Granger is devoid of value, and should be destroyed for the insults it has dealt you.”

The boy smiled without any humor. “Your own issues are showing, Professor. I don’t really go in for that sort of thing. Did you, at some point?”

“Not particularly. I have no great fondness for the universe, but I do live there.”

There was a pause.

“What are you planning, Mr.~Potter?” said the man in the corner. “You have come to some significant resolution, though you are trying to hide it from me. What do you now intend?”

The boy shook his head. “I’m still thinking, and would like to be left alone to do it.”

“I recall an offer you once made to me, some months ago,” said the Defense Professor. “Do you want someone intelligent to talk to? I will understand if you are not pleasant to be around.”

The boy shook his head again. “No, thank you.”

“Well, then,” said the Defense Professor. “What about someone who is powerful and not particularly bound by naive scruples?”

There was a hesitation, and then the boy once more shook his head.

“Someone who is knowledgeable of much secret lore, and magics that some might consider to be unnatural?”

There was a slight narrowing of the boy’s eyes, so imperceptible that someone else might not have—

“I see,” said the Defense Professor. “Go ahead and ask me about it, then. I give you my word that I will repeat nothing of it to the others.”

The boy took a while to speak, and when he did it was in a cracked voice.

“I mean to bring Hermione back. Because there isn’t an afterlife, and I’m not about to just let her—just \emph{not be}—”

The boy pressed his hands over his face, and when he withdrew them, he once more seemed as dispassionate as the man standing in the corner.

The Defense Professor’s eyes were abstract, and faintly puzzled.

“How?” the man said finally.

“However I have to.”

There was another pause.

“Regardless of the risks,” the man in the corner said. “Regardless of how dangerous the magic required to accomplish it.”

“Yes.”

The Defense Professor’s eyes were thoughtful. “But what general approach did you have in mind? I presume that turning her corpse into an Inferius is not what you—”

“Would she be able to think?” the boy said. “Would her body still decay?”

“No, and yes.”

“Then no.”

“What of the Resurrection Stone of Cadmus Peverell, if it could be obtained for you?”

The boy shook his head. “I don’t want an illusion of Hermione drawn from my memories. I want her to be able to \emph{live} her \emph{life—}” the boy’s voice cracked. “I haven’t decided yet on an object-level angle of attack. If I have to brute-force the problem by acquiring enough power and knowledge to just \emph{make it happen}, I will.”

Another pause.

“And to go about \emph{that,}” the man in the corner said, “you will use your favorite tool, science.”

“Of course.”

The Defense Professor exhaled, almost like a sigh. “I suppose that makes sense of it.”

“Are you willing to help, or not?” the boy said.

“What help do you seek?”

“Magic. Where does it come from?”

“I do not know,” said the man.

“And neither does anyone else?”

“Oh, the situation is far worse than that, Mr.~Potter. There is hardly a scholar of the esoteric who has not unraveled the nature of magic, and every one of them believes something different.”

“Where do new spells come from? I keep reading about someone who invented a spell to do something-or-other but there’s no mention of \emph{how}.”

A shrug of robed shoulders. “Where do new books come from, Mr.~Potter? Those who read many books sometimes become able to write them in turn. How? No one knows.”

“There are books on how to write—”

“Reading them will not make you a famous playwright. After all such advice is accounted for, what remains is mystery. The invention of new spells is a similar mystery of purer form.” The man’s head tilted. “Such endeavors are dangerous. The saying is that one should either not have children, or else wait until after they are grown. There is a reason why so many innovators seem to hail from Gryffindor, rather than Ravenclaw as might be expected.”

“And the more powerful sorts of magics?” the boy said.

“A legendary wizard might invent one sacrificial ritual in his life, and pass on the knowledge to his heirs. To try inventing five such would be suicide. That is why wizards of true power are those who have acquired ancient lore.”

The boy nodded distantly. “So much for the direct solution, then. It would’ve been nice to just invent a spell for ‘Raise Dead’, ‘Become God’ or ‘Summon Terminal’. Do you know anything about Atlantis?”

“Only what any scholar knows,” the man said dryly. “If you would like to hear about the top eighteen standard theories—do not glare at me, Mr.~Potter. If it were that simple, I would have done it many years earlier.”

“I understand. Sorry.”

There was a time of silence. The Defense Professor’s gaze rested on the boy, the boy stared off seemingly at nothing.

“There’s some magics I mean to learn. Spells I could’ve used earlier today, if I’d thought to study them beforehand.” The boy’s voice was cold. “Spells I’ll need, if this sort of thing goes on happening. Most I expect I can just look up. Some I expect I can’t.”

The Defense Professor inclined his head. “I shall teach you almost any magic you wish to know, Mr.~Potter. I do have some limits, but you may always ask. But what specifically do you seek? You lack the raw power for the Killing Curse and most other spells deemed forbidden—”

“That spell of cursed fire. I don’t suppose it’s a sacrificial ritual that even a child could use, if he dared?”

The Defense Professor’s lips twitched. “It requires the permanent sacrifice of a drop of blood; your body would be lighter by that drop of blood, from that day forward. Not the sort of thing one would wish to do often, Mr.~Potter. Strength of will is demanded for the cursed fire not to turn upon you and consume you; the usual practice is to first test one’s will in lesser trials. And although it is not a primary element of the ritual, I am afraid that it does require more magic than you shall possess for another few years.”

“Pity,” the boy said. “It would’ve been nice to see the look on the enemy’s face the next time they tried using a troll.”

The Defense Professor inclined his head, his lips twitching again.

“What about Memory Charms? The Weasley twins were acting oddly and the Headmaster said he thinks they’ve been Obliviated. It seems to be one of the enemy’s favorite tricks.”

“Rule Eight,” said the Defense Professor. “Any technique which is good enough to defeat me once is good enough to learn myself.”

The boy smiled humorlessly. “And I once heard about an adult casting Obliviate while she was almost completely drained, so it must not take too much magic to cast. It’s not even considered Unforgiveable, though I can’t imagine why not. If I could’ve made Mr.~Hagrid remember a different set of orders—”

“It is not that straightforward,” said the Defense Professor. “You are not powerful enough to use the False Memory Charm, and even a simple Obliviation will stretch the edge of your current stamina. It is a dangerous art, illegal to use without Ministry authorization, and I would caution you not to use it under circumstances where it would be inconvenient to accidentally erase ten years of someone’s life. I wish I could promise you that I would obtain one of those highly guarded tomes from the Department of Mysteries, and pass it to you beneath a disguised cover. But what I must actually tell you is that you will find the standard introductory text in the north-northwest stacks of the main Hogwarts library, filed under M.”

“Seriously,” the boy said flatly.

“Indeed.”

“Thank you for your guidance, Professor.”

“Your creativity has become a great deal more practical, Mr.~Potter, since I have known you.”

“Thank you for the compliment.” The boy did not look up from where he was again gazing down at the wand held between his hands. “I would like to go back to thinking now. Please explain to them on my behalf what happens if I am disturbed.”
\sbreak

The door to the storeroom clicked open, and Professor Quirrell stepped out. His face had a dead, emotionless look to it; she would have said that it reminded her of Severus, though Severus had never looked quite like that.

Even as the door clicked shut again, Minerva had thrown up a wordless Quieting barrier. The words spilled forth from her rapidly: “How did it go—you were in there for a while—is Harry talking now?”

Professor Quirrell paced swiftly across the room to the far wall near the entrance, looked back at her. The emotionlessness slid off his face, as though he were taking off a mask, leaving behind someone very grim. “I spoke to Mr.~Potter as he expected me to speak, and avoided saying things that would annoy him. I do not think it consoled him. I do not think I have the knack.”

“Thank you—it is good that he spoke at all—” She hesitated. “What did Mr.~Potter say?”

“I am afraid that I promised him not to speak of it. And now... I think that I must visit the Hogwarts library.”

“The \emph{library?}”

“Yes,” Professor Quirrell said. An uncharacteristic tension had come into his voice. “I intend to strengthen the security upon the Restricted Section with certain precautions of my own devising. The current wards are a joke. And Mr.~Potter must be kept out of the Restricted Section \emph{at all costs.}”

She stared at the Defense Professor, her heart suddenly in her throat.

Professor Quirrell continued speaking. “You will \emph{not} tell the boy that I have said this much to you. You will confirm to Flitwick and Vector that the boy is to be diverted by the usual evasions if he asks precocious questions about spell creation. And though it is not my own area of expertise, Deputy Headmistress, if there is any way you can imagine to convince the boy to stop sinking further into his grief and madness—any way at all to undo the resolutions he is coming to—then I suggest you resort to it \emph{immediately}.”
