\chapter*{Preface by Eliezer Yudkowsky}
% from http://www.hpmor.com/chapter/1
% This is not a strict single-point-of-departure fic - there exists a primary point of departure, at some point in the past, but also other alterations. The best term I've heard for this fic is "parallel universe".

The text contains many clues: obvious clues, not-so-obvious clues, truly obscure hints which I was shocked to see some readers successfully decode, and massive evidence left out in plain sight. This is a rationalist story; its mysteries are solvable, and meant to be solved.

The pacing of the story is that of serial fiction, i.e., that of a TV show running for a predetermined number of seasons, whose episodes are individually plotted but with an overall arc building to a final conclusion.

% The story has been corrected to British English up to Ch. 17, and further Britpicking is currently in progress (see the /HPMOR subreddit).

All science mentioned is real science. But please keep in mind that, beyond the realm of science, the views of the characters may not be those of the author. Not everything the protagonist does is a lesson in wisdom, and advice offered by darker characters may be untrustworthy or dangerously double-edged.

% TODO: better word?
\chapter*{Introduction}
% from http://www.hpmor.com/chapter/22

\section*{Something, somewhere, somewhen, must have happened differently…}

% TODO: improve layout
\begin{itemize}
\item PETUNIA EVANS married Michael Verres, a Professor of Biochemistry at Oxford.
\item HARRY JAMES POTTER-EVANS-VERRES grew up in a house filled to the brim with books. He once bit a math teacher who didn't know what a logarithm was. He's read \emph{Godel, Escher, Bach} and \emph{Judgment Under Uncertainty: Heuristics and Biases} and volume one of \emph{The Feynman Lectures on Physics}. And despite what everyone who's met him seems to fear, he doesn't want to become the next Dark Lord. He was raised better than that. He wants to discover the laws of magic and become a god.
\item HERMIONE GRANGER is doing better than him in every class except broomstick riding.
\item DRACO MALFOY is exactly what you would expect an eleven-year-old boy to be like if Darth Vader were his doting father.
\item PROFESSOR QUIRRELL is living his lifelong dream of teaching Defense Against the Dark Arts, or as he prefers to call his class, Battle Magic. His students are all wondering what's going to go wrong with the Defense Professor this time.
\item DUMBLEDORE is either insane, or playing some vastly deeper game which involved setting fire to a chicken.
\item DEPUTY HEADMISTRESS MINERVA MCGONAGALL needs to go off somewhere private and scream for a while.
\end{itemize}

\begin{center}
Presenting:

HARRY POTTER AND THE METHODS OF RATIONALITY

You ain't guessin' where this one's going.
\end{center}

\section*{Some notes}
The opinions of characters in this story are not necessarily those of the author. What warm!Harry thinks is \emph{often} meant as a good pattern to follow, especially if Harry thinks about how he can cite scientific studies to back up a particular principle. But not everything Harry does or thinks is a good idea. That wouldn't work as a story. And the less warm characters may sometimes have valuable lessons to offer, but those lessons may also be dangerously double-edged.

If you haven't visited \url{http://hpmor.com}, don't forget to do that at some point; otherwise you'll miss out on the fan art, how to learn everything Harry knows, and more.

If you haven't just enjoyed this fic, but learned something from it, then please consider blogging it or tweeting it. A work like this only does as much good as there are people who read it.

%  LocalWords:
