\partchapter{Humanism}{II}

\lettrine{“F}{awkes,”} said Albus Dumbledore, his voice cracking, “help him, please—”

A brilliant creature of red-gold shuffled into the field of vision, looking down quizzically; and it began to croon.

The meaningless chirps slid off the emptiness, there was nothing onto which they could hold.

“You’re noisy,” said the voice, “you should die.”

“Chocolate,” Albus Dumbledore said, “you need chocolate, and your friends—but I dare not take you back—”

Then a shining raven came, and spoke in Professor Flitwick’s voice; whereupon Albus Dumbledore gasped in sudden comprehension, and cursed aloud at his own stupidity.

The empty thing laughed at that, for it had retained the capacity to be amused.

And a moment later they had all vanished in another flash of fire.
\sbreak
It was only a moment, it seemed, between when Flitwick’s raven had flown to elsewhere, and when Albus Dumbledore reappeared in another crack of red and golden fire with Harry in his arms; but somehow in that time Hermione had already managed to fill her hands with chocolate.

Before Hermione even got there, chocolate had zoomed off the table and straight into Harry’s mouth, which a tiny part of her mind said was unfair, \emph{he’d} gotten a chance to do it for \emph{her—}

Harry spat the chocolate back out again.

“Go away,” said a voice so empty it wasn’t even cold.

...

Everything seemed to freeze, everyone who had been moving toward Harry halted, all movements broken by the shock of those two dead words.

Then: “No,” said Albus Dumbledore, “I will not,” and time resumed again, even as another piece of chocolate zoomed off the table and into Harry’s mouth.

Hermione was close enough now that she could see Harry’s expression become more hateful, as his mouth chewed with a mechanical, unnatural rhythm.

The Headmaster’s voice was grim as iron. “Filius, call Minerva, tell her she must come at speed.”

Professor Flitwick whispered to his silver raven, and it flew into the air and vanished.

Another piece of chocolate floated into Harry’s mouth, and the mechanical chewing continued.

There were more students gathering around where the Headmaster watched over Harry with grim eyes: Neville, Seamus, Dean, Lavender, Ernie, Terry, Anthony, none of them daring to approach any closer than Hermione had.

“What can we do?” said Dean in a trembling voice.

“Back off and give him more space—” said the dry voice of Professor Quirrell.

“No!” interrupted the Headmaster. “Let him be surrounded by his friends.”

Harry swallowed his chocolate, and said in that empty voice, “They’re stupid. They should die\emph{mmmppphhh}” as another piece of chocolate entered his mouth.

Hermione saw the looks of shock that crossed their faces.

“He doesn’t mean it, does he?” Seamus said it like he was begging.

“You don’t understand,” Hermione said, her voice breaking, “\emph{that’s not Harry—}” and she shut up before she said anything more, but she \emph{had} to say that much.

She saw from the look on his face that Neville understood, and she also saw that the others didn’t. If Harry had really never thought anything like that, then being exposed to a Dementor for less than a minute wouldn’t have made him say it. That’s what they were probably thinking.

Less than a minute of Dementor exposure couldn’t create a whole new evil person inside you out of nothing.

But if that person was \emph{already there}—

\emph{Does the Headmaster know?}

Hermione looked up at the Headmaster, and found that Albus Dumbledore was gazing at \emph{her}, and that his blue eyes had grown suddenly piercing—

Words came into her mind.

\emph{Do not speak of it,} said the will of Dumbledore to her.

\emph{You know,} thought Hermione. \emph{About his dark side.}

\emph{I know. But this is beyond even that. Fawkes’s song cannot reach him, where he is lost.}

\emph{What can we—}

\emph{I have a plan,} sent the Headmaster. \emph{Patience.}

Something about the tenor of that thought made Hermione nervous. \emph{What sort of plan?}

\emph{It is better that you not know,} sent the Headmaster.

Now Hermione was getting \emph{really} nervous. She didn’t know how \emph{much} the Headmaster knew about Harry’s dark side—

\emph{A fair point,} sent the Headmaster. \emph{I am about to tell you; steel yourself so as not to react. Are you ready? Good. I am going to pretend to cast the Killing Curse on Professor McGonagall—\shout{Do not react}, Hermione!}

That took work. The Headmaster really was crazy! That wouldn’t bring Harry \emph{out} of his dark side, Harry would go \emph{completely berserk}, he’d \emph{kill} the Headmaster—

\emph{But that is not true darkness,} sent Albus Dumbledore. \emph{That is protectiveness, that is love. Fawkes will be able to reach him, then. And when Harry sees that Minerva is alive after all, it will return him fully.}

The thought came to Hermione—

\emph{I doubt that will work,} sent the Headmaster, \emph{and you may not like the way he reacts if you try. But you may try if you wish.}

She hadn’t really meant that seriously! It was too—

Then her eyes moved, breaking gaze with the Headmaster, going to the boy looking around with empty, despising eyes as his mouth kept chewing and swallowing bar after bar of chocolate without effect. Her heart wrenched, and suddenly a lot of things didn’t seem to matter, only that there was a chance.
\sbreak
There was a compulsion to chew and swallow chocolate. The response to compulsion was killing.

People had gathered around and stared. That was annoying. The response to annoyance was killing.

Other people were chattering in the background. That was insolent. The response to insolence was to inflict pain, but since none of them were useful, killing them would be simpler.

Killing all those people would be difficult. But many of them didn’t trust Quirrell, who was strong. Finding exactly the right trigger could cause them all to kill each other.

Then a person leaned over into the field of vision and did something completely strange, something that belonged to a foreign mode of thought, for which there was only a single response stored anywhere—
\sbreak
She heard the gasps around her, and they didn’t matter, she maintained the kiss on those chocolate-smeared lips as the tears welled in her eyes.

And Harry’s arms came up and pushed her away, and his lips yelled, “\emph{I told you, no kissing!}”
\sbreak
“I think he’ll be all right now,” the Headmaster said, looking at where Harry was crying in great wretched sobs as Fawkes crooned over him. “Excellently done, Miss Granger. Do you know, not even I would have expected that to actually work?”

The phoenix’s song wasn’t meant for her, Hermione knew, but she could still be soothed by it, which she needed, because her life was officially over.

