\chapter{Noticing Confusion}

\lettrine{P}{rofessor} Quirrell’s office hours consisted of 11:40 to 11:55\AM on Thursday. That was for all of his students in all years. It cost a Quirrell point just to knock on the door, and if he didn’t think your reason was worth his time, you would lose another fifty.

Harry knocked on the door.

There was a pause. Then a biting voice said, “I suppose you may as well come in, Mr.~Potter.”

And before Harry could touch the doorknob, the door slammed open, hitting the wall with a sharp crack that sounded like something might have broken in the wood, or the stone, or both.

Professor Quirrell was leaning back in his chair and reading a suspiciously old-looking book, bound in night-blue leather with silver runes on the spine. His eyes had not moved from the pages. “I am not in a good mood, Mr.~Potter. And when I am not a good mood, I am not a pleasant person to be around. For your own sake, conduct your business quickly and depart.”

A cold chill seeped from the room, as though it contained something that cast darkness the way lamps cast light, and which hadn’t been fully shaded.

Harry was a bit taken aback. \emph{Not in a good mood} didn’t quite seem to cover it. What could be bothering Professor Quirrell this much...?

Well, you didn’t just walk out on friends when they were feeling down. Harry cautiously advanced into the room. “Is there anything I can do to help—”

“No,” said Professor Quirrell, still not looking up from the book.

“I mean, if you’ve been dealing with idiots and want someone sane to talk to...”

There was a surprisingly long pause.

Professor Quirrell slammed the book shut and it vanished with a small whispering sound. He looked up, then, and Harry flinched.

“I suppose an intelligent conversation would be pleasant for \emph{me} at this point,” said Professor Quirrell in the same biting tone that had invited Harry to enter. “\emph{You} are not likely to find it so, be warned.”

Harry drew a deep breath. “I promise I won’t mind if you snap at me. What happened?”

The cold in the room seemed to deepen. “A sixth-year Gryffindor cast a curse at one of my more promising students, a sixth-year Slytherin.”

Harry swallowed. “What...\ sort of curse?”

And the fury on Professor Quirrell’s face was no longer contained. “Why bother to ask an unimportant question like that, Mr.~Potter? Our friend the sixth-year Gryffindor did not think it was important!”

“Are you \emph{serious?}” Harry said before he could stop himself.

“No, I’m in a terrible mood today for no particular reason. \emph{Yes I’m serious, you fool!} He didn’t know. He \emph{actually didn’t know.} I didn’t believe it until the Aurors confirmed it under Veritaserum. He is in his \emph{sixth year at Hogwarts} and he cast a high-level Dark curse \emph{without knowing what it did.}”

“You don’t mean,” Harry said, “that he was \emph{mistaken} about what it did, that he somehow read the wrong spell description—”

“All he knew was that it was meant to be directed at an enemy. He \emph{knew} that was all he knew.”

And that had been enough to cast the spell. “I do not understand how anything with that small a brain could walk upright.”

“Indeed, Mr.~Potter,” said Professor Quirrell.

There was a pause. Professor Quirrell leaned forward and picked up the silver inkwell from his desk, turning it around in his hands, staring at it as though wondering how he could go about torturing an inkwell to death.

“Was the sixth-year Slytherin seriously hurt?” said Harry.

“Yes.”

“Was the sixth-year Gryffindor raised by Muggles?”

“\emph{Yes.}”

“Is Dumbledore refusing to expel him because the poor boy didn’t know?”

Professor Quirrell’s hands whitened on the inkwell. “\emph{Do you have a point, Mr.~Potter, or are you just stating the obvious?}”

“Professor Quirrell,” said Harry gravely, “all the Muggle-raised students in Hogwarts need a safety lecture in which they are told the things so ridiculously obvious that no wizardborn would ever think to mention them. Don’t cast curses if you don’t know what they do, if you discover something dangerous don’t tell the world about it, don’t brew high-level potions without supervision in a bathroom, the reason why there are underage magic laws, all the basics.”

“Why?” said Professor Quirrell. “Let the stupid ones die before they breed.”

“If you don’t mind losing a few sixth-year Slytherins along with them.”

The inkwell caught fire in Professor Quirrell’s hands and burned with a terrible slowness, hideous black-orange flames tearing at the metal and seeming to take tiny bites from it, the silver twisting as it melted, as though it were trying and failing to escape. There was a tinny shrieking sound, as though the metal were screaming.

“I suppose you are right,” Professor Quirrell said with a resigned smile. “I shall design a lecture to ensure that Muggleborns who are too stupid to live do not take anyone valuable with them as they depart.”

The inkwell went on screaming and burning in Professor Quirrell’s hands, tiny droplets of metal, still on fire, now dripping to the desk, as though the inkwell were crying.

“You’re not running away,” observed Professor Quirrell.

Harry opened his mouth—

“If you’re about to say you’re not scared of me,” said Professor Quirrell, “\emph{don’t.}”

“You are the scariest person I know,” Harry said, “and one of the top reasons for that is your control. I simply can’t imagine hearing that you’d hurt someone you had not made a deliberate decision to hurt.”

The fire in Professor Quirrell’s hands winked out, and he carefully placed the ruined inkwell on his desk. “You say the nicest things, Mr.~Potter. Have you been taking lessons in flattery? From, perhaps, Mr.~Malfoy?”

Harry kept his expression blank, and realized one second too late that it might as well have been a signed confession. Professor Quirrell didn’t care what your expression looked like, he cared which states of mind made it likely.

“I see,” said Professor Quirrell. “Mr.~Malfoy is a useful friend to have, Mr.~Potter, and there is much he can teach you, but I hope you have not made the mistake of trusting him with too many confidences.”

“He knows nothing which I fear becoming known,” said Harry.

“Well done,” said Professor Quirrell, smiling slightly. “So what was your original business here?”

“I think I’m done with the preliminary exercises in Occlumency and ready for the tutor.”

Professor Quirrell nodded. “I shall conduct you to Gringotts this Sunday.” He paused, looking at Harry, and smiled. “And we might even make it a little outing, if you like. I’ve just had a pleasant thought.”

Harry nodded, smiling back.

As Harry left the office, he heard Professor Quirrell humming a small tune.

Harry was glad he’d been been able to cheer him up.
\sbreak
That Sunday there seemed to be a rather large number of people whispering in the hallways, at least when Harry Potter walked past them.

And a lot of pointed fingers.

And a great deal of female giggling.

It had started at breakfast, when someone had asked Harry if he’d heard the news, and Harry had quickly interrupted and said that if the news was written by Rita Skeeter then he didn’t want to \emph{hear} about it, he wanted to read it in the paper himself.

It had then developed that not many students at Hogwarts got copies of the \emph{Daily Prophet,} and that the copies which had not already been bought up from their owners were being passed around in some sort of complicated order and nobody really knew who had one at the moment...

So Harry had used a Quieting Charm and gone on to eat his breakfast, trusting to his seat-mates to wave off the many, many questioners, and doing his best to ignore the incredulity, the laughter, the congratulatory smiles, the pitying looks, the fearful glances, and the dropped plates as new people came down for breakfast and heard.

Harry was feeling \emph{rather} curious, but it \emph{really} wouldn’t have done to spoil the artistry by hearing it secondhand.

He’d done homework in the safety of his trunk for the next couple of hours, after telling his dormmates to come get him if anyone found him an original newspaper.

Harry was still ignorant at 10\AM, when he’d left Hogwarts in a carriage with Professor Quirrell, who was in the front right, and currently slumped over in zombie-mode. Harry was sitting diagonally across, as far away as the carriage allowed, in the back left. Even so, Harry had a constant feeling of doom as the carriage rattled over a small path through a section of non-forbidden forest. It made it a bit hard to read, especially since the material was difficult, and Harry suddenly wished he was reading one of his childhood science fiction books instead—

“We’re outside the wards, Mr.~Potter,” said Professor Quirrell’s voice from the front. “Time to go.”

Professor Quirrell carefully disembarked from the carriage, bracing himself as he stepped down. Harry, on his own side, jumped off.

Harry was wondering exactly how they’d get there when Professor Quirrell said “Catch!” and threw a bronze Knut at him, and Harry caught it without thinking.

A giant intangible hook caught at Harry’s abdomen and yanked him back, hard, only without any sense of acceleration, and an instant later Harry was standing in the middle of Diagon Alley.

(\emph{Excuse me, what?} said his brain.)

(\emph{We just teleported,} explained Harry.)

(\emph{That didn’t used to happen in the ancestral environment,} Harry’s brain complained, and disoriented him.)

Harry staggered as his feet adjusted to the brick of the street instead of the dirt of the forest corridor they had been traversing. He straightened, still dizzy, with the bustling witches and wizards seeming to sway slightly, and the cries of the shopkeepers seeming to move around in his hearing, as his brain tried to place a world to be located in.

Moments later, there was a sort of sucking-popping sound from a few paces behind Harry, and when Harry turned to look Professor Quirrell was there.

“Do you mind—” said Harry, at the same time as Professor Quirrell said, “I’m afraid I—”

Harry stopped, Professor Quirrell didn’t.

“—need to go off and set something in motion, Mr.~Potter. As it has been thoroughly explained to me that I am responsible for anything whatsoever that happens to you, I’ll be leaving you with—”

“Newsstand,” Harry said.

“Pardon?”

“Or anywhere I can buy a copy of the \emph{Daily Prophet.} Put me there and I’ll be happy.”

Shortly after, Harry had been delivered into a bookstore, accompanied by several quietly spoken, ambiguous threats. And the shopkeeper had gotten \emph{less} ambiguous threats, judging by the way he had cringed, and how his eyes now kept darting between Harry and the entrance.

If the bookstore burned down, Harry was going to stick around in the middle of the fire until Professor Quirrell got back.

Meanwhile—

Harry took a quick glance around.

The bookstore seemed rather small and shoddy, with only four rows of bookcases visible, and the nearest shelf Harry’s eyes had jumped to seemed to deal with narrow, cheaply bound books with grim titles like \emph{The Massacre of Albania in the Fifteenth Century.}

First things first. Harry stepped over to the seller’s counter.

“Pardon me,” said Harry, “One copy of the \emph{Daily Prophet,} please.”

“Five Sickles,” said the shopkeeper. “Sorry, kid, I’ve only got three left.”

Five Sickles dropped onto the counter. Harry had the feeling he could have bargained him down a couple of points, but at this point he didn’t really care.

The shopkeeper’s eyes widened and he seemed to really notice Harry for the first time. “\emph{You!}”

“\emph{Me!}”

“Is it \emph{true?} Are you \emph{really}—”

“\emph{Shut up!} Sorry, I’ve been waiting \emph{all day} to read this in the original newspaper instead of hearing about it secondhand, so please just \emph{hand it over}, all right?”

The shopkeeper stared at Harry for a moment, then wordlessly reached under the counter and passed over one folded copy of the \emph{Daily Prophet}.

The headline read:

\headline{Harry Potter\\secretly betrothed\\to Ginevra Weasley}

Harry stared.

He lifted the newspaper off the counter, softly, reverently, like he was handling an original Escher painting, and unbent it to read...

...about the evidence that had convinced Rita Skeeter.

...and some interesting further details.

...and yet more evidence.

Fred and George had cleared it with their sister first, surely? Yes, of course they had. There was a picture of Ginevra Weasley sighing longingly over what Harry could see, looking closely, was a photo of himself. That had to have been staged.

But \emph{how} on \emph{Earth...?}

Harry was sitting in a cheap folding chair, rereading the newspaper for the fourth time, when the door whispered softly and Professor Quirrell came back into the shop.

“My apologies for—\emph{what} in Merlin’s name are you reading?”

“It would seem,” said Harry, awe in his voice, “that one Mr.~Arthur Weasley was placed under the Imperius Curse by a Death Eater whom my father killed, thus creating a debt to the Noble House of Potter, which my father demanded be repaid by the hand in marriage of the recently born Ginevra Weasley. Do people actually do that sort of thing around here?”

“How could Miss Skeeter \emph{possibly} be fool enough to believe—”

And Professor Quirrell’s voice cut off.

Harry had been reading the newspaper held vertically and unfolded, which meant that Professor Quirrell, from where he was standing, could see the text underneath the headline.

The look of shock on Professor Quirrell’s face was a work of art almost on par with the newspaper itself.

“Don’t worry,” said Harry cheerfully, “it’s all fake.”

From elsewhere in the store, he heard the shopkeeper gasp. There was the sound of a stack of books falling over.

“Mr.~Potter...” Professor Quirrell said slowly, “are you \emph{sure} of that?”

“Quite sure. Shall we go?”

Professor Quirrell nodded, looking rather abstracted, and Harry folded the newspaper back up, and followed him out of the door.

For some reason Harry didn’t seem to be hearing any street noises now.

They walked in silence for thirty seconds before Professor Quirrell spoke. “Miss Skeeter viewed the original proceedings of the restricted Wizengamot session.”

“Yes.”

“The \emph{original proceedings of the Wizengamot.}”

“Yes.”

“\emph{I} would have trouble doing that.”

“Really?” said Harry. “Because if my suspicions are correct, this was done by a Hogwarts student.”

“That is beyond impossible,” Professor Quirrell said flatly. “Mr.~Potter... I regret to say that this young lady expects to marry you.”

“But \emph{that} is improbable,” said Harry. “To quote Douglas Adams, the impossible often has a kind of integrity which the merely improbable lacks.”

“I see your point,” Professor Quirrell said slowly. “But...\ no, Mr.~Potter. It may be impossible, but I can \emph{imagine} tampering with the Wizengamot proceedings. It is \emph{unimaginable} that the Grand Manager of Gringotts should affix the seal of his office in witness to a false betrothal contract, and Miss Skeeter personally verified that seal.”

“Indeed,” said Harry, “you would expect the Grand Manager of Gringotts to get involved with that much money changing hands. It seems Mr.~Weasley was greatly in debt, and so demanded an additional payment of ten thousand Galleons—”

“\emph{Ten thousand} Galleons for a \emph{Weasley?} You could buy the daughter of a Noble House for that!”

“Excuse me,” Harry said. “I really have to ask at this point, do people actually do that sort of thing around here—”

“Rarely,” said Professor Quirrell, with a frown on his face. “And not at all, I suspect, since the Dark Lord departed. I suppose that according to the newspaper, your father just paid it?”

“He didn’t have any choice,” said Harry. “Not if he wanted to fulfill the conditions of the prophecy.”

“\emph{Give me that,}” said Professor Quirrell, and the newspaper leaped out of Harry’s hand so fast that he got a paper cut.

Harry automatically put the finger in his mouth to suck on, feeling rather shocked, and turned to remonstrate with Professor Quirrell—

Professor Quirrell had stopped short in the middle of the street, and his eyes were flickering rapidly back and forth as an invisible force held the newspaper suspended before him.

Harry watched, gaping in open awe, as the newspaper opened to reveal pages two and three. And not much long after, four and five. It was like the man had cast off a pretense of mortality.

And after a troublingly short time, the paper neatly folded itself up again. Professor Quirrell plucked it from the air and tossed it to Harry, who caught it in sheer reflex; and then Professor Quirrell started walking again, and Harry automatically trudged after.

“No,” said Professor Quirrell, “that prophecy didn’t sound quite right to me either.”

Harry nodded, still stunned.

“The centaurs could have been put under an \emph{Imperius},” Professor Quirrell said, frowning, “\emph{that} seems understandable. A goblin would be immune to that and all other mental influence, but what magic can make, magic can corrupt, and it is not unthinkable that the Great Seal of Gringotts could be twisted to another’s hand. The Unspeakable could have been impersonated with Polyjuice, likewise the Bavarian seer. And with \emph{enough} effort it might be possible to tamper with the proceedings of the Wizengamot. Do you have any idea how that was done?”

“I do not have one single plausible hypothesis,” said Harry. “I do know it was done on a total budget of forty Galleons.”

Professor Quirrell stopped short and whirled on Harry. His expression was now completely incredulous. “Forty Galleons will pay a competent ward-breaker to open a path into a home you wish to burglarize! Forty \emph{thousand} Galleons \emph{might} pay a team of the greatest professional criminals in the world to tamper with the proceedings of the Wizengamot!”

Harry shrugged helplessly. “I’ll remember that the next time I want to save thirty-nine thousand, nine hundred and sixty Galleons by finding the right contractor.”

“I do not say this often,” said Professor Quirrell. “I am impressed.”

“Likewise,” said Harry.

“And who is this incredible Hogwarts student?”

“I’m afraid I couldn’t say.”

Somewhat to Harry’s surprise, Professor Quirrell made no objection to this.

They walked in the direction of the Gringotts building, thinking, for they were neither of them the sort of person who would give up on the problem without considering it for at least five minutes.

“I have a feeling,” Harry said finally, “that we’re coming at this from the wrong angle. There’s a tale I once heard about some students who came into a physics class, and the teacher showed them a large metal plate near a fire. She ordered them to feel the metal plate, and they felt that the metal nearer the fire was cooler, and the metal further away was warmer. And she said, write down your guess for why this happens. So some students wrote down ‘because of how the metal conducts heat’, and some students wrote down ‘because of how the air moves’, and no one said ‘this just seems impossible’, and the real answer was that before the students came into the room, the teacher turned the plate around.”

“Interesting,” said Professor Quirrell. “That does sound similar. Is there a moral?”

“That your strength as a rationalist is your ability to be more confused by fiction than by reality,” said Harry. “If you’re equally good at explaining any outcome, you have zero knowledge. The students thought they could use words like ‘because of heat conduction’ to explain anything, even a metal plate being cooler on the side nearer the fire. So they didn’t notice how confused they were, and that meant they couldn’t be more confused by falsehood than by truth. If you tell me that the centaurs were under the \emph{Imperius} Curse, I still have the feeling of something being not quite right. I notice that I’m still confused even after hearing your explanation.”

“Hm,” said Professor Quirrell.

They walked on further.

“I don’t suppose,” said Harry, “that it’s possible to \emph{actually} swap people into alternate universes? Like, this isn’t our own Rita Skeeter, or they temporarily sent her somewhere else?”

“If \emph{that} was possible,” Professor Quirrell said, his voice rather dry, “would I still be \emph{here?}”

And just as they were almost to the huge white front of the Gringotts building, Professor Quirrell said:

“Ah. Of \emph{course.} I see it now. Let me guess, the Weasley twins?”

“\emph{What?}” said Harry, his voice going up another octave in pitch. “\emph{How?}”

“I’m afraid I couldn’t say.”

“...That is \emph{not} fair.”

“I think it is extremely fair,” said Professor Quirrell, and they entered through the bronze doors.
\sbreak
The time was just before noon, and Harry and Professor Quirrell were seated at the foot and head of a wide, long, flat table, in a sumptuously appointed private room with thoroughly cushioned couches and chairs along the walls, and soft curtains hanging everywhere.

They were about to eat lunch in Mary’s Place, which Professor Quirrell had said was known to him as one of the best restaurants in Diagon Alley, especially for—his voice had dropped meaningfully—\emph{certain purposes.}

It was the nicest restaurant that Harry had ever been in, and it was really eating away at Harry that Professor Quirrell was treating \emph{him} to the meal.

The first part of the mission, to find an Occlumency instructor, had been a success. Professor Quirrell, smiling evilly, had told Griphook to recommend the best he knew, and not worry about the expense, since Dumbledore was paying it; and the goblin had smiled in return. There might have been a certain amount of smiling on Harry’s part as well.

The second part of the plan had been a complete failure.

Harry was not allowed to take money out of his vault without Headmaster Dumbledore or some other school official present, and Professor Quirrell had not been given the vault key. Harry’s Muggle parents could not authorize it because they were Muggles, and Muggles had around the same legal standing as children or kittens: they were cute, so if you tortured them in public you could get arrested, but they weren’t \emph{people}. Some reluctant provision had been made for recognizing the parents of Muggleborns as human in a limited sense, but Harry’s adoptive parents did not fall into that legal category.

It seemed that Harry was effectively an orphan in the eyes of the wizarding world. As such, the Headmaster of Hogwarts, or his designees \emph{within} the school system, were Harry’s guardians until he graduated. Harry \emph{could} breathe without Dumbledore’s permission, but only so long as the Headmaster did not specifically prohibit it.

Harry had then asked if he could simply \emph{tell} Griphook how to diversify his investments beyond stacks of gold coins sitting in his vault.

Griphook had stared blankly and asked what ‘diversify’ meant.

Banks, it seemed, did not make investments. Banks stored your gold coins in secure vaults for an annual fee.

The wizarding world did not have a concept of stock. Or equity. Or corporations. Businesses were run by families out of their personal vaults.

Loans were made by rich people, not banks. Though Gringotts would witness the contract, for a fee, and enforce its collection, for a much larger fee.

Good rich people let their friends borrow money and pay it back whenever. \emph{Bad} rich people charged you \emph{interest.}

There was no secondary market in loans.

Evil rich people charged you annual interest rates of at least 20\%.

Harry had stood up, turned away, and rested his head against the wall.

Harry had asked if he needed the Headmaster’s permission before he could start a bank.

Professor Quirrell had interrupted at this point, saying that it was time for lunch, and swiftly conducted a fuming Harry out of the bronze doors of Gringotts, through Diagon Alley, and to a fine restaurant called Mary’s Place, where a room had been reserved for them. The owner had looked shocked at seeing Professor Quirrell accompanied by Harry Potter, but had conducted them to the room without complaint.

And Professor Quirrell had quite deliberately announced that he would pay the bill, seeming to rather enjoy the look on Harry’s face.

“No,” said Professor Quirrell to the waitress, “we will not require menus. I will have the daily special accompanied by a bottle of Chianti, and Mr.~Potter will have the Diracawl soup to start, followed by a plate of Roopo balls, and treacle pudding for dessert.”

The waitress, clad in robes that still looked severe and formal while being rather shorter than usual, bowed respectfully and departed, shutting the door behind her.

Professor Quirrell waved a hand in the direction of the door, and a bolt slid shut. “Note the bolt on the inside. This room, Mr.~Potter, is known as Mary’s Room. It happens to be proof against all scrying, and I do mean \emph{all;} Dumbledore himself could detect nothing of what happens here. Mary’s Room is used by two kinds of people. The first sort are engaged in illicit dalliances. And the second sort lead interesting lives.”

“\emph{Really,}” said Harry.

Professor Quirrell nodded.

Harry’s lips were parted in anticipation. “It would be a waste to just sit here and eat lunch, then, without doing anything special.”

Professor Quirrell grinned, then took out his wand and flicked it in the direction of the door. “Of course,” he said, “people who lead interesting lives take precautions more \emph{thorough} than the dalliers. I have just sealed us in. Nothing will now pass in or out of this room—through the crack under the door, for example. And...”

Professor Quirrell then spoke no fewer than four different Charms, none of which Harry recognized.

“Even that does not \emph{really} suffice,” said Professor Quirrell. “If we were doing anything of truly great import, it would be necessary to perform another twenty-three checks besides those. If, say, Rita Skeeter knew or guessed that we would come here, it is possible that she could be in this room wearing the true Cloak of Invisibility. Or she could be an Animagus with a tiny form, perhaps. There are tests to rule out such rare possibilities, but to perform all of them would be arduous. Still, I wonder if I should do them anyway, just so as not to teach you bad habits?” And Professor Quirrell tapped a finger on his cheek, looking abstracted.

“It’s fine,” Harry said, “I understand, and I’ll remember.” Though he was a little disappointed that they weren’t doing anything of truly great import.

“Very well,” Professor Quirrell said. He leaned back in his chair, smiling broadly. “You wrought quite well today, Mr.~Potter. The basic notion was yours, I’m sure, even if you delegated the execution. I don’t think we’ll be hearing much more from Rita Skeeter after this. Lucius Malfoy will not be pleased with her failure. If she’s smart, she’ll flee the country the instant she realizes she’s been fooled.”

A sinking sensation began to dawn in Harry’s stomach. “Lucius was behind Rita Skeeter...?”

“Oh, you didn’t realize that?” said Professor Quirrell.

Harry hadn’t thought about what would happen to Rita Skeeter afterward.

At all.

Not in the slightest.

But she would get fired from her job, \emph{of course} she would be fired, she might have children going through Hogwarts for all Harry knew, and now it was worse, much worse—

“Is Lucius going to have her killed?” Harry said in a barely audible voice. Somewhere in his head, the Sorting Hat was screaming at him.

Professor Quirrell smiled dryly. “If you have not dealt with journalists before, take it from me that the world gets a little brighter every time one dies.”

Harry jumped out of his chair with a convulsive movement, he had to find Rita Skeeter and warn her before it was too late—

“\emph{Sit down},” Professor Quirrell said sharply. “\emph{No}, Lucius won’t kill her. But Lucius makes life \emph{extremely} unpleasant for those who serve him ill. Miss Skeeter will flee and start her life over with a new name. \emph{Sit down,} Mr.~Potter; there is nothing you can do at this point, and you have a lesson to learn.”

Harry sat down, slowly. There was a disappointed, annoyed look on Professor Quirrell’s face that was doing more to stop him than the words.

“There are times,” Professor Quirrell said, his voice cutting, “when I worry that your brilliant Slytherin mind is simply wasted on you. Repeat after me. Rita Skeeter was a vile, disgusting woman.”

“Rita Skeeter was a vile, disgusting woman,” Harry said. He wasn’t comfortable saying it, but there didn’t seem to be any other possible actions, none at all.

“Rita Skeeter tried to destroy my reputation, but I executed an ingenious plan and destroyed \emph{her} reputation first.”

“Rita Skeeter challenged me. She lost the game, and I won.”

“Rita Skeeter was an obstacle to my future plans. I had no choice but to deal with her if I wanted those plans to succeed.”

“Rita Skeeter was my enemy.”

“I cannot possibly get anything done in life if I am not willing to defeat my enemies.”

“I have defeated one of my enemies today.”

“I am a good boy.”

“I deserve a special reward.”

“Ah,” said Professor Quirrell, who had been grinning a benevolent smile for the last few lines, “I see I have succeeded in catching your attention.”

That was true. And while Harry felt like he was being railroaded into something—no, that wasn’t just a feeling, he \emph{had} been railroaded—he couldn’t deny that saying those things, and seeing Professor Quirrell’s smile, \emph{did} make him feel better.

Professor Quirrell reached into his robes, the gesture slow and deliberately significant, and drew forth...

...a \emph{book}.

It was different from any book Harry had ever seen, the edges and corners visibly misshapen; \emph{rough-hewn} was the phrase that came to mind, like it had been hacked out of a book mine.

“What is it?” breathed Harry.

“A diary,” said Professor Quirrell.

“Whose?”

“That of a famous person.” Professor Quirrell was smiling broadly.

“Okay...”

Professor Quirrell’s expression became more serious. “Mr.~Potter, one of the requisites for becoming a powerful wizard is an excellent memory. The key to a puzzle is often something you read twenty years ago in an old scroll, or a peculiar ring you saw on the finger of a man you met only once. I mention this to explain how I managed to remember this item, and the placard attached to it, after meeting you a good deal later. You see, Mr.~Potter, over the course of my life, I have viewed a number of private collections held by individuals who are, perhaps, not quite deserving of all that they have—”

“You \emph{stole} it?” Harry said incredulously.

“That is correct,” said Professor Quirrell. “Very recently, in fact. I think you will appreciate this particular item much more than the vile little man who held it for no other purpose than impressing his equally vile friends with its rarity.”

Harry was simply gaping now.

“But if you feel that my actions were incorrect, Mr.~Potter, I suppose you needn’t accept your special present. Though of course I shan’t go to the trouble of stealing it \emph{back}. So which is it to be?”

Professor Quirrell tossed the book from one hand to another, causing Harry to reach out involuntarily with a look of dismay.

“Oh,” said Professor Quirrell, “don’t worry about a little rough handling. You could toss this diary in a fireplace and it would emerge unscathed. In any case, I await your decision.”

Professor Quirrell casually threw the book up into the air and caught it again, grinning.

\emph{No,} said Gryffindor and Hufflepuff.

\emph{Yes}, said Ravenclaw. \emph{What part of the word ‘book’ did you two not understand?}

\emph{The theft part,} said Hufflepuff.

\emph{Oh, come on,} said Ravenclaw, \emph{you can’t seriously ask us to say no and spend the rest of our life wondering what it was.}

\emph{It sounds like a net positive from a utilitarian standpoint,} said Slytherin. \emph{Think of it as an economic transaction which generates gains from trade, only without the trade part.} \emph{Plus,} we \emph{didn’t steal it and it won’t help anyone to have Professor Quirrell keep it.}

\emph{He’s trying to turn you Dark!} shrieked Gryffindor, and Hufflepuff nodded firmly.

\emph{Don’t be a naive little boy,} said Slytherin, \emph{he’s trying to teach you Slytherin.}

\emph{Yeah,} said Ravenclaw. \emph{Whoever owned the book originally was probably a Death Eater or something. It belongs with us.}

Harry’s mouth opened, then halted that way, an agonized look on his face.

Professor Quirrell seemed to be quite enjoying himself. He had balanced the book on its corner, on one finger, and was keeping it upright while humming a little tune.

There came a knock at the door.

The book vanished back into Professor Quirrell’s robes, and he rose up from his chair. Professor Quirrell started to walk over to the door—

—and staggered, suddenly lurching into the wall.

“It’s all right,” said Professor Quirrell’s voice, which suddenly soun\-ded a lot weaker than usual. “Sit down, Mr.~Potter, it’s just a dizzy spell. Sit down.”

Harry’s fingers gripped the edge of his chair, uncertain as to what he should do, what he \emph{could} do. Harry couldn’t even get too close to Professor Quirrell, not unless he wanted to defy that sense of Doom—

Professor Quirrell straightened, then, his breathing seeming a bit heavy, and opened the door.

The waitress came in, then, bearing a platter of food; and as she distributed the plates, Professor Quirrell walked slowly back to the table.

But by the time the waitress had bowed her way out, Professor Quirrell was sitting upright and smiling again.

Still, the brief episode of whatever-it-was had decided Harry. He couldn’t say no, not after Professor Quirrell had gone to that much trouble.

“Yes,” Harry said.

Professor Quirrell held up a cautioning finger, then took out his wand again, locked the door again, and repeated three of the same Charms from earlier.

Then Professor Quirrell took the book back out of his robes and tossed it to Harry, who almost dropped it into his soup.

Harry shot Professor Quirrell a look of helpless indignation. You weren’t supposed to \emph{do} that with books, enchanted or not.

Harry opened the book with ingrained, instinctive care. The pages seemed too thick, with a texture unlike either Muggle paper or wizarding parchment. And the contents were...

...blank?

“Am I supposed to be seeing—”

“Look nearer the beginning,” said Professor Quirrell, and Harry (again with that helpless, ingrained care) turned a block of pages back.

The lettering was obviously handwritten, and very hard to read, but Harry thought the words might be Latin.

“What \emph{is} this?” said Harry.

“That,” said Professor Quirrell, “is a record of the magical researches of a Muggleborn who never came to Hogwarts. He refused his letter, and conducted his own small investigations, which never did get very far without a wand. From the description on the placard, I expect that his name bears rather more significance to you than to me. That, Harry Potter, is the diary of Roger Bacon.”

Harry almost fainted.

Nestled up against the wall, where Professor Quirrell had stumbled, glistened the crushed remains of a beautiful blue beetle.


