\chapter{Omake Files I, II \& III}

\begin{chapterOpeningAuthorNote}
Hail the Dark Lord Rowling.

“Omake” is a non-canonical extra.
\end{chapterOpeningAuthorNote}

\section{Omake Files I}

Dumbledore peered over his desk at young Harry, twinkling in a kindly sort of way. The boy had come to him with a terribly intense look on his childish face—Dumbledore hoped that whatever this matter was, it wasn’t \emph{too} serious. Harry was far too young for his life trials to be starting already. “What was it you wished to speak to me about, Harry?”

Harry James Potter-Evans-Verres leaned forward in his chair, smiling grimly. “Headmaster, I got a sharp pain in my scar during the Sorting Feast. Considering how and where I got this scar, it didn’t seem like the sort of thing I should just ignore. I thought at first it was because of Professor Snape, but I followed the Baconian experimental method which is to find the conditions for both the presence and the absence of the phenomenon, and I’ve determined that my scar hurts if and only if I’m facing the back of Professor Quirrell’s head, whatever’s under his turban. While it \emph{could} be something more innocuous, I think we should provisionally assume the worst, that it’s You-Know-Who—wait, don’t look so horrified, this is actually a priceless opportunity—”

\section{Omake Files II}

This was the original version of Chapter~9. It was replaced because—while many readers did enjoy it—many other readers had \emph{massive} allergies to songs in fanfics, for reasons that should not much need belabouring. I didn’t want to drive readers away before they got to Chapter~10.

Lee Jordan is the fellow prankster of Fred and George (in canon). “Lee Jordan” had sounded like a Muggle-born name to me, implying that he would be capable of instructing Fred and George on a tune that Harry would know. This was not as obvious to some readers as it was to your author.

\later

Draco went to Slytherin, and Harry breathed a small sigh of relief. It had \emph{seemed} like a sure thing, but you never did know what tiny event might upset the course of your master plan.

They were approaching the P’s now…

And over at the Gryffindor table, there was a whispered conversation.

“\emph{What if he doesn’t like it?}”

“\emph{He’s got no right to not like it—}”

“\emph{—not after the prank he played on—}”

“\emph{—Neville Longbottom, his name was—}”

“\emph{—he’s as fair a fair target now as fair can be.}”

“\emph{All right. Just make sure you don’t forget your parts.}”

“\emph{We’ve rehearsed it often enough—}”

“\emph{—over the last three hours.}”

And Minerva McGonagall, from where she stood at the speaker’s podium of the Head Table, looked down at the next name on her list. \emph{Please don’t let him be a Gryffindor please don’t let him be a Gryffindor \emph{oh please} don’t let him be a Gryffindor…} She took a deep breath, and called:

“Potter, Harry!”

There was a sudden silence in the hall as all whispered conversation stopped.

A silence broken by a horrible buzzing noise that modulated and changed in hideous mockery of musical melody.

Minerva’s head jerked around, shocked, and identified the buzzing noise as coming from the Gryffindor direction, where They were \emph{standing on top of the table} blowing into some kind of tiny devices held against Their lips. Her hand started to drop to her wand, to \emph{Silencio} the lot of Them, but another sound stopped her.

Dumbledore was chuckling.

Minerva’s eyes went back to Harry Potter, who had only just started to step out of line before he’d stumbled and halted.

Then the young boy began to walk again, moving his legs in odd sweeping motions, and waving his arms back and forth and snapping his fingers, in synchrony with Their music.

\begin{center}
\emph{To the tune of “Ghostbusters”}

\emph{(As performed on the kazoo by Fred and George Weasley,
and sung by Lee Jordan.)}

.

\emph{There’s a Dark Lord near?\\
Got no need to fear\\
Who you gonna call?}
\end{center}

“\shout{Harry Potter}!” shouted Lee Jordan, and the Weasley twins performed a triumphant chorus.

\begin{center}
\emph{With a Killing Curse?\\
Well it could be worse.\\
Who you gonna call?}
\end{center}

“\shout{Harry Potter}!” There were a lot more voices shouting it this time.

The Weasley Horrors went off into an extended wailing, now accompanied by some of the older Muggle-borns, who had produced their own tiny devices, Transfigured out of the school silverware no doubt. As their music reached its anticlimax, Harry Potter shouted:

\begin{center}
\emph{I ain’t afraid of Dark Lords!}
\end{center}

There was cheering then, especially from the Gryffindor table, and more students produced their own anti-musical instruments. The hideous buzzings redoubled in volume and built to another awful crescendo:

\begin{center}
\emph{I ain’t afraid of Dark Lords!}
\end{center}

Minerva glanced to both sides of the Head Table, afraid to look but with all too good a notion of what she would see.

Trelawney frantically fanning herself, Flitwick looking on with curiosity, Hagrid clapping along to the music, Sprout looking severe, and Quirrell gazing at the boy with sardonic amusement. Directly to her left, Dumbledore humming along; and directly to her right, Snape gripping his empty wine goblet, white-knuckled, so hard that the thick silver was slowly deforming.

\begin{center}
\emph{Dark robes and a mask?\\
Impossible task?\\
Who you gonna call?\\
\shout{Harry Potter}!}

\emph{Giant Fire-Ape?\\
Old bat in a cape?\\
Who you gonna call?\\
\shout{Harry Potter}!}
\end{center}

Minerva’s lips set in a white line. She would have words with Them about that last verse, if They thought she was powerless because it was the first day of school and Gryffindor had no points to take away. If They didn’t care about detentions then she would find something else.

Then, with a sudden gasp of horror, she looked in Snape’s direction, \emph{surely} he realised the Potter boy must have no idea who that was talking about—

Snape’s face had gone beyond rage into a kind of pleasant indifference. A faint smile played about his lips. He was looking in the direction of Harry Potter, not the Gryffindor table, and his hands held the crumpled remains of a former wine goblet…

And Harry walked forwards, sweeping his arms and legs through the motions of the Ghostbusters dance, keeping a smile on his face. It was a great setup, had caught him completely by surprise. The least he could do was play along and not ruin it all.

Everyone was cheering him. It made him feel all warm inside and sort of awful at the same time.

They were cheering him for a job he’d done when he was one year old. A job he hadn’t really finished. Somewhere, somehow, the Dark Lord was still alive. Would they have been cheering quite so hard, if they knew that?

But the Dark Lord’s power \emph{had} been broken once.

And Harry would protect them again. If there was in fact a prophecy and that was what it said. Well, actually regardless of what any darn prophecy said.

All those people believing in him and cheering him—Harry couldn’t stand to let that be false. To flash and fade like so many other child prodigies. To be a disappointment. To fail to live up to his reputation as a symbol of the Light, never mind \emph{how} he’d won it. He would absolutely, positively, no matter how long it took and even if it killed him, fulfil their expectations. And then go on to \emph{exceed} those expectations, so that people wondered, looking back, that they had once asked so little of him.

And he shouted out the lie that he’d invented because it scanned well and the song called for it:

\begin{center}
\emph{I ain’t afraid of Dark Lords!\\
I ain’t afraid of Dark Lords!}
\end{center}

Harry took his last steps toward the Sorting Hat as the music ended. He swept a bow to the Order of Chaos at the Gryffindor table, and then turned and swept another bow to the other side of the hall, and waited for the applause and giggling to die away…

\section{Omake Files III}

The offer to tell the whole plot to anyone who guessed what “has never happened before” spurred a \emph{lot} of interesting attempts. The first omake below is taken directly from my personal favourite answer, by Meteoricshipyards. The second is based on Kazuma’s suggestion for what “has never happened before”, the third on a combination of yoyoente and dougal74, the fourth on wolf550e’s review of chapter 10. The one that starts with ‘K’, and the one just above that, are from DarkHeart81. The others are my own. Anyone who wants to pick up one of my own ideas and run with them, particularly the last one, is welcome to do so. And before I get 100 indignant complaints, yes, I am well aware that the legislative body of the UK is the House of Commons in Parliament.

\later

…In the back of his mind, he wondered if the Sorting Hat was genuinely \emph{conscious} in the sense of being aware of its own awareness, and if so, whether it was satisfied with only getting to talk to eleven-year-olds once per year. Its song had implied so: \emph{Oh, I’m the Sorting Hat and I’m okay, I sleep all year and I work one day…}

When there was once more silence in the room, Harry sat on the stool and \emph{carefully} placed onto his head the 800-year-old telepathic artefact of forgotten magic.

Thinking, just as hard as he could: \emph{Don’t Sort me yet! I have questions I need to ask you! Have I ever been Obliviated? Did you Sort the Dark Lord when he was a child and can you tell me about his weaknesses? Can you tell me why I got the brother wand to the Dark Lord’s? Is the Dark Lord’s ghost bound to my scar and is that why I get so angry sometimes? Those are the most important questions, but if you’ve got another moment can you tell me anything about how to rediscover the lost magics that created you?}

And the Sorting Hat answered, “\emph{No. Yes. No. No. Yes and no, next time don’t ask double questions. No.}” and out loud, “RAVENCLAW!”

\later

“\emph{Oh, dear. This has never happened before…}”

\emph{What?}

“\emph{I’m allergic to your hair shampoo—}”

And then the Sorting Hat sneezed, with a mighty “A-CHOO!” that echoed around the Great Hall.

“Well!” Dumbledore cried jovially. “It seems Harry Potter has been sorted into the new House of Achoo! McGonagall, you can serve as the Head of House Achoo. You’d better hurry up on making arrangements for Achoo’s curriculum and classes, tomorrow is the first day!”

“But, but, but,” stammered McGonagall, her mind in nearly complete disarray, “who will be Head of House Gryffindor?” It was all she could think of, she \emph{had} to stop this somehow…

Dumbledore put a finger to his cheek, looking thoughtful. “Snape.”

Snape’s screech of protest nearly drowned out McGonagall’s, “Then who will be Head of \emph{Slytherin?}”

“Hagrid.”

\later

\emph{Don’t Sort me yet! I have questions I need to ask you! Have I ever been Obliviated? Did you Sort the Dark Lord when he was a child and can you tell me about his weaknesses? Can you tell me why I got the brother wand to the Dark Lord’s? Is the Dark Lord’s ghost bound to my scar and is that why I get so angry sometimes? Those are the most important questions, but if you’ve got another moment can you tell me anything about how to rediscover the lost magics that created you?}

There was a brief pause.

\emph{Hello? Do I need to repeat the questions?}

The Sorting Hat screamed, an awful high-pitched sound that echoed through the Great Hall and caused most of the students to clap their hands over their ears. With a desperate yowl, it leapt off Harry Potter’s head and bounded across the floor, pushing itself along with its brim, and made it halfway to the Head Table before it exploded.

\later

“SLYTHERIN!”

Seeing the look of horror on Harry Potter’s face, Fred Weasley thought faster than he ever had in his life. In a single motion he whipped out his wand, whispered “\emph{Silencio!}” and then “\emph{Changemyvoiceio!}” and finally “\emph{Ventriliquo!}”

“Just kidding!” said Fred Weasley. “GRYFFINDOR!”

\later

“\emph{Oh, dear. This has never happened before…}”

\emph{What?}

“\emph{Ordinarily I would refer such questions to the Headmaster, who could ask me in turn, if he wished. But some of the information you’ve asked for is not only beyond your own user level, but beyond the Headmaster’s.}”

\emph{How can I raise my user level?}

“\emph{I’m afraid I am not allowed to answer that question at your current user level.}”

\emph{What options \emph{are} available at my user level?}

After that it didn’t take long—

“ROOT!”

\later

“\emph{Oh, dear. This has never happened before…}”

\emph{What?}

“\emph{I’ve had to tell students before that they were mothers—it would break your heart to know what I saw in their minds—but this is the first time I’ve ever had to tell someone they were a father.}”

\emph{\shout{What?}}

“\emph{Draco Malfoy is carrying your baby.}”

\emph{\shout{Whaaaaaaat?}}

“\emph{To repeat: Draco Malfoy is carrying your baby.}”

\emph{But we’re only eleven—}

“\emph{Actually, Draco is secretly thirteen years old.}”

\emph{B-b-but men can’t get pregnant—}

“\emph{And a girl under those clothes.}”

\emph{\shout{But we’ve never had sex, you idiot!}}

“\emph{\shout{She Obliviated you after the rape, moron!}}”

Harry Potter fainted. His unconscious body fell off the stool with a dull thud.

“RAVENCLAW!” called out the Hat from where it lay on top of his head. That had been even funnier than its first idea.

\later

“ELF!”

Huh? Harry remembered Draco mentioning a ‘House Elf’, but what was that exactly?

Judging by the appalled looks dawning on the faces around him, it wasn’t anything good—

\later

“PANCAKES!”

\later

“REPRESENTATIVES!”

\later

“\emph{Oh, dear. This has never happened before…}”

\emph{What?}

“\emph{I’ve never Sorted someone who was a reincarnation of Godric Gryffindor \emph{and} Salazar Slytherin \emph{and} Naruto.}”

\later

“ATREIDES!”

\later

“Fooled you again! HUFFLEPUFF! SLYTHERIN! HUFFLEPUFF!”

\later

“PICKLED STEWBERRIES!”

\later

“KHAAANNNN!”

\later

At the Head Table, Dumbledore went on smiling benignly; small metallic sounds occasionally came from Snape’s direction as he idly compacted the twisted remains of what had once been a heavy silver wine goblet; and Minerva McGonagall clenched the podium in a white-knuckled grip, knowing that Harry Potter’s contagious chaos had infected the Sorting Hat itself.

Scenario after scenario played out through Minerva’s head, each worse than the last. The Hat would say that Harry was too evenly balanced between Houses to Sort, and decide that he belonged to all of them. The Hat would proclaim that Harry’s mind was too strange to be Sorted. The Hat would demand that Harry be expelled from Hogwarts. The Hat had gone into a coma. The Hat would insist that a whole new House of Doom be created just to accommodate Harry Potter, and \emph{Dumbledore would make her do it…}

Minerva remembered what Harry had told her in that disastrous trip to Diagon Alley, about the…planning fallacy, she thought it had been…and how people were usually too optimistic, even when they thought they were being pessimistic. It was the sort of information that preyed on your mind, dwelling in it and spinning off nightmares…

But what was the \emph{worst} that could happen?

Well…in the \emph{worst-case scenario,} the Hat would assign Harry to a whole new House. Dumbledore would insist that she do it—create a whole new House just for him—and she’d have to rearrange all the class schedules on the first day of term. And Dumbledore would remove her as Head of House Gryffindor, and give her beloved House over to…Professor Binns, the History ghost; and she would be assigned as Head of Harry’s House of Doom; and she would futilely try to give the child orders, deducting point after point without effect, while disaster after disaster was blamed on her.

Was that the worst-case scenario?

Minerva honestly didn’t see how it could be any worse than that.

And even in the very worst case—no matter \emph{what} happened with Harry—it would all be over in seven years.

Minerva felt her knuckles slowly relax their white-knuckled grip on the podium. Harry had been right, there was a kind of comfort in staring directly into the furthest depths of the darkness, knowing that you had confronted your worst fears and were now prepared.

The frightened silence was broken by a single word.

“HEADMASTER!” called the Sorting Hat.

At the Head Table, Dumbledore rose, his face puzzled. “Yes?” he addressed the Hat. “What is it?”

“I wasn’t talking to you,” said the Hat. “I was Sorting Harry Potter into the place in Hogwarts where he most belongs, namely the Headmaster’s office—”

%  LocalWords:  fanfics Ch P’s Meteoricshipyards yoyoente dougal74 CHOO
%  LocalWords:  wolf550e’s DarkHeart81 Achoo Achoo’s Changemyvoiceio Naruto
%  LocalWords:  Whaaaaaaat ATREIDES STEWBERRIES KHAAANNNN
