% Omake section titles

\makeatletter
\newcommand{\OmakeIVspecialsection}[2][1.5]{%
\vspace*{2\baselineskip plus 1\baselineskip minus 1\baselineskip}%
\noindent\hfill\scalebox{#1}{#2}\hfill\mbox{}%
\vskip 1\baselineskip plus 1\baselineskip%
\@afterindentfalse\@afterheading
}
\makeatother

\newcommand{\OmakeIVsection}[2][1.5]{%
  \OmakeIVspecialsection[#1]{\MakeUppercase{#2}}}

\chapter{Omake Files IV, Alternate Parallels}

\OmakeIVspecialsection[1.6]{\fontspec[ExternalLocation]{RingBearer}
\settowidth{\versewidth}{\mbox{the}}
Lord\scalebox{.40}{\parbox[b]{\versewidth}{%
        \centering of\\\nointerlineskip\vskip 4pt the}}Ratîonalît\raisebox{-.32ex}{Y}}

Frodo glanced at all the faces, but they were not turned to him. All the Council sat with downcast eyes, as if in deep thought. A great dread fell on him, as if he was awaiting the pronouncement of some doom that he had long foreseen and vainly hoped might after all never be spoken. An overwhelming longing to rest and remain at peace by Bilbo’s side in Rivendell filled all his heart. At last with an effort he spoke, and wondered to hear his own words, as if some other will were using his small voice.

“We cannot,” said Frodo. “We must not. Do you not see? It is exactly what the Enemy desires. All of this he has foreseen.”

The faces turned to him, puzzled the Dwarves and grave the Elves; sternness in the eyes of the Men; and so keen the gazes of Elrond and of Gandalf that Frodo almost could not withstand it. It was very hard, then, not to grasp the Ring in his hand, and harder still not to put it on, to face them as only Frodo.

“Do you not question it?” Frodo said, thin like the wind his voice, and wavering like a breeze. “You have chosen, of all things, to send the Ring into Mordor; should you not wonder? How did it come to this? That we might, of all our choices, do that single thing our Enemy most desires? Perhaps the Cracks of Doom are already guarded, strongly enough to hold off Gandalf and Elrond and Glorfindel all together; or perhaps the Master of that place has cooled the lava there, set it to trap the Ring so that he may simply bring it out after it is thrown in…” A memory of awful clarity came over Frodo then, and a flash of black laughter, and the thought came to him that it was \emph{just} what the Enemy would do. Only the thought came to him so: \emph{thus it would amuse me to do, if I meant to rule…}

There were doubtful glances exchanged within the council; Glóin and Gimli and Boromir were now looking at the Elves more skeptically than before, like they had awoken out of a dream of words.

“The Enemy is very wise,” said Gandalf, “and weighs all things to a nicety in the scales of his malice. But the only measure that he knows is desire, desire for power; and so he judges all hearts. Into his heart the thought will not enter that any will refuse it, that having the Ring we may seek to destroy it—”

“He \emph{will} think of it!” cried Frodo. He struggled for words, trying to convey things that had once seemed perfect in his comprehension, and then faded like melting snow. “If the Enemy thought that all his foes were moved by desire for power alone—he would guess wrongly, over and over, and the Maker of this Ring would \emph{see} that, he would \emph{know} that somewhere he had made a mistake!” Frodo’s hands stretched forth pleadingly.

Boromir stirred, and his voice was doubtful. “You speak fair of the Enemy,” said Boromir, “for one of his foes.”

Frodo’s mouth opened and shut in desperate bewilderment; for Frodo knew, he knew the Man was mad, but he could think of nothing to say.

Then Bilbo spoke, and his withered voice silenced the whole room, even Elrond who had been about to speak. “Frodo is right, I fear,” whispered the old hobbit. “I remember, I remember what it was like. To see with the Black Sight. I remember. The Enemy will think that we might not trust one another, that the weaker among us will propose to destroy the Ring so that the stronger may not have it. He knows that even one not truly good might still cry to destroy the Ring, to make a show of pretended goodness. And the Enemy will \emph{not} think it impossible that such a decision be made by this council, for you see, he does not trust us to be wise.” A whispering chuckle rose from the ancient hobbit’s throat. “And if he did—why, he would \emph{still} guard the Cracks of Doom. It would cost him little.”

Now foreboding was on the faces even of the Elves, and the Wise; Elrond was frowning, and the sharp eyebrows of Gandalf furrowed.

Frodo gazed at them all, feeling a wildness come over him, a despair; and as his heart weakened a shadow came over his vision, a darkness and a wavering. From within the shadow Frodo saw Gandalf, and the wizard’s strength was revealed as weakness, and his wisdom as folly. For Frodo knew, as the Ring seemed to drag and weigh on his breast, that Gandalf had not thought at all of history and lore, when the wizard spoke of how the Enemy would not understand any desire save power; that Gandalf had not remembered how Sauron had cast down and corrupted the Men of Númenor in the days of their glory. Just as the Wizard had not thought that the Enemy might learn to comprehend foes of goodwill by \emph{looking…}

Frodo’s gaze swung to Elrond, but there was no hope there, no answer and no rescue in the shadowy vision; for Elrond had let Isildur go, carrying the Ring from the Cracks of Doom where it should have been destroyed, at the cost of all this war. Not for Isildur’s own sake, not for friendship had it been done, for the Ring had killed Isildur in the end, and far worse fates could have followed him. But the Doom that had stemmed from Isildur’s deed would have seemed unsure to Elrond then, unsure and distant in time; and yet the cost to Elrond himself of taking his sword’s pommel to the back of Isildur’s head would have been surer, and nearer…

As though in desperation, Frodo turned to look at Aragorn, the weathered man who had donned his travel-worn clothes for this council, the heir of kings who spoke softly to hobbits. But Frodo’s vision seemed to double, and in the shadowy second image Frodo saw a Man who had spent too much of his youth among Elves, who had learned to wear humble and stained clothes amid the gold and jewels, knowing he could not match them wisdom for wisdom, and hoping to outplay them in a fashion they would not emulate…

In the sight of the Ring, which was the sight of the Ring’s own Maker, all noble things faded into stratagems and lies, a world of grey and darkness without any light. They had not made their choices knowingly, Gandalf or Elrond or Aragorn; the impulses had come from the dark hidden parts of themselves, the black secret depths which the Ring had rendered plain in Frodo’s vision. Would they out-think the Shadow, when they could not comprehend even their own selves, or the forces that moved them?

“Frodo!” came the sharp whisper of Bilbo’s voice, and Frodo came to himself, and halted his hand reaching up toward where the Ring lay on his breast, on its chain, dragging like a vast stone around his neck.

Reaching up to grasp the Ring wherein all answers lay.

“How did you bear this thing?” Frodo whispered to Bilbo, as if the two of them were the only souls in the room, though all the Council watched them. “For years? I cannot imagine it.”

“I kept it locked in a room to which only Gandalf had the key,” said his uncle, “and when I began to imagine ways to open it, I remembered Gollum.”

A shudder went through Frodo, remembering the tales. The horror of the Misty Mountains, thinking, always thinking in the dark; ruling the goblins from the shadows and filling the tunnels with traps; but for Bilbo wearing the ring that first time not a single dwarf would have lived. And now, Legolas the Elf had told them, Gollum had ceased sending his agents against the Shire, had at last found the courage to leave his mountains and seek the Ring himself. That was Gollum, the fate which Frodo would share himself, if the Ring were not destroyed.

Only they had no way to destroy the Ring.

The Shadow had foreseen every move they could make. Had \emph{almost}—Frodo still could not imagine how it had been done, how the Shadow had arranged such a thing—had \emph{almost} manœuvred the Council into sending the Ring straight into Mordor with only a tiny guard set on it, as they would have done if Frodo and Bilbo had not been there.

And having foregone that swiftest of all possible defeats, the only question remaining was how long it would take to lose. Gandalf had delayed too long, delayed far too long to set this march in motion. It could have been so easy, if only Bilbo had set out eighty years earlier, if only Bilbo had been told what Gandalf had already suspected, if only Gandalf’s heart had not silently flinched away from the prospect of being embarrassingly wrong…

Frodo’s hand spasmed on his breast; without thought, his fingers began to rise again toward the vast weight of the chain on which the Ring hung.

All he had to do was put on the Ring.

Just that, and all would become clear to him, once more the slowness and mud would leave his thoughts, all possibilities and futures transparent to him, he would see through the Shadow’s plans and devise an irresistible counterstroke—

—and he would never be able to take off the Ring, not again, not by any will that would be left to him. All Frodo had of those moments were fading memories, but he knew that it had felt like dying, to let all his towers of thought collapse and become only Frodo once more. It had felt like dying, he remembered that much of Weathertop even if he remembered little else. And if he did wear the Ring again, it would be better to die with it on his finger, to end his life while he was still himself; for Frodo knew that he could not withstand the effects of wearing the Ring a second time, not afterwards when the limitless clarity was lost to him…

Frodo looked around the Council, at the poor lost leaderless Wise, and he knew they could not defeat the Shadow by their own strength.

“I will wear it one last time,” Frodo said, his voice broken and failing, as he had known from the beginning that he would say in the end, “one last time to find the answer for this Council, and then there will be other hobbits.”

“\emph{No!}” screamed the voice of Sam, as the other hobbit began to rush forward from where he had hidden; even as Frodo, with movement as swift and precise as a Nazgûl, took out the Ring from beneath his shirt; and somehow Bilbo was already standing there and had already thrust his finger through.

It all happened before even Gandalf’s staff could point, before Aragorn could level the hilt-shard of his sword; the Dwarves shouted in shock, and the Elves were dismayed.

“Of course,” said Bilbo’s voice, as Frodo began to weep, “I see it now, I understand everything at last. Listen, listen and swiftly, here is what you must do—”

% The Witch and the Wardrobe
\OmakeIVspecialsection[5]{\fontspec[ExternalLocation]{NarniaBLL}456}

With a critical eye, Peter looked over the encamped Centaurs with their bows, Beavers with their long daggers, and talking Bears with their chain-mail draped over them. He was in charge, because he was one of the mythical Sons of Adam and had declared himself High King of Narnia; but the truth was he didn’t really know much about encampments, weapons, and guard patrols. In the end all he could see was that they all looked proud and confident, and Peter had to hope they were right about that; because if you couldn’t believe in your own people, you couldn’t believe in anyone.

“They’d scare \emph{me}, if I had to fight ’em,” Peter said finally, “but I don’t know if it’s enough to beat…\emph{her.}”

“You don’t suppose this mysterious lion will actually show up and help us, d’you?” said Lucy. Her voice was very quiet, so that none of the creatures around them would hear. “Only it’d be nice to really have him, don’t you think, instead of just letting people think that he put us in charge?”

Susan shook her head, shaking the magical arrows in the quiver on her back. “If there was really someone like that,” Susan said, “he wouldn’t have let the White Witch cover the land in winter for a hundred years, would he?”

“I had the strangest dream,” Lucy said, her voice even quieter, “where we didn’t have to organize any creatures or convince them to fight, we just walked into this place and the lion was already here, with all the armies already mustered, and he went and rescued Edmund, and then we rode alongside him into this tremendous battle where he killed the White Witch…”

“Did the dream have a moral?” said Peter.

“I don’t know,” said Lucy, blinking and looking a little puzzled. “In the dream it all seemed useless somehow.”

“I think maybe the land of Narnia was trying to tell you,” said Susan, “or maybe it was just your own dreams trying to tell you, that if there was really such a person as that lion, there’d be no use for \emph{us}.”

\OmakeIVsection{My Little Pony: Friendship is Science}

“Applejack, who told me outright that I was mistaken, represents the spirit of…\emph{honesty!} “ Twilight Sparkle raised her head even higher, mane blowing like a wind about the dusky sky of her neck. “Fluttershy, who approached the manticore to find out about the thorn in its paw, represents the spirit of…\emph{investigation!} Pinkie Pie, who realized that the awful faces were just trees, represents the spirit of…\emph{formulating alternative hypotheses!} Rarity, who solved the serpent’s problem represents the spirit of…\emph{creativity!} Rainbow Dash, who saw through the false offer of her heart’s desire, represents the spirit of…\emph{analysis!} Marie-Susan, who made us convince her that we were right before she agreed to come on our expedition, represents the spirit of…\emph{peer review!} And when those Elements are ignited by the spark of curiosity that resides in the heart of all of us, it creates the seventh element—the Element of Sci-”

The blast of power that came forth was like a wind of moonless night, it caught Marie-Susan before the pony could even flinch, and she was gone without a trace before any of them had the chance to rear in shock.

From the dark thing that stood in the centre of the dais where the Elements had shattered, from the scarce-recognizable void-black outline of a horse, came a voice that seemed to bypass all ears and burn like cold fire, sounding directly in the brain of everypony who heard:

\emph{Did you expect me to just stand there and let you finish?}

Twilight Sparkle stared at the space where Marie-Susan had been, where not a trace of the unicorn remained. \emph{She—she just—she—} In the back of her mind, unheard, she was aware that Rarity was screaming.

\emph{That wasn’t a disintegration,} said the voice of Nightmare. \emph{I sent her somewhere else.}

Rarity’s scream stopped abruptly.

Twilight Sparkle felt like her own scream was only beginning. Seven. It took seven ponies to use the Elements of Inquiry. Everyone knew that no matter how honest, investigating, skeptical, creative, analytic, or curious you were, what really made your work Science was when you published your results in a prestigious journal. Everyone knew that. Could there be more than one Element of Peer Review at a time—how long would it take to find another one—and the Nightmare wouldn’t just stand there and let them do it—

“Where?” yelled Rainbow Dash. “Where’d you put her?”

\emph{I put the little pony in the same place I bound my pathetic sister, in the heart of her pathetic Sun.}

“She’ll die!” cried Fluttershy, staring at the Nightmare in horror. “It’s too hot, she’ll burn!”

\emph{Oh, don’t worry. The power of the Nightmare surrounds your little friend, keeping her safe and cool, sustaining her without food or drink. She will suffer nothing more than boredom…}

The void-black outline stepped off the dais, walking slowly, deliberately, past the remaining six ponies.

\emph{…so long as the Nightmare’s power is not broken. By any backup plans my sister may have set in motion, for example, and which may be known to you. In that case she will vaporize instantly. Such a lovely thing, friendship. It makes such a wonderful instrument of blackmail. Be sure to keep safe the Elements of Inquiry. You wouldn’t want anyone else using them on me, now would you?}

“No,” whispered Twilight Sparkle, as the horror began to dawn on her.

Then a crawling sensation all over her skin, as the Nightmare walked past her, and the deadly power brushed her with its cold caress.

\emph{Now if you’ll pardon me, my little ponies, I have an eternal night to rule over.}

\clearpage
\OmakeIVsection{The Village Hidden In The Clarity\protect\footnotemark}
\footnotetext{This has now inspired an extended fanfiction, \emph{Lighting Up the Dark} by Velorien.}

“Consider the computational power required to manifest over a hundred shadow clones,” the Uchiha genius said in his dispassionate tones. “It is an error of rationality, Sakura, to say ‘fluke’ and think you have explained anything. ‘Fluke’ is simply the name one gives to data that one is ignoring.”

“But it \emph{has} to be a fluke!” Sakura yelled. With effort, she calmed her voice into the careful precision expected of a rationality ninja; it wouldn’t do to have her crush think she was stupid. “Like you said, the computational power required to use over a hundred Kage Bunshin is simply absurd. We’re talking the level of a major superintelligence. Naruto’s the dead last of our class. He’s not even jōnin-level smart, let alone a superintelligence!”

The Uchiha’s eyes gleamed, almost as though he had activated his Smartingan. “Naruto can manifest a hundred independently acting clones. He \emph{must} have the raw brainpower. But, under ordinary circumstances, something prevents him from using this computational power efficiently…like a mind at war within itself, perhaps? We now have cause to believe that Naruto is in some way connected to a superintelligence, and as a recently graduated genin, he, like us, is fifteen years old. What happened fifteen years ago, Sakura?”

It took a moment for Sakura to comprehend, to remember, and then she understood.

The attack of the Nine-Brains Demon Fox.

Just a small bone-white creature with big ears and bigger tail and beady red eyes. It was no stronger than an ordinary fox, it didn’t breathe fire or flash laser eyes, it possessed no chakra and no magic of any kind, but its intelligence was over nine thousand times that of a human being.

Hundreds had been killed, half the buildings wrecked, almost the whole village of Beisugakure had been destroyed.

“You think the Kyubey is hiding inside Naruto?” Sakura said. A moment later, her brain automatically went on to fill in the obvious implications of the theory. “And the software conflict between their existences is why he acts like a gibbering idiot half the time, but can control a hundred Kage Bunshin. Huh. That makes…a lot of sense…actually…”

Sasuke gave her the brief, contemptuous nod of someone who had figured all this out on his own, without anyone else needing to prompt \emph{him}.

“Anōōō…” said Sakura. Only years of sanity exercises channelled her complete screaming panic into pragmatically useful policy options. “Shouldn’t we…\emph{tell} someone about this? Like, sometime in the next five seconds?”

“The adults already know,” Sasuke said emotionlessly. “It is the obvious explanation for their treatment of Naruto. No, the real question is how this fits into the outwitting of the Uchiha…”

“I don’t see how it fits at all—” began Sakura.

“It \emph{must} fit!” A tinge of frantic emotion flickered in Sasuke’s voice. “I asked that man \emph{why} he did it, and he told me that when I knew the answer to that, it would explain \emph{everything!} Surely \emph{this} must also be part of what is to be explained!”

Sakura sighed to herself. Her personal hypothesis was that Itachi had just been trying to drive his brother into clinical paranoia.

“Yo, kids,” said the voice of their rationality sensei from their radio earpieces. “There’s a village in Wave trying to build a bridge, and it keeps falling down for no reason anyone can figure out. Meet up at the gates at noon. It’s time for your first C-ranked analysis mission.”

\clearpage
\OmakeIVsection{Erdős in Chains}

“How could you do it, Anita?” said Richard, his voice very tight. “How could you co-author a paper with Jean-Claude? You \emph{study} the undead, you don’t \emph{collaborate} with them!”

“And what about you?” I spat. “You co-authored a paper with Sylvie! It’s all right for \emph{you} to be prolific but not \emph{me?}”

“I’m the \emph{head of her institute},” Richard growled. I could feel the waves of science radiating off him; he was angry. “I \emph{have} to work with Sylvie, it doesn’t mean anything! I thought our own research was special, Anita!”

“It \emph{is,}” I said, feeling helpless about my inability to explain things to Richard. He didn’t understand the thrill of being a polymath, the new worlds that were opening up to me. “I didn’t share \emph{our} research with anyone—”

“But you wanted to,” said Richard.

I didn’t say anything, but I knew that the look on my face said it all.

“God, Anita, you’ve changed,” said Richard. He seemed to slump in on himself. “Do you realize that the monsters are joking about Blake numbers, now? I used to be your partner in everything, and now—I’m just another werewolf with a Blake number of 1.”

\OmakeIVspecialsection[2]{\fontspec[ExternalLocation]{Thundercats}ThunderSmarts}

“I am \emph{sick} of this!” shouted Liono. “Sick of doing this \emph{every single week!} Our species was capable of \emph{interstellar travel}, Panthro, I \emph{know} the quantities of energy involved! There is no \emph{way} you can’t build a nuke or steer an asteroid or \emph{somehow} blow up that ever-living idiot’s pyramid!”

\clearpage
\OmakeIVsection[1.2]{He-Man and the Masters of Rationality}

“Fabulous secret knowledge was revealed to me on the day I held aloft my magic book and said: \emph{By the power of Bayes’s Theorem!}”

\OmakeIVsection{Fate/Sane Night}

\begin{emph}
I am the core of my thoughts\\
Belief is my body\\
And choice is my blood\\
I have revised over a thousand judgements\\
Unafraid of loss\\
Nor aware of gain\\
Have withstood pain to update many times\\
Waiting for truth’s arrival.\\
This is the one uncertain path.\\
My whole life has been…\\
Unlimited Bayes Works!
\end{emph}

\OmakeIVsection{The Name of the Rationality}

The eleven-year-old boy who would some day become legend—slayer of dragons, killer of kings—had but one thought upon his mind, as he approached the Sorting Hat to enter into the study of mysteries.

\emph{Anywhere but Ravenclaw anywhere but Ravenclaw oh please anywhere but Ravenclaw…}

But no sooner the brim of the ancient felted device slipped over his forehead—

“RAVENCLAW!”

As the table decked in blue began to applaud him, as he approached the dread table where he would spend the next seven years, Kvothe was already wincing inside, waiting for the inevitable; and the inevitable happened almost at once, exactly as he had feared it, before he’d even had a chance to sit down properly.

“So!” an older boy said with the happy expression of someone who’s thought of something terribly clever. “Kvothe the Raven, huh?”

\OmakeIVsection{Tengen Toppa Gurren Rationality 40k}

I have a truly marvellous story for this crossover which this margin is too narrow to contain.

\OmakeIVspecialsection{\fontspec[ExternalLocation]{Twilight}Utilitarian Twilight\protect\footnotemark}
\footnotetext{Written after I heard Alicorn was writing a Twilight fanfic, but before I read \emph{Luminosity}. It’s obvious if you’re one of us.}

“Edward,” said Isabella tenderly. She reached up a hand and stroked his cold, sparkling cheek. “You don’t have to protect me from anything. I’ve listed out all the upsides and all the downsides, assigned them consistent relative weights, and it’s just really obvious that the benefits of becoming a vampire outweigh the drawbacks.”

“Bella,” Edward said, and swallowed desperately. “Bella—”

“Immortality. Perfect health. Awakening psychic powers. Easy enough to survive on animal blood once you do it. Even the beauty, Edward, there are people who would give their lives to be pretty, and don’t you dare call them shallow until you’ve tried being ugly. Do you think I’m scared of the word ‘vampire’? I’m tired of your arbitrary deontological constraints, Edward. The whole human species ought to be in on your fun, and people are dying by the thousands even as you hesitate.”

The gun in his lover’s hand was cold against his forehead. It wouldn’t kill him, but it would disable him for long enough—

\OmakeIVsection{\sout{Aladdin} Jasmine}

Aladdin’s face was wistful, but determined, as the newly minted street urchin addressed the blue being of cosmic power for one last time, prepared to leave behind the wealth and hope he had so briefly tasted for the sake of his friend. “Genie, I make my third wish. I wish for you to be—”

Princess Jasmine, who had been staring at this with her mouth open, not quite believing what she was seeing, just barely managed to overcome her paralysis and yank the lamp out of the boy’s hand before he could finish the fatal sentence.

“Excuse me,” said Jasmine. “Aladdin, my darling, you’re cute but you’re an idiot, do you know that? Did you not notice how once Jafar got his hands on this lamp, he got his own three wishes—oh, never mind. Genie, I wish for everyone to always be young and healthy, I wish nobody ever had to die if they didn’t want to, and I wish for everyone’s intelligence to gradually increase at a rate of 1 IQ point per year.” She tossed the lamp back to Aladdin. “Go back to what you were doing.”

\OmakeIVsection[1.2]{Prince Hamlet and the Philosopher’s Stone\protect\footnotemark}%
\footnotetext{HonoreDB has now extended this to a complete e-book entitled
  \emph{A Will Most Incorrect to Heaven: The Tragedy of Prince Hamlet and
  the Philosopher’s Stone}, available for \$3 at \url{http://makefoil.com} (yes, really).}%

\begin{playdialog}%
HAMLET: Interloper, abandon this strange prank,\\
which makes cruel use of the blindness of my grief,\\
and the good heart of my good friend Horatio.\\
Or else, if thou hast true title to this belov’d form, tell me:\\ What drawing did I present to Hamlet King,\\ when six years old and scarce out of my sling?\\

GHOST: ’twas a unicorn clad all in mail.\\

HAMLET: What.\\

GHOST: Mark me.\\

HAMLET: Father, I will.\\

GHOST: My hour is almost come,\\
When I to sulphurous and tormenting flames\\
Must render up myself.\\

HAMLET: Thou art in torment?\\

GHOST: Ay, as are all who die unshriven.\\

HAMLET: Like every Dane this is what I’ve been taught.\\
Yet I did figure such caprice ill-suited to almighty God.\\
For all who suffer unlook’d-for deaths,\\
Unattended by God’s chosen priests,\\
to be then punish’d for the ill-ordering of the world…\\

GHOST: ’twas not the world that killed me, nor accident of any kind.\\

HAMLET: What?\\

GHOST: If thou didst ever thy dear father love,\\
Revenge his foul and most unnatural murder.\\

HAMLET: Oh God.\\

GHOST: My time grows ever shorter. Wilt thou hear the tale?\\

HAMLET: No.\\

GHOST: What?\\

HAMLET: My love for you does call me to avenge your death,\\ but greater crimes have I heard told this night.\\ If all those murdered go to Hell, and others as well,\\ who would have confess’d had they the time,\\ If people who are, in balance, good, suffer grisly\\ at the hands of God, then I defy God’s plan.\\ \\ Good Ghost, as one who dwells beyond the veil,\\ you know things that we mortals scarce conceive.\\ Tell me: is there some philter or device,\\ outside nature’s ken but not outside her means,\\ by which death itself may be escap’d?\\

GHOST: You seek to evade Hell?\\

HAMLET: I seek to deny Hell to everyone!\\
and Heaven too, for I suspect the Heaven of our mad God\\
might be a paltry thing, next to the Heaven I will make of Earth,\\ when I am its immortal king.\\

GHOST: I care not for these things.\\
Death and hell have stripp’d away all of my desires,\\
save for revenge upon my murderer.\\

HAMLET: Thou shalt not be avenged, save that thou swear:\\
an I slay thine killer, so wilt thou vouchsafe to me the means\\
by which I might slay death.\\
\\
He who killed you will join you in the Pit,\\
and then that’s it. No further swelling of Hell’s ranks will I permit.\\

GHOST: Done.\\
When my brother is slain, he who poured the poison in my ear,\\
then will I pour in yours the precious truth:\\
the making of the Philosopher’s Stone.\\
With this Stone, thou may’st procure\\
a philter to render any man immune to death, and more transmute\\ base metal to gold, to fund the gift of this philter to all mankind.\\

HAMLET: Truly there is nothing beyond the dreaming of philosophy.\\ Wait.\\ The man whom I must kill—my uncle the king?\\

GHOST: Ay, that incestuous, that adulterate beast,\\
With witchcraft of his wit, with traitorous gifts—\\

HAMLET: Indeed, he has such gifts I near despair,\\
of killing him and yet succeeding to his throne.\\
’twill be an awesome fight for awesome stakes.\\
Hast thou advice?\\

\emph{A cock crows. Exit Ghost.}
\end{playdialog}

\OmakeIVsection{Moby Who?}

“Revenge?” said the peg-legged man. “On a \emph{whale?} No, I decided I’d just get on with my life.”

\OmakeIVsection[0.9]{Alice in the Land Where Things Are Even Crazier Than Here}

Alice was sitting by her sister on the bank, reading a book. She had several friends who were older, and if she just asked nicely, they were often happy to lend her books without \emph{quite} so many pictures and conversations as was thought appropriate for a girl her age.

Hot days often made her feel sleepy and stupid, so Alice had thoughtfully wet a handkerchief and placed it at the back of her neck. Still her mind had gone off wandering (just as if it was some little kitten whose owner had taken their eyes off it for just a moment), and she had just decided that the pleasure of making a daisy-chain would be worth around 4/3 of the trouble of getting up and picking the daisies, which was nonetheless not equal to the opportunity cost of putting down her book, when suddenly a White Rabbit with pink eyes ran close by her.

There was nothing so \emph{very} remarkable in that; nor, in fact, did Alice think it so \emph{very} much out of the way to hear the Rabbit say to itself, “Oh dear! Oh dear! I shall be late!” But when the Rabbit actually \emph{took a watch out of its waistcoat pocket,} and looked at it, and then hurried on, Alice froze in sudden clarity and fear, for she had never before seen a rabbit with either a waistcoat-pocket, or a watch to take out of it. “Oh bother,” she said to herself (though not aloud; she had long since cured herself of that habit, as it made people take her even less seriously than they already did). “If I did not immediately recognize how much curiouser that was than the average rabbit, then something is interfering with my curiosity, and that is most curious of all.” So, burning with questions, she ran across the field after it, and was just in time to see it pop down a large rabbit-hole under the hedge.

\OmakeIVsection{Welcome to the Real World}

\begin{playdialog}
MORPHEUS: For the longest time, I wouldn’t believe it. But then I saw the fields with my own eyes, watched them liquefy the dead so they could be fed intravenously to the living—\\

NEO \emph{(politely)}: Excuse me, please.\\

MORPHEUS: Yes, Neo?\\

NEO: I’ve kept quiet for as long as I could, but I feel a certain need to speak up at this point. The human body is the most inefficient source of energy you could possibly imagine. The efficiency of a power plant at converting thermal energy into electricity \emph{decreases} as you run the turbines at lower temperatures. If you had any sort of food humans could eat, it would be more efficient to burn it in a furnace than feed it to humans. And now you’re telling me that their food is \emph{the bodies of the dead, fed to the living?} Haven’t you ever heard of the laws of thermodynamics?\\

MORPHEUS: Where did \emph{you} hear about the laws of thermodynamics, Neo?\\

NEO: Anyone who’s made it past one science class in high school ought to know about the laws of thermodynamics!\\

MORPHEUS: Where did you go to high school, Neo?\\

\emph{Pause.}\\

NEO: …in the Matrix.\\

MORPHEUS: The machines tell elegant lies.\\

\emph{Pause.}\\

NEO \emph{(in a small voice)}: Could I please have a real physics textbook?\\

MORPHEUS: There is no such thing, Neo. The universe doesn’t run on math.\\ \end{playdialog}

%  LocalWords:  Ratîonalît Applejack Fluttershy Sci everypony Velorien Kage
%  LocalWords:  Uchiha Sakura Bunshin superintelligence Naruto’s jōnin 40k
%  LocalWords:  Uchiha’s Smartingan Naruto genin Beisugakure Kyubey Sasuke
%  LocalWords:  Anōōō emotionlessly Sasuke’s Itachi ThunderSmarts Liono Ay
%  LocalWords:  Panthro Kvothe Tengen Toppa Gurren Jafar HonoreDB
%  LocalWords:  belov’d twas unshriven unlook’d punish’d confess’d philter
%  LocalWords:  escap’d stripp’d may’st Neo math
