\namedpartchapter{The Truth}{The Truth}{I}{Riddles and Answers}

\section{June 13th, 1992.}

\lettrine{I}{t} was the last week of school in Hogwarts, and Professor Quirrell was still alive, barely. The Defence Professor himself would be in a healer’s bed, this day, as he’d been for almost the last week.

Hogwarts tradition said that exams were given in the first week of June, that results were released in the second week, and that in the third week, there would be the Leave-Taking Feast on Sunday and the Hogwarts Express transporting you to London on Monday.

Harry had wondered, a long time ago when he’d first read about that schedule, just what exactly the students did during the \emph{rest} of the second week of June, since ‘waiting for exam results’ didn’t sound like much; and the answer had surprised him when he’d found out.

But now the second week of June was over as well, and it was Saturday; there was nothing left of the year but the Leave-Taking Feast on the 14th and the Hogwarts Express ride on the 15th.

And nothing had been answered.

Nothing had been resolved.

Hermione’s killer hadn’t been found.

Somehow Harry had been thinking that, surely, all the truth would come out by the end of the school year; like that was the end of a mystery novel and the mystery’s answer had been promised him. Certainly it had to be known by the time the Defence Professor…died, it couldn’t be allowed for Professor Quirrell to \emph{die} without knowing the answer, without everything being neatly resolved. Not exam grades, certainly not death, it was only truth that finished a story…

But unless you bought Draco Malfoy’s latest theory that Professor Sprout had been assigning and grading less homework around the time of Hermione being framed for attempted murder, thereby proving that Professor Sprout had been spending her time setting it up, the truth remained unfound.

And instead, as if the world had priorities that were more like other people’s way of thinking, the year was going to end with a climactic Quidditch match.

\later

In the air above the stadium, distant figures on broomsticks swooped and pirouetted and spun around each other. The red-purplish truncated tetrahedron that was the Quaffle was caught, tossed, blocked, and occasionally thrown through floating hoops, accompanied by stadium-rocking cries of triumph or dismay. Blue and green and yellow and red-trimmed robes shouted with the enthusiasm that people felt so easily when no action would be required from them personally.

It was the first Quidditch match Harry had attended at Hogwarts, and he’d already decided that it would be the last.

“Davies has the Quaffle!” shouted the amplified voice of Lee Jordan. “That’s another ten points for Ravenclaw in seven…six…five…holy smokes, he’s done it already! Smack through the centre of the central hoop! I’ve never seen such a winning streak—I’m calling it right now for Davies becoming Captain next year after Bortan steps down—”

Lee’s voice cut out abruptly and Professor McGonagall’s own amplified voice said, “That’s the Ravenclaw team’s own business, Mr~Jordan. Confine yourself to the match, please.”

“And the Slytherins take possession—Flint hands off the Quaffle to the lovely—”

“Mr~Jordan!”

“To the merely acceptable Sharon Vizcaino, whose hair trails behind her like a comet as she blazes toward the Ravenclaw defence—now with two Bludgers in close pursuit! Pucey’s on Sharon’s tail—what are you doing, Inglebee?—and she swerves in mid-air to avoid—\shout{is that the Snitch? Go, Cho Chang, go, Higgs is already—what are you two doing?}”

“Calm down, Mr~Jordan!”

“\shout{How am I supposed to calm down? That was the worst missed play I’ve ever seen!} And the Snitch is gone—maybe gone for good, after being missed that badly—Pucey’s heading off towards the goal posts, Inglebee’s nowhere near him—”

In a distant era of history, maybe in another world entirely, Professor Quirrell had undertaken that the House Cup would be awarded to either Slytherin or Ravenclaw. Or possibly, somehow, both; for he had promised that three wishes would be granted. So far it was looking good on two out of three.

If you just went by the current score, Hufflepuff was leading the race for the House Cup by something like five hundred points, thanks to Hufflepuff’s students doing their homework and \emph{staying out of trouble.} It appeared that Professor Snape had been strategically taking quite a lot of points from Hufflepuffs for, er, the last seven years or so. Slytherin House, reigning champion for the last seven years, still had to its advantage a certain \emph{generosity} of its Head of House in handing out points; and this was sufficient to put it neck-and-neck with Ravenclaw House, home of the academic achievers. Gryffindor was far behind in last place, as befit the House of nonconformists; Gryffindor had Slytherin’s profile when it came to academics and mischief, only without the advantage of Professor Snape. Even Fred and George had barely broken even on the year.

Ravenclaw House and Slytherin House both needed a lot of points from \emph{somewhere} if either wanted to catch up with Hufflepuff in the next two days.

And so far as anyone knew, Professor Quirrell hadn’t done a single thing leading to the obvious result. It was happening all by itself, now that one lone Professor in Hogwarts had taught a class with creative problem-solving.

The final Quidditch match of the year was between Ravenclaw and Slytherin. Earlier in the year, Gryffindor’s initial Quidditch lead had vanished after their new Seeker, Emmett Shear, fell off a possibly malfunctioning broomstick during his second game. This had also required some hasty rescheduling of the remaining games.

This, the final game of the year, wouldn’t end until the Snitch was caught.

Quidditch scores added directly onto the House points total.

And what did you know, today it seemed that both the Slytherin and Ravenclaw Seekers just could…not…catch…the…Snitch.

“\shout{The Snitch was practically on top of you, you dim-eyed dimwit!}”

“Language, Mr~Jordan, or I’ll remove you from this game! Though it \emph{was} terrible play, I admit.”

Harry had to admit that Lee Jordan and Professor McGonagall had a wonderful comedic routine, with Jordan as the banana-man and Professor McGonagall as the straight-woman; Harry now felt a little sorry to have missed it at the earlier Quidditch matches. It was a side of Professor McGonagall he hadn’t seen before.

A few seats down from where Harry sat in the Hufflepuff section of the stands, there lurked the hulking form of Cedric Diggory. The Super Hufflepuff had observed the most recent near-air-collision between Cho Chang and Terence Higgs with the keen eye of a wizard who was a Seeker and a Quidditch Captain in his own right.

“The Ravenclaw Seeker is new,” Cedric said. “But Higgs is in his seventh year; I’ve played against him. He’s better than that.”

“You think it’s a strategy?” asked one of the Hufflepuffs sitting next to Cedric.

“It would make sense if Slytherin needed some extra points to win the Quidditch Cup,” Cedric said. “But Slytherin already has the title in the bag. What are they thinking? They could’ve won right there!”

The game had started at six o’clock in the evening. A typical game would have gone until seven or so, at which point it would have been time for dinner. June in Scotland meant plenty of daylight; sunset wasn’t until ten.

It was at eight pm and six minutes, according to Harry’s watch, when Slytherin had just scored another 10 points bringing the score to 170–{140}, when Cedric Diggory leapt out of his seat and shouted “\emph{Those bastards!}”

“Yeah!” cried a young boy beside him, leaping to his own feet. “Who do they think they are, scoring points?”

“Not that!” cried Cedric Diggory. “They’re—they’re trying to \emph{steal the Cup from us!}”

“But we’re not in the running any more for—”

“\emph{Not the Quidditch Cup! The House Cup!}”

The word spread, with cries of outrage.

That was Harry’s cue.

Harry politely asked a Hufflepuff witch sitting next to him, and another Hufflepuff sitting one row above him, if they could move aside. Then Harry drew forth from his pouch a huge scroll, and unfurled it into a 2-metre-tall banner which stuck in place in mid-air. The enchantment had been done courtesy of a sixth-year Ravenclaw who had a reputation for knowing less about Quidditch than Harry did.

In huge, glowing purple letters, the sign read:

\begin{center}
JUST BUY A CLOCK

2 : 06 : 47
\end{center}

Beneath it was a Snitch, with a blinking red X over it.

\later

Second, after second, after second, the time counter incremented.

As that counter rose higher, there seemed to be an awful lot of Hufflepuffs who’d decided that they wanted to sit next to Harry’s banner.

As the game dragged on past nine, there also seemed to be a lot of Gryffindors.

As the sun set and Harry started using Lumos to read his books—he’d given up on the actual game a long time ago—there were a noticeable number of Ravenclaws who’d betrayed patriotism for sanity.

And Professor Sinistra.

And Professor Vector.

And as the stars began to come out, Professor Flitwick.

The climactic final Quidditch game of the year…dragged on.

\later

One of the things Harry hadn’t planned on, when he’d decided to do this, was that he would still be out here at—Harry glanced at his watch—eleven-oh-four at night. Harry was now reading a sixth-year Transfiguration textbook; or rather he’d weighted the book open, illuminated by a Muggle glow stick, while he did one of the exercises. Last week, when the graduating Ravenclaws were discussing their N.E.W.T. scores, Harry had overheard that upper-year Transfiguration practice involved several ‘shaping exercises’ that relied more on control and precise thinking than raw power; and Harry had promptly set out to learn those, whacking himself hard on the forehead for not trying to read \emph{all} the later-year textbooks earlier. Professor McGonagall had approved Harry doing a shaping exercise that involved controlling the way in which a Transfiguring object approached its final form—for example, Transfiguring a quill so that the shaft grew out first, then the barbs. Harry was doing an analogous exercise with pencils, growing out the lead first, then surrounding it with wood and finally having the eraser form on top. As Harry had suspected, focusing his attention and magic into a particular part of the pencil’s ongoing transformation had proven similar to the mental discipline used in partial Transfiguration—which could indeed have been used to fake the same effect, by partially Transfiguring only the outer layers of the object. This way was proving relatively easier, though.

Harry finished his current pencil and looked up at the Quidditch game, which was, check, still fantastically boring. Lee Jordan was commentating in a tone of dull disgust, “Another ten points—yay—whoopee—and now someone takes possession of the Quaffle again—ask if I care who.”

Almost nobody remaining in the stands was paying attention either, since everyone who’d remained in the stadium seemed to have discovered a new and more interesting sport, the debate about how to amend the House Cup rules and/or Quidditch. The argument had become heated to the point where all of the nearby Professors were barely keeping order at a level short of open combat. This argument, unfortunately, had considerably more than two factions. Some annoying busybodies were proposing sensible-sounding alternatives to eliminating the Snitch entirely, and this was threatening to split the vote and sap the momentum for reform.

In retrospect, Harry thought, it would have been nice to have Draco unfurl his own banner from the Slytherin side saying ‘SNITCHES ARE AWESOME’, to set the polarity of the debate. Harry had squinted over at the Slytherin section earlier, but he hadn’t been able to spot Draco anywhere in the stands. Severus Snape, who could also have been sympathetic enough to play the villainous opposition, was likewise nowhere to be seen.

“Mr~Potter?” said a voice next to him.

Beside Harry’s seat was standing a short but older Hufflepuff boy, someone who’d never before come to Harry’s attention, holding out a blank parchment envelope with wax dripped on the front. The wax was also blank, without impression.

“What is it?” said Harry.

“It’s \emph{me},” said the boy. “With the envelope you gave me. I know you said not to talk to you, but—”

“Then don’t talk to me,” Harry said.

The boy tossed the envelope at Harry and walked away, looking offended. It made Harry wince a little, but it probably hadn’t been the \emph{wrong} decision considering the temporal issues…

Then Harry broke the unsigned wax seal and drew out the envelope’s contents. It was parchment instead of the Muggle paper that Harry would have expected, but the writing on it was his own handwriting, if done with a quill instead of a pen. The parchment said:

\begin{writtenNote}
Beware the constellation,\\
and help the watcher of stars.\\
\\
Pass unseen by the life-eaters’ confederates,\\
and by the wise and the well-meaning.\\
\\
Six, and seven in a square,\\
in the place that is prohibited and bloody stupid.
\end{writtenNote}

Harry took it in at a glance, then folded the paper again and put it back into his cloak with another exhaled sigh. ‘Beware the constellation’, really? Harry would have expected a riddle left by himself, to himself, to have been easier to interpret…though some parts were obvious enough. Clearly future-Harry had been worried about this paper being intercepted, and while present-Harry wouldn’t ordinarily have thought of the local Aurors as ‘the ones in league with the Dementors of Azkaban’, maybe that had been the best way to say ‘Auror’ without potentially tipping off anyone else who read the parchment and did their own best to decrypt it. Translating the idiom back out of the Parseltongue he’d used during the Incident with Azkaban…that worked, Harry supposed.

The note had said that Professor Quirrell needed help, and that whatever was going on needed to pass unnoticed from the Aurors, and from Dumbledore and McGonagall and Flitwick. Since Time-Turning was involved already, the obvious solution was to leave for the loo, travel back in time, and return to the game right after he’d left.

Harry started to rise from his seat, then hesitated. His Hufflepuff side was remarking something about leaving the Auror escorts behind and not telling Professor McGonagall anything, and wondering if his future self was being \emph{stupid}.

Harry unfolded the parchment again, and took another glance at the contents.

On closer examination, the riddle-verse didn’t say that Harry couldn’t bring \emph{anyone} along. Draco Malfoy…was he missing from the Quidditch game because future-Harry, hours in the past, had brought Draco with him as backup? But that didn’t make sense, there wasn’t much marginal improvement in safety from bringing along another first-year…

…Draco Malfoy would certainly have been present, regardless of his personal feelings about Quidditch, to watch Slytherin clinch the House Cup. Had something happened to him?

Suddenly Harry didn’t feel as tired any more.

A trickle of adrenaline was starting to rise in Harry, but no, this wouldn’t be like the troll. The message had \emph{told} Harry when to arrive. Harry wouldn’t be too late, not this time.

Harry glanced over at where Cedric Diggory was looking back and forth, visibly torn between a clutch of Ravenclaws arguing that the Snitch had to be kept because it was traditional and rules were rules, and a pack of Hufflepuffs saying that it wasn’t fair for the Seeker to be more important than the other players.

Cedric Diggory had been an excellent duelling tutor to Harry and Neville, and Harry had thought they’d established a good relationship. More importantly, a student taking literally all of the electives would have his own Time-Turner. Maybe Harry could try to get Cedric to go back in time with him? The Super Hufflepuff seemed like a good spare wand to have by your side in any sort of sticky situation…

\latersection{Later, and earlier:}

Harry’s watch now said 11:45, which translated into 6:45\pm after looping back five hours.

“It’s time,” Harry murmured to the empty air, and began walking down the third-floor corridor above the grand staircase, on the right-hand side.

‘The place that is prohibited’ would ordinarily mean the Forbidden Forest; that was probably what someone intercepting the message was meant to think. But the Forbidden Forest was huge, and there was more than one distinguished location inside it. No obvious Schelling Point at which to rendezvous, or find some event that needed intervention.

But when you added the ‘bloody stupid’ modifier, there was only one prohibited place in Hogwarts that fit.

And so Harry set forth on that outlawed path where, if rumour spoke true, all the first-year Gryffindors had gone before. The third-floor corridor, on the right-hand side. A mysterious door leading to a series of rooms filled with dangerous and potentially lethal traps that nobody could possibly get through, especially if they were only in their first year.

Harry didn’t know himself what sort of traps awaited. Which, on reflection, meant that the students who’d gone through had been surprisingly scrupulous about not ruining the puzzle for others. Maybe there was a sign down there saying \emph{Don’t give it away, just as a favour to me, sincerely Headmaster Dumbledore}. All Harry knew so far was that the outer door would open to \emph{Alohomora,} and that the final room contained a magic mirror that would show your reflection in some situation you found highly appealing, which was apparently the big pay-off.

The third-floor corridor was illuminated by dim blue light that seemed to come from nowhere, and the arches were covered with cobwebs, as though the corridor hadn’t been used in centuries rather than just the last year.

Harry’s pouch was loaded with useful Muggle things, and useful wizarding things, and everything he’d found that could possibly be a quest item. (Harry had asked Professor McGonagall to recommend someone who could expand the pouch’s capacity, and she’d just done it herself.) Harry had applied the Charm he’d learned for battles that made his eyeglasses stick to his face, regardless of how his head moved. Harry had refreshed the Transfigurations he was maintaining, both the tiny jewel in the ring on his hand and the other one, in case he was knocked unconscious. He wasn’t literally ready for anything, but Harry was as ready as he thought he could be.

The five-sided floor tiles creaked beneath Harry’s shoes and vanished behind him like the future becoming the past. It was almost 6:49—\emph{six, and seven in a square.} Obvious if you thought in Muggle maths, otherwise not so much.

Just as Harry was about to round another corner, something tickled at the back of his mind, and he heard a soft voice talking.

“…sensible person…wait until later…after certain faculty
had departed…”

Harry stopped, then crept forward as lightly as he could, not going around the corner, trying to hear Professor Quirrell’s voice better.

There came a louder cough, and then the soft voice spoke again from around the corner. “But if they were also…to depart themselves…at that time…” murmured the voice, “they might think…this final game…makes for the best distraction…left in this year…a predictable distraction. So I looked…to see what people of significance…were not at the game…and I saw the Headmaster missing…but for all my magic can tell me…he could be in another…realm of existence…I also saw your own absence…so I decided to go…where you were. That is what I am doing here…now…what are \emph{you} doing here?”

Harry breathed shallowly, and listened.

“And just how did you know where I was?” drawled the voice of Severus Snape, so much louder that Harry nearly jumped.

A small, coughing laugh. “Check your wand…for Trace.”

Severus said something in magical pseudo-Latin, and then, “You dared tamper with my wand? You \emph{dared?}”

“You are a suspect…just like myself…so your false indignation is wasted…however finely crafted it may be…now tell me…what are you doing?”

“I am watching this door,” said the voice of Professor Snape. “And I will ask you to be off from it!”

“On whose authority…are you ordering me…my fellow Professor?”

There was a pause, then, “Why, the Headmaster’s,” came the smooth voice of Severus Snape. “I was ordered by him to watch this door during the Quidditch match, and as a Professor I must obey his whims. I shall have words about it with the Board of Governors later, but for now I am doing as I must. Now be off with you, as the Headmaster desires.”

“What? You mean I am to believe…that you abandoned your
Slytherins…during their most important…game of the year…and leapt up like a dog…at Dumbledore’s word? Well that…I must say…is entirely plausible. Even so…I think it would be wise…if I kept my own watch over you.. while you watch this fine door.” There was a sound of rustling cloth and a soft thud, as if someone had sat down hard upon the ground, or maybe just fallen.

“Oh, for the love of Merlin—” Severus Snape’s voice now sounded angry. “Get up, you!”

“Ba-blu-a-bu-bluh—” said the Defence Professor’s zombie-mode.

“Get up!” said Severus Snape, and there was a soft thud.

\emph{Help the watcher of stars—}

Harry stepped around the corner, though it was possible that he’d have done so even without an inter-temporal message. Had Professor Snape just \emph{kicked} Professor Quirrell? That would have been foolhardy if Professor Quirrell had been dead and \emph{buried.}

A round-topped door of dark wood was framed within a stone arch, set within the dusty marble bricks of Hogwarts. Where a Muggle would have set a doorknob there was only a handle of polished metal; there were no visible locks, or visible keyholes. Set upon the wall to either side, a pair of torches burned, sending forth an ominous orange glow. Before the door stood the Potions Master in his customary stained robes. Beside the door, to the left side beneath the orange torch, slumped the form of the Defence Professor, back against the wall, head staring out at the surroundings. The eyes seemed to flicker, as if halfway between awareness, and emptiness.

“\emph{What},” said the towering form of the Potions Master, “are you doing here, \emph{Potter?}”

Going by facial expressions and tone of voice, the Potions Master was quite angry with Harry; and certainly was not Harry’s co-conspirator in councils to which the Defence Professor had never been invited.

“I’m not sure,” Harry said. He wasn’t sure what role he should be playing, and was, in desperation, falling back on simple honesty. “I think perhaps I’m supposed to be keeping an eye on the Defence Professor.”

The Potions Master stared at him coldly. “Where’s your \emph{escort,} Potter? Students are not to wander these halls alone!”

Harry’s mind was genuinely blank. The game was afoot, and nobody had told him the rules. “I’m not sure how to answer that…”

The cold expression on Professor Snape’s face flickered. “Perhaps I should call the Aurors,” he said.

“Wait!” Harry blurted.

The Potions Master’s hand hovered about his robes. “Why?” said the Potions Master.

“I…I just think you probably shouldn’t call them…”

In a blur, the Potions Master’s wand was in his hand. “\emph{Nullus confundio!}” A black jet darted out and hit Harry, striking in the direction Harry had already started to dodge. There followed four other spells, containing words like \emph{Polyfluis} and \emph{Metamorphus;} and for those Harry politely stood still.

After all of those spells had failed to produce any effect, Severus Snape was staring at Harry with a dark glitter that now seemed genuine. “I suggest,” the Potions Master said softly, “that you explain yourself, Potter.”

“I can’t explain myself,” Harry said. “I don’t have the Time, not yet.”

Harry looked directly into the Potions Master’s gaze as he said the words \emph{myself} and \emph{time}, widening his own eyes to try to convey the key information, and the Potions Master hesitated.

Harry was frantically trying to work out who was pretending to be what. Since Professor Quirrell wasn’t in on Dumbledore’s conspiracy, Severus was pretending to be the evil Potions Master of Hogwarts, who’d been sent here by the Headmaster…and might or might not have actually been sent here by Dumbledore…but Professor Quirrell either thought, or was pretending to think, that someone needed to keep an eye on Professor Snape…and Harry himself had been sent here by future-Harry and had no idea why…and why were they all standing outside the Headmaster’s forbidden door in the first place?

And then…

From behind where Harry stood…

Came the growing sound of another set of footsteps, rapid and manyfold.

Professor Snape stabbed his wand once, creating a burst of darkness that shrouded where the Defence Professor was lying. “\emph{Muffliato,}” the Potions Master hissed. “Mr~Potter, if you must be here, then hide! Put on your invisibility cloak! My duty is to guard this door in case \emph{he} comes here. And there has been—a \emph{disturbance}, meant to draw the Headmaster, he thinks—”

“Who—”

Severus took a long stride forward and snapped his wand against the side of Harry’s head. There was a trickling sensation like an egg had been cracked over him, the feeling of a Disillusionment Charm; and Harry’s hands faded out, followed by the rest of him.

The darkness shrouding one side of the wall dissipated like slow mist, and there was again visible the huddled form of the Defence Professor, who said nothing.

Harry tiptoed away quietly as he could, then turned to watch.

The approaching footsteps rounded the corner—

“What are you doing here?” came many simultaneous cries.

Trimmed in three sets of Slytherin green and one Hufflepuff yellow stood Theodore Nott, Daphne Greengrass, Susan Bones, and Tracey Davis.

“\emph{Where,}” said Professor Snape with mounting wrath, “are your \emph{escorts,} children? First-years must be accompanied by a sixth or seventh-year student at all times! Especially you!”

Theodore Nott raised his hand. “We’re, um,” said Theodore Nott. “We’re doing what the Chaos Legion calls a team-building exercise…see, we realized just now that none of us had tried the Headmaster’s forbidden chamber yet, and there wasn’t much time left…and Harry Potter has authorized it, Professor, he said specifically that \emph{you} mustn’t interfere.”

Severus Snape turned to glance over at where Harry Potter had tiptoed; a storm seemed to be gathering on his brow, and a dark fury in his eyes.

\emph{I…maybe?} There was still one hour left on Harry’s Time-Turner, so it was possible.

“Harry Potter does not have that authority,” the Potions Master said in a deceptively mild tone. “Explain yourselves, now.”

“Really?” said the form of Susan Bones. “Really? You’re telling Professor Snape that Harry Potter authorized the mission, that’s your idea of a bluff?” The young Hufflepuff turned to Professor Snape and spoke, her voice strangely firm. “Professor, this is the truth and it’s urgent. Draco Malfoy is missing and we think he went down there—”

“If Mr~Malfoy is missing,” said Professor Snape, “\emph{why have the Aurors not been notified?}”

“Because of, because of \emph{reasons!}” cried Daphne Greengrass. “There’s no time, you’ve got to let us through!”

Professor Snape’s voice was now as sardonic as Harry had ever heard it. “Are you four morons under the impression that you are on some sort of adventure? Well, you are mistaken. I assure you that Mr~Malfoy has not passed through this door.”

“We think Mr~Malfoy has an invisibility cloak,” Susan Bones said rapidly. “Do you remember the door seeming to open for no reason?”

“No,” the Potions Master said. “Now be gone from here. This place is off-limits for today.”

“This is \emph{Dumbledore’s} forbidden corridor,” Tracey said. “The Headmaster himself said nobody was to come here. Who do you think you are, forbidding it too?”

“Miss~Davis,” said the Potions Master, “you need to stop associating with Gryffindors, especially those named Lavender Brown. And if you are still here in one minute, I will file papers requesting your transfer into that House.”

“\emph{You wouldn’t dare!}” shrieked Tracey.

“Hm,” Susan Bones said, her face screwed up in concentration. “Professor Snape, do you occasionally open the door yourself, to check on whatever’s inside?”

Professor Snape froze in place. Then he spun and put his right hand on the metal knocker—

Harry was watching the hand on the knocker, so he didn’t notice what Professor Snape was doing with his left hand until he heard the sudden cry.

“No, in fact,” said Professor Snape, now holding the choking head of Draco Malfoy by his collar, though the rest of Draco was still underneath his invisibility cloak. “A fine try, though.”

“\emph{What?}” cried Tracey and Daphne.

Susan Bones hit herself in the forehead. “I can’t \emph{believe} I fell for that.”

“So, Mr~Malfoy,” Professor Snape said. His voice had lowered. “You sent your friends here on a ruse…just in the hopes that you could pass through this door? Now why would you do that?”

“I think we should trust him—” said Theodore Nott. “Mr~Malfoy, we’ve \emph{got} to trust him, he’s the one Professor who would take our side!”

“No!” cried Draco’s floating head, from where Professor Snape was still grasping his collar. “You mustn’t say anything! Stop!”

“We’ve got to take the chance!” yelled Theodore. “Professor Snape, Mr~Malfoy finally worked out what’s been going on this whole year, and why—Dumbledore is trying to get the Philosopher’s Stone away from Nicholas Flamel! Because Dumbledore doesn’t think anyone ought to have immortality! So Dumbledore tried to convince Flamel that the Dark Lord was coming back and needed the Stone to revive, and asked Flamel to give it to him, but Flamel wouldn’t, and instead Flamel put the Stone in the magic mirror that’s down there, and Dumbledore is finding out right now how to get it, and then he’ll come for it and we’ve got to get to it first! Dumbledore really will be all-powerful if he gets the Philosopher’s Stone!”

“\emph{What?}” said Tracey. “That’s not what you said before!”

“It—” Daphne said. She looked frightened, but determined. “It doesn’t matter—Professor Snape, please, you \emph{have} to believe me. I looked at the books Hermione checked out of the library, and she was researching the Philosopher’s Stone just before someone killed her. Her notes said that something dangerous might happen if the Stone stays inside the mirror too long. We have to get it out of the castle right away.”

Susan Bones now had both hands over her face. “I’m not with them, I just came along to prevent anything even stupider from happening.”

Severus Snape was staring at Theodore Nott and the others. Then he turned his head to look at Draco Malfoy. “Mr~Malfoy,” the Potions Master drawled. “How did you come to discover Dumbledore’s plot?”

“I deduced it from evidence!” said Draco Malfoy’s floating head.

Professor Snape’s head swivelled back to Theodore Nott. “How did you intend to obtain this Stone from inside a magic mirror that could supposedly baffle Dumbledore himself? Answer me at once!”

“We’re going to take the whole mirror and send it back to Flamel,” said Theodore Nott. “It’s not like we want the Stone for ourselves, we just need to stop Dumbledore from stealing it.”

Professor Snape nodded, as though confirming something, and turned his head to look at the other students. “Tell me, have any of you noticed one of the others behaving in an unusual fashion? Especially if there is a peculiar object that they have in their possession, or they can use spells a first-year should not know?” Professor Snape’s right hand now pointed his wand at Susan Bones. “I see that Miss~Greengrass and Miss~Davis are trying not to look at you, Miss~Bones. If there is a mundane explanation, you would be wise to offer it \emph{immediately.}”

Susan Bones’s hair turned bright red, though her face didn’t change. “I suppose there’s not much point keeping it mum any longer,” she said, “since I’m graduating in two days anyway.”

“Double witches get to graduate \emph{six years} early?” said Tracey Davis. “That’s not fair!”

“\emph{Bones is a double witch?}” cried Theodore.

“No, she is Nymphadora Tonks, a Metamorphmagus,” Professor Snape said. “Masquerading as another student is extremely against regulation, as you are well aware, Miss~Tonks. It is not too late to expel you from Hogwarts two days before your graduation, which would be a dreadful tragedy—from your perspective, that is. From my perspective it would be hilarious. Now tell me what exactly you are doing here.”

“That explains it,” said Daphne Greengrass. “Um, is there \emph{actually} a Susan Bones, or is the House dying out so they had you secretly—”

The red-haired form of Susan Bones had a palm to her face. “Yes, Miss~Greengrass, there’s a real Susan Bones. She only sends me in when \emph{you} lot are about to get into ridiculous amounts of trouble. Professor Snape, the reason I’m here is because Draco Malfoy was missing, and this lot \emph{insisted} on trying to find him instead of calling the Aurors. For reasons the real Miss~Bones said there was no time to explain to me, which I now realize were stupid. But young students must never go alone, and must be accompanied by a sixth or seventh year at all times. And now we found Draco Malfoy and we can all go back. Please? Before this gets any more ridiculous?”

“\emph{What in Merlin’s name is going on here?}”

“Ah,” said Professor Snape, who was still pointing the wand at the red-haired form of Susan Bones, his other hand still grasping the collar below the disembodied head of Draco Malfoy, standing next to the crumpled form of the Defence Professor. “Professor Sprout, I perceive.”

“It’s not what it looks like,” volunteered Tracey Davis.

The short, dumpy form of the Herbology Professor stormed forwards. She had, by this point, drawn her wand, though she wasn’t pointing it at anyone. “\emph{I don’t even know what this looks like! \emph{Down wands, all of you,} right now!} Including you, Professor!”

\emph{Distraction.} The thought came to Harry with sudden clarity. Whatever he was watching now, from where he stood invisibly and well back of the action, it wasn’t \emph{what was really going on}, it wasn’t the true thread of the story, it had been \emph{arranged}. Professor Sprout’s arrival had broken Harry’s suspension of disbelief; things like that didn’t happen just for the sake of comedic coincidence. Someone was deliberately causing all this chaos, but what was the point?

Harry really hoped he hadn’t gone back in time and done this, because it did seem like the sort of thing he would do.

Severus Snape lowered his wand. His other hand released Draco Malfoy. “Professor Sprout,” the Potions Master said, “I am here on the Headmaster’s orders to watch this door. Everyone else present is \emph{not} supposed to be here, and I ask you to see them cleared away.”

“A likely story,” snapped Professor Sprout. “Why would Dumbledore set you of all people to guard the door to his playground? It’s not as if he wants to keep the students out, oh no, they need to go in and get stuck in \emph{my} Devil’s Snare! Susan, dear, you’ve got a communications mirror, don’t you? Use it to call the Aurors.”

The watching Harry nodded to himself. \emph{That} was the point. The Aurors would take away everyone present at this terribly confusing situation, no excuses accepted, and then the door would be unguarded.

But was Harry meant to go into the forbidden corridor himself? Or watch, to see who finally came once all the others were gone?

A loud fit of hacking and coughing caused everyone to look at where the Defence Professor lay.

“Snape…listen…” said the Defence Professor between coughs. “Why…Sprout…here…”

The Potions Master looked down.

“Memory Charm—implies—Professor—” The Defence Professor began coughing again.

“\emph{What?}”

And the logic unfolded in Harry’s mind in crystalline dismay, all the steps already suspected, the dreadful realization coming as a repetition with greater confidence.

Someone had Memory-Charmed Hermione to believe she’d tried to kill Draco.

Only a Hogwarts Professor could have done it without alarm.

So all the true mastermind needed to do was Legilimize or Imperius a Hogwarts Professor.

And the last person anyone would suspect would be the Head of House Hufflepuff.

Snape’s head snapped around, as Professor Sprout raised her wand, and the Potions Master managed to raise a wordless translucent ward between them. But the bolt that shot from Professor Sprout’s wand was a dark brown that produced a surge of awful apprehension in Harry’s mind; and the brown bolt made Severus’s shield wink out before they touched, clipping the Potions Master’s right arm even as he dodged. Professor Snape gave a muffled shriek and his hand spasmed, dropping his wand.

The next bolt that came from Sprout’s wand was a bright red the colour of a Stunning Hex, seeming to grow brighter and move faster even as it left her wand, accompanied by another surge of anxiety; and that blew the Potions Master into the door, dropping him motionless to the ground.

By that time pink-haired-Susan-Bones was surrounded by a multifaceted blue haze and she was firing hex after hex at Professor Sprout. Professor Sprout was ignoring the hexes to summon plant tendrils that entangled the younger students as they tried to run, except Draco Malfoy, who had again vanished beneath his invisibility cloak.

Not-Susan-Bones stopped casting hexes. She levelled her wand, took a deep breath, and cried aloud an incantation that sent golden worms of light chewing into the shield around Professor Sprout. At that the Herbology Professor turned to face not-Susan, her expression vacant, a new set of plant tentacles rising in the air behind her. Those stalks were a darker green, and seemed to have shields of their own.

Harry Potter murmured to the seemingly empty air, “Attack Sprout. Help Bones. Non-lethal only.”

“Yes, my lord,” whispered Lesath Lestrange beneath Harry’s Cloak of Invisibility, and the fifth-year Slytherin’s presence moved off toward the fight.

Harry looked down at at his own hands, and saw with a jolt of unpleasant shock that his Disillusionment Charm wasn’t as complete as it had been before. There were hints of distortion in the air, each time Harry moved…

Slowly, Harry stepped backward, until he came to a corner, and ducked behind a wall. Then he took out his communications mirror…which was blank and jammed. Of course. Harry levitated the mirror to where he could use it to see around the corner, and watch the end of the…distraction? \emph{What was happening, why?}

Professor Sprout and the form of Susan Bones were duelling in flashes of light and leaves; and the blazing green of a Greater Drill Hex erupted from mid-air and chewed halfway through the outer layer of Professor Sprout’s shields. The Herbology Professor turned and fired a broad wash of yellow at where the Drill Hex had come from, but the spell didn’t seem to hit anything.

Yellow blazes, blue facets, dark green plant-tendrils and swirling purple flower petals…

It was when Professor Sprout started firing arcs of crimson in all directions that one of the crimson blades caught something in mid-air, the Invisibility Cloak not concealing how the crimson arc was absorbed and winked out; and Lesath’s presence beneath the Invisibility Cloak fell to the ground.

And that gave not-Susan-Bones time enough to stand still, catch her breath, and scream something that inspired in Harry another surge of dread; and the white spark that blazed forth went through Professor Sprout’s chewed shields and her plant-armour and dropped her.

Not-Susan-Bones went to her knees, panting, her robes soaked in sweat.

Her head turned to look around her, at the bodies lying stunned on the floor or wrapped in vines.

“What,” said not-Susan. “What. What. \emph{What.}”

There was no reply. The victims entangled in Professor Sprout’s vines weren’t moving, though they did seem to be breathing.

“Malfoy…” said the pink-haired form of Susan, still gasping for breath. “Draco Malfoy, where are you? Are you there? Call the Aurors already! Merlin damn it—\emph{Hominem Revelio!}”

And Harry found himself visible again, staring in his mirror at the form of Draco Malfoy half-visible beneath a shimmering cloak, standing behind not-Susan, pointing his wand at a gap in not-Susan’s blue haze.

Harry’s mind moved in flashes of rapid insight, and yet too slow; even as Harry’s mouth opened and he inhaled in preparation to shout…

\noindent{}\emph{beware the constellation}\\
there was a constellation named Draco\\
if you could control a Professor you could control a student

“\emph{Duck!}” Harry shouted, but it was too late, a bolt of red light caught the back of not-Susan’s head point-blank, smashing her to the floor.

Harry stepped around the corner and said, “\emph{Somnium Somnium Somnium Somnium Somnium Somnium.}”

Draco Malfoy’s shimmering form collapsed in a heap.

Harry took a moment to catch his breath. Then Harry said “\emph{Stupefy!}” and verified that, yes, the Stunning Hex did hit Draco Malfoy’s form.

(You could be mistaken about whether a Somnium had really hit. Harry had seen enough horror films, not to mention the business with the Sunshine Regiment, that he wasn’t about to make \emph{that} error again.)

After a further reflection on this, Harry cast another Stunning Hex into the prostrate form of Professor Sprout.

Harry gripped his wand, staring at the scene, breathing heavily from the exhaustion. He didn’t have enough magic left to cast a messenger Patronus to Dumbledore and he \emph{really really} should have thought of that possibility immediately this time around. Harry started to reach back to where his mirror had fallen, to see if it was now unjammed.

And then Harry hesitated.

His note to himself had said to avoid notice from Aurors, and Harry still \emph{did not know what was going on.}

The crumpled form of Professor Quirrell gave another series of racking coughs, reached out a hand to the wall beside him, and slowly pulled himself to his feet.

“Harry,” croaked Professor Quirrell. “Harry. Are you there?”

It was the first time Professor Quirrell had ever called him by his first name.

“I’m here,” Harry said. Without any conscious thought, his feet were moving forward.

“Please,” said Professor Quirrell. “Please, I haven’t…much time. Please take me…to the mirror…help me…get the Stone.”

“The \emph{Philosopher’s} Stone?” Harry said. He glanced around at the scattered bodies, but he couldn’t see Draco any more, the revealment had worn off. “You think Mr~Nott was \emph{right?} I don’t think Dumbledore would—”

“Not—Dumbledore,” gasped Professor Quirrell. “Because—Sprout—”

“I understand,” Harry said. If Dumbledore had been the one behind it all, he wouldn’t have needed to mind-control a Professor in order to use Memory Charms.

“Mirror…ancient relic…could hide anything…Stone could
be there…many others want Stone…one sent Sprout…”

Harry repeated rapidly, “The mirror down there is an ancient relic that can be used to hide things, and it would be one possible place to hide the Philosopher’s Stone. If the Philosopher’s Stone is inside the mirror then any number of people might want to get it. One of them is controlling Sprout and that would explain what their goal really is…only…that doesn’t explain why Sprout’s controller would go after Hermione?”

“Harry, please,” Professor Quirrell said. His breathing was yet more laboured now, his voice came with excruciating slowness. “It’s the one thing…that can save my life…and I find, now…I don’t want to die…please, help me…”

And somehow that tore it.

Somehow that was a little too much.

The sense of detachment that had come over Harry when Professor Sprout had arrived, the broken suspension of disbelief, was returning; his Inner Critic weighing up everything as though it were a set-piece. Timing, probability, so many people showing up at the same door, the Defence Professor’s desperation…this whole situation didn’t feel real. But he might be able to \emph{solve it} if he just took time to think things through in advance, instead of running off at adventure’s first call. All the accumulated experience from the last year had finally crystallized into something like a touch of battle hardening. An instinct born of past disaster was telling Harry that if he just rushed on ahead, he would end up afterwards in a sad conversation, realizing that he’d been stupid. \emph{Again.}

“Let me think,” Harry said. “Let me think for a minute before we go.” He turned away from the Defence Professor, looking at the unconscious bodies draped in various shapes over the floor. There’d been so many puzzle pieces already, this last year, maybe everything would just fall into place with one more piece…

“Harry…” the Defence Professor said in a faltering voice. “Harry, I’m dying…”

\emph{One more minute can’t make the difference he’s had the \emph{whole year} to be sick it’s \emph{improbable} that his life versus death would be precisely timed to rest on this last minute no matter what happened to Hermione—}

“I \emph{know!}” Harry said. “I’ll think \emph{quickly!}”

Harry stared at the bodies and tried to think. There was no time for doubts, for caveats, no brakes or second-guessing just take the first thoughts and \emph{run with them—}

In the back of Harry’s mind, fragments of abstract thought flitted past, heuristics of problem-solving that there was no time to rehearse in words. In wordless flashes they shot past, to set up the object-level problem.

—\emph{what do I notice I am confused by—}

\emph{—the first place to look for a problem is whatever aspect of the situation seems most improbable—}

\emph{—simple explanations are more probable, eliminate separate improbabilities that must be postulated—}

Professor Snape had already been here then Professor Quirrell had arrived then Harry had arrived (via Time-Turner) then the adventuring party had arrived and Draco had been revealed (part of the party) then Professor Sprout had shown up.

Too many people had shown up \emph{synchronously} and that was too much coincidence, it was \emph{improbable} that so many different parties would show up at the same location within a five-minute window, there \emph{had} to be hidden entanglements.

Label Sprout’s controller as the mastermind who had ordered Hermione Memory-Charmed. The mastermind had sent Sprout.

Professor Snape had said that the Headmaster had sent him to guard the door after there’d been some sort of \emph{disturbance}, if the mastermind had caused that as a distraction then that explained Severus’s presence as well.

Harry wasn’t sure any more that Draco had been controlled by the mastermind, that hypothesis had come to him in the spur of the moment, Draco might have just been trying to drop not-Susan so he could get into the corridor unhindered—

No that was the wrong way to think, turn it around, try to \emph{explain} the timed presence of Draco and his adventuring party, no time for self-questioning, \emph{run with the hypothesis,} therefore suppose Sprout’s mastermind had sent Draco or triggered his coming.

That was three arrivals explained.

Harry had shown up because his note to himself had told him to do so. That could be attributed to time travel.

That left the Defence Professor who’d said he was following Snape, only that didn’t \emph{really} seem like an adequate reason for Professor Quirrell to show up it didn’t really make Harry feel less confused and so maybe the mastermind had also controlled the timing of Professor Quirrell’s presence somehow and even arranged for Harry himself to enter the time loop.

Harry’s mind hit a stumbling-block, he couldn’t see how to extend that reasoning further.

There was no time to stare blankly at stumbling-blocks.

Without any pause or braking Harry’s mind attacked the problem from a new angle.

Professor Quirrell had deduced a controlled Hogwarts Professor from the need for some Professor to Memory-Charm Hermione which meant that Professor Sprout’s controller had framed and then murdered Hermione which meant Professor Sprout’s controller had detailed information about Hogwarts life and maybe a personal interest in the Boy-Who-Lived and his friends.

Harry’s mind finally threw up the relevant memory, Dumbledore saying that Lord Voldemort’s strongest road to life was hidden here inside Hogwarts \emph{run with the hypothesis} so that resurrection tool was the Philosopher’s Stone hidden inside the mirror \emph{why had Dumbledore put the mirror into a corridor first-years could get through no ignore this question it’s not important right now} and Professor Quirrell had said the Philosopher’s Stone possessed great healing power so that part also fit.

But if it was the Philosopher’s Stone that was hidden in the mirror to keep it away from the Dark Lord, that meant the mirror also contained the one thing in the world that could save the Defence Professor’s life—

Harry’s mind tried to hesitate, to flinch away, feeling a sudden apprehension as to where this was going.

But there was no time allowed for hesitation.

-and that was also far too much coincidence just too much improbability if your mind didn’t write it off as an amazing plot twist like you were inside a story.

Could the putative Dark Lord also be manipulating Professor Quirrell so that Professor Quirrell would discover his supposed salvation at the right time so that Harry and Professor Quirrell would go get the resurrection tool from the mirror that might not even actually be the Philosopher’s Stone and then the Dark Lord’s avatar or some other servant would show up and seize it from them that would explain \emph{all} the synchronies and negate every coincidence.

Or Professor Quirrell had known from the beginning that the one thing that could save his life was hidden inside this mirror and that was why he had agreed to teach Defence at Hogwarts and now he was finally trying to get it but then why wait until he was this sick to even try and why had Sprout shown up at the same time as Professor Quirrell—

Harry’s mind faltered harder.

His inner eye was looking in a direction it was afraid to look.

\emph{The note I sent myself said to help the watcher of stars. I wouldn’t send myself a note saying that, if I hadn’t already worked out in the future that it was the right thing to do—maybe the note is just telling me to get on with it—}

A small note of confusion was promoted to conscious attention.

The coded message on the parchment…one or two lines hadn’t quite sounded right, hadn’t sounded like the code Harry would expect himself to use…

“Harry,” whispered the dying voice of Professor Quirrell from behind him. “Harry, please.”

“I’m almost done thinking,” Harry’s voice said aloud, and Harry realized as he spoke the words that they were true.

Turn it around.

Look at it from the Enemy’s perspective, from where the Enemy does their own intelligent planning, somewhere out of your sight.

There are Aurors in Hogwarts, and your target Harry Potter is now fully on guard. Harry Potter will call in Aurors at the first sign of trouble, or send a Patronus to Albus Dumbledore. Considering that as a puzzle, one creative solution is to—

—forge a supposedly Time-Turned message to Harry Potter from himself, telling Harry Potter \emph{not} to call for help, telling him to be at the place and time you want him to be. You get the target himself to bypass all the protections he set up. You even bypass his protection of skepticism with the overriding authority of his own future self’s judgement.

It isn’t even difficult. You can Memory-Charm some random student into remembering Harry Potter handing over an envelope to be given back to himself later.

You can Memory-Charm that student because you are a Hogwarts Professor.

You don’t go to the extra effort to steal a pencil and Muggle paper from Harry Potter’s pouch. Instead you forge Harry Potter’s handwriting on wizard parchment. You can forge Harry Potter’s handwriting because you have seen it on Ministry-mandated exams you have graded.

You call Draco Malfoy ‘the constellation’ because you know Harry Potter is interested in astronomy and you are a wizard and you have taken Astronomy and memorised the names of all the constellations. But it’s not the natural code that Harry Potter would use to describe Draco Malfoy to himself, that would have been ‘the apprentice’.

You call Professor Quirrell ‘the watcher of stars’, and tell Harry Potter to help him.

You know that life-eater is how you say ‘Dementor’ in Parseltongue and you expect Harry Potter to think of the Aurors as being in league with them.

You encode 6:49 as ‘six, and seven in a square’ because you have been reading a Muggle physics book that Harry Potter gave you.

Who are you, then?

Harry noticed his breathing had sped up, and, heart racing for a moment, slowed his breath down again; Professor Quirrell was \emph{watching him}.

What if hypothetically speaking Professor Quirrell was the mastermind and had faked Harry’s message then that explained all five parties showing up the whole synchronous coordination of the comedy and then Professor Sprout was just controlled to give Professor Quirrell deniability let him blame someone else for the False Memory Charm after the dust settled but

But why would Professor Quirrell risk the fragile alliance Harry had with Draco via the attempted murder-frame

(that Professor Quirrell had ‘detected’ and ‘stopped’ allegedly via a tracer put on Draco)

Why would Professor Quirrell kill Hermione

(if his first attempt to remove her hadn’t worked)

If Professor Quirrell was the bad guy then he might have lied about everything to do with horcruxes and maybe it wasn’t coincidence at all that the only thing that could save his life was the avenue that could resurrect the Dark Lord what if the Dark Lord had arranged that too somehow

(one day David Monroe had mysteriously disappeared, presumed dead at the Dark Lord’s hands)

An awful intuition had come over Harry, something separate from all the reasoning he’d done so far, an intuition that Harry couldn’t put into words; except that he and the Defence Professor were very much alike in certain ways, and faking a Time-Turned message was just the sort of creative method that Harry himself might have tried to bypass all of a target’s protections—

And that was when Harry finally realized what should have been obvious from the very, very beginning. \later Professor Quirrell was smart.

Professor Quirrell was smart in the same way as Harry.

Professor Quirrell was smart in exactly the same way as Harry’s mysterious dark side.

If you had to guess when the Boy-Who-Lived had acquired his mysterious dark side, the obvious guess was the night of October 31st, 1981.

\later

And\\
And\\
And Professor Quirrell had known a password that Bellatrix Black had thought identified the Dark Lord and his presence gave the Boy-Who-Lived a sense of doom and his magic interacted destructively with Harry’s and his favourite spell was Avada Kedavra and and and—

The realization blasted through Harry like a vast dam breaking, releasing out all its water, bursting through his mind in an irresistible flood that swept everything away.

There is only one reality that generates all of the observations.

If different observations seem to point in incompatible directions, it means the true hypothesis is one you haven’t thought of yet.

And in those cases, when you finally think of the correct hypothesis, everything aligns behind it, beyond denial or horror, tearing away every doubt and every emotion that might stand in its path.

—and then ‘David Monroe’ and ‘Lord Voldemort’ had just been one person playing both sides of the Wizarding War and that was why the Monroe family had been killed before they could meet ‘David Monroe’ just like Moody had suspected—

Reality settled down into a single known state, one coherent state-of-affairs that compactly generated the observation set.

Harry didn’t jump, didn’t change his breathing, tried not to show a single sign of the horror and agony flooding his mind.

The Enemy was behind him, watching him.

“All right,” Harry said out loud, as soon as he dared trust his voice to sound normal. He kept on staring at the bodies, looking away from Professor Quirrell, because Harry didn’t trust his own face. Harry lifted a sleeve to wipe away the sweat on his forehead, trying to make the gesture look casual; Harry couldn’t control the sweat, or the rapid hammering in his chest. “Let’s go get the Philosopher’s Stone.”

All Harry needed was a single moment of distraction anywhere along the way to use his Time-Turner.

There was no reply from behind him.

The silence stretched.

Slowly, Harry turned around.

Professor Quirrell was standing upright and smiling.

In the Defence Professor’s hand was a shape of black metal pointed at Harry’s wand arm, held with the sure grip of someone who knew exactly how to use a semi-automatic handgun.

Harry’s mouth was dry, even his lips were trembling with adrenaline, but he managed to speak. “Hello, Lord Voldemort.”

Professor Quirrell inclined his head in acknowledgement, and said, “Hello, Tom Riddle.”

%  LocalWords:  Bortan Vizcaino Pucey’s Inglebee Higgs Inglebee’s Ba blu bu
%  LocalWords:  bluh Metamorphus Muffliato revealment
