\partchapter{The Truth}{III}

\lettrine{A}{fter} a single step into Dumbledore’s forbidden chamber, Harry shrieked and jumped back and collided with Professor Snape, sending the two of them down in a heap.

Professor Snape picked himself up and resumed standing in front of the door. His head tracked to look at Harry. “I am guarding this door at the Headmaster’s orders,” said Professor Snape in his usual sardonic tones. “Be off with you at once, or I shall deduct House Points.”

This was bone-chillingly creepy, but Harry’s attention was occupied by the gigantic three-headed dog which had lunged forward, only to be stopped metres from Harry by the chains upon its three collars.

“That—that—that—” Harry said.

“Yes,” Professor Quirrell said from some way behind him, “that is indeed the usual occupant of that chamber, which is off-limits to all students, especially first-years.”

“\emph{That’s not safe even by wizard standards!}” Within the chamber, the enormous black beast gave a multi-voiced bellow, flecks of white saliva flying from three fanged mouths.

Professor Quirrell sighed. “It is enchanted not to eat students, just spit them back out through the door. Now, boy, how would you recommend that we deal with this dangerous creature?”

“Uh,” Harry stuttered, trying to think over the continued roaring of the chamber’s guardian. “Uh. If it’s like the Cerberus from the Muggle legend of Orpheus and Eurydice, then we have to sing it to sleep so we can pass—”

“\emph{Avada Kedavra.}”

The three-headed beast fell over.

Harry looked back at Professor Quirrell, who was giving him a look of extreme disappointment, as if to ask whether Harry had attended any of his classes, ever.

“I sort of \emph{assumed},” Harry said, still trying to catch his breath, “that going through this challenge in any way except the one used by first-years, might perhaps trigger an \emph{alarm}.”

“That is a lie, boy, you simply did not remember your lessons when you faced the occasion in true life. As for alarms, I have spent months befuddling all the wards and tripsigns upon these chambers.”

“Then why did you send me in first, exactly?”

Professor Quirrell just smiled. It looked significantly more evil than usual.

“Never mind,” Harry said, and walked slowly into the chamber, his limbs still shaking.

The chamber was all of stone, illuminated by a pale blue light that shone from arched nooks carved into the wall; as if the light of a grey sky were passing through windows, though there were no windows. At the far end of the chamber was a wooden trapdoor upon the floor, with a single ring attached. In the middle of the chamber lay a gigantic dead dog with three lifeless heads.

Harry turned toward one of the arched nooks and looked inside it. There was nothing there but the sourceless blue glow, so he walked over and looked in the next one, also scrutinizing the wall as he passed.

“What,” said Professor Quirrell, “are you doing?”

“Searching the room,” Harry said. “There could be a clue, or an inscription, or a key we’ll need later, or something—”

“Are you serious, or are you deliberately trying to slow us down? Answer in Parseltongue.”

Harry looked back. “\parsel{Was serious,}” hissed Harry. “\parsel{Would have done same if came by myself.}”

Professor Quirrell briefly massaged his forehead. “I confess,” he said, “that your approach would serve you well in, say, exploring the tomb of Amon-Set, so I will not quite call you an idiot, but still. The false puzzle, the outer form of the challenge, is a game meant for first-years. We simply go down through the trapdoor.”

Beneath the trapdoor was a gigantic plant, something like an enormous dieffenbachia with wide leaves emerging from the central stem like a spiral staircase, but darker-coloured than a normal dieffenbachia, with tendril-like vines emerging from the central stem and hanging down. The base spread out wide with bigger leaves and tendrils, as though promising to cushion anyone’s fall. Beneath was another stone chamber like the first, with the same nooks like false arched windows, emitting the same grey-blue light.

“The obvious thought is to fly down on the broomstick in my pouch, or toss something heavy to see if those tendrils are traps,” Harry said, peering down. “But I’m guessing you’ll say that we just walk down the leaves.” They certainly looked like they were meant to be a spiral staircase.

“After you,” said Professor Quirrell.

Harry carefully put a foot down on a leaf and found that it indeed supported his weight. Then Harry took a last look around the room before departing, to see if there was anything worth noticing.

The enormous dead dog called enough attention to itself that it was hard to focus on anything else.

“Professor Quirrell,” Harry said, omitting the phrase \emph{your approach to dealing with obstacles has certain drawbacks,} “what if somebody looks in the door and sees that the Cerberus is dead?”

“Then they have probably already noticed something wrong with Snape,” said Professor Quirrell. “But since you insist…” The Defence Professor walked over to the three-headed corpse and placed his wand against it. He began a Latin-sounding incantation that was accompanied by a sense of rising apprehension, the Boy-Who-Lived feeling the Dark Lord’s power as he always had.

The last word spoken was “\emph{Inferius}” and it was accompanied by a final surge of \emph{STOP, DON’T}.

And the three-headed dog rose to a stand, its six eyes dull and blank, turning to watch the door once more.

Harry stared at the huge Inferius with a horrible sinking sensation in his stomach, the third-worst feeling he’d ever felt in his life.

He knew then that he’d seen and sensed this procedure before, only without the spoken Latin.

The centaur who’d confronted him in the Forbidden Forest was dead. The Defence Professor had hit it with a real Avada Kedavra, not a fake one.

Somewhere in the back of his mind, Harry had thought that if he could just get Hermione \emph{back} then he could return to the code of nobody dying, the ethic of Batman. Most people went through their whole lives without anyone getting killed on whatever adventures they had.

And that was not to be.

He hadn’t even noticed, the day he lost his last chance to win. Even if Hermione was resurrected, now, Harry wouldn’t have come through the whole mess without anyone getting killed.

He hadn’t even learned the centaur’s name.

Harry said nothing aloud. The Defence Professor would either confirm the accusation in Parseltongue or lie in plain speech, and either way the Defence Professor would have more reason to suspect Harry’s next actions. But Harry knew that—although he didn’t know \emph{how} he would stop Professor Quirrell, although he didn’t dare any positive act of betrayal, maybe not even making the \emph{decision,} until it was almost time to win—there would never be an amicable settlement between him and Lord Voldemort, for those two different spirits could not exist in the same world.

And it was as if that resolution, that knowledge of opposition, invoked a strength from what Harry had thought of as his dark side. Harry had stopped trying to call deliberately on his dark side after the day he’d killed the troll. But his dark side had never been something separate from him. It had been something remembered from Tom Riddle. Harry didn’t know how that had happened, but taking the assumption and running with it, whatever echoes of cognitive skill were in his dark side should be there for him to use. Not as a separate mode, as Harry had conceptualized at first, but just as neural patterns with a strong tendency to chain into one another since they had once formed part of a connected whole.

This unfortunately did not change that Professor Quirrell had the same skills with far more life experience backing them up, and also had the gun.

Harry turned, and set foot on the giant plant, and began to walk down the spiral staircase provided by the leaves. It had taken Harry too long this time, but he’d recovered himself to some degree, despite the grief still weighing him down like thick water. It wasn’t a cold steel rod in his spine, but it was something straight and solid nonetheless. He was going to play this through, see Hermione returned to life first, and then, somehow, stop Professor Quirrell. Or stop Professor Quirrell first and then get the Stone himself. There had to be something, some possibility, some opportunity that would present itself, some way to stop Voldemort \emph{and} return Hermione to life…

Harry continued his descent.

Behind him, the three-headed dog waited, guarding the gate.

%  LocalWords:  fter Amon
