\partchapter{Roles}{II}

\lettrine{S}{hortly} after, there was another knock upon the storeroom door.

“If you actually care about my mental health,” the boy said without looking up, “you will go away, leave me alone, and wait for me to come down to dinner. This isn’t helping.”

The door opened, and the one who had waited outside stepped in.

“Seriously?” the boy said flatly.

The door closed and clicked behind Severus Snape.

The Potions Master of Hogwarts wore none of his customary arrogance, or even the dispassionate guise that he ordinarily took in the Headmaster’s office; his gaze was strange, as he looked down upon the boy guarding that door; his thoughts unfathomable.

“I also cannot imagine what the Deputy Headmistress is thinking,” said the Potions Master of Hogwarts. “Unless I am meant to serve as a warning of where it will lead you, if you decide to take the blame for her death upon yourself.”

The boy’s lips pressed together. “Fine. Let’s just skip ahead to the end of this conversation. You win, Professor Snape. I concede that you were more responsible for Lily Potter’s death than I was responsible for Hermione Granger’s death, and that my guilt can’t stack up to your guilt. And then I ask you to go, and you tell them that it would probably be best to let me alone for a while. Are we done?”

“Almost,” the Potions Master said. “I am the one who put the notes under Miss Granger’s pillow, telling her where to find the fights in which she intervened.”

The boy did not react to this at all. Finally he spoke. “Because you dislike bullying.”

“Not that alone.” There was a note of pain in the Potions Master’s voice that sounded alien to it; it was hard to imagine it being the same acid voice that instructed children not to stir one more time or they’d blow off their wrists. “I should have realized it... very much earlier, I suppose, and yet I did not see it at all, being entirely absorbed in myself. For me to be placed as Head of Slytherin... it means that Albus Dumbledore has entirely lost hope that Slytherin House can be helped. I am certain that Dumbledore must have tried, I cannot imagine that he did not try, when he first took trust of Hogwarts. It must have been a severe blow to him, when after that so much of Slytherin answered to the Dark Lord’s call... he would not have placed me in authority over that House, acting as I did, unless he had lost all hope.” The Potions Master’s shoulders fell, beneath his spotted and stained cloak. “But you and Miss Granger were trying to do something, and the two of you had even managed to bring over Mr.~Malfoy and Miss Greengrass, and perhaps those two could have set a different example... I suppose it was foolish for me to believe. The Headmaster does not know of what I have done, and I ask you not to tell him.”

“Why are you telling me this?”

“Matters have become far too serious not to tell someone.” Severus Snape’s lips twisted. “I have seen enough disastrous plotting, in my tenure as Head of Slytherin, to know how that sometimes goes. If, in the future, all should come to light—then at least I have told you, and you may say as much.”

“Lovely,” the boy said. “Thank you for clearing that up. Is that all?”

“Do you intend to declare that your life is now a ruin and that there is nothing left for you but vengeance?”

“No. I still have—” The boy cut himself off.

“Then there is very little advice that I can give you,” said Severus Snape.

The boy nodded distantly. “On Hermione’s behalf, thank you for helping her with the bullies. She would tell you that it was the right thing to do. And now I would be much obliged if you could tell them to \emph{leave me alone}.”

The Potions Master turned to the door, and when his face was unseen, his voice came in a whisper. “I truly am sorry for your loss.”

Severus Snape departed.

The boy stared after him, trying to remember, as best as he could at this distance, words which had been spoken some time earlier.

\emph{Your books betrayed you, Potter. They did not tell you the one thing you needed to know. You cannot learn from books what it is like to lose the one you love. That is something you could never know without experiencing it for yourself.}

It had gone something like that, the boy thought, if he was remembering correctly.
\sbreak

Hours had passed now, in the infirmary section with its closed door and a body lying in state behind it.

Harry went on staring at his wand, as it lay in his lap. At the tiny scratches and smudges on the eleven inches of holly, flaws he’d never looked closely enough to notice before. A quick mental calculation said there was no reason to worry since if this was six or seven months’ accumulation of damage, then a standard lifetime wouldn’t wear away the wand entirely. At the time, he probably would’ve worried about his own Time-Turner being taken away if he’d just openly yelled out ‘Does anyone have a Time-Turner?’ into the Great Hall, but it would have been easy enough to precommit to, after lunch, finding someone to send Professor Flitwick a message two hours earlier and then Professor Flitwick could’ve just gone straight to Hermione, or sent her his raven Patronus, long before the troll was anywhere near her. Or might that alternate Harry have already learned it was too late—heard about Hermione’s death after lunch and before he could buy any messages sent backwards in time? Maybe a basic guideline of working with time-travel was to make sure you never risked learning you were too late, if you hadn’t yet gone backwards. There was a tiny chemical burn now on the end of his wand, presumably from contacting the acid he’d partially Transfigured the troll’s brain into, but the wand seemed robust against losses of small amounts of wood. Really the concept of a ‘magic wand’ being required just got stranger the more you thought about it. Though if spells were always being invented in some mysterious way, new rituals being carved as new levers upon the unknown machine, it might just be that people just kept inventing rituals that involved wands, just like they invented phrases like ‘Wingardium Leviosa’. It really seemed like magic ought to be, in some sense, almost arbitrarily powerful, and it certainly would be convenient if Harry could just bypass whatever conceptual limitation prevented people from inventing spells like ‘Just Fix Everything Forever’, but somehow nothing was ever that easy where magic was concerned. Harry looked at his mechanical watch again, but it still wasn’t time.

He’d attempted to cast the Patronus Charm, meaning to tell his Patronus to go to Hermione Granger. Just in case it was all a lie, a False Memory Charm or one of the who-knew-how-many-ways that wizards could be made to close their eyes and dream. Just in case the real Hermione was alive and being held somewhere, despite his feeling her life as it left her. Just in case there was an afterlife and the True Patronus could reach it.

The spell hadn’t worked though, so that particular test had failed to provide any evidence, leaving him with the previous, unfavorable prior.

Time passed, and yet more time. From the outside you would’ve just seen a boy, sitting, staring at his wand with an abstracted gaze, looking at his watch every two minutes or so.

The door to the infirmary section opened once \emph{again}.

The boy sitting there looked up with a deadly, chilling glare.

Then the boy’s face cracked in dismay, and he scrambled to his feet.

“Harry,” said the man in the button-down formal shirt and a black vest thrown over it. His voice was hoarse. “Harry, what’s happening? The Headmaster of your school—he showed up in those ridiculous robes at my office and told me that Hermione Granger was dead!”

A moment later a woman followed the man into the room; she seemed less confused than the man, less bewildered and more frightened.

“Dad,” the boy said thinly. “Mum. Yes, she’s dead. They didn’t tell you anything else?”

“No! Harry, what’s happening?”

There was a pause.

The boy slumped back against the wall. “I c-can’t, I can’t, I can’t do this.”

“What?”

“I can’t pretend to be a little boy, I j-just don’t have the energy right now.”

“Harry,” the woman said falteringly. “Harry—”

“Dad, you know those fantasy books where the hero has to hide everything from his parents because they, they wouldn’t understand, they’d react stupidly and get in the hero’s way? It’s a plot device, right, so that the hero has to solve everything himself instead of telling his parents. P-please don’t be that plot device, Dad, or you either, Mum. Just... just don’t play that role. Don’t be the parents who won’t understand. D-don’t yell at me and give me parental demands I can’t follow. Because I’ve wandered into a bloody stupid fantasy novel and now Hermione’s—I j-just don’t have the energy to deal with it.”

Slowly, as though his limbs were only half-animated, the man in the black vest kneeled down to where Harry was standing, so that his eyes were level with his son’s. “Harry,” the man said. “I need you to tell me everything that has happened, right now.”

The boy took a deep breath, swallowed. “They t-tell me the Dark Lord I defeated may still be alive. Like that’s not the p-plot of a hundred sodding books, right? So, it could also be that the Headmaster of my school, who’s the most powerful wizard in the world, has gone insane. And, and Hermione was framed for an attempted murder just before this, not that anyone would’ve told her parents about it or anything. The student she was framed for attempted-murdering was the son of Lucius Malfoy, who’s the most powerful politician in magical Britain, and used to be the Dark Lord’s number two. The Defense Professor position at this school has a curse on it, nobody ever lasts more than a year, they have a saying that the Defense Professor is always a suspect. This year the Defense Professor is secretly a mysterious wizard who opposed the Dark Lord during the last war and may or may not be evil himself. Also the Potions Master has been pining after Lily Potter for years and might be behind this whole thing for some twisted psychological reason.” The boy’s lips pressed together bitterly. “I think that’s most of the bloody stupid plot.”

The man, who had listened to all this quietly, stood up. He put a gentle hand on the boy’s shoulder. “That’s enough, Harry,” he said. “I’ve heard enough. We’re leaving this school right now and taking you with us.”

The woman was looking at the boy, her face asking a question.

The boy gazed back at her and nodded.

The woman’s voice was thin when she spoke. “\emph{They} won’t let us, Michael.”

“They have no legal right to stop us—”

“\emph{Right?} You’re \emph{Muggles,}” said the boy. He smiled twistedly. “You have as much standing in the magical British legal system as mice. No wizard is going to care about any arguments you make about \emph{rights,} about \emph{fairness}, they won’t even take the time to listen. You don’t have any \emph{power,} see, so they don’t have to bother. No, Mum, I’m not smiling like this because I agree with their Muggle policies, I’m smiling because I disagree with your children policies.”

“Then,” Professor Michael Verres-Evans said firmly, “we shall see what the \emph{real} government has to say about that. I know an MP or three—”

“They’ll say, you’re crazy, have a nice stay in this asylum. That’s assuming the Ministry Obliviators don’t get to you first and erase your memories. They do that to Muggles a lot, I hear. I figure the real higher-ups in our government have formed some cozy accomodations of their own. Maybe they get a few healing Charms now and then, if someone important manages to get cancer.” The boy gave that twisted smile again. “And that’s the situation, Dad, as Mum already knows. They’d never have brought you here or told you anything, if there was a single thing you could do about it.”

The man’s mouth opened but no words came out, as though he had been reading from a script which described what a concerned parent ought to do in this sort of situation, and this script had suddenly arrived at a blank spot.

“Harry,” the woman said falteringly.

The boy looked at her.

“Harry, did something happen to you? You seem... different...”

“Petunia!” the man said, his tongue apparently working once more. “Don’t say such things! He’s under stress, that’s all.”

“Well, Mum, you see—” The boy’s voice cracked. “Are you sure you want this all at once, Mum?”

The woman nodded, though she didn’t speak.

“I’ve got... you know how that school psychiatrist thought I had anger management problems? Well—” The boy stopped, and swallowed. “I don’t know how to explain this to you, Mum. It’s something magical instead. Probably something to do with whatever happened on the night my parents died. I have... well, I was calling it a mysterious dark side and I know it sounds like a joke and I \emph{did} check with... with an ancient telepathic magical hat to make sure my scar wasn’t \emph{actually} inhabited by the Dark Lord’s spirit and it said that there was only one person under its brim and I don’t think wizards have actual souls anyway since they can still suffer from brain damage, only—”

“Harry, slow down!” said the man.

“—only, only whatever it is, it’s still \emph{real,} there’s something inside me, it gave me willpower when things were bad, I could face down anything so long as I was angry, Snape, Dumbledore, the entire Wizengamot, my dark side wasn’t afraid of anything but Dementors. And I wasn’t stupid, I knew that there might be a price for using my dark side and I kept on looking to see what the price might be. It didn’t change my magic, it didn’t seem to cause permanent alignment shift, it didn’t try to take me away from my friends or anything like that, so I kept on using it whenever I had to and I only figured out too late what the price really was—” The boy’s voice had become almost a whisper. “I only figured out today... every time I call on it... it uses up my childhood. I killed the thing that got Hermione. And it wasn’t my dark side that did it, it was me. Oh, Mum, Dad, I’m sorry.”

There was a long silence filled with the sound of broken masks.

“Harry,” the man said, kneeling down again, “I need you to start over from the beginning and explain that much more slowly.”

The boy spoke.

The parents listened.

Some time later, the father stood up.

The boy looked up at him, grimacing in bitter anticipation.

“Harry,” the man said, “Petunia and I are going to get you out of here as quickly as possible—”

“Don’t,” the boy said warningly. “I mean it, Dad. The Ministry of Magic isn’t something you can stand up to. Pretend they’re the tax office or the dean or something else that won’t brook any challenge to their dominance. In magical Britain you’re only allowed to remember what the government thinks you should remember, and remembering the existence of magic or that you have a son named Harry is a privilege, not a right. And if they did that I’d crack and turn the Ministry into a giant flaming crater. Mum, you know the score, you absolutely have to stop Dad from trying anything stupid.”

“And son—” The man rubbed at his temples. “Maybe I shouldn’t say this now... but are you sure that what you’re talking about is really a magical dark side, and not something normal for a boy your age?”

“Normal,” the boy said with elaborate patience. “Normal how, exactly? I could check again, but I’m reasonably sure there wasn’t anything about this in \emph{Childcraft: A Guide For Parents.} My dark side isn’t just an emotional state, it \emph{makes me smarter.} In some ways, anyhow. You can’t just \emph{pretend} yourself smarter.”

The man rubbed at his head again. “Well... there’s a certain well-known phenomenon wherein children undergo a biological process which can sometimes make them angry and dark and grim, and this process also significantly increases their intelligence and their height—”

The boy slumped back against the wall. “No, Dad, it’s not that I’m turning into a teenager. I checked with my brain and it still thinks that girls are icky. But if that’s what you want to pretend, then fine. Maybe I’m better off with you not believing me. I just—” The boy’s voice choked. “I just couldn’t stand lying about it.”

“Adolescence doesn’t necessarily work like that, Harry. It may still take a while for you to notice girls. If, in fact, you haven’t noticed one alrea-” and the man abruptly stopped.

“I didn’t like Hermione in that way,” the boy whispered. “Why does everyone keep thinking it has to be about that? It’s disrespectful to her, to think someone could only like her in that way.”

The man swallowed visibly. “Anyway, son, you keep yourself safe while we work on getting you out of here, is that understood? Don’t you go actually thinking that you’ve turned to the dark side. I know you’ve had, ah, what I used to call your Ender Wiggin moments—”

“I think we are now \emph{well} past Ender and on to Ender after the buggers kill Valentine.”

“Language!” said the woman, and then her hand flew to cover her mouth.

The boy spoke wearily. “Not that kind of bugger, Mum. They’re insectoid aliens—never mind.”

“Harry, that’s exactly what I’m saying you shouldn’t think,” Professor Verres-Evans said firmly. “You’re not to go believing that you’re turning evil. You are not to hurt anyone, place yourself in harm’s way, or mess around with any sort of black magic whatsoever, while your Mum and I work on extracting you from this situation. Is that clear, son?”

The boy closed his eyes. “That’d be wonderful advice, Dad, if only I were in a comic book.”

“\emph{Harry—}” the man began.

“Police can’t do that. Soldiers can’t do that. The most powerful wizard in the world couldn’t do that, and he tried. It’s not fair to the innocent bystanders to play at being Batman if you can’t actually protect everyone under that code. And I’ve just proven that I can’t.”

Beads of sweat were glistening on Professor Michael Verres-Evans’s forehead. “Now you listen to me. No matter what you’ve read in books, you aren’t \emph{supposed} to be protecting anyone! Or involving yourself in anything dangerous! Absolutely anything dangerous whatsoever! Just stay out of the way of \emph{everything,} every bit of craziness going on in this madhouse, while we get you out of here the first instant we possibly can!”

The boy looked searchingly at his father, then his mother. Then he looked at his wristwatch again.

“Excellent point,” said the boy.

The boy marched over to the door leading outward, and flung it open.
\sbreak

The door flew open with a crack that caused Minerva to startle where she stood, and before she had time to think, Harry Potter marched out of the room, glaring directly at her.

“You brought my parents \emph{here},” the Boy-Who-Lived said. “To \emph{Hogwarts.} Where You-Know-Who or \emph{someone} is lurking around, targeting my friends. What exactly were you thinking?”

She did not reply that she had been thinking about Harry sitting in front of the door to the storeroom containing Hermione’s body, refusing to move.

“Who else knows about this?” Harry Potter demanded. “Did anyone see them with you?”

“The Headmaster brought them here—”

“I want them out of here \emph{immediately} before anyone else notices, especially You-Know-Who, but also including Professor Quirrell or Professor Snape. Please send your Patronus to the Headmaster and tell him that he needs to bring it back at once. Do not mention my parents by name, or as people, in case somebody else is listening.”

“Indeed,” said Professor Verres-Evans, nodding sternly along with this from where he stood directly behind the boy, Petunia a step behind him. His hand rested firmly on Harry’s shoulder. “We’ll finish talking to our son at home.”

“A moment, please,” Minerva said in reflexive politeness. Her first try at casting the Patronus failed, a disadvantage of that Charm under certain circumstances. It wasn’t the first time she’d done it so, but she seemed to have lost some of the knack—

Minerva shut the thought down and concentrated.

When the message was sent, she turned back to Professor Verres-Evans. “Sir,” she said, “I’m afraid that Mr.~Potter must not leave the Hogwarts School—”

By the time Albus finally arrived, there was shouting, the Muggle man having given up on dignity. At least there was shouting on one side of the argument. Minerva’s heart wasn’t in it. The truth was that she couldn’t believe the words coming out of her mouth.

When the Professor turned to argue with the Headmaster, Harry Potter, who had remained silent through this, spoke up. “Not here,” said Harry. “You can argue with him anywhere but Hogwarts, Dad. Mum, please, please make sure that Dad doesn’t try anything that will get him in trouble with the Ministry.”

Michael Verres-Evans’s face screwed up. He turned, looked at Harry Potter. When his voice came out it was hoarse, accompanied by water in his eyes. “Son—what are you doing?”

“You know perfectly well what I’m doing,” Harry Potter said. “You read those comic books long before you gave them to me. I’ve been through a bunch of crap, matured a bit, and now I’m protecting my relatives. Actually, it’s simpler than that, you know what I’m doing because you tried to do the same thing. I’m having my loved ones taken out of Hogwarts immediately, that’s what I’m doing. Headmaster, please get them out of here before You-Know-Who discovers their presence and marks them for death.”

Michael Verres-Evans began a frantic dash toward Harry, and then all motion stopped with the Muggle man leaning forward in his flight.

“I am sorry,” the Headmaster said quietly. “We shall speak more soon. Minerva, I was with the others when you called, they are waiting in your office.”

The Headmaster passed forwards like he was gliding, until he stood in the midst of where the man and woman stood frozen; and there was another flash of flame.

Motion resumed.

Minerva looked at Harry.

Words did not come to her.

“Clever move, bringing them here,” Harry Potter said. “Probably damaged our relationship permanently. All I wanted was to be bloody left alone until bloody dinnertime. Which,” the boy looked at his wristwatch, “it now is \emph{anyway}. I’m going to go say goodbye to Hermione by myself, which I promise will take less than two minutes, and then after that I’ll come out and go eat something like I would have done regardless. Do \emph{not} disturb me for those two bloody minutes or I will snap and try to kill someone, I mean it, Professor.”

The boy turned and strode into the small room, opened the rear door to where Hermione Granger’s body was being kept, and strode inside before she could think to speak. Through the doorway she saw a flash of a sight she knew no child ought to see—

The door slammed shut.

She started forwards, unthinking.

Halfway to the door, she stopped herself.

Her mind was still slow, and hurting, and the part of her that Harry Potter would have called \emph{the picture of a stern disciplinarian} was lifelessly mouthing words about inappropriate behavior from children. The rest of her didn’t think it was a good idea to leave any child, even Harry Potter, alone in a room with the bloody corpse of his best friend. But the act of opening the door, or asserting any sort of authority, did not seem to her wise. There was no right thing to do, and no right thing to say; or if there was any right path, she did not know it.

Very slowly, a minute and a half passed.
\sbreak

When the door opened again, Harry seemed to have changed, as though that minute and a half had passed over the course of lifetimes.

“Seal up the room,” Harry said quietly, “and let’s go, Professor McGonagall.”

She walked over to the storeroom door. She wasn’t quite able to stop herself from looking in, and saw the dried blood, the sheet covering the lower half, the upper body waxy and doll-like, and a glimpse of Hermione Granger’s closed eyes. Something inside her began its weeping all over again.

She closed the door.

Her fingers moved upon her wand, her mouth spoke words without thought, Charms and wards to seal the room against entry.

“Professor McGonagall,” Harry said in a strange voice, as if by rote, “do you have the rock? The rock that the Headmaster gave me? I should Transfigure it into a jewel again, since it did prove useful.”

Automatically her eyes went to the ring on Harry’s left pinky finger, noting the emptiness of the setting where the jewel should have been. “I shall mention it to the Headmaster,” her tongue replied.

“Is that a usual tactic, by the way?” Harry said, voice still odd. “Carrying something large Transfigured into something small to use as a weapon? Or is that a usual exercise for Transfiguration practice?”

Distantly, she shook her head.

“Well, let’s go, then.”

“I have—” her voice stopped. “I’m afraid I have something else which I must do, now. Will you be all right on your own, and will you promise to go to the Great Hall directly and eat something, Mr.~Potter?”

The boy promised (barring exceptional and unforeseen circumstances, a clause with which she did not argue) and then walked out of the room.

What lay ahead of her... would be no easier, certainly, and might well be harder.
\sbreak

Minerva walked to her office at a swift pace; not slowly, for that would have been a discourtesy.

Professor McGonagall opened the door to her office.

“Madam Granger,” her voice said, “Mr.~Granger, I am so terribly sorry for—”
