\chapter{Rationalization}

\lettrine{H}{ermione} Granger had worried she was turning Bad.

\quad\quad The difference between Good and Bad was usually easy to grasp, she’d never understood why other people had so much trouble. At Hogwarts, “Good” was Professor Flitwick and Professor McGonagall and Professor Sprout. “Bad” was Professor Snape and Professor Quirrell and Draco Malfoy. Harry Potter...\ was one of those unusual cases where you \emph{couldn’t} tell just by looking. She was still trying to figure out where he belonged.

But when it came to \emph{herself}...

Hermione was having \emph{too much fun} crushing Harry Potter.

She’d done better than him in every single class they’d taken. (Except for broomstick riding which was like gym class, it didn’t count.) She’d gotten \emph{real} House points almost every day of their first week, not for weird heroic things, but \emph{smart} things like learning spells quickly and helping other students. She knew those kinds of House points were better, and the best part was, Harry Potter knew it too. She could see it in his eyes every time she won another \emph{real} House point.

If you were Good, you weren’t supposed to enjoy winning this much.

It had started on the day of the train ride, though it had taken a while for the whirlwind to sink in. It wasn’t until later that night that Hermione had begun to realize just \emph{how much} she’d let that boy walk all over her.

Before she’d met Harry Potter she hadn’t had anyone she’d wanted to crush. If someone wasn’t doing as well as her in class, it was her job to help them, not rub it in. That was what it meant to be Good.

And now...

...now she was \emph{winning}, Harry Potter was flinching every time she got another House point, and it was \emph{so much} fun, her parents had warned her against drugs and she suspected this was \emph{more fun} than that.

She’d always liked the smiles that teachers gave her when she did something right. She’d always liked seeing the long row of check-marks on a perfectly answered test. But now when she did well in class she would casually glance around and catch a glimpse of Harry Potter gritting his teeth, and it made her want to burst into song like a Disney movie.

That was Bad, wasn’t it?

Hermione had worried she was turning Bad.

And then a thought had come to her which wiped away all her fears.

She and Harry were getting into a Romance! Of course! Everyone knew what it meant when a boy and a girl started fighting all the time. They were \emph{courting} one another! There was nothing Bad about \emph{that.}

It couldn’t be that she just \emph{enjoyed} beating the living scholastic daylights out of the most famous student in the school, someone who was \emph{in} books and \emph{talked} like books, the boy who had somehow vanquished the Dark Lord and even smushed \emph{Professor Snape} like a sad little bug, the boy who was, as Professor Quirrell would have put it, dominant, over everyone else in first-year Ravenclaw \emph{except} for Hermione Granger who was utterly \emph{squishing} the Boy-Who-Lived in all his classes besides broomstick riding.

Because that would have been Bad.

No. It was Romance. \emph{That} was it. \emph{That} was why they were fighting.

Hermione was glad she had figured this out in time for today, when Harry would lose their book-reading contest, which the \emph{whole school} knew about, and she wanted to start \emph{dancing} with the sheer overflowing joy of it.

It was 2:45\PM on Saturday and Harry Potter had half of Bathilda Bagshot’s \emph{A History of Magic} left to read and she was staring at her pocket watch as it ticked with dreadful slowness toward 2:47\PM.

And the entire Ravenclaw common room was watching.

It wasn’t just the first-years, news had spread like spilled milk and fully half of Ravenclaw was crowded into the room, squeezed into sofas and leaning on bookcases and sitting on the arms of chairs. All six prefects were there including the Head Girl of Hogwarts. Someone had needed to cast an Air-Freshening Charm just so that there would be enough oxygen. And the din of conversation had died into whispers which had now faded into utter silence.

2:46\PM.

The tension was unbearable. If it had been anyone else, \emph{anyone} else, his defeat would have been a foregone conclusion.

But this was Harry Potter, and you couldn’t rule out the possibility that he would, sometime in the next few seconds, raise a hand and snap his fingers.

With sudden terror she realized how Harry Potter might be able to do exactly that. It would be \emph{just like him} to have \emph{already finished reading} the second half of the book earlier...

Hermione’s vision began to swim. She tried to make herself breathe, and found that she simply couldn’t.

Ten seconds left, and he still hadn’t raised his hand.

Five seconds left.

2:47\PM.

Harry Potter carefully placed a bookmark into his book, closed it, and laid it aside.

“I would like to note for the benefit of posterity,” said the Boy-Who-Lived in a clear voice, “that I had only half a book left, and that I ran into a number of unexpected delays—”

“\emph{You lost!}” shrieked Hermione. “You \emph{did!} You \emph{lost our contest!}”

There was a collective exhalation as everyone started breathing again.

Harry Potter shot her a Look of Flaming Fire, but she was floating in a halo of pure white happiness and nothing could touch her.

“\emph{Do you realize what kind of week I’ve had?}” said Harry Potter. “Any lesser being would have been hard-pressed to read eight Dr.~Seuss books!”

“\emph{You} set the time limit.”

Harry’s Look of Flaming Fire grew even hotter. “I did not have any logical way of knowing I’d have to save the entire school from Professor Snape, or get beaten up in Defense class, and if I told you how I lost all the time between 5\PM and dinner on Thursday you would think I was insane—”

“Awww, it sounds like \emph{someone} fell prey to the \emph{planning fallacy.}”

Raw shock showed on Harry Potter’s face.

“Oh that reminds me, I finished reading the first batch of books you lent me,” Hermione said with her best innocent look. A couple of them had been \emph{hard} books, too. She wondered how long it had taken \emph{him} to finish reading them.

“Someday,” said the Boy-Who-Lived, “when the distant descendants of \emph{Homo sapiens} are looking back over the history of the galaxy and wondering how it all went so wrong, they will conclude that the original mistake was when someone taught Hermione Granger how to read.”

“But you still lose,” said Hermione. She held a hand to her chin and looked contemplative. “Now what exactly should you lose, I wonder?”

“\emph{What?}”

“You lost the bet,” Hermione explained, “so you have to pay a forfeit.”

“I don’t remember agreeing to this!”

“Really?” said Hermione Granger. She put a thoughtful look on her face. Then, as if the idea had only just then occurred to her, “We’ll take a vote, then. Everyone in Ravenclaw who thinks Harry Potter has to pay up, raise your hand!”

“\emph{What?}” shrieked Harry Potter again.

He spun around and saw that he was surrounded by a sea of raised hands.

And if Harry Potter had looked \emph{more carefully}, he would have noticed that an awful lot of the onlookers seemed to be girls and that practically every female in the room had their hand raised.

“Stop!” wailed Harry Potter. “You don’t know what she’s going to ask! Don’t you \emph{realize} what she’s doing? She’s getting you to make an advance commitment now, and then the pressure of consistency will make you agree with whatever she says afterward!”

“Don’t worry,” said the prefect Penelope Clearwater. “If she asks for something unreasonable, we can just change our minds. Right, everyone?”

And there were eager nods from all the girls whom Penelope Clearwater had told about Hermione’s plan.
\sbreak
A silent figure quietly slipped through the chilled halls of the Hogwarts dungeons. He was to be present in a certain room at 6:00\PM to meet a certain someone, and if at all possible it was best to be early, to show respect.

But when his hand turned the doorknob and opened the door into that dark, silent, unused classroom, there was a silhouette already standing there amid the rows of dusty old desks. A silhouette which held a small green glowing rod, casting a pale light which hardly illuminated even he who held it, let alone the surrounding room.

The light of the hallway died as the door closed and shut behind him, and Draco’s eyes began the process of adjusting to the dim glow.

The silhouette slowly turned to behold him, revealing a shadowed face only partially lit by the eerie green light.

Draco liked this meeting already. Keep the chill green light, make them both taller, give them hoods and masks, move them from a classroom to a graveyard, and it would be just like the start of half the stories his father’s friends told about the Death Eaters.

“I want you to know, Draco Malfoy,” said the silhouette in tones of deadly calm, “that I do not blame you for my recent defeat.”

Draco opened his mouth in unthinking protest, there was no possible reason why he \emph{should} be blamed—

“It was due, more than anything else, to my own stupidity,” continued that shadowy figure. “There were many other things I could have done, at any step along the way. You did not ask me to do \emph{exactly} what I did. You only asked for help. I was the one who unwisely chose that particular method. But the fact remains that I lost the contest by half a book. The actions of your pet idiot, and the favor you asked for, and, yes, my own foolishness in going about it, caused me to \emph{lose time}. More time than you know. Time which, in the end, proved critical. The fact remains, Draco Malfoy, that if you had not asked that favor, I \emph{would} have won. And not...\ instead... \emph{lost}.”

Draco had already heard about Harry’s loss, and the forfeit Granger had claimed from him. The news had spread faster than owls could have carried it.

“I understand,” Draco said. “I’m sorry.” There was nothing else he \emph{could} say if he wanted Harry Potter to be friends with him.

“I am not asking for understanding or sorrow,” said the dark silhouette, still with that deadly calm. “But I have just spent two full hours in the presence of Hermione Granger, dressed in such clothing as was provided me, visiting such fascinating places in Hogwarts as a tiny burbling waterfall of what looked to me like snot, accompanied by a number of other girls who insisted on such helpful activities as strewing our path with Transfigured rose petals. I have been on a date, scion of Malfoy. My \emph{first} date. \emph{And when I call that favor due, you will pay it.}”

Draco nodded solemnly. Before arriving he had taken the wise precaution of learning every available detail of Harry’s date, so that he could get all of his hysterical laughing done before their appointed meeting time, and would not commit a \emph{faux pas} by giggling continuously until he lost consciousness.

“Do you think,” Draco said, “that something sad ought to happen to the Granger girl—”

“Spread the word in Slytherin that the Granger girl is \emph{mine} and anyone who meddles in \emph{my} affairs will have their remains scattered over an area wide enough to include twelve different spoken languages. And since I am not in Gryffindor and I use \emph{cunning} rather than immediate frontal attacks, they should not panic if I am seen smiling at her.”

“Or if you’re seen on a second date?” Draco said, allowing just a tiny note of skepticism into his voice.

“\emph{There will be no second date,}” said the green-lit silhouette in a voice so fearsome that it sounded, not only like a Death Eater, but like Amycus Carrow that one time just before Father told him to stop it, he wasn’t the Dark Lord.

Of course it \emph{was} still a young boy’s high unbroken voice and when you combined that with the \emph{actual words}, well, it just didn’t work. If Harry Potter \emph{did} become the next Dark Lord someday, Draco would use a Pensieve to store a copy of this memory somewhere safe, and Harry Potter would never dare betray him.

“But let us talk of happier matters,” said the green-shadowed figure. “Let us talk of knowledge and of power. Draco Malfoy, let us talk of Science.”

“Yes,” said Draco. “Let us speak.”

Draco wondered how much of his own face could be seen, and how much was in shadow, in that eerie green light.

And though Draco kept his face serious, there was a smile in his heart.

He was \emph{finally} having a real grownup conversation.

“I offer you power,” said the shadowy figure, “and I will tell you of that power and its price. The power comes from knowing the shape of reality and so gaining control over it. What you understand, you can command, and that is power enough to walk upon the Moon. The price of that power is that you must learn to ask questions of Nature, and far more difficult, accept Nature’s answers. You will do experiments, perform tests and see what happens. And you must accept the meaning of those results when they tell you that you are mistaken. You will have to \emph{learn how to lose}, not to me, but to Nature. When you find yourself arguing with reality, you will have to let reality win. You will find this painful, Draco Malfoy, and I do not know if you are strong in that way. Knowing the price, is it still your wish to learn the human power?”

Draco took a deep breath. He’d thought about this. And it was hard to see how he could answer any other way. He’d been instructed to take every avenue of friendship with Harry Potter. It was just \emph{learning,} he wasn’t promising to \emph{do} anything. He could always stop the lessons at any time...

There were certainly any number of things about the situation which made it look like a trap, but in all honesty, Draco didn’t see how this could go wrong.

Plus Draco did kind of want to rule the world.

“Yes,” said Draco.

“Excellent,” said the shadowy figure. “I have had something of a \emph{crowded week}, and it will take time to plan your curriculum—”

“I’ve got a lot of things I need to do myself to consolidate my power in Slytherin,” said Draco, “not to mention homework. Maybe we should just start in October?”

“Sounds sensible,” said the shadowy figure, “but what I meant to say is that to plan your curriculum, I need to know what I will be teaching you. Three thoughts come to me. The first is that I teach you of the human mind and brain. The second option is that I teach you of the physical universe, those arts which lie on the pathway to visiting the Moon. This involves a great deal of numbers, but to a certain kind of mind those numbers are more beautiful than anything else Science has to teach. Do you like numbers, Draco?”

Draco shook his head.

“Then so much for that. You will learn your mathematics eventually, but not right away, I think. The third option is that I teach you of genetics and evolution and inheritance, what you would call blood—”

“That one,” said Draco.

The figure nodded. “I thought you might say as much. But I think it will be the most painful path for you, Draco. What if your family and friends, the blood purists, say one thing, and you find that the experimental test says another?”

“Then I’ll figure out how to make the experimental test say the \emph{right} answer!”

There was a pause, as the shadowy figure stood there with its mouth open for a short while.

“Um,” said the shadowy figure. “It doesn’t really work like that. That’s what I was trying to warn you about here, Draco. You \emph{can’t} make the answer come out to be anything you like.”

“You can \emph{always} make the answer come out your way,” said Draco. That had been practically the first thing his tutors had taught him. “It’s just a matter of finding the right arguments.”

“No,” said the shadowy figure, voice rising in frustration, “no, no, no! Then you get the \emph{wrong answer} and you can’t go to the Moon that way! Nature isn’t a person, you can’t trick them into believing something else, if you try to tell the Moon it’s made of cheese you can argue for days and it won’t change the Moon! What you’re talking about is \emph{rationalization}, like starting with a sheet of paper, moving straight down to the bottom line, using ink to write ‘and \emph{therefore,} the Moon is made of cheese’, and then moving back up to write all sorts of clever arguments above. But either the Moon is made of cheese or it isn’t. The moment you wrote the bottom line, it was already true or already false. Whether or not the whole sheet of paper ends up with the right conclusion or the wrong conclusion is fixed the instant you write down the bottom line. If you’re trying to pick between two expensive trunks, and you like the shiny one, it doesn’t matter what clever arguments you come up with for buying it, the \emph{real} rule you used to \emph{choose which trunk to argue for} was ‘pick the shiny one’, and however effective that rule is at picking good trunks, that’s the kind of trunk you’ll get. Rationality \emph{can’t} be used to argue for a fixed side, its only possible use is \emph{deciding which side to argue}. Science isn’t for \emph{convincing} anyone that the blood purists are right. That’s \emph{politics!} The power of science comes from \emph{finding out the way Nature really is that can’t be changed by arguing!} What science \emph{can} do is tell us \emph{how blood really works,} how wizards really inherit their powers from their parents, and whether Muggleborns are really weaker or stronger—”

“\emph{Stronger!}” said Draco. He had been trying to follow this, a puzzled frown on his face, he could see how it \emph{sort} of made sense but it certainly wasn’t like anything he’d ever heard before. And then Harry Potter had said something Draco couldn’t possibly let pass. “You think mudbloods are \emph{stronger?}”

“I think nothing,” said the shadowy figure. “I know nothing. I believe nothing. My bottom line is not yet written. I will figure out how to test the magical strength of Muggleborns, and the magical strength of purebloods. If my tests tell me that Muggleborns are weaker, I will believe they are weaker. If my tests tell me that Muggleborns are stronger, I will believe they are stronger. Knowing this and other truths, I will gain some measure of power—”

“And you expect \emph{me} to believe whatever you say?” Draco demanded hotly.

“I expect you to perform the tests \emph{personally},” said the shadowy figure quietly. “Are you afraid of what \emph{you} will find?”

Draco stared at the shadowy figure for a while, his eyes narrowed. “Nice trap, Harry,” he said. “I’ll have to remember that one, it’s new.”

The shadowy figure shook his head. “It’s not a trap, Draco. Remember—I \emph{don’t know} what we’ll find. But you do not understand the universe by arguing with it or telling it to come back with a different answer next time. When you put on the robes of a scientist you must forget all your politics and arguments and factions and sides, silence the desperate clingings of your mind, and wish only to hear the answer of Nature.” The shadowy figure paused. “Most people can’t do it. That’s why this is difficult. Are you sure you wouldn’t rather just learn about the brain?”

“And if I tell you I’d rather learn about the brain,” Draco said, his voice now hard, “you’ll go around telling people that I was afraid of what I’d find.”

“No,” said the shadowy figure. “I will do no such thing.”

“But you might do the same sort of tests yourself, and if you got the wrong answer, I wouldn’t be there to say anything before you showed it to someone else.” Draco’s voice was still hard.

“I would still ask you first, Draco,” the shadowy figure said quietly.

Draco paused. He hadn’t been expecting that, he’d thought he saw the trap but... “You \emph{would?}”

“Of course. How would \emph{I} know who to blackmail or what we could ask from them? Draco, I say again that this is not a trap I set for you. At least not for you personally. If your politics were different, I would be saying, what if the test shows that purebloods are stronger.”

“Really.”

“\emph{Yes!} That’s the price \emph{anyone} has to pay to become a scientist!”

Draco held up a hand. He had to think.

The shadowy, green-lit figure waited.

It didn’t take long to think about, though. If you discarded all the confusing parts...\ then Harry Potter was planning to mess around with something that could cause a gigantic political explosion, and it would be insane to just walk away and let him do it on his own. “We’ll study blood,” said Draco.

“\emph{Excellent},” said the figure, and smiled. “Congratulations on being willing to ask the question.”

“Thanks,” Draco said, not quite managing to keep the irony out of his voice.

“Hey, did you think going to the Moon was \emph{easy?} Be glad this just involves changing your mind sometimes, and not a human sacrifice!”

“Human sacrifice would be \emph{way} easier!”

There was a slight pause, and then the figure nodded. “Fair point.”

“Look, Harry,” said Draco without much hope, “I thought the idea was to take all the things that Muggles know, combine them with things that wizards know, and become masters of both worlds. Wouldn’t it be a lot easier to just study all the things that Muggles \emph{already} found out, like the Moon stuff, and use \emph{that} power—”

“\emph{No,}” said the figure with a sharp shake of his head, sending green shadows moving around his nose and eyes. His voice had turned very grim. “If you cannot learn the scientist’s art of accepting reality, then I \emph{must not} tell you what that acceptance has discovered. It would be like a powerful wizard telling you of those gates which must not be opened, and those seals which must not be broken, before you had proven your intelligence and discipline by surviving the lesser perils.”

A chill went down Draco’s spine and he shuddered involuntarily. He knew it had been visible even in the dim light. “All right,” said Draco. “I understand.” Father had told him that many times. When a more powerful wizard told you that you weren’t ready to know, you didn’t pry any further if you wanted to live.

The figure inclined his head. “Indeed. But there is something else you should understand. The first scientists, being Muggles, lacked your traditions. In the beginning they simply did not comprehend the notion of dangerous knowledge, and thought that all things known should be spoken freely. When their searches turned dangerous, they told their politicians of things that should have stayed secret—don’t look like that, Draco, it wasn’t simple stupidity. They did have to be smart enough to uncover the secret in the first place. But they were Muggles, it was the first time they’d found anything \emph{really} dangerous, and they didn’t \emph{start out} with a tradition of secrecy. There was a war going on, and the scientists on one side worried that if they \emph{didn’t} talk, the scientists of the \emph{enemy} country would tell \emph{their} politicians first...” The voice trailed off significantly. “They didn’t destroy the world. But it was close. And \emph{we} are not going to repeat that mistake.”

“Right,” Draco said, his voice now very firm. “\emph{We} won’t. We’re wizards, and studying science doesn’t make us Muggles.”

“As you say,” said the green-lit silhouette. “We will establish our \emph{own} Science, a magical Science, and that Science will have smarter traditions from the very start.” The voice grew hard. “The knowledge I share with you will be taught alongside the disciplines of accepting truth, the level of this knowledge will be keyed to your progress in those disciplines, and you will share that knowledge with no one else who has not learned those disciplines. Do you accept this?”

“Yes,” said Draco. What was he supposed to do, say no?

“Good. And what you discover for yourself, you will keep to yourself unless you think that other scientists are ready to know it. What we do share among ourselves, we will not tell the world unless we agree it is safe for the world to know. And whatever our own politics and allegiances, we will \emph{all} punish \emph{any} of our number who reveal dangerous magics or give away dangerous weapons, no matter what sort of war is going on. From this day onward, that will be the tradition and the law of science among wizards. Are we agreed on that?”

“Yes,” said Draco. Actually this \emph{was} starting to sound pretty attractive. The Death Eaters had tried to take power by being scarier than everyone else, and they hadn’t actually won yet. Maybe it was time to try ruling using secrets instead. “And our group stays hidden for as long as possible, and everyone in it has to agree to our rules.”

“Of course. Definitely.”

There was a very short pause.

“We’re going to need better robes,” said the shadowy figure, “with hoods and so on—”

“I was \emph{just thinking} that,” said Draco. “We don’t need whole new robes, though, just cowled cloaks to put on. I have a friend in Slytherin, she’ll take your measurements—”

“Don’t tell her what it’s \emph{for}, though—”

“I’m not \emph{stupid!}”

“And no masks for now, not when it’s just you and I—” said the shadowy figure.

“Right! But later on we should have some sort of special mark that all our servants have, the Mark of Science, like a snake eating the Moon on their right arms—”

“It’s called a PhD and wouldn’t that make it too easy to identify our people?”

“Huh?”

“I mean, what if someone is like ‘okay, now everyone pull up their robes over their right arms’ and our guy is like ‘whoops, sorry, looks like I’m a spy’—”

\emph{“Forget I said anything,}” said Draco, sweat suddenly springing out all over his body. He needed a distraction, \emph{fast}—“And what do we call ourselves? The Science Eaters?”

“No,” said the shadowy figure slowly. “That doesn’t sound right...”

Draco wiped his robed arm across his forehead, wiping away beads of moisture. What had the Dark Lord been \emph{thinking?} Father had said the Dark Lord was \emph{smart!}

“I’ve got it!” said the shadowy figure suddenly. “You won’t understand yet, but trust me, it fits.”

Right now Draco would have accepted ‘Malfoy Munchers’ as long as it changed the subject. “What is it?”

And standing amid the dusty desks in an unused classroom in the dungeons of Hogwarts, the green-lit silhouette of Harry Potter spread his arms dramatically and said, “This day shall mark the dawn of...\ the \emph{Bayesian Conspiracy}.”
\sbreak
A silent figure trudged wearily through the halls of Hogwarts in the direction of Ravenclaw.

Harry had gone straight from the meeting with Draco to dinner, and stayed at dinner barely long enough to choke down a few fast gulps of food before going off to bed.

It wasn’t even 7\PM yet, but it was well past bedtime for Harry. He’d realized \emph{last} night that he wouldn’t be able to use the Time-Turner on Saturday until after the book-reading contest was already over. But he could still use the Time-Turner on \emph{Friday} night, and gain time that way. So Harry had pushed himself to stay awake until 9\PM on Friday, when the protective shell opened, and then used the four hours remaining on the Time-Turner to spin back to 5\PM and collapse into sleep. He’d woken up around 2\PM on Saturday morning, just as planned, and read for the next twelve hours straight...\ and it still hadn’t been enough. And now Harry would be going to sleep rather early for the next few days, until his sleep cycle caught up again.

The portrait on the door asked Harry some dumb riddle meant for eleven-year-olds that he answered without the words even passing through his conscious mind, and then Harry staggered up the stairs to his dorm room, changed into his pajamas and collapsed into bed.

And found that his pillow seemed rather lumpy.

Harry groaned. He sat up reluctantly, twisted in bed, and lifted up his pillow.

This revealed a note, two golden Galleons, and a book titled \emph{Occlumency: The Hidden Arte.}

Harry picked up the note and read:

\begin{writtenNote}
My, you do get yourself into trouble and quickly. James himself was no match for you.

You have made a powerful enemy. Snape commands the loyalty, admiration, and fear of all House Slytherin. You cannot trust any of that House now, whether they come to you in friendly guise or fearsome.

From now on you must not meet Snape’s eyes. He is a Legilimens and can read your mind if you do. I have enclosed a book which may help you learn to protect yourself, though there is only so far you can get without a tutor. Still you may hope to at least detect intrusion.

So that you may find some extra time in which to study Occlumency, I have enclosed 2 Galleons, which is the price of answer sheets and homework for the first-year History of Magic class (Professor Binns having given the same tests and same assignments every year since he died). Your newfound friends the Weasley twins should be able to sell you a copy. It goes without saying that you must not get caught with it in your possession.

Of Professor Quirrell I know little. He is a Slytherin and a Defense Professor, and that is two marks against him. Consider carefully any advice he gives you, and tell him nothing you do not wish known.

Dumbledore only pretends to be insane. He is extremely intelligent, and if you continue to step into closets and vanish, he will certainly deduce your possession of an invisibility cloak if he has not done so already. Avoid him whenever possible, hide the Cloak of Invisibility somewhere safe (\shout{not} your pouch) any time you cannot avoid him, and step with great care in his presence.

Please be more careful in the future, Harry Potter.

\letterClosing{—Santa Claus}
\end{writtenNote}

Harry stared at the note.

It \emph{did} seem to be pretty good advice. Of course Harry wasn’t going to cheat in History class even if they gave him a dead monkey for a professor. But Severus’s Legilimency...\ whoever’d sent this note knew a lot of important, secret things and was willing to tell Harry about them. The note was still warning him against Dumbledore stealing the Cloak but at this point Harry honestly had no clue if that was a bad sign, it could just be an understandable mistake.

There seemed to be some sort of intrigue going on inside Hogwarts. Maybe if Harry \emph{compared stories} between Dumbledore and the note-sender, he could work out a \emph{combined} picture that would be accurate? Like if they \emph{both} agreed on something, then...

...whatever...

Harry stuffed everything into his pouch and turned up the Quieter and pulled the cover over his head and died.
\sbreak
It was Sunday morning and Harry was eating pancakes in the Great Hall, sharp quick bites, glancing nervously at his watch every few seconds.

It was 8:02\AM, and in precisely two hours and one minute, it would be \emph{exactly one week} since he’d seen the Weasleys and crossed over onto Platform Nine and Three-Quarters.

And the thought had occurred to him... Harry didn’t know if this was a valid way to think about the universe, he didn’t know anything any more, but it \emph{seemed possible...}

That...

\emph{Not enough interesting things had happened to him over the last week.}

When he was done eating breakfast, Harry planned to go straight up to his room and hide in the bottom level of his trunk and not talk to anyone until 10:03\AM.

And that was when Harry saw the Weasley twins walking toward him. One of them was carrying something concealed behind his back.

He should scream and run away.

He should scream and run away.

Whatever this was...\ it could very well be...

...the \emph{grand finale...}

He really should just scream and run away.

With a resigned feeling that the universe would come and get him \emph{anyway}, Harry continued slicing at the pancake with his fork and knife. He couldn’t muster the energy. That was the sad truth. Harry knew now how people felt when they were tired of running, tired of trying to escape fate, and they just fell to the ground and let the horrifically befanged and tentacled demons of the darkest abyss drag them off to their unspeakable destiny.

The Weasley twins drew closer.

And yet closer.

Harry ate another bite of pancake.

The Weasley twins arrived, grinning brightly.

“Hello, Fred,” Harry said dully. One of the twins nodded. “Hello, George.” The other twin nodded.

“You sound tired,” said George.

“You should cheer up,” said Fred.

“Look what \emph{we} got you!”

And George took, from behind Fred’s back—

A cake with twelve flaming candles.

There was a pause, as the Ravenclaw table stared at them.

“That’s not right,” said someone. “Harry Potter was born on the thirty-first of Jul—”

“\prophecy{He is coming},” said a huge hollow voice that cut through all conversation like a sword of ice. “\prophecy{The one who will tear apart the very—}”

Dumbledore had leapt out of his throne and run straight over the Head Table and seized hold of the woman speaking those awful words, Fawkes had appeared in a flash, and all three of them vanished in a crack of fire.

There was a shocked pause...

...followed by heads turning in the direction of Harry Potter.

“I didn’t do it,” Harry said in a tired voice.

“That was a \emph{prophecy!}” someone at the table hissed. “And I bet it’s about \emph{you!}”

Harry sighed.

He stood up from his seat, raised his voice, and said very loudly over the conversations that were starting up, “\emph{It’s not about me! Obviously! I’m not coming here, I’m already here!}”

Harry sat back down again.

The people who had been looking at him turned away again.

Someone else at the table said, “Then who \emph{is} it about?”

And with a dull, leaden sensation, Harry realized who \emph{wasn’t} already at Hogwarts.

Call it a wild guess, but Harry had a feeling the undead Dark Lord would be showing up one of these days.

The conversation continued on around him.

“Not to mention, tear apart the very \emph{what?}”

“I thought I heard Trelawney start to say something with an ‘S’ just before the Headmaster grabbed her.”

“Like...\ soul? Sun?”

“If someone’s going to tear apart the Sun we’re \emph{really} in trouble!”

That seemed rather unlikely to Harry, unless the world contained scary things which had heard of David Criswell’s ideas about star lifting.

“So,” Harry said in tired tones, “this happens every Sunday breakfast, does it?”

“No,” said a student who might have been in his seventh year, frowning grimly. “It doesn’t.”

Harry shrugged. “Whatever. Anyone want some birthday cake?”

“But it’s \emph{not} your birthday!” said the same student who’d objected last time.

That was the cue for Fred and George to start laughing, of course.

Even Harry managed a weary smile.

As the first slice was served to him, Harry said, “I’ve had a \emph{really long week}.”
\sbreak
And Harry was sitting in the cavern level of his trunk, slid shut and locked so no one could get in, a blanket pulled over his head, waiting for the week to be over.

10:01.

10:02.

10:03, but just to be sure...

10:04 and the first week was done.

Harry breathed a sigh of relief, and gingerly pulled the blanket off of his head.

A few moments later, he had emerged into the bright sunlit air of his dorm.

Shortly after, and he was in the Ravenclaw common room. A few people looked at him, but no one said anything or tried to talk to him.

Harry found a nice wide writing desk, pulled back a comfortable chair, and sat down. From his pouch he drew a sheet of paper and a pencil.

Mum and Dad had told Harry in no uncertain terms that while they understood his enthusiasm for leaving home and getting away from his parents, he was to write them \emph{every week without fail}, just so that they knew he was alive, unharmed, and not in prison.

Harry stared down at the blank sheet of paper. \emph{Let’s see...}

After leaving his parents at the train station, he’d...

...gotten acquainted with a boy raised by Darth Vader, become friends with the three most infamous pranksters in Hogwarts, met Hermione, then there’d been the Incident with the Sorting Hat... Monday he’d been given a time machine to treat his sleep disorder, gotten a legendary invisibility cloak from an unknown benefactor, rescued seven Hufflepuffs by staring down five scary older boys one of whom had threatened to break his finger, realized that he possessed a mysterious dark side, learned to cast \emph{Frigideiro} in Charms class, and gotten started on his rivalry with Hermione... Tuesday had introduced Astronomy taught by Professor Aurora Sinistra who was nice, and History of Magic taught by a ghost who ought to be exorcised and replaced with a tape recorder... Wednesday, he’d been pronounced the Most Dangerous Student in the Classroom... Thursday, let’s not even think about Thursday... Friday, the Incident in Potions Class, followed by his blackmailing the Headmaster, followed by the Defense Professor having him beaten up in class, followed by the Defense Professor turning out to be the most awesome human being who still walked the face of the Earth... Saturday he’d lost a bet and gone on his first date and started redeeming Draco...\ and then this morning Professor Trelawney’s unheard prophecy might or might not indicate that an immortal Dark Lord was about to attack Hogwarts.

Harry mentally organized his material, and started writing.

\begin{writtenNote}
\letterAddress{Dear Mum and Dad:}

Hogwarts is lots of fun. I learned how to violate the Second Law of Thermodynamics in Charms class, and I met a girl named Hermione Granger who reads faster than I do.

I’d better leave it at that.

\letterClosing[Your loving son]{Harry James Potter-Evans-Verres.}
\end{writtenNote}


