\chapter{Hedonic Awareness}

\subsection{Thursday, April 16th, 1992.}

The school was almost deserted now, nine-tenths of the students having gone home for the Easter holiday, just about everyone she knew missing. Susan had stayed behind, her grand-aunt being quite busy, as had Ron for reasons she didn’t know—maybe the Weasley family was poor enough that feeding all the children for an extra week would’ve been a noticeable strain? It all worked out well enough, since Ron and Susan were just about the only ones left who’d still talk to her. (At least that she wanted to talk back \emph{to.} Lavender was still nice to her, and Tracey was, um, Tracey, but neither of them were quite \emph{relaxing} to spend a free hour around; and in any case, neither of those two had stayed over for the Easter hols.)

If she couldn’t go \emph{home}—and she wasn’t allowed to go home, her parents had been lied-to and told she’d had Glowpox—then an almost-empty Hogwarts was the next best thing.

She could even visit the library without people staring at her, since there were no lessons and nobody was trying to do schoolwork.

It would be a mistake to think that Hermione drooped about the corridors weeping all day long. Oh, she’d cried a lot the first two days, of course, but two days had been enough. There were parts of Harry’s borrowed books about that, how even people who were paralyzed in car accidents weren’t nearly as unhappy as they’d expected to be, six months later, just like lottery winners weren’t nearly as happy as they’d expected. People adjusted, their happiness levels went back to their happiness set point, life went on.

A shadow fell over where Hermione was reading her current book and she whirled around, the wand hidden on her lap coming up to point directly at the surprised face of—

“Sorry!” Harry Potter said, hastily holding up his palms to show his left hand empty, and his right hand holding a small red-velvet pouch. “Sorry. Didn’t mean to startle you.”

There was an awful silence, her heartbeat increasing and her palms starting to sweat as Harry Potter just looked at her. She’d \emph{almost} talked to him, on the first morning of the rest of her life; but when she’d come down to breakfast Harry Potter had looked so \emph{awful}—so she hadn’t sat down beside him at the breakfast-table, just quietly eaten in her own little bubble of nobody else sitting next to her, and it had been horrible, but Harry hadn’t come to her, and... she just hadn’t talked to him, since then. (It wasn’t hard to avoid everyone, if you stayed out of the Ravenclaw common room, and ran out of classes before anyone could talk to you.)

And ever since she’d been wondering what Harry thought of her now—if he hated her for having lost all his money—or if he really \emph{was} in love with her and that’s why he’d done it— or if he’d given up on her keeping pace with him because \emph{she} couldn’t \emph{frighten Dementors}—she couldn’t face him now, she just couldn’t, she spent sleepless nights worrying what Harry thought of her now, and she was afraid, and she’d been avoiding the boy who’d spent all his money to save her, and she was a horrible ungrateful wretch, and a terrible person and—

Then her eyes glanced down to see that Harry was reaching into the red-velvet pouch and taking out a heart-shaped red-foil-wrapped sweet, and her brain melted down like chocolate left out in the sun.

“I was going to give you more space,” said Harry Potter, “only I was reading up on Critch’s theories about hedonics and how to train your inner pigeon and how small immediate positive and negative feedbacks secretly control most of what we actually do, and it occurred to me that you might be avoiding me because seeing me made you think of things that felt like negative associations, and I really \emph{didn’t} want to let that run any longer without doing something about it, so I got ahold of a bag of chocolates from the Weasley twins and I’m just going to give you one every time you see me as a positive reinforcement if that’s all right with you—”

“\emph{Breathe}, Harry,” Hermione said without thinking about it.

It was the first word she’d spoken to him since the day of the trial.

The two of them stared at each other.

The books stared at them from the surrounding shelves.

They stared some more at each other.

“You’re supposed to eat the chocolate,” Harry said, holding out the heart-shaped sweet like a Valentine. “Unless just being given a chocolate feels good enough to count as a positive reinforcement, in which case you probably need to put it in your pocket or something.”

She knew that if she tried speaking again she’d fail, so she didn’t try.

Harry’s head slumped a bit. “\emph{Do} you hate me now?”

“\emph{No!}” she said. “No, you shouldn’t think that, Harry! Just—just—just \emph{everything!}” She realized that her wand was still pointed at Harry, and she lowered it. She was trying very hard not to burst out into tears. “\emph{Everything!}” she repeated, and couldn’t find any better to say than that, although she was certain that Harry wanted to tell her to be specific.

“I think I understand,” Harry said cautiously. “What’re you reading?”

Before she could stop him, them, Harry bent over the library-desk to see the book she was reading, leaning his head forward before she could think to grab the book away—

Harry stared at the open page.

“The World’s Wealthiest Wizards and How They Got That Way,” Harry read off the book’s title from the top. “Number sixty-five, Sir Gareth, owner of a transportation company that won the 19th-century shipping wars... monopoly on oh-tee-threes... I see.”

“I s’pose you’re going to tell me that I don’t need to worry about anything and you’ll take care of it all?” It came out sounding harsher than she would’ve wanted, and she felt another stab of guilt for being such a terrible person.

“Nah,” Harry said, sounding oddly cheerful. “I can put myself in your shoes well enough to know that if \emph{you} paid a bunch of money to save \emph{me, I’d} be trying to pay it back. I’d know it was silly on some level, and I’d \emph{still} be trying to pay it back all by myself. There’s no way I wouldn’t understand \emph{that}, Hermione.”

Hermione’s face screwed up and she felt moisture in the corners of her eyes.

“Fair warning, though,” Harry went on, “I might solve the debt to Lucius Malfoy myself if I see a way before you do, it’s more important to get that sorted immediately than \emph{which} one of us gets it sorted. Anything interesting so far?”

Three-quarters of her was running in circles and smashing into trees as she tried to figure out the implications of everything Harry had just said (\emph{did} he still respect her as a heroine? or did that mean he thought she \emph{couldn’t} do it on her own?) and meanwhile a much more sensible part of Hermione flipped back the book to page 37 which had the most promising entry she’d seen so far (though in her imagination she always did it on her own and took Harry completely by surprise)—“I thought this seemed quite interesting,” her voice said.

“Number fourteen, ‘Crozier’, true name unknown,” Harry read. “Wow, that is... that is the gaudiest checkered top hat I’ve ever seen. Wealth, at least six hundred thousand Galleons... so around thirty million pounds, not enough to make a Muggle famous, but good enough for the smaller wizard population, I guess. Rumored to be a modern alias of the six-century-old Nicholas Flamel, the only known wizard to succeed at the incredibly difficult alchemical procedure for creating the Philosopher’s Stone, which enables the transmutation of base metals into gold or silver as well as... the Elixir of Life which indefinitely prolongs the youth and health of the user... Um, Hermione, this seems obviously false.”

“I’ve read more references to Nicholas Flamel,” Hermione said. “\emph{The Rise and Fall of the Dark Arts} says he secretly trained Dumbledore to stand up to Grindelwald. There’s a lot of books that take the story seriously, not just this one... you think it’s too good to be true?”

“No, of course not,” said Harry. Harry pulled out the chair next to her own, at the small table, and sat down beside her in his accustomed place on her right, just like he’d never left; she had to choke back a catch in her throat. “The idea of ‘too good to be true’ isn’t causal reasoning, the universe doesn’t check if the output of the equations is ‘too good’ or ‘too bad’ before allowing it. People used to think that airplanes and smallpox vaccines were too good to be true. Muggles have figured out ways to travel to other stars without even using magic, and you and I can use our wands to do things that Muggle physicists think are literally impossible. I can’t even imagine what we could rule out the \emph{real} laws of magic being able to do.”

“So what’s the problem, then?” Hermione said. Her voice sounded more normal now, in her own ears.

“Well...” Harry said. The boy reached over her own outstretched arm, his robes brushing hers, and tapped the artist’s illustration of an ominously glowing red stone dripping scarlet liquid. “Problem one is that there’s no logical reason why the \emph{same} artifact would be able to transmute lead to gold \emph{and} produce an elixir that kept someone young. I wonder if there’s an official name for that in the literature? Like the ‘turned up to eleven effect’, maybe? If everyone can see a flower, you can’t get away with saying flowers are the size of houses. But if you’re in a flying saucer cult, since nobody can see the alien mothership anyway, you can say it’s the size of a city, or the size of the Moon. Observable things have to be constrained by evidence, but when somebody makes up a story, they can make the story as extreme as they want. So the Philosopher’s Stone gives you unlimited gold \emph{and} eternal life, not because there’s a single magical discovery that would produce both of those effects, but because someone made up a story about a super happy thingy.”

“Harry, there’s a lot of things in magic that aren’t sensible,” she said.

“Granted,” said Harry. “But Hermione, problem two is that not even \emph{wizards} are crazy enough to casually overlook the implications of \emph{this}. \emph{Everyone} would be trying to rediscover the formula for the Philosopher’s Stone, whole \emph{countries} would be trying to capture the immortal wizard and get the secret out of him—”

“It’s not a \emph{secret.}” Hermione flipped the page, showing Harry the diagrams. “The instructions are right on the next page. It’s just so difficult that only Nicholas Flamel’s \emph{done} it.”

“So entire countries would be trying to kidnap Flamel and force \emph{him} to make more Stones. Come on, Hermione, even wizards wouldn’t hear about \emph{immortality} and, and,” Harry Potter paused, his eloquence apparently failing him, “and \emph{just keep going.} Humans are crazy, but they’re not \emph{that} crazy!”

“Not everyone thinks the same way \emph{you} do, Harry.” He did have a point, but... \emph{how} many different references had she come across to Nicholas Flamel? Besides \emph{World’s Wealthiest Wizards} and \emph{Rise and Fall of the Dark Arts,} there’d also been \emph{Stories of Moderately Ancient Times} and \emph{Biographies of the Justly Famous...}

“All right then, \emph{Professor Quirrell} would’ve kidnapped this Flamel guy. It’s what an evil person \emph{or} a good person or just a \emph{selfish} person would do if they had any sense. The Defense Professor knows a lot of secrets and he wouldn’t miss \emph{that} one.” Harry sighed and looked up; she followed his gaze, but he was apparently just looking at the larger library, the rows and rows and rows of bookcases. “I don’t mean to mess with your project,” said Harry, “and I certainly don’t mean to discourage you, but... Honestly, Hermione, I’m not sure you’re going to find any good ideas for making money in a book like this. Like the old joke about how if an economist sees a twenty-pound note lying in the street, they won’t bother picking it up, because if it were real, someone else would’ve picked it up already. Any way of making lots of money that everyone \emph{knows} about to the point where it’s in books like this... you see what I’m saying? It can’t be possible for everyone to make a thousand Galleons a month in three easy steps, or everyone would be doing it.”

“So? That wouldn’t stop \emph{you,}” Hermione said, her voice now roughening again. “You do impossible things all the time, I bet you’ve done something impossible in the last \emph{week} and you didn’t bother \emph{telling} anyone.”

(There was a slight pause, which, if Miss Granger had known, was exactly the length of pause you’d make if you’d fought Mad-Eye Moody and won exactly eight days earlier.)

“Not in the last seven days, no,” Harry said. “Look... part of the trick of doing the impossible is being selective about \emph{which} impossibilities you challenge, and only trying when you have a special advantage. If there’s a money-making method in this book that sounds difficult for a wizard, but it’s easy if we can use Dad’s old Mac Plus, \emph{then} we’d have a plan.”

“I \emph{know that,} Harry,” Hermione said, her voice wavering only slightly. “I was looking to see if there was anything here I \emph{could} figure out how to do. I thought, maybe the difficult part about making a Philosopher’s Stone was that the alchemical circle had to be super precise, and I could get it right by using a Muggle microscope—”

“That’s \emph{brilliant,} Hermione!” The boy rapidly drew his wand, said “\emph{Quietus,}” and then continued after the small noises of the rowdier books had died down. “Even if the Philosopher’s Stone is just a myth, the same trick might work for other difficult alchemies—”

“Well, it \emph{can’t} work,” Hermione said. She’d flown across the library to look up the only book on alchemy that wasn’t in the Restricted Section. And then—she remembered the crushing letdown, all the sudden hope dissipating like mist. “Because \emph{all} alchemical circles have to be drawn ‘to the fineness of a child’s hair’, it isn’t any finer for some alchemies than others. And wizards \emph{have} Omnioculars, and I haven’t heard of any spells where you use Omnioculars to magnify things and do them exactly. I should’ve realized that!”

“Hermione,” Harry said seriously, as he started to dig down into the red-velvet pouch again, “don’t punish yourself when a bright idea doesn’t work out. You’ve got to go through a \emph{lot} of flawed ideas to find one that might work. And if you send your brain negative feedback by frowning when you think of a flawed idea, instead of realizing that idea-suggesting is good behavior by your brain to be encouraged, pretty soon you won’t think of any ideas at all.” Harry put down two heart-shaped chocolates beside the book. “Here, have another chocolate. Besides the one from earlier, I mean. This one is to reinforce your brain for generating a good candidate strategy.”

“I suppose you’re right,” Hermione said in a small voice, but she didn’t touch the chocolate. She started to turn the pages back to 167, where she’d been reading before Harry had come in.

(Hermione Granger did not require \emph{bookmarks,} of course.)

Harry was leaning over slightly, his head almost touching her shoulder, watching the pages as she turned them, as though he might be able to glean valuable information from glimpsing the page for only a quarter-second. Breakfast hadn’t been long ago, and she could clearly identify, from the faint scent of his breath, that Harry’d eaten banana pudding for dessert.

Harry spoke again. “So with all that said... and please take this as a positive reinforcement... did you really try to invent a way to \emph{mass-produce immortality} so that I could \emph{pay off my debt to Lucius Malfoy?}”

“Yes,” she said in an even smaller voice. Even when she \emph{tried} to think like Harry, it seemed she hadn’t yet got the knack of it. “So what’ve you been doing this whole time, Harry?”

Harry made a disgusted face. “Trying to collect evidence on the whole ‘Who Framed Hermione Granger’ mystery.”

“I...” Hermione looked up at Harry. “Shouldn’t I... be trying to solve my \emph{own} mystery, though?” It hadn’t been her first thought, her first priority, but now that Harry mentioned it...

“That wouldn’t work in this case,” Harry said soberly. “There’s too many people who’ll talk to me and not you... and I’m also sorry to say that some of them made me promise not to talk to anyone else. Sorry, I don’t think you can help much on this one.”

“Okay, I guess,” Hermione said leadenly. “Fine. You do everything. You gather all the clues and talk to all the suspects while I just sit here in the library. Let me know after it turns out that it was Professor Quirrell who did it.”

“Hermione...” Harry said. “Why is it so important \emph{who} does what? Shouldn’t it be more important to get everything solved, than who solves it?”

“I guess you’re right,” Hermione said. She lifted her hands to press up at her eyes. “I guess it doesn’t matter any more. Everyone’s going to think—I \emph{know} it’s not your fault, Harry, you were—you were being Good, you were a perfect gentleman —but no matter what I do now, they’ll all think that I’m just—someone for you to rescue.” She paused, and said, with her voice quivering, “And maybe they’re \emph{right}, Harry.”

“Whoa, whoa, hold on there a second—”

“I can’t scare Dementors. I can get Outstandings in Charms class, but I can’t scare Dementors.”

“\emph{I’ve got a mysterious dark side!}” Harry hissed, after his head turned around to scan the library. (There was one boy in a distant corner, who did look in their direction occasionally, but he would’ve been too far away to hear anything even without the Quieting Barrier.) “I’ve got a dark side that \emph{definitely} isn’t a child, and who knows what other crazy magical stuff going on in my head—Professor Quirrell claimed that I become whoever I believe I am—that’s all \emph{cheating,} don’t you see, Hermione? There’s an arrangement that the school administration made that I’m not supposed to talk about, so that the Boy-Who-Lived could have more time to study every day, I’m \emph{cheating} and you’re \emph{still beating me in Charms class.} I’m—I’m probably not—the Boy-Who-Lived probably isn’t even something that you could properly call a child—and you’re \emph{still competing} with that. Don’t you realize, if it \emph{wasn’t} for people paying attention to me, you’d look like the most powerful witch to come along in a century? When you can fight three older bullies by yourself, and win?”

“I don’t know,” she said, pressing her hands again over her eyes, with her voice wavering. “All I know is—even if that’s all \emph{true}—nobody’s ever going to see me for myself anymore, ever.”

“All right,” Harry said after a while. “I see what you mean. Instead of the famous Potter-and-Granger research team, there’ll be Harry Potter and his lab assistant. Um... here’s an idea. How about if I \emph{don’t} focus on making money for a while? I mean, the debt doesn’t come due until I graduate Hogwarts. So you can do it yourself and show the world you’ve still got it. And if you coincidentally crack the secret of immortality along the way, we’ll just call it a bonus.”

The thought of Harry relying on \emph{her} to come up with a solution seemed... like a crushing burden of responsibility to dump on a poor traumatized twelve-year-old girl, and she wanted to hug him for offering her a way to restore her self-respect as a heroine, and it was what she \emph{deserved} for being a horrible person and speaking sharply to Harry all the time, when all along he’d been a truer friend to her than she’d ever been to him, and it was good that he still thought she could do things, and...

“Is there some amazing rational thing you do when your mind’s running in all different directions?” she managed.

“My own approach is usually to identify the different desires, give them names, conceive of them as separate individuals, and let them argue it out inside my head. So far the main persistent ones are my Hufflepuff, Ravenclaw, Gryffindor, and Slytherin sides, my Inner Critic, and my simulated copies of you, Neville, Draco, Professor McGonagall, Professor Flitwick, Professor Quirrell, Dad, Mum, Richard Feynman, and Douglas Hofstadter.”

Hermione considered trying this before her Common Sense warned that it might be a dangerous sort of thing to pretend. “There’s a copy of \emph{me} inside your head?”

“Of course there is!” Harry said. The boy suddenly looked a bit more vulnerable. “You mean there \emph{isn’t} a copy of me living in \emph{your} head?”

There \emph{was,} she realized; and not only that, it talked in Harry’s exact voice.

“It’s rather unnerving now that I think about it,” said Hermione. “I do have a copy of you living in my head. It’s talking to me right now using your voice, arguing how this is perfectly normal.”

“Good,” Harry said seriously. “I mean, I don’t see how people could be friends without that.”

She continued reading her book, then, Harry seeming content to watch the pages over her shoulder.

She’d gotten all the way to number seventy, Katherine Scott, who’d apparently invented a way to turn small animals into lemon tarts, when she finally worked up the courage to speak.

“Harry?” she said. (She was leaning a bit away from him now, though she didn’t realize it.) “If there’s a copy of Draco Malfoy in your head, does that mean you’re friends with Draco Malfoy?”

“Well...” Harry said. He sighed. “Yeah, I’d been meaning to talk with you about this anyway. I kind of wish I’d talked to you sooner. Anyway, how can I put this... I was corrupting him?”

“What do you mean \emph{corrupting?}”

“Tempting him to the Light Side of the Force.”

Her mouth just stayed open.

“You know, like the Emperor and Darth Vader, only in reverse.”

“\emph{Draco Malfoy},” she said. “Harry, do you have \emph{any idea—}”

“Yes.”

“—the sort of things Malfoy has been \emph{saying} about me? What he said he’d \emph{do} to me, as soon as he got the chance? I don’t know what he told to \emph{you,} but Daphne Greengrass told me what Malfoy says when he’s in Slytherin. It’s \emph{unspeakable,} Harry! It’s unspeakable in the completely literal sense that I can’t say it out loud!”

“When was this?” Harry said. “At the start of the year? Did Daphne say \emph{when} this was?”

“No,” Hermione said. “Because it doesn’t matter when, Harry. Anyone who said things—like Malfoy said—they can’t be a good person. It doesn’t matter what you tempted him to, he’s still a rotten person, because no matter \emph{what} a good person would \emph{never}—”

“You’re wrong.” Harry said, looking her straight in the eyes. “I can guess what Draco threatened to do to you, because the second time I met him, he talked about doing it to a ten-year-old girl. But don’t you see, on the day Draco Malfoy arrived in Hogwarts, he’d spent his whole previous life being raised by \emph{Death Eaters.} It would’ve required a \emph{supernatural intervention} for him to have \emph{your} morality given \emph{his} environment—”

Hermione was shaking her head violently. “\emph{No,} Harry. Nobody has to \emph{tell} you that hurting people is wrong, it’s not something you don’t do because the teacher says it’s not allowed, it’s something you don’t do because—because you can \emph{see when people are hurting,} don’t you know that, Harry?” Her voice was shaking now. “That’s not—that’s not a \emph{rule} people follow like the rules for algebra! If you can’t \emph{see} it, if you can’t feel it \emph{here,}” her hand slapped down over the center of her chest, not quite where her heart was located, but that didn’t matter because it was all really in the brain anyway, “then you just don’t have it!”

The thought came to her, then, that Harry might \emph{not} have it.

“There’s history books you haven’t read,” Harry said quietly. “There’s books you haven’t read yet, Hermione, and they might give you a sense of perspective. A few centuries earlier—I think it was definitely still around in the seventeenth century—it was a popular village entertainment to take a wicker basket, or a bundle, with a dozen live cats in it, and—”

“Stop,” she said.

“—roast it over a bonfire. Just a regular celebration. Good clean fun. And I’ll give them this, it was cleaner fun than burning women they thought were witches. Because the way people are built, Hermione, the way people are built to \emph{feel} inside—” Harry put a hand over his own heart, in the anatomically correct position, then paused and moved his hand up to point toward his head at around the ear level, “—is that they hurt when they see their \emph{friends} hurting. Someone inside their circle of concern, a member of their own tribe. That feeling has an off-switch, an off-switch labeled ‘enemy’ or ‘foreigner’ or sometimes just ‘stranger’. That’s how people are, if they don’t \emph{learn} otherwise. So, no, it does \emph{not} indicate that Draco Malfoy was inhuman or even unusually evil, if he grew up believing that it was fun to hurt his enemies—”

“If you believe that\emph{,}” she said with her voice unsteady, “if you \emph{can} believe that, then you’re evil. People are always responsible for what they do. It doesn’t matter what anyone \emph{tells} you to do, you’re the one who does it. Everyone knows that—”

“\emph{No they don’t!} You grew up in a post-World-War-Two society where ‘I vas only followink orders’ is something \emph{everyone knows} the bad guys said. In the fifteenth century they would’ve called it honourable fealty.” Harry’s voice was rising. “Do you think you’re, you’re just \emph{genetically} better than everyone who lived back then? Like if you’d been transported back to fifteenth-century London as a baby, you’d realize \emph{all on your own} that burning cats was wrong, witch-burning was wrong, slavery was wrong, that every sentient being ought to be in your circle of concern? Do you think you’d \emph{finish} realizing all that by the first day you got to Hogwarts? Nobody ever \emph{told} Draco he was personally responsible for becoming more ethical than the society he grew up in. And \emph{despite that}, it only took him four months to get to the point where he’d grab a Muggleborn falling off a building.” Harry’s eyes were as fierce as she’d ever seen him. “I’m not \emph{finished} corrupting Draco Malfoy, but I think \emph{he’s done pretty well so far.}”

The problem with having such a good memory was that she \emph{did} remember.

She remembered Draco Malfoy grabbing her wrist, so hard she’d had a bruise afterward, while she was falling off the roof of Hogwarts.

She remembered Draco Malfoy helping her up, after that mysterious tripping jinx had sent her stumbling into the Slytherin Quidditch Captain’s plate of food.

And she remembered—it was, in fact, the reason she’d brought up the topic in the first place—how she’d felt when she’d heard Draco Malfoy’s testimony under Veritaserum.

“Why didn’t you \emph{tell} me any of this?” Hermione said, and despite herself, her voice rose in pitch. “If I’d \emph{known}—”

“It wasn’t my secret to tell you,” Harry said. “Draco’s the one who would’ve been at risk, if his father had found out.”

“I’m not stupid, Mr.~Potter. What’s the \emph{real} reason you didn’t tell me, and what were you \emph{actually} doing with Mr.~Malfoy?”

“Ah. Well...” Harry broke eye contact with her, and looked down at the library table.

“Draco Malfoy told the Aurors under Veritaserum that he wanted to know if he could beat me, so he challenged me to a duel to \emph{test it empirically}. Those were his \emph{exact words} according to the transcript.”

“Right,” Harry said, still not meeting her eyes. “Hermione Granger. Of \emph{course} she’ll remember the exact wording. It doesn’t matter if she’s chained to her chair, on trial for murder in front of the entire Wizengamot—”

“What were you \emph{really} doing with Draco Malfoy?”

Harry winced, and said, “Probably not \emph{quite} what you’re thinking, but...”

The horror scaled and scaled within her, and finally broke loose.

“\emph{You were doing SCIENCE with him?}”

“Well—”

“\emph{You were doing SCIENCE with him? You were supposed to be doing science with ME!}”

“It wasn’t like that! It’s not like I was doing \emph{real} science with him! I was just, you know, \emph{teaching} him some harmless bits of Muggle science, like elementary physics with algebra and so on—it’s not like I was doing original magical research with him, the way I was with you—”

“And I suppose you didn’t tell \emph{him} about \emph{me,} either?”

“Um, of course not?” Harry said. “I’ve been doing science with him since October, and he wasn’t exactly ready to hear about you then—”

The inexpressible sense of betrayal inside her was welling and welling, taking over everything, her rising voice, her glaring eyes, her nose that she was certain was starting to run, the burning in her throat. She shoved herself up from the table and took a step back, the better to look down on her betrayer, and her voice was very nearly screeching as she yelled, “\emph{That is not okay! You can’t do science with two people at once!}”

“Er—”

“I mean, you can’t do science with two different people and \emph{not tell them about each other!}”

“Ah...” Harry said cautiously. “I \emph{did} think of that, and I was very careful not to get your research mixed together with anything I did with him—”

“You were being \emph{careful.”} She would have \emph{hissed} it, if it had contained any Ss.

Harry raised a hand and rubbed at his messy hair, and somehow that made her want to scream at him even \emph{more.} “Miss Granger,” said Harry, “I think this conversation has become \emph{metaphorical} on a level that’s, um...”

\emph{“What?”} she screeched at him, at the top of her lungs inside their Quieting barrier.

Then she realized and got so red that if she’d had an adult level of magical power her hair would have spontaneously caught on fire.

The lone other patron in the library, the Ravenclaw boy sitting in the far opposite corner, was staring wide-eyed at both of them while making a rather sad attempt to conceal it by holding up a book just below his face.

“Right,” Harry said with a small sigh. “So, keeping \emph{firmly in mind} that it was just a bad metaphor, and that \emph{real scientists} collaborate with each other \emph{all the time,} I don’t think that I was cheating. Scientists often keep quiet about projects they’re working on. You and I are doing research that we’re keeping secret, and there were reasons not to tell Draco Malfoy in particular—he wouldn’t have stayed around me at all, in the beginning, if he’d known I was your friend and not your rival. And Draco would’ve been the one at risk if I’d told anyone else about \emph{him}—”

“Is that really all?” she said. “\emph{Really,} Harry? You didn’t want both of us to \emph{feel special,} like we were the \emph{only} ones you wanted to be with and the \emph{only} ones who got to be with you?”

“That was \emph{not} why I—”

Harry paused.

Harry looked at her.

All the blood was rushing back into her face, there probably should’ve been steam coming out of her ears, which in turn should’ve been melting off her head with the liquid flesh running down into her neck, as she realized what she’d just blurted out.

Harry was staring at her in dawning and complete terror.

“Well...” she said in a rather high-pitched voice, “it’s... oh, I don’t know, Harry! \emph{Is} it just a metaphor? When a boy spends a hundred thousand Galleons to save a girl from certain doom, she’s entitled to wonder, don’t you think? It’s like being bought flowers, only, you see, rather \emph{more} so—”

Harry shoved himself up from the table and took a staggering step back, even as he brought up his arms to wave frantically. \emph{“That’s not why I did it! I did it because we’re friends!”}

“Just friends?”

Harry Potter’s breathing was starting to scale up toward hyperventilation. “Very good friends! Extra-special friends, even! Best friends forever, possibly! But not \emph{that} kind of friends!”

“Is it really that awful to think about?” she said with a catch in her voice. “I mean—I’m not saying \emph{I’m} in love with \emph{you,} but—”

“Oh, you’re not? Thank \emph{goodness.}” Harry brought up the sleeve of his robe and wiped across his forehead. “Look, Hermione, please don’t misunderstand, I’m sure you’re a wonderful person—”

She took a staggering step back.

“—but—even with my dark side—”

“Is \emph{that} what this is about?” said Hermione. “But I—I wouldn’t—”

“No, no, I mean, I have a mysterious dark side and probably other weird magic stuff going on, you \emph{know} I’m not a normal child, not really—”

“It’s okay to not be normal,” she said, feeling increasingly desperate and confused. \emph{“I’m} okay with it—”

“But \emph{even with all that weird magical stuff} letting me be more adult than I should be, I haven’t gone through puberty yet and there’s no hormones in my bloodstream and my brain is \emph{physically incapable} of falling in love with anyone. So I’m not in love with you! I couldn’t possibly be in love with you! For all I know at this point, six months from now my brain is going to wake up and decide to fall in love with Professor Snape! Er, can I take it from this that you \emph{have} been through puberty?”

“Eep,” said Hermione in a high-pitched sound. She swayed where she stood, and a moment later Harry was rushing over to her side and helping lower her to sit on the ground, bracing her body with firm hands.

The fact was that she \emph{had} staggered over to Professor McGonagall’s office back in December, not in total surprise because she’d done her reading, but still rather \emph{queasily} and it was with great relief that she’d learned that witches had Charms to deal with the inconveniences and \emph{what was Harry even doing asking a poor innocent girl a question like that—}

“Look, I’m \emph{sorry},” Harry said frantically. “I really didn’t mean most of that the way it sounded! I’m sure that anyone taking the outside view of the whole situation and offering betting odds on who I finally married would assign a higher probability to you than anyone else I can think of—”

Her intelligence, which had barely been starting to pull itself together, promptly exploded into sparks and flame.

“—though not necessarily a probability higher than fifty percent, I mean, from the outside view there’s a lot of other possibilities, and who I like before I hit puberty probably isn’t all that strongly \emph{diagnostic} of who I’ll be with seven years later—I don’t want to sound like I’m \emph{promising} anything—”

Her throat was making some sort of high-pitched sounds and she wasn’t really listening to exactly what. All her universe had narrowed to Harry’s terrible, terrible voice.

“—and besides I’ve been reading about evolutionary psychology, and, well, there are all these suggestions that one man and one woman living together happily ever afterward may be more the exception rather than the rule, and in hunter-gatherer tribes it was more often just staying together for two or three years to raise a child during its most vulnerable stages—and, I mean, considering how many people end up horribly unhappy in traditional marriages, it seems like it might be the sort of thing that needs some clever reworking—especially if we actually do solve immortality—”
\sbreak

Tano Wolfe, of fifth-year Ravenclaw, slowly stood up from his library desk, from which vantage point he’d just watched Granger flee the library, sobbing. He hadn’t been able to hear the argument, but it had clearly been one of \emph{those.}

Slowly and with his knees trembling, Tano approached the Boy-Who-Lived, who was staring in the direction of the library doors, still vibrating from the force of how they’d been slammed.

Tano didn’t particularly want to do this, but Harry Potter \emph{had} been Sorted into Ravenclaw. The Boy-Who-Lived was, technically, his fellow Ravenclaw. And that meant there was a Code.

The Boy-Who-Lived didn’t say anything as Tano approached him, but his gaze wasn’t friendly.

Tano swallowed, laid a hand on Harry Potter’s shoulder, and recited, his voice cracking only slightly, “Witches! Go figure, huh?”

“\emph{Remove your hand before I cast it into the outer darkness.}”

The library doors slammed open again in the wake of another departure.