\partchapter{Roles}{VII}

\section[The fourth meeting:\\
(4:38\pm, April 17th, 1992)]{The fourth meeting:\\
(4:38\pm, April 17th, 1992)\protect\footnotemark}
\authorsnotetext{For those who have not read canon: the wooden sign has somewhat changed, but the inscription here is the same as in J.~K.~Rowling’s original.}

\lettrine{T}{he} man wearing the worn, warm coat, with three faint scars etched forever into his cheek, observed Harry Potter as closely as he could while the boy looked around politely at the rows of cottages. For someone whose best friend had died yesterday, Harry Potter seemed strangely composed, though not in any way reminiscent of unfeeling, or normality. \emph{I don’t wish to talk about that,} the boy had said, \emph{with you or anyone.} Saying ‘wish’ and not ‘want’, as though to emphasize that he was able to use grown-up words and make grown-up decisions. There had been only one thing Remus Lupin had thought of that might help, after he’d received the owls from Professor McGonagall and that strange man Quirinus Quirrell.

“There’s a lot of empty houses,” the boy said, glancing around again.

Godric’s Hollow had changed, in the decade since Remus Lupin had been a frequent visitor. Many of the old, peaked cottages looked deserted, with green leafy vines growing across their windows and their doors. Britain had contracted noticeably, in the aftermath of the Wizarding War, having lost not only the dead but the fled. Godric’s Hollow had been hard-hit. And afterwards still more families had moved elsewhere, to Hogsmeade or magical London, the deserted houses too uncomfortable a reminder.

Others had remained. Godric’s Hollow was older than Hogwarts, older than Godric Gryffindor whose name it had taken, and there were families which would reside here until the end of the world and its magic.

The Potters had been one such family, and would be again, if the last Potter so chose.

Remus Lupin tried to explain all that, simplifying it as best he could for the young boy. The Ravenclaw nodded thoughtfully and said nothing, as though he had understood it all without need of questions. Perhaps that was so; the child of James Potter and Lily Evans, the Head Boy and Head Girl of Hogwarts, would hardly be stupid. The child had certainly seemed highly intelligent, for the little time that they had spoken in January, though at that time Remus had done most of the talking.

(There was also that business with the Wizengamot which Remus had heard rumours about, but Remus didn’t believe a single word of that, any more than he’d believed it about James betrothing his son to Molly’s youngest.)

“There’s the monument,” Remus said, pointing ahead of them.

\later

Harry walked beside Mr~Lupin toward the black marble obelisk, thinking silently. It seemed to Harry that this adventure was essentially misguided; he had no use for grief counselling, that was not Harry’s chosen path. So far as Harry was concerned, the five stages of grief were Rage, Remorse, Resolve, Research, and Resurrection. (Not that the usual ‘five stages of grief’ had any experimental evidence whatsoever that Harry had ever heard about.) But Mr~Lupin had seemed too sincere to refuse; and visiting James and Lily’s home was something Harry felt he ought not to turn down. So Harry walked, feeling oddly detached; walking silently through a play whose script he was not interested in reading.

Harry had been told that he wasn’t to wear the Cloak of Invisibility for this journey, so that Mr~Lupin could keep track of him.

Harry was practically certain that Dumbledore, or both Dumbledore and Mad-Eye Moody, were following them invisibly to see if anyone tried for the bait. There was no way Harry would have been let out of Hogwarts with only Remus Lupin for a guard. Harry didn’t expect anything to happen, though. He’d seen nothing to contradict the hypothesis that all the danger centred on Hogwarts and only Hogwarts.

As the two of them walked closer toward the centre of town, the marble obelisk transformed into—

Harry drew in a breath. He’d been expecting a heroic pose of James Potter with wand levelled against Lord Voldemort, and Lily Potter with arms outstretched in front of the crib.

Instead there was a man with untidy hair and glasses, and a woman with her hair let down and a baby in her arms, and that was all.

“It looks very…normal,” Harry said, feeling an odd catch in his throat.

“Madam Longbottom and Professor Dumbledore put their foot down hard,” said Mr~Lupin, who was looking more at Harry than at the monument. “They said that the Potters should be remembered as they had lived, not as they had died.”

Harry looked at the statue, thinking. Very strange, to see himself as a baby of stone, with no scar upon his forehead. It was a glimpse at an alternate universe, one where Harry James Potter (no Evans-Verres to his name) became an intelligent but ordinary wizarding scholar, maybe Sorted into Gryffindor like his parents. A Harry Potter who grew up a proper young wizard, knowing little of science for all that his mother was Muggleborn. Ultimately changing…not much. James and Lily wouldn’t have raised their son with what Professor Quirrell would have called \emph{ambition} and what Professor Verres-Evans would have called \emph{the common endeavour.} His birth parents would have loved him very much, and that would not have been much help to anyone in the world except Harry. If someone had undone their death—

“You were their friend,” Harry said, turning to look at Lupin. “For a long time, since you were children.”

Mr~Lupin nodded silently.

Professor Quirrell’s voice resounded in Harry’s approximate memory: \emph{The most likely difference is not that you care more. Rather it is that, being a more logical creature than they, only you are aware that the role of Friend ought to require this of you…}

“When Lily and James died,” Harry said, “did you think at all of whether there might be some magical way to get them back? Like Orpheus and Eurydice? Or the, what was it, Elrin brothers?”

“There is no magic which can undo death,” Mr~Lupin said quietly. “There are some mysteries which wizardry cannot touch.”

“Did you do a mental check of what you thought you knew, how you thought you knew it, and how high the probability was of that conclusion?”

“What?” said Mr~Lupin. “Could you repeat that, Harry?”

“I’m saying, did you think about it anyway?”

Mr~Lupin shook his head.

“Why not?”

“Because it was already done, and over,” Remus Lupin said gently. “Because wherever James and Lily are now, they would wish me to act for the sake of the living, not the dead.”

Harry nodded silently. He’d been pretty sure of the answer to that question before he’d asked. He’d already read that script. But he’d asked anyway, just in case Mr~Lupin had spent a week obsessing about it, because Harry could have been wrong.

The soft voice of the Defence Professor seemed to speak in Harry’s mind. \emph{Surely, if Lupin truly cared, he would not need special instruction for something as simple as thinking for five minutes before giving up…}

\emph{Yes, he would,} Harry answered the mental voice. \emph{Human beings wouldn’t suddenly obtain a skill like that just because they cared. I learned about it because I’d read library books, produced by a huge scientific edifice—}

And that other part of Harry said, in that soft voice, \emph{But there is also another hypothesis, Mr~Potter, and it fits the data in a much less complicated way.}

\emph{No it doesn’t! How would people even know what to pretend, if nobody had ever cared?}

\emph{They don’t know. That is what you observe.}

The two of them walked onward toward a certain house, past a long row of occupied wizard cottages and other cottages overgrown with vines.

Coming finally to the house with half its top blown off, and green leaves growing over into the inside; behind a shoulder-high wild-growing hedge lining the pavement, and a narrow metal gate (Mr~Hagrid had probably stepped right over it, being unable to fit through). The gap in the roof was like a giant mouth had taken a circular bite from the house, leaving spines of wood, what had maybe been support beams, sticking out. To the right side a single chimney still stood upright, uneaten by the giant bite, but leaning dangerously without its former support. Windows were shattered. Where there should have been a front door were only splinters of wood.

To this place Lord Voldemort had come, \emph{silently, making less noise than the dead leaves slithering along the pavement…}

Remus Lupin put a hand upon Harry’s shoulder. “Touch the gate,” Mr~Lupin urged.

Harry reached out a hand and did so.

Like a fast-growing flower a sign burst from the tangled weeds in the ground behind the gate, a wooden sign with golden letters, and it said:

\begin{center}
On this spot, on the night of 31 October 1981,\\
Lily and James Potter lost their lives.

They were survived by their son, Harry Potter,\\
the only wizard ever to withstand the Killing Curse,\\
the Boy-Who-Lived, who broke You-Know-Who’s power.

This house has been left in its ruined state,\\
as a monument to the Potters,\\
as a reminder of their sacrifice.
\end{center}

In a blank space below the golden letters were written other messages, dozens of them, magical ink that rose to the surface and gleamed brightly enough to be read before fading and giving way to other messages.

\begin{center}
So my Gideon is avenged.

Thank you, Harry Potter. Fare well wherever you are.

We will always be in the Potters’ debt.

Oh James, oh Lily, I am sorry.

I hope you’re alive, Harry Potter.

There is always a price.

I wish our last words had been kinder, James. I’m sorry.

There is always a dawn after the night.

Rest well, Lily.

Bless you, Boy-Who-Lived. You were our miracle.
\end{center}

“I guess—” Harry said. “I guess that’s what people do—instead of trying to make it better—” Harry stopped. The thought seemed unworthy of this place. He looked up, and saw Remus Lupin gazing at him with a look so gentle that Harry wrenched his eyes away to the blasted and broken roof.

\emph{You were our miracle.} Harry had always heard the word ‘miracle’ in the context of how, in the natural universe, there was no such thing. And yet looking at the ruined house, he suddenly knew exactly what the word meant, the note of grace all unexplained, the blessing inexplicable. The Dark Lord had almost won, and then in one night all the darkness and terror had ended, salvation without justification, a sudden dawn from out of the darkness and even now nobody knew \emph{why}—

If Lily Potter had lived beyond her confrontation with Lord Voldemort, she would have felt that way when she saw her baby alive, afterwards.

“Let’s go,” whispered the baby boy, ten years later.

They went.

At  the entrance to the graveyard was a kissing gate.
Remus took out his wand (Harry was already
holding his) and there was a brief blur as they stepped through.

Some of the stones rising up from the ground looked as old as the wall in Oxford that his father had said was around a thousand years old.

\emph{Hallie Fleming,} said the first stone that Harry saw, in a carving almost invisibly faded with the erosion of time. \emph{Vienna Wood,} said another.

It had been a long time since Harry had visited a graveyard. His mind had still been childlike the last time he’d come to one, long before he’d seen within Death’s shadow. Coming here now was…strange, and sad, and puzzling, and \emph{this has been happening for so long, why haven’t wizards tried to stop it, why aren’t they putting all their strength into that like Muggles do with medical research, only more so, wizards have more reason to hope…}

“The Dumbledores lived in Godric’s Hollow too?” Harry said, as they walked past a pair of relatively new stones saying \emph{Kendra Dumbledore} and \emph{Ariana Dumbledore.}

“For a long, long time,” Mr~Lupin said.

They walked further into the graveyard, far toward the end, past many deaths that had been mourned.

Then Mr~Lupin pointed at a linked double headstone, of marble still white and unaged.

“Are there going to be messages there?” Harry said. He didn’t want to deal any more with the way that other people dealt with death.

Mr~Lupin shook his head.

They walked toward the linked white stones.

And stood before—

“What is this?” Harry whispered. “Who…\emph{who wrote this?}”

\begin{center}
JAMES POTTER\\
BORN 27 MARCH 1960\\
DIED 31 OCTOBER 1981
\end{center}

“Wrote what?” said Mr~Lupin, puzzled.

\begin{center}
LILY POTTER\\
BORN 30 JANUARY 1960\\
DIED 31 OCTOBER 1981
\end{center}

“\emph{This!}” Harry cried. “The \emph{inscription!}” There were tears welling up in Harry’s eyes, at the brightness out of place and unexplained, the touch of grace where no grace should have been, the mysterious blessing, tears welling up at

\begin{center}
THE LAST ENEMY THAT SHALL BE DESTROYED IS DEATH
\end{center}

“That?” Mr~Lupin said. “That’s the…motto, I suppose you could call it, of the Potters. Though I don’t think it was ever something as formal as that. Just a saying handed down from long, long ago…”

“This—that—” Harry scrambled down to kneel beside the grave, touched the inscription with a trembling hand. “\emph{How?} Things like that can’t just be, be \emph{genetic}—”

Then Harry saw what tears had blurred, the faint carving of a line, within a circle, within a triangle.

The symbol of the Deathly Hallows.

And Harry understood.

“They tried,” Harry whispered.

\emph{The three Peverell brothers.}

\emph{Had they lost someone precious to them, was that where it had begun?}

“With all their lives, they tried, and they made progress—”

\emph{The Cloak of Invisibility, that could defeat the Dementors’ sight.}

“—but their research wasn’t finished—”

\emph{Hiding from Death’s shadow is not defeating Death itself. The Resurrection Stone couldn’t really bring anyone back. The Elder Wand couldn’t protect you from old age.}

“—so they passed on the mission to their children, and their children’s children.”

\emph{Generation after generation.}

\emph{Until it came to me.}

Could Time echo like that, rhyming, between this far into the future, and that far in the past? It \emph{couldn’t} be coincidence, could it? Not this message, not in this place.

\emph{My family.}

\emph{You really were, my mother and my father.}

“It doesn’t mean resurrecting the dead, Harry,” Mr~Lupin said. “It means accepting death, and so being beyond death, mastering it.”

“Did James tell you that?” Harry said, his voice strange.

“No,” said Mr~Lupin, “but—”

“Good.”

Harry rose up slowly from where he had been kneeling, feeling as though he were pushing up a sun upon his shoulders, raising the dawn above the horizon.

\emph{Of \emph{course} other wizards have tried. I am not unique. I was never alone. These feelings in my heart, they’re not so special, not in the wizard world or the Muggle one.}

“Harry, your wand!” There was a sudden excitement in Mr~Lupin’s voice, and when Harry raised his wand to look at it closely, he saw that it was gleaming ever so faintly with a silver light, welling out of the wood.

“Cast the Patronus Charm!” urged Mr~Lupin. “Try casting it again, Harry!”

\emph{Oh, right. So far as Mr~Lupin knows, I can’t—}

Harry smiled, and even laughed a little. “I’d better not,” Harry said. “If I tried to cast the spell in this state of mind, it’d probably kill me.”

“\emph{What?}” said Mr~Lupin. “The Patronus Charm doesn’t do that!”

Harry James Potter-Evans-Verres raised his left hand, still laughing, and wiped away some more tears.

“You know, Mr~Lupin,” Harry said, “it really takes a \emph{baroque} interpretation to think that somebody would be walking around, pondering how death is just something we all have to accept, and communicate their state of mind by saying, ‘The last enemy that shall be destroyed is death.’ Maybe someone else thought it sounded poetic and picked up the phrase and tried to interpret it differently, but whoever said it first didn’t like death much.” Sometimes it puzzled Harry how most people didn’t seem to even \emph{notice} when they were twisting something around to the exact opposite of its obvious reading. It couldn’t be a raw brainpower thing, people could see the obvious reading of most other English sentences. “Also ‘shall be destroyed’ refers to a change of future state, so it can’t be about the way things are now.”

Remus Lupin was staring at him with wide eyes. “You certainly are James and Lily’s child,” the man said, sounding rather shocked.

“Yes, I am,” Harry said. But that wasn’t enough, he had to do something more, so Harry raised his wand in the air and said, his voice as steady as he could make it, “I am Harry James Potter-Evans-Verres, the son of Lily and James, of the house of Potter, and I accept my family’s quest. Death is my enemy, and I will defeat it.”

\emph{Thrayen beyn Peverlas soona ahnd thrih heera toal thissoom Dath bey yewoonen.}

“What?” Harry said aloud. The words had popped up into his stream of consciousness as though from his own thoughts, unexplained.

“What was that?” said Remus Lupin at the same time.

Harry turned, scanning the graveyard, but he didn’t see anything. Beside him, Mr~Lupin was doing the same.

Neither of them noticed the tall stone worn as though from a thousand years of age, upon it a line within a circle within a triangle glowing ever so faintly silver, like the light which had shone from Harry’s wand, invisible at that distance beneath the still-bright Sun.

\latersection{Some time later:}

“Thank you again, Mr~Lupin,” Harry said, the tall, faintly scarred man was about to depart once more. “Though I really wish you hadn’t—”

“Professor Dumbledore said that I was to portkey us back to Hogwarts if anything unusual happened, whether or not it seemed like an attack,” Mr~Lupin said firmly. “Which is eminently sensible.”

Harry nodded. And then, having carefully saved this question for last, “Do you have any idea of what the words meant?”

“If I did, I wouldn’t tell you,” Mr~Lupin said, looking rather severe. “Certainly not without Professor Dumbledore’s permission. I can understand your eagerness, but you should not go trying to uncover any ancestral secrets of the Potters until you are an adult. That means after you’ve passed your NEWTs, Harry, or at least your OWLs. And I still think you’ve picked up entirely the wrong idea of what your family motto is meant to say!”

Harry nodded, sighing internally, and bade Mr~Lupin farewell.

\later

Harry went back through Hogwarts, to the Ravenclaw Tower, feeling strange, and strengthened. He would not have expected any of that, but it had been all to the good.

He was passing through the Ravenclaw common room, on the way to his dorm.

That was when the shining creature came to him, gleaming soft white beneath the candle-fires of the Ravenclaw common room, as it slithered out from nowhere, the silver snake.

\later

\begin{center}
\emph{Þregen béon Pefearles suna and þrie hira tól þissum Déað béo gewunen.}

Three shall be Peverell’s sons and three their devices by which Death shall be defeated.

—Spoken in the presence of the three Peverell brothers,\\
in a small tavern on the outskirts of what would later be called Godric’s Hollow. \end{center}

%  LocalWords:  Elrin Hallie Thrayen beyn Peverlas soona ahnd thrih heera
%  LocalWords:  toal thissoom Dath bey yewoonen Þregen béon Pefearles suna
%  LocalWords:  þrie hira tól þissum Déað béo gewunen
