\partchapter{Taboo Tradeoffs, Aftermath}{I}

\lettrine{W}{hen} Padma entered the Transfiguration classroom, she saw that half the class had beaten her there, a strange, deathly silence pervading the room. Harry Potter sat alone in one corner, staring off into some unknown distance, his eyes half-lidded, nearly closed.

Rumor said that the Aurors had discovered that the Defense Professor had Polyjuiced as Granger to fool Malfoy.

Rumor said that Hermione had been bound by the Unbreakable Vow to be Draco Malfoy’s slave.

Rumor said that Hermione had gotten the Dementor’s Kiss.

But if \emph{that} were true, Harry Potter wouldn’t be sitting there, he would be—

Padma didn’t know what General Potter would do. Her mind went blank, trying to think about it.

Even when Professor McGonagall got there, the silence hadn’t broken. The Transfiguration Professor walked up to the board without a pause, erased it with a sweep of her hand, and then began to write.

“Today, children,” began the calm professional voice of the Transfiguration Professor, just as though nothing out of the ordinary had happened that week, “we shall learn how much effort it takes to sustain a Transfiguration, and why, at your age, you should not even try. The original Form is not gone, only suppressed; and to maintain that suppression—”

“Excuse me,” said Padma Patil. She knew her voice was shaking, she knew that she was trembling visibly, but she had to ask. “Excuse me, Professor, what happened with Miss Granger?”

The Transfiguration Professor paused at the board, and turned to look at Padma. The Professor should have looked stern, having been interrupted without a hand being raised, but instead her face was kindly. “You don’t already know, Miss Patil? I expected that rumor would have spread.”

“There’s too many rumors,” said Padma. “I don’t know what’s true.”

Morag MacDougal raised her hand, then said without waiting to be called, “I told you, Padma, what’s \emph{true} is that the Wizengamot found Granger guilty and ordered her to get the Dementor’s Kiss and they brought in the Dementor and Harry Potter glued it to the ceiling and wouldn’t let it down until—”

“Oh, dear Merlin,” said Professor McGonagall, her expression growing sharp, but then she visibly calmed herself. “The affair was utterly ridiculous and I shan’t go into detail. Let it stand that Miss Granger is resting with Madam Pomfrey for now, and coming back to classes tomorrow. And if I catch anyone bothering her, I shall turn them into glass vases and drop them.”

The entire class gasped at this; it wasn’t so much that the threat was fatal, as that it broke the safety rules for Transfiguration.

Professor McGonagall turned back to her board—

From a corner of the classroom, another voice rose up. “What about Professor Quirrell?” said Terry Boot. “Has he been arrested?”

“The Aurors are only detaining him,” said the Transfiguration Professor without turning around. “If they have not given back our Defense Professor by tomorrow, I shall ask the Headmaster to go fetch him. Though I may as well tell you now that the Board of Governors has scheduled a vote on whether Professor Quirrell’s battles shall be allowed to continue.”

Kevin Entwhistle spoke. “And General Malfoy? When’s he getting back from St.~Mungo’s?”

The Transfiguration Professor paused in her drawing.

She turned around again, more slowly, this time.

“I \emph{am} sorry, Mr.~Entwhistle,” said Professor McGonagall. Her face looked a little more lined than when she had entered the room. “Mr.~Malfoy’s health is in no danger, I am given to understand. Unfortunately, I have received an owl from Mr.~Malfoy’s father withdrawing him from Hogwarts. I am afraid he is not coming back.”

