\chapter{Egocentric Bias}

\lettrine{T}{here’d} been a sinking feeling in Hermione’s stomach lately, every time she heard the other students talking about her and Harry. She’d been in a shower stall this morning when she’d overheard a conversation between Morag and Padma that had been the last straw piled on top of quite a lot of other straws.

She was starting to think that getting involved in a rivalry with Harry Potter had been a terrible mistake.

If she’d just \emph{stayed away} from Harry Potter, she could have been Hermione Granger, the brightest academic star of Hogwarts, who was earning more points for Ravenclaw than anyone. She wouldn’t have been \emph{as} famous as the Boy-Who-Lived, but she would have been famous for \emph{herself}.

Instead the Boy-Who-Lived had an academic rival, and her name happened to be Hermione Granger.

And worse, she had gone on a date with him.

The idea of getting into a Romance with Harry had seemed like an appealing idea at first. She’d read books like that, and if there was anyone in Hogwarts who was a candidate for the heroine’s love interest it was obviously Harry Potter. Bright, funny, famous, sometimes scary...

So she’d forced Harry into going on a date with her.

And now \emph{she} was \emph{his} love interest.

Or worse, one of the options on his dinner menu.

She’d been in a shower stall that morning and just about to turn on the water, when she’d heard giggles coming from outside. And she’d heard Morag talking about how that Muggleborn girl probably wouldn’t fight hard enough to win against Ginevra Weasley, and Padma speculating that Harry Potter might decide he wanted \emph{both}.

It was like they didn’t understand that \shout{girls} had options on their dinner menu and \shout{boys} fought over them.

But that wasn’t even the part that hurt, really. It was that when she scored 98 on one of Professor McGonagall’s tests, the news wasn’t that Hermione Granger had scored the highest in the class, the news was that Harry Potter’s rival had scored seven more points than him.

If you got too close to the Boy-Who-Lived, you became part of his story.

You didn’t get your own.

And the thought had come to Hermione that she should just walk away, but that would’ve been too sad.

But she did want to get \emph{back} what she’d accidentally given away by letting herself become known as Harry’s rival. She wanted to be a separate person again instead of Harry’s third leg, was that too much to ask?

It was a hard trap to climb out of once you fell in. No matter how high you scored in class, even if you did something that deserved a special dinnertime announcement, it just meant you were rivaling Harry Potter again.

But she thought she’d come up with a way.

Something to do that \emph{wouldn’t} be seen as pushing up on the opposite end of Harry Potter’s seesaw.

It would be hard.

It would go against her nature.

She would have to fight someone very evil.

And she would need to ask someone even \emph{more} evil for help.

Hermione raised her hand to knock upon that terrible door.

She hesitated.

Hermione realized she was being \emph{silly}, and raised her hand a bit higher.

She tried to knock again.

Her hand quite failed to touch the door.

And then the door swung open anyway.

“Dear me,” said the spider, sitting in its web. “Was it really that hard to lose a single Quirrell point, Miss Granger?”

Hermione stood there with her hand raised, her cheeks growing pink. It \emph{had} been.

“Well, Miss Granger, I shall be merciful,” said the evil Professor Quirrell. “Consider it already lost. There, I have taken a hard choice from you. Are you are not grateful?”

“Professor Quirrell,” Hermione managed to say in a voice that squeaked a little. “I have a lot of Quirrell points, don’t I?”

“You do indeed,” said Professor Quirrell. “Though one less than you had before. Terrible, isn’t it? Just think, if I don’t like your reason for coming here, you could lose another fifty. Maybe I’d take them away one...\ by one...\ by one...”

Hermione’s cheeks were going even redder. “You’re really evil, did anyone ever tell you that?”

“Miss Granger,” Professor Quirrell said gravely, “it can be dangerous to give people compliments like that when they have not been truly earned. The recipient might feel bashful and undeserving and want to do something worthy of your praise. Now what was it you wanted to talk to me about, Miss Granger?”
\sbreak
It was after lunch on Thursday afternoon, and Hermione and Harry were ensconced in a little library nook, with a \emph{Quietus} field up so they could talk. Harry was lying stomach-down on the ground with his elbows resting on the floor and his head in his hands and his feet kicking up casually behind him. Hermione was occupying a stuffed chair much too large for her, like she was the Hermione center of a candy shell.

Harry had suggested that they could, as a first pass, read just the \emph{titles} of all the books in the library, and then Hermione could read all the tables of contents.

Hermione had thought this was a brilliant idea. She’d never done that with a library before.

Unfortunately there was a slight flaw in this plan.

Namely, they were both Ravenclaws.

Hermione was reading a book called \emph{Magical Mnemonics.}

Harry was reading a book called \emph{The Skeptical Wizard.}

Each had thought it was just one special exception they would make only this one time, and neither had yet realized it was impossible for either of them to ever finish reading all the book titles no matter how hard they tried.

The quiet of their little nook was broken by two words.

“Oh, \emph{no},” Harry suddenly said out loud, sounding like the words had been torn out of him, and like he was trying very hard not to laugh.

There was a bit more quiet.

“He \emph{didn’t},” Harry said, in the same voice.

Then she heard Harry start giggling helplessly.

Hermione looked up from her book.

“All right,” she said, “what \emph{is} it?”

“I just found out why you never ask the Weasleys about the family rat,” Harry said. “It’s \emph{really} awful and I shouldn’t be laughing and I’m a terrible person.”

“Yes,” Hermione said primly, “you are. Tell me too.”

“Okay, first the background. There’s a whole chapter in this book about Sirius Black conspiracy theories. You remember who that is, right?”

“Of course,” said Hermione. Sirius Black was a traitor, a friend of James Potter who’d betrayed the location of Harry’s parents to Voldemort.

“So it turns out there were a number of, shall we say, \emph{irregularities}, associated with Black going to Azkaban. He didn’t get a trial, and the Junior Minister in charge when the Aurors arrested Black was none other than Cornelius Fudge, who became our current Minister of Magic.”

That sounded a little suspicious to Hermione too, and she said as much.

Harry made a shrugging motion with his shoulders, as he lay on the floor looking at his book. “Suspicious things happen all the time, and if you’re a conspiracy theorist you can always find \emph{something}.”

“But \emph{no trial?}” said Hermione.

“It was right after the Dark Lord’s defeat,” Harry said, his voice serious as he said it. “Things were incredibly chaotic, and when the Aurors tracked down Black he was standing there laughing in a street ankle-deep in blood, with twenty eyewitnesses to recount how he’d killed a friend of my father’s named Peter Pettigrew plus twelve bystanders. I’m not saying I approve of Black not getting a trial. But these are wizards we’re talking about here, so it’s not really any more suspicious than, I don’t know, the sort of thing people point to when they want to argue over who shot John F. Kennedy. So anyway, Sirius Black is the wizarding Lee Harvey Oswald. There’s all sorts of conspiracy theories about who \emph{really} betrayed my parents instead of him, and one of the favorites is Peter Pettigrew, and this is where it starts getting complicated.”

Hermione listened, fascinated. “But how do you go from there to the Weasleys’ \emph{pet rat}—”

“Hold on,” said Harry, “I’m getting there. Now, after Pettigrew’s death it came out that he’d been a spy for the Light—not a double agent, just someone who snuck around and found things out. He’d been good at that since he was a teenager, even in Hogwarts he had a reputation for finding out all sorts of secrets. So the conspiracy theory is that Pettigrew became an unregistered Animagus while he was still in Hogwarts, an Animagus of something small that could scurry around and listen to conversations. The main problem being that successful Animagi are rare and doing it as a teenager would be really unlikely, so of course the conspiracy theory says that my father and Black were unregistered Animagi too. And in that conspiracy theory, Pettigrew himself killed the twelve bystanders, turned into his small Animagus form, and ran. So Michael Shermer says there are four additional problems with this. One, Black was the only one who knew where my parents were.” (Harry’s voice was a little hard as he said that.) “Two, Black was a more likely suspect to start with than Pettigrew, there’s a rumor Black deliberately tried to get a student killed during his time at Hogwarts, and he was from this really nasty pureblood family, Bellatrix Black was literally his cousin. Three, Black was twenty times the fighting wizard that Pettigrew was, even if he wasn’t as smart. The duel between them would have been like Professor Quirrell versus Professor Sprout. Pettigrew probably didn’t even get a chance to draw his wand, let alone fake all the evidence the conspiracy theory requires. And four, Black was standing in the street \emph{laughing.}”

“But the \emph{rat}—” said Hermione.

“Right,” Harry said. “Well, to make a long story short, Bill Weasley decided that his little brother Percy’s pet rat was Pettigrew’s Animagus form—”

Hermione’s jaw dropped.

“Yes,” Harry said, “you wouldn’t exactly expect Evil Pettigrew to be living a sad and furtive life as the pet rat of an enemy wizarding family, he’d either be with the Malfoys or, more likely, off in the Carribean after a bit of plastic surgery. Anyway, Bill knocks out his little brother Percy, stuns and grabs the rat, sends out all these emergency owl messages—”

“Oh, \emph{no!}” Hermione said, the words torn out of her.

“—and somehow manages to gather Dumbledore, the Minister of Magic, and the Head Auror—”

“He \emph{didn’t!}” said Hermione.

“And of course when they get there they think he’s crazy, but they use \emph{Veritas Oculum} on the rat anyway, just to be sure, and what do they discover?”

She would’ve \emph{died}. “A rat.”

“You win a cookie! So they dragged poor Bill Weasley off to St.~Mungo’s and it turned out to be a pretty standard schizophrenic break, it just happens to some people, especially young men around what we’d consider college age. Guy was convinced he was ninety-seven years old and had died and gone back in time to his younger self via train station. And he responded perfectly well to antipsychotics and is back to normal and everything’s fine now, except people don’t talk as much anymore about Sirius Black conspiracy theories, and you don’t ever ask the Weasleys about the family rat.”

Hermione was giggling helplessly. It was really awful and she shouldn’t be laughing and she was a terrible person.

“The thing I \emph{don’t} understand,” Harry said, after their giggles had died down, “is \emph{why} Black would hunt down Pettigrew instead of running as fast as he could. He had to know the Aurors would be after him. I wonder if they got the reason out of Black before they took him to Azkaban? See, this is why people who are absolutely positively guilty still go through the legal system and get trials.”

Hermione had to agree with that.

Soon Harry was done with his book while Hermione was only halfway through hers—hers was a much more difficult book than Harry’s, but she still felt embarrassed about that. And then she had to put \emph{Magical Mnemonics} back on the shelf and drag herself away, because it was time for her to face the most dreaded class in Hogwarts, \shout{broomstick riding}.

Harry tagged along as she walked there, even though his own class wasn’t until an hour and a half later, like a fighter jet escorting a sad little propeller plane on its way to its own funeral.

The boy wished her goodbye in a quiet, sympathetic voice, and she walked onto the grassy fields of Doom.

And there was much shrieking and almost falling and horrible brushes with death and the ground in completely the \emph{wrong place} and the sun getting in her eyes and Morag buzzing her and Mandy thinking she was being \emph{subtle} about always being near enough to catch her if she fell and she \emph{knew} the other students were laughing at both of them but she never said anything to Mandy because she didn’t actually want to die.

After ten million years the class ended, and she was back on the ground where she belonged until next Thursday. Sometimes she had nightmares about it always being Thursday.

\emph{Why} everyone had to learn this, when they were just going to Apparate or Floo or portkey everywhere once they grew up, was a complete and utter mystery to Hermione. Nobody actually needed to ride broomsticks as an adult, it was like being forced to play dodgeball in P.E.

At least Harry had the decency to be ashamed of being good at it.
\sbreak
It was a couple of hours later, and she was in a Hufflepuff study hall with Hannah, Susan, Leanne, and Megan. Professor Flitwick, surprisingly diffident for a teacher, had asked if she might possibly maybe help those four with their Charms homework for a while, even though they weren’t Ravenclaws, and Hermione had felt so proud she’d almost \emph{burst}.

Hermione took a piece of parchment, spilled a little bit of ink on it, tore it into four pieces, crumpled them, and tossed the pieces on the table.

\emph{She} could have gotten it just from crumpling it, but doing all that made it more like garbage, and that helped when someone was first practicing the Disposal Charm.

Hermione sharpened her ears and eyes, and said, “Okay, try it.”

“\emph{Everto.}”

“\emph{Everto.}”

“\emph{Everto.}”

“\emph{Everto.}”

Hermione didn’t think she’d quite caught all the problems. “Can you all try it again?”

An hour later Hermione had concluded that (1), Leanne and Megan were sort of sloppy, but if you asked them to keep practicing something, they would, (2) Hannah and Susan were focused and driven to the point where you had to keep telling them to \emph{slow down} and \emph{relax} and \emph{think} about things instead of \emph{trying} so hard—it was odd to think that those two would soon be \emph{hers}—and (3) she liked helping Hufflepuffs, the whole study hall had a very cheerful atmosphere.

When she left for dinner, she found the Boy-Who-Lived reading a book while he waited to escort her. It made her feel flattered, and also a little worried because Harry didn’t seem to really talk to \emph{anyone} besides her.

“Did you know there’s a fourth-year girl in Hufflepuff who’s a Metamorphmagus?” said Hermione as they headed toward the Great Hall. “She makes her hair really red, like stopsign red not Weasley red, and when she spilled hot tea on herself she turned into a black-haired boy until she got it under control again.”

“Really? Cool,” said Harry, sounding a bit distracted. “Um, Hermione, just to check, you know tomorrow is the last day to sign up for Professor Quirrell’s armies, right?”

“Yes,” Hermione said. “The armies of the evil Professor Quirrell.” Her voice was a little angry, though Harry didn’t know why, of course.

“Hermione,” Harry said, his voice exasperated, “he’s not evil. He’s a little bit Dark and a whole lot Slytherin. It’s not the same as being \emph{evil}.”

Harry Potter had too many words for things, that was his problem. He would have been better off if he’d just divided the universe into Good and Bad. “Professor Quirrell called me up in front of the whole class and told me to \emph{shoot someone!}”

“He was right,” Harry said, his face sober. “I’m sorry, Hermione, but he was. You should have shot \emph{me,} I wouldn’t have minded. You can’t learn Battle Magic if you can’t practice against real opponents using real spells. And now you’re doing okay in sparring, aren’t you?”

Hermione was only twelve, and so she knew, but she couldn’t put it into words, she couldn’t find the thing to say that would convince Harry.

Professor Quirrell had taken a young girl and called up that girl in front of everyone, and ordered her to open fire without provocation on a classmate.

It didn’t \emph{matter} if Professor Quirrell was right about her needing to learn it.

Professor McGonagall wouldn’t ever have done that.

Professor Flitwick wouldn’t ever have done that.

Maybe not even Professor Snape would have done that.

Professor Quirrell was \shout{evil}.

But she couldn’t find the words, and she knew that Harry would never believe her.

“Hermione, I’ve talked to older students,” Harry said. “Professor Quirrell could be the \emph{only} competent Defense Professor we get in all seven years at Hogwarts. \emph{Anything} else we can learn later. If we want to study Defense, we have to do it \emph{this year.} The students who sign up for the extracurricular stuff are going to be learning huge amounts, way beyond what the Ministry thinks first-years are supposed to study—did you know we’re going to be learning the Patronus Charm? In \emph{January?}”

“The \emph{Patronus Charm?}” Hermione said, her voice going up in surprise.

Her books said that was one of the brightest magics known, a weapon against the Darkest creatures, cast with pure positive emotions. It wasn’t something she’d expect the evil Professor Quirrell to teach—or arrange to be taught, since Hermione couldn’t imagine he could do the spell himself.

“Yes,” Harry said. “Students don’t usually learn the Patronus Charm until their fifth years or even later! But Professor Quirrell says the Ministry schedules were made up by talking Flobberworms, and the ability to cast the Patronus Charm depends on emotions more than magical strength. Professor Quirrell says that he thinks most students do \emph{way} less than they can, and this year he’s going to prove it.”

There was the usual tone of awed worship that Harry’s voice had when he talked about Professor Quirrell, and Hermione gritted her teeth and kept walking.

“I already signed up, actually,” Hermione said, her voice a little quiet. “I did it this morning. For everything, just like you said.”

\emph{In for a penny, in for a pound} was the usual expression.

Besides, she didn’t want to \emph{lose}, and if she wanted to win she had to learn.

“So you \emph{will} be in the armies, then?” Harry’s voice was suddenly enthusiastic. “That’s awesome, Hermione! I’ve already gotten my list of soldiers, but I’m sure Professor Quirrell will let me add one more, or trade—”

“I’m not joining \emph{your} army.” Hermione’s voice was sharp. She knew it was a reasonable assumption but it \emph{still} annoyed her.

Harry blinked. “Not Draco Malfoy’s, surely. So you want to be in the third army? Even though we don’t know who the general \emph{is} yet?” Harry sounded surprised and a little wounded, and she couldn’t blame him, though of course she did blame him, since in fact it was all his fault. “But why not mine?”

“Think about it,” Hermione snapped, “and maybe you’ll work it out!”

And she sped up her stride and left Harry gaping behind her.
\sbreak
“Professor Quirrell,” Draco said in his most formal voice, “I must protest your appointment of Hermione Granger as the third general.”

“Oh?” said Professor Quirrell, leaning back in his chair in a casual and relaxed manner. “Protest away, Mr.~Malfoy.”

“Granger is unfit for the position,” said Draco.

Professor Quirrell tapped a finger on his cheek thoughtfully. “Why yes, yes she is. Do you have any further protests?”

“Professor Quirrell,” said Harry Potter beside him, “with all due respect to Miss Granger’s many outstanding academic talents and the Quirrell points she has justly earned in your classes, her personality is not suited to military command.”

Draco had been relieved when Harry had agreed to accompany him to Professor Quirrell’s office. It wasn’t \emph{just} that Harry was a gigantic blatant teacher’s pet where Professor Quirrell was concerned. Draco had also started to worry that Harry actually \emph{was} friends with Granger, it had been a while now and he \emph{still} hadn’t made his move...\ but this was more like it.

“I agree with Mr.~Potter,” said Draco. “Appointing her as a general turns it into a farce.”

“Harshly put,” said Harry, “but I cannot bring myself to disagree with Mr.~Malfoy. To be blunt, Professor Quirrell, Hermione Granger has around as much intent to kill as a bowl of wet grapes.”

“That,” said Professor Quirrell mildly, “is not a thing I would fail to notice myself. You are telling me nothing I do not already know.”

It was Draco’s turn to say something, but the conversation had suddenly hiccupped. That answer had \emph{not} been in the possibilities he and Harry had brainstormed before coming here. What \emph{did} you say after the teacher said that he knew everything you knew and he was still going to commit an obvious mistake?

The silence stretched.

“Is this some sort of plot?” Harry said slowly.

“Must everything I do be some sort of plot?” said Professor Quirrell. “Can’t I ever create chaos just for the sake of chaos?”

Draco almost choked.

“Not in your Battle Magic class,” Harry said with calm certainty. “Other places, maybe, but not there.”

Professor Quirrell slowly raised his eyebrows.

Harry gazed steadily back at him.

Draco shivered.

“Well then,” Professor Quirrell said. “Neither of you seem to have considered a very simple question. Who could I appoint instead of Miss Granger?”

“Blaise Zabini,” Draco said without hesitation.

“Any other suggestions?” said Professor Quirrell, sounding quite amused.

\emph{Anthony Goldstein and Ernie Macmillan,} came the thought, before Draco’s common sense kicked in and ruled out mudbloods and Hufflepuffs no matter how aggressively they dueled. So instead Draco just said, “What’s wrong with Zabini?”

“I \emph{see}...” Harry said slowly.

“I \emph{don’t,}” said Draco. “Why not Zabini?”

Professor Quirrell looked at Draco. “Because, Mr.~Malfoy, no matter how hard he tries, he’ll never be able to keep up with you or Mr.~Potter.”

The shock of it staggered Draco. “You can’t believe \emph{Granger} is going to—”

“He’s gambling on her,” Harry said quietly. “It’s not guaranteed. The odds aren’t even good. She’ll probably never give us a good fight, and even if she does, it may take her months to learn. But she’s the only one in our year with any chance at all of growing to beat us.”

Draco’s hands twitched but didn’t clench into fists. Showing up as your supporter and then backing out was a classic undermining tactic, so Harry Potter \emph{was} in it with Granger and \emph{that} implied—

“But Professor,” Harry went on smoothly, “I’m worried Hermione will be \emph{miserable} as the general of an army. I’m speaking as her friend now, Professor Quirrell. The competition might be good for Draco and I, but what you’re asking her to do isn’t good for \emph{her!}”

Never mind.

“Your friendship for Hermione Granger does you credit,” Professor Quirrell said dryly. “Especially as you are able to be friends with Draco Malfoy at the same time. Quite a feat, that.”

Harry suddenly looked a little nervous, meaning he probably felt a lot \emph{more} nervous, and Draco silently swore to himself. Of course Harry wasn’t going to fool Professor Quirrell.

“And I doubt Miss Granger would appreciate your friendly concern,” said Professor Quirrell. “She asked me for the position, Mr.~Potter, I did not ask her.”

Harry was quiet at this for a moment. Then he flashed Draco a quick look that mixed apology and warning, saying at the same time, \emph{Sorry, I did my best} and \emph{We’d better not press it any further.}

“As for her being miserable,” Professor Quirrell went on, a slight smile now playing about his lips, “I suspect that she will have a much easier time with the rigors of her position than either of you suspect, and that she will put up a good fight much sooner than you think.”

Harry and Draco both gasped in horror.

“You’re not going to \emph{advise} her, are you?” said Draco, utterly aghast.

“I never signed up to fight \emph{you!}” said Harry.

The smile playing around Professor Quirrell’s lips grew wider. “As a matter of fact, I \emph{did} offer to share a few suggestions regarding Miss Granger’s first battles.”

“\emph{Professor Quirrell!}” said Harry.

“Oh, don’t worry,” Professor Quirrell said. “She turned me down. Just as I expected.”

Draco’s eyes narrowed.

“Dear me, Mr.~Potter,” said Professor Quirrell, “didn’t anyone ever tell you it’s rude to stare?”

“You’re not going to secretly help her some \emph{other} way, are you?” said Harry.

“Would I do that?” said Professor Quirrell.

“Yes,” said Draco and Harry at the same time.

“I am wounded by your lack of trust. Well then, I promise not to help General Granger in any way that the two of you don’t know about. And now I suggest that both of you be about your military affairs. November approaches, and swiftly.”
\sbreak
Draco saw the implications before the door had closed all the way behind them on their way out of Professor Quirrell’s office.

Harry had once spoken dismissively of “people stuff”.

And now that was Draco’s only hope.

Let him not realize, let him not realize...

“We should just attack the Granger girl first and get her out of our way,” said Draco. “After we crush her, we can have our own contest without any distractions.”

“Now that doesn’t really seem fair to her, does it?” said Harry in a mild voice.

“What do \emph{you} care?” said Draco. “She’s your rival, right?” Then, with just the right note of suspicion in his voice, “Don’t tell me you’ve started \emph{really} liking her, after being her rival all this time...”

“Founders forbid,” said Harry. “What can I say, Draco? I merely have a natural sense of justice. Granger does too, you know. She has a very firm grasp on good and evil, and she’s probably going to attack evil first. Having a name like ‘Malfoy’ is just asking for it, you know.”

\shout{Damn it!}

“Harry,” said Draco, sounding wounded and maybe a little superior, “don’t you want to fight \emph{fairly} against me?”

“You mean rather than attacking you after you’ve already lost some of your forces beating Granger?” said Harry. “Oh, I don’t know. Maybe after I get bored with just winning I’ll try that ‘fair’ thing.”

“Maybe she’ll attack \emph{you,}” Draco said. “\emph{You’re} her rival.”

“But I’m her \emph{friendly} rival,” Harry said with an evil grin. “I bought her a nice birthday present and everything. You wouldn’t go around sabotaging your friendly rival like that.”

“What about sabotaging your \emph{friend’s} chance at a fair fight?” said Draco angrily. “I thought we were friends!”

“Let me rephrase that,” said Harry. “\emph{Granger} wouldn’t sabotage a friendly rival. But that’s because she has the killing intention of a bowl of wet grapes. \emph{You} would. You \emph{totally} would. And guess what, so would I.”

\shout{Damn it!}
\sbreak
If it had been a play, there would have been dramatic music.

The hero, impeccably turned out in green-trimmed robes and perfectly combed white-blonde hair, faced the villain.

The villain, leaning back in a simple wooden chair with her buckteeth clearly visible and stray chestnut curls drifting over her cheeks, faced the hero.

It was Wednesday, October 30\Th, and the first battle was coming up on Sunday.

Draco was standing in General Granger’s office, a room the size of a small classroom. (\emph{Why} each general’s office was so large, Draco wasn’t quite sure. A chair and a desk would have worked for him. He wasn’t even clear on why the generals needed offices at all, his soldiers knew where to find him. Unless Professor Quirrell had deliberately arranged the huge offices for them as a sign of status, in which case Draco was all for it.)

Granger sat on the room’s single chair like a throne, all the way on the other end of the office from where the door opened. There was a long oblong table stretched across the middle of the room between them, and four small circular tables scattered around the corners, but only that one single chair, all the way at the opposite end. The room had windows along one wall, and one beam of sunlight touched the top of Granger’s hair like a glowing crown.

It would have been nice if Draco could have walked slowly forward. But there was a table in the way, and Draco had to go around it diagonally, and there was no good way to do that in a dramatic and dignified fashion. Had that been deliberate? If it had been his father, it surely would have been; but this was Granger, so surely not.

There was nowhere for him to sit, and Granger hadn’t stood up, either.

Draco kept the outrage entirely off his face.

“Well, Mr.~Draco Malfoy,” Granger said once he stood before her, “you requested an audience with me and I have been so gracious as to grant it. What was your plea?”

\emph{Come with me to visit Malfoy Manor, my father and I would like to show you some interesting spells.}

“Your rival, Potter, came to me with an offer,” said Draco, putting a serious look on his face. “He doesn’t mind losing to me, but would be humiliated if you won. So he wants to join with me and wipe you out immediately, not just in our first battle, all of them. If I won’t do that, Potter wants me to hold back or harass you, while he launches an all-out attack on you as his first move.”

“I see,” Granger said, looking surprised. “And you’re offering to help me against him?”

“Of course,” said Draco smoothly. “I didn’t think what he wanted to do to you was fair.”

“Why, that’s very nice of you, Mr.~Malfoy,” said Granger. “I’m sorry for how I spoke to you earlier. We should be friends. Can I call you Drakey?”

Alarm bells started to sound in Draco’s head, but there was a \emph{chance} she meant it...

“Of course,” said Draco, “if I can call you Hermy.”

Draco was pretty sure he saw her expression flicker.

“Anyway,” Draco said, “I was thinking it would serve Potter right if we both attacked him and wiped him out.”

“But that wouldn’t be fair to Mr.~Potter, would it?” said Granger.

“I think it’d be very fair,” Draco said. “He was planning to do it to you first.”

Granger was giving him a stern look that could possibly have intimidated him if he’d been a Hufflepuff instead of a Malfoy. “You think I’m pretty stupid, don’t you, Mr.~Malfoy?”

Draco smiled charmingly. “No, Miss Granger, but I thought I’d at least \emph{check.} So, what do you want?”

“Are you offering to \emph{bribe} me?” said Granger.

“Sure,” said Draco. “Can I just slip you a Galleon and have you beat on Potter instead of me for the rest of the year?”

“Nope,” said Granger, “but you can offer me ten Galleons and have me attack both of you equally, instead of just you.”

“Ten Galleons is a lot of money,” Draco said cautiously.

“I didn’t know the Malfoys were poor,” said Granger.

Draco stared at Granger.

He was starting to get a strange feeling about this.

That particular reply didn’t seem like it should have come from this particular girl.

“Well,” said Draco, “you don’t get to be rich by wasting money, you know.”

“I don’t know if you know what a dentist is, Mr.~Malfoy, but my parents are \emph{dentists} and anything less than ten Galleons isn’t worth my time at all.”

“Three Galleons,” Draco said, more as a probe than anything else.

“Nope,” said Granger. “If you want an equal fight at all, I don’t believe that a Malfoy wants an equal fight less than he wants ten Galleons.”

Draco was starting to get a \emph{very} strange feeling about this.

“No,” said Draco.

“No?” said Granger. “This is a limited time offer, Mr.~Malfoy. Are you sure you want to risk a whole year of being miserably crushed by the Boy-Who-Lived? That would be pretty embarrassing for the House of Malfoy, wouldn’t it?”

It was a very persuasive argument, one that was hard to refuse, but you didn’t get to be rich by spending money when your heart told you it was a setup.

“No,” said Draco.

“See you on Sunday,” said Granger.

Draco turned and walked out of the office without another word.

That had been \emph{not right...}
\sbreak
“Hermione,” Harry said patiently, “we’re \emph{supposed} to be plotting against each other. You could even betray me and it wouldn’t mean anything outside the battlefield.”

Hermione shook her head. “It wouldn’t be nice, Harry.”

Harry sighed. “I don’t think you’re getting into the spirit of this at all.”

\emph{It wouldn’t be nice.} She’d actually said that. Hermione didn’t know whether to be insulted at what Harry thought of her, or worried about whether she really \emph{did} sound like that much of a goody-two-shoes usually.

It was probably time to change the subject.

“Anyway, are you doing anything special for tomorrow?” said Hermione. “It’s—”

Her voice cut off abruptly as she realized.

“Yes, Hermione,” Harry said a little tightly, “what day is it?”
\replacement{\sbreak}{}

\subsection{Interlude:}

There was a time when October 31\St had been called Halloween in magical Britain.

Now it was Harry Potter Day.

Harry had turned down all the offers, even the one from Minister Fudge which might have been good for future political favors and which he \emph{really} should have gritted his teeth and taken. But to Harry, October 31\St would always be The Dark Lord Killed My Parents Day. There should have been a quiet, dignified memorial service somewhere, and if there was one, he hadn’t been invited.

Hogwarts got the day off to celebrate. Even the Slytherins didn’t dare wear black outside their own dorm. There were special events and special foods and the teachers looked the other way if anyone ran through the hallways. It was the tenth anniversary, after all.

Harry spent the day in his trunk so as not to spoil it for anyone else, eating snack bars in place of meals, reading some of his sadder science fiction books (no fantasy), and writing a letter to Mum and Dad that was much longer than the ones he usually sent.


