\chapter{Multiple Hypothesis Testing}

%FIXME Find a different formatting solution for the hypotheses

\begin{headlines}

\header{(International news headlines of April 7th, 1992:)}

\label{Toronto Magical Tribune:}

Entire British Wizengamot\\reports seeing ‘Boy-Who-Lived’\\frighten a Dementor

Expert on magical creatures:\\“Now you’re just lying”

France, Germany accuse Britain\\of making the whole thing up

\label{New Zealand Spellcrafter’s Diurnal Notice:}

What drove British legislature insane?\\Could our government be next?

Experts list top 28 reasons\\to believe it’s already happened

\label{American Mage:}

Werewolf clan to become\\First inhabitatnts of Wyoming

\label{The Quibbler:}

Malfoy flees Hogwarts\\As Veela powers awaken

\label{Daily Prophet:}

Legal tricks free\\
“Mad Muggleborn”\\
as Potter threatens Ministry\\
with attack on Azkaban

\end{headlines}
\sbreakit

\subsection{Hypothesis: Voldemort\\(April 8th, 1992, 7:22pm)}

The four of them gathered once more around the ancient desk of the Headmaster of Hogwarts, with its drawers within drawers within drawers, wherein all the past paperwork of the Hogwarts School was stored; legend had it that Headmistress Shehla had once gotten lost in that desk, and was, in fact, still there, and wouldn’t be let out again until she got her files organized. Minerva didn’t particularly look forward to inheriting those drawers, when she inherited that desk someday—if any of them survived.

Albus Dumbledore was seated behind his desk, looking grave and composed.

Severus Snape was standing next to the dead Floo and its ashes, hovering ominously like the vampire that students sometimes accused him of pretending to be.

Mad-Eye Moody had been meant to join them, but was yet to arrive.

And Harry...

A boy’s small, thin frame, perched on the arm of his chair, as though the energies running through him were too great to allow ordinary seating. Set face, sweaty hair, intent green eyes, and within it all, the jagged lightning-bolt of his never-healing scar. He seemed grimmer, now; even compared to a single week earlier.

For a moment Minerva flashed back to her trip to Diagon Alley with Harry, what seemed like ages and ages ago. There’d been this somber boy \emph{inside} that Harry, somehow, even then. This wasn’t entirely her own fault, or Albus’s fault. And yet there was something almost unbearably sad about the contrast between the young boy she’d first met, and what magical Britain had made of him. Harry had never had much of an ordinary childhood, she’d gathered; Harry’s adoptive parents had said to her that he’d spoken little and played less with Muggle children. It was painful to think that Harry might have had only a few months of playing beside the other children in Hogwarts, before the war’s demands had stripped it all away. Maybe there was another face that Harry showed to the children his own age, when he wasn’t staring down the Wizengamot. But she couldn’t stop herself from imagining Harry Potter’s childhood as a heap of firewood, and herself and Albus feeding the wooden branches, piece by piece, into the flames.

“Prophecies are strange things,” said Albus Dumbledore. The old wizard’s eyes were half-lidded, as though in weariness. “Vague, unclear, meaning escaping like water held between loose fingers. Prophecy is ever a burden, for there are no answers there, only questions.”

Harry Potter was sitting tensely. “Headmaster Dumbledore,” said the boy with soft precision, “my friends are being targeted. Hermione Granger almost went to Azkaban. The war has begun, as you put it. Professor Trelawney’s prophecy is key information for weighing up the balance of my hypotheses about what’s going on. Not to mention how silly it is—and \emph{dangerous}—that the Dark Lord knows the prophecy and \emph{I don’t}.”

Albus looked a grim question at her, and she shook her head in reply; in whatever unimaginable way Harry had discovered that Trelawney had made the prophecy and that the Dark Lord knew of it, he hadn’t learned that much from her.

“Voldemort, seeking to avert that very prophecy, went to his defeat at your hands,” the old wizard said then. “His knowledge brought him only harm. Ponder that carefully, Harry Potter.”

“Yes, Headmaster, I do understand that. My home culture also has a literary tradition of self-fulfilling and misinterpreted prophecies. I’ll interpret with caution, rest assured. But I’ve already guessed quite a bit. Is it safer for me to work from partial guesses?”

Time passed.

“Minerva,” said Albus. “If you would.”

“The one...” she began. The words came falteringly to her throat; she was no actress. She couldn’t imitate the deep, chilling tone of the original prophecy; and yet somehow that tone seemed to carry all the \emph{meaning.} “The one with the power to vanquish the Dark Lord approaches... born to those who have thrice defied him, born as the seventh month dies...”

“\emph{And the Dark Lord shall mark him as his equal,}” came Severus’s voice, making her jump within her chair. The Potions Master loomed tall by the fireplace. “\emph{But he shall have power the Dark Lord knows not... and either must destroy all but a remnant of the other, for those two different spirits cannot exist in the same world.}”

That last line Severus spoke with so much foreboding that it chilled her bones; it was almost like listening to Sybill Trelawney.

Harry was listening with a frown. “Can you repeat that?” said Harry.

“\emph{The one with the power to vanquish the Dark Lord approaches, born to those who have thrice defied him, born as the seventh month—}”

“Actually, hold on, can you write that down? I need to analyze this \emph{carefully}—”

This was done, with both Albus and Severus watching the parchment hawklike, as though to make sure that no unseen hand reached in and snatched the precious information away.

“Let’s see...” Harry said. “I’m male and born on July 31st, check. I did in fact vanquish the Dark Lord, check. Ambiguous pronoun in line two... but I wasn’t born yet so it’s hard to see how my parents could have thrice defied \emph{me.} This scar is an obvious candidate for the mark...” Harry touched his forehead. “Then there’s the power the Dark Lord knows not, which probably refers to my scientific background—”

“No,” said Severus.

Harry looked at the Potions Master in surprise.

Severus’s eyes were closed, his face tightened in concentration. “The Dark Lord could obtain that power by studying the same books as you, Potter. But the prophecy did not say, \emph{power the Dark Lord has not.} Nor even, \emph{power the Dark Lord cannot have.} She spoke of \emph{power the Dark Lord knows not}... it will be something stranger to him than Muggle artifacts. Something perhaps that he cannot comprehend at all, even having seen it...”

“Science is not a bag of technological tricks,” Harry said. “It’s not just the Muggle version of a wand. It’s not even knowledge like memorizing the periodic table. It’s a different way of \emph{thinking.}”

“Perhaps...” the Potions Master murmured, but his voice was skeptical.

“It is hazardous,” Albus said, “to read too far into a prophecy, even if you have heard it yourself. They are things of exceeding frustration.”

“So I see,” Harry said. His hand rose up, rubbed the scar on his forehead. “But... okay, if \emph{this} is really all we know... look, I’ll just put it bluntly. How do you \emph{know} that the Dark Lord actually survived?”

“\emph{What?}” she cried. Albus just sighed and leaned back in the vast Headmaster’s chair.

“Well,” Harry said, “imagine how this prophecy sounded back when it was made. You-Know-Who learns the prophecy, and it sounds like I’m destined to grow up and overthrow him. That the two of us are meant to have a final battle where either of us must destroy all but a remnant of the other. So You-Know-Who attacks Godric’s Hollow and \emph{immediately} gets vanquished, leaving behind \emph{some} remnant which may or may not be his disembodied soul. Maybe the Death Eaters are his remnant, or the Dark Mark. This prophecy could already be fulfilled, is what I’m saying. Don’t get me wrong—I do realize that my interpretation sounds stretched. Trelawney’s phrasing doesn’t seem natural for describing \emph{only} the events that historically happened on October 31st, 1981. Attacking a baby and having the spell bounce off, isn’t something you’d normally call ‘the power to vanquish’. But if you think of the prophecy as being about \emph{several} possible futures, only \emph{one} of which was actually realized on Halloween, then the prophecy could already be complete.”

“But—” Minerva blurted. “But the raid on Azkaban—”

“\emph{If} the Dark Lord survived, then sure, he’s the most likely suspect for the Azkaban breakout,” Harry said reasonably. “You could even say that the Azkaban breakout is Bayesian evidence for the Dark Lord surviving, because an Azkaban breakout is more likely to happen in worlds where he’s alive than worlds where he’s dead. But it’s not \emph{strong} Bayesian evidence. It’s not something that \emph{can’t possibly happen} unless the Dark Lord is alive. Professor Quirrell, who \emph{didn’t} start from the assumption that You-Know-Who was still around, had no trouble thinking of his own explanation. To him, it was obvious that some powerful wizard might want Bellatrix Black because she knew a secret of the Dark Lord’s, like some of his magical knowledge that he’d told to only her. The priors against anyone surviving their body’s death are very low, even if it’s magically possible. \emph{Most} times it doesn’t happen. So if it’s \emph{just} the Azkaban breakout... I’d have to say formally that it isn’t enough Bayesian evidence. The improbability of the evidence assuming that the hypothesis is false, is not commensurate with the prior improbability of the hypothesis.”

“No,” Severus said flatly. “The prophecy is not yet fulfilled. I would know if it were.”

“Are you \emph{sure} of that?”

“Yes, Potter. If the prophecy had already come true, I would \emph{understand} it! I heard Trelawney’s words, I remember Trelawney’s voice, and if I knew the events that matched the prophecy, I would \emph{recognize} them. What has already happened... does \emph{not} fit.” The Potions Master spoke with certainty.

“I’m not really sure what to do with that statement,” Harry said. His hand rose up, absently rubbed at his forehead. “Maybe it’s just what you \emph{think} happened that doesn’t fit, and the true history is different...”

“Voldemort \emph{is} alive,” Albus said. “There are other indications.”

“Such as?” Harry’s reply was instant.

Albus paused. “There are terrible rituals by which wizards have returned from death,” Albus said slowly. “That much, anyone can discern within history and legend. And yet those books are missing, I could not find them; it was Voldemort who removed them, I am sure—”

“So you \emph{can’t} find any books on immortality, and that proves that You-Know-Who has them?”

“Indeed,” said Albus. “There is a certain book—I will not name it aloud—missing from the Restricted Section of the Hogwarts library. An ancient scroll which should have been at Borgin and Burkes, with only an empty place on a shelf to show where it was—” The old wizard stopped. “But I suppose,” the old wizard said, as though to himself, “you will say that even if Voldemort tried to make himself immortal, it does not prove that he succeeded...”

Harry sighed. “Proof, Headmaster? There are only ever probabilities. If there are known, particular books on immortality rituals which are missing, that increases the probability that someone attempted one. Which, in turn, raises the prior probability of the Dark Lord surviving his death. This I concede, and thank you for contributing the fact. The question is whether the prior probability goes up \emph{enough.}”

“Surely,” Albus said quietly, “if you concede even a \emph{chance} that Voldemort survived, that is worth guarding against?”

Harry inclined his head. “As you say, Headmaster. Though once a probability drops low enough, it’s also an error to go on obsessing about it... Given that books on immortality are missing, and that this prophecy would sound \emph{somewhat} more natural if it refers to the Dark Lord and I having a future battle, I agree that the Dark Lord being alive is a probability, not just possibility. But other probabilities must \emph{also} be taken into account—and in the probable worlds where You-Know-Who is \emph{not} alive, someone else framed Hermione.”

“Foolishness,” Severus said softly. “Utter foolishness. The Dark Mark has not faded, nor has its master.”

“See, \emph{that’s} what I mean by formally insufficient Bayesian evidence. Sure, it sounds all grim and foreboding and stuff, but is it \emph{that} unlikely for a magical mark to stay around after the maker dies? Suppose the mark is certain to continue while the Dark Lord’s sentience lives on, but \emph{a priori} we’d only have guessed a twenty percent chance of the Dark Mark continuing to exist after the Dark Lord dies. Then the observation, ‘The Dark Mark has not faded’ is five times as likely to occur in worlds where the Dark Lord is alive as in worlds where the Dark Lord is dead. Is that really commensurate with the prior improbability of immortality? Let’s say the prior odds were a hundred-to-one against the Dark Lord surviving. If a hypothesis is a hundred times as likely to be false versus true, and then you see evidence five times more likely if the hypothesis is true versus false, you should update to believing the hypothesis is twenty times as likely to be false as true. Odds of a hundred to one, times a likelihood ratio of one to five, equals odds of twenty to one that the Dark Lord is dead—”

“\emph{Where} are you getting all these numbers, Potter?”

“That \emph{is} the admitted weakness of the method,” Harry said readily. “But what I’m \emph{qualitatively} getting at is why the observation, ‘The Dark Mark has not faded’, is not adequate support for the hypothesis, ‘The Dark Lord is immortal.’ The evidence isn’t as extraordinary as the claim.” Harry paused. “Not to mention that even if the Dark Lord is alive, he doesn’t \emph{have} to be the one who framed Hermione. As a cunning man once said, there could be more than one plotter and more than one plan.”

“Such as the Defense Professor,” Severus said with a thin smile. “I suppose I must agree that he is a suspect. It was the Defense Professor last year, after all; and the year before that, and the year before \emph{that}.”

Harry’s eyes dropped back to the parchment in his lap. “Let’s move on. Are we \emph{certain} that this Prophecy is accurate? Nobody messed with Professor McGonagall’s memory, maybe edited or subtracted a line?”

Albus paused, then spoke slowly. “There is a great spell laid over Britain, recording every prophecy said within our borders. Far beneath the Most Ancient Hall of the Wizengamot, in the Department of Mysteries, they are recorded.”

“The Hall of Prophecy,” Minerva whispered. She’d read about that place, said to be a great room of shelves filled with glowing orbs, one after another appearing over the years. Merlin himself had wrought it, it was said; the greatest wizard’s final slap to the face of Fate. Not all prophecies conduced to the good; and Merlin had wished for at least those spoken of in prophecy, to know what had been spoken \emph{of} them. That was the respect Merlin had given to their free will, that Destiny might not control them from the outside, unwitting. Those mentioned within a prophecy would have an glowing orb float to their hand, and then hear the prophet’s true voice speaking. Others who tried to touch an orb, it was said, would be driven mad—or possibly just have their heads explode, the legends were unclear on this point. Whatever Merlin’s original intention, the Unspeakables hadn’t let anyone enter in centuries, so far as she’d heard. \emph{Works of the Ancient Wizards} had stated that later Unspeakables had discovered that tipping off the subjects of prophecies could interfere with seers releasing whatever temporal pressures they released; and so the heirs of Merlin had sealed his Hall. It did occur to Minerva to wonder (now that she’d spent a few months around Mr.~Potter) how anyone could possibly \emph{know} that; but she also knew better than to ask Albus, in case Albus tried to tell her. Minerva firmly believed that you only ought to worry about Time if you were a clock.

“The Hall of Prophecy,” Albus confirmed lowly. “Those who are spoken of in a prophecy, may listen to that prophecy there. Do you see the implication, Harry?”

Harry frowned. “Well, I could listen to it, or the Dark Lord... oh, my \emph{parents}. Those who had thrice defied him. They were also mentioned in the prophecy, so they could hear the recording?”

“If James and Lily heard anything different from what Minerva reported,” Albus said evenly, “they did not say so to me.”

“You took James and Lily \emph{there?}” Minerva said.

“Fawkes can go to many places,” Albus said. “Do not mention the fact.”

Harry was staring directly at Albus. “Can \emph{I} go to this Department of Mysteries place and hear the recorded prophecy? The original tone of voice might be helpful, from what I’ve heard.”

Light glinted from the reflection of Albus’s half-moon glasses as the old wizard slowly shook his head. “I think that would be unwise,” Albus said. “For reasons beyond the obvious. It is dangerous, that place which Merlin made; more dangerous to some people than others.”

“I see,” Harry said tonelessly, and looked back down at the parchment. “I’ll take the prophecy as assumed accurate for now. The next part says that the Dark Lord has marked me as his equal. Any ideas on what that means exactly?”

“Surely not,” said Albus, “that you must imitate his ways, in any wise.”

“I’m not \emph{dumb,} Headmaster. Muggles have worked out a thing or two about temporal paradoxes, even if it’s all theoretical to them. I won’t throw away my ethics just because a signal from the future claims it’s going to happen, because then that becomes the only reason why it happened in the first place. Still, what \emph{does} it mean?”

“I do not know,” said Severus.

“Nor I,” she said.

Harry took out his wand, turned it over in his hands, gazing meditatively at the wood. “Eleven inches, holly, with a core of phoenix feather,” Harry said. “And the phoenix whose tail feather is in this wand, only ever gave one other, which Mr... what was his name, Olive-something... made into the core of the Dark Lord’s wand. \emph{And} I’m a Parselmouth. It seemed like a lot of coincidence even then. And now I find out there’s a prophecy stating that I’ll be the Dark Lord’s equal.”

Severus’s eyes were thoughtful; the Headmaster’s gaze, unreadable.

“Could it be,” Minerva said falteringly, “that You-Know-Who—that Voldemort—transferred some of his own powers to Mr.~Potter, the night he gave him that scar? Not something he intended to do, surely. Still... I don’t see how Mr.~Potter could be his \emph{equal,} if he had any less magic than the Dark Lord himself...”

“Meh,” said Harry, still looking meditatively at his wand. “I’d fight the Dark Lord without any magic at all, if I had to. \emph{Homo sapiens} didn’t become the dominant species on this planet by having the sharpest claws or hardest armor—though I suppose some of that point may be lost on wizards. Still, it’s beneath my dignity as a human being to be scared of anything that isn’t smarter than I am; and from what I’ve heard, on that particular dimension the Dark Lord wasn’t very scary.”

The Potions Master spoke, his voice taking on some of his customary contemptuous drawl. “You imagine yourself more intelligent than the Dark Lord, Potter?”

“Yes, in fact,” said Harry, pulling back the left sleeve of his robes, and rolling up the shirtsleeve beneath to expose the bare elbow. “Oh, that reminds me! Let’s make sure nobody here has the clearly visible tattoo in the standard, easily checkable location which would mark them as a secret enemy spy.”

Albus made a quieting gesture that halted the Potions Master before he could say anything scathing. “Tell me, Harry,” Albus said, “how would \emph{you} have crafted the Dark Mark?”

“Nonstandard locations,” Harry said promptly, “not easily found without embarrassment and fuss, though of course any security-conscious person would check anyway. Make it smaller, if possible. Overlay another non-magical tattoo to obscure the exact shape—better yet, cover it with a layer of fake skin—”

“Cunning indeed,” Albus said. “But tell me, suppose you could craft any conditions you wished into the Mark, fading it or raising it as you wished. What would you do then?”

“Make it completely invisible at all times,” Harry said in tones of stating the obvious. “You don’t want there to be any detectable difference between a spy and a non-spy.”

“Suppose you are more cunning still,” Albus said. “You are a master of trickery, a master of deception, and you employ your abilities to the fullest.”

“Well—” The boy stopped, frowning. “It seems unnecessarily complicated, more like a tactic a villain would use in a role-playing game than something you’d try in a real-life war. But I suppose you could put fake Dark Marks on people who aren’t really Death Eaters, and keep the Dark Marks on the real Death Eaters invisible. But then there’s the question of why people would start believing in the first place that the Dark Mark identified a Death Eater... I’d have to think about it for at least five minutes, if I were going to take the problem seriously.”

“I ask you this,” Albus said, still in that mild tone, “because I did indeed, in the early days of the war, perform such tests as you suggested. The Order survived my folly only because Alastor did not trust in the bare arms we saw. I had thought, afterward, that the bearers of the Mark might hide it or show it at their will. And yet when we hied Igor Karkaroff before the Wizengamot, that Mark showed clear on his arm, for all that Karkaroff wished to protest his innocence. What true rule may govern the Dark Mark, I do not know. Even Severus is still bound by his Mark not to reveal its secrets to any who do not know them.”

“Oh, well \emph{that} makes it \emph{obvious},” Harry said promptly. “Wait, hold on—you were a \emph{Death Eater?}” Harry transferred his stare to Severus.

Severus returned a thin smile. “I still am, so far as they know.”

“Harry,” said Albus, eyes only for the boy. “What do you mean, that makes it obvious?”

“Information theory 101,” the boy said in a lecturing tone. “Observing variable X conveys information about variable Y, if and only if the possible values of X have different probabilities given different states of Y. The instant you hear about anything whatsoever that varies between a spy and a nonspy, you should immediately think of exploiting it to distinguish spies from nonspies. Similarly, to distinguish reality from lies, you need a process which behaves differently in the presence of truth and falsehood—that’s why ‘faith’ doesn’t work as a discriminant, while ‘make experimental predictions and test them’ does. You say someone with the Dark Mark can’t reveal its secrets to anyone who doesn’t already know them. So to find out how the Dark Mark operates, write down every way you can imagine the Dark Mark \emph{might} work, then watch Professor Snape try to tell each of those things to a confederate—maybe one who doesn’t know what the experiment is about—I’ll explain binary search later so that you can play Twenty Questions to narrow things down—and whatever he \emph{can’t} say out loud is true. His silence would be something that behaves differently in the presence of true statements about the Mark, versus false statements, you see.”

Minerva’s mouth was hanging open, she realized; and she closed it abruptly. Even Albus looked surprised.

“And after that, like I said, \emph{any} behavioral difference between spies and nonspies can be used to identify spies. Once you’ve identified at least one magically censored secret of the Dark Mark, you can test someone for the Dark Mark by seeing if they can reveal that secret to somebody who doesn’t already know it—”

\emph{“Thank you, Mr.~Potter.”}

Everyone looked at Severus. The Potions Master was straightening, his teeth bared in a grimace of angry triumph. “Headmaster, I can now speak freely of the Mark. If we know we are caught for a Death Eater, before others who have not yet seen our bare arms, our Mark reveals itself whether we will it or no. But if they have already seen our arms bare, it does not reveal itself; nor if we are only being tested from suspicion. Thus the Dark Mark seems to identify Death Eaters—but only those already found, you perceive.”

“Ah...” Albus said. “Thank you, Severus.” He closed his eyes briefly. “That would indeed explain why Black escaped even Peter’s notice... ah, well. And Harry’s proposed test?”

The Potions Master shook his head. “The Dark Lord was no fool, despite Potter’s delusions. The moment such a test is suspected, the Mark ceases to bind our tongues. Yet I could not hint at the possibility, but only wait for another to deduce it.” Another thin smile. “I would award you a good many House points, Mr.~Potter, if it would not compromise my cover. But as you can see, the Dark Lord was quite cunning.” His gaze grew more distant. “Oh,” Severus breathed, “he was \emph{very} cunning indeed...”

Harry Potter sat still for a long moment.

Then—

“No,” Harry said. The boy shook his head. “No, that can’t \emph{actually} be true. First of all, we’re talking about the kind of logic puzzle that would appear in chapter \emph{one} of a Raymond Smullyan book, nowhere \emph{near} the level of what Muggle scientists do for a living. And second, for all I know, it took the Dark Lord five months of thinking to invent the puzzle I just solved in five seconds—”

“Is it \emph{that} inconceivable to you, Potter, that anyone could be so intelligent as yourself?” The Potions Master’s voice held more curiosity than scorn.

“It’s called a base rate, Professor Snape. The evidence is equally compatible with the Dark Lord inventing that puzzle over the course of five months or over the course of five seconds, but in any given population there’ll be many more people who can do it in five months than in five seconds...” Harry pasted a hand against his forehead. “Darn it, how can I explain this? I suppose, from your perspective, the Dark Lord came up with a clever puzzle and I cleverly solved it and that makes us look \emph{equal}.”

“I remember your first day of Potions class,” the Potions Master said dryly. “I think you have a ways still to go.”

“Peace, Severus,” Albus said. “Harry has already accomplished more than you know. Yet tell me, Harry—why \emph{do} you believe the Dark Lord is less than you? Surely he is a damaged soul in many ways. But cunning for cunning—you are not yet ready to face him, I would judge; and I know the full tally of your deeds.”
\sbreak

The frustrating thing about this conversation was that Harry \emph{couldn’t say his actual reasons for disagreeing,} which violated several basic principles of cooperative discourse.

He couldn’t explain how Bellatrix had really been removed from Azkaban—not by You-Know-Who in any guise, but by the combined wits of Harry and Professor Quirrell.

Harry didn’t want to say in front of Professor McGonagall that the existence of brain damage implied that there were no such things as souls. Which made a successful immortality ritual... well, not \emph{impossible,} Harry certainly intended to forge a road to magical immortality \emph{someday}, but it would be a \emph{lot harder} and require \emph{much more ingenuity} than just binding an already-existent soul to a lich’s phylactery. Which no intelligent wizard would bother doing in the first place, if they knew their souls were immortal.

And the true and honest reason Harry knew the Dark Lord couldn’t have been \emph{that} smart... well... there wasn’t any tactful way to say it, but...

Harry had \emph{been} to a convocation of the Wizengamot. He’d \emph{seen} the laughable ‘security precautions’, if you could call them that, guarding the deepest levels of the Ministry of Magic. They didn’t even have the Thief’s Downfall which goblins used to wash away Polyjuice and Imperius Curses on people entering Gringotts. The obvious takeover route would be to Imperius the Minister of Magic and a few department heads, and owl a hand grenade to anyone too powerful to Imperius. Or owl them knockout gas, if you needed them alive and in a state of Living Death to take hairs for Polyjuice potions. Legilimency, False Memories, the Confundus Charm—it was ridiculous, the magical world was \emph{supersaturated} with ways to cheat. Harry might not do any of those things himself, during his own takeover of Britain, since he was constrained by Ethics... well, Harry \emph{might} do some of the lesser ones, since Polyjuice or a temporary Confundus or read-only Legilimency all sounded better than an extra day of Azkaban... but...

If Harry hadn’t been constrained by Ethics, it was possible he could’ve wiped out the eviller sections of the Wizengamot that day; all by himself, using only a first-year’s magical power, on account of being clever enough to figure out Dementors. Though Harry might not have been in such a great political position after that, the surviving Wizengamot members might’ve found it easy and cheap to disavow his actions for P.R. purposes and condemn him, even if the smarter ones realized it was for the greater good... but \emph{still.}

If you were completely unrestrained by ethics, armed with the ancient secrets of Salazar Slytherin, had dozens of powerful followers including Lucius Malfoy, and it took you more than ten years to \emph{fail} to overthrow the government of magical Britain, it meant you were stupid.

“How can I put this...” Harry said. “Look, Headmaster, you’ve got ethics, there’s a lot of battle tactics you don’t use because you’re not evil. And you fought the Dark Lord, a tremendously powerful wizard who wasn’t so restrained, and you held him off \emph{anyway}. If You-Know-Who had been super-smart \emph{on top of that}, you’d be \emph{dead.} \emph{All} of you. You’d have died \emph{instantly—}”

“Harry,” Professor McGonagall said. Her voice was faltering. “Harry, we almost \emph{did} all die. More than half the Order of the Phoenix died. If not for Albus—Albus Dumbledore, the greatest wizard in two centuries, Harry—we surely would have perished.”

Harry passed a hand across his forehead. “I’m sorry,” Harry said. “I’m not trying to minimize what you went through. I know that You-Know-Who was a completely evil, incredibly powerful Dark Wizard with dozens of powerful followers, and that’s... bad, yes, definitely bad. It’s just...” \emph{All that isn’t on remotely the same threat scale as the enemy being smart, in which case they Transfigure botulinum toxin and sneak a millionth of a gram into your teacup.} Was there any safe way to convey that concept without citing specifics? Harry couldn’t think of one.

“Please, Harry,” said Professor McGonagall. “Please, Harry, I beg you—\emph{take the Dark Lord seriously!} He is more dangerous than—” The senior witch seemed to be having trouble finding words. “He is \emph{far} more dangerous than Transfiguration.”

Harry’s eyebrows went up before he could stop himself. A dark chuckle came from Severus Snape’s direction.

\emph{Um,} said the voice of Ravenclaw within him. \emph{Um, honestly Professor McGonagall is right, we’re not taking this as seriously as we’d take a scientific problem. The difficult thing is to react} at all \emph{to new information, instead of just flushing it out the window. Right now it looks like we didn’t shift belief} at all \emph{after encountering an unexpected, important argument. Our dismissal of Lord Voldemort as a serious threat} was \emph{originally based on the Dark Mark being blatantly stupid. It would require a focused effort to de-update and suspect the whole garden-path of reasoning we went down based on that false assumption, and we’re} not \emph{putting in that effort right now.}

“All right,” Harry said, just as Professor McGonagall seemed to be about to speak again. “All right, to take this seriously, I need to stop and think for five minutes.”

“Please do,” said Albus Dumbledore.

Harry closed his eyes.

His Ravenclaw side divided into three.

\emph{Probability estimate,} said Ravenclaw One, who was acting as moderator. \emph{That the Dark Lord is alive, and as smart as we are, and hence a genuine threat.}

\emph{Why aren’t all his enemies already dead?} said Ravenclaw Two, who was prosecuting.

\emph{Note,} said Ravenclaw One, \emph{we had already thought of that argument so we can’t use it to shift belief} again \emph{each time we rehearse it.}

\emph{But what’s the actual flaw in the logic?} said Ravenclaw Two. \emph{In worlds with a smart Lord Voldemort, everyone in the Order of the Phoenix died in the first five minutes of the war. The world doesn’t look like that, so we don’t live in that world. QED.}

\emph{Is that really certain?} asked Ravenclaw Three, who’d been appointed as the defender. \emph{Maybe there was some reason Lord Voldemort} wasn’t \emph{fighting all-out back then—}

\emph{Like what?} demanded Ravenclaw Two. \emph{Furthermore, whatever your excuse, I demand that the probability of your hypothesis be penalized in accordance with its added complexity—}

\emph{Let Three talk,} said Ravenclaw One.

\emph{Okay... look,} said Ravenclaw Three. \emph{First of all, we don’t} know \emph{that anyone can take over the Ministry just with mind control. Maybe magical Britain is really an oligarchy and you need enough military power to intimidate the family heads into submission—}

\emph{Imperius them too,} interjected Ravenclaw Two.

\emph{—and the oligarchs have Thief’s Downfall in the entrances to} their \emph{homes—}

\emph{Complexity penalty!} cried Ravenclaw Two. \emph{More epicycles!}

\emph{—oh, be reasonable,} said Ravenclaw Three. \emph{We haven’t actually} seen \emph{anyone taking over the Ministry with a couple of well-placed Imperius curses. We don’t} know \emph{that it can actually be done that easily.}

\emph{But,} said Ravenclaw Two, \emph{even taking that into account... it really seems like there should’ve been} some \emph{other way. Ten years of failure, really? Using only conventional terrorist tactics? That’s just... not even} trying.

\emph{Maybe Lord Voldemort did have more creative ideas,} replied Ravenclaw Three, \emph{but he didn’t want to tip his hand to} other \emph{countries’ governments, didn’t want} them \emph{to know how vulnerable they were and install Thief’s Downfall in} their \emph{Ministries. Not until he had Britain as a base and enough servants to subvert} all \emph{the other major governments simultaneously.}

\emph{You’re assuming he wants to conquer the whole world,} noted Ravenclaw Two.

\emph{Trelawney prophesized that he would be our equal,} intoned Ravenclaw Three solemnly. \emph{Therefore, he wanted to take over the world.}

\emph{And if he is your equal, and you do have to fight him—}

For an instant, Harry’s mind tried to imagine the specter of two \emph{creative} wizards fighting an all-out-war against each other.

Harry had noted all the Charms and Potions in his first-year books that could be creatively used to kill people. He hadn’t been able to help himself. Literally. He’d \emph{tried} to stop his brain from doing it each time, but it was like looking at a fish and trying to stop your brain from noticing it was a fish. What someone could creatively do with seventh-year, or Auror-level, or ancient lost magic such as Lord Voldemort had possessed... didn’t bear thinking about. A magically-superpowered creative-genius psychopath wasn’t a ‘threat’, it was an extinction event.

Then Harry shook his head, dismissing the gloomy line his reasoning had been going down. The question was whether there was a significant probability of facing anything so terrible as a Dark Rationalist in the first place.

\emph{Prior odds that someone attempting an immortality ritual would actually have it work...}

Call it one to a thousand, at a generous overestimate; it was not the case that roughly one wizard in a thousand survived their death. Though, admittedly Harry didn’t have data on how many had attempted immortality rituals first.

\emph{What if the Dark Lord} is \emph{as smart as us?} said Ravenclaw Three. \emph{You know, the way Trelawney prophesied him being our} equal. \emph{Then he would} make \emph{his immortality ritual work.} \emph{P.S., don’t forget that ‘destroy all but a remnant of the other’ line.}

Requiring that level of intelligence was an additional burdensome detail; prior odds of a random population member being that intelligent were low...

But Lord Voldemort wasn’t a randomly selected wizard, he was one particular wizard in the population who’d come to everyone’s attention. The puzzle of the Mark implied a certain minimum level of intelligence, even if (hypothetically) the Dark Lord had taken longer to think it through. Then again, in the Muggle world, all of the extremely intelligent people Harry knew about from history had \emph{not} become evil dictators or terrorists. The closest thing to that in the Muggle world was hedge-fund managers, and none of \emph{them} had tried to take over so much as a third-world country, a point which put upper bounds on both their possible evil and possible goodness.

There were hypotheses where the Dark Lord was smart and the Order of the Phoenix \emph{didn’t} just instantly die, but those hypotheses were more complicated and ought to get complexity penalties. After the complexity penalties of the further excuses were factored in, there would be a large likelihood ratio from the hypotheses ‘The Dark Lord is smart’ versus ‘The Dark Lord was stupid’ to the observation, ‘The Dark Lord did not instantly win the war’. That was probably worth a 10:1 likelihood ratio in favor of the Dark Lord being stupid... but maybe not 100:1. You couldn’t actually say that ‘The Dark Lord instantly wins’ had a probability of \emph{more} than 99 percent, assuming the Dark Lord started out smart; the sum over all possible excuses would be more than .01.

And then there was the Prophecy... which might or might not have \emph{originally} included a line about how Lord Voldemort would \emph{immediately} die if he confronted the Potters. Which Albus Dumbledore had then edited in Professor McGonagall’s memory, in order to lure Lord Voldemort to his doom. If there \emph{was} no such line, the Prophecy did sound \emph{somewhat} more like You-Know-Who and the Boy-Who-Lived were destined to have some later confrontation. But in \emph{that} case, it was less likely that Dumbledore would’ve come up with a plausible-sounding excuse not to take Harry to the Hall of Prophecy...

Harry was wondering if he could even \emph{get} a Bayesian calculation out of this. Of course, the point of a subjective Bayesian calculation wasn’t that, after you made up a bunch of numbers, multiplying them out would give you an exactly right answer. The real point was that the \emph{process} of making up numbers would force you to tally all the relevant facts and weigh all the relative probabilities. Like realizing, as soon as you actually \emph{thought} about the probability of the Dark Mark not-fading \emph{if} You-Know-Who \emph{was} dead, that the probability wasn’t low enough for the observation to count as strong evidence. One version of the process was to tally hypotheses and list out evidence, make up all the numbers, do the calculation, and then throw out the final answer and go with your brain’s gut feeling \emph{after} you’d forced it to really \emph{weigh} everything. The trouble was that the items of evidence weren’t conditionally independent, and there were multiple interacting background facts of interest...

...well, \emph{one} thing at least was certain.

If the calculation could be done at all, it was going to take a piece of paper and a pencil.

In the fireplace at one side of the Headmaster’s office, the flames suddenly flared up, turning from orange to bright billious green.

“Ah!” said Professor McGonagall into the uncomfortable non-silence. “That would be Mad-Eye Moody, I suppose.”

“Let this matter bide for now,” the Headmaster said in some relief, as he too turned to regard the Floo. “I believe we are about to receive some news regarding it, as well.”
\sbreak

\subsection{Hypothesis: Hermione Granger\\(April 8th, 1992, 6:53pm)}

Meanwhile in the Great Hall of Hogwarts, as the students who didn’t have secret meetings with the Headmaster bustled about their dinner around four huge tables—

“It’s funny,” Dean Thomas said thoughtfully. “I didn’t believe the General when he said that what we learned would change us forever, and we’d never be able to return to a normal life afterward. Once we knew. Once we saw what \emph{he} could see.”

“I know!” said Seamus Finnigan. “I thought it was just a joke too! Like, you know, everything else General Chaos ever said ever.”

“But now—” Dean said sadly. “We \emph{can’t} go back, can we? It’d be like going back to a Muggle school after having been to Hogwarts. We’ve just... we’ve just got to stay around each other. That’s all we can do, or we’ll go crazy.”

Seamus Finnigan, next to him, just nodded wordlessly and ate another bite of veldbeest.

Around them, the conversation at the Gryffindor table continued. It wasn’t as \emph{relentless} as it’d been yesterday, but now and then the topic wandered back.

“Well, there must’ve been \emph{some} sort of love triangle,” said a second-year witch named Samantha Crowley (she never answered when asked if there was any relation). “The question is, which ways was it \emph{going} before it all went wrong? Who was in love with who—and whether or not that person loved them back—I don’t know \emph{how} many possibilities there are—”

“Sixty-four,” said Sarah Varyabil, a blossoming beauty who probably should’ve been Sorted into Ravenclaw or Hufflepuff instead. “No, wait, that’s wrong. I mean, if nobody loved Malfoy and Malfoy didn’t love anyone then he wouldn’t really be part of the love triangle... this is going to take Arithmancy, could you all wait two minutes?”

“It’s so \emph{sad,}” said Sherice Ngaserin, who actually had tears in her eyes. “They were just—they were just so \emph{obviously} meant to be together!”

“You mean Potter and Malfoy?” said a second-year named Colleen Johnson. “I know—their families hated each other so much, there’s no way they \emph{couldn’t} fall in love—”

“No, I mean all three of them,” said Sherice.

This produced a brief pause in the huddled conversation. Dean Thomas was quietly choking on his lemonade, trying not to make any sounds as it trickled out of his mouth and soaked into his shirt.

“\emph{Wow,}” said a dark-haired witch by the name of Nancy Hua. “That’s really... \emph{sophisticated} of you, Sherice.”

“Look, you all, we need to keep this realistic,” said Eloise Rosen, a tall witch who’d been General of an army and hence spoke with an air of authority. “We \emph{know}—because she kissed him—that Granger was in love with Potter. So the only reason she’d try to kill Malfoy is if she knew that she was losing Potter to him. There’s no need to make it all sound so complicated—you’re all acting like this is a play instead of real life!”

“But even if Granger was in love, it’s still funny that she’d just \emph{snap} like that,” said Chloe, whose black robes combined with her night-black skin to make her look like a darkened silhouette. “I don’t know... I think maybe there’s more to this than just a romance novel gone wrong. I think maybe most people haven’t got any idea at all what’s going on.”

“\emph{Yes! Thank you!}” burst out Dean Thomas. “Look—don’t you realize—like Harry Potter \emph{told} us all—if you didn’t \emph{predict} that something would happen, if it took you completely by surprise, then what you believed about the world when you \emph{didn’t} see it coming, isn’t enough to explain...” Dean’s voice trailed off, as he saw that nobody was listening. “It’s \emph{completely hopeless,} isn’t it?”

“You hadn’t figured that out yet?” said Lavender Brown, who was sitting across the table from her two fellow former Chaotics. “How’d you ever make Lieutenant?”

“Oh, you two be quiet!” Sherice snapped at them. “It’s obvious you both want the three of them for yourselves!”

“I mean it!” Chloe said. “What if what’s \emph{really} going on is different from all the, you know, \emph{normal} things that all the \emph{ordinary} people are talking about? What if somebody—\emph{made} Granger do what she did, just like Potter was trying to tell everyone?”

“I think Chloe’s right,” said a foreign-looking boy wizard who always introduced himself as ‘Adrian Turnipseed’, though his parents had actually named him Mad Drongo. “I think this whole time there’s been...” Adrian lowered his voice ominously, “...a \emph{hidden hand}...” Adrian raised his voice again, “shaping all that’s happened. One person who’s been behind \emph{everything,} from the beginning. And I don’t mean Professor Snape, either.”

“You don’t mean—” gasped Sarah.

“Yes,” Adrian said. “The \emph{real} one behind it all is—\emph{Tracey Davis!}”

“That’s what I think too,” Chloe said. “After all—” She glanced around rapidly. “Ever since that thing with the bullies and the ceiling—even the trees in the forests around Hogwarts look like they’re \emph{shaking,} like they’re \emph{afraid—}”

Seamus Finnigan was frowning thoughtfully. “I think I see where Harry gets his... \emph{you know...} from,” Seamus said, lowering his voice so that only Lavender and Dean could hear.

“Oh, I totally know what you mean,” Lavender said. She didn’t bother to lower her own voice. “It’s a wonder he didn’t crack and just start killing everyone \emph{ages} ago.”

“Personally,” Dean said, also in a quieter voice, “I’d say the really scary part is—that could’ve been \emph{us.}”

“Yeah,” said Lavender. “It’s a good thing \emph{we’re} all perfectly sane now.”

Dean and Seamus nodded solemnly.
\sbreak

\subsection{Hypothesis: G.L.\\(April 8th, 1992, 8:08pm)}

The Floo-Fire of the Headmaster’s office blazed a bright pale-green, the fire concentrating in on itself into a spinning emeraldine whirlwind, and then flared even brighter and spit a human figure into the air—

There was a blur of motion as the resolving figure snapped up a wand, smoothly spinning with the Floo’s momentum like a ballet dance step, so that his firing arc covered the entire 360-degree arc of the room; and then just as abruptly, the figure stopped in place.

In the first instant that Harry saw that man, before Harry even took in the eye, he noticed the scars on the hands, the scars on the face, like the man had been burned and cut over his entire body; though only the man’s hands and face were visible, of all his flesh. The rest of the man’s body was hidden, encased not in robes, but in leather that looked more like armor than clothing; dark gray leather, matching the man’s mess of grayed hair.

The next thing that Harry’s vision comprehended was the brilliant blue eye occupying the right side of the man’s face.

One part of Harry’s mind realized that the person whom Professor McGonagall had named ‘Mad-Eye Moody’ was the same as the one Dumbledore had called ‘Alastor’, within the memory Dumbledore had shown Harry; an image from before whatever event had scarred every inch of the man’s body and taken a chunk out of his nose—

And another part of his mind noticed the jolt of adrenaline. Harry had drawn his wand in sheer reflex when the man had spun out of the Floo like that, there’d been something about it that felt like \emph{ambush,} Harry’s hand had already started to level his wand for a \emph{Somnium} before he’d managed to stop himself. Even now the armored man was holding his wand level, not pointed at any particular person but covering the whole room, and that wand was already in perfect line with his eyes, like a soldier sighting down a gun. There was danger in the man’s stance and the set of his boots, danger in the leather armor he wore and danger in that brilliant blue eye.

When the scarred man spoke, addressing the Headmaster, his voice was edged. “I suppose you think this room is secure?”

“There are only friends here,” Dumbledore said.

The man’s head jerked toward Harry. “That include \emph{him?}”

“If Harry Potter is not our friend,” Dumbledore said gravely, “then we are all certainly doomed; so we may as well assume that he is.”

The man’s wand stayed level, not quite pointing at Harry. “Boy almost drew on me just then.”

“Er...” Harry said. He noticed that his hand was still tightly holding the wand, and consciously relaxed his hand and dropped it back to his side. “Sorry about that, you looked a bit... combat-ready.”

The scarred man’s wand moved slightly away from where it had almost pointed at Harry, though it didn’t lower, and the man let out a short bark of laughter. “Constant vigilance, eh, lad?” said the man.

“It’s not paranoia if they really are out to get you,” Harry recited the proverb.

The man turned fully toward Harry; and insofar as Harry could read any expression on the scarred face, the man now looked \emph{interested}.

Dumbledore’s eyes had regained some of the brilliant twinkle that they’d had before the Azkaban breakout, a smile beneath his silver mustache as though that smile had never left. “Harry, this is Alastor Moody, called also Mad-Eye, who will command the Order of the Phoenix after me—if anything should happen to me, that is. Alastor, this is Harry Potter. I have every hope the two of you shall get along \emph{fantastically}.”

“I’ve heard a good deal about you, boy,” said Mad-Eye Moody. His one dark natural eye stayed fixed on Harry, while the point of brilliant blue spun frantically, seeming to rotate all the way around within its socket. “Not all of it good. Heard they’re calling you the Dementor Spooker, in the Department.”

After some consideration, Harry decided to reply with a knowing smile.

“How’d you pull off that one, boy?” the man said softly. Now his blue eye was fixed on Harry as well. “I had a little chat with one of the Aurors who escorted the Dementor there from Azkaban. Beth Martin said it came straight from the pit, and no-one gave it any special instructions along the way. Of course, she could be lying.”

“There wasn’t any sneaky trick to that one,” Harry said. “I just did it the hard way. Of course, I could also be lying.”

Dumbledore was leaning back in his chair, chuckling in the background, like he was just another device in the Headmaster’s Office and that was the sound he made.

The scarred man turned back to face the Headmaster, though his wand stayed pointed low and in Harry’s general direction. When he spoke his voice was gruff and businesslike. “I have a lead on a recent host of Voldie’s. You’re certain his shade is in Hogwarts now?”

“Not \emph{certain}—” Dumbledore began.

“Say \emph{what?}” Harry interrupted. After having nearly concluded that the Dark Lord didn’t exist, it was a shock to hear it being discussed that matter-of-factly.

“Voldie’s host,” Moody said shortly. “The one he possessed before he took over Granger.”

“If the tales speak true,” Dumbledore said, “there is some device of power which binds Voldemort’s shade to this world; and by that means he may bargain with a host for possession of their body, conferring on them some portion of his power and his pride—”

“So the obvious question is who’s gained too much power too quickly,” Moody said abruptly. “And it turns out that there’s a fellow who’s gone and banished the Bandon Banshee, staked an entire rogue vampire clan in Asia, tracked down the Wagga-Wagga Werewolf, and exterminated a pack of ghouls using a tea-strainer. \emph{And} he’s milking it for all it’s worth; there’s been talk of the Order of Merlin. Seems to have turned into a charmer and a politician, not just a powerful wizard.”

“Dear me,” murmured Dumbledore. “Are you certain that he is not relying on his own skills?”

“Checked his grades,” Moody said. “Record shows Gilderoy Lockhart received a Troll in his Defense O.W.L.S., didn’t bother with the N.E.W.T. Just the sort of sucker to take the deal Voldie was offering.” The blue eye whirled crazily within its socket. “Unless you remember Lockhart as a student, and think he had enough potential to do all that by himself?”

“No,” said Professor McGonagall. She frowned. “Not a chance, I should say.”

“I fear I must agree,” Dumbledore said with an undertone of pain. “Ah, Gilderoy, you poor fool...”

Moody’s grin was more like a snarl. “Three in the morning work for you, Albus? Lockhart should be at his home tonight.”

Harry listened to this with increasing alarm, wondering if even the \emph{Ministry} had any rules about magistrates needing to issue warrants—never mind the illegal vigilante organization Harry now seemed to have joined. “Excuse me,” Harry said. “What \emph{exactly} happens at three in the morning?”

There must have been something in Harry’s voice that gave him away, because the scarred man whirled on him. “You have a problem with that, boy?”

Harry paused, trying to figure out how to phrase this to the stranger—

“You want to take him down yourself?” pressed the scarred man. “Get revenge for your parents, eh?”

“No,” Harry said as politely he could. “Honestly—look, if we knew for \emph{certain} he was a willing host for You-Know-Who, that’s one thing, but if we’re \emph{not} sure and you’re heading off to kill him—”

“Kill?” Mad-Eye Moody snorted. “It’s what’s locked up in his head,” Moody tapped his forehead, “that we need from him, boy. If we’re lucky, Voldie can’t wipe the sucker’s memories as easy as in his living days, and Lockhart will remember what the horcrux looked like.”

Harry mentally noted down the word \emph{horcrux} for future research, and said, “I’m just worried that someone innocent—what sounds like a pretty decent person, if he \emph{did} do all that himself—might be about to get hurt.”

“Aurors hurt people,” the scarred man said shortly. “Bad people, if you’re lucky. Some days you won’t be lucky, and that’s all there is to it. Just remember, Dark Wizards hurt a lot more people than we do.”

Harry took a deep breath. “Can you at least \emph{try} not to hurt this person, in case he’s \emph{not—}”

“What is a first-year doing in this room, Albus?” demanded the scarred man, now whirling to face the Headmaster. “And don’t tell me it’s for what he did when he was a baby.”

“Harry Potter is not an ordinary first-year,” the Headmaster said quietly. “He has already accomplished feats impossible enough to shock even me, Alastor. His is the only intellect in the Order which might someday match that of Voldemort himself, as you or I never could.”

The scarred man leaned over the Headmaster’s desk. “He’s a liability. Naive. Doesn’t know a bloody thing about what war’s like. I want him out of here and all his memories of the Order wiped before one of Voldie’s servants plucks them straight out of his mind—”

“I’m an Occlumens, actually.”

Mad-Eye Moody directed a narrow look at the Headmaster, who nodded.

And then the scarred man turned to face Harry, their gazes meeting.

The sudden fury of the Legilimency attack almost made Harry fall off his chair, as a blade of white-hot steel cut into the imaginary person at the forefront of his mind. Harry hadn’t had a chance to practice since Mr.~Bester’s training, and Harry very nearly lost his grip on the imaginary person the back-of-his-mind was pretending to be, as that person’s world turned into searing lava and a furious probe of questions. Harry almost lost his grip on only \emph{pretending} to hallucinate, only \emph{pretending} to be the imaginary person that was screaming in shock and pain as the Legilimency tore apart his sanity and reshaped him to believe that he was on fire—

Harry managed to break eye contact, dropping his eyes to Moody’s chin.

“You’re out of practice, boy,” Moody said. Harry wasn’t looking at the man’s face, but his voice was deadly grim. “And I’ll warn you of this but once. Voldie isn’t like any other Legilimens in recorded history. He doesn’t need to look you in the eyes, and if your shields are that rusty he’d creep in so softly you’d never notice a thing.”

“Duly noted,” Harry said to the scarred chin. Harry was more shaken than he’d have admitted; Mr.~Bester hadn’t been anywhere near that powerful, and had never tested Harry like \emph{that}. Pretending to be someone hurting that much had... Harry couldn’t find words for describing what it felt like to contain an imaginary person in that much pain, but it hadn’t been \emph{normal}. “Do I get any credit for being an Occlumens in the first place?”

“So you’re think you’re all grown up already, eh? Look me in the eyes!”

Harry strengthened his shields, and looked once more into the dark grey eye and the brilliant blue.

“Ever watched someone die?” asked Mad-Eye Moody.

“My parents,” Harry said evenly. “I recovered the memory in January when I went in front of a Dementor to learn the Patronus Charm. I remember You-Know-Who’s voice—” A chill went through Harry’s body, his wand twitching in his hand. “My main tactical report is that You-Know-Who could speak the Killing Curse in less than half a second, but you probably already knew that.”

There was a gasp from Professor McGonagall’s direction, and Severus’s face had tightened.

“All right,” Mad-Eye Moody said softly. A strange, thin grin twisted up the lips within the scarred face. “I’ll make you the same offer I’d make to any trainee Auror. Land one touch on me, boy—one hit, one spell—and I’ll concede your right to talk back to me.”

“Alastor!” exclaimed Professor McGonagall’s voice. “Surely that’s an unreasonable test! Mr.~Potter, whatever his other merits, does not have a hundred years of fighting experience!”

Harry’s eyes made a lightning dart around the room, passing over the peculiar devices, glancing past Dumbledore and Severus and the Sorting Hat, settling briefly here and there. Harry couldn’t see Professor McGonagall from where he was, but that didn’t matter. There was only one device he’d really wanted to look at, and the point of all the other glances had just been to conceal which one.

“All righty,” Harry said, and hopped off his chair, ignoring Professor McGonagall’s inhalation and the Potions Master’s snort of disbelief. Dumbledore’s eyebrows had lifted, and Moody was grinning like a tiger. “Be sure to wake me up in forty minutes if he does get me.” Harry settled into a duelist’s starting stance, his wand held low. “Let’s go, then—”
\sbreak

Harry opened his eyes, his head feeling like it had been stuffed with cotton wool.

Everyone else was gone from the Headmaster’s office, the Floo-Fire dimmed; only Dumbledore still waited behind the desk.

“Hello, Harry,” the Headmaster said quietly.

“I didn’t even see him \emph{move,}” Harry marvelled, muscles creaking as he sat up.

“You were standing two paces away from Alastor Moody,” said Dumbledore, “and you took your eye off his wand.”

Harry nodded, as he took the Cloak of Invisibility out of his pouch. “I mean—I was taking the dueling stance so that he’d think I was a standard idiot and underestimate me—but I have to admit, \emph{that} was impressive.”

“So you planned it all along, Harry?” Dumbledore said.

“Of course,” Harry said. “Note how I’m doing this as soon as I wake up, rather than pausing to think of it.”

Harry drew the hood of the Cloak over his head, and glanced back up at the wall clock he’d surreptitiously glanced at earlier.

It had then shown around twenty-three minutes after eight, and now it was five minutes after nine.
\sbreak

Minerva stared as the boy put himself into the dueling stance, his wand held low. For a second Minerva wondered if Harry might possibly—no, that was completely ridiculous, it was \emph{Mad-Eye Moody} and that was beyond impossible. Of course that was what she’d thought about his partial Transfiguration, too...

“Let’s go, then,” Harry said and fell over.

Severus gave a single chuckle. “Mr.~Potter has his points, I must confess,” the Potions Master said. “Though I would never say it while he was awake, and if you repeat the words I shall deny them, for the boy’s ego is quite large enough already. Mr.~Potter does have his points, Mad-Eye, but duelling is not among them.”

Mad-Eye’s own chuckle was lower and grimmer. “Oh, yes,” said Mad-Eye. “Only fools duel. Standing like that and waiting for me to attack, what \emph{was} the boy thinking? Why, I ought to give him a scar, to remember this occasion—”

“Alastor!” barked Albus, just as she cried “Stop!”, Severus dashed forward, and Mad-Eye Moody deliberately leveled his wand on Harry Potter’s body.

“\emph{Stupefy!}”

Mad-Eye’s body seemed to almost flicker as he spun on his wooden foot like lightning, faster than she’d ever seen anyone move without magic, the red Stunning Hex passing through the suddenly empty air and barely missing Severus to crash into the opposite wall, and by the time her eyes jerked back to Moody there were seventeen radiant orbs in the pattern of a \emph{Sagitta Magica,} visible for only an instant before they streaked brilliance and struck \emph{something} that fell to the floor with a thud—
\sbreak

“Hello again, Harry,” said Dumbledore.

“I cannot \emph{believe} that guy’s reaction time,” Harry said, brushing off his Cloak as he stood up from where he’d been lying invisible on the floor, unseen by his previous self. “I can’t believe his movement speed either. I’m going to have to figure out some way to zap him without speaking an incantation that gives it away...”
\sbreak

—and then Mad-Eye ducked hard and fast, his hands hitting flat on the floor. She almost didn’t see the two tiny white threads passing through the space he’d been, but her eyes went to the blue spark when the threads impacted on one of the Headmaster’s devices, and by the time she managed to turn her eyes back, Mad-Eye had spun smoothly up to his feet, his wand was dancing unseeably fast and there was another thudding sound—
\sbreak

“Hello again, Harry.”

“Pardon me, Headmaster, but could you let me go down your stairs, and then come back up again, before I make the final jump backward? This is going to take longer than one hour of preparation—”
\sbreak

Minerva gaped at Mad-Eye Moody, who hadn’t lowered his wand in the slightest; and Severus had a look on his face that was almost like shock.

“Well, boy?” said Mad-Eye Moody. “What else have you got?”

Harry Potter’s head appeared, floating in midair as an invisible hand drew back the hood of his invisibility cloak.

“That eye,” said Harry Potter. There was a strange fierce light in the boy’s eyes. “That isn’t any ordinary device. It can see right through my invisibility cloak. You dodged my Transfigured taser as soon as I started raising it, even though I didn’t speak any incantations. And now that I’ve watched it again—you spotted all my Time-Turned selves the moment you Flooed into this room, didn’t you?”

Mad-Eye Moody was smiling, the same teeth-bared grin she’d seen him wear as they’d faced off against Voldemort himself. “Spend a hundred years hunting Dark wizards, and you see everything,” said Moody. “I once arrested a young Japanese who tried a similar trick. He found out the hard way that his shadow replica technique was no match for this eye of mine.”

“You see in all directions,” Harry Potter said, that strange fierce light still in his gaze. “No matter where that eye is pointing, it sees everything around you.”

Moody’s tiger-grin grew wider. “There’s no more of you in this room, now,” Mad-Eye said. “Think that’s because you’ll give up after this time, or because you’ll win? Any bets, boy?”

“It’s my final attempt because I decided to stake my last three hours on one shot,” said Harry Potter. “As for whether I win—”

There was a blur filling the whole air of the Headmaster’s office. Mad-Eye Moody leapt to one side with blinding speed and an instant later Harry’s head darted backward as he cried “\emph{Stuporfy!}”

Three shimmers in the air went past Harry’s moving head, just as a red bolt erupted from Harry’s location, shooting past Moody as he dodged in yet another direction—

If she’d blinked, she would have missed it, the red bolt making an angled turn in midair and slamming into Moody’s ear.

Moody fell.

Harry Potter’s floating head dropped to the height of a first-year on their hands and knees, then dropped further to the ground, his face showing sudden exhaustion.

Minerva McGonagall said, “What in \emph{Merlin’s name} just—”
\sbreak

“So you went to Flitwick, then,” Moody said. The retired Auror was now sitting in a chair, drinking long draughts from a restorative in a bottle he’d taken off his belt.

Harry Potter nodded, now sitting in his own chair instead of perched on an armrest. “I tried the Defense Professor first, but—” The boy grimaced. “He... wasn’t available. Well, I’d decided it was worth risking five House points, and if you say a risk is worth it, you can’t complain when you have to pay up. Anyway, I figured that if you had an eye that saw things other people couldn’t see, then as Isaac Asimov pointed out in \emph{Second Foundation}, the weapon to use is a brilliant light. Read enough science fiction, you know, and you’ll read everything at least once. Anyway, I told Professor Flitwick that I needed a Charm that would make a huge number of shapes, bright and flickering and filling the whole office, but invisible, so only your eye could see them. I had no idea what it would even \emph{mean} to cast an illusion and then make it invisible, but I figured if I didn’t mention that out loud, Professor Flitwick would just do it anyway, and he did. Turns out there was no spell like that I could cast myself, but Flitwick Charmed me a one-time device for it—though I had to persuade him that it wasn’t cheating, since nothing could \emph{possibly} be cheating against an Auror who’d lived long enough to retire. And then I still didn’t see how I could hit you, when you were moving that fast. So I asked about targeted spells, and that was when Flitwick showed me that hex I cast at the end, the Swerving Stunner. It’s one of Professor Flitwick’s own inventions—he’s a champion duellist as well as a Charms Master—”

“I know that, son.”

“Sorry. Anyway, the Professor says he left the duelling circuit before he got a chance to use that spell, since it only works as a finishing move on an unshielded opponent. The hex gets as close to the target as possible along its original trajectory, and then once it detects that the target is getting more distant again, the hex turns in midair and heads straight for the target. It can only swerve once—but the incantation sounds very close to ‘Stupefy’ and the hex is the same red color, so if the enemy thinks it’s a regular Stunning Hex and tries a normal dodge, that midair retargeting will finish them off. Oh, and the Professor requested that none of us talk about his special move, just in case he does get a chance to use it during competition someday.”

“But—” said Professor McGonagall. She glanced at Mad-Eye Moody, who was nodding his approval, and at Severus, who was keeping his face decidedly blank. “Mr.~Potter, you just stunned \emph{Mad-Eye Moody!} The most famous Dark wizard hunter in the history of the Auror Office! That should’ve been impossible!”

Moody let out a dark chuckle. “What’s \emph{your} answer to that one, kid? I’m curious.”

“Well...” Harry said. “First of all, Professor McGonagall, neither of us were fighting seriously.”

\emph{“Neither of you?”}

“Of course,” Harry said. “In a serious fight, Mr.~Moody would’ve dropped all my copies immediately without waiting for them to attack. And on my side, if it was \emph{actually} necessary to take down the most famous Auror in the history of the office, I’d get Headmaster Dumbledore to do it for me. And beyond that... since that \emph{wasn’t} a real fight...” Harry paused. “How can I put this? Wizards are used to duels where people fight back and forth with spells for a while. But if two Muggles with guns stand in a small room and fire bullets at each other... then whoever hits first, wins. And if one of them is deliberately missing his shots, giving the other person one chance after another—like Mr.~Moody gave me one chance after another—well, you’d have to be pretty pathetic to lose.”

“Oh, not \emph{that} pathetic,” Moody said with a slightly threatening grin.

Harry didn’t seem to notice. “You might say that Mr.~Moody was testing me to see if I would try to \emph{fight} him, or try to \emph{win.} That is, whether I’d carry out the \emph{role} of somebody fighting—use standard spells I already knew, even though I didn’t expect the \emph{consequences} of that action to be victory—or if I’d search through unusual plans until I found something that \emph{could} win. Like the difference between a student who sits in class because that’s what students do, versus a student who cares enough to ask themselves what it takes to \emph{actually} learn a piece of material, and practices however necessary—you see, Professor McGonagall? When you look at it that way—realize that Mr.~Moody was giving me chances, and that I shouldn’t attack in the first place unless I think I can win—then I don’t come out looking so well, since it actually took me three tries to get him. Plus, like I said, in a real fight Mr.~Moody could’ve turned \emph{himself} invisible, or put up shields—”

“Don’t go relying too much on shields, boy,” Mad-Eye said. The leather-clad Auror took another sip from his restorative flask. “What you learn in your first year at the academy doesn’t stay true forever, not against the strongest Dark Wizards. Every shield ever made, there’s some curse that goes straight through it, if you’re not quick enough to cast the counter. And there’s one curse that goes through everything, and it’s a curse any Death Eater will use.”

Harry Potter nodded gravely. “Right, some spells are impossible to block. I’ll remember that, in case anyone casts the Killing Curse at me. Again.”

“That kind of cleverness gets people killed, boy, and don’t you forget it.”

A sad-sounding sigh from the Boy-Who-Lived. “I know. Sorry.”

“So, son. You had something to say about when Albus and I go after Lockhart?”

Harry opened his mouth, then paused. “I won’t tell you how to run a war,” the Boy-Who-Lived said eventually. “I don’t have any experience at that. All I know is that there are consequences. Please be advised that my own assessment is that Lockhart is probably innocent, so if you can avoid hurting him without too much risk—” The boy shrugged. “I don’t know the cost. Just please, if you can, be careful not to hurt him if he’s innocent.”

“If I can,” said Moody.

“And—you’re aiming to look through his mind for evidence about the Dark Lord, aren’t you? I don’t know what the rules are in magical Britain about admissible evidence—but everyone’s always guilty of breaking \emph{some} law or another, there’s just too many laws. So if it’s \emph{not} about the Dark Lord, don’t turn him in to the Ministry, just Obliviate him and go, okay?”

Moody frowned. “Son, nobody gains power that fast without being up to \emph{something.}”

“Then leave it for the ordinary Aurors, if and when they find evidence the ordinary way. Please, Mr.~Moody. Call it a quirk of my Muggle upbringing, but if it’s \emph{not} about the war I don’t want us to be the evil police who break into people’s houses in the middle of the night, rummage through their minds and send them off to Azkaban.”

“I don’t see the sense of it, son, but I suppose I could do you the favor.”

“Is there aught else, Alastor?” inquired Albus.

“Yes,” said Moody. “About that Defense Professor of yours—”

\subsection*{Hypothesis: Gilderoy Lockhart: END}
\sbreak

\subsection{Hypothesis: Dumbledore\\(April 9th, 1992, 5:32pm)}

As Professor Quirrell slowly raised up his tea, the teacup jerked in midair, sending the dark translucent liquid just barely slopping over the side, so that only three single drops crawled down the side of the teacup. Harry would have missed it, if he hadn’t happened to be watching closely; for Professor Quirrell’s hand was perfectly steady on the cup before and after.

If that small jerky motion advanced to a constant tremor, it would be the end of any non-wandless magic for the Defense Professor. Wandwork had no room for trembling fingers. How much that would \emph{actually} handicap Professor Quirrell, if at all, Harry couldn’t guess. The Defense Professor was certainly capable of wandless magic, yet still tended to use a wand for larger things—but for him that might only be a convenience...

“Insanity,” said Professor Quirrell, as he carefully sipped from his tea—he was looking at the teacup, not at Harry, which was unusual for him—“can be a signature all its own.”

The Defense Professor’s small office was silent, the sound-warded room quiet in a way the Headmaster’s office never could be. Sometimes the two of them both happened to finish exhaling or inhaling at the same time; and then there was an auditory emptiness that was almost a sound in itself.

“I’ll agree with that in one sense,” Harry said. “If somebody tells me that everyone is \emph{staring} at them and that their underwear is being dusted with thought-controlling powder, I know they’re psychotic, because that’s the standard signature of psychosis. But if you tell me that \emph{anything} confusing points to Albus Dumbledore as a suspect, that seems... overreaching. Just because I can’t see a purpose doesn’t mean there \emph{is} no purpose.”

“Purposeless?” said Professor Quirrell. “Oh, but the madness of Dumbledore is not that he is purposeless, but that he has too many purposes. The Headmaster might have planned this to make Lucius Malfoy throw away his game for vengeance on you—or it might be a dozen other plots. Who knows what the Headmaster thinks he has reason to do, when he has found reason to do so many strange things already?”

Harry had politely declined tea, even knowing that Professor Quirrell would know what it meant. He’d considered bringing his own can of soda—but had decided against that as well, after realizing how easy it would be for the Defense Professor to teleport in a bit of potion, even if the two of them couldn’t touch each other with direct magic.

“I have seen a little now of Dumbledore,” Harry said. “Unless everything I have seen is a lie, I find it difficult to believe that he would plot to send any Hogwarts student to Azkaban. Ever.”

“Ah,” the Defense Professor said softly, the tiny reflection of the teacup gleaming in his pale eyes. “But perhaps that is another signature, Mr.~Potter. You have not yet comprehended the perspective of a man like Dumbledore. If he must, in some sufficiently noble cause, sacrifice a student—why, who would he choose, but she who declared herself a heroine?”

That gave Harry some pause. It might just be hindsight bias, but that \emph{did} seem to concentrate some of that hypotheses’s probability mass onto framing Hermione in particular. Similarly, Professor Quirrell \emph{had} predicted in advance that Dumbledore might target Draco...

\emph{But if it’s you behind all of this, Professor, you might have shaped your plans to frame the Headmaster, and taken care to cast suspicion on him in advance.}

The concept of ‘evidence’ had something of a different meaning, when you were dealing with someone who had declared themselves to play the game at ‘one level higher than you’.

“I see your point, Professor,” Harry said evenly, giving no hint of his other thoughts. “So you think it most probable that it was the Headmaster who framed Hermione?”

“Not necessarily, Mr.~Potter.” Professor Quirrell drained his teacup in one swallow and then set it down, the cup making a sharp rap as it descended. “There is also Severus Snape—though what he might think to gain from this, I could not guess. Thus he is not my prime suspect either.”

“Then who is?” Harry said, somewhat puzzled. Professor Quirrell surely wasn’t about to reply ‘You-Know-Who’—

“The Aurors have a rule,” said Professor Quirrell. “Investigate the victim. Many would-be criminals imagine that if they are the apparent victims of a crime, they shall not be suspected. So many criminals imagine it, indeed, that every senior Auror has seen it a dozen times over.”

“You’re not seriously trying to convince me that \emph{Hermione}—”

The Defense Professor was giving Harry one of those slit-eyed \emph{looks} that meant he was being stupid.

\emph{Draco?} Draco had been interrogated under Veritaserum—but Lucius might have had enough control to subvert Aurors to... oh.

“You think \emph{Lucius Malfoy} set up \emph{his own son?}” Harry said.

“Why not?” Professor Quirrell said softly. “From Mr.~Malfoy’s recorded testimony, Mr.~Potter, I gather that you enjoyed some success in changing Mr.~Malfoy’s political views. If Lucius Malfoy learned of that earlier... he might have decided that his \emph{former} heir had become a liability.”

“I don’t buy it,” Harry said flatly.

“You are being wantonly naive, Mr.~Potter. The history books are full of family disputes turned murderous, for inconveniences and threats far less than those which Mr.~Malfoy posed to his father. I suppose next you will tell me that Lord Malfoy of the Death Eaters is far too gentle to wish his son such harm.” A tinge of heavy sarcasm.

“Well, yes, frankly,” Harry said. “Love is real, Professor, a phenomenon with observable effects. Brains are real, emotions are real, and love is as much a part of the real world as apples and trees. If you made experimental predictions without taking parental love into account, you’d have a heck of a time explaining why my own parents didn’t abandon me at an orphanage after the Incident with the Science Project.”

The Defense Professor did not react to this at all.

Harry continued. “From what Draco says, Lucius prioritized him over important Wizengamot votes. That’s significant evidence, since there’s less expensive ways to fake love, if you just want to fake it. And it’s not like the prior probability of a parent loving their child is \emph{low}. I suppose it’s possible that Lucius was just taking on the \emph{role} of a loving father, and he renounced that role after he learned Draco was consorting with Muggleborns. But as the saying goes, Professor, one must distinguish possibility from probability.”

“All the better the crime,” the Defense Professor said, still in that soft tone, “if no one would believe it of him.”

“And how would Lucius even Memory-Charm Hermione in the first place, without setting off the wards? \emph{He’s} not a Professor—oh, right, you think it’s Professor Snape.”

“Wrong,” said the Defense Professor. “Lucius Malfoy would trust no servant with that mission. But suppose some Hogwarts Professor, intelligent enough to cast a well-formed Memory Charm but of no great fighting ability, is visiting Hogsmeade. From a dark alley the black-clad form of Malfoy steps forth—he would go in person, for this—and speaks to her a single word.”

“\emph{Imperio}.”

“\emph{Legilimens,} rather,” said Professor Quirrell. “I do not know if the Hogwarts wards would trigger for a returning Professor under the Imperius Curse. And if I do not know, Malfoy probably does not know either. But Malfoy is a perfect Occlumens at least; he might be able to use Legilimency. And for the target...perhaps Aurora Sinistra; none would question the Astronomy Professor moving about at night.”

“Or even more obviously, Professor Sprout,” said Harry. “Since she’s the last person anyone would suspect.”

The Defense Professor hesitated minutely. “Perhaps.”

“Actually,” Harry said then, putting a thoughtful frown on his face, “I don’t suppose you know offhand if any of the current Professors at Hogwarts were around back when Mr.~Hagrid got framed in 1943?”

“Dumbledore taught Transfiguration, Kettleburn taught Magical Creatures, and Vector taught Arithmancy,” Professor Quirrell said at once. “And I believe that Bathsheda Babbling, now of Ancient Runes, was then a Ravenclaw prefect. But Mr.~Potter, there is no reason to suppose that anyone besides You-Know-Who was involved in \emph{that} affair.”

Harry shrugged artfully. “Seemed worth asking the question, just to check. Anyway, Professor, I agree it’s possible that some outsider Legilimized a member of Hogwarts staff—and then Obliviated them afterward, there’s no way anyone would forget that part. But I \emph{don’t} think Lucius Malfoy is a probable candidate for the mastermind. It’s possible but not probable that all of Lucius’s apparent love for Draco was just a sense of duty, and that it all went up in a puff of smoke. It’s possible though not probable that everything Lucius did in front of the Wizengamot was just an act. People’s outsides do not always resemble their insides, like you said. But there’s one piece of evidence that doesn’t fit at all.”

“And that would be?” said the Defense Professor, his eyes half-lidded.

“Lucius tried to reject a hundred thousand Galleons for Hermione’s life. I saw how surprised the Wizengamot was, when Lucius said he was refusing it despite the rules of honor. The Wizengamot didn’t \emph{expect} that of him. Why \emph{wouldn’t} he just take the money while acting all indignant and pretending to grit his teeth? He wouldn’t actually care that much about throwing Hermione into Azkaban.”

There was a pause. “Perhaps the role he was playing ran away with him,” said Professor Quirrell. “It does happen, Mr.~Potter, in the heat of the moment.”

“Perhaps,” Harry said. “But it’s still one more \emph{improbability} to be postulated—and by the time you have to add up that many excuses in a theory, it can’t be at the top of the list anymore. Anything else in particular you think I ought to think about, within the range of all other possibilities?”

There was a long silence. The Defense Professor’s eyes dropped down to look at the empty teacup before them, seeming unusually distant.

“I suppose I can think of one final suspect,” the Defense Professor said at last.

Harry nodded.

The Defense Professor didn’t seem to notice, but only spoke on. “Has the Headmaster has told you anything—even a hint—about Professor Trelawney’s prophecy?”

“\emph{Huh?}” Harry said automatically, converting his own sudden shock into the best dissembling he could manage. It probably was at the wrong level to fool Professor Quirrell but Harry \emph{certainly} couldn’t take time to think before replying—\emph{wait, but how on Earth would Professor Quirrell know about} that \emph{–} “Professor Trelawney made a prophecy?”

“You \emph{were} there to hear its beginning,” Professor Quirrell said, frowning. “You called out to the entire school that the prophecy could not be about you, since you were not coming here, you were already here.”

\emph{HE IS COMING. THE ONE WHO WILL TEAR APART THE VERY—}

And that was as far as Professor Trelawney had gotten before Dumbledore had grabbed her and vanished.

“Oh, \emph{that} prophecy,” Harry said. “Sorry! It went clear out of my mind.”

Harry thought he’d put too much force into the end statement, and was 80\%-expecting Professor Quirrell to say, \emph{Aha, now Mr.~Potter, what is this mysterious} other \emph{prophecy you went to such lengths to deny—}

“That is foolish,” the Defense Professor said sharply, “if indeed you are telling me the truth. Prophecies are not trivial things. I have racked my brain much over the little that I heard, but such a small fragment is simply too little.”

“You think the one who’s coming is the one who might’ve framed Hermione?” said Harry. As his mind allocated yet another hypothesis, \emph{uncertain predicate referent, he-who-is-coming.}

“With no offense meant to Miss Granger,” the Defense Professor said with another frown, “her life or death does not seem that important. But someone \emph{was} to come—one who, in your interpretation, was not already there—and someone so significant, and unknown as a player... who knows what \emph{else} they may have done?”

Harry nodded, and mentally sighed because he was going to have to redo his Lord-Voldemort odds calculation with yet another piece of evidence in the mix.

Professor Quirrell spoke with eyes half-lidded, looking out like through slits. “More than the question of whom the prophecy spoke—who was meant to \emph{hear} it? It is said that fates are spoken to those with the power to cause them or avert them. Dumbledore. Myself. You. As a distant fourth, Severus Snape. But of those four, Dumbledore and Snape would often be in Trelawney’s presence. You and I are the ones who would not have spent much time around her before that Sunday. I think it quite likely that the prophecy was meant for one of \emph{us}—before Dumbledore took the prophetess away. \emph{Did} the Headmaster say nothing more to you?” Professor Quirrell’s voice was demanding now. “I thought I heard too much force in that denial, Mr.~Potter.”

“Honestly, no,” Harry said. “It had honestly slipped clear out of my mind.”

“Then I am rather put out with him,” Professor Quirrell said softly. “In fact, I think that I am angry.”

Harry said nothing. He didn’t even sweat. It might’ve been a poor reason for confidence, but on this particular score, Harry did happen to be innocent.

Professor Quirrell nodded once, sharply, as though in acknowledgment. “If there is nothing more to say between us, Mr.~Potter, you may go.”

“I can think of one \emph{other} suspect,” Harry said. “Someone you didn’t put on your list at all. Would you analyze him to me, Professor?”

There was another of those moments of silence that was almost a sound in itself.

“As for \emph{that} suspect,” the Defense Professor said softly, “I think you shall prosecute him on your own, Mr.~Potter, without help from me. I have heard such requests before, and experience leads me to refuse. Either I will do too good a job of prosecuting myself, and convince you that I am guilty—or else you will decide that my prosecution was too half-hearted, and that I am guilty. I will remark only this in my defense—that I would have needed a very good reason indeed to jeopardize your fragile alliance with the heir to House Malfoy.”
\sbreak

\subsection{Hypothesis: The Defense Professor\\(April 8th, 1992, 8:37pm)}
\sbreak

“...so I fear I must take my leave,” Dumbledore was saying gravely. “I promised Quirinus... that is to say, I promised the Defense Professor... that I would not make any attempt to uncover his true identity, in my own person or any other.”

“And why’d you make a fool promise like that, then?” snapped Mad-Eye Moody.

“It was an unalterable condition of his employment, or so he said.” Dumbledore glanced at Professor McGonagall, a wry smile briefly flitting over his face. “And Minerva made it clear to me that Hogwarts \emph{required} a competent Defense Professor this year, even if I had to haul Grindelwald out of Nurmengard and prevail on old affections to persuade him to take the position.”

“I did not \emph{quite} phrase it in that fashion—”

“Your expression said it for you, my dear.”

And so soon the four of them—Harry, Professor McGonagall, the Potions Master, and Alastor Moody aka ‘Mad-Eye’—were ensconced all by themselves in the Headmaster’s office.

It was strange how the Headmaster’s office seemed... \emph{unbalanced...} without the Headmaster in it. If you didn’t have the ancient wizened master to make it all seem \emph{solemn}, you were just four people trying to have a serious meeting while surrounded by bizarre, noisy gidgets. Clearly visible from where Harry had perched himself on his chair’s arm was a truncated-conical object, like a cone with its top snipped off, slowly spinning around a pulsating central light which it shaded but did not obscure; and each time the inner light pulsated, the assembly made a \emph{vroop-vroop-vroop} sound that sounded oddly distant, muffled like it was coming from behind four solid walls, even though the spinning-conical-section thingy was only a meter or two away.

\emph{Vroop... vroop... vroop}...

And then there were the various still-breathing bodies of Harry Potter he’d stashed in one quiet corner, cleaning up a mess that was his own in more ways than one. (Only one body \emph{wasn’t} inside a copy of the Invisibility Cloak; but then it merely took a small effort of concentration for Harry to perceive his other selves beneath the Cloak of which he was master—an effort which Harry had carefully \emph{not} put forth earlier, to avoid getting advance temporal information he wanted to determine by his own decision.) The sad thing was that by this point, having his own body visibly lying in a corner didn’t seem all that crazy. It was just... Hogwarts.

“All right, then,” Moody said, looking rather sour about it. From within his leather armor, the scarred man took out a black folder. “This is a copy of what Amelia’s people put together. She almost certainly knows we’ve got it, but it’s all off the books, that clear? Anyway—”

And Moody told them who the Department of Magical Law Enforcement thought ‘Quirinus Quirrell’ really was. A seemingly ordinary Hogwarts student (though talented enough that he’d been only narrowly beaten out for the Head Boy position) who’d gone vacationing in Albania after his graduation, disappeared, returned after 25 years, and then been caught up in the Wizarding War—

“It was murdering the House of Monroe that made Voldie’s name,” Moody said. “Until then, he was just another Dark Wizard with delusions of grandeur and Bellatrix Black. But after that—” Moody snorted. “Every fool in the country flocked to serve him. You would’ve \emph{hoped} the Wizengamot would turn serious, once they realized Voldie was willing to kill their own sacred selves. And that’s just what the bastards did—\emph{hope} that some other bastard would turn serious. None of the cowards wanted to step in front. It was Monroe, Crouch, Bones, and Longbottom. That was nearly everyone in the Ministry who’d dare say a word that might give Voldie offense.”

“That was how your House came to be ennobled, Mr.~Potter,” injected the solemn voice of Professor McGonagall. “There is an ancient law that if anyone ends a Most Ancient House, whoever avenges that blood will be made Noble. To be sure, the House of Potter was already older than some lines called Ancient. But yours was titled a Noble House of Britain after the end of the war, in recognition that you had avenged the Most Ancient House of Monroe.”

“Flush of gratitude and all that,” Mad-Eye Moody said sourly. “It didn’t last, but at least James and Lily got a fancy title and a useless medal to take to their graves. But that’s leaving out eight years of complete horror after Monroe disappeared and Regulus Black—he was Monroe’s private source in the Death Eaters, we’re pretty sure—was executed by Voldie. Like a dam breaking and gore flooding out, drowning the whole country. Albus bloody Dumbledore himself had to step into Monroe’s shoes, and that was barely enough for us to survive.”

Harry listened with an odd sense of unreality. Some of it \emph{felt} right, matched up with observation—especially with the speech Professor Quirrell had made before Christmas—and yet...

This was \emph{Professor Quirrell} they were talking about.

“So that’s who the Department thinks is your Defense Professor,” Mad-Eye Moody finished up his account. “Now what do \emph{you} think, son?”

“Well...” Harry said slowly. \emph{It is also possible to have a mask behind the mask.} “The obvious next thought is that this ‘David Monroe’ person died in the war after all, and this is just someone else pretending to be David Monroe pretending to be Quirinus Quirrell.”

“That’s \emph{obvious?}” said Professor McGonagall. “Dear Merlin...”

“Really, boy?” said Mad-Eye Moody, his blue eye spinning rapidly. “I’d say that’s a little... \emph{paranoid.}”

\emph{You don’t know Professor Quirrell,} Harry did not say. “It’s an easy theory to test,” Harry said out loud. “Just check whether the Defense Professor remembers something about the war that the real David Monroe would’ve known. Though I suppose, if he’s playing the part of David Monroe \emph{pretending} to be someone else, he has a good excuse to \emph{pretend} he’s pretending he doesn’t know what you’re talking about—”

“A \emph{little} paranoid,” said the scarred man, his voice rising. “\emph{Not paranoid enough! CONSTANT VIGILANCE!} Think about it, lad—what if the \emph{real} David Monroe never came back from Albania?”

There was a pause.

“I see...” Harry said.

“Of course you do,” Professor McGonagall said. “Don’t mind me, please. I’ll just sit here quietly going mad.”

“In this line of work, if you survive, you learn that there’s three kinds of Dark Wizards,” Moody said grimly; his wand wasn’t pointed at anyone, it was angled slightly downward, but it was in his hand. It had never left his hand since the moment he’d entered the room. “There’s Dark Wizards that have one name. There’s Dark Wizards that have two names. And there’s Dark Wizards that change names like you and I change clothes. I saw ‘Monroe’ go through three Death Eaters like he was snapping twigs. There’s not many wizards that good at age forty-five. Dumbledore, maybe, but not many others.”

“Perhaps that is true,” said the Potions Master from where he was lurking. “But what of it, Mad-Eye? Whatever his identity, Monroe was surely the Dark Lord’s enemy. I’ve heard Death Eaters curse his name even after they thought him dead. They feared him well.”

“So far as Defense Professors are concerned,” Professor McGonagall said primly, “I shall take it and be grateful.”

Moody swung around to glare at her. “Just where the devil was ‘Monroe’ all those years he was gone, eh? Maybe he thought he could make a name for himself in Britain by opposing Voldie, and vanished away when he found out he was wrong. Then why’d he come back \emph{now,} hah? What’s his \emph{new} plan?”

“He, ah...” Harry ventured tentatively. “He \emph{says} he always wanted to be a great Defense Professor because all the best fighting wizards have taught at Hogwarts. And he kind of \emph{is} being an incredibly good Defense Professor, actually... I mean, if he just wanted to keep up a disguise, he could get away with \emph{much} sloppier work...”

Professor McGonagall was nodding firmly.

“Naive,” Moody said flatly. “I suppose you all haven’t wondered if your Defense Professor set up the whole House of Monroe to be wiped out?”

“\emph{What?}” cried Professor McGonagall.

“Our mystery wizard hears about a missing kid from a Most Ancient House of Britain,” Moody said. “Steps into the shoes of ‘David Monroe’, but stays away from the real Monroe family. But eventually the House is bound to notice something wrong. So this imposter somehow prods Voldie into wiping them all out—maybe leaked a password they’d given him for their wards—and then he was a Lord of the Wizengamot!”

There seemed to be a fight going on inside Harry’s mind between Hufflepuff One, who’d never trusted the Defense Professor in the first place; and Hufflepuff Two, who was far too loyal to Harry’s friend, Professor Quirrell, to believe something like that just because Moody said so.

\emph{It} is \emph{kind of obvious, though,} observed his Slytherin part. \emph{I mean, do you actually believe that under natural circumstances, anyone would end up as the last heir to a Most Ancient House AND Lord Voldemort killed his family AND he has to avenge his martial arts sensei? If anything I’d say he went too far over the top in setting up his new identity as the ideal literary hero. That sort of thing doesn’t happen in real life.}

\emph{This from an orphan who was raised unaware of his heritage,} commented Harry’s Inner Critic. \emph{With a prophecy about him. You know, I don’t think we’ve ever read a story about two equally destined heroes competing to see who’s cliched enough to take down the villain—}

\emph{Yes,} replied the central Harry over the distant vroop-ing noise in the background, \emph{it’s a very sad life we lead and YOU’RE NOT HELPING.}

\emph{There’s only one thing to do at this point,} said Ravenclaw. \emph{And we all know what it is, so why argue?}

\emph{But,} Harry replied, \emph{how} do \emph{we test experimentally whether or not Professor Quirrell is the original David Monroe? I mean, what sort of observable behaves differently, depending on whether he’s the real David Monroe or an impostor?}

“What do you want me to do about it, Mad-Eye?” Professor McGonagall was demanding. “I can’t—”

“You can,” the scarred man said, glaring at her fiercely. “Just fire the bloody Defense Professor.”

“You say that \emph{every} year,” said Professor McGonagall.

“Yes, and I’m always right!”

“Constant vigilance or no, Alastor, the students must be taught!”

Moody snorted. “Pfah! I swear the curse gets worse every year, as you lot get more and more reluctant to let them go. Your precious Professor Quirrell would have to \emph{be} Grindelwald in disguise, to get himself sent off!”

“Is he?” Harry couldn’t help asking. “I mean, could he \emph{actually} be—”

“I check Grindie’s cell every two months,” Moody said. “He was there in March.”

“Could the person in the cell be a ringer?”

“I administer a blood test for his identity, son.”

“Where do you keep the blood you use as a reference?”

“In a safe place.” Something like a smile was stretching the scarred lips. “Have you considered the Auror Office after you graduate?”

“Alastor,” Professor McGonagall said reluctantly. “The Defense Professor \emph{does} have a... health condition. I suppose you will call it suspicious in itself—but it is by no means certain that it will be any ill-doing on his part which prevents us from renewing his employment.”

“Yes, his little naptimes,” Moody said darkly. “Amelia thinks he stepped into the path of a high-level curse. Sounds to \emph{me} more like a Dark ritual gone wrong!”

“You’ve no proof of that!” Professor McGonagall said.

“That man might as well be wearing a sign saying ‘Dark Wizard’ in glowing green letters over his head.”

“Ah...” Harry said. It didn’t seem like an especially good time to ask what Mr.~Moody thought of the ‘not all sacrificial rituals are evil’ standpoint. “Excuse me, but you said earlier that Professor Quirrell—I mean the old David Monroe—I mean the Monroe from the seventies—anyway, you said that person used the Killing Curse. What does that imply? Does somebody have to be a Dark Wizard to use it?”

Moody shook his head. “I’ve used it myself. All it takes is power and a certain \emph{mood.}” The grimacing lips were showing teeth. “The first time I cast it was against a wizard named Gerald Grice, and you can ask me what \emph{he} did after you graduate Hogwarts.”

“But why is it Unforgiveable, then?” Harry said. “I mean, a Cutting Hex can kill someone too. So why’s it any better to use a Reducto instead of Avada Kedav-”

“Shut your mouth!” Moody said sharply. “Someone might take it the wrong way, your saying that incantation. You \emph{look} too young to cast it, but there’s such a thing as Polyjuice. And to answer your question, boy, there’s two reasons why that spell’s in the blackest book. The first is that the Killing Curse strikes directly at the soul, and it’ll just keep going until it hits one. Straight through shields. Straight through \emph{walls.} There’s a \emph{reason} why even Aurors fighting Death Eaters weren’t allowed to use it before the Monroe Act.”

“Ah,” said Harry. “That does seem like an excellent reason to ban—”

“I’m not finished, son. The second reason is that the Killing Curse doesn’t \emph{just} take a powerful bit of magic. You’ve got to \emph{mean} it. You’ve got to \emph{want} someone dead, and not for the greater good, either. Killing Grice didn’t bring back Blair Roche, or Nathan Rehfuss, or David Capito. It wasn’t for justice, or to stop him doing it again. \emph{I wanted him dead.} You understand now, lad? You don’t have to be a Dark Wizard to use that spell—but you can’t be Albus Dumbledore, either. And if you’re arrested for killing with it, there’s no possible defense.”

“I... see,” murmured the Boy-Who-Lived. \emph{You can’t want the person dead as an instrumental value on the way to some positive future consequence, you can’t cast it if you believe it’s a necessary evil, you have to actually want them dead for the sake of being dead, as a terminal value in your utility function.} “A magically embodied preference for death over life, striking within the plane of pure life force... that does sound like a difficult spell to block.”

“Not difficult,” Moody snapped. “\emph{Impossible}.”

Harry nodded gravely. “But David Monroe—or whoever—used the Killing Curse against a couple of Death Eaters even \emph{before} they wiped out his family. Does that mean he already had to hate them? Like, the martial arts story was probably true?”

Moody shook his head slightly. “One of the dark truths of the Killing Curse, son, is that once you’ve cast it the first time, it doesn’t take much hate to do it again.”

“It damages the mind?”

Again Moody shook his head. “No. It’s the killing that does that. Murder tears the soul—but that’s just the same if it’s a Cutting Hex. The Killing Curse doesn’t crack your soul. It just takes a cracked soul to cast.” If there was a sad expression on the scarred face, it could not be read. “But that doesn’t tell us much about Monroe. The ones like Dumbledore who’ll never be able to cast the Curse all their lives, because they never crack no matter what—they’re the rare ones, very rare. It only takes a little cracking.”

There was a strange heavy feeling in Harry’s chest. He’d wondered what exactly it had meant, that Lily Potter had tried to cast the Killing Curse at Lord Voldemort with her last breath. But surely it was forgiveable, it was \emph{right} and \emph{proper} for a mother to hate the Dark Wizard who was coming to kill her baby, mocking her for how she couldn’t stop him. There was something wrong with you as a parent if you \emph{couldn’t} cast Avada Kedavra, in that situation. And no other spell could’ve gone past the Dark Lord’s shields; you’d have to at least \emph{try} to hate the Dark Lord enough to want him dead for the sake of dead, if that was the only way to save your baby.

\emph{It only takes a little cracking...}

“Enough,” said Professor McGonagall. “What would you have us do?”

Moody’s smile twisted. “Get rid of the Defense Professor and see if all your troubles mysteriously clear up. Bet you a Galleon they do.”

Professor McGonagall looked like she was in pain. “Alastor—but—will \emph{you} teach the classes, if—”

“Ha!” said Moody. “If I ever say yes to that question, check me for Polyjuice, because it’s not me.”

“I’ll test it experimentally,” Harry said. And then, as everyone looked at him, “I’ll ask Professor Quirrell a question that the real David Monroe would know—like who else was in the Slytherin class of 1945, or something like that—hopefully without making it obvious. It won’t be definitive proof, he could’ve studied the role, but it would be evidence. Still, Mr.~Moody, even if Professor Quirrell isn’t the original Monroe, I’m not sure that getting rid of him is a free action. He saved my life twice—”

“\emph{What?}” demanded Moody. “When? How?”

“Once when he knocked down a bunch of witches who were summoning me toward the ground, once when he figured out that the Dementor was draining me through my wand. And if Professor Quirrell \emph{wasn’t} the one who set up Draco Malfoy in the first place, then he saved Draco Malfoy’s life, and things would be a lot worse if he hadn’t. If the Defense Professor \emph{isn’t} behind it all—he’s not someone we can afford to just get rid of.”

Professor McGonagall nodded firmly.
\sbreak

\subsection{Hypothesis: Severus Snape\\(April 8th, 1992, 9:03pm)}
\sbreak

Harry and Professor McGonagall now stood on the slowly turning stairs, turning without descending; or at least \emph{one} Harry stood upon those stairs—his other three selves had been left behind in the Headmaster’s office.

“Can I ask you a private question?” Harry said, when he thought they were far enough away not to be heard. “And in particular, private from the Headmaster.”

“Yes,” Professor McGonagall said, not quite sighing. “Though I hope you realize that I cannot \emph{do} anything which conflicts with my duties to—”

“Yes,” Harry said, “that’s exactly what I need to ask you about. In front of the Wizengamot, when Lucius Malfoy was saying that Hermione was no part of House Potter and that he wouldn’t take the money, you told Hermione how to swear that oath. I want to know, if something like that comes up again, if your first duty is to the Hogwarts student Hermione Granger, or to the head of the Order of the Phoenix, Albus Dumbledore.”

Professor McGonagall looked like someone had hit her in the face with a cast-iron frying-pan, a few minutes earlier, and now she’d been told that somebody was about to do it again, and not to flinch.

Harry flinched a little himself. Somewhere along the line he needed to pick up the knack of \emph{not} phrasing things to hit as hard as he possibly could.

The walls rotated around them, behind them, and somehow, they descended.

“Oh, Mr.~Potter,” Professor McGonagall said with a low exhalation. “I... \emph{wish} you wouldn’t ask me such questions... oh, Harry, I wasn’t thinking then, not at all. I only saw a chance to help Miss Granger and... I \emph{was} Sorted into Gryffindor, after all.”

“You’ve got a chance to think now,” Harry said. It was all coming out wrong, but he had to say it \emph{anyway,} because—“I’m not asking you to be loyal to \emph{me.} But if you do know—if you \emph{are} sure—what you’ll do if it comes down to an innocent Hogwarts student versus the Order of the Phoenix a second time...”

But Professor McGonagall shook her head. “I’m \emph{not} sure,” the Transfiguration Professor whispered. “I don’t know if it was the right choice even then. I’m sorry. I can’t decide such awful things!”

“But you’ll do \emph{something} if it happens again,” Harry said. “Indecision is also a choice. You can’t just \emph{imagine} having to make an immediate decision?”

“No,” Professor McGonagall said, sounding a little stronger; and Harry realized that he’d accidentally offered a way out. The Professor’s next words confirmed Harry’s fears. “Such a dreadful choice as that, Mr.~Potter—I think I should not make it until I must.”

Harry gave an internal sigh. He supposed he had no right to expect Professor McGonagall to say anything else. In a moral dilemma where you lost something either way, making the choice would \emph{feel} bad either way, so you could temporarily save yourself a little mental pain by refusing to decide. At the cost of not being able to plan anything in advance, and at the cost of incurring a huge bias toward inaction or waiting until too late... but you couldn’t expect a witch to know all that. “All right,” Harry said.

Though it wasn’t right at all, not really. Dumbledore might want that debt removed, Professor Quirrell would also want Harry out of that debt. And if the Defense Professor \emph{was} David Monroe, or could convincingly \emph{appear} to be David Monroe, then Lord Voldemort technically hadn’t \emph{exterminated} the House of Monroe. In which case somebody might be able to pass a Wizengamot resolution revoking the Noble status of House Potter, which had been granted for avenging the Most Ancient House of Monroe.

In which case Hermione’s vow of service to a Noble House might be null and void.

Or maybe not. Harry didn’t know anything about the legalities, especially not whether House Potter got the money \emph{back} if someone managed to send Hermione to Azkaban. Just because you lost something might not mean the payment was returned, legally speaking. Harry wasn’t sure and he didn’t dare ask a magical solicitor...

...it would have been nice to be able to trust at least one adult to take Hermione’s side instead of Dumbledore’s, if an issue like that threatened to come up.

The stairs they were upon ceased rotating, and they were before the backs of the great stone gargoyles, which rumbled aside, revealing the hallway.

Harry stepped out—

A hand caught at Harry’s shoulder.

“Mr.~Potter,” Professor McGonagall said in a low voice, “why did you to tell me to keep watch over Professor Snape?”

Harry turned around again.

“You told me to keep watch, and see if he’d changed,” Professor McGonagall went on, her tone urgent. “\emph{Why} did you say that, Mr.~Potter?”

It took a moment, at this point, for Harry to think back and remember why he \emph{had} said that. Harry and Neville had rescued Lesath Lestrange from bullies, and then Harry had confronted Severus in the hallway and, at least according to the Potions Master’s own words, ‘almost died’—

“I learned something that made me worry,” Harry said after a moment. “From someone who made me promise not to tell anyone else.” Severus had made Harry swear that their conversations wouldn’t be shared with anyone, and Harry was still bound by it.

“\emph{Mr.} Potter—” began Professor McGonagall, and then exhaled, the flash of sharpness disappearing as quickly as it had come. “Never mind. If you cannot say, you cannot say.”

“Why do \emph{you} ask?” Harry said.

Professor McGonagall seemed to hesitate—

“All right, let me be more specific,” Harry said. After Professor Quirrell had done it to \emph{him} several times, Harry was starting to get the hang of it. “What change have you \emph{already} observed in Professor Snape that you’re trying to decide whether to tell me about?”

“Harry—” the Transfiguration Professor said, and then closed her mouth.

“I obviously know \emph{something} you don’t,” Harry said helpfully. “See, this is why we can’t always put off trying to decide our awful moral dilemmas.”

Professor McGonagall closed her eyes, drew in a deep breath, pinched the bridge of her nose and squeezed it several times. “All right,” she said. “It’s a subtle thing... but worrying. How can I put this... Mr.~Potter, have you read many books that young children are not meant to read?”

“I’ve read \emph{all} of them.”

“Of course you have. Well... I don’t quite understand it myself, but for so long as Severus has been employed in this school, stalking about in that awful stained cloak, there has been a \emph{certain sort of girl} that stares at him with longing eyes—”

“You say that like it’s a bad thing?” Harry said. “I mean, if there’s one thing I \emph{did} understand from those books, it’s that you’re not supposed to question people’s preferences.”

Professor McGonagall gave Harry a \emph{very} strange look.

“I mean,” Harry said again, “from what I’ve read, when I’m a bit older there’s something like a 10\% chance that \emph{I’ll} find Professor Snape attractive, and the important thing is for me to just accept whatever I—”

“\emph{In any case, Mr.~Potter,} Severus has always been entirely indifferent to the stares of those young girls. But now—” Professor McGonagall seemed to realize something, and hastily said, her hands rising in warding, “Please don’t mistake me, Professor Snape \emph{certainly} has not taken advantage of any young witches! Absolutely not! He has never even so much as smiled at one, not that I ever heard. He has told the young girls to stop gaping at him. And if they stare at him regardless, he looks away. That I have seen with my own eyes.”

“Er...” Harry said. “Sorry, but just because I’ve \emph{read} those books doesn’t mean I understood them. What does all that \emph{mean?}”

“That he is \emph{noticing},” Professor McGonagall said in a low voice. “It is a subtle thing, but now that I have seen it, I am certain. And \emph{that} means... I am very much afraid... that the bond which held Severus to Albus’s cause... may have weakened, or even broken.”

2 + 2 = ...

\emph{“Snape and Dumbledore?”} Then Harry heard the words that had just come out of his mouth, and hastily added, “Not that there’s anything wrong with that—”

\emph{“No!”} said Professor McGonagall. “Oh, for pity’s sake—I can’t explain it to you, Mr.~Potter!”

The other shoe finally dropped.

\emph{He was} still \emph{in love with my mother?}

This seemed somewhere between beautifully sad, and pathetic, for around five seconds before the \emph{third} shoe dropped.

\emph{Of course, that was before I gave him my helpful relationship advice.}

“I see,” Harry said carefully after a few moments. There were times when saying ‘Oops’ didn’t fully cover it. “You’re right, that’s not a good sign.”

Professor McGonagall put both hands over her face. “Whatever you’re thinking right now,” she said in a slightly muffled voice, “which I assure you is \emph{also} wrong, I don’t want to hear about it, ever.”

“So...” Harry said. “If, like you said, the bond that held Professor Snape to the Headmaster \emph{has} broken... what would he do then?”

There was a long silence.
\sbreak

\emph{What would he do then?}

Minerva lowered her hands, gazing down at the upturned face of the Boy-Who-Lived. One simple question shouldn’t have caused her so much dismay. She’d known Severus for years; the two of them bound, in some strange way, by the prophecy they’d both heard. Though Minerva suspected, from what she knew of the rules of prophecy, that she had only \emph{overheard} it herself. It had been Severus’s acts which had brought about the prophecy’s fulfillment. And the guilt, the heartbreak which had come of that choice, had been tormenting the Potions Master for years. She couldn’t imagine who Severus would be without it. Her mind went blank, trying to imagine; her thoughts an empty parchment.

\emph{Surely} Severus was no longer the man he’d once been, that angry and terribly foolish young man who’d brought the prophecy before Voldemort in exchange for being admitted into the Death Eaters. She’d known him for years, and surely Severus was no longer that man...

Did she really know him at all?

Had \emph{anyone} ever seen the real Severus Snape?
\sbreak

“I don’t know,” Professor McGonagall finally said. “I truly don’t know at all. I can’t even imagine. Do \emph{you} know anything of this, Mr.~Potter?”

“Er...” Harry said. “I think I can say that my own evidence points in the same direction as yours. I mean, it increases the probability that Professor Snape isn’t in love with my mother anymore.”

Professor McGonagall closed her eyes. “I give up.”

“I don’t know of anything wrong he’s done apart from that, though,” Harry added. “I assume the Headmaster cleared you to ask me about this?”

Professor McGonagall looked away from him, staring at the wall. “Please don’t, Harry.”

“All right,” Harry said, and turned and hurried out into the hallways, hearing Professor McGonagall more slowly walking after, and the rumbling sound of the gargoyles moving into place.
\sbreak

It was the morning after next, during Potions class, that Harry’s \emph{potion of cold resistance} boiled over his cauldron with a green froth and mildly nauseating smell, and Professor Snape, looking more resigned than disgusted, told Harry to stay after class. Harry had his own suspicions about this affair, and as soon as class let out—Hermione, as usual for the last few days, being the first to flee out the door—the door swung shot and locked behind the departing students.

“I apologize for ruining your potion, Mr.~Potter,” Severus Snape said quietly. There was upon his face the strange sad look that Harry had seen only once before, in a hallway some time ago. “It will not be reflected in your grades. Please, sit down.”

Harry sat back down at his desk, filling up the time by scrubbing a bit more at the green stain on the wooden surface, as the Potions Master incanted a few privacy spells.

When the Potions Master was done, he spoke again. “I... do not know how to broach this topic, Mr.~Potter, so I will simply say it... before the Dementor, you recovered your memory of the night your parents died?”

Harry silently nodded.

“If... I know it must not be a pleasant memory, but... if you could tell me what happened...?”

“Why?” Harry said. His voice was solemn, definitely \emph{not mocking} the pleading look that Harry had never expected to see from that person. “I wouldn’t think that would be a pleasant thing for you to hear either, Professor—”

The Potions Master’s voice was almost a whisper. “I have imagined it every night these last ten years.”

\emph{You know,} said Harry’s Slytherin side, \emph{it might not be such a good idea to give him closure, if his guilt-based loyalties are already wavering—}

\emph{Shut up. Overruled.}

It wasn’t something that Harry could \emph{actually} bring himself to deny. He took one suggestion from his Slytherin side, and that was it.

“Will you tell me \emph{exactly} how you came to learn about the Prophecy?” Harry said. “I’m sorry to make this a trade, I \emph{will} tell you afterward, only, it could be really important—”

“There is little to say. I had come to be interviewed by the Deputy Headmistress for the position of Potions Master, and so I was waiting outside the room of the Hog’s Head Inn when the applicant before me, Sybill Trelawney, came to seek the position of Professor of Divination. As soon as Trelawney finished speaking her words, I fled, forsaking my chance at Hogwarts’s Mastery, and went to the Dark Lord.” The Potions Master’s face was drawn and tight. “I did not even pause to consider why that riddle might have come to me, before I sold it to another.”

“A \emph{job interview?}” Harry said. “Where you and Professor Trelawney both happened to be applying, and Professor McGonagall was interviewing? That seems... like rather a large coincidence...”

“Seers are the pawns of time, Mr.~Potter. Coincidence is beneath them, and they are above it. I was the one meant to hear that prophecy and become its fool. Minerva’s presence made no final difference to how it came about. There was no Memory Charm as you supposed, I do not know why you thought that, but there was no Memory-Charm, there could have been no Memory-Charm. The voice of a seer has a quality, an enigma which even Legilimency cannot share, how could that be imbued in a false memory? Do you think the Dark Lord would believe my mere words? The Dark Lord seized my mind and saw the mystification there, even if he could not seize the mystery, and so he knew the prophecy had been true. The Dark Lord could have killed me then, having taken what he wanted—I was a fool indeed to go to him—but he saw something in me I do not know, and took me into the Death Eaters, though on his terms rather than mine. That is how I brought it about, brought it all about, from beginning to end, always my own doing.” Severus’s voice had gone rather hoarse, and his face was filled with naked pain. “Now tell me, please, how did Lily die?”

Harry swallowed twice, and began his recounting.

“James Potter shouted for Lily to run away with me, that he would hold off You-Know-Who.”

“You-Know-Who said—” Harry stopped, the chills going all over his own skin, his own muscles tightening as if in preparing for a seizure. The memory was returning strongly, now, accompanied by cold and darkness in association. “He used... the Killing Curse... and then he came upstairs somehow, I think he must have flown, I don’t remember any footsteps on stairs or anything like that... and then my mother said, ‘No, not Harry, please not Harry!’ or something like that. And the Dark Lord—his voice was so high, like water whistling out of a teakettle only \emph{cold}—the Dark Lord said—”

\emph{Stand aside, woman! For you I am not come, only the boy.}

The words were very clear in Harry’s memory.

“—he told my mother to get out of his way, that he was only there for \emph{me}, and my mother begged him to have mercy, and the Dark Lord said—”

\emph{I give you this rare chance to flee.}

“—that he was being generous and giving her a chance to run, but he wouldn’t bother fighting her, and even if she died, she couldn’t save me—” Harry’s voice was unsteady, “—and so she ought to get out of his way. And that was when my mother begged the Dark Lord to take her life instead of mine—and the Dark Lord—the Dark Lord said to her—and his voice was lower this time, like he was dropping a pose—”

\emph{Very well, I accept the bargain.}

“—he said that he accepted her offer, and that she should drop her wand so he could kill her. And then the Dark Lord waited, just waited. I, I don’t know what Lily Potter was thinking, it hadn’t even made sense in the first place, what she said, it wasn’t like the Dark Lord would kill her and then just \emph{leave,} when he’d come there for me. Lily Potter didn’t say anything, and then the Dark Lord started laughing at her and it was horrible and—and she finally tried the only thing left that wasn’t abandoning me or just giving up and dying. I don’t know if she even could’ve, if the spell would’ve worked for her, but when you think about, she had to try. The last thing my mother said was ‘Avada Ke—’ but the Dark Lord started his own curse as soon as she said ‘Av’ and he said it in less than half a second and there was a flash of green light and then—and then—\emph{and then}—”

“That’s enough.”

Slowly, like a body floating to the surface of water, Harry returned from wherever he’d been.

“That’s enough,” the Potions Master said hoarsely. “She died... Lily died without pain, then? The Dark Lord... did not do anything to her, before she died?”

\emph{She died thinking that she’d failed, and that the Dark Lord was going to kill her baby next. That’s pain.}

“He—the Dark Lord didn’t torture her—” Harry said. “If that’s what you’re asking.”

Behind Harry, the door unlocked itself and swung open.

Harry left.

It was Friday, April 10th, of 1992.
