\chapter{Prior Information}
\lettrine{A}{} boy waits at a small clearing at the edge of the non-forbidden forest, beside a dirt trail that runs back to the gates of Hogwarts in one direction, and off into the distance in another. There is a carriage nearby, and the boy is standing well away from it, looking at it, his eyes seldom wavering from its direction.

In the distance, a figure is approaching along the dirt path: A man wearing professorial robes, trudging slowly with his shoulders slumped low, his formal shoes kicking up small clouds of dust as he walks.

Half a minute later, the boy darts another quick glance before returning to his surveillance; and this glimpse shows that the man’s shoulders have straightened, his face unslackened, and that his shoes are now walking lightly across the dirt, leaving not a trace of dust in the air behind.

“Hello, Professor Quirrell,” Harry said without letting his eyes move again from the direction of their carriage.

“Salutations,” said the calm voice of Professor Quirrell. “You seem to be keeping your distance, Mr.~Potter. I don’t suppose you see something odd about our conveyance?”

“Odd?” Harry echoed. “Why no, I can’t say I see anything odd. There seem to be even numbers of everything. Four seats, four wheels, two huge skeletal winged horses...”

A skin-wrapped skull turned to look at him and flashed teeth, solid and white in that black cavernous mouth, as though to indicate that it was just about as fond of him as he was of it. The other black leathery horse-skeleton tossed its head like it was whickering, but there was no sound.

“They are Thestrals, and they have always drawn the carriage,” Professor Quirrell said, sounding quite undisturbed as he climbed into the front bench of the carriage, sitting down as far to the right as possible. “They are visible only to those who have seen death and comprehended it, a useful defense against most animal predators. Hm. I suppose that the first time you went in front of the Dementor, your worst memory proved to be the night of your encounter with He-Who-Must-Not-Be-Named?”

Harry nodded grimly. It was the right guess, even if for the wrong reasons. \emph{Those who have seen Death...}

“Did you recall anything of interest, thereby?”

“Yes,” Harry said, “I did,” only that and nothing more, for he was not ready as yet to make accusations.

The Defense Professor smiled one of his dry smiles, and beckoned with an impatient finger.

Harry closed the distance and climbed into the carriage, wincing. The sense of doom had grown significantly stronger after the day of the Dementor, even though it had been slowly weakening before then. The greatest distance that the carriage allowed him from Professor Quirrell no longer seemed like nearly far enough.

Then the skeletal horses trotted forward and the carriage started in motion, taking them toward the outer bounds of Hogwarts. As it did, Professor Quirrell slumped back down into zombie-mode, and the sense of doom retreated, though it still hovered at the edge of Harry’s perceptions, unignorable...

The forest scrolled by as the carriage rolled along, the trees moving past at a speed that seemed positively glacial by comparison to broomsticks or even cars. There was something oddly relaxing, Harry thought, about traveling that slowly. It had certainly relaxed the Defense Professor, who was slumped over with a small stream of drool coming out of his slack mouth and puddling on his robes.

Harry still hadn’t decided what he was allowed to eat for lunch.

His library research hadn’t turned up any sign of wizards speaking to nonmagical plants. Or any other nonmagical animals besides snakes, although \emph{Spell and Speak} by Paul Breedlove had recounted the probably-mythical tale of a sorceress called the Lady of Flying Squirrels.

What Harry \emph{wanted} to do was ask Professor Quirrell. The problem was that Professor Quirrell was \emph{too smart}. Judging by what Draco had said, the Heir of Slytherin business was a major bombshell, and Harry wasn’t sure he wanted anyone else to know. And the instant Harry asked about Parseltongue, Professor Quirrell would fix him with those pale blue eyes and say, ‘I see, Mr.~Potter, so you taught Mr.~Malfoy the Patronus Charm and accidentally spoke to his snake.’

It wouldn’t \emph{matter} that it shouldn’t be enough evidence to locate the true explanation as a hypothesis, let alone overcome its burden of prior improbability. Somehow the Defense Professor would deduce it \emph{anyway}. There were times when Harry suspected that Professor Quirrell had way more background information than he was telling, his priors were simply too good. Sometimes he got his amazing deductions right even when his \emph{reasons} were wrong. The problem was that Harry couldn’t see how Professor Quirrell could’ve snuck in an extra clue about half the stuff he guessed. Just \emph{once} Harry would have liked to make some sort of incredible deduction from something Professor Quirrell said which would catch \emph{him} completely off guard.
\sbreak
“I shall have a bowl of green lentil soup, with soy sauce,” Professor Quirrell said to the waitress. “And for Mr.~Potter, a plate of Tenorman’s family chili.”

Harry hesitated in sudden dismay. He’d resolved to stick to vegetarian dishes for the moment, but he’d forgotten in his deliberations that Professor Quirrell did the \emph{actual ordering} —and it would be awkward if he protested now—

The waitress bowed to them, and turned to go—

“Erm, excuse me, any meat in that from snakes or flying squirrels?”

The waitress didn’t so much as blink an eye, only turned back to Harry, shook her head, bowed politely to him again, and resumed her walk toward the door.

(The other parts of Harry were snickering at him. Gryffindor was making sardonic comments about how a little social discomfort was enough to get him to resort to \emph{Cannibalism!} (shouted by Hufflepuff), and Slytherin was remarking on how nice it was that Harry’s ethics were flexible when it came to important goals like maintaining his relationship with Professor Quirrell.)

After the waitress had closed the door behind her, Professor Quirrell waved a hand to slide home the locking bar, spoke the usual four Charms to ensure privacy, and then said, “An interesting question, Mr.~Potter. I wonder why you asked it?”

Harry kept his face steady. “I was looking up some facts about the Patronus Charm earlier,” he said. “According to \emph{The Patronus Charm: Wizards Who Could and Couldn’t,} it turns out that Godric couldn’t and Salazar could. I was surprised, so I looked up the reference, in \emph{Four Lives of Power.} And \emph{then} I discovered that Salazar Slytherin could supposedly talk to snakes.” (Temporal sequence wasn’t the same as causation, it wasn’t Harry’s fault if Professor Quirrell missed that.) “Further research turned up an old story about a mother goddess type who could talk to flying squirrels. I was a bit worried about the prospect of eating something that could talk.”

And Harry took a casual sip of his water—

—just as Professor Quirrell said, “Mr.~Potter, would I be correct in guessing that you are also a Parselmouth?”

When Harry was done coughing, he set his glass of water back down on the table, fixed his gaze on Professor Quirrell’s chin rather than looking him in the eyes, and said, “So you are able to perform Legilimency through my Occlumency barriers, then.”

Professor Quirrell was grinning widely. “I shall take that as a compliment, Mr.~Potter, but no.”

“I’m not buying this anymore,” Harry said. “There’s no \emph{way} you came to that conclusion based on that evidence.”

“Of course not,” Professor Quirrell said equably. “I had planned to ask you that question today in any case, and simply chose an opportune moment. I have suspected since December, in fact—”

“\emph{December?}” said Harry. “I found out \emph{yesterday!}”

“Ah, so you did not realize the Sorting Hat’s message to you was in Parseltongue?”

The Defense Professor had timed it exactly right the second time, too, just as Harry was taking a gulp of water to clear out his throat from the first coughing fit.

Harry \emph{hadn’t} realized, not until just now. Of course it was obvious the instant Pofessor Quirrell said it. Right, Professor McGonagall had even \emph{told} him not to talk to snakes where anyone could see him, but he’d thought she’d meant not to be seen talking to any statues or architectural features in Hogwarts that looked like snakes. Double illusion of transparency, he’d thought he’d understood her, she’d thought he’d understood her—but \emph{how} the \emph{hell—}

“So,” Harry said, “you performed Legilimency on me during my first Defense class, to find out what happened with the Sorting Hat—”

“Then I would not have found out in December.” Professor Quirell leaned back, smiling. “This is not a puzzle you can solve on your own, Mr.~Potter, so I will reveal the answer. Over the winter holiday, I was alerted to the fact that the Headmaster had filed a request for a closed judicial panel to review the case of one Mr.~Rubeus Hagrid, whom you know as the Keeper of Keys and Grounds at Hogwarts, and who was accused of the murder of Abigail Myrtle in 1943.”

“Oh, of course,” said Harry, “that makes it downright \emph{obvious} that I’m a Parselmouth. Professor, \emph{what} the sweet slithering snakes—”

“The \emph{other} suspect for that murder was Slytherin’s Monster, the legendary inhabitant of Slytherin’s Chamber of Secrets. Which is why certain sources alerted me to the fact, and why it caught my attention sufficiently that I spent a good deal of bribe money to learn the details of the case. Now in point of fact, Mr.~Potter, Mr.~Hagrid is innocent. Ridiculously obviously innocent. He is the most blatantly innocent bystander to be convicted by the magical British legal system since Grindelwald’s Confunding of Neville Chamberlain was pinned on Amanda Knox. Headmaster Dippet prompted a student puppet to accuse Mr.~Hagrid because Dippet needed a scapegoat to take the blame for the death of Miss Myrtle, and our marvelous justice system agreed that this was plausible enough to warrant Mr.~Hagrid’s expulsion and the snapping of his wand. Our current Headmaster needs merely provide some new item of evidence significant enough to reconvene the case; and with Dumbledore applying pressure instead of Dippet, the result is a foregone conclusion. Lucius Malfoy has no particular reason to fear Mr.~Hagrid’s vindication; thus Lucius Malfoy will only resist to the extent that he can do so costlessly in order to impose costs on Dumbledore, and Dumbledore is clearly willing to prosecute the case regardless.”

Professor Quirrell took a sip of his water. “But I digress. The new evidence that the Headmaster promises to provide is to exhibit a previously undetected spell on the Sorting Hat, which, the Headmaster asserts, he has personally determined to respond only to Slytherins who are also Parselmouths. The Headmaster further argues that this favors the interpretation that the Chamber of Secrets was indeed opened in 1943, approximately the right time frame for He-Who-Must-Not-Be-Named, a known Parselmouth, to have attended Hogwarts. It is a rather questionable logic, but a judicial panel may rule that it swings the case far enough to bring Mr.~Hagrid’s guilt into doubt, if they can manage to keep a straight face as they say it. And now we come to the key question: \emph{how} did the Headmaster discover this hidden spell on the Sorting Hat?”

Professor Quirrell was smiling thinly now. “Well now, let us suppose that there was a Parselmouth in this year’s crop of students, a potential Heir of Slytherin. You must admit, Mr.~Potter, that you stand out as a possibility whenever extraordinary people are considered. And if I then further ask myself which new Slytherin would be most likely to have his mental privacy invaded by the Headmaster, specifically hunting the memories of his Sorting, why, you stand out even more.” The smile vanished. “So you see, Mr.~Potter, it was not \emph{I} who invaded your mind, though I will not ask you to apologize. It is not your fault that you believed Dumbledore’s protestations of respecting your mental privacy.”

“My sincere apologies,” Harry said, keeping his face expressionless. The rigid control was a confession in its own right, as was the sweat beading his forehead; but he didn’t think the Defense Professor would take any evidence from that. Professor Quirrell would just think Harry was nervous at having been discovered as the Heir of Slytherin. Rather than being nervous that Professor Quirrell might realize that Harry had deliberately betrayed Slytherin’s secret...\ which itself was no longer seeming like such a smart move.

“So, Mr.~Potter. Any progress on finding the Chamber of Secrets?”

\emph{No,} thought Harry. But to maintain plausible deniability, you needed a general policy of sometimes evading questions even when you had nothing to hide... “With respect, Professor Quirrell, if I had made such progress, it is not \emph{quite} obvious to me that I should tell you about it.”

Professor Quirrell sipped from his own waterglass again. “Well then, Mr.~Potter, I shall freely tell you what I know or suspect. First, I believe the Chamber of Secrets is real, as is Slytherin’s Monster. Miss Myrtle’s death was not discovered until hours after her demise, even though the wards should have alerted the Headmaster instantly. Therefore her murder was performed either by Headmaster Dippet, which is unlikely, or by some entity which Salazar Slytherin keyed into his wards at a higher level than the Headmaster himself. Second, I suspect that contrary to popular legend, the purpose of Slytherin’s Monster was \emph{not} to rid Hogwarts of Muggleborns. Unless Slytherin’s Monster were powerful enough to defeat the Headmaster of Hogwarts and all the teachers, it could not triumph by force. Multiple murders in secrecy would result in the school’s closure, as nearly happened in 1943, or in the placing of new wards. So why Slytherin’s Monster, Mr.~Potter? What true purpose does it serve?”

“Ah...” Harry dropped his gaze to his waterglass and tried to think. “To kill anyone who got into the Chamber and didn’t belong there—”

“A monster powerful enough to defeat a team of wizards that had broken past the best wards Salazar could place on his Chamber? Unlikely.”

Harry was feeling a bit pressured now. “Well, it’s called the Chamber of Secrets, so maybe the Monster has a secret, or \emph{is} a secret?” For that matter, just what sort of secrets were in the Chamber of Secrets in the first place? Harry hadn’t done a lot of research on the subject, in part because he’d gotten the impression that nobody knew anything—

Professor Quirrell was smiling. “Why not just write the secret down?”

“Ahhh...” said Harry. “Because if the Monster spoke Parseltongue, that would ensure that only a true descendant of Slytherin could hear the secret?”

“Easy enough to key the wards on the Chamber to a phrase spoken in Parseltongue. Why go to the trouble of creating Slytherin’s Monster? It cannot have been easy to create a creature with a lifespan of centuries. Come, Mr.~Potter, it should be obvious; what are the secrets that can be told from one living mind to another, but never written down?”

Harry saw it then, with a burst of adrenaline that started his heart racing, his breath coming faster. “\emph{Oh.}”

Salazar Slytherin had been very cunning indeed. Cunning enough to come up with a way to bypass the Interdict of Merlin.

Powerful wizardries couldn’t be transmitted through books or ghosts, but if you could create a long-lived enough sentient creature with a good enough memory—

“It seems very probable to me,” said Professor Quirrell, “that He-Who-Must-Not-Be-Named began his climb to power with secrets obtained from Slytherin’s Monster. That Salazar’s lost knowledge is the source of You-Know-Who’s extraordinarily powerful wizardry. Hence my interest in the Chamber of Secrets and the case of Mr.~Hagrid.”

“I \emph{see},” Harry said. And if \emph{he,} Harry, could find Salazar’s Chamber of Secrets...\ then all of the lost knowledge that Lord Voldemort had obtained would be \emph{his} as well.

Yes. That was \emph{just} how the story should go.

Add in Harry’s superior intelligence and some original magical research and some Muggle rocket launchers, and the resulting fight would be completely one-sided, which was exactly how Harry wanted it.

Harry was grinning now, a very evil grin. \emph{New priority: Find everything in Hogwarts that looks remotely like a snake and try speaking to it. Starting with everything you’ve already tried, only this time be sure to use Parseltongue instead of English—get Draco to let you into the Slytherin dorms—}

“Don’t become too excited, Mr.~Potter,” said Professor Quirrell. His own face had become expressionless, now. “You must \emph{continue} thinking. What were the Dark Lord’s parting words to Slytherin’s Monster?”

“\emph{What?}” Harry said. “How could either of us possibly know that?”

“Visualize the scene, Mr.~Potter. Let your imagination fill in the details. Slytherin’s Monster—probably some great serpent, so that only a Parselmouth may speak to it—has finished imparting all of the knowledge it possesses to He-Who-Must-Not-Be-Named. It conveys to him Salazar’s final benediction, and warns him that the Chamber of Secrets must now remain closed until the next descendant of Salazar should prove cunning enough to open it. And he who will become the Dark Lord nods, and says to it—”

“Avada Kedavra,” said Harry, suddenly feeling sick to his stomach.

“Rule Twelve,” Professor Quirrell said quietly. “Never leave the source of your power lying around where someone else can find it.”

Harry’s gaze dropped to the tablecloth, which had decorated itself in a mournful pattern of black flowers and shadows. Somehow that seemed...\ too sad to be imagined, Slytherin’s great snake had only wanted to help Lord Voldemort, and Lord Voldemort had just...\ there was something unbearably sorrowful about it, what sort of person would \emph{do} that to a being who’d offered them nothing but friendship... “\emph{Do} you think the Dark Lord would have—”

“Yes,” Professor Quirrell said flatly. “He-Who-Must-Not-Be-Named left quite a trail of bodies behind him, Mr.~Potter; I doubt he would have omitted that one. If there were any artifacts left there that could be moved, the Dark Lord would have taken those with him as well. There might still be something worth seeing in the Chamber of Secrets, and to find it would prove yourself the true Heir of Slytherin. But do not raise your hopes too high. I suspect that all you will find is the remains of Slytherin’s Monster resting quietly in its grave.”

They sat in silence for a while.

“I could be wrong,” said Professor Quirrell. “In the end it is only a guess. But I did wish to warn you, Mr.~Potter, so that you would not be too sorely disappointed.”

Harry nodded shortly.

“One might even regret your infant self’s victory,” said Professor Quirrell. His smile twisted. “If only You-Know-Who had lived, you might have persuaded him to teach you some of the knowledge that would have been your heritage, from one Heir of Slytherin to another.” The smile twisted further, as though to mock the obvious impossibility, even given the premise.

\emph{Note to self,} thought Harry, with a slight chill and an edge of anger, \emph{make sure to extract my heritage out of the Dark Lord’s mind, one way or another.}

There was another silence. Professor Quirrell was looking at Harry as though waiting for him to ask something.

“Well,” said Harry, “so long as we’re on the topic, can I ask how you think the whole Parselmouth business actually—”

There came a knock at the door, then. Professor Quirrell raised a cautionary finger, then opened the door with a wave. The waitress entered, balancing a huge platter with their meals as though the whole assembly weighed nothing (which was in fact probably the case). She gave Professor Quirrell his bowl of green soup, and a glass of his usual Chianti; and set down before Harry a plate of small meat strips smothered in a heavy-looking sauce, plus a glass of his accustomed treacle soda. Then she bowed, managing to make it seem like sincere respect rather than perfunctory acknowledgment, and departed.

When she was gone, Professor Quirrell held up a finger for silence again, and drew his wand.

And then Professor Quirrell began performing a certain series of incantations that Harry recognized, making him take a sharp breath. It was the series and ordering that Mr.~Bester had used, the full set of twenty-seven spells that you would perform before discussing anything of truly great import.

If the discussion of the Chamber of Secrets \emph{hadn’t} counted as important—

When Professor Quirrell was done—he’d performed \emph{thirty} spells, three of which Harry hadn’t heard before—the Defense Professor said, “Now we shall not be interrupted for a time. Can you keep a secret, Mr.~Potter?”

Harry nodded.

“A serious secret, Mr.~Potter,” Professor Quirrell said. His eyes were intent, his face grave. “One which could potentially send me to Azkaban. Think about it before you reply.”

For a moment Harry didn’t even see why the question should be hard, given his growing collection of secrets. Then—

\emph{If this secret could send Professor Quirrell to Azkaban, that means he’s done something illegal...}

Harry’s brain performed a few calculations. Whatever the secret, Professor Quirrell did not think his illegal act would reflect badly on him in Harry’s eyes. There was no advantage to be gained from \emph{not} hearing it. And if it did reveal something wrong with Professor Quirrell, then it was very much to Harry’s advantage to know it, even if he had promised not to tell anyone.

“I never had very much respect for authority,” Harry said. “Legal and governmental authority included. I will keep your secret.”

Harry didn’t bother asking whether the revelation was worth the danger it would pose to Professor Quirrell. The Defense Professor wasn’t stupid.

“Then I must test whether you are truly a descendant of Salazar,” said Professor Quirrell, and stood up from his chair. Harry, prompted more by reflex and instinct than calculation, shoved himself up out of his own chair as well.

There was a blur, a shift, a sudden motion.

Harry aborted his panicked backward leap halfway through, leaving him windmilling his arms and trying not to fall over, a frantic flush of adrenaline running through him.

At the other end of the room swayed a snake a meter high, bright green and intricately banded in white and blue. Harry didn’t know enough snakelore to recognize it, but he knew that ‘brightly colored’ meant ‘poisonous’.

The constant sense of doom had diminished, ironically enough, after the Defense Professor of Hogwarts had turned into a venomous snake.

Harry swallowed hard and said, “Greetings—ah, hssss, no, ah, \emph{greetingss.}”

“\emph{Sso,}” hissed the snake. “\emph{You sspeak, I hear. I sspeak, you hear?}”

“\emph{Yess, I hear,}” hissed Harry. “\emph{You are an Animaguss?}”

“\emph{Obvioussly,}” hissed the snake. “\emph{Thirty-sseven ruless, number thirty-four: Become Animaguss. All ssensible people do, if can. Thuss,} \emph{very rare.}” The snake’s eyes were flat surfaces ensconced within dark pits, sharp black pupils in dark gray fields. “\emph{This iss mosst ssecure way to sspeak. You ssee? No otherss undersstand uss.}”

“\emph{Even if they are ssnake Animagi?}”

“\emph{Not unlesss heir of Sslytherin willss.}” The snake gave a series of short hisses which Harry’s brain translated as sardonic laughter. “\emph{Sslytherin not sstupid. Ssnake Animaguss not ssame as Parsselmouth. Would be huge flaw in sscheme.}”

Well \emph{that} definitely argued that Parseltongue was personal magic, not snakes being sentient beings with a learnable language—

“\emph{I am not regisstered,}” hissed the snake. The dark pits of its eyes stared at Harry. “\emph{Animaguss musst be regisstered. Penalty is two yearss imprissonment. Will you keep my ssecret, boy?}”

“\emph{Yess,}” hissed Harry. “\emph{Would never break promisse.}”

The snake seemed to hold still, as though in shock, and then began to sway again. “\emph{We come here next in sseven dayss. Bring cloak to passs unsseen, bring hourglasss to move through time—}”

“\emph{You know?}” hissed Harry in shock. “\emph{How—}”

Again the series of short quick hisses that translated as sardonic laughter. “\emph{You arrive in my firsst classs while sstill in other classs, sstrike down enemy with pie, two ballss of memory—}”

“\emph{Never mind,}” hissed Harry. “\emph{Sstupid question, forgot you were ssmart.}”

“\emph{Foolissh thing to forget,}” said the snake, but the hiss did not seem offended.

“\emph{Hourglasss is resstricted,}” Harry said. “\emph{Cannot usse until ninth hour.}”

The snake twitched its head, a snakish nod. “\emph{Many resstrictionss. Locked to your usse only, cannot be sstolen. Cannot transsport other humanss. But ssnake carried in pouch, I ssuspect will go with. Think posssible to hold hourglasss motionlesss within sshell, without dissturbing wardss, while you turn sshell around it. We will tesst in sseven dayss. Will not sspeak of planss beyond thiss. You ssay nothing, to no one. Give no ssign of expectancy, none. Undersstand?}”

Harry nodded.

“\emph{Ansswer in sspeech.}”

“\emph{Yess.}”

“\emph{Will do as I ssaid?}”

“\emph{Yess. But,”} Harry gave a wobbling rasp that was how his mind had translated a hesitant ‘Ahhh’ into snakish, “\emph{I do not promisse to do whatever thiss iss, you have not ssaid—}”

The snake performed a shiver that Harry’s mind translated as a severe glare. “\emph{Of coursse not. Will disscusss sspecificss at next meeting.}”

The blur and motion reversed itself, and Professor Quirrell was standing there once more. For a moment the Defense Professor himself seemed to sway, as the snake had swayed, and his eyes seemed cold and flat; and then his shoulders straightened and he was human once more.

And the aura of doom had returned.

Professor Quirrell’s chair scooted back for him, and he sat down in it. “No sense in letting this go to waste,” Professor Quirrell said as he picked up his spoon, “though at the moment I would much prefer a live mouse. One can never quite disentangle the mind from the body it wears, you see...”

Harry slowly took his seat and began eating.
\sbreak
“So the line of Salazar did not die with You-Know-Who after all,” said Professor Quirrell after a time. “It would seem that rumors have already begun to spread, among our fine student body, that you are Dark; I wonder what they would think, if they knew that.”

“Or if they knew that I had destroyed a Dementor,” Harry said, and shrugged. “I figure all the fuss will blow over over the next time I do something interesting. Hermione is having trouble, though, and I was wondering if you might have any suggestions for her.”

The Defense Professor ate several spoonfuls of soup in silence, then; and when he spoke again, his voice was oddly flat. “You really care about that girl.”

“Yes,” Harry said quietly.

“I suppose that is why she was able to bring you out of your Dementation?”

“More or less,” Harry said. The statement was true in a way, just not exact; it was not that his Demented self had cared, but that it had been confused.

“I did not have any friends like that when I was young.” Still the same emotionless voice. “What would have become of you, I wonder, if you had been alone?”

Harry shivered before he could stop himself.

“You must be feeling grateful to her.”

Harry just nodded. Not quite exact, but true.

“Then here is what I might have done at your age, if there had been anyone to do it for—”
