\chapter{Taboo Tradeoffs, Final}

\lettrine{P}{hoenix} travel was a sensation entirely unlike Apparition or portkeys. You caught on fire—you definitely felt yourself catching on fire, even though there was no pain—and instead of burning to ashes, the fire burned all the way through you and you \emph{became} fire, and then you went out in one place and blazed up in another. It didn’t sicken the stomach like portkeys or Apparition, but it was a rather unnerving experience nonetheless. If the underlying truth of phoenix travel really was becoming a specific instantiation of a more general Fire, then that seemed to hint you could potentially burn \emph{anywhere}—even in the distant past, or in another universe, or in two places at once. You might go out in one place and blaze up in a hundred others, and the you who arrived at Hogwarts would never know the difference. Though Harry had read what he could about phoenixes, trying to figure out how to get one of his own, and there’d been no hint of anything remotely like that capability.

Harry caught fire and went out and blazed up somewhere else; and just like that he, and the Headmaster, and the unconscious form of Hermione Granger held in the Headmaster’s arms, were occupying another place; with Fawkes above them all. A calm, warm room of bright stone columns, skylit on all four sides, populated by white beds in long rows, four of which had silencing veils drawn around them, and the rest empty.

In one corner of Harry’s vision, a surprised-looking Madam Pomfrey was turning toward them. Dumbledore seemed to pay the senior healer no heed, as he carefully laid down Hermione on an unoccupied white bed.

From a distant corner there was a flash of green, and from out of a fireplace strode Professor McGonagall, brushing herself off slightly from the Floo ashes.

The old wizard turned from the bed and reached one of his arms around Harry again; and then the Boy-Who-Lived and his wizard vanished in another burst of fire.
\sbreak
When Harry had fully lit up again he was standing in the Headmaster’s office, amid the noises of a dozen dozen inexplicable gidgets.

The young boy took a step away from the old wizard and then turned on him, emerald and sapphire eyes meeting.

The two of them did not speak for a time, looking at each other; as though all they had to speak could be said only by stares, and not said in any other way.

In time the boy enunciated words slowly and precisely.

“I cannot believe that a phoenix is still upon your shoulder.”

“The phoenix chooses but once,” said the old wizard. “They might perhaps leave a master who chooses evil over good; they will not leave a master forced to choose between one good and another. Phoenixes are not arrogant. They know the limits of their own wisdom.” Stern indeed, that ancient gaze. “Unlike you, Harry.”

“Choose between one good and another,” Harry echoed flatly. “Like Hermione Granger’s life, versus a hundred thousand Galleons.” The rage and indignation Harry wanted to put into his voice wasn’t quite there, for some reason, maybe because—

“You are hardly in a position to speak to me of that, Harry Potter.” The Headmaster’s voice was deceptively soft. “Or what was that look of reluctance that I saw upon your face, there in the Most Ancient Hall?”

The sense of inward hollowness grew worse. “I was looking for other alternatives,” Harry bit out. “Some way to save her that \emph{didn’t} lose the money.”

\emph{Wow,} said Ravenclaw. \emph{You just told an outright lie. Not only that, I think you actually} believed \emph{it for the seconds it took to say it. That’s kinda scary.}

“\emph{Is} that what you were thinking, Harry?” The blue eyes were keen, and there was a terrifying moment when Harry wondered if the world’s most powerful wizard could see right past his Occlumency barriers.

“\emph{Yes,}” Harry said, “I flinched away from the pain of losing all the money in my vault. But I \emph{did} it! \emph{That’s} what counts! And \emph{you}—” The indignation that had faltered out of Harry’s voice returned. “You \emph{actually} put a price on Hermione Granger’s life, and you put it below a hundred thousand Galleons!”

“Oh?” the old wizard said softly. “And what price do you put on her life, then? A million Galleons?”

“Are you familiar with the economic concept of ‘replacement value’?” The words were spilling from Harry’s lips almost faster than he could consider them. “Hermione’s replacement value is \emph{infinite!} There’s nowhere I can go to buy another one!”

\emph{Now you’re just talking mathematical nonsense,} said Slytherin. \emph{Ravenclaw, back me up here?}

“Is Minerva’s life also of infinite worth?” the old wizard said harshly. “Would you sacrifice Minerva to save Hermione?”

“Yes and yes,” Harry snapped. “That’s part of Professor McGonagall’s job and she knows it.”

“Then Minerva’s value is not infinite,” said the old wizard, “for all that she is loved. There can only be one king upon a chessboard, Harry Potter, only one piece that you will sacrifice any other piece to save. And Hermione Granger is not that piece. Make no mistake, Harry Potter, this day you may well have lost your war.”

And if the old wizard’s words hadn’t hit quite so hard, and quite so close to home, Harry might not have said what he said then.

“Lucius was right,” Harry ground out. “You never had a wife, you never had a daughter, you’ve never had anything but war—”

The old wizard’s left hand closed hard upon Harry’s wrist, bony fingers digging into the still-developing muscle of Harry’s arm, and for a moment Harry was paralyzed with the shock of it, he had forgotten what it meant that adults were stronger.

Albus Dumbledore did not seem to notice. He only turned, dragging Harry with him, and moved forward in hard steps toward the wall of the room.

“\emph{Phoenix’s price.}”

Harry was pulled up along the black stairs.

“\emph{Phoenix’s fate.}”

The room of black pedestals, silver light falling on shattered wands.

“You think,” yelled Harry, after his lips unlocked, “that you can win any argument, just by standing here?”

The old wizard ignored him, dragging Harry across the room. His right hand, no longer holding his wand, grabbed up a vial of silver fluid—

Harry blinked in shock; the vial of silver fluid had been standing next to a picture of \emph{Dumbledore,} or so it had appeared to Harry in the brief moment before he was dragged past.

Past the end of all the pedestals, at the farthest part of the room, rose a great stone basin with runes carved into it that Harry didn’t recognize. The center was a shallow depression filled with transparent liquid, and into this the old wizard dumped the canister of silver fluid, which at once began to spread out, to swirl, to set the entire basin glowing eerie white.

The old wizard’s hand let go of Harry’s arm and gestured to the glowing basin, commanding harshly, “Look!”

As requested, Harry stared at the glowing water.

“Put your head into the Pensieve, Harry Potter.” The old wizard’s voice was stern.

Harry had heard that word before, but he couldn’t remember where. “What—does this do—”

“Memories,” the old wizard said. “You will see my memory. My oath that it is safe. Now look into the Pensieve, Ravenclaw, if you still care anything at all for your precious truth!”

That was a request that Harry could not deny, and he stepped forward and thrust his head into the glowing water.
\sbreak
\begin{em}
Harry was sitting behind the desk in the Headmaster’s office of Hogwarts, and his wrinkled hands that clutched at his head were spotted with age and white hairs.

“He is all that I have!” wept a voice, very strange was Dumbledore’s voice as Dumbledore himself remembered it, from the inside it seemed far less stern and wise. “The last of my family! All that I have left!”

No emotion had been allowed to pass through the Pensieve, only the physical sensation of seeming to speak the words. Harry heard the utter desolation in Dumbledore’s words, the sounds that seemed to come from Harry’s own throat, but Harry did not feel it beyond the hearing.

“You’ve got no choice,” said a harsh voice.

The eyes moved, the field of vision jumped to a man that Harry didn’t recognize, in clothing tinged with Auror crimson but made of solid leather with many pockets.

His right eye was overlarge, with an electric-blue pupil that constantly darted and moved.

“You cannot ask this of me, Alastor!” Dumbledore’s voice was wild. “Not this! Anything but this!”

“I’m not asking,” growled the man. “Voldie’s the one who’s asking, and you’re going to tell him no.”

“For money, Alastor?” Dumbledore’s voice was begging. “Only for money?”

“You ransom Aberforth, you lose the war,” the man said sharply. “That simple. One hundred thousand Galleons is nearly all we’ve got in the war-chest, and if you use it like this, it won’t be refilled. What’ll you do, try to convince the Potters to empty their vault like the Longbottoms already did? Voldie’s just going to kidnap someone else and make another demand. Alice, Minerva, anyone you care about, they’ll all be targets if you pay off the Death Eaters. That’s not the lesson you should be trying to teach them.”

“If I do this I will have no one. No one.” Dumbledore’s voice broke, the world tilted as the outlooking head fell down into the ancient hands, and awful sounds came from not-Harry’s throat as he began to sob like a child.

“Shall I tell Voldie’s messenger no?” said Alastor’s voice, now strangely gentle. “You don’t have to do it yourself, old friend.”

“No—I will say it myself—I must—”
\end{em}
\sbreak
The memory ended with a shock and Harry ripped his head out of the glowing water, gasping as though he’d been deprived of air.

The transition between scenes, between decade-old reality and present moment, was another jolt to Harry’s mind; in some fashion his immersion in the past had unanchored him. The broken old man sobbing in his office had been another person in another era, Harry had understood that much; someone softer—

Before it had all vanished like dissipating smoke, returning the \emph{now,} the present day.

Terrible and stern stood the ancient wizard, like he was carven from stone; beard woven of thread like iron, half-moon glasses like mirrors, and the pupils behind as sharp and unyielding as black diamond.

“Do you also wish to see my brother as he died under the Cruciatus?” said Albus Dumbledore. “Voldemort sent me that memory as well!”

“And that—” Harry was having trouble producing a voice, for the growing sickness in his chest. “\emph{That} was when—” The words seemed to burn in his throat, as the awful knowledge dawned on him, the horrible understanding. “That was when you burned Narcissa Malfoy alive in her own bedroom.”

Albus Dumbledore’s gaze was cold as he answered. “To that question only a fool would say yea or nay. What matters is that the Death Eaters believe I killed her, and that belief kept safe the families of all who served the Order of the Phoenix—until this day. Now do you understand what you have done? What you have done to your \emph{friends,} Harry Potter, and to any that stand with you?” The old wizard seemed to grow still taller and more terrible, as his voice rose louder. “You have made them all targets, and targets they will remain! Until you prove, the only way it can be proven, that you are no longer willing to pay such prices!”

“And is it true?” Harry said. There was a buzzing sensation filling him, his body growing more distant. “What Draco said, that Narcissa Malfoy never got her hands dirty, that she was only Lucius’s wife? She was an enabler, I get that, but I can’t back that deserving being \emph{burned alive}.”

“Nothing less would have convinced them that I was done with hesitation.” The old wizard’s voice brooked no question and no refusal. “Always I was too reluctant to do as I must, always it was others who paid the cost of my mercy. So Alastor told me from the beginning, but I did not listen to him. You, I expect, shall prove better at such decisions than I.”

“I’m surprised,” Harry said, amazed that his voice was almost steady. “I would have expected the Death Eaters to go after another Light family and start a cycle of escalating retaliation, if you didn’t get them all with your first strike.”

“If my opponent had been Lucius, perhaps.” Dumbledore’s eyes were like stones. “I am told that Voldemort laughed at the news, and proclaimed to his Death Eaters that I had finally grown, and was at last a worthy opponent. Perhaps he was right. After the day I condemned my brother to his death, I began to weigh those who followed me, balancing them one against another, asking who I would risk, and who I would sacrifice, to what end. It was strange how many fewer pieces I lost, once I knew what they were worth.”

Harry’s jaw seemed locked, like it took a massive effort to make his lips move. “But then it’s not like Lucius was deliberately taking Hermione for ransom,” Harry’s voice said thinly. “From Lucius’s perspective, someone else broke the truce first. So with that in mind, how many Galleons \emph{was} Hermione worth, exactly? Leaving aside the Danegeld thing, if it was just some ordinary threat to her life, how much should I have paid to save her? Ten thousand Galleons? Five thousand?”

The old wizard did not answer.

“It’s a funny thing,” Harry said, his voice wavering like something seen through underwater. “Do you know, the day I went in front of the Dementor, what my worst memory was? It was my parents dying. I heard their voices and everything.”

The old wizard’s eyes widened behind the half-moon glasses.

“And here’s the thing,” Harry said, “here’s the thing I’ve been thinking about over and over. The Dark Lord gave Lily Potter the chance to walk away. He said that she could flee. He \emph{told} her that dying in front of the crib wouldn’t save her baby. ‘Step aside, foolish woman, if you have any sense in you at all—’” An awful chill came over Harry as he spoke those words from his own lips, but he shook it off and continued. “And afterward I kept thinking, I couldn’t seem to stop myself from thinking, wasn’t the Dark Lord \emph{right?} If only Mother had stepped away. She tried to curse the Dark Lord but it was suicide, she had to have \emph{known} that it was suicide. Her choice wasn’t between her life and mine, her choice was for herself to live or for both of us to die! If she’d only done the logical thing and walked away, I mean, I love Mum too, but Lily Potter would be alive right now and she would be my mother!” Tears were blurring Harry’s eyes. “Only now I understand, I know what Mother must have felt. She \emph{couldn’t} step aside from the crib. She couldn’t! Love doesn’t walk away!”

It was like the old wizard had been struck, struck by a chisel that shattered him straight down the middle.

“What have I said?” the old wizard whispered. “What have I said to you?”

“I don’t know!” shouted Harry. “I wasn’t listening either!”

“I—I’m sorry, Harry—I—” The old wizard pressed his hands to his face, and Harry saw that Albus Dumbledore was weeping. “I should not have said, such things to you—I should not, have resented, your innocence—”

Harry stared at the wizard for another second, and then Harry turned and marched out of the black room, down the stairs, through the office—

“I really don’t know why you’re still on his shoulder,” Harry said to Fawkes.

—out the oaken door and into the endlessly turning spiral.
\sbreak
Harry had arrived in the Transfiguration classroom before anyone else, before even Professor McGonagall. There was Charms class earlier, for his year, but that he hadn’t even bothered trying to attend. Whether Professor McGonagall would make today’s class he didn’t know. There was something ominous about all the empty desks beside him, the absence at the board. As if he stood alone in Hogwarts, with all his friends departed.

According to the class schedule, today’s lesson was on sustained Transfigurations, all the rules of which Harry had learned by heart back when he was Transfiguring a huge rock into the small diamond that shone on his pinky finger. It would be a theoretical subject, rather than practical, for the rest of the class; which was a pity, because he could have used a dose of Transfiguration’s trance.

Harry noted distantly that his hand was trembling, to the point where he had trouble undoing the pouch’s drawstring as he drew forth the Transfiguration textbook.

\emph{You were monstrously unfair to Dumbledore,} said the voice Harry had been calling Slytherin, only now it also seemed to be the Voice of Economic Sensibility and maybe also Conscience.

Harry’s eyes dropped down to his textbook, but the section was so familiar it might as well have been a blank parchment.

\emph{Dumbledore fought a war against a Dark Lord who deliberately set out to break him in the cruelest possible way. He had to choose between losing his war and his brother. Albus Dumbledore knows, he learned in the worst possible way, that there are limits to the value of one life; and it almost broke his sanity to admit it. But you, Harry Potter—\emph{you} already knew better.}

“Shut up,” the boy whispered to the empty Transfiguration classroom, though there was nobody there to hear it.

\emph{You’d already read about Philip Tetlock’s experiments on people asked to trade off a sacred value against a secular one, like a hospital administrator who has to choose between spending a million dollars on a kidney to save a five-year-old, and spending the million dollars to buy other hospital equipment or pay physician salaries. And the subjects in the experiment became indignant and wanted to punish the hospital administrator for even thinking about the choice. Do you remember reading about that, Harry Potter? Do you remember thinking how very stupid that was, since if hospital equipment and doctor salaries didn’t also save lives, there would be no point in having hospitals or doctors? Should the hospital administrator have paid a billion pounds for that liver, even if it meant the hospital going bankrupt the next day?}

“Shut up!” the boy whispered.

\emph{Every time you spend money in order to save a life with some probability, you establish a lower bound on the monetary value of a life. Every time you refuse to spend money to save a life with some probability, you establish an upper bound on the monetary value of life. If your upper bounds and lower bounds are inconsistent, it means you could move money from one place to another, and save more lives at the same cost. So if you want to use a bounded amount of money to save as many lives as possible, your choices must be consistent with} some \emph{monetary value assigned to a human life; if not then you could reshuffle the same money and do better. How very sad, how very hollow the indignation, of those who refuse to say that money and life can ever be compared, when all they’re doing is forbidding the strategy that saves the most people, for the sake of pretentious moral grandstanding...}

Harry’s head dropped into his hands.

\emph{You} knew \emph{that, and you still said what you did to Dumbledore.}

\emph{You deliberately} tried \emph{to hurt Dumbledore’s feelings.}

He’s \emph{never tried to hurt} you, \emph{Harry Potter, not once.}

Harry’s head dropped into his hands.

Why had Harry said what he’d said, to a sad old ancient wizard who’d fought hard and endured more than anyone should ever have to endure? Even if the old wizard was wrong, did he deserve to be hurt for it, after all that had happened to him? Why was there a part of him that seemed to get angry at the old wizard beyond reason, lashing out at him harder than Harry had ever hit anyone, without thought of moderation once the rage had been raised, only to quiet as soon as Harry left his presence?

\emph{Is it because you know Dumbledore won’t fight back? That no matter what you say to him, however unfair, he’ll never use his own power against you, he’ll never treat you the way you treat him? Is this the way you treat people when you know they won’t hit back? James Potter’s bullying genes, manifesting at last?}

Harry closed his eyes.

Like the Sorting Hat speaking inside his head—

\emph{What is the real reason for your anger?}

\emph{What do you fear?}

A whirlwind of images seemed to flash through Harry’s mind, then, the past Dumbledore weeping into his hands; the present form of the old wizard, standing tall and terrible; a vision of Hermione screaming in her chains, in the metal chair, as Harry abandoned her to the Dementors; and an imagination of a woman with long white hair (had she looked like her husband?) falling amid the flames of her bedroom, as a wand was held upon her and orange light reflected from half-moon glasses.

Albus Dumbledore had seemed to think that Harry would be better at that sort of thing than him.

And Harry knew that he probably would be. He knew the math, after all.

But it was understood, somehow it was understood, that utilitarian ethicists didn’t \emph{actually} rob banks so they could give the money to the poor. The end result of throwing away all ethical constraint wouldn’t \emph{actually} be sunshine and roses and happiness for all. The prescription of consequentialism was to take the action that led to the best net consequences, not actions that had one positive consequence and wrecked everything else along the way. Expected utility maximizers were allowed to take common sense into account, when they were calculating their expectations.

Somehow Harry had understood that, even before anyone else had warned him he’d understood. Before he’d read about Vladimir Lenin or the history of the French Revolution, he’d known. It might have been his earliest science fiction books warning him about people with good intentions, or maybe Harry had just seen the logic for himself. Somehow he’d known from the very beginning, that if he stepped outside his ethics \emph{whenever there was a reason,} the end result wouldn’t be good.

A final image came to him, then: Lily Potter standing in front of her baby’s crib and measuring the intervals between outcomes: the final outcome if she stayed and tried to curse her enemy (dead Lily, dead Harry), the final outcome if she walked away (live Lily, dead Harry), weighing the expected utilities, and making the only sensible choice.

She would’ve been Harry’s mother if she had.

“But human beings can’t live like that,” the boy’s lips whispered to the empty classroom. “Human beings can’t live like that.”
