\partchapter{Self-Actualization}{III}

\lettrine{H}{ermione} wasn’t feeling very nice right now, or Good either, there was a hot ball of anger burning inside her and she wondered if this was something like Harry’s darkness (though it probably wasn’t even close) and she shouldn’t have felt that way over some silly little game but—

Her whole army. Two soldiers had beaten her whole army. That was what she’d been told after she woke up.

It was a little too much.

“Well,” Professor Quirrell said. From up close the Defense Professor didn’t look quite as healthy as he had the last time she’d been in his office; his skin looked paler, and he moved a little slower. His expression was as stern as ever, and his gaze as penetrating; his fingers tapped sharply on his desk, rap-rap. “I would guess that of the three of you, only Mr.~Malfoy has guessed why I’ve asked you here.”

“Something to do with Noble and Most Ancient Houses?” said Harry from beside her, sounding puzzled. “I didn’t violate some kind of crazy law by firing on Daphne, did I?”

“Not quite,” the man said with heavy irony. “Since Miss Greengrass did not invoke the correct dueling forms, she is not entitled to demand that you be stripped of your House name. Although of course I would not have permitted a formal duel. Wars do not respect such rules.” The Defense Professor leaned forward and rested his chin on steepled hands, as though sitting upright had already tired him. His eyes gazed at them, sharp and dangerous. “General Malfoy. Why did I call you here?”

“General Potter against the two of us isn’t a fair fight anymore,” Draco Malfoy said in a quiet voice.

“\emph{What?}” blurted Hermione. “We almost \emph{had} them, if Daphne hadn’t fainted—”

“Miss Greengrass did not faint from magical exhaustion,” Professor Quirrell said dryly. “Mr.~Potter shot her in the back with a Sleep Hex while your soldiers were distracted by the sight of their general flying into a wall. But congratulations nonetheless, Miss Granger, on \emph{almost} defeating two Chaotic Legionnaires with a mere twenty-four Sunshine Soldiers.”

The blood flaming in her cheeks grew a little hotter. “That—that was just—if I’d only figured out he was wearing armor—”

Professor Quirrell gazed at her from over touched fingers. “Of course there are ways you \emph{could} have won, Miss Granger. There always are, in every lost battle. The world around us redounds with opportunities, explodes with opportunities, which nearly all folk ignore because it would require them to violate a habit of thought; a thousand Hufflepuff bones waiting to be sharpened into spears. If you had thought to try a \emph{Finite Incantatem} on general principles, you would have dispelled Mr.~Potter’s suit of chainmail and everything else he was wearing except his underwear, which leads me to suspect that Mr.~Potter did not quite realize his own vulnerability. Or you could have had your soldiers swarm Mr.~Potter and Mr.~Longbottom and physically wrest the wands from their hands. Mr.~Malfoy’s own response was not what I would term \emph{well-reasoned,} but at least he did not wholly ignore his thousand alternatives.” A sardonic smile. “But you, Miss Granger, had the misfortune to remember how to cast the Stunning Hex, and so you did not search your excellent memory for a dozen easier spells that might have proved efficacious. And you pinned all your army’s hopes on your own person, so they lost spirit when you fell. Afterward they continued to cast their futile Sleep Hexes, governed by the habits of fighting that had been trained into them, unable to break the pattern as Mr.~Malfoy did. I cannot quite comprehend what goes through people’s minds when they repeat the same failed strategy over and over, but apparently it is an astonishingly rare realization that you can try something else. And so the Sunshine Regiment was wiped out by two soldiers.” The Defense Professor grinned mirthlessly. “One perceives certain similarities to how fifty Death Eaters dominated all of magical Britain, and how our much-loved Ministry continues in its rule.”

The Defense Professor sighed. “\emph{Nonetheless,} Miss Granger, the fact remains that this is not the first such defeat for you. In the previous battle, you and Mr.~Malfoy united your forces, and yet you were fought to a standstill, so that you and Mr.~Malfoy had to pursue Mr.~Potter onto the roof. The Chaos Legion has now demonstrated, twice in succession, military strength equal to both other armies combined. This leaves me no choice. General Potter, you will select eight soldiers from your army, including at least one Chaotic Lieutenant, to be divided among Dragon Army and the Sunshine Regiment—”

“\emph{What?}” Hermione burst out again, she glanced over at the other generals and saw that Harry looked as shocked as her, while Draco Malfoy only looked resigned.

“General Potter is stronger than both of you together,” Professor Quirrell said with calm precision. “Your contest is over, he has won, and it is time to rebalance the three armies to present him with a renewed challenge.”

“\emph{Professor Quirrell!}” said Harry. “I didn’t—”

“This is my decision as the Professor of Battle Magic at the Hogwarts School of Witchcraft and Wizardry and it is not subject to negotiation.” The words were still precise, but the look in Professor Quirrell’s eyes chilled Hermione’s blood, even though he was glaring at Harry and not at her. “And I find it \emph{suspicious}, Mr.~Potter, that the moment you wished to isolate Miss Granger and Mr.~Malfoy and force them to chase you onto the roof, you were able to annihilate just exactly as much of their united force as you pleased. Indeed, that is the level of performance I \emph{expected} of you since the start of this year, and I am \emph{annoyed} to discover that you have been holding back in my classes this entire time! I have seen what you can truly do, Mr.~Potter. You are far beyond the point where Mr.~Malfoy or Miss Granger can fight you on an equal level, and you will not be permitted to pretend otherwise. This, Mr.~Potter, I tell you in my capacity as your professor: For you to learn to your full potential, you must exercise your full abilities and not hold back for \emph{any} reason—particularly not childish frets over what your friends might think!”
\sbreak
She left the Defense Professor’s office with a larger army, and less dignity, and feeling a lot like a sad little bug that had just been squished, and trying very very hard not to cry.

“I \emph{wasn’t} holding back!” Harry said as soon as they turned the first corner away from Professor Quirrell’s office, the moment the wooden door faded out of sight behind the stone walls. “I wasn’t pretending, I never \emph{let} either of you win!”

She didn’t answer, couldn’t answer, it would all break loose if she tried to say a word.

“Really?” said Draco Malfoy. The Dragon General still had that air of resignation. “Because Quirrell’s right, you know, it’s\emph{ suspicious} that you could beat nearly everyone in both our armies as soon as you wanted to make us chase you onto the roof. And didn’t you say something then, Potter, about us needing to beat you when you were fighting for real?”

The burning sensation was creeping up her throat, and when it reached her eyes she would burst into tears, and from then on she would be just a crying little girl to both of them.

“That—” Harry’s voice said urgently, she wasn’t looking at him but his voice sounded like he had his head turned toward her. “That was—I tried a lot harder that time, there was an important reason, I \emph{had} to, so I used a whole bunch of tricks I’d been saving up—and—”

She’d always been trying her hardest, every time.

“—and I, I let out a side of myself I wouldn’t usually use for something like Defense class—”

So if she ever got close to winning against Harry when it \emph{really} mattered, he could just go into his dark side and crush her, was that it?

...of course it was. She couldn’t even \emph{look} Harry in the eyes when he was being scary, how had she ever thought she could beat him for real?

The corridor forked, and Harry Potter and Draco Malfoy went left toward a staircase that climbed to the second floor, and she went right instead, she didn’t even know where that passage went but right now she’d rather be lost in the castle.

“Excuse me, Draco,” said Harry’s voice, and then there was a pattering of footsteps behind her.

“Leave me alone,” she said, it came out sounding stern but then she had to shut her mouth and press her lips together tightly and hold her breath to stop it all from coming out.

That boy just kept on coming, and ran around her and put himself in front of her, because he was stupid that was why, and Harry said, his voice now a high and desperate whisper, “I didn’t run away when \emph{you} were beating \emph{me} in all my classes except broomstick riding!”

He didn’t understand, and he would never understand, Harry Potter would never understand, because no matter what contest he lost he would still be the Boy-Who-Lived, if you were Harry Potter and Hermione Granger was beating you then it meant everyone was expecting you to rise to the challenge, if you were Hermione Granger and Harry Potter was beating you that meant you were just no one.

“It’s not fair,” she said, her voice was shaking but she wasn’t crying yet, not yet, “\emph{I} shouldn’t have to fight your dark side, I’m just—I’m only—” \emph{I’m only twelve,} that was what she thought then.

“I only used my dark side \emph{once} and that was—when I \emph{had} to!”

“So today you beat my \emph{whole army} being just Harry?” She still wasn’t crying yet, and she wondered what her face looked like right now, if she looked like an angry Hermione or a sad one.

“I—” Harry said. His voice got a little lower, “I wasn’t...\ really \emph{expecting} to win, that time, I know I said I was invincible but that was just to try to scare you, I really just thought we’d slow you down for a bit—”

She started walking again, walked right past him, and as she passed Harry’s face tightened up like \emph{he} was going to cry.

“Is Professor Quirrell right?” came a high desperate whisper from behind her. “If I have you for a friend, will I always be afraid to do better because I know it will hurt your feelings? That’s not fair, Hermione!”

She took a breath and held it and ran, her feet pattering across the stone as fast as they could, running as fast as she dared with her vision all blurry, ran so that no one would hear her, and this time Harry didn’t follow.
\sbreak
Minerva was going over the Transfiguration parchment due Monday, and had just marked down to negative two hundred points a fifth-year parchment with an error that could have potentially killed someone. During her first year as a professor she’d been indignant at the folly of older students, now she was just resigned. Some people not only never learned, they never noticed that they were hopeless, they stayed bright and eager and kept on trying. Sometimes they believed you when you told them, before they left Hogwarts, that they must \emph{never} try anything unusual, give up free Transfiguration and use the art only through established Charms; and sometimes...\ they didn’t.

She was in the middle of trying to unravel a particularly convoluted answer when a knock at the door disrupted her thoughts; and it wasn’t her office hours, but it had only taken a very short time as Head of Gryffindor House for her to learn to suspend judgment. You could always deduct House points \emph{afterward.}

“Come in,” she said in a crisp voice.

The young girl who entered her office had clearly been crying, and then afterward had washed her face in hopes it wouldn’t show—

“Miss Granger!” said Professor McGonagall. It had taken her a moment to recognize that face with its eyes reddened and cheeks puffed. “What happened?”

“Professor,” said the young girl in a wavering voice, “you said that if I was ever worried or uncomfortable about anything, I should come to you at once—”

“Yes,” said Professor McGonagall, “now what \emph{happened?}”

The girl started to explain—
\sbreak
Hermione stood still and the stairs turned around her, a revolving helix that shouldn’t have taken her anywhere at all, and instead bore her continuously \emph{upward.} Hermione thought it seemed like the Enchantment of the Endless Stair, which had been invented in 1733 by the wizard Arram Sabeti who’d lived on top of Mount Everest in the days when no Muggles could climb it. Only that couldn’t be right because Hogwarts was much older—maybe the enchantment had been \emph{re}invented?

She should’ve been frightened, should’ve been nervous about her second meeting with the Headmaster.

She \emph{was}, in fact, frightened and nervous about her second meeting with the Headmaster.

Only Hermione Granger had been thinking; she’d been thinking a lot, after she hadn’t been able to run any further and had slid down against the wall with her lungs on fire, thinking while she curled up in a ball with her back against the chilly stone wall and her legs drawn up and crying.

Even if she lost to Harry Potter she was never, ever going to lose to Draco Malfoy, that was just totally \emph{absolutely} unacceptable, and Professor Quirrell had praised General Malfoy for not ignoring his thousand alternatives; and so after Hermione had cried herself out she’d thought of fourteen other spells she \emph{should’ve} tried against Harry and Neville, and then she’d started wondering if she might be making the same sort of mistake about other things; and that was how she’d ended up knocking on Professor McGonagall’s door. Not asking for help, right now Hermione didn’t have any plans she could ask for help \emph{with,} just telling Professor McGonagall everything, because when she’d thought of it that had seemed like one of the thousand alternatives that Professor Quirrell had been talking about.

And she’d told Professor McGonagall about how Harry Potter had changed since the day the phoenix had been on his shoulder, and about how people more and more seemed to see her as just something of Harry’s, and how it seemed like Harry was pulling farther and farther away from everyone else in their school year and went around with a sad air sometimes like he was losing something, and \emph{she didn’t know what to do anymore.}

And Professor McGonagall had told her that they needed to talk to the Headmaster.

And Hermione had felt worried, but then the thought had come to her that \emph{Harry Potter} wouldn’t have been scared of the Headmaster. Harry Potter would have just barged ahead doing whatever he was trying to do. Maybe (the thought had come to her) it was worth \emph{trying} to be like that, \emph{not} being scared, just doing whatever, and seeing what happened to her, it couldn’t really be worse.

The Endless Stair stopped turning.

The great oaken door in front of them with the brass griffin knocker opened without being touched.

Behind a black oaken desk with dozens of drawers facing in every direction, looking like it had drawers set \emph{inside} other drawers, was the silver-bearded Headmaster of Hogwarts upon his throne, Albus Percival Wulfric Brian Dumbledore, into whose gently twinkling eyes Hermione looked for around three seconds before she was distracted by all the other things in the room.

Some time later—she wasn’t sure how long but it was while she was trying to count the number of things in the room for the third time and \emph{still} not getting the same answer, even though her memory insisted that nothing had been added or removed—the Headmaster cleared his throat and said, “Miss Granger?”

Hermione’s head snapped around, and she felt a little heat in her cheeks; but Dumbledore didn’t appear annoyed with her at all, only serene, and with an inquiring look in those mild, half-glassed eyes.

“Hermione,” said Professor McGonagall, the older witch’s voice was gentle and her hand rested reassuringly on Hermione’s shoulder, “please tell the Headmaster what you said to me about Harry.”

Hermione began speaking, despite her newfound resolution her voice still stumbled a little with nervousness, as she described how Harry had changed in the last few weeks since Fawkes had been on his shoulder.

When she was done there was a pause, and then the Headmaster sighed. “I am sorry, Hermione Granger,” said Dumbledore. Those blue eyes had grown sadder as she spoke. “That is...\ unfortunate, but I cannot say it is unexpected. That is a hero’s burden, which you see.”

“A \emph{hero?}” said Hermione. She looked up nervously at Professor McGonagall and saw that the Transfiguration Professor’s face had grown tight, though her hand still squeezed Hermione’s shoulder reassuringly.

“Yes,” said Dumbledore. “I was a hero myself once, before I was a mysterious old wizard, in the days when I opposed Grindelwald. You have read history books, Miss Granger?”

Hermione nodded.

“Well,” said Dumbledore, “that is what heroes have to do, Miss Granger, they have their tasks and they must grow strong to accomplish them, and that is what you see happening to Harry. If there is anything that can be done to gentle his pathway, then \emph{you} will be the one to do it, and not I. For I am not Harry’s friend, alas, but only his mysterious old wizard.”

“I—” said Hermione. “I’m not sure—I still want to be—” Her voice stopped, it seemed too awful to say aloud.

Dumbledore closed his eyes, and when he opened them, he looked a little older than before. “No one can stop you, Miss Granger, if you choose to stop being Harry’s friend. As for what it would do to him, you may know that better than I.”

“That—doesn’t seem \emph{fair,}” Hermione said, her voice trembling. “That I’ve \emph{got} to be Harry’s friend because he’s got no one else? That doesn’t seem fair.”

“\emph{Being} a friend is not something you can be forced to, Miss Granger.” The blue eyes seemed to look right through her. “The feelings are there, or they are not. If they are there, you can accept them or deny them. You \emph{are} Harry’s friend—and choosing to deny it would wound him terribly, perhaps beyond healing. But Miss Granger, what would drive you to such extremes?”

She couldn’t find words. She’d never been able to find words. “If you get too near Harry—you get \emph{swallowed up,} and no one sees \emph{you} any more, you’re just something of \emph{his,} everyone thinks the whole world revolves around him and...” She didn’t have the words.

The old wizard nodded slowly. “It is indeed an unjust world we live in, Miss Granger. All the world now knows that it is I who defeated Grindelwald, and fewer remember Elizabeth Beckett who died opening the way so I could pass through. And yet she is remembered. Harry Potter \emph{is} the hero of this play, Miss Granger; the world \emph{does} revolve around him. He is destined for great things; and I ween that in time the name of Albus Dumbledore will be remembered as Harry Potter’s mysterious old wizard, more than for anything else I have done. And perhaps the name of Hermione Granger will be remembered as his companion, if you prove worthy of it in your day. For this I tell you true: never will you find more glory on your own, than in Harry Potter’s company.”

Hermione shook her head rapidly. “But that’s \emph{not}—” She’d known she wouldn’t be able to explain. “It’s not about \emph{glory,} it’s about being—something that belongs to someone else!”

“So you think you would rather be the hero?” The old wizard sighed. “Miss Granger, I have \emph{been} a hero, and a leader; and I would have been a thousand times happier if I could have belonged to someone like Harry Potter. Someone made of sterner stuff than I, to make the hard decisions, and yet worthy to lead me. I thought, once, that I knew such a man, but I was mistaken... Miss Granger, you have no idea at \emph{all} how fortunate are those like you, compared to heroes.”

The hot burning feeling was creeping up her throat again, along with helplessness, she didn’t understand why Professor McGonagall had brought her here if the Headmaster wasn’t going to help, and from a glance at Professor McGonagall’s face, it looked like Professor McGonagall also wasn’t sure now that it had been a good idea.

“I don’t want to be a hero,” said Hermione Granger, “I don’t want to be a hero’s companion, I just want to be \emph{me.}”

(The thought came to her a few seconds later that maybe she \emph{did} in fact want to be a hero, but she decided not to change what she’d said.)

“Ah,” said the old wizard. “That is a tall order, Miss Granger.” Dumbledore rose from his throne, stepped out behind his desk, and pointed to a symbol on the wall, so ubiquitous that Hermione’s eyes had glossed right over it; a faded shield on which was inscribed the heraldry of Hogwarts, the lion and snake, and badger and raven, and in Latin engraved words whose point she’d never understood. Then, as she realized where that shield was, and how old it looked, it suddenly occurred to Hermione that this might be the \emph{original}—

“A Hufflepuff would say,” said Dumbledore, tapping his finger on the faded badger and making Hermione wince for the sacrilege (if it \emph{was} the original), “that people fail to become who they are meant to be, because they are too lazy to put in all the work involved. A Ravenclaw,” tapping the raven, “would repeat those words that the wise know to be far older than Socrates, \emph{know thyself,} and say that people fail to become who they are meant to be, through ignorance and lack of thought. And Salazar Slytherin,” Dumbledore frowned as his finger tapped the faded snake, “why, he said that we become who we are meant to be by following our desires wherever they lead. Perhaps he would say that people fail to become themselves because they refuse to do what is necessary to achieve their ambitions. But then one notes that nearly all of the Dark Wizards to come out of Hogwarts have been Slytherins. Did they become what they were meant to be? I think not.” Dumbledore’s finger tapped the lion, and then he turned toward her. “Tell me, Miss Granger, what would a Gryffindor say? I do not need to ask whether the Sorting Hat offered you that House.”

It didn’t seem like a hard question. “A Gryffindor would say that people don’t become who they should be, because they’re afraid.”

“Most people \emph{are} afraid, Miss Granger,” said the old wizard. “They live their whole lives circumscribed by crippling fear that cuts off everything they might accomplish, everything they might become. Fear of saying or doing the wrong thing, fear of losing their mere possessions, fear of death, and above all the fear of what other people will think of them. Such fear is a most terrible thing, Miss Granger, and it is terribly important to know that. But it is not what Godric Gryffindor would have said. People become who they are meant to be, Miss Granger, by doing what is right.” The old wizard’s voice was gentle. “So tell me, Miss Granger, what seems to you like the \emph{right} choice? For \emph{that} is who you truly are, and wherever that path leads, that is who you are meant to become.”

There was a long space filled with the sounds of things that could not be counted.

She thought about it, because she was a Ravenclaw.

“I don’t \emph{think} it’s right,” Hermione said slowly, “for someone to have to live inside someone else’s shadow like that...”

“Many things in the world are not right,” said the old wizard, “the question is what is right for \emph{you} to do about them. Hermione Granger, I shall be less subtle than is usual for a mysterious old wizard, and tell you outright that you cannot \emph{imagine} how badly things could go if the events surrounding Harry Potter turn to ill. His quest is a matter you would not even \emph{dream} of walking away from, if you knew.”

“\emph{What} quest?” said Hermione. Her voice was trembling, because it was very clear what answer the Headmaster was looking for and she didn’t want to give it. “What \emph{happened} to Harry back then, \emph{why} was Fawkes on his shoulder?”

“He grew up,” said the old wizard. His eyes blinked several times, beneath the half-moon glasses, and his face suddenly looked very lined. “You see, Miss Granger, people do not grow up because of time, people grow up when they are placed in grownup situations. That is what happened to Harry Potter that Saturday. He was told—you are not to share this information with anyone, you understand—he was told that he would have to fight someone. I cannot tell you who. I cannot tell you why. But that is what happened to him, and why he needs his friends.”

There was a pause.

“\emph{Bellatrix Black?}” Hermione said. She couldn’t have been more shocked if someone had plugged an electrical cord into her ear. “You’re going to make Harry fight \emph{Bellatrix Black?}”

“No,” said the old wizard. “Not her. I cannot tell you who, or why.”

She thought about it some more.

“Is there any way I can \emph{keep up} with Harry?” said Hermione. “I mean, I’m not saying it’s what I’ll \emph{do}, but—if he needs friends then can we be \emph{equal} friends? Can I be a hero too?”

“Ah,” said the old wizard, and smiled. “Only you can decide that, Miss Granger.”

“But you’re not going to help me like you’re helping Harry.”

The old wizard shook his head. “I have helped him little enough, Miss Granger. And if you are asking me for a quest—” The old wizard smiled again, rather wryly. “Miss Granger, you are in your first year of Hogwarts. Do not be too eager to grow up; there will be time enough for that later.”

“I’m twelve. Harry’s \emph{eleven.}”

“Harry Potter is special,” said the old wizard. “As you know, Miss Granger.” The blue eyes were suddenly piercing beneath the half-moon glasses, and she was reminded of the day of the Dementor when Dumbledore’s voice had said, inside her mind, that he knew about Harry’s dark side.

Hermione put up her hand and touched Professor McGonagall’s hand, which had stayed strong on her shoulder this whole time, and Hermione said, she was surprised that her voice didn’t break, “I’d like to go, now, please.”

“Of course,” said Professor McGonagall, and Hermione felt the hand on her shoulder gently turning her around to face the oaken door.

“Have you chosen your path yet, Hermione Granger?” said Albus Dumbledore’s voice from behind her, even as the door slowly creaked open to reveal the Enchantment of the Endless Stair.

She nodded.

“And?”

“I’ll,” she said, her voice stuck, “I’ll, I’ll—”

She swallowed.

“I’ll do—what’s right—”

She didn’t say anything else, she couldn’t, and then the Endless Stair began revolving around her once again.

Neither she nor Professor McGonagall spoke on the way down.

When the Flowing Stone gargoyles stepped out of their way, and the two of them stepped out into the corridors of Hogwarts, Professor McGonagall finally spoke, and she said in a whisper, “I’m so terribly sorry, Miss Granger. I did not think the Headmaster would say such things to you. I think he truly has forgotten what it is like to be a child.”

Hermione glanced back up to her and saw that Professor McGonagall looked like \emph{she} was about to burst into tears...\ only not really, but there was a tightness in her face that was like that.

“If I want to be a hero too,” said Hermione, “if I’ve decided to be a hero too, is there anything \emph{you} can do to help?”

Professor McGonagall rapidly shook her head, and said, “Miss Granger, I’m not sure the Headmaster is wrong about \emph{that.} You \emph{are} twelve.”

“Okay,” said Hermione.

They walked forward a bit.

“Excuse me,” said Hermione, “is it okay if I walk back to the Ravenclaw tower by myself? I’m sorry, it’s not your fault or anything, I just want to be by myself right now.”

“Of course, Miss Granger,” said Professor McGonagall, her voice sounding a little hoarse, and Hermione heard her footsteps stop, and then turn around behind her.

Hermione Granger walked away.

She climbed a flight of stairs, and then another, wondering if there was anyone else in Hogwarts who would give her a chance to be a hero. Professor Flitwick would say the same thing as Professor McGonagall, and even if he didn’t, he probably couldn’t help, Hermione didn’t know who \emph{could} help. Well, Professor Quirrell would come up with something clever if she used up enough Quirrell points, but she had a feeling that asking him would be a bad idea—that the Defense Professor couldn’t help anyone become the sort of hero that was worth becoming, and that he wouldn’t even understand the difference.

She had almost gotten to the Ravenclaw tower when she saw the flash of gold.


