\chapter[Something to Protect: Draco Malfoy]{Something to Protect: Draco Malfoy\protect\footnotemark}
\authorsnotetext{Farewell, Terry Pratchett, 1948–2015. Your characters were an inspiration to me, and now I can see how much they taught me about Level 1 and Level 3 Character Intelligence: that self-awareness often manifests as humour or as genre-savviness; that an inner spark of optimization can shine just as brightly through characters who are told (but not shown) to be lowly and stupid; that intelligent characters can go along with a spark of goodness and light running through a story, rather than cynicism. I wish I could have met you, and spoken with you about your methods. You were loved by so many, and surely at least one person who would tear apart the foundations of reality to bring you back; but your brain is dead and warm now, and so your story ends.
    \begin{verse}
      Even if the stars should die in heaven, \\
      Our sins can never be undone. \\
      No single death will be forgiven \\
      When fades at last the last lit sun. \\
      Then in the cold and silent black \\
      As light and matter end, \\
      We’ll have ourselves a last look back \\
      And toast and absent friend. \\
    \end{verse}}

\lettrine{T}{he} boy sat in an office near to where the once-Deputy Headmistress had held court. His tears had run dry hours ago. Now there was only the waiting to see what would become of him, the orphan ward of Hogwarts, whose life and happiness lay in the hands of his family’s enemies. The boy had been called to this room, and he had come because there was nothing else to do and nowhere else to go. Vincent and Gregory had left his side, called back by their mothers for their fathers’ hurried funerals. Perhaps the boy should have gone with them, but he could not bring himself to do so. He would not have been able to act the part of a Malfoy. The feeling of emptiness that filled him up was so profound that it left no room even for pretended courtesy.

Everyone was dead.

His father was dead, and his godfather Mr~Macnair, and his fallback godfather Mr~Avery. Even Sirius Black, his mother’s cousin, had somehow managed to die, and the last remnant of House Black was no friend to any Malfoy.

Everyone was dead.

There came a knock upon the office’s door; and then, when the boy made no reply, the door opened, revealing—

“Go away,” Draco Malfoy said to the Boy-Who-Lived. He couldn’t muster any force in the words.

“I will soon,” Harry Potter said, as he stepped into the room. “But there’s a decision to be made, and only you can make it.”

Draco turned his head toward the wall, because just looking at Harry Potter took more energy than he had left in him.

“You have to decide,” Harry said, “what happens to Draco Malfoy after this. I don’t mean that in any ominous way. No matter what, you’re still going to grow up to be the rich heir of a Noble and Most Ancient House. The thing is,” Harry’s voice was wavering now, “the thing is, there’s a horrible truth you don’t know, and I keep thinking that if you knew, you’d tell me not to be your friend any more. And I don’t want to stop being your friend. But to just—never tell you—and always maintain that lie so I can go on being your friend—I can’t do that. It’s also wrong. I don’t…don’t want this any more, I don’t want to be \emph{manipulating} you. I’ve hurt you too much already.”

\emph{Then stop trying to be my friend, you’re no good at it anyway.} The words rose up into Draco’s consciousness, and were rejected from his lips. He felt like he’d mostly lost Harry already, from the games Harry had played with their friendship, the lies and manipulations; and yet the thought of going back to Slytherin alone, maybe without Vincent and Gregory if their mothers terminated the arrangement…Draco didn’t want to do that, he didn’t want to go back to Slytherin and live out his life among only people who’d agreed to be Sorted into Slytherin House. Draco was just with it enough to remember how many of his real friends were also friends with Harry, that Padma was a Ravenclaw and even Theodore was a Chaotic Lieutenant. All that remained of Malfoy House was a tradition, now; and that tradition said it wasn’t clever to tell the war’s victor to go away and stop trying to be friends with you.

“All right,” Draco said emptily. “Tell me.”

“That’s what I’m going to do,” Harry said. “And then the Headmistress will come in after I leave, and seal away your last half-hour of memory. But before then, knowing the whole truth, you’ll get to decide whether you still want to be involved with me.” Harry’s voice was shaking. “Um. According to the records I was reading through before I came here, the story really began in 1926 with the birth of a half-blood wizard named Tom Morfin Riddle. His mother died in childbirth, and he grew up in a Muggle orphanage, until his Hogwarts letter was brought to him by Professor Dumbledore…”

The Boy-Who-Lived continued speaking, words that slammed into what was left of Draco’s mind like falling houses.

\emph{The Dark Lord had been a half-blood. He’d never believed in blood purity for a fraction of a second.}

\emph{Tom Riddle had come up with the idea of Lord Voldemort as a bad joke.}

\emph{The Death Eaters had been meant to lose to David Monroe, so Monroe could take over.}

\emph{After giving up on that, Tom Riddle had gone on playing Voldemort instead of actually trying to win, because he’d liked bossing the Death Eaters around.}

\emph{Voldemort used me to try to frame Father for my attempted murder, then used me again to go after the Philosopher’s Stone.} Draco couldn’t remember that part, but he’d already been told that he’d been used as a pawn alongside Professor Sprout, and that no charges would be filed.

And then the last horror.

“You—” whispered Draco Malfoy. “You—”

“I’m the one who killed your father and all the other Death Eaters last night. They’d been told to open fire on me the moment I did anything, so I had to kill them in order to have a chance at dealing with Voldemort, who was a danger to the entire world.” Harry Potter’s voice was strained. “I didn’t think about you and Theodore and Vincent and Gregory, but if I had, I’d have done it anyway. My mind managed not to realise until afterwards that Mr~White was Lucius, but if I’d realised, I still wouldn’t have risked leaving him alive, in case he knew wandless magic. The thought occurred to me long before that it would be pretty convenient, in terms of the political landscape, for all the Death Eaters to suddenly die. I always thought that the Death Eaters were horrible people, much more strongly than I ever let on to you, since the first day we met. But if your father hadn’t been there, and I’d had a button that could kill him remotely, I wouldn’t have pressed the button just for political reasons. The way I feel about what I’ve done, and whether there’s remorse…well, there’s a part of me that’s screaming in generic horror about having killed anyone. And another part that says that from a moral standpoint, the Death Eaters signed away their lives on the day they signed up with Voldemort. They pointed their wands at me first, blah blah and so on. But right now I just feel sick about what I’ve done to you. Again. I feel like,” Harry Potter’s voice wobbled a bit, “everything I do only hurts you, for all my \emph{good intentions,} that you’ve only ever lost things from being around me, so if you tell me to stay away entirely from Draco Malfoy after this, then I will. And if you want me to try to be your friend for real this time, without ever trying to manipulate you again, without ever using you again or risking hurting you again, then I will, I swear I will.”

The next Lord Malfoy was crying, openly in front of his enemy, decorum and composure abandoned, because he didn’t have anyone left for whose sake he could keep it.

A lie.

A lie.

Everything had been a lie, it was all lies piled on top of lies, lies lies lies—

“\emph{You} should die,” Draco forced out. “You should die for having killed Father.” The words only filled him with more emptiness, but they had to be said.

Harry Potter just shook his head. “And if that’s not an option?”

“You should \emph{hurt.}”

Harry only shook his head again.

The Boy-Who-Lived pressed the Lord Malfoy for his decision.

The Lord Malfoy refused to give it. He couldn’t say it, couldn’t bring himself to say it, either way. He didn’t want the war’s victor and their mutual friends to abandon him, and he wasn’t going to give Harry the absolution he wanted, either.

So Draco Malfoy refused to answer, and then the time of that self’s memory ended.

\later

The boy sat in an office near to where the once-Deputy Headmistress had held court. His tears had run dry hours ago. Now there was only the waiting to see what would become of him, the orphan ward of Hogwarts, whose life and happiness lay in the hands of his family’s enemies. The boy had been called to this room, and he had come, because there was nothing else to do, and nowhere else to go. Vincent and Gregory had left his side, called back by their mothers for their fathers’ hurried funerals. Perhaps the boy should have gone with them, but he could not bring himself to do so. He would not have been able to act the part of a Malfoy. The feeling of emptiness that filled him up was so profound that it left no room even for lies.

Everyone was dead.

Everyone was dead, and it had all been futile from the beginning.

There was a knock upon the office door, and then, after a polite pause, it opened to reveal Headmistress McGonagall, dressed much as she had dressed when she was a Professor. “Mr~Malfoy?” his family’s victorious enemy said. “Please come with me.”

Listlessly, Draco rose up, and followed her out of the office. Seeing Harry Potter waiting beside her gave him some pause, but then his mind simply shut it out.

“Here’s the last thing,” Harry Potter said. “I found it in a folded parchment whose outside said that it was the last weapon to be used against House Malfoy, telling me not to read any further until the whole war hung in the balance. I didn’t want to tell it to you before because I thought it might prejudice your decision unfairly. If you were a good person who never killed or lied, but you had to do one or the other, which would be worse?”

Draco ignored him and continued in Headmistress McGonagall’s company, leaving Harry behind looking sadly after.

They came to the Headmistress’s old office, where she lit her Floo-fire with a wave of her wand, said to the green flame “Gringotts travel office” and stepped through after a firm glance in his direction.

For lack of any other option, Draco Malfoy followed.

\later

She lay in bed, feeling more listless than usual that morning, awoken too early with the Sun just beginning to rise—though the direct sunlight was blocked by the skyscrapers that shadowed her house. A faint tinge of hangover gnawed at her temples, dried her mouth; she tried to be sparing with the drink (though she didn’t know why she bothered) but yesterday she’d felt…even more depressed than usual, like she’d lost something, somehow. Not for the first time, not for the hundredth time, she thought about moving—to Adelaide, to Perth, maybe to Perth Amboy if that was what it took. She always had the sense there was somewhere else she ought to be; but while she could live a comfortable life on the payments the insurance company made to her, she couldn’t afford luxuries. She couldn’t pay to go gallivanting around the world looking for somewhere that fit her unsatisfied sense of belonging. She’d watched the TV for long enough, she’d rented enough travelogues, to know that nowhere the VCR showed her gave her any more sense of rightness than Sydney.

She’d felt frozen, stopped in time, ever since the traffic accident that had stolen her memories—not just of a dead family that meant nothing to her now, but memories like how a stove worked. She suspected, no, she \emph{knew,} that whatever her heart was waiting for, whatever key needed to turn inside her to make her life begin moving again, it was one more thing she’d lost to that runaway minivan. She thought about that almost every morning, trying to guess what she was missing, missing, missing from her life and mind.

Somebody rang her doorbell.

She groaned, turning her head far enough to look at the LED alarm clock at the side of her bed. 6:31, it said, with the AM dot lit. \emph{Seriously?} Well, that idiot could wait while she staggered out of bed at her own pace, then.

Stagger out of bed she did, ignoring the doorbell as it rang again, as she ducked into the bathroom and dressed herself.

She clambered down the stairs, ignoring the ever-nagging sense that someone else ought to be answering her door for her. “Who’s there?” she called to the closed door; the door had a peep-hole, but it was fogged over.

“Are you Nancy Manson?” came a woman’s voice, speaking in a precise Scottish accent.

“Yes,” she said cautiously.

“\emph{Eunoe,}” spoke the Scottish voice, and Nancy leapt back in shock as a flash of light came from the door and \emph{hit} her and…

Nancy swayed, putting a hand to her forehead. Flashes of light just going through doors and hitting people, that was…that was…that wasn’t particularly surprising…

“Would you please open the door?” said the Scottish woman’s voice. “The war is over and your memories should be returning shortly. There’s someone here who ought to see you.”

\emph{My memories}—

Nancy’s head was already feeling clogged, like she was about to start hacking something out of her brain, but she managed to reach out and yank the door open.

There in front of her was a woman dressed as a \emph{(perfectly normal)} witch, from black robes to tall pointed hat—

—and standing beside her a boy, with short white-blonde hair and wearing \emph{(perfectly normal)} dark robes trimmed in green, staring at her with his jaw dropped and eyes wide and beginning to fill with tears.

\emph{Green-trimmed robes and white-blonde hair…}

Something warm stirred in her memory. She felt her heart rising into her throat as she realized that the thing that she’d been looking for these past ten years might be right in front of her this very instant. Somewhere deep inside her, ice was cracking around her heart, the piece of her that had been stopped for so long preparing to move once more.

The boy was staring at her, his mouth working soundlessly.

A mysterious name came into her mind, rose to her lips.

“Lucius?” she whispered.

%  LocalWords:  Morfin Amboy Eunoe
