\partchapter{Taboo Tradeoffs, Aftermath}{II}

\lettrine{W}{hen} Hermione Granger woke, she found herself lying in a soft, comfortable bed of the Hogwarts infirmary, with a square of setting sunlight falling on her midriff, warm through the thin blanket. Memory said that there would be a screen-sheet above her, either drawn around her bed or open, and that the rest of Madam Pomfrey’s domain would lie beyond: the other beds, occupied or unoccupied, and bright windows set in the curvily-carven stone of Hogwarts.

When Hermione opened her eyes, the first thing she saw was the face of Professor McGonagall, sitting on the left side of her bed. Professor Flitwick wasn’t there, but that was understandable, he’d stayed by her side all morning in the detention cell, his silver raven standing extra guard against the Dementor and his stern little face always turned outward toward the Aurors. The Head of Ravenclaw had surely spent way too much time on her, and probably had to get back to teaching his classes, instead of keeping watch on a convicted attempted-murderess.

She felt horribly, horribly sick and she didn’t think it was because of any potions. Hermione would’ve started crying again, only her throat hurt, her eyes still burned, and her mind just felt tired. She couldn’t have borne to weep again, couldn’t find the strength for tears.

“Where are my parents?” Hermione whispered to the Head of House Gryffindor. Somehow it seemed like the worst thing in the world to face them, even worse than everything else; and yet she still wanted to see them.

The gentle look on Professor McGonagall’s face Transfigured into something sadder. “I’m sorry, Miss Granger. Though it was not always so, we have found in recent years that it is wiser not to tell the parents of Muggleborns about any danger their child has faced. I should advise you also to remain silent, if you wish to stay at Hogwarts without trouble from them.”

“I’m not being expelled?” the girl whispered. “For what I did?”

“No,” said Professor McGonagall. “Miss Granger... surely you heard... I hope you heard Mr.~Potter, when he said that you were innocent?”

“He was just saying that,” she said dully. “To get me free, I mean.”

The older witch shook her head firmly. “No, Miss Granger. Mr.~Potter believes you were Memory-Charmed, that the whole duel never happened. The Headmaster suspects even Darker magics may have been involved—that your own hand might have cast the spell, but not your own will. Even Professor Snape finds the affair completely unbelievable, though he may not be able to say so publicly. He was wondering if Muggle drugs might have been used on you.”

Hermione’s eyes went on staring distantly at the Transfiguration Professor; she knew that she’d just been told something significant, but she couldn’t find the energy to propagate any changes through her mind.

“Surely \emph{you} don’t believe it?” said Professor McGonagall. “Miss Granger, you cannot believe of yourself that you would turn to murder!”

“But I—” Her excellent memory helpfully replayed it for the thousandth time, Draco Malfoy telling her with a sneer that she’d never beat him when he wasn’t tired, and then proceeding to prove just that, dancing like a duelist between the warded trophies while she frantically scrambled, and dealing the ending blow with a hex that sent her crashing against the wall and drew blood from her cheek—and then—then she’d—

“But you remember doing it,” said the older witch, who was watching over her with kindly understanding. “Miss Granger, there is no need for a twelve-year-old girl to bear such dreadful memories. Say the word and I shall be happy to lock them away for you.”

It was like a glass of warm water thrown into her face. “What?”

Professor McGonagall took out her wand, a gesture so practiced and quick that it seemed like pointing a finger. “I can’t offer to rid you of the memories entirely, Miss Granger,” the Transfiguration Professor said with her customary precision. “There may be important facts buried there. But there is a form of the Memory Charm which is reversible, and I shall be happy to cast that on you.”

Hermione stared at the wand, feeling the stirrings of hope for the first time in almost two days.

\emph{Make it didn’t happen...} she’d wished that over and over again, for the hands of time to turn back and erase the horrible choice that could never, ever be undone. And if erasing the memory wasn’t that, it was still a kind of release...

She looked back at Professor McGonagall’s kindly face.

“You \emph{really} don’t think I did it?” Hermione said, her voice trembling.

“I am \emph{quite} certain you would never do such a thing of your own will.”

Beneath her blankets, Hermione’s hands clutched at the sheets. “\emph{Harry} doesn’t think I did it?”

“Mr.~Potter is of the opinion that your memories are entire fabrications. I can rather see his point.”

Then Hermione’s clutching fingers let go of the sheet, and she slumped back into the bed, from which she’d partially risen.

No.

She hadn’t said anything.

She’d woken up and remembered what had happened last night, and it had been like—like—she couldn’t find words even in her own thoughts for what it had been like. But she’d known that Draco Malfoy was already dead, and she hadn’t said anything, hadn’t gone to Professor Flitwick and confessed. She’d just dressed herself and gone down to breakfast and \emph{tried to act normal} so that nobody would ever know, and she’d known it was wrong and \emcap{Wrong} and horribly horribly \scream{wrong} but she’d been so, so scared—

Even if Harry Potter was right, even if the duel with Draco Malfoy was a lie, she’d made \emph{that} choice all by herself. She didn’t deserve to forget that, or be forgiven for it.

And if she \emph{had} done the right thing, gone straight to Professor Flitwick, maybe that would’ve—helped, somehow, maybe everyone would’ve seen then that she regretted it, and Harry wouldn’t have had to give away all his money to save her—

Hermione shut her eyes, squeezed them shut really tight, she couldn’t bear to start crying again. “I’m a horrible person,” she said in a wavering voice. “I’m awful, I’m not heroic at all—”

Professor McGonagall’s voice was very sharp, like Hermione had just made some dreadful mistake on her Transfiguration homework. “Stop being foolish, Miss Granger! \emph{Horrible} is whoever did this to you. And as for being heroic—well, Miss Granger, you have already heard my opinion about young girls trying to involve themselves in such things before they are even fourteen, so I shall not lecture you on it again. I shall say only that you have just had an absolutely dreadful experience, which you survived as well as any witch in your year possibly could. Today you are allowed to cry as much as you like. Tomorrow you are going back to class.”

That was when Hermione knew that Professor McGonagall couldn’t help her. She needed someone to scold her, she couldn’t be absolved if she couldn’t be blamed, and Professor McGonagall would never do that for her, would never ask so much of a little Ravenclaw girl.

It was something Harry Potter wouldn’t help her with either.

Hermione turned over in the infirmary bed, huddling into herself, away from Professor McGonagall. “Please,” she whispered. “I want to talk—to the Headmaster—”
\sbreak

“Hermione.”

When Hermione Granger opened her eyes a second time, she saw the care-lined face of Albus Dumbledore leaning over her bedside, looking almost as though \emph{he’d} been crying, though that was impossible; and Hermione felt another stabbing pang of guilt for having bothered him so.

“Minerva said you wished to speak with me,” the old wizard said.

“I—” Suddenly Hermione didn’t know at all what to say. Her throat locked up, and all she could do was stammer, “I—I’m—”

Somehow her tone must have communicated the other word, the one she couldn’t even say anymore.

\emph{“Sorry?”} said Dumbledore. “Why, for what should you be sorry?”

She had to force the words out of her throat. “You were telling Harry—that he shouldn’t pay—so \emph{I} shouldn’t—have done what Professor McGonagall said, I shouldn’t have touched his wand—”

“My dear,” said Dumbledore, “had you not pledged yourself to the House of Potter, Harry would have attacked Azkaban singlehandedly, and quite possibly won. That boy may choose his words carefully, but I have never yet known him to lie; and in the Boy-Who-Lived there is power that the Dark Lord never knew. He would indeed have tried to break Azkaban, even at cost of his life.” The old wizard’s voice grew gentler, and kinder. “No, Hermione, you have nothing at all for which to blame yourself.”

“I could have \emph{made} him not do it.”

In Dumbledore’s eyes a small twinkle appeared before it was lost to weariness. “Really, Miss Granger? Perhaps you should be Headmistress in my place, for I myself have no such power over stubborn children.”

“Harry promised—” Her voice stopped. The awful truth was very hard to speak. “Harry Potter promised me—that he would never help me—if I told him not to.”

There was a pause. The distant noises of the infirmary that had accompanied Professor McGonagall had ceased, Hermione realized, when Dumbledore had awoken her. From where she lay in bed she could see only the ceiling, and the top of one wall’s windows, but nothing in her range of vision moved, and if there were sounds, she could not hear them.

“Ah,” said Dumbledore. The old wizard sighed heavily. “I suppose it \emph{is} possible that the boy would have kept his promise.”

“I should—I should’ve—”

“Gone to Azkaban of your own will?” Dumbledore said. “Miss Granger, that is more than I would ever ask anyone to take upon themselves.”

“But—” Hermione swallowed. She couldn’t help but notice the loophole, anyone who wanted to get through the portrait-door to the Ravenclaw dorm quickly learned to pay attention to exact wordings. “But it’s not more than you’d take on \emph{yourself}.”

“Hermione—” the old wizard began.

“Why?” said Hermione’s voice, it seemed to be running on without her mind, now. “Why couldn’t I be braver? I was going to run in front of the Dementor—for Harry—before, I mean, in January—so why—why—why couldn’t I—” Why had the thought of being sent to Azkaban just completely \emph{unglued} her, why had she forgotten everything about being Good—

“My dear girl,” Dumbledore said. The blue eyes behind the half-moon glasses showed a complete understanding of her guilt. “I would have done no better myself, in my first year in Hogwarts. As you would be kind to others, be kinder to yourself as well.”

“So I \emph{did} do the wrong thing.” Somehow she needed to say that, to be told that, even though she already knew.

There was a pause.

“Listen, young Ravenclaw,” the old wizard said, “hear me well, for I shall speak to you a truth. Most ill-doers do not think of themselves as evil; indeed, most conceive themselves the heroes of the stories they tell. I once thought that the greatest evil in this world was done in the name of the greater good. I was wrong. Terribly wrong. There is evil in this world which knows itself for evil, and hates the good with all its strength. All fair things does it desire to destroy.”

Hermione shivered in her bed, somehow it seemed very real, when Dumbledore said it.

The old wizard continued speaking. “You are one of the fair things of this world, Hermione Granger, and so that evil hates you as well. If you had stayed firm through even this trial, it would have struck you harder and yet harder, until you shattered. Do not think that heroes cannot be broken! We are only more difficult to break, Hermione.” The old wizard’s eyes had grown sterner than she had ever seen. “When you have been exhausted for many hours, when pain and death is not a passing fear but a certainty, then it is harder to be a hero. If I must speak the truth—then today, yes, I would not waver in the face of Azkaban. But when I was a first-year in Hogwarts—I would have fled from the Dementor that you confronted, for my father had died in Azkaban, and I feared them. Know this! The evil that struck at you could have broken anyone, even myself. Only Harry Potter has it within him to face that horror, when he has come fully into his power.”

Hermione’s neck couldn’t stare at the old wizard any longer; she let her head fall back, back to the pillow, where she stared up at the ceiling, absorbing what she could.

“Why?” Her voice trembled again. “Why would anyone be that evil? I don’t understand.”

“I, too, have wondered,” said Dumbledore’s voice, a deep sadness in it. “For thrice ten years I wondered, and I still do not understand. You and I will never understand, Hermione Granger. But at least I know now what true evil would say for itself, if we could speak to it and ask why it was evil. It would say, \emph{Why not?”}

A brief flare of indignation inside her. “There’s got to be a \emph{million} reasons why not!”

“Indeed,” said Dumbledore’s voice. “A million reasons and more. We will always know those reasons, you and I. If you insist on putting it that way—then yes, Hermione, this day’s trial broke you. But what happens \emph{after} you break—that, too, is part of being a hero. Which you are, Hermione Granger, and will always be.”

She raised her head again, staring at him.

The old wizard got up from beside her bed. His silver beard dipped down, as Dumbledore bowed to her gravely, and left.

She went on looking at where the old wizard had gone.

It should have meant something to her, should have touched her. Should have made her felt better inside, that Dumbledore, who had seemed so reluctant before, had now acknowledged her as a hero.

She felt nothing.

Hermione let her head fall back to the bed, as Madam Pomfrey came and made her drink something that seared her lips like the afterburn of spicy food, and smelled even hotter, and didn’t taste like anything at all. It meant nothing to her. She went on staring up at the distant stone tiles of the ceiling.
\sbreak

Minerva was waiting, doing her best not to hover, beside the double doors to the Hogwarts infirmary, she’d always thought of those doors as “the ominous gates” as a child in Hogwarts, and couldn’t help but remember that now. Too much bad news had been spoken here—

Albus stepped out. The old wizard did not pause on the way out of the infirmary, only kept walking toward Professor Flitwick’s office; and Minerva followed him.

Professor McGonagall cleared her throat. “Is it done, Albus?”

The old wizard nodded in affirmation. “If any hostile magic is cast on her, or any spirit touches her, I shall know, and come.”

“I spoke to Mr.~Potter after Transfiguration class,” said Professor McGonagall. “He was of the opinion that Miss Granger should go to Beauxbatons, rather than Hogwarts, from now on.”

The old wizard shook his head. “No. If Voldemort truly desires to strike at Miss Granger—he is tenacious beyond measure. His servants are returning to him, he could not have retrieved Bellatrix alone. Azkaban itself is not safe from his malice, and as for Beauxbatons—no, Minerva. I do not think Voldemort can essay such possessions often, or against stronger targets, or this year would have gone quite differently. And Harry Potter is here, whom Voldemort must fear whether he admits it or no. Now that I have warded her, Miss Granger will be safer within Hogwarts than without.”

“Mr.~Potter seemed to doubt that,” Minerva said. She couldn’t quite keep the edge from her voice; there was a part of her that agreed rather strongly. “He seemed to feel that common sense said Miss Granger should continue her education anywhere but Hogwarts.”

The old wizard sighed. “I fear the boy has spent too much time among the Muggles. Always they reach for safety; always they imagine that safety can be reached. If Miss Granger is not safe within the center of our fortress, she shall be no safer for leaving it.”

“Not everyone seems to think so,” said Professor McGonagall. It had been almost the first letter she’d seen when she’d taken a quick look at her desk; an envelope of the finest sheepskin, sealed in greenish-silver wax, pressed into the image of a snake that rose and hissed at her. “I have received Lord Malfoy’s owl withdrawing his son from Hogwarts.”

The old wizard nodded, but did not break stride. “Does Harry know?”

“Yes.” Her voice faltered, for a moment, remembering Harry’s expression. “After class, Mr.~Potter complimented Lord Malfoy’s excellent good sense, and said that he would be writing Madam Longbottom advising her to do the same with her grandson, in case he was the next target. In the event that Mr.~Longbottom’s guardian was so negligent as to keep him in Hogwarts, Mr.~Potter wanted him to have a Time-Turner, an invisibility cloak, a broomstick, and a pouch in which to carry them; also a toe-ring with an emergency portkey to a safe location, in case someone kidnaps Mr.~Longbottom and takes him outside Hogwarts’s wards. I told Mr.~Potter that I did not think the Ministry would consent to such use of our Time-Turners, and he said that we should not ask. I expect he will want Miss Granger to receive the same, if she stays. And for himself Mr.~Potter wants a three-person broomstick to carry in his pouch.” She wasn’t awed by the list of precautions. Impressed with the cleverness, but not awed; she was a Transfiguration Mistress, after all. But it still sent shivers of disquiet through her, that Harry Potter now thought Hogwarts as dangerous as spell research.

“The Department of Mysteries is not lightly defied,” said Albus. “But for the rest—” The old wizard seemed to slump in on himself slightly. “We may as well give the boy what he wishes. And I will ward Neville also, and write Augusta to say that he should stay here over holiday.”

“And finally,” she said, “Mr.~Potter says—this is a direct quote, Albus—whatever kind of Dark Wizard attractant the Headmaster is keeping here, he needs to get it out of this school, \emph{now}.” She couldn’t stop the edge in her own voice, that time.

“I asked as much of Flamel,” Albus said, the pain clear in his voice. “But Master Flamel has said—that even \emph{he} can no longer keep safe the Stone—that he believes Voldemort has means of finding it wherever it is hidden—and that he does not consent for it to be guarded anywhere but Hogwarts. Minerva, I am sorry, but it must be done—\emph{must!”}

“Very well,” said Professor McGonagall. “But for myself, I think that Mr.~Potter is right on every single count.”

The old wizard glanced at her, and his voice caught as he said, “Minerva, you have known me long, and as well as any soul still living—tell me, have I lost myself to darkness already?”

“What?” said Professor McGonagall in genuine surprise. Then, “Oh, Albus, no!”

The old wizard’s lips pressed together tightly before he spoke. “For the greater good. I have sacrificed so many, for the greater good. Today I almost condemned Hermione Granger to Azkaban for the greater good. And I find myself—today, I found myself—beginning to resent the innocence that is no longer mine—” The old wizard’s voice halted. “Evil done in the name of good. Evil done in the name of evil. Which \emph{is} worse?”

“You are being silly, Albus.”

The old wizard glanced at her again, before turning his eyes back to their way. “Tell me, Minerva—did you pause to weigh the consequences, before you told Miss Granger how to bind herself to the Potter family?”

She took an involuntary breath as she understood what she had done—

“So you did not.” Albus’s eyes were saddened. “No, Minerva, you must not apologize. It is well. For what you have seen of me this day—if your first loyalty is now to Harry Potter, and not to me, then that is right and proper.” She opened her lips to protest, but Albus went on before she could say a word. “Indeed—indeed—that will be necessary and more than necessary, if the Dark Lord that Harry must defeat to come into his power is not Voldemort after all—”

“Not \emph{this} again!” Minerva said. “Albus, it was You-Know-Who, not you, who marked Harry as his equal. There is no \emph{possible} way that the prophecy could be talking about you!”

The old wizard nodded, but his eyes still seemed distant, fixed only on the road ahead.
\sbreak

The holding cell, well to the center of Magical Law Enforcement, was luxuriously appointed; more a remark on what adult wizards took for granted, than any special feeling toward prisoners. There was a self-reclining, self-rocking chair with plush, richly textured, self-warming cushions. There was a bookcase containing random books rescued from a bargain bin, and a full shelf of ancient magazines, including one from 1883. As for toiletries, well, it wasn’t exactly luxurious, but there was a spell on the room which put all that business on hold; you weren’t to go anywhere that the watching Auror couldn’t see you. But aside from that, it was quite a pleasant little cell. The Defense Professor of Hogwarts was being detained, not arrested, not even intimidated. There was no evidence to indict him... except that a terrible and unusual crime had been committed at the Hogwarts School of Witchcraft and Wizardry, and going by previous occasions the odds were five to one that the current Defense Professor was tangled up in it \emph{somehow}. To this must be added the fact that nobody in the D.M.L.E. even knew who the Defense Professor \emph{was}, and that the man had literally \emph{sneezed} at all attempts to uncover his true identity. Why, no, they \emph{hadn’t} released ‘Quirinus Quirrell’ back to Hogwarts just yet.

Let us repeat this for emphasis:

The Defense Professor.

Was being detained.

In a cell.

The Defense Professor was staring at the watching Auror and humming.

The Defense Professor has not spoken a single word since he arrived in this particular cell. He has \emph{only} been humming.

The humming started as a simple children’s lullaby, the one that in Muggle Britain begins, \emph{Lullaby, and goodnight...}

This tune was hummed, without variation, over and over, for seven minutes, to establish the underlying pattern.

Then began the elaborations upon the theme. Phrases hummed too slow, with long pauses in between, so that the listener’s mind helplessly waits and waits for the next note, the next phrase. And then, when that next phrase comes, it is so out of key, so unbelievably awfully out of key, not just out of key for the previous phrases but sung at a pitch which does not correspond to \emph{any} key, that you would have to believe this person had spent hours deliberately practicing their humming just to acquire such perfect anti-pitch.

It bears the same semblance to music as the awful dead voice of a Dementor bears to human speech.

And this horrible, horrible humming is \emph{impossible} to ignore. It is similar to a known lullaby, but it departs from that pattern unpredictably. It sets up expectations and then violates them, never in any constant pattern that would permit the humming to fade into the background. The listener’s brain cannot prevent itself from expecting the anti-musical phrases to complete, nor prevent itself from noticing the surprises.

The only possible explanation for how this mode of humming came to exist is that it was deliberately designed by some unspeakably cruel genius who woke up one day, feeling bored with ordinary torture, who decided to handicap himself and find out whether he could break someone’s sanity \emph{just by humming at them}.

The Auror has been listening to this unimaginably dreadful humming for four hours, while being stared at by a huge, cold, lethal presence that feels equally horrible whether he looks at it directly or lets it hover at the corner of his vision—

The humming stopped.

There was a long wait. Time enough for false hope to rise, and be squashed down by the memory of previous disappointments. And then, as the interval lengthened, and lengthened, that hope rose again unstoppably—

The humming began once more.

The Auror cracked.

From his belt, the Auror took a mirror, tapped it once, and then said, “This is Junior Auror Arjun Altunay, I’m calling in code \accronym{RJ-L20} on cell three.”

“Code \accronym{RJ-L20}?” the mirror said in surprised tones. There was a sound of pages being flipped, then, “You want to be relieved because a prisoner is attempting psychological warfare and succeeding?”

(Amelia Bones really is quite intelligent.)

“What’d the prisoner say to you?” said the mirror.

(This question is \emph{not} part of procedure \accronym{RJ-L20}, but unfortunately Amelia Bones has failed to include an explicit instruction that the commanding officer should not ask.)

“He’s—” said the Auror, and glanced back at the cell. The Defense Professor was now leaning in back in his chair, looking quite relaxed. “He was \emph{staring} at me! And \emph{humming!”}

There was a pause.

The mirror spoke again. “And you’re calling in an \accronym{RJ-L20} over that? You’re sure you’re not just trying to get out of watching him?”

(Amelia Bones is surrounded by idiots.)

“You don’t understand!” yelled Auror Altunay. “It’s really awful humming!”

The mirror transmitted a sound of muffled laughter in the background, sounding like it was coming from more than one person. Then speech again. “Mr.~Altunay, if you don’t want to be busted to Junior Auror Second Class, I suggest you buckle down and get back to work—”

“Strike that,” a crisp voice said, sounding slightly remote due to its distance from the mirror.

(Which is why Amelia Bones often sits in on a coordination center of the \accronym{D.M.L.E.} while doing her Ministry-required paperwork.)

“Auror Altunay,” said the crisp voice, seeming to approach closer to the mirror, “you will be relieved shortly. Auror Ben Gutierrez, the procedure for \accronym{RJ-L20} does \emph{not} say that you ask why. It says that you relieve the Auror who calls it in. \emph{If} I find that Aurors seem to be abusing it, \emph{I} will modify the procedure to prevent its abuse—” The mirror cut off abruptly.

The Auror turned back to look triumphantly at where the current Defense Professor of Hogwarts was leaning back in his cushioned chair.

That man then spoke the first words that had left his lips since he entered the cell.

“Goodbye, Mr.~Altunay,” said the Defense Professor.

A few minutes later, the door to the detention cell opened, and in walked a grey-haired woman, dressed in the crimson-tinged robes of an Auror without any sign of rank or other ornamentation, carrying a black leather folder under her left arm. “You’re relieved,” the old woman said abruptly.

There was a brief delay while Auror Altunay tried to explain what had been happening. This was cut short by a nod and a stark, simple finger pointing out the door.

“Good evening, Madam Director,” said the Defense Professor.

Amelia Bones did not acknowledge this statement, but sat down abruptly in the vacated chair. The old witch opened the black folder and her gaze moved down to the parchments therein. “Possible hints to the identity of the current Hogwarts Defense Professor, as compiled by Auror Robards.” The title parchment was turned, flipped aside. “The Defense Professor said that he was Sorted into Slytherin. Claimed that his family was killed by Voldemort. Said he had studied at a martial arts center in Muggle Asia which was destroyed by Voldemort. A request filed with the Department of International Magical Cooperation identifies this incident as the Oni Affair of 1969.” Another parchment was flipped aside. “It also seems this Defense Professor gave a most stirring speech to his students, just before last Yule, castigating the previous generation for their disunity against the Death Eaters.” The old witch looked up from the leather folder. “Madam Longbottom was rather taken with it, and insisted that I read the entire thing. The argument struck me as familiar, though I could not place it at the time. But then, of course, I had thought you dead.”

The chief law enforcement officer of Magical Britain was now gazing sharply at the current Defense Professor of Hogwarts, across the pane of spell-reinforced glass separating them. The man in the cell returned the gaze equably, without apparent alarm.

“I shall not name any names,” said the old witch. “But I shall tell a story, and see if it sounds familiar.” Amelia Bones looked back down, turning to the next parchment. “Born 1927, entered Hogwarts in 1938, sorted into Slytherin, graduated 1945. Went on a graduation tour abroad and disappeared while visiting Albania. Presumed dead until 1970, when he returned to magical Britain just as suddenly, without any explanation for the missing twenty-five years. He remained estranged from his family and friends, living in isolation. In 1971, while visiting Diagon Alley, he fended off an attempt by Bellatrix Black to kidnap the daughter of the Minister of Magic, and used the Killing Curse to slay two of the three Death Eaters accompanying her. Beyond this all Britain knows the story; need I continue it?” The old witch looked up from her folder again. “Very well. There was a trial in the Wizengamot, during which this young man was exonerated for his use of the Killing Curse, not least due to the efforts of his grandmother, the Lady of his House. He was reconciled with his family, and they held a House gathering to welcome his return. The guest of honor arrived at that gathering to find his entire family slain by Death Eaters, even to the house elves; and that he himself, of cadet line, was now the last remaining scion of a Most Ancient House.”

The Defense Professor had not reacted at all to any of this, except that his eyes had half-closed, as though in weariness.

“The young man took up his family’s seat in the Wizengamot, becoming among the most steadfast voices against You-Know-Who. Several times he led forces against the Death Eaters, fighting with skillful tactics and extraordinary power. People began to speak of him as the next Dumbledore, it was thought that he might become Minister of Magic after the Dark Lord fell. On the third of July, 1973, he failed to appear at a key Wizengamot vote, and was never heard from again. We assumed You-Know-Who had killed him. It was a grave blow to all of us, and matters went much the worse from that day on.” The old witch’s gaze was questioning. “I mourned you myself. What happened?”

The Defense Professor’s shoulders moved lightly, a small shrug. “You make many assumptions,” the Defense Professor said softly. “For myself, I would believe that man died years ago. But if that man is nonetheless alive—then it is clear he does not wish the fact announced, and has reasons enough for silence. That man was once of some help to you, it seems.” The Defense Professor’s lips curved in a cynical smile. “But I am no longer surprised when gratitude is fleeting. Is there yet more that you would demand from him?”

The old witch leaned back in her Auror’s monitoring-chair, looking rather startled, maybe even hurt. “No—” she said after a moment. Her fingers tapped the leather folder; \emph{nervously,} you might have thought, if you had believed that Amelia Bones could ever be nervous. “But your \emph{House}—there are not many Ancient Houses remaining—”

“It shall matter little to this country whether eight Ancient Houses remain, or seven.”

The old witch sighed. “What does Dumbledore think of this?”

The man in the detention cell shook his head. “He does not know who I am, and promised not to inquire.”

The old witch’s eyebrows rose. “How did he identify you to the Hogwarts wards, then?”

A slight smile. “The Headmaster drew a circle, and told Hogwarts that he who stood within was the Defense Professor. Speaking of which—” The tone went lower, flatter. “I am missing my classes, Director Bones.”

“You seem to—\emph{rest}, sometimes, in a peculiar manner. This has also been reported. And you seem to be \emph{resting} more and more frequently, as time goes on.” The old witch’s fingers tapped the leather folder again. “I cannot recall reading of such a symptom, but when one hears of such a thing, one imagines... Dark Wizards fought, and terrible curses received...”

The Defense Professor remained expressionless.

“Do you require a healer’s help?” said Amelia Bones. Her own mask had slipped, clearly showing the pain in her eyes. “Is there anything at all that can be done for you?”

“I agreed to teach Defense at Hogwarts,” the man in the cell said flatly. “Draw your own conclusions, Madam. And I am missing my classes, of which there are not many left. I would return to Hogwarts, now.”
\sbreak

When Hermione woke the third time (though it felt like she’d only closed her eyes for a moment) the Sun was even lower in the sky, almost fully set. She felt a little more alive and, strangely, even more exhausted. This time it was Professor Flitwick who was standing next to her bed and shaking her shoulder, a tray of steaming food floating next to him. For some reason she’d thought Harry Potter ought to be leaning over her bedside, but he wasn’t there. Had she dreamed that? She couldn’t remember dreaming.

It developed (according to Professor Flitwick) that Hermione had missed dinner in the Great Hall, and was being woken to eat. And then she could go back to the Ravenclaw dorm, and her own bed, to sleep the rest of the night.

She ate in silence. There was a part of her that wanted to ask Professor Flitwick whether \emph{he} thought she’d been Memory-Charmed or she’d tried to kill Draco Malfoy of her own will—

\emph{—like she remembered doing—}

—but most of her was afraid to find out. \emph{Afraid to find out} was a warning sign, according to Harry Potter and his books; but her mind felt tired, \emph{bruised,} and she couldn’t muster the strength to override it.

When she and Professor Flitwick left the infirmary they found Harry Potter sitting cross-legged outside the door, quietly reading a psychology textbook.

“I’ll take her from here,” said the Boy-Who-Lived. “Professor McGonagall said it would be all right.”

Professor Flitwick seemed to accept this, and departed after a stern look at both of them. She couldn’t imagine what the stern look was supposed to say, unless it was \emph{don’t try to kill any more students.}

The footsteps of Professor Flitwick faded, and the two of them stood alone outside the doors of the infirmary.

She looked at the green eyes of the Boy-Who-Lived, the mess of hair that didn’t quite obscure the scar on his forehead; she looked upon the face of the boy who’d given all his money to save her without a second thought. There were feelings inside her—guilt, shame, embarrassment, other things as well—but no words. There was nothing she knew how to say.

“So,” Harry said abruptly, “I did a quick skim through my psychology books to see what they said about post-traumatic stress disorder. The old books said you should talk about the experience immediately afterward with a counselor. The newer research says that when they actually ran experiments, it turned out that talking about it immediately afterward made it worse. Apparently what you really ought to do is run with your mind’s natural impulse to repress the memories and just not think about it for a while.”

It was so \emph{normal} for the way she and Harry usually talked that she felt a sudden burning in her throat.

\emph{We don’t have to talk about it.} That was what Harry had just said, more or less. It felt like cheating, maybe even like a lie. Nothing \emph{was} normal. Everything wrong was still horribly wrong, everything left unsaid still needed to be said...

“Okay,” said Hermione, because there wasn’t anything else to say, anything else at all.

“I’m sorry I wasn’t waiting when you woke up,” Harry said, as they started to walk. “Madam Pomfrey wouldn’t let me in, so I just stayed out here.” He gave a small, sad-looking shrug. “I suppose I should be out there trying to run damage control on public relations, but... honestly I’ve never been good at that, I just end up speaking sharply at people.”

“How bad is it?” She thought her voice should have come out in a whisper, a croak, but it didn’t.

“Well—” Harry said with obvious hesitation. “The thing you’ve got to understand, Hermione, is that you had a lot of defenders at breakfast-time today, but everyone on your side was... \emph{making stuff up}. Draco tried to kill you first, things like that. It was Granger versus Malfoy, that’s how people saw it, like a seesaw where pushing his side down meant pushing your side up. I told them you were probably \emph{both} innocent, that you’d both been Memory-Charmed. They didn’t listen, both sides treated me like a traitor trying to play the middle. And then people heard that Draco had testified under Veritaserum that he’d been trying to help you before the battle—stop making that expression, Hermione, you didn’t actually do anything to him. Anyway, all people understood was that the pro-Malfoy faction had been right and the pro-Granger faction had been wrong.” Harry gave a small sigh. “I \emph{told} them that when the truth came out later they’d be embarrassed...”

“How bad is it?” she said again. This time her voice did come out weaker.

“Remember Asch’s conformity experiment?” Harry said, turning his head to give her a serious look.

Her mind was \emph{slow to remember} for a few seconds, which frightened her, but then the reference came back. In 1951, Solomon Asch had taken some experimental subjects, and each one had been put among a row of other people who looked like them, seeming like other experimental subjects, but actually confederates of the experimenter. They’d shown a reference line on a screen, labeled X, next to three other lines, labeled A, B, and C. The experimenter had asked which line X was the same length as. The correct answer had obviously been C. The other ‘subjects’, the confederates, had one after another said that X was the same length as B. The real subject had been put second-to-last in the order, so as not to arouse suspicion by being last. The test had been to see whether the real subject would ‘conform’ to the standard wrong answer of B, or voice the obviously correct answer of C.

75\% of the subjects had ‘conformed’ at least once. A third of the subjects had conformed more than half the time. Some had reported afterward actually believing that X was the same length as B. And that had been in a case where the subjects hadn’t known any of the confederates. If you put people around others who belonged to the same group as them, like someone in a wheelchair next to other people in a wheelchair, the conformity effect got even stronger...

Hermione had a sickening feeling where this was going. “I remember,” she whispered.

“I gave the Chaos Legion anti-conformity training, you know. I had each Legionnaire stand in the middle and say ‘Twice two is four!’ or ‘Grass is green!’ while everyone else in the Chaos Legion called them idiots or sneered at them—Allen Flint did really good sneers—or even just gave them blank looks and then walked away. The thing you’ve got to remember is, \emph{only} the Chaos Legion has ever practiced anything like that. Nobody else in Hogwarts even knows what conformity \emph{is.}”

“Harry!” Her voice was wobbling. “How bad \emph{is} it?”

Harry gave another sad-looking shrug. “Everyone in the second year and above, since they don’t know you. Everyone in Dragon Army. All of Slytherin, of course. And, well, most of the rest of magical Britain too, I think. Remember, Lucius Malfoy controls the \emph{Daily Prophet}.”

“Everyone?” she whispered. Her limbs had started to feel cold, like she’d just gotten out of an unheated swimming pool.

“What people really believe doesn’t feel like a \emph{belief}, it feels like the way the world \emph{is.} You and I are standing in a private little bubble of the universe where Hermione Granger got Memory-Charmed. Everyone else is living in the world where Hermione Granger tried to murder Draco Malfoy. If Ernie Macmillian—”

Her breath caught in her throat. \emph{Captain Macmillian—}

“—thinks he’s ethically prohibited from being your friend now, well, he’s trying to do the right thing as he understands it, in the world he thinks he lives in.” Harry’s eyes were very serious. “Hermione, you’ve told me a lot of times that I look down too much on other people. But if I expected too much of them—if I expected people to get things \emph{right}—I really would hate them, then. Idealism aside, Hogwarts students don’t \emph{actually} know enough cognitive science to take responsibility for how their own minds work. It’s not their fault they’re crazy.” Harry’s voice was strangely gentle, almost like an adult’s. “I know it’s going to be harder on you than it would be on me. But remember, eventually the real culprit gets nailed. The truth comes out, everyone who was confidently wrong gets embarrassed.”

“And if the real culprit doesn’t get caught?” she said in a trembling voice.

\emph{...or if it turns out to be me after all?}

“Then you can leave Hogwarts and go to the Salem Witches’ Institute in America.”

“\emph{Leave Hogwarts?}” She’d never even thought of that possibility except as an ultimate punishment.

“I... Hermione, I think you might want to do that anyway. Hogwarts isn’t a castle, it’s insanity with walls. You \emph{have} got other options.”

“I’ll...” she stammered. “I’ll have... to think about it...”

Harry nodded. “At least nobody’s going to try hexing you, not after what the Headmaster said at dinner tonight. Oh, and Ron Weasley came up to me, looking very serious, and told me that if I saw you first, I should tell you that he’s sorry for having thought badly of you, and he’ll never speak ill of you again.”

“\emph{Ron} believes I’m innocent?” said Hermione.

“Well... he doesn’t think you’re \emph{innocent,} per se...”
\sbreak

The whole Ravenclaw dorm went silent as the two of them walked in.

Staring at them.

Staring at her.

(She’d had nightmares like this.)

And then, one by one, people looked away from her.

Penelope Clearwater, the 5th-year prefect in charge of first-years, looked away slowly and deliberately, turning her head to face in another direction.

Su Li and Lisa Turpin and Michael Corner, all sitting at a table together, all of whom she’d helped with their homework at one time or another, all looked away, their faces suddenly nervous, the moment she tried to catch their eyes.

A third-year witch named Latisha Randle, whom S.P.H.E.W. had twice saved from Slytherin bullies, quickly bent back over her desk and started doing homework again.

Mandy Brocklehurst looked away from her.

If Hermione didn’t burst into tears, then, it was only because she’d expected it, had played it out in her mind over and over again. At least people weren’t screaming at her or shoving her or hexing her. They were just looking away—

Hermione walked very straight up to the staircaise that led toward the first-year girl’s dorms. (She didn’t see Padma Patil or Anthony Goldstein looking at her, those two lone heads turning to track her as she left.) From behind her, she heard Harry Potter saying in a very calm tone, “Now eventually the truth’s going to come out, you all. So if you’re all that confident she’s guilty, can I ask you all to sign this paper right here, saying that if she later turns out to be innocent, she gets to say ‘I told you so’ and then hold it over you for the rest of your lives? Step on up, one and all, don’t be cowards, if you really believe you shouldn’t be afraid to bet—”

She was halfway up the stairs when she realized that there would be other girls inside her dorm room, too.
\sbreak

The stars hadn’t quite come out yet, only one or two of the brightest ones visible through the reddish-purple haze of the horizon, though the sun had fully sunk.

Hermione’s hands dug into the harsh stone of the parapet guarding the small balcony, where she’d ducked out of the stairwell after realizing that—

—\emph{she couldn’t just go back to bed}—

—the words echoed in her mind like ‘You can’t go home again’ ought to sound.

She stared out at the empty grounds, the fading sunset, the sprouting grass so far below.

Tired, she was tired, she couldn’t think now, she needed to sleep. Professor Flitwick had told her that she needed to sleep, and there’d been yet another potion with her dinner. Maybe that was how wizarding society treated horrible traumas to innocent young girls, just made them sleep a lot afterward.

She should go to her room and sleep, but she was afraid to go someplace where other people were. Afraid of how they might look at her, or look away.

Fragments of thought chased themselves around a mind too exhausted to finish or connect them, as the night fully set in.

\emph{Why—}

\emph{Why did all this happen—}

\emph{Everything was fine a week ago—}

\emph{Why—}

From behind her came the creaky sound of an opening door.

She turned her head and looked.

Professor Quirrell was leaning against the doorway she’d walked through, silhouetted like a cardboard cutout by the light of the Hogwarts torches lit behind him, in the open door. She couldn’t see his expression, though the doorway behind him was bright; his eyes, his face, everything she could see from here lay within night’s shadow.

The Defense Professor of Hogwarts, number one on the list of people who might’ve done this. She hadn’t even realized she \emph{had} a suspect list until that moment.

The man stood within that doorway, saying nothing; and she couldn’t see his eyes. What was he even \emph{doing} there in the first place—

“Are you here to kill me?” said Hermione Granger.

Professor Quirrell’s head tilted at that.

Then the Defense Professor started toward her, the dark silhouette raising one hand slowly and deliberately, as though to push her off the Ravenclaw tower—

“\emph{Stupefy!”}

The burst of adrenaline overrode everything, she drew her wand without thinking, her lips formed the word of their own accord, the stunbolt leapt out of her wand and—

—\emph{slowed to a stop} in front of Professor Quirrell’s raised hand, rippling in midair like it was still trying to fly and making a slight hissing sound.

The red glow illuminated Professor Quirrell’s face for the first time, showing a strange fond smile.

“Better,” said Professor Quirrell. “Miss Granger, you are still a student in my Defense class. As such, if you consider me a threat, I do not expect you to just look at me sadly and ask if I am there to kill you. Minus two Quirrell points.”

She was entirely unable to form words.

The Defense Professor flicked his forefinger casually at the suspended stunbolt, sending the hex shooting back over her head, far into the night, so that they stood again in darkness. Then Professor Quirrell walked out of the doorway, which swung shut behind him; and a soft white light sprung up around the two of them, so that she could see his face once more, still with that strange fond smile.

“What are you—what are you \emph{doing} here?”

A few more steps took Professor Quirrell to a higher part of the balcony’s ramparts, where he put his elbows down on the stone, and leaned over heavily, looking up into the night.

“I came here straight upon being released by the Aurors, the moment I finished reporting to the Headmaster,” said Professor Quirrell in a quiet voice, “because I am your teacher, and you are my student, and I am responsible for you.”

Hermione understood, then; remembering what Professor Quirrell had said to Harry in the second Defense lesson of the year, about controlling his anger. She felt the flush of shame all the way down her chest. It took a moment after that for knowledge to override mortification, for her to force out the words—

“I—” said Hermione. “Harry thinks—that I \emph{didn’t}— lose my temper, I mean—”

“So I heard,” said Professor Quirrell in rather dry tones. He shook his head, as though at the stars themselves. “The boy is fortunate that I have crossed the line from annoyance with his self-destructiveness, into sheer curiosity as to what he shall do next. But I agree with Mr.~Potter’s assessment of the facts. This murder was well-planned to evade detection both by the wards of Hogwarts and the Headmaster’s timely eye. Naturally, in such a thoughtful murder, some innocent would be placed to take the blame.” A brief, wry smile crossed the Defense Professor’s lips, though he wasn’t looking at her. “As for the notion that you did it yourself—I consider myself a talented teacher, but even I could not teach such murderous intent to a student as obstinate and untalented as Hermione Granger.”

The part of her brain that said \emph{What?} in indignation wasn’t anywhere near loud enough to reach her lips.

“No...” said Professor Quirrell. “That is not why I am here. You have made no effort to hide your dislike for me, Miss Granger. I thank you for that lack of pretense, for I much prefer true hate to false love. But you are still my student, and I have a word to say to you, if you will hear it.”

Hermione looked at him, still fighting down the aftereffects of the adrenaline from before. The Defense Professor seemed to be just staring up at the dark sky, in which the stars were becoming visible.

“I was going to be a hero, once,” said Professor Quirrell, still looking upward. “Can you believe that, Miss Granger?”

“No.”

“Thank you again, Miss Granger. It is true nonetheless. Long ago, long before your time or Harry Potter’s, there was a man who was hailed as a savior. The destined scion, such a one as anyone would recognize from tales, wielding justice and vengeance like twin wands against his dreadful nemesis.” Professor Quirrell gave a soft, bitter laugh, looking up at the night sky. “Do you know, Miss Granger, at that time I thought myself already cynical, and yet... well.”

The silence stretched, in the cold and the night.

“In all honesty,” said Professor Quirrell, looking up at the stars, “I still don’t understand it. They should have known that their lives depended on that man’s success. And yet it was as if they tried to do everything they could to make his life \emph{unpleasant.} To throw every possible obstacle into his way. I was not naive, Miss Granger, I did not expect the power-holders to align themselves with me so quickly—not without something in it for themselves. But their power, too, was threatened; and so I was shocked how they seemed content to step back, and leave to that man all burdens of responsibility. They sneered at his performance, remarking among themselves how they would do better in his place, though they did not condescend to step forward.” Professor Quirrell shook his head as though in bemusement. “And it was the strangest thing—the Dark Wizard, that man’s dread nemesis—why, those who served \emph{him} leapt eagerly to their tasks. The Dark Wizard grew crueler toward his followers, and they followed him all the more. Men fought for the chance to serve \emph{him}, even as those whose lives depended on that other man made free to render his life difficult... I could not understand it, Miss Granger.” Professor Quirrell’s face was in shadow, as he looked upward. “Perhaps, by taking on himself the curse of action, that man removed it from all others? Was that why they felt free to hinder his battle against the Dark Wizard who would have enslaved them all? Believing men would act in their own interest was not cynicism, it turned out, but sheerest optimism; in reality men do not meet so high a standard. And so in time that one realized he might do better fighting the Dark Wizard alone, than with such followers at his back.”

“So—” Hermione’s voice sounded strange in the night. “You left your friends behind where they’d be safe, and tried to attack the Dark Wizard all by yourself?”

“Why, no,” said Professor Quirrell. “I stopped trying to be a hero, and went off to do something else I found more pleasant.”

\emph{“What?”} said Hermione without thinking at all. “That’s \emph{horrible!”}

The Defense Professor turned his head down from the sky to regard her; and she saw, in the light of the doorway, that he was smiling—or at least half his face was smiling. “Are you going to tell me, Miss Granger, that I am an awful person? Well, perhaps I am. But then are people who never even try to be heroes still worse? If I had never done anything at all, like them, would you have thought better of me?”

Hermione opened her mouth and then found that, once again, she didn’t have anything to say. It wasn’t right to walk away from being a hero, you couldn’t just \emph{do} that, but she didn’t \emph{want} to say that everyone who wasn’t a hero was nothing, that was Quirrell-thinking...

The smile, or half-smile, had disappeared. “You were foolish,” the Defense Professor said quietly, “to expect any lasting gratitude from those you tried to protect, once you named yourself a heroine. Just as you expected that man to go on being a hero, and called him horrible for stopping, when a thousand others never lifted a finger. It was only \emph{expected} that you should fight bullies. It was a tax you owed, and they accepted it like princes, with a sneer for the lateness of your payment. And you have already witnessed, I wager, that their fondness vanished like dust in the wind once it was no longer in their interest to associate with you...”

The Defense Professor slowly straightened off the balcony, standing almost straight, turning to regard her fully.

“But you don’t have to be a hero, Miss Granger,” said Professor Quirrell. “You can stop anytime you please.”

That idea...

...\emph{had} occurred to her before, several times over the last two days.

\emph{People become who they are meant to be, by doing what is right,} Headmaster Dumbledore had told her. The trouble was that there seemed to be two different right things to do. There was the part of her which said that \emph{right} was to go on being a heroine, and stay at Hogwarts, she didn’t know what was going on but a heroine wouldn’t just run away.

And there was also the voice of common sense saying that young children shouldn’t ever stay around danger, that was what adults were for; the voice of every school poster that said not to take candy from strangers. That was also right.

Hermione Granger stood there on that balcony, looking at Professor Quirrell silhouetted by the emerging stars, and she didn’t understand; she didn’t understand how the Defense Professor could be gazing at her with his face showing concern; she didn’t understand the notes of pain in the Defense Professor’s voice that caught at her; she didn’t understand \emph{why} she was being told all this.

“You don’t even like me, Professor,” said Hermione.

A small smile flickered on Professor Quirrell’s face. “I suppose I could go on about how I am angered that this affair has taken up my valuable time and disrupted my Defense classes. But mostly, Miss Granger, you are my student, and whatever other professions I may have once held, I think I have been a good teacher at Hogwarts, have I not?” Suddenly Professor Quirrell’s eyes seemed very tired. “As your teacher, then, I am advising you that you have other career options. I should not like to see anyone else going down my path.”

Hermione swallowed. It was a side of Professor Quirrell she’d never seen or imagined, and it was eating away at her preconceptions.

Professor Quirrell watched her for a moment, and then looked away from her again, back up at the stars. When he spoke this time his voice was quieter. “Someone here is targeting you, Miss Granger, and I cannot ward you as I warded Mr.~Malfoy. The Headmaster has prevented it, for what he claims to be good reasons. It is easy to become fond of Hogwarts, I know, for I am fond of it as well. But in France they take a different view of the Ancient Houses than in Britain; and Beauxbatons would not mistreat you, I think. Whatever else you imagine of me, I swear that if you asked me to see you safely in Beauxbatons, I would do all in my power to convey you there.”

“I can’t just—” Hermione said.

“But you \emph{can,} Miss Granger.” Now the pale blue eyes watched her intently. “Whatever you wish to make of your life, you cannot attain it at Hogwarts, not anymore. This place is ruined for you now, even leaving aside all other threats. Simply ask Harry Potter to command you to go to Beauxbatons and live out your life in peace. If you stay here, he is your master in the eyes of Britain and its laws!”

She hadn’t even been thinking about that, it paled so much in comparison to being eaten by Dementors; it had been important to her before, but now it all seemed childish, unimportant, pointless, so why were her eyes burning?

“And if that fails to move you, Miss Granger, consider also that Mr.~Potter has, just today at lunchtime, threatened Lucius Malfoy, Albus Dumbledore, and the entire Wizengamot because he cannot think sensibly when something threatens to take you from him. Are you not frightened of what he will do next?”

It made sense. Terrible sense. Dreadful awful sense.

It made \emph{too much} sense—

She couldn’t have described it in words, what triggered the realization, unless it was the sheer \emph{pressure} that the Defense Professor was exerting on her.

That if the Defense Professor \emph{was} behind this whole thing—then Professor Quirrell had done it all \emph{just to get her out of the way of his plans for Harry.}

Without any conscious decision, she shifted her weight to the other foot, her body moving away from the Defense Professor—

“So you think I am the one responsible?” said Professor Quirrell. His voice sounded a little sad as he said it, and her own heart almost stopped from hearing it. “I suppose I cannot blame you. I am the Defense Professor of Hogwarts, after all. But Miss Granger, even \emph{assuming} that I am your enemy, common sense should still tell you to get away from me \emph{very quickly}. You cannot use the Killing Curse, so the correct tactic is to Apparate away. I do not mind being the villain of your imagination if it makes matters clearer. Leave Hogwarts, and leave me to those who can handle me. I will arrange for the transportation to be through some family of good repute, and Mr.~Potter will know to blame me if you do not arrive safely.”

“I—” She was feeling cold, the night air chilling her skin, or maybe being chilled by it. “I’ve got to think about it—”

Professor Quirrell shook his head. “No, Miss Granger. Your departure will take time for me to arrange, and I have less time left than you may think. This decision may be painful for you, but it should not be ambiguous; much weighs in the balance of these scales, but not evenly. I must know tonight whether you intend to go.”

\emph{And if not—}

Was the Defense Professor warning her deliberately? That if she didn’t run, he would strike again?

Why would it matter so much, what did Professor Quirrell want to \emph{do} with Harry?

\emph{Hermione Granger, I shall be less subtle than is usual for a mysterious old wizard, and tell you outright that you cannot} \emph{imagine} \emph{how badly things could go if the events surrounding Harry Potter turn to ill.}

The most powerful wizard in the world had told her that, when he was talking about how important it was that she \emph{not} stop being Harry’s friend.

Hermione swallowed, she swayed a little where she stood, on the stone balcony of a magical castle. Suddenly the whole deadly absurdity of the situation seemed to rise up and grab her by the throat, that twelve-year-old girls \emph{shouldn’t} be in danger, \emph{shouldn’t} be thinking about such things, that Mum would want her to \scream{run away} and her father would have a heart attack if he even knew she was being faced with the question.

And she knew, then, as Harry and Dumbledore had both tried to warn her, that everything she’d ever thought about being a heroine had been mistaken. That there wasn’t really any such thing as heroes, outside of stories. There was just horrible danger, and being arrested by Aurors and put in cells next to Dementors, pain and fear and—

“Miss Granger?” said the Defense Professor.

She said nothing. All the words were blocked in her throat.

“I need a decision, Miss Granger.”

She kept her jaw locked, didn’t let any words come out.

Finally the Defense Professor sighed. Slowly the white light failed, and slowly the door behind him swung open, so that he was once again a black silhouette against the opening. “Good night, Miss Granger,” he said, and turned his back to her, and walked away into Hogwarts.

It took a while for her breathing to slow down again. Whatever had happened here tonight, it didn’t feel anything like victory. She’d fought so hard just to stop herself from saying \emph{Yes} in the face of the Defense Professor’s pressure, and now she didn’t even know if she’d done the right thing.

When she walked back into the light herself (after exhaustion had overtaken everything and sleep was once more a possibility), she thought she heard it as she was within the doorway, from behind her and above her, a distant cawing cry.

But it wasn’t meant for her, she knew, so she started climbing up the stairs toward her dorm room.

The other girls were probably asleep by now, and wouldn’t look at her, or look away—

She felt the tears start, and this time she didn’t stop them.