\chapter{Interlude with the Confessor: Sunk~Costs}

\lettrine{S}{he} descended the stairs of roughened stone and crude mortar, keeping a \emph{Lumos} lit through the distances between fire-sconces, holding aloft her wand through the gaps from light to light.

She came to the empty rock cavern pierced by many dark openings, lit by a torch of ancient style that fired as she entered.

There was no one else there, as yet, and after long minutes of nervous standing, she began the spell to Transfigure a cushioned sofa large enough for two people to sit, or maybe even lie down on. A simple wooden stool would have been easier, she could have done that in fifteen seconds, but—well—

Even when the sofa was fully conjured, Professor Snape still hadn’t arrived, and she sat down on the left side of her sofa with her pulse hammering in her throat. Somehow she was only becoming more nervous, not less, as the delay stretched.

She knew this was the last time.

The last time before all these memories went away, and Rianne Felthorne found herself in a mysterious cavern, wondering what was going on.

There was something about it that felt like dying.

The books said a properly done Obliviation wasn’t harmful, people forgot things all the time. People dreamed, and then woke up without remembering their dreams. Obliviation didn’t even involve that much discontinuity, it was like being distracted by a loud noise and losing track of a thought you couldn’t seem to remember afterward. That was what the books said, and why Memory Charms were fully approved by the Ministry for all authorized governmental purposes.

But still, \emph{these thoughts}, the thoughts she was thinking right now; soon nobody would have them anymore. When she looked ahead in the future, there was nobody to complete the thoughts she wasn’t finished thinking. Even if she managed to tie up all the loose ends in her mind over the next minute, there wouldn’t be anything left of it afterward. Wasn’t that exactly what you would find yourself reflecting on, if you were going to die in the next minute?

There came the sound of muffled steps...

Severus Snape emerged into the cavern.

His eyes moved to her sitting on the sofa, and a brief smile moved his lips; and it was strange, because the smile wasn’t sardonic, or angry, or cold.

“Thank you, Miss Felthorne,” Snape said quietly, “that was considerate of you.” The Potions Master took out his wand and performed the usual privacy Charms, and then he moved toward her, and sat down heavily beside her on the Transfigured sofa.

Her pulse was now pounding for another reason entirely.

She slowly turned to look at Professor Snape, and saw that his head was leaning back against the sofa, and his eyes were closed. Not sleeping, though. His face appeared tense, unrelaxed, bearing pain.

She knew—she was suddenly certain—that she was only allowed to see this sight because she wouldn’t remember it afterward; and that nobody before her had ever been allowed to see it.

The frantic conversation going on inside Rianne Felthorne’s mind sounded something like this: \emph{I could just lean over and kiss him, you are completely out of your tiny mind, his eyes are closed I bet he wouldn’t stop me in time, I bet it would be years before anyone found your body—}

But Professor Snape opened his eyes then (to her inner disappointment and relief), and said, in a more normal voice, “Your payment, Miss Felthorne.” From his robe he took a ruby, cut to Gringotts standard, and held it out toward her. “Fifty facets. I will not mind if you count them.”

She held out a trembling hand, hoping that Snape would press the ruby into her fingers, that she would feel a touch of his skin alive against hers—

But instead Snape raised his hand slightly and dropped the ruby into her hand, then leaned back against the couch. “You will remember finding it lying on the ground of this cavern, where you came exploring,” said Snape. “And since nobody except you will actually believe that, you will remember thinking that it would be less troublesome if you deposited the money into a separate box in Gringotts.”

For a stretch there was only the faint crackling of the torch.

“Why—” Rianne Felthorne said. \emph{He knows I won’t remember.} “Why \emph{did} you do it? I mean—you said to tell you where bullies would be, and who they would be, but not whether Granger would be there. And I know, the way the Time-Turner works, if you want to \emph{make} Granger be there, you can’t be told whether it’s already happened. So I did work out that \emph{we} were the ones telling her where to go. We were, weren’t we?”

Snape nodded without speaking. He had closed his eyes again.

“But,” said Rianne, “I didn’t understand \emph{why} you were helping her. And now—after what you did to Granger in the Great Hall—I just don’t understand at all.” Rianne had never thought of herself as particularly nice. She’d taken little notice of the controversy over the Sunshine General. But something about \emph{helping} Granger fight bullies had...\ well, she’d gotten used to thinking of that as the good side, and thinking of \emph{herself} as being on the good side. And she’d found she actually liked it. It was hard, to just let that go. “Why’d you do that, Professor Snape?”

Snape shook his head, his face tightened.

“Is—” Rianne said falteringly. “I mean—so long as we’re here—is there anything you do want to talk about?” There was something \emph{she} wanted to say, but she couldn’t make the words pass her own lips.

“I can think of one matter,” Snape said after a pause. “If you are interested, Miss Felthorne.”

Snape’s eyes were still shut, so she couldn’t just nod her head. Her voice almost broke, when she forced herself to say “Yes.”

“There’s a certain boy in your class who likes you, Miss Felthorne,” Snape said from behind his closed eyes. “I won’t say his name. But he watches you every time you walk across the room, when he thinks you aren’t looking. He dreams about you and desires to possess you, but he’s never asked you for so much as a kiss.”

Her heart started hammering even harder.

“Please tell me the honest truth, Miss Felthorne. What do you think of that boy?”

“Well—” she said. She was stumbling over her words. “I think—to never even ask for one kiss—would be—”

\emph{Sad.}

\emph{Just too p}\emph{itiful.}

“Weakness,” she said, her voice trembling.

“I agree,” said Snape. “Suppose that boy had helped you, though. Would you think that you owed him a kiss, if he asked?”

She inhaled sharply—

“Or would you think,” Snape continued, his eyes still closed, “that he was just being bothersome?”

The words stabbed into her like a knife and she couldn’t help gasping out loud.

Snape’s eyes flew open, and his gaze met hers across the sofa.

Then the Potions Master began to laugh, small sad chuckles.

“No, not \emph{you,} Miss Felthorne!” Snape said. “Not \emph{you!} We really \emph{are} talking about a boy. One who attends your Potions class, in fact.”

“Oh,” she said. She tried to remember what Snape had said before, now feeling rather unnerved as she thought of some boy watching her, always silently watching. “Well, um, in that case. That’s kind of \emph{creepy}, actually. Who is it?”

The Potions Master shook his head. “It doesn’t matter,” said Snape. “Out of curiosity, what would you think if that boy were still in love with you years later?”

“Um,” she said, feeling a bit confused, “that would be totally pathetic?”

The torch crackled a bit in the cavern.

“It’s strange,” Snape said quietly. “I have had two mentors, over the course of my days. Both were extraordinarily perceptive, and neither one ever told me the things I wasn’t seeing. It’s clear enough why the first said nothing, but the second...” Snape’s face tightened. “I suppose I would have to be naive, to ask why he stayed silent.”

The quiet stretched, while Rianne tried frantically to think of something to say.

“It is an odd thing,” Snape said, his voice still softer, “to look back after only thirty-two years, and wonder when your life was ruined past all rescuing. Was it determined when the Sorting Hat cried ‘Slytherin!’ for me? It seems unfair, since I was offered no choice; the Sorting Hat spoke the moment it touched upon my head. Yet I cannot claim it named me untruly. I never treasured knowledge for its own sake. I was not loyal to the one person I called friend. I was never one for righteous fury, then or now. Courage? There is no bravery in risking a life already ruined. My little fears have always mastered me, and I never turned aside from any of the paths I walked down, for those little fears. No, the Sorting Hat could never have put me in her House. Perhaps my final loss was determined, even then. Is that fair, I ask, even if the Sorting Hat speaks truly? Is it fair that some children should possess more courage than others, and thus a man’s life be judged?”

Rianne Felthorne was starting to realize that she’d never had the tiniest inkling of who her Potions Master was inside, and unfortunately all these dark hidden depths weren’t helping her with her problem.

“But no,” Snape said. “I know where it went wrong for the last time. I could point to the very day and hour I missed my final chance. Miss Felthorne, did the Sorting Hat offer you Ravenclaw?”

“Y-yes,” she said without thinking.

“Have you ever been any good at riddles?”

“Yes,” she said again, because whatever Professor Snape was about to say, she wouldn’t hear it if she said \emph{no.}

“I am terrible at riddles,” Snape said in a distant voice. “I was once given a riddle to solve, and I did not understand even the simplest part until too late. I did not even realize the riddle was meant for \emph{me} until too late. I thought I had merely happened to overhear it, when in truth it was I who was overheard. So I sold my riddle to another, and that is when the wreckage of my life passed beyond retrieval.” Snape’s voice was still distant, sounding more abstracted than sorrowful. “And even now, I understand nothing of importance. Tell me, Miss Felthorne, suppose I were carrying a knife, and I tripped over a baby and stabbed myself. Would you say that the baby had,” Snape’s voice lowered, as though he were imitating some still deeper voice, “\shout{The power to vanquish} me?”

“Um...\ no?” she said hesitantly.

“Then what \emph{does} it mean to have the power to vanquish someone?”

Rianne considered the puzzle. (Wishing, not for the first time in her life, that she had chosen Ravenclaw and to perdition with her parents’ disapproval; but the Sorting Hat had never offered her Gryffindor.) “Well...” Rianne said. She was having trouble putting her thoughts into words. “It means you’ve got the \emph{power}, but you don’t \emph{have} to do it. It means you could do it if you tried—”

“Choice,” the Potions Master said in the same faraway voice, as though he wasn’t really talking to her at all. “There will be a choice. That is what the riddle seems to imply. And that choice is not a foregone conclusion to the chooser, for the riddle does not say, \emph{will vanquish,} but rather \emph{the power to vanquish.} How would a grown man mark a baby as his equal?”

“What?” said Rianne. She didn’t understand that at all.

“\emph{Marking} a baby is simple. Any strong Dark curse would produce a lasting scar. But such may be done to any child. What mark would signify that a baby was your \emph{equal?}”

She answered with the first thought that came to mind. “If you signed a betrothal contract, that would mean you’d be equals with them someday, when they grew up and you got married.”

“That...” said Snape. “That’s probably not it, Miss Felthorne, but thank you for trying.” The long delicate fingers, honed by stirring potions to unimaginably fine tolerances, reached up and rubbed at the temples of the man’s forehead. “It is enough to drive me to madness, so much hinging on such fragile words. Power he knows not...\ it \emph{must} be more than some unknown spell. Not something \emph{he} could acquire simply by practice and study. Some innate talent? No one can learn to be a Metamorphmagus...\ and yet that hardly seems like a power he \emph{knows not}. Nor can I see how \emph{either} could destroy all but a remnant of the other; I can see it in one direction, but not the reverse...” The Potions Master sighed. “And none of this means anything to you, does it, Miss Felthorne? The words are nothing. The words are shadows. It is her \emph{intonation} which carries the meaning and that is something I’ve never been able to...”

The Potions Master trailed off, while Rianne stared at him.

“A \emph{prophecy?}” Rianne said in a high squeak. “You heard a \emph{prophecy?}” She’d taken Divination for a couple of months before dropping it in disgust, and she knew that much about how it worked.

“I will try one last thing,” said Snape. “Something I have not tried before. Miss Felthorne, listen to the \emph{sound} of my voice, the \emph{way} I say it\emph{,} not the words themselves, and tell me what you think it means. Can you do that? Good,” said Snape, as she nodded obediently, though she wasn’t sure at all what she was supposed to do.

And Severus Snape drew a breath, and intoned, “\shout{For those two different spellets cannot exist in the same vuld.}”

It sent shivers down her spine, all the worse for knowing the hollow words had been spoken in imitation of a true prophecy. Unnerved, she blurted out the first thing which came to mind, which might have been influenced by her present company. “Those two different ingredients cannot exist in the same cauldron?”

“But why\emph{ not}, Miss Felthorne? What is the \emph{meaning} of a statement like that? What are we really being told?”

“Ah...” she hazarded. “If the two ingredients mix, they’ll catch fire and burn the cauldron?”

Snape’s face did not change expression in the slightest.

“Perhaps,” Snape finally said, after they’d sat on the sofa in awful silence for what seemed like minutes. “It would explain the word \emph{must}. Thank you, Miss Felthorne. Once again you have been most helpful.”

“I—” she said, “I was glad to—” and the words stuck in her throat. The Potions Master had thanked her with a tone of finality, and she knew that the time of the Rianne Felthorne who remembered these moments was drawing to an end. “I wish I didn’t have to forget this, Professor Snape!”

“I wish,” Severus Snape said in a whisper so low she could hardly hear it, “that everything had been different...”

The Potions Master stood up from the sofa, the weight of his presence vanishing from beside her. He turned and drew his wand from his robes, pointing it at her.

“Wait—” she said. “Before that—”

Somehow it was unbelievably hard to take the first step from fantasy to reality, from imagining to doing. Even if it was only one step and would never go any further. The gap stretched like the distance between two mountains.

The Sorting Hat had never offered her Gryffindor...

...was it fair that thus a woman’s life be judged?

\emph{If you can’t} \emph{say it now, when you won’t even remember it afterward—when nothing will continue from this moment, just as if you were to die—then when will you ever say it, to anyone?}

“Can I have a kiss first?” said Rianne Felthorne.

Snape’s black eyes studied her so intensely that her blush started to reach all the way to her chest, and she wondered if he knew perfectly well that she was still being weak, and it wasn’t a kiss she’d truly wanted.

“Why not,” the Potions Master said quietly, and he leaned his head down over the sofa and kissed her.

It was nothing like she’d imagined. In her fantasies Snape’s kisses were fierce, seized from her, but this was—it was just \emph{awkward,} actually. Snape’s lips pressed down too hard on hers, forcing them back against her teeth, and the angle wasn’t right and their noses were sort of bending and his lips were too \emph{tight} and—

Only as the Potions Master straightened back up again, raising his wand once more, did she realize.

“That wasn’t—” she said in a wondering voice, looking up at him. “That wasn’t—was it—your \emph{first}—”

Rianne Felthorne blinked at the stone cavern she’d discovered, still holding the extraordinary ruby she’d found embedded in the dirt of one corner. It was an incredible windfall, and she didn’t know why looking at the ruby made her feel so sad, like she’d forgotten something, something that had been precious to her.


