\chapter{The Planning Fallacy}

\epigraph{You think your day was surreal? Try mine.}{}

\lettrinemph{S}{ome} people would have waited until \emph{after} their first trip to Diagon Alley.
“Bag of element 79,” Harry said, and withdrew his hand, empty, from the mokeskin pouch.

Most people would have at least waited to get their \emph{wands} first.

“Bag of \emph{okane,}” said Harry. The heavy bag of gold popped up into his hand.

Harry withdrew the bag, then plunged it again into the mokeskin pouch. He took out his hand, put it back in, and said, “Bag of tokens of economic exchange.” That time his hand came out empty.

Harry Potter had gotten his hands on at least one magical item. Why wait?

“Professor McGonagall,” Harry said to the bemused witch strolling beside him, “can you give me two words, one word for gold, and one word for something else that isn’t money, in a language that I wouldn’t know? But don’t tell me which is which.”

“\emph{Ahava} and \emph{zahav,}” said McGonagall. “That’s Hebrew, and the other word means love.”

“Thank you, Professor. Bag of \emph{ahava.}” Empty.

“Bag of \emph{zahav.}” And it popped up into his hand.

“Zahav is gold?” Harry questioned, and McGonagall nodded.

Harry thought over his collected experimental data. It was only the most crude and preliminary sort of effort, but it was enough to support at least one conclusion:

“\emph{Aaaaaaarrrgh this doesn’t make any sense!}”

The witch beside him lifted a lofty eyebrow. “Problems, Mr.~Potter?”

“I just falsified every single hypothesis I had! How can it know that ‘bag of 115 Galleons’ is okay but not ‘bag of 90 plus 25 Galleons’? It can \emph{count} but it can’t \emph{add?} It can understand nouns, but not noun phrases that mean the same thing? The person who made this probably didn’t speak Japanese and \emph{I} don’t speak any Hebrew, so it’s not using \emph{their} knowledge, and it’s not using \emph{my} knowledge—” Harry waved a hand helplessly. “The rules seem \emph{sorta} consistent but they don’t \emph{mean} anything! I’m not even going to ask how a \emph{pouch} ends up with voice recognition and natural language understanding when the best Artificial Intelligence programmers can’t get the fastest supercomputers to do it after thirty-five years of hard work,” Harry gasped for breath, “but \emph{what} is going \emph{on?}”

“Magic,” said Professor McGonagall. She shrugged.

“That’s just a \emph{word!} Even after you tell me that, I can’t make any new predictions! It’s exactly like saying ‘phlogiston’ or ‘elan vital’ or ‘emergence’ or ‘complexity’!”

Professor McGonagall laughed aloud. “But it \emph{is} magic, Mr.~Potter.”

Harry slumped over a little. “With respect, Professor McGonagall, I’m not quite sure you understand what I’m trying to do here.”

“With respect, Mr.~Potter, I’m quite sure I don’t. Unless—this is just a guess, mind—you’re trying to take over the world?”

“No! I mean yes—well, \emph{no!}”

“I think I should perhaps be alarmed that you have trouble answering the question.”

Harry glumly considered the Dartmouth Conference on Artificial Intelligence in 1956. It had been the first conference ever on the topic, the one that had coined the phrase “Artificial Intelligence”. They had identified key problems such as making computers understand language, learn, and improve themselves. They had suggested, in perfect seriousness, that significant advances on these problems might be made by ten scientists working together for two months.

\emph{No. Chin up. You’re just} starting \emph{on the problem of unraveling all the secrets of magic. You don’t actually} know \emph{whether it’s going to be too difficult to do in two months.}

“And you \emph{really} haven’t heard of other wizards asking these sorts of questions or doing this sort of scientific experimenting?” Harry asked again. It just seemed so \emph{obvious} to him.

Then again, it’d taken more than two hundred years \emph{after} the invention of the scientific method before any Muggle scientists thought to systematically investigate what a \emph{human four-year-old} could or couldn’t understand. They could’ve found out in the eighteenth century but no one even thought to look until the twentieth. So you couldn’t really blame the much smaller wizarding world for not investigating the Retrieval Charm.

McGonagall, after pursing her lips for a moment, shrugged. “I’m still not sure what you mean by ‘scientific experimenting’, Mr.~Potter. As I said, I’ve seen Muggleborn students try to get Muggle science to work inside Hogwarts, and people invent new Charms and Potions every year.”

Harry shook his head. “Technology isn’t the same thing as science at all. And trying lots of different ways to do something isn’t the same as experimenting to figure out the rules.” There were plenty of people who’d tried to invent flying machines by trying out lots of things-with-wings, but only the Wright Brothers had built a wind tunnel... “Um, how many Muggle-raised children \emph{do} you get at Hogwarts every year?”

McGonagall looked thoughtful for a moment. “Around ten or so?”

Harry missed a step and almost tripped over his own feet. “\emph{Ten?}”

The Muggle world had a population of six billion and counting. If you were one in a million, there were twelve of you in New York and a thousand more in China. It was inevitable that the Muggle world would produce \emph{some} eleven-year-olds who could do calculus—Harry knew he wasn’t the only one. He’d met other prodigies in math competitions. In fact he’d been thoroughly trounced by competitors who probably spent literally \emph{all day} practicing math problems and who’d \emph{never} read a science-fiction book and who would burn out \emph{completely} before \emph{puberty} and \emph{never} amount to \emph{anything} in their future lives because they’d just practiced \emph{known} techniques instead of learning to think \emph{creatively}. (Harry was something of a sore loser.)

But...\ in the wizarding world...

Ten Muggle-raised children per year, who’d all ended their Muggle educations at the age of eleven? And McGonagall might be biased, but she had claimed that Hogwarts was the largest and most eminent wizarding school in the world...\ and it only educated up to the age of seventeen.

Professor McGonagall undoubtedly knew every last detail of how you went about turning into a cat. But she seemed to have literally never \emph{heard} of the scientific method. To her it was just Muggle magic. And she didn’t even seem \emph{curious} about what secrets might be hiding behind the natural language understanding of the Retrieval Charm.

That left two possibilities, really.

Possibility one: Magic was so incredibly opaque, convoluted, and impenetrable, that even though wizards and witches had tried their best to understand, they’d made little or no progress and eventually given up; and Harry would do no better.

\emph{Or...}

Harry cracked his knuckles in determination, but they only made a quiet sort of clicking sound, rather than echoing ominously off the walls of Diagon Alley.

Possibility two: He’d be taking over the world.

Eventually. Perhaps not right away.

That sort of thing \emph{did} sometimes take longer than two months. Muggle science hadn’t gone to the moon in the first week after Galileo.

But Harry still couldn’t stop the huge smile that was stretching his cheeks so wide they were starting to hurt.

He’d always been frightened of ending up as one of those child prodigies that never amounted to anything and spent the rest of their lives boasting about how cool they’d been at age ten. But then most adult geniuses never amounted to anything either. There were probably like a thousand people as intelligent as Einstein for every actual Einstein in history. Because they hadn’t gotten their hands on the one thing you absolutely needed to achieve greatness. They’d never found an important problem.

\emph{You’re mine now,} Harry thought at the walls of Diagon Alley, and all the shops and items, and all the shopkeepers and customers; and all the lands and people of wizarding Britain, and all the wider wizarding world; and the entire greater universe of which Muggle scientists understood so much less than they believed. \emph{I, Harry James Potter-Evans-Verres, do now claim this territory in the name of Science.}

Lightning and thunder completely failed to flash and boom in the cloudless skies.

“What are you smiling about?” inquired McGonagall, warily and wearily.

“I’m wondering if there’s a spell to make lightning flash in the background whenever I make an ominous resolution,” explained Harry. He was carefully memorizing the exact words of his ominous resolution so that future history books would get it right.

“I have a distant feeling that I ought to be doing something about this,” sighed McGonagall.

“Ignore it, it’ll go away. Ooh, shiny!” Harry put his thoughts of world conquest temporarily on hold and skipped over to a shop with an open display, and Professor McGonagall followed.
\sbreak
Harry had now bought his potions ingredients and cauldron, and, oh, a few more things. Items that seemed like good things to carry in Harry’s Bag of Holding (aka Moke Super Pouch \abbrev{qx31} with Undetectable Extension Charm, Retrieval Charm, and Widening Lip). Smart, sensible purchases.

Harry genuinely didn’t understand why McGonagall was looking so \emph{suspicious}.

Right now, Harry was in a shop whose storefront rated the twisting main street of Diagon Alley. The store had an open front with merchandise laid out on slanted wooden displays, guarded only by slight gray glows and a young-looking salesgirl in a much-shortened version of witch’s robes that exposed her knees and elbows.

Harry was examining the wizarding equivalent of a first-aid kit, the Emergency Healing Pack Plus. There were two self-tightening tourniquets. A Stabilization Potion, which would slow blood loss and prevent shock. A syringe of what looked like liquid fire, which was supposed to drastically slow circulation in a treated area while maintaining oxygenation of the blood for up to three minutes, if you needed to prevent a poison from spreading through the body. White cloth that could be wrapped over a part of the body to temporarily numb pain. Plus any number of other items that Harry totally failed to comprehend, like the “Dementor Exposure Treatment”, which looked and smelled like ordinary chocolate. Or the “Bafflesnaffle Counter”, which looked like a small quivering egg and carried a placard showing how to jam it up someone’s nostril.

“A definite buy at five Galleons, wouldn’t you agree?” Harry said to McGonagall, and the teenage salesgirl hovering nearby nodded eagerly.

Harry had expected McGonagall to make some sort of approving remark about his prudence and preparedness.

What he was getting instead could only be described as the Evil Eye.

“And just \emph{why},” said Professor McGonagall with rather heavy skepticism, “do you expect to \emph{need} a healer’s kit, young man?” (After the unfortunate incident at the Potions store, McGonagall was trying to avoid saying “Mr.~Potter” while anyone else was nearby.)

Harry’s mouth opened and closed. “I don’t \emph{expect} to need it! It’s just in case!”

“Just in case of \emph{what?}”

Harry’s eyes widened. “You think I’m \emph{planning} to do something dangerous and \emph{that’s} why I want a medical kit?”

The look of grim suspicion and ironic disbelief that McGonagall gave him was answer enough.

“Great Scott!” Harry said. (This was an expression he’d learned from the mad scientist Doc Brown in \emph{Back to the Future}.) “Were you also thinking that when I bought the Feather-Falling Potion, the Gillyweed, and the bottle of Food and Water Pills?”

“Yes.”

Harry shook his head in amazement. “Just what sort of plan do you think I have \emph{going}, here?”

“I don’t know,” McGonagall said darkly, “but it ends either in you delivering a ton of silver to Gringotts, or in world domination.”

“World domination is such an ugly phrase. I prefer to call it world optimization.”

This failed to reassure Professor McGonagall, who was still giving him the Look of Doom.

“Wow,” Harry said, realizing that she was serious. “You really think that. You really think I’m planning to do something dangerous.”

“Yes.”

“Like that’s the \emph{only} reason anyone would ever buy a first-aid kit? Don’t take this the wrong way, Professor McGonagall, but \emph{what sort of crazy children are you used to dealing with}?”

“Gryffindors,” spat Professor McGonagall, the word carrying a freight of bitterness and despair that fell like an eternal curse on all youthful heroism and high spirits.

“Deputy Headmistress Professor Minerva McGonagall,” Harry said, putting his hands sternly on his hips. “I am not going to be in Gryffindor—”

At this point McGonagall interjected something about how if he \emph{was} she would figure out how to kill a hat, which strange remark Harry let pass without comment, though the salesgirl seemed to be having a sudden coughing fit.

“—I am going to be in Ravenclaw. And if you really think that I’m planning to do something dangerous, then, with respect, you don’t understand me \emph{at all.} I don’t \emph{like} danger, it is \emph{scary.} I am being \emph{prudent}. I am being \emph{cautious}. I am preparing for \emph{unforeseen contingencies}. Like my parents used to sing to me: \emph{Be prepared! That’s the Boy Scout’s marching song! Be prepared! As through life you march along! Don’t be nervous, don’t be flustered, don’t be scared—be prepared!}”

(Harry’s parents had in fact only ever sung him those \emph{particular} lines of that Tom Lehrer song, and Harry was blissfully unaware of the rest.)

McGonagall’s stance had slightly softened—though mostly when Harry had reminded her that he was heading for Ravenclaw. “What sort of \emph{contingency} do you imagine this kit might prepare you for, \emph{young man?}”

“One of my classmates gets bitten by a horrible monster, and as I scrabble frantically in my mokeskin pouch for something that could help her, she looks at me sadly and with her last breath says, \emph{‘Why weren’t you prepared?’} And then she dies, and I know as her eyes close that she won’t ever forgive me—”

Harry heard the salesgirl gasp, and he looked up to see her staring at him with her lips pressed tight. Then the young woman turned and fled into the deeper store.

\emph{What...?}

Professor McGonagall reached down, and took Harry’s hand in hers, gently but very firmly, and pulled Harry out of the main street of Diagon Alley, leading him into a byway between two shops that was paved in dirty bricks and which dead-ended in a wall of solid black dirt.

The tall witch pointed her wand at the main street and spoke, “\emph{Quietus}” she said, and a screen of silence descended around them, blocking out all the street noises.

\emph{What did I do wrong...}

Then the witch turned and sent Harry with a full-powered, icy glare. “I will thank you to remember, Mr.~Potter, that there was a \emph{war} in wizarding Britain not ten years ago and that \emph{everyone} here has lost someone and that talking about friends dying in your arms \emph{is, not, done!}”

“I, I didn’t mean to—” The inference dropped like a falling stone into Harry’s exceptionally vivid imagination. The war had ended ten years ago so that girl would have been eight or nine years old, at most, when, when, “I’m sorry, I didn’t mean to...” Harry choked up, and turned away to run from McGonagall’s cold stare but there was a wall of dirt blocking his way and he didn’t have his wand yet. “I’m sorry, I’m sorry, I’m \emph{sorry!}”

There came a heavy sigh from behind him. “I know you are, Mr.~Potter.”

Harry dared to peek behind him. The anger was gone from Professor McGonagall’s face. “I’m sorry,” Harry said again, feeling absolutely wretched. “I shouldn’t have said that. Did anything like that happen to—” and then Harry shut his lips and slapped a hand over his mouth for good measure.

McGonagall’s face grew a little sadder. “You \emph{must} learn to think before you speak, Mr.~Potter. Otherwise you’ll go through life without many friends. That has been the fate of many a Ravenclaw, and I hope it will not be yours.”

Harry wanted to just run away. He wanted to pull out a wand and erase the whole thing from McGonagall’s memory, be back with her outside the shop again, \emph{make it didn’t happen—}

“But to answer your question,” said McGonagall, “no, nothing like \emph{that} has ever happened to me.” Her face twisted. “Certainly I’ve watched a friend breathe their last breath, once or twice or a few times. But not one of them ever cursed me as they died, and I never thought that they wouldn’t forgive me. \emph{What in Merlin’s name possessed you to say such a thing, Harry Potter?} Why would you even \emph{think} it?”

Tears were creeping down Harry’s cheeks. “I’m sorry, I shouldn’t have said anything to you, I’m sorry—”

McGonagall drew in a tight breath. “I \emph{know} you’re sorry. What I don’t understand is why an eleven-year-old boy is \emph{thinking} about such things. Did you really decide to buy a five-Galleon healer’s kit to carry in a fifteen-Galleon pouch because you’re convinced that otherwise your classmates will \emph{curse you as they die?}”

“I, I, I,” Harry swallowed. “It’s just that I always try to imagine the worst thing that could happen,” and maybe he’d also been joking around a little but he would rather have bitten off his own tongue than say that now.

“\emph{Why?}”

“So I can stop it from happening!”

“Mr.~Potter...” McGonagall’s voice trailed off. Then she sighed, and knelt down beside him. “Mr.~Potter,” she said, gently now, “it’s not your responsibility to take care of the students at Hogwarts. It’s mine. I won’t let anything bad happen to you or anyone else. Hogwarts is the safest place in all wizarding Britain, and Madam Pomfrey has a full healer’s office. You don’t need a healer’s kit.”

“But I \emph{do!}” Harry burst out. “\emph{Nowhere} is perfectly safe! And what if my parents have a heart attack or get in an accident when I go home for Christmas—Madam Pomfrey won’t be there, I’ll need a healer’s kit of my own—”

“\emph{What} in Merlin’s name...” said McGonagall. She stood up, and looked down at Harry an expression torn between concern and annoyance. “There’s no need to think about such terrible things, Mr.~Potter!”

Harry’s expression twisted up into bitterness, at hearing that. “Yes there \emph{is!} If you don’t think, you don’t just get hurt yourself, you end up hurting other people!”

Professor McGonagall opened her mouth, then closed it. She rubbed the bridge of her nose, looking thoughtful. “Mr.~Potter...\ if I were to offer to stay quiet and listen to you for a while...\ is there anything you’d like to talk to me about?”

“About what?”

“About why you’re convinced that you always have to be on your guard against terrible things happening to you.”

Harry stared at her in puzzlement. That was a self-evident axiom. “Well...” Harry said slowly. He tried to organize his thoughts. How \emph{could} he explain himself to McGonagall, when she didn’t even know the basics? “Muggle researchers have found that people are always very optimistic, like they say something will take two days and it takes ten, or they say it’ll take two months and it takes over thirty-five years. Like, they asked students for times by which they were 50\% sure, 75\% sure, and 99\% sure they’d complete their homework, and only 13\%, 19\%, and 45\% of the students finished by those times. And they found that the reason was that when they asked people for their best-case estimates if everything went as well as possible, and their average-case estimates if everything went as normal, they got back answers that were statistically indistinguishable. See, if you ask someone what they expect in the \emph{normal} case, they visualize what looks like the line of maximum probability at each step along the way—namely, everything going according to plan, without any mistakes or surprises. But actually, since more than half the students didn’t finish by the time they were 99\% sure they’d be done, reality usually delivers results a little worse than the ‘worst-case scenario’. It’s called the \emph{planning fallacy,} and the best way to fix it is to ask how long things took the last time you tried them. That’s called using the outside view instead of the inside view. But when you’re doing something new and can’t do that, you just have to be really, really, really pessimistic. Like, so pessimistic that reality actually comes out \emph{better} than you expected around as often and as much as it comes out worse. It’s actually \emph{really hard} to be \emph{so} pessimistic that you stand a decent chance of \emph{undershooting} real life. Like I make this big effort to be gloomy and I imagine one of my classmates getting bitten, but what actually happens is that the surviving Death Eaters attack the whole school to get at me. But on a happier note—”

“Stop,” McGonagall said.

Harry stopped. He had just been about to point out that at least they knew the Dark Lord wouldn’t attack, since he was dead.

“I think I might not have made myself clear,” McGonagall said carefully. “Did anything happen to \emph{you personally} that would scare you?”

\sloppypar “What happened to me personally is only anecdotal evidence,” Harry explained to her. “It doesn’t carry the same weight as a replicated, peer-reviewed journal article about a controlled study with random assignment, many subjects, large effect sizes and strong statistical significance.”

McGonagall pinched the bridge of her nose, inhaled, and exhaled. “I would still like to hear about it,” she said.

“Um...” Harry said. He took a deep breath. “There’d been some muggings in our neighborhood, and my mother asked me to return a pan she’d borrowed to a neighbor two blocks down, and I said I didn’t want to because I might get mugged, and she said, ‘Harry, don’t say things like that!’ Like thinking about it would \emph{make} it happen, so if I didn’t talk about it, I would be safe. I tried to explain it to her and she made me carry over the pan anyway. I was too young to know how statistically unlikely it was for a mugger to target me, but I was old enough to know that not-thinking about something doesn’t stop it from happening, so I was really scared.”

“Nothing else?” McGonagall said after a pause, when it became clear that Harry was done. “There isn’t anything \emph{else} that happened to you?”

“I know it doesn’t \emph{sound} like much,” Harry defended. “But it was just one of those critical life moments, you know? I mean, I \emph{knew} that not thinking about something doesn’t stop it from happening, I \emph{knew} that, but I could see that Mom really thought that way.” Harry stopped, struggling with the anger that was starting to rise up again when he thought about it. “She \emph{wouldn’t listen}. I tried to tell her, I \emph{begged} her not to send me out, and she \emph{laughed it off.} Everything I said, she treated like some sort of big joke...” Harry forced the black rage back down again. “That’s when I realized that everyone who was supposed to protect me was actually crazy, and that they wouldn’t listen to me no matter how much I begged them, and that I couldn’t ever rely on them to get anything right.” Sometimes good intentions weren’t enough, sometimes you had to be sane...

There was a long silence.

Harry took the time to breathe deeply and calm himself down. There was no point in getting angry. There was no point in getting angry. \emph{All} parents were like that, \emph{no} adult would give up so much status as to place themselves on level ground with a child, his genetic parents would have been no different. Sanity was a tiny spark in the night, an infinitesimally rare exception to the rule and dominion of madness, so there was no point in getting angry.

Harry didn’t like himself when he was angry.

“Thank you for sharing that, Mr.~Potter,” said McGonagall after a while. There was an abstracted look on her face (almost exactly the same look that had appeared on Harry’s own face while experimenting on the pouch, if Harry had only seen himself in a mirror to realize that). “I shall have to think about this.” She turned toward the alley mouthway, and raised her wand—

“Um,” Harry said, “can we go get the healer’s kit now?”

McGonagall paused, and looked back at him steadily. “And if I say no, it’s too expensive and you won’t need it, what happens?”

Harry’s face twisted in bitterness. “Exactly what you’re thinking, Professor McGonagall. \emph{Exactly} what you’re thinking. I conclude you’re another crazy adult I can’t talk to, and I start planning how to get my hands on a healer’s kit anyway.”

“I am your guardian on this trip,” McGonagall said with a tinge of danger. “I \emph{will not} allow you to push me around.”

“I understand,” Harry said. He kept the resentment out of his voice, and didn’t say any of the other things that came to mind. McGonagall had told him to think before he spoke. He probably wouldn’t remember that tomorrow, but he could at least remember it for five minutes.

McGonagall’s wand twitched, and the noises of Diagon Alley came back. “All right, young man,” she said. “Let’s go get that healer’s kit.”

Harry’s jaw dropped in surprise. Then he hurried after her, almost stumbling in his sudden rush.
\sbreak
The store was the same as they had left it, recognizable and unrecognizable items still laid out on the slanted wooden display, the gray glow still protecting and the salesgirl back in her old position. The salesgirl looked up as they approached, her face showing surprise.

“I’m sorry,” she said as they got closer, and Harry spoke at almost the same moment, “I apologize for—”

They broke off and looked at each other, and then the salesgirl laughed a little. “I didn’t mean to get you in trouble with Professor McGonagall,” she said. Her voice lowered conspiratorily. “I hope she wasn’t \emph{too} awful to you.”

“\emph{Della!}” said McGonagall, scandalized.

“Bag of gold,” Harry said to his pouch, and then looked back up at the salesgirl while he counted out five Galleons. “Don’t worry, I understand that she’s only awful to me because she loves me.”

He handed the Galleons to the salesgirl while McGonagall was spluttering something unimportant. “One Emergency Healing Pack Plus, please.”

It was actually sort of unnerving to see how the Widening Lip swallowed the briefcase-sized medical kit. Harry couldn’t help wondering what would happen if he tried climbing into the mokeskin pouch himself, given that only the person who put something in was supposed to be able to take it out again.

When the pouch was done...\ eating...\ his hard-won purchase, Harry swore he heard a small burping sound afterward. That \emph{had} to have been spelled in on purpose. The alternative hypothesis was too horrifying to contemplate...\ in fact Harry couldn’t even \emph{think} of any alternative hypotheses. Harry looked back up at McGonagall. “Where to next?”

McGonagall pointed toward a store that looked as if it had been made from flesh instead of bricks and covered in fur instead of paint. “Small pets are permitted at Hogwarts—you could get an owl to send letters, for example—”

“Can I pay a Knut or something and \emph{rent} an owl when I need to send mail?”

“Yes,” said McGonagall.

“Then I think emphatically \emph{no.}”

McGonagall nodded, as though ticking off a point. “Might I ask why not?”

“I had a pet rock once. It died.”

“You don’t think you could take care of a pet?”

“I \emph{could,}” Harry said, “but I would end up obsessing all day long about whether I’d remembered to feed it that day or if it was slowly starving in its cage, wondering where its master was and why there wasn’t any food.”

“That poor owl,” McGonagall said in a soft voice. “Abandoned like that. I wonder what it would do.”

“Well, it’d get really hungry and start trying to claw its way out of the cage or the box or whatever, though it probably wouldn’t have much luck with that—” Harry stopped short.

McGonagall went on, still in that soft voice. “And what would happen to it afterward?”

“Excuse me,” Harry said, and he took McGonagall by the hand, gently but firmly, and steered her into yet another byway; after ducking so many well-wishers the process had become almost unnoticeably routine. “Please cast that Quietus thingy.”

“\emph{Quietus.}”

Harry’s voice was shaking. “That owl does \emph{not} represent me, my parents \emph{never} locked me in a closet and left me to starve, I do \emph{not} have abandonment fears and I \emph{don’t like the trend of your thoughts, Professor McGonagall!}”

The witch looked down at him. “And what thoughts would those be, Mr.~Potter?”

“You think I was,” Harry was having trouble saying it, “I was \emph{abused?}”

“Were you?”

“\emph{No!}” Harry shouted. “No, I never was! Do you think I’m \emph{stupid?} I \emph{know} about the concept of child abuse, I \emph{know} about inappropriate touching and all of that and if anything like that happened I would call the police! And report it to the school principal! And look up government offices in the phone book! And tell Grandma and Grandpa and Mrs.~Figg! But my parents \emph{never} did anything like that, never ever \emph{ever!} How \emph{dare} you suggest such a thing!”

McGonagall gazed at him steadily. “It is my duty as Deputy Headmistress to investigate possible signs of abuse in the children under my care.”

Harry’s anger was spiraling out of control into pure, black fury. “Don’t you ever \emph{dare} breathe a word of these, these \emph{insinuations} to anyone else! \emph{No one}, do you hear me, McGonagall? An accusation like that can ruin people and destroy families even when the parents are completely innocent! I’ve read about it in the newspapers!” Harry’s voice was climbing to a high-pitched scream. “The \emph{system} doesn’t know how to \emph{stop}, it doesn’t believe the parents \emph{or} the children when they say nothing happened! \emph{Don’t you dare threaten my family with that! I won’t let you destroy my home!}”

“Harry,” McGonagall said softly, and she reached out a hand toward him—

Harry took a fast step back, and his hand snapped up and knocked hers away.

McGonagall froze, then she pulled her hand back, and took a step backward. “Harry, it’s all right,” she said. “I believe you.”

“\emph{Do you,}” Harry hissed. The fury still roaring through his blood. “Or are you just waiting to get away from me so you can file the papers?”

“Harry, I saw your house. I saw with your parents. They love you. You love them. I do believe you when you say that your parents are not abusing you. But I \emph{had} to ask, because there is something very strange at work here.”

Harry stared at her coldly. “Like what?”

McGonagall took a deep breath. “Harry, I’ve seen a lot of abused children in my time at Hogwarts, it would break your heart to know how many. And, when you’re happy, you don’t behave like one of those children, not at \emph{all}. You smile at strangers, you hug people, I put my hand on your shoulder and you didn’t flinch. But sometimes, only sometimes, you say or do something that seems \emph{very} much like...\ someone who spent his first eleven years locked in a basement. Not the loving family that I saw.” McGonagall tilted her head, her expression growing puzzled again.

Harry took this in, processing it. The black rage began to drain away, as it dawned on him that he was being listened to respectfully, and that his family wasn’t in danger.

“And how \emph{do} you explain your observations, Professor McGonagall?”

“I don’t know,” she said. “But it’s possible that something could have happened to you that you don’t remember.”

Fury rose up again in Harry. That sounded all too much like what he’d read in the newspaper stories of shattered families. “Suppressed memory is a load of \emph{pseudoscience!} People do \emph{not} repress traumatic memories, they remember them all \emph{too} well for the rest of their lives!”

“No, Mr.~Potter. There is a Charm called Obliviation.”

Harry froze in place. “A spell that erases memories?”

McGonagall nodded. “But not all the effects of the experience, if you see what I’m saying, Mr.~Potter.”

A chill went down Harry’s spine. \emph{That} hypothesis...\ could \emph{not} be easily refuted. “But my parents couldn’t do that!”

“No,” McGonagall said. “It would have taken someone from the wizarding world. There’s...\ no way to test for it, I’m afraid, not that I know.”

Harry’s rationalist skills began to boot up again. “Professor McGonagall, how sure are you of your observations, and what alternative explanations could there also be?”

McGonagall opened her hands, as though to show their emptiness. “Sure? I’m sure of \emph{nothing}, Mr.~Potter. If I consider your whole person, then in all my life I’ve never met anyone else like you. Sometimes you just don’t seem eleven years old or even all that \emph{human}.”

Harry’s eyebrows rose toward the sky—

“I’m sorry!” McGonagall said quickly. “I’m very sorry, Mr.~Potter. I was trying to make a rhetorical point and I’m afraid that came out sounding a bit different from what I had in mind—”

“On the contrary, Professor McGonagall,” Harry said, and slowly smiled. “I shall take it as a very great compliment. But would you mind if I offered an alternative explanation?”

“Please do.”

“Children aren’t meant to be too much smarter than their parents,” Harry said. “Or too much saner, maybe—my father could probably outsmart me if he was, you know, actually \emph{trying,} instead of using his adult intelligence mainly to come up with new reasons not to change his mind—” Harry stopped. “I’m too smart, McGonagall. Normal children simply aren’t in my league. Adults don’t respect me enough to really talk to me. And frankly, even if they did, they wouldn’t sound as smart as Richard Feynman, so I might as well read something Richard Feynman wrote instead. I’m \emph{isolated}, Professor McGonagall. I’ve been isolated my whole life. Maybe that has some of the same effects as being locked in a basement. And I’m too intelligent to look up to my parents the way that children are designed to do. My parents love me, but they don’t feel obligated to respond to reason, and sometimes I feel like they’re the children—children who \emph{won’t listen} and have absolute authority over my whole existence. I try not to be too bitter about it, but I also try to be \emph{honest} with myself, so, yes, I’m bitter. And I also have an anger management problem, but I’m working on it. That’s all.”

“\emph{That’s all?}”

Harry nodded firmly. “That’s all. Surely, Professor McGonagall, even in magical Britain, the normal explanation is always worth \emph{considering?}”
\sbreak
It was later in the day, the sun lowering in the summer sky and shoppers beginning to peter out from the streets. Some stores had already closed; Harry and McGonagall had bought his textbooks from Flourish and Blotts just under the deadline. With only a slight explosion when Harry had made a beeline for the keyword “Arithmancy” and discovered that the seventh-year textbooks invoked nothing more mathematically advanced than trigonometry.

At this moment, though, dreams of low-hanging research fruit were very far from Harry’s mind.

At this moment, Harry and McGonagall were walking out of Ollivander’s, and Harry was staring at his wand. He’d waved it, and produced blue-bronze sparks, which really shouldn’t have come as such an extra shock after everything else he’d seen, but somehow—

\emph{I can do magic.}

\emph{Me. As in, me personally. I am magical; I am a wizard.}

He had \emph{felt} the magic pouring up his arm, and in that instant, realized that he had always had that sense, that he had possessed it his whole life, the sense that was not sight or sound or smell or taste or touch but only magic. Like an eye that had always \emph{always} been closed, the corresponding brain area representing only darkness since the moment of his birth; until one day the eye opened, and saw the world.

And—

\emph{“It is very curious indeed that you should be destined for this wand when its brother why, its brother gave you that scar.”}

That could not \emph{possibly} be coincidence. There had been \emph{thousands} of wands in that shop. Well, okay, actually it \emph{could} be coincidence, there were six billion people in the world and thousand-to-one coincidences happened every day. But Bayes’s Theorem 101: any reasonable hypothesis which said it was \emph{more} likely than a thousand-to-one that he’d end up with the brother to the Dark Lord’s wand, was going to have an advantage.

McGonagall had simply said \emph{how peculiar} and left it at that, which had put Harry into a state of shock at the sheer, overwhelming \emph{obliviousness} of wizards and witches. In no \emph{imaginable} world would Harry have just went “Hm” and walked out of the shop without even \emph{trying} to come up with a hypothesis for what was going on.

His left hand rose and touched his scar.

What... \emph{exactly...}

“You’re a full wizard now,” said McGonagall. “Congratulations.”

Harry nodded.

“And what do you think of the wizarding world?”

“It’s strange,” Harry said. “I ought to be thinking about everything I’ve seen of magic...\ everything that I now know is possible, and everything I now know to be a lie, and all the work left before me to understand it. And yet I find myself distracted by relative trivialities like,” Harry lowered his voice, “the whole Boy-Who-Lived thing.” There didn’t seem to be anyone nearby, but no point tempting fate.

McGonagall \emph{ahemed}. “Really? You don’t say.”

Harry nodded. “Yes. It’s just... \emph{odd.} To find out that you were part of this grand story, the quest to defeat the great and terrible Dark Lord, and it’s already \emph{done.} Finished. Completely over with. Like you’re Frodo Baggins and you find out that your parents took you to Mount Doom and had you toss in the Ring when you were one year old and you don’t even remember it.”

McGonagall’s smile had grown somewhat fixed.

“You know, if I were anyone else, anyone else at all, I’d probably be pretty worried about living up to that start. \emph{Gosh, Harry, what have you done since you defeated the Dark Lord? Your own bookstore? That’s great! Say, did you know I named my child after you?} But I have hopes that this will not prove to be a problem.” Harry sighed. “Still...\ it’s almost enough to make me wish that there were \emph{some} loose ends from the quest, just so I could say that I really, you know, \emph{participated} somehow.”

“Oh?” said McGonagall in an odd tone. “What did you have in mind?”

“Well, for example, you mentioned that my parents were betrayed. Who betrayed them?”

“Sirius Black,” McGonagall said. She almost hissed the name. “He’s in Azkaban. Wizarding prison.”

“How probable is it that Sirius Black will break out of prison and I’ll have to track him down and defeat him in some sort of spectacular duel, or better yet put a large bounty on his head and hide out in Australia while I wait for the results?”

McGonagall blinked. Twice. “Not likely. No one has ever escaped from Azkaban, and I doubt that \emph{he} will be the first.”

Harry was a bit skeptical of that “\emph{no one} has \emph{ever} escaped from Azkaban” line. Still, maybe with magic you could actually get close to a 100\% perfect prison, especially if you had a wand and they did not. The best way to get out would be to not go there in the first place.

“All right then,” Harry said. “Sounds pretty nicely wrapped up.” He sighed, scrubbing his palm over his head. “Or maybe the Dark Lord didn’t \emph{really} die that night. Not completely. His spirit lingers, whispering to people in nightmares that bleed over into the waking world, searching for a way back into the living lands he swore to destroy, and now, in accordance with the ancient prophecy, he and I are locked in a deadly duel where the winner shall lose and the loser shall win—”

McGonagall’s head swiveled, and her eyes darted around, searching the street for listeners.

“I’m \emph{joking}, Professor McGonagall,” Harry said with some annoyance. Jeebers, why did she always take everything so seriously—

A slow sinking sensation began to dawn in the pit of Harry’s stomach.

McGonagall looked at Harry with a calm expression. A very, \emph{very} calm expression. Then a smile was put on. “Of course you are, Mr.~Potter.”

\emph{Aw crap.}

If Harry had needed to rationalize the wordless inference that had just flashed into his mind, it would have come out something like, “If I estimate the probability of McGonagall doing what I just saw as the result of carefully controlling herself, versus the probability distribution for all the things she would do \emph{naturally} if I made a bad joke, then this behavior is significant evidence for her hiding something.”

But what Harry actually thought was, \emph{Aw crap.}

Harry turned his own head to scan the street. Nope, no one nearby. “He’s \emph{not} dead, is he,” Harry sighed.

“Mr.~Potter—”

“The Dark Lord is alive. Of \emph{course} he’s alive. It was an \emph{act} of utter \emph{optimism} for me to have even \emph{dreamed} otherwise. I \emph{must} have taken leave of my \emph{senses}, I can’t \emph{imagine} what I was \emph{thinking.} Just because \emph{someone} said that his body was found burned to a \emph{crisp}, I can’t imagine why I would have thought he was \emph{dead.} \emph{Clearly} I have \emph{much} left to learn about the art of proper \emph{pessimism.}”

“Mr.~Potter—”

“At least tell me there’s not really a prophecy...” But McGonagall was still giving him that bright, fixed smile. “Oh, you have \emph{got} to be kidding me.”

“Mr.~Potter, you shouldn’t go inventing things to worry about—”

“Are you \emph{actually} going to tell me \emph{that?} Imagine my reaction later, when I find out that there was something to worry about after all.”

McGonagall’s smile faltered.

Harry’s shoulders slumped. “I have a whole world of magic to analyze. I do \emph{not} have time for this.”

Then both of them shut up, as a man in flowing orange robes appeared on the street and slowly passed them by. McGonagall’s eyes tracked him, unobtrusively. Harry’s mouth was moving as he chewed hard on his lip, and someone watching closely would have noticed a tiny spot of blood appear.

When the orange-robed man had passed into the distance, Harry spoke again, in a low murmur. “Are you going to tell me the truth now, Professor McGonagall? And don’t bother trying to wave it off, I’m not stupid.”

“You’re \emph{eleven years old}, Mr.~Potter!” she said in a harsh whisper.

“And therefore subhuman. Sorry...\ for a moment there, I \emph{forgot}.”

“These are dreadful and important matters! They are \emph{secret,} Mr.~Potter! It is a \emph{catastrophe} that you, still a child, know even this much! You must not tell \emph{anyone,} do you understand? Absolutely no one!”

As sometimes happened when Harry got \emph{sufficiently} angry, his blood went cold, instead of hot, and a terrible dark clarity descended over his mind, mapping out possible tactics and assessing their consequences with iron realism.

\emph{Point out that you have a right to know: Failure. Eleven-year-old children do not have rights to know anything, in McGonagall’s eyes.}

\emph{Say that you will not be friends any more: Failure. She does not value your friendship sufficiently.}

\emph{Point out that you will be in danger if you do not know: Failure. Plans have already been made based on your ignorance. The} certain \emph{inconvenience of rethinking will seem far more unpalatable than the mere} uncertain \emph{prospect of your coming to harm.}

\emph{Justice and reason will both fail. You must either find something you have that she wants, or find something you can do which she fears...}

Ah.

“Well then, Professor McGonagall,” Harry said in a low, icy tone, “it sounds like I have something you want. You can, if you like, tell me the truth, the \emph{whole} truth, and in return I will keep your secrets. Or you can try to keep me ignorant so you can use me as a pawn, in which case I will owe you nothing.”

McGonagall stopped short in the street. Her eyes blazed and her voice descended into an outright hiss. “How dare you!”

“\emph{How dare you!}” he whispered back at her.

“You would \emph{blackmail} me?”

Harry’s lips twisted. “I am \emph{offering} you a \emph{favor.} I am \emph{giving} you a chance to keep \emph{your} precious secret. If you refuse I will have \emph{every} natural motive to make inquiries elsewhere, not to spite you, but because I \emph{have to know!} Get past your pointless anger at a \emph{child} who you think ought to obey you, and you’ll realize that any sane adult would do the same! \emph{Look at it from my perspective! How would you feel if it was \scream{you}?}”

Harry watched McGonagall, observed her harsh breathing. It occurred to him that it was time to ease off the pressure, let her simmer for a while. “You don’t have to decide right away,” Harry said in a more normal tone. “I’ll understand if you want time to think about my \emph{offer}...\ but I’ll warn you of one thing,” Harry said, his voice going colder. “Don’t try that Obliviation Charm on me. Some time ago I worked out a signal, and I have already sent that signal to myself. If I find that signal and I don’t \emph{remember} sending it...” Harry let his voice trail off significantly.

McGonagall’s face was working as her expressions shifted. “I...\ wasn’t thinking of Obliviating you, Mr.~Potter...\ but why would you have \emph{invented} such a signal if you didn’t know about—”

“I thought of it while reading a Muggle science-fiction book, and said to myself, \emph{well, just in case...} And no, I won’t tell you the signal, I’m not dumb.”

“I hadn’t planned to ask,” McGonagall said. She seemed to fold in on herself, and suddenly looked very old, and very tired. “This has been an exhausting day, Mr.~Potter. Can we get your trunk, and send you home? I will trust you not to speak upon this matter until I have had time to think. Keep in mind that there are only two other people in the whole world who know about this matter, and they are Headmaster Albus Dumbledore and Professor Severus Snape.”

So. New information; that was a peace offering. Harry nodded in acceptance, and turned his head to look forward, and started walking again.

“So now I’ve got to find some way to kill an immortal Dark Wizard,” Harry said, and sighed in frustration. “I really wish you had told me that \emph{before} I started shopping.”
\sbreak
The trunk shop was more richly appointed than any other shop Harry had visited; the curtains were lush and delicately patterned, the floor and walls of stained and polished wood, and the trunks occupied places of honor on polished ivory platforms. The salesman was dressed in robes of finery only a cut below those of Lucius Malfoy, and spoke with exquisite, oily politeness to both Harry and McGonagall.

Harry had asked his questions, and had gravitated to a trunk of heavy-looking wood, not polished but warm and solid, carved with the pattern of a guardian dragon whose eyes shifted to look at anyone nearing it. A trunk charmed to be light, to shrink on command, to sprout small clawed tentacles from its bottom and squirm after its owner. A trunk with two drawers on each of four sides that each slid out to reveal compartments as deep as the whole trunk. A lid with four locks each of which would reveal a different space inside. And—this was the important part—a handle on the bottom which slid out a frame containing a staircase leading down into a small, lighted room that would hold, Harry estimated, around twelve bookcases.

If they made luggages like this, Harry didn’t know why anyone bothered owning a house.

One hundred and eight golden Galleons. That was the price of a \emph{good} trunk, lightly used. At around fifty British pounds to the Galleon, that was enough to buy a used car. It would be more expensive than everything else Harry had ever bought in his whole life all put together.

Ninety-seven Galleons. That was how much was left in the bag of gold Harry had been allowed to take out of Gringotts.

McGonagall wore a look of chagrin upon her face. After a long day’s shopping she hadn’t needed to ask Harry how much gold was left in the bag after the salesman quoted his price, which meant the Professor could do good mental arithmetic without pen and paper. Once again, Harry reminded himself that \emph{scientifically illiterate} was not at all the same thing as \emph{stupid.}

“I’m sorry, young man,” McGonagall said. “This is entirely my fault. I would offer to take you back to Gringotts, but the bank will be closed for all but emergency services now.”

Harry took a deep breath. He needed to be a little angry for what he wanted to try now, there was no way he’d have the courage to do it otherwise. \emph{She didn’t listen to me,} he thought to himself, \emph{I would have taken more gold but she didn’t want to listen...} He thought back to that black rage of before, tried to call up a little of it. Visualized \emph{the person he needed to be,} and drew that personality over himself like a wizard’s robes. Focusing his entire world on McGonagall and the need to bend this conversation to his will, he spoke.

“Let me guess,” Harry said. “You thought you were leaving yourself \emph{plenty} of error margin, that one hundred Galleons would be \emph{more} than enough, and that’s why you didn’t bother warning me when it was down to ninety-seven.”

McGonagall closed her eyes in resignation. “Yes.”

“I anticpated this, Professor McGonagall. I expected this to happen. There are research studies showing that this is what happens when people think they’re \emph{leaving themselves plenty of error margin.} If it were \emph{me}, I’d have taken \emph{two hundred} Galleons just to be sure; there was plenty of money in that vault, and I could have put back any extra later. But I \emph{knew} that you wouldn’t let me do it. I knew there wasn’t even any point in asking. I knew you would be annoyed and maybe even \emph{angry} if I asked. Am I wrong?”

“No,” McGonagall said, “you’re right.” Her voice held a note of apology, and yet still a note of self-pride alongside that, as though Harry ought to notice how very, very honored he was to have \emph{Professor McGonagall} apologizing to him.

“You should understand, Professor McGonagall,” Harry spoke the words very carefully, “this is why I don’t trust adults. You thought that being adult meant it was your role to prevent me from taking too much money out of my vault. Not that it was your role to \emph{make sure the job got done no matter what.}”

McGonagall’s eyes flew open, and she gave Harry a hard look.

“Well, Professor McGonagall, if you had to do it all over again, and I suggested taking out an extra hundred Galleons \emph{just to be sure}, with no justification other than to be \emph{prepared,} would you listen to me \emph{that} time?”

“I take your point,” McGonagall said. “You don’t need to lecture \emph{me}, young man!”

“Ah, but I haven’t \emph{gotten} to my point. Do you know the difference between someone worth talking to and a mere obstacle, Professor McGonagall? From my perspective, that is? If an adult thinks that being superior to me, above me, getting obedience from me, is the \emph{most important} thing to them, then they will be an obstacle. A \emph{potential collaborator} is someone who thinks that \emph{getting the job done} is more important than making sure I know my place. Allow me to show you something, Professor McGonagall.”

The trunk salesman was watching them with undisguised fascination, as Harry took out the mokeskin pouch, and said, “Eleven loose Galleons, please.”

And there was gold in Harry’s hand.

“\emph{Where did you get that—}”

“From my vault, Professor McGonagall, when I fell into that pile of gold. I shoved some money into my pocket and then held the bag of gold against it, so jingles would seem to come from the right place. Since, you understand, I expected from the beginning that this would happen.”

McGonagall’s mouth was wide, wide open.

“So now the question is...\ are you angry at me for defying your authority? Or glad that now our day ends in success instead of failure? I’m not asking for anything \emph{else} from you by asking this question. I am neither promising nor demanding cooperation on future matters. I only want to know if you’re a \emph{potential} collaborator or an obstacle... Minerva.”

The salesman actually gasped out loud.

And the tall witch stood there, silent.

“Discipline at Hogwarts \emph{must} be enforced,” she said after almost a full minute. “For the sake of \emph{all} the students. And that \emph{must} include courtesy and obedience from you to \emph{all} professors.”

Harry inclined his head. “I understand. Professor McGonagall.” Though it was amazing how, somehow, it seemed \emph{so} much \emph{more} important to enforce discipline when \emph{you} were on \emph{top} of the heap, and not underneath...\ but Harry didn’t think it wise to press the point further.

“Then... I congratulate you on your preparedness.”

Harry wanted to cheer, or throw up, or faint, or something. That was the first time that speech had ever worked on an adult. That was the first time \emph{any} of his speeches had ever worked on \emph{anyone}. Maybe because it was also the first time he had something really serious that an adult needed from him, but still—

Minerva McGonagall, +1 point.

Harry bowed, and gave the bag of gold and the extra eleven Galleons into McGonagall’s hands. “I leave it to you, madam. For myself, I must use the restroom. May I ask where—”

The salesman, unctuous once more, pointed toward a door set into the wall with a gold-handled knob. As Harry started to walk away, he heard from behind the salesman ask in his oily voice, “May I inquire as to who that was, Madam McGonagall? I take it he is Slytherin—third-year, perhaps?—and from a prominent family, but I did not recognize—”

The slam of the bathroom door cut off his words, and after Harry had identified the lock and pressed it into place, he collapsed against the door. Harry’s entire body was sheathed in sweat that had soaked clear through his Muggle clothing, though at least it didn’t show through the robes. He bent down over the gold-etched ivory toilet, and retched a few times, but thankfully nothing came up.
\sbreak
And they stood again in the courtyard of the Leaky Cauldron, the small, leaf-dusted, deserted interface between magical Britain’s Diagon Alley and the entire Muggle world. That was one \emph{awfully} decoupled economy... Harry was to go to a payphone and call his father once he was on the other side. He did not, apparently, need to worry about his luggage being stolen from him; it had the status of a major wizarding item, something that most Muggles wouldn’t notice. That was part of what you could get in the wizarding world, if you were willing to pay the price of a used car. Harry wondered if his father would be able to see the trunk after it was pointed out to him.

“So here we part ways, for a time,” Professor McGonagall said. She shook her head in wonderment. “This has been the strangest day of my life for...\ many a year. Since the day I learned that a child had defeated You-Know-Who. I wonder now, in retrospect, if that was the last sane day of the world.”

Oh, like \emph{she} had anything to complain about. \emph{You think your day was surreal? Try mine.}

“I was very impressed with you today,” Harry said to her. “I should have remembered to compliment you out loud, I was awarding you points in my head and everything.”

“Thank you, Mr.~Potter,” McGonagall said. “If you had already been Sorted into a House I would have deducted so many points that their grandchildren would still be losing the House Cup.”

“Thank \emph{you}, Minerva.” It was probably too early to call her Minny.

\looseness+1 This woman might well be the sanest adult Harry had ever met, despite her lack of scientific background. Harry was even considering offering her the number-two position in whatever group he formed to fight the Dark Lord, though he wasn’t silly enough to say that out loud. \emph{Now what would be a good name for that...? The Death Eater Eaters?}

“I’ll see you again very soon, when school starts,” McGonagall said. “And, Mr.~Potter, about your wand—”

“I know what you’re going to ask,” Harry said. He took out his precious wand and, with a deep twinge of inner pain, flipped it over in his hand. Handle out, he presented it to McGonagall. “Take it. I hadn’t planned to do anything, not a single thing, but I don’t want you to have nightmares about me blowing up my house.”

McGonagall shook her head rapidly. “Oh no, Mr.~Potter! That isn’t done. I was just going to warn you not to \emph{use} your wand at home, since there are ways of detecting underage magic and it is prohibited without supervision.”

“Ah,” Harry said, and smiled. “\emph{That} sounds like a \emph{very} sensible rule. I’m glad to see the wizarding world takes that sort of thing seriously.”

McGonagall peered hard at him. “You really mean that.”

“Yes,” Harry said. “I get it. Magic is dangerous and the rules are there for good reasons. Certain other matters are also dangerous. I get that too. Remember that I am not stupid.”

“I am unlikely ever to forget it. Thank you, Harry, that does make me feel better about entrusting you with certain things. Goodbye for now.”

Harry turned to go, into the Leaky Cauldron and out toward the Muggle world.

As his hand touched the back door’s handle, he heard a last whisper from behind him.

“Hermione Granger.”

“What?” Harry said, his hand still on the door.

“Look for a first-year girl named Hermione Granger on the train to Hogwarts.”

“Who is she?”

There was no answer, and when Harry turned around, McGonagall was gone.
\replacement{\sbreak}{}

\subsection{Aftermath:}

Headmaster Dumbledore leaned forward over his desk. His twinkling eyes peered out at McGonagall. “So, Minerva, how did you find Harry?”

McGonagall opened her mouth. Then she closed her mouth. Then she opened her mouth again. No words came out.

“I see,” Dumbledore said gravely. “Thank you for your report, Minerva. You may go.”


