\chapter{Something to Protect: Professor Quirrell}

\lettrine{T}{he} Sun shone down on the Scottish green, striking sparks of reflected white from every passing dewdrop or reflective leaf that happened to position itself correctly, a clear blue sky for a funeral.

Harry had declined to give the eulogy. He’d declined for the second time. Professor Flitwick had asked him about it weeks ago in May, to give Harry time to write his lines before it would become necessary to speak; and Harry had said no then, too.

So it fell to a sixth-year Gryffindor, Oliver Habryka, who had the fourth-highest total of Quirrell points among all the students, and who had been General of an army. The seventeen-year-old boy was tall and not especially handsome in solid black robes; instead of a red tie, he was wearing a purple tie such as Professor Quirrell had sometimes favoured.

Speaking, under the circumstances, extempore. The previous eulogies, written well in advance, had been discarded; Oliver Habryka had a parchment in his left hand, but he wasn’t looking at it at all.

“Professor Quirrell was very sick,” the tall boy said, his wavering voice falling into a hush of students, occasionally broken by a muffled sob. “I think if Professor Quirrell had been able to fight in the fullness of his power, You-Know-Who couldn’t have beat him easily, and maybe not at all. They say that David Monroe was the only one that You-Know-Who was ever afraid of, in his day. But,” Oliver’s voice broke, “Professor Quirrell wasn’t in the fullness of his power. He was very sick. He had trouble walking by himself. And he went to face the Dark Lord, alone.”

There was a pause, then, while the students cried for a while.

Oliver wiped away his tears with his sleeve, and spoke again. “We don’t know exactly what happened,” said Oliver. “I imagine the Dark Lord laughed at him. Maybe made fun of the Professor, for challenging him when he couldn’t stand up. Well, \emph{he’s not laughing now,} is he.”

There were fierce nods from the students; all of them that Harry could see, from Gryffindor to Slytherin.

“Maybe the Dark Lord knew some way of curing Professor Quirrell, You-Know-Who did come back from the dead after all. Maybe he offered Professor Quirrell his life if Professor Quirrell would serve him. Professor Quirrell smiled, and told the Dark Lord it was time for them to play a game called Who’s The Most Dangerous Wizard In The World.”

\emph{If you don’t know, don’t just make stuff up.} But Harry didn’t say anything. It was what Lord Voldemort might have tried, it was what Professor Quirrell might have said back.

“And they aren’t telling us everything,” Oliver said, “but we can guess what happened next. We all know that Hermione Granger, who was one of the Professor’s best students, was killed by a troll earlier this year, it must have been the Dark Lord who made it happen, just like he framed her for the Blood-Cooling Charm. Professor Quirrell knew the Dark Lord was behind it, so he stole Miss~Granger’s body and preserved it, kept it safe—”

Couldn’t blame him for that one.

“Then Professor Quirrell went out to face the Dark Lord. The Dark Lord killed Professor Quirrell. And Hermione Granger came back to life. They say she’s alive and whole now, and maybe something more. When the Dark Lord tried to seize her, all that was left of him afterwards was his burned robes and his hands around Miss~Granger’s throat. Just as Harry Potter was protected from the Killing Curse by his mother’s love and sacrifice, Professor Quirrell willingly going out, to face, the Dark Lord alone, must have called, Hermione Granger’s spirit, back from, from wherever, she was—” Oliver’s voice was breaking.

“Not just like that,” Harry said from the front row of seats, his own voice hoarse. He \emph{had} to say something at this point, before it got out of control. If it wasn’t already out of control. “David Monroe was a powerful wizard, more powerful than anyone knew except him and me. I don’t think you can bring someone back from the dead just by sacrificing yourself. No one should try doing it that way.”

Such a beautiful story. It should have been true. \emph{It should have been true.}

“I don’t know very much about the person behind the Professor,” Oliver Habryka said, after he got himself under control again. “I know David Monroe wasn’t a happy man. He never could cast a Patronus Charm.”

Tears were gathering in Harry’s eyes again. It wasn’t right, it wasn’t fair, Voldemort had killed so many people, he should have died along with his followers, he didn’t deserve special treatment. But it hadn’t just been Harry’s weakness, it had been the horcruxes, Voldemort \emph{couldn’t} have been killed outright. So Harry could admit it, he was glad, he was \emph{glad} Professor Quirrell wasn’t all gone…

“But I, know,” said Oliver, tears glistening on his own cheeks, “Professor Quirrell, is happy, wherever, he is now.”

On Harry’s left hand, a tiny emerald glowed bright beneath the morning sun.

\emph{Not Heaven, not some faraway star, not a different place but a better person, I’ll show you, some day I’ll show you how to be happy—}

The tall boy glanced down at a parchment he held in his other hand, the first time he’d consulted it. “Professor Quirrell,” Oliver said, his voice now fiercer and faster, “was, by far, the best Professor of Battle Magic that Hogwarts ever had. Salazar Slytherin couldn’t have been half as good a teacher, no matter what spells he knew. Professor Quirrell told us at the beginning of this year that what he taught us would always be our firm foundation in the arts of Defence. And it will be. Forever. We’ll teach it to the new students next year, no matter who we have for a professor. The older students will teach the younger ones. That’s the solution to the curse on the Defence position. We won’t sit around waiting for authority to teach us. And we’ll make sure that Professor Quirrell’s teachings never die out of Hogwarts.”

Harry looked at where Professor—no, Headmistress McGonagall—was sitting, and saw the Headmistress nodding silently, a look that was sad and stern and proud.

“They haven’t let us see Miss~Granger yet,” Oliver said. His voice quavered. “The Girl-Who-Revived. But I’ll always think of the Defence Professor when I see her. His sacrifice lives on in her, just as his teachings live on in us.” Oliver glanced at where Harry sat, then looked down again at the parchment. “Here’s to Professor Quirrell, then, the best Slytherin that ever was, what every Slytherin should be! Three cheers for him!”

“\emph{Huzzah! Huzzah! Huzzah!}”

No one stayed silent this time, not a single student that Harry could see.

%  LocalWords:  Habryka
