\chapter{Courage}
\lettrinemph{“R}{omantic?”} Hermione said. “They’re both \emph{boys!}”

\hspace*{3em}“Wow,” Daphne said, sounding a little shocked. “You mean Muggles really \emph{do} hate that? I thought that was just something the Death Eaters made up.”

“No,” said an older Slytherin girl Hermione didn’t recognize, “it’s true, they have to get married in secret, and if they’re ever discovered, they get burned at the stake together. And if you’re a girl who thinks it’s romantic, they burn you too.”

“That can’t be right!” objected a Gryffindor girl, while Hermione was still trying to sort out what to say to that. “There wouldn’t be any Muggle girls \emph{left!}”

She’d kept on reading quietly, and Harry Potter had kept on trying to apologize, and it had soon dawned on Hermione that Harry had realized, possibly for the first time in his life, that he’d done something annoying; and that Harry, definitely for the first time in his life, was \emph{terrified} that he’d lost her as a friend; and she’d started to feel (a) guilty and (b) worried about the direction Harry’s increasingly desperate offers were going. But she still had no idea what sort of apology was appropriate, so she’d said that the Ravenclaw girls should vote on it—and this time she wouldn’t fix the outcome, though she hadn’t mentioned that part—to which Harry had instantly agreed.

The next day, practically every Ravenclaw girl over the age of thirteen had voted to have Draco drop Harry.

Hermione had felt mildly disappointed it was that simple, though it was obviously fair.

Right now, however, standing just outside the great doors of the castle amid half the female population of Hogwarts, Hermione was beginning to suspect that there were \emph{things} going on here that she did not understand and that she desperately hoped neither of her fellow generals ever heard about.
\sbreak
You couldn’t really see the details from up there, just the general fact of a sea of expectant female faces.

“You’ve got no idea what this is about, do you?” said Draco, sounding amused.

Harry had read a fair number of books he wasn’t supposed to read, not to mention a few \emph{Quibbler} headlines.

“Boy-Who-Lived gets Draco Malfoy pregnant?” said Harry.

“Okay, you \emph{do} know what this is about,” said Draco. “I thought Muggles hated that?”

“Only the dumb ones,” said Harry. “But, um, aren’t we, uh, a little \emph{young?}”

“Not too young for \emph{them,}” said Draco. He snorted. “\emph{Girls!}”

They silently walked toward the edge of the roof.

“So \emph{I’m} doing this for revenge on you,” said Draco, “but why are \emph{you} doing this?”

Harry’s mind made a lightning calculation, weighing the factors, whether it was too soon...

“Honestly?” said Harry. “Because I meant to have her climb up the icy walls, but I \emph{didn’t} mean to have her fall off the roof. And, um, I kinda \emph{did} feel really awful about that. I mean, I guess I actually did start seeing her as my friendly rival after a while. So this is a real apology to her, not a plot or anything.”

There was a pause.

Then—

“Yeah,” said Draco. “I understand.”

Harry didn’t smile. It might have been the most difficult nonsmile of his life.

Draco looked at the edge of the roof, and made a face. “This is going to be a lot harder to do on purpose than by accident, isn’t it.”
\sbreak
Harry’s other hand held the roof in a reflexively terrified grip, his fingers white on the cold, cold stone.

You could know with your conscious mind that you’d drunk the Feather-Falling Potion. Knowing it with your unconscious mind was another matter entirely.

It was every bit as scary as Harry had thought it might have been for Hermione, which was justice.

“Draco,” said Harry, controlling his voice wasn’t easy, but the Ravenclaw girls had given them a script, “You’ve got to let me go!”

“Okay!” said Draco, and let go of Harry’s arm.

Harry’s other hand scrabbled at the edge, and then, without any decision being made, his fingers failed, and Harry fell.

There was a brief moment when Harry’s stomach tried to leap up into his throat, and his body tried desperately to orient itself in the absence of any possible way to do so.

There was a brief moment when Harry could feel the Feather-Falling Potion kicking in, starting to slow him, a sort of lurching, cushioning feeling.

And then something \emph{pulled} on Harry and he accelerated downward again \emph{faster than gravity—}

Harry’s mouth had already opened and begun screaming while part of his brain tried to think of something creative he could do, part of his brain tried to calculate how much time he had left to be creative, and a tiny rump part of his brain noticed that he wasn’t even going to finish the remaining-time calculation before he hit the ground—
\sbreak
Harry was desperately trying to control his hyperventilating, and it wasn’t helping him to hear the shrieking of all the girls, now lying in heaps on the ground and each other.

“Good heavens,” said the unfamiliar man, he of the old-looking clothes and faintly scarred face, who was holding Harry in his arms. “Of all the ways I imagined we might meet again someday, I didn’t expect it to be you falling out of the sky.”

Harry remembered the last thing he’d seen, the falling body, and managed to gasp, “Professor... Quirrell...”

“He’ll be all right after a few hours,” said the unfamiliar man holding Harry. “He’s just exhausted. I wouldn’t have thought it possible...\ he must have knocked down \emph{two hundred students} just to make sure he got whoever was jinxing you...”

Gently, the man set Harry upright on the ground, supporting him the while.

Harry carefully balanced himself, and nodded to the man.

He let go, and Harry promptly fell over.

The man helped him rise again. Making sure, at all times, to stand between Harry and the girls now picking themselves up from the ground, his head constantly glancing in that direction.

“Harry,” the man said quietly, and very seriously, “do you have any idea which of these girls might have wanted to kill you?”

“Not murder,” said a strained voice. “Just stupidity.”

This time it was the unfamiliar man who seemed to almost fall over, utter shock on his face.

Professor Quirrell was already sitting up from where he’d fallen on the grass.

“Good heavens!” gasped the man. “You shouldn’t be—”

“Mr.~Lupin, your concerns are misplaced. No wizard, no matter how powerful, casts such a Charm by strength alone. You must do it by being \emph{efficient.}”

Professor Quirrell didn’t stand up, though.

“Thank you,” Harry whispered. And then, “Thank you,” to the man standing beside him as well.

“What happened?” said the man.

“I should have foreseen it myself,” Professor Quirrell said, his voice crisp with disapproval. “Some number of girls tried to summon Mr.~Potter to their own, particular arms. Individually, I suppose, they all thought they were being gentle.”

Oh.

“Consider it a lesson in preparedness, Mr.~Potter,” said Professor Quirrell. “Had I not \emph{insisted} that there be more than one adult witness to this little event, and that \emph{both} of us have our wands out, Mr.~Lupin would not have been available to slow your fall afterward, and you would have been gravely injured.”

“\emph{Sir!}” said the man—Mr.~Lupin, apparently. “You should not say such things to the boy!”

“Who is—” Harry started to say.

“The only other person who was available to watch, besides myself,” said Professor Quirrell. “I introduce you to Remus Lupin, who is here temporarily to instruct students in the Patronus Charm. Though I am told that the two of you have already met.”

Harry studied the man, puzzled. He should have remembered that faintly scarred face, that strange, gentle smile.

“Where did we meet?” said Harry.

“In Godric’s Hollow,” said the man. “I changed a number of your diapers.”
\sbreak
Mr.~Lupin’s temporary office was a small stone room with a small wooden desk, and Harry couldn’t see anything of what Mr.~Lupin was sitting on, suggesting that it was a small stool just like the one in front of his desk. Harry guessed that Mr.~Lupin wouldn’t be at Hogwarts for long, or use this office much, and so he’d told the house elves not to waste the effort. It said something about a person that he tried not to bother house elves. Specifically, it said that he’d been Sorted into Hufflepuff, since, to the best of Harry’s knowledge, Hermione was the only non-Hufflepuff who worried about bothering house elves. (Harry himself thought her qualms rather silly. Whoever had created house elves in the first place had been unspeakably evil, obviously; but that didn’t mean Hermione was doing the right thing \emph{now} by denying sentient beings the drudgery they had been shaped to enjoy.)

“Please sit down, Harry,” the man said quietly. His formal robes were of low quality, not quite tattered, but visibly worn by the passage of time in a way that simple Repair Charms couldn’t fix; \emph{shabby} was the word that came to mind. And despite that, somehow, there was a dignity about him that couldn’t have been obtained by fine and expensive robes, that wouldn’t have \emph{fit} with fine robes, that was the exclusive property of the shabby. Harry had \emph{heard} of humility, but he’d never seen the real thing before—only the satisfied modesty of people who thought it was part of their style and wanted you to notice.

Harry took a seat on the small wooden stool in front of Mr.~Lupin’s short desk.

“Thank you for coming,” the man said.

“No, thank \emph{you} for saving me,” said Harry. “Let me know if you ever need something impossible done.”

The man seemed to hesitate. “Harry, may I...\ ask a personal question?”

“You can ask, certainly,” Harry said. “I have a lot of questions for you, too.”

Mr.~Lupin nodded. “Harry, are your stepparents treating you well?”

“My \emph{parents},” Harry said. “I have four. Michael, James, Petunia, and Lily.”

“Ah,” said Mr.~Lupin. And then, “Ah” again. He seemed to be blinking rather hard. “I...\ that is good to hear, Harry, Dumbledore would tell none of us where you were... I was afraid he might think you ought to have wicked stepparents, or some such... “

Harry wasn’t sure Mr.~Lupin’s concern had been misplaced, considering his own first encounter with Dumbledore; but it had all turned out well enough, so he said nothing. “What about my...” Harry searched for a word that didn’t raise them higher or put them lower... “\emph{other} parents? I want to know, well, everything.”

“A tall order,” Mr.~Lupin said. He wiped a hand across his forehead. “Well, let us begin at the beginning. When you were born, James was so happy that he couldn’t touch his wand without it glowing gold, for a whole week. And even after that, whenever he held you, or saw Lily holding you, or just thought of you, it would happen again. James was an Auror, and it was hard for him to look properly imposing with his wand shining like that—”

“A tall order,” Mr.~Lupin said. He wiped a hand across his forehead. “Well, let us begin at the beginning. When you were born, James was so happy that he couldn’t touch his wand without it glowing gold, for a whole week. And even after that, whenever he held you, or saw Lily holding you, or just thought of you, it would happen again—”
\sbreak
Every now and then Harry would look at his watch, and find that another thirty minutes had passed. He felt slightly bad about making Remus miss dinner, especially since Harry himself would just drop back to 7\PM later, but that wasn’t enough to stop either of them.

Finally Harry screwed up enough courage to ask the critical question, while Remus was in the middle of an extended discourse on the wonders of James’s Quidditch that Harry couldn’t find the heart to squash more directly.

“And that was when,” Remus said, his eyes shining brightly, “James pulled off a \emph{triple reverse Mulhanney Dive} with \emph{extra backspin!} The whole crowd went wild, even some of the Hufflepuffs were cheering—”

\emph{I guess you had to be there,} Harry thought—not that being there would have helped in any way—and said, “Mr.~Lupin?”

Something about Harry’s voice must have reached the man, because he stopped in mid-sentence.

“Was my father a bully?” said Harry.

Remus looked at Harry for a long moment. “For a little while,” Remus said. “He grew out of it soon enough. Where did you hear that?”

Harry didn’t answer, he was trying to think of something true to say that would deflect suspicion, but he didn’t think fast enough.

“Never mind,” said Remus, and sighed. “I can guess who.” The faintly scarred face was pinched in disapproval. “What a thing to tell—”

“Did my father have any extenuating circumstances?” Harry said. “Poor home life, or something like that? Or was he just...\ being naturally nasty?” \emph{Cold?}

Remus’s hand swept his hair back, the first nervous gesture Harry had seen from him. “Harry,” Remus said, “you can’t judge your father by what he did as a young boy!”

“\emph{I’m} a young boy,” Harry said, “and I judge \emph{myself.}”

Remus blinked twice at that.

“I want to know \emph{why},” Harry said. “I want to \emph{understand}, because to me, it seems like there isn’t any possible excuse for that!” Voice shaking a bit. “Please tell me anything you know about why he did it, even if it doesn’t sound nice.” \emph{So I don’t fall into the same trap myself, whatever it is.}

“It was the thing to do if you were in Gryffindor,” Remus said, slowly, reluctantly. “And... I didn’t think so back then, I thought it was the other way around, but...\ it might have been \emph{Black} who got \emph{James} into it, really... Black wanted so much to show everyone that he was against Slytherin, you see, we all wanted to believe that blood wasn’t destiny—”
\sbreak
“No, Harry,” said Remus. “I don’t know why Black went after Peter instead of running. It was as though Black was making tragedy for the sake of tragedy that day.” The man’s voice was unsteady. “There was no hint, no warning, we all thought—to think that he was to be—” Remus’s voice cut off.

Harry was crying, he couldn’t help it, it hurt worse to hear it from Remus than anything he’d ever felt himself. Harry had lost two parents he didn’t remember, knew only from stories. Remus Lupin had lost all four of his best friends in less than twenty-four hours; and for the loss of his last remaining one, Peter Pettigrew, there’d just been no reason at all.

“Sometimes it still hurts to think of him in Azkaban,” Remus finished, his voice almost a whisper. “I am glad, Harry, that Death Eaters are not allowed visitors. It means I do not have to feel ashamed of not going.”

Harry had to swallow hard several times before he could speak. “Can you tell me about Peter Pettigrew? He was my father’s friend, and it seems—that I should know, that I should remember—”

Remus nodded, water glittering in his own eyes now. “I think, Harry, that if Peter had known it would end that way—” the man’s voice choked up. “Peter was more afraid of the Dark Lord than any of us, and if he’d known it would end that way, I don’t think he would have done it. But Peter knew the \emph{risk}, Harry, he knew the risk was real, that it \emph{could} happen, and yet he stayed by James and Lily’s side. All through Hogwarts I used to wonder why Peter hadn’t been sorted into Slytherin, or maybe Ravenclaw, because Peter so adored secrets, he couldn’t resist them, he would find out things about people, things they wanted kept hidden—” A brief wry look crossed Remus’s face. “But he didn’t \emph{use} those secrets, Harry. He just wanted to know. And then the Dark Lord’s shadow fell over everything, and Peter stood by James and Lily and put his talents to good use, and I understood why the Hat had sent him to Gryffindor.” Remus’s voice was fierce now, and proud. “It’s \emph{easy} to stand by your friends if you’re a hero like Godric, bold and strong like people think Gryffindors should be. But if Peter was more afraid than any of us, doesn’t that also make him the most brave?”

“It does,” Harry said. His own voice was choked to where he almost couldn’t talk. “If you could, Mr.~Lupin, if you have time, there’s someone else who I think should hear Peter Pettigrew’s story, a student in first-year Hufflepuff, named Neville Longbottom.”

“Alice and Frank’s boy,” said Remus, his voice turning sad. “I see. It is not a happy story, Harry, but I can tell it again, if you think it will help him.”

Harry nodded.

A brief silence fell.

“Did Black have \emph{any} unfinished business with Peter Pettigrew?” Harry said. “\emph{Anything} that would make him seek out Mr.~Pettigrew, even if it wasn’t a killing matter? Like a secret Mr.~Pettigrew knew, that Black wanted to know himself, or wanted to kill him to hide?”

Something flickered in Remus’s eyes, but the older man shook his head, and said, “Not really.”

“That means there \emph{is} something,” said Harry.

That wry smile appeared again beneath the salt-and-pepper mustache. “You have a bit of Peter in you yourself, I see. But it’s not important, Harry.”

“I’m a Ravenclaw, I’m not \emph{supposed} to resist the temptation of secrets. And,” Harry said more seriously, “if it was worth Black getting caught, I can’t help but think it might matter.”

Remus looked quite uncomfortable. “I suppose I could tell you when you’re older, but really, Harry, it’s \emph{not} important! Just something from our school days.”

Harry couldn’t have put his finger on exactly what tipped him off; it might have been something about the exact tone of nervousness in Remus’s voice, or the way the man had said \emph{when you’re older}, that sparked the sudden leap of Harry’s intuition...

“Actually,” said Harry, “I think I’ve sort of guessed it already, sorry.”

Remus raised his eyebrows. “Have you?” He sounded a bit skeptical.

“They were lovers, weren’t they?”

There was an awkward pause.

Remus gave a slow, grave nod.

“Once,” Remus said. “A long time ago. A sad affair, ending in vast tragedy, or so it seemed to us all when we were young.” The unhappy puzzlement was plain on his face. “But I had thought that long since over and done and buried beneath adult friendship, until the day that Black killed Peter.”

