\chapter{Delayed Gratification}

\lettrine{D}{raco} had a stern expression on his face, and his green-trimmed robes somehow looked far more formal, serious, and well-turned-out than the same exact robes as worn by the two boys behind him.

“Talk,” said Draco.

“Yeah! Talk!”

“You heard da boss! Talk!”

“You two, on the other hand, \emph{shut up.}”

The last session of classes on Friday was about to start, in that vast auditorium where all four Houses learned Defense, er, Battle Magic.

The last session of classes on Friday.

Harry was hoping that this class would be non-stressful, and that the brilliant Professor Quirrell would realize this was perhaps not the best time to single out Harry for anything. Harry had recovered a little, but...

...but just in case, it was probably best to get in a bit of stress relief first.

Harry leaned back in his chair and bestowed a look of great solemnity upon Draco and his minions.

“You ask, what is our aim?” Harry declaimed. “I can answer in one word. It is victory. Victory at all costs—Victory in spite of all terrors—Victory, however long and hard the road may be, for without victory there is no—”

“\emph{Talk about Snape,}” Draco hissed. “\emph{What did you do?}”

Harry wiped away the fake solemnity and gave Draco a more serious look.

“You saw it,” Harry said. “Everyone saw it. I snapped my fingers.”

“\emph{Harry! Stop teasing me!}”

So he’d been promoted to \emph{Harry} now. Interesting. And in fact Harry was fairly sure that he was meant to notice that, and feel bad if he didn’t respond somehow...

Harry tapped his ears and gave a significant glance at the minions.

“They won’t talk,” said Draco.

“Draco,” Harry said, “I’m going to be one hundred percent honest here and say that yesterday I was not particularly impressed with Mr.~Goyle’s cunning.”

Mr.~Goyle winced.

“Me neither,” said Draco. “I explained to him that I ended up owing you a favor because of it.” (Mr.~Goyle winced again.) “But there \emph{is} a big difference between that sort of mistake and being indiscreet. That really is something they’ve been trained from childhood to understand.”

“All right then,” Harry said. He lowered his voice, even though the background noises had gone to blurs in Draco’s presence. “I deduced one of Severus’s secrets and did a bit of blackmail.”

Draco’s expression hardened. “Good, now tell me something you didn’t tell in strict confidence to the idiots in Gryffindor, meaning that was the story you \emph{wanted} to get all over the school.”

Harry grinned involuntarily and he knew that Draco had caught it.

“What is Severus saying?” Harry said.

“That he hadn’t realized how sensitive the feelings of young children were,” Draco said. “Even in Slytherin! Even to \emph{me!}”

“Are you sure,” Harry said, “that you want to know something your Head of House would rather you not know?”

“Yes,” Draco said without hesitation.

\emph{Interesting.} “Then you really are going to send your minions away first, because I’m not sure I can believe everything you believe about them.”

Draco nodded. “Okay.”

Mr.~Crabbe and Mr.~Goyle looked \emph{very} unhappy. “Boss—” said Mr.~Crabbe.

“You’ve given Mr.~Potter no reason to trust you,” Draco said. “Go!”

They left.

“In particular,” Harry said, lowering his voice even further, “I’m not \emph{entirely} sure that they wouldn’t just report what I said to Lucius.”

“Father wouldn’t \emph{do} that!” Draco said, looking genuinely aghast. “They’re \emph{mine!}”

“I’m sorry, Draco,” Harry said. “I’m just not sure I can believe everything you believe about your father. Imagine it was your secret and me telling you my father wouldn’t do that.”

Draco nodded slowly. “You’re right. \emph{I’m} sorry, Harry. It was wrong of me to ask it of you.”

\emph{How did I get} this \emph{promoted? Shouldn’t he hate me now?} Harry had the feeling he was looking at something exploitable...\ he just wished his brain wasn’t so exhausted. Ordinarily he would have loved to try his hand at some complicated plotting.

“Anyway,” Harry said. “Trade. I tell you a fact that isn’t on the grapevine, and does not \emph{go} on the grapevine, and in \emph{particular} does not go to your father, and in return you tell me what you and Slytherin think about the whole business.”

“Deal!”

Now to make this as vague as possible...\ something that wouldn’t hurt much even if it did get out... “What I said was true. I did discover one of Severus’s secrets, and I did do some blackmail. But Severus wasn’t the only person involved.”

“\emph{I knew it!}” Draco said exultantly.

Harry’s stomach sank. He had apparently said something very significant and he did not know why. This was not a good sign.

“All right,” Draco said. He was grinning widely now. “So here’s what the reaction was like in Slytherin. First, all the idiots were like, ‘We hate Harry Potter! Let’s go beat him up!’”

Harry choked. “What is \emph{wrong} with the Sorting Hat? That’s not Slytherin, it’s \emph{Gryffindor}—”

“Not all children are prodigies,” Draco said, though he was smiling in a sort of nasty-conspiratorial way, as though to suggest that he privately agreed with Harry’s opinion. “And it took around fifteen seconds for someone to explain to them why this might not be such a favor to Snape, so you’re fine. Anyway, after that was the second wave of idiots, the ones who were saying, ‘Looks like Harry Potter was just another do-gooder after all.’”

“And then?” Harry said, smiling even though he had no idea why \emph{that} was stupid.

“And then the actual smart people started talking. It’s obvious that you found a way to put a \emph{lot} of pressure on Snape. And while that could be more than one thing...\ the obvious \emph{next} thought is that it has something to do with Snape’s unknown hold over Dumbledore. Am I right?”

“No comment,” Harry said. At least his brain was processing this part correctly. House Slytherin \emph{had} wondered why Severus wasn’t getting fired. And they’d concluded that Severus was blackmailing Dumbledore. Could that actually be true...? But Dumbledore hadn’t seemed to act like it...

Draco went on talking. “And the \emph{next} thing the smart people pointed out was that if you could put enough pressure on Snape to make him leave half of Hogwarts alone, that meant you probably had enough power to get rid of him entirely, if you wanted. What you did to him was a humiliation, just the same way he tried to humiliate you—but you left us our Head of House.”

Harry made his smile wider.

“And then the \emph{really} smart people,” Draco said, his face now serious, “went off and had a little discussion by themselves, and someone pointed out that it would be a very stupid thing to leave an enemy around like that. If you could break his hold over Dumbledore, the obvious thing would be to just do it. Dumbledore would kick Snape out of Hogwarts and maybe even have him killed, he’d be \emph{very} grateful to you, and you wouldn’t have to worry about Snape sneaking into your dorm room at night with interesting potions.”

Harry’s face was now neutral. He had not thought of that and he really, really should have. “And from this you concluded...?”

“Snape’s hold was some secret of Dumbledore’s and \emph{you’ve got the secret!}” Draco was looking exultant. “It can’t be powerful enough to destroy Dumbledore entirely, or Snape would have used it by now. Snape refuses to use his hold for anything except staying king of Slytherin House in Hogwarts, and he doesn’t always get what he wants even then, so it must have limits. But it’s \emph{got} to be really good! Father’s been trying to get Snape to tell him for \emph{years!}”

“And,” Harry said, “now Lucius thinks maybe \emph{I} can tell him. Did you already get an owl—”

“I will tonight,” Draco said, and laughed. “It will say,” his voice took on a different, more formal cadence, “\emph{My beloved son: I’ve already told you of Harry Potter’s potential importance. As you have already realized, his importance has now become greater and more urgent. If you see any possible avenue of friendship or point of pressure with him, you must pursue it, and the full resources of Malfoy are at your disposal if needed.}”

Gosh. “Well,” Harry said, “not commenting on whether or not your whole complicated edifice of theory is true, let me just say that we are not quite such good friends as yet.”

“I know,” Draco said. Then his face turned \emph{very} serious, and his voice grew quiet even within the blur. “Harry, has it occurred to you that if you know something Dumbledore doesn’t want known, Dumbledore might simply have you killed? And it would turn the Boy-Who-Lived from a potential competing leader into a valuable martyr, too.”

“No comment,” Harry said yet again. He hadn’t thought of that last part, either. Didn’t \emph{seem} to be Dumbledore’s style...\ but...

“Harry,” Draco said, “you’ve obviously got \emph{incredible} talent, but you’ve got no training and no mentors and you do stupid things sometimes and \emph{you really need an advisor who knows how to do this or you’re going to get hurt!}” Draco’s face was fierce.

“Ah,” Harry said. “An advisor like Lucius?”

“Like \emph{me!}” said Draco. “I’ll promise to keep your secrets from Father, from \emph{everyone,} I’ll just help you figure out whatever you want to do!”

Wow.

Harry saw that zombie-Quirrell was staggering in through the doors.

“Class is about to start,” said Harry. “I’ll think about what you said, there’s lots of times I \emph{do} wish I had all your training, it’s just I don’t know how I can trust you so quickly—”

“You shouldn’t,” Draco said, “it’s too soon. See? I’ll give you good advice even if it hurts me. But we should maybe \emph{hurry up} and become closer friends.”

“I’m open to that,” said Harry, who was already trying to figure out how to exploit it.

“Another bit of advice,” Draco said hurriedly as Quirrell slouched toward his desk, “right now everyone in Slytherin’s wondering about you, so if you’re courting us, which I think you are, you should do something that signals friendship to Slytherin. \emph{Soon}, like today or tomorrow.”

“Letting Severus go on awarding extra House points to Slytherin wasn’t enough?” No reason Harry couldn’t take credit for it.

Draco’s eyes flickered with realization, then he said rapidly, “It’s not the same, trust me, it’s got to be something obvious. Push your mudblood rival Granger into a wall or something, everyone in Slytherin will know what that means—”

“That is \emph{not} how it works in Ravenclaw, Draco! If you have to push someone into a wall it means your brain is too \emph{weak} to beat them the right way and everyone in Ravenclaw \emph{knows that}—”

The screen on Harry’s desk flickered on, provoking a sudden wash of nostalgia for television and computers.

“Ahem,” said Professor Quirrell’s voice, seeming to speak personally to Harry out of the screen. “Please take your seats.”
\sbreak
And the children were all seated and staring at the repeater screens on their desks, or looking down directly at the great white marble stage where Professor Quirrell stood, leaning on his desk atop the small dais of darker marble.

“Today,” said Professor Quirrell, “I had planned to teach you your first defensive spell, a small shield that was the ancestor of today’s \emph{Protego.} But on second thought I have changed today’s lesson plan in the light of recent events.”

Professor Quirrell’s gaze searched the rows of seats. Harry winced from where he was sitting, in the back row. He had a feeling he knew who was about to be called on.

“Draco, of the Noble and Most Ancient House of Malfoy,” said Professor Quirrell.

Whew.

“Yes, Professor?” said Draco. His voice was amplified, seeming to come from the repeater screen on Harry’s desk, which showed Draco’s face as he spoke. Then the screen shifted back to Professor Quirrell, who said:

“Is it your ambition to become the next Dark Lord?”

“That’s an odd question, Professor,” said Draco. “I mean, who’d be dumb enough to admit it?”

A few students laughed, but not many.

“Indeed,” said Professor Quirrell. “So while there’s no point in asking any of you, it would not surprise me in the slightest if there were a student or two in my classes who harbored ambitions of being the next Dark Lord. After all, \emph{I} wanted to be the next Dark Lord when \emph{I} was a young Slytherin.”

This time the laughter was much more widespread.

“Well, it \emph{is} the House of the ambitious, after all,” Professor Quirrell said, smiling. “I didn’t realize until later that what I really enjoyed was Battle Magic, and that my true ambition was to become a great fighting wizard and someday teach at Hogwarts. In any case, when I was thirteen years old, I read through the historical sections of the Hogwarts library, scrutinizing the lives and fates of past Dark Lords, and I made a list of all the mistakes that \emph{I} would never make when \emph{I} was a Dark Lord—”

Harry giggled before he could stop himself.

“Yes, Mr.~Potter, very amusing. So, Mr.~Potter, can you guess what was the very first item on that list?”

\emph{Great.} “Um...\ never use a complicated way of dealing with an enemy when you can just Abracadabra them?”

“The \emph{term,} Mr.~Potter, is \emph{Avada Kedavra,}” Professor Quirrell’s voice sounded a bit sharp for some reason, “and no, that was \emph{not} on the list I made at age thirteen. Would you care to guess again?”

“Ah...\ never brag to anyone about your evil master plan?”

Professor Quirrell laughed. “Ah, now \emph{that} was number two. My, Mr.~Potter, have we been reading the same books?”

There was more laughter, with an undertone of nervousness. Harry clenched his jaw tightly shut and said nothing. A denial would accomplish nothing.

“But no. The \emph{first} item was, ‘I will not go around provoking strong, vicious enemies.’ The history of the world would be very different if Mornelithe Falconsbane or Hitler had grasped that elementary point. Now \emph{if,} Mr.~Potter—just \emph{if} by some chance you harbor an ambition similar to the one I held as a young Slytherin—even so, I hope it is not your ambition to become a \emph{stupid} Dark Lord.”

“Professor Quirrell,” Harry said, gritting his teeth, “I am a \emph{Ravenclaw} and it is not my ambition to be stupid, period. I know that what I did today was dumb. But it wasn’t \emph{Dark!} I was \emph{not} the one who threw the first punch in that fight!”

“You, Mr.~Potter, are an idiot. But then so was I at your age. Thus I anticipated your answer and altered today’s lesson plan accordingly. Mr.~Gregory Goyle, if you would come forward, please?”

There was a surprised pause in the classroom. Harry hadn’t been expecting that.

Neither, from the looks of it, had Mr.~Goyle, who looked rather uncertain and worried as he mounted the marble stage and approached the dais.

Professor Quirrell straightened from where he was leaning on the desk. He looked suddenly stronger, and his hands formed fists and he drew himself up into a clearly recognizable martial arts stance.

Harry’s eyes widened at the sight, and he realized why Mr.~Goyle had been called up.

“Most wizards,” Professor Quirrell said, “do not bother much with what a Muggle would term martial arts. Is not a wand stronger than a fist? This attitude is stupid. Wands are held in fists. If you want to be a great fighting wizard you \emph{must} learn martial arts to a level which would impress even a Muggle. I will now demonstrate a certain vitally important technique, which I learned in a \emph{dojo,} a Muggle school of martial arts, of which I shall speak more shortly. For now...” Professor Quirrell took several steps forward, still in stance, advancing on where Mr.~Goyle stood. “Mr.~Goyle, I will ask you to attack me.”

“Professor Quirrell,” said Mr.~Goyle, his voice now amplified as the professor’s was, “can I ask what level—”

“Sixth \emph{dan}. You will not be hurt and neither will I. And if you see an opening, please take it.”

Mr.~Goyle nodded, looking much relieved.

“Note,” Professor Quirrell said, “that Mr.~Goyle was afraid to attack someone who did not know martial arts to an acceptable level, for fear that I, or he, would be hurt. Mr.~Goyle’s attitude is exactly correct and he has earned three Quirrell points for it. Now, fight!”

The young boy blurred forward, fists flying, and the Professor blocked every blow, dancing backward, Quirrell kicked and Goyle blocked and spun and tried to trip Quirrell with a sweeping leg and Quirrell hopped over it and it was all happening too fast for Harry to make sense of what was going on and then Goyle was on his back with his legs pushing and Quirrell was actually \emph{flying through the air} and then he hit the ground shoulder first and rolled.

“Stop!” cried Professor Quirrell from the ground, sounding a little panicked. “You win!”

Mr.~Goyle pulled up so sharply he staggered, almost tripping and falling from the aborted momentum of his headlong charge toward Professor Quirrell. His face showed utter shock.

Professor Quirrell arched his back and bounced to his feet using a peculiar springing motion that made no use of his hands.

There was a silence in the classroom, a silence born of total confusion.

“Mr.~Goyle,” said Professor Quirrell, “what vitally important technique did I demonstrate?”

“How to fall correctly when someone throws you,” said Mr.~Goyle. “It’s one of the very first lessons you learn—”

“That too,” said Professor Quirrell.

There was a pause.

“The vitally important technique which I demonstrated,” said Professor Quirrell, “was how to lose. You may go, Mr.~Goyle, thank you.”

Mr.~Goyle walked off the platform, looking rather bewildered. Harry felt the same way.

Professor Quirrell walked back to his desk and resumed leaning on it. “Sometimes we forget the most basic things, since it has been too long since we learned them. I realized I had done the same with my own lesson plan. You do not teach students to throw until you have taught them to fall. And I must not teach you to fight if you do not understand how to lose.”

Professor Quirrell’s face hardened, and Harry thought he saw a hint of pain, a touch of sorrow, in those eyes. “I learned how to lose in a \emph{dojo} in Asia, which, as any Muggle knows, is where all the good martial artists live. This \emph{dojo} taught a style which had a reputation among fighting wizards as adapting well to magical dueling. The Master of that \emph{dojo}—an old man by Muggle standards—was that style’s greatest living teacher. He had no idea that magic existed, of course. I applied to study there, and was one of the few students accepted that year, from among many contenders. There might have been a tiny bit of special influence involved.”

There was some laughter in the classroom. Harry didn’t share it. That hadn’t been right at all.

“In any case. During one of my first fights, after I had been beaten in a particularly humiliating fashion, I lost control and attacked my sparring partner—”

\emph{Yikes.}

“—thankfully with my fists, rather than my magic. The Master, surprisingly, did not expel me on the spot. But he told me that there was a flaw in my temperament. He explained it to me, and I knew that he was right. And then he said that I would learn how to lose.”

Professor Quirrell’s face was expressionless.

“Upon his strict orders, all of the students of the \emph{dojo} lined up. One by one, they approached me. I was \emph{not} to defend myself. I was only to beg for mercy. One by one, they slapped me, or punched me, and pushed me to the ground. Some of them spat on me. They called me awful names in their language. And to each one, I had to say, ‘I lose!’ and similar such things, such as ‘I beg you to stop!’ and ‘I admit you’re better than me!’”

Harry was trying to imagine this and simply failing. There was no way something like that could have happened to the dignified Professor Quirrell.

“I was a prodigy of Battle Magic even then. With wandless magic alone I could have killed everyone in that dojo. I did not do so. I learned to lose. To this day I remember it as one of the most unpleasant hours of my life. And when I left that dojo eight months later—which was not nearly enough time, but was all I could afford to spend—the Master told me that he hoped I understood why that had been necessary. And I told him that it was one of the most valuable lessons I had ever learned. Which was, and is, true.”

Professor Quirrell’s face turned bitter. “You are wondering where this marvelous \emph{dojo} is, and whether you can study there. You cannot. For not long afterward, another would-be student came to that hidden place, to that remote mountain. He-Who-Must-Not-Be-Named.”

There was the sound of many breaths being drawn in simultaneously. Harry felt sick to his stomach. He knew what was coming.

“The Dark Lord came to that school openly, without disguise, glowing red eyes and all. The students tried to bar his way and he simply Apparated through. There was terror there, but discipline, and the Master came forth. And the Dark Lord demanded—not asked, but demanded—to be taught.”

Professor Quirrell’s face was very hard. “Perhaps the Master had read too many books telling the lie that a true martial artist could defeat even demons. For whatever reason, the Master refused. The Dark Lord asked why he could not be a student. The Master told him he had no patience, and that was when the Dark Lord ripped his tongue out.”

There was a collective gasp.

“You can guess what happened next. The students tried to rush the Dark Lord and fell over, stunned where they stood. And then...”

Professor Quirrell’s voice faltered for a moment, then resumed.

“There is an Unforgiveable Curse, the Cruciatus Curse, which produces unbearable pain. If the Cruciatus is extended for longer than a few minutes it produces permanent insanity. One by one, the Dark Lord Crucioed the Master’s students into insanity, and then finished them off with the Killing Curse, while the Master was forced to watch. When all his students had died in this way, the Master followed. I learned this from the single surviving student, whom the Dark Lord had left alive to tell the tale, and who had been a friend of mine...”

Professor Quirrell turned away, and when he turned back a moment later, he once again seemed calm and composed.

“Dark Wizards cannot keep their tempers,” Professor Quirrell said quietly. “It is a nearly universal flaw of the species, and anyone who makes a habit of fighting them soon learns to rely on it. Understand that the Dark Lord did \emph{not} win that day. His goal was to learn martial arts, and yet he left without a single lesson. The Dark Lord was foolish to wish that story retold. It did not show his strength, but rather an exploitable weakness.”

Professor Quirrell’s gaze focused on a single child in the classroom.

“Harry Potter,” Professor Quirrell said.

“Yes,” Harry said, his voice hoarse.

“What \emph{precisely} did you do wrong today, Mr.~Potter?”

Harry felt like he was going to throw up. “I lost my temper.”

“That is \emph{not} precise,” said Professor Quirrell. “I will describe it more exactly. There are many animals which have what are called dominance contests. They rush at each other with horns—trying to knock each other down, not gore each other. They fight with their paws—with claws sheathed. But why with their claws sheathed? Surely, if they used their claws, they would stand a better chance of winning? But then their enemy might unsheathe their claws as well, and instead of resolving the dominance contest with a winner and a loser, both of them might be severely hurt.”

Professor Quirrell gaze seemed to come straight out at Harry from the repeater screen. “What you demonstrated today, Mr.~Potter, is that—unlike those animals who keep their claws sheathed and accept the results—you do not know how to lose a dominance contest. When a \emph{Hogwarts professor} challenged you, you did not back down. When it looked like you might lose, you unsheathed your claws, heedless of the danger. You \emph{escalated,} and then you escalated \emph{again.} It started with a slap at you from Professor Snape, who was obviously dominant over you. Instead of losing, you slapped back and lost ten points from Ravenclaw. Soon you were talking about leaving Hogwarts. The fact that you escalated even further in some unknown direction, and somehow won at the end, does not change the fact that you are an idiot.”

“I understand,” Harry said. His throat was dry. That \emph{had} been precise. \emph{Frighteningly} precise. Now that Professor Quirrell had said it, Harry could see in hindsight that it was an \emph{exactly} accurate description of what had happened. When someone’s model of you was that good, you had to wonder whether they were right about other things too, like your intent to kill.

“The \emph{next} time, Mr.~Potter, that you choose to escalate a contest rather than lose, you may lose \emph{all} the stakes you place on the table. I cannot guess what they were today. I can guess that they were far, far too high for the loss of ten House points.”

Like the fate of magical Britain. That was what he’d done.

“You will protest that you were trying to help all of Hogwarts, a much more important goal worthy of great risks. That is a \emph{lie.} If you had been—”

“I would have taken the slap, waited, and picked the best possible time to make my move,” Harry said, his voice hoarse. “But that would have meant \emph{losing}. Letting him be dominant over me. It was what the Dark Lord couldn’t do with the Master he wanted to learn from.”

Professor Quirrell nodded. “I see that you have understood perfectly. And so, Mr.~Potter, today you are going to learn how to lose.”

“I—”

“I will not hear any objections, Mr.~Potter. It is evident both that you need this and that you are strong enough to take it. I assure you that your experience will not be so harsh as what I went through, though you may well remember it as the worst fifteen minutes of your young life.”

Harry swallowed. “Professor Quirrell,” he said in a small voice, “can we do this some other time?”

“No,” Professor Quirrell said simply. “You are five days into your Hogwarts education and already this has happened. Today is Friday. Our \emph{next} defense class is on Wednesday. Saturday, Sunday, Monday, Tuesday, Wednesday... No, we do \emph{not} have time to wait.”

There were a few laughs at this, but very few.

“Please consider it an order from your professor, Mr.~Potter. What I would like to say is that otherwise I will not teach you any offensive spells, because I would then hear that you had severely hurt or even killed someone. Unfortunately I am told that your fingers are already powerful weapons. Do not snap them at any time during this lesson.”

More scattered laughter, sounding rather nervous.

Harry felt like he might cry. “Professor Quirrell, if you do anything like what you talked about, it’s going to make me angry, and I really would rather not get angry again today—”

“The point is \emph{not} to avoid getting angry,” Professor Quirrell said, his face looking grave. “Anger is natural. You need to learn how to lose even when you are angry. Or at least \emph{pretend} to lose so that you can \emph{plan} your vengeance. As I did with Mr.~Goyle today, unless of course any of you think he really \emph{is} better—”

“I’m not!” shouted Mr.~Goyle from his desk, sounding a little frantic. “I know you didn’t really lose! Please don’t plan any vengeances!”

Harry felt sick to his stomach. Professor Quirrell didn’t know about his mysterious dark side. “Professor, we really need to talk about this after class—”

“We will,” Professor Quirrell said in the tones of a promise. “After you learn how to lose.” His face was serious. “It should go without saying that I will exclude anything which could injure you or even cause you significant pain. The pain will come from the difficulty of losing, instead of fighting back and escalating the battle until you win.”

Harry’s breath was coming in short, panicky pants. He was more frightened than he’d been after leaving the Potions classroom. “Professor Quirrell,” he managed to say, “I don’t want you to get fired over this—”

“I will not be,” Professor Quirrell said, “if \emph{you} tell them afterward that it was necessary. And this I trust you to do.” For a moment Professor Quirrell’s voice turned very dry. “Believe me, they have tolerated worse in their hallways. This case will be exceptional only in that it happens within a classroom.”

“Professor Quirrell,” Harry whispered, but he thought his voice was still being repeated everywhere, “do you really believe that if I don’t do this, I might hurt someone?”

“Yes,” Professor Quirrell said simply.

“Then,” Harry felt nauseous, “I’ll do it.”

Professor Quirrell turned to regard the Slytherins. “So...\ with the full approval of your teacher, and in such a fashion that Snape cannot be blamed for your actions...\ do any of you wish to show your dominance over the Boy-Who-Lived? Shove him around, push him to the ground, hear him beg for your mercy?”

Five hands went up.

“Everyone with your hand raised, you are an absolute idiot. What part of \emph{pretending} to lose did you not understand? If Harry Potter does become the next Dark Lord he will hunt you down and kill you after he graduates.”

The five hands dropped abruptly back to their desks.

“I won’t,” Harry said, his voice coming out rather weakly. “I swear never to take vengeance upon those who help me learn to lose. Professor Quirrell...\ would you \emph{please}... \emph{stop} that?”

Professor Quirrell sighed. “I \emph{am} sorry, Mr.~Potter. I realize that you must find this equally annoying whether you intend to become a Dark Lord or not. But those children \emph{also} had an important life lesson to learn. Would it be acceptable if I awarded you a Quirrell point in apology?”

“Make it two,” Harry said.

There was a current of surprised laughter, defusing some of the tension.

“Done,” Professor Quirrell said.

“And after I graduate I’m going to hunt you down and \emph{tickle} you.”

There was more laughter, although Professor Quirrell didn’t smile.

Harry felt like he was wrestling an anaconda, trying to force the conversation through the narrow course that would make people realize he wasn’t a Dark Lord after all... \emph{why} was Professor Quirrell so suspicious of him?

“Professor,” said Draco’s unamplified voice. “It is also not my own ambition to become a stupid Dark Lord.”

There was a shocked silence in the classroom.

\emph{You don’t have to do this!} Harry almost blurted out loud, but checked himself in time; Draco might not wish it known that he was doing this out of friendship for Harry...\ or out of the desire to appear friendly...

Calling \emph{that} a \emph{desire to appear friendly} made Harry feel small, and mean. If Draco had intended to impress him, it was working perfectly.

Professor Quirrell was regarding Draco gravely. “\emph{You} worry that you cannot pretend to lose, Mr.~Malfoy? That this flaw which describes Mr.~Potter also describes you? \emph{Surely} your father taught you better.”

“When it comes to talking, maybe,” said Draco, now on the repeater screen. “Not when it comes to being shoved around and pushed to the ground. I want to be fully as strong as you, Professor Quirrell.”

Professor Quirrell’s eyebrows went up and stayed up. “I am afraid, Mr.~Malfoy,” he said after a time, “that the arrangements I made for Mr.~Potter, involving some older Slytherins who will be told \emph{afterward} how stupid they were, would not carry over onto you. But it is my professional opinion that you are already very strong. Should I hear that you have failed, as Mr.~Potter failed today, I will make the appropriate arrangements and apologize to you and whomever you have hurt. I do not think this will be necessary, however.”

“I understand, professor,” said Draco.

Professor Quirrell looked over the class. “Does anyone else wish to become strong?”

Some students glanced around nervously. Some, Harry thought from his back row, looked like they were opening their mouths but not saying anything. In the end, no one spoke.

“Draco Malfoy will be one of the generals of your year’s armies,” said Professor Quirrell, “should he deign to engage in that after-school activity. And now, Mr.~Potter, please come forward.”
\sbreak
\emph{Yes,} Professor Quirrell had said, \emph{it must be in front of everyone, in front of your friends, because that is where Snape confronted you and that is where you must learn to lose.}

So now the first year watched. In magically enforced silence, and with requests from both Harry and the professor not to intervene. Hermione had her face turned away, but she hadn’t spoken out or even given him any sort of significant look, maybe because she’d been there in Potions too.

Harry stood on a soft blue mat, such as might be found in a Muggle dojo, which Professor Quirrell had laid out upon the floor for when Harry was pushed down.

Harry was frightened of what he might do. If Professor Quirrell was right about his intent to kill...

Harry’s wand lay on Professor Quirrell’s desk, not because Harry knew any spells that could defend him, but because otherwise (Harry thought) he might have tried to jam it through someone’s eye socket. His pouch lay there, now containing his protected but still potentially fragile Time-Turner.

Harry had pleaded with Professor Quirrell to Transfigure him some boxing gloves and lock them on his hands. Professor Quirrell had given him a look of silent understanding, and refused.

\emph{I will not go for their eyes, I will not go for their eyes, I will not go for their eyes, it would be the end of my life in Hogwarts, I’ll be arrested,} Harry chanted to himself, trying to hammer the thought into his brain, hoping it would stay there if his intent to kill took over.

Professor Quirrell returned, escorting thirteen older Slytherins of different years. Harry recognized one of them as the one he’d hit with a pie. Two others from that confrontation were also present. The one who’d said to stop, that they really shouldn’t do this, was missing.

“I repeat,” Professor Quirrell said, sounding very stern, “Potter is \emph{not} to be really hurt. Any and all \emph{accidents} will be treated as deliberate. Do you understand?”

The older Slytherins nodded, grinning.

“Then please feel free to take the Boy-Who-Lived down a few pegs,” Professor Quirrell said, with a twisted smile that only the first-years understood.

By some form of mutual consent, the pie-target was at the front of the group.

“Potter,” said Professor Quirrell, “meet Mr.~Peregrine Derrick. He is better than you and he is about to show you that.”

Derrick strode forward and Harry’s brain screamed discordantly, he must not run away, he must not fight back—

Derrick stopped an arm’s length away from Harry.

Harry wasn’t angry yet, just frightened. And that meant he beheld a teenage boy fully half a meter taller than himself, with clearly defined muscles, facial hair, and a grin of terrible anticipation.

“Ask him not to hurt you,” Professor Quirrell said. “Perhaps if he sees that you’re pathetic enough, he’ll decide that you’re boring, and go away.”

There was laughter from the watching older Slytherins.

“Please,” Harry said, his voice faltering, “don’t, hurt, me...”

“That didn’t sound very sincere,” said Professor Quirrell.

Derrick’s smile widened. The clumsy imbecile was looking very superior and...

...Harry’s blood temperature was dropping...

“Please don’t hurt me,” Harry tried again.

Professor Quirrell shook his head. “How in Merlin’s name did you manage to make that sound like an insult, Potter? There is only one response you can possibly expect from Mr.~Derrick.”

Derrick stepped forward deliberately, and bumped into Harry.

Harry staggered back a few feet and, before he could stop himself, straightened up icily.

“Wrong,” said Professor Quirrell, “wrong, wrong, wrong.”

“You bumped into me, Potter,” Derrick said. “Apologize.”

“I’m sorry!”

“You don’t \emph{sound} sorry,” said Derrick.

Harry’s eyes widened in indignation, he \emph{had} managed to make that sound pleading—

Derrick pushed him, hard, and Harry fell to the mat on his hands and knees.

The blue fabric seemed to waver in Harry’s vision, not far away.

He was beginning to doubt Professor Quirrell’s real motives in teaching this so-called \emph{lesson.}

A foot rested on Harry’s buttocks and a moment later Harry was pushed hard to the side, sending him sprawling on his back.

Derrick laughed. “This is \emph{fun,}” he said.

All he had to do was say it was over. And report the whole thing to the Headmaster’s office. That would be the end of this \emph{Defense Professor} and his ill-fated stay at Hogwarts and... Professor McGonagall would be angry about that, but...

(An image of Professor McGonagall’s face flashed before his eyes, she didn’t look angry, just sad—)

“Now tell him that he’s better than you, Potter,” said Professor Quirrell’s voice.

“You’re, better, than, me.”

Harry started to raise himself and Derrick put a foot on his chest and shoved him back down to the mat.

The world was becoming transparent as crystal. Lines of action and their consequences stretched out before him in utter clarity. The fool wouldn’t be expecting him to strike back, a quick hit in the groin would stun him long enough for—

“Try again,” said Professor Quirrell and with a sudden sharp motion Harry rolled and sprang to his feet and whirled on where stood his real enemy, the Defense Professor—

Professor Quirrell said, “You have no patience.”

Harry faltered. His mind, well-honed in pessimism, drew a picture of a wizened old man with blood pouring from his mouth after Harry had ripped his tongue out—

A moment later, Derrick pushed Harry to the mat again and then sat down on him, sending Harry’s breath whooshing out.

“Stop!” Harry screamed. “Please stop!”

“Better,” said Professor Quirrell. “That even sounded sincere.”

It \emph{had} been. That was the horrible thing, the sickening thing, it \emph{had} been sincere. Harry was panting rapidly, fear and cold anger both flushing through him—

“Lose,” said Professor Quirrell.

“I, lose,” Harry forced out.

“I like it,” Derrick said from on top of him. “Lose some more.”
\sbreak
Hands shoved Harry, sending him stumbling across the circle of older Slytherins to another set of hands that shoved him again. Harry had long since passed the point of trying not to cry, and was now just trying not to fall down.

“What are you, Potter?” said Derrick.

“A, l-loser, I lose, I give up, you win, you’re b-better, than me, please stop—”

Harry tripped over a foot and went crashing to the ground, hands not quite able to catch himself. He was dazed for a moment, then began struggling to his feet again—

“\emph{Enough!}” said Professor Quirrell’s voice, sounding sharp enough to cut iron. “Step away from Mr.~Potter!”

Harry saw the surprised looks on their faces. The chill in his blood, which had been flowing and ebbing, smiled in cold satisfaction.

Then Harry collapsed to the mat.

Professor Quirrell talked. There were gasps from the older Sly\-ther\-ins.

“And I believe the scion of Malfoy has something he wants to explain to you as well,” finished Professor Quirrell.

Draco’s voice started talking. His voice sounded almost as sharp as professor Quirrell’s, it had acquired the same cadence Draco had used to imitate his father, and it was saying things like \emph{could have put Slytherin House in jeopardy} and \emph{who knows how many allies in this school alone} and \emph{total lack of awareness, never mind cunning} and \emph{dull thugs, useful for nothing but lackeys} and something in Harry’s hindbrain, despite everything he knew, was designating Draco as an ally.

Harry ached all over, was probably bruised, his body felt cold, his mind utterly exhausted. He tried to think of Fawkes’s song, but without the phoenix present he couldn’t remember the melody and when he tried to imagine it he couldn’t seem to think of anything except a bird chirping.

Then Draco stopped talking and Professor Quirrell told the older Slytherins they were dismissed, and Harry opened his eyes and struggled to sit up, “Wait,” Harry said, forcing the words out, “there’s something, I want, to say, to them—”

“Wait on Mr.~Potter,” Professor Quirrell said coldly to the departing Slytherins.

Harry swayed to his feet. He was careful not to look in the direction of his classmates. He didn’t want to see how they were looking at him now. He didn’t want to see their pity.

So instead Harry looked at the older Slytherins, who still seemed to be in a state of shock. They stared back at him. Dread was on their faces.

His dark side, when it was in control, had held to the imagination of this moment, and went on pretending to lose.

Harry said, “No one will—”

“Stop,” said Professor Quirrell. “If that’s what I think it is, please wait until after they’re gone. They’ll hear about it later. We all have our lessons to learn, Mr.~Potter.”

“All right,” Harry said.

“You. Go.”

The older Slytherins fled and the door closed behind them.

“No one’s to take any revenge on them,” Harry said hoarsely. “That’s a request to anyone who considers themselves my friend. I had my lesson to learn, they helped me learn it, they had their lesson to learn too, it’s over. If you tell this story, make sure you tell that part too.”

Harry turned to look at Professor Quirrell.

“You lost,” said Professor Quirrell, his voice gentle for the first time. It sounded strange coming from the professor, like his voice shouldn’t even be able to do that.

Harry \emph{had} lost. There had been moments when the cold anger had faded entirely, replaced by fear, and during those moments he’d begged the older Slytherins and he’d meant it...

“Is the Sun still in the sky?” said Professor Quirrell, still with that strange gentleness. “Is it still shining? Are you still alive?”

Harry managed to nod.

“Not all losing is like this,” said Professor Quirrell. “There are compromises and negotiated surrenders. There are other ways to placate bullies. There is a whole art form to manipulating others by letting them be dominant over you. But first, losing must be \emph{thinkable}. Will you remember how you lost?”

“Yes.”

“Will you be able to lose?”

“I...\ think so...”

“I think so too.” Professor Quirrell bowed so low that his thin hair almost touched the floor. “Congratulations, Harry Potter, you win.”

There was no single source, no first mover, the applause started all at once like a massive thunderclap.

Harry’s couldn’t keep the shock from his face. He risked a glance at his classmates, and he saw their faces showing not pity but awe. The applause was coming from Ravenclaw and Gryffindor and Hufflepuff and even Slytherin, probably because Draco Malfoy was applauding too. Some students were standing up from their chairs and half of Gryffindor was standing on their desks.

So Harry stood there, swaying, letting their respect wash over him, feeling stronger, and maybe even a little healed.

Professor Quirrell waited for the applause to die away. It took quite a while.

“Surprised, Mr.~Potter?” Professor Quirrell said. His voice sounded amused. “You have just found out that the real world does not \emph{always} work like your worst nightmares. Yes, if you had been some poor anonymous boy being abused, then they would probably have respected you less afterward, pitied you even as they comforted you from their loftier perches. That \emph{is} human nature, I’m afraid. But \emph{you} they already know for a figure of power. And they saw you confront your fear and keep confronting it, even though you could have walked away at any time. Did you think less of \emph{me} when I told you that I had deliberately endured being spat upon?”

Harry felt a burning sensation in his throat and frantically clamped down. He didn’t trust this miraculous respect enough to start crying again in front of it.

“Your \emph{extraordinary} achievement in my class deserves an extraordinary reward, Harry Potter. Please accept it with my compliments on behalf of my House, and remember from this day forward that not all Slytherins are alike. There are Slytherins, and then there are Slytherins.” Professor Quirrell was smiling quite broadly as he said this. “Fifty-one points to Ravenclaw.”

There was a shocked pause and then pandemonium broke out among the Ravenclaw students, howling and whistling and cheering.

(And in the same moment Harry felt something \emph{wrong} about that, Professor McGonagall had been right, there \emph{should} have been consequences, there should have been a cost and a price to be paid, you couldn’t just put everything back the way it was like that—)

But Harry saw the elated faces in Ravenclaw and knew he couldn’t possibly say no.

His brain made a suggestion. It was a good suggestion. Harry could not even believe his brain was still keeping him upright, let alone producing good suggestions.

“Professor Quirrell,” Harry said, as clearly as he could through his burning throat. “You are everything a member of your House should be, and I think you must be just what Salazar Slytherin had in mind when he helped found Hogwarts. I thank you and your House,” Draco was very slightly nodding and subtly turning his finger, \emph{keep going}, “and I think this calls for three cheers for Slytherin. With me, everyone?” Harry paused. “\emph{Huzzah!}” Only a few people managed to join in on the first try. “\emph{Huzzah!}” This time most of Ravenclaw was in on it. “\emph{Huzzah!}” That was almost all of Ravenclaw, a scattering of Hufflepuffs and around a quarter of Gryffindor.

Draco’s hand moved into a small, quick, thumbs-up gesture.

Most of the Slytherins had expressions of sheer shock. A few were staring at Professor Quirrell in wonder. Blaise Zabini was looking at Harry with a calculating, intrigued expression.

Professor Quirrell bowed. “Thank \emph{you}, Harry Potter,” he said, still with that broad smile. He turned to the class. “Now, believe it or not, we still have half an hour left in this session, and that is enough to introduce the Simple Shield. Mr.~Potter, of course, is going off and taking a well-earned rest.”

“I can—”

“Idiot,” Professor Quirrell said fondly. The class was already laughing. “Your classmates can teach you afterward, or I’ll tutor you privately if that’s what it takes. But \emph{right now}, you’re going through the third door from the left in the back of the stage, where you will find a bed, an assortment of exceptionally tasty snacks, and some extremely light reading from the Hogwarts library. You may not take anything else with you, particularly not your textbooks. Now go.”

Harry went.


