\chapter{Empathy}

\lettrine{I}{t} wasn’t every day you got to see Harry Potter beg.

\quad\quad“\emph{Pleeaaase,}” whined Harry Potter.

Fred and George shook their heads again, smiling.

There was an agonized look on Harry Potter’s face. “But I \emph{told} you how I did the one with Kevin Entwhistle’s cat, and Hermione and the vanishing soda, and I \emph{can’t} tell you about the Sorting Hat or the Remembrall or Professor Snape...”

Fred and George shrugged and turned to leave.

“If you ever do figure it out,” said the Weasley twins, “be sure to let us know.”

“\emph{You’re evil! You’re both evil!}”

Fred and George firmly closed the door to the empty classroom behind them, and made sure to keep the grin on their faces for a while, just in case Harry Potter could see through doors.

Then they turned a corner and their faces sagged.

“I don’t suppose Harry’s guesses—”

“—gave you any ideas?” they said to each other at the same time, and then their shoulders slumped further.

Their last relevant memory was of Flume refusing to help them, though they couldn’t remember \emph{what} they’d asked him to do...

...but they must have looked elsewhere and found \emph{someone} to help them do \emph{something} illegal, or they wouldn’t have agreed to be Obliviated afterward.

How had they \emph{possibly} been able to get all that done on just forty Galleons?

At first they’d worried that they’d forged evidence so good that Harry actually \emph{would} end up married to Ginny...\ but they’d thought of that too, it seemed. The Wizengamot proceedings had been tampered with \emph{again} to put them back the way they’d been originally, the fake betrothal contract had vanished from its dragon-guarded vault in Gringotts, and so on. It was pretty scary, actually. Most people now thought the \emph{Daily Prophet} had just made the whole thing up for unguessable reasons, and the \emph{Quibbler} had helpfully twisted the knife deeper with the next day’s headline, \headline{Harry Potter secretly betrothed to Luna Lovegood.}

Whoever they’d hired would tell them after the statute of limitations expired, they desperately hoped. But meanwhile it was awful, they’d pulled their greatest prank ever, maybe the greatest prank in the history of pranking, and they \emph{couldn’t remember how.} It was crazy, they’d been able to think of a way the \emph{first} time, so why couldn’t they see it now after \emph{knowing} everything they’d done?

Their only consolation was that Harry didn’t know they didn’t know.

Not even Mum had questioned them about it, despite the obvious Weasley connection. Whatever had been done, it was far out of the reach of any Hogwarts student...\ except possibly \emph{one}, who, if certain rumors were true, might have done it by snapping his fingers. \emph{Harry} had been questioned under Veritaserum, he’d told them...\ with Dumbledore present and giving the Aurors scary looks. The Aurors had asked just enough to determine that Harry hadn’t pulled the prank himself or disappeared anyone, and then gotten the heck out of Hogwarts.

Fred and George had wondered whether to feel insulted about Harry Potter being questioned by the Aurors for \emph{their} prank, but the look on \emph{Harry’s} face, probably for exactly the same reason, made everything worth it.

Unsurprisingly, Rita Skeeter and the editor of the \emph{Daily Prophet} had both vanished and were probably in another country by now. They \emph{would’ve} liked to be able to tell their family about that part. Dad would have congratulated them, they thought, after Mum had finished killing them and Ginny had burned the remains.

But everything was still all right, they’d tell Dad someday, and meanwhile...

...meanwhile Dumbledore had happened to sneeze while passing them in the hallway, and a small package had accidentally dropped out of his pockets, and inside had been two matched wardbreaker’s monocles of \emph{incredible} quality. The Weasley twins had tested their new monocles on the “forbidden” third-floor corridor, making a quick trip to the magic mirror and back, and they hadn’t been able to see \emph{all} the detection webs clearly, but the monocles had shown a \emph{lot} more than they’d seen the first time.

Of course they would have to be very careful never to get caught with the monocles in their possession, or they would end up in the Headmaster’s office getting a stern lecture and maybe even threats of expulsion.

It was good to know that not everyone who got Sorted into Gryffindor grew up to be Professor McGonagall.
\sbreak
Harry was in a white room, windowless, featureless, sitting before a desk, facing an expressionless man in formal robes of solid black.

The room was screened against detection, and the man had performed exactly twenty-seven spells before saying so much as “Hello, Mr.~Potter.”

It was oddly appropriate that the man in black was about to try reading Harry’s mind.

“Prepare yourself,” the man said tonelessly.

A human mind, Harry’s Occlumency book had said, was only exposed to a Legilimens along certain \emph{surfaces}. If you failed to defend your surfaces, the Legilimens would go \emph{through} and be able to access any part of you which their own mind was able to comprehend...

...which tended not to be much. Human minds, it seemed, were hard for humans to understand on any level but the shallowest. Harry had wondered if knowing lots of cognitive science could make him an incredibly powerful Legilimens, but repeated experience had \emph{finally} driven into him the lesson that he needed to get a little less excited in his anticipations about this sort of thing. It wasn’t as if any cognitive scientist understood humans well enough to make one.

To learn the counter, Occlumency, the first step was to imagine yourself to be a different person, pretending it as thoroughly as you could, immersing yourself entirely in that alternate persona. You wouldn’t always have to do that, but in the beginning, it was how you learned where your surfaces were. The Legilimens would try to read you, and you would feel it happening if you paid close enough attention, you would sense them trying to enter. And your job was to make sure that they always touched your imaginary persona and not the real one.

When you were good enough at that, you could imagine being a very \emph{simple} sort of person, pretend to be a rock, and make a habit of leaving the pretense in place where all your surfaces were. That was a standard Occlumency barrier. Pretending to be a rock was hard to learn, but easy to do afterward, and the exposed surface of a mind was much shallower than its interior, so with enough practice you could keep it up as a background habit.

Or if you were a \emph{perfect Occlumens}, you could race \emph{ahead} of any probes, answering queries as fast as they were asked, so that the Legilimens would enter through your surfaces and see a mind indistinguishable from whoever you were pretending to be.

Even the best Legilimens could be fooled that way. If a perfect Occlumens claimed they were dropping their Occlumency barriers, there was no way to know if they were lying. Worse, you might not know you were dealing with a perfect Occlumens. They were rare, but the fact that they existed meant you couldn’t trust Legilimency on \emph{anyone.}

It was a sad commentary on how little human beings understood each other, how little any wizard comprehended the depths lying beneath the mind’s surface, that you could fool the best human telepaths by pretending to be someone else.

But then human beings only understood each other in the first place by pretending. You didn’t make predictions about people by modeling the hundred trillion synapses in their brain as separate objects. Ask the best social manipulator on Earth to build you an Artificial Intelligence from scratch, and they’d just give you a dumb look. You predicted people by telling \emph{your} brain to act like theirs. You \emph{put yourself in their place}. If you wanted to know what an angry person would do, you activated your own brain’s anger circuitry, and whatever that circuitry output, that was your prediction. What did the neural circuitry for anger actually look like inside? Who knew? The best social manipulator on Earth might not know what neurons \emph{were}, and neither might the best Legilimens.

Anything a Legilimens could \emph{understand}, an Occlumens could \emph{pretend} to be. It was the same trick either way—probably implemented by the same neural circuitry in both cases, a single set of control circuits for reconfiguring your own brain to act as a model of someone else’s.

And so the race between telepathic offense and telepathic defense had been a decisive win for defense. Otherwise the entire magical world, maybe even the whole Earth, would have been a very different place...

Harry took a deep breath, and concentrated. There was a slight smile on his face.

For \emph{once,} just \emph{once,} Harry hadn’t gotten shortchanged in the mysterious powers department.

After almost a month of work, and more on a whim than any real hunch, Harry had decided to make himself coldly angry and then try the book’s Occlumency exercises again. At that point he’d mostly given up hope on that sort of thing, but it had still seemed worth a quick try—

He’d run through all the book’s hardest exercises in two hours, and the next day he’d gone and told Professor Quirrell he was ready.

His dark side, it had turned out, was very, \emph{very} good at pretending to be other people.

Harry thought of his standard trigger, from the first time he’d gone over entirely to his dark side...

\emph{Severus paused, looking quite pleased with himself. “And that will be...\ five points? No, let us make it an even ten points from Ravenclaw for backchat.”}

Harry’s smile grew chillier, and he regarded the black-robed man who thought he was going to read Harry’s mind.

And then Harry turned into someone else entirely, someone who had seemed appropriate to the occasion.

...in a white room, windowless, featureless, sitting before a desk, facing an expressionless man in formal robes of solid black.

Kimball Kinnison regarded the black-robed man who thought he was going to read the mind of a Second-Stage Lensman of the Galactic Patrol.

To say that Kimball Kinnison was confident of the outcome would be an understatement. He had been trained by Mentor of Arisia, the most powerful mind known to this or any other universe, and the mere wizard sitting across from him would see precisely what the Gray Lensman wanted him to see...

...the mind of the boy he was currently disguised as, an innocent child named Harry Potter.

“I’m ready,” said Kimball Kinnison in nervous tones that were exactly appropriate for an eleven-year-old boy.

“\emph{Legilimens,}” said the black-robed wizard.

There was a pause.

The black-robed wizard blinked, as if he’d seen something so shocking that it had been enough to make even \emph{his} eyelids move. His voice wasn’t quite toneless as he said, “The Boy-Who-Lived has a \emph{mysterious dark side?}”

The heat slowly crept up into Harry’s cheeks.

“Well,” the man said. His face had now settled back into perfect calm. “Excuse me. Mr.~Potter, it is good to know your advantages, but that is not the same as being wildly overconfident in them. You may indeed be able to learn Occlumency at eleven years of age. This astounds me. I had thought Mr.~Dumbledore was pretending to be insane again. Your dissociative talent is so strong that I am surprised to find no other signs of childhood abuse, and you may become a perfect Occlumens in time. But there is a considerable difference between that and expecting to put up a successful Occlumency barrier on your first attempt. That is merely ridiculous. Did you feel anything as I read your mind?”

Harry shook his head, now blushing furiously.

“Then pay closer attention next time. The goal is not to create a perfect image on your first day of lessons. The goal is to learn where your surfaces are. Prepare yourself.”

Harry tried to pretend to be Kimball Kinnison again, tried to pay more attention, but his thoughts were a little scattered and he was suddenly aware of all the things he shouldn’t be thinking about...

Oh, this was going to suck.

Harry gritted his teeth. At least the instructor would be Obliviated afterward.

“\emph{Legilimens.}”

There was a pause—
\sbreak
...in a white room, windowless, featureless, sitting before a desk, facing an expressionless man in formal robes of solid black.

It was their fourth day, on a Sunday evening. When you paid this much, you got your sessions any darned time you wanted, never mind the concept of weekends.

“Hello, Mr.~Potter,” the telepath said tonelessly, having cast the full suite of privacy spells.

“Hello, Mr.~Bester,” Harry said wearily. “Let’s just get the initial shock out of the way, shall we?”

“You managed to surprise me?” the man said, now sounding slightly interested. “Well then.” He pointed his wand and stared into Harry’s eyes. “\emph{Legilimens.}”

There was a pause, and then the black-robed wizard jerked as if someone had touched him with a cattle prod.

“The Dark Lord is \emph{alive?}” he choked. His eyes were suddenly wild. “\emph{Dumbledore turns himself invisible and sneaks into girls’ dorm rooms?}”

Harry sighed and looked down at his watch. In about another three seconds...

“So,” the man said. He hadn’t quite recovered his tonelessness. “You genuinely believe you’re going to discover the secret rules of magic and become all-powerful.”

“That’s right,” Harry said evenly, still looking at his watch. “I’m \emph{that} overconfident.”

“I wonder. It seems the Sorting Hat thinks you’ll be the next Dark Lord.”

“And \emph{you} know I’m trying pretty hard \emph{not} to be, and you saw that we already had a long discussion about whether you were willing to teach me Occlumency, and in the end you decided to do it, so can we just get this over with?”

“All right,” said the man exactly six seconds later, same as last time. “Prepare yourself.” He paused, and then said, his voice rather wistful, “Though I \emph{do} wish I could remember that trick with the gold and silver.”

Harry was finding himself very disturbed by how reproducible human thoughts were when you reset people back to the same initial conditions and exposed them to the same stimuli. It was dispelling illusions that a good reductionist wasn’t supposed to have in the first place.
\sbreak
Harry was in a rather bad mood as he stomped out of his Herbology class the next Monday morning.

Hermione was seething alongside him.

The other children were still inside, a bit slow to assemble their things because they were gibbering excitedly to each other about Ravenclaw winning the year’s second Quidditch match.

It seemed that last night after dinner, a girl had flown around on a broomstick for thirty minutes and then caught some sort of giant mosquito. There were other facts about what had happened during this match, but they were irrelevant.

Harry had missed this exciting sports event due to his Occlumency lesson, and also having a life.

He had then avoided all conversations in the Ravenclaw dorm, weren’t Quieting Charms and magical trunks wonderful. He had eaten breakfast at the Gryffindor table.

But Harry couldn’t avoid Herbology, and the Ravenclaws had talked about it before class, and after class, and \emph{during class,} until Harry had looked up from the baby furcot whose diaper he was changing, and announced loudly that some of them were trying to learn about \emph{plants} and Snitches didn’t grow on anything so could they all \emph{please} shut up about Quidditch. Everyone else present had given him shocked looks, except Hermione, who’d looked like she wanted to applaud, and Professor Sprout, who had awarded him a point for Ravenclaw.

\emph{A} point for Ravenclaw.

\emph{One} point.

The seven idiots on their idiot brooms playing their idiot game had earned \emph{one hundred and ninety points} for Ravenclaw.

It seemed that Quidditch scores \emph{added directly onto the House points total.}

In other words, catching a golden mosquito was worth 150 House points.

Harry couldn’t even \emph{imagine} what he would have to do to earn one hundred and fifty House points.

Besides, y’know, rescuing \emph{a hundred and fifty Hufflepuffs,} or coming up with \emph{fifteen ideas as good as putting protective shells on time machines,} or inventing \emph{one thousand five hundred creative ways to kill people,} or being Hermione Granger for the \emph{entire year}.

“We should kill them,” Harry said to Hermione, who was walking beside him with an equally offended air.

“Who?” said Hermione. “The Quidditch team?”

“I was thinking of everyone involved in any way with Quidditch anywhere, but the Ravenclaw team would be a start, yes.”

Hermione’s lips were pursed disapprovingly. “You \emph{do} know that killing people is wrong, Harry?”

“Yes,” Harry said.

“Okay, just checking,” Hermione said. “Let’s get the Seeker first. I’ve read some Agatha Christie mysteries, do you know how we can get her onto a train?”

“Two students plotting murder,” said a dry voice. “How shocking.”

From around a nearby corner strolled a man in lightly spotted robes, his greasy hair falling long and unkempt about his shoulders. Deadly danger seemed to radiate out from him, filling the hallway with improperly mixed potions and accidental falls and people dying in bed of what the Aurors would rule to be natural causes.

Without thinking about it at all, Harry stepped in front of Hermione.

There was an intake of breath from behind him, and then a moment later Hermione brushed past and stepped in front of \emph{him.} “Run, Harry!” she said. “Boys shouldn’t have to be in danger.”

Severus Snape smiled mirthlessly. “Amusing. I request a moment of your time, Potter, if you can tear yourself away from your flirtations with Miss Granger.”

Suddenly there was a very worried look on Hermione’s face. She turned to Harry and opened her mouth, then paused, looking distressed.

“Oh, don’t worry, Miss Granger,” said Severus’s silky voice. “I promise to return your beau unmaimed.” His smile vanished. “Now Potter and I are about to go off and have a private conversation, just by ourselves. I hope it is clear that you are not invited, but just in case, consider that an order from a Hogwarts professor. I’m sure a good little girl like you won’t disobey.”

And Severus turned and walked back around the corner. “Coming, Potter?” his voice said.

“Um,” Harry said to Hermione. “Can I just sort of go off and follow him and let \emph{you} work out what I should say to make sure you’re not all worried and offended?”

“No,” Hermione said, her voice trembling.

Severus’s laughter echoed from around the corner.

Harry bowed his head. “Sorry,” he said lowly, “really,” and he went off after the Potions Master.
\sbreak
“So,” Harry said. There were no other sounds now but two pairs of legs, the long and the short, padding across a random stone corridor. The Potions Master was striding quickly but not too fast for Harry to keep up, and insofar as Harry could apply the concept of directionality to Hogwarts, they were moving away from the frequented areas. “What’s this about?”

“I don’t suppose you could explain,” Severus said dryly, “why the two of you were plotting to murder Cho Chang?”

“I don’t suppose \emph{you} could explain,” Harry said dryly, “in your capacity as an official of the Hogwarts school system, why catching a golden mosquito is deemed an academic accomplishment worthy of a hundred and fifty House points?”

A smile crossed Severus’s lips. “Dear me, and I thought you were supposed to be perceptive. Are you truly so incapable of understanding your classmates, Potter, or do you dislike them too much to try? If Quidditch scores did not count toward the House Cup then none of them would care about House points at all. It would merely be an obscure contest for students like you and Miss Granger.”

It was a shockingly good answer.

And that shock brought Harry’s mind fully awake.

In retrospect it shouldn’t have been surprising that Severus understood his students, understood them very well indeed.

He had been reading their minds.

And...

...the book said that a successful Legilimens was extremely rare, rarer than a perfect Occlumens, because almost no one had enough mental discipline.

\emph{Mental discipline?}

Harry had collected stories about a man who routinely lost his temper in class and blew up at young children.

...but this same man, when Harry had spoken of the Dark Lord still being alive, had responded instantly and perfectly—reacting in precisely the way that someone completely ignorant would react.

The man stalked about Hogwarts with the air of an assassin, radiating danger...

...which was exactly \emph{not} what a real assassin should do. Real assassins should look like meek little accountants until they killed you.

He was the Head of House for proud and aristocratic Slytherin, and he wore a robe with spotted stains from bits of potions and ingredients, which two minutes of magic could have removed.

Harry noticed that he was confused.

And his threat estimate of the \emph{Head of House Slytherin} shot up astronomically.

Dumbledore had seemed to think Severus was his, and there’d been nothing to contradict that; the Potions Master had been “scary but not abusive”, as promised. So, Harry had reasoned earlier, this was Fellowship business. If Severus had been planning harm, surely he wouldn’t have come to get Harry in front of Hermione, a witness, when he could have simply waited for some time when Harry was alone...

Harry quietly bit his lip.

“I once knew a boy who truly adored Quidditch,” said Severus Snape. “He was an utter pillock. Just as you and I would expect, we two.”

“What \emph{is} this?” Harry said slowly.

“Patience, Potter.”

Severus turned his head, and then glided with his assassin’s bearing into a nearby opening in the corridor walls, a smaller and narrower hallway leading off.

Harry followed him, wondering if it would be smarter to simply run away.

They turned and made another turn, and came to a dead end, a simple blank wall. If Hogwarts had actually been built, rather than conjured or summoned or birthed or whatever, Harry would have had some sharp words for the architect about paying people to build hallways that didn’t go anywhere.

“\emph{Quietus,}” said Severus, and a few other things as well.

Harry leaned back, folded his arms across his chest, and watched Severus’s face.

“Looking me in the eyes, Potter?” said Severus Snape. “Your Occlumency lessons cannot have progressed far enough for you to block Legilimency. But then perhaps they have progressed far enough for you to detect it. Since I cannot know otherwise, I will not risk trying.” The man smiled thinly. “And the same will hold for Dumbledore, I think. Which is why we are \emph{now} having this little talk.”

Harry’s eyes widened involuntarily.

“To begin with,” Severus said, eyes glittering, “I should like you to promise not to speak of our conversations to \emph{anyone}. So far as the school is concerned, we are discussing your Potions homework. Whether or not they believe that is unimportant. So far as Dumbledore and McGonagall are concerned, I am violating Draco Malfoy’s confidences in me, and neither of us think it proper to speak further of the particulars.”

Harry’s brain tried to calculate the ramifications and implications of this and ran out of swap space.

“Well?” said the Potions Master.

“All right,” Harry said slowly. It was hard to see how having a conversation and being unable to tell anyone could be more constraining than \emph{not} having it, in which case you \emph{also} couldn’t tell anyone the contents. “I promise.”

Severus was watching Harry intently. “You said once in the Headmaster’s office that you would not tolerate bullying or abuse. And so I wonder, Harry Potter. Just how much do you resemble your father?”

“Unless we’re talking about Michael Verres-Evans,” Harry said, “the answer is that I know very little about James Potter.”

Severus nodded, as though to himself. “There is a fifth-year Slytherin. A boy named Lesath Lestrange. He is being bullied by Gryffindors. I am...\ constrained, in my ability to deal with such situations. \emph{You} could help him, perhaps. If you wished. I am not asking you for a favor, and will not owe you one. It is simply an opportunity to do as you will.”

Harry stared at Severus, thinking.

“Wondering if it’s a trap?” said Severus, a faint smile crossing his lips. “It is not. It \emph{is} a test. Call it curiosity on my part. But Lesath’s troubles are real, as are my own difficulties in intervening.”

That was the trouble with other people knowing you were a good guy. Even if you knew they knew, you still couldn’t ignore the bait.

And if his father had protected students from bullies too...\ it didn’t matter if Harry knew why Severus had told him. It still made him feel warm inside, and proud, and made it impossible to walk away.

“Fine,” Harry said. “Tell me about Lesath. Why is he being bullied?”

Severus’s face lost the faint smile. “You think there are \emph{reasons}, Potter?”

“Perhaps not,” Harry said quietly. “But the thought had occurred to me that he might have pushed some unimportant mudblood girl down the stairs.”

“Lesath Lestrange,” Severus said, his voice now cold, “is the son of Bellatrix Black, the most fanatic and evil servant of the Dark Lord. Lesath is the acknowledged bastard of Rastaban Lestrange. Shortly after the Dark Lord’s death, Bellatrix and Rastaban and Rastaban’s brother Rodolphus were captured while torturing Alice and Frank Longbottom. All three are in Azkaban for life. The Longbottoms were driven insane by repeated Cruciatus and remain in St.~Mungo’s incurable ward. Is any of that a good reason to bully him, Potter?”

“It is no reason at all,” Harry said, still quietly. “And Lesath himself has done no wrong that you know?”

The faint smile crossed Severus’s lips again. “He is no more a saint than anyone else. But he has pushed no mudblood girls down the stairs, not that I ever heard.”

“Or saw in his mind,” said Harry.

Severus’s expression was chill. “I did not invade his privacy, Potter. I looked within the Gryffindors, rather. He is simply a convenient target for their little satisfactions.”

A cold wash of anger ran down Harry’s spine, and he had to remind himself that Severus might not be a trustworthy source of information.

“And you think,” Harry said, “that an intervention by Harry Potter, the Boy-Who-Lived, might prove effective.”

“Indeed,” said Severus Snape, and told Harry when and where the Gryffindors were planning their next little game.
\sbreak
There is a main hallway running through the middle of Hogwarts’s second floor on the north-south axis, and near the center of this hallway there is an opening into a short corridor which goes a dozen paces back before turning at a right angle, making an L-shape, and then goes a dozen paces more before it ends at a bright, wide window, looking out from three stories above upon the light drizzle falling over the east grounds of Hogwarts. Standing by the window you can hear nothing of the main hallway, and no one in the hallway would hear what went on by the window. If you think there is anything odd about this, you haven’t been in Hogwarts very long.

Four boys in red-trimmed robes are laughing, and a boy in green-trimmed robes is screaming and grabbing frantically onto the edges of the opened window with his hands, as the four boys make as though to push him out. It’s just a joke, of course, and besides, a fall from that height wouldn’t kill a wizard. All good fun. If you think there is anything odd about this—

“\emph{What are you doing?}” says a sixth boy’s voice.

The four boys in red-trimmed robes spin around with sudden starts, and the boy in green-trimmed robes frantically pushes himself away from the window and falls to the floor, face streaked with tears.

“Oh,” says the most handsome of the boys in red-trimmed robes, sounding relieved, “it’s \emph{you.} Hey, Lessy, you know who this is?”

There isn’t any answer from the boy on the floor, who’s trying to get his sniffling under control, and the boy in the red-trimmed robes draws back his leg for a kick—

“\emph{Stop it!}” shouts the sixth boy.

The boy in the red-trimmed robes wobbles as he aborts the kick. “Um,” he says, “do \emph{you} know who this is?”

The sixth boy’s breathing sounds strange. “Lesath Lestrange,” he says, his breath coming in short pants, “and \emph{he} didn’t do anything to my parents, he was five years old.”
\sbreak
Neville Longbottom stared at the four huge fifth-year bullies in front of him, trying very hard to control his trembling.

He should have just told Harry Potter no.

“Why are \emph{you} defending him?” said the handsome one, slowly, sounding puzzled with the first hints of offense. “He’s a \emph{Slytherin.} And a \emph{Lestrange.}”

“He’s a boy who lost his parents,” said Neville Longbottom. “I know how that is.” He didn’t know where the words had come from. It sounded too cool, like something Harry Potter would say.

The trembling went on, though.

“\emph{Who} do you think you \emph{are?}” said the handsome one, starting to sound angry.

\emph{I am Neville, the last scion of the Noble and Most Ancient House of Longbottom—}

Neville couldn’t say it.

“I think he’s a \emph{traitor},” said one of the other Gryffindors, and there was a sudden sinking sensation in Neville’s stomach.

He’d known it, he’d just known it. Harry Potter had been wrong after all. Bullies wouldn’t stop only because Neville Longbottom told them to stop.

The handsome one took a step forward, and the three others followed.

“So that’s how it is for you,” Neville said, amazed at how steady his voice was. “It doesn’t matter to you if it’s Lesath Lestrange or Neville Longbottom.”

Lesath Lestrange let out a sudden gasp, from where he was lying on the floor.

“Evil is evil,” snarled the same boy who’d spoken before, “and if you’re friends with evil, you’re evil too.”

The four took another step forward.

Lesath rose, wobbling, to his feet. His face was gray, and he took a few steps forward, and leaned against the wall, and didn’t say anything. His eyes were fixed on the turn in the hallway, the way out.

“Friends,” Neville said. Now his voice was going up a bit in pitch. “Yes, I have friends. One of them is the Boy-Who-Lived.”

A couple of the Gryffindors looked suddenly worried. The handsome one didn’t flinch. “Harry Potter isn’t here,” he said, his voice hard, “and if he was, I don’t think he’d like to see a Longbottom defending a Lestrange.”

And the Gryffindors took another long step forward, and behind them, Lesath crept along the wall, waiting for his chance.

Neville swallowed, and raised his right hand with his thumb and forefinger pressed together.

He shut his eyes, because Harry Potter had made him promise not to peek.

If this didn’t work, he was never trusting anyone again.

His voice came out surprisingly clear, considering.

“Harry James Potter-Evans-Verres. Harry James Potter-Evans-Verres. Harry James Potter-Evans-Verres. By the debt that you owe me and the power of your true name I summon you, I open the way for you, I call upon you to manifest yourself before me.”

Neville snapped his fingers.

And then Neville opened his eyes.

Lesath Lestrange was staring at him.

The four Gryffindors were staring at him.

The handsome one started to chuckle, and that set off the other three.

“Was Harry Potter supposed to step around the corner or something?” said the handsome one. “Aw. Looks like you’ve been stood up.”

The handsome one took a menacing step forward toward Neville.

The other three followed in lockstep.

“Ahem,” said Harry Potter from behind them, leaning against the wall by the window, in the dead end of the hallway, where nobody could possibly have gotten to without being seen.

If watching people scream always felt this good, Neville could sort of understand why people became bullies.

Harry Potter stalked forward, placing himself between Lesath Lestrange and the others. He swept his icy gaze across the boys in red-trimmed robes, and then his eyes came to rest on the handsome one, the ringleader. “Mr.~Carl Sloper,” said Harry Potter. “I believe I have comprehended this situation fully. If Lesath Lestrange has ever committed a single evil himself, rather than being born to the wrong parents, the fact is not known to \emph{you.} If I am mistaken in this, Mr.~Sloper, I suggest you inform me at once.”

Neville saw the fear and awe on the other boys’ faces. He was feeling it himself. Harry had \emph{claimed} it would all be a trick, but how could it be?

“But he’s a \emph{Lestrange},” said the ringleader.

“He’s a boy who \emph{lost his parents},” Harry Potter said, his voice growing even colder.

This time all three of the other Gryffindors flinched.

“So,” said Harry Potter. “You saw that Neville didn’t want you tormenting an innocent boy on behalf of the Longbottoms. This failed to move you. If I tell you that the Boy-Who-Lived \emph{also} thinks you are in the wrong, that what you did today was a terrible mistake, does that make a difference?”

The ringleader took a step toward Harry.

The others did \emph{not} follow him.

“Carl,” one of them said, swallowing. “Maybe we should go.”

“They say you’re going to be the next Dark Lord,” the ringleader said, staring at Harry.

A grin crossed Harry Potter’s face. “They also say I’m secretly betrothed to Ginevra Weasley and there’s a prophecy about us conquering France.” The smile faded. “Since you’re determined to force the issue, Mr.~Carl Sloper, let me make things clear. \emph{Leave Lesath alone.} I will know if you don’t.”

“So Lessy snarked to you,” said the ringleader coldly.

“Sure,” said Harry Potter dryly, “and he also told me what you did today after you left Charms class, in a private secluded place where no one could see you, with a certain Hufflepuff girl wearing a white ribbon in her hair—”

The ringleader’s jaw dropped in shock.

“Eep,” said one of the other Gryffindors in a high-pitched voice, and spun on his heels and ran around the corner. His footsteps rapidly pattered away and faded.

And then there were six.

“Ah,” said Harry Potter, “there goes a slightly intelligent young man. The rest of you could stand to learn from Bertram Kirke’s example, before you get into, shall we say, trouble.”

“Are you threatening to snark on us?” said the handsome Gryffindor, his voice trying to be angry, and rather wavering. “Bad things happen to snarkers.”

The other two Gryffindors started slowly moving back.

Harry Potter started laughing. “Oh, you did not just say that. Are you \emph{really} trying to intimidate me? \emph{Me?} Now honestly, do you think you’re scarier than Peregrine Derrick, Severus Snape or for that matter You-Know-Who?”

Even the ringleader flinched at that.

Harry Potter raised his hand, fingers poised, and all three of the Gryffindors leaped backward, and one of them blurted “Don’t—!”

“See,” said Harry Potter, “this is where I snap my fingers and you become part of a hilariously amusing story that will be told with much nervous laughter at dinner tonight. But the thing is, people I trust keep telling me not to do that. Professor McGonagall told me I was taking the easy way out of everything and Professor Quirrell says I need to learn how to lose. So you remember that story where I let myself get beaten up by some older Slytherins? We could do that. You could bully me for a while and I could let you. Only you remember that part at the end where I tell my many, many friends inside this school not to do anything about it? This time we’ll skip that part. So go ahead. Bully me.”

Harry Potter stepped forward, his arms opened wide in invitation.

The three Gryffindors broke and ran, and Neville had to sidestep quickly to avoid getting run over.

There was silence, as their footsteps faded, and then more silence after that.

And then there were three.

Harry Potter drew a deep breath, then exhaled. “Whew,” he said. “How are you doing, Neville?”

Neville’s voice came out in a high-pitched squeak. “Okay, \emph{that} was really cool.”

A grin flashed across Harry Potter’s face. “\emph{You} were pretty cool too, you know.”

Neville knew that Harry Potter was just saying that, trying to make him feel good, and it still started a warm glow inside his chest.

Harry turned toward Lesath Lestrange—

“Are you okay, Lestrange?” said Neville before Harry could open his mouth.

Now there was something you didn’t expect to find yourself saying, ever.

Lesath Lestrange turned slowly, and stared at Neville, his face tight, no longer crying, tears glistening as they dried.

“You think you know how it is?” said Lesath, his voice high and shaking. “\emph{You think you know?} My parents are in \emph{Azkaban,} I try not to think about it and they always remind me, they think it’s \emph{great} that Mother is there in the cold and the dark with the Dementors sucking away her life, I wish I was like Harry Potter, at least his parents aren’t hurting, my parents are always hurting, every second of every day, I wish I was like you, at least you can see your parents sometimes, at least you know they loved you, if Mother ever loved me the Dementors will have eaten that thought by now—”

Neville’s eyes were wide with shock. He hadn’t expected this.

Lesath turned to Harry Potter, whose eyes were full of horror.

Lesath flung himself on the floor in front of Harry Potter, touched his forehead to the ground, and whispered, “Help me, Lord.”

There was an awful silence. Neville couldn’t think of a single thing to say, and from the naked shock on Harry’s face, he couldn’t think of anything either.

“They say you can do anything, please, please my Lord, get my parents out of Azkaban, I’ll be your loyal servant forever, my life will be yours and my death as well, only please—”

“Lesath,” Harry said, his voice breaking, “Lesath, I can’t, I can’t really do things like that, it’s all just stupid tricks.”

“It’s \emph{not!}” said Lesath, his voice high and desperate. “I \emph{saw} it, the stories are true, you \emph{can!}”

Harry swallowed. “Lesath, I set the whole thing up with Neville, we planned it all out in advance, ask him!”

They had, though Harry hadn’t said \emph{how} he was going to do any of it...

When Lesath looked up from the floor his face was ghastly, and his voice came out in a shriek that hurt Neville’s ears. “\emph{You son of a mudblood! You could get her out, you just won’t! I got down on my knees and begged you and you still won’t help! I should have known, you’re the Boy-Who-Lived, you think she belongs there!}”

“I \emph{can’t!}” Harry said, his voice as desperate as Lesath’s. “It’s not a question of what I want, I don’t have the \emph{power!}”

Lesath rose to his feet, and spat on the floor in front of Harry, and then turned and walked away. When he was around the corner the sound of his feet sped up, and as they faded Neville thought he heard a single sob.

And then there were two.

Neville looked at Harry.

Harry looked at Neville.

“Wow,” Neville said quietly. “He didn’t seem very grateful for being rescued.”

“He thought I could help him,” Harry said, his voice hoarse. “He had hope for the first time in years.”

Neville swallowed, and said it. “I’m sorry.”

“Wha?” said Harry, sounding totally confused.

“I wasn’t grateful when you helped me—”

“Every single thing you said before was completely right,” said the Boy-Who-Lived.

“No,” Neville said, “it wasn’t.”

They simultaneously gave brief sad smiles, each condescending to the other.

“I know this wasn’t real,” said Neville, “I know I couldn’t have done anything if you hadn’t been here, but thanks for letting me pretend.”

“Give me a break,” said Harry.

Harry had turned from Neville, and was staring out the window at the gloomy clouds.

A completely ridiculous thought came to Neville. “Are you feeling guilty because you can’t get Lesath’s parents out of Azkaban?”

“No,” said Harry.

A few seconds went by.

“Yes,” said Harry.

“You’re silly,” said Neville.

“I am aware of this,” said Harry.

“Do you have to do literally \emph{anything} anyone asks you?”

The Boy-Who-Lived turned back and looked at Neville again. “\emph{Do?} No. Feel guilty about not doing? Yes.”

Neville was having trouble finding words. “Once the Dark Lord died, Bellatrix Black was literally the most evil person in the entire world and that was \emph{before} she went to Azkaban. She tortured my mother and father into insanity because she wanted to find out what happened to the Dark Lord—”

“I know,” Harry said quietly. “I get that, but—”

“No! You \emph{don’t!} She had a \emph{reason} for doing that, and my parents were both Aurors! It’s not even \emph{close} to the worst thing she’s ever done!” Neville’s voice was shaking.

“Even so,” said the Boy-Who-Lived, his eyes distant as they stared off into somewhere else, some other place that Neville couldn’t imagine. “There might be some incredibly clever solution that makes it possible to save everyone and let them all live happily ever after, and if only I was smart enough I would have thought of it by now—”

“You have problems,” said Neville. “You think you ought to be what Lesath Lestrange thinks you are.”

“Yeah,” said the Boy-Who-Lived, “that pretty much nails it. Every time someone cries out in prayer and I can’t answer, I feel guilty about not being God.”

Neville didn’t quite understand that, but... “That doesn’t sound good.”

Harry sighed. “I understand that I have a problem, and I know what I need to do to solve it, all right? I’m working on it.”
\sbreak
Harry watched Neville leave.

Of course Harry hadn’t said what the solution was.

The solution, obviously, was to hurry up and become God.

Neville’s footsteps moved off, and soon could no longer be heard.

And then there was one.

“Ahem,” said Severus Snape’s voice from directly behind him.

Harry let out a small scream and instantly hated himself.

Slowly, Harry turned around.

The tall greasy man in the spotted robes was leaning against the wall in the same position Harry had occupied.

“A fine invisibility cloak, Potter,” drawled the Potions Master. “Much is explained.”

Oh, bloody crap.

“And perhaps I have been in Dumbledore’s company too long,” said Severus, “but I cannot help but wonder if that is \emph{the} Cloak of Invisibility.”

Harry immediately turned into someone who’d never heard of the Cloak of Invisibility and who was \emph{exactly} as smart as Harry thought Severus thought Harry was.

“Oh, possibly,” said Harry. “I trust you realize the implications, if it is?”

Severus’s voice was condescending. “You have no idea what I’m talking about, do you, Potter? A rather clumsy try at fishing.”

(Professor Quirrell had remarked over their lunch that Harry really needed to conceal his state of mind better than putting on a blank face when someone discussed a dangerous topic, and had explained about one-level deceptions, two-level deceptions, and so on. So either Severus \emph{was} in fact modeling Harry as a one-level player, which made Severus himself two-level, and Harry’s three-level move had been successful; or Severus was a four-level player and wanted Harry to \emph{think} the deception had been successful. Harry, smiling, had asked Professor Quirrell what level \emph{he} played at, and Professor Quirrell, also smiling, had responded, \emph{One level higher than you}.)

“So you were watching this whole time,” said Harry. “Disillusionment, I think it’s called.”

A thin smile. “It would have been foolish of me to take the slightest risk that you came to harm.”

“And you wanted to see the results of your test firsthand,” said Harry. “So. Am I like my father?”

A strange sad expression came over the man, one that looked foreign to his face. “I should sooner say, Harry Potter, that you resemble—”

Severus stopped short.

He stared at Harry.

“Lestrange called you a son of a mudblood,” Severus said slowly. “It didn’t seem to bother you much.”

Harry furrowed his eyebrows. “Not under those circumstances, no.”

“You’d just helped him,” Severus said. His eyes were intent on Harry. “And he threw it back in your face. Surely that isn’t something you’d just forgive?”

“He’d just been through a pretty harrowing experience,” Harry said. “And I don’t think being rescued by first-years helped his pride much, either.”

“I suppose it was easy enough to forgive,” Severus said, and his voice was odd, “since Lestrange means nothing to you. Just some strange Slytherin. If it was a friend, perhaps, you would have felt far more injured by what he said.”

“If he were a friend,” Harry said, “all the more reason to forgive him.”

There was a long silence. Harry felt, and he couldn’t have said why or from where, that the air was filling up with a dreadful tension, like water rising, and rising, and rising.

Then Severus smiled, looking suddenly relaxed once more, and all the tension vanished.

“You are a very forgiving person,” Severus said, still smiling. “I suppose your stepfather, Michael Verres-Evans, was the one who taught it to you.”

“More like Dad’s science fiction and fantasy collection,” said Harry. “Sort of my fifth parent, really. I’ve lived the lives of all the characters in all my books, and all their mighty wisdom thunders in my head. Somewhere in there was someone like Lesath, I expect, though I couldn’t say who. It wasn’t hard to put myself in his shoes. And it was my books that told me what to do about it, too. The good guys forgive.”

Severus gave a light, amused laugh. “I’m afraid I wouldn’t know much about what good people do.”

Harry looked at him. That was kind of sad, actually. “I’ll lend you some novels with good people in them, if you like.”

“I should like to ask your advice about something,” Severus said, his voice casual. “I know of another fifth-year Slytherin who was being bullied by Gryffindors. He was wooing a beautiful Muggleborn girl, who came across him being bullied, and tried to rescue him. And he called her a mudblood, and that was the end for them. He apologized, many times, but she never forgave him. Have you any thoughts for what he could have said or done, to win from her the forgiveness you gave Lestrange?”

“Erm,” Harry said, “based on only that information, I’m not sure \emph{he} was the main one who had a problem. I’d have told him not to date someone that incapable of forgiveness. Suppose they’d gotten married, can you imagine life in that household?”

There was a pause.

“Oh, but she \emph{could} forgive,” Severus said with amusement in his voice. “Why, afterward, she went off and became the girlfriend of the bully. Tell me, why would she forgive the bully, and not the bullied?”

Harry shrugged. “At a wild guess, because the bully had hurt someone \emph{else} very badly, and the bullied had hurt \emph{her} just a little, and to her that just felt far more unforgivable somehow. Or, not to put too fine a point on it, was the bully handsome? Or for that matter, rich?”

There was another pause.

“Yes to both,” said Severus.

“And there you have it,” said Harry. “Not that I’ve ever been through high school myself, but my books give me to understand that there’s a certain kind of teenage girl who’ll be outraged by a single insult if the boy is plain or poor, yet who can somehow find room in her heart to forgive a rich and handsome boy his bullying. She was shallow, in other words. Tell whoever it was that she wasn’t worthy of him and he needs to get over it and move on and next time date girls who are deep instead of pretty.”

Severus stared at Harry in silence, his eyes glittering. The smile had faded, and though Severus’s face twitched, it did not return.

Harry was starting to feel a bit nervous. “Um, not that I’ve got any experience in the area myself, obviously, but I think that’s what a wise adviser from my books would say.”

There was more silence and more glittering.

It was probably a good time to change the subject.

“So,” Harry said. “Did I pass your test, whatever it was?”

“I think,” Severus said, “that there should be no more conversations between us, Potter, and you would be exceedingly wise never to speak of this one.”

Harry blinked. “Would you mind telling me what I did wrong?”

“You offended me,” said Severus. “And I no longer trust your cunning.”

Harry stared at Severus, taken rather aback.

“But you have given me well-meant advice,” said Severus Snape, “and so I will give you true advice in return.” His voice was almost perfectly steady. Like a string stretched almost perfectly horizontal, despite the massive weight hanging from its middle, by a million tons of tension pulling at either end. “You almost died today, Potter. In the future, never share your wisdom with anyone unless you know exactly what you are both talking about.”

Harry’s mind finally made the connection.

“\emph{You} were that—”

Harry’s mouth snapped shut as the \emph{almost died} part sank in, two seconds too late.

“Yes,” said Severus, “I was.”

And the terrible tension flooded back into the room like water pressurized at the bottom of the ocean.

Harry couldn’t breathe.

\emph{Lose. Now.}

“I didn’t know,” Harry whispered. “I’m s—”

“No,” said Severus. Just that one word.

Harry stood there in silence, his mind frantically searching for options. Severus stood between him and the window, which was a real pity, because a fall from that height wouldn’t kill a wizard.

“Your books betrayed you, Potter,” said Severus, still in that voice stretched tight by a million tons of pull. “They did not tell you the one thing you needed to know. You cannot learn from stories what it is like to lose the one you love. That is something you could never understand without feeling it yourself.”

“My father,” Harry whispered. It was his best guess, the one thing that might save him. “My father tried to protect you from the bullies.”

A ghastly smile stretched across Severus’s face, and the man moved toward Harry.

And past him.

“Goodbye, Potter,” said Severus, not looking back on his way out. “We shall have little to say to each other from today on.”

And at the corner, the man stopped, and without turning, spoke one final time.

“Your father was the bully,” said Severus Snape, “and what your mother saw in him was something I never did understand until this day.”

He left.

Harry turned and walked toward the window. His shaking hands went onto the ledge.

\emph{Never give anyone wise advice unless you know exactly what you’re both talking about. Got it.}

Harry stared out at the clouds and the light drizzle for a while. The window looked out on the east grounds, and it was afternoon, so if the sun was visible through the clouds at all, Harry couldn’t see it.

His hands had stopped shaking, but there was a tight feeling in Harry’s chest, like it was being compressed by metal bands.

So his father had been a bully.

And his mother had been shallow.

Maybe they’d grown up later. Good people like Professor McGonagall did seem to think the world of them, and it might not be \emph{only} because they were heroic martyrs.

Of course, that was scant consolation when you were eleven and about to turn into a teenager, and wondering what sort of teenager you might become.

So very terrible.

So very sad.

Such an awful life Harry led.

Learning that his genetic parents hadn’t been perfect, why, he ought to spend awhile moping about that, feeling sorry for himself.

Maybe he could complain to Lesath Lestrange.

Harry had read about Dementors. Cold and darkness surrounded them, and fear, they sucked away all your happy thoughts and in that absence all your worst memories rose to the surface.

He could imagine himself in Lesath’s shoes, knowing that his parents were in Azkaban for life, that place from which no one had ever escaped.

And Lesath would be imagining himself in his mother’s place, in the cold and the darkness and the fear, alone with all of her worst memories, even in her dreams, every second of every day.

For an instant Harry imagined his own Mum and Dad in Azkaban with the Dementors sucking out their life, draining away the happy memories of their love for him. Just for an instant, before his imagination blew a fuse and called an emergency shutdown and told him never to imagine that again.

Was it right to do that to anyone, even the second most evil person in the world?

\emph{No,} said the wisdom of Harry’s books, \emph{not if there’s any other way, any other way at all.}

And unless the wizarding justice system was as perfect as their prisons—and that sounded rather improbable, all things considered—some\-where in Azkaban was a person who was entirely innocent, and probably more than one.

There was a burning sensation in Harry’s throat, and moisture gathering in his eyes, and he wanted to teleport all of Azkaban’s prisoners to safety and call down fire from the sky and blast that terrible place down to bedrock. But he couldn’t, because he wasn’t God.

And Harry remembered what Professor Quirrell had said beneath the starlight: \emph{Sometimes, when this flawed world seems unusually hateful, I wonder whether there might be some other place, far away, where I should have been... But the stars are so very, very far away... And I wonder what I would dream about, if I slept for a long, long time.}

Right now this flawed world seemed unusually hateful.

And Harry couldn’t understand Professor Quirrell’s words, it might have been an alien that had spoken, or an Artificial Intelligence, something built along such different lines from Harry that his brain couldn’t be forced to operate in that mode.

You couldn’t leave your home planet while it still contained a place like Azkaban.

You had to stay and fight.



