\partchapter{The Stanford Prison Experiment}{III}
\lettrine{T}{he} corpse of a woman opened her eyes, and the dull sunken orbs gazed out at nothing.

“Mad,” Bellatrix muttered in a cracked voice, “It seems that little Bella is going mad...”

Professor Quirrell had instructed Harry, calmly and precisely, how he was to act in Bellatrix’s presence; how to form the pretense he would maintain in his mind.

\emph{You found it expedient, or perhaps just amusing, to make Bellatrix fall in love with you, to bind her to your service.}

That love would have persisted through Azkaban, Professor Quirrell had said, because to Bellatrix it would not be a happy thought.

\emph{She loves you utterly, completely, with her whole being. You do not return her love, but consider her useful. She knows this.}

\emph{She was the deadliest weapon you possessed, and you called her your dear Bella.}

Harry remembered it from the night the Dark Lord killed his parents: the cold amusement, the contemptuous laughter, that high-pitched voice of deathly hate. It didn’t seem at all difficult to guess what the Dark Lord would say.

“I hope you are \emph{not} mad, Bella dear,” said the chill whisper. “Mad is not useful.”

Bellatrix’s eyes flickered, tried to focus on empty air.

“My... Lord... I went where you said to await you, but you did not come... I looked for you but I could not find you...\ you are alive...” All her words came out in a low mutter, if there was emotion in it, Harry could not tell.

“\emph{Sshow her your face,}” hissed the snake at Harry’s feet.

Harry cast back the hood of the Cloak of Invisibility.

The part of him that Harry had placed in control of his facial expressions looked at Bella without the slightest trace of pity, only cool, calm interest. (While in his core, Harry thought, \emph{I will save you, I will save you no matter what...})

“The scar...” muttered Bellatrix. “That child...”

“So they all still think,” said Harry’s voice, and gave a thin little chuckle. “You looked for me in the wrong place, Bella dear.”

(Harry had asked why Professor Quirrell couldn’t be the one to play the part of the Dark Lord, and Professor Quirrell had pointed out that there was no plausible reason for \emph{him} to be possessed by the shade of He-Who-Must-Not-Be-Named.)

Bellatrix’s eyes remained fixed on Harry, she said no word.

\emph{“Ssay ssomething in Parsseltongue,”} hissed the snake.

Harry’s face turned to the snake, to make it clear that he was addressing it, and hissed, “\emph{One two three four five ssix sseven eight nine ten.}”

There was a pause.

“Those who do not fear the darkness...” murmured Bellatrix.

The snake hissed, “\emph{Will be conssumed by it.}”

“Will be consumed by it,” whispered the chill voice. Harry didn’t particularly want to think about how Professor Quirrell had gotten that password. His brain, which thought about it anyway, suggested that it had probably involved a Death Eater, a quiet isolated place, and some lead-pipe Legilimency.

“Your wand,” murmured Bellatrix, “I hid it in the graveyard, my lord, before I left...\ under the tombstone to the right of your father’s grave...\ will you kill me, now, if that was all you wished of me... I think I must have always wanted you to be the one to kill me...\ but I can’t remember now, it must have been a happy thought...”

Harry’s heart wrenched inside him, it was unbearable, and—and he couldn’t cry, couldn’t let his Patronus fade—

Harry’s face showed a flicker of annoyance, and his voice was sharp as it said, “Enough foolishness. You’re to come with me, Bella dear, unless you prefer the company of the Dementors.”

Bellatrix’s face twitched in brief puzzlement, the shrunken limbs did not stir.

“\emph{You’ll need to float her out,}” Harry hissed to the snake. “\emph{Sshe can no longer think of esscaping.}”

“\emph{Yess,}” hissed the snake, “\emph{but do not underesstimate her, sshe wass the deadliesst of warriorss.}” The green head dipped in warning. “\emph{One would be wisse to fear me, boy, even were I sstarved and nine-tenthss dead; be wary of her, allow no ssingle flaw in your pretensse.}”

The green snake smoothly glided out of the door.

And shortly after, a man with sallow skin and a fearful expression on his bearded face cringed into the room with his wand in hand.

“My Lord?” the servant said falteringly.

“Do as you were instructed,” the Dark Lord whispered in that chill voice, sounding even more terrible coming from a child’s body. “And do not let your Patronus falter. Remember, if I do not return there will be no reward for you, and it will be long before your family is allowed to die.”

Having spoken those dreadful words, the Dark Lord pulled his invisibility cloak over his head, and disappeared.

The cringing servant opened the door to Bellatrix’s cage, and pulled a tiny needle from his robes with which he poked the human skeleton. The single drop of red blood produced was soon absorbed into a small doll, which was laid upon the floor, and the servant began to chant in a whisper.

Soon another living skeleton lay upon the floor, motionless. Afterward the servant seemed to hesitate for a moment, until from the empty air hissed an impatient command. Then the servant pointed his wand at Bellatrix and spoke a word, and the living skeleton lying on the bed was naked, and the skeleton lying on the floor was clothed in her faded dress.

The servant tore a small strip of cloth from the dress, as it lay upon the seeming corpse; and from his own robes, the fearful man then produced an empty glass flask with small traces of golden fluid clinging to its inside. This flask was concealed in a corner, the strip of skirt laid over it, the leached cloth nearly blending with the gray metal wall.

Another wave of the servant’s wand floated the human skeleton lying on the bed into the air, and in almost the same motion clothed her in new black robes. An ordinary-looking bottle of chocolate milk was put into her hand, and a chill whisper ordered Bellatrix to grasp the bottle and begin drinking it, which she did, her face still looking only puzzled.

Then the servant turned Bellatrix invisible, and turned himself invisible, and they left. The door closed behind them all and clicked as it locked, plunging the corridor into darkness once more, unchanged but for a small flask concealed in the corner of one cell, and a fresh corpse lying upon its floor.
\sbreak
Earlier, in the deserted shop, Professor Quirrell had told Harry that they were going to commit the perfect crime.

Harry had unthinkingly started to repeat back the standard proverb that there was no such thing as a perfect crime, before he actually thought about it for two-thirds of a second, remembered a wiser proverb, and shut his mouth in midsentence.

\emph{What do you think you know, and how do you think you know it?}

If you \emph{did} commit the perfect crime, nobody would ever find out—so how could anyone possibly \emph{know} that there weren’t perfect crimes?

And as soon as you looked at it that way, you realized that perfect crimes probably got committed \emph{all the time}, and the coroner marked it down as death by natural causes, or the newspaper reported that the shop had never been very profitable and had finally gone out of business...

When Bellatrix Black’s corpse was found dead in her cell the next morning, there within the prison of Azkaban from which (everyone knew) no one had ever escaped, nobody bothered doing an autopsy. Nobody thought twice about it. They just locked up the corridor and left, and the \emph{Daily Prophet} reported it in the obituary column the next day...

...that was the perfect crime which Professor Quirrell had planned.

And it wasn’t Professor Quirrell who screwed it up.

