\partchapter{Shut Up and Do The Impossible}{II}

\lettrine{S}{omething} like a fugue state had come over Harry’s mind. The absolute state had partially worn off him, partially stayed with him. Elements of his mind were numb, maybe deliberately numbed by some part that was smart enough to predict what would happen otherwise. What he’d just done—

The thought was shut off, making space for an awareness of other things.

Harry was standing in the middle of a haphazard graveyard, tombstones scattered without order.

By moonlight and starlight, it could be seen that black robes littered the ground, surrounded by textures that didn’t match the surrounding graveyard earth, wetness tinged red in the moonlight. Some heads had come loose from the surrounding hoods of the robes, revealing hair that was long or short, dark or bright, which was all that could be seen beneath the moon. The silver masks stayed on, making all the hair originate in skulls instead of human faces—

The thought was shut off, making space for awareness of other things.

A girl in a red-trimmed Hogwarts uniform slept upon an altar. Near the altar, Harry’s things lay in a heap.

Upon the ground lay a too-tall pale man of inhuman face, blood pouring from the stumps of his wrists.

\emph{As soon as the Dark Lord Voldemort awakens, he will destroy everything you love. Dumbledore is no longer there to stop him.}

\emph{He cannot be imprisoned, for he can abandon his body at any time.}

\emph{He cannot be killed permanently, not without destroying more than a hundred horcruxes, one of which is the Pioneer plaque.}

\emph{Materials: One wand, you are allowed to point it and speak this time.}

\emph{You have five minutes.}

\emph{Solve.}

Harry stumbled toward the altar, knelt at its side, and picked up his pouch.

He walked toward where Voldemort lay.

The sense of apprehension had diminished, after Voldemort had been hexed unconscious. Now, as Harry approached, it rose to a terrifying height, flaring also into pain in his scar.

Harry ignored the inner shriek. That had been the last memory of Tom Riddle seared into Harry’s brain, the last cognitive pattern to be transferred over into the infant baby before Tom Riddle had exploded: a sense of mounting horror and dismay associated with the resonance that had spun out of control. Harry knew the meaning of it now, that sense of apprehension, and that made it easier to disregard. He’d guessed that the effect of the resonance mostly hit the caster, with power proportional to the caster’s power, and the bet had paid off.

Harry looked upon Voldemort’s body, and breathed deeply—through his mouth, because coppery smells Harry was not thinking about were coming in through his nose.

Harry knelt by Voldemort’s side, took out his medical kit from his pouch, and placed a self-tightening tourniquet around the body’s left wrist, then another tourniquet about the right.

It felt \emph{wrong,} showing Voldemort that concern. Some part of Harry was aware, in the back of his mind, that some number of people had just had something extremely bad happen to them. What would have been balance, what would have been justice, was if Voldemort had suffered the same fate without an instant’s more hesitation. What Harry was doing now felt like Batman showing more concern for the Joker than for the Joker’s victims; it felt like a comic book where the writers wrung their hands endlessly about the morality of killing the Big Named Villains while innocents went on dying in the background. To show more solicitousness for the head villain than his minions, to pay \emph{more attention} to his fate than the fates of his lower-status followers, was a flaw in human nature.

So it felt wrong when Harry rose up from beside the body, the tourniquets having tightened upon Voldemort’s wrists; it felt like Harry was doing something ethically monstrous.

Even though any sane strategic thinking said that Voldemort’s body \emph{must not} die. The soul he’d created for himself had to be anchored in this brain, it mustn’t be allowed to float free.

Harry stepped back, back from Voldemort’s unconscious body, breathing deeply through his mouth. He went to the pile of his things, to put on his robes and other items, starting with placing the Time-Turner around his throat once more, readying his own escape and return if that was required…

More than a hundred horcruxes.

That had been insane, there wasn’t any other word for it, a sign of Voldemort’s damaged thinking about death. A Muggle security expert would have called it fence-post security, like building a fence-post over a hundred metres high in the middle of the desert. Only a very obliging attacker would try to climb the fence-post. Anyone sensible would just walk around the fence-post, and making the fence-post even higher wouldn’t stop that.

Once you forgot to be scared of how impossible the problem was supposed to be, it wasn’t even difficult, not by comparison to the last one.

Neville’s parents, for example, had been Crucioed into permanent insanity. Two hundred advanced horcruxes wouldn’t prevent that insanity, they would all just echo the same damaged mind.

It would be an ethically justified use of the Cruciatus Curse, if that were the only way to stop Voldemort permanently. It would be justice, balance, it would show that the Joker’s life wasn’t worth more than his meanest henchman…

All Harry needed to do was cast the Patronus Charm, send it to…Alastor Moody?…and tell him to come here. Well, no, it was a pretty good guess the Patronus Charm wouldn’t work if it was cast with \emph{that} intent. Maybe just resolve to tell Moody that, and use his Time-Turner once he was out of range of Voldemort’s wards.

And then Voldemort could be Crucioed into permanent insanity.

It wasn’t even the least merciful fate. That would have been throwing Voldemort’s wand into the pit at Azkaban, if the wand stayed connected to Voldemort’s life and magic no matter where his ghost tried to flee.

Harry turned to face where Voldemort lay. He walked forward, and continued to control his breathing, ignoring the burning feeling in his throat. Some part of him knew that Voldemort was \emph{also} Professor Quirrell, even though his body now was different. Even though the shift of personality had been perfect and that meant that Professor Quirrell had been just another mask…

Though Voldemort hadn’t planned to kill Harry painfully. Hadn’t thought to strike Harry with his followers’ Cruciatus, when Harry was being annoying before. That meant something, when your opponent was Voldemort. Maybe he’d had some remaining shred of fellow-feeling for the other Tom Riddle after all.

…it would be wrong to take that into account.

Wouldn’t it?

Harry looked back up at the stars. Here below the atmosphere the stars twinkled, they were embedded in the false dome of the night sky, stretched out across the wash of the Milky Way that glowed like a long ribbon, as if they were all close enough that you could fly up to them on a broomstick and touch them.

What would they want him to do now at this juncture, the children’s children’s children?

The answer to that also felt obvious, if it wasn’t just the part of Harry that still cared about Professor Quirrell doing the real talking.

Harry had needed to do the thing he’d done, it \emph{had} prevented greater evils, Harry couldn’t have stopped Voldemort if the Death Eaters had fired first. But that thing Harry had done wasn’t something that could be balanced by a not-necessary tragedy happening to one more sentient being, even if that being was Voldemort. It would just be one more element of the sorrows of ancient Earth so long ago.

The past was past. You did what you had to do, and you didn’t do one scrap of harm more than that. Not even to balance things out, and make it all symmetrical.

The children’s children’s children wouldn’t want Voldemort to die, even if his minions had. They wouldn’t want Voldemort to hurt, if it didn’t accomplish anything compared to him not hurting.

Harry breathed deeply, and let go of—not his hate—not quite his hate—he hadn’t been able to hate his creator even at the very end—but even so, Harry let go of \emph{something}. Of the sense that he \emph{ought} to hate Voldemort, that it was a hate he was obliged to feel, for the endless list of crimes that Voldemort had committed for no good reason, not even his own happiness…

\emph{It’s all right,} the stars whispered down at him. \emph{It’s all right not to hate him. It doesn’t make you a bad person.}

In the end, there was only one option he would take, and since Harry already knew that, there was no point agonizing about it. Whether it was the best option, only time would tell.

Harry breathed deeply, building up the magic inside himself. The spell he was going to cast didn’t need to be \emph{precise,} but it was still one of the most powerful spells he’d mastered.

Harry thought again of how unjust it was that Voldemort could not die with his followers, felt the slight trace of coldness in his blood that came with thoughts of ruthlessness. And then Harry let it go, let it all drain away beneath the starlight, because his dark side had never been anything except an inherited pattern of cognition, just one more bad habit of thinking to break.

Instead Harry looked at Hermione’s breathing form atop the altar, and let the tears finally start from his eyes. What would become of Hermione now, what path she would choose after this, Harry couldn’t guess; but she would be \emph{there} to have a choice, their friendship wouldn’t have destroyed her existence. He hadn’t realised how shaky his hope had been, until he’d noticed how surprised he’d been after the hope had come true. Sometimes things did go better than expected.

And Harry took that thought, too, and put it into the magic he was building.

The power he was storing up was vibrating in him, like his whole body was part of his wand, either Harry’s eyes were blurring or there was a luminous white quiver running over the holly. And Harry thought the shape of the spell he would cast, he didn’t have much fine control but the pattern he needed was simple, it just needed to include—

\emph{Everything, forget everything, Tom Riddle, Professor Quirrell, forget your whole life, forget your entire episodic memory, forget the disappointment and the bitterness and the wrong decisions, forget Voldemort—}

And at the last moment before Harry cast the spell, he had one final thought, a note of grace—

\emph{But if you ever had any truly happy memories, not hurting people or laughing at their pain, but the warm feeling of helping someone or being helped, there won’t be many, maybe just when you were a child, but if you had any truly happy memories then keep only those—}

Something bright in him unfolded at the decision, knowing he’d made the right choice, and Harry pushed that too into his wand—

\emph{“\shout{Obliviate!}”}

And it all poured out of Harry into the spell.

Harry fell over on his side, dropping his wand, strangled screams coming from his throat, his hands going helplessly to his scar, even as the sudden blast of pain in his head began to fade. Only dimly did his eyes see that the air was filled with glowing snowflakes, drifting motes of silver light like tiny specks of Patronus Charm.

Only a moment the silver light lasted, and then it was gone.

Professor Quirrell was gone.

Nothing left but a remnant.

And that spirit, what remained of it, wouldn’t be so different now from Harry’s own.

The Prophecy was complete.

They had each remade the other in their own image.

Harry started sobbing, then, from where he was curled up in the dirt.

He cried for a while.

And then eventually Harry staggered to his feet and picked up his wand again, because this day’s work wasn’t quite done.

\later

Harry laid his wand directly on Voldemort’s wrist-stump; it made his scar throb with an ongoing pain, but neither of them exploded.

And Harry began a Transfiguration.

Slowly—though faster than Harry had been able to Transfigure Hermione’s body, last time—the stunned form of the snake-man changed, reshaped itself. As the Transfiguration progressed, especially as the snake-man’s head began to turn glassy and shrunken, the pain in Harry’s scar faded.

It would be a spell to maintain whether Harry was waking or sleeping; and later, when Harry was older and more powerful and maybe had some help, he would un-Transfigure the mind-wiped Tom Riddle and heal his body with the power of the Stone. \emph{After} future-Harry had figured out what to do with an almost-completely-amnesiac wizard who still had some bad habits of thought and some highly negative emotional patterns—a dark side, as ’twere—plus a great deal of declarative and procedural knowledge about powerful magic. Harry had tried his best \emph{not} to Obliviate that part, because he might need it, some day.

And meanwhile, just like magic hadn’t defined a Transfigured unicorn as dead for purposes of setting off wards, Voldemort’s horcruxes wouldn’t define a Transfigured Voldemort as dead and try to bring him back.

That was the hope, anyway.

Harry’s scar twinged one last time when the steel ring went on his pinky finger, holding the tiny green emerald in contact with his skin. Then his scar subsided, and did not hurt again.

An upthrust rock served Harry for a chair, when he staggered over it and sat down motionless, resting after a fashion, shoving back the exhaustion that threatened the corners of his mind. \emph{It was not done, there was more to do.}

Harry took another deep breath, still inhaling through his mouth, said “\emph{Lumos,}” and looked around the graveyard.

Black robes and severed skull masks, surrounded by pools of blood—

Hermione Granger, asleep on an altar.

Voldemort’s empty robes and bloody hands, lying where the Dark Lord had fallen.

Quirinus Quirrell with his shredded robes, fallen in a heap where the Killing Curse had stricken him.

Harry imagined someone else looking at this scene, trying to understand it, and shook his head, because that wouldn’t do, it wouldn’t do at all.

Then Harry shoved himself up from his rock, grimacing as his mind, if not body, protested. He hadn’t been bloodied or beaten much today, but somehow Harry’s body was managing to feel like all the stress had hit it directly.

Harry staggered over toward where Voldemort had fallen, and picked up Voldemort’s left hand from where it lay upon the ground.

Even in just the left hand, you could see the faint trace of snake’s scales; it was very distinctively Voldemort. That was good.

Harry went to the altar where the sleeping Hermione lay, and gently placed the detached hand around Hermione’s neck, carefully moving the fingers to clutch at her throat. It was hard to do, Hermione seemed so peaceful and innocent when she was sleeping, and Voldemort’s severed hand seemed so ugly; Harry bluntly overrode whatever part of his mind was thinking that, since it made no sense in context.

A few weak Severing Charms served to mess up the almost perfectly fine cut the nanofibre had made, which was critical; it would not do to have the hand-stump look like the neck-stumps. The multiple \emph{Diffindos} scattered small bits of Voldemort-wrist all over Hermione’s shirt, which, Harry had to remind himself, was also part of the plan.

Harry repeated this with the right hand, arranging it symmetrically with the left.

Harry used \emph{Inflammare} to singe Voldemort’s robes where they lay, and then arranged the singed clothing around Hermione.

Voldemort’s gun, and his wand, went into Harry’s pouch. Harry placed the Stone of Permanency in an ordinary pocket, he wasn’t sure what the Stone might do to his pouch.

The heap of things from inside Quirrell’s robe, also near the altar, yielded the wand that the Defence Professor had used when he was being Quirrell. Harry went to where Quirrell lay, and straightened out the body as best he could, and put Quirrell’s wand into his hand. Tears predictably came to Harry’s eyes, and Harry wiped them away on his sleeve.

Harry took another deep breath, still inhaling through his mouth, said “\emph{Lumos}” again, and once more looked around the graveyard.

Black robes, severed skull masks, and Hermione Granger lying on an altar with Voldemort’s severed hands clutched around her throat, and Voldemort’s singed clothing scattered around her. Quirinus Quirrell lay dead with his clothes torn and shredded, his wand in his right hand.

That would do.

There remained the problem of calling attention to it.

Harry was very nearly out of magic at this point. But he still had enough left to Transfigure a leaf into the deflated form of a three-metre weather balloon.

Harry’s pouch produced a bottle of oxyacetylene, and a stick of dynamite, and a spool of fuse-cord. \emph{Be prepared, that’s the Boy Scout’s marching song, be prepared for a life that includes mountain trolls and who knows what else…}

Harry inflated the weather balloon with the oxyacetylene. That would produce a very sharp overpressure when it detonated, maybe as loud as a sonic boom.

He attached the stick of dynamite—it was overkill, for detonation, but it would do.

He attached a 60-second fuse to the stick of dynamite, but did not light it yet.

Harry put on his Cloak of Invisibility, that had been among the piles by the sacrificial altar.

He obtained his broomstick from his pouch, and mounted it.

Harry cast a Quieting Charm around Hermione Granger—it wouldn’t stop \emph{all} the noise, not even close, and it wasn’t like she’d be permanently hurt if her eardrums burst, but it still seemed polite.

And then that was it. The Quieting Charm had done it. Harry was drained of magic for at least the next hour.

Harry mounted the broomstick, slowly rising into the air, lifting the weather balloon filled with oxyacetylene with him. The castle Hogwarts came into view, distantly gleaming in moonlight a few kilometres away, as Harry rose above the trees; and Harry did his best to figure the distance, and the angle as it would be seen from Hogwarts.

When he had risen high above the forest, Harry used a lighter to ignite the fuse on the dynamite attached to the weather balloon full of oxyacetylene. Then Harry spun the broomstick and darted away—though not directly toward the castle, that might take him too close to the route past-Harry and Professor Quirrell had traversed, it wouldn’t do to have the Professor sense another Harry—

Harry felt a leaden stab of sadness, and refused it.

\emph{Thirty-one one-thousand, thirty-two one-thousand, thirty-three one\hyp{}thousand…}

When Harry reached forty, not wanting to take chances with his own eardrums, he glanced at his wristwatch, noting the exact time, and spun his Time-Turner once.

%  LocalWords:  omething un
