\partchapter{Self Awareness}{I}

\lettrinepara[ante=“]{A}{bbott}, Hannah!”

\hplettrineextrapara
Pause.

“HUFFLEPUFF!”

“Bones, Susan!”

Pause.

“HUFFLEPUFF!”

“Boot, Terry!”

Pause.

“RAVENCLAW!”

Harry glanced over briefly at his new House-mate, more to get a quick look at the face than anything else. He was still trying to get himself under control from his encounter with the ghosts. The sad, the really sad, the really truly sad thing was that he \emph{did} seem to be getting himself under control again. It seemed ill-fitting. Like he should have taken at least a day. Maybe a whole lifetime. Maybe just never.

“Corner, Michael!”

Long pause.

“RAVENCLAW!”

At the lectern before the huge Head Table stood Professor McGonagall, looking sharp and looking sharply around, as she called out one name after another, though she had smiled only for Hermione and a few others. Behind her, in the tallest chair at the table—really more of a golden throne—sat a wizened and bespectacled ancient, with a silver-white beard that looked like it would go almost to the floor if it were visible, watching over the Sorting with a benevolent expression; as stereotypical in appearance as a Wise Old Man could possibly be, without actually being Oriental. (Though Harry had learned to be wary of stereotypical appearances from the first time he’d met Professor McGonagall and thought that she ought to cackle.) The ancient wizard had applauded every student Sorted, with an unwavering smile that somehow seemed freshly delighted for each.

To the golden throne’s left side was a man with sharp eyes and a dour face who had applauded no-one, and who somehow managed to be looking straight back at Harry every time Harry looked at him. Further to the left, the pale-faced man Harry had seen in the Leaky Cauldron, whose eyes darted around as though in panic at the surrounding crowd, and who seemed to occasionally jerk and twitch in his seat; for some reason Harry kept finding himself staring at him. To that man’s left, a string of three older witches who didn’t seem much interested in the students. Then to the right side of the tall golden chair, a round-faced middle-aged witch with a yellow hat, who had applauded every student except the Slytherins. A tiny man standing on his chair, with a bushy white beard, who had applauded every student, but smiled only upon the Ravenclaws. And on the farthest right, occupying the same space as three lesser beings, the mountainous entity who’d greeted them all after they’d disembarked from the train, naming himself Hagrid, Keeper of Keys and Grounds.

“Is the man standing on his chair the Head of Ravenclaw?” Harry whispered towards Hermione.

For once Hermione didn’t answer this instantly; she was shifting constantly from side to side, staring at the Sorting Hat, and fidgeting so energetically that Harry thought her feet might be leaving the floor.

“Yes, he is,” said one of the prefects who’d accompanied them, a young woman wearing the blue of Ravenclaw. Miss~Clearwater, if Harry recalled correctly. Her voice was quiet, but conveyed a tinge of pride. “That is the Charms Professor of Hogwarts, Filius Flitwick, the most knowledgeable Charms Master alive, and a past Duelling Champion—”

“Why’s he so \emph{short?}” hissed a student whose name Harry didn’t recall. “Is he a \emph{halfbreed?}”

A chill glance from the young lady prefect. “The Professor does indeed have goblin ancestry—”

“What?” Harry said involuntarily, causing Hermione and four other students to hush him.

Now Harry was getting a surprisingly intimidating glare from the Ravenclaw prefect.

“I mean—” Harry whispered. “Not that I have a \emph{problem} with that—it’s just—I mean—how’s that \emph{possible?} You can’t just mix two different species together and get viable offspring! It ought to scramble the genetic instructions for every organ that’s different between the two species—it’d be like trying to build,” they didn’t have cars so he couldn’t use a scrambled-engine-blueprints analogy, “a half-carriage half-boat or something…”

The Ravenclaw prefect was still looking at Harry severely. “Why \emph{couldn’t} you have a half-carriage half-boat?”

“\emph{Hssh!}” hsshed another prefect, though the Ravenclaw witch had still spoken quietly.

“I mean—” Harry said even more quietly, trying to figure out how to ask whether goblins had evolved from humans, or evolved from a common ancestor of humans like \emph{Homo erectus}, or if goblins had been \emph{made} out of humans somehow—if, say, they were still genetically human under a heritable enchantment whose magical effect was diluted if only one parent was a ‘goblin’, which would explain how interbreeding was possible, and in which case goblins would \emph{not} be an incredibly valuable second data point for how intelligence had evolved in other species besides \emph{Homo sapiens}—now that Harry thought about it, the goblins in Gringotts \emph{hadn’t} seemed very much like genuinely alien, non-human intelligences, nothing like Dirdir or Puppeteers—“I mean, where did goblins \emph{come} from, anyway?”

“Lithuania,” Hermione whispered absently, her eyes still fixed firmly on the Sorting Hat.

Now Hermione was getting a smile from the lady prefect.

“Never mind,” whispered Harry.

At the lectern, Professor McGonagall called out, “Goldstein, Anthony!”

“RAVENCLAW!”

Hermione, next to Harry, was bouncing on her tiptoes so hard that her feet were actually leaving the ground on each bounce.

“Goyle, Gregory!”

There was a long, tense moment of silence under the Hat. Almost a minute.

“SLYTHERIN!”

“Granger, Hermione!”

Hermione broke loose and ran full tilt towards the Sorting Hat, picked it up and jammed the patchy old cloth-work down hard over her head, making Harry wince. Hermione had been the one to explain to \emph{him} about the Sorting Hat, but she certainly didn’t \emph{treat} it like an irreplaceable, vitally important, 800-year-old artefact of forgotten magic that was about to perform intricate telepathy on her mind and didn’t seem to be in very good physical condition.

“RAVENCLAW!”

And talk about your foregone conclusions. Harry didn’t see why Hermione had been so tense about it. In what weird alternative universe would that girl \emph{not} be Sorted into Ravenclaw? If Hermione Granger didn’t go to Ravenclaw then there was no good reason for Ravenclaw House to exist.

Hermione arrived at the Ravenclaw table and got a dutiful cheer; Harry wondered whether the cheer would have been louder, or quieter, if they’d had any idea just what level of competition they’d welcomed to their table. Harry knew pi to 3.141592 because accuracy to one part in a million was enough for most practical purposes. Hermione knew one hundred digits of pi because that was how many digits had been printed in the back of her maths textbook.

Neville Longbottom went to Hufflepuff, Harry was glad to see. If that House really did contain the loyalty and camaraderie it was supposed to exemplify, then a Houseful of reliable friends would do Neville a whole world of good. Clever kids in Ravenclaw, evil kids in Slytherin, wannabe heroes in Gryffindor, and everyone who does the actual work in Hufflepuff.

(Though Harry \emph{had} been right to consult a Ravenclaw prefect first. The young woman hadn’t even looked up from her reading or identified Harry, just jabbed a wand in Neville’s direction and muttered something. After which Neville had acquired a dazed expression and wandered off to the fifth carriage from the front and the fourth compartment on the left, which indeed had contained his toad.)

“Malfoy, Draco!” went to Slytherin, and Harry breathed a small sigh of relief. It had \emph{seemed} like a sure thing, but you never did know what tiny event might upset the course of your master plan.

Professor McGonagall called “Perks, Sally-Anne!”, and from the gathered children detached a pale waifish girl who looked oddly ethereal—like she might mysteriously disappear the moment you stopped looking at her, and never be seen again or even remembered.

And then (with a note of trepidation so firmly kept from her voice and face that you’d have needed to know her very well indeed to notice) Minerva McGonagall inhaled deeply, and called out, “Potter, Harry!”

There was a sudden silence in the hall.

All conversation stopped.

All eyes turned to stare.

For the first time in his entire life, Harry felt like he might be having an opportunity to experience stage fright.

Harry immediately stomped down this feeling. Whole roomfuls of people staring at him was something he’d have to accustom himself to, if he wanted to live in magical Britain, or for that matter do anything else interesting with his life. Affixing a confident and false smile to his face, he raised a foot to step forwards—

“Harry Potter!” cried the voice of either Fred or George Weasley, and then “Harry Potter!” cried the other Weasley twin, and a moment later the entire Gryffindor table, and soon after a good portion of Ravenclaw and Hufflepuff, had taken up the cry.

“\emph{Harry Potter! Harry Potter! Harry Potter!}”

And Harry Potter walked forwards. Much too slowly, he realized once he’d begun, but by then it was too late to alter his pace without it looking awkward.

\later

“\emph{Harry Potter! Harry Potter! \shout{Harry Potter!}}”

With all too good a notion of what she would see, Minerva McGonagall turned to look behind herself at the rest of the Head Table.

Trelawney frantically fanning herself, Filius looking on with curiosity, Hagrid clapping along, Sprout looking severe, Vector and Sinistra bemused, and Quirrell gazing vacuously at nothing. Albus smiling benevolently. And Severus Snape gripping his empty wine goblet, white-knuckled, so hard that the silver was slowly deforming.

With a wide grin, turning his head to bow to one side and then the other as he walked between the four House tables, Harry Potter walked forwards at a grandly measured pace, a prince inheriting his castle.

“\emph{Save us from some more Dark Lords!}” called one of the Weasley twins, and then the other Weasley twin cried, “\emph{Especially if they’re Professors!}”to general laughter from all the tables except Slytherin.

Minerva’s lips set in a white line. She would have words with the Weasley Horrors about that last part, if they thought she was powerless because it was the first day of school and Gryffindor had no points to take away. If they didn’t care about detentions then she would find something else.

Then, with a sudden gasp of horror, she looked in Severus’s direction, \emph{surely} he realized the Potter boy must have no idea who that was talking about—

Severus’s face had gone beyond rage into a kind of pleasant indifference. A faint smile played about his lips. He was looking in the direction of Harry Potter, not the Gryffindor table, and his hands held the crumpled remains of a former wine goblet.

\later

Harry Potter walked forwards with a fixed smile, feeling warm inside and sort of awful at the same time.

They were cheering him for a job he’d done when he was one year old. A job he hadn’t really finished. Somewhere, somehow, the Dark Lord was still alive. Would they have been cheering quite so hard, if they knew that?

But the Dark Lord’s power \emph{had} been broken once.

And Harry would protect them again. If there was in fact a prophecy and that was what it said. Well, actually regardless of what any darn prophecy said.

All those people believing in him and cheering him—Harry couldn’t stand to let that be false. To flash and fade like so many other child prodigies. To be a disappointment. To fail to live up to his reputation as a symbol of the Light, never mind \emph{how} he’d won it. He would absolutely, positively, no matter how long it took and even if it killed him, fulfil their expectations. And then go on to \emph{exceed} those expectations, so that people wondered, looking back, that they had once asked so little of him.

“\emph{HARRY POTTER! HARRY POTTER! HARRY POTTER!}”

Harry took his last steps towards the Sorting Hat. He swept a bow to the Order of Chaos at the Gryffindor table, and then turned and swept another bow to the other side of the hall, and waited for the applause and giggling to die away.

(In the back of his mind, he wondered if the Sorting Hat was genuinely \emph{conscious} in the sense of being aware of its own awareness, and if so, whether it was satisfied with only getting to talk to eleven-year-olds once per year. Its song had implied so: \emph{Oh, I’m the Sorting Hat and I’m okay, I sleep all year and I work one day…})

When there was once more silence in the room, Harry sat on the stool and \emph{carefully} placed onto his head the 800-year-old telepathic artefact of forgotten magic.

Thinking, just as hard as he could: \emph{Don’t Sort me yet! I have questions I need to ask you! Have I ever been Obliviated? Did you Sort the Dark Lord when he was a child and can you tell me about his weaknesses? Can you tell me why I got the brother wand to the Dark Lord’s? Is the Dark Lord’s ghost bound to my scar and is that why I get so angry sometimes? Those are the most important questions, but if you’ve got another moment can you tell me anything about how to rediscover the lost magics that created you?}

Into the silence of Harry’s spirit, where before there had never been any voice but one, there came a second and unfamiliar voice, sounding distinctly worried:

“\emph{Oh, dear. This has never happened before…}”

%  LocalWords:  bbott Hssh hsshed Dirdir
