\partchapter{The Stanford Prison Experiment}{IV}
\lettrine{A}{} faint green spark moved forward to set the pace, and behind it followed a brilliant silver figure, all other entities invisible. They had traversed five legs of corridor, turned right five times and gone up five flights of stairs; and when Bellatrix had finished her second bottle of chocolate milk, she had been given solid bars of chocolate to eat.

It was after her third bar of chocolate that strange noises began to come from Bellatrix’s throat.

It took a moment for Harry to understand, to process the sounds, it didn’t sound like anything he’d ever heard before; the rhythm of it was shattered, almost unrecognizable, it took him that long to realize that Bellatrix was crying.

Bellatrix Black was crying, the Dark Lord’s most terrible weapon was crying, she was invisible but you could hear it, tiny pathetic sounds she was trying to suppress, even now.

“It’s real?” said Bellatrix. Tonality had returned into her voice, no longer a dead mutter, it rose up at the end to form the question. “It’s real?”

\emph{Yes,} thought the part of Harry simulating the Dark Lord, \emph{now be silent—}

He couldn’t make those words pass his lips, he just couldn’t.

“I knew—you would—come to me—someday,” Bellatrix’s voice quavered and fractured as she drew breath for quiet sobs, “I knew—you were alive—that you would come—to me—my Lord...” there was a long inhalation like a huge gasp, “and that even—when you came—you still wouldn’t love me—never—you would never love me back—that was why—they couldn’t take—my love from me—even though I can’t remember—can’t remember so many other things—though I don’t know what I forgot—but I remember how much I love you, Lord—”

There was a knife stabbing through Harry’s heart, he’d never heard anything so terrible, he wanted to hunt down the Dark Lord and kill him just for this...

“Do you still—have use for me—my Lord?”

“No,” hissed Harry’s voice, without him even thinking, it just seemed to be operating on automatic, “I entered Azkaban on a whim. Of course I have use for you! Don’t ask foolish questions.”

“But—I’m weak,” said Bellatrix’s voice, and a full sob escaped her, it sounded much too loud in the corridors of Azkaban, “I can’t kill for you, my Lord, I’m sorry, they ate it all, ate me all up, I’m too weak to fight, what good am I to you now—”

Harry’s brain cast about desperately for some way to reassure her, from the lips of a Dark Lord who would never speak a single word of caring.

“Ugly,” said Bellatrix. Her voice said that word like it was the final nail in her coffin, the last despair. “I’m ugly, they ate that too, I’m, I’m not pretty any more, you won’t even, be able, to use me, as a reward, for your servants—even the Lestranges, won’t want, to hurt me, any more—”

The brilliant silver figure stopped walking.

Because Harry had stopped walking.

\emph{The Dark Lord, he...} The part of Harry’s self that was soft and vulnerable was screaming in disbelieving horror, trying to reject reality, refuse the understanding, even as a colder and harder part completed the pattern: \emph{She obeyed him in that as she obeyed him in all things.}

The green spark bobbed urgently, darted forward.

The silver humanoid stayed in place.

Bellatrix was sobbing harder.

“I’m, I’m not, I can’t be, useful, any more...”

Giant hands were squeezing Harry’s chest, wringing him like a washcloth, trying to crush his heart.

“Please,” whispered Bellatrix, “just kill me...” Her voice seemed to calm, once she said that. “Please Lord, kill me, I’ve no reason to live if I’m no use to you... I only want it to stop...\ please hurt me one last time, my Lord, hurt me until I stop... I love you...”

It was the saddest thing Harry had ever heard.

The bright silver shape of Harry’s Patronus flickered—

Wavered—

Brightened—

The fury that was rising in Harry, his rage against the Dark Lord who had done this, the rage against the Dementors, against Azkaban, against the world that allowed such horror, it all seemed to be pouring straight through his arm and into his wand without there being any way of blocking it, he tried willing it to stop and nothing happened.

“My Lord!” whispered the disguised voice of Professor Quirrell. “My spell is going out of control! Help me, my Lord!”

Brighter the Patronus, brighter and brighter, it was waxing faster than on the day that Harry had destroyed a Dementor.

“My Lord!” the silhouette said in a terrified whisper. “Help me! Everyone will feel it, my Lord!”

\emph{Everyone will feel it,} thought Harry. His imagination could picture it clearly, the prisoners in their cells stirring as the cold and darkness fell away, replaced by healing light.

Every exposed surface now burned like a white sun in the reflections, the silhouette of Bellatrix’s skeleton and the sallow man now clearly visible in the blaze, the Disillusionment spells unable to keep pace with the unearthly brilliance; only the Cloak of Invisibility out of the Deathly Hallows withstood it.

“My Lord! \emph{You must stop it!}”

But Harry could no longer will it to stop, he no longer wanted it to stop. He could sense it, more and more of the sparks of life in Azkaban being sheltered by his Patronus, \emph{as it unfolded like spreading wings of sunlight, the air turned to absolute silver as he thought it, Harry knew what he had to do.}

“\emph{Please, my Lord!}”

The words went unheard.

\emph{They were far from him, the Dementors in their pit, but Harry knew that they could be destroyed even at this distance if the light blazed bright enough, he knew that Death itself could not face him if he stopped holding back, so he unsealed all the gates inside him and sank the wells of his spell into all the deepest parts of his spirit, all his mind and all his will, and gave over absolutely everything to the spell—}

And in the interior of the Sun, an only slightly dimmer shadow moved forward, reaching out an entreating hand.

\headline{\scream{Wrong}\par\scream{Don’t}}

The sudden sense of doom clashed with Harry’s steel determination, dread and uncertainty striving against the bright purpose, nothing else might have reached him but that. The silhouette took another step forward and another, the sense of doom rising to a point of terrible catastrophe; and in the drench of cold water, Harry saw it, he realized the consequences of what he was doing, the danger and the trap.

If you had been watching from outside you would have seen the interior of the Sun brightening and dimming...

Brightening and dimming...

...and finally fading, fading, fading into ordinary moonlight that seemed like pitch darkness by contrast.

Within the darkness of that moonlight stood a sallow man with his hand outstretched in entreaty, and the skeleton of a woman, lying upon the floor, a puzzled look upon her face.

And Harry, still invisible, fallen to his knees. The greater danger had passed, and now Harry was just trying not to collapse, to keep the spell going at the lower level. He’d drained something, hopefully not lost something—he should have known, should have remembered, that it wasn’t mere magic that fueled the Patronus Charm—

“Thank you, my Lord,” whispered the sallow man.

“Fool,” said the hard voice of a boy pretending to be a Dark Lord. “Did I not warn you that the spell could prove fatal if you failed to control your emotions?”

Professor Quirrell’s eyes did not widen, of course.

“Yes, my Lord, I understand,” said the Dark Lord’s servant in a faltering voice, and turned to Bellatrix—

She was already pushing herself off the floor, slowly, like an old, old Muggle woman. “How funny,” Bellatrix whispered, “you were almost killed by a Patronus Charm...” A giggle that sounded like it was blowing dust out of her giggle pipes. “I could punish you, maybe, if my Lord froze you in place and I had knives...\ maybe I can be useful after all? Oh, I feel a little better now, how strange...”

“Be silent, dear Bella,” Harry said in a chill voice, “until I give you leave to speak.”

There was no reply, which was obedience.

The servant levitated the human skeleton, and made her invisible once more, followed shortly by his own disappearance with the sound of another cracking egg.

They passed on through the corridors of Azkaban.

And Harry knew that as they passed, the prisoners were stirring in their cells as the fear lifted for one precious moment, maybe even feeling a small touch of healing as his light passed them by, and then collapsing down again as the cold and darkness pressed back in.

Harry was trying very hard not to think about it.

Otherwise his Patronus would wax until it burned away every Dementor in Azkaban, blazing bright enough to destroy them even at this distance...

Otherwise his Patronus would wax until it burned away every Dementor in Azkaban, taking all of Harry’s life as fuel.
\sbreak
In the Auror’s quarters at the top of Azkaban, one Auror trio was snoring in the barracks, one Auror trio was resting in the breakroom, and one Auror trio was on duty in the command room, keeping their watch. The command room was simple but large, with three chairs at back where three Aurors sat, their wands always in hand to sustain their three Patronuses, as the bright white forms paced in front of the open window, sheltering them all from the Dementors’ fear.

The three of them usually stuck to the back, and played poker, and didn’t look out the window. You could have seen some sky there, sure, and there was even an hour or two every day where you could’ve seen some sun, but that window also looked down on the central pit of hell.

Just in case a Dementor wanted to float up and talk to you.

There was no way that Auror Li would have agreed to serve duty here, triple pay or no triple pay, if he hadn’t had a family to support. (His real name was Xiaoguang, and everyone called him Mike instead; he’d named his children Su and Kao, which hopefully would serve them better.) His only consolation, besides the money, was that at least his mates played an excellent game of Dragon Poker. Though it would be hard \emph{not} to, at this point.

It was their 5,366\Th game and Li had what would probably be his best hand of the 5300s. It was a Saturday in February and there were three players, which let him shift the suit of any one hole card except a two, three, or seven; and that was enough to let him build a Corps-a-Corps with Unicorns, Dragons, and sevens...

Across the table from him, Gerard McCusker looked up from the table cards toward the direction of the window, staring.

The sinking feeling came over Li’s stomach with surprising speed.

If his seven of hearts got hit by a Dementor Modifier and turned into a six, he was going straight down to two pair and McCusker might beat that—

“Mike,” said McCusker, “what’s with your Patronus?”

Li turned his head and looked.

His soft silver badger had turned away from its watch over the pit and was staring downward at something only it could see.

A moment later, Bahry’s moonlit duck and McCusker’s bright anteater followed suit, staring in the same downward direction.

They all exchanged glances, and then sighed.

“I’ll tell them,” said Bahry. Protocol called for sending the three Aurors who were off-duty but not sleeping to investigate anything anomalous. “Maybe relieve one of them and take the C spiral, if you two don’t mind.”

Li exchanged a glance with McCusker, and they both nodded. It wasn’t too hard to break into Azkaban, if you were wealthy enough to hire a powerful wizard, and well-intentioned enough to recruit someone who could cast the Patronus Charm. People with friends in Azkaban would do that, break in just to give someone a half-day’s worth of Patronus time, a chance at some real dreams instead of nightmares. Leave them a supply of chocolate to conceal in their cell, to increase the chance they lived through their sentence. And the Aurors on guard...\ well, even if you got caught, you could probably convince the Aurors to overlook it, in exchange for the right bribe.

For Li, the right bribe tended to be in the range of two Knuts and a silver Sickle. He hated this place.

But Bahry One-Hand had a wife and the wife had healer’s bills, and if you could afford to hire someone who could break into Azkaban, then you could afford to grease Bahry’s remaining palm pretty hard, if he was the one who caught you.

By unspoken agreement, none of them giving them anything away by being the first to propose it, the three of them finished out their poker hand first. Li won, since no Dementors had actually shown up. And by then the Patronuses had stopped staring and gone back to their normal patrol, so it was probably nothing, but procedure was procedure.

After Li raked in the pot, Bahry gave them all formal nods, and stood up from the table. The older man’s long white locks brushed against his fancy red robes, his robes brushed the metal floor of the command room, as Bahry went through the separating door that led to the formerly off-duty Aurors.

Li had been Sorted into Hufflepuff, and he sometimes felt a little queasy about this kind of business. But Bahry had shown them all the pictures, and you had to let a man do what he could for his poor sick wife, especially when he only had seven months left before his retirement.
\sbreak
The faint green spark floated through the metal corridors, and the silver humanoid, seeming a little dimmer now, followed after it. Sometimes the bright figure would flare, especially when they passed one of the huge metal doors, but it always died back down again.

Mere eyes could not have seen the invisible others: the eleven-year-old Boy-Who-Lived, and the living skeleton that was Bellatrix Black, and the Polyjuiced Defense Professor of Hogwarts, all traveling together through Azkaban. If that was the beginning of a joke, Harry didn’t know the punchline.

They’d gone up another four flights of stairs before the rough voice of the Defense Professor said, simply and without emphasis, “Auror coming.”

It took too long, a whole second maybe, for Harry to understand, for the jolt of adrenaline to pump into his blood, and for him to remember what Professor Quirrell had already discussed with him and told him to do in this case, and then Harry spun on his heel and flew back the way they’d come.

Harry reached the flight of stairs, and frantically laid himself down on the third step from the top, the cold metal feeling hard even through his cloak and robes. Trying to move his head up, to peer over the lip of the stairs, showed that he couldn’t see Professor Quirrell; and that meant that Harry was out of the line of any stray fire.

His shining Patronus followed after him, and lay down beside him on the step just beneath him; for it too must not be seen.

There was a faint sound as of wind or whooshing, and then the sound of Bellatrix’s invisible body coming to rest on a stair further below, she had no place in this except—

“Stay still,” said the cold high whisper, “stay silent.”

There was stillness, and silence.

Harry pressed his wand against the side of the metal step just above him. If he was anyone else he would have needed to take a Knut out of his pocket...\ or rip off a bit of cloth from his robe...\ or bite off one of his nails...\ or find a speck of rock large enough that he could see it and solid enough to stay in one place and orientation while it touched his wand. But with Harry’s almighty power of partial Transfiguration, this was not necessary; he could skip that particular step of the operation and use any material near to hand.

Thirty seconds later Harry was the proud new owner of a curved mirror, and...

“\emph{Wingardium Leviosa,}” Harry whispered as quietly as he could.

...was levitating it just above the steps, and watching, in that curved surface, almost the whole corridor where Professor Quirrell invisibly waited.

Harry heard it in the distance, then, the sound of footsteps.

And saw the form (a little hard to see in the mirror) of a person in red robes, coming down the stairs, entering the seemingly empty corridor; accompanied by a small Patronus animal that Harry couldn’t quite make out.

The Auror was protected by a blue shimmer, it was hard to see the details but Harry could see that much, the Auror had shields already raised and strengthened.

\emph{Crap,} thought Harry. According to the Defense Professor, the essential art of dueling consisted of trying to put up defenses that would block whatever someone was likely to throw at you, while trying in turn to attack in ways that were likely to go past their current set of defenses. And by far the easiest way to win any sort of real fight—Professor Quirrell had said this over and over—was to shoot the enemy before they raised a shield in the first place, either from behind or from close enough range that they couldn’t dodge or counter in time.

Though Professor Quirrell might still be able to get in a shot from behind, if—

But the Auror halted after taking three steps into the corridor.

“Nice Disillusionment,” said a hard male voice that Harry didn’t recognize. “Now show yourself, or you’ll be in \emph{real} trouble.”

The form of the sallow, bearded man became visible then.

“And you with the Patronus,” said the hard voice. “Come out too. \emph{Now.}”

“Wouldn’t be smart,” said the gravelly voice of the sallow man. It was no longer the terrified voice of the Dark Lord’s servant; it had suddenly become the professional intimidation of a competent criminal. “You don’t want to see who’s behind me. Trust me, you don’t. Five hundred Galleons, cold cash up front, if you turn around and walk away. Big trouble for your career if you don’t.”

There was a long pause.

“Look, whoever you are,” said the hard voice. “You seem confused about how this works. I don’t care if that’s Lucius Malfoy behind you or Albus bloody Dumbledore. You \emph{all} come out, I scan the whole lot of you, and \emph{then} we talk about how much this is going to cost you—”

“Two thousand Galleons, final offer,” said the gravelly voice, taking on a warning undertone. “That’s ten times the going rate and more than you make in a year. And believe me, if you see something you shouldn’t, you’re going to regret not taking that—”

“Shut it!” said the hard voice. “You’ve got exactly five seconds to drop that wand before I drop you. Five, four—”

\emph{What are you doing, Professor Quirrell?} Harry thought frantically. \emph{Attack first! Cast a shield at least!}

“—three, two, one! \emph{Stupefy!}”
\sbreak
Bahry stared, a chill running down his spine.

The man’s wand had moved so fast that it was like it had Apparated into place, and Bahry’s stunner was currently sparkling tamely at the end of it, not blocked, not countered, not deflected, \emph{caught} like a fly in honey.

“My offer has gone back down to five hundred Galleons,” said the man in a colder, more formal voice. He smiled dryly, and the smile looked wrong on that bearded face. “And you shall need to accept a Memory Charm.”

Bahry had already swapped the harmonics on his shields so that his own stunner couldn’t pass back through, already tilted his wand back into a defensive position, already raised his hardened artificial hand into position to block anything blockable, and was already thinking wordless spells to put more layers on his shields—

The man wasn’t looking at Bahry. Instead he was poking curiously at Bahry’s stunner where it still wavered on the end of his wand, drawing out red sparks and flicking them away with his fingers, slowly disassembling the hex like a child’s rod puzzle.

The man hadn’t raised any shields of his own.

“Tell me,” the man said in a disinterested voice that didn’t seem to quite fit the rough throat—Polyjuice, Bahry would have called it, if he’d thought that anyone could possibly do magic that delicate from inside someone else’s body—“what did you do in the last war? Put yourself in harm’s way, or stay out of trouble?”

“Harm’s way,” said Bahry. His voice kept the iron calm of an Auror with nearly a hundred full years on the force, seven months short of mandatory retirement, Mad-Eye Moody couldn’t have said it with any more hardness.

“Fight any Death Eaters?”

Now a grim smile graced Bahry’s own face. “Two at once.” Two of You-Know-Who’s own warrior-assassins, personally trained by their dark master. Two Death Eaters at once against Bahry alone. It had been the toughest fight of Bahry’s life, but he’d stood his ground, and walked away with only the loss of his left hand.

“Did you kill them?” The man sounded idly curious, and he continued to draw threads of fire out of the much-diminished stunbolt still captive on the end of his wand, his fingers now weaving small patterns of Bahry’s own magic before flicking to disperse them.

Sweat broke out on Bahry’s skin beneath his robes. His metal hand flashed downward, ripped the mirror from his belt—“Bahry to Mike, I need backup!”

There was a pause, and silence.

“Bahry to Mike!”

The mirror lay dull and lifeless in his hand. Slowly, Bahry put it back on his belt.

“It’s been quite a while since I had a serious fight with a serious opponent,” the man said, still not looking up at Bahry. “Try not to disappoint me too much. You can attack whenever you’re ready. Or you can walk away with five hundred Galleons.”

There was a long silence.

Then the air screamed like metal cutting glass as Bahry slashed his wand downward.
\sbreak
Harry could hardly see it, could hardly make out anything amid the lights and flashes, his mirror’s curve was perfect (they’d practiced that tactic before in the Chaos Legion) but the scene was still too small, and Harry had the feeling he wouldn’t be able to understand even if he was watching from a meter away, it was all happening too \emph{fast,} red blasts deflecting from blue shields, green bars of light clashing together, shadowy forms appearing and vanishing, he couldn’t even tell who was casting what, except that the Auror was shouting incantation after incantation and frantically dodging while Professor Quirrell’s Polyjuiced form stood in one place and flicked his wand, mostly silently, but now and then pronouncing words in unrecognizable languages that would white out the whole mirror and show half the Auror’s shielding torn away as he staggered back.

Harry had seen exhibition duels between the strongest seventh-year students, and this was so far above it that Harry’s mind felt numbed, looking at how far he had left to go. There wasn’t a single seventh-year student who could have lasted half a minute against the Auror, all three seventh-year armies put together might not be able to scratch the Defense Professor...

The Auror had fallen to the ground, one knee and one hand supporting himself as the other hand gestured frantically, the few shouted incantations that Harry recognized were all shield spells, as a flock of shadows spun around the Auror like a whirlwind of razors.

And Harry saw Professor Quirrell’s Polyjuiced form deliberately point his wand at where the Auror kneeled and fought the last moments of his battle.

“Surrender,” said the gravelly voice.

The Auror spat something unspeakable.

“So be it,” said the voice. “Avada—”

Time seemed to move very slowly, like there was time to hear the individual syllables, \emph{Ke,} and \emph{Da,} and \emph{Vra,} time to watch the Auror starting to throw himself desperately aside; and even though it was all happening so slowly, somehow there wasn’t time to \emph{do} anything, no time for Harry to open his lips and scream \scream{no}, no time to move, maybe even not any time to think.

Only time for one desperate wish that an innocent man should not die—

And a blazing silver figure stood before the Auror.

Stood there just a fraction of a second before the green light struck home.
\sbreak
Bahry was twisting frantically aside, not knowing if he was going to make it—

His eyes were focused on his opponent and his onrushing death, so Bahry only briefly saw the outline of the brilliant silhouette, the Patronus brighter than any he’d ever seen, saw it just barely long enough to recognize the impossible shape, before the green and the silver light collided and both lights vanished, it was impossible but both lights vanished, \emph{the Killing Curse had been blocked}, and then Bahry’s ears were pierced as he saw his terrible opponent screaming, screaming, screaming, clutching at his head and screaming, starting to fall as Bahry was already falling—

Bahry hit the ground, falling from his own frantic lunge, and his dislocated left shoulder and broken rib screamed in protest. Bahry ignored the pain, managed to scramble back to his knees, brought up his wand to stun his opponent, he didn’t understand what was happening but he knew that this was his only chance.

“\emph{Stupefy!}”

The red bolt struck out toward the man’s falling body, and was torn apart in midair and dissipated—and not by any shield. Bahry could \emph{see} it, the wavering in the air that surrounded his fallen and screaming opponent.

Bahry could feel it like a deadly pressure on his skin, the flux of magic building and building and building toward some terrible breaking point. His instincts screamed at him to run before the explosion came, this was no Charm, no Curse, this was wizardry run wild, but before Bahry could even finish getting to his feet—

The man threw his wand away from himself (he threw away his wand!) and a second later, his form blurred and vanished entirely.

A green snake lay motionless on the ground, unmoving even before Bahry’s next stunner spell, fired in sheer reflex, hit it without resistance.

As the dreadful flux and pressure began to dissipate, as the wild wizardry died back down, Bahry’s dazed mind noticed that the scream was continuing. Only it sounded different, like the scream of a young boy, coming from the stairs leading down to the next lower level.

That scream choked off too, and then there was silence except for Bahry’s frantic panting.

His thoughts were slow, confused, disarrayed. His opponent had been \emph{insanely} powerful, that hadn’t been a duel, it had been like his first year as a trainee Auror trying to fight Madam Tarma. The Death-Eaters hadn’t been a tenth that good, Mad-Eye Moody wasn’t that good...\ and who, what, how in the name of Merlin’s balls had anyone blocked a \emph{Killing Curse?}

Bahry managed to summon the energy to press his wand against his rib, mutter the healing spell, and then press it again to his shoulder. It took more out of him than it should have, took far too much out of him, his magic was within a bare breath of utter exhaustion; he didn’t have anything left for his minor cuts and bruises or even to reinforce the scraps left of his shielding. It was all he could do not to let his Patronus go out.

Bahry breathed deeply, heavily, steadied his breath as much as he could before he spoke.

“You,” Bahry said. “Whoever you are. Come out.”

There was silence, and it occurred to Bahry that whoever it was might be unconscious. He didn’t understand what had just happened, but he’d heard the scream...

Well, there was one way to test that.

“Come out,” said Bahry, making his voice harder, “or I start using area-effect curses.” He probably couldn’t have managed one if he’d tried.

“Wait,” said a boy’s voice, a \emph{young} boy’s voice, high and thin and wavering, like someone was holding back exhaustion or tears. The voice now seemed to be coming from closer to hand. “Please wait. I’m—coming out—”

“Drop the invisibility,” growled Bahry. He was too tired to bother with anti-Disillusionment Charms.

A moment later, a young boy’s face emerged from within an unfolding invisibility cloak, and Bahry saw the black hair, the green eyes, the glasses, and the angry red lightning-bolt scar.

If he’d had twenty fewer years of experience under his belt he might have blinked. Instead he just spat something that he probably shouldn’t ought to say in front of the Boy-Who-Lived.

“He, he,” the boy’s wavering voice said, his young face looked frightened and exhausted and tears were still trickling down his cheeks, “he kidnapped me, to make me cast my Patronus...\ he said he’d kill me if I didn’t...\ only I couldn’t let him just kill you...”

Bahry’s mind was still dazed, but things were slowly starting to click into place.

Harry Potter, the only wizard ever to survive a Killing Curse. Bahry might have been able to dodge the green death, he’d certainly been trying, but if the matter came up before the Wizengamot, they’d rule it was a life debt to a Noble House.

“I see,” Bahry said in a much gentler growl. He started to walk toward the boy. “Son, I’m sorry for what you’ve been through, but I need you to drop the cloak and drop your wand.”

The rest of Harry Potter emerged from invisibility, showing the sweat-soaked blue-trimmed Hogwarts robes, and his right hand clutching an eleven-inch holly wand so hard his knuckles were white.

“Your wand,” Bahry repeated.

“Sorry,” whispered the eleven-year-old boy, “here,” and he held out the wand toward Bahry.

Bahry barely stopped himself from snarling at the traumatized boy who’d just saved his life. Instead he overrode the impulse with a sigh, and just stretched out a hand to take the wand. “Look, son, you’re \emph{really} not supposed to point a wand at—”

The wand’s end twisted lightly beneath Bahry’s hand just as the boy whispered, “\emph{Somnium}.”
\sbreak
Harry stared at the Auror’s crumpled body, there was no sense of triumph, just a crushing sense of despair.

(Even then it might not have been too late.)

Harry turned to look at where the green snake lay motionless.

“\emph{Teacher?}” hissed Harry. “\emph{Friend? Pleasse, are you alive?}” An awful fear was taking hold in Harry’s heart; in that moment he had entirely forgotten that he’d just seen the Defense Professor try to kill a police officer.

Harry pointed his wand at the snake, and his lips even began to shape the word \emph{Innervate}, before his brain caught up with him and screamed at him.

He couldn’t use magic on Professor Quirrell.

Couldn’t ever use magic on Professor Quirrell.

Harry had felt it, the burning, tearing pain in his head, like his brain was about to split in half. He’d felt it, his magic and Professor Quirrell’s magic, matched and anti-harmonized in a fulfillment of doom. That was the mysterious terrible thing that would happen if Harry and Professor Quirrell ever got too close to each other, or if they ever cast magic on each other, or if \emph{their spells ever touched,} their magic would resonate out of control—

Harry stared at the snake, he couldn’t tell if it was breathing.

(The last seconds ticked away.)

He turned to stare at the Auror, who had seen the Boy-Who-Lived, who knew.

The full magnitude of the disaster crushed in on Harry like a thousand hundred-ton weights, he’d managed to stun the Auror but now there was nothing left to do, no way to recover, the mission had failed, everything had failed, \emph{he} had failed.

Shocked, dismayed, despairing, he \emph{didn’t think of it}, didn’t see the obvious, didn’t remember where the hopeless feelings were coming from, didn’t realize that he still needed to recast the True Patronus Charm—

And then it was already too late.
\sbreak
Auror Li and Auror McCusker had rearranged their chairs around the table, and so they both saw it at the same time, the naked, skeletally thin horror rising up to hover outside the window, the headache already hitting them from seeing it.

They both heard the voice, like a long-dead corpse had spoken words and those words themselves had aged and died.

The Dementor’s speech hurt their ears as it said, “Bellatrix Black is out of her cell.”

There was a split second of horrified silence, and then Li tore out of his chair, heading for the communicator to call in reinforcements from the Ministry, even as McCusker grabbed his mirror and started frantically trying to raise the three Aurors who’d gone on patrol.

