\chapter{The Cardinal Sin}

\lettrine{B}{right} the sun, bright the air, bright the students and bright their parents, clean the paved ground of Platform 9.75, the winter Sun hanging low in the sky at 9:45\AM in the morning on January 5\Th, 1992. Some of the younger students wore scarves and mittens, but most simply wore their robes; they were wizards, after all.

After Harry had moved away from the landing platform, he took off his scarf and coat, opened a compartment of his trunk, and stowed away his winter things.

For a long moment, he stood there letting the January air bite at him, just to see what it was like.

Harry took out his wizards’ robes, shrugged them on.

And finally, Harry drew his wand; and he couldn’t help thinking of the parents he’d only just kissed goodbye, of the world whose problems he was leaving behind...

With a strange feeling of guilt for the unavoidable, Harry said, “\emph{Thermos.}”

The warmth flowed through him.

And the Boy-Who-Lived was back.

Harry yawned and stretched, feeling more lethargic than anything else at the conclusion of his vacation. He didn’t feel like reading his textbooks, or even any serious science fiction, this morning; what he needed was something completely frivolous to occupy his attention...

Well, that wouldn’t be hard to come by, if he was willing to part with four Knuts.

Besides, if the \emph{Daily Prophet} was corrupt and the \emph{Quibbler} was the only competing newspaper, there might be some suppressed real news in there.

Harry trudged back over to the same newsstand from last time, wondering if the \emph{Quibbler} could top the headline he’d seen before.

The vendor started to smile as Harry approached, and then the man’s face suddenly changed, as he caught sight of the scar.

“\emph{Harry Potter?}” gasped the vendor.

“No, Mr.~Durian,” said Harry, eyes dipping briefly to the man’s nametag, “just an amazing imitation—”

And then Harry’s voice stopped in his throat, as he caught sight of the top fold of the \emph{Quibbler.}

\headline{Sloshed Seer spills secrets:\\Dark Lord to return,}

For just an instant, Harry tried to clamp down on his face, before realizing that \emph{not} being shocked could be just as revealing, in a sense—

“Excuse me,” Harry said. His voice sounded a little alarmed, and he didn’t even know whether that was too revealing, or just what his normal reaction \emph{would} be if he didn’t know anything. He’d spent too much time around Slytherins, he was forgetting how to keep secrets from ordinary people. Four Knuts hit the counter. “One copy of the \emph{Quibbler,} please.”

“Oh, no worries, Mr.~Potter!” said the vendor hastily, waving his hands. “It’s—never mind, just—”

A newspaper flew through the air and hit Harry’s fingers, and he unfolded it.

\headline{Sloshed Seer spills secrets:\\Dark Lord to return,\\Wed Draco Malfoy}

“It’s free,” said the vendor, “for \emph{you}, I mean—”

“No,” Harry said, “I was going to buy one anyway.”

The vendor took the coins, and Harry read on.

“Gosh,” Harry said half a minute later, “you get a seer smashed on six slugs of Scotch and she spills all \emph{sorts} of secret stuff. I mean, who’d have thought that Sirius Black and Peter Pettigrew were secretly the same person?”

“Not me,” said the vendor.

“They’ve even got a picture of the two of them together, so we know who it is that’s secretly the same person.”

“Yup,” said the vendor. “Pretty clever disguise, innit?”

“And I’m secretly sixty-five years old.”

“You don’t look half that,” the vendor said amiably.

“And I’m betrothed to Hermione Granger, \emph{and} Bellatrix Black, \emph{and} Luna Lovegood, and oh yes, Draco Malfoy too...”

“Goin’ ter be one interesting wedding,” said the vendor.

Harry looked up from the newspaper, and said in a pleasant voice, “You know, I heard at first that Luna Lovegood was insane, and I wondered if she really was, or if she was just making stuff up and giggling to herself the whole time. Then when I read my second \emph{Quibbler} headline, I decided that she \emph{couldn’t} be insane, I mean, it can’t be \emph{easy} to make this stuff up, you couldn’t do it by \emph{accident}. And \emph{now} do you know what I think? I think she must be mad after all. When ordinary people try to make stuff up, it doesn’t come out like \emph{this}. Something’s got to go really \emph{wrong} with the inside of your head before \emph{this} is what comes out when you start making stuff up!”

The vendor stared at Harry.

“Seriously,” said Harry. “Who \emph{reads} this stuff?”

“You,” said the vendor.

Harry wandered off to read his newspaper.

He didn’t sit at the same nearby table he’d sat down at with Draco, the \emph{first} time he’d prepared to board this train. That seemed like tempting history to repeat itself.

It wasn’t \emph{just} that his first week at Hogwarts had been, judging by the \emph{Quibbler}, fifty-four years long. It was that, in Harry’s humble opinion, his life did not \emph{need} any new threads of complexity.

So Harry found a small iron chair somewhere else, distant from the main crowd and the occasional muffled cracks of parents Apparating in with their children, and sat down and read the \emph{Quibbler} to see if it contained any suppressed news.

And besides the obvious craziness (heaven help them all if any of \emph{that} was real) there was a good deal of snide romantic gossip; but nothing that would really be all that \emph{important} if it was true.

Harry was just reading about the Ministry’s proposed marriage law, to ban all marriages, when—

“Harry Potter,” said a silken voice that sent a shock of adrenaline jolting through Harry’s blood.

Harry looked up.

“Lucius Malfoy,” Harry said, his voice weary. Next time he was going to do the smart thing, and wait outside in the Muggle part of King’s Cross until 10:55\AM.

Lucius inclined his head courteously, sending his long white hair drifting over his shoulders. The man was still carrying that same cane, lacquered in black with a silver snake’s head for its handle; and something about his grip silently said \emph{this is a weapon of deadly power,} not \emph{I am feeble and leaning on this.} His face was expressionless.

Two men flanked him, their eyes continuously scanning, their wands already gripped low in their hands. The two of them moved like a single organism with four legs and four arms, the senior Crabbe-and-Goyle, and Harry thought he could guess which was which, but then it didn’t really matter. They were merely Lucius’s appendages, as certainly as if they’d been the two rightmost toes on his left foot.

“I apologize for disturbing you, Mr.~Potter,” said the smooth, silken voice. “But you have answered none of my owls; and this, I thought, might be my only opportunity to meet you.”

“I have received none of your owls,” Harry said calmly. “Dumbledore intercepted them, I presume. But I would not have answered them if I had, except through Draco. For me to deal with you directly, without Draco’s knowledge, would trespass on our friendship.”

\emph{Please go away, please go away...}

The grey eyes glittered at him. “Is that your pose, then...” said the senior Malfoy. “Well. I shall play along a little. What was your purpose in maneuvering your good friend, my son, into a public alliance with that girl?”

“Oh,” Harry said lightly, “that’s obvious, right? Draco’s working with Granger will make him realize that Muggleborns are human after all. Bwa. Ha. Ha.”

A thin trace of a smile moved over Lucius’s lips. “Yes, that does sound like one of Dumbledore’s plans. Which it is \emph{not}.”

“Indeed,” said Harry. “It is part of my game with Draco, and no work of Dumbledore’s, and that is all I will say.”

“Let us dispense with games,” said the senior Malfoy, the grey eyes suddenly hardening. “If my suspicions are true, you would hardly do Dumbledore’s bidding in any case, \emph{Mr.~Potter.}”

There was a slight pause.

“So you know,” Harry said, his voice cold. “Tell me. At which point, exactly, did you realize?”

“When I read your response to Professor Quirrell’s little speech,” said the white-haired man, and chuckled grimly. “I was puzzled, at first, for it seemed not in your own interest; it took me days to understand whose interest was being served, and then it all finally became clear. And it is also obvious that you are weak, in some ways if not others.”

“Very clever of you,” said Harry, still cold. “But perhaps you mistake my interests.”

“Perhaps I do.” A hint of steel came into the silken voice. “Indeed, that is precisely what I fear. You are playing strange games with my son, to a purpose I cannot guess. That is not a friendly act, and you cannot but \emph{expect} me to be concerned!”

Lucius was leaning upon his cane with both hands now, and both those hands white, and his bodyguards had suddenly tensed.

Some instinct within Harry claimed that it would be a very bad idea to show his fear, to let Lucius see that he could be intimidated. They were in a public train station anyway—

“I find it interesting,” Harry said, putting steel into his own voice, “that you think I could benefit from doing Draco harm. But it is irrelevant, Lucius. \emph{He} is my friend, and I do not betray my friends.”

“\emph{What?}” whispered Lucius. His face showed sheer shock.

Then—

“Company,” said one of the minions, and Harry thought, from the voice, that it must be the senior Crabbe.

Lucius straightened and turned, then let out a hiss of disapproval.

Neville was approaching, looking scared but determined, in tow behind a tall woman who didn’t look scared at all.

“Madam Longbottom,” Lucius said icily.

“Mr.~Malfoy,” returned the woman with equal ice. “Are you being an annoyance to our Harry Potter?”

The bark of laughter that came from Lucius seemed strangely bitter. “Oh, I rather think not. Come to protect him from me, have you?” The white-haired head shifted toward Neville. “And this would be Mr.~Potter’s loyal lieutenant, the last scion of Longbottom, Neville, self-styled of Chaos. How strangely does the world turn. Sometimes I think it must all be mad.”

Harry had no idea at all what to say to that, and Neville looked confused, and frightened.

“I doubt it is the world that is mad,” said Madam Longbottom. Her voice took on a gloating tone. “You seem in a poor mood, Mr.~Malfoy. Did the speech of our dear Professor Quirrell cost you a few allies?”

“It was a clever enough slander of my abilities,” Lucius said coldly, “though only effective upon the fools who believe that I was truly a Death Eater.”

“\emph{What?}” blurted Neville.

“I was under the \emph{Imperius,} young man,” said Lucius, now sounding tired. “The Dark Lord could hardly have begun recruiting among pureblood families without the support of House Malfoy. I demurred, and he simply made sure of me. His own Death Eaters did not know it until afterward, hence the false Mark I bear; though since I did not truly consent, it does not bind me. Some of the Death Eaters still believe I was foremost among their number, and for the peace of this nation I let them believe it, to keep them controlled. But I was not such a fool as to support that ill-fated adventurer of my own choice—”

“Ignore him,” Madam Longbottom said, the instruction addressed to Harry as well as Neville. “He must spend the rest of his life pretending, for fear of your testimony under Veritaseum.” Said with malicious satisfaction.

Lucius turned his back on her dismissively, and faced Harry again. “Will you request this harridan to depart, \emph{Mr.~Potter?}”

“I think not,” said Harry in a dry voice. “I prefer to deal with the part of House Malfoy that’s my own age.”

There was a long pause, then. The grey eyes searched him.

“Of course...” said Lucius slowly. “I \emph{do} feel the fool now. This whole time you were just pretending to have no idea what we were talking about.”

Harry met the gaze, and said nothing.

Lucius raised his cane a few centimeters and struck it hard on the ground.

The world vanished in a pale haze, all sounds went quiet, there was nothing in the universe but Harry and Lucius Malfoy and the snake-headed cane.

“My son is my heart,” said the senior Malfoy, “the last worthwhile thing I have left in this world, and this I say to you in a spirit of friendship: if he were to come to harm, I would give my life over to vengeance. But so long as my son does \emph{not} come to harm, I wish you the best of luck in your endeavors. And as you have asked nothing more of me, I will ask nothing more of you.”

Then the pale haze vanished, showing an outraged Madam Longbottom being blocked from moving forward by the senior Crabbe; her wand was in her hand, now.

“How \emph{dare} you!” she hissed.

Lucius’s dark robes swirled around him, and his white hair, as he turned to the senior Goyle. “We return to Malfoy Manor.”

There were three pops of Apparition, and they were gone.

A silence followed.

“Dear \emph{heavens},” said Madam Longbottom. “What was that about?”

Harry shrugged helplessly. Then he looked at Neville.

There was sweat on Neville’s forehead.

“Thank you very much, Neville,” said Harry. “Your help was greatly appreciated, Neville. And now, Neville, I think you should sit down.”

“Yes, General,” said Neville, and instead of coming over to one of the other chairs near Harry, he semi-collapsed into a sitting position on the pavement.

“You have wrought many changes in my grandson,” said Madam Longbottom. “I approve of some, but not others.”

“Send me the list of which is which,” said Harry. “I’ll see what I can do.”

Neville groaned, but said nothing.

Madam Longbottom gave a chuckle. “I shall, young man, thank you.” Her voice lowered. “Mr.~Potter...\ the speech given by Professor Quirrell is something our nation has long needed to hear. I cannot say as much of your comment on it.”

“I will take your opinion under advisement,” Harry said mildly.

“I dearly hope that you do,” said Madam Longbottom, and turned back to her grandson. “Do I still need to—”

“It’s okay for you to go, Granma,” said Neville. “I’ll be fine on my own, this time.”

“Now \emph{that} I approve of,” she said, and popped and vanished like a soap bubble.

The two boys sat quietly for a moment.

Neville spoke first, his voice weary. “You’re going to try to fix all the changes she \emph{approves} of, right?”

“Not \emph{all} of them,” Harry said innocently. “I just want to make sure I’m not corrupting you.”
\sbreak
Draco looked \emph{very} worried. His head kept darting around, despite the fact that Draco had insisted on them going down into Harry’s trunk, and using a true Quieting Charm and not just the sound-blurring barrier.

“\emph{What} did you say to Father?” blurted Draco, the moment the Quieting Charm went up and the sounds of Platform 9\tq vanished.

“I...\ look, can you tell me what he said to \emph{you,} before he dropped you off?” said Harry.

“That I should tell him right away if you seemed to be threatening me,” said Draco. “That I should tell him right away if there was anything \emph{I} was doing that could pose a threat to \emph{you!} Father thinks you’re \emph{dangerous,} Harry, whatever you said to him today it \emph{scared} him! \emph{It’s not a good idea to scare Father!}”

\emph{Oh, hell...}

“\emph{What} did you talk about?” demanded Draco.

Harry leaned back wearily in the small folding chair that sat at the bottom of his trunk’s cavern. “You know, Draco, just as the fundamental question of rationality is ‘What do I think I know and how do I think I know it?’, there’s also a cardinal sin, a way of thinking that’s the opposite of that. Like the ancient Greek philosophers. They had no clue what was going on, so they’d go around saying things like ‘All is water’ or ‘All is fire’, and they never asked themselves, ‘Wait a minute, even if everything \emph{is} water, how could I possibly \emph{know} that?’ They didn’t ask themselves if they had evidence which discriminated \emph{that} possibility from all the \emph{other} possibilities you could imagine, evidence they’d be very unlikely to encounter if the theory \emph{wasn’t} true—”

“\emph{Harry},” Draco said, his voice strained, “\emph{What did you talk about with Father?}”

“I don’t know, actually,” said Harry, “so it’s very important that I \emph{not} just make stuff up—”

Harry had never heard Draco shriek in horror in quite that high a pitch before.

