\chapter[Interlude: Personal~Financial~Management]{Interlude:\protect\linebreak{}Personal Financial Management}

“But Headmaster,” Harry argued, some of his desperation leaking into his voice, “leaving all of my assets in one undiversified vault full of gold coins—it’s crazy, Headmaster! It’s like, I don’t know, doing Transfiguration experiments without consulting a recognized authority! You just don’t do that with money!”

From the lined face of the old wizard—underneath a festive holiday hat like a catastrophic automobile collision between cars of green and red cloth—a grave, sad look peered out at Harry.

“I’m sorry, Harry,” said Dumbledore, “and I do apologize, but allowing you control over your own finances would give you far too much independence of action.”

Harry’s mouth opened and no sound came out. He was, literally, speechless.

“I will permit you to withdraw five Galleons for Christmas presents,” said Dumbledore, “which is more than any boy your age should spend, but poses no threat, I think—”

“\emph{I can’t believe you just said that!}” the words burst out of Harry’s mouth. “You \emph{admit} to being that manipulative?”

“Manipulative?” said the old wizard, smiling slightly. “No, manipulative would be if I did \emph{not} admit it, or if I had some deeper motive behind the obvious. This is quite straightforward, Harry. You are not yet ready to play the game, and it would be foolish to allow you thousands of Galleons with which to upset the gameboard.”
\sbreak
The bright hustle and bustle of Diagon Alley had increased by a hundredfold and redoubled as Christmas approached, with all the shops enshrouded in brilliant sorceries that flashed and sparkled as though the season’s spirit was about to blaze out of control and turn the whole area into a cheerful holiday crater. The streets were so crowded with witches and wizards in festive and \emph{loud} clothing that your eyes were assaulted almost as severely as your ears; and it was clear, from the bewildering variety of the shoppers, that Diagon Alley was considered an international attraction. There were witches wrapped in giant swathes of cloth like toweled mummies, and wizards in formal top hats and bath-robes, and young children barely past toddling age who were decorated with lights that blazed almost as bright as the shops themselves, as their parents took them hand in hand through that magic wonderland and let them shriek to their heart’s content. It was the season to be merry.

And in the midst of all that light and cheer, a note of blackest night; a cold, dark atmosphere that cleared a few precious paces of distance even in the midst of all that crush.

“No,” said Professor Quirrell, with a look of grim revulsion, like he’d just bitten into food that not only tasted horrible but was morally repugnant to boot. It was the sort of grim face an ordinary person might make after biting into a meat pie, and discovering that it was rotten and had been made from kittens.

“Oh, come \emph{on},” Harry said. “You must have \emph{some} ideas.”

“Mr.~Potter,” Professor Quirrell said, his lips set in a thin line, “I agreed to act as your adult guardian on this expedition. I did not agree to advise you on your choice of presents. I don’t do Christmas, Mr.~Potter.”

“How about Newtonmas?” Harry said brightly. “Isaac Newton actually \emph{was} born on December 25\Th, unlike some other historical figures I could name.”

This failed to impress Professor Quirrell.

“Look,” said Harry, “I’m sorry, but I’ve got to do \emph{something} special for Fred and George and I’ve got no idea of my options.”

Professor Quirrell made a thoughtful humming sound. “You could ask which family members they most dislike, and then hire an assassin. I know someone from a certain government-in-exile who is quite competent, and he would give you a discount on multiple Weasleys.”

“\emph{This} Christmas,” Harry said, dropping his voice into a lower register, “give your friends the gift...\ of \emph{death}.”

That made Professor Quirrell smile. It went all the way to his eyes.

“Well,” said Harry, “at least you didn’t suggest getting them a pet rat—” Harry’s mouth snapped shut, and he was regretting the words almost as soon as they were out of his mouth.

“Pardon me?” said Professor Quirrell.

“Nothing,” Harry said at once, “long dumb story.” And telling it seemed wrong somehow, maybe because Harry was afraid Professor Quirrell would have laughed even if Bill Weasley \emph{hadn’t} been cured and everything put back to right...

And where had Professor Quirrell \emph{been} that he’d never heard the story? Harry had gotten the impression that everyone in magical Britain knew.

“Look,” said Harry, “I’m trying to \emph{solidify their loyalty to me,} you know? Make the Weasley twins my minions? Like the old saying goes: A friend isn’t someone you use once and then throw away, a friend is someone you use over and over again. Fred and George are two of the most useful friends I have in Hogwarts, Professor Quirrell, and I plan to use them over and over again. So if you’d help me be Slytherin here, and suggest something they might be \emph{very} grateful for...” Harry’s voice trailed off invitingly.

You just had to pitch these things the right way.

They walked on for a good way before Professor Quirrell spoke again, his voice practically dripping with distaste. “The Weasley twins are using secondhand wands, Mr.~Potter. They would be reminded of your generosity with every Charm they cast.”

Harry clapped his hands together in involuntary excitement. Just put the money on account at Ollivander’s, and tell Mr.~Ollivander to never refund it—no, better yet, to send it to Lucius Malfoy if the Weasley twins didn’t show up before the start of their next school year. “That’s \emph{brilliant}, Professor!”

Professor Quirrell did not look like he appreciated the compliment. “I suppose I can tolerate Christmas in \emph{that} spirit, Mr.~Potter, though only barely.” Then he smiled slightly. “Of course that will cost you fourteen Galleons, and you only have five.”

“\emph{Five} Galleons,” Harry said, with a sniff of outrage. “Just who does the Headmaster think he’s dealing with, anyway?”

“I think,” said Professor Quirrell, “that it simply did not occur to him to fear the consequences if you turned your ingenuity to the task of obtaining funds. Though you were wise to lose, rather than making it an explicit threat. Out of curiosity, Mr.~Potter, what \emph{would} you have done if I hadn’t turned away in boredom while you, in a fit of childish pique, counted out five Galleons worth of Knuts?”

“Well, the easiest way would’ve been to borrow money from Draco Malfoy,” said Harry.

Professor Quirrell chuckled briefly. “Seriously, Mr.~Potter.”

\emph{Duly noted.} “Probably I’d have done a few celebrity appearances. I wouldn’t resort to anything economically disruptive just for spending money.” Harry had checked, and he \emph{would} be allowed to keep the Time-Turner while he went home for the holidays, so that his sleep cycle didn’t start to rotate. But then it was \emph{also} possible that someone kept an eye out for magical day traders. The gold and silver trick would’ve taken work on the Muggle end, and seed funding, and the goblins might’ve gotten suspicious after the first cycle. And starting a real bank would be a \emph{lot} of work... Harry hadn’t \emph{quite} worked out any money-making methods that were fast \emph{and} certain \emph{and} safe, so he’d been very glad when Professor Quirrell had turned out to be so easily fooled.

“I do hope those five Galleons will be enough to last, since you counted them so carefully,” said Professor Quirrell. “I doubt the Headmaster shall be so eager to entrust me with your vault key a second time, once he discovers I’ve been tricked.”

“I’m sure you did your best,” Harry said with deep gratitude.

“Do you need any assistance finding a safe place to store all those Knuts, Mr.~Potter?”

“Well, sort of,” said Harry. “Do you know of any good investment opportunities, Professor Quirrell?”

And the two of them walked on, in their tiny sphere of silence and isolation, through the brilliant and bustling crowds; and if you looked carefully, you would see that where they went, leafy boughs faded, and flowers withered, and children’s toys that played cheerful bells changed to lower and more ominous notes.

Harry \emph{did} notice, but he didn’t say anything, just smiled a little to himself.

Everyone had their own way of celebrating the holidays, and the Grinch was as much a part of Christmas as Santa.
