\chapter{Roles, Final}

\section{Sunday, April 19th, 6:34\pm}

\lettrine{D}{aphne} Greengrass walked quietly toward the Greengrass room below the Slytherin dungeons, the privilege of an Ancient House; on her way to drop off her trunk from the Hogwarts Express, before she joined the other students for dinner. The whole private area had been hers alone ever since Malfoy had gone. Her hand, held behind her, made repeated come-along gestures at her huge emerald-studded trunk, which seemed hesitant to follow. Maybe the enchantments on the sturdy old family device needed to be reapplied; or maybe her trunk was reluctant to follow her into Hogwarts, which was no longer safe.

There’d been a long talk between Mother and Father, after they’d been told about Hermione; with Daphne hiding around a doorway to listen, choking back her tears and trying not to make sounds.

Mother had said that the sad fact was that if only one student died every year, well, that still made Hogwarts safer than Beauxbatons, let alone Durmstrang. There were more ways for a young witch to die than being murdered. Beauxbatons’s Transfiguration Master just wasn’t on the same level as McGonagall, Mother had said.

Father had soberly remarked how important it was for the Greengrass heir to stay at Hogwarts where all the other Noble families sent their children to school (it was the reason for the old tradition of the Noble families synchronizing the birth of their heirs, to put them in the same year of Hogwarts, if they could). And Father had said that being heiress to a Most Ancient House meant you couldn’t always stay away from trouble.

She could have done without hearing that last part.

Daphne gulped hard, as she turned the doorknob, and opened the door.

“Miss~Greengrass—” whispered a shadowy, silvery-robed figure.

Daphne screamed and slammed the door and drew her wand and turned to run.

“Wait!” cried the voice, now higher and louder.

Daphne paused. That couldn’t \emph{possibly} be who it had sounded like.

Slowly, Daphne turned, and opened the door again.

“\emph{You!}” Daphne said in astonishment, as she saw the face beneath the hood. “I thought you were—”

“I come back to you now,” the silvery-robed figure said in a strong voice, “at the turn of the—”

“\emph{What are you doing in my bedroom?}” shrieked Daphne.

“I heard you can cast the mist form of the Patronus Charm. Can I see?”

Daphne stared, and then her blood began to burn. “Why?” she said, keeping her wand level. “So you can \emph{kill} everyone in Slytherin who casts un-Slytherin spells? We all \emph{know} who it was had Hermione killed!”

The figure’s voice rose. “I testified under Veritaserum that I tried to help Miss~Granger! I really was trying to help her, when I grabbed her hand on the roof, when I helped her off the floor—”

Daphne kept her wand level. “Like your father couldn’t tamper with the Aurors’ record, if he wanted to! I wasn’t born yesterday, Mister \emph{Malfoy!}”

Slowly, as if not to cause alarm, the silver-robed figure drew a wand from his robes. Daphne’s hand tightened on her own wand, but then she recognized the position of the fingers on the wand, the stance the figure was assuming, and she drew a shocked breath—

“\emph{Expecto Patronum!}”

Silver light leapt from the end of the other’s wand—and condensed, forming a shining serpent that seemed to coil in the air as though nesting there.

She just gaped.

“I \emph{did} try to help Hermione Granger,” Draco Malfoy said with a level voice. “Because I know the sickness at the heart of Slytherin’s House, the reason why so many of us can’t cast the Patronus Charm any more, is hate. Hate of Muggleborns, or just anyone really. People think that’s all Slytherin is about now, not cunning or ambition or honourable nobility. And I even know, because it’s obvious if you just look, that Hermione Granger wasn’t weak at magic.”

Daphne’s mind had gone completely blank. Her eyes darted around nervously, just to check that there wasn’t blood coming from under the doors, like the last time Something had Broken.

“And I’ve also figured out,” Draco Malfoy said quietly, as the silver snake went on shining with unmistakeable light and warmth, “that Hermione Granger never really tried to kill me. Maybe she was False-Memory-Charmed, maybe she was Legilimized, but now that she’s been murdered, it’s obvious that Miss~Granger was the target in the first place, when somebody tried to set her up for murdering me—”

“D-do-do you know what you’re \emph{saying?}” Daphne’s voice broke. If Lucius Malfoy heard his heir saying that—he’d \emph{skin} Draco and turn him into \emph{trousers!}

Draco Malfoy smiled, metallic robes gleaming in the light of his full corporeal Patronus; it was a smile both arrogant and dangerous, like being turned into a pair of leather trousers was beneath his concerns. “Yes,” said Draco, “but it doesn’t matter now. House Malfoy is returning House Potter’s money and cancelling the debt.”

Daphne walked over to her bed and then fell on it, hoping she could wake up from the dream once she was in bed.

“I’d like you to join a conspiracy,” said the figure in the shining robes. “Everyone in Slytherin who can cast the Patronus Charm, and everyone who can learn. That’s how we’ll know to trust each other, when the Silvery Slytherins meet.” With a dramatic gesture, Draco Malfoy cast back his hood. “But it won’t work without \emph{you,} Daphne Greengrass. You and your family. Your mother will negotiate it with Father, but I’d like the Greengrasses to hear the proposal from you, first.” Draco Malfoy’s voice lowered grimly. “There is much we must speak of, before we eat dinner.”

\later

Harry Potter had, apparently, taken to being invisible; they had glimpsed his hand only briefly, when he was handing them the list, written on strange not-parchment. Harry had explained that, all things considered, he didn’t really think it was smart for him to be \emph{findable} except on special occasions, so he was just going to deal with people as a disembodied floating voice from now on, or as a brilliant silver light that hid behind corners where nobody could see it, and which could always find his friends no matter where they tried to hide. It was, in all honesty, one of the creepiest things which Fred and George had ever heard, over a lifetime which had included filling the shoes of every student in second-year Slytherin with Transfigured live millipedes. Fred and George didn’t think this could possibly be good for anyone’s sanity, but they didn’t know what to say. It couldn’t be denied, they’d seen with their own four eyes, that Hogwarts…

…wasn’t safe…

“I don’t know who you went to for the False Memory Charm on Rita Skeeter,” said the sourceless voice of Harry Potter. “Whoever it is…probably \emph{won’t} be able to fill this order directly, but they may know someone who can get things from the Muggle world. And—I know it may cost extra, but as few people as possible should know that Harry Potter is related to this.” Another flash of a small boy’s hand, and a bag hit the ground with the clinking noise. “Some of these items are expensive even in the Muggle world, and your contact may have to go outside Britain; but one hundred Galleons will be enough to pay for it all, I hope. I’d tell you where the Galleons came from, but I don’t want to spoil tomorrow’s surprise.”

“What \emph{is} this stuff?” said Fred or George, as they looked over the list. “Our father is a Muggle expert—”

“—and we don’t recognize \emph{half} this stuff—”

“—why, we don’t recognize any of it—”

“—just what are you planning to \emph{do?}”

“Things have become serious,” Harry’s voice said softly. “I don’t know what I’ll have to do. I may need the power of the Muggles, not just the wizards, before this is done—and I might need it right away, with no time to prepare. I’m not \emph{planning} to use any of this. I just want it around in case of…contingencies.” Harry’s voice paused. “Obviously I owe you more than I can ever repay and you won’t \emph{let} me give you \emph{any} of what you deserve, I don’t even know how to say thank you properly, and all I can do is hope that some day when you grow up you’ll be more sensible about this whole thing and would you \emph{please} take a ten percent commission—”

“Shut up, you,” said George or Fred.

“For God’s sake, you went after a troll for me and Fred had his ribs broken!”

They both just shook their heads. Harry had stayed behind when they’d told him to run, and stepped forward to distract the troll from eating George. Harry was the kind of person, they knew, who’d think that something like that didn’t cancel out what he owed the Weasley twins, that his own deed wasn’t properly commensurate. But what the Weasleys knew, and Harry wouldn’t understand until he was older, was that it meant that nothing was owed, or ever could be owed between them. It was a strange kind of selfishness, they thought, that Harry could understand kindness within himself—never dreaming of asking of money from anyone he’d helped more than they’d helped him, or calling that a debt—while being apparently unable to conceive that others might want to act the same way toward \emph{him}.

“Remind me to buy you a copy of the Muggle novel \emph{Atlas Shrugged,}” the sourceless voice said. “I’m starting to understand what sort of person can benefit from reading it.”

\latersection{Monday, April 20th, 7:00\pm}

It happened without any intervention or sign from the Head Table, as the students had finished their subdued dinner; it happened with no permission or forgiveness asked from the Professors or the Headmaster.

Shortly after the dessert dishes had appeared, a student stood up from the Slytherin Table and calmly made his way, not to the front of the Head Table, but toward the opposite side of the Four Tables of Hogwarts. A few whispers broke out at the sight of the white-blonde short-cropped hair, as Draco Malfoy stood there, silently regarding all of Hogwarts. Draco Malfoy had said almost nothing since his surprise return. The Slytherin had condescended neither to confirm nor deny that he had returned because, with Hermione Granger dead at his family’s hand, he no longer had anything to fear.

Then Draco Malfoy took up a spoon in one hand, and a glass of water in the other, and began tapping, producing a clear ringing sound.

\emph{Ting.}

\emph{Ting.}

\emph{Ting.}

It produced more excited babble at first. At the Head Table, the various Professors looked in puzzlement toward the Headmaster in his great chair, but the Headmaster gave no sign, and so the faculty did nothing.

Draco Malfoy continued tapping the spoon upon his glass, until the room fell silent, waiting.

Then another student arose from the Ravenclaw table, and made his way to where Draco Malfoy was standing, turning to face Hogwarts at his side. Breaths were drawn in surprise; those two should have been the bitterest of enemies—

“I, and my Father, the Lord of the Noble and Most Ancient House of Malfoy,” Draco Malfoy said in a clear voice, “have come to realize that there are ill forces at work in Hogwarts. That these ill forces, did wish Hermione Granger harm. That Hermione Granger was perhaps compelled, against her will, to raise her hand against our House; or perhaps she and I were both Memory-Charmed. We now say that whoever dared use the heir of Malfoy so, is the enemy of House Malfoy, upon whom we shall have our vengeance. And that honour be served, we have returned all moneys taken from House Potter, and cancelled all debt.”

Then Harry Potter spoke. “House Potter acknowledges that it was an honest mistake, and holds House Malfoy no ill will. We believe and publicly say that House Malfoy was not at fault in Hermione Granger’s death. Whoever harmed Hermione Granger is the enemy of House Potter, upon whom we shall have our vengeance. Both of us.”

Then Harry Potter began to walk back to the Ravenclaw table, and the babble of sheer, utter, reality-crashing bewilderment began to explode—

Draco Malfoy resumed tapping his spoon against his water-glass, creating a clear ringing chime.

\emph{Ting.}

\emph{Ting.}

\emph{Ting.}

And other students arose, from other tables, making their way to where Draco Malfoy stood, arranging themselves at his side, or behind him, or before him.

There was a dread silence in the Great Hall, a sense of the world shifting, of realigning Powers, almost tangible in the air.

“My father, Owen Greengrass, with the consent and full backing of my mother, the Lady of the Noble and Most Ancient House of Greengrass,” Daphne Greengrass spoke.

“And my forefather, Charles, of the House of Nott,” said the former Lieutenant Nott, once Theodore of Chaos, now standing behind Draco Malfoy.

“And my grand-aunt, Amelia, of the House of Bones, also Director of the Department of Magical Law Enforcement,” said Susan Bones, who stood next to Daphne Greengrass, beside whom she had fought.

“And my grandmother, Augusta, of the Noble and Most Ancient House of Longbottom,” said Neville Longbottom, who had returned for this one night.

“And my father, Lucius, the Lord Malfoy, of the Noble and Most Ancient House of Malfoy!”

“Together with Alanna Howe constituting a majority of the Hogwarts Board of Governors!” Daphne Greengrass said clearly. “Have, to ensure the safety of all students, including their own children, passed the following Educational Decrees upon the Hogwarts School of Witchcraft and Wizardry!”

\later

“First!” Daphne said. Daphne was trying to keep her trembling under control, as she faced the Four Houses at the forefront of the five. There was only so far her parents’ lessons in speech-making could take her. Daphne’s eyes darted down quickly to her hand, upon which, written with a quill in faint red ink, cues to her lines had been written. “Students are not to go anywhere alone, not even to the toilets! You will travel in groups of at least three, and every group must have a sixth-year or seventh-year student!”

“Second!” Susan Bones said from behind her, voice almost firm. “To further ensure the students’ safety, nine Aurors have been dispatched to Hogwarts to form an Auxiliary Protective Force!” Susan took a small, round glass object from within her robes, one of the communicators that the DMLE used, which they’d all been given. Susan raised it to her mouth and said, her voice now higher, “Auror Brodski, this is Susan Bones. \emph{Enter!}”

The doors to the Hall slammed open, and in marched nine Aurors in the reinforced leather gear they used when on duty. At once they spread out, two Aurors taking up station by each of the four tables, and the last took up watch at the Head Table. There were more gasps.

“Third!” said Draco Malfoy, his voice commanding. Malfoy had apparently memorized his own lines, since there was nothing written on his hand that Daphne could see. “In the face of a common enemy who does not balk at killing students from any House, the four Houses of Hogwarts must come together and act as one! To emphasize this, the House Points system is temporarily suspended! \emph{All} Professors will encourage solidarity between Houses, by decree of the Hogwarts Board of Governors!”

“Fourth!” recited Neville Longbottom. “All students not already in the Defence Professor’s after-school classes, will receive special training in self-defence by Auror instructors!”

“Fifth!” Theodore Nott yelled in a menacing tone. “All fighting in the corridors or anywhere outside of Defence lessons will be dealt with severely! Fight together or don’t fight at all!”

“Sixth!” said Daphne Greengrass, and took a deep breath. When she’d found out what was planned, she’d made her own little extra request to Mother through the Floo. Even with Lucius Malfoy going along with Amelia Bones—a thought her mind was still having trouble grasping—the Greengrass swing vote had still been vital, since Jugson and his own faction had refused to back Malfoy. Not to mention that Bones didn’t trust Malfoy, and Malfoy didn’t trust Bones. So Mother had demanded, and the Greengrasses had received—”Since Memory Charms have been used on students without setting off wards, it is possible that someone on the Hogwarts faculty may be implicated. Therefore! The Auxiliary Protective force reports directly to my father, Lord Greengrass!” And this part was only symbolic, she knew, there’d be no reason anyone wouldn’t just contact the Aurors directly; but it might turn into more, some day, which was why she’d asked Mother to demand it—“And if anyone wants to report something to the Auxiliary Protectors, they can talk to the Aurors, or go through \emph{me}—” Daphne’s arm swept behind her to indicate the gathered students. “The duly appointed President of the Auxiliary Protective Special Committee!”

And Daphne paused dramatically. They’d all rehearsed this part.

“We don’t know who the enemy is,” said Neville, whose voice did not squeak.

“We don’t know what the enemy wants,” said Theodore, still looking menacing.

“But we know who the enemy is attacking,” said Susan, as fierce as when she’d taken on three seventh-year students.

“The enemy is attacking Hogwarts students,” said Draco Malfoy, clear and commanding, like all this was his natural element.

“And Hogwarts,” spoke Daphne of Greengrass, feeling her blood burn like it never had before in her life, “is going to \emph{fight back.}”

%  LocalWords:  aphne un Alanna
