\chapter{Something to Protect: Albus Dumbledore}

\lettrine{H}{arry} stood now before the gargoyles that guarded the Headmaster’s, no, the Headmistress’s office. He had been summoned by Professor Sinistra, told that it was an emergency, but the gates were not opening for him.

Experiment had showed that the Stone made one Transfiguration permanent every three minutes and fifty-four seconds, irrespective of the size of object Transfigured. Just once, holding the Philosopher’s Stone up to the light of Harry’s most powerful torch in an otherwise darkened closet, Harry had thought he’d seen an array of tiny points inside the chunk of crimson glass; but Harry hadn’t been able to see it again, and now suspected himself of having imagined it. The Stone had no other powers that Harry could detect, nor did it respond to any attempted mental commands.

Harry had given himself until noon tomorrow to figure out how to begin using the Stone without it being grabbed by someone else, trying not to think about what was still happening, what had always been happening, in the meanwhile.

Ten minutes late, Minerva McGonagall approached, moving in a swift stride. Her arms were full of papers, she was once again wearing the Sorting Hat.

The gargoyles, with a brief sound of grinding stone, bowed low before her.

“The new password is ‘Impermanence’,” Minerva said to the gargoyles, and they stepped aside. “I’m sorry, Mr~Potter, I was delayed—”

“Understood.”

Minerva mounted the long spiral stairs, climbing instead of waiting to be carried, Harry following behind her.

“We are meeting with Amelia Bones, Director of the Department of Magical Law Enforcement; with Alastor Moody, whom you have met; and with Bartemius Crouch, Director of the Department of International Magical Cooperation,” Minerva said as she climbed. “They are Dumbledore’s heirs as much as you or I.”

“How—how’s Hermione doing?” Harry hadn’t had a chance to ask until now.

“Filius said she seemed rather in shock, which I suppose is not surprising. She asked where you were, was told you were at a Quidditch game, asked where you really were, and refused to speak with anyone about what happened until she was allowed to talk with you. She was taken to St. Mungo’s, where,” the Headmistress now sounded slightly perturbed, “a standard diagnostic Charm showed Miss~Granger as a healthy unicorn in excellent physical condition except that her mane needs combing. Charms to detect active magic have each time detected her as being in the process of transforming into another shape. There was an Unspeakable who showed up before Filius, ah, removed him. He performed certain spells he probably ought not to have known, and declared that Hermione’s soul was in healthy condition but at least a mile away from her body. At that point the senior healers gave up. She’s currently alone in a cell with the rats and flies—”

“She’s what?”

“I’m sorry, Mr~Potter, that’s Transfiguration jargon. Miss~Granger is in an isolation chamber with a cage of tame rats, and a box of flies that will bear offspring in a single day. Logic suggests that whatever mystery underlies her resurrection, it left behind an emanation that is causing the healers’ Charms to produce gibberish. But if nothing happens to the rats or to the flies’ offspring, Miss~Granger will be declared safe to return to Hogwarts after she wakes up again tomorrow morning.”

Harry still wasn’t sure…wasn’t sure at \emph{all}, what Hermione would think of having been resurrected, at least under these particular circumstances. He didn’t actually think Hermione would yell at him for doing it wrong. That was just Harry’s brain trying to imagine her as a stereotype. Harry had been legitimately exhausted and not thinking very straight when he’d come up with that cover story, and Hermione would probably understand that part. But he couldn’t imagine what Hermione \emph{would} think…

“I wonder how Miss~Granger will feel about having also vanquished You-Know-Who,” Minerva said reflectively, climbing the moving stairs fast enough that Harry felt out of breath trying to keep up. “And people believing the most interesting things about her.”

“You mean, because she’s always self-identified as a normal academic genius, and now a bunch of people think of her as the Girl-Who-Revived and everyone wants to shake her hand?” Harry said. \emph{Even though she doesn’t remember doing anything to earn it. Even though it was all someone else’s work and other people’s sacrifices, and she’s getting the credit. Even though she doesn’t feel like she’s actually done anything worthy of the way other people treat her, and she’s not sure if she can ever live up to the person they imagine.} “Gosh, I don’t know, I can’t imagine what that feels like.”

\emph{Maybe I shouldn’t have subjected her to it. But people had to be given \emph{something} to believe or heaven knows what they’d have made up. Feeling guilty about this would be stupid. I think.}

The two of them reached the top of the stairs, and came into the office filled with dozens of strange objects, all facing a great desk and a mighty throne behind it.

Minerva’s hand passed over one of those objects, the one with golden wibblers, her eyes closing briefly. Then Minerva took off the Sorting Hat and put it on a hat rack that held three slippers for left feet. She transformed the mighty throne into a simple cushioned chair and the great desk into a round table, around which four other chairs rose up.

Harry watched it all with a strange pang in his throat. He knew, without either of them saying anything, that there should have been more ceremony for the changing of the chairs, the changing of the table. Much more ceremony, for the first time the Headmistress sat down in her new office. But for whatever reason, there wasn’t time, and Minerva McGonagall was discarding all that for speed.

A wave of Minerva’s wand lit the Floo-fire in the fireplace, even as Minerva sat down into the chair that had been Dumbledore’s.

Harry quietly took one of the chairs around the table, sitting at Minerva’s left.

Almost at once, the Floo-fire burned emeraldine and whirled out Alastor Moody, who spun around with his wand raised, taking in the whole room at a seeming glance, and then pointed his wand directly at Harry and said “Avada Kedavra.”

It happened so fast, and took him so completely by surprise, that Harry’s wand wasn’t even half-raised by the time Alastor Moody finished the incantation.

“Just checking,” Alastor said to the Headmistress, whose own wand was now pointed at Alastor, her mouth open as if to say words she couldn’t find. “Voldie would’ve tried to dodge, if he’d taken over the boy’s body last night. I’ll still need to check the Granger girl, though.” Alastor Moody went to Minerva’s right and sat down.

Harry had thought, in that split second, to try producing a wordless silver Patronus glow from his wand; but his wand hadn’t been in place to intercept in time, not even close.

\emph{Well, if I was feeling invincible before, that does for that. What a valuable life lesson, Mr~Moody.}

Then the Floo-fire burned green again, and spat out the oldest, grimmest, toughest-looking witch Harry had ever seen, like beef jerky given human shape. The old witch did not have her wand in her hand, but she projected an air of authority that was stronger and stricter than Dumbledore’s.

“This is Director Amelia Bones, Mr~Potter,” said Headmistress McGonagall, who’d regained her poise. “We are still waiting on Director Crouch—”

“The corpse of Bartemius Crouch Jr. was identified among the dead Death Eaters,” the old witch said without preamble, even as she continued toward the chairs. “It took us entirely by surprise, and I’m afraid Bartemius is in considerable grief about it, on both counts. He will not be with us today.”

Harry kept the flinch inward.

Amelia Bones sat down in a chair, sitting to Moody’s own right.

“Headmistress McGonagall,” said the elder witch, still without hesitation or delay, “The Line of Merlin Unbroken, which Dumbledore left to me in regency, is not responding to my hand. The Wizengamot must have a Chief Warlock who is trustworthy, \emph{at once;} matters are in great flux in Britain. I must know what Dumbledore has done, immediately!”

“Crap,” muttered Moody. His mad-eye was rolling wildly. “That’s not good, not good at all.”

“Yes, well,” said Minerva McGonagall, who looked rather apprehensive. “I cannot say that for certain. Albus—well, he clearly had an intimation that he might not survive this war. But I do not think he was expecting Miss~Granger to come back from the dead and kill Voldemort only hours later. I do not think Albus was expecting that at all. I am not quite sure what his legacies will make of that—”

Amelia Bones rose half out of her chair. “You mean to imply that the \emph{Granger} girl may have inherited the Line of Merlin Unbroken? This is a \emph{catastrophe!} She is twelve years old, untested—surely Albus would not be so irresponsible as to leave the Line to whoever happened to defeat Voldemort, without knowing \emph{who!}”

“Well, putting it simply,” Minerva said. Her fingers squared the paperwork she’d taken with her, now lying on the desk. “Albus \emph{did} think he knew who would defeat Voldemort. There was a prophecy concerning it, a verified one, which now seems to be in abeyance, or—I don’t know, Madam Bones! I have one letter for Mr~Potter that I am to give him in the event of Albus’s death or other departure, and then another letter that Albus said Mr~Potter would be able to open only after he defeated Voldemort. I am not sure what will happen to it now. Perhaps Miss~Granger will be able to open it, or perhaps it can never be opened—”

“Hold up,” Mad-Eye Moody said. He reached into his robes, drew out a long, grey-knobbed wand that Harry recognized; it was Dumbledore’s wand, of a form and style not like any other wand in Hogwarts. Moody laid the wand on the table. “Before we go any further, Albus left me an instruction or two of his own. Pick up this wand, boy.”

Harry hesitated, thinking.

\emph{Albus Dumbledore sacrificed himself for me. He trusted Moody. This probably isn’t a trap.}

Then Harry began to reach for the wand.

It leaped up and flew across the table, into Harry’s hand. And the moment that Harry’s fingers grasped the handle it was like he heard a song, a pæan of glory and battle that resonated in his mind. A wave of white fire ran up the handle and over the wood, magnifying as it moved, bursting from the end in a tremendous spray of sparks. Through the wood beneath his fingers ran a sense of strength and constrained danger, like a leashed wolf.

Harry was also receiving an impression of distinct skepticism, as if the wand had some level of awareness, and it was wondering how the hell it had ended up being held by a Hogwarts first-year.

“Right,” said Mad-Eye Moody into the puzzled stares. “So it wasn’t Miss~Granger who defeated Voldie, then. Didn’t think so.”

“What.” Amelia Bones spoke the word flatly.

Mad-Eye Moody gave her a respectful nod. “Albus said this wand goes to whoever defeats its previous master. Took it off old Grindie, he did. Then Voldie defeated Albus, yesterday. Do I need to spell it out, Amelia?”

Amelia Bones was staring at Harry, her mouth wide open.

“That might not be right,” Harry said. He swallowed another pang of the awful guilt. “I mean, Voldemort used me as a hostage because I, I was stupid, and Dumbledore gave himself up to save me, maybe the wand thinks that counts as my defeating Dumbledore. Um, I did defeat Voldemort, though. Vanquished him. But I think it’s better if nobody has any idea I was there.”

Beep. Tick. Whirr. Ding. Poot.

“\emph{That} must have taken \emph{some} doing,” Mad-Eye said. The scarred man inclined his head slowly, a gesture of profound respect. “Don’t feel too guilty about losing Albus and David and Flamel, son, no matter how stupid you were. You won in the end. All of us put together never could. Just to check, son, you and David also destroyed Voldie’s horcrux? And you’re \emph{certain} it was the real thing?”

Harry hesitated, weighing up the probable consequences of trust, the possible disasters of silence, and then shook his head to Moody in reply. He’d been planning to tell at least McGonagall about what was now inside her school, anyway. “Voldemort had…rather a lot of horcruxes, actually. So instead I Obliviated most of his memories, then Transfigured him into this.” Harry raised his hand, and silently pointed to the emerald on his ring.

Splat. Boing. Splat. Splat.

“Huh,” Moody said, leaning back in his chair. “Minerva and I will be putting some alarms and enchantments on that ring of yours, son, if you don’t mind. Just in case you forget to sustain that Transfiguration one day. And don’t go hunting any other Dark wizards, ever, just live a quiet and peaceful life.” The scarred man took a handkerchief and wiped at the beads of sweat that had now appeared on his forehead. “But well done, lad, you and David both, may he rest in peace. This was his idea, I’m guessing? Well done, I say.”

“Indeed,” said Amelia Bones, who had now regained her composure. “We all owe the both of you a tremendous debt of gratitude. But I say again that there is urgent business regarding the Line of Merlin Unbroken.”

“I believe,” Minerva McGonagall said slowly, “that I had best give Albus’s letters to Mr~Potter, right now.” At the top of her stack of papers now lay a parchment envelope, and a rolled-up parchment scroll sealed with a grey ribbon.

The Headmistress gave Harry the parchment envelope, first, and Harry opened it.

\later

\begin{writtenNote}
If you are reading this, Harry Potter, then I have fallen to Voldemort, and the quest now lies in your hands.

Though it may shock you to learn, this was the end that I wished in my heart would come to pass. For as I write this, it yet seems possible that Voldemort may fall by my own hand. And then, in time, I shall myself become the darkness you must overcome, to enter fully into your power. For it was said once that you might need to raise your hand against your mentor, the one who made you, who you loved; it was said that you might be my downfall. If you are reading this, then that shall never come to pass, and I am glad of it.

Even so, Harry, I would spare you this, the lonely fight against
Voldemort. I write this, vowing to shelter you as long as I can, no matter the final cost to myself. But if I have failed, then know that I am glad of it, in my own selfish way.

With my passing, there is none left to oppose Voldemort as an equal save you. His shadow will fall long and terrible over magical Britain, and many will suffer and die for it. That shadow will not lift until you destroy its source, until you cleanse the heart of the darkness. How you are to do this, I do not know. If Voldemort knows not the power you bear, then neither do I\@. You must find that power within yourself, you must learn to wield it, you must become Voldemort’s final judge, and I beg you not to make the error of showing him mercy.

My wand, which I have left to you in Moody’s keeping, you must not dare to wield against Voldemort. For when that wand’s master is defeated, it passes to the victor in turn. When you have conquered my conqueror, then the wand will answer truly to your hand; but if you try to turn it against Voldemort before then, it will betray you for certain. Keep it out of Voldemort’s grasp at all costs. I should advise you not to wield that wand at all, yet it is a device of great power, which you might need in some desperate case. But if you pick it up you must fear its treachery at all times.

In my absence, the Wizengamot will inevitably fall to Malfoy. The Line of Merlin Unbroken I have passed to you, with Amelia Bones as your regent, until you come of age or come into your power. But she cannot oppose Malfoy for long, not with myself gone and Voldemort returned to advise him. Soon, I think, the Ministry will fall, and Hogwarts will become the last fortress. To Minerva I have left Hogwarts’s keys, but you alone are its prince, and she will help you however she can.

Alastor now leads the Order of the Phœnix. Heed his words well, both his advice and his confidences. It is one of my life’s greatest regrets that I did not heed Alastor more and sooner.

That you will in the end defeat Voldemort, I have no doubt.

For that will be only the beginning of your life’s destiny. Of that, too, I am certain.

When you have vanquished Voldemort, when you have saved this country, then, I hope, you may embark upon the true meaning of your days.

Hurry then to begin.

\letterClosing[Yours in death (or in whatever),]{Dumbledore.}

P.S. The passwords are ‘phœnix’s price’, ‘phœnix’s fate’, and ‘phœnix’s egg’, spoken within my office. Minerva can move those rooms to where you can reach them more easily. \end{writtenNote}

\later

Harry folded up the parchment and put its back into the envelope, frowning thoughtfully, then took the grey-ribboned scroll from the Headmistress. When the long grey wand in Harry’s hand touched the ribbon, it fell away at once; and Harry unrolled the scroll, and read it.

\later

\begin{writtenNote}
\letterAddress{Dear Harry James Potter-Evans-Verres:}

If you are reading this, you have defeated Voldemort.

Congratulations on that.

I hope you had some time in which to celebrate before you opened this scroll, because the news in it is not cheerful.

During the First Wizarding War, there came a time when I realised that Voldemort was winning, that he would soon hold all within his hand.

In that extremity, I went into the Department of Mysteries and I invoked a password which had never been spoken in the history of the Line of Merlin Unbroken, did a thing forbidden and yet not utterly forbidden.

I listened to every prophecy that had ever been recorded.

And so I learned that my troubles were far worse than Voldemort.

From certain seers and diviners have come an increasing chorus of foretellings that this world is doomed to destruction.

And you, Harry James Potter-Evans-Verres, are one of those foretold to destroy it.

By rights I should have ended your line of possibility, stopped you from ever being born, as I did my best to end all the other possibilities I discovered on that day of terrible awakening.

Yet in your case, Harry, and in your case alone, the prophecies of your apocalypse have loopholes, though those loopholes be ever so slight.

Always ‘he will end the world’, not ‘he will end life’.

Even when it was said that you would tear apart the very stars in heaven, it was not said that you would tear apart the people.

And so, it being clear that this world is not meant to last, I have gambled literally everything upon you, Harry James Potter-Evans-Verres. There were no prophecies of how the world might be saved, so I found the prophecies that offered loopholes in the destruction; and I brought about the strange and complex conditions for those prophecies to come to pass. I ensured that Voldemort discovered a certain one of those prophecies, and so (even as I had feared) condemned your parents to death and made you what you are. I wrote a strange hint in your mother’s Potions textbook, having no idea why I must; and this proved to show Lily how to help her sister, and ensured you would gain Petunia Evans’s heartfelt love. I sneaked invisibly into your bedroom in Oxford and administered the potion that is given to students with Time-Turners, to extend your day’s cycle by two hours. When you were six years old I smashed a rock that was on your windowsill, and to this day I cannot imagine why.

All in the desperate hope that you can pass us through the eye of the storm, somehow end this world and yet bring out its people alive.

Now that you have passed the preliminary test of defeating Voldemort, I place my all in your hands, all the tools I can possibly give you. The Line of Merlin Unbroken, the command of the Order of the Phœnix, all my wealth and all my treasures, the Elder Wand of the Deathly Hallows, the loyalty of such of my friends as may heed me. I have left Hogwarts in Minerva’s care, for I do not think you will have time for it, but even that is yours if you demand it from her.

One thing I do not give you, and that is the prophecies. Upon the moment of my departure, they will be destroyed, and no future ones will be recorded, for it was said that you must not look upon them. If you think this frustrating, believe me when I say that even your wit cannot comprehend what frustration you have been spared. I will die, or be lost by you, or in some other way be taken from you—the prophecies are unclear, naturally—without ever once knowing what the future truly holds, or why I must do what I do. It is all cryptic madness and you are well rid of it.

There can only be one king upon the chessboard.

There can only be one piece whose value is beyond price.

That piece is not the world, it is the world’s peoples, wizard and Muggle alike, goblins and house-elves and all.

While survives any remnant of our kind, that piece is yet in play, though the stars should die in heaven.

And if that piece be lost, the game ends.

Know the value of all your other pieces, and play to win.

\letterClosing{—Albus}
\end{writtenNote}

\later

Harry held the parchment scroll for a long time, staring at nothing.

So.

There were times when the phrase ‘That explains it’ didn’t really seem to cover it, but nonetheless, that explained it.

Absently Harry rolled up the parchment scroll in his fist, still staring at nothing.

“What does it say?” said Amelia Bones.

“It’s a confession letter,” Harry said. “Turns out Dumbledore’s the one who killed my pet rock.”

“\emph{This is not a time for jokes!}” cried the elder witch. “Are you the true holder of the Line of Merlin Unbroken?”

“Yes,” Harry said absently, his mind occupied with thoughts that were, by any objective quantification, overwhelmingly more important.

The old witch was sitting very still in her chair. She turned her head, and locked eyes with Minerva McGonagall.

Meanwhile Harry’s brain, which was juggling way too many possibilities over way too many time horizons, some of them involving literally billions of years and stellar disassembly procedures, declared cognitive bankruptcy and started over. \emph{All right, what’s the \emph{first} thing I have to do to save the world…no, make it even more local, what do I have to do \emph{today}…besides figuring out what to do, that is, and I’d better not delay before looking at whatever Dumbledore left me in the Phœnix’s Egg room…}

Harry raised his eyes from the rolled-up parchment and looked at Professor—at Headmistress McGonagall, at Mad-Eye Moody, and at the leathery-looking old witch, as though seeing them for the first time. Though he was in fact seeing Amelia Bones for mostly the first time.

Amelia Bones, head of the Department of Magical Law Enforcement, whom Albus Dumbledore had thought worthy to lead the Wizengamot at least temporarily. Her cooperation would be invaluable, maybe \emph{necessary,} for…for whatever was headed Harry’s way. Dumbledore had chosen her, and he’d read prophecies Harry hadn’t seen.

Amelia Bones, who had thought she’d been appointed regent over the Line of Merlin Unbroken and made the next Chief Warlock, only to find that instead the position had gone to, apparently, an eleven-year-old boy.

\emph{You will now,} said the voice of Hufflepuff inside his head, \emph{you will now be polite. You will not be your usual brand of bloody idiot. Because the fate of the world might just depend on it. Or not. We don’t even know.}

“I’m terribly sorry about all this,” Harry Potter said, then paused to see what effect, if any, this polite statement had produced.

“Minerva seems to think,” the old witch said, “that you will not take offense to honest words.”

Harry nodded. His Ravenclaw part wanted to include the disclaimer about that being different from people blatantly trying to push you down while crying that you were intolerant of criticism, but Hufflepuff vetoed. Whatever she had to say, Harry would hear.

“I do not wish to speak ill of the departed,” the old witch said. “But since time immemorial, the Line of Merlin Unbroken has passed to those who have \emph{thoroughly} demonstrated themselves to be, not only good people, but wise enough to distinguish successors who are themselves both good and wise. A single break, anywhere along the chain, and the succession might go astray and never return! It was a mad act for Dumbledore to pass the Line to you at such a young age, even having made it conditional upon your defeat of You-Know-Who. A tarnish upon Dumbledore’s legacy, that is how it will be seen.” The old witch hesitated, her eyes still watching Harry. “I think it best that nobody outside this room ever learn of it.”

“Um,” Harry said. “You…don’t think very much of Dumbledore, I take it?”

“I thought…” said the old witch. “Well. Albus Dumbledore was a better wizard than I, a better \emph{person} than I, in more ways than I can easily count. But the man had his faults.”

“Because, um. I mean. Dumbledore \emph{knew} everything you just said. About my being young and how the Line works. You’re acting like you think Dumbledore was unaware of those facts, or just ignoring them, when he made his decision. It’s true that sometimes stupid people, like me, make decisions that crazy. But not Dumbledore. He was \emph{not} mad.” Harry swallowed, forcing a sudden moisture away from his eyes. “I think…I’m beginning to realize…Dumbledore was the only sane person, in all of this, all along. The \emph{only} one who was doing the right things for anything like the right reasons…”

Madam Bones was cursing under her breath, low dire imprecations that were making Minerva McGonagall twitch.

“I’m sorry,” Harry said helplessly.

Mad-Eye was grinning, the scarred face twisting up in a smile. “Always knew Albus was up to \emph{something} he never told the rest of us. Lad, you have no idea how hard it is for me not to use my Eye on that scroll.”

Harry quickly shoved the scroll into his mokeskin pouch.

“Alastor,” Amelia said. The old witch’s voice was rising. “You are a man of sense, you cannot think the lad is able to fill Dumbledore’s socks! Not \emph{today!}”

“Dumbledore,” Harry said, the name tasting strange on his tongue, “did make one wrong assumption, when he made his decisions. He thought we’d be fighting Voldemort for years, all of us together. He didn’t know I’d vanquish Voldemort immediately. It was the right thing for me to do, it saved a lot of lives compared to fighting a long battle. But Dumbledore thought you would have years to learn me, trust me…and instead it was all over in an evening.” Harry inhaled. “Can’t you just \emph{pretend} we’ve been fighting Voldemort for years and I earned your trust and everything? So that I’m not penalised for winning more quickly than Dumbledore expected?”

“You are still a first-year in Hogwarts!” the old witch said. “You \emph{cannot} take Dumbledore’s place, whatever his intentions!”

“Right, that whole ‘looking like an eleven-year-old’ thing.” Harry’s hand came up, rubbed at his nose where his glasses lay. \emph{I suppose I could just use the Stone, change myself to look like ninety…}

“I am not a fool,” the old witch said. “I know you are no ordinary child. I have seen you speak to Lucius Malfoy, watched you frighten off a Dementor, and witnessed Fawkes grant your plea. Anyone with wisdom who saw you before the Wizengamot—by which I mean myself and at most two others—could guess that you had absorbed some portion of You-Know-Who’s shredded soul on the night of his undeath, but subdued it and turned his knowledge to good ends.”

There was a slight pause in the room.

“Well, yes, of course,” said Minerva McGonagall. She sighed, slumped a bit in the Headmistress’s chair. “As Albus clearly knew \emph{from the very beginning,} but thoughtfully declined to warn me about \emph{in any way whatsoever}.”

“Right,” Moody said. “I knew that. Yep. Perfectly obvious. Wasn’t confused at all.”

“I guess that’s close enough to the truth,” said Harry. “So, um. What’s the problem, exactly?”

“The problem,” Amelia Bones said, her voice perfectly even, “is that you are a bubbling, unstable blend of a Hogwarts first-year and You-Know-Who.” She paused, as though waiting for something.

“I’m getting better about that,” Harry said, since she seemed to be waiting on his reply. “Quite rapidly, in fact. More importantly, it’s not something Dumbledore didn’t know.”

The old witch continued. “Giving away your fortune and going in debt to Lucius Malfoy to keep your best friend out of Azkaban, as much as it demonstrates your upstanding moral character, also demonstrates that you cannot corral the Wizengamot. I can see now that you did the right thing for yourself, the thing you had to do to maintain your lease on sanity and hold back your inner darkness. But you also did a thing that Merlin’s heir must not do. A sentimental leader can be far worse than a selfish one. Albus, master and servant of a phœnix, was barely survivable—and even he opposed you that day.” Amelia gestured in the direction of Mad-Eye Moody. “Alastor has hardness. He has cunning. He still does not have the talent for government. You, Harry Potter, do not yet have the sternness, the capacity for sacrifice, to direct even the Order of the Phœnix. And being what you are, you \emph{must not try} to become that person. Not now, not at your age. Align and fuse your divided soul in your own time, if you possibly can. Do not try to be Chief Warlock while you are doing it. If Albus thought that was a good idea, he was crafting a nicer story at the expense of real-world practicality. I do think the man had a problem with that.”

Harry’s eyes were a bit wide, listening to all this. “Um…what exactly do you think is going on in here?” Harry tapped his head just above his ear.

“I imagine that inside you is the soul of a boy who remains honest and true, gathering his will to force down the fragment of Voldemort’s spirit that tries to consume him, even as it howls at him that he is sentimental and weak—did you just giggle?”

“Sorry. But seriously, it wasn’t ever \emph{that} bad. More like having a lot of bad habits I needed to break.”

“Ahem,” said Headmistress McGonagall. “Mr~Potter, I think at the start of this year it \emph{was} that bad.”

“Bad habits that chained into and triggered each other. Yes, those are a bit more of a problem.” Harry sighed. “And you, Madam Bones…er. Sorry if I’m wrong about this. But my guess is that you’re feeling a bit upset that the Line went to an eleven-year-old?”

“Not the way you are thinking,” the old witch said calmly. “Though it is natural for you to suspect me. The position of Chief Warlock is not one I will find pleasant, even compared to the horrors of Magical Law Enforcement. Albus persuaded me on the matter, and I would say that I took some convincing, but the truth is that I did not waste his time in an argument I expected to lose. I knew I would hate the task, and I knew I would do it anyway. Minerva says you have some amount of common sense, especially when others remind you of it. Can you really see yourself standing upon the Wizengamot’s high dais? Are you sure it is not some remnant of You-Know-Who that imagines himself suited to the position, or even desires it at all?”

Harry took off his glasses and massaged his forehead. His scar still ached a bit, from the damage he’d done by picking at it yesterday until it bled in a suitably dramatic fashion. “I do have some common sense, and yes, being Chief Warlock sounds like a huge amount of aggravation and a job that, in reality, does not fit me the tiniest bit. The trouble is. Um. I’m not sure the Line of Merlin is just about being Chief Warlock. There’s, um. I suspect…that there’s weird other stuff that goes along with it. And that Dumbledore meant me to take responsibility for the…other stuff. And that the other stuff is…possibly quite \emph{amazingly} important.”

“Crap,” Moody said. Then Alastor Moody repeated, “Crap. Kid, should you even be saying this to us?”

“I don’t know,” Harry said. “If there’s a user manual, I haven’t looked at it yet.”

“Crap.”

“And if these other matters require sternness and sacrifice?” Amelia Bones said, still calmly. “If they test you as you were tested before the Wizengamot? I am old, Harry Potter, and I am not without knowledge of mysteries. You have seen how I was able to perceive your own nature at nearly a glance.”

“Amelia,” Mad-Eye Moody said. “What would have happened if you’d had to fight You-Know-Who last night?”

The old witch shrugged. “I would have died, I expect.”

“You’d have \emph{lost,}” said Alastor Moody. “And the Boy-Who-Lived didn’t just take out Voldie, he set it up so that his good friend Hermione Granger came \emph{back from the dead} at the same time Voldie resurrected himself. There’s no way in hell or double hell that was an accident, and I don’t think it was David’s idea either. Amy, the truth is, none of us know what the keeper of Merlin’s legacy has to \emph{do}. But we’re not the right kind of crazy for this crap.”

Amelia Bones frowned. “Alastor, you know I’ve dealt with strange things before. Dealt with them quite well, in my opinion.”

“Yeah. You \emph{dealt with} the crap so you could go back to real life. You’re not the kind of crazy that builds a castle out of the crap and lives there.” Moody sighed. “Amy, on some level you know exactly why Albus had to leave who-knows-what-job to the poor kid.”

The old witch’s fists clenched on the table. “Do you have any idea of the \emph{disaster} it would be for Britain? Call me sane, but I cannot accept that outcome! I have worked too long toward this day to see it fall apart now, \emph{now} of all times!”

“Excuse me,” Headmistress McGonagall said, sounding quite precise and Scottish. “Is there any reason why Mr~Potter cannot simply instruct the Line that Madam Bones is his regent for the position of Chief Warlock, but not anything having to do with the Department of Mysteries, until he comes of age? If Albus could tell the Line to appoint a regent only until Voldemort’s defeat, it is clearly capable of following complex orders.”

Slowly, this unexpected hammer-blow of common sense was absorbed by everyone present.

Harry opened his mouth to agree to appoint Amelia Bones his regent for Wizengamot-related matters, and then hesitated again.

“Um,” Harry said. “Um. Madam Bones, I would much prefer if you took charge of handling the Wizengamot instead of me.”

“In that we are agreed,” said the old witch. “Shall we let it be done?”

“But—”

There was a sort of frustrated dropping-back of the others. “What is the problem, Mr~Potter?” said the Headmistress, in a voice that indicated she hoped it was nothing serious.

“Um. I think there’s a couple of things I might have to do very soon that could…prove politically controversial, and in exchange for handing over the Line’s political power to Madam Bones I’m going to want her…um, cooperation on some things.”

Amelia Bones exchanged another long stare with Minerva McGonagall. Then she looked back at Harry Potter.

“I am indignant at your request!” Amelia Bones said. “Your hesitancy has told me that you are weak and unused to bargaining, and will probably fold if I push back.”

Harry closed his eyes.

\emph{Slightly} dark-tinged Harry opened them.

“All right,” Harry said, “let me rephrase. I don’t mean to interfere with your work on a day-to-day or even month-to-month basis, but I can’t just toss off the final responsibility that Dumbledore left me. I’m not going to owl you bizarre parchments out of nowhere, there can be discussions first, but at some point I may have to give you an order. If you refuse the order I might have to take back the Line’s Wizengamot functions and assume direct control. Can you handle that?”

“And if I say no?” said the old witch.

\emph{Slight, slight the dark tinge…} “I don’t have an alternative to you lined up. I could start by asking Augusta Longbottom who she thought might be suitable and work from there. But it may be important that we keep to Dumbledore’s plan as much as possible, since I don’t know exactly why he did the things he did, and he thought Amelia Bones should be Chief Warlock for a time. I’m not going to pull Merlin’s name on you, but…no, strike that, I \emph{am} going to pull Merlin’s name on you, this might or might not be insanely important.”

The old witch thought for a time, her eyes going from person to person around the table. “I am not satisfied with this,” she said after a time. “But the Wizengamot must be called to order soon. It will do for now.”

Slowly the old witch reached into her robes, and took out a short rod of stone, dark stone.

She placed the rod on the table before Harry. “Take what is yours,” she said. “And then do please give it back.”

Harry reached out his hand to take it.

In the moment that Harry’s fingers first touched the dark stone—

—nothing happened.

Well, perhaps Merlin hadn’t been given to melodrama. That could explain why his final legacy looked like a small, unassuming dark rod. If that was all that was needed for its function, that would be all that was there.

Harry took up the Line, frowning at it. “I’d like to appoint Amelia Bones as my regent for Wizengamot-related functions.” Then, the thought occurring to him that he needed to specify a stopping point to define a regency, Harry added, “Until I say that I’ve taken it back.”

Then Harry made a face. He’d been hoping for more from the Line, but it was just a key to places in the Department of Mysteries where interesting things were kept, or to seals where Merlin and his successors had stashed things that shouldn’t be destroyed but ought to be kept from general circulation. Aside from that, the Line didn’t do much.

The Line didn’t let you bypass the Interdict of Merlin either. No, not even if the fate of the galaxy was at stake. Not even if the person seemed sane, had taken an Unbreakable Vow, and honestly believed the world was about to be destroyed otherwise.

Merlin had dreamed of a long run, a world that would last for æons and not just centuries. The world had no reason not to last \emph{forever,} if the truly dangerous powers were removed and kept gone. Conversely, a single loophole in the safeguards made the world’s destruction only a matter of time. Someday Merlin’s Line would pass to the wrong person. It could reject the obviously unworthy, but eventually it would pass into hands too subtly flawed for the Line to detect. This was inevitable, when dealing with human beings, and Harry needed to keep that in mind before he sealed something where future Line-holders could retrieve it—the disaster of its inevitable misuse \emph{some day} needed to be outweighed by its benefits over the next few thousand years.

Harry let out a sad small sigh, under his breath. \emph{Merlin, you idiot…}

Thinking that didn’t unlock any final safeguards.

There wasn’t anything currently on fire in the Department of Mysteries, so Harry carefully placed the Line back on the table.

“Thank you,” the old witch said. She picked up the rod of dark stone. “Do you know how I am to use it to call the Wizengamot to order, or—never mind, I shall just try striking the podium. That seems obvious enough. To the rest of the country, of course, I am the Chief Warlock so far as anyone knows except us four.”

Harry hesitated. Then he imagined the owls he would receive if anyone knew he was allowed to second-guess the Chief Warlock, and what that would do to Amelia’s negotiating power. “Fine.”

Amelia tucked the rod back into her robes. “I will not say it was a pleasure doing business with you, Boy-Who-Lived, but it could have been much worse. Thank you kindly for that.”

Harry was already feeling worried about the exact balance of power here, from the way Madam Bones was acting. The others had, quite logically, deduced that it had been mostly David Monroe who’d planned the way to defeating Voldemort, which meant they were still underestimating him. It might take a crisis of some type, with Harry figuring it out successfully for once instead of screwing up, before Amelia Bones started to respect his authority. Or believe in it at all, actually…”So,” Harry said. “Any weirdness for me that you would have brought to Dumbledore while he was around?”

Amelia looked thoughtful. “Since you ask…I can think of three things, indeed. First, we don’t have the faintest notion what ritual was used to sacrifice the Death Eaters and resurrect You-Know-Who. It corresponds to no known legend, and the magic traces from the ritual have been eradicated. So far as my Aurors can tell, everyone’s heads fell off their necks due to natural causes. Except for Walden Macnair, who was killed by magical fire after firing a Killing Curse from his wand. A very mysterious ritual indeed.” She was giving Harry Potter a rather \emph{precise} look.

Harry considered this, choosing his words carefully. Voldemort had said he’d put up wards, so Harry had been confident of not being observed by Time-Turned Aurors, but still…“I think this is a matter you don’t need to investigate too hard, Madam Bones.”

The old witch grinned slightly. “We can’t be seen to go easy on the investigation of so many Noble deaths, Harry Potter. When I heard retold your particular account of David’s last stand, I made certain to send investigators whom I considered \emph{reliable} in the usual quality of their work. Auror Nobbs and Auror Colon, in fact, who are widely respected outside my Department. I found their report to be quite fascinating reading.” Amelia paused. “There’s a possibility that Augustus Rookwood left a ghost—”

“Exorcise it before anyone talks to it,” Harry said, conscious of the sudden hammering of his heart.

“Yes, sir,” the old witch said dryly. “I shall disrupt the soul’s anchoring a little, and none shall be the wiser when it fails to materialize. The second matter is that there was a still-living human arm found among the Dark Lord’s things—”

“Bellatrix,” Harry said. His mind had leaped back, made the connection that ongoing trauma had blurred. “I think that’s Bellatrix Black’s arm.” \emph{Lesath Lestrange hadn’t been named as someone who’d lost a parent.} “Oh, bloody hell. She’s still out there, isn’t she. Can you use her arm to track her down somehow?”

Amelia Bones had acquired a sour look. “I see. As I was saying, a still-living human arm was found among the Dark Lord’s things, but it proved to be easily incinerated.”

“What \emph{idiot}—” Harry stopped himself. “No, \emph{not} an idiot. Because immediately destroying Dark objects is Department policy. Because of past experiences with rings that really should’ve been dropped into volcanos immediately. Right?”

Moody and Amelia nodded in unison. “Good guess, son,” said Moody.

It might seem literarily inevitable that Harry’s past stupidity was going to come back and haunt him in some horrible fashion later, but that was no reason not to try subverting the plot. “I expect you’ve thought of this already,” Harry said, “but the obvious next step is to put out your equivalent of an international bulletin for a thin witch missing her left arm. Oh, and add twenty-five thousand Galleons pledged from me—Headmistress, it’s fine, please trust me on this—to whatever reward is being offered.”

“Well said.” The old witch leaned forward slightly. “The third and final matter…there was one truly puzzling element to last night’s events, and I am curious to see what you make of it, Harry Potter. Found among the corpses was the head and the body of Sirius Black.”

“\emph{What?}” yelled Moody, starting half from his chair. “\emph{I thought he was in Azkaban!}”

“So he is,” said Madam Bones. “We checked that at once. The Azkaban guards reported that Sirius Black was still in his cell. Black’s head and body have been transported to the St. Mungo’s morgue, and show the same cause of death as the other Death Eaters, that is to say, his head spontaneously fell off. I am also told that Sirius Black is, as of this morning, sitting in the corner of his cell rocking back and forth with his head between his hands. No other duplicate Death Eaters have been found. Yet.”

There was a pause filled with ticking and whooping things, as people considered this.

“Ah…” said Minerva. “That’s not possible even by You-Know-Who’s standards of possibility. Is it?”

“I would have thought so too when I was your age, dear,” said Amelia. “It is the sixth strangest thing I have ever seen.”

“You see, son?” said Moody. “This sort of thing is why nobody, even me, can ever be paranoid enough.” The scarred man tilted his head, looking thoughtful, as his bright blue eye kept ever-roving. “Twin brother, concealed from the rest of the world? Walpurga Black gave birth to twins, couldn’t bear to kill one, knew old Pollux would demand it…nah, ain’t buyin’ it.”

“Any ideas, Mr~Potter?” said Amelia Bones. “Or is this another matter into which my Department should not inquire too closely?”

Harry closed his eyes and thought.

Sirius Black had hunted down Peter Pettigrew, instead of fleeing the country as common sense would have suggested.

Black had been found in the middle of the street, surrounded by bodies, laughing.

Nothing left of Pettigrew except one finger.

Pettigrew had been a spy for the Light, not a double agent but somebody who sneaked around and found things out.

One of the conspiracy theories about Pettigrew had been that he was an Animagus, since he’d been good at ferreting out secrets even in his Hogwarts years.

Dementors sapped all the magic in their vicinity.

Professor Quirrell had said something about a particular type of magic that rearranged flesh like a Muggle smith reshaping metal with hammer and tongs…

Harry opened his eyes again.

“Was Peter Pettigrew a secret Metamorphmagus?”

Amelia Bones’s face changed. She made a single croaking noise and fell backward within her chair.

“Yes, in fact…” Minerva said slowly. “Why?”

“Sirius Black Confunded Peter Pettigrew,” Harry’s voice explained patiently, “to force him to change shape and pretend to be Black. By the time the Confundus wore off, Peter was in Azkaban and couldn’t change back. The Aurors are used to people in Azkaban saying absolutely anything to get out, so they didn’t listen while Peter Pettigrew was screaming about it over and over again until his voice wore out.”

Even Mad-Eye Moody’s face showed the horror, then.

“In retrospect,” said Harry’s voice, which seemed to be operating entirely on automatic, “you should have been suspicious when you managed to get that \emph{one} Death Eater hauled off to Azkaban without a trial.”

“We thought Malfoy was distracted,” whispered the old witch. “That he was only trying to save himself. There were other Death Eaters we managed to get then, like Bellatrix—”

Harry nodded, feeling like his neck and head were moving on puppet strings. “The Dark Lord’s most fanatic and devoted servant, a natural nucleus of opposition for anyone who contested Lucius’s control of the Death Eaters. You thought Lucius was distracted.”

“Get him out of there,” said Minerva McGonagall. Her voice rose to a scream. “\emph{Get him out of there!}”

Amelia Bones shoved herself up from the chair, whirled on the Floo—

“Stop.”

Everyone looked at Harry with astonishment, none more than Minerva McGonagall.

Something else seemed to have taken over Harry’s voice. “There’s four things we still need to discuss. An innocent man has been in Azkaban for ten years, eight months, and fourteen days. He can stay there a few minutes longer. That’s how urgent those four things are.”

“You—” whispered Amelia Bones. “You should not try to be this person, at your age—”

“First. I think I should look at the complete police records on every other Death Eater that went to Azkaban \emph{while Lucius was distracted.} Can you compile that by tonight?”

“Within the hour,” said Amelia Bones. She looked grey.

Harry nodded. “Second. Azkaban is over. You’ll need to start preparations now to move the prisoners to Nurmengard or other secure non-Dementor prisons, and to provide treatment for their Dementor exposure.”

“I,” said Amelia. The old witch seemed bent, diminished. “I…do not think, that even with this…scandal, that the remainder of the Wizengamot will bend…and the Dementors must be fed, not so much as we have fed them, but they must be given some victims, or they will roam the world, prey on innocents…”

“It doesn’t matter what the Wizengamot says,” Harry said. “Because—” Harry’s voice choked. “Because—” Harry took a deep breath, steadied himself. He thought he could see the shape now of the immediate future, could see it stretching out before him like a golden pathway lit with sunlight. \emph{Was this also written, in the book of Time that I must not see?} “Because if I’m right about what comes next, then sometime very soon, Hermione Granger, the Girl-Who-Revived, is going to go to Azkaban and destroy all the Dementors there.”

“Impossible!” spat Mad-Eye Moody.

“Merlin,” whispered Amelia Bones. “Oh, dear Merlin. That’s what happened to the Dementor that Dumbledore ‘lost’. That’s why they’re afraid of you—and now her as well?” Her voice trembled. “What is this, what is all this?”

\emph{If Hermione believes that Death can be defeated—}

\emph{Whether or not she could’ve believed that before, she’ll believe it now.}

“An authorized portkey to Azkaban would be appreciated—” Harry’s voice broke again. Tears were streaming down his cheeks.

\emph{She can’t die. I have her horcrux.}

\emph{But Hermione doesn’t need to know about that. Not for one more week.}

\emph{If she’s willing to risk her own life to end this—}

“Though I think, she might make, her own way there…”

“Harry?” said Headmistress McGonagall.

Harry was crying now, huge ragged breaths bursting from him. But he didn’t stop talking. Somewhere out there Peter Pettigrew was waiting while Harry cried.

Somewhere out there, everyone was waiting while he cried.

“Third. Somewhere just inside the wards of Hogwarts. In a highly defensible position. But where emergency cases can be portkeyed in from just outside the wards. There’s going to be a high-security h-h-hospital. With very powerful guards, that have taken Unbreakable Vows, I don’t, I don’t care how much gold it takes to pay for the Vows, it genuinely does not matter any more. And, and Alastor Moody is going to design the security architecture, and go completely overboard on paranoia without being constrained by a budget or sanity or common sense, only it has to open \emph{soon.}” Couldn’t stop talking to cry.

“Harry,” said the Headmistress, “both of them think you’ve gone mad, they don’t know you well enough to know better. You need to slow down and explain.”

Instead Harry reached into his pouch and signed letters with his fingers, and lifted out, his fingers straining, a five-kilo chunk of gold larger than his fist, from when he’d been experimenting this morning. It made a heavy thud as it landed on the table.

Moody reached over and tapped it with his wand, and then his throat made an incomprehensible sound.

“That’s your starting budget, Alastor, if you need money right away. Nicholas Flamel didn’t make the Philosopher’s Stone, he stole it, Dumbledore didn’t know the secret history but Monroe did. Once you know how it works, the Stone can do one complete restoration to full health and youth every two hundred and thirty-four seconds. Three hundred sixty people per day. One hundred and thirty-four thousand healings per year. That should be enough to stop, all the wizards everywhere, and all the goblins and house-elves and whoever, from dying. Of old age, or anything else.” Harry was wiping away tears, over and over. “Flamel had more blood on his hands than a hundred Voldemorts, for all the people he could’ve saved and didn’t. The whole time, Moody, the Philosopher’s Stone could’ve healed all your scars and given you back your leg, any time Flamel felt like it. Dumbledore didn’t know. I’m sure he didn’t know.” Harry smiled shakily. “I can’t imagine you as a teenage witch, Madam Bones, but I bet it looks good on you. That’ll give you more energy for trying to keep the Wizengamot from messing with me, because if they get the idea that the Stone is something they can mess with in any way, tax, regulate, I don’t care, Hogwarts is going to secede from Britain and become its own country. Headmistress, Hogwarts is no longer dependent on the Ministry for gold, or for that matter food. You may reform the educational curriculum at will. I’m thinking we may want to add some more advanced courses soon, especially in Muggle studies.”

“Slow \emph{down!}” said Minerva McGonagall.

“Fourth—” Harry said, and then stopped.

\emph{Fourth. Begin preparations for an orderly take-down of the Statute of Secrecy and to provide magical healing on a mass scale to the Muggle world. Those who oppose this agenda in any way may be denied services by the Stone…}

Harry’s lips couldn’t move. Not wouldn’t, \emph{couldn’t.}

With six billion Muggles thinking creatively about how to use magic…

Transfiguring antimatter was just one idea. It wasn’t even the most destructive idea. There were also black holes and negatively charged strangelets. And if black holes couldn’t be Transfigured because they didn’t \emph{already exist} as magic defined that to within some spatial radius, there was just Transfiguring lots and lots of nuclear weapons and Black Death plague that could reproduce before the Transfiguration wore off and Harry hadn’t even thought about the problem for five minutes but it didn’t matter because he’d already thought of enough. Someone would think of it, someone would talk, someone would try it. The probability was as close to certainty as made no difference.

What happened if you Transfigured a cubic millimetre of up quarks, just the up quarks without any down quarks to bind them? Harry didn’t even know, and up quarks were certainly a kind of substance that already existed. All it might take was one single Muggleborn who knew the names of the six quarks deciding to try it. That could \emph{be} the clock ticking down to the prophesied end of the world.

Harry would have tried to deny the thought, rationalize it away.

He couldn’t do that either.

It wasn’t a thing-Harry-Potter-would-do.

Like water flowing downhill, Harry Potter would take no chances when it came to not destroying the world.

“Fourth?” said Amelia Bones, who was looking like she’d been hit repeatedly in the face with a planet. “\emph{What comes fourth?}”

“Never mind,” said Harry. His voice did not break. He did not fold over sobbing. There were still lives he could save and those took precedence. “Never mind. Chief Warlock Bones, I’ve given the regency of the Wizengamot into your hands. Please use that position to announce internationally that the Stone’s healing power will soon be made available to all, and that meanwhile, all dying patients are to be kept alive at any cost, no matter what magic is required to do it. That announcement is your absolute priority. When you have done that you may rescue Peter Pettigrew and tell your old Department to begin preparations for shutting down Azkaban. Then please have someone prepare a full list of imprisoned Death Eaters and what was said at their trials and whether Lucius seemed strangely uninterested in defending them. Thank you. That’s all.”

Amelia Bones turned without another word, and dashed into the Floo like it was her own self that was on fire.

“And someone,” Harry said, his voice breaking again now that it was all set in motion, and crying wasn’t costing time, though the vast majority of total lives at stake had turned out not to be savable just yet, “someone has to, someone tell Remus Lupin.”

%  LocalWords:  arry wibblers Poot undeath Nobbs Rookwood literarily Pollux
%  LocalWords:  Walpurga buyin
