\namedpartchapter{The Stanford Prison Experiment}{TSPE}{XI}{Secrecy and Openness}

\lettrine{T}{hrough} green flame they whirled, through the Floo network they spun, Minerva’s heart racing with a pounding horror that she hadn’t felt in ten years and three months, the corridors between space coughed and spit them out into the lobby of Gringotts (the safest Floo receiver in Diagon Alley, the connection most difficult to intercept, the fastest way out of Hogwarts without a phoenix). A goblin attendant turned toward them, his eyes widened, he began a slightly respectful bow—

\emph{Determination, Destination, Deliberation!}

And the two of them were in the alley just in back of Mary’s Place, wands already out and raised, spinning around back-to-back and the words of an Anti-Disillusionment Charm already rising to Severus’s lips.

The alley was empty.

When she turned back to look at Severus, his wand was already cracking down on his own head with a sound like smashing an egg, as his lips chanted words of invisibility; he took on the colors of his surroundings, became a blur of his surroundings, the blur moved and matched what was behind him and then there was nothing there.

She lowered her wand and stepped forward to receive her own Disillusionment—

From behind her, the unmistakable sound of a burst of flame.

She spun and saw Albus there, his long wand already drawn and raised in his right hand. His eyes were grim beneath the half-circles of his glasses, and Fawkes upon his shoulder had spread his fire-colored wings in readiness for flight and fight.

“Albus!” she said. “I thought—” She’d just seen him depart for Azkaban, and she’d thought not even phoenixes could return from there so easily.

Then she realized.

“She escaped,” said Albus. “Did your Patronus reach him?”

The pounding in her heart grew stronger, the horror in her veins solidified. “He said he was here, in the washroom—”

“Let us hope he spoke true,” said Albus, the wand tapped her head with a sensation like water trickling over her, and a moment later the four of them (even Fawkes had been rendered invisible, though sometimes you saw a flicker of something like fire in his air) were racing to the front of the restaurant. They paused before the door while Albus whispered something, and a moment later one of the customers visible through the windows stood up with a vague look on his face and opened the door as though taking a quick look outside for some friend; and the three of them were through, racing past the unwitting customers (Severus was marking their faces, Minerva knew, and Albus would see any Disillusioned) toward the sign that pointed to the washroom—

An old wooden door marked with the sign of a toilet burst open with a slam, and four invisible rescuers stormed through it.

The small but clean wooden room was empty, fresh droplets of water showed in the sink but there was no sign of Harry, only a sheet of paper left on the closed lid of the toilet.

She couldn’t breathe.

The sheet of paper rose up into the air as Albus took it, and a moment later was thrust in her own direction.

\emph{M: What did the hat tell me to tell you?}

\emph{—H}

“Ah,” Minerva said aloud in surprise, her mind taking a moment to place the question, it wasn’t the sort of thing you’d forget but she hadn’t been thinking in that \emph{mode,} really—“I’m an impudent youngster and I should get off its lawn.”

“\emph{Eh?}” said the air in Albus’s voice, as if even he could be shocked.

And then Harry Potter’s head appeared, suspended next to the air beside the toilet, his face was cold and alert, the too-adult Harry she’d seen sometimes, eyes darting back and forth and around.

“What’s going on—” the boy began.

Albus, now visible once more along with her and Fawkes, was moving forward in an instant, his left hand reached forward and plucked a hair from Harry’s head (producing a startled yelp from the boy), Minerva accepted the hair in her own hand, and a moment later Albus swept up the mostly-invisible boy in his arms and there was a flash of red-golden fire.

And Harry Potter was safe.

Minerva took a few steps forward, leaned against the wall where Albus and Harry had been, trying to recover her poise.

She’d...\ lost some habits, in the ten years since the Order of the Phoenix had disbanded.

Beside her, Severus shimmered into visibility. His right hand was already drawing forth the flask from his robes, his left hand already stretching forth in demand. She gave him Harry’s hair, and a moment later, it dropped into the flask of unfinished Polyjuice, which at once began fizzing and bubbling as it settled into the potency that would enable Severus to act his part as bait.

“That was unexpected,” the Potions Master said slowly. “Why did our Headmaster not retrieve Mr.~Potter \emph{earlier}, I wonder, if he was going so far as to twist Time? There should have been nothing preventing him from doing so...\ indeed, your Patronus should have found Mr.~Potter already safe...”

She hadn’t thought of that, a different realization having jumped to the forefront of her mind. It wasn’t nearly as horrifying as Bellatrix Black having escaped from Azkaban, but still—

“Harry has an \emph{invisibility cloak?}” she said.

The Potions Master did not answer; he was shrinking.
\sbreak
Tick-snick, drip-blip, ding-ring-ting—

It still annoyed her, though it faded past attention after a while; and when and if she became Headmistress, she intended to Silence the whole lot. Which Head of Hogwarts, she wondered, had first been so inconsiderate as to create a device that made \emph{noise}, to pass on to their successors?

She was sitting in the Headmaster’s office with a quickly Transfigured desk of her own, doing some of the hundred little pieces of necessary paperwork that kept Hogwarts from grinding to a halt; she could lose herself in it easily, and it prevented her from thinking about other things. Albus had once remarked, sounding rather wry, that Hogwarts seemed to run even more smoothly when there was an outside crisis for her to avoid thinking about...

...ten years ago, that was the last time Albus had said that.

There was the chime that indicated an approaching visitor.

Minerva kept reading her current parchment.

The door slammed open, revealing Severus Snape, who took three steps inward and demanded without the slightest pause, “Any word from Mad-Eye?”

Albus was already rising from his chair, even as she tucked away her parchments and dispelled the desk. “Moody’s Patronus is reporting to the me in Azkaban,” Albus said. “His Eye saw nothing; and if the Eye of Vance does not see a thing, then that thing does not exist. Yourself?”

“No one has tried to forcibly take my blood,” Severus said. He gave a quick grimace of a smile. “Except the Defense Professor.”

“\emph{What?}” said Minerva.

“He saw me for an impostor before I could even open my lips, and quite reasonably attacked me on the spot, demanding to know the whereabouts of Mr.~Potter.” Another grimace of a smile. “Shouting that I was Severus Snape did not seem to reassure him, for some reason. I do believe that man would kill me for a Sickle and give back five Knuts change. I had to stun our good Professor Quirrell, which was not easy, and then he reacted poorly to the hex. ‘Harry Potter’, naturally alarmed, ran out and told the owner, and the Defense Professor was taken to St.~Mungo’s—”

“\emph{St.~Mungo’s?}”

“—which said he had probably been overworking himself for weeks before he collapsed, such was his state of exhaustion. Your precious Defense Professor is fine, Minerva, the stunner may have helped him by forcing him to take a few days off. Afterward I declined the offer of a Floo to Hogwarts, and went back to Diagon Alley and wandered; but no one seems to have wanted Mr.~Potter’s blood today.”

“Our Defense Professor is in the best of hands, I am sure,” said Albus. “Greater matters command our attention, Minerva.”

It took considerable effort for her to wrench her attention back, but she sat back down, and Severus gestured up a chair for himself as well, and the three of them drew together to begin their council.

She felt like a Polyjuiced impostor, sitting with those two. War was not her art, nor plotting. She had to strain to keep one step ahead of the Weasley twins, and sometimes she failed at that. She was sitting here, ultimately, only because she had heard the prophecy...

“We are faced,” the Headmaster spoke first, “with a rather alarming mystery. I can think of only two wizards who might have engineered this escape.”

Minerva drew in her breath sharply. “There is a chance it is \emph{not} You-Know-Who?”

“I’m afraid so,” said the Headmaster.

She glanced to her side and saw that Severus looked as puzzled as herself. \emph{Afraid} the Dark Lord was not rising again? She would have given almost anything for that to be true.

“So,” Albus said heavily. “Our first suspect is Voldemort, risen again and seeking to resurrect himself. I have studied many books I wish I had not read, seeking his every possible avenue of return, and I have found only three. His strongest road to life is the Philosopher’s Stone, which Flamel assures me that not even Voldemort could create on his own; by that road he would rise greater and more terrible than ever before. I would not have thought Voldemort able to resist the temptation of the Stone, still less because such an obvious trap is a challenge to his wit. But his second avenue is nearly as strong: The flesh of his servant, willingly given; the blood of his foe, forcibly taken; and the bone of his ancestor, unknowingly bequeathed. Voldemort is a perfectionist—” Albus glanced at Severus, who nodded agreement, “—and he would certainly seek the most powerful combination: the flesh of Bellatrix Black, the blood of Harry Potter, and the bone of his father. Voldemort’s final avenue is to seduce a victim and drain the life from them over a long period; in which case Voldemort would be weak compared to his former power. His motive to spirit away Bellatrix is clear. And if he is keeping her in reserve, to use only in case he cannot attain the Stone, that would explain why no kidnap attempt was made on Harry this day.”

Minerva glanced again at Severus, saw him listening attentively but without surprise.

“What is \emph{not} clear,” the Headmaster continued, “is \emph{how} Voldemort could have engineered this escape. A death doll was left in Bellatrix’s place, her escape was meant to be undetected; and even though that went wrong, the Dementors could not find her after their first warning. Azkaban has stood impenetrable for centuries, and I cannot imagine any means by which Voldemort could have accomplished this.”

“That may mean little,” Severus said, expressionless. “For the Dark Lord to do what we cannot imagine requires only that he has a better imagination.”

Albus nodded grimly. “Unfortunately there is now another wizard who laughs at impossibilities. A wizard who, not long ago, developed a new and powerful Charm which could have blinded the Dementors to Bellatrix Black’s escape. And he is implicated for other reasons, as well.”

Minerva’s heart was skipping beats, she didn’t know \emph{how,} or \emph{why,} but a terrible apprehension was dawning on her as to \emph{who—}

“Who would \emph{that} be?” said Severus, sounding puzzled.

Albus leaned back and said the fatal words, even as she had feared them: “Harry James Potter-Evans-Verres.”

“\emph{Potter?}” demanded the Potions Master, as much shock in that usually-silken voice as she had ever heard from him. “Headmaster, is this one of your jokes? He is in his first year at Hogwarts! A temper tantrum and a few childish pranks with an invisibility cloak does not make him—”

“It is no joke,” said Minerva, her voice barely above a whisper. “Harry is already making original discoveries in Transfiguration, Severus. Though I did not know he was researching Charms as well.”

“Harry is no ordinary first-year,” the Headmaster said solemnly. “He is marked as the Dark Lord’s equal, and he has power the Dark Lord knows not.”

Severus was looking at her, and you would have needed to know him well to recognize that his glance was pleading. “Am I to take this seriously?”

Minerva simply nodded.

“Does anyone \emph{else} know of this...\ new and powerful Charm?” Severus demanded.

The Headmaster glanced at her apologetically—

Somehow she knew, she knew before he even said it, and she wanted to scream at the top of her lungs.

—and said, “Quirinus Quirrell.”

“\emph{Why,}” she said, in a voice that should have melted half the devices in the office, “\emph{did Mr.~Potter even \shout{tell} our Defense Professor about his brilliant new Charm for breaking out of prisons—}”

The Headmaster passed a weary wrinkled hand across his equally wrinkled forehead. “Quirinus just happened to be there, Minerva. Even I saw no harm in it at the time.” The Headmaster hesitated. “And Harry said his Charm was too dangerous to be explained to either of us; and when I asked him again, this day, he insisted he had still not explained it to Quirinus, nor had he ever dropped his Occlumency barriers in the Defense Professor’s presence—”

“Mr.~Potter is an \emph{Occlumens?} You gave him an invisibility cloak and he is immune to Veritaserum \emph{and he is friends with the Weasley twins?} Albus, do you have any idea what you have unleashed upon this school?” Her voice was nearly shrieking, now. “By his seventh year there won’t be anything left of Hogwarts but a smoking hole in the ground!”

Albus leaned back in his great cushioned chair, and said, smiling, “Don’t forget the Time-Turner.”

She did scream then, but quietly.

Severus drawled, “Should I teach him to brew Polyjuice, Headmaster? I ask only for the sake of completeness, in case you are not satisfied with the magnitude of your pet disaster.”

“Perhaps next year,” said Albus. “My dearest friends, the question before us is whether Harry Potter has spirited Bellatrix Black out of Azkaban, which is more than youthful high spirits even by my tolerant standards.”

“Excuse me, Headmaster,” Severus said with one of the dryer smiles she had ever seen him deliver to Albus, “but I will register my opinion that the answer is no. This is the Dark Lord’s work, pure and simple.”

“Then why,” Albus said, and now there was no humor at all in his voice, “when I planned to retrieve Harry immediately after his arrival in Diagon Alley, did I find that this would result in paradox?”

Minerva sank further back into her chair, dropped her left elbow onto the hard uncushioned armrest, leaned her head into her hand, and shut her eyes in despair.

There was a narrowly circulated proverb to the effect that only one Auror in thirty was qualified to investigate cases involving Time-Turners; and that of those few, the half who weren’t \emph{already} insane, soon would be.

“So you suspect,” Severus’s voice was saying, “that Harry went from Diagon Alley to Azkaban, then looped back to Diagon Alley afterward to be picked up by us—”

“Precisely,” said Albus’s voice. “Though it is also possible that Voldemort or his servants watched to make sure Harry did arrive in Diagon Alley, before they began their attempt on Azkaban. And that they had someone with a Time-Turner who would send back the message of their success, to trigger the abduction. Indeed, it was my suspicion of this possibility that caused me to dispatch you and Minerva on your own mission, before I myself went to Azkaban. I thought then that their breakout would fail, but if retrieving Harry Potter meant observing the fact of their eventual failure, then I myself could not have gone to Azkaban after I had interacted with him, for Azkaban’s future cannot touch its past. When, in Azkaban, I received no report from you or Minerva, nor from Flitwick whom I told to try contacting you, I knew that your interaction with Harry Potter had been an interaction with Azkaban’s future, meaning that someone was sending messages through Time—”

Then Albus’s voice stopped.

“But Headmaster,” said Severus, “\emph{you} came back from Azkaban’s future and interacted with us...”

The Potions Master’s voice trailed off.

“But Severus, if I had \emph{received} reports from you and Minerva of Harry’s safety, I would not, in the first place, have gone backward in time to—”

“Headmaster, I think we must draw diagrams for this.”

“I agree, Severus.”

There was the sound of parchment being spread on a table, and then quills scratching, and more arguing.

Minerva sat in her chair, head resting in her hand, eyes shut.

There was a story she’d once heard about a criminal who had possessed a Time-Turner which the Department of Mysteries had sealed to him, in a case of extremely bad judgment as to who needed one; and there had been an Auror assigned to track down this unknown time-criminal, who had also been given a Time-Turner; and the story ended with both of them in St.~Mungo’s ward for Total Unrecoverable Nutcases.

Minerva sat there with her eyes shut, trying not to listen, trying not to think about it, and trying not to go insane.

After awhile, when the argument seemed to have wound down, she said aloud, “Mr.~Potter’s Time-Turner is restricted to the hours of nine \PM through midnight. Was the shell tampered with, Albus?”

“Not to my most discerning Charms,” said Albus. “But the shells are new things; and to defeat the Unspeakables’ precautions and leave no trace of the defeat...\ might \emph{not} be impossible.”

She opened her eyes, and saw Severus and the Headmaster staring intently at a parchment covered with tangled squiggles that would have no doubt driven her mad to comprehend.

“Have you come to any \emph{conclusions?}” Minerva said. “And please don’t tell me how you arrived at them.”

Severus and the Headmaster looked at each other, then turned to look at her.

“We have concluded,” the Headmaster said gravely, “that either Harry was involved or he was not; that either Voldemort has access to a Time-Turner or he does not; and that regardless of what could have happened within Azkaban, nobody would have visited the Little Hangleton graveyard during the period Moody has already watched over it within my own past.”

“In short,” Severus drawled, “we know nothing, dear Minerva; though it seems at least \emph{likely} that another Time-Turner was involved, somehow. My own suspicion is that Potter has been bribed, tricked, or threatened into conveying messages backward in time, perhaps even regarding this very prison break. I shall not make the obvious suggestion as to who is pulling his strings. But I suggest that at nine o’ clock tonight, we test whether Potter is able to travel the full six hours backward to three o’ clock, to see if he has yet used his Time-Turner.”

“That seems wise to do in any case,” said Dumbledore. “See that done, Minerva, and tell Harry to stop in my office at his convenience, afterward.”

“But you still suspect Harry of direct involvement in the prison break itself?” Minerva said.

“Possible but unlikely,” said Severus, at the same time Albus said, “Yes.”

Minerva pinched the bridge of her nose, took a deep breath, let it out. “Albus, Severus, what possible \emph{reason} has Mr.~Potter to do such a thing!”

“None that I can think of,” said Albus, “but it remains that Harry’s magics alone, of all the means known to me, might have—”

“Hold,” said Severus. All expression vanished from his face. “A thought occurs to me, I must check—” The Potions Master seized a pinch of Floo powder, strode across the room toward the fireplace—Albus hastily waved his wand to light it—and then in a flare of green flame, and the words “Slytherin Head of House office”, Severus was gone.

She and Albus looked at each other and both shrugged; and then Albus turned back to studying the parchment.

It was only a few minutes later that Severus spun back out of the Floo, brushing traces of ash from himself.

“Well,” said the Potions Master. Again the expressionless face. “I am afraid that Mr.~Potter does have a motive.”

“Speak!” said Albus.

“I found Lesath Lestrange in the Slytherin common room, studying,” Severus said. “He was not reluctant to meet my eyes. And it seems that Mr.~Lestrange did not like to think of his parents in Azkaban, in the cold and the darkness, with the Dementors sucking away their life, hurting every second of every day, and he told Mr.~Potter so in as many words, and begged him to get them out. Since, you see, Mr.~Lestrange had heard that the Boy-Who-Lived could do anything.”

She and Albus exchanged glances.

“Severus,” Minerva said, “\emph{surely...} even \emph{Harry}...\ has more common sense than \emph{that...}”

Her voice trailed off.

“Mr.~Potter thinks he is God,” Severus said without expression, “and Lesath Lestrange fell to his knees before him in a heartfelt cry of prayer.”

Minerva stared at Severus, feeling sick to her stomach. She had studied Muggle religion—it was the most common reason for needing to Memory-Charm the parents of Muggleborns—and she knew enough to understand what Severus had just said.

“In any case,” said the Potions Master. “I looked within Mr.~Lestrange to see if he knew anything of his mother’s escape. He has heard nothing. But the instant he learns, he will conclude that the person responsible was Harry Potter.”

“I see...” Albus said slowly. “Thank you, Severus. That is good news.”

“\emph{Good news?}” Minerva burst out.

Albus looked at her, his face as expressionless as Severus’s, now; and she remembered, with a shock, that Albus’s own—“It is the best reason I can possibly imagine for removing Bellatrix from Azkaban,” Albus said quietly. “And if it is \emph{not} Harry, let us recall, then it is certainly Voldemort himself making his first moves. But let us not be hasty in judgment while there is much we do not yet know, but soon will.”

Albus once more stood up from behind his desk, strode to the fireplace still alight, cast in another pinch of green powder, and stuck his head into the flames. “Department of Magical Law Enforcement,” he said, “Director’s office.”

After a moment, the voice of Madam Bones came through clear and sharp, “What is it, Albus? I am somewhat busy.”

“Amelia,” said Albus, “I beg of you to share any discoveries you have made concerning this matter.”

There was a pause. “Oh,” said the cold voice of Madam Bones from the blazing fire, “and is that a two-way road then, Albus?”

“It may be,” the old wizard said calmly.

“If any Auror dies of your reticence, old meddler, I will hold you responsible in full measure.”

“I understand, Amelia,” Albus said, “but I have no wish to spark needless alarm and incredulity—”

“\emph{Bellatrix Black} has escaped from \emph{Azkaban!} What alarm or incredulity do you think I will call \emph{needless,} in the face of that?”

“I may call on you to remember those words,” said the old wizard into the green flames. “For if I learn that my fears are not needless, I \emph{will} tell you. Now, Amelia, I beg you, if you have learned anything whatsoever upon this matter, please share it.”

There was another pause, and then Madam Bones’s voice said, “I have information which I learned four hours into the future, Albus. Do you still want it?”

Albus paused—

(weighing, Minerva knew, the possibility that he might want to go back more than two hours from this instant; for you couldn’t send information further back in time than six hours, not through any chain of Time-Turners)

—and finally said, “Yes, please.”

“We had a lucky break,” said Madam Bones’s voice, “one of the Aurors who witnessed the escape was a Muggleborn, and she told us that the Flying-Fire spell, as we were calling it, might be no spell at all, but a Muggle artifact.”

Like a punch in the stomach, that was how it felt, and the sickness in Minerva’s belly redoubled. Anyone who’d watched a Chaos Legion battle knew whose hand that showed...

Madam Bones’s voice continued. “We brought in Arthur Weasley from Misuse of Muggle Artifacts—he knows more about Muggle artifacts than any wizard alive—and gave him the descriptions from the Aurors on the scene, and he cracked it. It was a Muggle artifact called a rocker, and they call it that because you’d have to be off your rocker to ride one. Just six years ago one of their rockers blew up, killed hundreds of Muggles in a flash and almost set fire to the Moon. Weasley says that rockers use a special kind of science called opposite reaction, so the plan is to develop a jinx which will prevent that science from working around Azkaban.”

“Thank you, Amelia,” Albus said gravely. “Is that everything?”

“I’ll check if we have anything from six hours forward,” said the voice of Madam Bones, “if so they wouldn’t have told me, but I’ll have them tell you. Do \emph{you} have anything you want to tell me, Albus? Which of those two possibilities is it looking like?”

“Not yet, Amelia,” Albus said, “but I may have word for you soon.”

He straightened up from the fire, then, which faded back to ordinary yellow flames. Every minute of the old wizard’s years, every natural second since his birth and every second which Time-Turning had added, all of that plus a few extra decades for stress, was visible on his lined face.

“Severus?” the old wizard said. “What was it actually?”

“A rocket,” said the half-blood Potions Master, who had grown up in the Muggle town of Spinner’s End. “One of the most impressive Muggle technologies.”

“How likely is \emph{Harry} to know such arts?” said Minerva.

Severus drawled, “Oh, a boy like Mr.~Potter knows \emph{all} about rockets; that, dear Minerva, is a certainty. You must remember that things are done differently in the Muggle world.” Severus frowned. “But rockets \emph{are} dangerous, and expensive...”

“Harry has stolen and hidden an unknown amount of money from his Gringotts vault, perhaps thousands of Galleons,” said the Headmaster, and then, to their twin stares, “That was \emph{not} in my plan, but I made the mistake of sending the Defense Professor to supervise Harry’s withdrawal of five Galleons for Christmas presents...” The Headmaster shrugged. “Yes, I agree, sheer folly in retrospect, let us continue.”

Minerva quietly thudded her head a few times against the headrest of her chair.

“Nonetheless, Headmaster,” Severus said. “Just because the Death Eaters never used Muggle artifacts in the first war, that does not mean \emph{he} is ignorant. Rockets fell on Britain as weapons, in the Muggle side of Grindelwald’s war. If he spent the summers of those years in a Muggle orphanage, as you told us, Headmaster...\ then he, too, has heard of rockets. And if he has been listening to reports of Mr.~Potter and his mock battles using Muggle artifacts, he would certainly learn his enemy’s strengths and try to redouble them himself. That is \emph{just} how he thinks; any power he sees he will try to take for his own.”

The old wizard was standing stock still, utterly motionless, even the hairs of his beard frozen in place like solid wires; and the thought came to Minerva, as frightening as any thought she’d ever had, that Albus Dumbledore was rooted to the spot in horror.

“Severus,” Albus Dumbledore said, and his voice almost cracked, “do you realize what you are saying? If Harry Potter and Voldemort fight their war with Muggle weapons there will be nothing left of the world but fire!”

“\emph{What?}” said Minerva. She had heard of guns, of course, but they weren’t \emph{that} dangerous to an experienced witch—

Severus spoke as though she weren’t in the room. “Then perhaps, Headmaster, he is sending a deliberate warning to Harry Potter of exactly that; saying that any attack with Muggle weapons will be met with retaliation in kind. Command Mr.~Potter to cease his use of Muggle technology in his battles; that will show him the message is received...\ and not give him any more ideas.” Severus frowned. “Though, come to think of it, Mr.~Malfoy—and of course Miss Granger—well, on second thought a blanket prohibition on technology seems wiser—”

The old wizard pressed both his hands to his forehead, and from his lips came an unsteady voice, “I begin to \emph{hope} that it is Harry behind this escape...\ oh, Merlin defend us all, what have I done, what have I done, what will become of the world?”

Severus shrugged. “From the rumors I have heard, Headmaster, Muggle weapons are only slightly worse than the more... \emph{recondite} aspects of wizardry—”

“\emph{Worse?}” gasped Minerva, and then shut her mouth as though by force.

“Worse than any peril I know,” said Albus. “But probably not worse than whatever erased Atlantis from Time.”

Minerva stared at him, feeling the sweat break out all along her spine.

Severus continued, still addressing Albus. “All the Death Eaters save Bellatrix would have betrayed him, all his supporters turned against him, all the powers of the world converged to destroy him, if he had been reckless with any truly dangerous potency. Is this so different, then?”

Some motion, some color, had returned to the old wizard’s face. “Perhaps not...”

“And in any case,” Severus said with a slightly condescending smile, “Muggle weapons are not so easy to obtain, not for a thousand Galleons or a thousand thousand.”

\emph{Doesn’t Harry just Transfigure the devices he uses in his battles?} thought Minerva, but before she could open her mouth to ask—

The fireplace erupted in green flames, then, and the face of Pius Thicknesse, Madam Bones’s assistant, appeared therein. “Chief Warlock?” said Thicknesse. “I have a report for you, transmitted from—” Thicknesse’s eyes flickered over Minerva and Severus, “six minutes ago.”

“Six hours ahead, you mean,” said Albus. “These two are meant to hear it; deliver your report.”

“We know how it was done,” said Thicknesse. “In Bellatrix Black’s cell, hidden in one corner, was a potions vial; and testing the traces of remaining fluid shows that it was an Animagus potion.”

There was a long pause.

“I see...” Albus said heavily.

“Pardon me?” said Minerva. She didn’t.

Thicknesse’s head turned toward her. “Animagi, Madam McGonagall, in their Animagus forms, are of less interest to Dementors. All prisoners are tested before their arrival at Azkaban; and if they are Animagi, their Animagus form is destroyed. But we had not considered that someone protected by a Patronus Charm while taking the potion and performing the meditation, might be able to become an Animagus \emph{after} they went to Azkaban—”

“I understood,” Severus said, having by now put on his customary sneer, “that the Animagus meditation required considerable time.”

“Well, Mr.~Snape,” Thicknesse barked, “records show that Bellatrix Black was an Animagus \emph{before} she was sentenced to Azkaban and her form destroyed; so maybe her \emph{second} meditation didn’t take as much time as her first!”

“I would not have thought it possible for any prisoner of Azkaban to do such a thing...” Albus said. “But Bellatrix Black was a most powerful sorceress before her incarceration, and she might have done it if any witch could. Can Azkaban be secured against this method?”

“Yes,” said the confident head of Pius Thicknesse. “Our expert says that it is nigh-unimaginable that an Animagus meditation could be performed in less than three hours, regardless of experience. All visits to prisoners allowed to receive them will be limited to two hours henceforth, and the Dementors will inform us if any Patronus Charm is maintained in the prison areas for longer than that.”

Albus looked unhappy at that, but nodded. “I see. There will be no further attempts of that sort, of course, but do not relax your vigilance. And when Amelia has been told all this, tell her that I have information for her.”

The head of Pius Thicknesse vanished without another word.

“No further attempts...?” said Minerva.

“Because, dear Minerva,” Severus drawled, having not quite taken off his habitual sneer, “if the Dark Lord had planned to free any of his other servants from Azkaban, he would not have left behind the vial of potion to tell us how it was done.” Severus frowned. “I confess...\ even so I do not see why that vial was left there.”

“It is some kind of message...” Albus said slowly. “And I cannot see what it means, not at all...” He drummed his fingers on his desk.

For a long minute or three, the old wizard stared off into nothingness, frowning; while Severus also sat in silence.

Then Albus shook his head in dismay, and said, “Severus, do \emph{you} comprehend this?”

“No,” said the Potions Master, and with a sardonic smile, “which is probably all the better for us; whatever we are \emph{intended} to conclude from it, that part of his plan has misfired.”

“You are certain, now, that it \emph{is} You-Know...\ that it is Voldemort?” said Minerva. “It could not be that some other Death Eater conceived this clever notion?”

“And they knew about rockets, too?” Severus said dryly. “I don’t believe the other Death Eaters were so fond of Muggle Studies. It is he.”

“Aye, it is he,” Albus said. “Azkaban has endured impenetrable for ages, only to fall to an ordinary Animagus potion. It is too clever and too impossible, which was ever Voldemort’s signature since the days he was known as Tom Riddle. Anyone who wished to forge that signature must needs be as cunning as Voldemort himself to do so. And there is no one else in the world who would accidentally overestimate my wit, and leave me a message I cannot understand at all.”

“Unless he has gauged you exactly,” Severus said tonelessly, “in which case all that is just what he intended you to think.”

Albus sighed. “Indeed. But even if he has tricked me perfectly, we may at least rely on the conclusion that it was not Harry Potter.”

It should have come as a relief, and yet Minerva felt the chill spreading through her spine and her veins, her lungs and her bones.

She remembered conversations like this.

She remembered conversations like this from ten years ago, from a time when blood had run through Britain in wide rivers, when wizards and witches she had once taught in class had been slaughtered by the hundreds, she remembered burning homes and screaming children and flashes of green light—

“What will you tell Madam Bones?” she whispered.

Albus stood from his desk and paced to the center of the room, his hand lightly touching the devices, here an instrument of light, there an instrument of sound; he adjusted his glasses with one hand, used the other to center the long silver beard against his robes, and then finally that ancient wizard turned back and faced them.

“I will tell her what little I know of the Dark Art called horcrux, by which a soul is deprived of death,” said Albus Dumbledore, in a soft voice that seemed to fill the whole room, “and I will tell her what may be done with the flesh of the servant.”

“I will tell her that I am reconstituting the Order of the Phoenix.”

“I will tell her that Voldemort has returned.”

“And that the Second Wizarding War is begun.”
\sbreak
\emph{Some hours later...}

The antique old clock upon the wall of the Deputy Headmistress’s office had golden hands, and silver numerals to make the clock-face; it ticked and jerked soundlessly through its motions, for there was a Quieting enchantment on it.

The golden hour hand approached the silver numeral of nine, the golden minute hand did the same, the two linked components of Time nearing each other, soon to be in the same place and never to collide.

It was 8:43\PM, and the time approached when Harry’s Time-Turner would open, to be tested in the one way that no imaginable spell could fool, unless that spell could bypass the laws of Time itself. No body or soul, no knowledge or substance, could stretch an extra seven hours in a single day. She would make up a message on the spot, and tell Harry to take that message back six hours to Professor Flitwick at 3\PM, and she would ask Professor Flitwick if he had received it in that hour.

And Professor Flitwick would tell her that he had indeed received it at 3\PM.

And she would tell Severus and Albus to have a \emph{little} more faith in Harry next time.

Professor McGonagall cast the Patronus Charm, and told her shining cat, “Go to Mr.~Potter, and tell him this: Mr.~Potter, please come to my office as soon as you hear this, without doing anything else along the way.”

