\chapter{Tests}

\subsection{June 4th, 1992.}

\lettrine{D}{aphne} Greengrass was in the Slytherin common room, writing a letter to her
Lady Mother (who was surprisingly intransigent about power-sharing, despite not
even \emph{being} in Hogwarts to exercise control) when she saw Draco Malfoy
stagger in through the portrait door carrying what must have been a dozen
books, Vincent and Gregory behind him each carrying a dozen more. The Auror
who'd accompanied Malfoy stuck his head in briefly, then withdrew to
who-knew-where.

Draco looked around, then seemed to be struck by a bright idea as he staggered
toward her, Vincent and Gregory following after.

"Can you help me read these?" said Draco, sounding slightly out of breath as he
approached.

"What." Lessons were over, only the exams were left now, and since when
did \emph{Malfoys} ask \emph{Greengrasses} for help with their homework?

"These," Draco Malfoy said importantly, "are all the library books Miss Granger
borrowed between April 1st and April 16th. I thought I'd go through them in
case there are any Clues there, only then I thought, maybe \emph{you} should
help because you knew Miss Granger better."

Daphne stared at the books. "The General read all that in \emph{two weeks?}" A
twinge of pain went through her heart, but she suppressed it.

"Well, I don't know if Miss Granger finished them all," Draco said. He held up
a cautioning finger. "In fact, we don't know if she read any of them, or if she
really borrowed them, I mean, all we've \emph{observed} is that the library
ledger says she checked them out---"

Daphne suppressed a groan. Malfoy had been talking like this for weeks. There
were some people who clearly were not meant to be involved with mysterious
murders because it did \emph{strange things to their minds}. "Mr.~Malfoy, I
couldn't read all these if I spent my whole summer doing nothing else."

"Then just skim through them, please?" Draco said. "Especially if there's, you
know, mysterious words scribbled in her handwriting, or a bookmark left inside,
or---"

"I've seen those plays too, Mr.~Malfoy." Daphne rolled her eyes. "Don't we have
\emph{Aurors} now for---"

"\emph{We're doomed!}" shrieked Millicent Bulstrode, as she burst up from the
lower chambers into the Slytherin common room.

People paused to look at her.

"\emph{It's Professor Quirrell!}"

A sudden air of attentiveness, as of long-standing disputes about to be
settled. "Well, finally," someone said, as Millicent tried to catch her breath.
"He's only got, what, ten days left to go bad?"

"Eleven days," said the seventh-year who was running the betting pool.

"\emph{He's gotten a little better suddenly and he's going to summon the
first-years for our Defense final! By surprise! In fifty minutes!}"

"A Defense final?" Pansy said blankly. "But Professor Quirrell doesn't give
exams."

"The \emph{Ministry} Defense final!" shrieked Millicent.

"But Professor Quirrell doesn't teach anything from the Ministry curriculum,"
objected Pansy.

Daphne was already fleeing to her room, racing for the first-year Defense
textbook that she hadn't touched since September and screaming curses inside
her mind.
\sbreak
One desk back of her, someone was crying, their soft sobs providing a
background chant of despair for the classroom. Daphne looked back, expecting to
see a Hufflepuff and hoping it wasn't Hannah, and was surprised at first
(though not on further reflection) to see it was a Ravenclaw.

Before them were set the exam parchments, turned over, waiting for the bell.

Fifty minutes hadn't been nearly enough preparation time, but it was something,
and Daphne was now feeling ashamed that she hadn't thought to send messengers
to warn the Hufflepuff, Ravenclaw, and Gryffindor Houses. They'd started giving
House Points again just three days ago, at the beginning of June, but the
Auxiliary Protective Special Committee still ought to promote House unity.

Another Ravenclaw, sitting four desks to her left, also started to cry. That
was Katherine Tung of Dragon Army, if she recalled correctly, whom she'd once
seen take on three Sunshine Soldiers simultaneously without a flinch.

Daphne had calmed down after the first couple of minutes of frantic reading. It
was just a test, not a \emph{murder} or anything; and if almost all the
first-year students turned in mostly blank parchments then it stood to reason
that nobody would be shamed. But Daphne could understand, if not exactly
sympathize, that Ravenclaws and Hufflepuffs might not see it that way.

"He's evil," another Ravenclaw witch said in a shaking voice. "One hundred
percent pure Dark Wizard to the bone. The Dark Lord Grindelwald wouldn't do
this, not to children, he's worse than You-Know-Who."

Daphne looked reflexively at where Professor Quirrell was sitting, slumped to
one side but his eyes alert; and she thought she saw the Defense Professor
smile for one tiny instant. No, that had to be her imagination, there was no
way the Defense Professor could have heard that.

The bell rang.

Daphne flipped the parchment over.

The top was stamped with the seals for the Ministry, the Hogwarts Board of
Governors, and the Department of Magical Education, and runes to detect
cheating. Below that was a line for her to write her name, and a list of exam
rules with a picture of Lindsay Gagnon, the Director of the Department of
Magical Education, shaking an admonishing finger at everyone.

Halfway down the page was the first exam question.

It was, \emph{Why is it important for children to stay away from strange
creatures?}

There was a stunned pause.

One student began laughing, she thought it was from the Gryffindor section of
the class. Professor Quirrell made no motion to censor it, and the laughter
spread.

Nobody spoke aloud, but the students looked around at each other, exchanging
glances as the laughter died down, and then as if by some unspoken agreement
they all looked at Professor Quirrell, who was smiling down at them
benevolently.

Daphne bent over her exam, wearing a defiant evil smile that would have done
proud to either Godric Gryffindor or Grindelwald; and she wrote down,
\emph{Because my Stunning Hex, my Most Ancient Blade, and my Patronus Charm
won't work against everything.}
\sbreak
Harry Potter turned over the last page of his Defense exam.

Even Harry had needed to quash a small bit of nervousness, some tiny remnant of
his childhood, upon reading the first real question (`How can you make a
Shrieking Eel be silent?'). Professor Quirrell's lessons had spent roughly zero
time on the surprising yet useless trivia that some idiot had imagined a
`Defense class' should look like. In principle, Harry could have used his
Time-Turner to read through the first-year Defense book after being notified of
the surprise exam; but that might have unfairly skewed the grading curve for
others. After staring at the question for a couple of seconds, Harry had
written down `Quieting Charm', and included the casting directions in case the
Ministry grader didn't believe that Harry knew it.

Once Harry had decided to just answer all the questions \emph{correctly,} the
exam had gone by very quickly. The most realistic answer to more than half the
questions was `Stunning Hex', and many of the other questions had optimal
solutions along the lines of `Turn around and walk in the opposite direction'
or `Throw away the cheese and buy a new pair of shoes.'

The last question on the test was "What would you do if you suspected there
might be a Bogeysnake underneath your bed?" The Ministry-approved answer, Harry
could in fact recall from his read-through of the textbook at the start of the
year, was \emph{Tell your parents.} The problem with this had occurred to Harry
right away, which was why Harry had remembered it.

After some pondering, Harry wrote down:

\emph{Dear Ministry grader: I'm afraid the real answer to that is a secret, but
rest assured that a Bogeysnake would present no more trouble to me than a
mountain troll, a Dementor, or You-Know-Who. Please inform your superiors that
I find your standard answer prejudicial to Muggleborns, and that I expect this
failing will be corrected at once without any need for my direct intervention.}

\emph{Sincerely, the Boy-Who-Lived.}

Harry signed the last parchment with a broad flourish, turned it over into his
stack, put down his quill, and sat up.

Looking around, Harry saw that Professor Quirrell seemed to be looking in his
rough direction, though the Defense Professor's head had nodded to one side.
The other students were still writing. Some of them were silently crying, but
they were still writing. \emph{Continuing to fight} was also a lesson Professor
Quirrell had taught.

Interminably later, the official exam time was up. A seventh-year student went
from desk to desk, collecting the exams in Professor Quirrell's place.

The last exam parchment was collected, and Professor Quirrell sat up straight.

"My young students," he said softly. The seventh-year student had her wand
trained on the Defense Professor's mouth, so that they all heard his voice
seeming to come from right beside them. "I know{\ldots} that probably seemed
very fearsome to some of you{\ldots} it is a different kind of fear from facing
the enemy's wand{\ldots} you must conquer it separately. So I{\ldots} shall
tell you this now. It is the custom of Hogwarts{\ldots} that grades are given
in the second week of June. But for my case{\ldots} they can make an exception,
I think." The Defense Professor smiled his familiar dry smile, tinged now as
though by a suppressed grimace. "I know you are worried{\ldots} that you were
not prepared for this exam{\ldots} that my lessons have not covered this
material{\ldots} and I quite forgot to mention{\ldots} that it was
approaching{\ldots} though you should have known{\ldots} it would come in time.
But I have just now magically checked{\ldots} the answers you have given on
that{\ldots} terribly, terribly important final exam{\ldots} though of course
only the Ministry grade is official{\ldots} and assigned your full-year grades
taking the results into account{\ldots} and magically written your full grades
down on these parchments," Professor Quirrell tapped a stack of parchments on
the side of his desk, "which will now be handed out{\ldots} an incredible
spell{\ldots} is it not?"

A few students on the Ravenclaw side were looking indignant, but for the most
part the students just looked relieved, and some Slytherins were chuckling.
Harry would have laughed too, if not for the pain of watching Professor
Quirrell gasp out the words.

The seventh-year student standing beside Professor Quirrell pointed her wand
and spoke an incantation in magical pseudo-Latin. The parchments rose up and
started to drift through the air, separating in mid-flow to drift toward each
student.

Harry waited until his parchment had arrived on his desk, and then unfolded it.

The parchment said EE+, which stood for Exceeds Expectations. It was the
second-highest grade letter, the highest being Outstanding.

In another world, a distant vanished world, a little boy named Harry would have
shouted with indignation about receiving only the second-highest grade. This
Harry sat quietly and thought. Professor Quirrell was making some point, and it
wasn't as though the exact grade letter mattered in any other way. Was
Professor Quirrell saying that Harry had done relatively well, but not lived up
to his full potential? Or was the grade meant to be read literally, that Harry
had in fact exceeded the Defense Professor's expectations?

"All of you{\ldots} pass," Professor Quirrell said, as the students all looked
at their final grades, as sighs of relief rose from desks and Lavender Brown
raised her parchment in a clenched fist held high with triumph. "Every student
in first-year Battle Magic has passed{\ldots} except for one."

A number of students looked up in sudden terror.

Harry sat there silently. He had seen the point immediately, and even if it was
a wrong point, he knew Professor Quirrell would never, ever be talked out of
making it.

"All of you in this room{\ldots} have received grades of at least Acceptable.
Neville Longbottom{\ldots} who took this test in the Longbottom home{\ldots}
received a grade of Outstanding. But the other student who is not here{\ldots}
has had a Dreadful grade entered on her record{\ldots} for failing the only
important test{\ldots} that was given her this year. I would have marked her
even lower{\ldots} but that would have been in poor taste."

The room was very quiet, though a number of students were staring angrily at
the Professor.

"You may think that a grade of Dreadful{\ldots} is not fair. That Miss Granger
was faced with a test{\ldots} for which her lessons{\ldots} had not prepared
her. That she was not told{\ldots} that the exam was coming on that day."

The Defense Professor drew in a shaking breath.

"Such is realism," said Professor Quirrell. "The only important test{\ldots}
may come at any time{\ldots} be better prepared for it{\ldots} than she was. As
for the rest of you{\ldots} those who have received Exceeds Expectations or
above{\ldots} have received my letters of recommendation{\ldots} to certain
organizations beyond Britain's shores{\ldots} where your training might be
completed. They will contact you{\ldots} when you are old enough{\ldots} if you
still appear worthy{\ldots} and if you have not failed an important test. And
remember{\ldots} from this day{\ldots} you must train yourselves{\ldots} you
cannot rely{\ldots} on future Defense professors. Your first year of Battle
Magic is over{\ldots} you are dismissed."

Professor Quirrell sat back with his eyes closed, seeming to ignore the excited
babble that broke out around him.

In time most of the students had departed, and one remained, staying a
prescribed distance from the Defense Professor.

The Defense Professor opened his eyes.

Harry raised the parchment with its \emph{EE+,} still silent.

The Defense Professor smiled, and it went all the way to those tired eyes.

"It is the same grade{\ldots} that I received in my own first year."

"Th, th, th," Harry couldn't make the words \emph{thank you} come out, they
were stuck in his suddenly closed throat, the Defense Professor tilting his
head and giving him an inquiring stare, so Harry just bowed jerkily and then
left the room.

Nine days yet remained.
